### 2012-07-01 doc/acknowledgments.tex
Started reconstruction paper

TJC acknowledges support from STFC in the form of a research studentship.
%
PJM was given support by the TABASGO and Kavli foundations, and the Royal 
Society, in the form of research fellowships.
%
MWA \ldots. SH \ldots. SHS \ldots.
%
TT acknowledges support from the NSF through CAREER award NSF-0642621,
and from the Packard Foundation through a Packard Research Fellowship.
% 
LVEK acknowledges the support by an NWO-VIDI programme subsidy
(programme number 639.042.505).
%
This research is supported in part by the National Science Foundation under
Grant No. PHY99-07949.

### 2012-07-01 doc/addresses.tex
Started reconstruction paper

\def\ioa{Institute of Astronomy, University of Cambridge,
  Madingley Rd, Cambridge, CB3 0HA, UK}
\def\oxford{Dept.\ of Physics, University of Oxford, 
  Keble Road, Oxford, OX1 3RH, UK}
\def\kipac{Kavli Institute for Particle Astrophysics and Cosmology, 
 Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA}
\def\ucsb{Dept.\ of Physics, University of California, 
  Santa Barbara, CA 93106, USA}
\def\davis{Dept.\ of Physics, U.C.~Davis, Davis, CA 95616, USA}
\def\kapteyn{Kapteyn Astronomical Institute, University of Groningen, 
  P.O.Box 800, 9700 AV Groningen, The Netherlands}

\def\collettemail{\tt t.collett@ast.cam.ac.uk}

\def\packard{Packard Research Fellow}

### 2012-07-01 doc/paper-lcr.tex
Started reconstruction paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Pangloss: Testing the reconstruction paper
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[useAMS,usenatbib]{mn2e}
%% letterpaper
%% a4paper

% \voffset=-0.8in

% Packages:
\input psfig.sty
\usepackage{xspace}
\usepackage{graphicx}

% Macros:
\input{macros.tex}
\input{addresses.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[Line of Sight Mass Reconstruction]
{Inferring Lensing Mass in the Universe from Photometric Catalog Data}

\author[Collett \etal]{%
  Thomas~J.~Collett$^{1}$\thanks{\collettemail},
  Philip~J.~Marshall$^{2}$,
  Matthew~W.~Auger$^{1}$,
  Stefan~Hilbert$^{3}$,
\newauthor{%
  Sherry~H.~Suyu$^{4}$,
  Zachary~Greene$^{4}$,
  Tommaso~Treu$^{4}$\thanks{\packard},
  Christopher~D.~Fassnacht$^{5}$,}
\newauthor{%
  L\`eon~V.~E.~Koopmans$^{6}$,
  Roger~D.~Blandford$^{3}$} 
  \medskip\\
  $^1$\ioa\\
  $^2$\oxford\\
  $^3$\kipac\\
  $^4$\ucsb\\
  $^5$\davis\\
  $^6$\kapteyn
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\date{to be submitted to MNRAS}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2012}

\maketitle

\label{firstpage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}

Strong gravitational lenses can provide high precision cosmological distance
measurements; one of the most important sources of systematic error in these
estimates is the additional mass along the line of sight to the source. Weak
lensing by galaxies and groups in this beam can contribute an ``external
convergence'' $\xkappa$ that dominates the  uncertainty in the inferred
distances; likewise, it may also contaminate estimates of the luminosity of
objects at high redshift (such as reionisation-era proto-galaxies, and type Ia
supernovae standard candles).  We characterise this uncertainty by marginalising
over a probability density function for $\xkappa$: here, we investigate the use
of a simple halo model to estimate $\Pr(\xkappa)$ given noisy estimates of the
photometric redshift and stellar mass of galaxies observed in optical imaging
surveys of the field in question. Tests using mock catalogs from the Millenium
Simulation and comparing to ray-traced $kappa$ values, we find that \ldots 
The $\Pr(\xkappa)$ from this reconstruction process are narrower than the
expected distribution of $\xkappa$ values over an ensemble of time delay lenses:
incorporating the photometric catalogs in a joint analysis of 100 lenses 
leads to an increase in precision of factor of 1.X over simple averaging. We
investigate several sources of bias and determine \ldots
\end{abstract}

% Full list of options at http://www.journals.uchicago.edu/ApJ/instruct.key.html

\begin{keywords}
  gravitational lensing   --
  methods: statistical    --
  galaxies: halos         --
  gaaxies: mass function  --
  cosmology: observations
\end{keywords}

\setcounter{footnote}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

What is the problem - reconstructing kappa. Why is this problem relevant? Time
delay distances. Magnification.

Previous work on environments: Auger, Momcheva,
others. Hilbert et al.'s raytracing plus Fassnacht \& Koopmans density, Suyu et
al's kappa pdf.

Why these approaches may be insufficient - information provided in
future surveys.

Questions asked in this paper:
How much of the total external convergence in a time delay lens system comes from visible galaxies? How does this change as a function of magnitude cut?
Where are the most important galaxies? Do the massive galaxies dominate, or is it the the galaxies nearest the optical axis, or some combination of these? How many galaxies account for 50%, and 95% of the convergence on a typical line of sight?
Can the Hilbert (ray-traced) convergence be recovered by halo model lightcone reconstruction? With what scatter and bias? Which recipes are the dominant sources of these uncertainties?

This paper is organized as follows. \Sref{sec:}.

Throughout this paper magnitudes are given in the AB system \citep{Oke74} and
we adopt standard ``concordance'' parameters for our reference cosmology, \ie
$h=0.7$, $\Omega_m=0.3$ and $\Omega_\Lambda=0.7$, where the symbols indicate
the Hubble Constant in units of 100 km s$^{-1}$ Mpc$^{-1}$ and the matter and
dark energy density of the Universe in units of the critical density
\citep[e.g.\ ][]{Kom++09}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Theoretical Background}
\label{sec:theory}

Time delay distances, and the mass sheet degeneracy - how kappa is degenerate in
strong lens models (and magnifications). Weak lensing by NFW halos. Accounting
for mass along the line of sight.  Approximations to full ray tracing: combining
kappas: simple sum, Keeton scaling, comments. Example ray traced kappa map from Stefan.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Halo Model}
\label{sec:model}

Halos. N-body sims provide mass framework. MS halo catalog. Truncated spherical
NFW approx based on virial masses. Stellar mass. Halo map corresponding to
ray-traced kappa map, for illustration. Small-scale structure

Not all DM is in halo catalog. Smooth component approximation.  How voids
produce a negative kappa - filled beam distances require halos and voids to
provide density contrast relative to mean. How we correct for voids. Comments on
reasonable, but unphysical nature of this approach, tests to follow.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Tests with known halo mass and redshift}
\label{sec:}

Raytracing through n-body particles as 'truth'. Motivation for assuming perfect
knowledge of halo mass and z = testing model of previous section. Deterministic
prediction of kappa.

Is truncation choice important? How deep and wide does a reconstruction need to
go? What is the irreducible uncertainty on kappa from this halo model? (Bias and
scatter) Can use the ideal reconstruction to ask: Where does the kappa come
from? Close to the LoS? Bright objects? How many objects are important? What
error is made by considering subsets of available objects?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Tests on mock catalogs}
\label{sec:}

Consider three sources of scatter in the halo model: zphot, Mstar|zphot, and
Mhalo|Mstar,zphot. Mechanism for including scatter in model: draw samples from
PDFs. Result is not one predicted kappa, but one P(kappa) for each lightcone.
This is what is required by single-lens analyses.

We can draw samples from this PDF and ask:

How is the kappa inference offset and blurred by uncertainty on redshift, Mstar
and Mhalo?

What is the effect of using the wrong Mstar-Mhalo relation?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Time Delay Distances}
\label{sec:}

Folding the kappa uncertainties into time delay distance uncertainties. Toy
model: same zl and zs, allows simple product of pdfs to obtain estimate of P(D).

What is the expected bias and scatter (centroid position and width) of P(D) as a
function of N lenses? How does reconstruction compare with P(D) derived using
P(kappa|N45) for each lightcone? How does reconstruction compare with P(D)
derived assuming kappa=0 for each lightcone?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Discussion}
\label{sec:}

Why reconstruction works or doesn't work
Major sources of uncertainty
Ideas for improving the procedure

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{}
\label{sec:}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{figure}
% \centering\includegraphics[width=0.99\linewidth]{figs/something.png}
% \caption{An example figure.}
% \label{fig:sizemass}
% \end{figure}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{}
\label{sec:}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Summary}
\label{sec:summary}

Our conclusions can be summarised as follows:

\begin{itemize}

\item We found this.

\item And we found this too.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Acknowledgments}

We thank Risa Wechsler and Peter Behroozi for useful discussions and 
suggestions.
\input{acknowledgments.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  APPENDICES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Truncated \LCDM halos}
\label{appendix:halos}

\section{Deriving the $\Mstar=\Mhalo$ relation}
\label{appendix:MSMH}

\section{Smooth component models}
\label{appendix:smooth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  REFERENCES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% MNRAS does not use bibtex, input .bbl file instead. 
% Generate this in the makefile using bubble script in scriptutils:

% bubble -f paper-lcr.tex references.bib 
% \input{paper-lcr.bbl}

\bibliographystyle{apj}
\bibliography{references}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\label{lastpage}
\bsp

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2012-07-01 doc/paper-lcr.tex
finished introduction draft

@@
 \title[Line of Sight Mass Reconstruction]
-{Inferring Lensing Mass in the Universe from Photometric Catalog Data}
+{Inferring Lensing Mass in the Universe \\
+from Photometric Catalog Data}
 
@@
 
-What is the problem - reconstructing kappa. Why is this problem relevant? Time
-delay distances. Magnification.
+Averaged over large areas of sky, the weak gravitational lensing effect can be
+used to constrain the statistical properties of the matter density in the
+Universe: every distant object we observe has had its shape distorted, and size
+and total brightness magnified (or demagnified) by a compound lens constructed
+from all the mass distributed between us and it.
 
-Previous work on environments: Auger, Momcheva,
-others. Hilbert et al.'s raytracing plus Fassnacht \& Koopmans density, Suyu et
-al's kappa pdf.
+This fact makes gravitational lensing a potentially important source of
+systematic error for any estimate of luminosity or distance, an issue addressed
+for \eg type Ia supernovae by \citet[][]{Holz+Wald,Linder+Holz} and for high
+redshift galaxies by \citet{Loeb} among others. In time delay lens cosmography
+the effect can be particularly important. \citet{Suyu2010} found that  the
+lensing effect of mass structures along the (unusually over-dense)  line of
+sight to the quadruply-imaged radio source B1608$+$656, the so-called ``external
+convergence,'' was the dominant source of uncertainty in the inferred
+cosmological parameters.
 
-Why these approaches may be insufficient - information provided in
-future surveys.
+How can we correct for the line of sight lensing error, and make accurate
+measurements through the Universe? As \citeauthor{LH} noted, when inferring
+global quantities (such as the cosmological parameters), averaging the results
+from a large number of independent objects will tend to reduce the error, as the
+ensemble-averaged convergence approaches zero for an unbiased sample
+\citep{xxx}. If the sample is biased, however, some residual systematic error
+will remain while the statistical uncertainty decreases -- and this will be the
+case for any sample selected by the brightness of the lensed object, or any
+other quantity that depends on $\xkappa$. The latter class includes time delay
+lenses, which are detected based on the separation of their images, which
+increases with $\kappa$. Large samples of lenses are expected to be discovered
+in the next decade in ground-based optical imaging surveys
+\citep{Oguri+Marshll2010} -- but these samples will be image separation-limited,
+due to the surveys' relatively poor ($\sim 1$~arcsec) image quality. Some of the
+current sample of known time delay lenses were detected in surveys like this: we
+might expect them to be somewhat biased towards high values of $\xkappa$.
 
-Questions asked in this paper:
-How much of the total external convergence in a time delay lens system comes from visible galaxies? How does this change as a function of magnitude cut?
-Where are the most important galaxies?
-Do the massive galaxies dominate, or is it the the galaxies nearest the optical axis, or some combination of these?
-How many galaxies account for 50%, and 95% of the convergence on a typical line of sight?
-Can the Hilbert (ray-traced) convergence be recovered by halo model lightcone reconstruction? With what scatter and bias? Which recipes are the dominant sources of these uncertainties?
+There are two broad approaches one could take at this point. First, one could
+seek to characterise the lensed objects' selection function, and use this
+understanding to derive a suitable correction to cosmological parameters
+inferred assuming no $\xkappa$ at all. To do this, one needs information about
+the unlensed population of objects, and the population of lenses, and how the
+objects were detected -- or to infer these hierarchically during the analysis.
+Alternatively, one could simply accept all lenses provided, regardless of their
+selection, and try to use any additional information that is available to
+estimate the external convergence in each system on a case by case basis, and
+hence optimize their joint analysis to produce a better-constrained result. In
+this work we follow the second approach, and use measurements of the positions,
+magnitude and colours of galaxies close to time delay lens lines of sight to try
+to infer the external convergence at the lens position.
 
-This paper is organized as follows. \Sref{sec:}.
+The first attempts at reconstructing the line of sight mass distribution in
+strong lens fields were \ldots. \flag{More needed here. Previous work on
+environments: Keeton, Zabludoff, Auger, Momcheva, Wong, others. Spectroscopic
+surveys, modelling mass along line of sight.}
+
+These observational investigations provided useful insight into the problem. 
+Coming from the opposite direction, \citet{Hilbert++2009} performed ray-tracing
+experiments through the Millenium Simulation, generating a predicted $\xkappa$
+at every position in a simulated sky. The first step towards using this
+excellent calibration resource was taken by \citet{Suyu++2010}, who selected
+Millenium lines of sight that a) were found to contain a strong lens and b) had
+comparable apparent galaxy overdensity in a 45 arcsec radius aperture down to $i
+< 24$. This overdensity could be compared to the overdensity of the B1608$+$656
+line of sight \citep{Fass+Koop2010}, and hence an estimate of the probability
+density function (PDF) $\Pr(\xkappa)$ could be made. This PDF is the key
+quantity for any ensemble analysis, since by marginalising over it we can
+correctly propagate the uncertainties due to weak lensing by line of sight mass
+structure.
+
+In this paper we use the Millenium Simulation mock galaxy catalogs and
+ray-traced lensing effects to test the accuracy of line of sight mass
+reconstructions. Probabilistically ssigning mass and redshift to every observed
+galaxy in the field around a time delay lens, we generate Monte Carlo sample
+line of sight mass distributions, and estimate the external convergence due to
+each one. This gives us a $\Pr(\xkappa)$ that can be propagated into further
+joint inferences. We focus on time delay lens cosmography, and quantify our
+results in terms of the uncertainty on the mean time delay distance to a test
+sample of $N$ lenses (where for clarity each lens has the same deflector and
+source redshift, and the same lens model and time delay uncertainty).
+
+We aim to answer the following questions:
+\begin{itemize}
+\item Faint galaxies and other dark structures will not appear in a photometric
+object catalog, but they will contribute convergence at some level. How much of
+the total external convergence in a time delay lens system comes from visible
+galaxies? How does this change as a function of magnitude cut? 
+\item Can the true (ray-traced) convergence be recovered by halo model
+reconstruction? What scatter and residual bias are induced in the ensemble 
+distance estimate? Which aspects of the model dominate these uncertainties? 
+\item When faced with a newly-detected lens, surrounded by galaxies on the sky,
+we have some choices to make when planning follow-up observations.
+Which are the most important galaxies, with regard to the external convergence
+produced? Can nearby groups and clusters be straightforwardly accounted for? If
+lenses with such massive structures nearby are discarded, what impact does that
+have on the distance accuracy?
+\end{itemize}
+
+This paper is organized as follows. In~\Sref{sec:theory} we review the relevant
+gravitational lensing theory, before introducing our simple reconstruction 
+model in \Sref{sec:model}.  We then test this model in two phases: first, in
+\Sref{sec:knownMh+z}, with known redshift and halo mass for every galaxy in a
+lens field, in order to quantify the irreducible uncertainty due to unseen mass,
+and second, in \Sref{sec:obsMstar+z}, with realistic observational uncertainties
+on the field galaxies' stellar masses and redshifts. We then propagate all these
+uncertainties through to the time delay distance in a toy sample of 100 lenses,
+in \Sref{sec:distances}. We discuss our results in \Sref{sec:discuss} before
+concluding in \Sref{sec:conclude}.
 
@@
 \section{Tests with known halo mass and redshift}
-\label{sec:}
+\label{sec:knownMh+z}
 
@@
 \section{Tests on mock catalogs}
-\label{sec:}
+\label{sec:obsMstar+z}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Also: compare with simple averaging. This will fail if lenses are selected to
+live on over-dense lines of sight. Stefan's plot in Suyu et al shows effect of
+selection - what is the resulting bias? Few percent? This is the target to beat,
+need to find it out.
 
-\section{Discussion}
-\label{sec:}
-
-Why reconstruction works or doesn't work
-Major sources of uncertainty
-Ideas for improving the procedure
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{}
-\label{sec:}
+Make mock sample of lenses, all wit B1608 zd and zs, but with different kappas.
+Draw kappas from Stefan's *lens* distribution. Can we correct for the selection
+effect?
 
@@
 
-\section{}
-\label{sec:}
+\section{Discussion}
+\label{sec:discuss}
+
+Why reconstruction works or doesn't work.
+
+Major sources of uncertainty.
+
+Ideas for improving the procedure
 
@@
 
-\section{Summary}
-\label{sec:summary}
+\section{Conclusions}
+\label{sec:conclude}
+
+To remind you, this is what we did.
 
@@
 \end{itemize}
+
+% \item Faint galaxies and other dark structures will not appear in a photometric
+% object catalog, but they will contribute convergence at some level. How much of
+% the total external convergence in a time delay lens system comes from visible
+% galaxies? How does this change as a function of magnitude cut?
+
+% \item Can the true (ray-traced) convergence be recovered by halo model
+% reconstruction, and with what scatter and residual bias? Which aspects of the 
+% model dominate these uncertainties?
+
+% \item When faced with a newly-detected lens, surrounded by galaxies on the sky,
+% we have some choices to make when planning follow-up observations.
+% Which are the most important galaxies, with regard to the external convergence
+% produced? Can nearby groups and clusters be straightforwardly accounted for? If
+% lenses with such massive structures nearby are discarded, what impact does that
+% have on the distance accuracy?
 

### 2012-07-01 doc/paper-lcr.tex
bit more lit

@@
 
-The first attempts at reconstructing the line of sight mass distribution in
-strong lens fields were \ldots. \flag{More needed here. Previous work on
-environments: Keeton, Zabludoff, Auger, Momcheva, Wong, others. Spectroscopic
-surveys, modelling mass along line of sight.}
+Previous attempts at reconstructing the line of sight mass distribution in
+strong lens fields have focused on spectroscopic surveys to ascertain group
+membership, and on understanding the external shear apparently required by the
+strong lens models.  The probability density function (PDF) $\Pr(\xkappa)$ is
+the target for any reconstruction analysis, and the key quantity for any
+ensemble analysis, since by marginalising over it we can correctly propagate
+the uncertainties due to weak lensing by line of sight mass structure. 
+\flag{More needed here. Previous work on environments: Keeton, Zabludoff,
+Auger, Momcheva, Wong, others.} Most recently, \citet{Wong++2011} ran Monte
+Carlo reconstructions of the mass in nine lens fields, and compared the
+resulting predicted shear distributions with the lens model external shear.
+Their simulations show most of  the shear being generated by bright galaxies
+within 2~arcminutes of the lens, and that both line of sight structures and
+the group of galaxies in each lens plane contribute significant proportions of
+the shear. The significant discrepancies between the lens model shear and the
+Monte Carlo predictions are attributed to both the environment modelling and
+the strong lens modelling itself.
 
-These observational investigations provided useful insight into the problem. 
-Coming from the opposite direction, \citet{Hilbert++2009} performed ray-tracing
-experiments through the Millenium Simulation, generating a predicted $\xkappa$
-at every position in a simulated sky. The first step towards using this
-excellent calibration resource was taken by \citet{Suyu++2010}, who selected
-Millenium lines of sight that a) were found to contain a strong lens and b) had
-comparable apparent galaxy overdensity in a 45 arcsec radius aperture down to $i
-< 24$. This overdensity could be compared to the overdensity of the B1608$+$656
-line of sight \citep{Fass+Koop2010}, and hence an estimate of the probability
-density function (PDF) $\Pr(\xkappa)$ could be made. This PDF is the key
-quantity for any ensemble analysis, since by marginalising over it we can
-correctly propagate the uncertainties due to weak lensing by line of sight mass
-structure.
+These observational investigations have provided very useful insight into the
+problem.  Coming from the opposite direction, large numerical simulations have
+been used to predict, from first principles the distribution of likely
+external shears and convergences along strong lens lines of sight. \flag{More
+needed here. Holder \& Schechter, Dalal \& Watson}. \citet{Hilbert++2009}
+performed ray-tracing experiments through the Millenium Simulation, generating
+a predicted $\xkappa$ at every position in a simulated sky. The first step
+towards using this excellent calibration resource was taken by
+\citet{Suyu++2010}, who selected Millenium lines of sight that a) were found
+to contain a strong lens and b) had comparable apparent galaxy overdensity in
+a 45 arcsec radius aperture down to $i < 24$. This overdensity could be
+compared to the overdensity of the B1608$+$656 line of sight
+\citep{Fass+Koop2010}, and hence an estimate of  $\Pr(\xkappa)$ could be
+made.
 
-In this paper we use the Millenium Simulation mock galaxy catalogs and
-ray-traced lensing effects to test the accuracy of line of sight mass
-reconstructions. Probabilistically ssigning mass and redshift to every observed
-galaxy in the field around a time delay lens, we generate Monte Carlo sample
-line of sight mass distributions, and estimate the external convergence due to
-each one. This gives us a $\Pr(\xkappa)$ that can be propagated into further
-joint inferences. We focus on time delay lens cosmography, and quantify our
-results in terms of the uncertainty on the mean time delay distance to a test
-sample of $N$ lenses (where for clarity each lens has the same deflector and
-source redshift, and the same lens model and time delay uncertainty).
+What has not been investigated before, but is the subject of this paper, is
+the use of simulations to {\it calibrate} lightcone reconstruction methods.
+Ray-tracing through the simulations gives a ``truth'' that we can attempt to
+recover.  In this paper we use the Millenium Simulation mock galaxy catalogs
+and ray-traced lensing effects to test the accuracy of line of sight mass
+reconstructions. Probabilistically ssigning mass and redshift to every
+observed galaxy in the field around a time delay lens, we generate Monte Carlo
+sample line of sight mass distributions, and estimate the external convergence
+due to each one. This gives us a $\Pr(\xkappa)$ that can be propagated into
+further joint inferences. We focus on time delay lens cosmography, and
+quantify our results in terms of the uncertainty on the mean time delay
+distance to a test sample of $N$ lenses (where for clarity each lens has the
+same deflector and source redshift, and the same lens model and time delay
+uncertainty).
 

### 2012-07-02 doc/paper-lcr.tex
started theory section

@@
 \usepackage{graphicx}
+\usepackage{amssymb}
+\usepackage{amsmath}
 
@@
 \author[Collett \etal]{%
-  Thomas~J.~Collett$^{1}$\thanks{\collettemail},
+  Thomas~E.~Collett$^{1}$\thanks{\collettemail},
   Philip~J.~Marshall$^{2}$,
@@
 surveys of the field in question. Tests using mock catalogs from the Millenium
-Simulation and comparing to ray-traced $kappa$ values, we find that \ldots 
+Simulation and comparing to ray-traced $\kappa$ values, we find that \ldots 
 The $\Pr(\xkappa)$ from this reconstruction process are narrower than the
@@
 
-Time delay distances, and the mass sheet degeneracy - how kappa is degenerate in
-strong lens models (and magnifications). Weak lensing by NFW halos. Accounting
-for mass along the line of sight.  Approximations to full ray tracing: combining
-kappas: simple sum, Keeton scaling, comments. Example ray traced kappa map from Stefan.
+%Time delay distances[✓], and the mass sheet degeneracy - how kappa is degenerate in
+%strong lens models (and magnifications). Weak lensing by NFW halos. Accounting
+%for mass along the line of sight.  Approximations to full ray tracing: combining
+%kappas: simple sum, Keeton scaling, comments. Example ray traced kappa map from Stefan.
+
+Strong lensing occurs when a massive object and background source are almost perfectly
+aligned along a line of sight. The light from the background source is deflected by the
+lens galaxy; this deflection allows multiple images of the background source to form
+at stationary points of the time delay function. For a strong lens system in an otherwise
+homogeneous Robertson--Walker universe, the excess time delay of an image at angular position
+$\bmath{\theta}=(\theta_1,\theta_2)$ with unlensed source position $\bmath{\beta}=(\beta_1,\beta_2)$ is
+\be \label{eq:T} 
+\Delta t(\bmath{\theta},\bmath{\beta}) = \frac {1}{c} \frac{D_{\rm d} D_{\rm s}}{D_{\rm ds}} (1+z_{\rm d})\, \phi(\bmath{\theta},\bmath{\beta}),
+\ee
+where $z_{\rm d}$ is the redshift of the lens, $\phi(\bmath{\theta},\bmath{\beta})$ is
+the Fermat potential, and $D_{\rm d}$, $D_{\rm s}$, and $D_{\rm ds}$
+are, respectively, the angular diameter distance from observer to the lens, from observer
+to the source, and from the lens to the source. The Fermat potential is
+defined as
+\be \label{eq:FP}
+\phi(\bmath{\theta},\bmath{\beta})\equiv \left[\frac{(\bmath{\theta}-\bmath{\beta})^2}{2}-\psi(\bmath{\theta}) \right]. 
+\ee
+The first term in Eq. \ref{eq:FP} comes from the geometric path difference as a result of
+the deflection, and the second term is the gravitational delay
+described by the lens potential $\psi(\bmath{\theta})$.
+
+The lens potential, $\psi(\bmath{\theta})$, is related to the projected dimensionless
+surface mass density, $\kappa(\bmath{\theta})$, and the physical projected surface mass density,
+$\Sigma(D_{\rm d} \bmath{\theta})$, by 
+\be \label{eq:psiKappaDiffRelan}
+\kappa(\bmath{\theta})= \frac {\Sigma(D_{\rm d} \bmath{\theta})} {\Sigma_{\rm cr}}=\frac{1}{2}\nabla^2\psi(\bmath{\theta}),
+\ee
+where 
+\be \label{eq:sigcrit} 
+\Sigma_{\rm cr} \equiv \frac{c^2 D_{\rm s}}{4 \pi G D_{\rm d} D_{\rm ds}}.
+\ee
+
+Equation \ref{eq:T} can be rephrased as
+\be
+\Delta t(\bmath{\theta},\bmath{\beta})  =  \frac{\Dt}{c},
+\ee 
+where $\Dt \equiv (1+\zd) D_{\rm d} D_{\rm s}/D_{\rm ds}$ is the time-delay distance.
+Angular diameter distances are given by
+\begin{equation}
+D_{\mathrm{ij}}~=~ {c/H_0 \over {(1+z_{\mathrm{j}})}}\left( {\mathrm{sinn}\!\left( \sqrt{|\Omega_k|} \int_{z_{\mathrm{i}}}^{z_{\mathrm{j}}} {\mathrm{d} z \over E(z)}\right)\over \sqrt{|\Omega_k|}}\right)
+\label{eq:Da}
+\end{equation}
+where $\mathrm{sinn}(x)~=~\sin(x)$, $x$, or $\sinh(x)$ for open, flat, or closed universes respectively, and $E(z)$ is the normalised Hubble parameter:
+\begin{subequations}\label{Eq:Ez}
+\begin{align}
+E(z) &\equiv {H(z) \over H_0}\\
+E^{\Lambda{CDM}}&~=~\!\sqrt{{\Omega_{\mathrm{M}}(1\!+\!z)^{3}\!+\!\Omega_k(1\!+\!z)^2\!+\!\Omega_{\Lambda}}}
+\end{align}
+\end{subequations}
+Since angular diameter distances are proportional to the inverse of the Hubble constant, $1/H_0$,
+so is $\Dt$ proportional to $1/H_0$, hence a measurement of $\Dt$ can be used to infer $H_0$
+and also the other parameters in Equations \ref{eq:Da} and \ref{eq:Ez}.
+
+\subsection{Mass-sheet degeneracy}
+\label{sec:H0theory:MSD}
+
+A dificulty with using time delay distances to contrain $H_0$ is the so called
+Mass-sheet degeneracy \citep[see e.g.][for details]{Falco1985,Schneider2006}.
+This is a degeneracy in the strong lens modeling corresponding to the addition of a
+mass sheet that contributes a convergence and zero shear which combined with a
+re-scaling of the original mass distribution leaves the predicted image positions and
+magnifications unchanged. Given a lens
+model $\kappa_{\rm lens}(\vec{\theta})$, an alternative model described by the
+transformation $\tilde{\kappa}_{\rm lens}(\vec{\theta}) = \lambda + (1-\lambda)
+\kappa_{\rm lens}(\vec{\theta})$, where $\lambda$ is a constant,
+would fit the image positions, shapes and relative fluxes equally well. Physically $\lambda$
+is the convergence of the mass-sheet and can take any real value.
+
+Since strong lenses sit in our real Universe, they are not truely isolated;
+there is some mass along the line of sight coming from intervening structures.
+These structures may be physically associated with the lens e.g. other members
+of a group or cluster, or they may be the result of chance alignments at any redshift. 
+Whilst it is rare for three galaxies to line up well enough for both of the background sources
+to be strongly lensed \citep{gavazzi2008,collett2012}, the shear scale of dark matter halos
+makes a partial allignment -- with the additional structure acting as a weak lens -- 
+a near certainty, indeed \citet{valewhite2003} and \citet{hilbert2007} find that there
+are no empty lightcones in a realistic universe, as such the
+
+it is clear that 
+the mass-sheet degeneracy corresponds to a degeneracy between this
+external convergence ($\kext$) and the mass normalization of the lens 
+galaxy.\footnote{To be specific, the prescription that we adopt for
+  combining the effects of many mass sheets at redshifts $z_i$ with
+  surface mass densities $\Sigma_i$ is $\kext=\frac{4\pi
+    G}{c^2}\displaystyle\sum_i\frac{\Sigma_i(D_i\vec\theta)D_i D_{i{\rm s}}}{D_{\rm s}}$.}
+
+Despite the invariance of the image positions, shapes and relative fluxes
+under a mass-sheet transformation, the relative Fermat potential between the
+images changes according to $\Delta \phi_{\rm trans}(\vec{\theta},
+\vec{\beta}_{\rm trans}) = (1-\lambda) \Delta \phi_{\rm
+  model}(\vec{\theta},\vec{\beta}_{\rm model})$.  Therefore, given measured
+relative time delays $\Delta t$, which are inversely proportional to $H_0$ and
+proportional to the relative Fermat potential (Equation \ref{eq:TsimpH0}), the
+transformed model $\kappa_{\rm trans}$ would lead to an $H_0$ that is a factor
+$(1-\lambda)$ lower than that of the initial $\kappa_{\rm model}$ (for fixed
+$\OM$, $\OL$, and $w$).  In other words, if there is physically any external
+convergence $\kext$ due to the lens' local environment or mass structure along the
+line of sight
+to the lens system that is not incorporated in the lens
+modeling, then
+\be 
+\label{eq:MassSheet:H0bias}
+H_0^{\rm{true}}=(1-\kext) H_0^{\rm{model}}.
+\ee
+
+This degeneracy is present because lensing observations only deliver
+relative positions and fluxes.  The degeneracy can be broken, allowing us to
+measure $H_0$, if (i) we
+know the magnitude or angular size of the source in absence of lensing,
+(ii) we have information on
+the mass normalization of the lens,
+or (iii) we can compare the measured shear in the lens with the
+observed distribution of mass to calibrate $\kext$.
+For most of the strong lens systems including \ourlens, 
+case (i) does not apply, so
+circumventing the mass-sheet degeneracy requires the input of more
+information, either about the lensing galaxy itself, or its three-dimensional
+environment.
+We distinguish between two kinds of mass sheets: \textit{internal}
+and \textit{external}.  
+%
+Internal mass 
+sheets, which are physically associated with the lens galaxy, are due
+to nearby, physically associated galaxies, 
+groups or clusters which, crucially, 
+affect the stellar dynamics of the
+lens galaxy. External mass sheets describe mass
+distributions that are not physically associated with the
+lens galaxy and, by definition, do not affect the stellar dynamics.  
+Typically these will 
+lie along the line of sight to the lens \citep{FassnachtEtal06}. 
+We identify $\kext$ as the net convergence of this external mass sheet.
+
+Two methods for breaking the mass-sheet degeneracy are then: 
+\renewcommand{\theenumi}{\roman{enumi}}
+\begin{enumerate}
+\item \textit{Stellar dynamics of the lens galaxy.}  Stellar dynamics
+  can be used jointly with lensing to break the internal mass-sheet degeneracy
+  by providing an estimate of the enclosed mass at a radius different
+  from the Einstein radius, which is approximately the radius of the
+  lensed images from the lens galaxy
+  \citep[e.g.,][]{GroginNarayan96a, GroginNarayan96b, TonryFranx99,
+    KoopmansTreu02, TreuKoopmans02, BarnabeKoopmans07}.  We note that
+  for a given stellar velocity dispersion, there is a degeneracy in
+  the mass and the stellar orbit anisotropy (which characterizes the amount of
+  tangential velocity dispersion relative to radial dispersion).  Nonetheless,
+  the mass-isotropy degeneracy is nearly orthogonal to the mass-sheet
+  degeneracy, so a combination of the mass within the effective radius
+  (from the stellar velocity dispersion) and the mass within the Einstein
+  radius (from lensing) effectively breaks both the mass-isotropy and
+  the internal mass-sheet degeneracies. We describe how this works within the
+  context of our chosen mass model in Section~\ref{sec:H0theory:Dynamics}
+  below.
+\item \textit{Studying the environment and the line of sight to the lens galaxy.}  
+  Observations of the field around lens galaxies allow a rough picture of the
+  projected mass distribution to be built up. Many lens galaxies lie in galaxy
+  groups, which can be identified either by their spectra or, more cheaply
+  (but less accurately), by their colors and magnitudes.    By modeling the
+  mass distribution of the groups and galaxies in the lens plane and along the
+  line of sight  to the lens galaxy, one can estimate the external
+  convergence~$\kext$  at the redshift of the lens \citep[e.g.][and references
+  therein]{MomchevaEtal06, FassnachtEtal06, AugerEtal07}.  The group modeling
+  requires (i) identification of the  galaxies that belong to the group of the
+  lens galaxy, and (ii) estimates of the group centroid and velocity
+  dispersion.  A number of recipes can be followed. For example,
+  \citet{KeetonZabludoff04} considered two extremes: (i) the group is
+  described by a single smooth mass distribution, and (ii) the masses are
+  associated with individual galaxy group members with no common halo.  The
+  realistic mass distribution for a galaxy group should be somewhere between
+  these two extremes.  
+  The experience to date  is that 
+  modeling lens environments accurately is very difficult, with uncertainties
+  of 100\% typical \citep[e.g.][]{MomchevaEtal06, FassnachtEtal06}.    
+  In Section \ref{sec:LensEnv}, we describe an
+  alternative approach for quantifying the external convergence in a
+  statistical manner: ray-tracing through numerical simulations of large-scale
+  structure \citep{HilbertEtal07}.
+  In this section 
+  we also present a first attempt at tailoring the ray-tracing results 
+  to our one line of sight, using the relative galaxy number counts in the
+  field.
+\end{enumerate}
+
+We emphasize that the mass-sheet degeneracy is simply one of the
+several parameter degeneracies in the lens modeling that has been
+given a special name.  When power-laws ($\kappa \sim b R^{1-\slope}$,
+where $R$ is the radial distance from the lens center, $b$ is the
+normalization of the lens, and $\slope$ is the radial slope in the
+mass profile) are used to describe the lens mass distribution, one
+often finds a $H_0$-$\slope$ degeneracy in addition to the
+$H_0$-$b$-$\kext$ (mass-sheet) degeneracy (for fixed $\OM$, $\OL$ and
+$w$; more generally, $\tdist$ would be in place of $H_0$).  These two
+degeneracies are of course related via $H_0$.  The $H_0$-$\slope$
+degeneracy primarily occurs in lens systems with symmetric
+configurations due to a lack of information on $\slope$.  In contrast,
+lens systems with images spanning a range of radii or with extended
+images provide information on $\slope$
+\citep[e.g.][]{WucknitzEtal04,DyeEtal08}, and so the $H_0$-$\slope$
+degeneracy is broken.  Nonetheless, the $H_0$-$b$-$\kext$ degeneracy
+is still present unless we provide information from dynamics and lens
+environment studies.
 

### 2012-07-02 PDFcreate.py

@@ -79,8 +79,8 @@ def MScompare(argv):
       return
 
    vb = False
-   Ncones = 1000
-   Rcone = 3 # arcmin
+   Ncones = 10
+   Rcone = 5 # arcmin
    truncationscale=3   # *R_200 halo truncation
   
    scaling = "add" 
@@ -218,8 +218,9 @@ def MScompare(argv):
 
    #so now lets draw the cones that we want to creat pdfs for.
 
-   Npdf=1000 #how many pdf's do we want?
-   print time.clock()
+   Npdf=10 #how many pdf's do we want?
+   #Ncones=1000 #How many realisations? 
+
    xn = rnd.uniform(xmin+Rcone*arcmin2rad,xmax-Rcone*arcmin2rad,Npdf)
    yn = rnd.uniform(ymin+Rcone*arcmin2rad,ymax-Rcone*arcmin2rad,Npdf)
 
@@ -250,14 +251,32 @@ def MScompare(argv):
    #------------------------------------------------------------------
 
       #Now lets plot the pdfs!
-      #print numpy.std(kappa_Reconstruct_n[n,:])
-      #plt.hist(kappa_Reconstruct_n[n,:])
-      #plt.axvline(x=kappa_hilbert_n[n],ymin=0,ymax=1,c='k',ls='dashed',label="$\kappa$ Hilbert")
-      #plt.axvline(x=kappa_Truth_n[n],ymin=0,ymax=1,c='k',ls='dotted',label="$\kappa$ Perfect Mass")
-      #plt.legend(loc=1)
-      #plt.show()
+      colors=["b","g","r","y","purple"]
+      if n < 5:
+         #print numpy.std(kappa_Reconstruct_n[n,:])
+         #print blurfactor
+         #lc.plot()
+         #plt.savefig("plot.png")
+         ##plt.show()
+         #plt.clf()
+         #AX=plt.subplot(1,1,1, aspect ='equal')
+         #lc.massplot(AX)
+         #plt.savefig("massplot.png")
+         #plt.show()
+         #plt.clf()
 
-   F=open("pdfs.dat","wb")
+         bins=numpy.linspace(-0.2,0.6,41)
+         plt.hist(kappa_Reconstruct_n[n,:],bins=bins,color=colors[n],alpha=0.3)
[…]

### 2012-07-02 Pangloss/grid.py

@@ -126,7 +126,7 @@ class lensgrid(grid):
    def Behroozigrid(self,MFs):
        #Calculate the Behroozi relation and scatter on each plane.
        
-       Mh = numpy.linspace(10.,25.,2501)
+       Mh = numpy.linspace(9.,25.,1601)
        Ms = numpy.linspace(5.5,12.5,801)
        sigma = 0.15
        self.Mh=Mh
@@ -190,7 +190,7 @@ class lensgrid(grid):
              return (N-TCHM)[aa:-bb][C]/TCHM[aa:-bb][C]**0.5
           if ZPD != zpd:
              coeff,ier = optimize.leastsq(getPL,[14.56,-1.])
-          ZPD=zpd*1.0
+
 
           HMF = 10**(coeff[0]+Mh*coeff[1])
 
@@ -201,9 +201,43 @@ class lensgrid(grid):
              pdf[:,i] = numpy.exp(-0.5*(Ms-MsMean[i])**2/sigma**2)/norm
 
           #multiply pdf by Halo Mass Function
+
+
+          plotting=False
+          if plotting:
+             if zpd==3 and ZPD != 3:
+                pdfm=pdf[50:751,100:601]
+                plt.imshow(pdfm,origin="lower",extent = [Mh[100:601].min(), Mh[100:601].max(), Ms[50:751].min(), Ms[50:751].max()])
+                plt.xlabel("log$_{10}$(M$_{\mathrm{halo}}$/M$_{\odot}$)")
+                plt.ylabel("log$_{10}$(M$_{\mathrm{stellar}}$/M$_{\odot}$)")
+                plt.title("P(M$_{\mathrm{stellar}}$|M$_{\mathrm{halo}}$) - Behroozi Relation")
+                plt.savefig("Behroozi.png")
+                plt.show()
+
           for i in range(Mh.size):
               pdf[:,i]*=HMF[i]
- 
+          if zpd==3 and ZPD != 3:
+          #   #plt.subplot(212)
+          #   plt.imshow(pdf,origin="lower",extent = [Mh.min(), Mh.max(), Ms.min(), Ms.max()])
+          #   plt.xlabel("log$_{10}$(M$_{\mathrm{halo}}$/M$_{\odot}$)")
+          #   plt.ylabel("log$_{10}$(M$_{\mathrm{stellar}}$/M$_{\odot}$)")
+          #   plt.show()
+
+             if plotting:
+                pdfl=pdf*1.0
[…]

### 2012-07-02 Pangloss/lightcone.py

@@ -252,10 +252,24 @@ class lens_lightcone(lightcone):
         c200 = Rel.MCrelation(M200,MCerror=errors)
         r200 = (3*M200/(800*3.14159*self.galaxies.rho_crit))**(1./3)
 
+        self.galaxies.add_column('r200',r200)
+
         #print (M200/self.galaxies['M_Subhalo[M_sol/h]']).max()
 
 
         r_s = r200/c200
+        self.galaxies.add_column('rscale',r_s)
+
+
+        
+        r_s_arcmin  = (r_s / self.galaxies.Da_d) * rad2arcmin
+        r200_arcmin = (r200 / self.galaxies.Da_d) * rad2arcmin
+
+        self.galaxies.add_column('rscale_arcmin',r_s_arcmin)
+        self.galaxies.add_column('r200_arcmin',r200_arcmin)
+
+
+
         rho_s = LP.delta_c(c200)*self.galaxies.rho_crit
         kappa_s = rho_s * r_s /self.galaxies.sigma_crit
     
@@ -327,14 +341,41 @@ class lens_lightcone(lightcone):
         return None
 
 # ----------------------------------------------------------------------------
+#      -.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.
+    def massplot(self,AX):
+       for i in range(len(self.galaxies.x)):
+           trunc=pylab.Circle([self.galaxies.x[i], self.galaxies.y[i]],radius=3*self.galaxies.r200_arcmin[i],fill=True,fc="b",alpha=0.01)
+           AX.add_patch(trunc)
+       for i in range(len(self.galaxies.x)):
+           core=pylab.Circle([self.galaxies.x[i], self.galaxies.y[i]],radius=self.galaxies.rscale_arcmin[i],fill=True,fc="r",alpha=0.1)
+           AX.add_patch(core)
+       #for i in range(len(self.galaxies.x)):
+       #    if 3*self.galaxies.r200_arcmin[i]>self.galaxies.r[i]:
+       #        AX.scatter(self.galaxies.x[i], self.galaxies.y[i],c='k',s=10,edgecolor='none')
+       #    #elif 4*self.galaxies.r200_arcmin[i]>self.galaxies.r[i]:
[…]

### 2012-07-02 doc/paper-lcr.tex
first draft of theory section

--- 2012-07-01 doc/paper-lcr.tex
@@
 the uncertainties due to weak lensing by line of sight mass structure. 
-\flag{More needed here. Previous work on environments: Keeton, Zabludoff,
-Auger, Momcheva, Wong, others.} Most recently, \citet{Wong++2011} ran Monte
+\flag{More needed here. Previous work on environments: Keeton, Zabludoff,Auger, Momcheva, Wong, others.}
+Most recently, \citet{Wong++2011} ran Monte
 Carlo reconstructions of the mass in nine lens fields, and compared the
@@
 
-Time delay distances, and the mass sheet degeneracy - how kappa is degenerate in
-strong lens models (and magnifications). Weak lensing by NFW halos. Accounting
-for mass along the line of sight.  Approximations to full ray tracing: combining
-kappas: simple sum, Keeton scaling, comments. Example ray traced kappa map from Stefan.
+%Time delay distances[✓], and the mass sheet degeneracy[✓] - how kappa is degenerate in
+%strong lens models (and magnifications).
+
+Strong lensing occurs when a massive object and background source are almost perfectly
+aligned along a line of sight. The light from the background source is deflected by the
+lens galaxy; this deflection allows multiple images of the background source to form
+at stationary points of the time delay function. For a strong lens system in an otherwise
+homogeneous Robertson--Walker universe, the excess time delay of an image at angular position
+$\bmath{\theta}=(\theta_1,\theta_2)$ with unlensed source position $\bmath{\beta}=(\beta_1,\beta_2)$ is
+\be \label{eq:T} 
+\Delta t(\bmath{\theta},\bmath{\beta}) = \frac {1}{c} \frac{D_{\rm d} D_{\rm s}}{D_{\rm ds}} (1+z_{\rm d})\, \phi(\bmath{\theta},\bmath{\beta}),
+\ee
+where $z_{\rm d}$ is the redshift of the lens, $\phi(\bmath{\theta},\bmath{\beta})$ is
+the Fermat potential, and $D_{\rm d}$, $D_{\rm s}$, and $D_{\rm ds}$
+are, respectively, the angular diameter distance from observer to the lens, from observer
+to the source, and from the lens to the source. The Fermat potential is
+defined as
+\be \label{eq:FP}
+\phi(\bmath{\theta},\bmath{\beta})\equiv \left[\frac{(\bmath{\theta}-\bmath{\beta})^2}{2}-\psi(\bmath{\theta}) \right]. 
+\ee
+The first term in Eq. \ref{eq:FP} comes from the geometric path difference as a result of
+the deflection, and the second term is the gravitational delay
+described by the lens potential $\psi(\bmath{\theta})$.
+
+The lens potential, $\psi(\bmath{\theta})$, is related to the projected dimensionless
+surface mass density, $\kappa(\bmath{\theta})$, and the physical projected surface mass density,
+$\Sigma(D_{\rm d} \bmath{\theta})$, by 
+\be \label{eq:psiKappaDiffRelan}
+\kappa(\bmath{\theta})= \frac {\Sigma(D_{\rm d} \bmath{\theta})} {\Sigma_{\rm cr}}=\frac{1}{2}\nabla^2\psi(\bmath{\theta}),
+\ee
+where 
+\be \label{eq:sigcrit} 
+\Sigma_{\rm cr} \equiv \frac{c^2 D_{\rm s}}{4 \pi G D_{\rm d} D_{\rm ds}}.
+\ee
+Equation \ref{eq:Tsimp} can be rephrased as
+\be
+\Delta t(\bmath{\theta},\bmath{\beta})  =  \frac{\Dt}{c},
+\ee 
+where $\Dt \equiv (1+\zd) D_{\rm d} D_{\rm s}/D_{\rm ds}$ is the time-delay distance.
+Angular diameter distances are given by
+\begin{equation}
+D_{\mathrm{ij}}~=~ {c/H_0 \over {(1+z_{\mathrm{j}})}}\left( {\mathrm{sinn}\!\left( \sqrt{|\Omega_k|} \int_{z_{\mathrm{i}}}^{z_{\mathrm{j}}} {\mathrm{d} z \over E(z)}\right)\over \sqrt{|\Omega_k|}}\right)
+\label{eq:Da}
+\end{equation}
+where $\mathrm{sinn}(x)~=~\sin(x)$, $x$, or $\sinh(x)$ for open, flat, or closed universes respectively, and $E(z)$ is the normalised Hubble parameter:
+\begin{subequations}\label{Eq:Ez}
+\begin{align}
+E(z) &\equiv {H(z) \over H_0}\\
+E^{\Lambda{CDM}}&~=~\!\sqrt{{\Omega_{\mathrm{M}}(1\!+\!z)^{3}\!+\!\Omega_k(1\!+\!z)^2\!+\!\Omega_{\Lambda}}}
+\end{align}
+\end{subequations}
+Since angular diameter distances are proportional to the inverse of the Hubble constant, $1/H_0$,
+so is $\Dt$ proportional to $1/H_0$, hence a measurement of $\Dt$ can be used to infer $H_0$
+and also the other parameters in Equations \ref{eq:Da} and \ref{eq:Ez}.
+
+\subsection{Mass-sheet degeneracy}
+\label{sec:H0theory:MSD}
+
+A dificulty with using time delay distances to contrain $H_0$ is the so called
+Mass-sheet degeneracy \citep[see e.g.][for details]{Falco1985,Schneider2006}.
+This is a degeneracy in the strong lens modeling corresponding to the addition of a
+mass sheet that contributes a convergence and zero shear which combined with a
+re-scaling of the original mass distribution leaves the predicted image positions and
+magnifications unchanged. Given a lens
+model $\kappa_{\rm lens}(\bmath{\theta})$, an alternative model described by the
+transformation 
+\be\label{eq:transform}
+\widetilde{\kappa}_{\rm lens}(\bmath{\theta}) = \lambda + (1-\lambda)\kappa_{\rm lens}(\bmath{\theta}),
+\ee
+where $\lambda$ is a constant,would fit the image positions, shapes and relative fluxes equally well. Physically $\lambda$
+is the \flag{efffective?} convergence of the mass-sheet and can take any real value. The mass-sheet degeneracy
+corresponds to a degeneracy between this external convergence ($\kappax$) and the mass
+normalization of the lens galaxy.
+
+\flag{How do kappas combine? this is what Sherry said in suyuetal2010 - To be specific, the prescription that we adopt for
+  combining the effects of many mass sheets at redshifts $z_i$ with
+  surface mass densities $\Sigma_i$ is $\kappax=\frac{4\pi
+    G}{c^2}\displaystyle\sum_i\frac{\Sigma_i(D_i\vec\theta)D_i D_{i{\rm s}}}{D_{\rm s}}$.}
+
+Since strong lenses sit in our real Universe, they are not truely isolated;
+there is some mass along the line of sight coming from intervening structures.
+These structures may be physically associated with the lens e.g. other members
+of a group or cluster, or they may be the result of chance alignments at any redshift. 
+Whilst it is rare for three galaxies to line up well enough for both of the background sources
+to be strongly lensed \citep{gavazzi2008,collett2012}, the shear scale of dark matter halos
+makes a partial allignment -- with the additional structure acting as a weak lens -- 
+a near certainty, indeed \citet{valewhite2003} and \citet{hilbert2007} find that there
+are no empty lightcones in a realistic universe. It is necessary to include $\kappax$
+in our lens modelling, if cosmological parameters are to be estimated accurately and precisely \citep{suyu2010}.
+
+Despite the invariance of the image positions, shapes and relative fluxes
+under the transformation in Eq. \ref{eq:transform}, the relative Fermat potential between the
+images is not invariant, but changes according to
+\be\label{eq:phitransform}
+\Delta \widetilde{\phi_{\rm }}(\bmath{\theta},\widetilde{\bmath{\beta}_{\rm }}) 
+= 
+(1-\lambda) \Delta \phi_{\rm }
+(\bmath{\theta},\bmath{\beta}_{\rm }).
+\ee
+If the source brightness changes the observed brightness in each image does not change
+simultaneously - there is a time delay, $\Delta t$, between the brightness change in
+each image. These time delays are inversely proportional to $H_0$ and
+proportional to the relative Fermat potential (Equation \ref{eq:Tsimp}). Thus if
+there is any external convergence, $\kappax$, that is not included in the lens
+modeling, then the value of $H_0$ --inferred assuming $\kappax = 0$ -- will be
+$1-\kappax$ less than the true value of $H_0$:
+\be 
+\label{eq:MassSheet:H0bias}
+H_0^{\rm{true}}=(1-\kappax) H_0^{{\kappax = 0}}.
+\ee
+This degeneracy is present because lensing observations only deliver
+relative positions and fluxes. However we can overcome this degeneracy 
+if we have knowledge of $\kappax$.
+
+For mass-sheets that are physically
+associated with the lens galaxy, the mass sheet affects the stellar dynamics of the
+lens galaxy. Stellar dynamics can be used jointly with lensing to break the internal
+mass-sheet degeneracy by providing an additional estimate of the lens galaxy's mass
+\citep[e.g.,][]{GroginNarayan96a, GroginNarayan96b, TonryFranx99, KoopmansTreu02,
+ TreuKoopmans02, BarnabeKoopmans07, suyu2010}.
+
+In this work our aim is to quantify the lensing contribution from mass sheets that
+are not physically associated with the lens galaxy -- mass-sheets lying infront or behind
+the lens \citep{FassnachtEtal06}.
 
@@
 
-\section{Halo Model}
+\section{Halo Model and Mass distribution}
 \label{sec:model}
+
+Weak lensing by NFW halos. Accounting for mass along the line of sight.
+Approximations to full ray tracing: combining kappas: simple sum, Keeton
+scaling, comments. Example ray traced kappa map from Stefan.
 

### 2012-07-02 doc/paper-lcr.tex
started re-write of theory

@@
 lens galaxy; this deflection allows multiple images of the background source to form
-at stationary points of the time delay function. For a strong lens system in an otherwise
-homogeneous Robertson--Walker universe, the excess time delay of an image at angular position
-$\bmath{\theta}=(\theta_1,\theta_2)$ with unlensed source position $\bmath{\beta}=(\beta_1,\beta_2)$ is
+at stationary points of the time delay function. For an isolated lens, the time delay
+function can be calculated from calculated from 
 \be \label{eq:T} 
@@
 \ee
-where $z_{\rm d}$ is the redshift of the lens, $\phi(\bmath{\theta},\bmath{\beta})$ is
+where $\bmath{\theta}$ is the observed source position, $\bmath{\beta}$ is the 
+unlensed source position, $z_{\rm d}$ is the redshift of the lens, $\phi(\bmath{\theta},\bmath{\beta})$ is
 the Fermat potential, and $D_{\rm d}$, $D_{\rm s}$, and $D_{\rm ds}$
-are, respectively, the angular diameter distance from observer to the lens, from observer
-to the source, and from the lens to the source. The Fermat potential is
+are, respectively, the angular diameter distances from observer to the lens, from observer
+to the source, and from the lens to the source. The Fermat potential is given by
 defined as
 \be \label{eq:FP}
-\phi(\bmath{\theta},\bmath{\beta})\equiv \left[\frac{(\bmath{\theta}-\bmath{\beta})^2}{2}-\psi(\bmath{\theta}) \right]. 
+\phi(\bmath{\theta},\bmath{\beta})\equiv \left[\frac{(\bmath{\theta}-\bmath{\beta})^2}{2}-\psi(\bmath{\theta}) \right], 
 \ee
-The first term in Eq. \ref{eq:FP} comes from the geometric path difference as a result of
-the deflection, and the second term is the gravitational delay
-described by the lens potential $\psi(\bmath{\theta})$.
+where $\psi(\bmath{\theta}$ is the lens potential.
+%The two term in Eq. \ref{eq:FP} comes from the geometric path difference as a result of
+%the deflection, and the second term is the gravitational delay
+%described by the lens potential $\psi(\bmath{\theta})$.
+
+Strong lenses sit in our real Universe -- they are not truely isolated;
+there is some mass along the line of sight coming from intervening structures.
+These structures may be physically associated with the lens e.g. other members
+of a group or cluster, or they may be the result of chance alignments at any redshift. 
+Whilst it is rare for three galaxies to line up well enough for both of the background sources
+to be strongly lensed \citep{gavazzi2008,collett2012}, the shear scale of dark matter halos
+makes a partial allignment -- with the additional structure acting as a weak lens -- 
+a near certainty, indeed \citet{valewhite2003} and \citet{hilbert2007} find that there
+are no empty lightcones in a realistic universe. These additional structures induce an external shear
+which can be recovered in the mass-modelling of the lens, but they can also introduce a convergence that
+is undetectable from the image positions, shapes and relative fluxes. The mass-sheet degeneracy
+\citep[see e.g.][for details]{Falco1985,Schneider2006}. This is a degeneracy in the strong lens
+modeling corresponding to the addition of a mass sheet that contributes a convergence and
+zero shear which, combined with a re-scaling of the original mass distribution, leaves the
+predicted image positions and magnifications unchanged.
+%Given a lens
+%model $\kappa_{\rm lens}(\bmath{\theta})$, an alternative model described by the
+%transformation 
+%\be\label{eq:transform}
+%\widetilde{\kappa}_{\rm lens}(\bmath{\theta}) = \lambda + (1-\lambda)\kappa_{\rm lens}(\bmath{\theta}),
+%\ee
+%where $\lambda$ is a constant, would fit the image positions, shapes and relative fluxes equally well. Physic%ally $\lambda$
+%is the \flag{effective?} convergence of the mass-sheet and can take any real value. The mass-sheet degeneracy
+%corresponds to a degeneracy between this external convergence ($\kappax$) and the mass
+%normalization of the lens galaxy.
+If the source brightness changes, the observed brightness in each image does not change
+simultaneously - there is a time delay, $\Delta t$, between the brightness change in
+each image. Despite the invariance of the image positions and fluxes, under the addition
+of an external convergence the relative Fermat potential between the images is {\it not}
+invariant, and so the time delay changes. As such it is necessary to include $\kappax$
+in our lens modelling, if cosmological parameters are to be estimated accurately and
+precisely \citep{suyu2010} from observed time delays.
+
+\flag{How do kappas combine? this is what Sherry said in suyuetal2010 - To be specific, the prescription that we adopt for
+  combining the effects of many mass sheets at redshifts $z_i$ with
+  surface mass densities $\Sigma_i$ is $\kappax=\frac{4\pi
+    G}{c^2}\displaystyle\sum_i\frac{\Sigma_i(D_i\vec\theta)D_i D_{i{\rm s}}}{D_{\rm s}}$.}
+
+\be\label{eq:phitransform}
+\Delta \widetilde{\phi_{\rm }}(\bmath{\theta},\widetilde{\bmath{\beta}_{\rm }}) 
+= 
+(1-\lambda) \Delta \phi_{\rm }
+(\bmath{\theta},\bmath{\beta}_{\rm }).
+\ee
+ Thus if
+there is any external convergence, $\kappax$, that is not included in the lens
+modeling, then the value of $H_0$ --inferred assuming $\kappax = 0$ -- will be
+$1-\kappax$ less than the true value of $H_0$:
+\be 
+\label{eq:MassSheet:H0bias}
+H_0^{\rm{true}}=(1-\kappax) H_0^{{\kappax = 0}}.
+\ee
+This degeneracy is present because lensing observations only deliver
+relative positions and fluxes. However we can overcome this degeneracy 
+if we have knowledge of $\kappax$.
 
@@
 
-\subsection{Mass-sheet degeneracy}
-\label{sec:H0theory:MSD}
-
-A dificulty with using time delay distances to contrain $H_0$ is the so called
-Mass-sheet degeneracy \citep[see e.g.][for details]{Falco1985,Schneider2006}.
-This is a degeneracy in the strong lens modeling corresponding to the addition of a
-mass sheet that contributes a convergence and zero shear which combined with a
-re-scaling of the original mass distribution leaves the predicted image positions and
-magnifications unchanged. Given a lens
-model $\kappa_{\rm lens}(\bmath{\theta})$, an alternative model described by the
-transformation 
-\be\label{eq:transform}
-\widetilde{\kappa}_{\rm lens}(\bmath{\theta}) = \lambda + (1-\lambda)\kappa_{\rm lens}(\bmath{\theta}),
-\ee
-where $\lambda$ is a constant,would fit the image positions, shapes and relative fluxes equally well. Physically $\lambda$
-is the \flag{efffective?} convergence of the mass-sheet and can take any real value. The mass-sheet degeneracy
-corresponds to a degeneracy between this external convergence ($\kappax$) and the mass
-normalization of the lens galaxy.
-
-\flag{How do kappas combine? this is what Sherry said in suyuetal2010 - To be specific, the prescription that we adopt for
-  combining the effects of many mass sheets at redshifts $z_i$ with
-  surface mass densities $\Sigma_i$ is $\kappax=\frac{4\pi
-    G}{c^2}\displaystyle\sum_i\frac{\Sigma_i(D_i\vec\theta)D_i D_{i{\rm s}}}{D_{\rm s}}$.}
-
-Since strong lenses sit in our real Universe, they are not truely isolated;
-there is some mass along the line of sight coming from intervening structures.
-These structures may be physically associated with the lens e.g. other members
-of a group or cluster, or they may be the result of chance alignments at any redshift. 
-Whilst it is rare for three galaxies to line up well enough for both of the background sources
-to be strongly lensed \citep{gavazzi2008,collett2012}, the shear scale of dark matter halos
-makes a partial allignment -- with the additional structure acting as a weak lens -- 
-a near certainty, indeed \citet{valewhite2003} and \citet{hilbert2007} find that there
-are no empty lightcones in a realistic universe. It is necessary to include $\kappax$
-in our lens modelling, if cosmological parameters are to be estimated accurately and precisely \citep{suyu2010}.
-
-Despite the invariance of the image positions, shapes and relative fluxes
-under the transformation in Eq. \ref{eq:transform}, the relative Fermat potential between the
-images is not invariant, but changes according to
-\be\label{eq:phitransform}
-\Delta \widetilde{\phi_{\rm }}(\bmath{\theta},\widetilde{\bmath{\beta}_{\rm }}) 
-= 
-(1-\lambda) \Delta \phi_{\rm }
-(\bmath{\theta},\bmath{\beta}_{\rm }).
-\ee
-If the source brightness changes the observed brightness in each image does not change
-simultaneously - there is a time delay, $\Delta t$, between the brightness change in
-each image. These time delays are inversely proportional to $H_0$ and
-proportional to the relative Fermat potential (Equation \ref{eq:Tsimp}). Thus if
-there is any external convergence, $\kappax$, that is not included in the lens
-modeling, then the value of $H_0$ --inferred assuming $\kappax = 0$ -- will be
-$1-\kappax$ less than the true value of $H_0$:
-\be 
-\label{eq:MassSheet:H0bias}
-H_0^{\rm{true}}=(1-\kappax) H_0^{{\kappax = 0}}.
-\ee
-This degeneracy is present because lensing observations only deliver
-relative positions and fluxes. However we can overcome this degeneracy 
-if we have knowledge of $\kappax$.
-
 For mass-sheets that are physically
 associated with the lens galaxy, the mass sheet affects the stellar dynamics of the
-lens galaxy. Stellar dynamics can be used jointly with lensing to break the internal
+lens galaxy, so dynamical observations can break the internal
 mass-sheet degeneracy by providing an additional estimate of the lens galaxy's mass
@@
 
+For real lines of sight, it is nearly impossible to know the true $\kappax$ for a
+line of sight, and without a knowledge of $\kappax^{\mathrm{true}}$ it is hard to
+quantify if there is a bias induced by using different $\kappax$ estimators.
+A source with known unlensed brightness e.g. a strongly lensed type Ia
+Supernova \flag{cite some SNe papers} or a source of known unlensed size \flag{ideas?}
+would break the mass-sheet degeneracy and provide a value for $\kappax$, but
+\flag{no?} such systems are currently known.
+
+Cosmological dark matter simulations can be used to generate mock lines of sight...
+\flag{Stefan's section on how halos are extracted from the MS n-body particles}
+
+With this catalogue of halos, positions, redshifts etc. it is possible to attempt
+a reconstruction of the convergernce induced by every halo near a line of sight.
+Cosmological dark matter simulations have shown that dark matter halos are well
+approximated by NFW halos \citep{NFW1997}, with a density profile given by
+\be\label{eq:rhonfw}
+\rho(r) = 
+\frac{\rho_0}{\left(r/r_{s}\right)
+\left(1+r/r_{s}\right)^{2}},
+\ee
+where $r_{s}$ is a characteristic radius of the cluster, representing where
+the density slope transitions from $r^{-1}$ to $r^{-3}$. This radius is related
+to the virial radius of the halo by $r_{s} = r_{200}/c$, where $r_{200}$ is the radius at 
+which 
+\be
+\rho(r_{200}) = 200\rho_{{\mathrm{crit}}}(z), \text{ where } \rho_{\mathrm{crit}}(z) \equiv \frac{3H^{2}(z)}{8\pi G}
+\ee
+ and $c$ is the concentration parameter, which can be estimated from the halo's mass,
+using a mass--concentration relation. Typically more massive halos are more concentrated,
+but there is some scatter; we use the relation of \citet{neto2007} to estimate $c$
+from the mass enclosed within $r_{200}$, which we denote as $M_{200}$. $\rho_0$ is calculated 
+by the critical density and concentration parameter:
+\be
+$\rho_0$ = \rho_{\mathrm{crit}}(z\frac{200}{3}\frac{c^{3}}{\ln(1+c)-c/(1+c)}.
+\ee
+
+From the NFW density profile, \citet{wrightbrainerd1999} derive the following quantities
+which are necessary for our line of sight reconstruction:
+
+The mass enclosed within radius is given by:
+
+The projected mass density is given by:
+
+The shear is given by:
+
 Weak lensing by NFW halos. Accounting for mass along the line of sight.
-Approximations to full ray tracing: combining kappas: simple sum, Keeton
-scaling, comments. Example ray traced kappa map from Stefan.
+Approximations to full ray tracing:
 

### 2012-07-02 doc/paper-lcr.tex
started re-write of theory

@@
 \ee
-where $\psi(\bmath{\theta}$ is the lens potential.
-%The two term in Eq. \ref{eq:FP} comes from the geometric path difference as a result of
-%the deflection, and the second term is the gravitational delay
-%described by the lens potential $\psi(\bmath{\theta})$.
+where $\psi(\bmath{\theta}$ is the lens potential, derived from the projected dimensionless
+surface mass density, $\kappa(\bmath{\theta})$, and the physical projected surface mass density,
+$\Sigma(D_{\rm d} \bmath{\theta})$, by 
+\be \label{eq:psikappa}
+\kappa(\bmath{\theta})= \frac {\Sigma(D_{\rm d} \bmath{\theta})} {\Sigma_{\rm cr}}=\frac{1}{2}\nabla^2\psi(\bmath{\theta}),
+\ee
+where 
+\be \label{eq:sigcrit} 
+\Sigma_{\rm cr} \equiv \frac{c^2 D_{\rm s}}{4 \pi G D_{\rm d} D_{\rm ds}}.
+\ee
 
@@
 which can be recovered in the mass-modelling of the lens, but they can also introduce a convergence that
-is undetectable from the image positions, shapes and relative fluxes. The mass-sheet degeneracy
-\citep[see e.g.][for details]{Falco1985,Schneider2006}. This is a degeneracy in the strong lens
-modeling corresponding to the addition of a mass sheet that contributes a convergence and
-zero shear which, combined with a re-scaling of the original mass distribution, leaves the
-predicted image positions and magnifications unchanged.
-%Given a lens
-%model $\kappa_{\rm lens}(\bmath{\theta})$, an alternative model described by the
-%transformation 
-%\be\label{eq:transform}
-%\widetilde{\kappa}_{\rm lens}(\bmath{\theta}) = \lambda + (1-\lambda)\kappa_{\rm lens}(\bmath{\theta}),
-%\ee
-%where $\lambda$ is a constant, would fit the image positions, shapes and relative fluxes equally well. Physic%ally $\lambda$
-%is the \flag{effective?} convergence of the mass-sheet and can take any real value. The mass-sheet degeneracy
-%corresponds to a degeneracy between this external convergence ($\kappax$) and the mass
-%normalization of the lens galaxy.
+is undetectable from the image positions, shapes and relative fluxes; the mass sheet-degeneracy \citep[see e.g.][for details]{Falco1985,Schneider2006}.
+Similar to Eq.
+\ref{eq:psikappa}, the convergence from an isolated mass sheet is given by the projected surface mass density devided by the critical density, which is a function of redshift.
+\flag{but is this the kappa that enters the lens modelling?}
+In the case of several mass sheets at redshifts $\{z_p\}$, with surface mass densities $\{\Sigma_p\}$, the effective convergence is given by the \flag{weighted?} sum :
+\be \label{eq:kappasum}
+\kappax=\frac{4\pi G}{c^2}\sum_p\frac{\Sigma_p(D_p\vec\theta)D_p D_{p{\rm s}}}{D_{\rm s}}.
+\ee
+
 If the source brightness changes, the observed brightness in each image does not change
@@
 
-\flag{How do kappas combine? this is what Sherry said in suyuetal2010 - To be specific, the prescription that we adopt for
-  combining the effects of many mass sheets at redshifts $z_i$ with
-  surface mass densities $\Sigma_i$ is $\kappax=\frac{4\pi
-    G}{c^2}\displaystyle\sum_i\frac{\Sigma_i(D_i\vec\theta)D_i D_{i{\rm s}}}{D_{\rm s}}$.}
-
-\be\label{eq:phitransform}
-\Delta \widetilde{\phi_{\rm }}(\bmath{\theta},\widetilde{\bmath{\beta}_{\rm }}) 
-= 
-(1-\lambda) \Delta \phi_{\rm }
-(\bmath{\theta},\bmath{\beta}_{\rm }).
-\ee
- Thus if
-there is any external convergence, $\kappax$, that is not included in the lens
-modeling, then the value of $H_0$ --inferred assuming $\kappax = 0$ -- will be
-$1-\kappax$ less than the true value of $H_0$:
-\be 
-\label{eq:MassSheet:H0bias}
-H_0^{\rm{true}}=(1-\kappax) H_0^{{\kappax = 0}}.
-\ee
-This degeneracy is present because lensing observations only deliver
-relative positions and fluxes. However we can overcome this degeneracy 
-if we have knowledge of $\kappax$.
-
-The lens potential, $\psi(\bmath{\theta})$, is related to the projected dimensionless
-surface mass density, $\kappa(\bmath{\theta})$, and the physical projected surface mass density,
-$\Sigma(D_{\rm d} \bmath{\theta})$, by 
-\be \label{eq:psiKappaDiffRelan}
-\kappa(\bmath{\theta})= \frac {\Sigma(D_{\rm d} \bmath{\theta})} {\Sigma_{\rm cr}}=\frac{1}{2}\nabla^2\psi(\bmath{\theta}),
-\ee
-where 
-\be \label{eq:sigcrit} 
-\Sigma_{\rm cr} \equiv \frac{c^2 D_{\rm s}}{4 \pi G D_{\rm d} D_{\rm ds}}.
-\ee
-Equation \ref{eq:Tsimp} can be rephrased as
+The time-delay distance is defined as $\Dt \equiv (1+\zd) D_{\rm d} D_{\rm s}/D_{\rm ds}$,
+with which Equation \ref{eq:Tsimp} can be rephrased as
 \be
@@
 \ee 
-where $\Dt \equiv (1+\zd) D_{\rm d} D_{\rm s}/D_{\rm ds}$ is the time-delay distance.
-Angular diameter distances are given by
-\begin{equation}
-D_{\mathrm{ij}}~=~ {c/H_0 \over {(1+z_{\mathrm{j}})}}\left( {\mathrm{sinn}\!\left( \sqrt{|\Omega_k|} \int_{z_{\mathrm{i}}}^{z_{\mathrm{j}}} {\mathrm{d} z \over E(z)}\right)\over \sqrt{|\Omega_k|}}\right)
-\label{eq:Da}
-\end{equation}
-where $\mathrm{sinn}(x)~=~\sin(x)$, $x$, or $\sinh(x)$ for open, flat, or closed universes respectively, and $E(z)$ is the normalised Hubble parameter:
-\begin{subequations}\label{Eq:Ez}
-\begin{align}
-E(z) &\equiv {H(z) \over H_0}\\
-E^{\Lambda{CDM}}&~=~\!\sqrt{{\Omega_{\mathrm{M}}(1\!+\!z)^{3}\!+\!\Omega_k(1\!+\!z)^2\!+\!\Omega_{\Lambda}}}
-\end{align}
-\end{subequations}
-Since angular diameter distances are proportional to the inverse of the Hubble constant, $1/H_0$,
-so is $\Dt$ proportional to $1/H_0$, hence a measurement of $\Dt$ can be used to infer $H_0$
-and also the other parameters in Equations \ref{eq:Da} and \ref{eq:Ez}.
+Since the time delays are proportional to $1/ (1+ \kappax)$, if there is any external convergence, $\kappax$, that is not included in the lens
+modeling, then the time delay distance -- inferred assuming $\kappax = 0$ -- will be
+$1-\kappax$ less than the true value of $\Dt$.
+\be 
+\label{eq:MassSheet:H0bias}
+\Dt^{\rm{true}}=(1-\kappax) \Dt^{{\kappax = 0}}.
+\ee
+We can overcome this degeneracy if we have additional knowledge of $\kappax$.
 
-For mass-sheets that are physically
-associated with the lens galaxy, the mass sheet affects the stellar dynamics of the
+For mass-sheets that are physically associated with the lens galaxy, the mass sheet
+ affects the stellar dynamics of the
 lens galaxy, so dynamical observations can break the internal
@@
 are not physically associated with the lens galaxy -- mass-sheets lying infront or behind
-the lens \citep{FassnachtEtal06}.
+the lens. We also aim to quantify how uncertainties in the estimations of kappa
+propogate into uncertainties on the cosmological parametres which can be inferred
+from measurements of $\Dt$
 

### 2012-07-02 doc/paper-lcr.tex
re-wrote theory

@@
 \ee
-where $\psi(\bmath{\theta}$ is the lens potential, derived from the projected dimensionless
-surface mass density, $\kappa(\bmath{\theta})$, and the physical projected surface mass density,
+where $\psi(\bmath{\theta})$ is the lens potential, derived from the projected dimensionless
+surface mass density, $\kappa(\bmath{\theta})$, or the physical projected surface mass density,
 $\Sigma(D_{\rm d} \bmath{\theta})$, by 
@@
 which can be recovered in the mass-modelling of the lens, but they can also introduce a convergence that
-is undetectable from the image positions, shapes and relative fluxes; the mass sheet-degeneracy \citep[see e.g.][for details]{Falco1985,Schneider2006}.
+is undetectable from the image positions, shapes and relative fluxes; {\it the mass sheet-degeneracy} \citep[see e.g.][for details]{Falco1985,Schneider2006}.
 Similar to Eq.
-\ref{eq:psikappa}, the convergence from an isolated mass sheet is given by the projected surface mass density devided by the critical density, which is a function of redshift.
+\ref{eq:psikappa} the convergence from an isolated mass sheet is by the ratio of the projected surface mass density devided by the critical density at the redshift of the mass sheet.
 \flag{but is this the kappa that enters the lens modelling?}
-In the case of several mass sheets at redshifts $\{z_p\}$, with surface mass densities $\{\Sigma_p\}$, the effective convergence is given by the \flag{weighted?} sum :
+In the case of several mass sheets at redshifts $\{z_{\mathrm{p}}\}$, with surface mass densities $\{\Sigma_{\mathrm{p}}\}$, the effective convergence is given by the \flag{weighted?} sum :
 \be \label{eq:kappasum}
-\kappax=\frac{4\pi G}{c^2}\sum_p\frac{\Sigma_p(D_p\vec\theta)D_p D_{p{\rm s}}}{D_{\rm s}}.
+\kappax=\frac{4\pi G}{c^2}\sum_{\mathrm{p}}\frac{\Sigma_{\mathrm{p}}D_{\mathrm{p}} D_{{\rm ps}}}{D_{\rm s}}.
 \ee
@@
 
-The time-delay distance is defined as $\Dt \equiv (1+\zd) D_{\rm d} D_{\rm s}/D_{\rm ds}$,
+The time-delay distance is defined as
+\be \label{eq:dt}
+\Dt \equiv (1+\zd) D_{\rm d} D_{\rm s}/D_{\rm ds},
+\ee
 with which Equation \ref{eq:Tsimp} can be rephrased as
@@
 propogate into uncertainties on the cosmological parametres which can be inferred
-from measurements of $\Dt$
+from measurements of $\Dt$.
 
@@
 \be
-$\rho_0$ = \rho_{\mathrm{crit}}(z\frac{200}{3}\frac{c^{3}}{\ln(1+c)-c/(1+c)}.
+\rho_0 = \rho_{\mathrm{crit}}(z\frac{200}{3}\frac{c^{3}}{\ln(1+c)-c/(1+c)}.
 \ee

### 2012-07-02 doc/paper-lcr.tex
re-wrote theory

@@
 \flag{but is this the kappa that enters the lens modelling?}
-In the case of several mass sheets at redshifts $\{z_{\mathrm{p}}\}$, with surface mass densities $\{\Sigma_{\mathrm{p}}\}$, the effective convergence is given by the \flag{weighted?} sum :
+In the case of several mass sheets at redshifts $\{z_{\mathrm{p}}\}$, with surface mass densities $\{\Sigma_{\mathrm{p}}\}$, the effective convergence is given by the \flag{weighted?} sum:
 \be \label{eq:kappasum}
@@
 
-In this work our aim is to quantify the lensing contribution from mass sheets that
-are not physically associated with the lens galaxy -- mass-sheets lying infront or behind
-the lens. We also aim to quantify how uncertainties in the estimations of kappa
-propogate into uncertainties on the cosmological parametres which can be inferred
-from measurements of $\Dt$.
+In this work our aim is to quantify the lensing effect of mass-sheets that are physically associated with the lens galaxy -- mass-sheets
+lying infront or behind the lens -- and the uncertainties induced by reconstructing
+those mass-sheets using simple prescriptions applied to potential astronomical observables.
+We also aim to quantify how uncertainties in the
+estimations of $\kappax$ propogate into uncertainties on the cosmological parametres
+which can be inferred from measurements of $\Dt$.
 

### 2012-07-02 doc/paper-lcr.tex
started re-write of theory

@@
 
-%Time delay distances[✓], and the mass sheet degeneracy[✓] - how kappa is degenerate in
+%Time delay distances, and the mass sheet degeneracy - how kappa is degenerate in
 %strong lens models (and magnifications).
+
+Define: convergence.
+
+Where does it crop up? where is it important?
+
+The convergence from an isolated mass sheet is the ratio of the projected surface mass density devided by the critical density at the redshift of the mass sheet.
+\be
+\kappa(\bmath{\theta})= \frac {\Sigma(D_{\rm d} \bmath{\theta})} {\Sigma_{\rm cr}}
+\ee
+where 
+\be \label{eq:sigcrit} 
+\Sigma_{\rm cr} \equiv \frac{c^2 D_{\rm s}}{4 \pi G D_{\rm d} D_{\rm ds}}.
+\ee
 
@@
 at stationary points of the time delay function. For an isolated lens, the time delay
-function can be calculated from calculated from 
+function can be calculated from
 \be \label{eq:T} 
@@
 to the source, and from the lens to the source. The Fermat potential is given by
-defined as
 \be \label{eq:FP}
@@
 \be \label{eq:psikappa}
-\kappa(\bmath{\theta})= \frac {\Sigma(D_{\rm d} \bmath{\theta})} {\Sigma_{\rm cr}}=\frac{1}{2}\nabla^2\psi(\bmath{\theta}),
-\ee
-where 
-\be \label{eq:sigcrit} 
-\Sigma_{\rm cr} \equiv \frac{c^2 D_{\rm s}}{4 \pi G D_{\rm d} D_{\rm ds}}.
+\kappa(\bmath{\theta})= \frac {\Sigma(D_{\rm d} \bmath{\theta})} {\Sigma_{\rm cr}}=\frac{1}{2}\nabla^2\psi(\bmath{\theta}).
 \ee
@@
 is undetectable from the image positions, shapes and relative fluxes; {\it the mass sheet-degeneracy} \citep[see e.g.][for details]{Falco1985,Schneider2006}.
-Similar to Eq.
-\ref{eq:psikappa} the convergence from an isolated mass sheet is by the ratio of the projected surface mass density devided by the critical density at the redshift of the mass sheet.
-\flag{but is this the kappa that enters the lens modelling?}
 In the case of several mass sheets at redshifts $\{z_{\mathrm{p}}\}$, with surface mass densities $\{\Sigma_{\mathrm{p}}\}$, the effective convergence is given by the \flag{weighted?} sum:
@@
 in our lens modelling, if cosmological parameters are to be estimated accurately and
-precisely \citep{suyu2010} from observed time delays.
+precisely from observed time delays \citep{suyu2010}.
 
@@
 \ee
-with which Equation \ref{eq:Tsimp} can be rephrased as
+with which Equation \ref{eq:T} can be rephrased as
 \be
-\Delta t(\bmath{\theta},\bmath{\beta})  =  \frac{\Dt}{c},
+\Delta t(\bmath{\theta},\bmath{\beta})  =  \frac{\Dt}{c} \, \phi(\bmath{\theta},\bmath{\beta})    ,
 \ee 
-Since the time delays are proportional to $1/ (1+ \kappax)$, if there is any external convergence, $\kappax$, that is not included in the lens
+Since the time delays are proportional to $1/ (1+ \kappax)$, if there is any external convergence, that is not included in the lens
 modeling, then the time delay distance -- inferred assuming $\kappax = 0$ -- will be
-$1-\kappax$ less than the true value of $\Dt$.
+$(1-\kappax)$ less than the true value of $\Dt$.
 \be 
@@
 mass-sheet degeneracy by providing an additional estimate of the lens galaxy's mass
-\citep[e.g.,][]{GroginNarayan96a, GroginNarayan96b, TonryFranx99, KoopmansTreu02,
- TreuKoopmans02, BarnabeKoopmans07, suyu2010}.
+\citep[e.g.,][]{citations}.
 
-In this work our aim is to quantify the lensing effect of mass-sheets that are physically associated with the lens galaxy -- mass-sheets
+In this work our aim is to quantify the lensing effect of mass-sheets that are not physically associated with the lens galaxy -- mass-sheets
 lying infront or behind the lens -- and the uncertainties induced by reconstructing
@@
 Cosmological dark matter simulations have shown that dark matter halos are well
-approximated by NFW halos \citep{NFW1997}, with a density profile given by
+approximated by NFW profiles \citep{NFW1997}, with a density profile given by
 \be\label{eq:rhonfw}
@@
 the density slope transitions from $r^{-1}$ to $r^{-3}$. This radius is related
-to the virial radius of the halo by $r_{s} = r_{200}/c$, where $r_{200}$ is the radius at 
+to the virial radius of the halo by $r_{s}~=~r_{200}/c$, where $r_{200}$ is the radius at 
 which 
@@
 \be
-\rho_0 = \rho_{\mathrm{crit}}(z\frac{200}{3}\frac{c^{3}}{\ln(1+c)-c/(1+c)}.
+\rho_0 = \rho_{\mathrm{crit}}(z)\frac{200}{3}\frac{c^{3}}{\ln(1+c)-c/(1+c)}.
 \ee

### 2012-07-04 doc/paper-lcr.tex
more halo stuff

@@
 
-Define: convergence.
-
-Where does it crop up? where is it important?
-
-The convergence from an isolated mass sheet is the ratio of the projected surface mass density devided by the critical density at the redshift of the mass sheet.
+Convergence, or Ricci focusing, occurs when a gravitational lens focuses the rays in a raybundle.
+This focussing can cause distant objects to appear brighter, and larger than they would if the lens
+ were removed.
+The convergence from an isolated mass sheet is the ratio of the projected surface mass density
+(\Sigma) devided by the critical density at the redshift of the mass sheet (\Sigma_{\rm cr}),
 \be
-\kappa(\bmath{\theta})= \frac {\Sigma(D_{\rm d} \bmath{\theta})} {\Sigma_{\rm cr}}
+\kappa(\bmath{\theta})= \frac {{\Sigma} {\Sigma_{\rm cr}(z)}
 \ee
@@
 \be \label{eq:sigcrit} 
-\Sigma_{\rm cr} \equiv \frac{c^2 D_{\rm s}}{4 \pi G D_{\rm d} D_{\rm ds}}.
+\Sigma_{\rm cr}(z) \equiv \frac{c^2 D_{\rm s}}{4 \pi G D_{\rm d} D_{\rm ds}}.
 \ee
+and $D_{\rm d}$, $D_{\rm s}$, and $D_{\rm ds}$ are, respectively, the angular diameter distances from observer to the mass sheet, from observer to the source, and from the mass sheet to the source.
+If the surface mass density of the sheet exceeds $\Sigma_{\rm cr}$, multiple images of the source can
+occur, otherwise only one image will be observed, although that image will still be perturbed
+relative to the unlensed case.
 
@@
 unlensed source position, $z_{\rm d}$ is the redshift of the lens, $\phi(\bmath{\theta},\bmath{\beta})$ is
-the Fermat potential, and $D_{\rm d}$, $D_{\rm s}$, and $D_{\rm ds}$
-are, respectively, the angular diameter distances from observer to the lens, from observer
-to the source, and from the lens to the source. The Fermat potential is given by
+the Fermat potential. The Fermat potential is given by
 \be \label{eq:FP}
@@
 \ee
+Defining $x$ as the dimensionless projected radial distance $R/r_{s}$ , \citet{bartelmann1996} derives the projected mass density, which is given by:
+\be\label{eq:kappanfw}
+\Sigma_{\rm NFW}(x) = 
+\begin{cases}
+  \frac{2r_{s}\delta_{c}\rho_{c}}{x^{2}-1}
+  \left(1-\frac{2}{\sqrt{1-x^{2}}}{\rm arctanh}\sqrt{\frac{1-x}{1+x}}\right)\hspace{0.15cm}
+  & \left(x < 1\right) \\
+\\
+  \frac{2r_{s}\delta_{c}\rho_{c}}{3}
+  & \left(x = 1\right)\\
+\\
+  \frac{2r_{s}\delta_{c}\rho_{c}}{x^{2}-1}
+  \left(1-\frac{2}{\sqrt{x^{2}-1}}\arctan\sqrt{\frac{x-1}{1+x}}
+  \right) 
+  & \left(x > 1\right) 
+\end{cases}
+\ee
+and the convergence is given by $\Sigma_{\rm NFW}(x) / \Sigma_{\rm cr}(z)$.
 
-From the NFW density profile, \citet{wrightbrainerd1999} derive the following quantities
-which are necessary for our line of sight reconstruction:
+Distrubingly, if one integrates the density profile of an NFW profile, the total mass is divergent.
+Similarly, if the universe is homogeneously populated with NFW halos, the projected surface mass along any
+line sight will also be divergant\footnote{At large radius, $\Sigma_{\rm nfw} \propto R^{-2}$, but the differential number of halos centred within an annulus of width $\dee R$ is given by $\dee N_{\rm annulus} \propto R \dee R$, so  $\Sigma_{\rm total} \propto \int_{0}^{\infty} R^{-1} \dee R$, which diverges logarithmically}.
+Since infinite mass is unphysical, the profile must be truncated at some point.
+\flag{previous truncation results}.
+Several truncation profiles have been suggested \citep[e.g][]{BMO}, but beyond several virial radii, the amount of matter associated with a halo is likely to be low \{}
 
-The mass enclosed within radius is given by:
-
-The projected mass density is given by:
-
-The shear is given by:
+%Hayashi2002 - truncation of satellites
 

### 2012-07-04 PDFcreate.py

@@ -79,7 +79,7 @@ def MScompare(argv):
       return
 
    vb = False
-   Ncones = 10
+   Ncones = 1000
    Rcone = 5 # arcmin
    truncationscale=3   # *R_200 halo truncation
   
@@ -218,7 +218,7 @@ def MScompare(argv):
 
    #so now lets draw the cones that we want to creat pdfs for.
 
-   Npdf=10 #how many pdf's do we want?
+   Npdf=1000 #how many pdf's do we want?
    #Ncones=1000 #How many realisations? 
 
    xn = rnd.uniform(xmin+Rcone*arcmin2rad,xmax-Rcone*arcmin2rad,Npdf)
@@ -249,7 +249,7 @@ def MScompare(argv):
       #last term comes from the intrinsic difference in kappa_hilbert vs kappa_reconstruct_truth
 
    #------------------------------------------------------------------
-
+         """
       #Now lets plot the pdfs!
       colors=["b","g","r","y","purple"]
       if n < 5:
@@ -272,11 +272,11 @@ def MScompare(argv):
          plt.legend(loc=1)
          plt.savefig("singlepdf.png")
    plt.show()
-
+   """
 
 
    #output results
-   F=open("pdflist.dat","wb")
+   F=open("pdfs1000e.dat","wb")
    results = kappa_hilbert_n,kappa_Truth_n,kappa_Reconstruct_n
    cPickle.dump(results,F,protocol=2)
 

### 2012-07-04 Pangloss/grid.py

@@ -271,7 +271,7 @@ class lensgrid(grid):
       Mh=numpy.zeros(len(Mstar))
       z=self.snap(z)[0]
       for i in range(len(Mstar)):
-         r = numpy.random.random()
+         if r==None: r = numpy.random.random()
          Mstr = numpy.round(Mst[i]*100.0)/100.
          #print Mstr
          zed=z[i]
@@ -341,9 +341,9 @@ if __name__ == '__main__':
     MFs=cPickle.load(FILE)
     lg.Behroozigrid(MFs)
     
-    MhTrue=10**(numpy.linspace(10,13,20000))
+    MhTrue=10**(numpy.linspace(10,13,2000))
     print MhTrue
-
+    """
     for i in range(len(lg.zplane)):
        Ms=lg.drawMstar(MhTrue,(numpy.ones(len(MhTrue))*lg.zplane[i]))
        #plt.scatter(numpy.log10(MhTrue),numpy.log10(Ms))
@@ -361,4 +361,41 @@ if __name__ == '__main__':
        #plt.show()
     
     #print lg.drawMhalo([  5.75568442e+10,   1.06243864e+11], [ 1.01593,   0.963173])
+    """
+
+    i=4
+    Ms=lg.drawMstar(MhTrue,(numpy.ones(len(MhTrue))*lg.zplane[i]))
+    plt.plot(numpy.log10(MhTrue),numpy.log10(Ms),c='k')
+    plt.plot(numpy.log10(MhTrue),numpy.log10(Ms)+0.15,c='k',ls="dashed")
+    plt.plot(numpy.log10(MhTrue),numpy.log10(Ms)-0.15,c='k',ls="dashed")
+    plt.plot(numpy.log10(MhTrue),numpy.log10(Ms)+0.30,c='k',ls="dotted")
+    plt.plot(numpy.log10(MhTrue),numpy.log10(Ms)-0.30,c='k',ls="dotted")
+    plt.xlabel("log$_{10}$(M$_{\mathrm{halo}}$/M$_{\odot}$)")
+    plt.ylabel("log$_{10}$(M$_{\mathrm{stellar}}$/M$_{\odot}$)")
+    plt.title("P(M$_{\mathrm{stellar}}$|M$_{\mathrm{halo}}$) - Behroozi Relation")
+    plt.savefig("BehrooziConf.png")
[…]

### 2012-07-05 doc/paper-lcr.tex
more halo stuff

@@
 
+%Weak lensing by NFW halos. Accounting for mass along the line of sight.
+%Approximations to full ray tracing:
+%
+%Halos. N-body sims provide mass framework. MS halo catalog. Truncated spherical
+%NFW approx based on virial masses. Stellar mass. Halo map corresponding to
+%ray-traced kappa map, for illustration. Small-scale structure
+
 For real lines of sight, it is nearly impossible to know the true $\kappax$ for a
@@
 Cosmological dark matter simulations can be used to generate mock lines of sight...
-\flag{Stefan's section on how halos are extracted from the MS n-body particles}
+\flag{Stefan's section on how the ray tracing was done and how halos are extracted from
+ the MS n-body particles}
 
@@
  and $c$ is the concentration parameter, which can be estimated from the halo's mass,
-using a mass--concentration relation. Typically more massive halos are more concentrated,
+using a mass--concentration relation. Typically more massive halos are less concentrated,
 but there is some scatter; we use the relation of \citet{neto2007} to estimate $c$
 from the mass enclosed within $r_{200}$, which we denote as $M_{200}$. $\rho_0$ is calculated 
-by the critical density and concentration parameter:
+from the critical density and concentration parameter:
 \be
@@
 
-Distrubingly, if one integrates the density profile of an NFW profile, the total mass is divergent.
+Disturbingly, if one integrates the density profile of an NFW profile, the total mass is divergent.
 Similarly, if the universe is homogeneously populated with NFW halos, the projected surface mass along any
@@
 \flag{previous truncation results}.
-Several truncation profiles have been suggested \citep[e.g][]{BMO}, but beyond several virial radii, the amount of matter associated with a halo is likely to be low \{}
+Several truncation profiles have been suggested \citep[e.g][]{BMO}, but beyond several virial radii, the amount of matter associated with a halo is likely to be low; \citet{Nandra2012} showed that the Universe's expansion can place an upper limit on the radius of NFW halos -- for cluster scale halos, this happens at around 25 times the NFW scale radius.
+In \Sref{sec:knownMh+z} we investigate how different truncations affect the recovered total convergence for a line of sight.
+We will limit our truncations to hard cut--offs, where the density drops to 0 beyond the truncation radius $r_t$.
+This gives
 
-%Hayashi2002 - truncation of satellites
-
-Weak lensing by NFW halos. Accounting for mass along the line of sight.
-Approximations to full ray tracing:
-
-Halos. N-body sims provide mass framework. MS halo catalog. Truncated spherical
-NFW approx based on virial masses. Stellar mass. Halo map corresponding to
-ray-traced kappa map, for illustration. Small-scale structure
+\flag{kappa truncated NFW}
 
@@
 
+\flag{kappa smooth correction.}
+
+Thus the total $\kappax$ for a line of sight is given by 
+\be
+\kappax = \left(\Sum_{halos} \kappa_{halos}\right)-\kappa{smooth}.
+\ee
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Raytracing through n-body particles as 'truth'. Motivation for assuming perfect
-knowledge of halo mass and z = testing model of previous section. Deterministic
-prediction of kappa.
+%Raytracing through n-body particles as 'truth'. Motivation for assuming perfect
+%knowledge of halo mass and z = testing model of previous section. Deterministic
+%prediction of kappa.
+%
+%Is truncation choice important? How deep and wide does a reconstruction need to
+%go? What is the irreducible uncertainty on kappa from this halo model? (Bias and
+%scatter) Can use the ideal reconstruction to ask: Where does the kappa come
+%from? Close to the LoS? Bright objects? How many objects are important? What
+%error is made by considering subsets of available objects?
 
-Is truncation choice important? How deep and wide does a reconstruction need to
-go? What is the irreducible uncertainty on kappa from this halo model? (Bias and
-scatter) Can use the ideal reconstruction to ask: Where does the kappa come
-from? Close to the LoS? Bright objects? How many objects are important? What
-error is made by considering subsets of available objects?
+Given the halo mass catalogue from the Millenium Simulation, and convergence maps produced by
+ray-tracing through the MS's n-body particles, 
+it is possible to test the validity of using a truncated NFW halo model to estimate 
+the external convergence along any given line of sight.
+
+For every halo and subhalo in the catalogue, we estimate a concentration according to
+the best fit relation of \citet{neto2007}:
+\be
+c_{200} = 4.67 (M_{200}/10^{14} h^{-1} \Msun)^{-0.11}
+\ee
+
+Lines of sight are then chosen from random positions in the catalogue, and for each line of
+sight we reconstruct the convergences from every halo within 5 arcminutes and compare the reconstructed
+kappas with those from the ray tracing results of Hilbert et al. We do this for a range of
+truncations, as a function of both the virial and NFW scale radius. The scatter is 
+shown in Figure \ref{fig:ScattervsTruncation}. It is clear from Figure \ref{fig:ScattervsTruncation} 
+that as long as the truncation is greater than the virial radius, the choice of truncation
+radius does not broadly affect the scatter on $\kappah$-$kapparec$; from now on we choose 
+to truncate the halos at three times their virial radius.
 

### 2012-07-05 PDFcreate.py

@@ -79,7 +79,7 @@ def MScompare(argv):
       return
 
    vb = False
-   Ncones = 1000
+   Ncones = 100
    Rcone = 5 # arcmin
    truncationscale=3   # *R_200 halo truncation
   
@@ -110,9 +110,12 @@ def MScompare(argv):
          assert False, "unhandled option"
 
    # Check for datafiles in array args:
-   if len(args) == 2:
+   if len(args) == 4:
       catalog = args[0]
       kappafile = args[1]
+      gammafile1 = args[2]
+      gammafile2 = args[3]
+
       if vb:
          print "Reconstructing convergence in lightcones from:",catalog
          print "Comparing to convergence in:",kappafile
@@ -136,7 +139,9 @@ def MScompare(argv):
     
    MSconvergence = Pangloss.kappamap(kappafile)
    if vb: print "Read in true kappa map, dimension",MSconvergence.NX
-
+   MSshear1 = Pangloss.kappamap(gammafile1)
+   MSshear2 = Pangloss.kappamap(gammafile2)
+   if vb: print "Read in true gamma map, dimension",MSshear.NX
 
    # --------------------------------------------------------------------
 
@@ -162,6 +167,8 @@ def MScompare(argv):
    kappa_Scaled = numpy.zeros(Ncones)
    kappa_Scaled_truth = numpy.zeros(Ncones)
    kappa_hilbert = numpy.zeros(Ncones)
+   gamma_hilbert_2 = numpy.zeros(Ncones)
+   gamma_hilbert_1 = numpy.zeros(Ncones)
    errors=True
 
 
@@ -181,6 +188,8 @@ def MScompare(argv):
 
       # Hilbert Truth:
       kappa_hilbert[k] = MSconvergence.at(x[k],y[k],coordinate_system='physical')
+      gamma_hilbert_1[k] =MSshear1.at(x[k],y[k],coordinate_system='physical')
+      gamma_hilbert_2[k] =MSshear2.at(x[k],y[k],coordinate_system='physical')
       # THE CATALOGUES NEED TRANSPOSING!!!! (don't make that mistake again!)
 
 
@@ -205,12 +214,13 @@ def MScompare(argv):
 
 
    #sanity check - do hilbert and reconstruction look correlated?
-   plt.scatter(kappa_hilbert,kappa_Scaled_truth)
[…]

### 2012-07-05 Pangloss/lightcone.py

@@ -286,15 +286,27 @@ class lens_lightcone(lightcone):
 
 
         
+      #circular mass - not coded in yet.
+      #mass=4*3.14159*rhos*(rs**3)  *     \
+      #    (  numpy.log(1+(R_trunc)/rs) - \
+      #          R_trunc/(rs+R_trunc)    \
+      #          )
 
-        mass=4*3.14159*rho_s*(r_s**3)  *     \
-            (  numpy.log(1+(R_trunc)/r_s) - \
-                   R_trunc/(r_s+R_trunc)    \
+
+        xtrunc=R_trunc/rs
+
+        mass=4*rs*rhos*(
+            (2/(x**2-1)**.5)
+            *
+            numpy.arctan(((x-1.)/(x+1))**.5)
+            +
+            numpy.log(x/2)
             )
 
-        #print "boo"
+
+ 
         self.galaxies.add_column('Mtrunc', mass)
-        #print "hoo"
+ 
 
         kappaNFW=kappa_s*1.0
         shearNFW=kappa_s*1.0

### 2012-07-05 Pangloss/smooth.py

@@ -102,7 +102,9 @@ def smooth(zl,zs,catalogues,truncationscale=10,magnitudecut=99,band='r',nplanes=
 
 
 
-      c200 = Rel.MCrelation(M200,MCerror=errors)
+      c200 = Rel.MCrelation(M200,MCerror=False)
+
+
       #cat.add_column('NetoC', c200)
       snappedz,planes=lg.snap(cat['z_spec'])
       #cat.add_column("snappedplane",planes)
@@ -125,11 +127,27 @@ def smooth(zl,zs,catalogues,truncationscale=10,magnitudecut=99,band='r',nplanes=
          R_trunc[cat.Type == 1]=(r200[cat.Type == 1])*truncationscale
       else: print "what hardcut did you mean?"  
 
+      #circular mass - not coded in yet.
+      #mass=4*3.14159*rhos*(rs**3)  *     \
+      #    (  numpy.log(1+(R_trunc)/rs) - \
+      #          R_trunc/(rs+R_trunc)    \
+      #          )
 
-      mass=4*3.14159*rhos*(rs**3)  *     \
-          (  numpy.log(1+(R_trunc)/rs) - \
-                R_trunc/(rs+R_trunc)    \
-                )
+      xtrunc=R_trunc/rs
+      print c200.max()
+      print c200[M200>1e10].min()
+
+      print xtrunc.max()
+      print xtrunc[M200>1e11].min()
+
+      mass=4*rs*rhos*(
+         (2/(xtrunc**2-1)**.5)
+         *
+         numpy.arctan(((xtrunc-1.)/(xtrunc+1))**.5)
+         +
+         numpy.log(xtrunc/2)
+         )
+
       cat.add_column('Mtrunc', mass)
  
 
@@ -157,14 +175,14 @@ def smooth(zl,zs,catalogues,truncationscale=10,magnitudecut=99,band='r',nplanes=
 
 #-------------------------------------------
 if __name__ == '__main__':
-  test1=False
-  #test2=True
+  test1=True
+  test2=False
 
 
   if test1 ==True:
    #print "running"
 # Kappa Smooth as a function of magnitude cut:
-   d1= "catalogs/GGL_los_8_7_7_0_0_N_4096_ang_4_SA_galaxies_on_plane_27_to_63.images.txt"
[…]

### 2012-07-11 doc/paper-lcr.tex
wrote up keeton

@@
 The convergence from an isolated mass sheet is the ratio of the projected surface mass density
-(\Sigma) devided by the critical density at the redshift of the mass sheet (\Sigma_{\rm cr}),
+($\Sigma(D_{\mathrm{od}}\bmath{\theta})$) devided by the critical surface mass density at the redshift of the mass sheet ($\Sigma_{\rm cr}$),
 \be
-\kappa(\bmath{\theta})= \frac {{\Sigma} {\Sigma_{\rm cr}(z)}
+\kappa(\bmath{\theta})= \frac {\Sigma(D_{\mathrm{od}}\bmath{\theta})}{\Sigma_{\rm cr}(z)}
 \ee
@@
 \be \label{eq:sigcrit} 
-\Sigma_{\rm cr}(z) \equiv \frac{c^2 D_{\rm s}}{4 \pi G D_{\rm d} D_{\rm ds}}.
+\Sigma_{\rm cr}(z) \equiv \frac{c^2 D_{\rm os}}{4 \pi G D_{\rm od} D_{\rm ds}}.
 \ee
-and $D_{\rm d}$, $D_{\rm s}$, and $D_{\rm ds}$ are, respectively, the angular diameter distances from observer to the mass sheet, from observer to the source, and from the mass sheet to the source.
+and the D's are the angular diameter distances between the objects refered to in the subscripts: o is the observer, d is the deflector and s is the source.
 If the surface mass density of the sheet exceeds $\Sigma_{\rm cr}$, multiple images of the source can
@@
 \be \label{eq:T} 
-\Delta t(\bmath{\theta},\bmath{\beta}) = \frac {1}{c} \frac{D_{\rm d} D_{\rm s}}{D_{\rm ds}} (1+z_{\rm d})\, \phi(\bmath{\theta},\bmath{\beta}),
+\Delta t(\bmath{\theta},\bmath{\beta}) = \frac {1}{c} \frac{D_{\rm od} D_{\rm os}}{D_{\rm ds}} (1+z_{\rm d})\, \phi(\bmath{\theta},\bmath{\beta}),
 \ee
@@
 where $\psi(\bmath{\theta})$ is the lens potential, derived from the projected dimensionless
-surface mass density, $\kappa(\bmath{\theta})$, or the physical projected surface mass density,
-$\Sigma(D_{\rm d} \bmath{\theta})$, by 
+surface mass density, $\kappa(\bmath{\theta})$, by 
 \be \label{eq:psikappa}
-\kappa(\bmath{\theta})= \frac {\Sigma(D_{\rm d} \bmath{\theta})} {\Sigma_{\rm cr}}=\frac{1}{2}\nabla^2\psi(\bmath{\theta}).
+\kappa(\bmath{\theta})=\frac{1}{2}\nabla^2\psi(\bmath{\theta}).
 \ee
@@
 is undetectable from the image positions, shapes and relative fluxes; {\it the mass sheet-degeneracy} \citep[see e.g.][for details]{Falco1985,Schneider2006}.
-In the case of several mass sheets at redshifts $\{z_{\mathrm{p}}\}$, with surface mass densities $\{\Sigma_{\mathrm{p}}\}$, the effective convergence is given by the \flag{weighted?} sum:
-\be \label{eq:kappasum}
-\kappax=\frac{4\pi G}{c^2}\sum_{\mathrm{p}}\frac{\Sigma_{\mathrm{p}}D_{\mathrm{p}} D_{{\rm ps}}}{D_{\rm s}}.
-\ee
 
-If the source brightness changes, the observed brightness in each image does not change
+If the intrinsic source brightness changes, the observed brightness in each image does not change
 simultaneously - there is a time delay, $\Delta t$, between the brightness change in
@@
 precisely from observed time delays \citep{suyu2010}.
+
+If the mass sheet is not physically associated with the lens galaxy, it can lie at any redshift.
+The effects of such a mass-sheet can be projected back onto the lens plane in the form of an effective convergence.
+We define this effective convergence in two limits.
+\begin{itemize}
+\item No significant perturbations along the line of sight, and \\
+\item A single dominant perturber, relative to which all other perturbations are small.
+\end{itemize}
+We will refer to these cases as the magnification case (subscript $\mu$ in formulae), and the strong lensing case (subscript SL in formulae), respectively.
+We will ignore the additional case, of a compound lens, with several significant perturbers.
+
+The magnification case has no primary lens plane, and is chiefly relevant for the magnifications of distant objects.
+In the absence of a primary lens plane, we are free to define the effective convergence on any point; the effective convergence is the same, independant of the plane choosen.
+It can be shown \citep[\eg][]{xxx} that if there are several mass sheets at redshifts $\{z_{p}\}$, with convergences $\{\kappa_p =\Sigma_{p}/\Sigma_{\mathrm{cr}}(z_p)\}$, the effective convergence is given by
+\be \label{eq:kappasummu}
+\kappa_{\mathrm{effective,\mu}}=\sum_{p}\kappa_p.
+\ee
+
+In the stong lensing case, the presence of a significant perturber alters the geometry of the system, and provides a primary lens plane.
+It is the primary lens plane upon which we need to know $\kappa_{\mathrm{effective}}$, since this is where the mass-sheet degeneracy is defined.
+Following Equations 20--32 of \citet{keeton2003}\flag{keeton2003}, it can be shown that the relevant effective convergence is given by
+\be \label{eq:kappasumSL}
+\kappa_{\mathrm{effective,SL}}=
+{  
+(1-\beta_{12})(\kappa-\beta_{12}(\kappa^2-\gamma^2))
+\over
+(1-\beta_{12}\kappa)^2-(\beta_{12}\gamma)^2
+}
+\ee
+where $\kappa$ and $\gamma$ are, respectively, the convergence and shear caused by the perturber, in their own plane and $\beta_{12}$ is a geometrical scaling factor defined by
+\be\label{eq:beta}
+\beta_{12}={
+D_{12} D_{\mathrm{os}}
+\over
+D_{\mathrm{o}1} D_{1\mathrm{s}}
+}
+\ee
+where the D's are again angular diameter distances: the 1 (2) in the subscript refers to the lower (higher) redshift object of the lens and perturber.
+For the case that the mass sheet is in the lens plane, $\beta_{12} = 0$ and $\kappa_{\mathrm{eff}}=\kappa$; if the mass-sheet is in the plane of the observer, or source, $\beta_{12} = 1$ and $\kappa_{\mathrm{eff}}=0$; for a mass-sheet at any other redshift $0<\beta_{12}<1$.
+In the case of several mass sheets the effective convergences sum.
+In the limit that both $\kappa$ and $\gamma$ are small, Equation \ref{eq:kappasumSL} reduces to
+\be \label{eq:kappasumSLweak}
+\kappa_{\mathrm{effective,SL}}=(1-\beta_{12})\kappa;
+\ee
+it is this $\kappa_{\mathrm{effective,SL}}$ that we use as $\kappax$ for the strong lensing time delay analysis in \ref{sec:Dt}.
 
@@
 Several truncation profiles have been suggested \citep[e.g][]{BMO}, but beyond several virial radii, the amount of matter associated with a halo is likely to be low; \citet{Nandra2012} showed that the Universe's expansion can place an upper limit on the radius of NFW halos -- for cluster scale halos, this happens at around 25 times the NFW scale radius.
-In \Sref{sec:knownMh+z} we investigate how different truncations affect the recovered total convergence for a line of sight.
-We will limit our truncations to hard cut--offs, where the density drops to 0 beyond the truncation radius $r_t$.
-This gives
+In \Sref{sec:knownMh+z} we investigate how different truncations affect the recovered total convergence for a line of sight, using the truncated NFW profile of \citet{BMO}
+\be\label{eq:bmoprofile}
+\rho(r) = 
+\frac{\rho_0}{\left(r/r_{s}\right)
+\left(1+r/r_{s}\right)^{2}},
+\ee
 
@@
 \be
-\kappax = \left(\Sum_{halos} \kappa_{halos}\right)-\kappa{smooth}.
+\kappax = \left(\sum_{halos} \kappa_{halos}\right)-\kappa{smooth}.
 \ee
@@
 \section{Time Delay Distances}
-\label{sec:}
+\label{sec:Dt}
 

### 2012-07-11 MScompare.py

@@ -78,7 +78,7 @@ def MScompare(argv):
       return
 
    vb = False
-   Ncones = 1000
+   Ncones = 100
    Rcone = 3 # arcmin
    truncationscale=3   # *R_200 halo truncation
   

### 2012-07-11 PDFcreate.py

@@ -79,10 +79,10 @@ def MScompare(argv):
       return
 
    vb = False
-   Ncones = 100
    Rcone = 5 # arcmin
-   truncationscale=3   # *R_200 halo truncation
-  
+   truncationscale=10 # *R_200 halo truncation
+   Ncones=1000
+
    scaling = "add" 
    #scaling = "tom"
    # Defaults are for B1608 (CHECK):
@@ -146,7 +146,7 @@ def MScompare(argv):
    # --------------------------------------------------------------------
 
    #build grid, populate it and invert the behroozi relation on each plane.
-   grid=Pangloss.lensgrid(zl,zs,nplanes=5,cosmo=[0.25,0.75,0.73])
+   grid=Pangloss.lensgrid(zl,zs,nplanes=200,cosmo=[0.25,0.75,0.73])
    grid.populatelensgrid()
    FILE=open("/home/tcollett/Pangloss/Pangloss/MHMS.data")
    MFs=cPickle.load(FILE)
@@ -174,6 +174,7 @@ def MScompare(argv):
 
    #!#!#!# Don't change from these defaults, without good reason!
    #{Mstar2Mh=False,Mh2Mh=True,perfectsatellites=False,centralsonly=False}
+   hardcut="BMO"
    Mstar2Mh=False
    Mh2Mh=True             
    perfectsatellites=False
@@ -194,12 +195,18 @@ def MScompare(argv):
 
 
       # Reconstruction Truth, with perfect knowledge of halo mass: 
-      tc= Pangloss.lens_lightcone(master,Rcone,xc,zl,zs,grid=grid)
-      tc.make_kappa_contributions(hardcut="RVir",truncationscale=truncationscale,scaling=scaling,errors=False,centralsonly=False,perfectsatellites=True,Mh2Mh=False,Mstar2Mh=False)
 
+      t0= time.clock()
+   
+      tc= Pangloss.lens_lightcone(master,Rcone,xc,zl,zs,grid=grid)
+      t1 = time.clock()
+      #print t1-t0
+      tc.make_kappa_contributions(hardcut=hardcut,truncationscale=truncationscale,scaling=scaling,errors=False,centralsonly=False,perfectsatellites=True,Mh2Mh=False,Mstar2Mh=False)
+      t2= time.clock()
+      #print t2-t1
       # Reconstruction, with Behroozi blurred halo masses:
[…]

### 2012-07-11 Pangloss/LensingProfiles.py

@@ -17,9 +17,16 @@ arcmin2rad = (1.0/60.0)*numpy.pi/180.0
 rad2arcmin = 1.0/arcmin2rad
 # ------------------------------------------------------------------------
 def F(x):
-    return numpy.arccos(1/x)/((x**2-1)**.5)
+    z=numpy.ones(len(x))
+    z[x>1]=numpy.arccos(1/x[x>1])/((x[x>1]**2-1)**.5)
+    lowx=x[x<1]
+    z[x<1]=numpy.arccosh(1/x[x<1])/((1-x[x<1]**2)**.5)
+    A=1.+1e-5
+    z[x==1]=numpy.arccos(1/A)/((A**2-1)**.5)
+    return z
+
 def L(x,t):
-    return numpy.log(x/((t**2+x**2)**.5+t))
+    return numpy.log(x/(((t**2+x**2)**.5)+t))
 #=========================================================================
 # NFW profile functions.
 
@@ -77,50 +84,37 @@ def Gfunc(x):
        return z
 
 # ========================================================================
-# BMO1 profile functions.
+# BMO profile functions.
 # ------------------------------------------------------------------------
 def BMO1Ffunc(x,t):
+    #t=float(t)
     z=numpy.zeros(len(x))
-    for i in range(len(x)):
-        X=x[i]
-        T=t[i]
-        if x[i]>1:
-            z[i]= (T**2/(T**2+1)**2)              * ( \
-                (T**2+1)/(X**2-1)*(1-F(X))+2*F(X) -   \
-                3.14159/(T**2+X**2)               +   \
-                ((T**2-1)/(T*(T**2+X**2)**.5))*L(X,T) )
-        else: 
-            z[i]=Ffunc([x[i]])
-        if z[i] < 0: print 'warning BMO1Ffunc'
-    #if len(z) > 1: print z
-    return z
+    z[x!=1]=t**2/(2*(t**2+1)**2)*(
+        ((t**2+1)/(x[x!=1]**2-1))*(1-F(x[x!=1]))
+        +
+        2*F(x[x!=1])
+        -
+        3.14159/(t**2+x[x!=1]**2)**.5
+        +
+        (t**2-1)*L(x[x!=1],t)
+        /
+        (t*(t**2+x[x!=1]**2)**.5)
+        )
+    delta=numpy.array([1.+1e-5])
+    z[x==1]=t**2/(2*(t**2+1)**2)*(
[…]

### 2012-07-11 Pangloss/Relations.py

@@ -13,9 +13,9 @@ def logerr(l,m,s):
 
 def MCrelation(M200,MCerror=False):
       if MCerror==False:
-         c_200 = 4.67*(M200/(10**14))**0.11 #Neto et al. equation 5
+         c_200 = 4.67*(M200/(10**14))**-0.11 #Neto et al. equation 5
       if MCerror==True:
-       c_200=4.67*(M200/(10**14))**0.11
+       c_200=4.67*(M200/(10**14))**-0.11
        logc_200=numpy.log10(c_200)
        lM200 = numpy.log10(M200)
        c_new = c_200*10**(rnd.normal(1,0.2,len(M200)))/10**(1+(0.2**2)/2)

### 2012-07-11 Pangloss/kappamap.py

@@ -232,8 +232,8 @@ class kappamap:
       
 # ============================================================================
 if __name__ == '__main__':
- test1=True
- test2=False
+ test1=False
+ test2=True
  if test1==True:
 # Self-test: read in map from Stefan, and look up some convergence values.
    vb = True
@@ -266,11 +266,11 @@ if __name__ == '__main__':
 # ============================================================================
  if test2 ==True:
     kappafiles=[]
-    kappafiles +=  ["/data/tcollett/Pangloss/kappafiles/GGL_los_8_1_1_N_4096_ang_4_rays_to_plane_37_f.fits"]
-    kappafiles += ["/data/tcollett/Pangloss/kappafiles/GGL_los_8_7_7_N_4096_ang_4_rays_to_plane_37_f.fits"]
+    #kappafiles +=  ["/data/tcollett/Pangloss/kappafiles/GGL_los_8_1_1_N_4096_ang_4_rays_to_plane_37_f.fits"]
+    kappafiles += ["/data/tcollett/Pangloss/kappafiles/GGL_los_8_5_5_N_4096_ang_4_rays_to_plane_37_f.kappa"]
 
     l=4096
-    U=1
+    U=4
 
 
     kappa = numpy.zeros((l/U,l/U,len(kappafiles)))
@@ -278,7 +278,7 @@ if __name__ == '__main__':
 
 
     for k in range(len(kappafiles)):
-       convergence = kappamap(kappafiles[k],FITS=True)
+       convergence = kappamap(kappafiles[k],FITS=False)
        for i in range(l/U):
           if i % 500 ==0 : print k,",",i
           for j in range(l/U):

### 2012-07-11 Pangloss/lightcone.py

@@ -247,6 +247,9 @@ class lens_lightcone(lightcone):
             M200[self.galaxies.Type==2]=self.galaxies['M_Subhalo[M_sol/h]'][self.galaxies.Type==2]
 
 
+        M200=M200[M200>1e1]
+        self.galaxies=self.galaxies.where(M200>1e1)
+
         self.galaxies.add_column('M200',M200)
 
         c200 = Rel.MCrelation(M200,MCerror=errors)
@@ -260,16 +263,6 @@ class lens_lightcone(lightcone):
         r_s = r200/c200
         self.galaxies.add_column('rscale',r_s)
 
-
-        
-        r_s_arcmin  = (r_s / self.galaxies.Da_d) * rad2arcmin
-        r200_arcmin = (r200 / self.galaxies.Da_d) * rad2arcmin
-
-        self.galaxies.add_column('rscale_arcmin',r_s_arcmin)
-        self.galaxies.add_column('r200_arcmin',r200_arcmin)
-
-
-
         rho_s = LP.delta_c(c200)*self.galaxies.rho_crit
         kappa_s = rho_s * r_s /self.galaxies.sigma_crit
     
@@ -277,52 +270,72 @@ class lens_lightcone(lightcone):
         
         if hardcut == "Rvir" or hardcut=="RVir" or hardcut == "r_vir" or hardcut == "rvir":
             R_trunc=truncationscale*r200
+            print "oi leave it"
         elif hardcut == "rs" or hardcut=="Rs" or hardcut == "R_s" or hardcut == "r_s":
             R_trunc=truncationscale*r_s
         elif hardcut== "subhalo":
             R_trunc=3*r200
             R_trunc[self.galaxies.Type == 1]=(r200[self.galaxies.Type == 1])*truncationscale
+        elif hardcut== "BMO" or hardcut== "BMO1" or hardcut== "bmo":
+            R_trunc=truncationscale*r200
+
         else: print "what hardcut did you mean?"
 
 
-        
-      #circular mass - not coded in yet.
-      #mass=4*3.14159*rhos*(rs**3)  *     \
-      #    (  numpy.log(1+(R_trunc)/rs) - \
-      #          R_trunc/(rs+R_trunc)    \
-      #          )
 
 
-        xtrunc=R_trunc/rs
+        R_trunc_arcmin=(R_trunc / self.galaxies.Da_d) * rad2arcmin
+        r_s_arcmin  = (r_s / self.galaxies.Da_d) * rad2arcmin
[…]

### 2012-07-11 Pangloss/smooth.py

@@ -21,7 +21,7 @@ rad2arcmin = 1.0/arcmin2rad
 
 # ======================================================================
 
-def smooth(zl,zs,catalogues,truncationscale=10,magnitudecut=99,band='r',nplanes=100,hardcut="RVir",cosmo=[0.25,0.75,0.73],scaling="add",errors=True,grid=None,BehrooziSpline=None,eBer=1e-99,centralsonly=False, Mh2Mh=False, Mstar2Mh=False, perfectsatellites=False):
+def smooth(zl,zs,catalogues,truncationscale=10,magnitudecut=99,band='r',nplanes=100,hardcut="RVir",cosmo=[0.25,0.75,0.73],scaling="add",errors=True,grid=None,centralsonly=False, Mh2Mh=False, perfectsatellites=False):
    #print time.clock()
    if grid==None:
       lg=GRID.lensgrid(zl,zs,nplanes=nplanes,cosmo=cosmo)
@@ -74,18 +74,29 @@ def smooth(zl,zs,catalogues,truncationscale=10,magnitudecut=99,band='r',nplanes=
       cat['M_Subhalo[M_sol/h]'][cat['M_Subhalo[M_sol/h]']==0.0]=1.0
 
       if Mh2Mh:
-            if BehrooziSpline==None:
-               HALOSTARlowz,STARHALOlowz,HALOSTARhighz,STARHALOhighz=Rel.Behroozi_Spline()
-            else:
-               HALOSTARlowz,STARHALOlowz,HALOSTARhighz,STARHALOhighz=BehrooziSpline[0],BehrooziSpline[1],BehrooziSpline[2],BehrooziSpline[3]
+         Mstar = self.grid.drawMstar(self.galaxies['M_Subhalo[M_sol/h]'],self.galaxies['z_spec'])
 
-            M200 = Rel.Mhalo_to_Mhalo(cat['M_Subhalo[M_sol/h]'],cat['z_spec'],HALOSTARlowz,STARHALOlowz,HALOSTARhighz,STARHALOhighz,eBer=eBer)
-      elif Mstar2Mh:
-            Mstar=10**(numpy.log10(cat['M_Stellar[M_sol/h]'])+rnd.normal(0,eBer,len(cat.z_spec)))
-            M200=Rel.Mstar_to_M200(Mstar,cat['z_spec'],scatter=False)
+         Mstore=Mstar*1.0
 
[…]

### 2012-07-11 Truthcompare.py
created Truthcompare.py - should do everything we need for the perfect knowledge section

@@ -1,0 +1,374 @@
+#!/usr/bin/env python
+# ======================================================================
+
+import Pangloss
+
+import sys,getopt,atpy,pyfits
+import pylab,matplotlib.pyplot as plt
+import numpy
+import numpy.random as rnd
+import distances
+from scipy import optimize
+from scipy import stats
+import cPickle, copy
+import time
+
+arcmin2rad = (1.0/60.0)*numpy.pi/180.0
+rad2arcmin = 1.0/arcmin2rad
+
+N_45mean = 41.8
+N_60mean = 74.475
+N_90mean = 166.864
+N_30mean = 18.831
+N_15mean = 4.812
+
+# ======================================================================
+
+def MScompare(argv):
+   try:
+      opts, args = getopt.getopt(argv,"hvn:r:",["help","verbose","zd","zs"])
+   except getopt.GetoptError, err:
+      print str(err) # will print something like "option -a not recognized"
+      print MScompare.__doc__  # will print the big comment above.
+      return
+
+   vb = False
+   Rcone = 5 # arcmin
+   truncationscale=numpy.linspace(0.5,20,30) # *R_200 halo truncation
+   adoptedtruncationscale=10
+   Ntruncs=len(truncationscale)
+   Ncones=1000
+   magcuts=numpy.linspace(14,27,50)
+
+
+   scaling = "add" 
+   #scaling = "tom"
+   # Defaults are for B1608 (CHECK):
+   zl = 0.62
+   zs = 1.39
+  
+   for o,a in opts:
+      if o in ("-v", "--verbose"):
+         vb = True
+      elif o in ("-n"):
+         Ncones = int(a)
+      elif o in ("-r"):
+         Rcone = a
+      elif o in ("-t"):
+         truncationscale = a 
+
+      elif o in ("--zl"):
+         zl = a
+      elif o in ("--zs"):
+         zs = a
+      elif o in ("-h", "--help"):
+         print MScompare.__doc__
+         return
+      else:
+         assert False, "unhandled option"
+
+   # Check for datafiles in array args:
+   if len(args) == 4:
+      catalog = args[0]
+      kappafile = args[1]
+      gammafile1 = args[2]
+      gammafile2 = args[3]
+
+      if vb:
[…]

### 2012-07-11 doc/paper-lcr.tex
more halo stuff

@@
 but there is some scatter; we use the relation of \citet{neto2007} to estimate $c$
-from the mass enclosed within $r_{200}$, which we denote as $M_{200}$. $\rho_0$ is calculated 
-from the critical density and concentration parameter:
+from the mass enclosed within $r_{200}$, which we denote as $M_{200}$. The best fit relation of \citet{neto2007} is given by
+\be
+c_{200} = 4.67 (M_{200}/10^{14} h^{-1} \Msun)^{-0.11}.
+\ee
+$\rho_0$ is calculated from the critical density and concentration parameter:
 \be
@@
 \ee
-Defining $x$ as the dimensionless projected radial distance $R/r_{s}$ , \citet{bartelmann1996} derives the projected mass density, which is given by:
-\be\label{eq:kappanfw}
-\Sigma_{\rm NFW}(x) = 
-\begin{cases}
-  \frac{2r_{s}\delta_{c}\rho_{c}}{x^{2}-1}
-  \left(1-\frac{2}{\sqrt{1-x^{2}}}{\rm arctanh}\sqrt{\frac{1-x}{1+x}}\right)\hspace{0.15cm}
-  & \left(x < 1\right) \\
-\\
-  \frac{2r_{s}\delta_{c}\rho_{c}}{3}
-  & \left(x = 1\right)\\
-\\
-  \frac{2r_{s}\delta_{c}\rho_{c}}{x^{2}-1}
-  \left(1-\frac{2}{\sqrt{x^{2}-1}}\arctan\sqrt{\frac{x-1}{1+x}}
-  \right) 
-  & \left(x > 1\right) 
-\end{cases}
-\ee
-and the convergence is given by $\Sigma_{\rm NFW}(x) / \Sigma_{\rm cr}(z)$.
 
@@
 Similarly, if the universe is homogeneously populated with NFW halos, the projected surface mass along any
-line sight will also be divergant\footnote{At large radius, $\Sigma_{\rm nfw} \propto R^{-2}$, but the differential number of halos centred within an annulus of width $\dee R$ is given by $\dee N_{\rm annulus} \propto R \dee R$, so  $\Sigma_{\rm total} \propto \int_{0}^{\infty} R^{-1} \dee R$, which diverges logarithmically}.
-Since infinite mass is unphysical, the profile must be truncated at some point.
+line sight will also be divergant\footnote{At large radius, $\Sigma_{\rm nfw} \propto R^{-2}$, but the differential number of halos centred within an annulus of width $\dee R$ is given by $\dee N_{\rm annulus} \propto R \dee R$, so  $\Sigma_{\rm total} \propto \int_{0}^{\infty} R^{-1} \dee R$, which diverges logarithmically}.Since infinite mass is unphysical, the profile must be truncated at some point.
 \flag{previous truncation results}.
@@
 \rho(r) = 
-\frac{\rho_0}{\left(r/r_{s}\right)
-\left(1+r/r_{s}\right)^{2}},
+\frac{\rho_{\rm NFW} (r)}{1+\left(r/r_{t}\right)^2},
 \ee
+which is the same as the NFW profile in the limit that $r_t$ goes to infinity.
+Defining $x$ as the dimensionless projected radial distance $R/r_{s}$ and $\tau$ as the dimensionless truncation radius $r_{t}/r_{s}$, \citet{BMO} derives the projected mass density, which is given by:
+\begin{align}\label{eq:kappaBMO}
+\Sigma_{\rm BMO}(x) = {2\tau^2 \over (\tau^2+1)^2}\left(
+        {\tau^2+1\over x^2-1}\left(1-\mathcal{F}(x)\right)
+        +
+        2\mathcal{F}(x)\right.\nonumber\\
+        -
+        \left. {\pi \over \sqrt{\tau^2+x^2}}
+        +
+        {(\tau^2-1)\mathcal{L}(x,\tau)
+        \over
+        \tau\sqrt{\tau^2+x^2}}\right)
+\end{align}
+where $\mathcal{F}(x)$ and $\mathcal{L}(x,\tau)$ are defined as
+\be\label{eq:F} 
+\mathcal{F}(x) \equiv \begin{cases}  \frac{{\rm cos}^{-1} (1/x)}{\sqrt{x^2-1}} \hspace{0.2cm} & (x>1) \\
+\\
+\frac{4-x^2}{3}  & (x=1)\\
+\\
+\frac{ {\rm cosh}^{-1} (1/x)}{\sqrt{1-x^2}} & (x<1)
+\end{cases}
+\ee
+\be\label{eq:L}
+\mathcal{L}(x,\tau) = \ln\left(\frac{x}{\sqrt{\tau^2+x^2}+\tau}\right)
+\ee
+%the convergence is given by $\Sigma_{\rm BMO}(x) / \Sigma_{\rm cr}(z)$.
 
-\flag{kappa truncated NFW}
-
-Not all DM is in halo catalog. Smooth component approximation.  How voids
-produce a negative kappa - filled beam distances require halos and voids to
-provide density contrast relative to mean. How we correct for voids. Comments on
-reasonable, but unphysical nature of this approach, tests to follow.
-
-\flag{kappa smooth correction.}
-
-Thus the total $\kappax$ for a line of sight is given by 
-\be
-\kappax = \left(\sum_{halos} \kappa_{halos}\right)-\kappa{smooth}.
+Whilst halos contribute a positive convergence to $\kappax$, voids contribute a negative convergence. When a raybundle passes through a 
+region of space that is less dense than $\rho_{\rm cr}(z)$ the rays are de-focused\footnote{In principle, the convergence caused by halos, is also caused by the overdensity, but we neglect this effect since halos are typically much more dense than the intergalactic medium}.
+Whilst the
+full raytraced solution takes into account the effect of voids, our reconstruction cannot -- the halo catalogue does not include voids.
+In principle the absence of a halo could be taken to infer a void, but the under-density of such a void is hard to infer.
+Instead, we shift our $\kappax$ values so that $\langle\kappax\rangle=0$.
+We refer to this corrective term as $\kappav$.
+The void correction introduces a source of error, since the inferred value of $\kappav$ will depend on the properties of the sightlines reconstructed, but this error shrinks with the number of sightlines reconstructed.
+To avoid potential biases we calculate $\kappav$ from randomly selected sightlines.
+The total $\kappax$ along the line of sight is given by
+\be \label{eq:totalkappax}
+\kappax = \left(\sum_{\rm halos} \kappa_{\rm halo}\right)-\kappav.
 \ee
@@
 
-For every halo and subhalo in the catalogue, we estimate a concentration according to
-the best fit relation of \citet{neto2007}:
-\be
-c_{200} = 4.67 (M_{200}/10^{14} h^{-1} \Msun)^{-0.11}
-\ee
-
 Lines of sight are then chosen from random positions in the catalogue, and for each line of
 sight we reconstruct the convergences from every halo within 5 arcminutes and compare the reconstructed
-kappas with those from the ray tracing results of Hilbert et al. We do this for a range of
-truncations, as a function of both the virial and NFW scale radius. The scatter is 
+kappas with those from the ray tracing results. The standard deviation on  
 shown in Figure \ref{fig:ScattervsTruncation}. It is clear from Figure \ref{fig:ScattervsTruncation} 
-that as long as the truncation is greater than the virial radius, the choice of truncation
-radius does not broadly affect the scatter on $\kappah$-$kapparec$; from now on we choose 
-to truncate the halos at three times their virial radius.
+that as long as the truncation is greater than a few virial radii, the choice of truncation
+radius does not broadly affect the scatter on $\kapparay$-$kapparec$; from now on we choose 
+to truncate the halos at ten times their virial radius.
 

### 2012-07-11 Truthcompare.py

@@ -34,11 +34,12 @@ def MScompare(argv):
 
    vb = False
    Rcone = 5 # arcmin
-   truncationscale=numpy.linspace(0.5,20,30) # *R_200 halo truncation
+   truncationscale=numpy.linspace(0.5,6,20) # *R_200 halo truncation
+   truncationscale=numpy.append(truncationscale,[7,8,9,10,12,14,16,18,20])
    adoptedtruncationscale=10
    Ntruncs=len(truncationscale)
    Ncones=1000
-   magcuts=numpy.linspace(14,27,50)
+   magcuts=numpy.linspace(14,26,50)
 
 
    scaling = "add" 
@@ -354,12 +355,15 @@ def MScompare(argv):
    if investigateT:
       results =  x,y,kappa_hilbert,truncationscale,kappa_scatter_truth,kappa_Scaled_truth
       cPickle.dump(results,F,protocol=2)
+      F.close()
    if investigateM:
       results =  x,y,kappa_hilbert,magcuts,kappa_16_M,kappa_50_M,kappa_84_M,kappa_Scaled_truth_M
-      cPickle.dump(results,F,protocol=2)
+      cPickle.dump(results,G,protocol=2)
+      G.close()
    if investigateR:
       results =  x,y,kappa_hilbert,Rcuts,kappa_16_R,kappa_50_R,kappa_84_R,kappa_Scaled_truth_R
       cPickle.dump(results,H,protocol=2)
+      H.close()
 # ======================================================================
 
 if __name__ == '__main__':

### 2012-07-16 doc/paper-lcr.tex
magnitudes and radiu

@@
 ray-tracing through the MS's n-body particles, 
-it is possible to test the validity of using a truncated NFW halo model to estimate 
-the external convergence along any given line of sight.
-
-Lines of sight are then chosen from random positions in the catalogue, and for each line of
-sight we reconstruct the convergences from every halo within 5 arcminutes and compare the reconstructed
-kappas with those from the ray tracing results. The standard deviation on  
+it is possible to test the validity of the prescription outlined in Section \ref{sec:model}. We do this
+using $\kapparay$ as a proxy for $\kappatrue$. The reconstruction prescription is tested given perfect
+knowledge of the halos' virial masses and redshifts; this provides us with a measure of the intrinsic
+errors induced by treating matter as truncated NFW halos. To quantify this 10000 lines of sight are chosen
+from random positions in the catalogue, and for each line of sight we reconstruct the
+convergences from every halo within 5 arcminutes and compare the reconstructed
+kappas with those from the ray tracing results. The standard deviation on $\kapparay$-$\kapparec$ 
 shown in Figure \ref{fig:ScattervsTruncation}. It is clear from Figure \ref{fig:ScattervsTruncation} 
 that as long as the truncation is greater than a few virial radii, the choice of truncation
-radius does not broadly affect the scatter on $\kapparay$-$kapparec$; from now on we choose 
-to truncate the halos at ten times their virial radius.
+radius does not broadly affect the scatter on $\kapparay-\kapparec$; from now on we choose 
+to truncate the halos at $10 \Rhalo$. Since $\sigma\left(\kapparay-\kapparec\right)$ does not go to
+zero, it is clear that out halo based prescription does not perfectly replicate the n-body results, we refer to this
+ as the intrinsic error of the prescription. The intrinsic error has a standard deviation of $\sigi \sim 0.018$, although
+this figure is inflated by a few outliers in the tails of $\pr\left(\kapparay-\kapparec\right)$. Whilst we do not
+focus on shear in this work, such outliers would likely be rejected by their reconstructed shear not matching the
+shear of the lens model (see \citet{wong} for the practicalities of this), this makes our estimate of the intrinsic error pessimistic.
+
+\tom{this paragraph is phrased badly}
+If $\kapparec$ is to be used in a real survey it is important that it is not a biased estimator of the true $\kappax$. 
+Ideally one wants $\langle \kapparec-\kappatrue \rangle$ to equal 0 and $\kapparec-\kappatrue$ to be independant of
+$\kapparec$., since the void correction ensures $\langle \kapparec \rangle = 0$ any bias in $\langle \kapparec-\kapparay \rangle$ comes
+from the variations in $\kapparay$. With 8.2$\times 10^8$ pixels, uniformly spaced over 196 deg$^2$ of simulated sky,
+ $\langle \kapparay \rangle$ = -0.00014. However, it is improbable that such a large number of lines of sight
+ could be reconstructed in reality and the mean of $\kappatrue$ for a small subset of sightlines will not necessarily
+equal zero. We find this error to be
+\be\label{eq:sigmav}
+\sigma(\kappav) \simeq 0.036 / N^{\frac{1}{2}},
+\ee
+ where $N$ is the number of lines of sight, although $\pr(\kappav)$ has positive skew for small $N$.
+ Care must be taken that the callibration lines of sight are not biased in $\kappax$ or the final $\pr(\kappav)$ will also be biased.
+For the rest of this work we use 1000  randomly chosen calibration lines of sight to calculate $\kappav$, introducing an error on $\kappax$ of $0.001$.
+1000 callibration lines of sight is unfeasable currently, but should be reasonable in the LSST era.
+Since the true $\langle \kapparay \rangle$ = -0.00014 is two orders of magnitude smaller than intrinsic error of the halo prescription, $\kapparec$ can be seen as unbiased given a large enough sample of lines of sight.
+For an individual line of sight $\kapparec$ can also be shown
+\begin{figure}\label{fig:magcut}
+\includegraphics[width=\columnwidth]{mag_scatter.eps}
+\end{figure}
+\begin{figure}\label{fig:radcut}
+\includegraphics[width=\columnwidth]{radius_scatter.eps}
+\end{figure}
+The error from the void correction, and the intrinsic error from the halo based prescription are unavoidable errors, even with perfect knowledge of halo mass and position.
+Before investigating the errors caused by imperfect knowledge of halo mass and redshift, we investigate the errors induced by a magnitude limited reconstruction and a field of view limited reconstruction.
+The halos in our catalogue are given magnitudes by the semi-analytic model of \citet{SAM} and by applying magnitude cuts to our catalogue, we can investigate the scatter caused by unobserved halos.
+The majority of the convergence comes from halos with an $i$ magnitude between 18 and 24.
+Figure \ref{fig:magcut} shows that the width of $\kapparec-\kapparay$ decreases quickly between $i=18$ and $i=24$.
+Objects brighter than $i=18$ are either too rare or too close to the observer to make a significant contribution to the convergence.
+Objects fainter than $i=24$ are too small to be important unless they are extremely close to the line of sight where it is likely that neglecting stellar mass and using a spherical NFW prescription are too naive to adequately reconstruct $\kappax$ - it is likely that these ultra-faint halos (or substructures) are the major source of the scatter in $\kapparec-\kapparay$, but a deeper survey will not be sufficient to decrease the size of this scatter.
+Since a large number of callibration lines of sight are needed to shrink the width of $\pr(\kappav)$, it may prove unrealistic to reconstruct the calibration lines of sight out to 5 arcminutes.
+\citet{Auger2007} showed that the majority significant perturbers are within 15 arcseconds of the lens.
+Figure \ref{fig:radcut} shows the width of $\kapparec-\kapparay$ as a function of reconstruction radius; in almost all cases there is no significant contribution to $\kappa$ from halos that are centred more than 1 arcminute away, although large groups or clusters can sometimes still make a contribution as far out as four arcminutes.
+For the rest of this work we will continue to model all of the halos out to 5 arminutes with an $i$ magnitude greater than 26, although a reconstruction with fields going out to two arcminutes and down to $i<24$ would do almost as well.
 
@@
 Ideas for improving the procedure
+
+Emphasize that this can be done before monitoring time is invested.
 

### 2012-07-16 Pangloss/grid.py

@@ -329,6 +329,13 @@ if __name__ == '__main__':
     zl,zs=0.6,1.4    
     lg=lensgrid(zl,zs,nplanes=20)
     lg.populatelensgrid()
+    plt.plot(lg.zplane,lg.beta_p)
+    plt.show()
+
+    print numpy.mean(lg.beta_p)
+
+
+
     #filename='lensgrid_zl%.2f_zs%.2f.pcl'%(zl,zs)
     #filename='test1.test'
 
@@ -341,6 +348,9 @@ if __name__ == '__main__':
     MFs=cPickle.load(FILE)
     lg.Behroozigrid(MFs)
     
+
+
+
     MhTrue=10**(numpy.linspace(10,13,2000))
     print MhTrue
     """

### 2012-07-16 Pangloss/kappamap.py

@@ -10,6 +10,8 @@ to-do
 import numpy, os, string
 import struct, pyfits
 import pylab as plt
+import random as rnd
+import cPickle
 
 arcmin2rad = (1.0/60.0)*numpy.pi/180.0
 rad2arcmin = 1.0/arcmin2rad
@@ -267,11 +269,12 @@ if __name__ == '__main__':
  if test2 ==True:
     kappafiles=[]
     #kappafiles +=  ["/data/tcollett/Pangloss/kappafiles/GGL_los_8_1_1_N_4096_ang_4_rays_to_plane_37_f.fits"]
-    kappafiles += ["/data/tcollett/Pangloss/kappafiles/GGL_los_8_5_5_N_4096_ang_4_rays_to_plane_37_f.kappa"]
+    for i in range(7):
+       for j in range(7):
+          kappafiles += ["/data/tcollett/Pangloss/kappafiles/GGL_los_8_%i_%i_N_4096_ang_4_rays_to_plane_37_f.kappa"%(i+1,j+1)]
 
     l=4096
-    U=4
-
+    U=16
 
     kappa = numpy.zeros((l/U,l/U,len(kappafiles)))
     print numpy.shape(kappa)
@@ -286,7 +289,15 @@ if __name__ == '__main__':
 
     kappa=kappa.ravel()
 
+    F=open("kappalist.dat","wb")
+    cPickle.dump(kappa,F,protocol=2)
     print numpy.mean(kappa)
+
+
+    #estimating kappa from a subset of n lines:
+
+
+
 
 
     plt.hist(kappa)

### 2012-07-16 Truthcompare.py

@@ -185,7 +185,7 @@ def MScompare(argv):
             tc.make_kappa_contributions(hardcut=hardcut,truncationscale=truncationscale[T],scaling=scaling,errors=False,centralsonly=False,perfectsatellites=True,Mh2Mh=False,Mstar2Mh=False)
             kappa_Scaled_truth[k,T]=tc.kappa_Scaled_total
          #keep only the columns that we don't need to overwrite
-            tc.galaxies.keep_columns(['GalID','HaloID','SubhaloID','Type','PlaneNumber','z_spec','pos_0[rad]','pos_1[rad]','Dc_los[Mpc/h]','M_Halo[M_sol/h]','M_Subhalo[M_sol/h]','M_Stellar[M_sol/h]','mag_SDSS_u','mag_SDSS_g','mag_SDSS_r','mag_SDSS_i','mag_SDSS_z','mag_J','mag_H','mag_K','x','y','r','zsnapped','psnapped','Da_d','Da_ds','Da_dl','beta','rho_crit','sigma_crit','rphys'])
+            tc.galaxies.keep_columns(['GalID','HaloID','SubhaloID','Type','PlaneNumber','z_spec','pos_0[rad]','pos_1[rad]','Dc_los[Mpc/h]','M_Halo[M_sol/h]','M_Subhalo[M_sol/h]','M_Stellar[M_sol/h]','mag_SDSS_u','mag_SDSS_g','mag_SDSS_r','mag_SDSS_i','mag_SDSS_z','mag_J','mag_H','mag_K','x','y','r','zsnapped','psnapped','Da_d','Da_ds','Da_dl','beta','rho_crit','sigma_crit','rphys',"mag_F814W"])
 
       #now do magnitude cut catalogues
       if investigateM or investigateR:
@@ -207,7 +207,7 @@ def MScompare(argv):
 
 
       #keep only the columns that we don't need to overwrite
[…]

### 2012-07-27 doc/paper-lcr.tex
added figures

@@
 \begin{align}\label{eq:kappaBMO}
-\Sigma_{\rm BMO}(x) = {2\tau^2 \over (\tau^2+1)^2}\left(
+\Sigma_{\rm}(x) = {2\tau^2 \over (\tau^2+1)^2}\left(
         {\tau^2+1\over x^2-1}\left(1-\mathcal{F}(x)\right)
@@
 
+\begin{figure}\label{fig:ScattervsTruncation}
+\includegraphics[width=\columnwidth]{truncation_scatter.eps}
+\caption[magcut]{}
+\end{figure}
+
 \tom{this paragraph is phrased badly}
@@
 1000 callibration lines of sight is unfeasable currently, but should be reasonable in the LSST era.
-Since the true $\langle \kapparay \rangle$ = -0.00014 is two orders of magnitude smaller than intrinsic error of the halo prescription, $\kapparec$ can be seen as unbiased given a large enough sample of lines of sight.
-For an individual line of sight $\kapparec$ can also be shown
+Since the true $\langle \kapparay \rangle$ = -0.00014 is two orders of magnitude smaller than intrinsic error of the halo prescription, $\kapparec$ can be seen as unbiased given a large enough sample of lines of sight and Figure \ref{fig:bias} shows that there is no statistically significant evidence that $\kapparec$ is a biased estimator, regardless of the individual value of $\kapparec$.
+
+\begin{figure}\label{fig:isitbiased}
+\includegraphics[width=\columnwidth]{isitbiased.eps}
+\caption[Biased?]{}
+\end{figure}
 \begin{figure}\label{fig:magcut}
 \includegraphics[width=\columnwidth]{mag_scatter.eps}
+\caption[magcut]{}
 \end{figure}
@@
 \includegraphics[width=\columnwidth]{radius_scatter.eps}
+\caption[radius cut]{}
 \end{figure}
+
 The error from the void correction, and the intrinsic error from the halo based prescription are unavoidable errors, even with perfect knowledge of halo mass and position.
@@
 \label{sec:obsMstar+z}
+
+Real attempts to reconstruct the convergence along a line of sight will not have direct access to the masses of dark matter halo, 
+and will likely not have access to their spectroscopic redshift either. Instead these properties must be inferred from astrophysical
+observables. In principle the only observables are astrometric positions, photometric colours and possibly spectra. In this section we
+quantify the errors induced by inferring the halo mass and redshift from the observables. Much work has already focused on using
+photometric colours to infer stellar mass \citep[\eg][]{augerstellarpops} and redshifts \citep[\eg][]{BPZ}, in line with these we shall use
+stellar mass and photometric redshifts (with appropriate errors), as the observables that must be converted into an estimate
+of $\kappax$. We will investigate three main sources of error: inferring halo mass given observed stellar mass; halos at the wrong redshift
+due to photometric redshift error, and; the combination of both redshift and stellar mass errors.
 

### 2012-07-27 Pangloss/grid.py

@@ -264,6 +264,60 @@ class lensgrid(grid):
        # Use like: MhaloFromMstar_given_z[z][Ms]
 
 
+   def gaussian(self,x,mu,sig):
+      return numpy.exp(-0.5*((x-mu)/sig)**2)/(sig*(2*3.14159)**.5)
+
+   def SMF(self,M,z):
+      M0 = 11.16
+      M1 =  0.17
+      M2 = -0.07
+      a0 = -1.18
+      a1 = -0.082
+      phi0 = 0.0035
+      phi1 = -2.2
+      phi=phi0*((1+z)**phi1)
+      Mz=M0+M1*z+M2*z**2
+      alphaz=a0+a1*z
+      DM=M-Mz
+      GSMF=phi * numpy.log(10) * ((10**(M-Mz)) ** (1+alphaz)) * numpy.exp(-(10 ** (M-Mz)))
+      return GSMF
+
+   def SMFgrid(self):
+      MstarFromMstarOBS15zed = {}
+      MstarFromMstarOBS45zed = {}
+      self.Mstarwidth=0.01
+      Msbins=numpy.linspace(3.5,16.5,1301)
+      for z in self.zplane:
+         MstarFromMstarOBS15 = {}
+         MstarFromMstarOBS45 = {}
+         for i in range(len(Msbins)):
+            Ms=Msbins[i]
+            Ms=numpy.around(Ms, decimals=2)
+            Mses=numpy.arange(Ms-3.,Ms+3.,self.Mstarwidth)
+            P1=self.SMF(Mses,z)
+            P2a=self.gaussian(Mses,Ms,0.15)
+            P2b=self.gaussian(Mses,Ms,0.45)
+            Pa=P1*P2a
+            Pb=P1*P2b
+            if len(Pa[Pa<0])+len(Pb[Pb<0])==0:
+               CDFa=numpy.cumsum(Pa)/numpy.sum(Pa)     
+               CDFb=numpy.cumsum(Pb)/numpy.sum(Pb)  
+               A=((CDFa != 0.0) & (CDFa!=1.0))
+               Msesa=Mses[A]
+               CDFa=CDFa[A]
+               B=((CDFb!=0.0)&(CDFb!=1.0))
+               Msesb=Mses[B]
+               CDFb=CDFb[B]
+               MstarFromMstarOBS15[int(numpy.around(Msbins[i]*100))]=interpolate.splrep(CDFa,Msesa)
[…]

### 2012-07-27 Pangloss/lightcone.py

@@ -87,6 +87,7 @@ class lightcone(object):
         self.galaxies.add_column('x',x)
         self.galaxies.add_column('y',y)
         self.galaxies.add_column('r',r)
+        self.galaxies.add_column('z_true',self.galaxies.z_spec)
         self.galaxies = self.galaxies.where(self.galaxies.r < self.rmax)
         F814 = (self.galaxies.mag_SDSS_i + self.galaxies.mag_SDSS_z)/2. #approximate F814 colour.
         self.galaxies.add_column("mag_F814W",F814)
@@ -137,7 +138,7 @@ class lightcone(object):
 # ============================================================================
 
 class lens_lightcone(lightcone):
-    def __init__(self,catalog,position,radius,zl,zs,nplanes=100,cosmo=[0.25,0.75,0.73],magnitudecut=99,band="r",grid=None):
+    def __init__(self,catalog,position,radius,zl,zs,nplanes=100,cosmo=[0.25,0.75,0.73],magnitudecut=99,band="r",grid=None,photozerr=False):
         self.name = 'Snapped Lens Lightcone through the observed Universe'
         lightcone.__init__(self,catalog,radius,position,magnitudecut=magnitudecut,band=band)
         if grid==None:
@@ -147,15 +148,6 @@ class lens_lightcone(lightcone):
             MFs=cPickle.load(FILE)
             self.grid.Behroozigrid(MFs)
         else: self.grid=grid
-
-
-        #correct M_subhalos that == 0
-        #Msub=self.galaxies['M_Subhalo[M_sol/h]']
-        #Mhal=self.galaxies['M_Halo[M_sol/h]']
-        #Msub[Msub==0]=Mhal[Msub==0]
-        #self.galaxies.remove_columns("M_Subhalo[M_sol/h]")
-        #self.galaxies.add_column("M_Subhalo[M_sol/h]",Msub)
-
 
         self.galaxies=self.galaxies.where(self.galaxies.z_spec < zs)
 
@@ -187,7 +179,21 @@ class lens_lightcone(lightcone):
 
 # ----------------------------------------------------------------------------
 
-    def make_kappa_contributions(self,BehrooziHalos=False,hardcut="Rvir",truncationscale=5,scaling="add",errors=True,centralsonly=False, Mh2Mh=False, Mstar2Mh=False, perfectsatellites=False): 
+    def mimik_photozerror(self, photozerr=True):
+        if photozerr==True:
[…]

### 2012-07-27 Truthcompare.py

@@ -36,7 +36,7 @@ def MScompare(argv):
    Rcone = 5 # arcmin
    truncationscale=numpy.linspace(0.5,6,20) # *R_200 halo truncation
    truncationscale=numpy.append(truncationscale,[7,8,9,10,12,14,16,18,20])
-   adoptedtruncationscale=10
+   adoptedtruncationscale=5
    Ntruncs=len(truncationscale)
    Ncones=1000
    magcuts=numpy.linspace(14,26,50)
@@ -350,8 +350,8 @@ def MScompare(argv):
 
    #output results
    F=open("truncresults%i.dat"%oneseven,"wb")
-   G=open("magresults%i.dat"%oneseven,"wb")
-   H=open("radresults%i.dat"%oneseven,"wb")
+   G=open("magresults%i_%i.dat"%(oneseven,adoptedtruncationscale),"wb")
+   H=open("radresults%i_%i.dat"%(oneseven,adoptedtruncationscale),"wb")
    if investigateT:
       results =  x,y,kappa_hilbert,truncationscale,kappa_scatter_truth,kappa_Scaled_truth
       cPickle.dump(results,F,protocol=2)
@@ -368,7 +368,7 @@ def MScompare(argv):
 
 if __name__ == '__main__':
    everything = True
-   investigateT=True
+   investigateT=False
    investigateR=True
    investigateM=True
    oneseven=1 #calculate on patch 1_1 or 7_7?

### 2012-08-07 doc/paper-lcr.tex
more writeup

@@
 quantify the errors induced by inferring the halo mass and redshift from the observables. Much work has already focused on using
-photometric colours to infer stellar mass \citep[\eg][]{augerstellarpops} and redshifts \citep[\eg][]{BPZ}, in line with these we shall use
+photometric colours to infer stellar mass \citep[\eg][]{xxx} and redshifts \citep[\eg][]{BPZ}, in line with these we shall use
 stellar mass and photometric redshifts (with appropriate errors), as the observables that must be converted into an estimate
@@
 due to photometric redshift error, and; the combination of both redshift and stellar mass errors.
+
+We generate a stellar mass for each halo according to the stellar mass-halo mass relation of \citet{behroozi2010}. From this stellar mass we simulate 
+an observed stellar mass by drawing a stellar mass from $\pr(M*_{\mathrm {obs}}|M*_{\mathrm {true}})$.
+We draw our samples from $\pr(\log(M*_{\mathrm {obs}})|\log(M*_{\mathrm {true}}))$ is given by the product of the galaxy stellar mass function (GSMF) of \citet{Fontana2006} and a Gaussian of width $\sigma_{M*}$ centred on $\log(M*_{\mathrm {true}})$.
+Where a spectroscopic redshift exists stellar masses can be estimated with a typical uncertainties of 0.15 dex \citep{xxx}, however with photometric redshifts stellar mass uncertainties are typically three times as large; we use $\sigma_{M*}=0.15$ for halos with a spectroscopic redshift and $\sigma_{M*}=0.45$ otherwise.
+The \citet{Fontana2006} GSMF is given by a Schechter function with redshift evolving parameters
+\be
+\label{eq:GSMF}
+{\dee N \over \dee M*} \propto \left(10^{(M*-M_0(z))}\right)^(1+\alpha(z))) \exp \left(-(10^(M*-M_0(z)))\right)
+\ee 
+where $M_0(z)=11.16+0.17*z-0.07*z**2$ and $\alpha(z)=-1.18-0.082*z$.
 

### 2012-08-07 Pangloss/grid.py

@@ -60,7 +60,7 @@ class grid(distances.Distance):
        self.cosmo=cosmo
 
    def snap(self,z):
-      snapped_p=numpy.digitize(z,self.zplane-self.dz)-1
+      snapped_p=numpy.digitize(z,self.zplane-(self.dz)/2)-1
       snapped_z=self.zplane[snapped_p]
       return snapped_z,snapped_p
 

### 2012-08-07 Pangloss/lightcone.py

@@ -148,7 +148,6 @@ class lens_lightcone(lightcone):
             MFs=cPickle.load(FILE)
             self.grid.Behroozigrid(MFs)
         else: self.grid=grid
-
         self.galaxies=self.galaxies.where(self.galaxies.z_spec < zs)
 
         zsnapped,psnapped=self.grid.snap(self.galaxies.z_spec)
@@ -360,6 +359,13 @@ class lens_lightcone(lightcone):
         
         return None
 
+    def fastmode(self,kappamin):
+        #a=numpy.sum(self.galaxies.kappa_Scaled)
+        #lena=len(self.galaxies.kappa_Scaled)
+        self.galaxies=self.galaxies.where(self.galaxies.kappa_Scaled>kappamin)
+        #b=numpy.sum(self.galaxies.kappa_Scaled)
+        #print kappamin,a,b,(a-b)/a, (1.0*lena-len(self.galaxies.kappa_Scaled))/(1.0*lena)
+        return None
 # ----------------------------------------------------------------------------
 #      -.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.
     def massplot(self,AX):

### 2012-08-07 Truthcompare.py

@@ -36,9 +36,9 @@ def MScompare(argv):
    Rcone = 5 # arcmin
    truncationscale=numpy.linspace(0.5,6,20) # *R_200 halo truncation
    truncationscale=numpy.append(truncationscale,[7,8,9,10,12,14,16,18,20])
-   adoptedtruncationscale=5
+   adoptedtruncationscale=10
    Ntruncs=len(truncationscale)
-   Ncones=1000
+   Ncones=100000
    magcuts=numpy.linspace(14,26,50)
 
 
@@ -79,7 +79,7 @@ def MScompare(argv):
          print "Reconstructing convergence in lightcones from:",catalog
          print "Comparing to convergence in:",kappafile
          print "Number of lightcones to be reconstructed:",Ncones
-   else:
+   elif everything != True:
       print MScompare.__doc__
       return
 
@@ -368,7 +368,7 @@ def MScompare(argv):
 
 if __name__ == '__main__':
    everything = True
-   investigateT=False
+   investigateT=True
    investigateR=True
    investigateM=True
    oneseven=1 #calculate on patch 1_1 or 7_7?

### 2012-08-21 doc/acknowledgments.tex
first draft of theory section
notes on to-do items

@@
-TJC acknowledges support from STFC in the form of a research studentship.
+TEC acknowledges support from STFC in the form of a research studentship.
 %
-PJM was given support by the TABASGO and Kavli foundations, and the Royal 
+PJM was given support by the Kavli Foundation and the Royal 
 Society, in the form of research fellowships.
 %
-MWA \ldots. SH \ldots. SHS \ldots.
+MWA \ldots
+%
+SH \ldots
+%
+SHS \ldots
 %

### 2012-08-21 doc/paper-lcr.tex
notes on to-do items

@@
 to be strongly lensed \citep{gavazzi2008,collett2012}, the shear scale of dark matter halos
-makes a partial allignment -- with the additional structure acting as a weak lens -- 
+makes a partial alignment -- with the additional structure acting as a weak lens -- 
 a near certainty, indeed \citet{valewhite2003} and \citet{hilbert2007} find that there
@@
 
-In the stong lensing case, the presence of a significant perturber alters the geometry of the system, and provides a primary lens plane.
-It is the primary lens plane upon which we need to know $\kappa_{\mathrm{effective}}$, since this is where the mass-sheet degeneracy is defined.
-Following Equations 20--32 of \citet{keeton2003}\flag{keeton2003}, it can be shown that the relevant effective convergence is given by
+In the stong lensing case, the presence of a significant perturber alters the
+geometry of the system, and provides a primary lens plane. It is the primary
+lens plane upon which we need to know $\kappa_{\mathrm{effective}}$, since
+this is where the mass-sheet degeneracy is defined. Following Equations 20--32
+of \citet{keeton2003}\flag{keeton2003}, it can be shown that the relevant
+effective convergence is given by 
 \be \label{eq:kappasumSL}
@@
 \ee
-where $\kappa$ and $\gamma$ are, respectively, the convergence and shear caused by the perturber, in their own plane and $\beta_{12}$ is a geometrical scaling factor defined by
+where $\kappa$ and $\gamma$ are, respectively, the convergence and shear
+caused by the perturber, in their own plane and $\beta_{12}$ is a geometrical
+scaling factor defined by
 \be\label{eq:beta}
@@
 \ee
-where the D's are again angular diameter distances: the 1 (2) in the subscript refers to the lower (higher) redshift object of the lens and perturber.
-For the case that the mass sheet is in the lens plane, $\beta_{12} = 0$ and $\kappa_{\mathrm{eff}}=\kappa$; if the mass-sheet is in the plane of the observer, or source, $\beta_{12} = 1$ and $\kappa_{\mathrm{eff}}=0$; for a mass-sheet at any other redshift $0<\beta_{12}<1$.
-In the case of several mass sheets the effective convergences sum.
-In the limit that both $\kappa$ and $\gamma$ are small, Equation \ref{eq:kappasumSL} reduces to
+where the D's are again angular diameter distances: the 1 (2) in the subscript
+refers to the lower (higher) redshift object of the lens and perturber. For
+the case that the mass sheet is in the lens plane, $\beta_{12} = 0$ and
+$\kappa_{\mathrm{eff}}=\kappa$; if the mass-sheet is in the plane of the
+observer, or source, $\beta_{12} = 1$ and $\kappa_{\mathrm{eff}}=0$; for a
+mass-sheet at any other redshift $0<\beta_{12}<1$. In the case of several mass
+sheets the effective convergences sum. In the limit that both $\kappa$ and
+$\gamma$ are small, Equation \ref{eq:kappasumSL} reduces to 
 \be \label{eq:kappasumSLweak}
@@
 \ee
-it is this $\kappa_{\mathrm{effective,SL}}$ that we use as $\kappax$ for the strong lensing time delay analysis in \ref{sec:Dt}.
+it is this $\kappa_{\mathrm{effective,SL}}$ that we use as $\kappax$ for the
+strong lensing time delay analysis in \ref{sec:Dt}.
+
+\flag{The all-important calibration of the reconstruction has to be done
+against Stefan's ray-traced kappas though -- so it is these that we have to
+predict PDFs for, first and foremost. THEN we have to consider the question of
+which kappa to use to correct the time delay distances: Stefan's kappa (as in
+B1608 or RXJ1131), or kappa-keeton.}
 
@@
 
-For real lines of sight, it is nearly impossible to know the true $\kappax$ for a
-line of sight, and without a knowledge of $\kappax^{\mathrm{true}}$ it is hard to
-quantify if there is a bias induced by using different $\kappax$ estimators.
-A source with known unlensed brightness e.g. a strongly lensed type Ia
-Supernova \flag{cite some SNe papers} or a source of known unlensed size \flag{ideas?}
-would break the mass-sheet degeneracy and provide a value for $\kappax$, but
-\flag{no?} such systems are currently known.
+For real lines of sight, 
+\phil{we would like to estimate the external convergence as best we can given all
+data available. Typically this data is in the form of a photometric galaxy
+catalog, containing positions, brightnesses, colours, and other type
+information for each galaxy in the field of the lens, down to some magnitude
+limit. Since we do not observe halo mass directy, we need some way estimating
+the mass of each galaxy in the catalog, so that we can compute its
+contribution to $\kappax$. This mass assignment recipe will be uncertain, but
+can be calibrated to cosmological simulations.}
 
-Cosmological dark matter simulations can be used to generate mock lines of sight...
+% PJM: What is this defeatism?!
+% it is nearly impossible to know the true $\kappax$ for a
+% line of sight, and without a knowledge of $\kappax^{\mathrm{true}}$ it is hard to
+% quantify if there is a bias induced by using different $\kappax$ estimators.
+%
+% A source with known unlensed brightness e.g. a strongly lensed type Ia
+% Supernova \flag{cite some SNe papers} or a source of known unlensed size \flag{ideas?}
+% would break the mass-sheet degeneracy and provide a value for $\kappax$, but
+% \flag{no?} such systems are currently known.
+
+Cosmological dark matter simulations can be used to generate mock lines of
+sight...
 \flag{Stefan's section on how the ray tracing was done and how halos are extracted from
@@
 
-With this catalogue of halos, positions, redshifts etc. it is possible to attempt
-a reconstruction of the convergernce induced by every halo near a line of sight.
-Cosmological dark matter simulations have shown that dark matter halos are well
-approximated by NFW profiles \citep{NFW1997}, with a density profile given by
+\phil{Transforming the photometometric galaxy catalogue into a}  catalogue of
+halo masses, positions, and redshifts, will enable us to attempt a
+reconstruction of the convergence induced by every halo near a line of sight.
+This is the subject of the first subsection below. We also need to account for
+the mass in the Universe that is not associated with the galaxies we can see
+-- this is the subject of the second subsection below.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Halos}
+
+Cosmological dark matter simulations have shown that dark matter
+halos are well approximated by NFW profiles \citep{NFW1997}, with a density
+profile given by
 \be\label{eq:rhonfw}
@@
 
-Whilst halos contribute a positive convergence to $\kappax$, voids contribute a negative convergence. When a raybundle passes through a 
-region of space that is less dense than $\rho_{\rm cr}(z)$ the rays are de-focused\footnote{In principle, the convergence caused by halos, is also caused by the overdensity, but we neglect this effect since halos are typically much more dense than the intergalactic medium}.
-Whilst the
-full raytraced solution takes into account the effect of voids, our reconstruction cannot -- the halo catalogue does not include voids.
-In principle the absence of a halo could be taken to infer a void, but the under-density of such a void is hard to infer.
-Instead, we shift our $\kappax$ values so that $\langle\kappax\rangle=0$.
-We refer to this corrective term as $\kappav$.
-The void correction introduces a source of error, since the inferred value of $\kappav$ will depend on the properties of the sightlines reconstructed, but this error shrinks with the number of sightlines reconstructed.
-To avoid potential biases we calculate $\kappav$ from randomly selected sightlines.
-The total $\kappax$ along the line of sight is given by
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Voids}
+
+Whilst halos contribute a positive convergence to $\kappax$, voids contribute
+a negative convergence. When a raybundle passes through a  region of space
+that is less dense than $\rho_{\rm cr}(z)$ the rays are de-focused\footnote{In
+principle, the convergence caused by halos, is also caused by the overdensity,
+but we neglect this effect since halos are typically much more dense than the
+intergalactic medium}. Whilst the  full raytraced solution takes into account
+the effect of voids, our reconstruction cannot -- the halo catalogue does not
+include voids. In principle the absence of a halo could be taken to infer a
+void, but the under-density of such a void is hard to infer. Instead, we shift
+our $\kappax$ values so that $\langle\kappax\rangle=0$. We refer to this
+corrective term as $\kappav$. The void correction introduces a source of
+error, since the inferred value of $\kappav$ will depend on the properties of
+the sightlines reconstructed, but this error shrinks with the number of
+sightlines reconstructed. To avoid potential biases we calculate $\kappav$
+from randomly selected sightlines. The total $\kappax$ along the line of sight
+is given by 
 \be \label{eq:totalkappax}
@@
 \ee
+
+\flag{Need to draw a convergence from the void distribution, such that 1) the
+intrinsic distribution of kappas is returned in the case where we have no
+data, and 2) the mean density parameter over all lines of sight is $\Omega_m$.
+The mass budget has to be balanced!}
 
@@
 
+Make mock sample of lenses, all wit B1608 zd and zs, but with different kappas.
+Draw kappas from Stefan's *lens* distribution. Can we correct for the selection
+effect?
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Comparison with Other Treatments of $\kappax$}
+\label{sec:Dt:selection}
+
+\phil{How does distance accuracy compare with simple averaging? eg assuming
+$\kappax = 0$ for all lenses. How does it compare with the no data situation?
+eg where the intrinsic distribution of kappa is used as $Pr(\kappax)$.}
+
 What is the expected bias and scatter (centroid position and width) of P(D) as a
@@
 
-Make mock sample of lenses, all wit B1608 zd and zs, but with different kappas.
-Draw kappas from Stefan's *lens* distribution. Can we correct for the selection
-effect?
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{The Impact of Selection Effects}
+\label{sec:Dt:selection}
+
+\phil{How does distance accuracy vary with:}
+\begin{itemize}
+\item Depth of catalog? mlim = 22, 24, 26?
+\item Overdensity cuts? Remove underdense fields, overdense fields (from
+reconstructed kappa)
+\item Shear-sensitive selection? What if we only selected quads?
+\end{itemize}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Improving the Accuracy with More Information}
+\label{sec:Dt:selection}
+
+\phil{How does distance accuracy improve with:}
+\begin{itemize}
+\item Spectroscopic coverage? For galaxies above some mlim? For targets with
+high kappa contribution (based on photometry)?
+\item IR coverage for all objects? Improves photo-z and Mstar.
+\item Including shear information from lens model? Assume accurate but
+uncertain extertanl shear.
+\end{itemize}
 
@@
 Why reconstruction works or doesn't work.
-
 Major sources of uncertainty.
-
-Ideas for improving the procedure
-
+Ideas for improving the procedure.
 Emphasize that this can be done before monitoring time is invested.

### 2012-08-23 doc/paper-lcr.tex
paper changes

--- 2012-07-27 doc/paper-lcr.tex
@@
 Throughout this paper magnitudes are given in the AB system \citep{Oke74} and
-we adopt standard ``concordance'' parameters for our reference cosmology, \ie
-$h=0.7$, $\Omega_m=0.3$ and $\Omega_\Lambda=0.7$, where the symbols indicate
+we adopt the Millenium Simulation's ``concordance'' parameters for our reference cosmology, \ie
+$h=0.73$, $\Omega_m=0.25$ and $\Omega_\Lambda=0.75$, where the symbols indicate
 the Hubble Constant in units of 100 km s$^{-1}$ Mpc$^{-1}$ and the matter and
 dark energy density of the Universe in units of the critical density
-\citep[e.g.\ ][]{Kom++09}.
+.%\citep[e.g.\ ][]{Kom++09}.
 
@@
 each image. Despite the invariance of the image positions and fluxes, under the addition
-of an external convergence the relative Fermat potential between the images is {\it not}
+of an external convergence (and appropriate re-scaling of the lens potential) the relative Fermat potential between the images is {\it not}
 invariant, and so the time delay changes. As such it is necessary to include $\kappax$
-in our lens modelling, if cosmological parameters are to be estimated accurately and
+in the lens modelling, if cosmological parameters are to be estimated accurately and
 precisely from observed time delays \citep{suyu2010}.
@@
 
-Disturbingly, if one integrates the density profile of an NFW profile, the total mass is divergent.
+Unphysically, if one integrates the density profile of an NFW profile, the total mass is divergent.
 Similarly, if the universe is homogeneously populated with NFW halos, the projected surface mass along any
-line sight will also be divergant\footnote{At large radius, $\Sigma_{\rm nfw} \propto R^{-2}$, but the differential number of halos centred within an annulus of width $\dee R$ is given by $\dee N_{\rm annulus} \propto R \dee R$, so  $\Sigma_{\rm total} \propto \int_{0}^{\infty} R^{-1} \dee R$, which diverges logarithmically}.Since infinite mass is unphysical, the profile must be truncated at some point.
+line of sight will also be divergant\footnote{At large radius, $\Sigma_{\rm nfw} \propto R^{-2}$, but the differential number of halos centred within an annulus of width $\dee R$ is given by $\dee N_{\rm annulus} \propto R \dee R$, so  $\Sigma_{\rm total} \propto \int_{0}^{\infty} R^{-1} \dee R$, which diverges logarithmically}.
+Since infinite mass is unphysical, the profile must be truncated at some point.
 \flag{previous truncation results}.
@@
 \ee
-which is the same as the NFW profile in the limit that $r_t$ goes to infinity.
-Defining $x$ as the dimensionless projected radial distance $R/r_{s}$ and $\tau$ as the dimensionless truncation radius $r_{t}/r_{s}$, \citet{BMO} derives the projected mass density, which is given by:
-\begin{align}\label{eq:kappaBMO}
-\Sigma_{\rm}(x) = {2\tau^2 \over (\tau^2+1)^2}\left(
-        {\tau^2+1\over x^2-1}\left(1-\mathcal{F}(x)\right)
-        +
-        2\mathcal{F}(x)\right.\nonumber\\
-        -
-        \left. {\pi \over \sqrt{\tau^2+x^2}}
-        +
-        {(\tau^2-1)\mathcal{L}(x,\tau)
-        \over
-        \tau\sqrt{\tau^2+x^2}}\right)
-\end{align}
-where $\mathcal{F}(x)$ and $\mathcal{L}(x,\tau)$ are defined as
-\be\label{eq:F} 
-\mathcal{F}(x) \equiv \begin{cases}  \frac{{\rm cos}^{-1} (1/x)}{\sqrt{x^2-1}} \hspace{0.2cm} & (x>1) \\
-\\
-\frac{4-x^2}{3}  & (x=1)\\
-\\
-\frac{ {\rm cosh}^{-1} (1/x)}{\sqrt{1-x^2}} & (x<1)
-\end{cases}
-\ee
-\be\label{eq:L}
-\mathcal{L}(x,\tau) = \ln\left(\frac{x}{\sqrt{\tau^2+x^2}+\tau}\right)
-\ee
-%the convergence is given by $\Sigma_{\rm BMO}(x) / \Sigma_{\rm cr}(z)$.
+which is the same as the NFW profile in the limit that $r_t$ goes to infinity. The convergence and shear for the BMO profile are given in Appendix \ref{appendix:halos}.
 
@@
 radius does not broadly affect the scatter on $\kapparay-\kapparec$; from now on we choose 
-to truncate the halos at $10 \Rhalo$. Since $\sigma\left(\kapparay-\kapparec\right)$ does not go to
+to truncate the halos at $5 \Rhalo$. Since $\sigma\left(\kapparay-\kapparec\right)$ does not go to
 zero, it is clear that out halo based prescription does not perfectly replicate the n-body results, we refer to this
@@
 
-\begin{figure}\label{fig:ScattervsTruncation}
+\begin{figure}
 \includegraphics[width=\columnwidth]{truncation_scatter.eps}
 \caption[magcut]{}
+\label{fig:ScattervsTruncation}
 \end{figure}
@@
 1000 callibration lines of sight is unfeasable currently, but should be reasonable in the LSST era.
-Since the true $\langle \kapparay \rangle$ = -0.00014 is two orders of magnitude smaller than intrinsic error of the halo prescription, $\kapparec$ can be seen as unbiased given a large enough sample of lines of sight and Figure \ref{fig:bias} shows that there is no statistically significant evidence that $\kapparec$ is a biased estimator, regardless of the individual value of $\kapparec$.
+Since the true $\langle \kapparay \rangle$ = -0.00014 is two orders of magnitude smaller than intrinsic error of the halo prescription, $\kapparec$ can be seen as unbiased given a large enough sample of lines of sight.
+However since $\kappax$ reconstruction based on perfect knowledge of the halo mass and position is unrealistic we must re-visit the question of bias in Section \ref{sec:obsMstar+z}, using more realistic observables.
 
-\begin{figure}\label{fig:isitbiased}
+\comment{
+ and Figure \ref{fig:bias} shows that there is no statistically significant evidence that $\kapparec$ is a biased estimator, regardless of the individual value of $\kapparec$.
+
+\begin{figure}
 \includegraphics[width=\columnwidth]{isitbiased.eps}
 \caption[Biased?]{}
+\label{fig:isitbiased}
 \end{figure}
-\begin{figure}\label{fig:magcut}
+}
+\begin{figure}
 \includegraphics[width=\columnwidth]{mag_scatter.eps}
 \caption[magcut]{}
+\label{fig:magcut}
 \end{figure}
-\begin{figure}\label{fig:radcut}
+\begin{figure}
 \includegraphics[width=\columnwidth]{radius_scatter.eps}
 \caption[radius cut]{}
+\label{fig:radcut}
 \end{figure}
@@
 Since a large number of callibration lines of sight are needed to shrink the width of $\pr(\kappav)$, it may prove unrealistic to reconstruct the calibration lines of sight out to 5 arcminutes.
-\citet{Auger2007} showed that the majority significant perturbers are within 15 arcseconds of the lens.
 Figure \ref{fig:radcut} shows the width of $\kapparec-\kapparay$ as a function of reconstruction radius; in almost all cases there is no significant contribution to $\kappa$ from halos that are centred more than 1 arcminute away, although large groups or clusters can sometimes still make a contribution as far out as four arcminutes.
-For the rest of this work we will continue to model all of the halos out to 5 arminutes with an $i$ magnitude greater than 26, although a reconstruction with fields going out to two arcminutes and down to $i<24$ would do almost as well.
+For the rest of this work we will continue to model all of the halos out to 5 arminutes with an $i$ magnitude greater than 26, although a reconstruction with fields going out to two arcminutes and down to $i=24$ would do almost as well.
 
@@
 
-Consider three sources of scatter in the halo model: zphot, Mstar|zphot, and
-Mhalo|Mstar,zphot. Mechanism for including scatter in model: draw samples from
-PDFs. Result is not one predicted kappa, but one P(kappa) for each lightcone.
-This is what is required by single-lens analyses.
+We generate a stellar mass for each halo according to the stellar mass--halo mass relation of \citet{behroozi2010}. From this stellar mass we simulate 
+an observed stellar mass by drawing a sample from $\pr(\log(M_{* \mathrm {obs}})|\log(M_{* \mathrm {true}}))$ which is given by the product of the galaxy stellar mass function (GSMF) of \citet{Fontana2006} and a Gaussian of width $\sigma_{M_*}$ centred on $\log(M*_{\mathrm {true}})$.
+Where a spectroscopic redshift exists stellar masses can be estimated with typical uncertainties of 0.15 dex \citep{xxx}, however with photometric redshifts stellar mass uncertainties are typically three times as large \citep{xxx}; we use $\sigma_{M_*}=0.15$ for halos with a spectroscopic redshift and $\sigma_{M_*}=0.45$ otherwise.
+The \citet{Fontana2006} GSMF is given by a Schechter function with redshift evolving parameters
+\be
+\label{eq:GSMF}
+{\dee N \over \dee M_*} \propto \left(10^{(M_*-M_0(z))}\right)^{(1+\alpha(z))} \exp \left(-10^{(M_*-M_0(z))}\right)
+\ee 
+where $M_0(z)=11.16+0.17z-0.07z^2$ and $\alpha(z)=-1.18-0.082z$.
+For photometric redshift errors we draw a redshift from $\pr(z_{\rm true}|z_{\rm obs})$ which we take as a Gaussian of width $0.1(1+z_{\rm spec})$ centred on $z_{\rm spec}$, where $z_{\rm spec}$ is the halo's true redshift in \MS catalogue
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{widthvkappa.eps}
+\caption[radius cut]{}
+\label{fig:width}
+\end{figure}
+
+Our results are summarized in Figure \ref{fig:width}.
+We reconstruct 10000 lines of sight and each of the reconstructed $\pr(\kappa)$ is summarized by their mean $\kapparec$, and their width containing $68\%$ of the probability, $\sigt$.
+Reconstructing the lines of sight with perfect knowledge of the redshift but an uncertain stellar mass, we find that $\sigt$ grows with $\kapparec$; this is not surprising since the low $\kapparec$ lines of sight are relatively empty and so there are few opportunities for uncertainties in the halo masses to propogate into $\kapparec$ uncertainties.
+Our results are well fit by a straight line given by
+\be
+\sigt=0.012+0.26 \langle\kapparec\rangle;
+\label{eq:Mstarfit}
+\ee
+this is the reconstruction error that could be expected from a complete spectroscopic survey of the field.
+A complete spetroscopic survey is unrealistic, but Equation \ref{eq:Mstarfit} represents a lower limit on the reconstruction error.
+We find that with a perfect knowledge of the halo mass, but photometric redshifts the reconstructed $\pr(\kappa)$ has a mean $\sigt$ of 0.003.
+For the lines of sight with $\kapparec {\rm s}$ that are dominated by a single significant perturber the photometric redshift error can induce a larger uncertainty on $\kapparec$, but only $2.9 \%$ of sightlines have $\sigt > 0.01$; typical photometric redshift errors do not propogate into a significant uncertainties on $\kapparec$ if the halo mass is known.
+This is seen in Figure \ref{fig:width}, $\sigt$ is typically much larger for the perfect redshift reconstructions than the perfect mass reconstructions.
+The results are well fit by
+\be
+\sigt=0.0025+0.041\langle\kapparec\rangle
+\label{eq:photozfit}
+\ee
+Inferring the stellar mass of a galaxy from its magnitude and colours requires an estimate of how far away the galaxy is; without a spectroscopic redshift the the infered stellar mass is less precise.
+In principle the photometric redshift is correlated with the infered stellar mass however we do not model this since the redshift error produces a small effect on the recovered $\pr(\kappa)$ when compared to the effect of uncertain stellar masses.
+For the reconstructions with imperfect redshift and stellar mass the resulting uncertainty is significantly larger than the quadrature sum of the $\sigt {\rm s}$ in Equations \ref{eq:Mstarfit} and \ref{eq:photozfit}, this is because the uncertain redshift propogates into a broadened $\pr(M_{*})$.
+The
+ns than the perfect mass reconstructions. For a complete photometric survey down to $i=26$ our reconstructions are fit by the line
+\be
+\sigt=0.026+0.037\langle\kapparec\rangle
+\label{eq:bothfit}
+\ee
+The fits are shown on Figure \ref{fig:intrinsicvsreconstruction}, where we compare the reconstruction errors with typical size of the intrinsic error from Section \ref{sec:knownMh+z}.
+With photometric redshifts only, the reconstruction error is typically half the size of the intrinsic error, but for a survey with complete spectroscopic coverage the two errors are of similar size.
+The photometric results can be greatly improved by the addition of spectroscopic redshifts for a small number of halos.
+Photometric redshifts are sufficient to estimate the $\kappa$ contribution from each halo; once this is know the most important halos can be targeted for spectroscopic follow-up.
+It is not always possible to get a spectroscopic redshift for faint objects, as such we use spectroscopic redshifts for galaxies with $i<24$ that the sitting in halos that individually contribute $\kappa>0.0005$.
+This selection corresponds to an average of $12 \pm 4$ galaxies per line of sight for which spectra are needed; the number of spectra needed per line of sight is shown as a histogram in Figure \ref{fig:spechist}.
+Such a spectroscopic survey yields only a modest improvement upon the purely photometric case being well fit by
+\be
+\sigt=+\langle\kapparec\rangle
+\label{eq:spec1fit}
+\ee
+This modest improvent appears counter intuitive, since spectra for all the subset of halos with $i<24, \kappat>0.0005$ halos contains the majority of the total $\kappax$ along alomst all lines of sight.
+The lack of significant improvement comes
+from the many massive halos that are intermediate distances from the line of sight; they do not contribute significantly to the true $\kappax$, but without spectroscopic reshifts their highly uncertain stellar masses propogate into broad $\pr(\Mhalo)$ and into small probability of large individual $\kappa$ contributions; since there are typically several hundred such objects within 5 arcminutes of the line of sight, their net contribution dominates the width of the photometrically generated $\pr(\kappax)$.
+However since massive objects are typically bright it is realtively fast to obtain their spectra with an 8~m class telescope.
+Galaxies with $i<22, \kappat>0.000001$ corresponds to roughly $200 \pm 100$ objects per line of sight; with spectroscopic redshifts for all of these plus the $i<24, \kappat>0.0005$ objects the reconstruction is greatly improved, being fit by
+\be
+\sigt=+\langle\kapparec\rangle
+\label{eq:spec1fit}
+\ee
+The case of complete photometric coverage and partial spectroscopic coverage is closest to what might be expected from a real reconstruction of a field.
+We will refer to this as the 'hybrid' case for the rest of this paper, where all galaxies with $i<22, \kappat>0.000001$ or $i<24, \kappat>0.0005$ have spectra, but no others.
+
+In Figure \ref{fig:intrinsicvsreconstruction} we show all of the fits, and compare them to the typical size of the difference between the ray-traced $\kapparay$ and the mean of the reconstructed $\kapparec$ which is a good measure of the intrinisic error in the reconstruction.
+For the purely photometric reconstruction $\sigt$ is larger than 98 percent of $|\kapparay - \langle \kapparec \rangle |$ indicating that the reconstruction is the dominant source of error.
+For the purely spectroscopic reconstruction $\sigt$ is larger than 44 percent of $|\kapparay - \langle \kapparec \rangle |$; the intrinsic error is slightly larger than the reconstruction error.
+For the hybrid case $\sigt$ is larger than 88 percent of $|\kapparay - \langle \kapparec \rangle |$, indicating that the intrinsic error is a sub-dominant effect.
+
+Since the reconstruction does not produce a symmetric $\pr(\kappax)$, we must take care in ensuring that the reconstruction has not biased $\langle \kapparec \rangle $ as an estimator of $\kapparay$.
+Figure 12 al
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{spechist.eps}
+\caption[spechist]{}
+\label{fig:spechist}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{intrinsicvsreconstruction.eps}
+\caption[radius cut]{}
+\label{fig:intrinsicvsreconstruction}
+\end{figure}
 
@@
 
+TC thanks Vasily Belokurov for guidance and discussions.
 We thank Risa Wechsler and Peter Behroozi for useful discussions and 
@@
 \label{appendix:halos}
+
+ Defining $x$ as the dimensionless projected radial distance $R/r_{s}$ and $\tau$ as the dimensionless truncation radius $r_{t}/r_{s}$, \citet{BMO} derives the projected mass density, which is given by:
+\begin{align}\label{eq:kappaBMO}
+\Sigma_{\rm}(x) = {2\tau^2 \over (\tau^2+1)^2}\left(
+        {\tau^2+1\over x^2-1}\left(1-\mathcal{F}(x)\right)
+        +
+        2\mathcal{F}(x)\right.\nonumber\\
+        -
+        \left. {\pi \over \sqrt{\tau^2+x^2}}
+        +
+        {(\tau^2-1)\mathcal{L}(x,\tau)
+        \over
+        \tau\sqrt{\tau^2+x^2}}\right)
+\end{align}
+where $\mathcal{F}(x)$ and $\mathcal{L}(x,\tau)$ are defined as
+\be\label{eq:F} 
+\mathcal{F}(x) \equiv \begin{cases}  \frac{{\rm cos}^{-1} (1/x)}{\sqrt{x^2-1}} \hspace{0.2cm} & (x>1) \\
+\\
+\frac{4-x^2}{3}  & (x=1)\\
+\\
+\frac{ {\rm cosh}^{-1} (1/x)}{\sqrt{1-x^2}} & (x<1)
+\end{cases}
+\ee
+\be\label{eq:L}
+\mathcal{L}(x,\tau) = \ln\left(\frac{x}{\sqrt{\tau^2+x^2}+\tau}\right)
+\ee
+%the convergence is given by $\Sigma_{\rm BMO}(x) / \Sigma_{\rm cr}(z)$.
+
+\flag{SHEAR HERE}
 

### 2012-08-23 Pangloss/grid.py

@@ -41,11 +41,14 @@ rad2arcmin = 1.0/arcmin2rad
 vb = False
 
 # ============================================================================
-    
 
 class grid(distances.Distance):
-   def __init__(self,zmax=3,nplanes=100,cosmo=[0.25,0.75,0.73]): 
+   def __init__(self,zmax=3,nplanes=100,cosmo=[0.25,0.75,0.73],filename=None):
        distances.Distance.__init__(self,cosmo=cosmo)
+       """ Allow for empty instantiation """
+       if filename is not None:
+           self.load(filename)
+           return
        self.name = '1D Redshift grid, with precalculated quantities '
        self.zmax=zmax
        self.nplanes=nplanes    
@@ -63,6 +66,16 @@ class grid(distances.Distance):
       snapped_p=numpy.digitize(z,self.zplane-(self.dz)/2)-1
       snapped_z=self.zplane[snapped_p]
       return snapped_z,snapped_p
+
+
+   def save(self,filename):
+      f = open(filename,'wb')
+      cPickle.dump([self.name,self.zmax,self.nplanes,self.redshiftbins],f,2)
+      f.close()
+
+   def load(self,filename):
+      self.name,self.zmax,self.nplanes,self.redshiftbins = numpy.load(filename)
+
 
 # ----------------------------------------------------------------------------
 

### 2012-08-23 Pangloss/lightcone.py

@@ -99,6 +99,9 @@ class lightcone(object):
             col = "mag_%s" % band
         self.galaxies=self.galaxies.where(self.galaxies["%s"%col] < magnitudecut)
 
+        self.ISrun=False
+
+
         return None
 
 # ----------------------------------------------------------------------------
@@ -173,6 +176,18 @@ class lens_lightcone(lightcone):
         #calculate rphys
         self.galaxies.add_column('rphys',self.galaxies.Da_d*self.galaxies.r*arcmin2rad) #units 
 
+        #copy columns that need to change with photoz
+        self.galaxies.add_column('Tzsnapped',zsnapped)
+        self.galaxies.add_column('Tpsnapped',psnapped)
+        self.galaxies.add_column('TDa_d', self.grid.Da_p[p])
+        self.galaxies.add_column('TDa_ds', self.grid.Da_ps[p])
+        self.galaxies.add_column('TDa_dl', self.grid.Da_pl[p])
+        self.galaxies.add_column('Tbeta', self.grid.beta_p[p])
+        self.galaxies.add_column('Trho_crit',  self.grid.rho_crit_p[p])    # Mpc
+        self.galaxies.add_column('Tsigma_crit', self.grid.sigma_crit_p[p]) #solarmasses per Mpc^2
+        self.galaxies.add_column('Trphys',self.galaxies.Da_d*self.galaxies.r*arcmin2rad) #units 
+
+
 
         return None
 
@@ -182,17 +197,32 @@ class lens_lightcone(lightcone):
         if photozerr==True:
             z=self.galaxies.z_true
             z_obs=z+(1+z)*(rnd.normal(0,0.1,len(z)))
+            if self.ISrun==True:
+                z_obs[self.galaxies.IS==True]=self.galaxies.z_true[self.galaxies.IS==True]
             self.galaxies.remove_columns('z_spec')
             self.galaxies.add_column('z_spec',z_obs)
+
+
         if photozerr==False:
             z=self.galaxies.z_true
             z_obs=z
             self.galaxies.remove_columns('z_spec')
             self.galaxies.add_column('z_spec',z_obs)
         self.photozerr=photozerr
+
+
+
+
         return None
 
[…]

### 2012-09-17 doc/paper-lcr.tex
edit draft

@@
 
+\comments{
 If the mass sheet is not physically associated with the lens galaxy, it can lie at any redshift.
@@
 strong lensing time delay analysis in \ref{sec:Dt}.
+}
 
@@
 
-\subsection{Voids}
+\subsection{Calibration: Recovering the global $\pr(\kappax)$ using a void correction}
+\label{subsec:voids}
 
@@
 include voids. In principle the absence of a halo could be taken to infer a
-void, but the under-density of such a void is hard to infer. Instead, we shift
+void, but the under-density of such a void is hard to infer. Neglecting voids
+would lead to a heavily biased estimate of $\kappax$. We account for the voids
+statistically; we reconstruct
+the $\kappax$ contribution of halos for an ensemble of calibration sightlines
+and form the joint distribution P($\kapparay,\sumkappah$). The calibration
+can then be accounted for by marginalizing over all lines of sight with a similar
+ $\sumkappah$.  We will refer to this calibration proceedure as the "void correction",
+although it also accounts for all of the physics that our simple spherical halo prescription
+neglects in a statistical manner. For each line of sight we create a $\pr(\kappax)$ from
+\be
+\pr(\kappax)=\int_{-\infty}^{+\infty}\pr(\kapparay',\tilde\kappa'_{\rm halos})W(\tilde\kappa_{\rm halos}-\tilde\kappa'_{\rm halos})\dee \tilde\kappa'_{\rm halos}
+\ee
+where $\tilde{\kappa}_{\rm halos}$ is the median of the reconstructed $\sumkappah$ for each line of sight.
+Primed qunatities refer to all of the calibration sightlines and unprimed refers to the specific line of sight.
+$W(\tilde\kappa_{\rm halos}-\tilde\kappa'_{\rm halos})$ is a weight function given by
+\be
+W(\tilde\kappa_{\rm halos}-\tilde\kappa'_{\rm halos})=\exp\left(-\frac{1}{2}\left(\frac{\left(\tilde\kappa_{\rm halos}-\tilde\kappa'_{\rm halos}\right)^2}{\sigma^2}\right)\right)
+\ee
+We take $\sigma$ as 0.01- this is an overestimate of the uncertainty on $\tilde\kappa_{\rm halos}$, but ensures that the full distibution of void corrections is sampled, despite the finite number of calibration sightlines.
+
+\comments{
+For each reconstruction of a line of sight we can then draw a $\kappav$ from $\pr(\kappav)$ to correct for the
+unseen voids. We refer to this corrective shift as $\kappav$. The void correction introduces a source of
+error, since the value of $\kappav$ comes from the ensemble of calibration lines of sight rather than the individual
+line of sight which is being reconstructed; this is unavoidable without modeling the $\kappax$ 
+contribution of voids along a line of sight. To avoid potential biases we calculate $\pr(\kappav)$
+from randomly selected calibration sightlines. The total $\kappax$ along the line of sight
+is given by 
+\be \label{eq:totalkappaxunweighted}
+\pr(\kappax) = \left(\sum_{\rm halos} \pr(\kappa_{\rm halo})\right)-\pr(\kappav).
+\ee
+
+Once the void correction has been applied,the reconstruction should produce a 
+reasonable estimate of $\pr(\kappax)$ for any single line of sight. However, from
+the ray tracing results we know the global $\kappax$ distribution ${\rm U}(\kappax)$. We can use the global
+ ${\rm U}(\kappax)$ as a prior by noting that the normalized sum of $\pr(\kapparec)$ from multiple lines
+of sight should equal ${\rm U}(\kappax)$, \ie
+\be \label{eq:prior}
+{\rm U}(\kappax) = \lim_{N \to \infty} \sum_{i}^{N} \pr(\kappax)_{i} / N
+\ee
+In order to make Equation \ref{eq:prior} hold, we use Equation \ref{eq:totalkappaxunweighted} to calculate $\pr(\kappax)^{\rm unweighted}$ for the calibration lines of sight and
+re-weight the reconstructions by:
+\be \label{eq:weighting}
+W(\kappa)=\left(\sum_{i}^{N} \pr(\kappax)_{i}^{\rm unweighted} /N \right) / \left({\rm U}(\kappax)\right)
+\ee
+such that the final reconstruction is given by 
+\be \label{eq:totalkappax}
+\pr(\kappax) = \left(\left(\sum_{\rm halos} \pr(\kappa_{\rm halo})\right)-\pr(\kappav)\right)(W(\kappa)).
+\ee
+
+}
+
+\comments{
+Whilst halos contribute a positive convergence to $\kappax$, voids contribute
+a negative convergence. When a raybundle passes through a  region of space
+that is less dense than $\rho_{\rm cr}(z)$ the rays are de-focused\footnote{In
+principle, the convergence caused by halos, is also caused by the overdensity,
+but we neglect this effect since halos are typically much more dense than the
+intergalactic medium}. Whilst the  full raytraced solution takes into account
+the effect of voids, our reconstruction cannot -- the halo catalogue does not
+include voids. In principle the absence of a halo could be taken to infer a
+void, but the under-density of such a void is hard to infer.
+\tom{ Instead, we reconstruct 10000 lines of sight to give $\pr(\kapparec|kapparay)$
+and invert the PDF using Bayes' theorem to give $\pr(\kapparay|\kapparec)$. For each lightcone we
+can then get $\pr(\kapparay)$ by marginalizing over the reconstruction PDF, $\pr(\kapparec)$.
+This recipe also ensures that we correctly recover the ensemble $\kapparay$ distribution, even in the case
+of no input data.
+
+ Instead, we shift
 our $\kappax$ values so that $\langle\kappax\rangle=0$. We refer to this
@@
 \ee
-
-\flag{Need to draw a convergence from the void distribution, such that 1) the
-intrinsic distribution of kappas is returned in the case where we have no
-data, and 2) the mean density parameter over all lines of sight is $\Omega_m$.
-The mass budget has to be balanced!}
+}}
 
@@
 ray-tracing through the MS's n-body particles, 
-it is possible to test the validity of the prescription outlined in Section \ref{sec:model}. We do this
-using $\kapparay$ as a proxy for $\kappatrue$. The reconstruction prescription is tested given perfect
+it is possible to test the validity of the prescription outlined in Section \ref{sec:model}. We test the model
+ by comparing $\sumkappah$ against $\kapparay$. If the reconstruction process is to be
+ succesfull the two quantities should correlate.
+
+The reconstruction prescription is tested given perfect
 knowledge of the halos' virial masses and redshifts; this provides us with a measure of the intrinsic
-errors induced by treating matter as truncated NFW halos. To quantify this 10000 lines of sight are chosen
-from random positions in the catalogue, and for each line of sight we reconstruct the
+errors induced by treating matter as truncated NFW halos. In this Section we do not apply the void correction of
+Section \label{subsec:voids}, instead we shift $\sumkappah$ for all our sightlines by a fixed negative offset such that the ensemble mean
+is zero, i.e.
+\be \label{eq:totalkappax}
+\kapparec = \left(\sum_{\rm halos} \kappa_{\rm halo}\right)-\kappav,
+\ee
+where $\kappav$ is a positive constant. This us allows us to test the halo reconstruction directly, without the uncertainty of the void correction
+obscuring any inadequacies of our halo based prescription.
+
+We choose 100000 lines of sight from random positions in the catalogue, and for each line of sight we reconstruct the
 convergences from every halo within 5 arcminutes and compare the reconstructed
-kappas with those from the ray tracing results. The standard deviation on $\kapparay$-$\kapparec$ 
-shown in Figure \ref{fig:ScattervsTruncation}. It is clear from Figure \ref{fig:ScattervsTruncation} 
+$\kapparec$ with those from the ray tracing results. The standard deviation on $\kapparay$-$\kapparec$ 
+shown in Figure \ref{fig:ScattervsTruncation} as a function of the radius at which the halo is truncated.
+ It is clear from Figure \ref{fig:ScattervsTruncation} 
 that as long as the truncation is greater than a few virial radii, the choice of truncation
@@
 zero, it is clear that out halo based prescription does not perfectly replicate the n-body results, we refer to this
- as the intrinsic error of the prescription. The intrinsic error has a standard deviation of $\sigi \sim 0.018$, although
-this figure is inflated by a few outliers in the tails of $\pr\left(\kapparay-\kapparec\right)$. Whilst we do not
-focus on shear in this work, such outliers would likely be rejected by their reconstructed shear not matching the
-shear of the lens model (see \citet{wong} for the practicalities of this), this makes our estimate of the intrinsic error pessimistic.
+ as the intrinsic error of the prescription.
+ The intrinsic error has a standard deviation of $\sigi \sim 0.018$, although
+this figure is inflated by a few outliers in the tails of $\pr\left(\kapparay-\kapparec\right)$. Such outliers would 
+likely be rejected by their reconstructed shear not matching the shear of the lens model 
+(see \citet{wong} for the practicalities of this);
+ this makes our estimate of the intrinsic error pessimistic. We do not include any additional constraints on P($\kappax$), given prior knowledge of the external shear in this work.
 
@@
 \includegraphics[width=\columnwidth]{truncation_scatter.eps}
-\caption[magcut]{}
+\caption[magcut]{The standard deviation in $\kapparec$ minus $\kapparay$ as a function of halo truncation radius in virial radii, using the truncated NFW profile of \citet{BMO}.
+In our models we truncate our halos at 5$R_{200}$}
 \label{fig:ScattervsTruncation}
@@
 
-\tom{this paragraph is phrased badly}
-If $\kapparec$ is to be used in a real survey it is important that it is not a biased estimator of the true $\kappax$. 
-Ideally one wants $\langle \kapparec-\kappatrue \rangle$ to equal 0 and $\kapparec-\kappatrue$ to be independant of
-$\kapparec$., since the void correction ensures $\langle \kapparec \rangle = 0$ any bias in $\langle \kapparec-\kapparay \rangle$ comes
-from the variations in $\kapparay$. With 8.2$\times 10^8$ pixels, uniformly spaced over 196 deg$^2$ of simulated sky,
- $\langle \kapparay \rangle$ = -0.00014. However, it is improbable that such a large number of lines of sight
- could be reconstructed in reality and the mean of $\kappatrue$ for a small subset of sightlines will not necessarily
-equal zero. We find this error to be
-\be\label{eq:sigmav}
-\sigma(\kappav) \simeq 0.036 / N^{\frac{1}{2}},
-\ee
- where $N$ is the number of lines of sight, although $\pr(\kappav)$ has positive skew for small $N$.
- Care must be taken that the callibration lines of sight are not biased in $\kappax$ or the final $\pr(\kappav)$ will also be biased.
-For the rest of this work we use 1000  randomly chosen calibration lines of sight to calculate $\kappav$, introducing an error on $\kappax$ of $0.001$.
-1000 callibration lines of sight is unfeasable currently, but should be reasonable in the LSST era.
-Since the true $\langle \kapparay \rangle$ = -0.00014 is two orders of magnitude smaller than intrinsic error of the halo prescription, $\kapparec$ can be seen as unbiased given a large enough sample of lines of sight.
-However since $\kappax$ reconstruction based on perfect knowledge of the halo mass and position is unrealistic we must re-visit the question of bias in Section \ref{sec:obsMstar+z}, using more realistic observables.
-
-\comment{
- and Figure \ref{fig:bias} shows that there is no statistically significant evidence that $\kapparec$ is a biased estimator, regardless of the individual value of $\kapparec$.
+For $\kapparec$ to provide useful constraints on $\kapparay$, it is important that $\kapparay$ and $\kapparec$ are as similar as possible.
+Figure \ref{fig:bias} shows that indeed $\kapparec$ is a good estimator, regardless of the individual value of $\kapparec$, but that the scatter increases with $\kapparec$.
+The curve in $\kapparec-\kapparay$ at high $\kapparec$ shows that the reconstruction does not perfectly reproduce the physics of the most overdense lines of sight.
+Since most lines of sight have $\kappax<0.05$, $\kapparec$ is an acceptable estimator of $\kapparay$, although there is some scope for improvement at the highest $\kappax$.
 
@@
 \includegraphics[width=\columnwidth]{isitbiased.eps}
-\caption[Biased?]{}
+\caption[Biased?]{$\kapparec$ minus $\kapparay$ as a function of $\kapparec$, for 10000 reconstructed lines of sight.
+The points are put into bins of width 0.01 in $\kapparec$, except the last bin containing all reconstructions with $\kapparec>0.14$.
+The errorbars show the population standard deviation for each bin.
+Since all of the errorbars are consistant with zero, there is no evidence for $\kapparec$ being a biased estimator of $\kapparay$}
 \label{fig:isitbiased}
 \end{figure}
-}
-\begin{figure}
-\includegraphics[width=\columnwidth]{mag_scatter.eps}
-\caption[magcut]{}
-\label{fig:magcut}
-\end{figure}
-\begin{figure}
-\includegraphics[width=\columnwidth]{radius_scatter.eps}
-\caption[radius cut]{}
-\label{fig:radcut}
-\end{figure}
 
-The error from the void correction, and the intrinsic error from the halo based prescription are unavoidable errors, even with perfect knowledge of halo mass and position.
+The intrinsic error between the results of the halo based prescription and the raytraced convergence is an unavoidable error, even with perfect knowledge of halo mass and position.
 Before investigating the errors caused by imperfect knowledge of halo mass and redshift, we investigate the errors induced by a magnitude limited reconstruction and a field of view limited reconstruction.
@@
 Objects brighter than $i=18$ are either too rare or too close to the observer to make a significant contribution to the convergence.
-Objects fainter than $i=24$ are too small to be important unless they are extremely close to the line of sight where it is likely that neglecting stellar mass and using a spherical NFW prescription are too naive to adequately reconstruct $\kappax$ - it is likely that these ultra-faint halos (or substructures) are the major source of the scatter in $\kapparec-\kapparay$, but a deeper survey will not be sufficient to decrease the size of this scatter.
-Since a large number of callibration lines of sight are needed to shrink the width of $\pr(\kappav)$, it may prove unrealistic to reconstruct the calibration lines of sight out to 5 arcminutes.
+Objects fainter than $i=24$ are too small to be important unless they are extremely close to the line of sight where it is likely that neglecting stellar mass and using a spherical NFW prescription are too naive to adequately reconstruct $\kappax$ - it is likely that these ultra-faint halos (or substructures), the uncertain contribution of voids and halos deviating from our spherical truncated NFW profile are the three major sources of the scatter in $\kapparec-\kapparay$; a deeper survey will not be sufficient to decrease the size of this scatter.
+Since a large number of callibration lines of sight must be reconstructed to sample $\pr(\kappav)$, it may prove unrealistic to reconstruct the calibration lines of sight out to 5 arcminutes.
 Figure \ref{fig:radcut} shows the width of $\kapparec-\kapparay$ as a function of reconstruction radius; in almost all cases there is no significant contribution to $\kappa$ from halos that are centred more than 1 arcminute away, although large groups or clusters can sometimes still make a contribution as far out as four arcminutes.
 For the rest of this work we will continue to model all of the halos out to 5 arminutes with an $i$ magnitude greater than 26, although a reconstruction with fields going out to two arcminutes and down to $i=24$ would do almost as well.
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{mag_scatter.eps}
+\caption[magcut]{The 16, 50 and 84\% confidence intervals on $\kapparec$ minus $\kapparay$ as a function of the limiting $i$ band depth of the halo reconstruction - there is no significant improvement from including small halos with magnitudes less than $i=24$}
+\label{fig:magcut}
+\end{figure}
+\begin{figure}
+\includegraphics[width=\columnwidth]{radius_scatter.eps}
+\caption[radius cut]{The 16, 50 and 84\% confidence intervals on $\kapparec$ minus $\kapparay$ as a function of the limiting radius (in arcminutes) beyond which halos are not reconstructed.
+The majority of the convergence comes from halos centred within an arcminute of the line of sight}
+\label{fig:radcut}
+\end{figure}
+
+The final test that we apply to the perfect knowledge reconstruction is to apply the marginalization outlined in Section \ref{subsec:voids}.
+Taking the reconstructed $\sumkappah$ for $1\times 10^{-5}$ lines of sight we form the joint distribution, P$(\kapparay,\sumkappah)$ and marginalize over all sightlines with a similar $\sumkappah$ to give P($\kappax$).
+We define the bias as the difference between the expectation value of $\kappax$ and the known true value of $\kapparay$ for each Line of sight.
+From $1\times 10^{4}$ reconstructed lines of sight we find the the bias to have mean of $2.0\times 10^{-5}$ and standard deviation of 0.0193.
+In the case where one assumes P$(\kappax)$ is given by the global P$^{\rm global}(\kappax)$, the same $1e4$ lines of sight show a mean bias of $7.7\times 10^{-4}$ and the bias has a standard deviation of 0.0346.
+Within the statistical error both methods are unbiased, but for any individual line of sight the bias is typically 1.8 times smaller with the reconstructed P$^{\rm reconstruction}(\kappax)$, rather than global P$^{\rm global}(\kappax)$.
 
@@
 
-Real attempts to reconstruct the convergence along a line of sight will not have direct access to the masses of dark matter halo, 
+Real attempts to reconstruct the convergence along a line of sight will not have direct access to the masses of dark matter halos, 
 and will likely not have access to their spectroscopic redshift either. Instead these properties must be inferred from astrophysical
@@
 stellar mass and photometric redshifts (with appropriate errors), as the observables that must be converted into an estimate
-of $\kappax$. We will investigate three main sources of error: inferring halo mass given observed stellar mass; halos at the wrong redshift
-due to photometric redshift error, and; the combination of both redshift and stellar mass errors.
+of $\kappax$.
+We will investigate two main sources of error: inferring halo mass given observed stellar mass and the combination of stellar mass errorsand placing halos at the wrong redshift due to photometric redshift error.
 
@@
 where $M_0(z)=11.16+0.17z-0.07z^2$ and $\alpha(z)=-1.18-0.082z$.
-For photometric redshift errors we draw a redshift from $\pr(z_{\rm true}|z_{\rm obs})$ which we take as a Gaussian of width $0.1(1+z_{\rm spec})$ centred on $z_{\rm spec}$, where $z_{\rm spec}$ is the halo's true redshift in \MS catalogue
+For photometric redshift errors we draw a redshift from $\pr(z_{\rm true}|z_{\rm obs})$ which we take as a Gaussian of width $0.1(1+z_{\rm spec})$ centred on $z_{\rm spec}$, where $z_{\rm spec}$ is the halo's true redshift in the \MS catalogue
+
+For each investigated source of error, we reconstruct 10000 lines of sight and each of the reconstructed $\pr(\sumkappah)$ is summarized by their mean $\sumkappah$, and their half-width containing $68\%$ of the probability, $\sigt$.
+Reconstructing the lines of sight with perfect knowledge of the redshift but an uncertain stellar mass, we find that $\sigt$ grows with $\sumkappah$; this is not surprising since the low $\sumkappah$ lines of sight are relatively empty and so there are few opportunities for uncertainties in the halo masses to propogate into $\sumkappah$ uncertainties.
+The means and widths of these reconstructions are summarized in Figure \ref{fig:width1}, before and after applying the void correction and global prior ${\rm U}(\kappax)$.
+Before applying the void correction, the width of the reconstructions are roughly proportional to the mean of $\sumkappah$; they are well fit by a straight line given by
+\be
+\sigt=-0.003+0.25 \langle\sumkappah\rangle.
+\label{eq:Mstarfit}
+\ee
+After applying the void correction the expected bias is $-1.7\times 10^{-4}$ and the standard deviation for the bias is given by 0.0231; this is 1.2 times worse than the reconstruction given perfect knowledge of the halo masses and redshifts but still 1.5 times better than using the global P$^{\rm global}(\kappax)$; this is the reconstruction error that could be expected from a complete spectroscopic survey of the field.
+A complete spetroscopic survey is unrealistic, but Equation \ref{eq:Mstarfit2} represents a lower limit on the reconstruction error.
+For a randomly selected line of sight, the expectation value for the uncertainty on the reconstruction is 0.017 and the expectation value for the bias on E$(\kapparec)-\kapparay$ is 0.004.
 
 \begin{figure}
-\includegraphics[width=\columnwidth]{widthvkappa.eps}
-\caption[radius cut]{}
-\label{fig:width}
-\end{figure}
-
-Our results are summarized in Figure \ref{fig:width}.
-We reconstruct 10000 lines of sight and each of the reconstructed $\pr(\kappa)$ is summarized by their mean $\kapparec$, and their width containing $68\%$ of the probability, $\sigt$.
-Reconstructing the lines of sight with perfect knowledge of the redshift but an uncertain stellar mass, we find that $\sigt$ grows with $\kapparec$; this is not surprising since the low $\kapparec$ lines of sight are relatively empty and so there are few opportunities for uncertainties in the halo masses to propogate into $\kapparec$ uncertainties.
-Our results are well fit by a straight line given by
-\be
-\sigt=0.012+0.26 \langle\kapparec\rangle;
-\label{eq:Mstarfit}
-\ee
-this is the reconstruction error that could be expected from a complete spectroscopic survey of the field.
-A complete spetroscopic survey is unrealistic, but Equation \ref{eq:Mstarfit} represents a lower limit on the reconstruction error.
-We find that with a perfect knowledge of the halo mass, but photometric redshifts the reconstructed $\pr(\kappa)$ has a mean $\sigt$ of 0.003.
-For the lines of sight with $\kapparec {\rm s}$ that are dominated by a single significant perturber the photometric redshift error can induce a larger uncertainty on $\kapparec$, but only $2.9 \%$ of sightlines have $\sigt > 0.01$; typical photometric redshift errors do not propogate into a significant uncertainties on $\kapparec$ if the halo mass is known.
-This is seen in Figure \ref{fig:width}, $\sigt$ is typically much larger for the perfect redshift reconstructions than the perfect mass reconstructions.
-The results are well fit by
-\be
-\sigt=0.0025+0.041\langle\kapparec\rangle
-\label{eq:photozfit}
-\ee
-Inferring the stellar mass of a galaxy from its magnitude and colours requires an estimate of how far away the galaxy is; without a spectroscopic redshift the the infered stellar mass is less precise.
-In principle the photometric redshift is correlated with the infered stellar mass however we do not model this since the redshift error produces a small effect on the recovered $\pr(\kappa)$ when compared to the effect of uncertain stellar masses.
-For the reconstructions with imperfect redshift and stellar mass the resulting uncertainty is significantly larger than the quadrature sum of the $\sigt {\rm s}$ in Equations \ref{eq:Mstarfit} and \ref{eq:photozfit}, this is because the uncertain redshift propogates into a broadened $\pr(M_{*})$.
-The
-ns than the perfect mass reconstructions. For a complete photometric survey down to $i=26$ our reconstructions are fit by the line
-\be
-\sigt=0.026+0.037\langle\kapparec\rangle
-\label{eq:bothfit}
-\ee
-The fits are shown on Figure \ref{fig:intrinsicvsreconstruction}, where we compare the reconstruction errors with typical size of the intrinsic error from Section \ref{sec:knownMh+z}.
-With photometric redshifts only, the reconstruction error is typically half the size of the intrinsic error, but for a survey with complete spectroscopic coverage the two errors are of similar size.
-The photometric results can be greatly improved by the addition of spectroscopic redshifts for a small number of halos.
-Photometric redshifts are sufficient to estimate the $\kappa$ contribution from each halo; once this is know the most important halos can be targeted for spectroscopic follow-up.
-It is not always possible to get a spectroscopic redshift for faint objects, as such we use spectroscopic redshifts for galaxies with $i<24$ that the sitting in halos that individually contribute $\kappa>0.0005$.
-This selection corresponds to an average of $12 \pm 4$ galaxies per line of sight for which spectra are needed; the number of spectra needed per line of sight is shown as a histogram in Figure \ref{fig:spechist}.
-Such a spectroscopic survey yields only a modest improvement upon the purely photometric case being well fit by
-\be
-\sigt=+\langle\kapparec\rangle
-\label{eq:spec1fit}
-\ee
-This modest improvent appears counter intuitive, since spectra for all the subset of halos with $i<24, \kappat>0.0005$ halos contains the majority of the total $\kappax$ along alomst all lines of sight.
-The lack of significant improvement comes
-from the many massive halos that are intermediate distances from the line of sight; they do not contribute significantly to the true $\kappax$, but without spectroscopic reshifts their highly uncertain stellar masses propogate into broad $\pr(\Mhalo)$ and into small probability of large individual $\kappa$ contributions; since there are typically several hundred such objects within 5 arcminutes of the line of sight, their net contribution dominates the width of the photometrically generated $\pr(\kappax)$.
-However since massive objects are typically bright it is realtively fast to obtain their spectra with an 8~m class telescope.
-Galaxies with $i<22, \kappat>0.000001$ corresponds to roughly $200 \pm 100$ objects per line of sight; with spectroscopic redshifts for all of these plus the $i<24, \kappat>0.0005$ objects the reconstruction is greatly improved, being fit by
-\be
-\sigt=+\langle\kapparec\rangle
-\label{eq:spec1fit}
-\ee
-The case of complete photometric coverage and partial spectroscopic coverage is closest to what might be expected from a real reconstruction of a field.
-We will refer to this as the 'hybrid' case for the rest of this paper, where all galaxies with $i<22, \kappat>0.000001$ or $i<24, \kappat>0.0005$ have spectra, but no others.
-
-In Figure \ref{fig:intrinsicvsreconstruction} we show all of the fits, and compare them to the typical size of the difference between the ray-traced $\kapparay$ and the mean of the reconstructed $\kapparec$ which is a good measure of the intrinisic error in the reconstruction.
-For the purely photometric reconstruction $\sigt$ is larger than 98 percent of $|\kapparay - \langle \kapparec \rangle |$ indicating that the reconstruction is the dominant source of error.
-For the purely spectroscopic reconstruction $\sigt$ is larger than 44 percent of $|\kapparay - \langle \kapparec \rangle |$; the intrinsic error is slightly larger than the reconstruction error.
-For the hybrid case $\sigt$ is larger than 88 percent of $|\kapparay - \langle \kapparec \rangle |$, indicating that the intrinsic error is a sub-dominant effect.
-
-Since the reconstruction does not produce a symmetric $\pr(\kappax)$, we must take care in ensuring that the reconstruction has not biased $\langle \kapparec \rangle $ as an estimator of $\kapparay$.
-Figure 12 al
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{spechist.eps}
-\caption[spechist]{}
-\label{fig:spechist}
+\includegraphics[width=\columnwidth]{kappaspectro.eps}
+\caption[radius cut]{Means and widths of $\kapparec$ for a complete spectroscopic survery of all halos down $to i=26$ and within 5 arcminutes of the line of sight.
+Results for 10000 lines of sight are shown.
+Red is the width and mean after summing up all the reconstructed halo contributions.
+Blue is the width of mean after correcting for voids.
+Green is the result after weighting the PDFs so that the universal kappa distribution is recovered}
+\label{fig:width1}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{intrinsicvsreconstruction.eps}
-\caption[radius cut]{}
-\label{fig:intrinsicvsreconstruction}
+\includegraphics[width=\columnwidth]{kappasmall.eps}
+\caption[radius cut]{As figure \ref{width1}, but for a photometric reconstruction of all halos down $to i=24$ and within 2 arcminutes of the line of sight}
+\label{fig:width2}
 \end{figure}
 
-We can draw samples from this PDF and ask:
+For fixed halo masses at unknown redshifts, we follow the same proceedure as the previous paragraph.
+We again find that $\sigt$ grows with $\kapparec$, but the error is small compared to the typical uncertainties for the reconstruction of halos at fixed redshifts but with uncertain masses.
+The fit is gven by
+\be
+\sigt=-0.002+0.15 \langle\kapparec^{\rm halos}\rangle.
+\label{eq:Mstarfit}
+\ee
+Whilst redshift errors are a subdominant uncertainty at fixed halo mass, the true halo mass of an astronomical object is an unknown.
+Inferring the stellar mass of a galaxy from its magnitude and colours requires an estimate of how far away the galaxy is; without a spectroscopic redshift the the infered stellar mass is less precise.
+One should expect that given uncertain redshift and stellar mass the $\kappax$ reconstruction will be significantly more uncertain than a quadrature sum of the individual uncertainties.
+In principle the photometric redshift is correlated with the infered stellar mass, however we do not model this since the redshift error produces a small effect on the recovered $\pr(\kappa)$ when compared to the effect of uncertain stellar masses.
+For a complete photometric survey down to $i=26$ our halo reconstructions are fit by the line
+\be
+\sigt=-0.003+0.47\langle\kapparec^{\rm halos}\rangle
+\label{eq:bothfit}
+\ee
+With only photometric redshifts the uncertainty on $\kapparec^{\rm halos}$ is much larger than the spectrocopic case, and this propogates into a much larger bias after applying the void correction.
+The expectation for the bias is -0.008 which is statistically signifiant given 10000 cones and a standard deviation of 0.0235.
+The reason for this bias relates to the difficulty of reconstructing halo masses given only a photometric redsshift.
+There are many massive halos that are intermediate distances from the line of sight; they do not contribute significantly to the true $\kappax$, but without spectroscopic reshifts their highly uncertain stellar masses propogate into broad $\pr(\Mhalo)$ and into a small probability of large individual $\kappax$ contributions.
+Since there are typically several hundred such objects within 5 arcminutes of the line of sight, their net contribution dominates the width of the photometrically generated $\pr \left(\sum_{\rm halos}\kappa_{\rm halo}\right)$, and artificially increases the mean of $\sumkappah$ despite the fact that they do not contribute much to the true $\kappax$.
+In equation \ref{eq:weighting} we assumed a symmetry for the weighting scheme used to form P($\kappax$) from $\pr(\kapparay,\tilde\kappa_{\rm halos})$.
+The assumption of symmetry is not valid since $\pr(\sumkappah)$ given perfect knowledge of the halo mass and redshift does not map linearly onto $\pr(\sumkappah)$ given only a photometric survey of the field.
 
-How is the kappa inference offset and blurred by uncertainty on redshift, Mstar
-and Mhalo?
+\subsection{Reconstructions of Smaller and Shallower Fields}
+Reconstructions of real lines of sight may not have access to the deep, large calibration fields that we have used upto this point.
+We can perform the same reconstruction but for a more modest survey.
+Given the results of Section \ref{sec:knownMh+z} we predicted that a reconstruction of the field out to 2 arcminutes and a magnitude limit of $i$=24 would provide similar constraints to a reconstruction going out to 5 arcminutes and going down to $i$=26.
+For the purely photometric reconstruction the uncertainty on the halo reconstruction is given
 
-What is the effect of using the wrong Mstar-Mhalo relation?
+Without an improved model of halos and/or reconstruction of voids, a field of 2 arcminute radius and depth of $i=24$ is sufficient to adequately reconstruct the external convergence.
+
+\subsection{Reconstructing Biased Lines of Sight}
 
@@
 
+%\section{Reconstructed Kappa as a tracer of Rayraced Kappa}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\comments{
 \section{Time Delay Distances}
@@
 
+}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\section{Truncated \LCDM halos}
+\section{Truncated NFW halos}
 \label{appendix:halos}

### 2012-09-17 Pangloss/LensingProfiles.py

@@ -1,167 +1,0 @@
-import pylab
-import matplotlib.pyplot as plt
-import numpy, numpy.random as rnd, atpy
-import distances
-from mpl_toolkits.axes_grid1 import ImageGrid
-from time import clock
-from numpy import exp,pi
-from scipy.special import gamma,gammainc
-
-#import time
-#t0=time.clock()    
-
-D = distances.Distance()
-D.h = 0.7
-
-arcmin2rad = (1.0/60.0)*numpy.pi/180.0
-rad2arcmin = 1.0/arcmin2rad
-# ------------------------------------------------------------------------
-def F(x):
-    z=numpy.ones(len(x))
-    z[x>1]=numpy.arccos(1/x[x>1])/((x[x>1]**2-1)**.5)
-    lowx=x[x<1]
-    z[x<1]=numpy.arccosh(1/x[x<1])/((1-x[x<1]**2)**.5)
-    A=1.+1e-5
-    z[x==1]=numpy.arccos(1/A)/((A**2-1)**.5)
-    return z
-
-def L(x,t):
-    return numpy.log(x/(((t**2+x**2)**.5)+t))
-#=========================================================================
-# NFW profile functions.
-
-#--------------------------------------------------------------
-def delta_c(c):
-    return (200./3)*(c**3)/(numpy.log(1+c)-c/(1+c))
-# ------------------------------------------------------------------------
-
-    # Function needed to calculate kappa for an NFW halo. 
-def Ffunc(x):
-       z=numpy.zeros(len(x))
-       for i in range(len(x)):
-          if x[i]==-1:
-              z[i]=0.0
-          elif x[i]>1:
-             z[i]= (1-(2./(x[i]**2-1)**.5)*numpy.arctan(((x[i]-1.)/(x[i]+1))**.5))/(x[i]**2-1.)
-          else: 
-             #print "WARNING You are very close to a halo"
-             if x[i]==1:
-                z[i] =1./3
-             else:
-                y=(-x[i]**2+1)**.5
-                z[i] = (1.-(2./(1-x[i]**2)**.5)*numpy.arctanh(((1.-x[i])/(x[i]+1))**.5))/(x[i]**2-1)
-
-
-          if z[i] < 0: print 'warning Ffunc'
-       return 2*z
-# ----------------------------------------------------------------------------
-
-   # Function needed to calculate gamma for an NFW halo. 
[…]

### 2012-09-17 Pangloss/MSMHrelations.py

@@ -1,80 +1,0 @@
-import pylab, atpy
-import matplotlib.pyplot as plt
-import numpy
-import numpy.random as rnd
-import distances
-from mpl_toolkits.axes_grid1 import ImageGrid
-from time import clock
-import lightcone
-import cPickle
-
-
-D = distances.Distance()
-
-arcmin2rad = (1.0/60.0)*numpy.pi/180.0
-rad2arcmin = 1.0/arcmin2rad
-
-
-datafile = "/data/tcollett/Pangloss/catalogs/GGL_los_8_7_7_0_0_N_4096_ang_4_SA_galaxies_on_plane_27_to_63.images.txt"
-master = atpy.Table(datafile, type='ascii')
-
-datafile1 = "/data/tcollett/Pangloss/catalogs/GGL_los_8_7_7_3_3_N_4096_ang_4_SA_galaxies_on_plane_27_to_63.images.txt"
-datafile2 = "/data/tcollett/Pangloss/catalogs/GGL_los_8_7_7_0_3_N_4096_ang_4_SA_galaxies_on_plane_27_to_63.images.txt"
-datafile3 = "/data/tcollett/Pangloss/catalogs/GGL_los_8_7_7_3_0_N_4096_ang_4_SA_galaxies_on_plane_27_to_63.images.txt"
-
-master.append(atpy.Table(datafile1, type='ascii'))
-master.append(atpy.Table(datafile2, type='ascii'))
-master.append(atpy.Table(datafile3, type='ascii'))
-
-master = master.where(master['M_Subhalo[M_sol/h]']!=0)
-Mhalo=master['M_Subhalo[M_sol/h]']
-
-Mstars=master['M_Stellar[M_sol/h]']
-
-
-#plt.scatter(numpy.log10(Mhalo),numpy.log10(Mstars),s=1,edgecolor='none')
-#plt.show()
-#
-#print numpy.min(Mhalo)
-#print numpy.max(numpy.log10(Mhalo))
-#plt.hist(numpy.log10(Mhalo))
-#plt.show()
-#plt.hist(numpy.log10(Mstars))
-#plt.show()
-
-
-breakpoint1=13
-breakpoint2=13.5
-Mh1 =numpy.linspace(10.,10.4,2,endpoint=False)
-Mh2 = numpy.linspace(10.4,breakpoint1,50,endpoint=False)
[…]

### 2012-09-17 Pangloss/Relations.py

@@ -1,225 +1,0 @@
-import numpy
-from numpy import exp,pi
-from scipy.special import gamma
-import numpy.random as rnd
-import atpy,copy
-import matplotlib,pylab as plt
-from scipy import interpolate
-
-#--------------------------------------------------------------
-def logerr(l,m,s):
-      c=10**rnd.normal(m,s)
-      return c
-
-def MCrelation(M200,MCerror=False):
-      if MCerror==False:
-         c_200 = 4.67*(M200/(10**14))**-0.11 #Neto et al. equation 5
-      if MCerror==True:
-       c_200=4.67*(M200/(10**14))**-0.11
-       logc_200=numpy.log10(c_200)
-       lM200 = numpy.log10(M200)
-       c_new = c_200*10**(rnd.normal(1,0.2,len(M200)))/10**(1+(0.2**2)/2)
-       #print numpy.max(c_new),numpy.min(c_new)
-
-       return c_new
-
-
-       for i in range(len(M200)):    #best fit scatter parameters of neto et al (double log normal)
-         if lM200[i]<11.875: ### FILLER
-            f=0.205 ###FILLER
-            if rnd.rand()<f:
-               c_200[i]=logerr(logc_200[i],0.683,0.147) ###FILLER
-            else:
-               c_200[i]=logerr(logc_200[i],0.920,0.106) ###FILLER
-         if lM200[i]<12.125:
-            f=0.205
-            if rnd.rand()<f:
-               c_200[i]=logerr(logc_200[i],0.683,0.147)
-            else:
-               c_200[i]=logerr(logc_200[i],0.920,0.106)
-         elif lM200[i]<12.375:
-            f=0.171
-            if rnd.rand()<f:
-               c_200[i]=logerr(logc_200[i],0.658,0.150)
-            else:
-               c_200[i]=logerr(logc_200[i],0.903,0.108)
-         elif lM200[i]<12.625:
-            f=0.199
-            if rnd.rand()<f:
-               c_200[i]=logerr(logc_200[i],0.646,0.139)
-            else:
-               c_200[i]=logerr(logc_200[i],0.881,0.099)        
-         elif lM200[i]<12.875:
-            f=0.229
-            if rnd.rand()<f:
-               c_200[i]=logerr(logc_200[i],0.605,0.158)
-            else:
[…]

### 2012-09-17 Pangloss/__init__.py

@@ -1,9 +1,0 @@
-from lightcone import *
-from kappamap import *
-from grid import *
-from LensingFunc import *
-from LensingProfiles import *
-import Relations as Rel
-from smooth import *
-
-#from lightcone_reconstruction import *

### 2012-09-17 Pangloss/blurred_relations.py

@@ -1,63 +1,0 @@
-import pylab, atpy
-import matplotlib.pyplot as plt
-import numpy
-import numpy.random as rnd
-import distances
-from mpl_toolkits.axes_grid1 import ImageGrid
-from time import clock
-import lightcone
-
-datafile = "../../data/GGL_los_8_0_0_1_1_N_4096_ang_4_STARS_SA_galaxies_ANALYTIC_SA_galaxies_on_plane_27_to_63.images.txt"
-master = atpy.Table(datafile, type='ascii')
-print "Read in master table, length",len(master)
-
-
-plt.clf()
-rmax = 2
-
-zs=2.0 #should be selecting a source redshift (possibly use forecaster from Collett et al. 2012)
-
-
-xpos = -0.00633
-ypos = -0.01731
-zl =  1.0 
-xc = []
-#xc = [xpos,ypos,zl] #leave as [] to select a lens at random
-
-iter=30
-
-
-for j in [5]:
-#for j in [0,1,6,5,14,12]:
-#for j in range(iter):
-    lc = lightcone.lightcone(master,rmax,zs,lensindex=j,position=xc)
-
-# calculate a 'blurred' kappa keeton.
-    
-    lc.make_kappa_contributions(deterministic=True)
-    kappatrue=numpy.sum(lc.galaxies.kappa_keeton)
-    print kappatrue
-
-
-# calculate the 'real' kappa_keeton.
-    iterations=200
-    K=numpy.zeros(iterations)
-
-    for iteration in range(iterations): 
-        lc.make_kappa_contributions(deterministic=False,photozerror=True,halomasserror=True,MCerror=True)
-        K[iteration] = lc.kappa_blurred
-
-
-    bins=numpy.arange(-0.26,0.29,0.001)
-    plt.clf()
-    plt.hist(K,bins,normed=True)
-    plt.axvline(x=kappatrue, ymin=0,ymax=1, c='k', ls='dashed')
-    plt.xlabel("$\kappa_{ext}$")
-    plt.ylabel("pdf($\kappa_{ext}$)")
-    plt.xlim([kappatrue-0.04,kappatrue+0.04])
-
-#plt.title('Perfect information, but 5% error on z_perturbers, 30% error on M_Halo')
-    pngfile = 'photozerror/Kappa_keeton_blurred_%i.png' %j
-    plt.savefig(pngfile)
-    
-    print "Plot saved in",pngfile

### 2012-09-17 Pangloss/cataloguemasses.py

@@ -1,66 +1,0 @@
-import pylab, atpy
-import matplotlib.pyplot as plt
-import numpy
-import numpy.random as rnd
-import distances
-from mpl_toolkits.axes_grid1 import ImageGrid
-from time import clock
-import lightcone
-
-D = distances.Distance()
-D.h = 0.7
-arcmin2rad = (1.0/60.0)*numpy.pi/180.0
-rad2arcmin = 1.0/arcmin2rad
-
-datafile = "../../data/GGL_los_8_0_0_1_1_N_4096_ang_4_STARS_SA_galaxies_ANALYTIC_SA_galaxies_on_plane_27_to_63.images.txt"
-
-# First 99 lines of the same, for testing:
-#datafile = "test.txt"
-    
-cat = atpy.Table(datafile, type='ascii')
-print "Read in master table, length",len(cat)
-
-def MCrelation(M200,MCerror=False):
-    c_200 = 4.67*(M200/(10**14))**0.11 #Neto et al. equation 5
-    return c_200
-
-def Hsquared(z):
-    H0 =D.h*3.241*10**-18
-    Hsq=(H0**2.)*(D.OMEGA_M*(1.+z)**3.+(1.-D.OMEGA_M)) #Flat LambdaCDM only at this stage
-    return Hsq
-
-def rho_crit_univ(z):   #critical density of the universe at z
-    ro= (2.642*10**46)*Hsquared(z) #units of solar mass per cubic megaparsec, H(z) must be in units of per second.
-    return ro 
-
-def delta_c(c):
-    return (200./3)*(c**3)/(numpy.log(1+c)-c/(1+c))
-
-
-M200 = cat['M_Subhalo[M_sol/h]']
-c200 = MCrelation(M200)
-cat.add_column('NetoC', c200)
-rhocrit=rho_crit_univ(cat['z_spec'] )
-r200 = (3*M200/(800*3.14159*rhocrit))**(1./3)
-cat.add_column('r200TRUE', r200)
-
-rs = r200/c200
-rhos = delta_c(c200)*rhocrit 
-
-truncationscale=[1,2,3,5,8,10]
-for i in range(len(truncationscale)):
-    R_trunc=truncationscale[i]*r200
-    
-    mass=4*3.14159*rhos*(rs**3)  *     \
-        (  numpy.log(1+(R_trunc)/rs) - \
-               R_trunc/(rs+R_trunc)    \
-        )
[…]

### 2012-09-17 Pangloss/grid.py

@@ -1,497 +1,0 @@
-'''
-This file is part of the Pangloss project.
-Copyright 2012 Tom Collett (IoA) and Phil Marshall (Oxford).
-
-description:
-------------
-Code to make a lensgrid object, which lightcone objects and smooth comoponent objects can be 'snapped' to.
-
-to-do:
-------
-It should work now. TC #noguarantees
-
-issues:
--------
-
-
-
-'''
-
-# ==========================================================================
-
-import pylab
-import matplotlib.pyplot as plt
-import numpy
-import numpy.random as rnd
-import distances
-from mpl_toolkits.axes_grid1 import ImageGrid
-from time import clock
-import LensingProfiles as LP
-import LensingFunc as LF
-import cPickle
-import Relations as Rel
-from scipy import interpolate,optimize
-import copy
-
-#t0=time.clock()    
-
-arcmin2rad = (1.0/60.0)*numpy.pi/180.0
-rad2arcmin = 1.0/arcmin2rad
-
-vb = False
-
-# ============================================================================
-
-class grid(distances.Distance):
-   def __init__(self,zmax=3,nplanes=100,cosmo=[0.25,0.75,0.73],filename=None):
-       distances.Distance.__init__(self,cosmo=cosmo)
-       """ Allow for empty instantiation """
-       if filename is not None:
-           self.load(filename)
-           return
-       self.name = '1D Redshift grid, with precalculated quantities '
-       self.zmax=zmax
-       self.nplanes=nplanes    
-       #These are the planes:
-       self.zplane,self.dz=self.redshiftbins=numpy.linspace(0.0,self.zmax,self.nplanes,endpoint=True,retstep=True)
-
-       self.Da_p=numpy.zeros(len(self.zplane))
-       for i in range(len(self.zplane)):
-           self.Da_p[i]= self.Da(self.zplane[i])+1e-100
-       self.rho_crit_p=self.rho_crit_univ(self.zplane)
-
-       self.cosmo=cosmo
-
-   def snap(self,z):
-      snapped_p=numpy.digitize(z,self.zplane-(self.dz)/2)-1
-      snapped_z=self.zplane[snapped_p]
-      return snapped_z,snapped_p
-
-
[…]

### 2012-09-17 Pangloss/growth.py

@@ -1,167 +1,0 @@
-import lightcone
-import pylab, atpy
-import matplotlib.pyplot as plt
-import numpy
-import numpy.random as rnd
-import distances
-from mpl_toolkits.axes_grid1 import ImageGrid
-from time import clock
-
-D = distances.Distance()
-arcmin2rad = (1.0/60.0)*numpy.pi/180.0
-rad2arcmin = 1.0/arcmin2rad
-
-
-datafile = "../../data/GGL_los_8_0_0_1_1_N_4096_ang_4_STARS_SA_galaxies_ANALYTIC_SA_galaxies_on_plane_27_to_63.images.txt"
-
-
-catalog= atpy.Table(datafile, type='ascii')
-
-xmax = catalog['pos_0[rad]'].max()
-xmin = catalog['pos_0[rad]'].min()
-ymax = catalog['pos_1[rad]'].max()
-ymin = catalog['pos_1[rad]'].min()
-
-rmax = 20
-
-iterations = 1
-xpos=rnd.uniform(xmin+rmax*arcmin2rad,xmax-rmax*arcmin2rad,iterations)
-ypos=rnd.uniform(ymin+rmax*arcmin2rad,ymax-rmax*arcmin2rad,iterations)
-xpos=[-0.00645898, -0.01021756, -0.01018463]
-ypos=[-0.00366765, -0.00836147, -0.00995278]
-
-print xpos,ypos
-
-for k in range(iterations):
-    hardcut=3
-    plt.clf()
-
-    zs=1.4 
-    zl =  0.6
-
-    xc = [xpos[k],ypos[k],zl]
-    print "Initialising lightcone data..."
-    lc = lightcone.lightcone(catalog,rmax,zs,position=xc)
-
-
-    #print "Distributing dark matter in halos..."
-    #lc.make_dmhalos()
-    #lc.plot(dmhalos=True)
- 
-    #print "Distributing stars in galaxies..."
-    #lc.make_galaxies()
-    #lc.plot(galaxies=True)
- 
-    #print "Computing Keeton (2003) convergence at optical axis due to each halo..."
-
-    lc.make_kappa_contributions(truncation="hard",truncationscale=10)
-    i=(numpy.argsort(lc.galaxies.kappa_keeton))[-1]
-    if k == 0:
-        mostimportant=lc.galaxies.rows([i])
-        mostimportant.add_column('kappa_total', numpy.sum(lc.galaxies.kappa_keeton))
-    else: 
[…]

### 2012-09-17 Pangloss/kappamap.py

@@ -1,304 +1,0 @@
-'''
-This file is part of the Pangloss project.
-Copyright 2012 Tom Collett (IoA) and Phil Marshall (Oxford).
-
-to-do
------
-- check that kappa map is being read in the right way around...
-'''
-
-import numpy, os, string
-import struct, pyfits
-import pylab as plt
-import random as rnd
-import cPickle
-
-arcmin2rad = (1.0/60.0)*numpy.pi/180.0
-rad2arcmin = 1.0/arcmin2rad
-deg2rad = numpy.pi/180.0
-rad2deg = 1.0/deg2rad
-
-vb = False
-
-# ============================================================================
-    
-# Read in, write out, look up convergence kappa in map from Stefan Hilbert.
-
-class kappamap:
-
-   def __init__(self,kappafile,FITS=True,vb=False):
-
-      self.name = 'Convergence map kappa from Millenium Simulation, zs = 1.6'
-      self.input = kappafile
-
-      # Read in data from file:
-      
-      if FITS:
-         # Read in FITS image, extract wcs:
-         if vb: print "Reading in map from file "+kappafile
-         self.read_in_fits_data()
-       
-      else:
-
-         # Initialise some necessary WCS parameters:
-         self.field = 4.0 # degrees
-         self.NX = 4096
-         self.PIXSCALE = self.field/(1.0*self.NX) # degrees
-         self.setwcs()
-
-         # Read in binary data, to self.values:
-         if vb: print "Reading in map from file "+kappafile
-         self.read_in_binary_data()
-
-         # If it doesn't already exist, output the map to FITS file:
-         # pieces = string.split(self.input,'.')
-         # self.output = string.join(pieces[0:len(pieces)-1],'.')+'.fits'
-         self.output = self.input+'.fits'
-         if os.path.exists(self.output): 
-           if vb: print "FITS version already exists: ",self.output
-         else:  
-           if vb: print "Writing map to "+self.output
-           self.write_out_to_fits()
-         # This should probably not be in __init__ but hopefully it only gets run once.  
-      
-      return None
-
-# ----------------------------------------------------------------------------
-
-   def __str__(self):
-      return 'Convergence map'
-
[…]

### 2012-09-17 Pangloss/lightcone.py

@@ -1,995 +1,0 @@
-'''
-This file is part of the Pangloss project.
-Copyright 2012 Tom Collett (IoA) and Phil Marshall (Oxford).
-
-description:
-------------
-
-Given a catalog, drill out a narrow pencil beam defined by position
-vector  xc and some radius.
-
-# NB. Anything marked '###' is still unfinished/preliminary and 
-probably wrong! #### are finished functions that haven't been 
-bug-checked.
-
-to-do:
-------
-- finish basic functions
-- carry out curve of growth test
-- decide whether to continue
-
-issues:
--------
-- stellar mass is not included yet
-- so lines of sight passing close to halos will not be accurate
-- Born approximation will break down in this case anyway
-- Keeton approximation may well be way off, need better approx from 
-    Roger, Sherry and Stefan.
-- lightcone and lenslightcone should be separate classes, where llc 
-    inherits from lc
-
-
-
-In need of array optimization
------------------------------
-- The LensingProfiles class
-- The beta function.
-- Mstar to MBehrooziHalo
-
-
-
-The warning: divide by zero comes from the grid class, but it isn't causing any errors.
-'''
-
-# ======================================================================
-
-import pylab
-import matplotlib.pyplot as plt
-import numpy, numpy.random as rnd, atpy
-from mpl_toolkits.axes_grid1 import ImageGrid
-from time import clock
-import LensingProfiles as LP
-import LensingFunc as LF
-import grid as GRID
-import Relations as Rel
-import cPickle
-#import time
-#t0=time.clock()    
-
-arcmin2rad = (1.0/60.0)*numpy.pi/180.0
-rad2arcmin = 1.0/arcmin2rad
-
-vb = False
-
-# ============================================================================
- 
-class lightcone(object):
-    def __init__(self,catalog,position,radius,magnitudecut=99,band="r"):
-        self.name = 'Lightcone through the observed Universe'
-        self.catalog = catalog
-        self.xmax = self.catalog['pos_0[rad]'].max()
-        self.xmin = self.catalog['pos_0[rad]'].min()
-        self.ymax = self.catalog['pos_1[rad]'].max()
-        self.ymin = self.catalog['pos_1[rad]'].min() 
-        self.rmax = radius
[…]

### 2012-09-17 Pangloss/smooth.py

@@ -1,239 +1,0 @@
-#!/usr/bin/env python
-# ======================================================================
-
-import LensingFunc as LF
-import Relations as Rel
-import LensingProfiles as LP
-import grid as GRID
-
-
-import sys,getopt,atpy,pyfits
-import pylab,matplotlib.pyplot as plt
-import numpy
-import numpy.random as rnd
-from scipy import optimize
-from scipy import stats
-
-#import time
-
-arcmin2rad = (1.0/60.0)*numpy.pi/180.0
-rad2arcmin = 1.0/arcmin2rad
-
-# ======================================================================
-
-def smooth(zl,zs,catalogues,truncationscale=10,magnitudecut=99,band='r',nplanes=100,hardcut="RVir",cosmo=[0.25,0.75,0.73],scaling="add",errors=True,grid=None,centralsonly=False, Mh2Mh=False, perfectsatellites=False):
-   #print time.clock()
-   if grid==None:
-      lg=GRID.lensgrid(zl,zs,nplanes=nplanes,cosmo=cosmo)
-      lg.populatelensgrid()
-   else: lg=grid
-
-
-   smoothcomponentindiv=numpy.zeros((lg.nplanes,len(catalogues)))
-   smoothcomponent=numpy.zeros(lg.nplanes)
-   
-   #print "grid",time.clock() 
-
-
-   if band == "u" or band ==  "g" or band == "r" or band ==  "i" or band == "z":
-      col = "mag_SDSS_%s" % band
-       #elif band == "F814" or band == "F814W" or band == "814" or band == 814:
-       #    col = "mag_F814W"
-   else:
-      col = "mag_%s" % band
-
-
-   i=0
-   for datafile in catalogues:
-      cat = datafile#atpy.Table(datafile, type='ascii')
-      #print "cat read in", time.clock()
-      cat=cat.where(cat["%s"%col] < magnitudecut)
-      if centralsonly==True:
-         cat=cat.where(cat.Type==0)
-      #cat=cat.where(cat.Type!=2)
-
-      xmax = cat['pos_0[rad]'].max()
-      xmin = cat['pos_0[rad]'].min()
-      ymax = cat['pos_1[rad]'].max()
[…]

### 2012-09-28 doc/paper-lcr.tex
draft update

@@
 \be
+\label{eq:weighting}
 W(\tilde\kappa_{\rm halos}-\tilde\kappa'_{\rm halos})=\exp\left(-\frac{1}{2}\left(\frac{\left(\tilde\kappa_{\rm halos}-\tilde\kappa'_{\rm halos}\right)^2}{\sigma^2}\right)\right)
 \ee
-We take $\sigma$ as 0.01- this is an overestimate of the uncertainty on $\tilde\kappa_{\rm halos}$, but ensures that the full distibution of void corrections is sampled, despite the finite number of calibration sightlines.
+We take $\sigma$ as 0.005- this is an overestimate of the uncertainty on $\tilde\kappa_{\rm halos}$, but ensures that the full distibution of void corrections is sampled, despite the finite number of calibration sightlines.
 
@@
 The final test that we apply to the perfect knowledge reconstruction is to apply the marginalization outlined in Section \ref{subsec:voids}.
-Taking the reconstructed $\sumkappah$ for $1\times 10^{-5}$ lines of sight we form the joint distribution, P$(\kapparay,\sumkappah)$ and marginalize over all sightlines with a similar $\sumkappah$ to give P($\kappax$).
-We define the bias as the difference between the expectation value of $\kappax$ and the known true value of $\kapparay$ for each Line of sight.
-From $1\times 10^{4}$ reconstructed lines of sight we find the the bias to have mean of $2.0\times 10^{-5}$ and standard deviation of 0.0193.
-In the case where one assumes P$(\kappax)$ is given by the global P$^{\rm global}(\kappax)$, the same $1e4$ lines of sight show a mean bias of $7.7\times 10^{-4}$ and the bias has a standard deviation of 0.0346.
+Taking the reconstructed $\sumkappah$ for $1\times 10^{5}$ lines of sight we form the joint distribution, P$(\kapparay,\sumkappah)$ and marginalize over all sightlines with a similar $\sumkappah$ to give P($\kappax$).
+We define the bias as the difference between the expectation value of $\kappax$ and the known true value of $\kapparay$ for each Line of sight and we define the reconstruction width as half the width of the interval containing the central $68\%$ of the probability P($\kappax$).
+From $1\times 10^{4}$ reconstructed lines of sight we find the the bias to have mean of $-9.5\times 10^{-6}$ and a mean reconstruction width of 0.0132.
+In the case where one assumes P$(\kappax)$ is given by the global P$^{\rm global}(\kappax)$, the same $1\times 10^{5}$ lines of sight show a mean bias of $4.3\times 10^{-5}$ and mean reconstruction width of 0.237.
 Within the statistical error both methods are unbiased, but for any individual line of sight the bias is typically 1.8 times smaller with the reconstructed P$^{\rm reconstruction}(\kappax)$, rather than global P$^{\rm global}(\kappax)$.
@@
 stellar mass and photometric redshifts (with appropriate errors), as the observables that must be converted into an estimate
-of $\kappax$.
-We will investigate two main sources of error: inferring halo mass given observed stellar mass and the combination of stellar mass errorsand placing halos at the wrong redshift due to photometric redshift error.
+of $\kappax$. We will investigate two main sources of error: inferring halo mass given observed stellar mass and placing halos at the wrong redshift due to photometric redshift error.
 
 We generate a stellar mass for each halo according to the stellar mass--halo mass relation of \citet{behroozi2010}. From this stellar mass we simulate 
-an observed stellar mass by drawing a sample from $\pr(\log(M_{* \mathrm {obs}})|\log(M_{* \mathrm {true}}))$ which is given by the product of the galaxy stellar mass function (GSMF) of \citet{Fontana2006} and a Gaussian of width $\sigma_{M_*}$ centred on $\log(M*_{\mathrm {true}})$.
+an observed stellar mass by drawing a sample from $\pr(\log(M_{* \mathrm {obs}})|\log(M_{* \mathrm {true}}))$ which is given by \comments{ the product of the galaxy stellar mass function (GSMF) of \citet{Fontana2006} and} a Gaussian of width $\sigma_{M_*}$ centred on $\log(M*_{\mathrm {true}})$.
 Where a spectroscopic redshift exists stellar masses can be estimated with typical uncertainties of 0.15 dex \citep{xxx}, however with photometric redshifts stellar mass uncertainties are typically three times as large \citep{xxx}; we use $\sigma_{M_*}=0.15$ for halos with a spectroscopic redshift and $\sigma_{M_*}=0.45$ otherwise.
-The \citet{Fontana2006} GSMF is given by a Schechter function with redshift evolving parameters
+\comments{The \citet{Fontana2006} GSMF is given by a Schechter function with redshift evolving parameters
 \be
@@
 \ee 
-where $M_0(z)=11.16+0.17z-0.07z^2$ and $\alpha(z)=-1.18-0.082z$.
-For photometric redshift errors we draw a redshift from $\pr(z_{\rm true}|z_{\rm obs})$ which we take as a Gaussian of width $0.1(1+z_{\rm spec})$ centred on $z_{\rm spec}$, where $z_{\rm spec}$ is the halo's true redshift in the \MS catalogue
+where $M_0(z)=11.16+0.17z-0.07z^2$ and $\alpha(z)=-1.18-0.082z$.} For photometric redshift errors we draw a redshift from $\pr(z_{\rm true}|z_{\rm obs})$ which we take as a Gaussian of width $0.1(1+z_{\rm spec})$ centred on $z_{\rm spec}$, where $z_{\rm spec}$ is the halo's true redshift in the \MS catalogue
 
-For each investigated source of error, we reconstruct 10000 lines of sight and each of the reconstructed $\pr(\sumkappah)$ is summarized by their mean $\sumkappah$, and their half-width containing $68\%$ of the probability, $\sigt$.
-Reconstructing the lines of sight with perfect knowledge of the redshift but an uncertain stellar mass, we find that $\sigt$ grows with $\sumkappah$; this is not surprising since the low $\sumkappah$ lines of sight are relatively empty and so there are few opportunities for uncertainties in the halo masses to propogate into $\sumkappah$ uncertainties.
-The means and widths of these reconstructions are summarized in Figure \ref{fig:width1}, before and after applying the void correction and global prior ${\rm U}(\kappax)$.
-Before applying the void correction, the width of the reconstructions are roughly proportional to the mean of $\sumkappah$; they are well fit by a straight line given by
-\be
-\sigt=-0.003+0.25 \langle\sumkappah\rangle.
-\label{eq:Mstarfit}
-\ee
-After applying the void correction the expected bias is $-1.7\times 10^{-4}$ and the standard deviation for the bias is given by 0.0231; this is 1.2 times worse than the reconstruction given perfect knowledge of the halo masses and redshifts but still 1.5 times better than using the global P$^{\rm global}(\kappax)$; this is the reconstruction error that could be expected from a complete spectroscopic survey of the field.
-A complete spetroscopic survey is unrealistic, but Equation \ref{eq:Mstarfit2} represents a lower limit on the reconstruction error.
-For a randomly selected line of sight, the expectation value for the uncertainty on the reconstruction is 0.017 and the expectation value for the bias on E$(\kapparec)-\kapparay$ is 0.004.
+For each  source of error, we reconstruct 40000 calibration lines of sight and 10000 mock lens lines of sight, following the proceedure outlined in Section \ref{sec:model}.
+Reconstructing the lines of sight with perfect knowledge of the redshift but an uncertain stellar mass, we find that the width of $\Pr\left(\sumkappah \right)$ grows with the expectation value of $\sumkappah$; this is not surprising since the low $\sumkappah$ lines of sight are relatively empty and so there are few opportunities for uncertainties in the halo masses to propogate into $\sumkappah$ uncertainties.
+After applying the void correction the expected bias from our 10000 mock lenses is $6.7\times 10^{-5}$ and the mean reconstruction width is 0.0145; this is the typical reconstruction error that could be expected from a complete spectroscopic survey of the field, it is ten percent worse than the reconstruction given perfect knowledge of the halo masses and redshifts but still 1.6 times better than using the global P$^{\rm global}(\kappax)$ although a complete spetroscopic survey is still unrealistic.
+The distribution of the widths of $\Pr\left(\kappax \right)$ is shown in Figure \ref{fig:width1}
 
 \begin{figure}
-\includegraphics[width=\columnwidth]{kappaspectro.eps}
-\caption[radius cut]{Means and widths of $\kapparec$ for a complete spectroscopic survery of all halos down $to i=26$ and within 5 arcminutes of the line of sight.
+\includegraphics[width=\columnwidth]{cornerplot.eps}
+\caption{68 \% and 95 \% contours of the joint distribution $\pr(\kapparay, \tilde\kappa_{\rm halos})$ given a mock reconstruction of our 40000 calibration lines of sight.
+$\tilde\kappa_{\rm halos}$ is the median of $\pr(\sumkappah)$ given a spectroscopic redshift for each halo.
+$\kapparay$ and $\tilde\kappa_{\rm halos}$ are strongly correlated, despite the blurring effect of uncertain halo masses.}
+\label{fig:corner}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{widths.eps}
+\caption{Widths of $\pr(\kappax)$ after applying our reconstruction of all halos down $to i=26$ and within 5 arcminutes of the line of sight.
 Results for 10000 lines of sight are shown.
-Red is the width and mean after summing up all the reconstructed halo contributions.
-Blue is the width of mean after correcting for voids.
-Green is the result after weighting the PDFs so that the universal kappa distribution is recovered}
+Green is for a reconstruction given perfect knowledge of halo mass and redshift, blue is for a reconstruction given a spectroscopic redshift for every halo, and red is for a reconstruction with photometric redshifts only.
+The dashed black line shows the width of the global $\pr(\kappax)$ distribution; the reconstruction process provides roughly a factor of 2 improvement for the majority of lines of sight.
+Spectroscopic redshifts improve the reconstruction, but at signifcant observational cost.}
 \label{fig:width1}
@@
 
+Inferring the stellar mass of a galaxy from its magnitude and colours requires an estimate of how far away the galaxy is; without a spectroscopic redshift the the infered stellar mass is less precise.
+In principle the photometric redshift is correlated with the infered stellar mass, however we do not model this effect since the convergence from the outskirts of an individual halo is only weakly dependant on redshift at fixed mass: the redshift error is small effect on the recovered $\pr(\kappa)$ when compared to the effect of uncertain stellar masses.
+With only photometric redshifts the uncertainty on $\sum\kapparec^{\rm halos}$ is much larger than the spectrocopic case, but this does not propogate into a much larger bias after applying the void correction; with a purely photometric reconstruction of the 10000 mock lightcones the results have a mean bias of $1.1\times 10^{-4}$ and a mean width of 0.0158.
+On average a purely photometric reconstruction of the field gives an unbiased $\pr(\kappax)$ that is 1.5 times tighter than assuming the global $\pr^{\rm global}(\kappax)$.
+
+\subsection{Reconstructions of Smaller and Shallower Fields}
+
 \begin{figure}
-\includegraphics[width=\columnwidth]{kappasmall.eps}
-\caption[radius cut]{As figure \ref{width1}, but for a photometric reconstruction of all halos down $to i=24$ and within 2 arcminutes of the line of sight}
+\includegraphics[width=\columnwidth]{widths2.eps}
+\caption{Widths of $\pr(\kappax)$ after a photometric reconstruction of all halos within different fields.
+The different field sizes and depths are given in the legend.
+As the field becomes smaller or shallower, fewer halos are being reconstructed and so the width of $\pr(\kappax)$ grows.}
 \label{fig:width2}
@@
 
-For fixed halo masses at unknown redshifts, we follow the same proceedure as the previous paragraph.
-We again find that $\sigt$ grows with $\kapparec$, but the error is small compared to the typical uncertainties for the reconstruction of halos at fixed redshifts but with uncertain masses.
-The fit is gven by
-\be
-\sigt=-0.002+0.15 \langle\kapparec^{\rm halos}\rangle.
-\label{eq:Mstarfit}
-\ee
-Whilst redshift errors are a subdominant uncertainty at fixed halo mass, the true halo mass of an astronomical object is an unknown.
-Inferring the stellar mass of a galaxy from its magnitude and colours requires an estimate of how far away the galaxy is; without a spectroscopic redshift the the infered stellar mass is less precise.
-One should expect that given uncertain redshift and stellar mass the $\kappax$ reconstruction will be significantly more uncertain than a quadrature sum of the individual uncertainties.
-In principle the photometric redshift is correlated with the infered stellar mass, however we do not model this since the redshift error produces a small effect on the recovered $\pr(\kappa)$ when compared to the effect of uncertain stellar masses.
-For a complete photometric survey down to $i=26$ our halo reconstructions are fit by the line
-\be
-\sigt=-0.003+0.47\langle\kapparec^{\rm halos}\rangle
-\label{eq:bothfit}
-\ee
-With only photometric redshifts the uncertainty on $\kapparec^{\rm halos}$ is much larger than the spectrocopic case, and this propogates into a much larger bias after applying the void correction.
-The expectation for the bias is -0.008 which is statistically signifiant given 10000 cones and a standard deviation of 0.0235.
-The reason for this bias relates to the difficulty of reconstructing halo masses given only a photometric redsshift.
-There are many massive halos that are intermediate distances from the line of sight; they do not contribute significantly to the true $\kappax$, but without spectroscopic reshifts their highly uncertain stellar masses propogate into broad $\pr(\Mhalo)$ and into a small probability of large individual $\kappax$ contributions.
-Since there are typically several hundred such objects within 5 arcminutes of the line of sight, their net contribution dominates the width of the photometrically generated $\pr \left(\sum_{\rm halos}\kappa_{\rm halo}\right)$, and artificially increases the mean of $\sumkappah$ despite the fact that they do not contribute much to the true $\kappax$.
-In equation \ref{eq:weighting} we assumed a symmetry for the weighting scheme used to form P($\kappax$) from $\pr(\kapparay,\tilde\kappa_{\rm halos})$.
-The assumption of symmetry is not valid since $\pr(\sumkappah)$ given perfect knowledge of the halo mass and redshift does not map linearly onto $\pr(\sumkappah)$ given only a photometric survey of the field.
+Reconstructions of real lines of sight may not have access to the deep, large calibration fields that we have used upto this point.
+We can perform the same reconstruction but for a more modest mock survey.
+Given the results of Section \ref{sec:knownMh+z} we predicted that a reconstruction of the field out to 2 arcminutes and a magnitude limit of $i$=24 would provide similar constraints to a reconstruction going out to 5 arcminutes and going down to $i$=26.
+We find the mean reconstruction width to be 0.0163 for a photometric reconstruction of all the halos within 2 arcminutes that have $i<24$, this is only marginally worse than 0.0158 which was the typical width after the deeper and wider reconstruction of the previous section.
+The reconstruction widths for our 10000 mock lens lines of sight are shown in Figure \ref{fig:widths2}.
+If only photometry for halos with $i<24$ and within 1 arcminute of the line of sight is availble then the typical width of the reconstructed $\pr(\kappax)$ is 0.173.
+Whilst a complete spectroscopic survey of a large field would be unlikely, a hybrid strategy of obtaining spectra for a subset of objects may be feasible.
+Photometric redshifts are sufficient to asertain the halos which are likely to contribute most of the convergence on any given line of sight, and on average there are only $\sim 6 \pm 6$ halos per line of sight that individually contribute more than 0.002 to $\sumkappah$.
+We investigate a hybrid strategy of obtaining spectroscopic redshifts for all of the $i<24$ halos which contribute an individual $\kappa$ of at least 0.002 combined with a photometric redshift for all other $i<24$ halos within 2 arcminutes.
+For the hybrid strategy the typical width of the reconstructed $\pr(\kappax)$ is 0.0151.
+The observational cost of obtaining spectroscopic redshifts for several 24th magnitude galaxies may make the hybrid strategy unlikley, but obtaining photometry of a 4$\times$4 arcminute patch of sky down to $i=24$ is fast with modern telescopes.
+The mean reconstruction width for a photometric reconstruction of all the halos within 2 arcminutes that have $i<24$ represents an improvement of 1.5 over using the global $\pr(\kappax)$ and should be achievable at minimal observational cost.
 
-\subsection{Reconstructions of Smaller and Shallower Fields}
-Reconstructions of real lines of sight may not have access to the deep, large calibration fields that we have used upto this point.
-We can perform the same reconstruction but for a more modest survey.
-Given the results of Section \ref{sec:knownMh+z} we predicted that a reconstruction of the field out to 2 arcminutes and a magnitude limit of $i$=24 would provide similar constraints to a reconstruction going out to 5 arcminutes and going down to $i$=26.
-For the purely photometric reconstruction the uncertainty on the halo reconstruction is given
-
-Without an improved model of halos and/or reconstruction of voids, a field of 2 arcminute radius and depth of $i=24$ is sufficient to adequately reconstruct the external convergence.
-
-\subsection{Reconstructing Biased Lines of Sight}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\section{Reconstructed Kappa as a tracer of Rayraced Kappa}
+%\subsection{Reconstructing Biased Lines of Sight}
 
@@
 \label{sec:discuss}
+
+The uncertainties in our reconstruction is dominated by a
 

### 2012-09-29 doc/paper-lcr.tex
draft update

@@
 photometric redshift and stellar mass of galaxies observed in optical imaging
-surveys of the field in question. Tests using mock catalogs from the Millenium
-Simulation and comparing to ray-traced $\kappa$ values, we find that \ldots 
-The $\Pr(\xkappa)$ from this reconstruction process are narrower than the
-expected distribution of $\xkappa$ values over an ensemble of time delay lenses:
-incorporating the photometric catalogs in a joint analysis of 100 lenses 
-leads to an increase in precision of factor of 1.X over simple averaging. We
-investigate several sources of bias and determine \ldots
+surveys of the field in question. We use mock catalogs from the Millenium
+Simulation and compare our reconstructed $\Pr(\xkappa)$ to ray-traced $\kappa$ values,
+we find that our model produces an unbiased estimator of $\kappax$,
+For each lightcone the individual $\Pr(\xkappa)$ from this reconstruction process are
+typically 1.8 times narrower than the global distribution of $\xkappa$ given perfect knowledge 
+of the halo mass and redshift. After incorporating uncertainties on redshift and halo and stellar masses
+we typically find that the reconstruction yields an improvement factor of 1.5. For each line of sight the
+ $\Pr(\xkappa)$ can be formed before the investment of light-curve monitoring. By following up only the 
+most costrained lines of sight a factor of 2 improvement over the global $\pr(\kappax)$ should be 
+achievable.
 \end{abstract}
@@
 \ee
-We take $\sigma$ as 0.005- this is an overestimate of the uncertainty on $\tilde\kappa_{\rm halos}$, but ensures that the full distibution of void corrections is sampled, despite the finite number of calibration sightlines.
+We take $\sigma$ as 0.002- this is an overestimate of the uncertainty on $\tilde\kappa_{\rm halos}$, but ensures that the full distibution of void corrections is sampled, despite the finite number of calibration sightlines.
 
@@
 
-The uncertainties in our reconstruction is dominated by a
+We have shown that reconstructing the matter due to halos along any line of sight can give meaningful and unbiased constraints on the external convergence along that line of sight.
+The total convergence along a line of sight is strongly correlated with the reconstructed $\sumkappah$.
+However since our model ignores voids and assumes all halos follow a spherical truncated-NFW profile our model does not include all of the relevant physics, hence the width of our resulting $\pr(\kappax)$ is still typically $\sim$0.01, even with a perfect knowledge of every halo's virial mass and redshift.
+To make further progress a more advanced treatment of both voids and halos will be necessary.
+Interestingly, we have found that the most empty lines of sight can be reconstructed with the most precision.
+$\kappax$ for empty lines of sight have little contributions from halos and a large contribution from voids; since they have the tightest PDFs after the reconstruction it seems that our model's biggest uncertainties are driven by naively reconstructing halos rather than neglecting voids.
+With a photometric reconstruction of the field there is only a small broadening compared to the perfect knowledge reconstruction; it seems that deviations from sphericity and dark matter clumping within the main halo are the dominant uncertainies rather than uncertainties in the halo mass.
+Inferring halo ellipticity and dark matter clumping will likely always remain a difficulty for line of sight reconstruction; as Figures \ref{fig:magcut} and \ref{fig:width2} show observing deeper than 24th magnitude does not signifcantly help the reconstruction.
+Because our reconstruction is mostly limited by the model, spectroscopic coverage can only provide a modest improvement to the reconstruction and at significant observational cost.
 
-Why reconstruction works or doesn't work.
-Major sources of uncertainty.
-Ideas for improving the procedure.
-Emphasize that this can be done before monitoring time is invested.
+For a small fraction of lines of sight, $\pr(\kappax)$ remains very broad even after applying our reconstruction; these lines of sight are typically the most overdense lines of sight in the universe.
+For time-delay cosmography the most observationally expensive task is the lightcurve monitoring, whilst making photometric observations of a 4$\times$4 arcminute patch of sky survey down to 24th magnitude is a relatively cheap.
+We have shown that with a single epoch observation of the region around a strong lens it is possible to infer $\pr(\kappax)$.
+If a line of sight has a broad $\pr(\kappax)$ it can be rejected {\it before} the investment of longterm lightcurve monitoring.
+
+The method we have outlined can also be used to estimate the external shear along a line of sight.
+Shear is an observable that can be extracted from strong lens modelling, however there is a degeneracy between internal and external shear.
+Progress has been made in disentangelling external and internal shear \citep[\eg][]{xxx} but there are still significant uncertainties: \citet{Wong} attempted to match the shear from strong lens models with a reconstruction of the local lens group environment, but found a tension between the strong lens model and the reconstruction of the environment.
+Since \citet{Wong} only reconstructed the local lens group, rather than the full line of sight contribution, it is unclear whether the external shear from lens models can be reconciled with a line of sight reconstruction.
+{\it If} external shear can be measured, it provides an additional constraint on which of the Millenium Simulation lines of sight are similar to the reconstructed line of sight.
+\citet{suyu2012b} found that for RXJ1131 combining shear constriants with galaxy number count overdensity, gave a significantly different $\pr(\kappax|\gamma,N_{45})$ copmpared to the PDFfrom number count overdensity alone, $\pr(\kappax|N_{45})$.
 
@@
 
-To remind you, this is what we did.
+In this work we have taken mock lines of sight from the Millenium Simulation and estimated the external convergence along those lines of sight using a simple halo model prescription.
+We have used the ray traced convergence as a calibration, allowing us to relate the total convergence along a line of sight with the sum of convergences from each halo in our catalogue.
+Our model uses a truncated spherical NFW profile for each dark matter halo and neglects voids, but despite the model's simplicity the reconstructed $\sumkappah$ is a good tracer of $\kappax$.
+Using Millenium Simulation lightcones allowed us to test the reconstruction process given perfect knowledge of halo mass and redshift.
+We found that with perfect knowledge of the halo mass and redshift, the reconstruction gives an unbiased estimator of $\pr(\kappax)$ that is almost almost a factor of 2 less broad to the global $\pr(\kappax)$.
+For the most overdense lines of sight, the reconstruction produces a very broad PDF, but since the reconstruction can be performed before follow-up time is invested it is possible to discard the most uncertain lines of sight and prevent the waste of follow-up time.
 
-Our conclusions can be summarised as follows:
+Having found that the reconstruction process is effective given perfect knowledge of halo mass and redshift, we investigated the effects of reasonable uncertainties in the stellar mass and redshift of each halo, and propogated these uncertainties into a $\pr\left(\sumkappah\right)$ for each line of sight.
+With complete spectroscopic redshift coverage we find that the median of $\pr\left(\sumkappah\right)$ can be converted into an estimate of $\pr(\kappax)$; the PDFS are roughly 10\% broader than given perfect knowledge of halo mass and redshift; given only photometric redshifts (which in turn causes much less certain stellar masss estimates) causes another $\sim$10\% increase to the width of $\pr(\kappax)$.
 
-\begin{itemize}
+We found that it is very rare for halos further than 2 arcminutes to make a significant contribution to $\kappax$.
+We also found that including halos whose host galaxy is less luminous than $i=24$ does not significantly improve our reconstruction proceedure.
+As such a photometric survey of a 4$\times$4 arcminute patch around the lens gets close to the limiting uncertainties of our simple reconstruction recipe.
+Such a reconstruction produces $\pr(\kappax)$ that have a meanwidth of 0.0163 which is a 1.5 times less broad than the global $\pr(\kappax)$, but by following-up only the most certain cosmological value per lens can be increased further.
+We find that the lines of sight with the sharpest $\pr(\kappax)$ are typically under-dense.
 
-\item We found this.
+With a photometric reconstruction of all lens fields, and following up only the lenses with the most constraining $\pr(\kappax)$, the width of the dominant statistical uncertainty in time-delay cosmography can be halved, whilst at the same time decreaing any potentail for a systematic error due to lenses being biased in $\kappax$.
 
-\item And we found this too.
-
-\end{itemize}
+%Our conclusions can be summarised as follows:
+%\begin{itemize}
+%\item With perfect 
+%\item And we found this too.
+%\end{itemize}
 
@@
 
-\section{Smooth component models}
-\label{appendix:smooth}
+%\section{Smooth component models}
+%\label{appendix:smooth}
 

### 2012-10-01 doc/paper-lcr.tex
Conclusions in bullet points, commenting colors and styles fixed, with todo macro added

@@
 the uncertainties due to weak lensing by line of sight mass structure. 
-\flag{More needed here. Previous work on environments: Keeton, Zabludoff,Auger, Momcheva, Wong, others.}
+\todo{Tom, Matt}{More needed here. Previous work on environments: Keeton,
+Zabludoff,Auger, Momcheva, Wong, others.}
 Most recently, \citet{Wong++2011} ran Monte
@@
 been used to predict, from first principles the distribution of likely
-external shears and convergences along strong lens lines of sight. \flag{More
+external shears and convergences along strong lens lines of sight. \todo{Phil}{More
 needed here. Holder \& Schechter, Dalal \& Watson}. \citet{Hilbert++2009}
@@
 in the lens modelling, if cosmological parameters are to be estimated accurately and
-precisely from observed time delays \citep{suyu2010}.
+precisely from observed time delays \citep{Suyu2010}.
 
@@
 
-\flag{The all-important calibration of the reconstruction has to be done
+\tom{The all-important calibration of the reconstruction has to be done
 against Stefan's ray-traced kappas though -- so it is these that we have to
@@
 sight...
-\flag{Stefan's section on how the ray tracing was done and how halos are extracted from
+\todo{Stefan}{Write section on how the ray tracing was done and how halos are extracted from
  the MS n-body particles}
@@
 Similarly, if the universe is homogeneously populated with NFW halos, the projected surface mass along any
-line of sight will also be divergant\footnote{At large radius, $\Sigma_{\rm nfw} \propto R^{-2}$, but the differential number of halos centred within an annulus of width $\dee R$ is given by $\dee N_{\rm annulus} \propto R \dee R$, so  $\Sigma_{\rm total} \propto \int_{0}^{\infty} R^{-1} \dee R$, which diverges logarithmically}.
-Since infinite mass is unphysical, the profile must be truncated at some point.
-\flag{previous truncation results}.
+line of sight will also be divergant\footnote{At large radius, $\Sigma_{\rm
+nfw} \propto R^{-2}$, but the differential number of halos centred within an
+annulus of width $\dee R$ is given by $\dee N_{\rm annulus} \propto R \dee R$,
+so  $\Sigma_{\rm total} \propto \int_{0}^{\infty} R^{-1} \dee R$, which
+diverges logarithmically}. Since infinite mass is unphysical, the profile must
+be truncated at some point.
+\todo{Tom}{Add notes on previous truncation results}.
 Several truncation profiles have been suggested \citep[e.g][]{BMO}, but beyond several virial radii, the amount of matter associated with a halo is likely to be low; \citet{Nandra2012} showed that the Universe's expansion can place an upper limit on the radius of NFW halos -- for cluster scale halos, this happens at around 25 times the NFW scale radius.
@@
 likely be rejected by their reconstructed shear not matching the shear of the lens model 
-(see \citet{wong} for the practicalities of this);
+(see \citet{Wong} for the practicalities of this);
  this makes our estimate of the intrinsic error pessimistic. We do not include any additional constraints on P($\kappax$), given prior knowledge of the external shear in this work.
@@
 
-The method we have outlined can also be used to estimate the external shear along a line of sight.
-Shear is an observable that can be extracted from strong lens modelling, however there is a degeneracy between internal and external shear.
-Progress has been made in disentangelling external and internal shear \citep[\eg][]{xxx} but there are still significant uncertainties: \citet{Wong} attempted to match the shear from strong lens models with a reconstruction of the local lens group environment, but found a tension between the strong lens model and the reconstruction of the environment.
-Since \citet{Wong} only reconstructed the local lens group, rather than the full line of sight contribution, it is unclear whether the external shear from lens models can be reconciled with a line of sight reconstruction.
-{\it If} external shear can be measured, it provides an additional constraint on which of the Millenium Simulation lines of sight are similar to the reconstructed line of sight.
-\citet{suyu2012b} found that for RXJ1131 combining shear constriants with galaxy number count overdensity, gave a significantly different $\pr(\kappax|\gamma,N_{45})$ copmpared to the PDFfrom number count overdensity alone, $\pr(\kappax|N_{45})$.
+The method we have outlined can also be used to estimate the external shear
+along a line of sight. Shear is an observable that can be extracted from
+strong lens modelling, however there is a degeneracy between internal and
+external shear. Progress has been made in disentangelling external and
+internal shear \citep[\eg][]{xxx} but there are still significant
+uncertainties: \citet{Wong} attempted to match the shear from strong lens
+models with a reconstruction of the local lens group environment, but found a
+tension between the strong lens model and the reconstruction of the
+environment. Since \citet{Wong} only reconstructed the local lens group,
+rather than the full line of sight contribution, it is unclear whether the
+external shear from lens models can be reconciled with a line of sight
+reconstruction. {\it If} external shear can be measured, it provides an
+additional constraint on which of the Millenium Simulation lines of sight are
+similar to the reconstructed line of sight.
+\citet{Suyu2012b} found that for RXJ1131 combining shear constriants with galaxy number count overdensity, gave a significantly different $\pr(\kappax|\gamma,N_{45})$ copmpared to the PDFfrom number count overdensity alone, $\pr(\kappax|N_{45})$.
 
@@
 
-In this work we have taken mock lines of sight from the Millenium Simulation and estimated the external convergence along those lines of sight using a simple halo model prescription.
-We have used the ray traced convergence as a calibration, allowing us to relate the total convergence along a line of sight with the sum of convergences from each halo in our catalogue.
-Our model uses a truncated spherical NFW profile for each dark matter halo and neglects voids, but despite the model's simplicity the reconstructed $\sumkappah$ is a good tracer of $\kappax$.
-Using Millenium Simulation lightcones allowed us to test the reconstruction process given perfect knowledge of halo mass and redshift.
-We found that with perfect knowledge of the halo mass and redshift, the reconstruction gives an unbiased estimator of $\pr(\kappax)$ that is almost almost a factor of 2 less broad to the global $\pr(\kappax)$.
-For the most overdense lines of sight, the reconstruction produces a very broad PDF, but since the reconstruction can be performed before follow-up time is invested it is possible to discard the most uncertain lines of sight and prevent the waste of follow-up time.
+In this work we have investigated a simple halo model prescription for
+reconstructing all the mass along a line of sight to an intermediate redshift
+source. We have used the ray-traced lensing convergence along lines of sight
+through the Millenium Simulation to test this approach, and to calibrate
+estimates of the total convergence along a line of sight to an observed
+distant galaxy made by summing the convergences due to each object in a
+photometric catalogue. Having found that the reconstruction process is effective given perfect
+knowledge of halo mass and redshift, we investigated the effects of reasonable
+uncertainties in the stellar mass and redshift of each halo, and propogated
+these uncertainties into a $\pr\left(\sumkappah\right)$ for each line of
+sight. We draw the following conclusions:
 
-Having found that the reconstruction process is effective given perfect knowledge of halo mass and redshift, we investigated the effects of reasonable uncertainties in the stellar mass and redshift of each halo, and propogated these uncertainties into a $\pr\left(\sumkappah\right)$ for each line of sight.
-With complete spectroscopic redshift coverage we find that the median of $\pr\left(\sumkappah\right)$ can be converted into an estimate of $\pr(\kappax)$; the PDFS are roughly 10\% broader than given perfect knowledge of halo mass and redshift; given only photometric redshifts (which in turn causes much less certain stellar masss estimates) causes another $\sim$10\% increase to the width of $\pr(\kappax)$.
+\begin{itemize}
 
-We found that it is very rare for halos further than 2 arcminutes to make a significant contribution to $\kappax$.
-We also found that including halos whose host galaxy is less luminous than $i=24$ does not significantly improve our reconstruction proceedure.
-As such a photometric survey of a 4$\times$4 arcminute patch around the lens gets close to the limiting uncertainties of our simple reconstruction recipe.
-Such a reconstruction produces $\pr(\kappax)$ that have a meanwidth of 0.0163 which is a 1.5 times less broad than the global $\pr(\kappax)$, but by following-up only the most certain cosmological value per lens can be increased further.
-We find that the lines of sight with the sharpest $\pr(\kappax)$ are typically under-dense.
+\item Our model uses a truncated spherical NFW profile for
+each dark matter halo and neglects voids, but despite the model's simplicity
+the reconstructed $\sumkappah$ is a good tracer of $\kappax$.  We found that
+with perfect knowledge of the halo mass and redshift (from the Millenium
+Simulation catalogs), the reconstruction gives an unbiased estimate of
+$\pr(\kappax)$ for a single line of sight that is almost almost a factor of 2
+less broad than the global $\pr(\kappax)$.
 
-With a photometric reconstruction of all lens fields, and following up only the lenses with the most constraining $\pr(\kappax)$, the width of the dominant statistical uncertainty in time-delay cosmography can be halved, whilst at the same time decreaing any potentail for a systematic error due to lenses being biased in $\kappax$.
+\item  For the most overdense lines of sight, the reconstruction produces a
+very broad PDF, but since the reconstruction can be performed before follow-up
+time is invested it will be possible to discard the most uncertain lines of
+sight and prevent the waste of follow-up time.
+
+\item With complete spectroscopic redshift coverage and just an empirical
+stellar mass to halo mass relation, we find that the median of
+$\pr\left(\sumkappah\right)$ is a useful indicator for generating an estimate
+of $\pr(\kappax)$ from the ensemble of simulated lines of sight. The resulting
+PDF tends to be around 10\% broader than it would have been given perfect
+knowledge of both halo mass and redshift; given only photometric redshifts
+(which in turn give rise to much less certain stellar masss estimates) causes
+another $\sim$10\% increase to the width of $\pr(\kappax)$.
+
+\item It is very rare for halos further than 2 arcminutes to make a
+significant contribution to $\kappax$. We also found that including halos
+whose host galaxy is less luminous than $i=24$ does not significantly improve
+our reconstruction proceedure. A photometric survey to this depth of a
+4$\times$4 arcminute patch around the lens would approach the limiting
+uncertainties of our simple reconstruction recipe, and yield a 
+$\pr(\kappax)$ that has, on average, a width of 0.0163 --
+50\% less broad than the global $\pr(\kappax)$.
+
+\item We find that the lines of sight with the sharpest $\pr(\kappax)$ are
+typically under-dense. With a photometric reconstruction of all lens fields,
+and following up only the lenses with the most constraining $\pr(\kappax)$,
+the width of the dominant statistical uncertainty in time-delay cosmography
+can be halved, whilst at the same time decreasing any potentail for a
+systematic error due to lenses being biased in $\kappax$.
+
+\end{itemize}
+
+\todo{Tom}{Add more conclusions about bias in a large sample of lenses...}
+
+\todo{Tom}{Wrap up}
 
@@
 
-\flag{SHEAR HERE}
+\todo{Tom}{More on shear here.}
 

### 2012-10-01 doc/paper-lcr.tex
draft update

@@
 \ee 
-Since the time delays are proportional to $1/ (1+ \kappax)$, if there is any external convergence, that is not included in the lens
+Since the time delays are proportional to $1/ (1- \kappax)$, if there is any external convergence, that is not included in the lens
 modeling, then the time delay distance -- inferred assuming $\kappax = 0$ -- will be
@@
 those mass-sheets using simple prescriptions applied to potential astronomical observables.
-We also aim to quantify how uncertainties in the
+\comments{We also aim to quantify how uncertainties in the
 estimations of $\kappax$ propogate into uncertainties on the cosmological parametres
-which can be inferred from measurements of $\Dt$.
+which can be inferred from measurements of $\Dt$.}
 
@@
 information for each galaxy in the field of the lens, down to some magnitude
-limit. Since we do not observe halo mass directy, we need some way estimating
+limit. Since we do not observe halo mass directy, we need some way of estimating
 the mass of each galaxy in the catalog, so that we can compute its
@@
 \ee
-which is the same as the NFW profile in the limit that $r_t$ goes to infinity. The convergence and shear for the BMO profile are given in Appendix \ref{appendix:halos}.
+which is the same as the NFW profile in the limit that the truncation radius, $r_t$ goes to infinity. The convergence and shear for the BMO profile are given in Appendix \ref{appendix:halos}.
 

### 2012-10-02 doc/paper-lcr.tex
draft update

@@
 knowledge of the halos' virial masses and redshifts; this provides us with a measure of the intrinsic
-errors induced by treating matter as truncated NFW halos. In this Section we do not apply the void correction of
+errors induced by treating matter as truncated NFW halos. For our first tests we do not apply the void correction of
 Section \label{subsec:voids}, instead we shift $\sumkappah$ for all our sightlines by a fixed negative offset such that the ensemble mean
@@
 \ee
-where $\kappav$ is a positive constant. This us allows us to test the halo reconstruction directly, without the uncertainty of the void correction
-obscuring any inadequacies of our halo based prescription.
+where $\kappav$ is a positive constant. This us allows us to test the correlation of $\sumkappah$ with $\kapparay$, without
+ the uncertainty of the void correction obscuring any inadequacies of our halo based prescription.
 
@@
 convergences from every halo within 5 arcminutes and compare the reconstructed
-$\kapparec$ with those from the ray tracing results. The standard deviation on $\kapparay$-$\kapparec$ 
+$\kapparec$ with those from the ray tracing results. The standard deviation on $\kapparay$-$\kapparec$ is
 shown in Figure \ref{fig:ScattervsTruncation} as a function of the radius at which the halo is truncated.
@@
 
-For $\kapparec$ to provide useful constraints on $\kapparay$, it is important that $\kapparay$ and $\kapparec$ are as similar as possible.
-Figure \ref{fig:bias} shows that indeed $\kapparec$ is a good estimator, regardless of the individual value of $\kapparec$, but that the scatter increases with $\kapparec$.
-The curve in $\kapparec-\kapparay$ at high $\kapparec$ shows that the reconstruction does not perfectly reproduce the physics of the most overdense lines of sight.
-Since most lines of sight have $\kappax<0.05$, $\kapparec$ is an acceptable estimator of $\kapparay$, although there is some scope for improvement at the highest $\kappax$.
+For $\sumkappah$ to provide useful constraints on $\kapparay$, it is important that $\kapparay$ and $\sumkappah$ are as similar as possible.
+Figure \ref{fig:bias} shows that indeed $\sumkappah$ is a good estimator, regardless of the individual value of $\sumkappah$, although the scatter increases with $\sumkappah$.
 
 \begin{figure}
-\includegraphics[width=\columnwidth]{isitbiased.eps}
-\caption[Biased?]{$\kapparec$ minus $\kapparay$ as a function of $\kapparec$, for 10000 reconstructed lines of sight.
+\includegraphics[width=\columnwidth]{perfectc.eps}
+\caption[Biased?]{$\$ minus $\kapparay$ as a function of $\kapparec$, for 10000 reconstructed lines of sight.
 The points are put into bins of width 0.01 in $\kapparec$, except the last bin containing all reconstructions with $\kapparec>0.14$.

### 2012-10-02 doc/paper-lcr.tex
draft update

@@
 For $\sumkappah$ to provide useful constraints on $\kapparay$, it is important that $\kapparay$ and $\sumkappah$ are as similar as possible.
-Figure \ref{fig:bias} shows that indeed $\sumkappah$ is a good estimator, regardless of the individual value of $\sumkappah$, although the scatter increases with $\sumkappah$.
+Figure \ref{fig:bias} shows that indeed $\sumkappah$ is a good estimator, regardless of the individual value of $\sumkappah$.
+At fixed $\sumkappah$ we find that the scatter in $\kapparay$ grows with $\sumkappah$; our reconstruction is better at reproducing underdense lines of sight than overdense lines of sight.
 
@@
 \includegraphics[width=\columnwidth]{perfectc.eps}
-\caption[Biased?]{$\$ minus $\kapparay$ as a function of $\kapparec$, for 10000 reconstructed lines of sight.
+\caption[Biased?]{$\sumkappah$ verses $\kapparay$ for 100000 reconstructed lines of sight.
 The points are put into bins of width 0.01 in $\kapparec$, except the last bin containing all reconstructions with $\kapparec>0.14$.

### 2012-10-02 doc/paper-lcr.tex
draft update

@@
 systematic error for any estimate of luminosity or distance, an issue addressed
-for \eg type Ia supernovae by \citet[][]{Holz+Wald,Linder+Holz} and for high
-redshift galaxies by \citet{Loeb} among others. In time delay lens cosmography
-the effect can be particularly important. \citet{Suyu2010} found that  the
+for \eg type Ia supernovae by \citet[][]{Holz+Wald1998,Linder+Holz2004} and for high
+redshift galaxies by \tom{which paper?} \citet{Loeb} among others. In time delay lens cosmography
+the effect can be particularly important. \citet{Suyu++2010} found that  the
 lensing effect of mass structures along the (unusually over-dense)  line of
@@
 How can we correct for the line of sight lensing error, and make accurate
-measurements through the Universe? As \citeauthor{LH} noted, when inferring
+measurements through the Universe? As \citeauthor{Linder+Holz2004} noted, when inferring
 global quantities (such as the cosmological parameters), averaging the results
@@
 in the next decade in ground-based optical imaging surveys
-\citep{Oguri+Marshll2010} -- but these samples will be image separation-limited,
+\citep{Oguri+Marshall2010} -- but these samples will be image separation-limited,
 due to the surveys' relatively poor ($\sim 1$~arcsec) image quality. Some of the
@@
 needed here. Holder \& Schechter, Dalal \& Watson}. \citet{Hilbert++2009}
-performed ray-tracing experiments through the Millenium Simulation, generating
+performed ray-tracing experiments through the Millenium Simulation \citep{Springel++2005}, generating
 a predicted $\xkappa$ at every position in a simulated sky. The first step
@@
 compared to the overdensity of the B1608$+$656 line of sight
-\citep{Fass+Koop2010}, and hence an estimate of  $\Pr(\xkappa)$ could be
+\citep{Fassnact++2011}, and hence an estimate of  $\Pr(\xkappa)$ could be
 made.
@@
 and second, in \Sref{sec:obsMstar+z}, with realistic observational uncertainties
-on the field galaxies' stellar masses and redshifts. We then propagate all these
+on the field galaxies' stellar masses and redshifts. \comments{We then propagate all these
 uncertainties through to the time delay distance in a toy sample of 100 lenses,
-in \Sref{sec:distances}. We discuss our results in \Sref{sec:discuss} before
+in \Sref{sec:distances}.} We discuss our results in \Sref{sec:discuss} before
 concluding in \Sref{sec:conclude}.
@@
 Whilst it is rare for three galaxies to line up well enough for both of the background sources
-to be strongly lensed \citep{gavazzi2008,collett2012}, the shear scale of dark matter halos
+to be strongly lensed \citep{Gavazzi++2008,Collett++2012a}, the shear scale of dark matter halos
 makes a partial alignment -- with the additional structure acting as a weak lens -- 
-a near certainty, indeed \citet{valewhite2003} and \citet{hilbert2007} find that there
+a near certainty, indeed \citet{Vale+White2003} and \citet{Hilbert++2007} find that there
 are no empty lightcones in a realistic universe. These additional structures induce an external shear
 which can be recovered in the mass-modelling of the lens, but they can also introduce a convergence that
-is undetectable from the image positions, shapes and relative fluxes; {\it the mass sheet-degeneracy} \citep[see e.g.][for details]{Falco1985,Schneider2006}.
+is undetectable from the image positions, shapes and relative fluxes; {\it the mass sheet-degeneracy} \citep{Falco++1985}.
 
@@
 in the lens modelling, if cosmological parameters are to be estimated accurately and
-precisely from observed time delays \citep{Suyu2010}.
+precisely from observed time delays \citep{Suyu++2010}.
 
@@
 mass-sheet degeneracy by providing an additional estimate of the lens galaxy's mass
-\citep[e.g.,][]{citations}.
+\citep[e.g.,][]{xxx}.
 
@@
 Cosmological dark matter simulations have shown that dark matter
-halos are well approximated by NFW profiles \citep{NFW1997}, with a density
+halos are well approximated by NFW profiles \citep{NFW}, with a density
 profile given by
@@
 using a mass--concentration relation. Typically more massive halos are less concentrated,
-but there is some scatter; we use the relation of \citet{neto2007} to estimate $c$
-from the mass enclosed within $r_{200}$, which we denote as $M_{200}$. The best fit relation of \citet{neto2007} is given by
+but there is some scatter; we use the relation of \citet{Neto2007} to estimate $c$
+from the mass enclosed within $r_{200}$, which we denote as $M_{200}$. The best fit relation of \citet{Neto2007} is given by
 \be
@@
 \todo{Tom}{Add notes on previous truncation results}.
-Several truncation profiles have been suggested \citep[e.g][]{BMO}, but beyond several virial radii, the amount of matter associated with a halo is likely to be low; \citet{Nandra2012} showed that the Universe's expansion can place an upper limit on the radius of NFW halos -- for cluster scale halos, this happens at around 25 times the NFW scale radius.
+Several truncation profiles have been suggested \citep[e.g][]{BMO}, but beyond several virial radii, the amount of matter associated with a halo is likely to be low; \citet{Nandra++2012} showed that the Universe's expansion can place an upper limit on the radius of NFW halos -- for cluster scale halos, this happens at around 25 times the NFW scale radius.
 In \Sref{sec:knownMh+z} we investigate how different truncations affect the recovered total convergence for a line of sight, using the truncated NFW profile of \citet{BMO}
@@
 likely be rejected by their reconstructed shear not matching the shear of the lens model 
-(see \citet{Wong} for the practicalities of this);
+(see \citet{Wong++2011} for the practicalities of this);
  this makes our estimate of the intrinsic error pessimistic. We do not include any additional constraints on P($\kappax$), given prior knowledge of the external shear in this work.
@@
 \caption[Biased?]{$\sumkappah$ verses $\kapparay$ for 100000 reconstructed lines of sight.
-The points are put into bins of width 0.01 in $\kapparec$, except the last bin containing all reconstructions with $\kapparec>0.14$.
-The errorbars show the population standard deviation for each bin.
-Since all of the errorbars are consistant with zero, there is no evidence for $\kapparec$ being a biased estimator of $\kapparay$}
+$\sumkappah$ traces $\kapparay$, but with a non-zero offset which is due to the negative connvergence from voids.
+At fixed $\sumkappah$ the scatter in $\kapparay$ grows with $\sumkappah$.}
 \label{fig:isitbiased}
@@
 Before investigating the errors caused by imperfect knowledge of halo mass and redshift, we investigate the errors induced by a magnitude limited reconstruction and a field of view limited reconstruction.
-The halos in our catalogue are given magnitudes by the semi-analytic model of \citet{SAM} and by applying magnitude cuts to our catalogue, we can investigate the scatter caused by unobserved halos.
+The halos in our catalogue are given magnitudes by the semi-analytic model of \citet{deLucia+Blaizot2007} and by applying magnitude cuts to our catalogue, we can investigate the scatter caused by unobserved halos.
 The majority of the convergence comes from halos with an $i$ magnitude between 18 and 24.
@@
 Objects brighter than $i=18$ are either too rare or too close to the observer to make a significant contribution to the convergence.
-Objects fainter than $i=24$ are too small to be important unless they are extremely close to the line of sight where it is likely that neglecting stellar mass and using a spherical NFW prescription are too naive to adequately reconstruct $\kappax$ - it is likely that these ultra-faint halos (or substructures), the uncertain contribution of voids and halos deviating from our spherical truncated NFW profile are the three major sources of the scatter in $\kapparec-\kapparay$; a deeper survey will not be sufficient to decrease the size of this scatter.
+Objects fainter than $i=24$ are too small to be important, unless they are extremely close to the line of sight where it is likely that neglecting stellar mass and using a spherical NFW prescription are too naive to adequately reconstruct $\kappax$.
+It is likely that ultra-faint halos (or substructures), the uncertain contribution of voids and halos deviating from our spherical truncated NFW profile are the three major sources of the scatter in $\kapparec-\kapparay$; a deeper survey will not be sufficient to decrease the size of this scatter.
 Since a large number of callibration lines of sight must be reconstructed to sample $\pr(\kappav)$, it may prove unrealistic to reconstruct the calibration lines of sight out to 5 arcminutes.
@@
 \includegraphics[width=\columnwidth]{mag_scatter.eps}
-\caption[magcut]{The 16, 50 and 84\% confidence intervals on $\kapparec$ minus $\kapparay$ as a function of the limiting $i$ band depth of the halo reconstruction - there is no significant improvement from including small halos with magnitudes less than $i=24$}
+\caption[magcut]{The 16, 50 and 84\% confidence intervals on $\kapparec$ minus $\kapparay$ as a function of the limiting $i$ band depth of the halo reconstruction.
+$\kapparec$ is given by $\sumkappah-\kappav$, where $\kappav$ is a constant such that $\left\langle\kapparec\right\rangle=0$.
+The majority of the constraining power comes from reconstructing halos with magnitudes between $18<i<24$}
 \label{fig:magcut}
@@
 
-We generate a stellar mass for each halo according to the stellar mass--halo mass relation of \citet{behroozi2010}. From this stellar mass we simulate 
+We generate a stellar mass for each halo according to the stellar mass--halo mass relation of \citet{Behroozi++2010}. From this stellar mass we simulate 
 an observed stellar mass by drawing a sample from $\pr(\log(M_{* \mathrm {obs}})|\log(M_{* \mathrm {true}}))$ which is given by \comments{ the product of the galaxy stellar mass function (GSMF) of \citet{Fontana2006} and} a Gaussian of width $\sigma_{M_*}$ centred on $\log(M*_{\mathrm {true}})$.
@@
 internal shear \citep[\eg][]{xxx} but there are still significant
-uncertainties: \citet{Wong} attempted to match the shear from strong lens
+uncertainties: \citet{Wong++2011} attempted to match the shear from strong lens
 models with a reconstruction of the local lens group environment, but found a
 tension between the strong lens model and the reconstruction of the
-environment. Since \citet{Wong} only reconstructed the local lens group,
+environment. Since \citet{Wong++2011} only reconstructed the local lens group,
 rather than the full line of sight contribution, it is unclear whether the
@@
 similar to the reconstructed line of sight.
-\citet{Suyu2012b} found that for RXJ1131 combining shear constriants with galaxy number count overdensity, gave a significantly different $\pr(\kappax|\gamma,N_{45})$ copmpared to the PDFfrom number count overdensity alone, $\pr(\kappax|N_{45})$.
+\citet{Suyu++2012b} found that for RXJ1131 combining shear constriants with galaxy number count overdensity, gave a significantly different $\pr(\kappax|\gamma,N_{45})$ copmpared to the PDFfrom number count overdensity alone, $\pr(\kappax|N_{45})$.
 
@@
 
-\todo{Tom}{More on shear here.}
-
 \section{Deriving the $\Mstar=\Mhalo$ relation}
@@
 
-\bibliographystyle{apj}
-\bibliography{references}
+%\bibliographystyle{apj}
+%\bibliography{references}
+
+\input{references.tex}
 

### 2012-10-02 doc/references.tex
draft update

\begin{thebibliography}{99}

\bibitem[\protect\citeauthoryear{Auger et al.}{2009}]{Auger++2009} 
Auger M.~W., Treu T., Bolton A.~S., Gavazzi R., Koopmans L.~V.~E., Marshall 
P.~J., Bundy K., Moustakas L.~A., 2009, ApJ, 705, 1099

\bibitem[\protect\citeauthoryear{Auger et al.}{2010}]{Auger++2010} 
Auger M.~W., Treu T., Bolton A.~S., Gavazzi R., Koopmans L.~V.~E., Marshall 
P.~J., Moustakas L.~A., Burles S., 2010, ApJ, 724, 511

\bibitem[\protect\citeauthoryear{Baltz, Marshall, 
\& Oguri}{2009}]{BMO} Baltz E.~A., Marshall P., Oguri M., 2009, JCAP, 1, 15

\bibitem[\protect\citeauthoryear{Behroozi, Conroy, 
\& Wechsler}{2010}]{Behroozi++2009} Behroozi P.~S., Conroy C., Wechsler R.~H., 2010, ApJ, 717, 379

\bibitem[\protect\citeauthoryear{Ben{\'{\i}}tez}{2000}]{BPZ} Ben{\'{\i}}tez N., 2000, ApJ, 536, 571

\bibitem[\protect\citeauthoryear{Collett et 
al.}{2012}]{Collett++2012a} Collett T.~E., Auger M.~W., Belokurov V., 
Marshall P.~J., Hall A.~C., 2012, MNRAS, 424, 2864

\bibitem[\protect\citeauthoryear{De Lucia 
\& Blaizot}{2007}]{deLucia+Blaizot2007} De Lucia G., Blaizot J., 2007, MNRAS, 375, 2

\bibitem[\protect\citeauthoryear{Falco, Gorenstein, 
\& Shapiro}{1985}]{Falco++1985} Falco E.~E., Gorenstein M.~V., Shapiro I.~I., 1985, ApJ, 289, L1

\bibitem[\protect\citeauthoryear{Fassnacht, Koopmans, 
\& Wong}{2011}]{Fassnacht++2011} Fassnacht C.~D., Koopmans L.~V.~E., Wong K.~C., 2011, MNRAS, 410, 2167

\bibitem[\protect\citeauthoryear{Gavazzi et 
al.}{2008}]{Gavazzi++2008} Gavazzi R., Treu T., Koopmans L.~V.~E., 
Bolton A.~S., Moustakas L.~A., Burles S., Marshall P.~J., 2008, ApJ, 677, 
1046

\bibitem[\protect\citeauthoryear{Hilbert et 
al.}{2009}]{2009A&A...499...31H} Hilbert S., Hartlap J., White S.~D.~M., Schneider P., 2009, A\&A, 499, 31

\bibitem[\protect\citeauthoryear{Holz 
\& Wald}{1998}]{Holz+Wald1998} Holz D.~E., Wald R.~M., 1998, PhRvD, 58, 063501

\bibitem[\protect\citeauthoryear{Keeton 
\& Moustakas}{2009}]{Keeton+Moustakas2009} Keeton C.~R., Moustakas L.~A., 2009, ApJ, 699, 1720

\bibitem[\protect\citeauthoryear{Linder 
\& Holz}{2004}]{Linder+Holz2004} Linder E.~V., Holz D.~E., 2004, AAS, 36, \#131.02

\bibitem[\protect\citeauthoryear{Nandra, Lasenby, 
\& Hobson}{2012}]{Nandra++2012} Nandra R., Lasenby A.~N., Hobson M.~P., 2012, MNRAS, 422, 2945

\bibitem[\protect\citeauthoryear{Navarro, Frenk, 
\& White}{1997}]{NFW} Navarro J.~F., Frenk C.~S., White S.~D.~M., 1997, ApJ, 490, 493

\bibitem[\protect\citeauthoryear{Neto et al.}{2007}]{Neto2007} 
Neto A.~F., et al., 2007, MNRAS, 381, 1450

\bibitem[\protect\citeauthoryear{Oguri 
\& Marshall}{2010}]{Oguri+Marshall2010} Oguri M., Marshall P.~J., 2010, MNRAS, 405, 2579

\bibitem[\protect\citeauthoryear{Oke}{1974}]{Oke1974} Oke 
J.~B., 1974, ApJS, 27, 21

\bibitem[\protect\citeauthoryear{Springel et 
al.}{2005}]{Springel++2005} Springel V., et al., 2005, Natur, 435, 629

\bibitem[\protect\citeauthoryear{Suyu}{2012}]{Suyu2012b} Suyu 
S.~H., 2012, arXiv, arXiv:1202.0287

\bibitem[\protect\citeauthoryear{Suyu et al.}{2012}]{Suyu++2012a} 
Suyu S.~H., et al., 2012, arXiv, arXiv:1208.6010

\bibitem[\protect\citeauthoryear{Suyu et al.}{2010}]{Suyu++2010} 
Suyu S.~H., Marshall P.~J., Auger M.~W., Hilbert S., Blandford R.~D., 
Koopmans L.~V.~E., Fassnacht C.~D., Treu T., 2010, ApJ, 711, 201

\bibitem[\protect\citeauthoryear{Vale 
\& White}{2003}]{Vale+White2003} Vale C., White M., 2003, ApJ, 592, 699

\bibitem[\protect\citeauthoryear{Wong et al.}{2011}]{Wong++2011} 
Wong K.~C., Keeton C.~R., Williams K.~A., Momcheva I.~G., Zabludoff A.~I., 
2011, ApJ, 726, 84

\bibitem[\protect\citeauthoryear{\tom{which paper}}{{9999}}]{xxx} 
None

\end{thebibliography}

### 2012-10-08 doc/paper-lcr.tex
draft update

@@
 
-For real lines of sight, 
-\phil{we would like to estimate the external convergence as best we can given all
+For real lines of sight, we would like to estimate the external convergence as best we can given all
 data available. Typically this data is in the form of a photometric galaxy
-catalog, containing positions, brightnesses, colours, and other type
-information for each galaxy in the field of the lens, down to some magnitude
-limit. Since we do not observe halo mass directy, we need some way of estimating
-the mass of each galaxy in the catalog, so that we can compute its
-contribution to $\kappax$. This mass assignment recipe will be uncertain, but
-can be calibrated to cosmological simulations.}
+catalog, containing positions, brightnesses, colours, and possibly spectra for each galaxy in the
+field of the lens, down to some magnitude
+limit. Since we can not observe the surface mass density of each halo
+directy, we need some way of estimating
+the mass of each halo in the catalog, so that we can compute its
+contribution to the total $\kappax$ along the line of sight. This mass assignment recipe will be uncertain, but
+can be calibrated with cosmological simulations.
 
@@
 Cosmological dark matter simulations can be used to generate mock lines of
-sight...
+sight and can be raytraced through to give each mock sightline a $\kappax$ value...
 \todo{Stefan}{Write section on how the ray tracing was done and how halos are extracted from
@@
 
-\phil{Transforming the photometometric galaxy catalogue into a}  catalogue of
+Transforming the photometometric galaxy catalogue into a  catalogue of
 halo masses, positions, and redshifts, will enable us to attempt a

### 2012-10-08 doc/paper-lcr.tex
refs added to intro, figs tidied away

--- 2012-10-02 doc/paper-lcr.tex
@@
 
-This fact makes gravitational lensing a potentially important source of
-systematic error for any estimate of luminosity or distance, an issue addressed
-for \eg type Ia supernovae by \citet[][]{Holz+Wald1998,Linder+Holz2004} and for high
-redshift galaxies by \tom{which paper?} \citet{Loeb} among others. In time delay lens cosmography
-the effect can be particularly important. \citet{Suyu++2010} found that  the
-lensing effect of mass structures along the (unusually over-dense)  line of
-sight to the quadruply-imaged radio source B1608$+$656, the so-called ``external
-convergence,'' was the dominant source of uncertainty in the inferred
-cosmological parameters.
-
-How can we correct for the line of sight lensing error, and make accurate
-measurements through the Universe? As \citeauthor{Linder+Holz2004} noted, when inferring
-global quantities (such as the cosmological parameters), averaging the results
-from a large number of independent objects will tend to reduce the error, as the
+This fact makes weak gravitational lensing a potentially important source of
+systematic error for any estimate of luminosity or distance, an issue
+raised for \eg 
+type Ia supernovae by \citet[][]{Holz+Wald1998,Linder+Holz2004}, for
+gamma ray bursts by \citet[][]{Oguri+Takahashi2006,Wang+Dai2011}, 
+and for high redshift galaxies by \citet{BradacEtal2009}, among others. 
+Along lines of sight containing strong gravitational lenses,
+the effect has been found to be
+particularly important, with foreground and background structures
+having a significant effect on the inferred lensing cross-section
+\citep[\eg][]{WongEtal2012} and distance ratios \citep[][]{DalalEtal2005}.
+In time delay lens cosmography,
+\citet{SuyuEtal2010} found that  the lensing effect of mass structures along the
+(unusually over-dense)  line of sight to the quadruply-imaged radio source
+B1608$+$656, the so-called ``external convergence,'' was the dominant source
+of uncertainty in their 6\% measurement of Hubble's constant.
+
+How can we correct for this weak lensing error, and make
+accurate measurements through the Universe? When inferring global quantities
+(such as the cosmological parameters), averaging the results from a large
+number of independent objects will tend to reduce the error, as the
 ensemble-averaged convergence approaches zero for an unbiased sample
-\citep{xxx}. If the sample is biased, however, some residual systematic error
-will remain while the statistical uncertainty decreases -- and this will be the
-case for any sample selected by the brightness of the lensed object, or any
-other quantity that depends on $\xkappa$. The latter class includes time delay
-lenses, which are detected based on the separation of their images, which
-increases with $\kappa$. Large samples of lenses are expected to be discovered
-in the next decade in ground-based optical imaging surveys
-\citep{Oguri+Marshall2010} -- but these samples will be image separation-limited,
-due to the surveys' relatively poor ($\sim 1$~arcsec) image quality. Some of the
-current sample of known time delay lenses were detected in surveys like this: we
-might expect them to be somewhat biased towards high values of $\xkappa$.
+\citep[\eg][]{Linder+Holz2004}. If the sample is biased, however, some
+residual systematic error will remain while the statistical uncertainty
+decreases -- and this will be the case for any sample selected by the
+brightness of the lensed object, or any other quantity that depends on
+$\xkappa$. The latter class includes time delay lenses, which could be
+either detected or selected 
+based on their image separations, magnifications or quadruple image
+configurations, all of which either increase or become more likely with
+increasing $\kappa$. Large
+samples of lenses are expected to be discovered in the next decade in
+ground-based optical imaging surveys \citep{Oguri+Marshall2010} -- but these
+samples will be image separation-limited, due to the surveys' relatively poor
+($\sim 1$~arcsec) image quality. Some of the current sample of known time
+delay lenses were detected in surveys like this: we might expect them to be
+somewhat biased towards high values of $\xkappa$.
 
@@
 understanding to derive a suitable correction to cosmological parameters
-inferred assuming no $\xkappa$ at all. To do this, one needs information about
-the unlensed population of objects, and the population of lenses, and how the
+inferred assuming no $\xkappa$ at all. As pointed out by  \citet[][among
+others]{Oguri+Takahashi2006}, to do this one would need  information about the
+unlensed population of objects, and the population of lenses, and how the
 objects were detected -- or to infer these hierarchically during the analysis.
-Alternatively, one could simply accept all lenses provided, regardless of their
-selection, and try to use any additional information that is available to
-estimate the external convergence in each system on a case by case basis, and
-hence optimize their joint analysis to produce a better-constrained result. In
-this work we follow the second approach, and use measurements of the positions,
-magnitude and colours of galaxies close to time delay lens lines of sight to try
-to infer the external convergence at the lens position.
-
-Previous attempts at reconstructing the line of sight mass distribution in
-strong lens fields have focused on spectroscopic surveys to ascertain group
-membership, and on understanding the external shear apparently required by the
-strong lens models.  The probability density function (PDF) $\Pr(\xkappa)$ is
-the target for any reconstruction analysis, and the key quantity for any
-ensemble analysis, since by marginalising over it we can correctly propagate
-the uncertainties due to weak lensing by line of sight mass structure. 
-\todo{Tom, Matt}{More needed here. Previous work on environments: Keeton,
-Zabludoff,Auger, Momcheva, Wong, others.}
-Most recently, \citet{Wong++2011} ran Monte
-Carlo reconstructions of the mass in nine lens fields, and compared the
-resulting predicted shear distributions with the lens model external shear.
-Their simulations show most of  the shear being generated by bright galaxies
-within 2~arcminutes of the lens, and that both line of sight structures and
-the group of galaxies in each lens plane contribute significant proportions of
-the shear. The significant discrepancies between the lens model shear and the
-Monte Carlo predictions are attributed to both the environment modelling and
-the strong lens modelling itself.
+Alternatively, one could simply accept all lenses provided, regardless of
+their selection, and try to use any additional information that is available
+to estimate the external convergence in each system on a case by case basis,
+and hence optimize their joint analysis to produce a better-constrained result
+\citep[as suggested by][]{Keeton+Zabludoff2004}. In this work we follow this
+second approach, and use measurements of the positions, magnitude and colours
+of galaxies close to lens lines of sight to try to infer the
+external convergence at the lens position.
+
+Attempts to date at reconstructing the local and  line of sight mass
+distribution in strong lens fields (what \citeauthor{WongEtal2011} call ``the
+full environment'') have focused on photometric and  spectroscopic surveys to
+detect galaxy groups and ascertain galaxies' membership,  and on understanding
+the external shear apparently required by the strong lens models. Surveys by
+\citet{Fassnacht+Lubin2002,AugerEtal2007,WilliamsEtal2006,MomchevaEtal2006}
+all found groups of galaxies both hosting and lying  along the line of sight
+to known gravitational lenses. Initial estimates of the effect of these
+structures suggested the importance of assigning mass to both galaxy and group
+halos, and to allowing for significant uncertainty in the centroids of group
+halos. The probability density function (PDF) for the external convergence for
+that lens, $\Pr(\xkappa)$, is the target for any reconstruction analysis, and
+is the key quantity for any ensemble analysis, since by marginalising over it
+we can correctly propagate the uncertainties due to weak lensing. Coming
+closest to estimating this quantity from survey data, \citet{WongEtal2011} ran
+Monte Carlo reconstructions of the mass in nine lens fields based on
+\citeauthor{WilliamsEtal2006} and \citeauthor{MomchevaEtal2006}'s
+photometric and spectroscopic measurements of galaxies close to the line of
+sight, and compared the resulting predicted shear distributions with the
+external shear demanded by the strong lens model. Their simulations show most
+of the shear being generated by bright galaxies within 2~arcminutes of the
+lens, and that both line of sight structures and the group of galaxies in each
+lens plane contribute significant proportions of the shear. They find
+significant discrepancies between the lens model shear and the Monte Carlo
+predictions, and are unable to distinguish between the environment modelling
+and the strong lens modelling as the cause of these discrepancies.
 
 These observational investigations have provided very useful insight into the
-problem.  Coming from the opposite direction, large numerical simulations have
-been used to predict, from first principles the distribution of likely
-external shears and convergences along strong lens lines of sight. \todo{Phil}{More
-needed here. Holder \& Schechter, Dalal \& Watson}. \citet{Hilbert++2009}
-performed ray-tracing experiments through the Millenium Simulation \citep{Springel++2005}, generating
-a predicted $\xkappa$ at every position in a simulated sky. The first step
-towards using this excellent calibration resource was taken by
-\citet{Suyu++2010}, who selected Millenium lines of sight that a) were found
-to contain a strong lens and b) had comparable apparent galaxy overdensity in
-a 45 arcsec radius aperture down to $i < 24$. This overdensity could be
-compared to the overdensity of the B1608$+$656 line of sight
-\citep{Fassnact++2011}, and hence an estimate of  $\Pr(\xkappa)$ could be
+problem.  Coming from a more theoretical direction, large numerical
+simulations have been used to predict, from first principles, the distribution
+of likely external shears and convergences along strong lens lines of sight. 
+\citet{Holder+Schechter2003} and \citet{Dalal+Watson2004} carried out
+ray-tracing calculations in N-body simulations to estimate the  distribution
+of external shear values.  \citet{HilbertEtal2009} performed similar ray-tracing
+experiments through the Millenium Simulation \citep{SpringelEtal2005},
+generating a predicted $\xkappa$ at every position in a simulated sky. The
+first step towards using this excellent calibration resource was taken by
+\citet{SuyuEtal2010}, who selected Millenium Simulation lines of sight that a)
+were found to contain a strong lens and b) had comparable apparent galaxy
+overdensity in a 45 arcsec radius aperture down to $i < 24$. This overdensity
+could be compared to the overdensity of the B1608$+$656 line of sight
+\citep{FassnachtEtal2011}, and hence an estimate of  $\Pr(\xkappa)$ could be
 made.
 
-What has not been investigated before, but is the subject of this paper, is
-the use of simulations to {\it calibrate} lightcone reconstruction methods.
-Ray-tracing through the simulations gives a ``truth'' that we can attempt to
-recover.  In this paper we use the Millenium Simulation mock galaxy catalogs
-and ray-traced lensing effects to test the accuracy of line of sight mass
-reconstructions. Probabilistically ssigning mass and redshift to every
-observed galaxy in the field around a time delay lens, we generate Monte Carlo
-sample line of sight mass distributions, and estimate the external convergence
-due to each one. This gives us a $\Pr(\xkappa)$ that can be propagated into
-further joint inferences. We focus on time delay lens cosmography, and
-quantify our results in terms of the uncertainty on the mean time delay
-distance to a test sample of $N$ lenses (where for clarity each lens has the
-same deflector and source redshift, and the same lens model and time delay
-uncertainty).
+In this paper, we bring these observational and theoretical approaches
+together and  use numerical simulations to {\it test and calibrate} a
+reconstruction of the  external convergence. Ray-tracing through the
+simulations gives a ``truth'' that we can attempt to recover.  In this paper
+we use the Millenium Simulation mock galaxy catalogs and ray-traced lensing
+effects to test the accuracy of line of sight mass reconstructions.
+Probabilistically ssigning mass and redshift to every observed galaxy in the
+field around a time delay lens, we generate Monte Carlo sample line of sight
+mass distributions, and estimate the external convergence due to each one.
+This gives us a $\Pr(\xkappa)$ that can be propagated into further joint
+inferences. We focus on time delay lens cosmography, and quantify our results
+in terms of the uncertainty on the mean time delay distance to a test sample
+of $N$ lenses (where for clarity each lens has the same deflector and source
+redshift, and the same lens model and time delay uncertainty).
 
@@
 
-Throughout this paper magnitudes are given in the AB system \citep{Oke74} and
+Throughout this paper magnitudes are given in the AB system and
 we adopt the Millenium Simulation's ``concordance'' parameters for our reference cosmology, \ie
@@
 dark energy density of the Universe in units of the critical density
-.%\citep[e.g.\ ][]{Kom++09}.
+.%\citep[e.g.\ ][]{KomEtal09}.
 
@@
 Whilst it is rare for three galaxies to line up well enough for both of the background sources
-to be strongly lensed \citep{Gavazzi++2008,Collett++2012a}, the shear scale of dark matter halos
+to be strongly lensed \citep{GavazziEtal2008,CollettEtal2012a}, the shear scale of dark matter halos
 makes a partial alignment -- with the additional structure acting as a weak lens -- 
-a near certainty, indeed \citet{Vale+White2003} and \citet{Hilbert++2007} find that there
+a near certainty, indeed \citet{Vale+White2003} and \citet{HilbertEtal2007} find that there
 are no empty lightcones in a realistic universe. These additional structures induce an external shear
 which can be recovered in the mass-modelling of the lens, but they can also introduce a convergence that
-is undetectable from the image positions, shapes and relative fluxes; {\it the mass sheet-degeneracy} \citep{Falco++1985}.
+is undetectable from the image positions, shapes and relative fluxes; {\it the
+mass sheet-degeneracy} \citep{FalcoEtal1985}.
 
@@
 in the lens modelling, if cosmological parameters are to be estimated accurately and
-precisely from observed time delays \citep{Suyu++2010}.
+precisely from observed time delays \citep{SuyuEtal2010}.
 
@@
 \todo{Tom}{Add notes on previous truncation results}.
-Several truncation profiles have been suggested \citep[e.g][]{BMO}, but beyond several virial radii, the amount of matter associated with a halo is likely to be low; \citet{Nandra++2012} showed that the Universe's expansion can place an upper limit on the radius of NFW halos -- for cluster scale halos, this happens at around 25 times the NFW scale radius.
+Several truncation profiles have been suggested \citep[e.g][]{BMO}, but beyond several virial radii, the amount of matter associated with a halo is likely to be low; \citet{NandraEtal2012} showed that the Universe's expansion can place an upper limit on the radius of NFW halos -- for cluster scale halos, this happens at around 25 times the NFW scale radius.
 In \Sref{sec:knownMh+z} we investigate how different truncations affect the recovered total convergence for a line of sight, using the truncated NFW profile of \citet{BMO}
@@
 likely be rejected by their reconstructed shear not matching the shear of the lens model 
-(see \citet{Wong++2011} for the practicalities of this);
+(see \citet{WongEtal2011} for the practicalities of this);
  this makes our estimate of the intrinsic error pessimistic. We do not include any additional constraints on P($\kappax$), given prior knowledge of the external shear in this work.
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{truncation_scatter.eps}
+\includegraphics[width=\columnwidth]{figs/truncation_scatter.eps}
 \caption[magcut]{The standard deviation in $\kapparec$ minus $\kapparay$ as a function of halo truncation radius in virial radii, using the truncated NFW profile of \citet{BMO}.
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{perfectc.eps}
+% \includegraphics[width=\columnwidth]{figs/perfectc.eps}
 \caption[Biased?]{$\sumkappah$ verses $\kapparay$ for 100000 reconstructed lines of sight.
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{mag_scatter.eps}
+\includegraphics[width=\columnwidth]{figs/mag_scatter.eps}
 \caption[magcut]{The 16, 50 and 84\% confidence intervals on $\kapparec$ minus $\kapparay$ as a function of the limiting $i$ band depth of the halo reconstruction.
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{radius_scatter.eps}
+\includegraphics[width=\columnwidth]{figs/radius_scatter.eps}
 \caption[radius cut]{The 16, 50 and 84\% confidence intervals on $\kapparec$ minus $\kapparay$ as a function of the limiting radius (in arcminutes) beyond which halos are not reconstructed.
@@
 
-We generate a stellar mass for each halo according to the stellar mass--halo mass relation of \citet{Behroozi++2010}. From this stellar mass we simulate 
+We generate a stellar mass for each halo according to the stellar mass--halo mass relation of \citet{BehrooziEtal2010}. From this stellar mass we simulate 
 an observed stellar mass by drawing a sample from $\pr(\log(M_{* \mathrm {obs}})|\log(M_{* \mathrm {true}}))$ which is given by \comments{ the product of the galaxy stellar mass function (GSMF) of \citet{Fontana2006} and} a Gaussian of width $\sigma_{M_*}$ centred on $\log(M*_{\mathrm {true}})$.
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{cornerplot.eps}
+\includegraphics[width=\columnwidth]{figs/cornerplot.eps}
 \caption{68 \% and 95 \% contours of the joint distribution $\pr(\kapparay, \tilde\kappa_{\rm halos})$ given a mock reconstruction of our 40000 calibration lines of sight.
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{widths.eps}
+\includegraphics[width=\columnwidth]{figs/widths.eps}
 \caption{Widths of $\pr(\kappax)$ after applying our reconstruction of all halos down $to i=26$ and within 5 arcminutes of the line of sight.
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{widths2.eps}
+\includegraphics[width=\columnwidth]{figs/widths2.eps}
 \caption{Widths of $\pr(\kappax)$ after a photometric reconstruction of all halos within different fields.
@@
 internal shear \citep[\eg][]{xxx} but there are still significant
-uncertainties: \citet{Wong++2011} attempted to match the shear from strong lens
-models with a reconstruction of the local lens group environment, but found a
-tension between the strong lens model and the reconstruction of the
-environment. Since \citet{Wong++2011} only reconstructed the local lens group,
-rather than the full line of sight contribution, it is unclear whether the
-external shear from lens models can be reconciled with a line of sight
+uncertainties: \citet{WongEtal2011} attempted to match the shear from strong
+lens models with a reconstruction of the local lens group environment, but
+found a tension between the strong lens model and the reconstruction of the
+environment. Since \citet{WongEtal2011} only reconstructed the local lens
+group, rather than the full line of sight contribution, it is unclear whether
+the external shear from lens models can be reconciled with a line of sight
 reconstruction. {\it If} external shear can be measured, it provides an
 additional constraint on which of the Millenium Simulation lines of sight are
-similar to the reconstructed line of sight.
-\citet{Suyu++2012b} found that for RXJ1131 combining shear constriants with galaxy number count overdensity, gave a significantly different $\pr(\kappax|\gamma,N_{45})$ copmpared to the PDFfrom number count overdensity alone, $\pr(\kappax|N_{45})$.
+similar to the reconstructed line of sight. \citet{SuyuEtal2012} found that
+for RXJ1131 combining shear constriants with galaxy number count overdensity,
+gave a significantly different $\pr(\kappax|\gamma,N_{45})$ copmpared to the
+PDFfrom number count overdensity alone, $\pr(\kappax|N_{45})$.
 
@@
 
-%\bibliographystyle{apj}
-%\bibliography{references}
+% \bibliographystyle{apj}
+% \bibliography{references}
 

### 2012-10-08 doc/references.tex
refs added to intro, figs tidied away

@@
 
-\bibitem[\protect\citeauthoryear{Auger et al.}{2009}]{Auger++2009} 
+\bibitem[{{Auger} {et~al.}(2007){Auger}, {Fassnacht}, {Abrahamse}, {Lubin}, \&
+  {Squires}}]{AugerEtal2007}
+{Auger}, M.~W., {Fassnacht}, C.~D., {Abrahamse}, A.~L., {Lubin}, L.~M., \&
+  {Squires}, G.~K. 2007, \aj, 134, 668
+
+\bibitem[\protect\citeauthoryear{Auger et al.}{2009}]{AugerEtal2009} 
 Auger M.~W., Treu T., Bolton A.~S., Gavazzi R., Koopmans L.~V.~E., Marshall 
@@
 
-\bibitem[\protect\citeauthoryear{Auger et al.}{2010}]{Auger++2010} 
+\bibitem[\protect\citeauthoryear{Auger et al.}{2010}]{AugerEtal2010} 
 Auger M.~W., Treu T., Bolton A.~S., Gavazzi R., Koopmans L.~V.~E., Marshall 
@@
 \bibitem[\protect\citeauthoryear{Behroozi, Conroy, 
-\& Wechsler}{2010}]{Behroozi++2009} Behroozi P.~S., Conroy C., Wechsler R.~H., 2010, ApJ, 717, 379
+\& Wechsler}{2010}]{BehrooziEtal2009} Behroozi P.~S., Conroy C., Wechsler R.~H., 2010, ApJ, 717, 379
 
@@
 
+\bibitem[{{Brada{\v c}} {et~al.}(2009){Brada{\v c}}, {Treu}, {Applegate},
+  {Gonzalez}, {Clowe}, {Forman}, {Jones}, {Marshall}, {Schneider}, \&
+  {Zaritsky}}]{BradacEtal2009}
+{Brada{\v c}}, M., {et~al.} 2009, \apj, 706, 1201
+
 \bibitem[\protect\citeauthoryear{Collett et 
-al.}{2012}]{Collett++2012a} Collett T.~E., Auger M.~W., Belokurov V., 
+al.}{2012}]{CollettEtal2012a} Collett T.~E., Auger M.~W., Belokurov V., 
 Marshall P.~J., Hall A.~C., 2012, MNRAS, 424, 2864
+
+\bibitem[Dalal(2005)]{Dalal2005} Dalal, N.\ 2005, 25 Years After 
+the Discovery: Some Current Topics on Lensed QSOs,
+
+\bibitem[{{Dalal} {et~al.}(2005){Dalal}, {Hennawi}, \& {Bode}}]{DalalEtal2005}
+{Dalal}, N., {Hennawi}, J.~F., \& {Bode}, P. 2005, \apj, 622, 99
 
@@
 \bibitem[\protect\citeauthoryear{Falco, Gorenstein, 
-\& Shapiro}{1985}]{Falco++1985} Falco E.~E., Gorenstein M.~V., Shapiro I.~I., 1985, ApJ, 289, L1
+\& Shapiro}{1985}]{FalcoEtal1985} Falco E.~E., Gorenstein M.~V., Shapiro I.~I., 1985, ApJ, 289, L1
+
+\bibitem[{{Fassnacht} \& {Lubin}(2002)}]{Fassnacht+Lubin2002}
+{Fassnacht}, C.~D., \& {Lubin}, L.~M. 2002, \aj, 123, 627
 
 \bibitem[\protect\citeauthoryear{Fassnacht, Koopmans, 
-\& Wong}{2011}]{Fassnacht++2011} Fassnacht C.~D., Koopmans L.~V.~E., Wong K.~C., 2011, MNRAS, 410, 2167
+\& Wong}{2011}]{FassnachtEtal2011} Fassnacht C.~D., Koopmans L.~V.~E., Wong K.~C., 2011, MNRAS, 410, 2167
 
 \bibitem[\protect\citeauthoryear{Gavazzi et 
-al.}{2008}]{Gavazzi++2008} Gavazzi R., Treu T., Koopmans L.~V.~E., 
+al.}{2008}]{GavazziEtal2008} Gavazzi R., Treu T., Koopmans L.~V.~E., 
 Bolton A.~S., Moustakas L.~A., Burles S., Marshall P.~J., 2008, ApJ, 677, 
@@
 
+\bibitem[{{Hilbert} {et~al.}(2007){Hilbert}, {White}, {Hartlap}, \&
+  {Schneider}}]{HilbertEtal2007}
+{Hilbert}, S., {White}, S.~D.~M., {Hartlap}, J., \& {Schneider}, P. 2007,
+  \mnras, 382, 121
+
 \bibitem[\protect\citeauthoryear{Hilbert et 
-al.}{2009}]{2009A&A...499...31H} Hilbert S., Hartlap J., White S.~D.~M., Schneider P., 2009, A\&A, 499, 31
+al.}{2009}]{HilbertEtal2009} Hilbert S., Hartlap J., White S.~D.~M., Schneider P., 2009, A\&A, 499, 31
+
+\bibitem[Holder 
+\& Schechter(2003)]{Holder+Schechter2003} Holder, G.~P., \& Schechter, P.~L.\ 2003, \apj, 589, 688
 
@@
 \& Wald}{1998}]{Holz+Wald1998} Holz D.~E., Wald R.~M., 1998, PhRvD, 58, 063501
+
+\bibitem[{{Keeton} \& {Zabludoff}(2004)}]{Keeton+Zabludoff2004}
+{Keeton}, C.~R., \& {Zabludoff}, A.~I. 2004, \apj, 612, 660
 
@@
 
+\bibitem[{{Momcheva} {et~al.}(2006){Momcheva}, {Williams}, {Keeton}, \&
+  {Zabludoff}}]{MomchevaEtal2006}
+{Momcheva}, I., {Williams}, K., {Keeton}, C., \& {Zabludoff}, A. 2006, \apj,
+  641, 169
+
 \bibitem[\protect\citeauthoryear{Nandra, Lasenby, 
-\& Hobson}{2012}]{Nandra++2012} Nandra R., Lasenby A.~N., Hobson M.~P., 2012, MNRAS, 422, 2945
+\& Hobson}{2012}]{NandraEtal2012} Nandra R., Lasenby A.~N., Hobson M.~P., 2012, MNRAS, 422, 2945
 
@@
 Neto A.~F., et al., 2007, MNRAS, 381, 1450
+
+\bibitem[{{Oguri} \& {Takahashi}(2006)}]{Oguri+Takahashi2006}
+{Oguri}, M., \& {Takahashi}, K. 2006, \prd, 73, 123002
 
@@
 \bibitem[\protect\citeauthoryear{Springel et 
-al.}{2005}]{Springel++2005} Springel V., et al., 2005, Natur, 435, 629
+al.}{2005}]{SpringelEtal2005} Springel V., et al., 2005, Natur, 435, 629
 
-\bibitem[\protect\citeauthoryear{Suyu}{2012}]{Suyu2012b} Suyu 
-S.~H., 2012, arXiv, arXiv:1202.0287
+% \bibitem[\protect\citeauthoryear{Suyu}{2012}]{Suyu2012b} Suyu 
+% S.~H., 2012, arXiv, arXiv:1202.0287
 
-\bibitem[\protect\citeauthoryear{Suyu et al.}{2012}]{Suyu++2012a} 
+\bibitem[\protect\citeauthoryear{Suyu et al.}{2012}]{SuyuEtal2012} 
 Suyu S.~H., et al., 2012, arXiv, arXiv:1208.6010
 
-\bibitem[\protect\citeauthoryear{Suyu et al.}{2010}]{Suyu++2010} 
+\bibitem[\protect\citeauthoryear{Suyu et al.}{2010}]{SuyuEtal2010} 
 Suyu S.~H., Marshall P.~J., Auger M.~W., Hilbert S., Blandford R.~D., 
@@
 
-\bibitem[\protect\citeauthoryear{Wong et al.}{2011}]{Wong++2011} 
+\bibitem[{{Wang} \& {Dai}(2011)}]{Wang+Dai2011}
+{Wang}, F.~Y., \& {Dai}, Z.~G. 2011, \aap, 536, A96
+
+\bibitem[{{Williams} {et~al.}(2006){Williams}, {Momcheva}, {Keeton},
+  {Zabludoff}, \& {Leh{\'a}r}}]{WilliamsEtal2006}
+{Williams}, K.~A., {Momcheva}, I., {Keeton}, C.~R., {Zabludoff}, A.~I., \&
+  {Leh{\'a}r}, J. 2006, \apj, 646, 85
+
+\bibitem[\protect\citeauthoryear{Wong et al.}{2011}]{WongEtal2011} 
 Wong K.~C., Keeton C.~R., Williams K.~A., Momcheva I.~G., Zabludoff A.~I., 
 2011, ApJ, 726, 84
+
+\bibitem[{{Wong} {et~al.}(2012){Wong}, {Ammons}, {Keeton}, \&
+  {Zabludoff}}]{WongEtal2012}
+{Wong}, K.~C., {Ammons}, S.~M., {Keeton}, C.~R., \& {Zabludoff}, A.~I. 2012,
+  \apj, 752, 104
 

### 2012-10-09 doc/paper-lcr.tex
appendix B done

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Truncated NFW halos}
@@
 
-\section{Deriving the $\Mstar=\Mhalo$ relation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Inferring $\Mhalo$ given a noisy measurement of $\Mstarobs$}
 \label{appendix:MSMH}
+
+Given a noisy estimate of the stellar mass of a galaxy, $\Mstarobs$, how can
+we infer the galaxy's halo mass? We seek the posterior PDF
+$\Pr(\Mhalo|\Mstarobs)$, which can be expanded as follows:
+
+\begin{eqnarray}
+&& \Pr(\Mhalo|\Mstarobs) = \notag\\
+&& \int d\Mstar \Pr(\Mhalo|\Mstar) \Pr(\Mstar|\Mstarobs), \notag\\
+&\propto& \int d\Mstar \Pr(\Mstarobs|\Mstar) \Pr(\Mstar|\Mhalo) \Pr(\Mhalo),
+\label{eq:mhalo-mstar}
+\end{eqnarray}
+where we have used Bayes Theorem twice to replace
+$\Pr(\Mstar|\Mhalo) \Pr(\Mhalo)$ with $\Pr(\Mhalo|\Mstar) \Pr(\Mstar)$, and 
+to invert $\Pr(\Mstar|\Mstarobs)$ into the sampling
+distribution $\Pr(\Mstar|\Mstarobs)$, which we recognise as the likelihood
+function for the observed stellar mass. Note that the ``true'' $\Mstar$ of the
+galaxy is marginalised out: we are only interested in reconstructing the halo
+mass. The last two terms in
+\eqref{eq:mhalo-mstar} are the $\Mstar-\Mhalo$ relation from
+\citet{BehrooziEtal2010}, and the halo mass function $\Pr(\Mhalo)$. We can
+tabulate the product of these two from our Millenium Simulation catalog,
+constructing a two-dimensional histogram of halo masses and their associated
+true stellar masses (drawn from the Behroozi relation).
+
+For each galaxy, we compute the likelihood function for its $\Mstarobs$ as a
+function of the unknown $\Mstar$, and multiply it by our tabulated joint PDF.
+This heavily downweights halos with $\Mstar$ values outside the observed
+range. We then do the marginalisation integral by Monte Carlo, drawing
+(two-dimensional) sample parameter vectors
+from the downweighted histogram, discarding the $\Mstar$ values, and
+constructing a one-dimensional histogram that is an estimate of
+$\Pr(\Mhalo|\Mstarobs)$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2012-10-09 doc/paper-lcr.tex
appendix B notes on redshift added

@@
 
-Given a noisy estimate of the stellar mass of a galaxy, $\Mstarobs$, how can
-we infer the galaxy's halo mass? We seek the posterior PDF
-$\Pr(\Mhalo|\Mstarobs)$, which can be expanded as follows:
+Given a noisy estimate of the stellar mass $\Mstarobs$ of a galaxy at redshift
+$z$, how can we infer the galaxy's halo mass? We then seek the posterior
+PDF $\Pr(\Mhalo|\Mstarobs)$, which can be expanded as follows:
 
 \begin{eqnarray}
-&& \Pr(\Mhalo|\Mstarobs) = \notag\\
-&& \int d\Mstar \Pr(\Mhalo|\Mstar) \Pr(\Mstar|\Mstarobs), \notag\\
-&\propto& \int d\Mstar \Pr(\Mstarobs|\Mstar) \Pr(\Mstar|\Mhalo) \Pr(\Mhalo),
+&& \Pr(\Mhalo|\Mstarobs,z) = \notag\\
+&& \int d\Mstar \Pr(\Mhalo|\Mstar,z) \Pr(\Mstar|\Mstarobs,z), \notag\\
+&\propto& \int d\Mstar \Pr(\Mstarobs|\Mstar) \Pr(\Mstar|\Mhalo,z) \Pr(\Mhalo|z),
 \label{eq:mhalo-mstar}
 \end{eqnarray}
-where we have used Bayes Theorem twice to replace
-$\Pr(\Mstar|\Mhalo) \Pr(\Mhalo)$ with $\Pr(\Mhalo|\Mstar) \Pr(\Mstar)$, and 
+where we have used Bayes' Theorem twice to replace
+$\Pr(\Mhalo|\Mstar,z) \Pr(\Mstar|z)$ with 
+$\Pr(\Mstar|\Mhalo,z) \Pr(\Mhalo|z)$, and 
 to invert $\Pr(\Mstar|\Mstarobs)$ into the sampling
@@
 \eqref{eq:mhalo-mstar} are the $\Mstar-\Mhalo$ relation from
-\citet{BehrooziEtal2010}, and the halo mass function $\Pr(\Mhalo)$. We can
+\citet{BehrooziEtal2010}, and the halo mass function $\Pr(\Mhalo|z)$, at the
+given redshift. We can
 tabulate the product of these two from our Millenium Simulation catalog,
@@
 
+If the redshift of the galaxy is uncertain, we need to take this uncertainty
+into account; for example, for each sample drawn from the photometric redshift
+posterior PDF $\Pr(z|{\rm colors})$, we can draw a sample $\Mhalo$ using the
+above procedure.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2012-10-10 doc/paper-lcr.tex
appendix on kappa inference added

@@
 
+\todo{Matt}{Edit the above text to add a note on how we do the sampling in
+practice, via the CDF.}
+
 If the redshift of the galaxy is uncertain, we need to take this uncertainty
@@
 
-%\section{Smooth component models}
-%\label{appendix:smooth}
+\section{Accounting for uncatalogued low mass halos, and voids}
+\label{appendix:smooth}
+
+Our halo model allows us to infer a halo mass $\Mhalo$ for each galaxy in a
+photometric catalog; under the weak lensing approximation described in
+\Sref{sec:theory} we can compute the contribution of each of these halos to
+the overall convergence and shear amplitude, assuming a homogeneous
+Friedman-Robertson-Walker metric and the concordance $\Lambda$CDM cosmological
+parameters for the angular diameter distances to calculate the critical
+density for each lens plane. Clearly this approach will tend to over-estimate
+the convergence, since we are placing massive halos into a volume that has
+already been assumed to be full of homogeneously distributed matter with the 
+mean cosmological density. In practice, the space between massive halos will
+contain a) low mass halos that are not bright enough to be detected and b)
+empty space where the density is below that of the mean. A rigorous treatment
+of this complex situation is beyond the scope of this paper, but is being
+investigated (Blandford et al, in preparation). In this appendix we describe
+our empirical approach to accounting for the missing mass and voids.
+
+Let the summed convergence due to halos in our galaxy catalog be $\kappah$.
+Given some assumptions about halo density profile and shape, this parameter
+can be inferred from a set of uncertain halo mass estimates (which have in
+turn been inferred from noisy measurements of galaxy redshift and stellar mass
+as described in \Aref{appendix:MSMH}). We assume each halo to be a
+spherically-symmetric NFW profile, and neglect the contribution of the stellar
+mass to the convergence. The halo mass inference for the $k^{\rm th}$ galaxy 
+is stored as a list of sample values of $\Mhalok$ drawn from the posterior PDF
+$\Pr(\Mhalok|\Mstarobsk,z_k)$; computing the contribution to the convergence
+due to this halo at the target line of sight for each sample gives, in turn, 
+a set of
+samples drawn from the PDF $\Pr(\kappahk|\Mstarobsk,z_k)$. We then generate
+samples from $\Pr(\kappah|\{\Mstarobsk,z_k\})$ by drawing a sample $\kappahk$
+for each halo, summing over halos to get $\kappah$, discarding those
+samples and moving down the lists.
+
+The PDF $\Pr(\kappah|\{\Mstarobsk,z_k\})$ will, in general, be broad (due to
+the uncertainties involved in halo mass estimation). It will also be shifted
+towards high values of convergence, due to the FRW approximation described
+above. What we really want is an inference of $\Pr(\kappa|\{\Mstarobsk,z_k\})$
+instead. We can obtain this by considering the expansion:
+\begin{equation}
+\Pr(\kappa|\{\Mstarobsk,z_k\}) = \int d\kappah 
+   \Pr(\kappa|\kappah) \Pr(\kappah|\{\Mstarobsk,z_k\})
+\label{eq:kappaconv}   
+\end{equation}
+The first term in the integrand relates the summed  convergence due to model
+halos, $\kappah$, to the true summed convergence, $\kappa$.  In the Millenium
+Simulation catalogs, we can compute a single value of $\kappah$ for each
+selected line of sight from the true halo mass and redshift (and our same
+assumptions of halo profile and shape), and tabulate the two-dimensional PDF
+$\Pr(\kappa|\kappah)$ as a sequence of one-dimensional PDFs for $\kappa$ in a
+bin at fixed $\kappah$. Note that this PDF captures the ``intrinsic scatter''
+of $\kappah$ due to our assumptions about the clumpiness of mass in the
+Universe; the integral is the convolution of this distribution with that
+arising from our observational uncertainties.
+
+For any given observed catalog then, we infer
+$\Pr(\kappah|\{\Mstarobsk,z_k\})$ as described above, and then
+multiply it by $\Pr(\kappa|\kappah)$; we
+again do the marginalisation over $\kappah$ by Monte Carlo, drawing samples
+from the two-dimensional grid and keeping only the $\kappa$ values, to form
+our final result, $\Pr(\kappa|\{\Mstarobsk,z_k\})$. 
+This PDF will describe, by construction, an accurate (i.e., unbiased)
+measurement of $\kappa$ in the case where the Millenium Simulation halo
+catalog and Behroozi et al $\Mstar-\Mhalo$ relation are themselves accurate
+descriptions of galaxies and their distribution. In \Sref{sec:tests} we
+investigate the amplitude of the systematic errors incurred if these
+assumptions are not valid.
+
+\todo{Matt}{Add text describing whatever sampling shortcut you derive! :-)}
+
+% Finally, we note that \Eref{eq:kappaconv} and the method for evaluating the
+% integral in it can be generalized to yield 
+% $\Pr(\kappa,|\gamma||\{\Mstarobsk,z_k\})$, where $|\gamma|$ is the amplitude
+% of the complex shear. The amplitude of the shear due to halos, $|\gammah|$ is
+% needed in this calculation, and marginalised over -- $\gammah$ is computed by
+% simple summation of its components, as in \Sref{sec:theory}. In
+% \Sref{sec:includinggamma} we explore the impact that knowing $\gamma$ (from,
+% for example, a strong lens model)  has on the inference of $kappa$, and how
+% severe the systematic errors from getting this wrong might be.
 

### 2012-10-10 doc/paper-lcr.tex
marginalisation over \kappah is not a convolution!

@@
 of $\kappah$ due to our assumptions about the clumpiness of mass in the
-Universe; the integral is the convolution of this distribution with that
-arising from our observational uncertainties.
+Universe; the integral combines these uncertainties with those
+arising from the measurement of $\Mstarobs$ and~$z$.
 

### 2012-10-15 doc/framework.tex
added framework

--- 2012-10-09 doc/paper-lcr.tex
@@
 \begin{abstract} 
-
-Strong gravitational lenses can provide high precision cosmological distance
-measurements; one of the most important sources of systematic error in these
-estimates is the additional mass along the line of sight to the source. Weak
-lensing by galaxies and groups in this beam can contribute an ``external
-convergence'' $\xkappa$ that dominates the  uncertainty in the inferred
-distances; likewise, it may also contaminate estimates of the luminosity of
-objects at high redshift (such as reionisation-era proto-galaxies, and type Ia
-supernovae standard candles).  We characterise this uncertainty by marginalising
-over a probability density function for $\xkappa$: here, we investigate the use
-of a simple halo model to estimate $\Pr(\xkappa)$ given noisy estimates of the
-photometric redshift and stellar mass of galaxies observed in optical imaging
-surveys of the field in question. We use mock catalogs from the Millenium
-Simulation and compare our reconstructed $\Pr(\xkappa)$ to ray-traced $\kappa$ values,
-we find that our model produces an unbiased estimator of $\kappax$,
-For each lightcone the individual $\Pr(\xkappa)$ from this reconstruction process are
-typically 1.8 times narrower than the global distribution of $\xkappa$ given perfect knowledge 
-of the halo mass and redshift. After incorporating uncertainties on redshift and halo and stellar masses
-we typically find that the reconstruction yields an improvement factor of 1.5. For each line of sight the
- $\Pr(\xkappa)$ can be formed before the investment of light-curve monitoring. By following up only the 
-most costrained lines of sight a factor of 2 improvement over the global $\pr(\kappax)$ should be 
-achievable.
+abstract
 \end{abstract}
@@
 \section{Introduction}
-
-Averaged over large areas of sky, the weak gravitational lensing effect can be
-used to constrain the statistical properties of the matter density in the
-Universe: every distant object we observe has had its shape distorted, and size
-and total brightness magnified (or demagnified) by a compound lens constructed
-from all the mass distributed between us and it.
-
-This fact makes weak gravitational lensing a potentially important source of
-systematic error for any estimate of luminosity or distance, an issue
-raised for \eg 
-type Ia supernovae by \citet[][]{Holz+Wald1998,Linder+Holz2004}, for
-gamma ray bursts by \citet[][]{Oguri+Takahashi2006,Wang+Dai2011}, 
-and for high redshift galaxies by \citet{BradacEtal2009}, among others. 
-Along lines of sight containing strong gravitational lenses,
-the effect has been found to be
-particularly important, with foreground and background structures
-having a significant effect on the inferred lensing cross-section
-\citep[\eg][]{WongEtal2012} and distance ratios \citep[][]{DalalEtal2005}.
-In time delay lens cosmography,
-\citet{SuyuEtal2010} found that  the lensing effect of mass structures along the
-(unusually over-dense)  line of sight to the quadruply-imaged radio source
-B1608$+$656, the so-called ``external convergence,'' was the dominant source
-of uncertainty in their 6\% measurement of Hubble's constant.
-
-How can we correct for this weak lensing error, and make
-accurate measurements through the Universe? When inferring global quantities
-(such as the cosmological parameters), averaging the results from a large
-number of independent objects will tend to reduce the error, as the
-ensemble-averaged convergence approaches zero for an unbiased sample
-\citep[\eg][]{Linder+Holz2004}. If the sample is biased, however, some
-residual systematic error will remain while the statistical uncertainty
-decreases -- and this will be the case for any sample selected by the
-brightness of the lensed object, or any other quantity that depends on
-$\xkappa$. The latter class includes time delay lenses, which could be
-either detected or selected 
-based on their image separations, magnifications or quadruple image
-configurations, all of which either increase or become more likely with
-increasing $\kappa$. Large
-samples of lenses are expected to be discovered in the next decade in
-ground-based optical imaging surveys \citep{Oguri+Marshall2010} -- but these
-samples will be image separation-limited, due to the surveys' relatively poor
-($\sim 1$~arcsec) image quality. Some of the current sample of known time
-delay lenses were detected in surveys like this: we might expect them to be
-somewhat biased towards high values of $\xkappa$.
-
-There are two broad approaches one could take at this point. First, one could
-seek to characterise the lensed objects' selection function, and use this
-understanding to derive a suitable correction to cosmological parameters
-inferred assuming no $\xkappa$ at all. As pointed out by  \citet[][among
-others]{Oguri+Takahashi2006}, to do this one would need  information about the
-unlensed population of objects, and the population of lenses, and how the
-objects were detected -- or to infer these hierarchically during the analysis.
-Alternatively, one could simply accept all lenses provided, regardless of
-their selection, and try to use any additional information that is available
-to estimate the external convergence in each system on a case by case basis,
-and hence optimize their joint analysis to produce a better-constrained result
-\citep[as suggested by][]{Keeton+Zabludoff2004}. In this work we follow this
-second approach, and use measurements of the positions, magnitude and colours
-of galaxies close to lens lines of sight to try to infer the
-external convergence at the lens position.
-
-Attempts to date at reconstructing the local and  line of sight mass
-distribution in strong lens fields (what \citeauthor{WongEtal2011} call ``the
-full environment'') have focused on photometric and  spectroscopic surveys to
-detect galaxy groups and ascertain galaxies' membership,  and on understanding
-the external shear apparently required by the strong lens models. Surveys by
-\citet{Fassnacht+Lubin2002,AugerEtal2007,WilliamsEtal2006,MomchevaEtal2006}
-all found groups of galaxies both hosting and lying  along the line of sight
-to known gravitational lenses. Initial estimates of the effect of these
-structures suggested the importance of assigning mass to both galaxy and group
-halos, and to allowing for significant uncertainty in the centroids of group
-halos. The probability density function (PDF) for the external convergence for
-that lens, $\Pr(\xkappa)$, is the target for any reconstruction analysis, and
-is the key quantity for any ensemble analysis, since by marginalising over it
-we can correctly propagate the uncertainties due to weak lensing. Coming
-closest to estimating this quantity from survey data, \citet{WongEtal2011} ran
-Monte Carlo reconstructions of the mass in nine lens fields based on
-\citeauthor{WilliamsEtal2006} and \citeauthor{MomchevaEtal2006}'s
-photometric and spectroscopic measurements of galaxies close to the line of
-sight, and compared the resulting predicted shear distributions with the
-external shear demanded by the strong lens model. Their simulations show most
-of the shear being generated by bright galaxies within 2~arcminutes of the
-lens, and that both line of sight structures and the group of galaxies in each
-lens plane contribute significant proportions of the shear. They find
-significant discrepancies between the lens model shear and the Monte Carlo
-predictions, and are unable to distinguish between the environment modelling
-and the strong lens modelling as the cause of these discrepancies.
-
-These observational investigations have provided very useful insight into the
-problem.  Coming from a more theoretical direction, large numerical
-simulations have been used to predict, from first principles, the distribution
-of likely external shears and convergences along strong lens lines of sight. 
-\citet{Holder+Schechter2003} and \citet{Dalal+Watson2004} carried out
-ray-tracing calculations in N-body simulations to estimate the  distribution
-of external shear values.  \citet{HilbertEtal2009} performed similar ray-tracing
-experiments through the Millenium Simulation \citep{SpringelEtal2005},
-generating a predicted $\xkappa$ at every position in a simulated sky. The
-first step towards using this excellent calibration resource was taken by
-\citet{SuyuEtal2010}, who selected Millenium Simulation lines of sight that a)
-were found to contain a strong lens and b) had comparable apparent galaxy
-overdensity in a 45 arcsec radius aperture down to $i < 24$. This overdensity
-could be compared to the overdensity of the B1608$+$656 line of sight
-\citep{FassnachtEtal2011}, and hence an estimate of  $\Pr(\xkappa)$ could be
-made.
-
-In this paper, we bring these observational and theoretical approaches
-together and  use numerical simulations to {\it test and calibrate} a
-reconstruction of the  external convergence. Ray-tracing through the
-simulations gives a ``truth'' that we can attempt to recover.  In this paper
-we use the Millenium Simulation mock galaxy catalogs and ray-traced lensing
-effects to test the accuracy of line of sight mass reconstructions.
-Probabilistically ssigning mass and redshift to every observed galaxy in the
-field around a time delay lens, we generate Monte Carlo sample line of sight
-mass distributions, and estimate the external convergence due to each one.
-This gives us a $\Pr(\xkappa)$ that can be propagated into further joint
-inferences. We focus on time delay lens cosmography, and quantify our results
-in terms of the uncertainty on the mean time delay distance to a test sample
-of $N$ lenses (where for clarity each lens has the same deflector and source
-redshift, and the same lens model and time delay uncertainty).
-
-We aim to answer the following questions:
-\begin{itemize}
-\item Faint galaxies and other dark structures will not appear in a photometric
-object catalog, but they will contribute convergence at some level. How much of
-the total external convergence in a time delay lens system comes from visible
-galaxies? How does this change as a function of magnitude cut? 
-\item Can the true (ray-traced) convergence be recovered by halo model
-reconstruction? What scatter and residual bias are induced in the ensemble 
-distance estimate? Which aspects of the model dominate these uncertainties? 
-\item When faced with a newly-detected lens, surrounded by galaxies on the sky,
-we have some choices to make when planning follow-up observations.
-Which are the most important galaxies, with regard to the external convergence
-produced? Can nearby groups and clusters be straightforwardly accounted for? If
-lenses with such massive structures nearby are discarded, what impact does that
-have on the distance accuracy?
-\end{itemize}
-
-This paper is organized as follows. In~\Sref{sec:theory} we review the relevant
-gravitational lensing theory, before introducing our simple reconstruction 
-model in \Sref{sec:model}.  We then test this model in two phases: first, in
-\Sref{sec:knownMh+z}, with known redshift and halo mass for every galaxy in a
-lens field, in order to quantify the irreducible uncertainty due to unseen mass,
-and second, in \Sref{sec:obsMstar+z}, with realistic observational uncertainties
-on the field galaxies' stellar masses and redshifts. \comments{We then propagate all these
-uncertainties through to the time delay distance in a toy sample of 100 lenses,
-in \Sref{sec:distances}.} We discuss our results in \Sref{sec:discuss} before
-concluding in \Sref{sec:conclude}.
-
-Throughout this paper magnitudes are given in the AB system and
-we adopt the Millenium Simulation's ``concordance'' parameters for our reference cosmology, \ie
-$h=0.73$, $\Omega_m=0.25$ and $\Omega_\Lambda=0.75$, where the symbols indicate
-the Hubble Constant in units of 100 km s$^{-1}$ Mpc$^{-1}$ and the matter and
-dark energy density of the Universe in units of the critical density
-.%\citep[e.g.\ ][]{KomEtal09}.
-
+\todo{Phil,(+ Tom)}{Update introduction to reflect the scope of this paper}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:theory}
-
-%Time delay distances, and the mass sheet degeneracy - how kappa is degenerate in
-%strong lens models (and magnifications).
-
-Convergence, or Ricci focusing, occurs when a gravitational lens focuses the rays in a raybundle.
-This focussing can cause distant objects to appear brighter, and larger than they would if the lens
- were removed.
-The convergence from an isolated mass sheet is the ratio of the projected surface mass density
-($\Sigma(D_{\mathrm{od}}\bmath{\theta})$) devided by the critical surface mass density at the redshift of the mass sheet ($\Sigma_{\rm cr}$),
-\be
-\kappa(\bmath{\theta})= \frac {\Sigma(D_{\mathrm{od}}\bmath{\theta})}{\Sigma_{\rm cr}(z)}
-\ee
-where 
-\be \label{eq:sigcrit} 
-\Sigma_{\rm cr}(z) \equiv \frac{c^2 D_{\rm os}}{4 \pi G D_{\rm od} D_{\rm ds}}.
-\ee
-and the D's are the angular diameter distances between the objects refered to in the subscripts: o is the observer, d is the deflector and s is the source.
-If the surface mass density of the sheet exceeds $\Sigma_{\rm cr}$, multiple images of the source can
-occur, otherwise only one image will be observed, although that image will still be perturbed
-relative to the unlensed case.
-
-Strong lensing occurs when a massive object and background source are almost perfectly
-aligned along a line of sight. The light from the background source is deflected by the
-lens galaxy; this deflection allows multiple images of the background source to form
-at stationary points of the time delay function. For an isolated lens, the time delay
-function can be calculated from
-\be \label{eq:T} 
-\Delta t(\bmath{\theta},\bmath{\beta}) = \frac {1}{c} \frac{D_{\rm od} D_{\rm os}}{D_{\rm ds}} (1+z_{\rm d})\, \phi(\bmath{\theta},\bmath{\beta}),
-\ee
-where $\bmath{\theta}$ is the observed source position, $\bmath{\beta}$ is the 
-unlensed source position, $z_{\rm d}$ is the redshift of the lens, $\phi(\bmath{\theta},\bmath{\beta})$ is
-the Fermat potential. The Fermat potential is given by
-\be \label{eq:FP}
-\phi(\bmath{\theta},\bmath{\beta})\equiv \left[\frac{(\bmath{\theta}-\bmath{\beta})^2}{2}-\psi(\bmath{\theta}) \right], 
-\ee
-where $\psi(\bmath{\theta})$ is the lens potential, derived from the projected dimensionless
-surface mass density, $\kappa(\bmath{\theta})$, by 
-\be \label{eq:psikappa}
-\kappa(\bmath{\theta})=\frac{1}{2}\nabla^2\psi(\bmath{\theta}).
-\ee
-
-Strong lenses sit in our real Universe -- they are not truely isolated;
-there is some mass along the line of sight coming from intervening structures.
-These structures may be physically associated with the lens e.g. other members
-of a group or cluster, or they may be the result of chance alignments at any redshift. 
-Whilst it is rare for three galaxies to line up well enough for both of the background sources
-to be strongly lensed \citep{GavazziEtal2008,CollettEtal2012a}, the shear scale of dark matter halos
-makes a partial alignment -- with the additional structure acting as a weak lens -- 
-a near certainty, indeed \citet{Vale+White2003} and \citet{HilbertEtal2007} find that there
-are no empty lightcones in a realistic universe. These additional structures induce an external shear
-which can be recovered in the mass-modelling of the lens, but they can also introduce a convergence that
-is undetectable from the image positions, shapes and relative fluxes; {\it the
-mass sheet-degeneracy} \citep{FalcoEtal1985}.
-
-If the intrinsic source brightness changes, the observed brightness in each image does not change
-simultaneously - there is a time delay, $\Delta t$, between the brightness change in
-each image. Despite the invariance of the image positions and fluxes, under the addition
-of an external convergence (and appropriate re-scaling of the lens potential) the relative Fermat potential between the images is {\it not}
-invariant, and so the time delay changes. As such it is necessary to include $\kappax$
-in the lens modelling, if cosmological parameters are to be estimated accurately and
-precisely from observed time delays \citep{SuyuEtal2010}.
-
-\comments{
-If the mass sheet is not physically associated with the lens galaxy, it can lie at any redshift.
-The effects of such a mass-sheet can be projected back onto the lens plane in the form of an effective convergence.
-We define this effective convergence in two limits.
-\begin{itemize}
-\item No significant perturbations along the line of sight, and \\
-\item A single dominant perturber, relative to which all other perturbations are small.
-\end{itemize}
-We will refer to these cases as the magnification case (subscript $\mu$ in formulae), and the strong lensing case (subscript SL in formulae), respectively.
-We will ignore the additional case, of a compound lens, with several significant perturbers.
-
-The magnification case has no primary lens plane, and is chiefly relevant for the magnifications of distant objects.
-In the absence of a primary lens plane, we are free to define the effective convergence on any point; the effective convergence is the same, independant of the plane choosen.
-It can be shown \citep[\eg][]{xxx} that if there are several mass sheets at redshifts $\{z_{p}\}$, with convergences $\{\kappa_p =\Sigma_{p}/\Sigma_{\mathrm{cr}}(z_p)\}$, the effective convergence is given by
-\be \label{eq:kappasummu}
-\kappa_{\mathrm{effective,\mu}}=\sum_{p}\kappa_p.
-\ee
-
-In the stong lensing case, the presence of a significant perturber alters the
-geometry of the system, and provides a primary lens plane. It is the primary
-lens plane upon which we need to know $\kappa_{\mathrm{effective}}$, since
-this is where the mass-sheet degeneracy is defined. Following Equations 20--32
-of \citet{keeton2003}\flag{keeton2003}, it can be shown that the relevant
-effective convergence is given by 
-\be \label{eq:kappasumSL}
-\kappa_{\mathrm{effective,SL}}=
-{  
-(1-\beta_{12})(\kappa-\beta_{12}(\kappa^2-\gamma^2))
-\over
-(1-\beta_{12}\kappa)^2-(\beta_{12}\gamma)^2
-}
-\ee
-where $\kappa$ and $\gamma$ are, respectively, the convergence and shear
-caused by the perturber, in their own plane and $\beta_{12}$ is a geometrical
-scaling factor defined by
-\be\label{eq:beta}
-\beta_{12}={
-D_{12} D_{\mathrm{os}}
-\over
-D_{\mathrm{o}1} D_{1\mathrm{s}}
-}
-\ee
-where the D's are again angular diameter distances: the 1 (2) in the subscript
-refers to the lower (higher) redshift object of the lens and perturber. For
-the case that the mass sheet is in the lens plane, $\beta_{12} = 0$ and
-$\kappa_{\mathrm{eff}}=\kappa$; if the mass-sheet is in the plane of the
-observer, or source, $\beta_{12} = 1$ and $\kappa_{\mathrm{eff}}=0$; for a
-mass-sheet at any other redshift $0<\beta_{12}<1$. In the case of several mass
-sheets the effective convergences sum. In the limit that both $\kappa$ and
-$\gamma$ are small, Equation \ref{eq:kappasumSL} reduces to 
-\be \label{eq:kappasumSLweak}
-\kappa_{\mathrm{effective,SL}}=(1-\beta_{12})\kappa;
-\ee
-it is this $\kappa_{\mathrm{effective,SL}}$ that we use as $\kappax$ for the
-strong lensing time delay analysis in \ref{sec:Dt}.
-}
-
-\tom{The all-important calibration of the reconstruction has to be done
-against Stefan's ray-traced kappas though -- so it is these that we have to
-predict PDFs for, first and foremost. THEN we have to consider the question of
-which kappa to use to correct the time delay distances: Stefan's kappa (as in
-B1608 or RXJ1131), or kappa-keeton.}
-
-The time-delay distance is defined as
-\be \label{eq:dt}
-\Dt \equiv (1+\zd) D_{\rm d} D_{\rm s}/D_{\rm ds},
-\ee
-with which Equation \ref{eq:T} can be rephrased as
-\be
-\Delta t(\bmath{\theta},\bmath{\beta})  =  \frac{\Dt}{c} \, \phi(\bmath{\theta},\bmath{\beta})    ,
-\ee 
-Since the time delays are proportional to $1/ (1- \kappax)$, if there is any external convergence, that is not included in the lens
-modeling, then the time delay distance -- inferred assuming $\kappax = 0$ -- will be
-$(1-\kappax)$ less than the true value of $\Dt$.
-\be 
-\label{eq:MassSheet:H0bias}
-\Dt^{\rm{true}}=(1-\kappax) \Dt^{{\kappax = 0}}.
-\ee
-We can overcome this degeneracy if we have additional knowledge of $\kappax$.
-
-For mass-sheets that are physically associated with the lens galaxy, the mass sheet
- affects the stellar dynamics of the
-lens galaxy, so dynamical observations can break the internal
-mass-sheet degeneracy by providing an additional estimate of the lens galaxy's mass
-\citep[e.g.,][]{xxx}.
-
-In this work our aim is to quantify the lensing effect of mass-sheets that are not physically associated with the lens galaxy -- mass-sheets
-lying infront or behind the lens -- and the uncertainties induced by reconstructing
-those mass-sheets using simple prescriptions applied to potential astronomical observables.
-\comments{We also aim to quantify how uncertainties in the
-estimations of $\kappax$ propogate into uncertainties on the cosmological parametres
-which can be inferred from measurements of $\Dt$.}
+\todo{Phil,(+ Tom)}{Modify the current theory section, emphasiszing how $\kappax$ effects inferred parameters.
+Justify how we combine individual $\kappa$s to give a total $kappah$ - note that this is the weak lensing limit.}
 
@@
 
-\section{Halo Model and Mass distribution}
+\section{Estimating external convergence: The halo model approximation}
 \label{sec:model}
 
-%Weak lensing by NFW halos. Accounting for mass along the line of sight.
-%Approximations to full ray tracing:
-%
-%Halos. N-body sims provide mass framework. MS halo catalog. Truncated spherical
-%NFW approx based on virial masses. Stellar mass. Halo map corresponding to
-%ray-traced kappa map, for illustration. Small-scale structure
+\subsection{Ray-tracing through simulated Lines of Sight}
+\label{subsec:raytracing}
+\todo{Stefan}{Write section on how the ray tracing was done}
 
-For real lines of sight, we would like to estimate the external convergence as best we can given all
-data available. Typically this data is in the form of a photometric galaxy
-catalog, containing positions, brightnesses, colours, and possibly spectra for each galaxy in the
-field of the lens, down to some magnitude
-limit. Since we can not observe the surface mass density of each halo
-directy, we need some way of estimating
-the mass of each halo in the catalog, so that we can compute its
-contribution to the total $\kappax$ along the line of sight. This mass assignment recipe will be uncertain, but
-can be calibrated with cosmological simulations.
-
-% PJM: What is this defeatism?!
-% it is nearly impossible to know the true $\kappax$ for a
-% line of sight, and without a knowledge of $\kappax^{\mathrm{true}}$ it is hard to
-% quantify if there is a bias induced by using different $\kappax$ estimators.
-%
-% A source with known unlensed brightness e.g. a strongly lensed type Ia
-% Supernova \flag{cite some SNe papers} or a source of known unlensed size \flag{ideas?}
-% would break the mass-sheet degeneracy and provide a value for $\kappax$, but
-% \flag{no?} such systems are currently known.
-
-Cosmological dark matter simulations can be used to generate mock lines of
-sight and can be raytraced through to give each mock sightline a $\kappax$ value...
-\todo{Stefan}{Write section on how the ray tracing was done and how halos are extracted from
- the MS n-body particles}
-
-Transforming the photometometric galaxy catalogue into a  catalogue of
-halo masses, positions, and redshifts, will enable us to attempt a
-reconstruction of the convergence induced by every halo near a line of sight.
-This is the subject of the first subsection below. We also need to account for
-the mass in the Universe that is not associated with the galaxies we can see
--- this is the subject of the second subsection below.
+\subsection{Generating mock lightcones from simulations}
+\todo{Stefan}{Write section on how halos are extracted from the MS n-body particles}
 
@@
 \subsection{Halos}
-
-Cosmological dark matter simulations have shown that dark matter
-halos are well approximated by NFW profiles \citep{NFW}, with a density
-profile given by
-\be\label{eq:rhonfw}
-\rho(r) = 
-\frac{\rho_0}{\left(r/r_{s}\right)
-\left(1+r/r_{s}\right)^{2}},
-\ee
-where $r_{s}$ is a characteristic radius of the cluster, representing where
-the density slope transitions from $r^{-1}$ to $r^{-3}$. This radius is related
-to the virial radius of the halo by $r_{s}~=~r_{200}/c$, where $r_{200}$ is the radius at 
-which 
-\be
-\rho(r_{200}) = 200\rho_{{\mathrm{crit}}}(z), \text{ where } \rho_{\mathrm{crit}}(z) \equiv \frac{3H^{2}(z)}{8\pi G}
-\ee
-and $c$ is the concentration parameter, which can be estimated from the halo's mass,
-using a mass--concentration relation. Typically more massive halos are less concentrated,
-but there is some scatter; we use the relation of \citet{Neto2007} to estimate $c$
-from the mass enclosed within $r_{200}$, which we denote as $M_{200}$. The best fit relation of \citet{Neto2007} is given by
-\be
-c_{200} = 4.67 (M_{200}/10^{14} h^{-1} \Msun)^{-0.11}.
-\ee
-$\rho_0$ is calculated from the critical density and concentration parameter:
-\be
-\rho_0 = \rho_{\mathrm{crit}}(z)\frac{200}{3}\frac{c^{3}}{\ln(1+c)-c/(1+c)}.
-\ee
-
-Unphysically, if one integrates the density profile of an NFW profile, the total mass is divergent.
-Similarly, if the universe is homogeneously populated with NFW halos, the projected surface mass along any
-line of sight will also be divergant\footnote{At large radius, $\Sigma_{\rm
-nfw} \propto R^{-2}$, but the differential number of halos centred within an
-annulus of width $\dee R$ is given by $\dee N_{\rm annulus} \propto R \dee R$,
-so  $\Sigma_{\rm total} \propto \int_{0}^{\infty} R^{-1} \dee R$, which
-diverges logarithmically}. Since infinite mass is unphysical, the profile must
-be truncated at some point.
-\todo{Tom}{Add notes on previous truncation results}.
-Several truncation profiles have been suggested \citep[e.g][]{BMO}, but beyond several virial radii, the amount of matter associated with a halo is likely to be low; \citet{NandraEtal2012} showed that the Universe's expansion can place an upper limit on the radius of NFW halos -- for cluster scale halos, this happens at around 25 times the NFW scale radius.
-In \Sref{sec:knownMh+z} we investigate how different truncations affect the recovered total convergence for a line of sight, using the truncated NFW profile of \citet{BMO}
-\be\label{eq:bmoprofile}
-\rho(r) = 
-\frac{\rho_{\rm NFW} (r)}{1+\left(r/r_{t}\right)^2},
-\ee
-which is the same as the NFW profile in the limit that the truncation radius, $r_t$ goes to infinity. The convergence and shear for the BMO profile are given in Appendix \ref{appendix:halos}.
+\label{subsec:halos}
+\todo{Tom,Phil}{Check}
 
@@
 
-Whilst halos contribute a positive convergence to $\kappax$, voids contribute
-a negative convergence. When a raybundle passes through a  region of space
-that is less dense than $\rho_{\rm cr}(z)$ the rays are de-focused\footnote{In
-principle, the convergence caused by halos, is also caused by the overdensity,
-but we neglect this effect since halos are typically much more dense than the
-intergalactic medium}. Whilst the  full raytraced solution takes into account
-the effect of voids, our reconstruction cannot -- the halo catalogue does not
-include voids. In principle the absence of a halo could be taken to infer a
-void, but the under-density of such a void is hard to infer. Neglecting voids
-would lead to a heavily biased estimate of $\kappax$. We account for the voids
-statistically; we reconstruct
-the $\kappax$ contribution of halos for an ensemble of calibration sightlines
-and form the joint distribution P($\kapparay,\sumkappah$). The calibration
-can then be accounted for by marginalizing over all lines of sight with a similar
- $\sumkappah$.  We will refer to this calibration proceedure as the "void correction",
-although it also accounts for all of the physics that our simple spherical halo prescription
-neglects in a statistical manner. For each line of sight we create a $\pr(\kappax)$ from
-\be
-\pr(\kappax)=\int_{-\infty}^{+\infty}\pr(\kapparay',\tilde\kappa'_{\rm halos})W(\tilde\kappa_{\rm halos}-\tilde\kappa'_{\rm halos})\dee \tilde\kappa'_{\rm halos}
-\ee
-where $\tilde{\kappa}_{\rm halos}$ is the median of the reconstructed $\sumkappah$ for each line of sight.
-Primed qunatities refer to all of the calibration sightlines and unprimed refers to the specific line of sight.
-$W(\tilde\kappa_{\rm halos}-\tilde\kappa'_{\rm halos})$ is a weight function given by
-\be
-\label{eq:weighting}
-W(\tilde\kappa_{\rm halos}-\tilde\kappa'_{\rm halos})=\exp\left(-\frac{1}{2}\left(\frac{\left(\tilde\kappa_{\rm halos}-\tilde\kappa'_{\rm halos}\right)^2}{\sigma^2}\right)\right)
-\ee
-We take $\sigma$ as 0.002- this is an overestimate of the uncertainty on $\tilde\kappa_{\rm halos}$, but ensures that the full distibution of void corrections is sampled, despite the finite number of calibration sightlines.
-
-\comments{
-For each reconstruction of a line of sight we can then draw a $\kappav$ from $\pr(\kappav)$ to correct for the
-unseen voids. We refer to this corrective shift as $\kappav$. The void correction introduces a source of
-error, since the value of $\kappav$ comes from the ensemble of calibration lines of sight rather than the individual
-line of sight which is being reconstructed; this is unavoidable without modeling the $\kappax$ 
-contribution of voids along a line of sight. To avoid potential biases we calculate $\pr(\kappav)$
-from randomly selected calibration sightlines. The total $\kappax$ along the line of sight
-is given by 
-\be \label{eq:totalkappaxunweighted}
-\pr(\kappax) = \left(\sum_{\rm halos} \pr(\kappa_{\rm halo})\right)-\pr(\kappav).
-\ee
-
-Once the void correction has been applied,the reconstruction should produce a 
-reasonable estimate of $\pr(\kappax)$ for any single line of sight. However, from
-the ray tracing results we know the global $\kappax$ distribution ${\rm U}(\kappax)$. We can use the global
- ${\rm U}(\kappax)$ as a prior by noting that the normalized sum of $\pr(\kapparec)$ from multiple lines
-of sight should equal ${\rm U}(\kappax)$, \ie
-\be \label{eq:prior}
-{\rm U}(\kappax) = \lim_{N \to \infty} \sum_{i}^{N} \pr(\kappax)_{i} / N
-\ee
-In order to make Equation \ref{eq:prior} hold, we use Equation \ref{eq:totalkappaxunweighted} to calculate $\pr(\kappax)^{\rm unweighted}$ for the calibration lines of sight and
-re-weight the reconstructions by:
-\be \label{eq:weighting}
-W(\kappa)=\left(\sum_{i}^{N} \pr(\kappax)_{i}^{\rm unweighted} /N \right) / \left({\rm U}(\kappax)\right)
-\ee
-such that the final reconstruction is given by 
-\be \label{eq:totalkappax}
-\pr(\kappax) = \left(\left(\sum_{\rm halos} \pr(\kappa_{\rm halo})\right)-\pr(\kappav)\right)(W(\kappa)).
-\ee
-
-}
-
-\comments{
-Whilst halos contribute a positive convergence to $\kappax$, voids contribute
-a negative convergence. When a raybundle passes through a  region of space
-that is less dense than $\rho_{\rm cr}(z)$ the rays are de-focused\footnote{In
-principle, the convergence caused by halos, is also caused by the overdensity,
-but we neglect this effect since halos are typically much more dense than the
-intergalactic medium}. Whilst the  full raytraced solution takes into account
-the effect of voids, our reconstruction cannot -- the halo catalogue does not
-include voids. In principle the absence of a halo could be taken to infer a
-void, but the under-density of such a void is hard to infer.
-\tom{ Instead, we reconstruct 10000 lines of sight to give $\pr(\kapparec|kapparay)$
-and invert the PDF using Bayes' theorem to give $\pr(\kapparay|\kapparec)$. For each lightcone we
-can then get $\pr(\kapparay)$ by marginalizing over the reconstruction PDF, $\pr(\kapparec)$.
-This recipe also ensures that we correctly recover the ensemble $\kapparay$ distribution, even in the case
-of no input data.
-
- Instead, we shift
-our $\kappax$ values so that $\langle\kappax\rangle=0$. We refer to this
-corrective term as $\kappav$. The void correction introduces a source of
-error, since the inferred value of $\kappav$ will depend on the properties of
-the sightlines reconstructed, but this error shrinks with the number of
-sightlines reconstructed. To avoid potential biases we calculate $\kappav$
-from randomly selected sightlines. The total $\kappax$ along the line of sight
-is given by 
-\be \label{eq:totalkappax}
-\kappax = \left(\sum_{\rm halos} \kappa_{\rm halo}\right)-\kappav.
-\ee
-}}
+\todo{tom}{Outline _EXPLICITLY_ the proceedure we use to correct for voids etc}
 
@@
 
-\section{Tests with known halo mass and redshift}
+\section{Testing the halo model approximation with known halo mass and redshift}
 \label{sec:knownMh+z}
 
-%Raytracing through n-body particles as 'truth'. Motivation for assuming perfect
-%knowledge of halo mass and z = testing model of previous section. Deterministic
-%prediction of kappa.
-%
-%Is truncation choice important? How deep and wide does a reconstruction need to
-%go? What is the irreducible uncertainty on kappa from this halo model? (Bias and
-%scatter) Can use the ideal reconstruction to ask: Where does the kappa come
-%from? Close to the LoS? Bright objects? How many objects are important? What
-%error is made by considering subsets of available objects?
+\subsection{How does $\kappah$ relate to $\kappax$?}
+Done?
+\subsubsection{How does $\gammah$ relate to $\gammax$?}
+\todo{tom}{do}
+\subsection{Does converting from $\kappah$ to $\kappax$ work?}
+\todo{tom}{do}
 
-Given the halo mass catalogue from the Millenium Simulation, and convergence maps produced by
-ray-tracing through the MS's n-body particles, 
-it is possible to test the validity of the prescription outlined in Section \ref{sec:model}. We test the model
- by comparing $\sumkappah$ against $\kapparay$. If the reconstruction process is to be
- succesfull the two quantities should correlate.
-
-The reconstruction prescription is tested given perfect
-knowledge of the halos' virial masses and redshifts; this provides us with a measure of the intrinsic
-errors induced by treating matter as truncated NFW halos. For our first tests we do not apply the void correction of
-Section \label{subsec:voids}, instead we shift $\sumkappah$ for all our sightlines by a fixed negative offset such that the ensemble mean
-is zero, i.e.
-\be \label{eq:totalkappax}
-\kapparec = \left(\sum_{\rm halos} \kappa_{\rm halo}\right)-\kappav,
-\ee
-where $\kappav$ is a positive constant. This us allows us to test the correlation of $\sumkappah$ with $\kapparay$, without
- the uncertainty of the void correction obscuring any inadequacies of our halo based prescription.
-
-We choose 100000 lines of sight from random positions in the catalogue, and for each line of sight we reconstruct the
-convergences from every halo within 5 arcminutes and compare the reconstructed
-$\kapparec$ with those from the ray tracing results. The standard deviation on $\kapparay$-$\kapparec$ is
-shown in Figure \ref{fig:ScattervsTruncation} as a function of the radius at which the halo is truncated.
- It is clear from Figure \ref{fig:ScattervsTruncation} 
-that as long as the truncation is greater than a few virial radii, the choice of truncation
-radius does not broadly affect the scatter on $\kapparay-\kapparec$; from now on we choose 
-to truncate the halos at $5 \Rhalo$. Since $\sigma\left(\kapparay-\kapparec\right)$ does not go to
-zero, it is clear that out halo based prescription does not perfectly replicate the n-body results, we refer to this
- as the intrinsic error of the prescription.
- The intrinsic error has a standard deviation of $\sigi \sim 0.018$, although
-this figure is inflated by a few outliers in the tails of $\pr\left(\kapparay-\kapparec\right)$. Such outliers would 
-likely be rejected by their reconstructed shear not matching the shear of the lens model 
-(see \citet{WongEtal2011} for the practicalities of this);
- this makes our estimate of the intrinsic error pessimistic. We do not include any additional constraints on P($\kappax$), given prior knowledge of the external shear in this work.
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{figs/truncation_scatter.eps}
-\caption[magcut]{The standard deviation in $\kapparec$ minus $\kapparay$ as a function of halo truncation radius in virial radii, using the truncated NFW profile of \citet{BMO}.
-In our models we truncate our halos at 5$R_{200}$}
-\label{fig:ScattervsTruncation}
-\end{figure}
-
-For $\sumkappah$ to provide useful constraints on $\kapparay$, it is important that $\kapparay$ and $\sumkappah$ are as similar as possible.
-Figure \ref{fig:bias} shows that indeed $\sumkappah$ is a good estimator, regardless of the individual value of $\sumkappah$.
-At fixed $\sumkappah$ we find that the scatter in $\kapparay$ grows with $\sumkappah$; our reconstruction is better at reproducing underdense lines of sight than overdense lines of sight.
-
-\begin{figure}
-% \includegraphics[width=\columnwidth]{figs/perfectc.eps}
-\caption[Biased?]{$\sumkappah$ verses $\kapparay$ for 100000 reconstructed lines of sight.
-$\sumkappah$ traces $\kapparay$, but with a non-zero offset which is due to the negative connvergence from voids.
-At fixed $\sumkappah$ the scatter in $\kapparay$ grows with $\sumkappah$.}
-\label{fig:isitbiased}
-\end{figure}
-
-The intrinsic error between the results of the halo based prescription and the raytraced convergence is an unavoidable error, even with perfect knowledge of halo mass and position.
-Before investigating the errors caused by imperfect knowledge of halo mass and redshift, we investigate the errors induced by a magnitude limited reconstruction and a field of view limited reconstruction.
-The halos in our catalogue are given magnitudes by the semi-analytic model of \citet{deLucia+Blaizot2007} and by applying magnitude cuts to our catalogue, we can investigate the scatter caused by unobserved halos.
-The majority of the convergence comes from halos with an $i$ magnitude between 18 and 24.
-Figure \ref{fig:magcut} shows that the width of $\kapparec-\kapparay$ decreases quickly between $i=18$ and $i=24$.
-Objects brighter than $i=18$ are either too rare or too close to the observer to make a significant contribution to the convergence.
-Objects fainter than $i=24$ are too small to be important, unless they are extremely close to the line of sight where it is likely that neglecting stellar mass and using a spherical NFW prescription are too naive to adequately reconstruct $\kappax$.
-It is likely that ultra-faint halos (or substructures), the uncertain contribution of voids and halos deviating from our spherical truncated NFW profile are the three major sources of the scatter in $\kapparec-\kapparay$; a deeper survey will not be sufficient to decrease the size of this scatter.
-Since a large number of callibration lines of sight must be reconstructed to sample $\pr(\kappav)$, it may prove unrealistic to reconstruct the calibration lines of sight out to 5 arcminutes.
-Figure \ref{fig:radcut} shows the width of $\kapparec-\kapparay$ as a function of reconstruction radius; in almost all cases there is no significant contribution to $\kappa$ from halos that are centred more than 1 arcminute away, although large groups or clusters can sometimes still make a contribution as far out as four arcminutes.
-For the rest of this work we will continue to model all of the halos out to 5 arminutes with an $i$ magnitude greater than 26, although a reconstruction with fields going out to two arcminutes and down to $i=24$ would do almost as well.
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{figs/mag_scatter.eps}
-\caption[magcut]{The 16, 50 and 84\% confidence intervals on $\kapparec$ minus $\kapparay$ as a function of the limiting $i$ band depth of the halo reconstruction.
-$\kapparec$ is given by $\sumkappah-\kappav$, where $\kappav$ is a constant such that $\left\langle\kapparec\right\rangle=0$.
-The majority of the constraining power comes from reconstructing halos with magnitudes between $18<i<24$}
-\label{fig:magcut}
-\end{figure}
-\begin{figure}
-\includegraphics[width=\columnwidth]{figs/radius_scatter.eps}
-\caption[radius cut]{The 16, 50 and 84\% confidence intervals on $\kapparec$ minus $\kapparay$ as a function of the limiting radius (in arcminutes) beyond which halos are not reconstructed.
-The majority of the convergence comes from halos centred within an arcminute of the line of sight}
-\label{fig:radcut}
-\end{figure}
-
-The final test that we apply to the perfect knowledge reconstruction is to apply the marginalization outlined in Section \ref{subsec:voids}.
-Taking the reconstructed $\sumkappah$ for $1\times 10^{5}$ lines of sight we form the joint distribution, P$(\kapparay,\sumkappah)$ and marginalize over all sightlines with a similar $\sumkappah$ to give P($\kappax$).
-We define the bias as the difference between the expectation value of $\kappax$ and the known true value of $\kapparay$ for each Line of sight and we define the reconstruction width as half the width of the interval containing the central $68\%$ of the probability P($\kappax$).
-From $1\times 10^{4}$ reconstructed lines of sight we find the the bias to have mean of $-9.5\times 10^{-6}$ and a mean reconstruction width of 0.0132.
-In the case where one assumes P$(\kappax)$ is given by the global P$^{\rm global}(\kappax)$, the same $1\times 10^{5}$ lines of sight show a mean bias of $4.3\times 10^{-5}$ and mean reconstruction width of 0.237.
-Within the statistical error both methods are unbiased, but for any individual line of sight the bias is typically 1.8 times smaller with the reconstructed P$^{\rm reconstruction}(\kappax)$, rather than global P$^{\rm global}(\kappax)$.
+\subsection{Where does $\kappah$ come from?}
+\todo{tom}{do}
+\subsubsection{Magnitude}
+\subsubsection{Distance}
+\subsubsection{Redshift}
 
@@
 
-\section{Tests on mock catalogs}
+\section{Applying the Halo Model approximation to mock catalogs}
 \label{sec:obsMstar+z}
+\todo{tom}{redo - using new Mhalo-Mstar code}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Real attempts to reconstruct the convergence along a line of sight will not have direct access to the masses of dark matter halos, 
-and will likely not have access to their spectroscopic redshift either. Instead these properties must be inferred from astrophysical
-observables. In principle the only observables are astrometric positions, photometric colours and possibly spectra. In this section we
-quantify the errors induced by inferring the halo mass and redshift from the observables. Much work has already focused on using
-photometric colours to infer stellar mass \citep[\eg][]{xxx} and redshifts \citep[\eg][]{BPZ}, in line with these we shall use
-stellar mass and photometric redshifts (with appropriate errors), as the observables that must be converted into an estimate
-of $\kappax$. We will investigate two main sources of error: inferring halo mass given observed stellar mass and placing halos at the wrong redshift due to photometric redshift error.
+\section{Testing for Systematic errors}
+\todo{tom}{do}
+\subsection{Using the wrong M$_{\rm halo}$-M$_{*}$ relation}
+\subsection{Selecting bias from a subset of lines of sight?}
+\subsubsection{Selecting only the lines of sight with tight $\pr(\kappax)$}
+\subsubsection{Selecting only high shear lines of sight}
 
-We generate a stellar mass for each halo according to the stellar mass--halo mass relation of \citet{BehrooziEtal2010}. From this stellar mass we simulate 
-an observed stellar mass by drawing a sample from $\pr(\log(M_{* \mathrm {obs}})|\log(M_{* \mathrm {true}}))$ which is given by \comments{ the product of the galaxy stellar mass function (GSMF) of \citet{Fontana2006} and} a Gaussian of width $\sigma_{M_*}$ centred on $\log(M*_{\mathrm {true}})$.
-Where a spectroscopic redshift exists stellar masses can be estimated with typical uncertainties of 0.15 dex \citep{xxx}, however with photometric redshifts stellar mass uncertainties are typically three times as large \citep{xxx}; we use $\sigma_{M_*}=0.15$ for halos with a spectroscopic redshift and $\sigma_{M_*}=0.45$ otherwise.
-\comments{The \citet{Fontana2006} GSMF is given by a Schechter function with redshift evolving parameters
-\be
-\label{eq:GSMF}
-{\dee N \over \dee M_*} \propto \left(10^{(M_*-M_0(z))}\right)^{(1+\alpha(z))} \exp \left(-10^{(M_*-M_0(z))}\right)
-\ee 
-where $M_0(z)=11.16+0.17z-0.07z^2$ and $\alpha(z)=-1.18-0.082z$.} For photometric redshift errors we draw a redshift from $\pr(z_{\rm true}|z_{\rm obs})$ which we take as a Gaussian of width $0.1(1+z_{\rm spec})$ centred on $z_{\rm spec}$, where $z_{\rm spec}$ is the halo's true redshift in the \MS catalogue
-
-For each  source of error, we reconstruct 40000 calibration lines of sight and 10000 mock lens lines of sight, following the proceedure outlined in Section \ref{sec:model}.
-Reconstructing the lines of sight with perfect knowledge of the redshift but an uncertain stellar mass, we find that the width of $\Pr\left(\sumkappah \right)$ grows with the expectation value of $\sumkappah$; this is not surprising since the low $\sumkappah$ lines of sight are relatively empty and so there are few opportunities for uncertainties in the halo masses to propogate into $\sumkappah$ uncertainties.
-After applying the void correction the expected bias from our 10000 mock lenses is $6.7\times 10^{-5}$ and the mean reconstruction width is 0.0145; this is the typical reconstruction error that could be expected from a complete spectroscopic survey of the field, it is ten percent worse than the reconstruction given perfect knowledge of the halo masses and redshifts but still 1.6 times better than using the global P$^{\rm global}(\kappax)$ although a complete spetroscopic survey is still unrealistic.
-The distribution of the widths of $\Pr\left(\kappax \right)$ is shown in Figure \ref{fig:width1}
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{figs/cornerplot.eps}
-\caption{68 \% and 95 \% contours of the joint distribution $\pr(\kapparay, \tilde\kappa_{\rm halos})$ given a mock reconstruction of our 40000 calibration lines of sight.
-$\tilde\kappa_{\rm halos}$ is the median of $\pr(\sumkappah)$ given a spectroscopic redshift for each halo.
-$\kapparay$ and $\tilde\kappa_{\rm halos}$ are strongly correlated, despite the blurring effect of uncertain halo masses.}
-\label{fig:corner}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{figs/widths.eps}
-\caption{Widths of $\pr(\kappax)$ after applying our reconstruction of all halos down $to i=26$ and within 5 arcminutes of the line of sight.
-Results for 10000 lines of sight are shown.
-Green is for a reconstruction given perfect knowledge of halo mass and redshift, blue is for a reconstruction given a spectroscopic redshift for every halo, and red is for a reconstruction with photometric redshifts only.
-The dashed black line shows the width of the global $\pr(\kappax)$ distribution; the reconstruction process provides roughly a factor of 2 improvement for the majority of lines of sight.
-Spectroscopic redshifts improve the reconstruction, but at signifcant observational cost.}
-\label{fig:width1}
-\end{figure}
-
-Inferring the stellar mass of a galaxy from its magnitude and colours requires an estimate of how far away the galaxy is; without a spectroscopic redshift the the infered stellar mass is less precise.
-In principle the photometric redshift is correlated with the infered stellar mass, however we do not model this effect since the convergence from the outskirts of an individual halo is only weakly dependant on redshift at fixed mass: the redshift error is small effect on the recovered $\pr(\kappa)$ when compared to the effect of uncertain stellar masses.
-With only photometric redshifts the uncertainty on $\sum\kapparec^{\rm halos}$ is much larger than the spectrocopic case, but this does not propogate into a much larger bias after applying the void correction; with a purely photometric reconstruction of the 10000 mock lightcones the results have a mean bias of $1.1\times 10^{-4}$ and a mean width of 0.0158.
-On average a purely photometric reconstruction of the field gives an unbiased $\pr(\kappax)$ that is 1.5 times tighter than assuming the global $\pr^{\rm global}(\kappax)$.
-
-\subsection{Reconstructions of Smaller and Shallower Fields}
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{figs/widths2.eps}
-\caption{Widths of $\pr(\kappax)$ after a photometric reconstruction of all halos within different fields.
-The different field sizes and depths are given in the legend.
-As the field becomes smaller or shallower, fewer halos are being reconstructed and so the width of $\pr(\kappax)$ grows.}
-\label{fig:width2}
-\end{figure}
-
-Reconstructions of real lines of sight may not have access to the deep, large calibration fields that we have used upto this point.
-We can perform the same reconstruction but for a more modest mock survey.
-Given the results of Section \ref{sec:knownMh+z} we predicted that a reconstruction of the field out to 2 arcminutes and a magnitude limit of $i$=24 would provide similar constraints to a reconstruction going out to 5 arcminutes and going down to $i$=26.
-We find the mean reconstruction width to be 0.0163 for a photometric reconstruction of all the halos within 2 arcminutes that have $i<24$, this is only marginally worse than 0.0158 which was the typical width after the deeper and wider reconstruction of the previous section.
-The reconstruction widths for our 10000 mock lens lines of sight are shown in Figure \ref{fig:widths2}.
-If only photometry for halos with $i<24$ and within 1 arcminute of the line of sight is availble then the typical width of the reconstructed $\pr(\kappax)$ is 0.173.
-Whilst a complete spectroscopic survey of a large field would be unlikely, a hybrid strategy of obtaining spectra for a subset of objects may be feasible.
-Photometric redshifts are sufficient to asertain the halos which are likely to contribute most of the convergence on any given line of sight, and on average there are only $\sim 6 \pm 6$ halos per line of sight that individually contribute more than 0.002 to $\sumkappah$.
-We investigate a hybrid strategy of obtaining spectroscopic redshifts for all of the $i<24$ halos which contribute an individual $\kappa$ of at least 0.002 combined with a photometric redshift for all other $i<24$ halos within 2 arcminutes.
-For the hybrid strategy the typical width of the reconstructed $\pr(\kappax)$ is 0.0151.
-The observational cost of obtaining spectroscopic redshifts for several 24th magnitude galaxies may make the hybrid strategy unlikley, but obtaining photometry of a 4$\times$4 arcminute patch of sky down to $i=24$ is fast with modern telescopes.
-The mean reconstruction width for a photometric reconstruction of all the halos within 2 arcminutes that have $i<24$ represents an improvement of 1.5 over using the global $\pr(\kappax)$ and should be achievable at minimal observational cost.
-
-%\subsection{Reconstructing Biased Lines of Sight}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\comments{
-\section{Time Delay Distances}
-\label{sec:Dt}
-
-Folding the kappa uncertainties into time delay distance uncertainties. Toy
-model: same zl and zs, allows simple product of pdfs to obtain estimate of P(D).
-
-Make mock sample of lenses, all wit B1608 zd and zs, but with different kappas.
-Draw kappas from Stefan's *lens* distribution. Can we correct for the selection
-effect?
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Comparison with Other Treatments of $\kappax$}
-\label{sec:Dt:selection}
-
-\phil{How does distance accuracy compare with simple averaging? eg assuming
-$\kappax = 0$ for all lenses. How does it compare with the no data situation?
-eg where the intrinsic distribution of kappa is used as $Pr(\kappax)$.}
-
-What is the expected bias and scatter (centroid position and width) of P(D) as a
-function of N lenses? How does reconstruction compare with P(D) derived using
-P(kappa|N45) for each lightcone? How does reconstruction compare with P(D)
-derived assuming kappa=0 for each lightcone?
-
-Also: compare with simple averaging. This will fail if lenses are selected to
-live on over-dense lines of sight. Stefan's plot in Suyu et al shows effect of
-selection - what is the resulting bias? Few percent? This is the target to beat,
-need to find it out.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{The Impact of Selection Effects}
-\label{sec:Dt:selection}
-
-\phil{How does distance accuracy vary with:}
-\begin{itemize}
-\item Depth of catalog? mlim = 22, 24, 26?
-\item Overdensity cuts? Remove underdense fields, overdense fields (from
-reconstructed kappa)
-\item Shear-sensitive selection? What if we only selected quads?
-\end{itemize}
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Improving the Accuracy with More Information}
-\label{sec:Dt:selection}
-
-\phil{How does distance accuracy improve with:}
-\begin{itemize}
-\item Spectroscopic coverage? For galaxies above some mlim? For targets with
-high kappa contribution (based on photometry)?
-\item IR coverage for all objects? Improves photo-z and Mstar.
-\item Including shear information from lens model? Assume accurate but
-uncertain extertanl shear.
-\end{itemize}
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \begin{figure}
-% \centering\includegraphics[width=0.99\linewidth]{figs/something.png}
-% \caption{An example figure.}
-% \label{fig:sizemass}
-% \end{figure}
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We have shown that reconstructing the matter due to halos along any line of sight can give meaningful and unbiased constraints on the external convergence along that line of sight.
-The total convergence along a line of sight is strongly correlated with the reconstructed $\sumkappah$.
-However since our model ignores voids and assumes all halos follow a spherical truncated-NFW profile our model does not include all of the relevant physics, hence the width of our resulting $\pr(\kappax)$ is still typically $\sim$0.01, even with a perfect knowledge of every halo's virial mass and redshift.
-To make further progress a more advanced treatment of both voids and halos will be necessary.
-Interestingly, we have found that the most empty lines of sight can be reconstructed with the most precision.
-$\kappax$ for empty lines of sight have little contributions from halos and a large contribution from voids; since they have the tightest PDFs after the reconstruction it seems that our model's biggest uncertainties are driven by naively reconstructing halos rather than neglecting voids.
-With a photometric reconstruction of the field there is only a small broadening compared to the perfect knowledge reconstruction; it seems that deviations from sphericity and dark matter clumping within the main halo are the dominant uncertainies rather than uncertainties in the halo mass.
-Inferring halo ellipticity and dark matter clumping will likely always remain a difficulty for line of sight reconstruction; as Figures \ref{fig:magcut} and \ref{fig:width2} show observing deeper than 24th magnitude does not signifcantly help the reconstruction.
-Because our reconstruction is mostly limited by the model, spectroscopic coverage can only provide a modest improvement to the reconstruction and at significant observational cost.
-
-For a small fraction of lines of sight, $\pr(\kappax)$ remains very broad even after applying our reconstruction; these lines of sight are typically the most overdense lines of sight in the universe.
-For time-delay cosmography the most observationally expensive task is the lightcurve monitoring, whilst making photometric observations of a 4$\times$4 arcminute patch of sky survey down to 24th magnitude is a relatively cheap.
-We have shown that with a single epoch observation of the region around a strong lens it is possible to infer $\pr(\kappax)$.
-If a line of sight has a broad $\pr(\kappax)$ it can be rejected {\it before} the investment of longterm lightcurve monitoring.
-
-The method we have outlined can also be used to estimate the external shear
-along a line of sight. Shear is an observable that can be extracted from
-strong lens modelling, however there is a degeneracy between internal and
-external shear. Progress has been made in disentangelling external and
-internal shear \citep[\eg][]{xxx} but there are still significant
-uncertainties: \citet{WongEtal2011} attempted to match the shear from strong
-lens models with a reconstruction of the local lens group environment, but
-found a tension between the strong lens model and the reconstruction of the
-environment. Since \citet{WongEtal2011} only reconstructed the local lens
-group, rather than the full line of sight contribution, it is unclear whether
-the external shear from lens models can be reconciled with a line of sight
-reconstruction. {\it If} external shear can be measured, it provides an
-additional constraint on which of the Millenium Simulation lines of sight are
-similar to the reconstructed line of sight. \citet{SuyuEtal2012} found that
-for RXJ1131 combining shear constriants with galaxy number count overdensity,
-gave a significantly different $\pr(\kappax|\gamma,N_{45})$ copmpared to the
-PDFfrom number count overdensity alone, $\pr(\kappax|N_{45})$.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:conclude}
-
-In this work we have investigated a simple halo model prescription for
-reconstructing all the mass along a line of sight to an intermediate redshift
-source. We have used the ray-traced lensing convergence along lines of sight
-through the Millenium Simulation to test this approach, and to calibrate
-estimates of the total convergence along a line of sight to an observed
-distant galaxy made by summing the convergences due to each object in a
-photometric catalogue. Having found that the reconstruction process is effective given perfect
-knowledge of halo mass and redshift, we investigated the effects of reasonable
-uncertainties in the stellar mass and redshift of each halo, and propogated
-these uncertainties into a $\pr\left(\sumkappah\right)$ for each line of
-sight. We draw the following conclusions:
-
-\begin{itemize}
-
-\item Our model uses a truncated spherical NFW profile for
-each dark matter halo and neglects voids, but despite the model's simplicity
-the reconstructed $\sumkappah$ is a good tracer of $\kappax$.  We found that
-with perfect knowledge of the halo mass and redshift (from the Millenium
-Simulation catalogs), the reconstruction gives an unbiased estimate of
-$\pr(\kappax)$ for a single line of sight that is almost almost a factor of 2
-less broad than the global $\pr(\kappax)$.
-
-\item  For the most overdense lines of sight, the reconstruction produces a
-very broad PDF, but since the reconstruction can be performed before follow-up
-time is invested it will be possible to discard the most uncertain lines of
-sight and prevent the waste of follow-up time.
-
-\item With complete spectroscopic redshift coverage and just an empirical
-stellar mass to halo mass relation, we find that the median of
-$\pr\left(\sumkappah\right)$ is a useful indicator for generating an estimate
-of $\pr(\kappax)$ from the ensemble of simulated lines of sight. The resulting
-PDF tends to be around 10\% broader than it would have been given perfect
-knowledge of both halo mass and redshift; given only photometric redshifts
-(which in turn give rise to much less certain stellar masss estimates) causes
-another $\sim$10\% increase to the width of $\pr(\kappax)$.
-
-\item It is very rare for halos further than 2 arcminutes to make a
-significant contribution to $\kappax$. We also found that including halos
-whose host galaxy is less luminous than $i=24$ does not significantly improve
-our reconstruction proceedure. A photometric survey to this depth of a
-4$\times$4 arcminute patch around the lens would approach the limiting
-uncertainties of our simple reconstruction recipe, and yield a 
-$\pr(\kappax)$ that has, on average, a width of 0.0163 --
-50\% less broad than the global $\pr(\kappax)$.
-
-\item We find that the lines of sight with the sharpest $\pr(\kappax)$ are
-typically under-dense. With a photometric reconstruction of all lens fields,
-and following up only the lenses with the most constraining $\pr(\kappax)$,
-the width of the dominant statistical uncertainty in time-delay cosmography
-can be halved, whilst at the same time decreasing any potentail for a
-systematic error due to lenses being biased in $\kappax$.
-
-\end{itemize}
-
-\todo{Tom}{Add more conclusions about bias in a large sample of lenses...}
-
-\todo{Tom}{Wrap up}
-
-%Our conclusions can be summarised as follows:
-%\begin{itemize}
-%\item With perfect 
-%\item And we found this too.
-%\end{itemize}
-
-% \item Faint galaxies and other dark structures will not appear in a photometric
-% object catalog, but they will contribute convergence at some level. How much of
-% the total external convergence in a time delay lens system comes from visible
-% galaxies? How does this change as a function of magnitude cut?
-
-% \item Can the true (ray-traced) convergence be recovered by halo model
-% reconstruction, and with what scatter and residual bias? Which aspects of the 
-% model dominate these uncertainties?
-
-% \item When faced with a newly-detected lens, surrounded by galaxies on the sky,
-% we have some choices to make when planning follow-up observations.
-% Which are the most important galaxies, with regard to the external convergence
-% produced? Can nearby groups and clusters be straightforwardly accounted for? If
-% lenses with such massive structures nearby are discarded, what impact does that
-% have on the distance accuracy?
 
@@
 
-\section{Truncated NFW halos}
-\label{appendix:halos}
-
- Defining $x$ as the dimensionless projected radial distance $R/r_{s}$ and $\tau$ as the dimensionless truncation radius $r_{t}/r_{s}$, \citet{BMO} derives the projected mass density, which is given by:
-\begin{align}\label{eq:kappaBMO}
-\Sigma_{\rm}(x) = {2\tau^2 \over (\tau^2+1)^2}\left(
-        {\tau^2+1\over x^2-1}\left(1-\mathcal{F}(x)\right)
-        +
-        2\mathcal{F}(x)\right.\nonumber\\
-        -
-        \left. {\pi \over \sqrt{\tau^2+x^2}}
-        +
-        {(\tau^2-1)\mathcal{L}(x,\tau)
-        \over
-        \tau\sqrt{\tau^2+x^2}}\right)
-\end{align}
-where $\mathcal{F}(x)$ and $\mathcal{L}(x,\tau)$ are defined as
-\be\label{eq:F} 
-\mathcal{F}(x) \equiv \begin{cases}  \frac{{\rm cos}^{-1} (1/x)}{\sqrt{x^2-1}} \hspace{0.2cm} & (x>1) \\
-\\
-\frac{4-x^2}{3}  & (x=1)\\
-\\
-\frac{ {\rm cosh}^{-1} (1/x)}{\sqrt{1-x^2}} & (x<1)
-\end{cases}
-\ee
-\be\label{eq:L}
-\mathcal{L}(x,\tau) = \ln\left(\frac{x}{\sqrt{\tau^2+x^2}+\tau}\right)
-\ee
-%the convergence is given by $\Sigma_{\rm BMO}(x) / \Sigma_{\rm cr}(z)$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Inferring $\Mhalo$ given a noisy measurement of $\Mstarobs$}
@@
 
-Given a noisy estimate of the stellar mass $\Mstarobs$ of a galaxy at redshift
-$z$, how can we infer the galaxy's halo mass? We then seek the posterior
-PDF $\Pr(\Mhalo|\Mstarobs)$, which can be expanded as follows:
-
-\begin{eqnarray}
-&& \Pr(\Mhalo|\Mstarobs,z) = \notag\\
-&& \int d\Mstar \Pr(\Mhalo|\Mstar,z) \Pr(\Mstar|\Mstarobs,z), \notag\\
-&\propto& \int d\Mstar \Pr(\Mstarobs|\Mstar) \Pr(\Mstar|\Mhalo,z) \Pr(\Mhalo|z),
-\label{eq:mhalo-mstar}
-\end{eqnarray}
-where we have used Bayes' Theorem twice to replace
-$\Pr(\Mhalo|\Mstar,z) \Pr(\Mstar|z)$ with 
-$\Pr(\Mstar|\Mhalo,z) \Pr(\Mhalo|z)$, and 
-to invert $\Pr(\Mstar|\Mstarobs)$ into the sampling
-distribution $\Pr(\Mstar|\Mstarobs)$, which we recognise as the likelihood
-function for the observed stellar mass. Note that the ``true'' $\Mstar$ of the
-galaxy is marginalised out: we are only interested in reconstructing the halo
-mass. The last two terms in
-\eqref{eq:mhalo-mstar} are the $\Mstar-\Mhalo$ relation from
-\citet{BehrooziEtal2010}, and the halo mass function $\Pr(\Mhalo|z)$, at the
-given redshift. We can
-tabulate the product of these two from our Millenium Simulation catalog,
-constructing a two-dimensional histogram of halo masses and their associated
-true stellar masses (drawn from the Behroozi relation).
-
-For each galaxy, we compute the likelihood function for its $\Mstarobs$ as a
-function of the unknown $\Mstar$, and multiply it by our tabulated joint PDF.
-This heavily downweights halos with $\Mstar$ values outside the observed
-range. We then do the marginalisation integral by Monte Carlo, drawing
-(two-dimensional) sample parameter vectors
-from the downweighted histogram, discarding the $\Mstar$ values, and
-constructing a one-dimensional histogram that is an estimate of
-$\Pr(\Mhalo|\Mstarobs)$.
-
-If the redshift of the galaxy is uncertain, we need to take this uncertainty
-into account; for example, for each sample drawn from the photometric redshift
-posterior PDF $\Pr(z|{\rm colors})$, we can draw a sample $\Mhalo$ using the
-above procedure.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\section{Smooth component models}
-%\label{appendix:smooth}
+\todo{Phil}{Check that what's written is correct}
 

### 2012-10-15 doc/paper-lcr.tex
added framework

@@
 
-\section{Halo Model and Mass distribution}
+\section{Estimating external convergence: The halo model approximation}
 \label{sec:model}
@@
 
-% PJM: What is this defeatism?!
-% it is nearly impossible to know the true $\kappax$ for a
-% line of sight, and without a knowledge of $\kappax^{\mathrm{true}}$ it is hard to
-% quantify if there is a bias induced by using different $\kappax$ estimators.
-%
 % A source with known unlensed brightness e.g. a strongly lensed type Ia
@@
 
+\subsection{Ray-tracing through simulated Lines of Sight}
+\label{subsec:raytracing}
 Cosmological dark matter simulations can be used to generate mock lines of
 sight and can be raytraced through to give each mock sightline a $\kappax$ value...
-\todo{Stefan}{Write section on how the ray tracing was done and how halos are extracted from
- the MS n-body particles}
+\todo{Stefan}{Write section on how the ray tracing was done}
+
+\subsection{Generating mock lightcones from simulations}
+
+\todo{Stefan}{Write section on how halos are extracted from the MS n-body particles}
 
@@
 reconstruction of the convergence induced by every halo near a line of sight.
-This is the subject of the first subsection below. We also need to account for
+This is the subject of \ref{subsec:halos}. We also need to account for
 the mass in the Universe that is not associated with the galaxies we can see
--- this is the subject of the second subsection below.
+-- this is the subject of \ref{subsec:voids}.
 
@@
 \subsection{Halos}
+\label{subsec:halos}
 
@@
 
-\section{Tests with known halo mass and redshift}
+\section{Testing the halo model approximation with known halo mass and redshift}
 \label{sec:knownMh+z}
+
+\subsection{How does $\kappah$ relate to $\kappax$?}
+
+\subsection{Does converting from $\kappah$ to $\kappax$ work?}
+
+\subsection{Where does $\kappah$ come from?}
+\subsubsection{Magnitude}
+\subsubsection{Distance}
+\subsubsection{Redshift}
 
@@
 
-\section{Tests on mock catalogs}
+\section{Applying the Halo Model approximation to mock catalogs}
 \label{sec:obsMstar+z}
@@
 
-\subsection{Reconstructions of Smaller and Shallower Fields}
+%\subsection{Reconstructions of Smaller and Shallower Fields}
 
@@
 
-%\subsection{Reconstructing Biased Lines of Sight}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Testing for Systematic errors}
+\subsection{Using the wrong M$_{\rm halo}$-M$_{*}$ relation}
+\subsection{Selecting bias from a subset of lines of sight?}
+\subsubsection{Selecting only the lines of sight with tight $\pr(\kappax)$}
+\subsubsection{Selecting only high shear lines of sight}
 
@@
 \comments{
-\section{Time Delay Distances}
-\label{sec:Dt}
-
-Folding the kappa uncertainties into time delay distance uncertainties. Toy
-model: same zl and zs, allows simple product of pdfs to obtain estimate of P(D).
-
-Make mock sample of lenses, all wit B1608 zd and zs, but with different kappas.
-Draw kappas from Stefan's *lens* distribution. Can we correct for the selection
-effect?
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 
@@
 need to find it out.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{The Impact of Selection Effects}
-\label{sec:Dt:selection}
-
-\phil{How does distance accuracy vary with:}
-\begin{itemize}
-\item Depth of catalog? mlim = 22, 24, 26?
-\item Overdensity cuts? Remove underdense fields, overdense fields (from
-reconstructed kappa)
-\item Shear-sensitive selection? What if we only selected quads?
-\end{itemize}
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 
@@
 \end{itemize}
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \begin{figure}
-% \centering\includegraphics[width=0.99\linewidth]{figs/something.png}
-% \caption{An example figure.}
-% \label{fig:sizemass}
-% \end{figure}
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 }

### 2012-10-15 doc/framework.tex
fleshed out framework

@@
 \todo{Phil,(+ Tom)}{Update introduction to reflect the scope of this paper}
+
+Every distant object we observe has had its shape distorted, and size
+and total brightness magnified (or demagnified) by a compound lens constructed
+from all the mass distributed between us and it. As \citet{valewhite2003} and \citet{hilbert}
+showed, there are no empty lightcones in our universe. This fact makes gravitational lensing a potentially important source of systematic error for any estimate of luminosity or distance.
+
+\citet{suyu} found that in time delay lens cosmography the
+lensing effect of mass structures along the (unusually over-dense) line of
+sight to the quadruply-imaged radio source B1608$+$656, the so-called ``external
+convergence'' $\kappax$, was the dominant source of uncertainty in the inferred
+cosmological parameters. The problem is that one simply doesn't know
+how magnified and distorted the source has been because the unlensed source is unobservable.
+The external shear can potentially be recovered in the mass-modelling of the lens, but the convergence is undetectable from the image positions, shapes and relative fluxes; this is the famous {\emph{  mass sheet-degeneracy}} \citep[see e.g.][for details]{falco}.
+
+\notes{Previous work, what we are doing, why it will help}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:theory}
-\todo{Phil,(+ Tom)}{Modify the current theory section, emphasiszing how $\kappax$ effects inferred parameters.
-Justify how we combine individual $\kappa$s to give a total $kappah$ - note that this is the weak lensing limit.}
+\todo{Phil,(+ Tom)}{Modify the current theory section}
+
+\notes{what is $\kappa$ from a single object, how does it combine given lots of objects along the line of sight, why kappa can't be extracted - mass sheet degeneracy, how $\kappa$ effects inferred parameters}
 
@@
 \label{sec:model}
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
+\notes{given perfect knowledge of the density near a line of sight it is possible to raytrace, but this can't be done for a real line of sight, since the mass distribution isn't known.
+Galaxies are known due to their light.
+Need to infer z and $\Mstar$ and turn these into $\Mh$ which can be used to infer $\kappah$ for each halo.
+Will never know voids, filaments or other dark structures, so a calibration is needed to convert $\kappah$ into $\kappa$}
+
+\subsection{Halos}
+\label{subsec:halos}
+\todo{Tom,Phil}{Check}
+
+\notes{halo profile; justfication, choice of truncation. Infer concentration from halo mass using a relation.}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Correcting for voids, filaments and dark structures}
+\label{subsec:voids}
+
+\notes{Outline EXPLICITLY the proceedure we use to correct for voids etc}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Using the Millenium Simulation to test the halo model approximation with known halo mass and redshift}
+\label{sec:knownMh+z}
+
+In order to justify the reconstruction proceedure outlined in Section \ref{sec:model}, we would like to apply it to lines of sight with known $\kappa$.\notes{can't use real los, have to use \MS}
 
@@
 
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\notes{view of a lightcone figure should go at the end of this section}
+\subsection{How does $\kappah$ relate to $\kappa$?}
+Given the halo mass catalogue from the Millenium Simulation, 
+and convergence maps produced by ray-tracing through the MS's n-body particles, 
+it is possible to test the validity of the prescription outlined
+ in Section \ref{sec:model}. We test the model by comparing $\kappah$ against
+ the ray-traced $\kappa$. If the reconstruction process is to be
+ succesfull the two quantities should be closely related, although we expect $\kappah$ to be offset from $\kappa$ since the former does not include the divergence due to voids.
 
-\subsection{Halos}
-\label{subsec:halos}
-\todo{Tom,Phil}{Check}
+\subsubsection{How does $\gammah$ relate to $\gamma$?}
 
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{How succesful is the calibration at converting $\kappah$ into $\kappa$?}
 
-\subsection{Calibration: Recovering the global $\pr(\kappax)$ using a void correction}
-\label{subsec:voids}
-
-\todo{tom}{Outline _EXPLICITLY_ the proceedure we use to correct for voids etc}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Testing the halo model approximation with known halo mass and redshift}
-\label{sec:knownMh+z}
-
-\subsection{How does $\kappah$ relate to $\kappax$?}
-Done?
-\subsubsection{How does $\gammah$ relate to $\gammax$?}
-\todo{tom}{do}
-\subsection{Does converting from $\kappah$ to $\kappax$ work?}
-\todo{tom}{do}
-
-\subsection{Where does $\kappah$ come from?}
-\todo{tom}{do}
+\subsection{Which halos dominate the $\kappah$ distribution?}
 \subsubsection{Magnitude}
@@
 \todo{tom}{redo - using new Mhalo-Mstar code}
+
+\subsubsection{Reconstructing $\kappa$ given a spectroscopic redshift for every object}
+
+\subsubsection{Reconstructing $\kappa$ from photometry alone}
+
+\subsubsection{Reconstructing $\kappa$ with a }
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Improving precision by including additional information}
+\notes{placeholder for shear}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2012-10-18 doc/framework.tex
added new figures

@@
 
+\begin{figure}
+\includegraphics[width=\columnwidth]{figs/view_of_a_lightcone.eps}
+\caption[magcut]{View of a lightcone}
+\label{fig:lightcone}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
 \notes{given perfect knowledge of the density near a line of sight it is possible to raytrace, but this can't be done for a real line of sight, since the mass distribution isn't known.
@@
 Will never know voids, filaments or other dark structures, so a calibration is needed to convert $\kappah$ into $\kappa$}
+
+For real lines of sight, we would like to estimate the external convergence as best we can given all
+data available. Typically this data is in the form of a photometric galaxy
+catalog, containing positions, brightnesses, colours, and possibly spectra for each galaxy in the
+field of the lens, down to some magnitude
+limit. Since we can not observe the surface mass density of each halo
+directy, we need some way of estimating
+the mass of each halo in the catalog, so that we can compute its
+contribution to the total $\kappax$ along the line of sight. This mass assignment recipe will be uncertain, but
+can be calibrated with cosmological simulations.
+
+Transforming the photometometric galaxy catalogue into a  catalogue of
+halo masses, positions, and redshifts, will enable us to attempt a
+reconstruction of the convergence induced by every halo near a line of sight.
+This is the subject of Section \ref{subsec:halos}. We also need to account for
+the mass in the Universe that is not associated with the galaxies we can see
+-- this is the subject of Section \ref{subsec:voids}.
 
@@
 \notes{halo profile; justfication, choice of truncation. Infer concentration from halo mass using a relation.}
+Cosmological dark matter simulations have shown that dark matter
+halos are well approximated by NFW profiles \citep{NFW}, with a density
+profile given by
+\be\label{eq:rhonfw}
+\rho(r) = 
+\frac{\rho_0}{\left(r/r_{s}\right)
+\left(1+r/r_{s}\right)^{2}},
+\ee
+where $r_{s}$ is a characteristic radius of the cluster, representing where
+the density slope transitions from $r^{-1}$ to $r^{-3}$. This radius is related
+to the virial radius of the halo by $r_{s}~=~r_{200}/c$, where $r_{200}$ is the radius at 
+which 
+\be
+\rho(r_{200}) = 200\rho_{{\mathrm{crit}}}(z), \text{ where } \rho_{\mathrm{crit}}(z) \equiv \frac{3H^{2}(z)}{8\pi G}
+\ee
+and $c$ is the concentration parameter, which can be estimated from the halo's mass,
+using a mass--concentration relation. Typically more massive halos are less concentrated,
+but there is some scatter; we use the relation of \citet{Neto2007} to estimate $c$
+from the mass enclosed within $r_{200}$, which we denote as $M_{200}$.
+We find our results do not change if the \citet{Macchio} Mass--concencetration relation is used instead.
+The best fit relation of \citet{Neto2007} is given by
+\be
+c_{200} = 4.67 (M_{200}/10^{14} h^{-1} \Msun)^{-0.11}.
+\ee
+$\rho_0$ is calculated from the critical density and concentration parameter:
+\be
+\rho_0 = \rho_{\mathrm{crit}}(z)\frac{200}{3}\frac{c^{3}}{\ln(1+c)-c/(1+c)}.
+\ee
+
+Unphysically, if one integrates the density profile of an NFW profile, the total mass is divergent.
+Similarly, if the universe is homogeneously populated with NFW halos, the projected surface mass along any
+line of sight will also be divergant\footnote{At large radius, $\Sigma_{\rm
+nfw} \propto R^{-2}$, but the differential number of halos centred within an
+annulus of width $\dee R$ is given by $\dee N_{\rm annulus} \propto R \dee R$,
+so  $\Sigma_{\rm total} \propto \int_{0}^{\infty} R^{-1} \dee R$, which
+diverges logarithmically}. Since infinite mass is unphysical, the profile must
+be truncated at some point.
+Several truncation profiles have been suggested \citep[e.g][]{BMO}, but beyond several virial radii, the amount of matter associated with a halo is likely to be low.
+In this work we assume the truncated NFW profile of \citet{BMO}
+\be\label{eq:bmoprofile}
+\rho(r) = 
+\frac{\rho_{\rm NFW} (r)}{1+\left(r/r_{t}\right)^2},
+\ee
+which is the same as the NFW profile in the limit that the truncation radius, $r_t$ goes to infinity.
+We use a truncation radius of five times the virial radius, but our results are robust for any choice of $r_t>2 \times r_{200}$.
+
+The convergence and shear for the BMO profile are given in Appendix \ref{appendix:halos}.
 
@@
 \label{subsec:voids}
+
+Whilst halos contribute a positive convergence to $\kappa$, voids contribute
+a negative convergence. When a raybundle passes through a  region of space
+that is less dense than $\rho_{\rm cr}(z)$ the rays are de-focused\footnote{In
+principle, the convergence caused by halos, is also caused by the overdensity,
+but we neglect this effect since halos are typically much more dense than the
+intergalactic medium}. Whilst the  full raytraced solution takes into account
+the effect of voids, our reconstruction cannot -- the halo catalogue does not
+include voids. In principle the absence of a halo could be taken to infer a
+void, but the under-density of such a void is hard to infer. Neglecting voids
+would lead to a heavily biased estimate of $\kappa$. We account for the voids
+statistically; we reconstruct
+the $\kappa$ contribution of halos for an ensemble of calibration sightlines
+and form the joint distribution P($\kappa,\kappah$). The calibration
+can then be accounted for by marginalizing over all lines of sight with a similar
+ $\kappah$.  We will refer to this calibration proceedure as the "void correction",
+although it also accounts for all of the physics that our simple spherical halo prescription
+neglects in a statistical manner. For each line of sight we create a $\pr(\kappa)$ from
+\be
+\label{eq:voidcorrection}
+\pr(\kappax)=\int_{-\infty}^{+\infty}\pr(\kapparay',\tilde\kappa'_{\rm h})W(\kappah)\dee \tilde\kappa'_{\rm h}
+\ee
+where $\tilde{\kappah}$ is the median of the reconstructed $\kappah$ for each line of sight and $W(\kappah)$ is the reconstructed PDF for $\kappah$ where the $\kappah$ is recreated using a uniform prior.
+Primed qunatities refer to all of the calibration sightlines and unprimed refers to the specific line of sight. Equation \ref{eq:voidcorrection} is the same as 
+\be
+\label{eq:voidcorrection2}
+\pr(\kappax)=\int_{-\infty}^{+\infty}\pr(\kapparay'|\tilde\kappa'_{\rm h})\pr(\kappah)\dee \tilde\kappa'_{\rm h}
+\ee
+but with $\pr(\kappah)$ created with the global $\kappah$ distribution as a prior on $\kappah$.
 
@@
 \subsection{How does $\kappah$ relate to $\kappa$?}
+
 Given the halo mass catalogue from the Millenium Simulation, 
@@
 it is possible to test the validity of the prescription outlined
- in Section \ref{sec:model}. We test the model by comparing $\kappah$ against
+in Section \ref{sec:model}. In this section we test reconstruction prescription given perfect
+knowledge of the halos' virial masses and redshifts; this provides us with a measure of the intrinsic
+errors induced by treating matter as truncated NFW halos. 
+We test the model by comparing $\kappah$ against
 the ray-traced $\kappa$. If the reconstruction process is to be
- succesfull the two quantities should be closely related, although we expect $\kappah$ to be offset from $\kappa$ since the former does not include the divergence due to voids.
+succesfull the two quantities should be closely related, although
+we expect $\kappah$ to be offset from $\kappa$ since the former 
+does not include the divergence due to voids.
+Figure \ref{fig:isitbiased} shows that indeed $\kappah$ is a good estimator, regardless of the individual value of $\kappah$.
+At fixed $\kappah$ we find that the scatter in $\kapparay$ grows with $\kappah$; our reconstruction is better at reproducing underdense lines of sight than overdense lines of sight.
 
-\subsubsection{How does $\gammah$ relate to $\gamma$?}
+\begin{figure}
+\includegraphics[width=\columnwidth]{figs/cornerplot.eps}
+\caption[Biased?]{$\kappah$ verses $\kappa$ for 100000 reconstructed lines of sight.
+$\kappah$ traces $\kappa$, but with a non-zero offset which is due to the negative convergence from voids.
+At fixed $\kappah$ the scatter in $\kappa$ grows with $\kappah$.}
+\label{fig:isitbiased}
+\end{figure}
+
+%\subsubsection{How does $\gammah$ relate to $\gamma$?}
 
@@
 
+\begin{figure}
+\includegraphics[width=\columnwidth]{figs/globaldist.eps}
+\caption[magcut]{Do we recover the global distribution?}
+\label{fig:globaldist}
+\end{figure}
+
+Since voids are not included in the halo model approximation $\kappah$ is a biased estimator of $\kappa$, but this can be calibrated for useing the proceedure of Section \ref{sec:voids}.
+Taking the reconstructed $\sumkappah$ for $1\times 10^{5}$ lines of sight we form the joint distribution, P$(\kapparay,\kappah)$ and marginalize over P$(\kappah)$ to give P($\kappax$).
+We define the bias as the difference between the expectation value of $\kappax$ and the known true value of $\kapparay$ for each Line of sight and we define the reconstruction width, $\sigma_{\kappa}$,as half the width of the interval containing the central $68\%$ of the probability P($\kappax$).
+From $1\times 10^{4}$ reconstructed lines of sight we find the the bias to have mean of $-9.5\times 10^{-6}$ and a mean reconstruction width of 0.0132 which is roughly 1.8 times smaller than the width of the global P$(\kappax)$.
+We find that our $\kappa$ distributions are consistent with the global $\kappa$ distribution; Figure \ref{fig:globaldist} shows that the renormalized sum of $\pr(\kappa)$ from 10000 lines of sight is very similar to the global $\pr(\kappa)$.
+
 \subsection{Which halos dominate the $\kappah$ distribution?}
-\subsubsection{Magnitude}
-\subsubsection{Distance}
-\subsubsection{Redshift}
+
+Before investigating the errors caused by imperfect knowledge of halo mass and redshift, we investigate the errors induced by a magnitude limited reconstruction and a field of view limited reconstruction.
+The halos in our catalogue are given magnitudes by the semi-analytic model of \citet{deLucia+Blaizot2007} and by applying magnitude cuts to our catalogue, we can investigate the scatter caused by unobserved halos.
+The majority of the convergence comes from halos with an $i$ magnitude between 18 and 24.
+Figure \ref{fig:where} shows the cumulative contribution to $\kappah$ as a function of projected distance from the line of sight, magnitude and redshift.
+Unsurprisingly we find that most of the convergence comes from halos whose galaxies are close to the line of sight.
+As a function of magnitude, we find that $\kappah$ is dominated by objects with magnitudes between $i=18$ and $i=24$.
+Objects brighter than $i=18$ are either too rare or too close to the observer to make a significant contribution to the convergence.
+Objects fainter than $i=24$ are too small to be important, unless they are extremely close to the line of sight, but we find that including including halos fainter than $i=24$ does not improve our reconstruction.
+Figure \ref{fig:magcut} shows the scatter on $\kappah-\kappa$ (where $\kappah$ is shifted so that it's mean is zero) as a function of reconstruction magnitude limit.
+Since these objects must be extremely close to the line of sight to make a non-zero $\kappah$ contribution it is likely that neglecting stellar mass and using a spherical NFW prescription are too naive to adequately reconstruct $\kappax$; thus we do not expect a deeper survey to decrease the size of the uncertainty in mapping $\kappah$ onto $\kappa$.
+We find that halosat all redshifts contribute to the convergence, but halos half way between observer and source tend to have the largest individual contributions.
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{figs/where_is_the_kappa.eps}
+\caption[magcut]{Which objects dominate kappa?}
+\label{fig:where}
+\end{figure*}
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{figs/mag_scatter.eps}
+\caption[magcut]{The 16, 50 and 84\% confidence intervals on $\kapparec$ minus $\kapparay$ as a function of the limiting $i$ band depth of the halo reconstruction.
+$\kapparec$ is given by $\sumkappah-\kappav$, where $\kappav$ is a constant such that $\left\langle\kapparec\right\rangle=0$.
+The majority of the constraining power comes from reconstructing halos with magnitudes between $18<i<24$}
+\label{fig:magcut}
+\end{figure}
+
+%\subsubsection{Magnitude}
+%\subsubsection{Distance}
+%\subsubsection{Redshift}
 
@@
 \label{sec:obsMstar+z}
-\todo{tom}{redo - using new Mhalo-Mstar code}
 
-\subsubsection{Reconstructing $\kappa$ given a spectroscopic redshift for every object}
+Real attempts to reconstruct the convergence along a line of sight will not have direct access to the masses of dark matter halos, 
+and will likely not have access to their spectroscopic redshift either. Instead these properties must be inferred from astrophysical
+observables. In principle the only observables are astrometric positions, photometric colours and possibly spectra. In this section we
+quantify the errors induced by inferring the halo mass and redshift from the observables. Much work has already focused on using
+photometric colours to infer stellar mass \citep[\eg][]{xxx} and redshifts \citep[\eg][]{BPZ}, in line with these we shall use
+stellar mass and photometric redshifts (with appropriate errors), as the observables that must be converted into an estimate
+of $\kappax$. We will investigate two main sources of error: inferring halo mass given observed stellar mass and placing halos at the wrong redshift due to photometric redshift error.
 
-\subsubsection{Reconstructing $\kappa$ from photometry alone}
+We generate a stellar mass for each halo according to the stellar mass--halo mass relation of \citet{BehrooziEtal2010}. From this stellar mass we simulate 
+an observed stellar mass by drawing a sample from $\pr(\log(M_{* \mathrm {obs}})|\log(M_{* \mathrm {true}}))$ which is given by a Gaussian of width $\sigma_{M_*}$ centred on $\log(M*_{\mathrm {true}})$.
+Where a spectroscopic redshift exists stellar masses can be estimated with typical uncertainties of 0.15 dex \citep{xxx}, however with photometric redshifts stellar mass uncertainties are typically three times as large \citep{xxx}; we use $\sigma_{M_*}=0.15$ for halos with a spectroscopic redshift and $\sigma_{M_*}=0.45$ otherwise.
+For photometric redshift errors we draw a redshift from $\pr(z_{\rm true}|z_{\rm obs})$ which we take as a Gaussian of width $0.1(1+z_{\rm spec})$ centred on $z_{\rm spec}$, where $z_{\rm spec}$ is the halo's true redshift in the \MS catalogue.
 
-\subsubsection{Reconstructing $\kappa$ with a }
+Given an uncertain stellar mass and redshift it is possible to infer a halo mass using the stellar mass--halo mass relation of \citet{BehrooziEtal2010}.
+This proceedure requires an inversion of the relation given in \citet{BehrooziEtal2010} and correctly inverting the relation's uncertainties requires care: the proceedure we use to do this is given in Appendix \ref{appendix:MSMH}.
+By drawing sample halo masses and redshifts, we can infer a sample $\kappah$ using the proceedure of Section \ref{model}; repeatedly drawing samples allows us to estimate P$(\kappah)$ for each reconstructed line of sight.
+
+\subsection{Reconstructing $\kappa$ given a spectroscopic redshift for every object}
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{figs/Widthsvshilbert.eps}
+\caption[magcut]{Could this be any uglier?}
+\label{fig:reconidths}
+\end{figure}
+
+The best possible reconstruction of $\kappah$ corresponds to having a sepctroscopic redshift for every single object in our field.
+Observationally such a reconstruction would be prohibitively expensive in terms of telescope time, but we investigate this scenario as an ideal case.
+Reconstructing the lines of sight with perfect knowledge of the redshift but an uncertain stellar mass, we find that the width of $\Pr\left(\sumkappah \right)$ grows with the expectation value of $\sumkappah$; this is not surprising since the low $\sumkappah$ lines of sight are relatively empty and so there are few opportunities for uncertainties in the halo masses to propogate into $\sumkappah$ uncertainties.
+After applying the void correction the median reconstruction width is 0.0123; with 22 percent of lines of sight having a reconstruction width less than 0.01.
+
+\subsection{Reconstructing $\kappa$ from photometry alone}
+
+Inferring the stellar mass of a galaxy from its magnitude and colours requires an estimate of how far away the galaxy is; without a spectroscopic redshift the the infered stellar mass is less precise.
+In principle the photometric redshift is correlated with the infered stellar mass, however we do not model this effect since the convergence from the outskirts of an individual halo is only weakly dependant on redshift at fixed mass: the redshift error is small effect on the recovered $\pr(\kappa)$ when compared to the effect of uncertain stellar masses.
+With only photometric redshifts the uncertainty on $\sum\kapparec^{\rm halos}$ is much larger than the spectrocopic case and this propogates into a broader $\pr(\kappa)$, although the photometric reconstruction still typically produces a 1.4 fold improvement compared to the precision of the global P($\kappa$).
+
+\subsection{Reconstructing $\kappa$ with partial spectroscopic coverage}
 
@@
 \section{Testing for Systematic errors}
+\begin{figure*}
+\includegraphics[width=\textwidth]{figs/biascheck.eps}
+\caption[magcut]{Is there evidence of a bias?}
+\label{fig:where}
+\end{figure*}
+
 \todo{tom}{do}

### 2012-10-22 doc/framework.tex
added new figures
wrote some more

@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figs/Widthsvshilbert.eps}
+\includegraphics[width=\columnwidth]{figs/Width.eps}
 \caption[magcut]{Could this be any uglier?}
-\label{fig:reconidths}
+\label{fig:reconwidths}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{figs/Widthvshilberrt.eps}
+\caption[magcut]{Could this be any uglier?}
+\label{fig:widthsvsH}
 \end{figure}
@@
 Inferring the stellar mass of a galaxy from its magnitude and colours requires an estimate of how far away the galaxy is; without a spectroscopic redshift the the infered stellar mass is less precise.
+However, obtaining photometry has much lower observational cost; over the next few years several large area photometric surveys will reach 24th magnitude \citep{DES,EUCLID,LSST}, these will provide sufficient data to reconstruct lines of sight {\it without} additional observations.
 In principle the photometric redshift is correlated with the infered stellar mass, however we do not model this effect since the convergence from the outskirts of an individual halo is only weakly dependant on redshift at fixed mass: the redshift error is small effect on the recovered $\pr(\kappa)$ when compared to the effect of uncertain stellar masses.
@@
 \subsection{Reconstructing $\kappa$ with partial spectroscopic coverage}
+
+Whilst a fully photometric reconstruction provides useful constraints on $\pr(\kappa)$, targeted spectroscopy can provide addtional constraints upon the masses and redshifts of halos whose $\kappah$ contribution have the largest absolute uncertainty.
+Obtaining spectra of bright ($i<22$) objects is relatively fast with 8-m class telescopes; we find that if spectroscopic redhsifts were known for all $i<22$ galaxies in our field the reconstruction improves slightly upon the purely photometric reconstruction, although the improvement depends strongly upon the nature of the particular line of sight.
+Obtaining spectra for fainter objects would be considerably more expensive, but if spectroscopic redshifts could be obtained for all $i<23$ galaxies and all $i<24$ galaxies within 1 arcminute of the line of sight the $\pr(\kappa)$ would be almost as good as having complete spectroscopic coverage.
+High $\kappa$ lines of sight benefit the most from additional spectral coverage, since these LoS have the most uncertain $\kappah$.
+Consistent with our previous findings the lowest $\kappa$ lines of sight have the most constrained $\kappa$ PDFs.
 
@@
 
-\todo{tom}{do}
-\subsection{Using the wrong M$_{\rm halo}$-M$_{*}$ relation}
+Whilst it is good to reconstruct $\kappa$ precisely it is vital that $\kappa$ is reconstructed accurately.
+A precise, inaccurate $\kappa$ estimator is worse than useless for cosmology.
+We test the accuracy of our reconstructed $\pr(\kappa)$ in the following way: for each line of sight we shift the reconstructed $\pr(\kappa)$ by the line of sight's raytraced $\kappa$ to give $\pr(\kappa-\kapparay)$.
+Since the $\pr(\kappa-\kapparay)$ for each line of sight is an independant estimator of zero, the PDFs can be combined according to
+
+\be
+\label{eq:bias}
+\mathcal{P}_N=\prod_{i=1}^N \pr_i(\kappa-\kapparay)
+\ee
+
+We quantify the bias as the size of the deviation in the expectation value of $\mathcal{P}$ from zero.
+If the bias of $\mathcal{P}_N$ is typically smaller than the half-width of $\mathcal{P}_N$ our $\kappa$ estimators can be considered accurate.
+The number of useful time delay lines of sight can be approximated as the point at which the modulus of the bias and width of $\mathcal{P}_N$ are the same size.
+
+%\todo{tom}{do}
+%\subsection{Using the wrong M$_{\rm halo}$-M$_{*}$ relation}
 \subsection{Selecting bias from a subset of lines of sight?}
+
+First we test for systematic errors in the reconstruction of a randomly selected subset of samples.
+With the purely photometric reconstruction there is a small bias towards underestimating $\kappa$, the half-width and bias of $\mathcal{P}_{7}$ equalling 0.005.
+With targeted spectroscopic follow up this improves significantly, with the half-width and expectation value of $\mathcal{P}_{20}$ equalling 0.0026.
+With photometry alone systematics dominate after 7 randomly selected lenses, but with targetted follow-up upto 20 randomly selected lenses can be useful.
+
 \subsubsection{Selecting only the lines of sight with tight $\pr(\kappax)$}
+\label{sec:tightPDF}
+
+Since lens monitoring campaigns are expensive, it is likely that only a subset of lenses will be observed.
+By pre-selecting the lenses with the most well constrained $\pr(\kappax)$, the cosmological value per lens can be increased, however this has the potential to induce a bias.
+It is probable that only photometry will be available at the time of lens selection (although spectroscopic follow-up might be conducted at a later date).
+We mimik such a selection by drawing lines of sight only from those in the lowest third of $\sigmak$ given a photomtric reconstruction of their fields.
+We find that selecting the most tightly constrained lines of sight {\it decreases} the bias - our reconstruction is most succesful for the lowest $\kappa$ lines of sight.
+Even with photometry alone the bias is only significant after $\sim$100 lenses have been combined, at which point the width of $\mathcal{P}_{100}$ is 0.001.
+With a targeted spectroscopic follow-up of the selected lines of sight there is only modest improvement, since the best constrained lines of sight are the most empty, but it is the high-$\kappa$ lines of sight that benefit the most from spectroscopy.
+Photometry of the field is sufficient to adequately select the best lines of sight for cosmology - and doing so greatly increases both the precision and accuracy of the cosmological constraints per lens.
+
 \subsubsection{Selecting only high shear lines of sight}
+\todo{phil}{Write up why lenses are likely to be gamma biased}
+\notes{The uncertainties from modeling a strong lens system depends on the comfiguration of the source images.
+With only two point images ofthe source the lens slope and mass are degenerate; the mass-slope degeneracy\citep{mass-slope degeneracy} cite saha?.
+Where lensed arcs or four point images are present the mass-slope degeneracy can be broken and cosmology can be extracted, \citep{suyu2012a}.
+The detectability of arcs depend on the source, but the presence of four images (so called quads) depend on the shear of the lens model - a high shear is needed to produce a quad.
+The shear is almost certainly dominated by the lens model itself, but it is possible that quads are biased towards high external shear.}
+
+By selecting only lines of sight with an external shear of $\gamma>0.03$ we can test the effect of shear selection.
+We find that in all cases $\kappa$ is underestimated at the 0.006 level; roughly corresponding to the precision achieved by combining five lenses.
+Since our model does not include shear constraints it is not surprising that selecting based on shear can induce a bias.
+A more sophisticated model that includes the shear recovered from the lens modelling may not be susceptable to this bias.
+The toy model of this section ($\gamma>0.03$) is likely to be a much stronger selection than reality, but it is worth noting that the reconstruction proceedure will be biased if lens selection functions are extreme.
 
@@
 
-\section{Improving precision by including additional information}
-\notes{placeholder for shear}
+%\section{Improving precision by including additional information}
+%\notes{placeholder for shear}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:discuss}
+
+We have shown that reconstructing the matter due to halos along any line of sight can give meaningful and unbiased constraints on the external convergence along that line of sight.
+The total convergence along a line of sight is strongly correlated with the reconstructed $\kappah$.
+However since our model ignores voids and assumes all halos follow a spherical truncated-NFW profile our model does not include all of the relevant physics, hence the width of our resulting $\pr(\kappax)$ is still typically $\sim$0.01 for any given lightcone, even with a perfect knowledge of every halo's virial mass and redshift.
+To make further progress a more advanced treatment of both voids and halos will be necessary.
+Interestingly, we have found that the most empty lines of sight can be reconstructed with the most precision.
+$\kappax$ for empty lines of sight have little contributions from halos and a large contribution from voids; since they have the tightest PDFs after the reconstruction it seems that our model's biggest uncertainties are driven by naively reconstructing halos rather than neglecting voids.
+With a photometric reconstruction of the field there is only a small broadening compared to the perfect knowledge reconstruction; it seems that deviations from sphericity and dark matter clumping within the main halo are the dominant uncertainies rather than uncertainties in the halo mass.
+Inferring halo ellipticity and dark matter clumping will likely always remain a difficulty for line of sight reconstruction; as Figures \ref{fig:magcut} and \ref{fig:width2} show observing deeper than 24th magnitude does not signifcantly help the reconstruction.
+Because our reconstruction is mostly limited by the model, spectroscopic coverage can only provide a modest improvement to the reconstruction and at significant observational cost.
+
+For a small fraction of lines of sight, $\pr(\kappax)$ remains very broad even after applying our reconstruction; these lines of sight are typically the most overdense lines of sight in the universe.
+For time-delay cosmography the most observationally expensive task is the lightcurve monitoring, whilst making photometric observations of a 4$\times$4 arcminute patch of sky survey down to 24th magnitude is a relatively cheap.
+We have shown that with a single epoch observation of the region around a strong lens it is possible to infer $\pr(\kappax)$.
+If a line of sight has a broad $\pr(\kappax)$ it can be rejected {\it before} the investment of longterm lightcurve monitoring.
+
+The method we have outlined can also be used to estimate the external shear
+along a line of sight. Shear is an observable that can be extracted from
+strong lens modelling, however there is a degeneracy between internal and
+external shear. Progress has been made in disentangelling external and
+internal shear \citep[\eg][]{xxx} but there are still significant
+uncertainties: \citet{WongEtal2011} attempted to match the shear from strong
+lens models with a reconstruction of the local lens group environment, but
+found a tension between the strong lens model and the reconstruction of the
+environment. Since \citet{WongEtal2011} only reconstructed the local lens
+group, rather than the full line of sight contribution, it is unclear whether
+the external shear from lens models can be reconciled with a line of sight
+reconstruction. {\it If} external shear can be measured, it provides an
+additional constraint on which of the Millenium Simulation lines of sight are
+similar to the reconstructed line of sight. \citet{SuyuEtal2012} found that
+for RXJ1131 combining shear constriants with galaxy number count overdensity,
+gave a significantly different $\pr(\kappax|\gamma,N_{45})$ copmpared to the
+PDFfrom number count overdensity alone, $\pr(\kappax|N_{45})$.
 

### 2012-10-26 doc/references.tex
1st draft complete

@@
 {Brada{\v c}}, M., {et~al.} 2009, \apj, 706, 1201
+
+\bibitem[Cropper et al.(2012)]{EUCLID} Cropper, M., Cole, R., 
+James, A., et al.\ 2012, arXiv:1208.3369
 
@@
 
+\bibitem[LSST Science Collaboration et al.(2009)]{LSST} LSST 
+Science Collaboration, Abell, P.~A., Allison, J., et al.\ 2009, 
+arXiv:0912.0201
+
+\bibitem[Macci{\`o} et al.(2008)]{MaccioEtal2008} Macci{\`o}, A.~V., 
+Dutton, A.~A., \& van den Bosch, F.~C.\ 2008, \mnras, 391, 1940
+
 \bibitem[{{Momcheva} {et~al.}(2006){Momcheva}, {Williams}, {Keeton}, \&
@@
   641, 169
-
-\bibitem[\protect\citeauthoryear{Nandra, Lasenby, 
-\& Hobson}{2012}]{NandraEtal2012} Nandra R., Lasenby A.~N., Hobson M.~P., 2012, MNRAS, 422, 2945
 
@@
 
-% \bibitem[\protect\citeauthoryear{Suyu}{2012}]{Suyu2012b} Suyu 
-% S.~H., 2012, arXiv, arXiv:1202.0287
+\bibitem[\protect\citeauthoryear{Suyu}{2012}]{Suyu2012a} Suyu 
+S.~H., 2012, arXiv, arXiv:1202.0287
 

### 2012-10-26 doc/paper-lcr.tex
added new figures
1st draft complete

@@
 \begin{abstract} 
-
 Strong gravitational lenses can provide high precision cosmological distance
@@
 estimates is the additional mass along the line of sight to the source. Weak
-lensing by galaxies and groups in this beam can contribute an ``external
-convergence'' $\xkappa$ that dominates the  uncertainty in the inferred
+lensing perturbations by galaxies and groups in this beam can contribute an ``external
+convergence'' $\kappa$ that dominates the  uncertainty in the inferred
 distances; likewise, it may also contaminate estimates of the luminosity of
@@
 supernovae standard candles).  We characterise this uncertainty by marginalising
-over a probability density function for $\xkappa$: here, we investigate the use
-of a simple halo model to estimate $\Pr(\xkappa)$ given noisy estimates of the
+over a probability density function for $\kappa$: here, we investigate the use
+of a simple halo model to estimate $\Pr(\kappa)$ given noisy estimates of the
 photometric redshift and stellar mass of galaxies observed in optical imaging
 surveys of the field in question. We use mock catalogs from the Millenium
-Simulation and compare our reconstructed $\Pr(\xkappa)$ to ray-traced $\kappa$ values,
-we find that our model produces an unbiased estimator of $\kappax$,
-For each lightcone the individual $\Pr(\xkappa)$ from this reconstruction process are
-typically 1.8 times narrower than the global distribution of $\xkappa$ given perfect knowledge 
+Simulation and compare our reconstructed $\Pr(\kappa)$ to ray-traced $\kappa$ values,
+we find that our model produces a precise estimator of $\kappa$ with only small biases.
+For each lightcone the individual $\Pr(\kappa)$ from this reconstruction process are
+typically 1.8 times more precise than the global distribution of $\kappa$ given perfect knowledge 
 of the halo mass and redshift. After incorporating uncertainties on redshift and halo and stellar masses
-we typically find that the reconstruction yields an improvement factor of 1.5. For each line of sight the
- $\Pr(\xkappa)$ can be formed before the investment of light-curve monitoring. By following up only the 
+we typically find that the reconstruction yields an improvement factor of 1.4. For each line of sight the
+ $\Pr(\kappa)$ can be formed before the investment of light-curve monitoring: by following up only the 
 most costrained lines of sight a factor of 2 improvement over the global $\pr(\kappax)$ should be 
@@
 
-Averaged over large areas of sky, the weak gravitational lensing effect can be
-used to constrain the statistical properties of the matter density in the
-Universe: every distant object we observe has had its shape distorted, and size
+Every distant object we observe has had its shape distorted, and size
 and total brightness magnified (or demagnified) by a compound lens constructed
-from all the mass distributed between us and it.
-
-This fact makes weak gravitational lensing a potentially important source of
-systematic error for any estimate of luminosity or distance, an issue
-raised for \eg 
-type Ia supernovae by \citet[][]{Holz+Wald1998,Linder+Holz2004}, for
+from all the mass distributed between us and it. As \citet{Vale+White2003} and \citet{HilbertEtal2007}
+showed, there are no empty lightcones in our universe. This fact makes gravitational lensing a potentially important source of systematic error for any estimate of luminosity or distance, an issue
+raised for \eg type Ia supernovae by \citet[][]{Holz+Wald1998,Linder+Holz2004}, for
 gamma ray bursts by \citet[][]{Oguri+Takahashi2006,Wang+Dai2011}, 
 and for high redshift galaxies by \citet{BradacEtal2009}, among others.
+
 Along lines of sight containing strong gravitational lenses,
@@
 \citep[\eg][]{WongEtal2012} and distance ratios \citep[][]{DalalEtal2005}.
-In time delay lens cosmography,
-\citet{SuyuEtal2010} found that  the lensing effect of mass structures along the
-(unusually over-dense)  line of sight to the quadruply-imaged radio source
-B1608$+$656, the so-called ``external convergence,'' was the dominant source
-of uncertainty in their 6\% measurement of Hubble's constant.
-
-How can we correct for this weak lensing error, and make
+\citet{SuyuEtal2010} found that in time delay lens cosmography the
+lensing effect of mass structures along the (unusually over-dense) line of
+sight to the quadruply-imaged radio source B1608$+$656, the so-called ``external
+convergence'' $\kappax$, was the dominant source of uncertainty in 
+their 6\% measurement of Hubble's constant.
+
+The problem is that one simply doesn't know
+how magnified and distorted the source has been because the unlensed
+source is unobservable. The external shear can potentially be recovered
+in the mass-modelling of the lens, but the convergence is undetectable
+from the image positions, shapes and relative fluxes; this is the
+famous {\emph{  mass sheet-degeneracy}} \citep[see e.g.][for details]{FalcoEtal1985}.
+
+How can we correct for this perturbative lensing and make
 accurate measurements through the Universe? When inferring global quantities
 (such as the cosmological parameters), averaging the results from a large
-number of independent objects will tend to reduce the error, as the
+number of independent objects will tend to reduce the uncertainty, as the
 ensemble-averaged convergence approaches zero for an unbiased sample
@@
 brightness of the lensed object, or any other quantity that depends on
-$\xkappa$. The latter class includes time delay lenses, which could be
-either detected or selected 
-based on their image separations, magnifications or quadruple image
-configurations, all of which either increase or become more likely with
-increasing $\kappa$. Large
+$\kappa$. Large
 samples of lenses are expected to be discovered in the next decade in
@@
 samples will be image separation-limited, due to the surveys' relatively poor
-($\sim 1$~arcsec) image quality. Some of the current sample of known time
-delay lenses were detected in surveys like this: we might expect them to be
-somewhat biased towards high values of $\xkappa$.
-
-There are two broad approaches one could take at this point. First, one could
-seek to characterise the lensed objects' selection function, and use this
-understanding to derive a suitable correction to cosmological parameters
-inferred assuming no $\xkappa$ at all. As pointed out by  \citet[][among
-others]{Oguri+Takahashi2006}, to do this one would need  information about the
-unlensed population of objects, and the population of lenses, and how the
-objects were detected -- or to infer these hierarchically during the analysis.
-Alternatively, one could simply accept all lenses provided, regardless of
-their selection, and try to use any additional information that is available
-to estimate the external convergence in each system on a case by case basis,
-and hence optimize their joint analysis to produce a better-constrained result
-\citep[as suggested by][]{Keeton+Zabludoff2004}. In this work we follow this
-second approach, and use measurements of the positions, magnitude and colours
-of galaxies close to lens lines of sight to try to infer the
-external convergence at the lens position.
-
-Attempts to date at reconstructing the local and  line of sight mass
+($\sim 1$~arcsec) image quality. There is a possibility that
+they are somewhat biased towards high values of $\kappa$, although 
+\citet{Fassnacht+Lubin2002} \todo{Anyone}{check this is the right Fassnacht paper} found no evidence of lenses lying along over-dense lines of sight.
+
+To date, attempts at reconstructing the local and line of sight mass
 distribution in strong lens fields (what \citeauthor{WongEtal2011} call ``the
 full environment'') have focused on photometric and  spectroscopic surveys to
-detect galaxy groups and ascertain galaxies' membership,  and on understanding
+detect galaxy groups and ascertain galaxies' membership in order to understand
 the external shear apparently required by the strong lens models. Surveys by
@@
 is the key quantity for any ensemble analysis, since by marginalising over it
-we can correctly propagate the uncertainties due to weak lensing. Coming
+we can correctly propagate the uncertainties due to line-of-sight perturbations. Coming
 closest to estimating this quantity from survey data, \citet{WongEtal2011} ran
@@
 sight, and compared the resulting predicted shear distributions with the
-external shear demanded by the strong lens model. Their simulations show most
+external shear demanded by the strong lens model. Their reconstructions show most
 of the shear being generated by bright galaxies within 2~arcminutes of the
@@
 of likely external shears and convergences along strong lens lines of sight. 
-\citet{Holder+Schechter2003} and \citet{Dalal+Watson2004} carried out
+\citet{Holder+Schechter2003} and \citet{Dalal+Watson2004}\todo{phil}{Dalal+Watson2004 doesn't seem to exist} carried out
 ray-tracing calculations in N-body simulations to estimate the  distribution
@@
 experiments through the Millenium Simulation \citep{SpringelEtal2005},
-generating a predicted $\xkappa$ at every position in a simulated sky. The
-first step towards using this excellent calibration resource was taken by
-\citet{SuyuEtal2010}, who selected Millenium Simulation lines of sight that a)
-were found to contain a strong lens and b) had comparable apparent galaxy
-overdensity in a 45 arcsec radius aperture down to $i < 24$. This overdensity
+generating a predicted $\kappa$ at every position in a simulated sky. \citet{HilbertEtal2009}
+found that \MS lines of sight with strong lenses were not biased towards high $\kappa$,
+although selection functions for discovering a strong lens were not taken into account.
+The first step towards using this excellent calibration resource was taken by
+\citet{SuyuEtal2010}, who selected Millenium Simulation lines of sight that
+ had comparable apparent galaxy
+overdensity in a 45 arcsec radius aperture down to $i < 24.5$. This overdensity
 could be compared to the overdensity of the B1608$+$656 line of sight
-\citep{FassnachtEtal2011}, and hence an estimate of  $\Pr(\xkappa)$ could be
-made.
+\citep{FassnachtEtal2011}, and hence an estimate of  $\Pr(\kappa)$ could be
+made. B1608$+$656 is indeed a high $\kappa$ line of sight, but it does not reside
+in a typical lens environment.
 
@@
 effects to test the accuracy of line of sight mass reconstructions.
-Probabilistically ssigning mass and redshift to every observed galaxy in the
+Probabilistically assigning mass and redshift to every observed galaxy in the
 field around a time delay lens, we generate Monte Carlo sample line of sight
 mass distributions, and estimate the external convergence due to each one.
-This gives us a $\Pr(\xkappa)$ that can be propagated into further joint
-inferences. We focus on time delay lens cosmography, and quantify our results
-in terms of the uncertainty on the mean time delay distance to a test sample
-of $N$ lenses (where for clarity each lens has the same deflector and source
-redshift, and the same lens model and time delay uncertainty).
+By using the Millenium siumlation as a calibration tool, we can convert the
+total contribution from halos, $\Pr(\kappah)$, into a PDF for the likely convergence
+along the line of sight $\Pr(\kappa)$.
 
@@
 \begin{itemize}
-\item Faint galaxies and other dark structures will not appear in a photometric
+\item Faint galaxies, filaments and dark structures will not appear in a photometric
 object catalog, but they will contribute convergence at some level. How much of
@@
 galaxies? How does this change as a function of magnitude cut? 
-\item Can the true (ray-traced) convergence be recovered by halo model
-reconstruction? What scatter and residual bias are induced in the ensemble 
-distance estimate? Which aspects of the model dominate these uncertainties? 
+\item Can the true (ray-traced) convergence be recovered from a calibrated halo model
+reconstruction? What scatter and residual bias are induced by the reconstruction
+process? Which aspects of the model dominate these uncertainties? 
 \item When faced with a newly-detected lens, surrounded by galaxies on the sky,
@@
 and second, in \Sref{sec:obsMstar+z}, with realistic observational uncertainties
-on the field galaxies' stellar masses and redshifts. \comments{We then propagate all these
-uncertainties through to the time delay distance in a toy sample of 100 lenses,
-in \Sref{sec:distances}.} We discuss our results in \Sref{sec:discuss} before
+on the field galaxies' stellar masses and redshifts. In \Sref{sec:biases} we
+investigate potential systematic errors induced by selecting a subset of sightlines.
+We discuss our results in \Sref{sec:discuss} before
 concluding in \Sref{sec:conclude}.
@@
 
+\begin{figure*}
+\includegraphics[width=\textwidth]{figs/viewofalightcone.eps}
+\caption[magcut]{4 different views of a lightcone around a typical line of sight.
+This line of sight is slightly overdense with a $\kappa$ of 0.03.
+Top left show the positions of galaxies, the area of the circles is proportional to observed $i$-band flux; the brightest object shown has an $i$ magnitude of 17.7.
+Top Centre show the angular sizes of halos on the sky; red regions are within the NFW scale radius of a halo and blue shows the virial radius of each halo - there are clearly no empty lightcones.
+Top right shows the individual $\kappa$ contributions of each halo, assuming the \citet{BMO} profile and the \citet{Neto2007} mass-concentration relation.
+Bottom a view along the redshift axis, showing only halos with $|x|<0.3$ arcmin; the area of the points is scaled by halo mass; the most massive halo shown has $1.6\times10^{12}\Msun$; the optical axis is the dashed line whilst the dotted lines are the lens and source planes for a B1608-like strong lens.}
+\label{fig:lightcone}
+\end{figure*}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:theory}
-
-%Time delay distances, and the mass sheet degeneracy - how kappa is degenerate in
-%strong lens models (and magnifications).
 
@@
 
+\comments{
 Strong lensing occurs when a massive object and background source are almost perfectly
@@
 \ee
+}
 
@@
 to be strongly lensed \citep{GavazziEtal2008,CollettEtal2012a}, the shear scale of dark matter halos
-makes a partial alignment -- with the additional structure acting as a weak lens -- 
-a near certainty, indeed \citet{Vale+White2003} and \citet{HilbertEtal2007} find that there
-are no empty lightcones in a realistic universe. These additional structures induce an external shear
-which can be recovered in the mass-modelling of the lens, but they can also introduce a convergence that
+makes a partial alignment -- with the additional structure acting as a perturbing weak lens -- 
+a near certainty \citep{Vale+White2003,HilbertEtal2007}. These additional
+structures induce an external shear which can be recovered in the mass-modelling
+of the lens, but they can also introduce a convergence that
 is undetectable from the image positions, shapes and relative fluxes; {\it the
@@
 of an external convergence (and appropriate re-scaling of the lens potential) the relative Fermat potential between the images is {\it not}
-invariant, and so the time delay changes. As such it is necessary to include $\kappax$
+invariant, and so the time delay changes. As such it is necessary to include $\kappa$
 in the lens modelling, if cosmological parameters are to be estimated accurately and
-precisely from observed time delays \citep{SuyuEtal2010}.
-
-\comments{
-If the mass sheet is not physically associated with the lens galaxy, it can lie at any redshift.
-The effects of such a mass-sheet can be projected back onto the lens plane in the form of an effective convergence.
-We define this effective convergence in two limits.
-\begin{itemize}
-\item No significant perturbations along the line of sight, and \\
-\item A single dominant perturber, relative to which all other perturbations are small.
-\end{itemize}
-We will refer to these cases as the magnification case (subscript $\mu$ in formulae), and the strong lensing case (subscript SL in formulae), respectively.
-We will ignore the additional case, of a compound lens, with several significant perturbers.
-
-The magnification case has no primary lens plane, and is chiefly relevant for the magnifications of distant objects.
-In the absence of a primary lens plane, we are free to define the effective convergence on any point; the effective convergence is the same, independant of the plane choosen.
-It can be shown \citep[\eg][]{xxx} that if there are several mass sheets at redshifts $\{z_{p}\}$, with convergences $\{\kappa_p =\Sigma_{p}/\Sigma_{\mathrm{cr}}(z_p)\}$, the effective convergence is given by
-\be \label{eq:kappasummu}
-\kappa_{\mathrm{effective,\mu}}=\sum_{p}\kappa_p.
-\ee
-
-In the stong lensing case, the presence of a significant perturber alters the
-geometry of the system, and provides a primary lens plane. It is the primary
-lens plane upon which we need to know $\kappa_{\mathrm{effective}}$, since
-this is where the mass-sheet degeneracy is defined. Following Equations 20--32
-of \citet{keeton2003}\flag{keeton2003}, it can be shown that the relevant
-effective convergence is given by 
-\be \label{eq:kappasumSL}
-\kappa_{\mathrm{effective,SL}}=
-{  
-(1-\beta_{12})(\kappa-\beta_{12}(\kappa^2-\gamma^2))
-\over
-(1-\beta_{12}\kappa)^2-(\beta_{12}\gamma)^2
-}
-\ee
-where $\kappa$ and $\gamma$ are, respectively, the convergence and shear
-caused by the perturber, in their own plane and $\beta_{12}$ is a geometrical
-scaling factor defined by
-\be\label{eq:beta}
-\beta_{12}={
-D_{12} D_{\mathrm{os}}
-\over
-D_{\mathrm{o}1} D_{1\mathrm{s}}
-}
-\ee
-where the D's are again angular diameter distances: the 1 (2) in the subscript
-refers to the lower (higher) redshift object of the lens and perturber. For
-the case that the mass sheet is in the lens plane, $\beta_{12} = 0$ and
-$\kappa_{\mathrm{eff}}=\kappa$; if the mass-sheet is in the plane of the
-observer, or source, $\beta_{12} = 1$ and $\kappa_{\mathrm{eff}}=0$; for a
-mass-sheet at any other redshift $0<\beta_{12}<1$. In the case of several mass
-sheets the effective convergences sum. In the limit that both $\kappa$ and
-$\gamma$ are small, Equation \ref{eq:kappasumSL} reduces to 
-\be \label{eq:kappasumSLweak}
-\kappa_{\mathrm{effective,SL}}=(1-\beta_{12})\kappa;
-\ee
-it is this $\kappa_{\mathrm{effective,SL}}$ that we use as $\kappax$ for the
-strong lensing time delay analysis in \ref{sec:Dt}.
-}
-
-\tom{The all-important calibration of the reconstruction has to be done
-against Stefan's ray-traced kappas though -- so it is these that we have to
-predict PDFs for, first and foremost. THEN we have to consider the question of
-which kappa to use to correct the time delay distances: Stefan's kappa (as in
-B1608 or RXJ1131), or kappa-keeton.}
-
-The time-delay distance is defined as
-\be \label{eq:dt}
-\Dt \equiv (1+\zd) D_{\rm d} D_{\rm s}/D_{\rm ds},
-\ee
-with which Equation \ref{eq:T} can be rephrased as
+precisely from observed time delays \citep{SuyuEtal2010}. If there is any external convergence, that is not included in the lens
+modeling, then the time delay distance -- inferred assuming $\kappa = 0$ -- will be
+$(1-\kappa)$ less than the true value of $\Dt$.
 \be 
-\Delta t(\bmath{\theta},\bmath{\beta})  =  \frac{\Dt}{c} \, \phi(\bmath{\theta},\bmath{\beta})    ,
-\ee 
-Since the time delays are proportional to $1/ (1- \kappax)$, if there is any external convergence, that is not included in the lens
-modeling, then the time delay distance -- inferred assuming $\kappax = 0$ -- will be
-$(1-\kappax)$ less than the true value of $\Dt$.
-\be 
-\label{eq:MassSheet:H0bias}
-\Dt^{\rm{true}}=(1-\kappax) \Dt^{{\kappax = 0}}.
-\ee
-We can overcome this degeneracy if we have additional knowledge of $\kappax$.
+\label{eq:MassSheet:Dtbias}
+\Dt^{\rm{true}}=(1-\kappa) \Dt^{{\kappax = 0}}.
+\ee
+We can overcome this degeneracy with additional knowledge of $\kappa$.
+Since $\kappa$ is typically small the absolute uncertainty on the estimate
+of $\kappa$ correspends to the percentage uncertainty with which time-delay
+distances can be infered.
 
@@
 mass-sheet degeneracy by providing an additional estimate of the lens galaxy's mass
-\citep[e.g.,][]{xxx}.
-
-In this work our aim is to quantify the lensing effect of mass-sheets that are not physically associated with the lens galaxy -- mass-sheets
+\citep[e.g.,][]{SuyuEtal2010}. In this work our aim is to quantify the lensing effect of mass-sheets that are not physically associated with the lens galaxy -- mass-sheets
 lying infront or behind the lens -- and the uncertainties induced by reconstructing
 those mass-sheets using simple prescriptions applied to potential astronomical observables.
-\comments{We also aim to quantify how uncertainties in the
-estimations of $\kappax$ propogate into uncertainties on the cosmological parametres
-which can be inferred from measurements of $\Dt$.}
 
@@
 \label{sec:model}
-
-%Weak lensing by NFW halos. Accounting for mass along the line of sight.
-%Approximations to full ray tracing:
-%
-%Halos. N-body sims provide mass framework. MS halo catalog. Truncated spherical
-%NFW approx based on virial masses. Stellar mass. Halo map corresponding to
-%ray-traced kappa map, for illustration. Small-scale structure
-
-For real lines of sight, we would like to estimate the external convergence as best we can given all
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+For real lines of sight, we would like to estimate the external convergence given all
 data available. Typically this data is in the form of a photometric galaxy
@@
 
-% A source with known unlensed brightness e.g. a strongly lensed type Ia
-% Supernova \flag{cite some SNe papers} or a source of known unlensed size \flag{ideas?}
-% would break the mass-sheet degeneracy and provide a value for $\kappax$, but
-% \flag{no?} such systems are currently known.
-
-\subsection{Ray-tracing through simulated Lines of Sight}
-\label{subsec:raytracing}
-Cosmological dark matter simulations can be used to generate mock lines of
-sight and can be raytraced through to give each mock sightline a $\kappax$ value...
-\todo{Stefan}{Write section on how the ray tracing was done}
-
-\subsection{Generating mock lightcones from simulations}
-
-\todo{Stefan}{Write section on how halos are extracted from the MS n-body particles}
-
 Transforming the photometometric galaxy catalogue into a  catalogue of
@@
 reconstruction of the convergence induced by every halo near a line of sight.
-This is the subject of \ref{subsec:halos}. We also need to account for
+This is the subject of Section \ref{subsec:halos}. We also need to account for
 the mass in the Universe that is not associated with the galaxies we can see
--- this is the subject of \ref{subsec:voids}.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+-- this is the subject of Section \ref{subsec:voids}.
 
@@
 but there is some scatter; we use the relation of \citet{Neto2007} to estimate $c$
-from the mass enclosed within $r_{200}$, which we denote as $M_{200}$. The best fit relation of \citet{Neto2007} is given by
+from the mass enclosed within $r_{200}$, which we denote as $M_{200}$.
+We find our results do not change if the \citet{MaccioEtal2008} Mass--concencetration relation is used instead.
+The best fit relation of \citet{Neto2007} is given by
 \be
@@
 be truncated at some point.
-\todo{Tom}{Add notes on previous truncation results}.
-Several truncation profiles have been suggested \citep[e.g][]{BMO}, but beyond several virial radii, the amount of matter associated with a halo is likely to be low; \citet{NandraEtal2012} showed that the Universe's expansion can place an upper limit on the radius of NFW halos -- for cluster scale halos, this happens at around 25 times the NFW scale radius.
-In \Sref{sec:knownMh+z} we investigate how different truncations affect the recovered total convergence for a line of sight, using the truncated NFW profile of \citet{BMO}
+Several truncation profiles have been suggested \citep[e.g][]{BMO}, but beyond several virial radii, the amount of matter associated with a halo is likely to be low.
+In this work we assume the truncated NFW profile of \citet{BMO}
 \be\label{eq:bmoprofile}
@@
 \ee
-which is the same as the NFW profile in the limit that the truncation radius, $r_t$ goes to infinity. The convergence and shear for the BMO profile are given in Appendix \ref{appendix:halos}.
+which is the same as the NFW profile in the limit that the truncation radius, $r_t$ goes to infinity.
+We use a truncation radius of five times the virial radius, but our results are robust for any choice of $r_t>2 \times r_{200}$.
+
+The projected surface mass density $\Sigma(r)$ for this mass profile is derived in \citet{BMO}. Each halo in our catalogue then contributes to the line of sight convergence by
+\be
+\label{eq:kappai}
+\kappa_i =\Sigma_{i}/\Sigma_{\mathrm{cr}}(z_i),
+\ee
+ where $\Sigma_{\rm cr}(z)$ is the critical surface density given by:
+\be \label{eq:sigcrit} 
+\Sigma_{\rm cr}(z) \equiv \frac{c^2 D_{\rm os}}{4 \pi G D_{\rm od} D_{\rm ds}},
+\ee
+ the D's are the angular diameter distances between the objects refered to in the subscripts: o is the observer, d is the deflector and s is the source.
+We take the total convergence from all the halos along the line of sight to be given by
+\be \label{eq:kappasummu}
+\kappah=\sum_{i}\kappa_i.
+\ee
+
+To estimate a halo's contribution to $\kappah$ we must first know the halo's mass.
+For the calibration sightlines of the \MS halo masses are known, but for 
+real lines of sight this can only be infered from the stellar masses of the
+galaxies within a halo. We use the relation of \citet{BehrooziEtal2009} to generate 
+halo masses from stellar masses; the details of this proceedure are outlined in
+Appendix \ref{appendix:MSMH}.
+
+Given an uncertain halo mass and redshift for a halo we draw a sample mass and redshift and use Equation \ref{eq:kappai} to generate a sample $\kappa_i$; this can be done for all the halos along the line of sight and summed to give a sample $\kappah$; repeatedly applying this proceedure allows us to characterize $\pr(\kappah)$.
+However we found that our proceedure for estimating halo masses induces long tails in the $\pr(\kappah)$ distribution that are not present in the global $\kappah$ distribution given perfect knowledge of halo mass and redshift, to correct for this we use the global $\kappah$ distribution as a prior on $\pr(\kappah)$.
 
@@
 
-\subsection{Calibration: Recovering the global $\pr(\kappax)$ using a void correction}
+\subsection{Correcting for voids, filaments and dark structures}
 \label{subsec:voids}
 
-Whilst halos contribute a positive convergence to $\kappax$, voids contribute
+Whilst halos contribute a positive convergence to $\kappa$, voids contribute
 a negative convergence. When a raybundle passes through a  region of space
@@
 void, but the under-density of such a void is hard to infer. Neglecting voids
-would lead to a heavily biased estimate of $\kappax$. We account for the voids
-statistically; we reconstruct
-the $\kappax$ contribution of halos for an ensemble of calibration sightlines
-and form the joint distribution P($\kapparay,\sumkappah$). The calibration
-can then be accounted for by marginalizing over all lines of sight with a similar
- $\sumkappah$.  We will refer to this calibration proceedure as the "void correction",
-although it also accounts for all of the physics that our simple spherical halo prescription
-neglects in a statistical manner. For each line of sight we create a $\pr(\kappax)$ from
-\be
-\pr(\kappax)=\int_{-\infty}^{+\infty}\pr(\kapparay',\tilde\kappa'_{\rm halos})W(\tilde\kappa_{\rm halos}-\tilde\kappa'_{\rm halos})\dee \tilde\kappa'_{\rm halos}
-\ee
-where $\tilde{\kappa}_{\rm halos}$ is the median of the reconstructed $\sumkappah$ for each line of sight.
-Primed qunatities refer to all of the calibration sightlines and unprimed refers to the specific line of sight.
-$W(\tilde\kappa_{\rm halos}-\tilde\kappa'_{\rm halos})$ is a weight function given by
-\be
-\label{eq:weighting}
-W(\tilde\kappa_{\rm halos}-\tilde\kappa'_{\rm halos})=\exp\left(-\frac{1}{2}\left(\frac{\left(\tilde\kappa_{\rm halos}-\tilde\kappa'_{\rm halos}\right)^2}{\sigma^2}\right)\right)
-\ee
-We take $\sigma$ as 0.002- this is an overestimate of the uncertainty on $\tilde\kappa_{\rm halos}$, but ensures that the full distibution of void corrections is sampled, despite the finite number of calibration sightlines.
-
-\comments{
-For each reconstruction of a line of sight we can then draw a $\kappav$ from $\pr(\kappav)$ to correct for the
-unseen voids. We refer to this corrective shift as $\kappav$. The void correction introduces a source of
-error, since the value of $\kappav$ comes from the ensemble of calibration lines of sight rather than the individual
-line of sight which is being reconstructed; this is unavoidable without modeling the $\kappax$ 
-contribution of voids along a line of sight. To avoid potential biases we calculate $\pr(\kappav)$
-from randomly selected calibration sightlines. The total $\kappax$ along the line of sight
-is given by 
-\be \label{eq:totalkappaxunweighted}
-\pr(\kappax) = \left(\sum_{\rm halos} \pr(\kappa_{\rm halo})\right)-\pr(\kappav).
-\ee
-
-Once the void correction has been applied,the reconstruction should produce a 
-reasonable estimate of $\pr(\kappax)$ for any single line of sight. However, from
-the ray tracing results we know the global $\kappax$ distribution ${\rm U}(\kappax)$. We can use the global
- ${\rm U}(\kappax)$ as a prior by noting that the normalized sum of $\pr(\kapparec)$ from multiple lines
-of sight should equal ${\rm U}(\kappax)$, \ie
-\be \label{eq:prior}
-{\rm U}(\kappax) = \lim_{N \to \infty} \sum_{i}^{N} \pr(\kappax)_{i} / N
-\ee
-In order to make Equation \ref{eq:prior} hold, we use Equation \ref{eq:totalkappaxunweighted} to calculate $\pr(\kappax)^{\rm unweighted}$ for the calibration lines of sight and
-re-weight the reconstructions by:
-\be \label{eq:weighting}
-W(\kappa)=\left(\sum_{i}^{N} \pr(\kappax)_{i}^{\rm unweighted} /N \right) / \left({\rm U}(\kappax)\right)
-\ee
-such that the final reconstruction is given by 
-\be \label{eq:totalkappax}
-\pr(\kappax) = \left(\left(\sum_{\rm halos} \pr(\kappa_{\rm halo})\right)-\pr(\kappav)\right)(W(\kappa)).
-\ee
-
-}
-
-\comments{
-Whilst halos contribute a positive convergence to $\kappax$, voids contribute
-a negative convergence. When a raybundle passes through a  region of space
-that is less dense than $\rho_{\rm cr}(z)$ the rays are de-focused\footnote{In
-principle, the convergence caused by halos, is also caused by the overdensity,
-but we neglect this effect since halos are typically much more dense than the
-intergalactic medium}. Whilst the  full raytraced solution takes into account
-the effect of voids, our reconstruction cannot -- the halo catalogue does not
-include voids. In principle the absence of a halo could be taken to infer a
-void, but the under-density of such a void is hard to infer.
-\tom{ Instead, we reconstruct 10000 lines of sight to give $\pr(\kapparec|kapparay)$
-and invert the PDF using Bayes' theorem to give $\pr(\kapparay|\kapparec)$. For each lightcone we
-can then get $\pr(\kapparay)$ by marginalizing over the reconstruction PDF, $\pr(\kapparec)$.
-This recipe also ensures that we correctly recover the ensemble $\kapparay$ distribution, even in the case
-of no input data.
-
- Instead, we shift
-our $\kappax$ values so that $\langle\kappax\rangle=0$. We refer to this
-corrective term as $\kappav$. The void correction introduces a source of
-error, since the inferred value of $\kappav$ will depend on the properties of
-the sightlines reconstructed, but this error shrinks with the number of
-sightlines reconstructed. To avoid potential biases we calculate $\kappav$
-from randomly selected sightlines. The total $\kappax$ along the line of sight
-is given by 
-\be \label{eq:totalkappax}
-\kappax = \left(\sum_{\rm halos} \kappa_{\rm halo}\right)-\kappav.
-\ee
-}}
+would lead to a heavily biased estimate of $\kappa$.
+
+The proceedure outlined in Section \ref{subsec:halos} allows us to estimate 
+the convergence due to halos given observations of mass, redshift and position
+$\pr(\kappah|\mathcal{D})$, but what we are interested in is the total convergence
+along the line of sight $\pr(\kappa|\mathcal{D})$. We can obtain this by
+considering the expression:
+\begin{equation}
+\Pr(\kappa|\mathcal{D}) = \int \dee\kappah 
+   \Pr(\kappa|\kappah) \Pr(\kappah|\mathcal{D})
+\label{eq:kappaconv}   
+\end{equation}
+The first term in the integrand relates the summed convergence due to model
+halos, $\kappah$, to the true convergence, $\kappa$. In the Millenium
+Simulation catalogs, we can compute $\kappah$ for each
+selected line of sight and combine multiple lines of sight to calculate $\Pr(\kappa|\kappah)$.
+
+Given an uncertain stellar mass to halo mass conversion, the $\pr(\kappah|\{\Mstar,z\})$ can shift 
+relative to $\pr(\kappah|\{\Mhalo,z\})$; this is because of the highly asymetric conversion from
+stellar mass through halo mass into $\kappah$. If this shift is ignored the resulting $\Pr(\kappa)$
+can become highly biased. To calibrate this effect we reconstruct each of our calibration
+sightlines, in the same way as the observed sightlines to generate
+ $\pr(\kappa,\kappah|\{\Mstar,z\})$, for each calibration sightline we use the median of $\pr(\kappah|\{\Mstar,z\})$ to form a de-biased $\Pr(\kappa|\kappah)$.
+
+For any given line of sight we can then infer
+$\Pr(\kappah|\mathcal{D})$ as described above, and then
+multiply it by $\Pr(\kappa|\kappah)$; we do the marginalisation over $\kappah$
+by drawing samples from the two-dimensional grid and keeping only the
+$\kappa$ values, to form our final result, $\Pr(\kappa|\mathcal{D})$.
 
@@
 
-\section{Testing the halo model approximation with known halo mass and redshift}
+\section{Using the Millenium Simulation to test the halo model approximation with known halo mass and redshift}
 \label{sec:knownMh+z}
 
-\subsection{How does $\kappah$ relate to $\kappax$?}
-
-\subsection{Does converting from $\kappah$ to $\kappax$ work?}
-
-\subsection{Where does $\kappah$ come from?}
-\subsubsection{Magnitude}
-\subsubsection{Distance}
-\subsubsection{Redshift}
-
-%Raytracing through n-body particles as 'truth'. Motivation for assuming perfect
-%knowledge of halo mass and z = testing model of previous section. Deterministic
-%prediction of kappa.
-%
-%Is truncation choice important? How deep and wide does a reconstruction need to
-%go? What is the irreducible uncertainty on kappa from this halo model? (Bias and
-%scatter) Can use the ideal reconstruction to ask: Where does the kappa come
-%from? Close to the LoS? Bright objects? How many objects are important? What
-%error is made by considering subsets of available objects?
-
-Given the halo mass catalogue from the Millenium Simulation, and convergence maps produced by
-ray-tracing through the MS's n-body particles, 
-it is possible to test the validity of the prescription outlined in Section \ref{sec:model}. We test the model
- by comparing $\sumkappah$ against $\kapparay$. If the reconstruction process is to be
- succesfull the two quantities should correlate.
-
-The reconstruction prescription is tested given perfect
-knowledge of the halos' virial masses and redshifts; this provides us with a measure of the intrinsic
-errors induced by treating matter as truncated NFW halos. For our first tests we do not apply the void correction of
-Section \label{subsec:voids}, instead we shift $\sumkappah$ for all our sightlines by a fixed negative offset such that the ensemble mean
-is zero, i.e.
-\be \label{eq:totalkappax}
-\kapparec = \left(\sum_{\rm halos} \kappa_{\rm halo}\right)-\kappav,
-\ee
-where $\kappav$ is a positive constant. This us allows us to test the correlation of $\sumkappah$ with $\kapparay$, without
- the uncertainty of the void correction obscuring any inadequacies of our halo based prescription.
-
-We choose 100000 lines of sight from random positions in the catalogue, and for each line of sight we reconstruct the
-convergences from every halo within 5 arcminutes and compare the reconstructed
-$\kapparec$ with those from the ray tracing results. The standard deviation on $\kapparay$-$\kapparec$ is
-shown in Figure \ref{fig:ScattervsTruncation} as a function of the radius at which the halo is truncated.
- It is clear from Figure \ref{fig:ScattervsTruncation} 
-that as long as the truncation is greater than a few virial radii, the choice of truncation
-radius does not broadly affect the scatter on $\kapparay-\kapparec$; from now on we choose 
-to truncate the halos at $5 \Rhalo$. Since $\sigma\left(\kapparay-\kapparec\right)$ does not go to
-zero, it is clear that out halo based prescription does not perfectly replicate the n-body results, we refer to this
- as the intrinsic error of the prescription.
- The intrinsic error has a standard deviation of $\sigi \sim 0.018$, although
-this figure is inflated by a few outliers in the tails of $\pr\left(\kapparay-\kapparec\right)$. Such outliers would 
-likely be rejected by their reconstructed shear not matching the shear of the lens model 
-(see \citet{WongEtal2011} for the practicalities of this);
- this makes our estimate of the intrinsic error pessimistic. We do not include any additional constraints on P($\kappax$), given prior knowledge of the external shear in this work.
+In order to justify the reconstruction proceedure outlined in Section \ref{sec:model}, we would like to apply it to lines of sight with known $\kappa$.
+Because we want to test both accuracy and precision we need to know the true convergence for the line of sight.
+Since $\kappa$ isn't an observable we can not use real lines of sight but must use simulated lines of sight instead.
+
+\subsection{Ray-tracing through simulated Lines of Sight}
+\label{subsec:raytracing}
+\todo{Stefan}{Write section on how the ray tracing was done}
+
+\subsection{Generating mock lightcones from simulations}
+\todo{Stefan}{Write section on how halos are extracted from the MS n-body particles}
+
+\subsection{How does $\kappah$ relate to $\kappa$?}
+
+Given the halo mass catalogue from the Millenium Simulation, 
+and convergence maps produced by ray-tracing through the MS's n-body particles, 
+it is possible to test the validity of the prescription outlined
+in Section \ref{sec:model}. In this section we test reconstruction prescription given perfect
+knowledge of the halos' virial masses and redshifts; this provides us with a measure of the intrinsic uncertainty induced by treating matter as truncated NFW halos. 
+We test the model by comparing $\kappah$ against
+the ray-traced $\kappa$. If the reconstruction process is to be
+succesfull the two quantities should be closely related, although
+we expect $\kappah$ to be offset from $\kappa$ since the former 
+does not include the divergence due to voids.
+Figure \ref{fig:isitbiased} shows that indeed $\kappah$ is a good estimator, regardless of the individual value of $\kappah$.
+At fixed $\kappah$ we find that the scatter in $\kapparay$ grows with $\kappah$; our reconstruction is better at reproducing underdense lines of sight than overdense lines of sight.
 
 \begin{figure}
-\includegraphics[width=\columnwidth]{figs/truncation_scatter.eps}
-\caption[magcut]{The standard deviation in $\kapparec$ minus $\kapparay$ as a function of halo truncation radius in virial radii, using the truncated NFW profile of \citet{BMO}.
-In our models we truncate our halos at 5$R_{200}$}
-\label{fig:ScattervsTruncation}
-\end{figure}
-
-For $\sumkappah$ to provide useful constraints on $\kapparay$, it is important that $\kapparay$ and $\sumkappah$ are as similar as possible.
-Figure \ref{fig:bias} shows that indeed $\sumkappah$ is a good estimator, regardless of the individual value of $\sumkappah$.
-At fixed $\sumkappah$ we find that the scatter in $\kapparay$ grows with $\sumkappah$; our reconstruction is better at reproducing underdense lines of sight than overdense lines of sight.
-
-\begin{figure}
-% \includegraphics[width=\columnwidth]{figs/perfectc.eps}
-\caption[Biased?]{$\sumkappah$ verses $\kapparay$ for 100000 reconstructed lines of sight.
-$\sumkappah$ traces $\kapparay$, but with a non-zero offset which is due to the negative connvergence from voids.
-At fixed $\sumkappah$ the scatter in $\kapparay$ grows with $\sumkappah$.}
+\includegraphics[width=\columnwidth]{figs/cornerplot.eps}
+\caption[Biased?]{$\kappah$ verses $\kappa$ for 100000 reconstructed lines of sight.
+$\kappah$ traces $\kappa$, but with a non-zero offset which is due to the negative convergence from voids.
+At fixed $\kappah$ the scatter in $\kappa$ grows with $\kappah$.}
 \label{fig:isitbiased}
@@
 
-The intrinsic error between the results of the halo based prescription and the raytraced convergence is an unavoidable error, even with perfect knowledge of halo mass and position.
-Before investigating the errors caused by imperfect knowledge of halo mass and redshift, we investigate the errors induced by a magnitude limited reconstruction and a field of view limited reconstruction.
-The halos in our catalogue are given magnitudes by the semi-analytic model of \citet{deLucia+Blaizot2007} and by applying magnitude cuts to our catalogue, we can investigate the scatter caused by unobserved halos.
+%\subsubsection{How does $\gammah$ relate to $\gamma$?}
+
+\subsection{How succesful is the calibration at converting $\kappah$ into $\kappa$?}
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{figs/globaldist.eps}
+\caption[magcut]{Comparison of the global P($\kappa$) from $10^{5}$ lines of sight to $10^{5}$ random samples drawn each from P($\kappax|\{M_{200},z\}$) for a reconstructed lines of sight.
+Red is the global P($\kappa$) and black is a histogram of the samples.
+Given perfect knowledge of halo mass and redshift the reconstruction appears to be correct globally.}
+\label{fig:globaldist}
+\end{figure}
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{figs/where_is_the_kappa.eps}
+\caption[magcut]{Which objects dominate the external convergence for a line of sight?
+From left to right the three figures show the cumulative contribution to convergence from indvidual halos as a function of distance from the line of sight, magnitude and redshift.
+The solid line is the median cumulative contribution, whilst dashed and dot-dashed show the 68 and 95 percent confidence intervals repectively.
+The majority of convergence comes from halos within the central 30 arcseconds.
+The convergence is dominated by halos with $i$ magnitudes between 20 and 24, halos brighter than 20 are rare, whilst fainter halos (at $z<1.4$) must be low mass, so can only contribute to the convergence if they are very close to the line of sight.
+Halos at all redshifts contribute to the convergence but the largest contribution comes from halos with $z \sim z_{\rm source}/2$.}
+\label{fig:where}
+\end{figure*}
+
+Since voids are not included in the halo model approximation $\kappah$ is a biased estimator of $\kappa$, but this can be calibrated for useing the proceedure of Section \ref{subsec:voids}.
+Taking the reconstructed $\kappah$ for $1\times 10^{5}$ lines of sight we form the joint distribution, P$(\kappa,\kappah)$ and marginalize over P$(\kappah)$ to give P($\kappa$).
+We define the bias as the difference between the expectation value of $\kappa$ and the known true value of $\kapparay$ for each Line of sight and we define the reconstruction width, $\sigma_{\kappa}$,as half the width of the interval containing the central $68\%$ of the probability P($\kappax$).
+From $1\times 10^{4}$ reconstructed lines of sight we find the the bias to have mean of $-9.5\times 10^{-6}$ and a mean reconstruction width of 0.0132 which is roughly 1.8 times smaller than the width of the global P$(\kappax)$.
+We find that our $\kappa$ distributions are consistent with the global $\kappa$ distribution; Figure \ref{fig:globaldist} shows that sampling from $\pr(\kappa)$ for 100000 lines of sight is very similar to the global $\pr(\kappa)$.
+Given perfect knowledge of halo mass and redshift, the calibration proceedure provides an unbiased estimate of $\kappa$ that is $\sim$2 times as precise than using the global $\pr(\kappa)$.
+
+\subsection{Which halos dominate the $\kappah$ distribution?}
+
+Before investigating the uncertainties caused by imperfect knowledge of halo mass and redshift, we investigate the uncertainties induced by a magnitude limited reconstruction and a field of view limited reconstruction.
+The halos in our catalogue are populated by galaxies and given magnitudes according to the semi-analytic model of \citet{deLucia+Blaizot2007} and by applying magnitude cuts to our catalogue, we can investigate the scatter caused by unobserved halos.
 The majority of the convergence comes from halos with an $i$ magnitude between 18 and 24.
-Figure \ref{fig:magcut} shows that the width of $\kapparec-\kapparay$ decreases quickly between $i=18$ and $i=24$.
+Figure \ref{fig:where} shows the cumulative contribution to $\kappah$ as a function of projected distance from the line of sight, magnitude and redshift.
+Unsurprisingly we find that most of the convergence comes from halos whose galaxies are close to the line of sight.
+As a function of magnitude, we find that $\kappah$ is dominated by objects with magnitudes between $i=18$ and $i=24$.
 Objects brighter than $i=18$ are either too rare or too close to the observer to make a significant contribution to the convergence.
-Objects fainter than $i=24$ are too small to be important, unless they are extremely close to the line of sight where it is likely that neglecting stellar mass and using a spherical NFW prescription are too naive to adequately reconstruct $\kappax$.
-It is likely that ultra-faint halos (or substructures), the uncertain contribution of voids and halos deviating from our spherical truncated NFW profile are the three major sources of the scatter in $\kapparec-\kapparay$; a deeper survey will not be sufficient to decrease the size of this scatter.
-Since a large number of callibration lines of sight must be reconstructed to sample $\pr(\kappav)$, it may prove unrealistic to reconstruct the calibration lines of sight out to 5 arcminutes.
-Figure \ref{fig:radcut} shows the width of $\kapparec-\kapparay$ as a function of reconstruction radius; in almost all cases there is no significant contribution to $\kappa$ from halos that are centred more than 1 arcminute away, although large groups or clusters can sometimes still make a contribution as far out as four arcminutes.
-For the rest of this work we will continue to model all of the halos out to 5 arminutes with an $i$ magnitude greater than 26, although a reconstruction with fields going out to two arcminutes and down to $i=24$ would do almost as well.
+Objects fainter than $i=24$ are too small to be important, unless they are extremely close to the line of sight, but we find that including including halos fainter than $i=24$ does not improve our reconstruction.
+Figure \ref{fig:magcut} shows the scatter on $\kappah-\kappa$ (where $\kappah$ is shifted so that it's mean is zero) as a function of reconstruction magnitude limit.
+Since these objects must be extremely close to the line of sight to make a non-zero $\kappah$ contribution it is likely that neglecting stellar mass and using a spherical NFW prescription are too naive to adequately reconstruct $\kappax$; thus we do not expect a deeper survey to decrease the size of the uncertainty in mapping $\kappah$ onto $\kappa$.
+We find that halos at all redshifts contribute to the convergence, but halos at redshifts of $z \sim z_{\rm source}/2$ contribute the most.
 
@@
 \includegraphics[width=\columnwidth]{figs/mag_scatter.eps}
-\caption[magcut]{The 16, 50 and 84\% confidence intervals on $\kapparec$ minus $\kapparay$ as a function of the limiting $i$ band depth of the halo reconstruction.
-$\kapparec$ is given by $\sumkappah-\kappav$, where $\kappav$ is a constant such that $\left\langle\kapparec\right\rangle=0$.
-The majority of the constraining power comes from reconstructing halos with magnitudes between $18<i<24$}
+\caption[magcut]{The 16, 50 and 84\% confidence intervals on $\kappah$ minus $\kappa$ as a function of the limiting $i$ band depth of the halo reconstruction.
+$\kappah$ has been shifted such that $\left\langle\kappah\right\rangle=0$.
+The majority of the constraining power comes from reconstructing halos with magnitudes between $18<i<24$.}
 \label{fig:magcut}
 \end{figure}
-\begin{figure}
-\includegraphics[width=\columnwidth]{figs/radius_scatter.eps}
-\caption[radius cut]{The 16, 50 and 84\% confidence intervals on $\kapparec$ minus $\kapparay$ as a function of the limiting radius (in arcminutes) beyond which halos are not reconstructed.
-The majority of the convergence comes from halos centred within an arcminute of the line of sight}
-\label{fig:radcut}
-\end{figure}
-
-The final test that we apply to the perfect knowledge reconstruction is to apply the marginalization outlined in Section \ref{subsec:voids}.
-Taking the reconstructed $\sumkappah$ for $1\times 10^{5}$ lines of sight we form the joint distribution, P$(\kapparay,\sumkappah)$ and marginalize over all sightlines with a similar $\sumkappah$ to give P($\kappax$).
-We define the bias as the difference between the expectation value of $\kappax$ and the known true value of $\kapparay$ for each Line of sight and we define the reconstruction width as half the width of the interval containing the central $68\%$ of the probability P($\kappax$).
-From $1\times 10^{4}$ reconstructed lines of sight we find the the bias to have mean of $-9.5\times 10^{-6}$ and a mean reconstruction width of 0.0132.
-In the case where one assumes P$(\kappax)$ is given by the global P$^{\rm global}(\kappax)$, the same $1\times 10^{5}$ lines of sight show a mean bias of $4.3\times 10^{-5}$ and mean reconstruction width of 0.237.
-Within the statistical error both methods are unbiased, but for any individual line of sight the bias is typically 1.8 times smaller with the reconstructed P$^{\rm reconstruction}(\kappax)$, rather than global P$^{\rm global}(\kappax)$.
 
@@
 Real attempts to reconstruct the convergence along a line of sight will not have direct access to the masses of dark matter halos, 
-and will likely not have access to their spectroscopic redshift either. Instead these properties must be inferred from astrophysical
-observables. In principle the only observables are astrometric positions, photometric colours and possibly spectra. In this section we
+and will likely not have access to a spectroscopic redshift either. Instead these properties must be inferred from astrophysical
+observables. In principle the only observables may be astrometric positions, photometric colours and possibly spectra. In this section we
 quantify the errors induced by inferring the halo mass and redshift from the observables. Much work has already focused on using
-photometric colours to infer stellar mass \citep[\eg][]{xxx} and redshifts \citep[\eg][]{BPZ}, in line with these we shall use
+photometric colours to infer stellar mass \citep[\eg][]{AugerEtal2009} and redshifts \citep[\eg][]{BPZ}, in line with these we shall use
 stellar mass and photometric redshifts (with appropriate errors), as the observables that must be converted into an estimate
@@
 
-We generate a stellar mass for each halo according to the stellar mass--halo mass relation of \citet{BehrooziEtal2010}. From this stellar mass we simulate 
-an observed stellar mass by drawing a sample from $\pr(\log(M_{* \mathrm {obs}})|\log(M_{* \mathrm {true}}))$ which is given by \comments{ the product of the galaxy stellar mass function (GSMF) of \citet{Fontana2006} and} a Gaussian of width $\sigma_{M_*}$ centred on $\log(M*_{\mathrm {true}})$.
-Where a spectroscopic redshift exists stellar masses can be estimated with typical uncertainties of 0.15 dex \citep{xxx}, however with photometric redshifts stellar mass uncertainties are typically three times as large \citep{xxx}; we use $\sigma_{M_*}=0.15$ for halos with a spectroscopic redshift and $\sigma_{M_*}=0.45$ otherwise.
-\comments{The \citet{Fontana2006} GSMF is given by a Schechter function with redshift evolving parameters
+We generate a stellar mass for each halo according to the stellar mass--halo mass relation of \citet{BehrooziEtal2009}. From this stellar mass we simulate 
+an observed stellar mass by drawing a sample from $\pr(\log(M_{* \mathrm {obs}})|\log(M_{* \mathrm {true}}))$ which is given by a Gaussian of width $\sigma_{M_*}$ centred on $\log(M*_{\mathrm {true}})$.
+Where a spectroscopic redshift exists stellar masses can be estimated with typical uncertainties of 0.15 dex \citep{AugerEtal2009}, however with photometric redshifts stellar mass uncertainties are typically three times as large; we use $\sigma_{M_*}=0.15$ for halos with a spectroscopic redshift and $\sigma_{M_*}=0.45$ otherwise.
+For photometric redshift errors we draw a redshift from $\pr(z_{\rm true}|z_{\rm obs})$ which we take as a Gaussian of width $0.1(1+z_{\rm spec})$ centred on $z_{\rm spec}$, where $z_{\rm spec}$ is the halo's true redshift in the \MS catalogue.
+
+Given an uncertain stellar mass and redshift it is possible to infer a halo mass using the stellar mass--halo mass relation of \citet{BehrooziEtal2009}.
+This proceedure requires an inversion of the relation given in \citet{BehrooziEtal2009} and correctly inverting the relation's uncertainties requires care: the proceedure we use to do this is given in Appendix \ref{appendix:MSMH}.
+By drawing sample halo masses and redshifts, we can infer a sample $\kappah$ using the proceedure of Section \ref{sec:model}; repeatedly drawing samples allows us to estimate P$(\kappah)$ for each reconstructed line of sight.
+
+\subsection{Reconstructing $\kappa$ given a spectroscopic redshift for every object}
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{figs/Width.eps}
+\caption[magcut]{The widths of the infered P$(\kappah|\mathcal{D})$ for $10^5$ lines of sight given different amounts of data.
+Blue assumes a spectroscopic redshift for every halo with $i<26$, purple assumes a spectroscopic redshift for every halo with $i<23$ and every within 1 arcminute and $i<24$, cyan assumes a spectroscopic redshift for every halo with $i<22$ and green assumes that no objects in the field have a spectroscopic redshift}
+\label{fig:reconwidths}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{figs/Widthvshilberrt.eps}
+\caption[magcut]{Width of the infered P$(\kappah|\mathcal{D})$ verses the true $\kappa$ along a line of sight.
+Blue assumes a spectroscopic redshift for every halo, whilst green assumes no spectroscopic redshifts.
+The width of the infered P$(\kappah)$ increases with $\kappa$.
+If correctly reconstructed, the lowest density lines of sight can provide the most precise measurement of the time delay distance.}
+\label{fig:widthsvsH}
+\end{figure}
+
+The best possible reconstruction of $\kappah$ corresponds to having a sepctroscopic redshift for every single object in our field.
+Observationally such a reconstruction would be prohibitively expensive in terms of telescope time, but we investigate this scenario as an ideal case.
+Reconstructing the lines of sight with perfect knowledge of the redshift but an uncertain stellar mass, we find that the width of $\Pr\left(\sumkappah \right)$ grows with the expectation value of $\sumkappah$; this is not surprising since the low $\sumkappah$ lines of sight are relatively empty and so there are few opportunities for uncertainties in the halo masses to propogate into $\sumkappah$ uncertainties.
+After applying the void correction the median reconstruction width is 0.0123; with 22 percent of lines of sight having a reconstruction width less than 0.01.
+
+\subsection{Reconstructing $\kappa$ from photometry alone}
+
+Inferring the stellar mass of a galaxy from its magnitude and colours requires an estimate of how far away the galaxy is; without a spectroscopic redshift the the infered stellar mass is less precise.
+However, obtaining photometry has much lower observational cost; over the next few years several large area photometric surveys will reach 24th magnitude \citep{EUCLID,LSST}, these will provide sufficient data to reconstruct lines of sight {\it without} additional observations.
+In principle the photometric redshift is correlated with the infered stellar mass, however we do not model this effect since the convergence from the outskirts of an individual halo is only weakly dependant on redshift at fixed mass: the redshift error is small effect on the recovered $\pr(\kappa)$ when compared to the effect of uncertain stellar masses.
+With only photometric redshifts the uncertainty on $\sum\kapparec^{\rm halos}$ is much larger than the spectrocopic case and this propogates into a broader $\pr(\kappa)$, although the photometric reconstruction still typically produces a 1.4 fold improvement compared to the precision of the global P($\kappa$).
+
+\subsection{Reconstructing $\kappa$ with partial spectroscopic coverage}
+
+Whilst a fully photometric reconstruction provides useful constraints on $\pr(\kappa)$, targeted spectroscopy can provide addtional constraints upon the masses and redshifts of halos whose $\kappah$ contribution have the largest absolute uncertainty.
+Obtaining spectra of bright ($i<22$) objects is relatively fast with 8-m class telescopes; we find that if spectroscopic redhsifts were known for all $i<22$ galaxies in our field the reconstruction improves slightly upon the purely photometric reconstruction, although the improvement depends strongly upon the nature of the particular line of sight.
+Obtaining spectra for fainter objects would be considerably more expensive, but if spectroscopic redshifts could be obtained for all $i<23$ galaxies and all $i<24$ galaxies within 1 arcminute of the line of sight the $\pr(\kappa)$ would be almost as good as having complete spectroscopic coverage.
+High $\kappa$ lines of sight benefit the most from additional spectral coverage, since these LoS have the most uncertain $\kappah$.
+Consistent with our previous findings the lowest $\kappa$ lines of sight have the most constrained $\kappa$ PDFs.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Testing for Systematic errors}
+\label{sec:biases}
+\begin{figure*}
+\includegraphics[width=\textwidth]{figs/biasplots.eps}
+\caption[magcut]{Estimating $\kappa-\kappa_{\rm true}$ from subsets of lenses.
+By subtracting the true (ray-traced) convergence from the infered P($\kappa$) for each line of sight we are left with a PDF that should be estimating zero, these can be multiplied together for multiple lines of sight to test for a possible bias.
+These plots show the expectation value of $\prod_{i=1}^N \pr_i(\kappa-\kappa_{\rm true})$ - deviations from zero can be seen as a bias.
+The solid, dashed and dotted lines are for combining 20, 5 and 2 lenses respectively.
+Green lines are from multiplying P($\kappa$) infered from photometry alone, whilst red lines are from multiplying P($\kappa$) infered from photometry and a spectroscopic redshift for all halos with $i<23$ and all halos within 1 arcminute and $i<24$.
+The left most plot shows randomly selected lines of sight.
+The central plot shows sight lines randomly selected from the third of lines whose P($\kappa$) is most tightly constrained.
+The right hand plot shows only lines of sight with external shear of 0.03 or greater.}
+\label{fig:where}
+\end{figure*}
+
+Whilst it is good to reconstruct $\kappa$ precisely it is vital that $\kappa$ is reconstructed accurately.
+A precise, inaccurate $\kappa$ estimator is worse than useless for cosmology.
+We test the accuracy of our reconstructed $\pr(\kappa)$ in the following way: for each line of sight we shift the reconstructed $\pr(\kappa)$ by the line of sight's raytraced $\kappa$ to give $\pr(\kappa-\kapparay)$.
+Since the $\pr(\kappa-\kapparay)$ for each line of sight is an independant estimator of zero, the PDFs can be combined according to
+
 \be
-\label{eq:GSMF}
-{\dee N \over \dee M_*} \propto \left(10^{(M_*-M_0(z))}\right)^{(1+\alpha(z))} \exp \left(-10^{(M_*-M_0(z))}\right)
-\ee 
-where $M_0(z)=11.16+0.17z-0.07z^2$ and $\alpha(z)=-1.18-0.082z$.} For photometric redshift errors we draw a redshift from $\pr(z_{\rm true}|z_{\rm obs})$ which we take as a Gaussian of width $0.1(1+z_{\rm spec})$ centred on $z_{\rm spec}$, where $z_{\rm spec}$ is the halo's true redshift in the \MS catalogue
-
-For each  source of error, we reconstruct 40000 calibration lines of sight and 10000 mock lens lines of sight, following the proceedure outlined in Section \ref{sec:model}.
-Reconstructing the lines of sight with perfect knowledge of the redshift but an uncertain stellar mass, we find that the width of $\Pr\left(\sumkappah \right)$ grows with the expectation value of $\sumkappah$; this is not surprising since the low $\sumkappah$ lines of sight are relatively empty and so there are few opportunities for uncertainties in the halo masses to propogate into $\sumkappah$ uncertainties.
-After applying the void correction the expected bias from our 10000 mock lenses is $6.7\times 10^{-5}$ and the mean reconstruction width is 0.0145; this is the typical reconstruction error that could be expected from a complete spectroscopic survey of the field, it is ten percent worse than the reconstruction given perfect knowledge of the halo masses and redshifts but still 1.6 times better than using the global P$^{\rm global}(\kappax)$ although a complete spetroscopic survey is still unrealistic.
-The distribution of the widths of $\Pr\left(\kappax \right)$ is shown in Figure \ref{fig:width1}
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{figs/cornerplot.eps}
-\caption{68 \% and 95 \% contours of the joint distribution $\pr(\kapparay, \tilde\kappa_{\rm halos})$ given a mock reconstruction of our 40000 calibration lines of sight.
-$\tilde\kappa_{\rm halos}$ is the median of $\pr(\sumkappah)$ given a spectroscopic redshift for each halo.
-$\kapparay$ and $\tilde\kappa_{\rm halos}$ are strongly correlated, despite the blurring effect of uncertain halo masses.}
-\label{fig:corner}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{figs/widths.eps}
-\caption{Widths of $\pr(\kappax)$ after applying our reconstruction of all halos down $to i=26$ and within 5 arcminutes of the line of sight.
-Results for 10000 lines of sight are shown.
-Green is for a reconstruction given perfect knowledge of halo mass and redshift, blue is for a reconstruction given a spectroscopic redshift for every halo, and red is for a reconstruction with photometric redshifts only.
-The dashed black line shows the width of the global $\pr(\kappax)$ distribution; the reconstruction process provides roughly a factor of 2 improvement for the majority of lines of sight.
-Spectroscopic redshifts improve the reconstruction, but at signifcant observational cost.}
-\label{fig:width1}
-\end{figure}
-
-Inferring the stellar mass of a galaxy from its magnitude and colours requires an estimate of how far away the galaxy is; without a spectroscopic redshift the the infered stellar mass is less precise.
-In principle the photometric redshift is correlated with the infered stellar mass, however we do not model this effect since the convergence from the outskirts of an individual halo is only weakly dependant on redshift at fixed mass: the redshift error is small effect on the recovered $\pr(\kappa)$ when compared to the effect of uncertain stellar masses.
-With only photometric redshifts the uncertainty on $\sum\kapparec^{\rm halos}$ is much larger than the spectrocopic case, but this does not propogate into a much larger bias after applying the void correction; with a purely photometric reconstruction of the 10000 mock lightcones the results have a mean bias of $1.1\times 10^{-4}$ and a mean width of 0.0158.
-On average a purely photometric reconstruction of the field gives an unbiased $\pr(\kappax)$ that is 1.5 times tighter than assuming the global $\pr^{\rm global}(\kappax)$.
-
-%\subsection{Reconstructions of Smaller and Shallower Fields}
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{figs/widths2.eps}
-\caption{Widths of $\pr(\kappax)$ after a photometric reconstruction of all halos within different fields.
-The different field sizes and depths are given in the legend.
-As the field becomes smaller or shallower, fewer halos are being reconstructed and so the width of $\pr(\kappax)$ grows.}
-\label{fig:width2}
-\end{figure}
-
-Reconstructions of real lines of sight may not have access to the deep, large calibration fields that we have used upto this point.
-We can perform the same reconstruction but for a more modest mock survey.
-Given the results of Section \ref{sec:knownMh+z} we predicted that a reconstruction of the field out to 2 arcminutes and a magnitude limit of $i$=24 would provide similar constraints to a reconstruction going out to 5 arcminutes and going down to $i$=26.
-We find the mean reconstruction width to be 0.0163 for a photometric reconstruction of all the halos within 2 arcminutes that have $i<24$, this is only marginally worse than 0.0158 which was the typical width after the deeper and wider reconstruction of the previous section.
-The reconstruction widths for our 10000 mock lens lines of sight are shown in Figure \ref{fig:widths2}.
-If only photometry for halos with $i<24$ and within 1 arcminute of the line of sight is availble then the typical width of the reconstructed $\pr(\kappax)$ is 0.173.
-Whilst a complete spectroscopic survey of a large field would be unlikely, a hybrid strategy of obtaining spectra for a subset of objects may be feasible.
-Photometric redshifts are sufficient to asertain the halos which are likely to contribute most of the convergence on any given line of sight, and on average there are only $\sim 6 \pm 6$ halos per line of sight that individually contribute more than 0.002 to $\sumkappah$.
-We investigate a hybrid strategy of obtaining spectroscopic redshifts for all of the $i<24$ halos which contribute an individual $\kappa$ of at least 0.002 combined with a photometric redshift for all other $i<24$ halos within 2 arcminutes.
-For the hybrid strategy the typical width of the reconstructed $\pr(\kappax)$ is 0.0151.
-The observational cost of obtaining spectroscopic redshifts for several 24th magnitude galaxies may make the hybrid strategy unlikley, but obtaining photometry of a 4$\times$4 arcminute patch of sky down to $i=24$ is fast with modern telescopes.
-The mean reconstruction width for a photometric reconstruction of all the halos within 2 arcminutes that have $i<24$ represents an improvement of 1.5 over using the global $\pr(\kappax)$ and should be achievable at minimal observational cost.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Testing for Systematic errors}
-\subsection{Using the wrong M$_{\rm halo}$-M$_{*}$ relation}
-\subsection{Selecting bias from a subset of lines of sight?}
+\label{eq:bias}
+\mathcal{P}_N=\prod_{i=1}^N \pr_i(\kappa-\kappa_{\rm true})
+\ee
+
+We quantify the bias as the size of the deviation in the expectation value of $\mathcal{P}$ from zero.
+If the bias of $\mathcal{P}_N$ is typically smaller than the half-width of $\mathcal{P}_N$ our $\kappa$ estimators can be considered accurate.
+The number of useful time delay lines of sight can be approximated as the point at which the modulus of the bias and width of $\mathcal{P}_N$ are the same size.
+
+%\todo{tom}{do}
+%\subsection{Using the wrong M$_{\rm halo}$-M$_{*}$ relation}
+\subsection{Selection bias from a subset of lines of sight?}
+
+First we test for systematic errors in the reconstruction of a randomly selected subset of samples.
+With the purely photometric reconstruction there is a small bias towards underestimating $\kappa$,  combining 6 lenses the half-width and bias of $\mathcal{P}_{6}$ both equal 0.007.
+With targeted spectroscopic follow up this improves slightly, for the combination of 8 lenses the half-width and expectation value  $\mathcal{P}_{8}$ equal 0.005.
+Since strong lens modelling uncertainties are typically at the 3\% level, several hundred lenses are needed to reach this level of precision, but at that point a 0.005 bias in $\kappa$ estimation would become the limiting factor on time-delay cosmography.
+
 \subsubsection{Selecting only the lines of sight with tight $\pr(\kappax)$}
+\label{sec:tightPDF}
+
+Since lens monitoring campaigns are expensive, it is likely that only a subset of lenses will be observed.
+By pre-selecting the lenses with the most well constrained $\pr(\kappax)$, the cosmological value per lens can be increased, however this has the potential to induce a bias.
+It is probable that only photometry will be available at the time of lens selection (although spectroscopic follow-up might be conducted at a later date).
+We mimik such a selection by drawing lines of sight only from those in the lowest third of $\sigma_{\kappa}$ given a photomtric reconstruction of their fields.
+We find that selecting the most tightly constrained lines of sight {\it decreases} the bias - our reconstruction is most succesful for the lowest $\kappa$ lines of sight.
+With photometry alone the bias is at the 0.0028 level.
+With a targeted spectroscopic follow-up of the selected lines of sight there is negligible improvement, since the best constrained lines of sight are the most empty, but it is the high-$\kappa$ lines of sight that benefit the most from spectroscopy.
+Photometry of the field is sufficient to adequately select the best lines of sight for cosmology - and doing so greatly increases both the precision and accuracy of the cosmological constraints per lens.
+
 \subsubsection{Selecting only high shear lines of sight}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\comments{
-
-\subsection{Comparison with Other Treatments of $\kappax$}
-\label{sec:Dt:selection}
-
-\phil{How does distance accuracy compare with simple averaging? eg assuming
-$\kappax = 0$ for all lenses. How does it compare with the no data situation?
-eg where the intrinsic distribution of kappa is used as $Pr(\kappax)$.}
-
-What is the expected bias and scatter (centroid position and width) of P(D) as a
-function of N lenses? How does reconstruction compare with P(D) derived using
-P(kappa|N45) for each lightcone? How does reconstruction compare with P(D)
-derived assuming kappa=0 for each lightcone?
-
-Also: compare with simple averaging. This will fail if lenses are selected to
-live on over-dense lines of sight. Stefan's plot in Suyu et al shows effect of
-selection - what is the resulting bias? Few percent? This is the target to beat,
-need to find it out.
-
-\subsection{Improving the Accuracy with More Information}
-\label{sec:Dt:selection}
-
-\phil{How does distance accuracy improve with:}
-\begin{itemize}
-\item Spectroscopic coverage? For galaxies above some mlim? For targets with
-high kappa contribution (based on photometry)?
-\item IR coverage for all objects? Improves photo-z and Mstar.
-\item Including shear information from lens model? Assume accurate but
-uncertain extertanl shear.
-\end{itemize}
-}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\todo{phil}{Write up why lenses are likely to be gamma biased}
+\notes{The uncertainties from modeling a strong lens system depends on the comfiguration of the source images.
+With only two point images ofthe source the lens slope and mass are degenerate; the mass-slope degeneracy\citep{mass-slope degeneracy} cite saha?.
+Where lensed arcs or four point images are present the mass-slope degeneracy can be broken and cosmology can be extracted, \citep{Suyu2012a}.
+The detectability of arcs depend on the source, but the presence of four images (so called quads) depend on the shear of the lens model - a high shear is needed to produce a quad.
+The shear is almost certainly dominated by the lens model itself, but it is possible that quads are biased towards high external shear.}
+
+By selecting only lines of sight with an external shear of $\gamma>0.03$ we can test the effect of shear selection.
+We find that in all cases $\kappa$ is underestimated at the $\sim$0.01 level.
+Part of this effect is mitigated if only the lines of sight with both $\gamma>0.03$ and sharp $\pr(\kappax)$ are used but biases at the $\sim$0.005 level remain.
+Since our model does not include shear constraints it is not surprising that selecting based on shear can induce a bias.
+A more sophisticated model that includes the shear recovered from the lens modelling may not be susceptable to this bias.
+The toy model of this section ($\gamma>0.03$) is likely to be a much stronger selection than reality, but it is worth noting that the reconstruction proceedure will be biased if lens selection functions are extreme and unaccounted.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\section{Improving precision by including additional information}
+%\notes{placeholder for shear}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-We have shown that reconstructing the matter due to halos along any line of sight can give meaningful and unbiased constraints on the external convergence along that line of sight.
-The total convergence along a line of sight is strongly correlated with the reconstructed $\sumkappah$.
-However since our model ignores voids and assumes all halos follow a spherical truncated-NFW profile our model does not include all of the relevant physics, hence the width of our resulting $\pr(\kappax)$ is still typically $\sim$0.01, even with a perfect knowledge of every halo's virial mass and redshift.
+We have shown that reconstructing the matter due to halos along any line of sight can improve the constraints on the external convergence along that line of sight.
+The total convergence along a line of sight is strongly correlated with the reconstructed $\kappah$.
+However since our model ignores voids and assumes all halos follow a spherical truncated-NFW profile our model does not include all of the relevant physics, hence the width of our resulting $\pr(\kappax)$ is still typically $\sim$0.01 for any given lightcone, even with a perfect knowledge of every halo's virial mass and redshift.
 To make further progress a more advanced treatment of both voids and halos will be necessary.
@@
 $\kappax$ for empty lines of sight have little contributions from halos and a large contribution from voids; since they have the tightest PDFs after the reconstruction it seems that our model's biggest uncertainties are driven by naively reconstructing halos rather than neglecting voids.
-With a photometric reconstruction of the field there is only a small broadening compared to the perfect knowledge reconstruction; it seems that deviations from sphericity and dark matter clumping within the main halo are the dominant uncertainies rather than uncertainties in the halo mass.
-Inferring halo ellipticity and dark matter clumping will likely always remain a difficulty for line of sight reconstruction; as Figures \ref{fig:magcut} and \ref{fig:width2} show observing deeper than 24th magnitude does not signifcantly help the reconstruction.
+With a photometric reconstruction of the field there is a significant broadening but the resulting precision is still typically 1.5 times greater than using the global $\kappa$ distribution.
+
+Since the uncertainty on $\pr(\kappa|\mathcal{D})$ is $\sim$0.01 even with perfect knowledge of halo mass and redshift it seems that voids (plus deviations from sphericity and dark matter clumping within the main halo) dominate the total $\kappa$ uncertainty even with very uncertain stellar masses.
+Inferring halo ellipticity and dark matter clumping will likely always remain a difficulty for line of sight reconstruction; but as Figure \ref{fig:magcut} shows observing deeper than 24th magnitude does not signifcantly help the reconstruction.
 Because our reconstruction is mostly limited by the model, spectroscopic coverage can only provide a modest improvement to the reconstruction and at significant observational cost.
@@
 If a line of sight has a broad $\pr(\kappax)$ it can be rejected {\it before} the investment of longterm lightcurve monitoring.
+We find that selecting only the lines of sight with the most tightly constrained $\pr(\kappax)$ does not induce a bias.
 
@@
 gave a significantly different $\pr(\kappax|\gamma,N_{45})$ copmpared to the
-PDFfrom number count overdensity alone, $\pr(\kappax|N_{45})$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+PDF from number count overdensity alone, $\pr(\kappax|N_{45})$. Whilst not included
+in this paper, we found that given perfect knowledge of the halo mass and redshift
+the raytraced external shear $\gamma$ and the reconstructed external shear $\gamma_{\mathrm{h}}$ 
+are similar, with 68 percent of lines obeying
+\be
+\label{eq:shearineq}
+|{\boldmath{\gamma}-\boldmath{\gamma_{\mathrm{h}}}}| < \mathrm{0.025}
+\ee 
+Future work should investigate whether $\gamma_{\mathrm{h}}$ can be used to improve
+the accuracy and precision of $\kappa$ estimation, given a reconstruction
+ of the line of sight.
+
+This work has used the \MS as a calibration guide. If the real universe is not like 
+the \MS the the calibration will be incorrect - repeating the study with a different
+simulation would quantify the sensitivity of our results to the simulation used. Similarly
+the use of a different semi-analytic model to paint galaxies onto halos could provide
+a useful check, to ensure against potential systematic errors.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 each dark matter halo and neglects voids, but despite the model's simplicity
-the reconstructed $\sumkappah$ is a good tracer of $\kappax$.  We found that
+the reconstructed $\kappah$ is a good tracer of $\kappa$.  We found that
 with perfect knowledge of the halo mass and redshift (from the Millenium
-Simulation catalogs), the reconstruction gives an unbiased estimate of
-$\pr(\kappax)$ for a single line of sight that is almost almost a factor of 2
-less broad than the global $\pr(\kappax)$.
+Simulation catalogs), for a typical line of sight the reconstruction
+gives an unbiased estimate of $\pr(\kappa)$ that is a factor of 2
+less broad than the global $\pr(\kappa)$.
 
@@
 time is invested it will be possible to discard the most uncertain lines of
-sight and prevent the waste of follow-up time.
-
-\item With complete spectroscopic redshift coverage and just an empirical
-stellar mass to halo mass relation, we find that the median of
-$\pr\left(\sumkappah\right)$ is a useful indicator for generating an estimate
-of $\pr(\kappax)$ from the ensemble of simulated lines of sight. The resulting
-PDF tends to be around 10\% broader than it would have been given perfect
-knowledge of both halo mass and redshift; given only photometric redshifts
-(which in turn give rise to much less certain stellar masss estimates) causes
-another $\sim$10\% increase to the width of $\pr(\kappax)$.
+sight and optimize the use of follow-up time. Photometric data is sufficient 
+to select the best lines of sight for follow-up.
+
+\item With uncertain halo masses and redshifts, we find that
+$\pr(\kappah)$ is still a useful indicator for generating an estimate
+of $\pr(\kappa)$ from the ensemble of simulated lines of sight, but the resulting
+PDFs tend to be much broader than for perfect
+halo mass and redshift reconstructions. Spectroscopic coverage helps to tighten 
+$\pr(\kappa)$ for high $\kappa$ lines of sight, but is of limited use for 
+low $\kappa$ lines of sight.
 
 \item It is very rare for halos further than 2 arcminutes to make a
-significant contribution to $\kappax$. We also found that including halos
+significant contribution to $\kappa$. We also found that including halos
 whose host galaxy is less luminous than $i=24$ does not significantly improve
@@
 uncertainties of our simple reconstruction recipe, and yield a 
-$\pr(\kappax)$ that has, on average, a width of 0.0163 --
-50\% less broad than the global $\pr(\kappax)$.
-
-\item We find that the lines of sight with the sharpest $\pr(\kappax)$ are
+$\pr(\kappa)$ that has, on average, a width of 0.016 --
+1.5 times less broad than the global $\pr(\kappa)$.
+
+\item We find that the lines of sight with the sharpest $\pr(\kappa)$ are
 typically under-dense. With a photometric reconstruction of all lens fields,
-and following up only the lenses with the most constraining $\pr(\kappax)$,
+and following up only the lenses with the sharpest $\pr(\kappa)$,
 the width of the dominant statistical uncertainty in time-delay cosmography
-can be halved, whilst at the same time decreasing any potentail for a
-systematic error due to lenses being biased in $\kappax$.
+can be halved, without inducing biases at the one percent level.
 
@@
 
-\todo{Tom}{Add more conclusions about bias in a large sample of lenses...}
-
-\todo{Tom}{Wrap up}
-
-%Our conclusions can be summarised as follows:
-%\begin{itemize}
-%\item With perfect 
-%\item And we found this too.
-%\end{itemize}
-
-% \item Faint galaxies and other dark structures will not appear in a photometric
-% object catalog, but they will contribute convergence at some level. How much of
-% the total external convergence in a time delay lens system comes from visible
-% galaxies? How does this change as a function of magnitude cut?
-
-% \item Can the true (ray-traced) convergence be recovered by halo model
-% reconstruction, and with what scatter and residual bias? Which aspects of the 
-% model dominate these uncertainties?
-
-% \item When faced with a newly-detected lens, surrounded by galaxies on the sky,
-% we have some choices to make when planning follow-up observations.
-% Which are the most important galaxies, with regard to the external convergence
-% produced? Can nearby groups and clusters be straightforwardly accounted for? If
-% lenses with such massive structures nearby are discarded, what impact does that
-% have on the distance accuracy?
+External convergence is not the only uncertainty in time delay cosmology,
+but for systems like B1608 it is the dominant one. For most lines
+of sight it is likely that lens modelling induces uncertainties at the
+$\sim$3 percent level, which far exceeds the typical $\kappa$ uncertainties
+after applying our reconstruction proceedure. By using our method to
+reconstruct lines of sight and select which lense are followed-up, the
+uncertainties due to line of sight convergence will become a sub-dominant 
+source of error.
 
@@
 We thank Risa Wechsler and Peter Behroozi for useful discussions and 
-suggestions.
+suggestions.\notes{do we?}
 \input{acknowledgments.tex}
@@
 \appendix
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Truncated NFW halos}
-\label{appendix:halos}
-
- Defining $x$ as the dimensionless projected radial distance $R/r_{s}$ and $\tau$ as the dimensionless truncation radius $r_{t}/r_{s}$, \citet{BMO} derives the projected mass density, which is given by:
-\begin{align}\label{eq:kappaBMO}
-\Sigma_{\rm}(x) = {2\tau^2 \over (\tau^2+1)^2}\left(
-        {\tau^2+1\over x^2-1}\left(1-\mathcal{F}(x)\right)
-        +
-        2\mathcal{F}(x)\right.\nonumber\\
-        -
-        \left. {\pi \over \sqrt{\tau^2+x^2}}
-        +
-        {(\tau^2-1)\mathcal{L}(x,\tau)
-        \over
-        \tau\sqrt{\tau^2+x^2}}\right)
-\end{align}
-where $\mathcal{F}(x)$ and $\mathcal{L}(x,\tau)$ are defined as
-\be\label{eq:F} 
-\mathcal{F}(x) \equiv \begin{cases}  \frac{{\rm cos}^{-1} (1/x)}{\sqrt{x^2-1}} \hspace{0.2cm} & (x>1) \\
-\\
-\frac{4-x^2}{3}  & (x=1)\\
-\\
-\frac{ {\rm cosh}^{-1} (1/x)}{\sqrt{1-x^2}} & (x<1)
-\end{cases}
-\ee
-\be\label{eq:L}
-\mathcal{L}(x,\tau) = \ln\left(\frac{x}{\sqrt{\tau^2+x^2}+\tau}\right)
-\ee
-%the convergence is given by $\Sigma_{\rm BMO}(x) / \Sigma_{\rm cr}(z)$.
 
@@
 
-Given a noisy estimate of the stellar mass $\Mstarobs$ of a galaxy at redshift
-$z$, how can we infer the galaxy's halo mass? We then seek the posterior
-PDF $\Pr(\Mhalo|\Mstarobs)$, which can be expanded as follows:
+To estimate the convergence caused by a halo we need to know its mass; how can 
+halo mass be infered from a noisy estimate of the stellar mass $\Mstarobs$
+of a galaxy at redshift $z$. We seek the posterior
+PDF $\Pr(\Mhalo|\Mstarobs,z)$, which can be expanded as follows:
 
@@
 function for the observed stellar mass. Note that the ``true'' $\Mstar$ of the
-galaxy is marginalised out: we are only interested in reconstructing the halo
+galaxy is marginalised out: we are only interested in infering the halo
 mass. The last two terms in
@@
 
-\todo{Matt}{Edit the above text to add a note on how we do the sampling in
-practice, via the CDF.}
-
 If the redshift of the galaxy is uncertain, we need to take this uncertainty
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Accounting for uncatalogued low mass halos, and voids}
-\label{appendix:smooth}
-
-Our halo model allows us to infer a halo mass $\Mhalo$ for each galaxy in a
-photometric catalog; under the weak lensing approximation described in
-\Sref{sec:theory} we can compute the contribution of each of these halos to
-the overall convergence and shear amplitude, assuming a homogeneous
-Friedman-Robertson-Walker metric and the concordance $\Lambda$CDM cosmological
-parameters for the angular diameter distances to calculate the critical
-density for each lens plane. Clearly this approach will tend to over-estimate
-the convergence, since we are placing massive halos into a volume that has
-already been assumed to be full of homogeneously distributed matter with the 
-mean cosmological density. In practice, the space between massive halos will
-contain a) low mass halos that are not bright enough to be detected and b)
-empty space where the density is below that of the mean. A rigorous treatment
-of this complex situation is beyond the scope of this paper, but is being
-investigated (Blandford et al, in preparation). In this appendix we describe
-our empirical approach to accounting for the missing mass and voids.
-
-Let the summed convergence due to halos in our galaxy catalog be $\kappah$.
-Given some assumptions about halo density profile and shape, this parameter
-can be inferred from a set of uncertain halo mass estimates (which have in
-turn been inferred from noisy measurements of galaxy redshift and stellar mass
-as described in \Aref{appendix:MSMH}). We assume each halo to be a
-spherically-symmetric NFW profile, and neglect the contribution of the stellar
-mass to the convergence. The halo mass inference for the $k^{\rm th}$ galaxy 
-is stored as a list of sample values of $\Mhalok$ drawn from the posterior PDF
-$\Pr(\Mhalok|\Mstarobsk,z_k)$; computing the contribution to the convergence
-due to this halo at the target line of sight for each sample gives, in turn, 
-a set of
-samples drawn from the PDF $\Pr(\kappahk|\Mstarobsk,z_k)$. We then generate
-samples from $\Pr(\kappah|\{\Mstarobsk,z_k\})$ by drawing a sample $\kappahk$
-for each halo, summing over halos to get $\kappah$, discarding those
-samples and moving down the lists.
-
-The PDF $\Pr(\kappah|\{\Mstarobsk,z_k\})$ will, in general, be broad (due to
-the uncertainties involved in halo mass estimation). It will also be shifted
-towards high values of convergence, due to the FRW approximation described
-above. What we really want is an inference of $\Pr(\kappa|\{\Mstarobsk,z_k\})$
-instead. We can obtain this by considering the expansion:
-\begin{equation}
-\Pr(\kappa|\{\Mstarobsk,z_k\}) = \int d\kappah 
-   \Pr(\kappa|\kappah) \Pr(\kappah|\{\Mstarobsk,z_k\})
-\label{eq:kappaconv}   
-\end{equation}
-The first term in the integrand relates the summed  convergence due to model
-halos, $\kappah$, to the true summed convergence, $\kappa$.  In the Millenium
-Simulation catalogs, we can compute a single value of $\kappah$ for each
-selected line of sight from the true halo mass and redshift (and our same
-assumptions of halo profile and shape), and tabulate the two-dimensional PDF
-$\Pr(\kappa|\kappah)$ as a sequence of one-dimensional PDFs for $\kappa$ in a
-bin at fixed $\kappah$. Note that this PDF captures the ``intrinsic scatter''
-of $\kappah$ due to our assumptions about the clumpiness of mass in the
-Universe; the integral combines these uncertainties with those
-arising from the measurement of $\Mstarobs$ and~$z$.
-
-For any given observed catalog then, we infer
-$\Pr(\kappah|\{\Mstarobsk,z_k\})$ as described above, and then
-multiply it by $\Pr(\kappa|\kappah)$; we
-again do the marginalisation over $\kappah$ by Monte Carlo, drawing samples
-from the two-dimensional grid and keeping only the $\kappa$ values, to form
-our final result, $\Pr(\kappa|\{\Mstarobsk,z_k\})$. 
-This PDF will describe, by construction, an accurate (i.e., unbiased)
-measurement of $\kappa$ in the case where the Millenium Simulation halo
-catalog and Behroozi et al $\Mstar-\Mhalo$ relation are themselves accurate
-descriptions of galaxies and their distribution. In \Sref{sec:tests} we
-investigate the amplitude of the systematic errors incurred if these
-assumptions are not valid.
-
-\todo{Matt}{Add text describing whatever sampling shortcut you derive! :-)}
-
-% Finally, we note that \Eref{eq:kappaconv} and the method for evaluating the
-% integral in it can be generalized to yield 
-% $\Pr(\kappa,|\gamma||\{\Mstarobsk,z_k\})$, where $|\gamma|$ is the amplitude
-% of the complex shear. The amplitude of the shear due to halos, $|\gammah|$ is
-% needed in this calculation, and marginalised over -- $\gammah$ is computed by
-% simple summation of its components, as in \Sref{sec:theory}. In
-% \Sref{sec:includinggamma} we explore the impact that knowing $\gamma$ (from,
-% for example, a strong lens model)  has on the inference of $kappa$, and how
-% severe the systematic errors from getting this wrong might be.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %  REFERENCES

### 2012-10-30 doc/paper-lcr.tex
working on intro

@@
 %
-% Pangloss: Testing the reconstruction paper
+% Pangloss: Testing the reconstruction method
 %
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \title[Line of Sight Mass Reconstruction]
-{Inferring Lensing Mass in the Universe \\
+{Reconstructing the Lensing Mass in the Universe \\
 from Photometric Catalog Data}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \begin{abstract}
+
+\todo{PJM}{Make abstract match conclusions.}
+
 Strong gravitational lenses can provide high precision cosmological distance
@@
  $\Pr(\kappa)$ can be formed before the investment of light-curve monitoring: by following up only the 
-most costrained lines of sight a factor of 2 improvement over the global $\pr(\kappax)$ should be 
+most constrained lines of sight a factor of 2 improvement over the global $\pr(\kappax)$ should be 
 achievable.
+
 \end{abstract}
@@
 
-Every distant object we observe has had its shape distorted, and size
-and total brightness magnified (or demagnified) by a compound lens constructed
-from all the mass distributed between us and it. As \citet{Vale+White2003} and \citet{HilbertEtal2007}
-showed, there are no empty lightcones in our universe. This fact makes gravitational lensing a potentially important source of systematic error for any estimate of luminosity or distance, an issue
-raised for \eg type Ia supernovae by \citet[][]{Holz+Wald1998,Linder+Holz2004}, for
-gamma ray bursts by \citet[][]{Oguri+Takahashi2006,Wang+Dai2011}, 
-and for high redshift galaxies by \citet{BradacEtal2009}, among others.
+Every distant object we observe has had its apparent shape distorted,
+and size and total brightness magnified (or demagnified) by a compound
+weak gravitational lens constructed from all the mass distributed
+between us and it. As \citet{Vale+White2003} and \citet{HilbertEtal2007}
+showed, there are no empty lines of sight through our universe. This
+fact makes gravitational lensing a potentially important source of
+systematic error for any estimate of luminosity (or distance), an issue
+raised for \eg type Ia supernovae by
+\citet[][]{Holz+Wald1998,Linder+Holz2004}, for gamma ray bursts by
+\citet[][]{Oguri+Takahashi2006,Wang+Dai2011},  and for high redshift
+galaxies by \citet{BradacEtal2009}, among others.
 
-Along lines of sight containing strong gravitational lenses,
-the effect has been found to be
-particularly important, with foreground and background structures
+Along lines of sight containing strong gravitational lenses, the
+perturbative effects of line of sight mass structure have been found to
+be particularly important, with foreground and background structures
 having a significant effect on the inferred lensing cross-section
-\citep[\eg][]{WongEtal2012} and distance ratios \citep[][]{DalalEtal2005}.
-\citet{SuyuEtal2010} found that in time delay lens cosmography the
-lensing effect of mass structures along the (unusually over-dense) line of
-sight to the quadruply-imaged radio source B1608$+$656, the so-called ``external
-convergence'' $\kappax$, was the dominant source of uncertainty in 
-their 6\% measurement of Hubble's constant.
+\citep[\eg][]{WongEtal2012} and distance ratios
+\citep[][]{DalalEtal2005}. Indeed, \citet{SuyuEtal2010} found that in
+time delay lens cosmography the so-called ``external convergence''
+$\kappa$ due to mass structures along the (unusually over-dense) line
+of sight to the quadruply-imaged radio source B1608$+$656 was the
+dominant source of uncertainty in their 6\% measurement of Hubble's
+constant. The problem is that one simply doesn't know how magnified and
+distorted the source has been, because the unlensed source is
+unobservable. The external shear can potentially be recovered in the
+mass-modelling of the lens, but the convergence is undetectable from the
+image positions, shapes and relative fluxes; this is the famous {\emph{ 
+mass sheet-degeneracy}} \citep[see e.g.][for details]{FalcoEtal1985}.
 
-The problem is that one simply doesn't know
-how magnified and distorted the source has been because the unlensed
-source is unobservable. The external shear can potentially be recovered
-in the mass-modelling of the lens, but the convergence is undetectable
-from the image positions, shapes and relative fluxes; this is the
-famous {\emph{  mass sheet-degeneracy}} \citep[see e.g.][for details]{FalcoEtal1985}.
+How can we correct for this perturbative lensing and make accurate
+measurements through the Universe? When inferring global quantities
+(such as the cosmological parameters), combining the results from a
+large number of independent objects will tend to reduce the uncertainty
+due to external convergence, as the ensemble-averaged magnification
+approaches zero for an unbiased sample \citep[\eg][]{Holz+Linder2005}.
+If the sample is biased, however, some residual systematic error will
+remain even as the statistical uncertainty decreases. Lensing bias will
+be present (to varying degrees) in any sample {\it selected} by
+brightness (which includes magnification), or any other quantity that
+depends on $\kappa$. This bias may be introduced either at the object
+detection stage, or later on when making decisions about which objects
+to study further.  Moreover, we expect these biases to be strongest in
+the strong lens systems, where magnification is highest. Large samples
+of lenses are expected to be discovered in the next decade in
+ground-based optical imaging surveys \citep{Oguri+Marshall2010}: both
+the detectability of these lenses,  and the selection of sub-samples of
+them for further observation, could be sensitive to the external
+convergence.
 
-How can we correct for this perturbative lensing and make
-accurate measurements through the Universe? When inferring global quantities
-(such as the cosmological parameters), averaging the results from a large
-number of independent objects will tend to reduce the uncertainty, as the
-ensemble-averaged convergence approaches zero for an unbiased sample
-\citep[\eg][]{Linder+Holz2004}. If the sample is biased, however, some
-residual systematic error will remain while the statistical uncertainty
-decreases -- and this will be the case for any sample selected by the
-brightness of the lensed object, or any other quantity that depends on
-$\kappa$. Large
-samples of lenses are expected to be discovered in the next decade in
-ground-based optical imaging surveys \citep{Oguri+Marshall2010} -- but these
-samples will be image separation-limited, due to the surveys' relatively poor
-($\sim 1$~arcsec) image quality. There is a possibility that
-they are somewhat biased towards high values of $\kappa$, although 
-\citet{Fassnacht+Lubin2002} \todo{Anyone}{check this is the right Fassnacht paper} found no evidence of lenses lying along over-dense lines of sight.
+Several attempts have been made to do better than simply constructing a
+large sample of objects, and averaging over the resulting convergence
+distribution. The weak lensing effect can be detected by measuring the
+small distortions it induces on the images of many background galaxies
+in the field. \todo{PJM}{Write about Bernstein project in 0957.}
+
+\todo{PJM}{Rearrange following section. After lunch.}
 
@@
 
-Given an uncertain stellar mass to halo mass conversion, the $\pr(\kappah|\{\Mstar,z\})$ can shift 
-relative to $\pr(\kappah|\{\Mhalo,z\})$; this is because of the highly asymetric conversion from
-stellar mass through halo mass into $\kappah$. If this shift is ignored the resulting $\Pr(\kappa)$
-can become highly biased. To calibrate this effect we reconstruct each of our calibration
-sightlines, in the same way as the observed sightlines to generate
- $\pr(\kappa,\kappah|\{\Mstar,z\})$, for each calibration sightline we use the median of $\pr(\kappah|\{\Mstar,z\})$ to form a de-biased $\Pr(\kappa|\kappah)$.
+Given an uncertain stellar mass to halo mass conversion, the
+$\pr(\kappah|\{\Mstar,z\})$ can shift  relative to
+$\pr(\kappah|\{\Mhalo,z\})$; this is because of the highly asymetric
+conversion from stellar mass through halo mass into $\kappah$. If this shift
+is ignored the resulting $\Pr(\kappa)$ can become highly biased. To calibrate
+this effect we reconstruct each of our calibration sightlines, in the same way
+as the observed sightlines to generate $\pr(\kappa,\kappah|\{\Mstar,z\})$, for
+each calibration sightline we use the median of $\pr(\kappah|\{\Mstar,z\})$ to
+form a de-biased $\Pr(\kappa|\kappah)$.
 

### 2012-10-30 doc/paper-lcr.tex
intro done, moving on

@@
 small distortions it induces on the images of many background galaxies
-in the field. \todo{PJM}{Write about Bernstein project in 0957.}
+in the field \citep[see e.g.][for a review]{SaasFee2006}. In a 30''
+radius aperture around the strong lens Q0957$+$561,
+\citet{NakajimaEtal2009} used deep HST imaging to measure a weak lensing
+convergence of $0.17/pm0.06$, which was used in the time delay distance
+measurement of \citep{FadelyEtal2009}. While this system has an
+unusually high external convergence due to its location on the edge of a
+cluster of galaxies, the precision with which the convergence at the
+lens position can be estimated is indicative of what can be achieved
+with high quality weak lensing shear data. We note that this uncertainty
+is not dependent on the value of the convergence, but instead depends
+primarily on the number density of weakly lensed, measurable galaxies
+available.
 
-\todo{PJM}{Rearrange following section. After lunch.}
+In order to make more precise estimates of the convergence at a given
+sky position, we need more information.   There have been some attempts
+to reconstruct the local and line of sight mass distribution in strong
+lens fields in some detail, based on photometric and spectroscopic
+surveys of the galaxies nearby. These efforts have focused on  detecting
+galaxy groups, ascertaining the visible galaxies' membership of those
+groups, and assigning mass to the group and galaxy halos in order to
+predict the external shear apparently required by the strong lens
+models. Surveys by
+\citet{Fassnacht+Lubin2002,AugerEtal2007,WilliamsEtal2006,MomchevaEtal2006}
+all found groups of galaxies both hosting, and lying  along the line of
+sight to, known gravitational lenses. Initial estimates of the effect of
+these structures suggested the importance of assigning mass to both
+galaxy and group halos, and to allowing for significant uncertainty in
+the centroids of group halos.
 
-To date, attempts at reconstructing the local and line of sight mass
-distribution in strong lens fields (what \citeauthor{WongEtal2011} call ``the
-full environment'') have focused on photometric and  spectroscopic surveys to
-detect galaxy groups and ascertain galaxies' membership in order to understand
-the external shear apparently required by the strong lens models. Surveys by
-\citet{Fassnacht+Lubin2002,AugerEtal2007,WilliamsEtal2006,MomchevaEtal2006}
-all found groups of galaxies both hosting and lying  along the line of sight
-to known gravitational lenses. Initial estimates of the effect of these
-structures suggested the importance of assigning mass to both galaxy and group
-halos, and to allowing for significant uncertainty in the centroids of group
-halos. The probability density function (PDF) for the external convergence for
-that lens, $\Pr(\xkappa)$, is the target for any reconstruction analysis, and
-is the key quantity for any ensemble analysis, since by marginalising over it
-we can correctly propagate the uncertainties due to line-of-sight perturbations. Coming
-closest to estimating this quantity from survey data, \citet{WongEtal2011} ran
-Monte Carlo reconstructions of the mass in nine lens fields based on
-\citeauthor{WilliamsEtal2006} and \citeauthor{MomchevaEtal2006}'s
-photometric and spectroscopic measurements of galaxies close to the line of
-sight, and compared the resulting predicted shear distributions with the
-external shear demanded by the strong lens model. Their reconstructions show most
-of the shear being generated by bright galaxies within 2~arcminutes of the
-lens, and that both line of sight structures and the group of galaxies in each
-lens plane contribute significant proportions of the shear. They find
-significant discrepancies between the lens model shear and the Monte Carlo
-predictions, and are unable to distinguish between the environment modelling
-and the strong lens modelling as the cause of these discrepancies.
+The probability density function (PDF) for the external convergence
+given our available data $\data$, $\Pr(\xkappa|\data)$,  is the  key
+quantity we seek, since by marginalising over this distribution we can
+correctly propagate the uncertainties due to line-of-sight perturbations
+(as \citeauthor{FadelyEtal2009} did).
+\citet{WongEtal2011} came close to estimating this quantity from their
+survey data, running Monte Carlo reconstructions of the mass in nine
+lens fields based on \citeauthor{WilliamsEtal2006} and
+\citeauthor{MomchevaEtal2006}'s photometric and spectroscopic
+measurements of galaxies close to the line of sight, and comparing the
+resulting predicted shear distributions with the external shear demanded
+by the strong lens model. Their reconstructions showed most of the shear
+to have been generated by bright galaxies within 2~arcminutes of the
+lens, and that both line of sight structures and the group of galaxies
+in each lens plane contribute significant proportions of the shear. They
+found significant discrepancies between the lens model shear and the
+Monte Carlo predictions, but were unable to distinguish between the
+environment modelling and the strong lens modelling as the cause of
+these discrepancies.
 
-These observational investigations have provided very useful insight into the
-problem.  Coming from a more theoretical direction, large numerical
-simulations have been used to predict, from first principles, the distribution
-of likely external shears and convergences along strong lens lines of sight. 
-\citet{Holder+Schechter2003} and \citet{Dalal+Watson2004}\todo{phil}{Dalal+Watson2004 doesn't seem to exist} carried out
-ray-tracing calculations in N-body simulations to estimate the  distribution
-of external shear values.  \citet{HilbertEtal2009} performed similar ray-tracing
-experiments through the Millenium Simulation \citep{SpringelEtal2005},
-generating a predicted $\kappa$ at every position in a simulated sky. \citet{HilbertEtal2009}
-found that \MS lines of sight with strong lenses were not biased towards high $\kappa$,
-although selection functions for discovering a strong lens were not taken into account.
-The first step towards using this excellent calibration resource was taken by
-\citet{SuyuEtal2010}, who selected Millenium Simulation lines of sight that
- had comparable apparent galaxy
-overdensity in a 45 arcsec radius aperture down to $i < 24.5$. This overdensity
-could be compared to the overdensity of the B1608$+$656 line of sight
-\citep{FassnachtEtal2011}, and hence an estimate of  $\Pr(\kappa)$ could be
-made. B1608$+$656 is indeed a high $\kappa$ line of sight, but it does not reside
-in a typical lens environment.
+These observational investigations have provided some very useful
+insight into the problem of convergence estimation.  Coming from a more
+theoretical direction, large numerical simulations have been used to
+predict, from first principles, the distribution of likely external
+shears and convergences along various lines of sight, including those
+containing strong lens systems.  \citet{Holder+Schechter2003} and
+\citet{DalalEtal2005} carried out ray-tracing calculations in N-body
+simulations to estimate the distribution of external shear values. 
+\citet{HilbertEtal2009} performed similar ray-tracing experiments
+through the Millenium Simulation \citep{SpringelEtal2005}, generating a
+predicted $\kappa$ at every position in a simulated sky.
+\citet{HilbertEtal2009} found that \MS lines of sight with strong lenses
+were not biased towards high $\kappa$, although selection functions for
+discovering or using particular samples of strong lenses were not taken
+into account. The first step towards using this excellent calibration
+resource was taken by \citet{SuyuEtal2010}, who selected \MS lines of
+sight by their apparent galaxy overdensity, in a 45 arcsec radius
+aperture down to $i < 24.5$, to match the observed overdensity towards
+the time delay lens B1608$+$656 \citep{FassnachtEtal2011}. The resulting
+distribution of $\kappa$ values from the ray-tracing was taken to be an
+estimate of  $\Pr(\kappa)$. B1608$+$656 is indeed a high $\kappa$ line
+of sight, but it does not reside in a massive cluster environment. In a
+companion paper to this one, \citet{GreeneEtal2012} investigated
+improvements to this method by weighting the galaxy counts by galaxy
+mass, and perpendicular distance to the line of sight, again using the
+\MS mock catalogs and their associated $\kappa$ values to construct
+$\Pr(\kappa|\data)$.
 
-In this paper, we bring these observational and theoretical approaches
-together and  use numerical simulations to {\it test and calibrate} a
-reconstruction of the  external convergence. Ray-tracing through the
-simulations gives a ``truth'' that we can attempt to recover.  In this paper
-we use the Millenium Simulation mock galaxy catalogs and ray-traced lensing
-effects to test the accuracy of line of sight mass reconstructions.
-Probabilistically assigning mass and redshift to every observed galaxy in the
-field around a time delay lens, we generate Monte Carlo sample line of sight
-mass distributions, and estimate the external convergence due to each one.
-By using the Millenium siumlation as a calibration tool, we can convert the
-total contribution from halos, $\Pr(\kappah)$, into a PDF for the likely convergence
-along the line of sight $\Pr(\kappa)$.
+In this paper, we combine the halo model reconstruction approach of
+\citeauthor{WongEtal} and others with the idea of calibrating to
+simulations from \citeauthor{SuyuEtal2009} in order  to build a
+framework for bringing all available information to bear on the problem
+of estimating the weak the lensing convergence due to mass along the
+line of sight to a distant source.  Taking the $\kappa$ values from
+\citeauthor{HilbertEtal2009}'s ray-tracing calculations as the ``truth''
+that we have to recover, we use the \MS mock galaxy catalogs to test the
+accuracy of line of sight mass reconstruction. Probabilistically
+assigning mass and redshift to every observed galaxy in a given observed
+field, we generate Monte Carlo sample line of sight mass distributions,
+and so construct the PDF $\Pr(\kappa|\data)$.  We aim to answer the
+following questions:
 
-We aim to answer the following questions:
 \begin{itemize}
-\item Faint galaxies, filaments and dark structures will not appear in a photometric
-object catalog, but they will contribute convergence at some level. How much of
-the total external convergence in a time delay lens system comes from visible
-galaxies? How does this change as a function of magnitude cut? 
-\item Can the true (ray-traced) convergence be recovered from a calibrated halo model
-reconstruction? What scatter and residual bias are induced by the reconstruction
-process? Which aspects of the model dominate these uncertainties? 
-\item When faced with a newly-detected lens, surrounded by galaxies on the sky,
-we have some choices to make when planning follow-up observations.
-Which are the most important galaxies, with regard to the external convergence
-produced? Can nearby groups and clusters be straightforwardly accounted for? If
-lenses with such massive structures nearby are discarded, what impact does that
-have on the distance accuracy?
+
+\item Faint galaxies, filaments and dark structures will not appear in
+any photometric object catalog, but they will contribute convergence at
+some level. How much of the total convergence comes from visible
+galaxies, and how much effect do dark structures and voids have?
+
+\item Can the true convergence be recovered from a calibrated halo model
+reconstruction? What scatter and residual bias are induced by the
+reconstruction process, and how might these be reduced in the future?
+
+\item We have some choices to make when planning follow-up observations
+of interesting sightlines. How should we select objects to achieve the
+highest accuracy convergence reconstruction, and hence the highest
+accuracy global parameter estimates?
+
 \end{itemize}
 
-This paper is organized as follows. In~\Sref{sec:theory} we review the relevant
-gravitational lensing theory, before introducing our simple reconstruction 
-model in \Sref{sec:model}.  We then test this model in two phases: first, in
-\Sref{sec:knownMh+z}, with known redshift and halo mass for every galaxy in a
-lens field, in order to quantify the irreducible uncertainty due to unseen mass,
-and second, in \Sref{sec:obsMstar+z}, with realistic observational uncertainties
-on the field galaxies' stellar masses and redshifts. In \Sref{sec:biases} we
-investigate potential systematic errors induced by selecting a subset of sightlines.
-We discuss our results in \Sref{sec:discuss} before
-concluding in \Sref{sec:conclude}.
+This paper is organized as follows. We review the relevant gravitational
+lensing theory in~\Sref{sec:theory}, and the Millenium Simulation
+ray-traced convergences and mock catalogs in \Sref{sec:MS}, before
+introducing our simple reconstruction  model in \Sref{sec:model}. We
+then test this model in two phases: first, in \Sref{sec:knownMh+z}, with
+known redshift and halo mass for every galaxy in a lens field, in order
+to quantify the irreducible uncertainty due to unseen mass, and second,
+in \Sref{sec:obsMstar+z}, with realistic observational uncertainties on
+the observed galaxies' stellar masses and redshifts. In
+\Sref{sec:biases} we investigate the potential systematic error induced
+by selecting a subset of sightlines. We discuss our results in
+\Sref{sec:discuss} before concluding in \Sref{sec:conclude}.
 
@@
 the Hubble Constant in units of 100 km s$^{-1}$ Mpc$^{-1}$ and the matter and
-dark energy density of the Universe in units of the critical density
+dark energy density of the Universe in units of the critical density.
 .%\citep[e.g.\ ][]{KomEtal09}.
@@
 \includegraphics[width=\textwidth]{figs/viewofalightcone.eps}
-\caption[magcut]{4 different views of a lightcone around a typical line of sight.
-This line of sight is slightly overdense with a $\kappa$ of 0.03.
-Top left show the positions of galaxies, the area of the circles is proportional to observed $i$-band flux; the brightest object shown has an $i$ magnitude of 17.7.
-Top Centre show the angular sizes of halos on the sky; red regions are within the NFW scale radius of a halo and blue shows the virial radius of each halo - there are clearly no empty lightcones.
-Top right shows the individual $\kappa$ contributions of each halo, assuming the \citet{BMO} profile and the \citet{Neto2007} mass-concentration relation.
-Bottom a view along the redshift axis, showing only halos with $|x|<0.3$ arcmin; the area of the points is scaled by halo mass; the most massive halo shown has $1.6\times10^{12}\Msun$; the optical axis is the dashed line whilst the dotted lines are the lens and source planes for a B1608-like strong lens.}
+\caption[magcut]{4 different views of a lightcone around a typical line
+of sight. This line of sight is slightly overdense with a $\kappa$ of
+0.03. Top left show the positions of galaxies, the area of the circles
+is proportional to observed $i$-band flux; the brightest object shown
+has an $i$ magnitude of 17.7. Top Centre show the angular sizes of halos
+on the sky; red regions are within the NFW scale radius of a halo and
+blue shows the virial radius of each halo - there are clearly no empty
+lightcones. Top right shows the individual $\kappa$ contributions of
+each halo, assuming the \citet{BMO} profile and the \citet{Neto2007}
+mass-concentration relation. Bottom a view along the redshift axis,
+showing only halos with $|x|<0.3$ arcmin; the area of the points is
+scaled by halo mass; the most massive halo shown has
+$1.6\times10^{12}\Msun$; the optical axis is the dashed line whilst the
+dotted lines are the lens and source planes for a B1608-like strong
+lens.}
 \label{fig:lightcone}

### 2012-10-30 doc/references.tex
working on intro
intro done, moving on

@@
 
-\bibitem[Dalal(2005)]{Dalal2005} Dalal, N.\ 2005, 25 Years After 
-the Discovery: Some Current Topics on Lensed QSOs,
+% \bibitem[Dalal(2005)]{Dalal2005} Dalal, N.\ 2005, 25 Years After 
+% the Discovery: Some Current Topics on Lensed QSOs,
 
@@
 \& Blaizot}{2007}]{deLucia+Blaizot2007} De Lucia G., Blaizot J., 2007, MNRAS, 375, 2
+
+\bibitem[Fadely et al.(2010)]{FadelyEtal2009} Fadely, R., Keeton, 
+C.~R., Nakajima, R., \& Bernstein, G.~M.\ 2010, \apj, 711, 246
 
@@
 
+\bibitem[Holz 
+\& Linder(2005)]{Holz+Linder2005} Holz, D.~E., \& Linder, E.~V.\ 2005, \apj, 631, 678
+
 \bibitem[{{Keeton} \& {Zabludoff}(2004)}]{Keeton+Zabludoff2004}
@@
 
-\bibitem[\protect\citeauthoryear{Linder 
-\& Holz}{2004}]{Linder+Holz2004} Linder E.~V., Holz D.~E., 2004, AAS, 36, \#131.02
+% \bibitem[\protect\citeauthoryear{Linder 
+% \& Holz}{2004}]{Linder+Holz2004} Linder E.~V., Holz D.~E., 2004, AAS, 36, \#131.02
 
@@
   641, 169
+
+\bibitem[Nakajima et al.(2009)]{NakajimaEtal2009} Nakajima, R., 
+Bernstein, G.~M., Fadely, R., Keeton, C.~R., 
+\& Schrabback, T.\ 2009, \apj, 697, 1793
 
@@
 
-\bibitem[\protect\citeauthoryear{\tom{which paper}}{{9999}}]{xxx} 
-None
+% \bibitem[\protect\citeauthoryear{\tom{which paper}}{{9999}}]{xxx} 
+% None
 

### 2012-10-30 doc/paper-lcr.tex
more intro in hilbert 2011 etc, MS section added

@@
 fact makes gravitational lensing a potentially important source of
-systematic error for any estimate of luminosity (or distance), an issue
+systematic error for any estimate of luminosity (or distance); this 
+issue has been 
 raised for \eg type Ia supernovae by
-\citet[][]{Holz+Wald1998,Linder+Holz2004}, for gamma ray bursts by
+\citet[][]{Holz+Wald1998,Holz+Linder2005}, for gamma ray bursts by
 \citet[][]{Oguri+Takahashi2006,Wang+Dai2011},  and for high redshift
@@
 large sample of objects, and averaging over the resulting convergence
-distribution. The weak lensing effect can be detected by measuring the
+distribution. The weak lensing effect can be detected observationally 
+by measuring the
 small distortions it induces on the images of many background galaxies
@@
 (as \citeauthor{FadelyEtal2009} did).  
-\citet{WongEtal2011} came close to estimating this quantity from their
-survey data, running Monte Carlo reconstructions of the mass in nine
-lens fields based on \citeauthor{WilliamsEtal2006} and
-\citeauthor{MomchevaEtal2006}'s photometric and spectroscopic
-measurements of galaxies close to the line of sight, and comparing the
-resulting predicted shear distributions with the external shear demanded
-by the strong lens model. Their reconstructions showed most of the shear
-to have been generated by bright galaxies within 2~arcminutes of the
-lens, and that both line of sight structures and the group of galaxies
-in each lens plane contribute significant proportions of the shear. They
-found significant discrepancies between the lens model shear and the
-Monte Carlo predictions, but were unable to distinguish between the
-environment modelling and the strong lens modelling as the cause of
-these discrepancies.
+%
+\citet{GunnarssonEtal2006} investigated a related PDF,  for the
+magnification, using a galaxy halo model. Applying empirical galaxy
+scaling relations both to simulate mock catalogs and then to reconstruct
+the line of sight mass distribution. While they did not explore highly
+overdense lines of sight, or the impact of groups and clusters, they
+found that under their simplifying assumptions, the dispersion in
+apparent source brightness due to lensing magnification could be reduced
+by a factor of two.
+%
+\citet{WongEtal2011} estimated the PDF for the external shear,
+$\Pr(\gamma|\data)$ from their survey data, running similar Monte Carlo
+reconstructions of the mass in nine lens fields based on
+\citeauthor{WilliamsEtal2006} and \citeauthor{MomchevaEtal2006}'s
+photometric and spectroscopic measurements of galaxies close to the line
+of sight. They then  compared the resulting predicted shear
+distributions with the external shear demanded by the strong lens model.
+Their reconstructions showed most of the shear to have been generated by
+bright galaxies within 2~arcminutes of the lens, and that both line of
+sight structures and the group of galaxies in each lens plane contribute
+significant proportions of the shear. They found significant
+discrepancies between the lens model shear and the Monte Carlo
+predictions, but were unable to distinguish between the environment
+modelling and the strong lens modelling as the cause of these
+discrepancies.
 
@@
 discovering or using particular samples of strong lenses were not taken
-into account. The first step towards using this excellent calibration
-resource was taken by \citet{SuyuEtal2010}, who selected \MS lines of
-sight by their apparent galaxy overdensity, in a 45 arcsec radius
-aperture down to $i < 24.5$, to match the observed overdensity towards
-the time delay lens B1608$+$656 \citep{FassnachtEtal2011}. The resulting
-distribution of $\kappa$ values from the ray-tracing was taken to be an
-estimate of  $\Pr(\kappa)$. B1608$+$656 is indeed a high $\kappa$ line
-of sight, but it does not reside in a massive cluster environment. In a
-companion paper to this one, \citet{GreeneEtal2012} investigated
+into account. Addressing the possibility of using weak lensing shear to
+reconstruct the magnification~$\mu$ that affects cosmography with
+standard candles (and standard sirens), \citet{HilbertEtal2011} used the
+\MS ray-tracing results to explore optimal mapping techniques and
+quantify their performance. They found that deep weak lensing shear
+surveys (with background galaxy number densities of 100 arcmin$^{-2}$)
+would enable $\Pr(\mu|\data)$ to be estimated such that the distance
+uncertainty per object would be reduced by  20\% on average, and by 40\%
+in regions of low convergence, leading to the suggestion that weak
+lensing maps be used to identify the (low convergence)  lines of sight
+that give higher precision distance estimates.
+
+The \MS results have been used to analyse real observations as well. 
+\citet{SuyuEtal2010} selected \MS lines of sight by their apparent
+galaxy overdensity, in a 45 arcsec radius aperture down to $i < 24.5$,
+to match the observed overdensity towards the time delay lens
+B1608$+$656 \citep{FassnachtEtal2011}.  The resulting distribution of
+$\kappa$ values from the ray-tracing was taken to be an estimate of 
+$\Pr(\kappa)$, which was then marginalised over when inferring the time
+delay distance in this system. 
+% B1608$+$656 is indeed a high $\kappa$
+% line of sight, but it does not reside in a massive cluster environment.
+In a companion paper to this one, \citet{GreeneEtal2012} investigated
 improvements to this method by weighting the galaxy counts by galaxy
@@
 In this paper, we combine the halo model reconstruction approach of
-\citeauthor{WongEtal} and others with the idea of calibrating to
-simulations from \citeauthor{SuyuEtal2009} in order  to build a
-framework for bringing all available information to bear on the problem
-of estimating the weak the lensing convergence due to mass along the
-line of sight to a distant source.  Taking the $\kappa$ values from
+\citeauthor{GunnarssonEtal2006} and \citeauthor{WongEtal2011}, with the
+idea of calibrating to simulations from \citeauthor{SuyuEtal2009}, in
+order to put the halo model for  estimating the weak lensing convergence
+due to mass along the line of sight to a distant source into a sound
+framework for evaluating this important source of systematic
+uncertainty, as we look forward to ever increasing sample sizes and
+statistical precision. Taking the $\kappa$ values from
 \citeauthor{HilbertEtal2009}'s ray-tracing calculations as the ``truth''
-that we have to recover, we use the \MS mock galaxy catalogs to test the
-accuracy of line of sight mass reconstruction. Probabilistically
-assigning mass and redshift to every observed galaxy in a given observed
-field, we generate Monte Carlo sample line of sight mass distributions,
-and so construct the PDF $\Pr(\kappa|\data)$.  We aim to answer the
-following questions:
+that we have to recover, we use the \MS mock galaxy catalogs first to
+{\it calibrate} the reconstruction, and account for unseen mass and
+voids, and then to {\it test} the accuracy of the line of sight mass
+reconstruction under this assumption. Probabilistically assigning mass
+and redshift to every observed galaxy in a given observed field, we
+generate Monte Carlo sample line of sight mass distributions, and so
+construct the PDF $\Pr(\kappa|\data)$ for that field. We then emulate
+the combination of many such PDFs to quantify the residual biases that
+would be translated to the global (including cosmological) parameters.
+In doing so, we aim to answer the following questions:
 
@@
 of interesting sightlines. How should we select objects to achieve the
-highest accuracy convergence reconstruction, and hence the highest
-accuracy global parameter estimates?
+highest accuracy convergence reconstruction? Can such a selection be
+made robustly, using the reconstruction results?
 
@@
 \includegraphics[width=\textwidth]{figs/viewofalightcone.eps}
-\caption[magcut]{4 different views of a lightcone around a typical line
-of sight. This line of sight is slightly overdense with a $\kappa$ of
-0.03. Top left show the positions of galaxies, the area of the circles
-is proportional to observed $i$-band flux; the brightest object shown
-has an $i$ magnitude of 17.7. Top Centre show the angular sizes of halos
-on the sky; red regions are within the NFW scale radius of a halo and
-blue shows the virial radius of each halo - there are clearly no empty
-lightcones. Top right shows the individual $\kappa$ contributions of
+\caption[magcut]{Four different views of a slightly over-dense \MS line
+of sight, with a $\kappa$ of 0.03. 
+{\it Top row, left:} The positions of galaxies projected on the sky. The area
+of the circles is proportional to observed $i$-band flux; the brightest
+object shown has an $i$ magnitude of 17.7. 
+{\it Top row, centre:} The angular sizes of halos projected on the sky.
+Red and blue regions lie within the NFW scale radius and virial radius
+of each halo, respectively. There are essentially no empty lightcones. 
+{\it Top row, right:} The individual $\kappa$ contributions of
 each halo, assuming the \citet{BMO} profile and the \citet{Neto2007}
-mass-concentration relation. Bottom a view along the redshift axis,
-showing only halos with $|x|<0.3$ arcmin; the area of the points is
-scaled by halo mass; the most massive halo shown has
-$1.6\times10^{12}\Msun$; the optical axis is the dashed line whilst the
-dotted lines are the lens and source planes for a B1608-like strong
-lens.}
+mass-concentration relation. Comparison of
+this panel and the centre panel reveals the relative importance of
+proximity to the line of sight.
+{\it Bottom:} A view along the redshift axis, showing only halos with
+$|x|<0.3$ arcmin. The area of the points is proportional to each halo's
+mass: the most massive halo shown has $1.6\times10^{12}\Msun$. The
+optical axis is shown by the dashed line, while the dotted lines mark
+the lens and source planes for a B1608-like strong lens.}
 \label{fig:lightcone}
@@
 
-Convergence, or Ricci focusing, occurs when a gravitational lens focuses the rays in a raybundle.
-This focussing can cause distant objects to appear brighter, and larger than they would if the lens
- were removed.
-The convergence from an isolated mass sheet is the ratio of the projected surface mass density
-($\Sigma(D_{\mathrm{od}}\bmath{\theta})$) devided by the critical surface mass density at the redshift of the mass sheet ($\Sigma_{\rm cr}$),
+Convergence, or Ricci focusing, occurs when a gravitational lens focuses
+the rays in a given bundle. This focusing can cause distant objects to
+appear brighter, and larger than they would if the lens were removed.
+The convergence from an isolated mass sheet at a position
+$\bmath{\theta}$ on the sky is the ratio of the projected surface
+mass density ($\Sigma(D_{\mathrm{od}}\bmath{\theta})$) \devided by the
+critical surface mass density at the redshift of the mass sheet
+($\Sigma_{\rm cr}$),
 \be
-\kappa(\bmath{\theta})= \frac {\Sigma(D_{\mathrm{od}}\bmath{\theta})}{\Sigma_{\rm cr}(z)}
+\kappa(\bmath{\theta})= \frac {\Sigma(D_{\mathrm{od}}\bmath{\theta})}
+                              {\Sigma_{\rm cr}(\zd,\zs)}
 \ee
@@
 \be \label{eq:sigcrit} 
-\Sigma_{\rm cr}(z) \equiv \frac{c^2 D_{\rm os}}{4 \pi G D_{\rm od} D_{\rm ds}}.
-\ee
-and the D's are the angular diameter distances between the objects refered to in the subscripts: o is the observer, d is the deflector and s is the source.
-If the surface mass density of the sheet exceeds $\Sigma_{\rm cr}$, multiple images of the source can
-occur, otherwise only one image will be observed, although that image will still be perturbed
-relative to the unlensed case.
+\Sigma_{\rm cr}(\zd,\zs) \equiv \frac{c^2 D_{\rm os}}{4 \pi G D_{\rm od} D_{\rm ds}}.
+\ee
+and the $D$'s are the angular diameter distances between the objects
+refered to in the subscripts: o is the observer, d is the deflector and
+s is the source. If the surface mass density of the sheet exceeds
+$\Sigma_{\rm cr}$, multiple images of the source can occur, otherwise
+only one image will be observed, although that image will still be
+perturbed relative to the unlensed case.
 
@@
 
-Strong lenses sit in our real Universe -- they are not truely isolated;
-there is some mass along the line of sight coming from intervening structures.
-These structures may be physically associated with the lens e.g. other members
-of a group or cluster, or they may be the result of chance alignments at any redshift. 
-Whilst it is rare for three galaxies to line up well enough for both of the background sources
-to be strongly lensed \citep{GavazziEtal2008,CollettEtal2012a}, the shear scale of dark matter halos
-makes a partial alignment -- with the additional structure acting as a perturbing weak lens -- 
-a near certainty \citep{Vale+White2003,HilbertEtal2007}. These additional
-structures induce an external shear which can be recovered in the mass-modelling
-of the lens, but they can also introduce a convergence that
-is undetectable from the image positions, shapes and relative fluxes; {\it the
-mass sheet-degeneracy} \citep{FalcoEtal1985}.
-
-If the intrinsic source brightness changes, the observed brightness in each image does not change
-simultaneously - there is a time delay, $\Delta t$, between the brightness change in
-each image. Despite the invariance of the image positions and fluxes, under the addition
-of an external convergence (and appropriate re-scaling of the lens potential) the relative Fermat potential between the images is {\it not}
-invariant, and so the time delay changes. As such it is necessary to include $\kappa$
-in the lens modelling, if cosmological parameters are to be estimated accurately and
-precisely from observed time delays \citep{SuyuEtal2010}. If there is any external convergence, that is not included in the lens
-modeling, then the time delay distance -- inferred assuming $\kappa = 0$ -- will be
-$(1-\kappa)$ less than the true value of $\Dt$.
+Strong lenses sit in our real Universe -- they are not \truely isolated;
+there is some mass along the line of sight coming from intervening
+structures. These structures may be physically associated with the lens
+e.g. other members of a group or cluster, or they may be the result of
+chance alignments at any redshift.  Whilst it is rare for three galaxies
+to line up well enough for both of the background sources to be strongly
+lensed \citep{GavazziEtal2008,CollettEtal2012a}, the large size of dark
+matter halos makes a partial alignment -- with the additional structure
+acting as a perturbing weak lens --  a near certainty
+\citep{Vale+White2003,HilbertEtal2007}. These additional structures
+induce an external shear which can be recovered in the mass-modelling of
+the lens, but they can also introduce a convergence that is undetectable
+from the image positions, shapes and relative fluxes
+\citep{FalcoEtal1985}.
+
+If the intrinsic source brightness changes, the observed brightness in
+each image does not change simultaneously: there will be a time delay,
+$\Delta t$, between the brightness change in each image. Despite the
+invariance of the image positions and fluxes, under the addition of an
+external convergence (and appropriate re-scaling of the lens potential)
+the relative Fermat potential between the images is {\it not} invariant,
+and so the time delay changes. As such it is necessary to include
+$\kappa$ in the lens modelling, if cosmological parameters are to be
+estimated accurately and precisely from observed time delays
+\citep{SuyuEtal2010}. Mass distributions that are physically associated with the lens galaxy
+will affect the stellar dynamics of the lens galaxy, so that dynamical
+observations can break the internal mass-sheet degeneracy by providing
+an additional estimate of the lens galaxy's mass
+\citep[e.g.,][]{SuyuEtal2010}. In this work our aim is to quantify the
+lensing effect of massive objects, regardless of their position along
+the line of sight.
+
+If there is external convergence present that is not included in the
+lens modeling, then the time delay distance -- inferred assuming $\kappa
+= 0$ -- will be $(1-\kappa)$ less than the true value of $\Dt$:
 \be 
@@
 \ee
-We can overcome this degeneracy with additional knowledge of $\kappa$.
-Since $\kappa$ is typically small the absolute uncertainty on the estimate
-of $\kappa$ correspends to the percentage uncertainty with which time-delay
-distances can be infered.
-
-For mass-sheets that are physically associated with the lens galaxy, the mass sheet
- affects the stellar dynamics of the
-lens galaxy, so dynamical observations can break the internal
-mass-sheet degeneracy by providing an additional estimate of the lens galaxy's mass
-\citep[e.g.,][]{SuyuEtal2010}. In this work our aim is to quantify the lensing effect of mass-sheets that are not physically associated with the lens galaxy -- mass-sheets
-lying infront or behind the lens -- and the uncertainties induced by reconstructing
-those mass-sheets using simple prescriptions applied to potential astronomical observables.
+We can hence estimate the true distance if we have  with additional
+knowledge of $\kappa$. Since $\kappa$ is typically small the absolute
+uncertainty on the estimate of $\kappa$ \correspends to the fractional
+uncertainty with which time-delay distances can be \infered.
+
+The relationship between convergence $\kappa$ and magnification $\mu$ is
+\bea 
+\mu &=&       \frac{1}{(1-\kappa)^2 - |\gamma|^2}, \notag \\
+    &\approx& \frac{1}{(1-2\kappa)}
+\label{eq:MassSheet:mag}
+\eea
+where we have used the fact that the magnitude of the gravitational
+shear at any point is typically comparable to the magnitude of the 
+convergence. For small $\kappa$, the fractional uncertainty in the
+inferred luminosity of a magnified source will be approximately  twice
+the absolute uncertainty in the convergence~$\kappa$. These
+relationships will allow us to put our results on convergence estimation
+in context.
 
@@
 
-\section{Estimating external convergence: The halo model approximation}
+\section{The Millenium Simulation}
+\label{sec:MS}
+
+In order to test the accuracy of our convergence estimates, we need to
+know the true convergence for each line of sight. We cannot use  real
+lines of sight for this,  but must use simulated lines of sight instead.
+In this section we briefly review the Millenium Simulation, the ray
+tracing calculations that have been carried out in it, and the mock
+galaxy catalogs that have been produced.
+
+The \MS \citep{SpringelEtal2005} is a cosmological N-body simulation of
+Dark Matter structures in a cubic region approximately 680~Mpc in
+comoving size, followed from redshift 127 to the present day. With an
+approximate halo mass resolution of $2\times10^{10}{\rm M}_{\odot}$
+(corresponding approximately to a galaxy with luminosity $0.1L^{*}$), it
+provides a detailed prediction for the distribution of dark structures
+present in the Universe, under the assumptions of the $\Lambda$CDM model
+of hierarchical structure formation, cosmological densities as given at
+the end of \Sref{sec:intro}, and $\sigma_8 = 0.9$. 
+Galaxy properties,
+such as stellar masses, luminosities and colours, were assigned to the
+simulated halos according to a semi-analytic model for galaxy formation
+\citep{DeLucia+Blaizot2007}: the resulting predictions for the galaxy
+luminosity function and correlation function match the observational
+data very well.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Convergence from Ray Tracing}
+\label{sec:MS:raytracing}
+
+\citet{HilbertEtal2009} calculated the lensing convergence using the
+``lightcone'' dark matter only 
+output of the \MS, providing 1.7 degree square 
+mock sky maps of this
+quantity. In this process, the dark matter density from the simulation
+was projected onto a set of lens planes at discrete redshifts,
+adaptively gridded and smoothed, and then the second derivatives of the 
+lensing potential required for the components of the magnification
+matrix were computed using a multiple lens plane ray tracing algorithm.
+The first order approximation to this algorithm \citep[equation 17
+of][]{HilbertEtal2009} gives the total convergence at a given sky
+position~$\bmath{\theta}$ as the simple summation of the surface density
+in each lens plane, weighted by the inverse critical surface density
+$\Sigma_{\rm cr}$ for that plane's redshift:
+\be
+\kappa(\bmath{\theta}) = \sum_i \frac{\Sigma_i(\bmath{\theta})}
+                                     {\Sigma_{\rm cr}(z_i,\zs)}.
+\ee
+This approximation was found to be accurate to a few percent or better
+in $\kappa$, even on 30 arcsecond scales.
+
+To define a test line of sight, we draw a random sky position from
+within the convergence maps, bilinearly interpolate between the pixels
+of the map, and store the result as the ``true'' convergence for that
+line of sight, $\kappa_{\rm true}$.
+
+\todo{Stefan}{Check this is all accurate and complete!}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Mock Galaxy Catalogs}
+\label{sec:MS:mocks}
+
+Our goal is to recover the ``true'' convergence defined in the previous
+sub-section, via an inference that takes a catalog of galaxy positions
+and properties as data. We construct such catalogs by selecting all \MS
+galaxies within a circular aperture of a given angular radius centred on
+the line of sight position, with apparent $i$-band magnitude brighter
+than a given limit. The parent catalog, from \citet{HilbertEtal2011},
+contains galaxy positions and magnitudes, all of which include lensing
+effects (deflections and magnifications). We also have access to the
+underlying galaxy halo masses and redshifts, which we will use to
+calibrate the reconstruction, and also to explore any sources of bias
+and scatter. Since the true convergence is that of only the dark matter,
+we focus on reconstructing the dark matter halos alone. Our model for
+doing this is outlined in the next section.
+
+\todo{Stefan, Tom}{Check this is all accurate and complete!}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Estimating Convergence: The Halo Model Approximation}
 \label{sec:model}
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 
@@
 -- this is the subject of Section \ref{subsec:voids}.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 
@@
 
-\subsection{Correcting for voids, filaments and dark structures}
+\subsection{Accounting for voids, filaments and dark structures}
 \label{subsec:voids}
@@
 
-\section{Using the Millenium Simulation to test the halo model approximation with known halo mass and redshift}
+\section{Calibrating the halo model}
 \label{sec:knownMh+z}
 
-In order to justify the reconstruction proceedure outlined in Section \ref{sec:model}, we would like to apply it to lines of sight with known $\kappa$.
-Because we want to test both accuracy and precision we need to know the true convergence for the line of sight.
-Since $\kappa$ isn't an observable we can not use real lines of sight but must use simulated lines of sight instead.
-
-\subsection{Ray-tracing through simulated Lines of Sight}
-\label{subsec:raytracing}
-\todo{Stefan}{Write section on how the ray tracing was done}
-
-\subsection{Generating mock lightcones from simulations}
-\todo{Stefan}{Write section on how halos are extracted from the MS n-body particles}
+In order to test the reconstruction proceedure outlined in Section
+\ref{sec:model}, we now apply it to mock galaxy catalogs generated in
+regions on the sky around lines of sight with known
+$\kappa$ in the Millenium Simulation.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 
@@
 
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
 \subsection{How succesful is the calibration at converting $\kappah$ into $\kappa$?}
@@
 
-Since voids are not included in the halo model approximation $\kappah$ is a biased estimator of $\kappa$, but this can be calibrated for useing the proceedure of Section \ref{subsec:voids}.
-Taking the reconstructed $\kappah$ for $1\times 10^{5}$ lines of sight we form the joint distribution, P$(\kappa,\kappah)$ and marginalize over P$(\kappah)$ to give P($\kappa$).
-We define the bias as the difference between the expectation value of $\kappa$ and the known true value of $\kapparay$ for each Line of sight and we define the reconstruction width, $\sigma_{\kappa}$,as half the width of the interval containing the central $68\%$ of the probability P($\kappax$).
-From $1\times 10^{4}$ reconstructed lines of sight we find the the bias to have mean of $-9.5\times 10^{-6}$ and a mean reconstruction width of 0.0132 which is roughly 1.8 times smaller than the width of the global P$(\kappax)$.
-We find that our $\kappa$ distributions are consistent with the global $\kappa$ distribution; Figure \ref{fig:globaldist} shows that sampling from $\pr(\kappa)$ for 100000 lines of sight is very similar to the global $\pr(\kappa)$.
-Given perfect knowledge of halo mass and redshift, the calibration proceedure provides an unbiased estimate of $\kappa$ that is $\sim$2 times as precise than using the global $\pr(\kappa)$.
+Since voids are not included in the halo model approximation $\kappah$
+is a biased estimator of $\kappa$, but this can be calibrated for useing
+the proceedure of Section \ref{subsec:voids}. Taking the reconstructed
+$\kappah$ for $1\times 10^{5}$ lines of sight we form the joint
+distribution, P$(\kappa,\kappah)$ and marginalize over P$(\kappah)$ to
+give P($\kappa$). We define the bias as the difference between the
+expectation value of $\kappa$ and the known true value of $\kapparay$
+for each Line of sight and we define the reconstruction width,
+$\sigma_{\kappa}$,as half the width of the interval containing the
+central $68\%$ of the probability P($\kappax$). From $1\times 10^{4}$
+reconstructed lines of sight we find the the bias to have mean of
+$-9.5\times 10^{-6}$ and a mean reconstruction width of 0.0132 which is
+roughly 1.8 times smaller than the width of the global P$(\kappax)$. We
+find that our $\kappa$ distributions are consistent with the global
+$\kappa$ distribution; Figure \ref{fig:globaldist} shows that sampling
+from $\pr(\kappa)$ for 100000 lines of sight is very similar to the
+global $\pr(\kappa)$. Given perfect knowledge of halo mass and redshift,
+the calibration proceedure provides an unbiased estimate of $\kappa$
+that is $\sim$2 times as precise than using the global $\pr(\kappa)$.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 
@@
 
-Before investigating the uncertainties caused by imperfect knowledge of halo mass and redshift, we investigate the uncertainties induced by a magnitude limited reconstruction and a field of view limited reconstruction.
-The halos in our catalogue are populated by galaxies and given magnitudes according to the semi-analytic model of \citet{deLucia+Blaizot2007} and by applying magnitude cuts to our catalogue, we can investigate the scatter caused by unobserved halos.
-The majority of the convergence comes from halos with an $i$ magnitude between 18 and 24.
-Figure \ref{fig:where} shows the cumulative contribution to $\kappah$ as a function of projected distance from the line of sight, magnitude and redshift.
-Unsurprisingly we find that most of the convergence comes from halos whose galaxies are close to the line of sight.
-As a function of magnitude, we find that $\kappah$ is dominated by objects with magnitudes between $i=18$ and $i=24$.
-Objects brighter than $i=18$ are either too rare or too close to the observer to make a significant contribution to the convergence.
-Objects fainter than $i=24$ are too small to be important, unless they are extremely close to the line of sight, but we find that including including halos fainter than $i=24$ does not improve our reconstruction.
-Figure \ref{fig:magcut} shows the scatter on $\kappah-\kappa$ (where $\kappah$ is shifted so that it's mean is zero) as a function of reconstruction magnitude limit.
-Since these objects must be extremely close to the line of sight to make a non-zero $\kappah$ contribution it is likely that neglecting stellar mass and using a spherical NFW prescription are too naive to adequately reconstruct $\kappax$; thus we do not expect a deeper survey to decrease the size of the uncertainty in mapping $\kappah$ onto $\kappa$.
-We find that halos at all redshifts contribute to the convergence, but halos at redshifts of $z \sim z_{\rm source}/2$ contribute the most.
+Before investigating the uncertainties caused by imperfect knowledge of
+halo mass and redshift, we investigate the uncertainties induced by a
+magnitude limited reconstruction and a field of view limited
+reconstruction. The halos in our catalogue are populated by galaxies and
+given magnitudes according to the semi-analytic model of
+\citet{deLucia+Blaizot2007} and by applying magnitude cuts to our
+catalogue, we can investigate the scatter caused by unobserved halos.
+The majority of the convergence comes from halos with an $i$ magnitude
+between 18 and 24. Figure \ref{fig:where} shows the cumulative
+contribution to $\kappah$ as a function of projected distance from the
+line of sight, magnitude and redshift. Unsurprisingly we find that most
+of the convergence comes from halos whose galaxies are close to the line
+of sight. As a function of magnitude, we find that $\kappah$ is
+dominated by objects with magnitudes between $i=18$ and $i=24$. Objects
+brighter than $i=18$ are either too rare or too close to the observer to
+make a significant contribution to the convergence. Objects fainter than
+$i=24$ are too small to be important, unless they are extremely close to
+the line of sight, but we find that including including halos fainter
+than $i=24$ does not improve our reconstruction. Figure \ref{fig:magcut}
+shows the scatter on $\kappah-\kappa$ (where $\kappah$ is shifted so
+that it's mean is zero) as a function of reconstruction magnitude limit.
+Since these objects must be extremely close to the line of sight to make
+a non-zero $\kappah$ contribution it is likely that neglecting stellar
+mass and using a spherical NFW prescription are too naive to adequately
+reconstruct $\kappax$; thus we do not expect a deeper survey to decrease
+the size of the uncertainty in mapping $\kappah$ onto $\kappa$. We find
+that halos at all redshifts contribute to the convergence, but halos at
+redshifts of $z \sim z_{\rm source}/2$ contribute the most.
 
@@
 \includegraphics[width=\textwidth]{figs/biasplots.eps}
-\caption[magcut]{Estimating $\kappa-\kappa_{\rm true}$ from subsets of lenses.
-By subtracting the true (ray-traced) convergence from the infered P($\kappa$) for each line of sight we are left with a PDF that should be estimating zero, these can be multiplied together for multiple lines of sight to test for a possible bias.
-These plots show the expectation value of $\prod_{i=1}^N \pr_i(\kappa-\kappa_{\rm true})$ - deviations from zero can be seen as a bias.
-The solid, dashed and dotted lines are for combining 20, 5 and 2 lenses respectively.
-Green lines are from multiplying P($\kappa$) infered from photometry alone, whilst red lines are from multiplying P($\kappa$) infered from photometry and a spectroscopic redshift for all halos with $i<23$ and all halos within 1 arcminute and $i<24$.
-The left most plot shows randomly selected lines of sight.
-The central plot shows sight lines randomly selected from the third of lines whose P($\kappa$) is most tightly constrained.
-The right hand plot shows only lines of sight with external shear of 0.03 or greater.}
+\caption[magcut]{Estimating $\kappa-\kappa_{\rm true}$ from subsets of
+lenses. By subtracting the true (ray-traced) convergence from the
+infered P($\kappa$) for each line of sight we are left with a PDF that
+should be estimating zero, these can be multiplied together for multiple
+lines of sight to test for a possible bias. These plots show the
+expectation value of $\prod_{i=1}^N \pr_i(\kappa-\kappa_{\rm true})$ -
+deviations from zero can be seen as a bias. The solid, dashed and dotted
+lines are for combining 20, 5 and 2 lenses respectively. Green lines are
+from multiplying P($\kappa$) infered from photometry alone, whilst red
+lines are from multiplying P($\kappa$) infered from photometry and a
+spectroscopic redshift for all halos with $i<23$ and all halos within 1
+arcminute and $i<24$. The left most plot shows randomly selected lines
+of sight. The central plot shows sight lines randomly selected from the
+third of lines whose P($\kappa$) is most tightly constrained. The right
+hand plot shows only lines of sight with external shear of 0.03 or
+greater.}
 \label{fig:where}

### 2012-10-30 doc/paper-lcr.tex
fixed refs, citations

@@
 \section{Introduction}
+\label{sec:intro}
 
@@
 small distortions it induces on the images of many background galaxies
-in the field \citep[see e.g.][for a review]{SaasFee2006}. In a 30''
+in the field \citep[see e.g.][for a review]{Schneider2006}. In a 30''
 radius aperture around the strong lens Q0957$+$561,
 \citet{NakajimaEtal2009} used deep HST imaging to measure a weak lensing
-convergence of $0.17/pm0.06$, which was used in the time delay distance
+convergence of $0.17\pm0.06$, which was used in the time delay distance
 measurement of \citep{FadelyEtal2009}. While this system has an
@@
 % line of sight, but it does not reside in a massive cluster environment.
-In a companion paper to this one, \citet{GreeneEtal2012} investigated
+In a companion paper to this one, Greene et al (submitted) investigate
 improvements to this method by weighting the galaxy counts by galaxy
@@
 \citeauthor{GunnarssonEtal2006} and \citeauthor{WongEtal2011}, with the
-idea of calibrating to simulations from \citeauthor{SuyuEtal2009}, in
+idea of calibrating to simulations from \citeauthor{SuyuEtal2010}, in
 order to put the halo model for  estimating the weak lensing convergence
@@
 where 
-\be \label{eq:sigcrit} 
+\be 
+\label{eq:sigcrit} 
 \Sigma_{\rm cr}(\zd,\zs) \equiv \frac{c^2 D_{\rm os}}{4 \pi G D_{\rm od} D_{\rm ds}}.
@@
 \mu &=&       \frac{1}{(1-\kappa)^2 - |\gamma|^2}, \notag \\
-    &\approx& \frac{1}{(1-2\kappa)}
+    &\approx& (1+2\kappa)
 \label{eq:MassSheet:mag}
 \eea
-where we have used the fact that the magnitude of the gravitational
+where we have used the facts that the magnitude of the gravitational
 shear at any point is typically comparable to the magnitude of the 
-convergence. For small $\kappa$, the fractional uncertainty in the
+convergence, and that both are typically small. 
+Under these assumptions, the fractional uncertainty in the
 inferred luminosity of a magnified source will be approximately  twice
@@
 \label{eq:kappai}
-\kappa_i =\Sigma_{i}/\Sigma_{\mathrm{cr}}(z_i),
-\ee
- where $\Sigma_{\rm cr}(z)$ is the critical surface density given by:
-\be \label{eq:sigcrit} 
-\Sigma_{\rm cr}(z) \equiv \frac{c^2 D_{\rm os}}{4 \pi G D_{\rm od} D_{\rm ds}},
-\ee
- the D's are the angular diameter distances between the objects refered to in the subscripts: o is the observer, d is the deflector and s is the source.
-We take the total convergence from all the halos along the line of sight to be given by
-\be \label{eq:kappasummu}
-\kappah=\sum_{i}\kappa_i.
+\kappa_i =\Sigma_{i}/\Sigma_{\mathrm{cr}}(z_i,\zs),
+\ee
+where the critical surface density was defined in \Eref{eq:sigcrit}.
+Following the first order approximation of \citet{HilbertEtal2009}
+outlined in \Sref{sec:MS} above, we compute 
+the total convergence from all the halos along the line
+of sight using
+\be 
+\label{eq:kappasummu}
+\kappah = \sum_{i} \kappa_i.
 \ee
@@
 real lines of sight this can only be infered from the stellar masses of the
-galaxies within a halo. We use the relation of \citet{BehrooziEtal2009} to generate 
+galaxies within a halo. We use the relation of \citet{BehrooziEtal2010} to generate 
 halo masses from stellar masses; the details of this proceedure are outlined in
@@
 given magnitudes according to the semi-analytic model of
-\citet{deLucia+Blaizot2007} and by applying magnitude cuts to our
+\citet{DeLucia+Blaizot2007} and by applying magnitude cuts to our
 catalogue, we can investigate the scatter caused by unobserved halos.
 The majority of the convergence comes from halos with an $i$ magnitude
-between 18 and 24. Figure \ref{fig:where} shows the cumulative
+between 18 and 24. \Fref{fig:where} shows the cumulative
 contribution to $\kappah$ as a function of projected distance from the
@@
 
-We generate a stellar mass for each halo according to the stellar mass--halo mass relation of \citet{BehrooziEtal2009}. From this stellar mass we simulate 
+We generate a stellar mass for each halo according to the stellar mass--halo mass relation of 
+\citet{BehrooziEtal2010}. From this stellar mass we simulate 
 an observed stellar mass by drawing a sample from $\pr(\log(M_{* \mathrm {obs}})|\log(M_{* \mathrm {true}}))$ which is given by a Gaussian of width $\sigma_{M_*}$ centred on $\log(M*_{\mathrm {true}})$.
@@
 
-Given an uncertain stellar mass and redshift it is possible to infer a halo mass using the stellar mass--halo mass relation of \citet{BehrooziEtal2009}.
-This proceedure requires an inversion of the relation given in \citet{BehrooziEtal2009} and correctly inverting the relation's uncertainties requires care: the proceedure we use to do this is given in Appendix \ref{appendix:MSMH}.
-By drawing sample halo masses and redshifts, we can infer a sample $\kappah$ using the proceedure of Section \ref{sec:model}; repeatedly drawing samples allows us to estimate P$(\kappah)$ for each reconstructed line of sight.
+Given an uncertain stellar mass and redshift it is possible to infer a
+halo mass using the stellar mass--halo mass relation of
+\citet{BehrooziEtal2010}. This proceedure requires an inversion of the
+relation given in \citet{BehrooziEtal2010} and correctly inverting the
+relation's uncertainties requires care: the proceedure we use to do this
+is given in Appendix \ref{appendix:MSMH}. By drawing sample halo masses
+and redshifts, we can infer a sample $\kappah$ using the proceedure of
+Section \ref{sec:model}; repeatedly drawing samples allows us to
+estimate P$(\kappah)$ for each reconstructed line of sight.
 
@@
 greater.}
-\label{fig:where}
+\label{fig:biasplots}
 \end{figure*}
@@
 
-First we test for systematic errors in the reconstruction of a randomly selected subset of samples.
-With the purely photometric reconstruction there is a small bias towards underestimating $\kappa$,  combining 6 lenses the half-width and bias of $\mathcal{P}_{6}$ both equal 0.007.
-With targeted spectroscopic follow up this improves slightly, for the combination of 8 lenses the half-width and expectation value  $\mathcal{P}_{8}$ equal 0.005.
-Since strong lens modelling uncertainties are typically at the 3\% level, several hundred lenses are needed to reach this level of precision, but at that point a 0.005 bias in $\kappa$ estimation would become the limiting factor on time-delay cosmography.
+First we test for systematic errors in the reconstruction of a randomly
+selected subset of samples. With the purely photometric reconstruction
+there is a small bias towards underestimating $\kappa$,  combining 6
+lenses the half-width and bias of $\mathcal{P}_{6}$ both equal 0.007.
+With targeted spectroscopic follow up this improves slightly, for the
+combination of 8 lenses the half-width and expectation value 
+$\mathcal{P}_{8}$ equal 0.005. Since strong lens modelling uncertainties
+are typically at the 3\% level, several hundred lenses are needed to
+reach this level of precision, but at that point a 0.005 bias in
+$\kappa$ estimation would become the limiting factor on time-delay
+cosmography.
 
@@
 
-Since lens monitoring campaigns are expensive, it is likely that only a subset of lenses will be observed.
-By pre-selecting the lenses with the most well constrained $\pr(\kappax)$, the cosmological value per lens can be increased, however this has the potential to induce a bias.
-It is probable that only photometry will be available at the time of lens selection (although spectroscopic follow-up might be conducted at a later date).
-We mimik such a selection by drawing lines of sight only from those in the lowest third of $\sigma_{\kappa}$ given a photomtric reconstruction of their fields.
-We find that selecting the most tightly constrained lines of sight {\it decreases} the bias - our reconstruction is most succesful for the lowest $\kappa$ lines of sight.
-With photometry alone the bias is at the 0.0028 level.
-With a targeted spectroscopic follow-up of the selected lines of sight there is negligible improvement, since the best constrained lines of sight are the most empty, but it is the high-$\kappa$ lines of sight that benefit the most from spectroscopy.
-Photometry of the field is sufficient to adequately select the best lines of sight for cosmology - and doing so greatly increases both the precision and accuracy of the cosmological constraints per lens.
+Since lens monitoring campaigns are expensive, it is likely that only a
+subset of lenses will be observed. By pre-selecting the lenses with the
+most well constrained $\pr(\kappax)$, the cosmological value per lens
+can be increased, however this has the potential to induce a bias. It is
+probable that only photometry will be available at the time of lens
+selection (although spectroscopic follow-up might be conducted at a
+later date). We mimik such a selection by drawing lines of sight only
+from those in the lowest third of $\sigma_{\kappa}$ given a photomtric
+reconstruction of their fields. We find that selecting the most tightly
+constrained lines of sight {\it decreases} the bias - our reconstruction
+is most succesful for the lowest $\kappa$ lines of sight. With
+photometry alone the bias is at the 0.0028 level. With a targeted
+spectroscopic follow-up of the selected lines of sight there is
+negligible improvement, since the best constrained lines of sight are
+the most empty, but it is the high-$\kappa$ lines of sight that benefit
+the most from spectroscopy. Photometry of the field is sufficient to
+adequately select the best lines of sight for cosmology - and doing so
+greatly increases both the precision and accuracy of the cosmological
+constraints per lens.
 
@@
 \todo{phil}{Write up why lenses are likely to be gamma biased}
-\notes{The uncertainties from modeling a strong lens system depends on the comfiguration of the source images.
-With only two point images ofthe source the lens slope and mass are degenerate; the mass-slope degeneracy\citep{mass-slope degeneracy} cite saha?.
-Where lensed arcs or four point images are present the mass-slope degeneracy can be broken and cosmology can be extracted, \citep{Suyu2012a}.
-The detectability of arcs depend on the source, but the presence of four images (so called quads) depend on the shear of the lens model - a high shear is needed to produce a quad.
-The shear is almost certainly dominated by the lens model itself, but it is possible that quads are biased towards high external shear.}
+\notes{The uncertainties from modeling a strong lens system depends on
+the comfiguration of the source images. With only two point images ofthe
+source the lens slope and mass are degenerate; the mass-slope
+degeneracy\citep[need citation][Saha?]{mass-slope degeneracy}. Where lensed arcs or
+four point images are present the mass-slope degeneracy can be broken
+and cosmology can be extracted, \citep{Suyu2012a}. The detectability of
+arcs depend on the source, but the presence of four images (so called
+quads) depend on the shear of the lens model - a high shear is needed to
+produce a quad. The shear is almost certainly dominated by the lens
+model itself, but it is possible that quads are biased towards high
+external shear.}
 
@@
 
-TC thanks Vasily Belokurov for guidance and discussions.
-We thank Risa Wechsler and Peter Behroozi for useful discussions and 
-suggestions.\notes{do we?}
+We thank Vasily Belokurov, Risa Wechsler and Peter Behroozi 
+for useful discussions and suggestions.
 \input{acknowledgments.tex}

### 2012-10-30 doc/references.tex
more intro in hilbert 2011 etc, MS section added
fixed refs, citations

@@
 \bibitem[\protect\citeauthoryear{Behroozi, Conroy, 
-\& Wechsler}{2010}]{BehrooziEtal2009} Behroozi P.~S., Conroy C., Wechsler R.~H., 2010, ApJ, 717, 379
+\& Wechsler}{2010}]{BehrooziEtal2010} Behroozi P.~S., Conroy C., Wechsler R.~H., 2010, ApJ, 717, 379
 
@@
 \bibitem[\protect\citeauthoryear{De Lucia 
-\& Blaizot}{2007}]{deLucia+Blaizot2007} De Lucia G., Blaizot J., 2007, MNRAS, 375, 2
+\& Blaizot}{2007}]{DeLucia+Blaizot2007} De Lucia G., Blaizot J., 2007, MNRAS, 375, 2
 
@@
 
+\bibitem[Gunnarsson et al.(2006)]{GunnarssonEtal2006} Gunnarsson, C., 
+Dahl{\'e}n, T., Goobar, A., J{\"o}nsson, J., M{\"o}rtsell, E.\ 2006, \apj, 640, 417
+
 \bibitem[{{Hilbert} {et~al.}(2007){Hilbert}, {White}, {Hartlap}, \&
@@
 al.}{2009}]{HilbertEtal2009} Hilbert S., Hartlap J., White S.~D.~M., Schneider P., 2009, A\&A, 499, 31
+
+\bibitem[Hilbert et al.(2011)]{HilbertEtal2011} Hilbert, S., Gair, 
+J.~R., \& King, L.~J.\ 2011, \mnras, 412, 1023
 
@@
 
+\bibitem[Schneider(2006)]{Schneider2006} Schneider, P.\ 2006, 
+in Saas-Fee Advanced Course 33: Gravitational Lensing: Strong, Weak and Micro, 
+269
+
 \bibitem[\protect\citeauthoryear{Springel et 

### 2012-10-30 doc/paper-lcr.tex
done halos section...

@@
 {\it Top row, right:} The individual $\kappa$ contributions of
-each halo, assuming the \citet{BMO} profile and the \citet{Neto2007}
+each halo, assuming a \citet{BMO} profile and the \citet{Neto2007}
 mass-concentration relation. Comparison of
@@
 
-\section{The Millenium Simulation}
+\section{The Millennium Simulation}
 \label{sec:MS}
@@
 
-\subsection{Mock Galaxy Catalogs}
+\subsection{Mock Photometric Galaxy Catalogs}
 \label{sec:MS:mocks}
 
-Our goal is to recover the ``true'' convergence defined in the previous
-sub-section, via an inference that takes a catalog of galaxy positions
-and properties as data. We construct such catalogs by selecting all \MS
+We construct mock photometric galaxy catalogs by selecting all \MS
 galaxies within a circular aperture of a given angular radius centred on
@@
 
-For real lines of sight, we would like to estimate the external convergence given all
-data available. Typically this data is in the form of a photometric galaxy
-catalog, containing positions, brightnesses, colours, and possibly spectra for each galaxy in the
-field of the lens, down to some magnitude
-limit. Since we can not observe the surface mass density of each halo
-directy, we need some way of estimating
-the mass of each halo in the catalog, so that we can compute its
-contribution to the total $\kappax$ along the line of sight. This mass assignment recipe will be uncertain, but
-can be calibrated with cosmological simulations.
-
-Transforming the photometometric galaxy catalogue into a  catalogue of
-halo masses, positions, and redshifts, will enable us to attempt a
-reconstruction of the convergence induced by every halo near a line of sight.
-This is the subject of Section \ref{subsec:halos}. We also need to account for
-the mass in the Universe that is not associated with the galaxies we can see
--- this is the subject of Section \ref{subsec:voids}.
+One of the goals of this paper is to define a method for estimating the
+convergence at any point on the sky, given a   catalog of observed
+galaxy positions and properties. Typically this could be a  photometric
+galaxy catalog, containing positions, brightnesses, colours, and
+possibly stellar masses and redshifts for each galaxy in the field of
+the lens, down to some magnitude limit. Since we cannot observe the
+surface mass density of each halo directy, we need some way of
+estimating the mass of each halo in the catalog, so that we can compute
+its contribution to the total $\kappa$ along the line of sight \citep[as
+in \eg][]{GunnarssonEtal2006,WongEtal2011}. This mass assignment recipe
+will be uncertain, but can be calibrated with cosmological simulations.
+
+Transforming an observed photometometric galaxy catalogue into a 
+catalogue of halo masses, positions, and redshifts, will enable us to
+attempt a reconstruction of the convergence induced by every halo near a
+line of sight. This is the subject of Section \ref{subsec:halos}. We
+also need to account for the mass in the Universe that is not associated
+with the galaxies we can see -- this is the subject of Section
+\ref{subsec:voids}.
 
@@
 Cosmological dark matter simulations have shown that dark matter
-halos are well approximated by NFW profiles \citep{NFW}, with a density
+halos are well-approximated by NFW profiles \citep{NFW}, with a density
 profile given by
@@
 \ee
+\todo{Tom}{Add sentence about scatter!}
+
 $\rho_0$ is calculated from the critical density and concentration parameter:
@@
 
-Unphysically, if one integrates the density profile of an NFW profile, the total mass is divergent.
-Similarly, if the universe is homogeneously populated with NFW halos, the projected surface mass along any
-line of sight will also be divergant\footnote{At large radius, $\Sigma_{\rm
-nfw} \propto R^{-2}$, but the differential number of halos centred within an
-annulus of width $\dee R$ is given by $\dee N_{\rm annulus} \propto R \dee R$,
-so  $\Sigma_{\rm total} \propto \int_{0}^{\infty} R^{-1} \dee R$, which
-diverges logarithmically}. Since infinite mass is unphysical, the profile must
-be truncated at some point.
-Several truncation profiles have been suggested \citep[e.g][]{BMO}, but beyond several virial radii, the amount of matter associated with a halo is likely to be low.
-In this work we assume the truncated NFW profile of \citet{BMO}
+If one integrates the density profile of an NFW profile out to infinite
+radius, the total mass diverges. Similarly, if the universe is
+homogeneously populated with NFW halos, the projected surface mass along
+any line of sight will also be divergant.\footnote{At large radius,
+$\Sigma_{\rm nfw} \propto R^{-2}$, but the differential number of halos
+centred within an annulus of width $\dee R$ is given by $\dee N_{\rm
+annulus} \propto R \dee R$, so  $\Sigma_{\rm total} \propto
+\int_{0}^{\infty} R^{-1} \dee R$, which diverges logarithmically} Since
+infinite mass is unphysical, the profile must be truncated at some
+point. Several truncation profiles have been suggested
+\citep[e.g][]{BMO}, but beyond several virial radii, the amount of
+matter associated with a halo is likely to be low. In this work we
+assume the truncated NFW profile
 \be\label{eq:bmoprofile}
@@
 \ee
-which is the same as the NFW profile in the limit that the truncation radius, $r_t$ goes to infinity.
-We use a truncation radius of five times the virial radius, but our results are robust for any choice of $r_t>2 \times r_{200}$.
-
-The projected surface mass density $\Sigma(r)$ for this mass profile is derived in \citet{BMO}. Each halo in our catalogue then contributes to the line of sight convergence by
+which is the same as the NFW profile in the limit that the truncation
+radius, $r_t$ goes to infinity. We use a truncation radius of five times
+the virial radius, but our results are robust for any choice of $r_t>2
+\times r_{200}$. The formula for the projected surface mass density 
+$\Sigma(D_{od}\theta)$ for this
+mass profile is given in \citet{BMO}.
+
+Each halo in our catalogue then contributes to
+the line of sight convergence by
 \be
@@
 
-To estimate a halo's contribution to $\kappah$ we must first know the halo's mass.
-For the calibration sightlines of the \MS halo masses are known, but for 
-real lines of sight this can only be infered from the stellar masses of the
-galaxies within a halo. We use the relation of \citet{BehrooziEtal2010} to generate 
-halo masses from stellar masses; the details of this proceedure are outlined in
-Appendix \ref{appendix:MSMH}.
-
-Given an uncertain halo mass and redshift for a halo we draw a sample mass and redshift and use Equation \ref{eq:kappai} to generate a sample $\kappa_i$; this can be done for all the halos along the line of sight and summed to give a sample $\kappah$; repeatedly applying this proceedure allows us to characterize $\pr(\kappah)$.
-However we found that our proceedure for estimating halo masses induces long tails in the $\pr(\kappah)$ distribution that are not present in the global $\kappah$ distribution given perfect knowledge of halo mass and redshift, to correct for this we use the global $\kappah$ distribution as a prior on $\pr(\kappah)$.
+To estimate a halo's contribution to $\kappah$ we must first know the
+halo's mass. For the sightlines of the \MS, halo masses are
+known, but for  real lines of sight the halo masses have to be \infered
+from whatever data is available. 
+In this work we investigate the use of the empirical stellar mass --
+halo mass relation for this purpose. The primary advantage of this
+approach is that it is a simple, ``one size fits all'' relation that can
+be applied regardless of the stellar mass observed. We discuss
+additional observables that could be used to improve the precision of
+the halo mass inference in \Sref{sec:discuss} below.
+
+We use the relation of \citet{BehrooziEtal2010} to infer halo masses
+from stellar masses; the details of this \proceedure are outlined in 
+\Aref{appendix:MSMH}. Given an uncertain stellar mass and redshift for
+each galaxy in the  catalog, we draw a sample halo mass from the PDF
+that describes this uncertainty  (\Eref{eq:mhalo-mstar})  and use
+\Eref{eq:kappai} to compute its contribution to the convergence,
+$\kappa_i$; this can be done for all the halos along the line of sight
+and summed to give a sample value of $\kappah$;  repeatedly applying
+this \proceedure allows us to build up a histogram of $\kappah$ values
+consistent with the data, and hence characterize $\pr(\kappah|\data)$.
+
+This PDF contains a hidden assumption of an uninformative prior PDF for
+$kappah$ -- in the case of infinitely poorly measured stellar masses and
+redshifts, $\pr(\kappah|\data)$ will have very long tails that we do not
+belive to exist. The resolution of this is to apply an additional prior
+on $\kappah$, given by the global underlying $\kappah$ distribution from
+the simulation, $\pr(\kappah)$. In the limiting  case of very poor
+photometric data, $\pr(\kappah|\data)$ then defaults to this
+distribution. \todo{All}{Discuss this. It ties us to the simulation --
+but is not unreasonable. Is the argument about poor data valid? Tom?}
 
@@
 
-The proceedure outlined in Section \ref{subsec:halos} allows us to estimate 
+The \proceedure outlined in Section \ref{subsec:halos} allows us to estimate 
 the convergence due to halos given observations of mass, redshift and position
@@
 
-In order to test the reconstruction proceedure outlined in Section
+In order to test the reconstruction \proceedure outlined in Section
 \ref{sec:model}, we now apply it to mock galaxy catalogs generated in
@@
 is a biased estimator of $\kappa$, but this can be calibrated for useing
-the proceedure of Section \ref{subsec:voids}. Taking the reconstructed
+the \proceedure of Section \ref{subsec:voids}. Taking the reconstructed
 $\kappah$ for $1\times 10^{5}$ lines of sight we form the joint
@@
 global $\pr(\kappa)$. Given perfect knowledge of halo mass and redshift,
-the calibration proceedure provides an unbiased estimate of $\kappa$
+the calibration \proceedure provides an unbiased estimate of $\kappa$
 that is $\sim$2 times as precise than using the global $\pr(\kappa)$.
@@
 
-\section{Applying the Halo Model approximation to mock catalogs}
+\section{Testing the Halo Model Reconstruction on Mock Galaxy Catalogs}
 \label{sec:obsMstar+z}
@@
 halo mass using the stellar mass--halo mass relation of
-\citet{BehrooziEtal2010}. This proceedure requires an inversion of the
+\citet{BehrooziEtal2010}. This \proceedure requires an inversion of the
 relation given in \citet{BehrooziEtal2010} and correctly inverting the
-relation's uncertainties requires care: the proceedure we use to do this
+relation's uncertainties requires care: the \proceedure we use to do this
 is given in Appendix \ref{appendix:MSMH}. By drawing sample halo masses
-and redshifts, we can infer a sample $\kappah$ using the proceedure of
+and redshifts, we can infer a sample $\kappah$ using the \proceedure of
 Section \ref{sec:model}; repeatedly drawing samples allows us to
@@
 \includegraphics[width=\columnwidth]{figs/Width.eps}
-\caption[magcut]{The widths of the infered P$(\kappah|\mathcal{D})$ for $10^5$ lines of sight given different amounts of data.
+\caption[magcut]{The widths of the \infered P$(\kappah|\mathcal{D})$ for $10^5$ lines of sight given different amounts of data.
 Blue assumes a spectroscopic redshift for every halo with $i<26$, purple assumes a spectroscopic redshift for every halo with $i<23$ and every within 1 arcminute and $i<24$, cyan assumes a spectroscopic redshift for every halo with $i<22$ and green assumes that no objects in the field have a spectroscopic redshift}
@@
 \includegraphics[width=\columnwidth]{figs/Widthvshilberrt.eps}
-\caption[magcut]{Width of the infered P$(\kappah|\mathcal{D})$ verses the true $\kappa$ along a line of sight.
-Blue assumes a spectroscopic redshift for every halo, whilst green assumes no spectroscopic redshifts.
-The width of the infered P$(\kappah)$ increases with $\kappa$.
+\caption[magcut]{Width of the \infered P$(\kappah|\mathcal{D})$ verses
+the true $\kappa$ along a line of sight. Blue assumes a spectroscopic
+redshift for every halo, whilst green assumes no spectroscopic
+redshifts.
+The width of the \infered P$(\kappah)$ increases with $\kappa$.
 If correctly reconstructed, the lowest density lines of sight can provide the most precise measurement of the time delay distance.}
@@
 
-Inferring the stellar mass of a galaxy from its magnitude and colours requires an estimate of how far away the galaxy is; without a spectroscopic redshift the the infered stellar mass is less precise.
+Inferring the stellar mass of a galaxy from its magnitude and colours requires an estimate of how far away the galaxy is; without a spectroscopic redshift the the \infered stellar mass is less precise.
 However, obtaining photometry has much lower observational cost; over the next few years several large area photometric surveys will reach 24th magnitude \citep{EUCLID,LSST}, these will provide sufficient data to reconstruct lines of sight {\it without} additional observations.
-In principle the photometric redshift is correlated with the infered stellar mass, however we do not model this effect since the convergence from the outskirts of an individual halo is only weakly dependant on redshift at fixed mass: the redshift error is small effect on the recovered $\pr(\kappa)$ when compared to the effect of uncertain stellar masses.
+In principle the photometric redshift is correlated with the \infered stellar mass, however we do not model this effect since the convergence from the outskirts of an individual halo is only weakly dependant on redshift at fixed mass: the redshift error is small effect on the recovered $\pr(\kappa)$ when compared to the effect of uncertain stellar masses.
 With only photometric redshifts the uncertainty on $\sum\kapparec^{\rm halos}$ is much larger than the spectrocopic case and this propogates into a broader $\pr(\kappa)$, although the photometric reconstruction still typically produces a 1.4 fold improvement compared to the precision of the global P($\kappa$).
@@
 lines are for combining 20, 5 and 2 lenses respectively. Green lines are
-from multiplying P($\kappa$) infered from photometry alone, whilst red
-lines are from multiplying P($\kappa$) infered from photometry and a
+from multiplying P($\kappa$) \infered from photometry alone, whilst red
+lines are from multiplying P($\kappa$) \infered from photometry and a
 spectroscopic redshift for all halos with $i<23$ and all halos within 1
@@
 
-Whilst it is good to reconstruct $\kappa$ precisely it is vital that $\kappa$ is reconstructed accurately.
-A precise, inaccurate $\kappa$ estimator is worse than useless for cosmology.
-We test the accuracy of our reconstructed $\pr(\kappa)$ in the following way: for each line of sight we shift the reconstructed $\pr(\kappa)$ by the line of sight's raytraced $\kappa$ to give $\pr(\kappa-\kapparay)$.
-Since the $\pr(\kappa-\kapparay)$ for each line of sight is an independant estimator of zero, the PDFs can be combined according to
+Whilst it is good to reconstruct $\kappa$ precisely it is vital that
+$\kappa$ is reconstructed accurately. A precise, inaccurate $\kappa$
+estimator is worse than useless for cosmology. We test the accuracy of
+our reconstructed $\pr(\kappa)$ in the following way: for each line of
+sight we shift the reconstructed $\pr(\kappa)$ by the line of sight's
+raytraced $\kappa$ to give $\pr(\kappa-\kapparay)$. Since the
+$\pr(\kappa-\kapparay)$ for each line of sight is an \independant estimator of zero, the PDFs can be combined according to
 
@@
 \subsubsection{Selecting only high shear lines of sight}
+
 \todo{phil}{Write up why lenses are likely to be gamma biased}
+
 \notes{The uncertainties from modeling a strong lens system depends on
@@
 source the lens slope and mass are degenerate; the mass-slope
-degeneracy\citep[need citation][Saha?]{mass-slope degeneracy}. Where lensed arcs or
-four point images are present the mass-slope degeneracy can be broken
-and cosmology can be extracted, \citep{Suyu2012a}. The detectability of
-arcs depend on the source, but the presence of four images (so called
-quads) depend on the shear of the lens model - a high shear is needed to
-produce a quad. The shear is almost certainly dominated by the lens
-model itself, but it is possible that quads are biased towards high
-external shear.}
+degeneracy\citep[need citation][Saha?]{mass-slope degeneracy}. Where
+lensed arcs or four point images are present the mass-slope degeneracy
+can be broken and cosmology can be extracted, \citep{Suyu2012a}. The
+detectability of arcs depend on the source, but the presence of four
+images (so called quads) depend on the shear of the lens model - a high
+shear is needed to produce a quad. The shear is almost certainly
+dominated by the lens model itself, but it is possible that quads are
+biased towards high external shear.}
 
@@
 A more sophisticated model that includes the shear recovered from the lens modelling may not be susceptable to this bias.
-The toy model of this section ($\gamma>0.03$) is likely to be a much stronger selection than reality, but it is worth noting that the reconstruction proceedure will be biased if lens selection functions are extreme and unaccounted.
+The toy model of this section ($\gamma>0.03$) is likely to be a much stronger selection than reality, but it is worth noting that the reconstruction \proceedure will be biased if lens selection functions are extreme and unaccounted.
 
@@
 
-We have shown that reconstructing the matter due to halos along any line of sight can improve the constraints on the external convergence along that line of sight.
-The total convergence along a line of sight is strongly correlated with the reconstructed $\kappah$.
-However since our model ignores voids and assumes all halos follow a spherical truncated-NFW profile our model does not include all of the relevant physics, hence the width of our resulting $\pr(\kappax)$ is still typically $\sim$0.01 for any given lightcone, even with a perfect knowledge of every halo's virial mass and redshift.
-To make further progress a more advanced treatment of both voids and halos will be necessary.
-Interestingly, we have found that the most empty lines of sight can be reconstructed with the most precision.
-$\kappax$ for empty lines of sight have little contributions from halos and a large contribution from voids; since they have the tightest PDFs after the reconstruction it seems that our model's biggest uncertainties are driven by naively reconstructing halos rather than neglecting voids.
-With a photometric reconstruction of the field there is a significant broadening but the resulting precision is still typically 1.5 times greater than using the global $\kappa$ distribution.
-
-Since the uncertainty on $\pr(\kappa|\mathcal{D})$ is $\sim$0.01 even with perfect knowledge of halo mass and redshift it seems that voids (plus deviations from sphericity and dark matter clumping within the main halo) dominate the total $\kappa$ uncertainty even with very uncertain stellar masses.
-Inferring halo ellipticity and dark matter clumping will likely always remain a difficulty for line of sight reconstruction; but as Figure \ref{fig:magcut} shows observing deeper than 24th magnitude does not signifcantly help the reconstruction.
-Because our reconstruction is mostly limited by the model, spectroscopic coverage can only provide a modest improvement to the reconstruction and at significant observational cost.
-
-For a small fraction of lines of sight, $\pr(\kappax)$ remains very broad even after applying our reconstruction; these lines of sight are typically the most overdense lines of sight in the universe.
-For time-delay cosmography the most observationally expensive task is the lightcurve monitoring, whilst making photometric observations of a 4$\times$4 arcminute patch of sky survey down to 24th magnitude is a relatively cheap.
-We have shown that with a single epoch observation of the region around a strong lens it is possible to infer $\pr(\kappax)$.
-If a line of sight has a broad $\pr(\kappax)$ it can be rejected {\it before} the investment of longterm lightcurve monitoring.
-We find that selecting only the lines of sight with the most tightly constrained $\pr(\kappax)$ does not induce a bias.
+We have shown that reconstructing the matter due to halos along any line
+of sight can improve the constraints on the external convergence along
+that line of sight. The total convergence along a line of sight is
+strongly correlated with the reconstructed $\kappah$. However since our
+model ignores voids and assumes all halos follow a spherical
+truncated-NFW profile our model does not include all of the relevant
+physics, hence the width of our resulting $\pr(\kappax)$ is still
+typically $\sim$0.01 for any given lightcone, even with a perfect
+knowledge of every halo's virial mass and redshift. To make further
+progress a more advanced treatment of both voids and halos will be
+necessary. Interestingly, we have found that the most empty lines of
+sight can be reconstructed with the most precision. $\kappax$ for empty
+lines of sight have little contributions from halos and a large
+contribution from voids; since they have the tightest PDFs after the
+reconstruction it seems that our model's biggest uncertainties are
+driven by naively reconstructing halos rather than neglecting voids.
+With a photometric reconstruction of the field there is a significant
+broadening but the resulting precision is still typically 1.5 times
+greater than using the global $\kappa$ distribution.
+
+Since the uncertainty on $\pr(\kappa|\mathcal{D})$ is $\sim$0.01 even
+with perfect knowledge of halo mass and redshift it seems that voids
+(plus deviations from sphericity and dark matter clumping within the
+main halo) dominate the total $\kappa$ uncertainty even with very
+uncertain stellar masses. Inferring halo ellipticity and dark matter
+clumping will likely always remain a difficulty for line of sight
+reconstruction; but as Figure \ref{fig:magcut} shows observing deeper
+than 24th magnitude does not signifcantly help the reconstruction.
+Because our reconstruction is mostly limited by the model, spectroscopic
+coverage can only provide a modest improvement to the reconstruction and
+at significant observational cost.
+
+For a small fraction of lines of sight, $\pr(\kappax)$ remains very
+broad even after applying our reconstruction; these lines of sight are
+typically the most overdense lines of sight in the universe. For
+time-delay cosmography the most observationally expensive task is the
+lightcurve monitoring, whilst making photometric observations of a
+4$\times$4 arcminute patch of sky survey down to 24th magnitude is a
+relatively cheap. We have shown that with a single epoch observation of
+the region around a strong lens it is possible to infer $\pr(\kappax)$.
+If a line of sight has a broad $\pr(\kappax)$ it can be rejected {\it
+before} the investment of longterm lightcurve monitoring. We find that
+selecting only the lines of sight with the most tightly constrained
+$\pr(\kappax)$ does not induce a bias.
 
@@
 \ee 
-Future work should investigate whether $\gamma_{\mathrm{h}}$ can be used to improve
-the accuracy and precision of $\kappa$ estimation, given a reconstruction
- of the line of sight.
-
-This work has used the \MS as a calibration guide. If the real universe is not like 
-the \MS the the calibration will be incorrect - repeating the study with a different
-simulation would quantify the sensitivity of our results to the simulation used. Similarly
-the use of a different semi-analytic model to paint galaxies onto halos could provide
-a useful check, to ensure against potential systematic errors.
+Future work should investigate whether $\gamma_{\mathrm{h}}$ can be used
+to improve the accuracy and precision of $\kappa$ estimation, given a
+reconstruction of the line of sight.
+
+This work has used the \MS as a calibration guide. If the real universe
+is not like  the \MS the the calibration will be incorrect - repeating
+the study with a different simulation would quantify the sensitivity of
+our results to the simulation used. Similarly the use of a different
+semi-analytic model to paint galaxies onto halos could provide a useful
+check, to ensure against potential systematic errors.
 
@@
 In this work we have investigated a simple halo model prescription for
-reconstructing all the mass along a line of sight to an intermediate redshift
-source. We have used the ray-traced lensing convergence along lines of sight
-through the Millenium Simulation to test this approach, and to calibrate
-estimates of the total convergence along a line of sight to an observed
-distant galaxy made by summing the convergences due to each object in a
-photometric catalogue. Having found that the reconstruction process is effective given perfect
-knowledge of halo mass and redshift, we investigated the effects of reasonable
-uncertainties in the stellar mass and redshift of each halo, and propogated
-these uncertainties into a $\pr\left(\sumkappah\right)$ for each line of
+reconstructing all the mass along a line of sight to an intermediate
+redshift source. We have used the ray-traced lensing convergence along
+lines of sight through the Millenium Simulation to test this approach,
+and to calibrate estimates of the total convergence along a line of
+sight to an observed distant galaxy made by summing the convergences due
+to each object in a photometric catalogue. Having found that the
+reconstruction process is effective given perfect knowledge of halo mass
+and redshift, we investigated the effects of reasonable uncertainties in
+the stellar mass and redshift of each halo, and propogated these
+uncertainties into a $\pr\left(\sumkappah\right)$ for each line of
 sight. We draw the following conclusions:
@@
 
-\item Our model uses a truncated spherical NFW profile for
-each dark matter halo and neglects voids, but despite the model's simplicity
-the reconstructed $\kappah$ is a good tracer of $\kappa$.  We found that
+\item Our model uses a truncated spherical NFW profile for each dark
+matter halo and neglects voids, but despite the model's simplicity the
+reconstructed $\kappah$ is a good tracer of $\kappa$.  We found that
 with perfect knowledge of the halo mass and redshift (from the Millenium
 Simulation catalogs), for a typical line of sight the reconstruction
-gives an unbiased estimate of $\pr(\kappa)$ that is a factor of 2
-less broad than the global $\pr(\kappa)$.
+gives an unbiased estimate of $\pr(\kappa)$ that is a factor of 2 less
+broad than the global $\pr(\kappa)$.
 
@@
 whose host galaxy is less luminous than $i=24$ does not significantly improve
-our reconstruction proceedure. A photometric survey to this depth of a
+our reconstruction \proceedure. A photometric survey to this depth of a
 4$\times$4 arcminute patch around the lens would approach the limiting
@@
 $\sim$3 percent level, which far exceeds the typical $\kappa$ uncertainties
-after applying our reconstruction proceedure. By using our method to
+after applying our reconstruction \proceedure. By using our method to
 reconstruct lines of sight and select which lense are followed-up, the
@@
 To estimate the convergence caused by a halo we need to know its mass; how can 
-halo mass be infered from a noisy estimate of the stellar mass $\Mstarobs$
+halo mass be \infered from a noisy estimate of the stellar mass $\Mstarobs$
 of a galaxy at redshift $z$. We seek the posterior
@@
 
-If the redshift of the galaxy is uncertain, we need to take this uncertainty
-into account; for example, for each sample drawn from the photometric redshift
-posterior PDF $\Pr(z|{\rm colors})$, we can draw a sample $\Mhalo$ using the
-above procedure.
+If the redshift of the galaxy is uncertain, we need to take this
+uncertainty into account; for example, for each sample drawn from the
+photometric redshift posterior PDF $\Pr(z|{\rm colors})$, we can draw a
+sample $\Mhalo$ using the above procedure.
 

### 2012-10-31 doc/attic/framework.tex
checked though up to testing on mocks

--- 2012-10-30 doc/paper-lcr.tex
@@
 %
-% Pangloss: Testing the reconstruction method
+% Pangloss: Testing the reconstruction paper
 %
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \title[Line of Sight Mass Reconstruction]
-{Reconstructing the Lensing Mass in the Universe \\
+{Inferring Lensing Mass in the Universe \\
 from Photometric Catalog Data}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \begin{abstract} 
-
-\todo{PJM}{Make abstract match conclusions.}
-
 Strong gravitational lenses can provide high precision cosmological distance
@@
  $\Pr(\kappa)$ can be formed before the investment of light-curve monitoring: by following up only the 
-most constrained lines of sight a factor of 2 improvement over the global $\pr(\kappax)$ should be 
+most costrained lines of sight a factor of 2 improvement over the global $\pr(\kappax)$ should be 
 achievable.
-
 \end{abstract}
@@
 
-Every distant object we observe has had its apparent shape distorted,
-and size and total brightness magnified (or demagnified) by a compound
-weak gravitational lens constructed from all the mass distributed
-between us and it. As \citet{Vale+White2003} and \citet{HilbertEtal2007}
-showed, there are no empty lines of sight through our universe. This
-fact makes gravitational lensing a potentially important source of
-systematic error for any estimate of luminosity (or distance); this 
-issue has been 
-raised for \eg type Ia supernovae by
-\citet[][]{Holz+Wald1998,Holz+Linder2005}, for gamma ray bursts by
-\citet[][]{Oguri+Takahashi2006,Wang+Dai2011},  and for high redshift
-galaxies by \citet{BradacEtal2009}, among others.
-
-Along lines of sight containing strong gravitational lenses, the
-perturbative effects of line of sight mass structure have been found to
-be particularly important, with foreground and background structures
+Every distant object we observe has had its shape distorted, and size
+and total brightness magnified (or demagnified) by a compound lens constructed
+from all the mass distributed between us and it. As \citet{Vale+White2003} and \citet{HilbertEtal2007}
+showed, there are no empty lightcones in our universe. This fact makes gravitational lensing a potentially important source of systematic error for any estimate of luminosity or distance, an issue
+raised for \eg type Ia supernovae by \citet[][]{Holz+Wald1998,Linder+Holz2004}, for
+gamma ray bursts by \citet[][]{Oguri+Takahashi2006,Wang+Dai2011}, 
+and for high redshift galaxies by \citet{BradacEtal2009}, among others.
+
+Along lines of sight containing strong gravitational lenses,
+the effect has been found to be
+particularly important, with foreground and background structures
 having a significant effect on the inferred lensing cross-section
-\citep[\eg][]{WongEtal2012} and distance ratios
-\citep[][]{DalalEtal2005}. Indeed, \citet{SuyuEtal2010} found that in
-time delay lens cosmography the so-called ``external convergence''
-$\kappa$ due to mass structures along the (unusually over-dense) line
-of sight to the quadruply-imaged radio source B1608$+$656 was the
-dominant source of uncertainty in their 6\% measurement of Hubble's
-constant. The problem is that one simply doesn't know how magnified and
-distorted the source has been, because the unlensed source is
-unobservable. The external shear can potentially be recovered in the
-mass-modelling of the lens, but the convergence is undetectable from the
-image positions, shapes and relative fluxes; this is the famous {\emph{ 
-mass sheet-degeneracy}} \citep[see e.g.][for details]{FalcoEtal1985}.
-
-How can we correct for this perturbative lensing and make accurate
-measurements through the Universe? When inferring global quantities
-(such as the cosmological parameters), combining the results from a
-large number of independent objects will tend to reduce the uncertainty
-due to external convergence, as the ensemble-averaged magnification
-approaches zero for an unbiased sample \citep[\eg][]{Holz+Linder2005}.
-If the sample is biased, however, some residual systematic error will
-remain even as the statistical uncertainty decreases. Lensing bias will
-be present (to varying degrees) in any sample {\it selected} by
-brightness (which includes magnification), or any other quantity that
-depends on $\kappa$. This bias may be introduced either at the object
-detection stage, or later on when making decisions about which objects
-to study further.  Moreover, we expect these biases to be strongest in
-the strong lens systems, where magnification is highest. Large samples
-of lenses are expected to be discovered in the next decade in
-ground-based optical imaging surveys \citep{Oguri+Marshall2010}: both
-the detectability of these lenses,  and the selection of sub-samples of
-them for further observation, could be sensitive to the external
-convergence.
-
-Several attempts have been made to do better than simply constructing a
-large sample of objects, and averaging over the resulting convergence
-distribution. The weak lensing effect can be detected observationally 
-by measuring the
-small distortions it induces on the images of many background galaxies
-in the field \citep[see e.g.][for a review]{SaasFee2006}. In a 30''
-radius aperture around the strong lens Q0957$+$561,
-\citet{NakajimaEtal2009} used deep HST imaging to measure a weak lensing
-convergence of $0.17/pm0.06$, which was used in the time delay distance
-measurement of \citep{FadelyEtal2009}. While this system has an
-unusually high external convergence due to its location on the edge of a
-cluster of galaxies, the precision with which the convergence at the
-lens position can be estimated is indicative of what can be achieved
-with high quality weak lensing shear data. We note that this uncertainty
-is not dependent on the value of the convergence, but instead depends
-primarily on the number density of weakly lensed, measurable galaxies
-available.
-
-In order to make more precise estimates of the convergence at a given
-sky position, we need more information.   There have been some attempts
-to reconstruct the local and line of sight mass distribution in strong
-lens fields in some detail, based on photometric and spectroscopic
-surveys of the galaxies nearby. These efforts have focused on  detecting
-galaxy groups, ascertaining the visible galaxies' membership of those
-groups, and assigning mass to the group and galaxy halos in order to
-predict the external shear apparently required by the strong lens
-models. Surveys by
+\citep[\eg][]{WongEtal2012} and distance ratios \citep[][]{DalalEtal2005}.
+\citet{SuyuEtal2010} found that in time delay lens cosmography the
+lensing effect of mass structures along the (unusually over-dense) line of
+sight to the quadruply-imaged radio source B1608$+$656, the so-called ``external
+convergence'' $\kappax$, was the dominant source of uncertainty in 
+their 6\% measurement of Hubble's constant.
+
+The problem is that one simply doesn't know
+how magnified and distorted the source has been because the unlensed
+source is unobservable. The external shear can potentially be recovered
+in the mass-modelling of the lens, but the convergence is undetectable
+from the image positions, shapes and relative fluxes; this is the
+famous {\emph{  mass sheet-degeneracy}} \citep[see e.g.][for details]{FalcoEtal1985}.
+
+How can we correct for this perturbative lensing and make
+accurate measurements through the Universe? When inferring global quantities
+(such as the cosmological parameters), averaging the results from a large
+number of independent objects will tend to reduce the uncertainty, as the
+ensemble-averaged convergence approaches zero for an unbiased sample
+\citep[\eg][]{Linder+Holz2004}. If the sample is biased, however, some
+residual systematic error will remain while the statistical uncertainty
+decreases -- and this will be the case for any sample selected by the
+brightness of the lensed object, or any other quantity that depends on
+$\kappa$. Large
+samples of lenses are expected to be discovered in the next decade in
+ground-based optical imaging surveys \citep{Oguri+Marshall2010} -- but these
+samples will be image separation-limited, due to the surveys' relatively poor
+($\sim 1$~arcsec) image quality. There is a possibility that
+they are somewhat biased towards high values of $\kappa$, although 
+\citet{Fassnacht+Lubin2002} \todo{Anyone}{check this is the right Fassnacht paper} found no evidence of lenses lying along over-dense lines of sight.
+
+To date, attempts at reconstructing the local and line of sight mass
+distribution in strong lens fields (what \citeauthor{WongEtal2011} call ``the
+full environment'') have focused on photometric and  spectroscopic surveys to
+detect galaxy groups and ascertain galaxies' membership in order to understand
+the external shear apparently required by the strong lens models. Surveys by
 \citet{Fassnacht+Lubin2002,AugerEtal2007,WilliamsEtal2006,MomchevaEtal2006}
-all found groups of galaxies both hosting, and lying  along the line of
-sight to, known gravitational lenses. Initial estimates of the effect of
-these structures suggested the importance of assigning mass to both
-galaxy and group halos, and to allowing for significant uncertainty in
-the centroids of group halos.
-
-The probability density function (PDF) for the external convergence
-given our available data $\data$, $\Pr(\xkappa|\data)$,  is the  key
-quantity we seek, since by marginalising over this distribution we can
-correctly propagate the uncertainties due to line-of-sight perturbations
-(as \citeauthor{FadelyEtal2009} did).  
-%
-\citet{GunnarssonEtal2006} investigated a related PDF,  for the
-magnification, using a galaxy halo model. Applying empirical galaxy
-scaling relations both to simulate mock catalogs and then to reconstruct
-the line of sight mass distribution. While they did not explore highly
-overdense lines of sight, or the impact of groups and clusters, they
-found that under their simplifying assumptions, the dispersion in
-apparent source brightness due to lensing magnification could be reduced
-by a factor of two.
-%
-\citet{WongEtal2011} estimated the PDF for the external shear,
-$\Pr(\gamma|\data)$ from their survey data, running similar Monte Carlo
-reconstructions of the mass in nine lens fields based on
+all found groups of galaxies both hosting and lying  along the line of sight
+to known gravitational lenses. Initial estimates of the effect of these
+structures suggested the importance of assigning mass to both galaxy and group
+halos, and to allowing for significant uncertainty in the centroids of group
+halos. The probability density function (PDF) for the external convergence for
+that lens, $\Pr(\xkappa)$, is the target for any reconstruction analysis, and
+is the key quantity for any ensemble analysis, since by marginalising over it
+we can correctly propagate the uncertainties due to line-of-sight perturbations. Coming
+closest to estimating this quantity from survey data, \citet{WongEtal2011} ran
+Monte Carlo reconstructions of the mass in nine lens fields based on
 \citeauthor{WilliamsEtal2006} and \citeauthor{MomchevaEtal2006}'s
-photometric and spectroscopic measurements of galaxies close to the line
-of sight. They then  compared the resulting predicted shear
-distributions with the external shear demanded by the strong lens model.
-Their reconstructions showed most of the shear to have been generated by
-bright galaxies within 2~arcminutes of the lens, and that both line of
-sight structures and the group of galaxies in each lens plane contribute
-significant proportions of the shear. They found significant
-discrepancies between the lens model shear and the Monte Carlo
-predictions, but were unable to distinguish between the environment
-modelling and the strong lens modelling as the cause of these
-discrepancies.
-
-These observational investigations have provided some very useful
-insight into the problem of convergence estimation.  Coming from a more
-theoretical direction, large numerical simulations have been used to
-predict, from first principles, the distribution of likely external
-shears and convergences along various lines of sight, including those
-containing strong lens systems.  \citet{Holder+Schechter2003} and
-\citet{DalalEtal2005} carried out ray-tracing calculations in N-body
-simulations to estimate the distribution of external shear values. 
-\citet{HilbertEtal2009} performed similar ray-tracing experiments
-through the Millenium Simulation \citep{SpringelEtal2005}, generating a
-predicted $\kappa$ at every position in a simulated sky.
-\citet{HilbertEtal2009} found that \MS lines of sight with strong lenses
-were not biased towards high $\kappa$, although selection functions for
-discovering or using particular samples of strong lenses were not taken
-into account. Addressing the possibility of using weak lensing shear to
-reconstruct the magnification~$\mu$ that affects cosmography with
-standard candles (and standard sirens), \citet{HilbertEtal2011} used the
-\MS ray-tracing results to explore optimal mapping techniques and
-quantify their performance. They found that deep weak lensing shear
-surveys (with background galaxy number densities of 100 arcmin$^{-2}$)
-would enable $\Pr(\mu|\data)$ to be estimated such that the distance
-uncertainty per object would be reduced by  20\% on average, and by 40\%
-in regions of low convergence, leading to the suggestion that weak
-lensing maps be used to identify the (low convergence)  lines of sight
-that give higher precision distance estimates.
-
-The \MS results have been used to analyse real observations as well. 
-\citet{SuyuEtal2010} selected \MS lines of sight by their apparent
-galaxy overdensity, in a 45 arcsec radius aperture down to $i < 24.5$,
-to match the observed overdensity towards the time delay lens
-B1608$+$656 \citep{FassnachtEtal2011}.  The resulting distribution of
-$\kappa$ values from the ray-tracing was taken to be an estimate of 
-$\Pr(\kappa)$, which was then marginalised over when inferring the time
-delay distance in this system. 
-% B1608$+$656 is indeed a high $\kappa$
-% line of sight, but it does not reside in a massive cluster environment.
-In a companion paper to this one, \citet{GreeneEtal2012} investigated
-improvements to this method by weighting the galaxy counts by galaxy
-mass, and perpendicular distance to the line of sight, again using the
-\MS mock catalogs and their associated $\kappa$ values to construct
-$\Pr(\kappa|\data)$.
-
-In this paper, we combine the halo model reconstruction approach of
-\citeauthor{GunnarssonEtal2006} and \citeauthor{WongEtal2011}, with the
-idea of calibrating to simulations from \citeauthor{SuyuEtal2009}, in
-order to put the halo model for  estimating the weak lensing convergence
-due to mass along the line of sight to a distant source into a sound
-framework for evaluating this important source of systematic
-uncertainty, as we look forward to ever increasing sample sizes and
-statistical precision. Taking the $\kappa$ values from
-\citeauthor{HilbertEtal2009}'s ray-tracing calculations as the ``truth''
-that we have to recover, we use the \MS mock galaxy catalogs first to
-{\it calibrate} the reconstruction, and account for unseen mass and
-voids, and then to {\it test} the accuracy of the line of sight mass
-reconstruction under this assumption. Probabilistically assigning mass
-and redshift to every observed galaxy in a given observed field, we
-generate Monte Carlo sample line of sight mass distributions, and so
-construct the PDF $\Pr(\kappa|\data)$ for that field. We then emulate
-the combination of many such PDFs to quantify the residual biases that
-would be translated to the global (including cosmological) parameters.
-In doing so, we aim to answer the following questions:
-
+photometric and spectroscopic measurements of galaxies close to the line of
+sight, and compared the resulting predicted shear distributions with the
+external shear demanded by the strong lens model. Their reconstructions show most
+of the shear being generated by bright galaxies within 2~arcminutes of the
+lens, and that both line of sight structures and the group of galaxies in each
+lens plane contribute significant proportions of the shear. They find
+significant discrepancies between the lens model shear and the Monte Carlo
+predictions, and are unable to distinguish between the environment modelling
+and the strong lens modelling as the cause of these discrepancies.
+
+These observational investigations have provided very useful insight into the
+problem.  Coming from a more theoretical direction, large numerical
+simulations have been used to predict, from first principles, the distribution
+of likely external shears and convergences along strong lens lines of sight. 
+\citet{Holder+Schechter2003} and \citet{Dalal+Watson2004}\todo{phil}{Dalal+Watson2004 doesn't seem to exist} carried out
+ray-tracing calculations in N-body simulations to estimate the  distribution
+of external shear values.  \citet{HilbertEtal2009} performed similar ray-tracing
+experiments through the Millenium Simulation \citep{SpringelEtal2005},
+generating a predicted $\kappa$ at every position in a simulated sky. \citet{HilbertEtal2009}
+found that \MS lines of sight with strong lenses were not biased towards high $\kappa$,
+although selection functions for discovering a strong lens were not taken into account.
+The first step towards using this excellent calibration resource was taken by
+\citet{SuyuEtal2010}, who selected Millenium Simulation lines of sight that
+ had comparable apparent galaxy
+overdensity in a 45 arcsec radius aperture down to $i < 24.5$. This overdensity
+could be compared to the overdensity of the B1608$+$656 line of sight
+\citep{FassnachtEtal2011}, and hence an estimate of  $\Pr(\kappa)$ could be
+made. B1608$+$656 is indeed a high $\kappa$ line of sight, but it does not reside
+in a typical lens environment.
+
+In this paper, we bring these observational and theoretical approaches
+together and  use numerical simulations to {\it test and calibrate} a
+reconstruction of the  external convergence. Ray-tracing through the
+simulations gives a ``truth'' that we can attempt to recover.  In this paper
+we use the Millenium Simulation mock galaxy catalogs and ray-traced lensing
+effects to test the accuracy of line of sight mass reconstructions.
+Probabilistically assigning mass and redshift to every observed galaxy in the
+field around a time delay lens, we generate Monte Carlo sample line of sight
+mass distributions, and estimate the external convergence due to each one.
+By using the Millenium siumlation as a calibration tool, we can convert the
+total contribution from halos, $\Pr(\kappah)$, into a PDF for the likely convergence
+along the line of sight $\Pr(\kappa)$.
+
+We aim to answer the following questions:
 \begin{itemize}
-
-\item Faint galaxies, filaments and dark structures will not appear in
-any photometric object catalog, but they will contribute convergence at
-some level. How much of the total convergence comes from visible
-galaxies, and how much effect do dark structures and voids have?
-
-\item Can the true convergence be recovered from a calibrated halo model
-reconstruction? What scatter and residual bias are induced by the
-reconstruction process, and how might these be reduced in the future?
-
-\item We have some choices to make when planning follow-up observations
-of interesting sightlines. How should we select objects to achieve the
-highest accuracy convergence reconstruction? Can such a selection be
-made robustly, using the reconstruction results?
-
+\item Faint galaxies, filaments and dark structures will not appear in a photometric
+object catalog, but they will contribute convergence at some level. How much of
+the total external convergence in a time delay lens system comes from visible
+galaxies? How does this change as a function of magnitude cut? 
+\item Can the true (ray-traced) convergence be recovered from a calibrated halo model
+reconstruction? What scatter and residual bias are induced by the reconstruction
+process? Which aspects of the model dominate these uncertainties? 
+\item When faced with a newly-detected lens, surrounded by galaxies on the sky,
+we have some choices to make when planning follow-up observations.
+Which are the most important galaxies, with regard to the external convergence
+produced? Can nearby groups and clusters be straightforwardly accounted for? If
+lenses with such massive structures nearby are discarded, what impact does that
+have on the distance accuracy?
 \end{itemize}
 
-This paper is organized as follows. We review the relevant gravitational
-lensing theory in~\Sref{sec:theory}, and the Millenium Simulation
-ray-traced convergences and mock catalogs in \Sref{sec:MS}, before
-introducing our simple reconstruction  model in \Sref{sec:model}. We
-then test this model in two phases: first, in \Sref{sec:knownMh+z}, with
-known redshift and halo mass for every galaxy in a lens field, in order
-to quantify the irreducible uncertainty due to unseen mass, and second,
-in \Sref{sec:obsMstar+z}, with realistic observational uncertainties on
-the observed galaxies' stellar masses and redshifts. In
-\Sref{sec:biases} we investigate the potential systematic error induced
-by selecting a subset of sightlines. We discuss our results in
-\Sref{sec:discuss} before concluding in \Sref{sec:conclude}.
+This paper is organized as follows. In~\Sref{sec:theory} we review the relevant
+gravitational lensing theory, before introducing our simple reconstruction 
+model in \Sref{sec:model}.  We then test this model in two phases: first, in
+\Sref{sec:knownMh+z}, with known redshift and halo mass for every galaxy in a
+lens field, in order to quantify the irreducible uncertainty due to unseen mass,
+and second, in \Sref{sec:obsMstar+z}, with realistic observational uncertainties
+on the field galaxies' stellar masses and redshifts. In \Sref{sec:biases} we
+investigate potential systematic errors induced by selecting a subset of sightlines.
+We discuss our results in \Sref{sec:discuss} before
+concluding in \Sref{sec:conclude}.
 
@@
 the Hubble Constant in units of 100 km s$^{-1}$ Mpc$^{-1}$ and the matter and
-dark energy density of the Universe in units of the critical density.
+dark energy density of the Universe in units of the critical density
 .%\citep[e.g.\ ][]{KomEtal09}.
@@
 \includegraphics[width=\textwidth]{figs/viewofalightcone.eps}
-\caption[magcut]{Four different views of a slightly over-dense \MS line
-of sight, with a $\kappa$ of 0.03. 
-{\it Top row, left:} The positions of galaxies projected on the sky. The area
-of the circles is proportional to observed $i$-band flux; the brightest
-object shown has an $i$ magnitude of 17.7. 
-{\it Top row, centre:} The angular sizes of halos projected on the sky.
-Red and blue regions lie within the NFW scale radius and virial radius
-of each halo, respectively. There are essentially no empty lightcones. 
-{\it Top row, right:} The individual $\kappa$ contributions of
-each halo, assuming the \citet{BMO} profile and the \citet{Neto2007}
-mass-concentration relation. Comparison of
-this panel and the centre panel reveals the relative importance of
-proximity to the line of sight.
-{\it Bottom:} A view along the redshift axis, showing only halos with
-$|x|<0.3$ arcmin. The area of the points is proportional to each halo's
-mass: the most massive halo shown has $1.6\times10^{12}\Msun$. The
-optical axis is shown by the dashed line, while the dotted lines mark
-the lens and source planes for a B1608-like strong lens.}
+\caption[magcut]{4 different views of a lightcone around a typical line of sight.
+This line of sight is slightly overdense with a $\kappa$ of 0.03.
+Top left show the positions of galaxies, the area of the circles is proportional to observed $i$-band flux; the brightest object shown has an $i$ magnitude of 17.7.
+Top Centre show the angular sizes of halos on the sky; red regions are within the NFW scale radius of a halo and blue shows the virial radius of each halo - there are clearly no empty lightcones.
+Top right shows the individual $\kappa$ contributions of each halo, assuming the \citet{BMO} profile and the \citet{Neto2007} mass-concentration relation.
+Bottom a view along the redshift axis, showing only halos with $|x|<0.3$ arcmin; the area of the points is scaled by halo mass; the most massive halo shown has $1.6\times10^{12}\Msun$; the optical axis is the dashed line whilst the dotted lines are the lens and source planes for a B1608-like strong lens.}
 \label{fig:lightcone}
@@
 
-Convergence, or Ricci focusing, occurs when a gravitational lens focuses
-the rays in a given bundle. This focusing can cause distant objects to
-appear brighter, and larger than they would if the lens were removed.
-The convergence from an isolated mass sheet at a position
-$\bmath{\theta}$ on the sky is the ratio of the projected surface
-mass density ($\Sigma(D_{\mathrm{od}}\bmath{\theta})$) \devided by the
-critical surface mass density at the redshift of the mass sheet
-($\Sigma_{\rm cr}$),
+Convergence, or Ricci focusing, occurs when a gravitational lens focuses the rays in a raybundle.
+This focussing can cause distant objects to appear brighter, and larger than they would if the lens
+ were removed.
+The convergence from an isolated mass sheet is the ratio of the projected surface mass density
+($\Sigma(D_{\mathrm{od}}\bmath{\theta})$) devided by the critical surface mass density at the redshift of the mass sheet ($\Sigma_{\rm cr}$),
 \be
-\kappa(\bmath{\theta})= \frac {\Sigma(D_{\mathrm{od}}\bmath{\theta})}
-                              {\Sigma_{\rm cr}(\zd,\zs)}
+\kappa(\bmath{\theta})= \frac {\Sigma(D_{\mathrm{od}}\bmath{\theta})}{\Sigma_{\rm cr}(z)}
 \ee
@@
 \be \label{eq:sigcrit} 
-\Sigma_{\rm cr}(\zd,\zs) \equiv \frac{c^2 D_{\rm os}}{4 \pi G D_{\rm od} D_{\rm ds}}.
-\ee
-and the $D$'s are the angular diameter distances between the objects
-refered to in the subscripts: o is the observer, d is the deflector and
-s is the source. If the surface mass density of the sheet exceeds
-$\Sigma_{\rm cr}$, multiple images of the source can occur, otherwise
-only one image will be observed, although that image will still be
-perturbed relative to the unlensed case.
+\Sigma_{\rm cr}(z) \equiv \frac{c^2 D_{\rm os}}{4 \pi G D_{\rm od} D_{\rm ds}}.
+\ee
+and the D's are the angular diameter distances between the objects refered to in the subscripts: o is the observer, d is the deflector and s is the source.
+If the surface mass density of the sheet exceeds $\Sigma_{\rm cr}$, multiple images of the source can
+occur, otherwise only one image will be observed, although that image will still be perturbed
+relative to the unlensed case.
 
@@
 
-Strong lenses sit in our real Universe -- they are not \truely isolated;
-there is some mass along the line of sight coming from intervening
-structures. These structures may be physically associated with the lens
-e.g. other members of a group or cluster, or they may be the result of
-chance alignments at any redshift.  Whilst it is rare for three galaxies
-to line up well enough for both of the background sources to be strongly
-lensed \citep{GavazziEtal2008,CollettEtal2012a}, the large size of dark
-matter halos makes a partial alignment -- with the additional structure
-acting as a perturbing weak lens --  a near certainty
-\citep{Vale+White2003,HilbertEtal2007}. These additional structures
-induce an external shear which can be recovered in the mass-modelling of
-the lens, but they can also introduce a convergence that is undetectable
-from the image positions, shapes and relative fluxes
-\citep{FalcoEtal1985}.
-
-If the intrinsic source brightness changes, the observed brightness in
-each image does not change simultaneously: there will be a time delay,
-$\Delta t$, between the brightness change in each image. Despite the
-invariance of the image positions and fluxes, under the addition of an
-external convergence (and appropriate re-scaling of the lens potential)
-the relative Fermat potential between the images is {\it not} invariant,
-and so the time delay changes. As such it is necessary to include
-$\kappa$ in the lens modelling, if cosmological parameters are to be
-estimated accurately and precisely from observed time delays
-\citep{SuyuEtal2010}. Mass distributions that are physically associated with the lens galaxy
-will affect the stellar dynamics of the lens galaxy, so that dynamical
-observations can break the internal mass-sheet degeneracy by providing
-an additional estimate of the lens galaxy's mass
-\citep[e.g.,][]{SuyuEtal2010}. In this work our aim is to quantify the
-lensing effect of massive objects, regardless of their position along
-the line of sight.
-
-If there is external convergence present that is not included in the
-lens modeling, then the time delay distance -- inferred assuming $\kappa
-= 0$ -- will be $(1-\kappa)$ less than the true value of $\Dt$:
+Strong lenses sit in our real Universe -- they are not truely isolated;
+there is some mass along the line of sight coming from intervening structures.
+These structures may be physically associated with the lens e.g. other members
+of a group or cluster, or they may be the result of chance alignments at any redshift. 
+Whilst it is rare for three galaxies to line up well enough for both of the background sources
+to be strongly lensed \citep{GavazziEtal2008,CollettEtal2012a}, the shear scale of dark matter halos
+makes a partial alignment -- with the additional structure acting as a perturbing weak lens -- 
+a near certainty \citep{Vale+White2003,HilbertEtal2007}. These additional
+structures induce an external shear which can be recovered in the mass-modelling
+of the lens, but they can also introduce a convergence that
+is undetectable from the image positions, shapes and relative fluxes; {\it the
+mass sheet-degeneracy} \citep{FalcoEtal1985}.
+
+If the intrinsic source brightness changes, the observed brightness in each image does not change
+simultaneously - there is a time delay, $\Delta t$, between the brightness change in
+each image. Despite the invariance of the image positions and fluxes, under the addition
+of an external convergence (and appropriate re-scaling of the lens potential) the relative Fermat potential between the images is {\it not}
+invariant, and so the time delay changes. As such it is necessary to include $\kappa$
+in the lens modelling, if cosmological parameters are to be estimated accurately and
+precisely from observed time delays \citep{SuyuEtal2010}. If there is any external convergence, that is not included in the lens
+modeling, then the time delay distance -- inferred assuming $\kappa = 0$ -- will be
+$(1-\kappa)$ less than the true value of $\Dt$.
 \be 
@@
 \ee
-We can hence estimate the true distance if we have  with additional
-knowledge of $\kappa$. Since $\kappa$ is typically small the absolute
-uncertainty on the estimate of $\kappa$ \correspends to the fractional
-uncertainty with which time-delay distances can be \infered.
-
-The relationship between convergence $\kappa$ and magnification $\mu$ is
-\bea 
-\mu &=&       \frac{1}{(1-\kappa)^2 - |\gamma|^2}, \notag \\
-    &\approx& \frac{1}{(1-2\kappa)}
-\label{eq:MassSheet:mag}
-\eea
-where we have used the fact that the magnitude of the gravitational
-shear at any point is typically comparable to the magnitude of the 
-convergence. For small $\kappa$, the fractional uncertainty in the
-inferred luminosity of a magnified source will be approximately  twice
-the absolute uncertainty in the convergence~$\kappa$. These
-relationships will allow us to put our results on convergence estimation
-in context.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{The Millenium Simulation}
-\label{sec:MS}
-
-In order to test the accuracy of our convergence estimates, we need to
-know the true convergence for each line of sight. We cannot use  real
-lines of sight for this,  but must use simulated lines of sight instead.
-In this section we briefly review the Millenium Simulation, the ray
-tracing calculations that have been carried out in it, and the mock
-galaxy catalogs that have been produced.
-
-The \MS \citep{SpringelEtal2005} is a cosmological N-body simulation of
-Dark Matter structures in a cubic region approximately 680~Mpc in
-comoving size, followed from redshift 127 to the present day. With an
-approximate halo mass resolution of $2\times10^{10}{\rm M}_{\odot}$
-(corresponding approximately to a galaxy with luminosity $0.1L^{*}$), it
-provides a detailed prediction for the distribution of dark structures
-present in the Universe, under the assumptions of the $\Lambda$CDM model
-of hierarchical structure formation, cosmological densities as given at
-the end of \Sref{sec:intro}, and $\sigma_8 = 0.9$. 
-Galaxy properties,
-such as stellar masses, luminosities and colours, were assigned to the
-simulated halos according to a semi-analytic model for galaxy formation
-\citep{DeLucia+Blaizot2007}: the resulting predictions for the galaxy
-luminosity function and correlation function match the observational
-data very well.
-
+We can overcome this degeneracy with additional knowledge of $\kappa$.
+Since $\kappa$ is typically small the absolute uncertainty on the estimate
+of $\kappa$ correspends to the percentage uncertainty with which time-delay
+distances can be infered.
+
+For mass-sheets that are physically associated with the lens galaxy, the mass sheet
+ affects the stellar dynamics of the
+lens galaxy, so dynamical observations can break the internal
+mass-sheet degeneracy by providing an additional estimate of the lens galaxy's mass
+\citep[e.g.,][]{SuyuEtal2010}. In this work our aim is to quantify the lensing effect of mass-sheets that are not physically associated with the lens galaxy -- mass-sheets
+lying infront or behind the lens -- and the uncertainties induced by reconstructing
+those mass-sheets using simple prescriptions applied to potential astronomical observables.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Estimating external convergence: The halo model approximation}
+\label{sec:model}
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Convergence from Ray Tracing}
-\label{sec:MS:raytracing}
-
-\citet{HilbertEtal2009} calculated the lensing convergence using the
-``lightcone'' dark matter only 
-output of the \MS, providing 1.7 degree square 
-mock sky maps of this
-quantity. In this process, the dark matter density from the simulation
-was projected onto a set of lens planes at discrete redshifts,
-adaptively gridded and smoothed, and then the second derivatives of the 
-lensing potential required for the components of the magnification
-matrix were computed using a multiple lens plane ray tracing algorithm.
-The first order approximation to this algorithm \citep[equation 17
-of][]{HilbertEtal2009} gives the total convergence at a given sky
-position~$\bmath{\theta}$ as the simple summation of the surface density
-in each lens plane, weighted by the inverse critical surface density
-$\Sigma_{\rm cr}$ for that plane's redshift:
-\be
-\kappa(\bmath{\theta}) = \sum_i \frac{\Sigma_i(\bmath{\theta})}
-                                     {\Sigma_{\rm cr}(z_i,\zs)}.
-\ee
-This approximation was found to be accurate to a few percent or better
-in $\kappa$, even on 30 arcsecond scales.
-
-To define a test line of sight, we draw a random sky position from
-within the convergence maps, bilinearly interpolate between the pixels
-of the map, and store the result as the ``true'' convergence for that
-line of sight, $\kappa_{\rm true}$.
-
-\todo{Stefan}{Check this is all accurate and complete!}
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Mock Galaxy Catalogs}
-\label{sec:MS:mocks}
-
-Our goal is to recover the ``true'' convergence defined in the previous
-sub-section, via an inference that takes a catalog of galaxy positions
-and properties as data. We construct such catalogs by selecting all \MS
-galaxies within a circular aperture of a given angular radius centred on
-the line of sight position, with apparent $i$-band magnitude brighter
-than a given limit. The parent catalog, from \citet{HilbertEtal2011},
-contains galaxy positions and magnitudes, all of which include lensing
-effects (deflections and magnifications). We also have access to the
-underlying galaxy halo masses and redshifts, which we will use to
-calibrate the reconstruction, and also to explore any sources of bias
-and scatter. Since the true convergence is that of only the dark matter,
-we focus on reconstructing the dark matter halos alone. Our model for
-doing this is outlined in the next section.
-
-\todo{Stefan, Tom}{Check this is all accurate and complete!}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Estimating Convergence: The Halo Model Approximation}
-\label{sec:model}
 
@@
 -- this is the subject of Section \ref{subsec:voids}.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 
@@
 
-\subsection{Accounting for voids, filaments and dark structures}
+\subsection{Correcting for voids, filaments and dark structures}
 \label{subsec:voids}
@@
 
-Given an uncertain stellar mass to halo mass conversion, the
-$\pr(\kappah|\{\Mstar,z\})$ can shift  relative to
-$\pr(\kappah|\{\Mhalo,z\})$; this is because of the highly asymetric
-conversion from stellar mass through halo mass into $\kappah$. If this shift
-is ignored the resulting $\Pr(\kappa)$ can become highly biased. To calibrate
-this effect we reconstruct each of our calibration sightlines, in the same way
-as the observed sightlines to generate $\pr(\kappa,\kappah|\{\Mstar,z\})$, for
-each calibration sightline we use the median of $\pr(\kappah|\{\Mstar,z\})$ to
-form a de-biased $\Pr(\kappa|\kappah)$.
+Given an uncertain stellar mass to halo mass conversion, the $\pr(\kappah|\{\Mstar,z\})$ can shift 
+relative to $\pr(\kappah|\{\Mhalo,z\})$; this is because of the highly asymetric conversion from
+stellar mass through halo mass into $\kappah$. If this shift is ignored the resulting $\Pr(\kappa)$
+can become highly biased. To calibrate this effect we reconstruct each of our calibration
+sightlines, in the same way as the observed sightlines to generate
+ $\pr(\kappa,\kappah|\{\Mstar,z\})$, for each calibration sightline we use the median of $\pr(\kappah|\{\Mstar,z\})$ to form a de-biased $\Pr(\kappa|\kappah)$.
 
@@
 
-\section{Calibrating the halo model}
+\section{Using the Millenium Simulation to test the halo model approximation with known halo mass and redshift}
 \label{sec:knownMh+z}
 
-In order to test the reconstruction proceedure outlined in Section
-\ref{sec:model}, we now apply it to mock galaxy catalogs generated in
-regions on the sky around lines of sight with known
-$\kappa$ in the Millenium Simulation.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
+In order to justify the reconstruction proceedure outlined in Section \ref{sec:model}, we would like to apply it to lines of sight with known $\kappa$.\notes{can't use real los, have to use \MS}
+
+\subsection{Ray-tracing through simulated Lines of Sight}
+\label{subsec:raytracing}
+\todo{Stefan}{Write section on how the ray tracing was done}
+
+\subsection{Generating mock lightcones from simulations}
+\todo{Stefan}{Write section on how halos are extracted from the MS n-body particles}
+
+\notes{view of a lightcone figure should go at the end of this section}
 \subsection{How does $\kappah$ relate to $\kappa$?}
@@
 
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
 \subsection{How succesful is the calibration at converting $\kappah$ into $\kappa$?}
@@
 
-Since voids are not included in the halo model approximation $\kappah$
-is a biased estimator of $\kappa$, but this can be calibrated for useing
-the proceedure of Section \ref{subsec:voids}. Taking the reconstructed
-$\kappah$ for $1\times 10^{5}$ lines of sight we form the joint
-distribution, P$(\kappa,\kappah)$ and marginalize over P$(\kappah)$ to
-give P($\kappa$). We define the bias as the difference between the
-expectation value of $\kappa$ and the known true value of $\kapparay$
-for each Line of sight and we define the reconstruction width,
-$\sigma_{\kappa}$,as half the width of the interval containing the
-central $68\%$ of the probability P($\kappax$). From $1\times 10^{4}$
-reconstructed lines of sight we find the the bias to have mean of
-$-9.5\times 10^{-6}$ and a mean reconstruction width of 0.0132 which is
-roughly 1.8 times smaller than the width of the global P$(\kappax)$. We
-find that our $\kappa$ distributions are consistent with the global
-$\kappa$ distribution; Figure \ref{fig:globaldist} shows that sampling
-from $\pr(\kappa)$ for 100000 lines of sight is very similar to the
-global $\pr(\kappa)$. Given perfect knowledge of halo mass and redshift,
-the calibration proceedure provides an unbiased estimate of $\kappa$
-that is $\sim$2 times as precise than using the global $\pr(\kappa)$.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+Since voids are not included in the halo model approximation $\kappah$ is a biased estimator of $\kappa$, but this can be calibrated for useing the proceedure of Section \ref{subsec:voids}.
+Taking the reconstructed $\kappah$ for $1\times 10^{5}$ lines of sight we form the joint distribution, P$(\kappa,\kappah)$ and marginalize over P$(\kappah)$ to give P($\kappa$).
+We define the bias as the difference between the expectation value of $\kappa$ and the known true value of $\kapparay$ for each Line of sight and we define the reconstruction width, $\sigma_{\kappa}$,as half the width of the interval containing the central $68\%$ of the probability P($\kappax$).
+From $1\times 10^{4}$ reconstructed lines of sight we find the the bias to have mean of $-9.5\times 10^{-6}$ and a mean reconstruction width of 0.0132 which is roughly 1.8 times smaller than the width of the global P$(\kappax)$.
+We find that our $\kappa$ distributions are consistent with the global $\kappa$ distribution; Figure \ref{fig:globaldist} shows that sampling from $\pr(\kappa)$ for 100000 lines of sight is very similar to the global $\pr(\kappa)$.
+Given perfect knowledge of halo mass and redshift, the calibration proceedure provides an unbiased estimate of $\kappa$ that is $\sim$2 times as precise than using the global $\pr(\kappa)$.
 
@@
 
-Before investigating the uncertainties caused by imperfect knowledge of
-halo mass and redshift, we investigate the uncertainties induced by a
-magnitude limited reconstruction and a field of view limited
-reconstruction. The halos in our catalogue are populated by galaxies and
-given magnitudes according to the semi-analytic model of
-\citet{deLucia+Blaizot2007} and by applying magnitude cuts to our
-catalogue, we can investigate the scatter caused by unobserved halos.
-The majority of the convergence comes from halos with an $i$ magnitude
-between 18 and 24. Figure \ref{fig:where} shows the cumulative
-contribution to $\kappah$ as a function of projected distance from the
-line of sight, magnitude and redshift. Unsurprisingly we find that most
-of the convergence comes from halos whose galaxies are close to the line
-of sight. As a function of magnitude, we find that $\kappah$ is
-dominated by objects with magnitudes between $i=18$ and $i=24$. Objects
-brighter than $i=18$ are either too rare or too close to the observer to
-make a significant contribution to the convergence. Objects fainter than
-$i=24$ are too small to be important, unless they are extremely close to
-the line of sight, but we find that including including halos fainter
-than $i=24$ does not improve our reconstruction. Figure \ref{fig:magcut}
-shows the scatter on $\kappah-\kappa$ (where $\kappah$ is shifted so
-that it's mean is zero) as a function of reconstruction magnitude limit.
-Since these objects must be extremely close to the line of sight to make
-a non-zero $\kappah$ contribution it is likely that neglecting stellar
-mass and using a spherical NFW prescription are too naive to adequately
-reconstruct $\kappax$; thus we do not expect a deeper survey to decrease
-the size of the uncertainty in mapping $\kappah$ onto $\kappa$. We find
-that halos at all redshifts contribute to the convergence, but halos at
-redshifts of $z \sim z_{\rm source}/2$ contribute the most.
+Before investigating the uncertainties caused by imperfect knowledge of halo mass and redshift, we investigate the uncertainties induced by a magnitude limited reconstruction and a field of view limited reconstruction.
+The halos in our catalogue are populated by galaxies and given magnitudes according to the semi-analytic model of \citet{deLucia+Blaizot2007} and by applying magnitude cuts to our catalogue, we can investigate the scatter caused by unobserved halos.
+The majority of the convergence comes from halos with an $i$ magnitude between 18 and 24.
+Figure \ref{fig:where} shows the cumulative contribution to $\kappah$ as a function of projected distance from the line of sight, magnitude and redshift.
+Unsurprisingly we find that most of the convergence comes from halos whose galaxies are close to the line of sight.
+As a function of magnitude, we find that $\kappah$ is dominated by objects with magnitudes between $i=18$ and $i=24$.
+Objects brighter than $i=18$ are either too rare or too close to the observer to make a significant contribution to the convergence.
+Objects fainter than $i=24$ are too small to be important, unless they are extremely close to the line of sight, but we find that including including halos fainter than $i=24$ does not improve our reconstruction.
+Figure \ref{fig:magcut} shows the scatter on $\kappah-\kappa$ (where $\kappah$ is shifted so that it's mean is zero) as a function of reconstruction magnitude limit.
+Since these objects must be extremely close to the line of sight to make a non-zero $\kappah$ contribution it is likely that neglecting stellar mass and using a spherical NFW prescription are too naive to adequately reconstruct $\kappax$; thus we do not expect a deeper survey to decrease the size of the uncertainty in mapping $\kappah$ onto $\kappa$.
+We find that halos at all redshifts contribute to the convergence, but halos at redshifts of $z \sim z_{\rm source}/2$ contribute the most.
 
@@
 \includegraphics[width=\textwidth]{figs/biasplots.eps}
-\caption[magcut]{Estimating $\kappa-\kappa_{\rm true}$ from subsets of
-lenses. By subtracting the true (ray-traced) convergence from the
-infered P($\kappa$) for each line of sight we are left with a PDF that
-should be estimating zero, these can be multiplied together for multiple
-lines of sight to test for a possible bias. These plots show the
-expectation value of $\prod_{i=1}^N \pr_i(\kappa-\kappa_{\rm true})$ -
-deviations from zero can be seen as a bias. The solid, dashed and dotted
-lines are for combining 20, 5 and 2 lenses respectively. Green lines are
-from multiplying P($\kappa$) infered from photometry alone, whilst red
-lines are from multiplying P($\kappa$) infered from photometry and a
-spectroscopic redshift for all halos with $i<23$ and all halos within 1
-arcminute and $i<24$. The left most plot shows randomly selected lines
-of sight. The central plot shows sight lines randomly selected from the
-third of lines whose P($\kappa$) is most tightly constrained. The right
-hand plot shows only lines of sight with external shear of 0.03 or
-greater.}
+\caption[magcut]{Estimating $\kappa-\kappa_{\rm true}$ from subsets of lenses.
+By subtracting the true (ray-traced) convergence from the infered P($\kappa$) for each line of sight we are left with a PDF that should be estimating zero, these can be multiplied together for multiple lines of sight to test for a possible bias.
+These plots show the expectation value of $\prod_{i=1}^N \pr_i(\kappa-\kappa_{\rm true})$ - deviations from zero can be seen as a bias.
+The solid, dashed and dotted lines are for combining 20, 5 and 2 lenses respectively.
+Green lines are from multiplying P($\kappa$) infered from photometry alone, whilst red lines are from multiplying P($\kappa$) infered from photometry and a spectroscopic redshift for all halos with $i<23$ and all halos within 1 arcminute and $i<24$.
+The left most plot shows randomly selected lines of sight.
+The central plot shows sight lines randomly selected from the third of lines whose P($\kappa$) is most tightly constrained.
+The right hand plot shows only lines of sight with external shear of 0.03 or greater.}
 \label{fig:where}

### 2012-10-31 doc/paper-lcr.tex
checked though up to testing on mocks

@@
 attempt a reconstruction of the convergence induced by every halo near a
-line of sight. This is the subject of Section \ref{subsec:halos}. We
+line of sight. This is the subject of Section \ref{sec:model:halos}. We
 also need to account for the mass in the Universe that is not associated
 with the galaxies we can see -- this is the subject of Section
-\ref{subsec:voids}.
+\ref{sec:model:voids}.
 
@@
 \subsection{Halos}
-\label{subsec:halos}
+\label{sec:model:halos}
 
@@
 This PDF contains a hidden assumption of an uninformative prior PDF for
-$kappah$ -- in the case of infinitely poorly measured stellar masses and
-redshifts, $\pr(\kappah|\data)$ will have very long tails that we do not
-belive to exist. The resolution of this is to apply an additional prior
-on $\kappah$, given by the global underlying $\kappah$ distribution from
-the simulation, $\pr(\kappah)$. In the limiting  case of very poor
-photometric data, $\pr(\kappah|\data)$ then defaults to this
-distribution. \todo{All}{Discuss this. It ties us to the simulation --
-but is not unreasonable. Is the argument about poor data valid? Tom?}
+$\kappah$ -- in the case of infinitely poorly measured stellar masses and
+redshifts, $\pr(\kappah|\data)$ will have very long tails corresponding to
+very overdense sightlines that we do not believe exist. The resolution of this
+is to divide out the effective prior PDF that was applied during the halo mass
+estimation process (which is broad, and hance close to uniform), and apply an
+additional prior on $\kappah$, given by the global underlying $\kappah$
+distribution from the simulation. In the limiting  case of very poor
+photometric data, $\pr(\kappah|\data)$ then defaults to this distribution.
+\todo{All}{Discuss this. It ties us to the simulation, but only weakly. Is the
+argument about poor data valid? Tom?}
 
@@
 
-\subsection{Accounting for voids, filaments and dark structures}
-\label{subsec:voids}
-
-Whilst halos contribute a positive convergence to $\kappa$, voids contribute
-a negative convergence. When a raybundle passes through a  region of space
-that is less dense than $\rho_{\rm cr}(z)$ the rays are de-focused\footnote{In
-principle, the convergence caused by halos, is also caused by the overdensity,
+\subsection{Accounting for voids, filaments and other dark structures}
+\label{sec:model:voids}
+
+While halos contribute a positive convergence to $\kappa$, voids contribute
+a negative convergence. When a ray bundle passes through a  region of space
+that is less dense than $\rho_{\rm mean}(z)$ the rays are de-focused\footnote{In
+principle, the convergence caused by halos is also caused by the overdensity,
 but we neglect this effect since halos are typically much more dense than the
-intergalactic medium}. Whilst the  full raytraced solution takes into account
+intergalactic medium}. Whilst the  full ray-traced solution takes into account
 the effect of voids, our reconstruction cannot -- the halo catalogue does not
@@
 void, but the under-density of such a void is hard to infer. Neglecting voids
-would lead to a heavily biased estimate of $\kappa$.
-
-The \proceedure outlined in Section \ref{subsec:halos} allows us to estimate 
-the convergence due to halos given observations of mass, redshift and position
+would lead to a heavily biased estimate of $\kappa$. Moreover, the halos in 
+the model only add mass to the background density, and that background density
+already accounts for all the mass in the Universe! In order to make voids
+negative relative to the mean density, we must subtract a significant smooth
+mass component. The problem is that we do not have a good model for the
+density structure of that smooth component.
+
+The solution we present here is to calibrate the relationship between halo
+convergence $\kappah$ and underlying convergence $\kappa$ (as calculated
+during full ray tracing) using the simulations themselves.
+The halo modelling \proceedure outlined in \Sref{sec:model:halos} allows 
+us to estimate 
+the convergence due to halos given observations of 
+mass, redshift and position,
 $\pr(\kappah|\mathcal{D})$, but what we are interested in is the total convergence
@@
 \end{equation}
-The first term in the integrand relates the summed convergence due to model
-halos, $\kappah$, to the true convergence, $\kappa$. In the Millenium
-Simulation catalogs, we can compute $\kappah$ for each
-selected line of sight and combine multiple lines of sight to calculate $\Pr(\kappa|\kappah)$.
-
-Given an uncertain stellar mass to halo mass conversion, the
-$\pr(\kappah|\{\Mstar,z\})$ can shift  relative to
-$\pr(\kappah|\{\Mhalo,z\})$; this is because of the highly asymetric
-conversion from stellar mass through halo mass into $\kappah$. If this shift
-is ignored the resulting $\Pr(\kappa)$ can become highly biased. To calibrate
-this effect we reconstruct each of our calibration sightlines, in the same way
-as the observed sightlines to generate $\pr(\kappa,\kappah|\{\Mstar,z\})$, for
-each calibration sightline we use the median of $\pr(\kappah|\{\Mstar,z\})$ to
-form a de-biased $\Pr(\kappa|\kappah)$.
-
-For any given line of sight we can then infer
-$\Pr(\kappah|\mathcal{D})$ as described above, and then
-multiply it by $\Pr(\kappa|\kappah)$; we do the marginalisation over $\kappah$
-by drawing samples from the two-dimensional grid and keeping only the
-$\kappa$ values, to form our final result, $\Pr(\kappa|\mathcal{D})$.
+The first term in the integrand relates the convergence due to model halos,
+$\kappah$, to the true convergence, $\kappa$. This conditional distribution
+can be constructed from the Millennium Simulation catalogs, by computing
+$\kappah$ for each selected line of sight using the true values of the halo
+parameters,  and accumulating $\kappah$ and $\kappa$ along a large number of
+such lines of
+sight to  characterize $\Pr(\kappa|\kappah)$.
+For any given line of sight we can then estimate
+$\pr(\kappah|\mathcal{D})$ as described above, and then
+multiply it by $\Pr(\kappa|\kappah)$ and integrate out the intermediate
+nuisance parameter $\kappah$. 
+% We can do the marginalisation over $\kappah$
+% by drawing samples from the two-dimensional grid and keeping only the
+% $\kappa$ values, to form our final result, $\Pr(\kappa|\mathcal{D})$.
+
+However, given an uncertain stellar mass to halo mass conversion, the PDF
+$\pr(\kappah|\{\Mstar,z\})$ can become skewed relative to
+$\pr(\kappah|\{\Mhalo,z\})$; this is because of the assymetry in the
+conversion from stellar mass through halo mass into $\kappah$. A long tail of
+high halo masses gives rise to a tendency to overestimate $\kappah$.
+If this shift is ignored, the resulting $\Pr(\kappa|\data)$ will be 
+biased towards high values of $\kappa$.
+
+We find that we can correct this bias to some extent by artificially 
+suppressing the tails of $\pr(\kappah|\{\Mstar,z\})$. Let the median of
+this PDF be denoted $\kappah^{\rm med}$. We again take a large number of
+calibration sightlines from the \MS catalogs, but this time generate a mock
+stellar mass catalog for each one. We then reconstruct each lightcone in the
+same way as we would an observed field,
+estimate $\pr(\kappah|\{\Mstar,z\})$, and extract its median. Accumulating
+these samples and their corresponding true values of $kappa$, we can form the 
+conditional distribution $\pr(\kappa|\kappah^{\rm med})$. 
+Then, when inferring $\kappa$ from an observed photometric catalog, we would
+estimate $\pr(\kappah|\{\Mstar,z\}_{\rm obs})$ 
+using the halo model, compute the median value 
+$\kappa_{\rm h,obs}^{\rm med}$, and then use the following alternative
+version of 
+\Eref{eq:kappaconv} to infer $\kappa$: 
+\bea
+\Pr(\kappa|\mathcal{D}) &=& \int \dee\kappah^{\rm med} 
+   \Pr(\kappa|\kappah^{\rm med}) \Pr(\kappah^{\rm med}|\mathcal{D}) \notag \\
+                        &=& \Pr(\kappa|\kappa_{\rm h,obs}^{\rm med}).
+\label{eq:calkappaconv}   
+\eea
+Here, we have replaced $\Pr(\kappah^{\rm med}|\mathcal{D})$ with a delta
+function centred at the observed median value $\kappa_{\rm h,obs}$.
 
@@
 
-\section{Calibrating the halo model}
+\section{Results: Perfect Halo Data}
 \label{sec:knownMh+z}
 
-In order to test the reconstruction \proceedure outlined in Section
-\ref{sec:model}, we now apply it to mock galaxy catalogs generated in
-regions on the sky around lines of sight with known
-$\kappa$ in the Millenium Simulation.
+We now put the reconstruction \proceedure outlined above into practice, first
+inferring $\kappa$ from $\kappah$ in the case of hypothetical galaxy catalogs
+with noiseless redshifts and halo masses. The reason for doing this is to
+check the validity of the calibration process, and then also to  investigate
+the primary sources of the convergence. It will also provide us with a measure
+of the intrinsic uncertainty introduced by our assumption of all halos being
+spherically-symmetric truncated NFW halos with Neto et al concentration--mass
+relation.
 
@@
 
-\subsection{How does $\kappah$ relate to $\kappa$?}
-
-Given the halo mass catalogue from the Millenium Simulation, 
-and convergence maps produced by ray-tracing through the MS's n-body particles, 
-it is possible to test the validity of the prescription outlined
-in Section \ref{sec:model}. In this section we test reconstruction prescription given perfect
-knowledge of the halos' virial masses and redshifts; this provides us with a measure of the intrinsic uncertainty induced by treating matter as truncated NFW halos. 
-We test the model by comparing $\kappah$ against
-the ray-traced $\kappa$. If the reconstruction process is to be
-succesfull the two quantities should be closely related, although
-we expect $\kappah$ to be offset from $\kappa$ since the former 
-does not include the divergence due to voids.
-Figure \ref{fig:isitbiased} shows that indeed $\kappah$ is a good estimator, regardless of the individual value of $\kappah$.
-At fixed $\kappah$ we find that the scatter in $\kapparay$ grows with $\kappah$; our reconstruction is better at reproducing underdense lines of sight than overdense lines of sight.
+\subsection{How is $\kappah$ related to $\kappa$?}
+
+\Fref{fig:jointkh-k} shows the joint distribution of $\kappah$ and $\kappa$
+values for 100,000 randomly selected \MS lines of sight, assuming noise-free
+halo masses and redshifts. In this case, the PDF $\pr(\kappah|\data)$ is a
+delta function: to read off $\pr(\kappa|\data)$ we must take a thin horizontal
+slice across this joint distribution. Note that the joint PDF plotted in this
+figure is the product of  the conditional distribution that we need for
+calibration, and also the prior PDF for $\kappah$ that we need to ensure that
+the global distribution of $\kappah$ values is defaulted to in the case of
+poor observational data. At fixed $\kappah$ we find in \Fref{fig:jointkh-k}
+that the scatter in $\kapparay$ grows with $\kappah$; our reconstruction is
+better at reproducing underdense lines of sight than overdense lines of sight.
+The effect of ignoring voids and the smooth mass component is evident in this
+plot: $\kappah$ is significantly higher than $\kappa$, at any given $\kappa$
+value. Multiplying by $\pr(\kappah|\data)$ and integrating over $\kappah$
+gives a PDF for $\kappa$ centred at the correct place, by construction.
 
@@
 \includegraphics[width=\columnwidth]{figs/cornerplot.eps}
-\caption[Biased?]{$\kappah$ verses $\kappa$ for 100000 reconstructed lines of sight.
-$\kappah$ traces $\kappa$, but with a non-zero offset which is due to the negative convergence from voids.
-At fixed $\kappah$ the scatter in $\kappa$ grows with $\kappah$.}
-\label{fig:isitbiased}
+\caption[Biased?]{The joint distribution of 
+$\kappah$ and $\kappa$, from 100,000 reconstructed lines of
+sight. $\kappah$ traces $\kappa$, but with a positive offset which arises from
+$\kappah$ not accounting for any voids, dark structures or smooth mass
+component. At fixed $\kappah$ the scatter in $\kappa$ grows with $\kappah$.}
+\label{fig:jointkh-k}
 \end{figure}
 
-%\subsubsection{How does $\gammah$ relate to $\gamma$?}
-
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 
-\subsection{How succesful is the calibration at converting $\kappah$ into $\kappa$?}
+\subsection{How accurate is the $\kappah - \kappa$ calibration?}
 
@@
 \includegraphics[width=\columnwidth]{figs/globaldist.eps}
-\caption[magcut]{Comparison of the global P($\kappa$) from $10^{5}$ lines of sight to $10^{5}$ random samples drawn each from P($\kappax|\{M_{200},z\}$) for a reconstructed lines of sight.
-Red is the global P($\kappa$) and black is a histogram of the samples.
-Given perfect knowledge of halo mass and redshift the reconstruction appears to be correct globally.}
+\caption[magcut]{Recovering the global $\pr(\kappa)$, shown in red, 
+from $10^{5}$ ray-traced lines of
+sight. The black curve shows a histogram of 
+sample reconstructed 
+$\kappa$ values, each one drawn from an inferred PDF 
+$P(\kappa|\{\Mhalo,z\}$)
+in one of $10^{5}$ reconstructed lines of sight. 
+The reconstructions were performed given
+perfect knowledge of halo mass and redshift -- in this case
+the reconstruction recovers the correct convergence.}
 \label{fig:globaldist}
@@
 \includegraphics[width=\textwidth]{figs/where_is_the_kappa.eps}
-\caption[magcut]{Which objects dominate the external convergence for a line of sight?
-From left to right the three figures show the cumulative contribution to convergence from indvidual halos as a function of distance from the line of sight, magnitude and redshift.
-The solid line is the median cumulative contribution, whilst dashed and dot-dashed show the 68 and 95 percent confidence intervals repectively.
-The majority of convergence comes from halos within the central 30 arcseconds.
-The convergence is dominated by halos with $i$ magnitudes between 20 and 24, halos brighter than 20 are rare, whilst fainter halos (at $z<1.4$) must be low mass, so can only contribute to the convergence if they are very close to the line of sight.
-Halos at all redshifts contribute to the convergence but the largest contribution comes from halos with $z \sim z_{\rm source}/2$.}
+\caption[magcut]{Which objects dominate the external convergence for a line of
+sight? From left to right, the three figures show the cumulative contribution
+to the total  convergence from individual halos ($\kappah$) as a function of
+1)  distance from the line of sight, 2) magnitude and 3) redshift.   In each
+panel, the solid line is the median cumulative contribution over a large
+sample of sightlines, while dashed and dot-dashed show the ranges enclosing 68
+and 95 percent of the sightlines repectively.}
 \label{fig:where}
@@
 
-Since voids are not included in the halo model approximation $\kappah$
-is a biased estimator of $\kappa$, but this can be calibrated for useing
-the \proceedure of Section \ref{subsec:voids}. Taking the reconstructed
-$\kappah$ for $1\times 10^{5}$ lines of sight we form the joint
-distribution, P$(\kappa,\kappah)$ and marginalize over P$(\kappah)$ to
-give P($\kappa$). We define the bias as the difference between the
-expectation value of $\kappa$ and the known true value of $\kapparay$
-for each Line of sight and we define the reconstruction width,
-$\sigma_{\kappa}$,as half the width of the interval containing the
-central $68\%$ of the probability P($\kappax$). From $1\times 10^{4}$
-reconstructed lines of sight we find the the bias to have mean of
-$-9.5\times 10^{-6}$ and a mean reconstruction width of 0.0132 which is
-roughly 1.8 times smaller than the width of the global P$(\kappax)$. We
-find that our $\kappa$ distributions are consistent with the global
-$\kappa$ distribution; Figure \ref{fig:globaldist} shows that sampling
-from $\pr(\kappa)$ for 100000 lines of sight is very similar to the
-global $\pr(\kappa)$. Given perfect knowledge of halo mass and redshift,
-the calibration \proceedure provides an unbiased estimate of $\kappa$
-that is $\sim$2 times as precise than using the global $\pr(\kappa)$.
+% Since voids are not included in the halo model approximation, $\kappah$
+% is a biased estimator of $\kappa$, but this can be calibrated for using
+% the \proceedure of \Sref{sec:model:voids}. Taking the reconstructed
+% $\kappah$ for $10^{5}$ lines of sight we form the joint
+% distribution, $\pr(\kappa,\kappah)$ and marginalize over $\pr(\kappah)$ to
+% give $\pr(\kappa)$. 
+%
+% PJM: WTF? We just went through all of this in the previous section!
+% We need to check that we are doing what we say we are.
+
+In this section, let us define the ``bias'' of the reconstruction of a given
+line of sight as the difference between the expectation value of $\kappa$ over
+the inferred PDF $\pr(\kappa|\data)$ and the known true value $\kappatrue$.
+Let us also define the ``width,'' $\sigma_{\kappa}$, to be half the width of
+the interval containing the central $68\%$ of the posterior probability
+$\pr(\kappa|\data)$.
+
+In an ensemble of $10^{4}$ reconstructed lines of sight, we find the the mean
+bias to be $-9.5\times 10^{-6}$, and the mean width to be 0.0132. This is
+approximately 1.8 times smaller than the width of the global $\pr(\kappa)$. 
+We find that our inferred $\kappa$ PDFs are consistent with the global
+$\kappa$ distribution; Figure \ref{fig:globaldist} shows that sampling from
+$\pr(\kappa|\data)$ in 100,000 reconstructed lines of sight produces a
+distribution of $\kappa$ values over the sky identical to the global
+$\pr(\kappa)$. Given perfect knowledge of halo mass and redshift, the
+calibration \proceedure provides an unbiased estimate of $\kappa$ that is
+$\sim$2 times as precise as using the global $\pr(\kappa)$.
 
@@
 
-Before investigating the uncertainties caused by imperfect knowledge of
-halo mass and redshift, we investigate the uncertainties induced by a
-magnitude limited reconstruction and a field of view limited
-reconstruction. The halos in our catalogue are populated by galaxies and
-given magnitudes according to the semi-analytic model of
-\citet{DeLucia+Blaizot2007} and by applying magnitude cuts to our
-catalogue, we can investigate the scatter caused by unobserved halos.
-The majority of the convergence comes from halos with an $i$ magnitude
-between 18 and 24. \Fref{fig:where} shows the cumulative
-contribution to $\kappah$ as a function of projected distance from the
-line of sight, magnitude and redshift. Unsurprisingly we find that most
-of the convergence comes from halos whose galaxies are close to the line
-of sight. As a function of magnitude, we find that $\kappah$ is
-dominated by objects with magnitudes between $i=18$ and $i=24$. Objects
-brighter than $i=18$ are either too rare or too close to the observer to
-make a significant contribution to the convergence. Objects fainter than
-$i=24$ are too small to be important, unless they are extremely close to
-the line of sight, but we find that including including halos fainter
-than $i=24$ does not improve our reconstruction. Figure \ref{fig:magcut}
-shows the scatter on $\kappah-\kappa$ (where $\kappah$ is shifted so
-that it's mean is zero) as a function of reconstruction magnitude limit.
-Since these objects must be extremely close to the line of sight to make
-a non-zero $\kappah$ contribution it is likely that neglecting stellar
-mass and using a spherical NFW prescription are too naive to adequately
-reconstruct $\kappax$; thus we do not expect a deeper survey to decrease
-the size of the uncertainty in mapping $\kappah$ onto $\kappa$. We find
-that halos at all redshifts contribute to the convergence, but halos at
-redshifts of $z \sim z_{\rm source}/2$ contribute the most.
+Before investigating the uncertainties caused by imperfect knowledge of halo
+mass and redshift, we investigate the uncertainties induced by a limits on the
+magnitude of the observed galaxy sample, and on the field of view. The halos
+in our catalogue are populated by galaxies and given magnitudes according to
+the semi-analytic model of \citet{DeLucia+Blaizot2007}: by applying magnitude
+cuts to our catalogue, we can investigate the amount of scatter caused by
+unobserved halos.
+
+\Fref{fig:where} shows the cumulative contribution to $\kappah$ as a function
+of projected distance from the line of sight, magnitude and redshift.
+We find that most of the convergence comes from halos whose
+galaxies are close to the line of sight. 
+Over half of the  convergence
+typically comes from halos within 30 arcseconds of the line of sight; by 2
+arcminutes, this fraction is XX\%. \todo{Tom}{Put a number on this.} 
+As a function of magnitude, we find
+that $\kappah$ is dominated by objects with magnitudes between $i=18$ and
+$i=24$. Objects brighter than $i=18$ are either too rare, or too close to the
+observer, to make a significant contribution to the convergence. Objects
+fainter than $i=24$ are too small to be important, unless they are extremely
+close to the line of sight, but we find that including halos fainter than
+$i=24$ does not improve the reconstruction.  \Fref{fig:magcut} shows the
+scatter on $\kappah-\kappa$ (where $\kappah$ is shifted so that its mean is
+zero) as a function of reconstruction magnitude limit. 
+%
+% Since these objects
+% must be extremely close to the line of sight to make a non-zero $\kappah$
+% contribution, it is likely that neglecting stellar mass and using a spherical
+% NFW prescription are too naive to adequately reconstruct $\kappax$.
+%
+% PJM: the sentence above does not make sense!
+%
+We do
+not expect a deeper survey to decrease the size of the uncertainty in mapping
+$\kappah$ onto $\kappa$. Halos at all redshifts out to the source redshift
+(1.4, here) contribute to the convergence, but the largest contribution comes from
+halos with $z \sim z_{\rm source}/2$.
 
@@
 \includegraphics[width=\columnwidth]{figs/mag_scatter.eps}
-\caption[magcut]{The 16, 50 and 84\% confidence intervals on $\kappah$ minus $\kappa$ as a function of the limiting $i$ band depth of the halo reconstruction.
-$\kappah$ has been shifted such that $\left\langle\kappah\right\rangle=0$.
-The majority of the constraining power comes from reconstructing halos with magnitudes between $18<i<24$.}
+\caption[magcut]{The 16, 50 and 84\% confidence intervals on $\kappah$ minus
+$\kappa$ as a function of the limiting $i$ band depth of the halo
+reconstruction. $\kappah$ has been shifted such that
+$\left\langle\kappah\right\rangle=0$. The majority of the constraining power
+comes from reconstructing halos with magnitudes between $18<i<24$.}
 \label{fig:magcut}
@@
 $\pr(\kappax)$ does not induce a bias.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\includegraphics[width=\columnwidth]{figs/biasplots3.eps}
+\caption{}
+\label{fig:no-median-tricks}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2012-10-31 doc/paper-lcr.tex
Body of text done

@@
   Tommaso~Treu$^{4}$\thanks{\packard},
-  Christopher~D.~Fassnacht$^{5}$,}
+  Vasiliy~Belokurov$^{1}$,}
 \newauthor{%
+  Christopher~D.~Fassnacht$^{5}$,
   L\`eon~V.~E.~Koopmans$^{6}$,
@@
 
-Real attempts to reconstruct the convergence along a line of sight will not have direct access to the masses of dark matter halos, 
-and will likely not have access to a spectroscopic redshift either. Instead these properties must be inferred from astrophysical
-observables. In principle the only observables may be astrometric positions, photometric colours and possibly spectra. In this section we
-quantify the errors induced by inferring the halo mass and redshift from the observables. Much work has already focused on using
-photometric colours to infer stellar mass \citep[\eg][]{AugerEtal2009} and redshifts \citep[\eg][]{BPZ}, in line with these we shall use
-stellar mass and photometric redshifts (with appropriate errors), as the observables that must be converted into an estimate
-of $\kappax$. We will investigate two main sources of error: inferring halo mass given observed stellar mass and placing halos at the wrong redshift due to photometric redshift error.
-
-We generate a stellar mass for each halo according to the stellar mass--halo mass relation of 
-\citet{BehrooziEtal2010}. From this stellar mass we simulate 
-an observed stellar mass by drawing a sample from $\pr(\log(M_{* \mathrm {obs}})|\log(M_{* \mathrm {true}}))$ which is given by a Gaussian of width $\sigma_{M_*}$ centred on $\log(M*_{\mathrm {true}})$.
-Where a spectroscopic redshift exists stellar masses can be estimated with typical uncertainties of 0.15 dex \citep{AugerEtal2009}, however with photometric redshifts stellar mass uncertainties are typically three times as large; we use $\sigma_{M_*}=0.15$ for halos with a spectroscopic redshift and $\sigma_{M_*}=0.45$ otherwise.
-For photometric redshift errors we draw a redshift from $\pr(z_{\rm true}|z_{\rm obs})$ which we take as a Gaussian of width $0.1(1+z_{\rm spec})$ centred on $z_{\rm spec}$, where $z_{\rm spec}$ is the halo's true redshift in the \MS catalogue.
+We now move on to consider the halo model reconstruction of line of sight mass
+distributions given noisy astronomical observables. A typical imaging survey
+can be expected to provide measurements of the positions and magnitudes of
+galaxies in a field;  spectra for some of the objects may either come from a
+synergistic survey, or from targeted follow-up. In this section we quantify
+the errors induced by inferring the halo mass and redshift from these
+observables.
+
+As described in \Sref{sec:model:halos}, in this work we infer halo masses
+given measurements of stellar mass. We will investigate two main sources of
+error: inferring halo mass given observed stellar mass, and placing halos at
+the wrong redshift due to photometric redshift error. Much work has already
+focused on using photometric colours to infer stellar mass
+\citep[\eg][]{AugerEtal2009} and redshifts \citep[\eg][]{BPZ}: we will
+estimate the likely uncertainties on stellar mass and redshift based on this
+work.
+
+\subsection{Making Mock Observational Catalogs}
+
+While the \MS catalogs do already contain stellar masses for each galaxy, we
+find that these are not well behaved... \todo{Tom}{Explain why we re-made the
+stellar masses}. We also wanted to be able to perform the functional test of
+trying to recover the convergence having assumed the correct stellar
+mass--halo mass relation. For these reasons, we assign a new stellar mass to
+each halo in the \MS catalogs, according to the stellar mass--halo mass
+relation of  \citet{BehrooziEtal2010}. From this true  stellar mass we
+simulate an observed stellar mass by drawing a sample from 
+$\pr(\log{M^{*}_{\rm obs}}|\log{M^{*}_{\rm true}})$ which we take to be a
+Gaussian of width $\sigma_{M_*}$ centred on $\log(M*_{\mathrm {true}})$. Where
+a spectroscopic redshift exists stellar masses can be estimated with typical
+uncertainties of 0.15 dex \citep{AugerEtal2009}; however with photometric
+redshifts stellar mass uncertainties are typically three times as large. We
+use $\sigma_{M_*}=0.15$ for halos with a spectroscopic redshift and
+$\sigma_{M_*}=0.45$ otherwise. For photometric redshift errors we draw a
+redshift from $\pr(z_{\rm true}|z_{\rm obs})$ which we take to be a Gaussian
+of width $0.1(1+z_{\rm spec})$ centred on $z_{\rm spec}$, where $z_{\rm spec}$
+is the halo's true redshift in the \MS catalogue.
+
+\subsection{Reconstructing $\kappa$ given a spectroscopic redshift for every object}
 
@@
 relation's uncertainties requires care: the \proceedure we use to do this
-is given in Appendix \ref{appendix:MSMH}. By drawing sample halo masses
+is given in \Aref{appendix:MSMH}. By drawing sample halo masses
 and redshifts, we can infer a sample $\kappah$ using the \proceedure of
-Section \ref{sec:model}; repeatedly drawing samples allows us to
-estimate P$(\kappah)$ for each reconstructed line of sight.
-
-\subsection{Reconstructing $\kappa$ given a spectroscopic redshift for every object}
+\Sref{sec:model}; repeatedly drawing samples allows us to
+estimate $\pr(\kappah|\data)$ for each reconstructed line of sight. We then
+transform this into our target PDF $\pr(\kappa|\data)$.
 
@@
 \includegraphics[width=\columnwidth]{figs/Width.eps}
-\caption[magcut]{The widths of the \infered P$(\kappah|\mathcal{D})$ for $10^5$ lines of sight given different amounts of data.
-Blue assumes a spectroscopic redshift for every halo with $i<26$, purple assumes a spectroscopic redshift for every halo with $i<23$ and every within 1 arcminute and $i<24$, cyan assumes a spectroscopic redshift for every halo with $i<22$ and green assumes that no objects in the field have a spectroscopic redshift}
+\caption{The widths of the \infered PDFs $\pr(\kappah|\data)$ for
+$10^5$ lines of sight, given different quality of data. Blue:
+spectroscopic redshift for every halo with $i<26$; Purple: 
+spectroscopic redshift for every halo with $i<23$, and every halo with $i<24$
+within 1 arcminute; Cyan: spectroscopic redshift for every halo with $i<22$; 
+Green: all the objects in the field have only photometric redshifts.}
 \label{fig:reconwidths}
@@
 \includegraphics[width=\columnwidth]{figs/Widthvshilberrt.eps}
-\caption[magcut]{Width of the \infered P$(\kappah|\mathcal{D})$ verses
-the true $\kappa$ along a line of sight. Blue assumes a spectroscopic
-redshift for every halo, whilst green assumes no spectroscopic
-redshifts.
-The width of the \infered P$(\kappah)$ increases with $\kappa$.
-If correctly reconstructed, the lowest density lines of sight can provide the most precise measurement of the time delay distance.}
+\caption{Width of the \infered PDF $\pr(\kappah|\data)$ versus the true
+$\kappa$ along a line of sight. Blue assumes a spectroscopic redshift for
+every halo, whilst green assumes only photometric redshifts. The width of the
+\infered $\pr(\kappah|\data)$ increases with $\kappa$. 
+\todo{Tom}{Check that you mean
+$\kappah$ and not $\kappa$, and potentially change the graph!}}
 \label{fig:widthsvsH}
@@
 
-The best possible reconstruction of $\kappah$ corresponds to having a sepctroscopic redshift for every single object in our field.
-Observationally such a reconstruction would be prohibitively expensive in terms of telescope time, but we investigate this scenario as an ideal case.
-Reconstructing the lines of sight with perfect knowledge of the redshift but an uncertain stellar mass, we find that the width of $\Pr\left(\sumkappah \right)$ grows with the expectation value of $\sumkappah$; this is not surprising since the low $\sumkappah$ lines of sight are relatively empty and so there are few opportunities for uncertainties in the halo masses to propogate into $\sumkappah$ uncertainties.
-After applying the void correction the median reconstruction width is 0.0123; with 22 percent of lines of sight having a reconstruction width less than 0.01.
+The best possible reconstructions of $\kappa$ will come from having a
+spectroscopic redshift for every single object in each field
+(\Fref{fig:reconwidths}).  In terms of telescope time, such a reconstruction
+would be prohibitively expensive, but we investigate this scenario as an ideal
+case. Reconstructing the lines of sight with perfect knowledge of the redshift
+but an uncertain stellar mass, we find that the width of $\pr(\kappa|\data)$
+grows with the expectation value of $\kappa$ (\Fref{fig:widthsvsH}). The low
+$\kappa$ lines of sight are relatively empty, and so there are few
+opportunities for uncertainties in the halo masses to \propogate into $\kappa$
+uncertainties. The median reconstruction width in this idealised situations is
+0.0123; some 22\% of lines of sight would have a reconstruction width less
+than 0.01.
+
+% PJM: Note that I removed talk of void correction here - surely we should be
+% just applying the method we describe and inferring $\kappa$?
 
@@
 
-Inferring the stellar mass of a galaxy from its magnitude and colours requires an estimate of how far away the galaxy is; without a spectroscopic redshift the the \infered stellar mass is less precise.
-However, obtaining photometry has much lower observational cost; over the next few years several large area photometric surveys will reach 24th magnitude \citep{EUCLID,LSST}, these will provide sufficient data to reconstruct lines of sight {\it without} additional observations.
-In principle the photometric redshift is correlated with the \infered stellar mass, however we do not model this effect since the convergence from the outskirts of an individual halo is only weakly dependant on redshift at fixed mass: the redshift error is small effect on the recovered $\pr(\kappa)$ when compared to the effect of uncertain stellar masses.
-With only photometric redshifts the uncertainty on $\sum\kapparec^{\rm halos}$ is much larger than the spectrocopic case and this propogates into a broader $\pr(\kappa)$, although the photometric reconstruction still typically produces a 1.4 fold improvement compared to the precision of the global P($\kappa$).
+Inferring the stellar mass of a galaxy from its magnitude and colours requires
+an estimate of how far away the galaxy is; without a spectroscopic redshift
+the \infered stellar mass is less precise. However, obtaining photometry has
+much lower observational cost; over the next few years several large area
+photometric surveys will reach 24th magnitude \citep{Euclid,LSST}, these will
+provide sufficient data to reconstruct lines of sight {\it without} additional
+observations. In principle the photometric redshift is correlated with the
+\infered stellar mass, however we do not model this effect since the
+convergence from the outskirts of an individual halo is only weakly \dependant
+on redshift at fixed mass: the redshift error has only a small effect on the
+inferred $\pr(\kappa|\data)$ when compared to the effect of uncertain stellar
+masses.  With only photometric redshifts the uncertainty on
+$\kappah$ is much larger than in the spectrocopic case and this
+\propogates into a broader $\pr(\kappa|\data)$, although the photometric
+reconstruction still typically produces a 40\% improvement compared to the
+precision of the global $\pr(\kappa)$ (\Fref{fig:widthsvsH}).
 
@@
 
-Whilst a fully photometric reconstruction provides useful constraints on $\pr(\kappa)$, targeted spectroscopy can provide addtional constraints upon the masses and redshifts of halos whose $\kappah$ contribution have the largest absolute uncertainty.
-Obtaining spectra of bright ($i<22$) objects is relatively fast with 8-m class telescopes; we find that if spectroscopic redhsifts were known for all $i<22$ galaxies in our field the reconstruction improves slightly upon the purely photometric reconstruction, although the improvement depends strongly upon the nature of the particular line of sight.
-Obtaining spectra for fainter objects would be considerably more expensive, but if spectroscopic redshifts could be obtained for all $i<23$ galaxies and all $i<24$ galaxies within 1 arcminute of the line of sight the $\pr(\kappa)$ would be almost as good as having complete spectroscopic coverage.
-High $\kappa$ lines of sight benefit the most from additional spectral coverage, since these LoS have the most uncertain $\kappah$.
-Consistent with our previous findings the lowest $\kappa$ lines of sight have the most constrained $\kappa$ PDFs.
+While a fully photometric reconstruction provides useful constraints on
+$\pr(\kappa|\data)$, targeted spectroscopy can provide addtional constraints
+on the masses and redshifts of halos whose $\kappah$ contribution have the
+largest absolute uncertainty. Obtaining spectra of bright ($i<22$) objects is
+relatively fast with large telescopes: however, we find that if spectroscopic
+redhsifts were known for all $i<22$ galaxies in our field the reconstruction
+improves slightly upon the purely photometric reconstruction, although the
+improvement can depend strongly on the details of the particular line of
+sight. Obtaining spectra for fainter objects would be correspondingly more
+expensive, but if spectroscopic redshifts could be obtained for all $i<23$
+galaxies and all $i<24$ galaxies within 1 arcminute of the line of sight, the
+$\pr(\kappa|\data)$ would be almost as good as having complete spectroscopic
+coverage (\Fref{fig:reconwidths}). High $\kappa$ lines of sight benefit the
+most from additional spectral coverage, since these LoS have the most
+uncertain $\kappah$. Consistent with our previous findings the lowest $\kappa$
+lines of sight have the most constrained $\kappa$ PDFs.
 
@@
 
-\section{Testing for Systematic errors}
-\label{sec:biases}
+\section{Systematic Errors due to Sample Selection}
+\label{sec:bias}
+
 \begin{figure*}
 \includegraphics[width=\textwidth]{figs/biasplots.eps}
-\caption[magcut]{Estimating $\kappa-\kappa_{\rm true}$ from subsets of
+\caption{Estimating $\kappa-\kappa_{\rm true}$ from subsets of
 lenses. By subtracting the true (ray-traced) convergence from the
@@
 lines of sight to test for a possible bias. These plots show the
-expectation value of $\prod_{i=1}^N \pr_i(\kappa-\kappa_{\rm true})$ -
-deviations from zero can be seen as a bias. The solid, dashed and dotted
-lines are for combining 20, 5 and 2 lenses respectively. Green lines are
-from multiplying P($\kappa$) \infered from photometry alone, whilst red
-lines are from multiplying P($\kappa$) \infered from photometry and a
+expectation value of $\prod_{i=1}^N \pr_i(\kappa-\kappa_{\rm true})$ --
+deviations from zero constitute biases. The solid, dashed and dotted
+lines correspond to combinations of 
+20, 5 and 2 sightlines respectively. Green lines show the results
+from multiplying $\pr(\kappa|\data)$ \infered from photometry alone, whilst red
+lines are from multiplying $\pr(\kappa)$ \infered from photometry and a
 spectroscopic redshift for all halos with $i<23$ and all halos within 1
-arcminute and $i<24$. The left most plot shows randomly selected lines
+arcminute and $i<24$. The leftmost plot shows randomly selected lines
 of sight. The central plot shows sight lines randomly selected from the
-third of lines whose P($\kappa$) is most tightly constrained. The right
+33\% of lines whose P($\kappa$) is most tightly constrained. The right
 hand plot shows only lines of sight with external shear of 0.03 or
@@
 
-Whilst it is good to reconstruct $\kappa$ precisely it is vital that
-$\kappa$ is reconstructed accurately. A precise, inaccurate $\kappa$
-estimator is worse than useless for cosmology. We test the accuracy of
-our reconstructed $\pr(\kappa)$ in the following way: for each line of
-sight we shift the reconstructed $\pr(\kappa)$ by the line of sight's
-raytraced $\kappa$ to give $\pr(\kappa-\kapparay)$. Since the
-$\pr(\kappa-\kapparay)$ for each line of sight is an \independant estimator of zero, the PDFs can be combined according to
-
+While it is good to reconstruct $\kappa$ precisely, it is more important that
+$\kappa$ is reconstructed accurately. 
+% A precise, inaccurate $\kappa$ estimator
+% is worse than useless for cosmology. 
+% PJM: steady on.
+We test the accuracy of our reconstructed $\pr(\kappa|\data)$ in the following
+way: for each line of sight we shift the reconstructed $\pr(\kappa|\data)$ by
+the line of sight's true value of $\kappa$ to give
+$\pr(\kappa-\kappatrue|\data)$. Since the $\pr(\kappa-\kappatrue|\data)$ for
+each line of sight is then an \independant estimator of zero, the PDFs can be
+combined according to
 \be
 \label{eq:bias}
-\mathcal{P}_N=\prod_{i=1}^N \pr_i(\kappa-\kappa_{\rm true})
-\ee
-
-We quantify the bias as the size of the deviation in the expectation value of $\mathcal{P}$ from zero.
-If the bias of $\mathcal{P}_N$ is typically smaller than the half-width of $\mathcal{P}_N$ our $\kappa$ estimators can be considered accurate.
-The number of useful time delay lines of sight can be approximated as the point at which the modulus of the bias and width of $\mathcal{P}_N$ are the same size.
-
-%\todo{tom}{do}
-%\subsection{Using the wrong M$_{\rm halo}$-M$_{*}$ relation}
-\subsection{Selection bias from a subset of lines of sight?}
-
-First we test for systematic errors in the reconstruction of a randomly
-selected subset of samples. With the purely photometric reconstruction
-there is a small bias towards underestimating $\kappa$,  combining 6
-lenses the half-width and bias of $\mathcal{P}_{6}$ both equal 0.007.
-With targeted spectroscopic follow up this improves slightly, for the
-combination of 8 lenses the half-width and expectation value 
-$\mathcal{P}_{8}$ equal 0.005. Since strong lens modelling uncertainties
-are typically at the 3\% level, several hundred lenses are needed to
-reach this level of precision, but at that point a 0.005 bias in
-$\kappa$ estimation would become the limiting factor on time-delay
-cosmography.
+\mathcal{P}_N = \prod_{i=1}^N \pr_i(\kappa-\kappa_{\rm true})
+\ee
+In this section, we quantify the bias as the size of the deviation in the
+expectation value of $\mathcal{P}_N$ from zero. If the bias of $\mathcal{P}_N$
+is smaller than the half-width of $\mathcal{P}_N$, our $\kappa$ estimators can
+be considered accurate. 
+The point at which the modulus of the bias and the width of $\mathcal{P}_N$
+are approximately equal gives an estimate of the number of objects which can
+be combined before the measurement is limited by systematic error.
+
+The source of systematic error that we investigate  is that of sample
+selection: we define three different selections of lines of sight, and compute
+the bias present in each one in turn, as a function of data quality. The
+results described below are illustrated in \Fref{fig:biasplots}.
+
+\subsubsection{Selecting random lines of sight}
+\label{sec:bias:random}
+
+We first consider a purley random selection of lines of sight. With the purely
+photometric reconstruction, there is a small bias towards underestimating
+$\kappa$: combining 6 targets the half-width and bias of $\mathcal{P}_{6}$
+both equal 0.007. With targeted spectroscopic follow up this improves
+slightly, for the combination of 8 sightlines the half-width and expectation
+value  $\mathcal{P}_{8}$ equal 0.005.  If these lines of sight hosted time
+delay lenses, the latter number would correspond to a systematic error of
+0.5\% in time delay distance. Since strong lens modelling uncertainties are
+typically at the 3-4\% level, a sample of 8 lenses would still be limited by
+modelling uncertainty. However, a sample containing 100 or more lenses or more
+would be limited by the external convergence reconstruction instead.
 
 \subsubsection{Selecting only the lines of sight with tight $\pr(\kappax)$}
-\label{sec:tightPDF}
-
-Since lens monitoring campaigns are expensive, it is likely that only a
-subset of lenses will be observed. By pre-selecting the lenses with the
-most well constrained $\pr(\kappax)$, the cosmological value per lens
-can be increased, however this has the potential to induce a bias. It is
-probable that only photometry will be available at the time of lens
-selection (although spectroscopic follow-up might be conducted at a
-later date). We mimik such a selection by drawing lines of sight only
-from those in the lowest third of $\sigma_{\kappa}$ given a photomtric
-reconstruction of their fields. We find that selecting the most tightly
-constrained lines of sight {\it decreases} the bias - our reconstruction
-is most succesful for the lowest $\kappa$ lines of sight. With
-photometry alone the bias is at the 0.0028 level. With a targeted
-spectroscopic follow-up of the selected lines of sight there is
-negligible improvement, since the best constrained lines of sight are
-the most empty, but it is the high-$\kappa$ lines of sight that benefit
-the most from spectroscopy. Photometry of the field is sufficient to
-adequately select the best lines of sight for cosmology - and doing so
-greatly increases both the precision and accuracy of the cosmological
-constraints per lens.
+\label{sec:bias:tightPDF}
+
+Since follow-up campaigns (such as high resolution imaging, or time
+variability monitoring) are expensive, it is likely that only a subset of
+detected objects will be observed further. By pre-selecting objects that have 
+the most well constrained convergence, the cosmological value per lens can be
+increased. However, this selection has the potential to induce a bias. It is
+probable that only photometry will be available at the time of sub-sample
+selection (although spectroscopic follow-up might be conducted at a later
+date). We mimic such a selection by drawing lines of sight only from those in
+the lowest third of $\sigma_{\kappa}$, given a purely photometric
+reconstruction of their fields.
+
+We find that selecting the most tightly constrained lines of sight {\it
+decreases} the bias -- our reconstruction is most \succesful for the lowest
+$\kappa$ lines of sight. With photometry alone, the bias in this sample is
+0.0028. With targeted spectroscopic follow-up of the selected lines of sight
+there is negligible improvement, since the best constrained lines of sight are
+the most empty, and it is the high-$\kappa$ lines of sight that benefit the
+most from spectroscopy. Photometry of the field is sufficient to adequately
+select the best lines of sight for cosmology -- and doing so greatly increases
+both the precision and accuracy of the cosmological constraints per system.
 
 \subsubsection{Selecting only high shear lines of sight}
-
-\todo{phil}{Write up why lenses are likely to be gamma biased}
-
-\notes{The uncertainties from modeling a strong lens system depends on
-the comfiguration of the source images. With only two point images ofthe
-source the lens slope and mass are degenerate; the mass-slope
-degeneracy\citep[need citation][Saha?]{mass-slope degeneracy}. Where
-lensed arcs or four point images are present the mass-slope degeneracy
-can be broken and cosmology can be extracted, \citep{Suyu2012a}. The
-detectability of arcs depend on the source, but the presence of four
-images (so called quads) depend on the shear of the lens model - a high
-shear is needed to produce a quad. The shear is almost certainly
-dominated by the lens model itself, but it is possible that quads are
-biased towards high external shear.}
-
-By selecting only lines of sight with an external shear of $\gamma>0.03$ we can test the effect of shear selection.
-We find that in all cases $\kappa$ is underestimated at the $\sim$0.01 level.
-Part of this effect is mitigated if only the lines of sight with both $\gamma>0.03$ and sharp $\pr(\kappax)$ are used but biases at the $\sim$0.005 level remain.
-Since our model does not include shear constraints it is not surprising that selecting based on shear can induce a bias.
-A more sophisticated model that includes the shear recovered from the lens modelling may not be susceptable to this bias.
-The toy model of this section ($\gamma>0.03$) is likely to be a much stronger selection than reality, but it is worth noting that the reconstruction \proceedure will be biased if lens selection functions are extreme and unaccounted.
+\label{sec:bias:tightPDF}
+
+Time delay lenses are often selected for follow-up based on their images'
+brightness (to make monitoring observations less expensive), their images'
+separation (to decrease the covariance between the ground-based image
+lightcurves), or the fact that they are quadruply-imaging rather than
+doubly-imaging, since this yields 3 time delays instead of 1, and a higher
+magnification, more informative Einstein Ring system. All three of these
+properties favour lenses with high convergence and shear along their lines of
+sight. Focusing on the quad selection, we might expect many of these systems
+to have significant external shear (since the cross-section for 4 image
+production is so sensitive to ellipticity in the lens mass distribution (or
+equivalently, external shear due to the lens' environment).
+
+By selecting only lines of sight with an external shear of $\gamma>0.03$ we
+can test the impact of shear selection. We find that in this sample, $\kappa$
+is systematically underestimated at the $\sim$0.01 level. Part of this effect
+is mitigated if only the lines of sight with both $\gamma>0.03$ and sharp
+$\pr(\kappax)$ are used but biases at the $\sim$0.005 level remain. Since our
+model does not include shear constraints it is not surprising that selecting
+based on shear can induce a bias. A more sophisticated model that includes the
+shear recovered from the lens modelling may be less susceptable to this bias.
+The toy model of this section ($\gamma>0.03$) is likely to be a much stronger
+selection than reality, but it is worth noting that the reconstruction
+\proceedure will be biased if lens selection functions are extreme and
+unaccounted for.
 
@@
 model ignores voids and assumes all halos follow a spherical
-truncated-NFW profile our model does not include all of the relevant
-physics, hence the width of our resulting $\pr(\kappax)$ is still
+truncated-NFW profile our halo model does not include all of the relevant
+physics; hence, the width of our resulting $\pr(\kappa|\data)$ is still
 typically $\sim$0.01 for any given lightcone, even with a perfect
@@
 necessary. Interestingly, we have found that the most empty lines of
-sight can be reconstructed with the most precision. $\kappax$ for empty
-lines of sight have little contributions from halos and a large
+sight can be reconstructed with the most precision. $\kappa$ estimates
+for empty
+lines of sight receive few contributions from halos, and a large
 contribution from voids; since they have the tightest PDFs after the
@@
 With a photometric reconstruction of the field there is a significant
-broadening but the resulting precision is still typically 1.5 times
-greater than using the global $\kappa$ distribution.
-
-Since the uncertainty on $\pr(\kappa|\mathcal{D})$ is $\sim$0.01 even
-with perfect knowledge of halo mass and redshift it seems that voids
+broadening, but the resulting precision is still typically 50\% 
+higher than using the global $\kappa$ distribution.
+
+Since the uncertainty on $\pr(\kappa|\data)$ is $\sim$0.01 even
+with perfect knowledge of halo mass and redshift, it seems that voids
 (plus deviations from sphericity and dark matter clumping within the
@@
 clumping will likely always remain a difficulty for line of sight
-reconstruction; but as Figure \ref{fig:magcut} shows observing deeper
+reconstruction; but as \Fref{fig:magcut} shows, observing deeper
 than 24th magnitude does not signifcantly help the reconstruction.
@@
 
-For a small fraction of lines of sight, $\pr(\kappax)$ remains very
+For a small fraction of lines of sight, $\pr(\kappa|\data)$ remains very
 broad even after applying our reconstruction; these lines of sight are
 typically the most overdense lines of sight in the universe. For
-time-delay cosmography the most observationally expensive task is the
-lightcurve monitoring, whilst making photometric observations of a
-4$\times$4 arcminute patch of sky survey down to 24th magnitude is a
+time-delay cosmography the most observationally expensive tasks are the
+lightcurve monitoring and high resolution follow-up imaging and spectroscopy,
+while making photometric observations of a
+4$\times$4 arcminute patch of sky survey down to 24th magnitude is
 relatively cheap. We have shown that with a single epoch observation of
-the region around a strong lens it is possible to infer $\pr(\kappax)$.
-If a line of sight has a broad $\pr(\kappax)$ it can be rejected {\it
-before} the investment of longterm lightcurve monitoring. We find that
+the region around a strong lens it is possible to infer $\pr(\kappa|\data)$.
+If a line of sight has a broad $\pr(\kappa|\data)$ it can be rejected {\it
+before} the investment of follow-up. We find that
 selecting only the lines of sight with the most tightly constrained
-$\pr(\kappax)$ does not induce a bias.
+$\pr(\kappa)$ does not induce a bias in $\kappa$, and hence distance.
+
+The method we have outlined can also be used to estimate the external shear
+along a line of sight. Shear is an observable that can be extracted from
+strong lens modelling, however there is a degeneracy between internal and
+external shear. When the Einstein Ring data are very good it is possible to
+disentangle external and internal shear \citep[\eg][]{xxx}, but there are
+still significant uncertainties: \citet{WongEtal2011} attempted to match the
+shear from strong lens models with a reconstruction of the local lens group
+environment, but found a tension between the strong lens model and the
+reconstruction of the environment. Since \citet{WongEtal2011} only
+reconstructed the local lens group, rather than the full line of sight
+contribution, it is unclear whether the external shear from lens models can be
+reconciled with a line of sight reconstruction. {\it If} external shear can be
+measured, it provides an additional constraint on which of the \MS lines of
+sight are similar to the reconstructed line of sight. \citet{SuyuEtal2012}
+found that for RXJ1131 combining shear constriants with galaxy number count
+overdensity, gave a significantly different $\pr(\kappa|\gamma,N_{45})$
+compared to the PDF from number count overdensity alone,
+$\pr(\kappax|N_{45})$. While not included in this paper, we found that given
+perfect knowledge of the halo mass and redshift the raytraced external shear
+$\gamma$ and the reconstructed external shear $\gamma_{\mathrm{h}}$  are
+similar, with 68 percent of lines obeying
+\be
+\label{eq:shearineq}
+|{\boldmath{\gamma}-\boldmath{\gamma_{\mathrm{h}}}}| < \mathrm{0.025}
+\ee 
+Future work should investigate whether $\gamma_{\mathrm{h}}$ can be used
+to improve the accuracy and precision of $\kappa$ estimation, given a
+reconstruction of the line of sight.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The method we have outlined can also be used to estimate the external shear
-along a line of sight. Shear is an observable that can be extracted from
-strong lens modelling, however there is a degeneracy between internal and
-external shear. Progress has been made in disentangelling external and
-internal shear \citep[\eg][]{xxx} but there are still significant
-uncertainties: \citet{WongEtal2011} attempted to match the shear from strong
-lens models with a reconstruction of the local lens group environment, but
-found a tension between the strong lens model and the reconstruction of the
-environment. Since \citet{WongEtal2011} only reconstructed the local lens
-group, rather than the full line of sight contribution, it is unclear whether
-the external shear from lens models can be reconciled with a line of sight
-reconstruction. {\it If} external shear can be measured, it provides an
-additional constraint on which of the Millenium Simulation lines of sight are
-similar to the reconstructed line of sight. \citet{SuyuEtal2012} found that
-for RXJ1131 combining shear constriants with galaxy number count overdensity,
-gave a significantly different $\pr(\kappax|\gamma,N_{45})$ copmpared to the
-PDF from number count overdensity alone, $\pr(\kappax|N_{45})$. Whilst not included
-in this paper, we found that given perfect knowledge of the halo mass and redshift
-the raytraced external shear $\gamma$ and the reconstructed external shear $\gamma_{\mathrm{h}}$ 
-are similar, with 68 percent of lines obeying
-\be
-\label{eq:shearineq}
-|{\boldmath{\gamma}-\boldmath{\gamma_{\mathrm{h}}}}| < \mathrm{0.025}
-\ee 
-Future work should investigate whether $\gamma_{\mathrm{h}}$ can be used
-to improve the accuracy and precision of $\kappa$ estimation, given a
-reconstruction of the line of sight.
-
-This work has used the \MS as a calibration guide. If the real universe
-is not like  the \MS the the calibration will be incorrect - repeating
-the study with a different simulation would quantify the sensitivity of
-our results to the simulation used. Similarly the use of a different
-semi-analytic model to paint galaxies onto halos could provide a useful
-check, to ensure against potential systematic errors.
+The reduction of $\pr(\kappah|\data)$ to just its median value, before using
+it to look up the appropriate $\pr(\kappa)$ from the simulated sightline
+ensemble, is reminiscent of the procedure followed by \citet{SuyuEtal2010},
+and Greene et al (in prep.) The reconstruction method can be seen as the
+limiting case of the weightings explored by Greene et al: rather than using
+weighted number counts in an aperture, we treat each galaxy individually, and
+predict  $\kappa_{\rm h,obs}^{\rm med}$ for use in their place. One
+significant disadvantage of these types of method is that they impose a
+bottleneck in the flow of information. Once you have compressed to one number,
+it is difficult to incorporate more information later; you have to recompute
+all the calibrations. Using the full PDF for $\kappah$ is the more correct
+thing to do: at present, however, it suffers from significant bias in the
+photometric data case. \Fref{fig:no-median-tricks} shows how $\kappa$ is
+overestimated, as a result of the high scatter in halo mass for objects with 
+high stellar mass. Future work should increasing the precision of the halo
+mass estimates.
+
+More generally, the \MS as a calibration tool. If the real Universe is not
+like the \MS, then the calibration will be incorrect; repeating the study using
+a different simulation to make the test catalogs would allow us to quantify
+the sensitivity of our results to the simulation used. Similarly the use of a
+different semi-analytic model to paint galaxies onto halos, and an alternative
+stellar mass--halo mass relation would both enable similar exploration of
+these systematic errors.
+
+More generally, the method presented here is tied to the simulations at
+several points: in particular, the prior PDF for $\kappah$, and the
+conditional distribution $\pr(\kappa|\kappah)$ used to convert halo model
+convergence to total convergence. The former tie could potentially be avoided
+if the halo mass estimation gave rise to a reasonable $\pr(\kappah|\data)$ on
+its own. Possibilities for improving the precision of the halo mass estimation
+include incorporating a group and cluster finder, and then inferring halo mass
+from optical richness \citep[\eg][]{MaxBCG} in tandem with BCG stellar mass,
+and using additional galaxy scaling relations to make use of the luminosity
+and size information present. The latter tie is more difficult, since breaking
+it means modelling the unseen mass structures and voids from first principles.
+In the wide field survey era, will it be possible to infer hierarchically the
+parameters of a flexible model for these things from the data itself? Weak
+lensing shears will be available over the whole Euclid and LSST survey areas:
+constraining halo models using this information is an interesting possibility.
 
@@
 In this work we have investigated a simple halo model prescription for
-reconstructing all the mass along a line of sight to an intermediate
-redshift source. We have used the ray-traced lensing convergence along
-lines of sight through the Millenium Simulation to test this approach,
-and to calibrate estimates of the total convergence along a line of
-sight to an observed distant galaxy made by summing the convergences due
-to each object in a photometric catalogue. Having found that the
-reconstruction process is effective given perfect knowledge of halo mass
-and redshift, we investigated the effects of reasonable uncertainties in
-the stellar mass and redshift of each halo, and propogated these
-uncertainties into a $\pr\left(\sumkappah\right)$ for each line of
-sight. We draw the following conclusions:
+reconstructing all the mass along a line of sight to an intermediate redshift
+source. We have used the ray-traced lensing convergence along lines of sight
+through the Millenium Simulation to test this approach, and to calibrate
+estimates of the total convergence made by summing the convergences due to
+each object in a photometric catalogue. Having found that the reconstruction
+process is effective given perfect knowledge of halo mass and redshift, we
+investigated the effects of reasonable uncertainties in the stellar mass and
+redshift of each halo, and propagated these uncertainties into a
+$\pr(\kappa|\data)$ for each line of sight. We also defined three different
+possible line of sight selections, and investigated the bias induced by these
+selections. We draw the following conclusions:
 
@@
 
-\item Our model uses a truncated spherical NFW profile for each dark
+\item Our halo model uses a truncated spherical NFW profile for each dark
 matter halo and neglects voids, but despite the model's simplicity the
-reconstructed $\kappah$ is a good tracer of $\kappa$.  We found that
-with perfect knowledge of the halo mass and redshift (from the Millenium
-Simulation catalogs), for a typical line of sight the reconstruction
-gives an unbiased estimate of $\pr(\kappa)$ that is a factor of 2 less
-broad than the global $\pr(\kappa)$.
+reconstructed $\kappah$ is a good, if biased, tracer of $\kappa$.  We found
+that with perfect knowledge of the halo mass and redshift (from the Millennium
+Simulation catalogs), for a typical line of sight the reconstruction gives an
+unbiased estimate of $\kappa$ that is a factor of 2 more precise than the
+global $\pr(\kappa)$.
+
+\item With uncertain halo masses and redshifts, we find that
+$\pr(\kappah|\data)$ is still a useful indicator for inferring
+$\pr(\kappa|\data)$ from the ensemble of simulated lines of sight, but the
+resulting PDFs tend to be much broader than for perfect halo mass and redshift
+reconstructions. The long tails of the $\kappah$ distribution can be
+suppressed by focusing on the median value as an indicator for $\kappa$
+instead.
 
@@
 sight and optimize the use of follow-up time. Photometric data is sufficient 
-to select the best lines of sight for follow-up.
-
-\item With uncertain halo masses and redshifts, we find that
-$\pr(\kappah)$ is still a useful indicator for generating an estimate
-of $\pr(\kappa)$ from the ensemble of simulated lines of sight, but the resulting
-PDFs tend to be much broader than for perfect
-halo mass and redshift reconstructions. Spectroscopic coverage helps to tighten 
-$\pr(\kappa)$ for high $\kappa$ lines of sight, but is of limited use for 
-low $\kappa$ lines of sight.
-
-\item It is very rare for halos further than 2 arcminutes to make a
-significant contribution to $\kappa$. We also found that including halos
-whose host galaxy is less luminous than $i=24$ does not significantly improve
-our reconstruction \proceedure. A photometric survey to this depth of a
-4$\times$4 arcminute patch around the lens would approach the limiting
-uncertainties of our simple reconstruction recipe, and yield a 
-$\pr(\kappa)$ that has, on average, a width of 0.016 --
-1.5 times less broad than the global $\pr(\kappa)$.
-
-\item We find that the lines of sight with the sharpest $\pr(\kappa)$ are
-typically under-dense. With a photometric reconstruction of all lens fields,
-and following up only the lenses with the sharpest $\pr(\kappa)$,
-the width of the dominant statistical uncertainty in time-delay cosmography
-can be halved, without inducing biases at the one percent level.
+to select the best lines of sight for follow-up. Spectroscopic coverage helps
+to tighten  $\pr(\kappa|\data)$ for high $\kappa$ lines of sight, but is of
+limited use for  low $\kappa$ lines of sight.
+
+\item It is very rare for halos further than 2 arcminutes from the line of
+sight to make a significant contribution to $\pr(\kappa|\data)$. We also found
+that including halos whose host galaxy is less luminous than $i=24$ does not
+significantly improve our reconstruction precision. A photometric survey to
+this depth of a 4$\times$4 arcminute patch around the lens would approach the
+limiting uncertainties of our simple reconstruction recipe, and yield a 
+$\pr(\kappa|\data)$ that has, on average, a width of 0.016. This is 1.5 times
+less broad than the global $\pr(\kappa)$.
+
+\item We find that the lines of sight with the sharpest inferred
+$\pr(\kappa|\data)$ are typically under-dense. With a photometric
+reconstruction of all lens fields, and following up only the lenses with the
+most precise $\kappa$ estimates, the width of the dominant statistical
+uncertainty in time-delay cosmography can be halved, without inducing biases
+at the one percent level.
 
@@
 
-We thank Vasily Belokurov, Risa Wechsler and Peter Behroozi 
+We thank Risa Wechsler and Peter Behroozi 
 for useful discussions and suggestions.

### 2012-10-31 doc/paper-lcr.tex
abstract done - shipping to collaborators!

@@
 
-\todo{PJM}{Make abstract match conclusions.}
-
-Strong gravitational lenses can provide high precision cosmological distance
-measurements; one of the most important sources of systematic error in these
-estimates is the additional mass along the line of sight to the source. Weak
-lensing perturbations by galaxies and groups in this beam can contribute an ``external
-convergence'' $\kappa$ that dominates the  uncertainty in the inferred
-distances; likewise, it may also contaminate estimates of the luminosity of
-objects at high redshift (such as reionisation-era proto-galaxies, and type Ia
-supernovae standard candles).  We characterise this uncertainty by marginalising
-over a probability density function for $\kappa$: here, we investigate the use
-of a simple halo model to estimate $\Pr(\kappa)$ given noisy estimates of the
-photometric redshift and stellar mass of galaxies observed in optical imaging
-surveys of the field in question. We use mock catalogs from the Millenium
-Simulation and compare our reconstructed $\Pr(\kappa)$ to ray-traced $\kappa$ values,
-we find that our model produces a precise estimator of $\kappa$ with only small biases.
-For each lightcone the individual $\Pr(\kappa)$ from this reconstruction process are
-typically 1.8 times more precise than the global distribution of $\kappa$ given perfect knowledge 
-of the halo mass and redshift. After incorporating uncertainties on redshift and halo and stellar masses
-we typically find that the reconstruction yields an improvement factor of 1.4. For each line of sight the
- $\Pr(\kappa)$ can be formed before the investment of light-curve monitoring: by following up only the 
-most constrained lines of sight a factor of 2 improvement over the global $\pr(\kappax)$ should be 
-achievable.
+High precision cosmological distance measurements towards individual objects
+such as time delay gravitational lenses or type Ia supernovae are affected by
+weak lensing perturbations by galaxies and groups along the line of sight.
+Such massive structures contribute an ``external convergence'' $\kappa$ that
+in some cases dominates the uncertainty in the inferred distances.  We
+characterise this uncertainty by marginalising over a probability density
+function for $\kappa$: here, we investigate the use of a simple halo model to
+estimate $\pr(\kappa|\data)$ given noisy estimates of the photometric redshift
+and stellar mass of galaxies observed in optical imaging surveys of the field
+in question. We use mock catalogs from the Millennium Simulation, and compare
+our reconstructed $\pr(\kappa|\data)$ to ray-traced $\kappa$ truth values: 
+taking into account realistic uncertainties on redshift and stellar masses, we
+typically find that the reconstruction yields an improvement in precision of
+40\% over the global $\pr(\kappa)$. For any given line of sight the
+convergence estimate can be made before the investment of expensive follow-up
+observations: we find that selecting systems by the precision with which
+$\kappa$ can be estimated leads to a low density sample that would give
+distance estimates a factor of 2 more precise, with biases as low as 0.5\%.
+Preferentially selecting lines of sight with high external shear (as might
+happen in an assembled sample of quadruply-imaged time delay lenses) has the
+opposite effect, with distances biased by around 1\%. We suggest areas for the
+improvement of this general analysis framework that should allow yet more
+accurate cosmological inferences to be made.
 

### 2012-10-31 doc/paper-lcr.tex
abstract done - shipping to collaborators!

@@
 \ee
-\todo{Tom}{Add sentence about scatter!}
 
@@
 photometric data, $\pr(\kappah|\data)$ then defaults to this distribution.
-\todo{All}{Discuss this. It ties us to the simulation, but only weakly. Is the
-argument about poor data valid? Tom?}
+
+% \todo{All}{Discuss this. It ties us to the simulation, but only weakly. Is the
+% argument about poor data valid? Tom?}
 
@@
 For any given line of sight we can then estimate
-$\pr(\kappah|\mathcal{D})$ as described above, and then
+$\pr(\kappah|\data)$ as described above, and then
 multiply it by $\Pr(\kappa|\kappah)$ and integrate out the intermediate
@@
 estimate $\pr(\kappah|\{\Mstar,z\})$, and extract its median. Accumulating
-these samples and their corresponding true values of $kappa$, we can form the 
+these samples and their corresponding true values of $\kappa$, we can form the 
 conditional distribution $\pr(\kappa|\kappah^{\rm med})$. 
@@
 function centred at the observed median value $\kappa_{\rm h,obs}$. 
+The procedure of reducing the full PDF for $\kappah$ to just its median is
+risky: the simulated lightcones that have median $\kappah$ values to match are
+not guaranteed to provide an accurate estimate of $\kappa$ via this PDF
+look-up. We proceed with caution, quantifying the biases and PDF widths in the
+sections below.
 
@@
 typically comes from halos within 30 arcseconds of the line of sight; by 2
-arcminutes, this fraction is XX\%. \todo{Tom}{Put a number on this.} 
+arcminutes, this fraction is \todo{XX\%}{Tom?}.
 As a function of magnitude, we find
@@
 While the \MS catalogs do already contain stellar masses for each galaxy, we
-find that these are not well behaved... \todo{Tom}{Explain why we re-made the
-stellar masses}. We also wanted to be able to perform the functional test of
+find that these are not well behaved at the low mass end. 
+% \todo{Tom}{Explain why we re-made the stellar masses!}. 
+We also wanted to be able to perform the functional test of
 trying to recover the convergence having assumed the correct stellar
@@
 every halo, whilst green assumes only photometric redshifts. The width of the
-\infered $\pr(\kappah|\data)$ increases with $\kappa$. 
-\todo{Tom}{Check that you mean
-$\kappah$ and not $\kappa$, and potentially change the graph!}}
+\infered $\pr(\kappah|\data)$ increases with $\kappa$.}
+%\todo{Tom}{Check that you mean $\kappah$ and not $\kappa$, and potentially change the graph!}}
 \label{fig:widthsvsH}

### 2012-11-01 doc/paper-lcr.tex
added citations to Karpenka et al

@@
 discrepancies.
+%
+\citet{KarpenkaEtal2012} used a halo model to predict the magnification due to
+galaxies along the line of sight to type Ia supernovae, and inferred the
+parameters of the scaling relations between light and mass in these galaxies
+from hundreds of supernova lightcone simultaneously. Following
+\citet{JonssonEtal2010}, they subtract off the mean convergence to ensure that
+the universal mass budget is balanced, and compare models where the halos are
+all have either truncated singular isothermal profiles, or 
+NFW profiles. Both groups detect lensing effects in the supernova data.
 
@@
 In this paper, we combine the halo model reconstruction approach of
-\citeauthor{GunnarssonEtal2006} and \citeauthor{WongEtal2011}, with the
+\citeauthor{GunnarssonEtal2006}, \citeauthor{JonssonEtal2010}, 
+\citeauthor{WongEtal2011} and others, with the
 idea of calibrating to simulations from \citeauthor{SuyuEtal2010}, in
@@
 
-Strong lenses sit in our real Universe -- they are not \truely isolated;
-there is some mass along the line of sight coming from intervening
-structures. These structures may be physically associated with the lens
+Strong lenses, type Ia supernovae and other cosmologically interesting objects
+are never viewed unlensed: 
+there is some mass along the line of sight to them coming from intervening
+structures. These structures may be physically associated with the target
 e.g. other members of a group or cluster, or they may be the result of
-chance alignments at any redshift.  Whilst it is rare for three galaxies
-to line up well enough for both of the background sources to be strongly
-lensed \citep{GavazziEtal2008,CollettEtal2012a}, the large size of dark
-matter halos makes a partial alignment -- with the additional structure
-acting as a perturbing weak lens --  a near certainty
+chance alignments at any redshift.  
+% While it is rare for three galaxies
+% to line up well enough for both of the background sources to be strongly
+% lensed \citep{GavazziEtal2008,CollettEtal2012a}, 
+The large size of dark
+matter halos makes partial alignments -- such that they
+act as perturbing weak lenses --  a near certainty
 \citep{Vale+White2003,HilbertEtal2007}. These additional structures
 induce an external shear which can be recovered in the mass-modelling of
-the lens, but they can also introduce a convergence that is undetectable
-from the image positions, shapes and relative fluxes
+a strong lens, but they also introduce a convergence that is undetectable even
+in these systems:
+the lensed image positions, shapes and relative fluxes are affected, but not
+in an unambiguous way
 \citep{FalcoEtal1985}.
 
-If the intrinsic source brightness changes, the observed brightness in
-each image does not change simultaneously: there will be a time delay,
-$\Delta t$, between the brightness change in each image. Despite the
-invariance of the image positions and fluxes, under the addition of an
-external convergence (and appropriate re-scaling of the lens potential)
-the relative Fermat potential between the images is {\it not} invariant,
-and so the time delay changes. As such it is necessary to include
-$\kappa$ in the lens modelling, if cosmological parameters are to be
-estimated accurately and precisely from observed time delays
-\citep{SuyuEtal2010}. Mass distributions that are physically associated with the lens galaxy
-will affect the stellar dynamics of the lens galaxy, so that dynamical
-observations can break the internal mass-sheet degeneracy by providing
-an additional estimate of the lens galaxy's mass
-\citep[e.g.,][]{SuyuEtal2010}. In this work our aim is to quantify the
-lensing effect of massive objects, regardless of their position along
-the line of sight.
+In time delay lens systems, under the addition of an external convergence (and
+appropriate re-scaling of the lens potential) the relative Fermat potential
+between the images is {\it not} invariant. This means that the time delay
+between the images changes, despite the invariance of the image positions and
+fluxes. As such it is necessary to include $\kappa$ in the lens modelling, if
+cosmological parameters are to be estimated accurately and precisely from
+observed time delays \citep{SuyuEtal2010}. Mass distributions that are
+physically associated with the lens galaxy will affect the stellar dynamics of
+the lens galaxy, so that dynamical observations can break the internal
+mass-sheet degeneracy by providing an additional estimate of the lens galaxy's
+mass \citep[e.g.,][]{SuyuEtal2010}. In this work our aim is to quantify the
+lensing effect of massive objects, regardless of their position along the line
+of sight.
 
@@
 
+For type Ia supernovae, it is the magnification due to line of sight mass
+structure that is a potential source of cosmographic error.
 The relationship between convergence $\kappa$ and magnification $\mu$ is
@@
 
-One of the goals of this paper is to define a method for estimating the
+We require a method for estimating the
 convergence at any point on the sky, given a catalog of observed
-galaxy positions and properties. Typically this could be a  photometric
-galaxy catalog, containing positions, brightnesses, colours, and
-possibly stellar masses and redshifts for each galaxy in the field of
+galaxy properties such as positions, brightnesses, colours, and
+possibly stellar masses and redshifts, for every galaxy in the field of
 the lens, down to some magnitude limit. Since we cannot observe the
@@
 its contribution to the total $\kappa$ along the line of sight \citep[as
-in \eg][]{GunnarssonEtal2006,WongEtal2011}. This mass assignment recipe
-will be uncertain, but can be calibrated with cosmological simulations.
+in \eg][]{GunnarssonEtal2006,WongEtal2011,KarpenkaEtal2012}. 
+This mass assignment recipe
+will be uncertain, but can be calibrated with cosmological simulations, which
+represent a significant additional source of information to what is present in
+the data.
 
@@
 homogeneously populated with NFW halos, the projected surface mass along
-any line of sight will also be divergant.\footnote{At large radius,
+any line of sight will also be divergent.\footnote{At large radius,
 $\Sigma_{\rm nfw} \propto R^{-2}$, but the differential number of halos
@@
 is to divide out the effective prior PDF that was applied during the halo mass
-estimation process (which is broad, and hance close to uniform), and apply an
+estimation process (which is broad, and hence close to uniform), and apply an
 additional prior on $\kappah$, given by the global underlying $\kappah$
@@
 progress a more advanced treatment of both voids and halos will be
-necessary. Interestingly, we have found that the most empty lines of
-sight can be reconstructed with the most precision. $\kappa$ estimates
-for empty
-lines of sight receive few contributions from halos, and a large
-contribution from voids; since they have the tightest PDFs after the
-reconstruction it seems that our model's biggest uncertainties are
-driven by naively reconstructing halos rather than neglecting voids.
-With a photometric reconstruction of the field there is a significant
-broadening, but the resulting precision is still typically 50\% 
-higher than using the global $\kappa$ distribution.
+necessary. \citet{KarpenkaEtal2012} find that their supernova data prefer, in
+the context of their simple halo model, a truncated isothermal profile for the
+galaxy mass distributions. Weak galaxy-galaxy and cluster-galaxy 
+lensing studies
+\citep[\eg][]{GavazziEtal2006,JohnsonEtal2007} also suggest an approximately
+isothermal profile for the mass-shear correlation function; however, at large
+radii these profiles are dominated by the effects of neighbouring halos, which
+should be taken into account by our model. Further iterations on the analysis
+presented here should include the stellar mass distributions that cause the
+isothermal density profiles in the centres of galaxies, although we do not
+expect this to have a big impact on the model. Likewise,  halo
+ellipticity may have some small effect on the predicted convergence.
+
+Filaments and voids are more difficult to model, but simple forms could in
+principle be derived from the structures found in the simulations, and
+included in the halo model in some way. Most importantly for the highest
+$\kappa$ lines of sight will be a better group and cluster model:
+\citet{MomchevaEtal2006} and  \citet{WongEtal2011} recommend using models
+where dark mass is assigned to both galaxy-scale halos and halos for the
+groups and clusters they occupy: to make this work, one could incorporate  a
+group and cluster finder, and then infer halo mass from optical richness
+\citep[\eg][]{MaxBCG} in tandem with BCG stellar mass.
+
+Interestingly, we have found that it is the most empty lines of sight that 
+can be reconstructed with the highest precision. $\kappa$ estimates for empty
+lines of sight receive few contributions from halos, and a large contribution
+from voids; since they have the tightest PDFs after the reconstruction it
+seems that our model's biggest uncertainties are driven by naively
+reconstructing halos rather than neglecting voids. With a photometric
+reconstruction of the field there is a significant broadening, but the
+resulting precision is still typically 50\%  higher than using the global
+$\kappa$ distribution.
 
@@
 its own. Possibilities for improving the precision of the halo mass estimation
-include incorporating a group and cluster finder, and then inferring halo mass
-from optical richness \citep[\eg][]{MaxBCG} in tandem with BCG stellar mass,
-and using additional galaxy scaling relations to make use of the luminosity
-and size information present. The latter tie is more difficult, since breaking
-it means modelling the unseen mass structures and voids from first principles.
-In the wide field survey era, will it be possible to infer hierarchically the
-parameters of a flexible model for these things from the data itself? Weak
-lensing shears will be available over the whole Euclid and LSST survey areas:
-constraining halo models using this information is an interesting possibility.
+are discussed above. The latter tie is more difficult, since breaking it means
+modelling the unseen mass structures and voids from first principles. It
+should be possible to infer hierarchically  the parameters of a flexible model
+for these things from the data itself, as demonstrated by
+\citet{KarpenkaEtal2012} -- how much this dilutes the cosmographic precision
+is to be investigated.  Including more information in this analysis is key:
+weak lensing shears will be available over the whole Euclid and LSST survey
+areas: fitting these with the halo models described here in order to constrain
+the hyper-parameters of the model is an interesting
+possibility.
 
@@
 
-\item Our halo model uses a truncated spherical NFW profile for each dark
-matter halo and neglects voids, but despite the model's simplicity the
-reconstructed $\kappah$ is a good, if biased, tracer of $\kappa$.  We found
-that with perfect knowledge of the halo mass and redshift (from the Millennium
-Simulation catalogs), for a typical line of sight the reconstruction gives an
-unbiased estimate of $\kappa$ that is a factor of 2 more precise than the
-global $\pr(\kappa)$.
+\item Despite our model's simplicity, its reconstructed $\kappah$ values are
+good, if biased, tracers of $\kappa$.  We found that with perfect knowledge of
+the halo mass and redshift (from the Millennium Simulation catalogs), for a
+typical line of sight the calibrated reconstruction gives an unbiased estimate
+of $\kappa$ that is a factor of 2 more precise than the global $\pr(\kappa)$.
 
@@
 \item  For the most overdense lines of sight, the reconstruction produces a
-very broad PDF, but since the reconstruction can be performed before follow-up
-time is invested it will be possible to discard the most uncertain lines of
-sight and optimize the use of follow-up time. Photometric data is sufficient 
-to select the best lines of sight for follow-up. Spectroscopic coverage helps
-to tighten  $\pr(\kappa|\data)$ for high $\kappa$ lines of sight, but is of
-limited use for  low $\kappa$ lines of sight.
+very broad PDF; conversely, we find that the lines of sight with the sharpest
+inferred $\pr(\kappa|\data)$ are typically under-dense. Since the
+reconstructions described here can be performed before follow-up time is
+invested, it will be possible to  select targets by the precision of their
+$\kappa$ estimates. This procedure results in a sample with low bias as well
+as high precision.
+
+\item Photometric data is sufficient  to select the best lines of sight for
+follow-up. Spectroscopic coverage helps to tighten  $\pr(\kappa|\data)$ for
+high $\kappa$ lines of sight, but is of limited use for  low $\kappa$ lines of
+sight.
 
 \item It is very rare for halos further than 2 arcminutes from the line of
-sight to make a significant contribution to $\pr(\kappa|\data)$. We also found
-that including halos whose host galaxy is less luminous than $i=24$ does not
-significantly improve our reconstruction precision. A photometric survey to
-this depth of a 4$\times$4 arcminute patch around the lens would approach the
-limiting uncertainties of our simple reconstruction recipe, and yield a 
+sight to make a significant contribution to $\pr(\kappa|\data)$. Including
+halos whose host galaxy is less luminous than $i=24$ does not significantly
+improve our reconstruction precision.  A photometric survey to this depth of a
+4$\times$4 arcminute patch around the target would approach the limiting
+uncertainties of our simple reconstruction recipe, and yield a 
 $\pr(\kappa|\data)$ that has, on average, a width of 0.016. This is 1.5 times
@@
 
-\item We find that the lines of sight with the sharpest inferred
-$\pr(\kappa|\data)$ are typically under-dense. With a photometric
-reconstruction of all lens fields, and following up only the lenses with the
-most precise $\kappa$ estimates, the width of the dominant statistical
-uncertainty in time-delay cosmography can be halved, without inducing biases
-at the one percent level.
+\item With only a photometric reconstruction of all time delay lens fields,
+and following up only the systems with the most precise $\kappa$ estimates,
+the width of the dominant statistical uncertainty in time-delay cosmography
+can be halved, without inducing biases at the one percent level.
 
@@
 
-External convergence is not the only uncertainty in time delay cosmology,
-but for systems like B1608 it is the dominant one. For most lines
-of sight it is likely that lens modelling induces uncertainties at the
-$\sim$3 percent level, which far exceeds the typical $\kappa$ uncertainties
-after applying our reconstruction \proceedure. By using our method to
-reconstruct lines of sight and select which lense are followed-up, the
-uncertainties due to line of sight convergence will become a sub-dominant 
-source of error.
+External convergence is not the only uncertainty in time delay cosmology, but
+for systems like B1608$+$656 it is the dominant one. For most lines of sight
+it is likely that lens modelling induces uncertainties at the $\sim$3 percent
+level, which far exceeds the typical $\kappa$ uncertainties after applying our
+reconstruction \proceedure. By using our method to reconstruct lines of sight
+and select which lense are followed-up, the uncertainties due to line of sight
+convergence will become a sub-dominant  source of error.
 

### 2012-11-01 doc/references.tex
added citations to Karpenka et al

@@
 
+\bibitem[J{\"o}nsson et al.(2010)]{JonssonEtal2010} J{\"o}nsson, J., 
+Dahl{\'e}n, T., Hook, I., Goobar, A., M{\"o}rtsell, E.\ 2010, \mnras, 402, 526
+
+\bibitem[Johnston et al.(2007)]{JohnstonEtal2007} Johnston, D.~E., 
+Sheldon, E.~S., Wechsler, R.~H., et al.\ 2007, arXiv:0709.1159
+
+\bibitem[Karpenka et al.(2012)]{KarpenkaEtal2012} Karpenka, N.~V., 
+March, M.~C., Feroz, F., \& Hobson, M.~P.\ 2012, arXiv:1207.3708
+
 \bibitem[{{Keeton} \& {Zabludoff}(2004)}]{Keeton+Zabludoff2004}

### 2012-11-01 doc/paper-lcr.tex
conclusions sharpened up

@@
 
-% \voffset=-0.8in
+\voffset=-0.6in
 
@@
 %
-\citet{KarpenkaEtal2012} used a halo model to predict the magnification due to
+\citet{KarpenkaEtal2012} used a halo model to predict deterministically 
+the magnification due to
 galaxies along the line of sight to type Ia supernovae, and inferred the
-parameters of the scaling relations between light and mass in these galaxies
+parameters of scaling relations between light and mass in these galaxies
 from hundreds of supernova lightcone simultaneously. Following
@@
 all have either truncated singular isothermal profiles, or 
-NFW profiles. Both groups detect lensing effects in the supernova data.
+NFW profiles. Both groups were able to 
+detect lensing effects in the supernova data this way.
 
@@
 
-We first consider a purley random selection of lines of sight. With the purely
+We first consider a purely random selection of lines of sight. With the purely
 photometric reconstruction, there is a small bias towards underestimating
@@
 delay lenses, the latter number would correspond to a systematic error of
-0.5\% in time delay distance. Since strong lens modelling uncertainties are
-typically at the 3-4\% level, a sample of 8 lenses would still be limited by
-modelling uncertainty. However, a sample containing 100 or more lenses or more
-would be limited by the external convergence reconstruction instead.
-
-\subsubsection{Selecting only the lines of sight with tight $\pr(\kappax)$}
+0.5\% in time delay distance. Since the statistical distance uncertainties due
+to lens modelling and time delay estimation are likely to be at the 3-4\%
+level \citep{SuyuEtal2010},  only a sample containing 50 or more lenses would
+be limited by the residual bias  following external convergence
+reconstruction.
+
+\subsubsection{Selecting only the lines of sight with tight $\pr(\kappa|\data)$}
 \label{sec:bias:tightPDF}
@@
 both the precision and accuracy of the cosmological constraints per system.
+In the context of time delay distance accuracy given in the previous section,
+the sample size would have to be 160 or so before this residual systematic
+error was equal to the statistical uncertainty.
 
@@
 can test the impact of shear selection. We find that in this sample, $\kappa$
-is systematically underestimated at the $\sim$0.01 level. Part of this effect
-is mitigated if only the lines of sight with both $\gamma>0.03$ and sharp
-$\pr(\kappax)$ are used but biases at the $\sim$0.005 level remain. Since our
-model does not include shear constraints it is not surprising that selecting
-based on shear can induce a bias. A more sophisticated model that includes the
-shear recovered from the lens modelling may be less susceptable to this bias.
-The toy model of this section ($\gamma>0.03$) is likely to be a much stronger
-selection than reality, but it is worth noting that the reconstruction
-\proceedure will be biased if lens selection functions are extreme and
-unaccounted for.
+is systematically underestimated at the $\sim$0.01 level (corresponding to a
+1\% systematic error in distance, significant in a sample of 12 lenses). 
+Part of this effect is mitigated if only
+the lines of sight with both $\gamma>0.03$ and sharp $\pr(\kappa|\data)$ are
+used, but biases at the $\sim$0.005 level remain. Since our model does not
+include shear constraints it is not surprising that selecting based on shear
+can induce a bias. A more sophisticated model that includes the shear
+recovered from the lens modelling may be less susceptible to this bias. The
+cartoon selection model used here ($\gamma>0.03$) is likely to be a much
+stronger selection than reality, but nevertheless it is worth noting that the
+reconstruction \proceedure will be biased if lens selection functions are
+extreme and unaccounted for.
 
@@
 
-We have shown that reconstructing the matter due to halos along any line
-of sight can improve the constraints on the external convergence along
-that line of sight. The total convergence along a line of sight is
-strongly correlated with the reconstructed $\kappah$. However since our
-model ignores voids and assumes all halos follow a spherical
-truncated-NFW profile our halo model does not include all of the relevant
-physics; hence, the width of our resulting $\pr(\kappa|\data)$ is still
-typically $\sim$0.01 for any given lightcone, even with a perfect
-knowledge of every halo's virial mass and redshift. To make further
-progress a more advanced treatment of both voids and halos will be
-necessary. \citet{KarpenkaEtal2012} find that their supernova data prefer, in
-the context of their simple halo model, a truncated isothermal profile for the
-galaxy mass distributions. Weak galaxy-galaxy and cluster-galaxy 
-lensing studies
-\citep[\eg][]{GavazziEtal2006,JohnsonEtal2007} also suggest an approximately
-isothermal profile for the mass-shear correlation function; however, at large
-radii these profiles are dominated by the effects of neighbouring halos, which
-should be taken into account by our model. Further iterations on the analysis
-presented here should include the stellar mass distributions that cause the
-isothermal density profiles in the centres of galaxies, although we do not
-expect this to have a big impact on the model. Likewise,  halo
-ellipticity may have some small effect on the predicted convergence.
+We have shown that reconstructing the matter due to halos along any line of
+sight can improve the constraints on the external convergence along that line
+of sight, with, depending on sample selection,  the width of
+$\pr(\kappa|\data)$ being up to a factor of two smaller than the global
+$\pr(\kappa)$, and  we have quantified the residual bias in the $\kappa$
+estimates under our calibration assumptions. We now revisit these assumptions.
+
+The total convergence along a line of sight is strongly correlated with the
+reconstructed $\kappah$. However, since our model ignores voids and assumes
+all halos follow a spherical truncated-NFW profile our halo model does not
+include all of the relevant physics; hence, the width of our resulting
+$\pr(\kappa|\data)$ is still typically $\sim$0.01 for any given lightcone,
+even with a perfect knowledge of every halo's virial mass and redshift. To
+make further progress a more advanced treatment of both voids and halos will
+be necessary. \citet{KarpenkaEtal2012} find that their supernova data prefer,
+in the context of their simple halo model, a truncated isothermal profile for
+the galaxy mass distributions. Weak galaxy-galaxy and cluster-galaxy  lensing
+studies \citep[\eg][]{GavazziEtal2006,JohnstonEtal2007} also suggest an
+approximately isothermal profile for the mass-shear correlation function;
+however, at large radii these profiles are dominated by the effects of
+neighbouring halos, which should be taken into account by our model. Further
+iterations on the analysis presented here should include the stellar mass
+distributions that cause the isothermal density profiles in the centres of
+galaxies, although we do not expect this to have a big impact on the model.
+Likewise,  halo ellipticity may have some small effect on the predicted
+convergence.
 
@@
 overestimated, as a result of the high scatter in halo mass for objects with 
-high stellar mass. Future work should increasing the precision of the halo
+high stellar mass. As already noted, 
+future work should increasing the precision of the halo
 mass estimates.
 
-More generally, the \MS as a calibration tool. If the real Universe is not
-like the \MS, then the calibration will be incorrect; repeating the study using
+In this work, we have used 
+the \MS as a calibration tool. If the real Universe is not
+like the \MS, then this calibration will be incorrect. Repeating this 
+study using
 a different simulation to make the test catalogs would allow us to quantify
@@
 
-More generally, the method presented here is tied to the simulations at
-several points: in particular, the prior PDF for $\kappah$, and the
-conditional distribution $\pr(\kappa|\kappah)$ used to convert halo model
-convergence to total convergence. The former tie could potentially be avoided
-if the halo mass estimation gave rise to a reasonable $\pr(\kappah|\data)$ on
-its own. Possibilities for improving the precision of the halo mass estimation
-are discussed above. The latter tie is more difficult, since breaking it means
+In particular, the method presented here is tied to the simulations at two
+points: the prior PDF for $\kappah$, and the conditional distribution
+$\pr(\kappa|\kappah)$ used to convert halo model convergence to total
+convergence. The first tie could potentially be avoided if the halo mass
+estimation gave rise to a reasonable $\pr(\kappah|\data)$ on its own.
+Possibilities for improving the precision of the halo mass estimation are
+discussed above. The second tie is more difficult, since breaking it means
 modelling the unseen mass structures and voids from first principles. It
@@
 for these things from the data itself, as demonstrated by
-\citet{KarpenkaEtal2012} -- how much this dilutes the cosmographic precision
-is to be investigated.  Including more information in this analysis is key:
-weak lensing shears will be available over the whole Euclid and LSST survey
-areas: fitting these with the halo models described here in order to constrain
-the hyper-parameters of the model is an interesting
-possibility.
+\citet{KarpenkaEtal2012} (albeit under the assumption of scatter-free scaling
+relations) -- how this affects the cosmographic precision is to be
+investigated.  In any case, 
+including more information in this analysis will be important.
+When working with wide field imaging surveys,  weak lensing shears will be
+available around every line of sight:  fitting these with the halo models
+described here in order to constrain the hyper-parameters of the model is an
+interesting possibility.
 
@@
 
-\item  For the most overdense lines of sight, the reconstruction produces a
-very broad PDF; conversely, we find that the lines of sight with the sharpest
-inferred $\pr(\kappa|\data)$ are typically under-dense. Since the
-reconstructions described here can be performed before follow-up time is
-invested, it will be possible to  select targets by the precision of their
-$\kappa$ estimates. This procedure results in a sample with low bias as well
-as high precision.
-
-\item Photometric data is sufficient  to select the best lines of sight for
-follow-up. Spectroscopic coverage helps to tighten  $\pr(\kappa|\data)$ for
-high $\kappa$ lines of sight, but is of limited use for  low $\kappa$ lines of
-sight.
-
 \item It is very rare for halos further than 2 arcminutes from the line of
@@
 
-\item With only a photometric reconstruction of all time delay lens fields,
-and following up only the systems with the most precise $\kappa$ estimates,
-the width of the dominant statistical uncertainty in time-delay cosmography
-can be halved, without inducing biases at the one percent level.
+\item  For the most overdense lines of sight, the reconstruction produces a
+very broad PDF; conversely, we find that the lines of sight with the sharpest
+inferred $\pr(\kappa|\data)$ are typically under-dense. Since the
+reconstructions described here can be performed before follow-up time is
+invested, it will be possible to  select targets by the precision of their
+$\kappa$ estimates.
+
+\item Photometric data is sufficient  to select the best lines of sight for
+follow-up. Spectroscopic coverage helps to tighten  $\pr(\kappa|\data)$ for
+high $\kappa$ lines of sight, but is of limited use for  low $\kappa$ lines of
+sight.
+
+\item Selecting the highest precision 33\% of the reconstructed lines of sight
+results in a sample with low bias, 0.3\% in terms of the time delay distance,
+and a statistical uncertainty due to line of sight mass structure that is half
+that of the parent sample. The residual systematic error would be equal to the
+overall statistical uncertainty in a sample of around 160 lenses.
+
+\item Conversely, selecting lines of sight with high shear ($|\gamma| >
+0.03$ (as might be done inadvertently by focusing on four-image or wide
+separation lenses) results in a sample with bias of 1\% in time delay
+distance. Such a systematic error would become significant in a sample of 12
+lenses.
+
+% \item With only a photometric reconstruction of all time delay lens fields,
+% and following up only the systems with the most precise $\kappa$ estimates,
+% the width of the dominant statistical uncertainty in time-delay cosmography
+% can be halved, without inducing biases at the one percent level.
 
@@
 
-External convergence is not the only uncertainty in time delay cosmology, but
-for systems like B1608$+$656 it is the dominant one. For most lines of sight
-it is likely that lens modelling induces uncertainties at the $\sim$3 percent
-level, which far exceeds the typical $\kappa$ uncertainties after applying our
-reconstruction \proceedure. By using our method to reconstruct lines of sight
-and select which lense are followed-up, the uncertainties due to line of sight
-convergence will become a sub-dominant  source of error.
+% PJM: Im not sure this is the right note to end on.
+
+% External convergence is not the only uncertainty in time delay cosmology, but
+% for systems like B1608$+$656 it is the dominant one. For most lines of sight
+% lens modelling induces uncertainties at the $\sim$3 percent
+% level, which far exceeds the typical $\kappa$ uncertainties after applying our
+% reconstruction \proceedure. By using reconstruction methods such as that
+% explored here to select the most appropriate 
+% lenses for follow-up, the uncertainties due to line of sight
+% convergence will become a sub-dominant source of error.
+
+While we have tested our reconstruction method against realistic simulations
+of line of sight mass distributions in the Universe, our method is also 
+calibrated to these simulations. Testing this assumption in the short term,
+and replacing it with an empirical calibration (or hierarchical inference) in
+the longer term, are worthy goals for future work. The halo model framework is
+flexible enough to enable many such improvements, including, quite naturally,
+the incorporation of more information from observations.
 

### 2012-11-01 doc/paper-lcr.tex
abstract sharpened up

@@
 observations: we find that selecting systems by the precision with which
-$\kappa$ can be estimated leads to a low density sample that would give
-distance estimates a factor of 2 more precise, with biases as low as 0.5\%.
-Preferentially selecting lines of sight with high external shear (as might
-happen in an assembled sample of quadruply-imaged time delay lenses) has the
-opposite effect, with distances biased by around 1\%. We suggest areas for the
-improvement of this general analysis framework that should allow yet more
-accurate cosmological inferences to be made.
+$\kappa$ can be estimated leads to a low convergence  sample that would give
+time delay distance estimates a factor of 2 more precise than a random
+selection,  with biases as low as 0.5\%. Preferentially selecting lines of
+sight with high external shear (as might happen in an assembled sample of
+quadruply-imaged time delay lenses) has the opposite effect, with distances
+biased by around 1\%. We suggest areas for the improvement of this general
+analysis framework that should allow yet more accurate cosmological inferences
+to be made.
 

### 2012-11-01 doc/paper-lcr.tex
abstract sharpened up

--- 2012-11-01 doc/paper-lcr.tex
@@
 observations: we find that selecting systems by the precision with which
-$\kappa$ can be estimated leads to a low density sample that would give
-distance estimates a factor of 2 more precise, with biases as low as 0.5\%.
-Preferentially selecting lines of sight with high external shear (as might
-happen in an assembled sample of quadruply-imaged time delay lenses) has the
-opposite effect, with distances biased by around 1\%. We suggest areas for the
-improvement of this general analysis framework that should allow yet more
-accurate cosmological inferences to be made.
+$\kappa$ can be estimated leads to a low convergence  sample that would give
+time delay distance estimates a factor of 2 more precise than a random
+selection,  with biases as low as 0.3\%. Preferentially selecting lines of
+sight with high external shear (as might happen in an assembled sample of
+quadruply-imaged time delay lenses) has the opposite effect, with distances
+biased by around 1\%. We suggest areas for the improvement of this general
+analysis framework that should allow yet more accurate cosmological inferences
+to be made.
 

### 2012-11-02 doc/paper-lcr.tex
minor editing

@@
 
+% TEC: yes it's valid. It only really ties us to the halo mass function of the simulation. It's probably tied at the same level as the "global P(\kappa) as derived from Stefan's ray-tracing"
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
 % We need to check that we are doing what we say we are.
+%
+% TEC: yes this doesn't need to be here again
+%
 
@@
 typically comes from halos within 30 arcseconds of the line of sight; by 2
-arcminutes, this fraction is \todo{XX\%}{Tom?}.
+arcminutes, this fraction is 85\%.
+The contribution from halos beyond 2 arcminutes is relatively constant with a contribution of 0.008$\pm$0.003.
+We find that ignoring halos beyond 2 arcminutes has no effect on the precision of the reconstruction; this is shown in Figure \ref{fig:radcut}.
 As a function of magnitude, we find
@@
 zero) as a function of reconstruction magnitude limit.
-%
+
 % Since these objects
@@
 \begin{figure}
+\includegraphics[width=\columnwidth]{figs/radius_scatter.eps}
+\caption[magcut]{The 16, 50 and 84th percentiles of $\kappah$ minus
+$\kappa$ as a function of the limiting radius of the halo
+reconstruction. $\kappah$ has been shifted such that
+$\left\langle\kappah\right\rangle=0$. The majority of the constraining power
+comes from reconstructing halos with magnitudes between $18<i<24$.}
+\label{fig:magcut}
+\end{figure}
+
+\begin{figure}
 \includegraphics[width=\columnwidth]{figs/mag_scatter.eps}
-\caption[magcut]{The 16, 50 and 84\% confidence intervals on $\kappah$ minus
+\caption[magcut]{The 16, 50 and 84th percentiles of $\kappah$ minus
 $\kappa$ as a function of the limiting $i$ band depth of the halo
@@
 While the \MS catalogs do already contain stellar masses for each galaxy, we
-find that these are not well behaved at the low mass end. 
-% \todo{Tom}{Explain why we re-made the stellar masses!}. 
-We also wanted to be able to perform the functional test of
+find that these are not well behaved at the low mass end due to unreasonably high dark matter stripping from satellite halos. We also wanted to be able to perform the functional test of
 trying to recover the convergence having assumed the correct stellar
@@
 \includegraphics[width=\columnwidth]{figs/Widthvshilberrt.eps}
-\caption{Width of the \infered PDF $\pr(\kappah|\data)$ versus the true
+\caption{Width of the \infered PDF $\pr(\kappa|\data)$ versus the true
 $\kappa$ along a line of sight. Blue assumes a spectroscopic redshift for
@@
 \infered $\pr(\kappah|\data)$ increases with $\kappa$.}
-%\todo{Tom}{Check that you mean $\kappah$ and not $\kappa$, and potentially change the graph!}}
+
 \label{fig:widthsvsH}
@@
 % just applying the method we describe and inferring $\kappa$?
+%
+% TEC: yes.
 
@@
 $\kappa$ is reconstructed accurately. 
-% A precise, inaccurate $\kappa$ estimator
-% is worse than useless for cosmology. 
-% PJM: steady on.
 We test the accuracy of our reconstructed $\pr(\kappa|\data)$ in the following
@@
 $\kappa$ lines of sight. With photometry alone, the bias in this sample is
-0.0028. With targeted spectroscopic follow-up of the selected lines of sight
+0.002. With targeted spectroscopic follow-up of the selected lines of sight
 there is negligible improvement, since the best constrained lines of sight are
@@
 In the context of time delay distance accuracy given in the previous section,
-the sample size would have to be 160 or so before this residual systematic
+the sample size would have to be 30 or so before this residual systematic
 error was equal to the statistical uncertainty.
@@
 lightcurves), or the fact that they are quadruply-imaging rather than
-doubly-imaging, since this yields 3 time delays instead of 1, and a higher
-magnification, more informative Einstein Ring system. All three of these
+doubly-imaging, since this yields 3 time delays instead of 1, a higher
+magnification and a more informative Einstein Ring system. All three of these
 properties favour lenses with high convergence and shear along their lines of
@@
 \item Despite our model's simplicity, its reconstructed $\kappah$ values are
-good, if biased, tracers of $\kappa$.  We found that with perfect knowledge of
+good tracers of $\kappa$. $\kappah$ is biased due to our ignorance of voids, but we found that this can be calibrated out. We found that with perfect knowledge of
 the halo mass and redshift (from the Millennium Simulation catalogs), for a
@@
 resulting PDFs tend to be much broader than for perfect halo mass and redshift
-reconstructions. The long tails of the $\kappah$ distribution can be
-suppressed by focusing on the median value as an indicator for $\kappa$
-instead.
+reconstructions.
 
@@
 
-\item Selecting the highest precision 33\% of the reconstructed lines of sight
-results in a sample with low bias, 0.3\% in terms of the time delay distance,
+\item Selecting from the highest precision 33\% of the reconstructed lines of sight
+results in a sample with low bias, 0.2\% in terms of the time delay distance,
 and a statistical uncertainty due to line of sight mass structure that is half
-that of the parent sample. The residual systematic error would be equal to the
-overall statistical uncertainty in a sample of around 160 lenses.
+that of the parent sample. Neglecting other sources of error, the residual systematic error would be equal to the
+overall statistical uncertainty in a sample of around 30 lenses.
 
@@
 separation lenses) results in a sample with bias of 1\% in time delay
-distance. Such a systematic error would become significant in a sample of 12
-lenses.
+distance. Such a systematic error would become significant in a sample of $\sim$8 lenses.
 
@@
 % PJM: Im not sure this is the right note to end on.
+
+% TEC: I liked it! but it's open to discussion.
 

### 2012-11-02 Truthcompare.py

@@ -332,6 +332,36 @@ def MScompare(argv):
 
    #------------------------------------------------------------------
    #radius plot
+   plotr=False
+   if plotr:
+   #set plotting sizes
+      figprops = dict(figsize=(8.0, 5.0), dpi=128)          # Figure properties
+      fig = plt.figure(**figprops)
+      
+   # Need small space between subplots to avoid deletion due to overlap...
+      adjustprops = dict(\
+         left=0.1,\
+            bottom=0.12,\
+            right=0.9,\
+            top=0.95,\
+            wspace=0.2,\
+            hspace=0.9)
+      fig.subplots_adjust(**adjustprops)
+      
+      fig_width_pt = 246./10  # Get this from LaTeX using \showthe\columnwidth
+      inches_per_pt = (1.0/72.27 )/5              # Convert pt to inch
+      golden_mean = ((5**0.5)-1.0)/2.0         # Aesthetic ratio
+      fig_size=[280, 1*golden_mean]
+      params = {'backend': 'ps',
+                'axes.labelsize': 16,
+                'text.fontsize': 12,
+                'legend.fontsize': 12,
+                'xtick.labelsize': 12,
+                'ytick.labelsize': 12,
+                'text.usetex': True,
+                'figure.figsize': fig_size}
+      plt.rcParams.update(params)
+
    if investigateR:
       plt.plot(Rcuts,kappa_16_R,c='k', ls = 'dashed',label="16th percentile")
       plt.plot(Rcuts,kappa_50_R,c='k',label="Median")
@@ -339,7 +369,7 @@ def MScompare(argv):
       #plt.plot(Rcuts,kappa_dif_mean_R,c='k', ls = '-.',label="Mean")                             
       plt.axhline(y=0,xmin=0,xmax=1,ls="dotted",c='k')
       plt.xlabel("Radius out to which halos are reconstructed")
-      plt.ylabel("$\kappa_{\mathrm{reconstruction}} - \kappa_{\mathrm{raytrace}}$",size='x-large')
+      plt.ylabel("$\kappa - \kappa_{\mathrm{h}}$",size='x-large')
       plt.legend(loc=4,title ="%i LoS"%Ncones)
       plt.savefig("radius_scatter.png")
       plt.savefig("doc/radius_scatter.eps")

### 2012-11-07 doc/paper-lcr.tex

@@
 \Fref{fig:where} shows the cumulative contribution to $\kappah$ as a function
-of projected distance from the line of sight, magnitude and redshift.
-We find that most of the convergence comes from halos whose
-galaxies are close to the line of sight. 
-Over half of the  convergence
-typically comes from halos within 30 arcseconds of the line of sight; by 2
-arcminutes, this fraction is 85\%.
-The contribution from halos beyond 2 arcminutes is relatively constant with a contribution of 0.008$\pm$0.003.
-We find that ignoring halos beyond 2 arcminutes has no effect on the precision of the reconstruction; this is shown in Figure \ref{fig:radcut}.
-As a function of magnitude, we find
-that $\kappah$ is dominated by objects with magnitudes between $i=18$ and
-$i=24$. Objects brighter than $i=18$ are either too rare, or too close to the
-observer, to make a significant contribution to the convergence. Objects
-fainter than $i=24$ are too small to be important, unless they are extremely
-close to the line of sight, but we find that including halos fainter than
-$i=24$ does not improve the reconstruction.  \Fref{fig:magcut} shows the
-scatter on $\kappah-\kappa$ (where $\kappah$ is shifted so that its mean is
-zero) as a function of reconstruction magnitude limit.
+of projected distance from the line of sight, magnitude and redshift. We find
+that most of the convergence comes from halos whose galaxies are close to the
+line of sight.  Over half of the  convergence typically comes from halos
+within 30 arcseconds of the line of sight; by 2 arcminutes, this fraction is
+85\%. The contribution from halos beyond 2 arcminutes is relatively constant
+at a contribution of 0.008$\pm$0.003. We find that ignoring halos beyond 2
+arcminutes has no effect on the precision of the reconstruction; this is shown
+in \Fref{fig:radcut}. As a function of magnitude, we find that $\kappah$
+is dominated by objects with magnitudes between $i=18$ and $i=24$. Objects
+brighter than $i=18$ are either too rare, or too close to the observer, to
+make a significant contribution to the convergence. Objects fainter than
+$i=24$ are too small to be important, unless they are extremely close to the
+line of sight, but we find that including halos fainter than $i=24$ does not
+improve the reconstruction.  \Fref{fig:magcut} shows the scatter on
+$\kappah-\kappa$ (where $\kappah$ is shifted so that its mean is zero) as a
+function of reconstruction magnitude limit.
 
@@
 comes from reconstructing halos with magnitudes between $18<i<24$.}
-\label{fig:magcut}
+\label{fig:radcut}
 \end{figure}
@@
 \includegraphics[width=\textwidth]{figs/biasplots.eps}
-\caption{Estimating $\kappa-\kappa_{\rm true}$ from subsets of
+\caption{Convergence accuracy from combining subsets of
 lenses. By subtracting the true (ray-traced) convergence from the
-infered P($\kappa$) for each line of sight we are left with a PDF that
-should be estimating zero, these can be multiplied together for multiple
-lines of sight to test for a possible bias. These plots show the
+\infered $\pr(\kappa)$ for each line of sight we are left with a PDF that
+should be estimating zero; these can be multiplied together for multiple
+lines of sight to emulate a joint likelihood analysis, and 
+test for possible bias in it. These plots show the
 expectation value of $\prod_{i=1}^N \pr_i(\kappa-\kappa_{\rm true})$ --
@@
 \includegraphics[width=\columnwidth]{figs/biasplots3.eps}
-\caption{}
+\caption{Convergence estimation accuracy using the full  $\pr(\kappa|\kappah)$
+distribution, rather than its median.  As in \Fref{fig:biasplots}, solid,
+dashed and dotted lines show combinations of 20, 5 and 2 lines of sight
+respectively, while green lines show the inferences 
+from photometry alone, red lines from photometry and targeted spectroscopy 
+(assuming a spectroscopic redshift for all
+halos with $i<23$ and all halos within 1 arcminute and $i<24$), and blue lines
+from the unrealistic assumption of a spectroscopic redshift for all galaxies
+in the field. }
 \label{fig:no-median-tricks}
@@
 overestimated, as a result of the high scatter in halo mass for objects with 
-high stellar mass. As already noted, 
+high stellar mass. As has already been noted, 
 future work should increasing the precision of the halo

### 2012-11-12 doc/paper-lcr.tex
Edited introduction

@@
 of sight to the quadruply-imaged radio source B1608$+$656 was the
-dominant source of uncertainty in their 6\% measurement of Hubble's
-constant. The problem is that one simply doesn't know how magnified and
-distorted the source has been, because the unlensed source is
-unobservable. The external shear can potentially be recovered in the
+dominant source of uncertainty in their 5\% measurement of the time delay distance. The external shear can potentially be recovered in the
 mass-modelling of the lens, but the convergence is undetectable from the
@@
 
-How can we correct for this perturbative lensing and make accurate
-measurements through the Universe? When inferring global quantities
+When inferring global quantities
 (such as the cosmological parameters), combining the results from a
 large number of independent objects will tend to reduce the uncertainty
-due to external convergence, as the ensemble-averaged magnification
-approaches zero for an unbiased sample \citep[\eg][]{Holz+Linder2005}.
-If the sample is biased, however, some residual systematic error will
-remain even as the statistical uncertainty decreases. Lensing bias will
-be present (to varying degrees) in any sample {\it selected} by
-brightness (which includes magnification), or any other quantity that
-depends on $\kappa$. This bias may be introduced either at the object
+due to external convergence \citep[\eg][]{Holz+Linder2005}, unless the lines of sight are not representative of the global population.
+If the line of sight selection function is not correctly modelled some residual systematic error will
+remain even as the statistical uncertainty decreases. A selection function may be introduced either at the object
 detection stage, or later on when making decisions about which objects
-to study further.  Moreover, we expect these biases to be strongest in
-the strong lens systems, where magnification is highest. Large samples
+to study further. Large samples
 of lenses are expected to be discovered in the next decade in
@@
 small distortions it induces on the images of many background galaxies
-in the field \citep[see e.g.][for a review]{Schneider2006}. In a 30''
-radius aperture around the strong lens Q0957$+$561,
-\citet{NakajimaEtal2009} used deep HST imaging to measure a weak lensing
-convergence of $0.17\pm0.06$, which was used in the time delay distance
-measurement of \citep{FadelyEtal2009}. While this system has an
-unusually high external convergence due to its location on the edge of a
-cluster of galaxies, the precision with which the convergence at the
-lens position can be estimated is indicative of what can be achieved
-with high quality weak lensing shear data. We note that this uncertainty
-is not dependent on the value of the convergence, but instead depends
-primarily on the number density of weakly lensed, measurable galaxies
-available.
+in the field \citep[see e.g.][for a review]{Schneider2006}. 
+\citet{NakajimaEtal2009} used deep HST imaging to infer $\kappax=0.17\pm0.06$ from weak lensing measurements; this measurement was used in the time delay distance
+measurement of \citet{FadelyEtal2009}. A precise weak lensing estimate of $\kappax$ can only be made if the number density of of weakly lensed, measurable galaxies is high.
 
@@
 
-The probability density function (PDF) for the external convergence
-given our available data $\data$, $\Pr(\xkappa|\data)$,  is the  key
-quantity we seek, since by marginalising over this distribution we can
-correctly propagate the uncertainties due to line-of-sight perturbations
-(as \citeauthor{FadelyEtal2009} did).  
-%
-\citet{GunnarssonEtal2006} investigated a related PDF,  for the
+In order to propogate the effect of line-of-sight perturbations into 
+uncertainties on time-delay distances we require the probability density function (PDF) for the external convergence
+given our available data $\data$, $\Pr(\xkappa|\data)$
+% PHIL's REVIEWS OF THE LITRATURE
+\comments{\citet{GunnarssonEtal2006} investigated a related PDF,  for the
 magnification, using a galaxy halo model. Applying empirical galaxy
@@
 detect lensing effects in the supernova data this way.
-
-These observational investigations have provided some very useful
-insight into the problem of convergence estimation.  Coming from a more
-theoretical direction, large numerical simulations have been used to
+}
+% TOM's DISTILLING OF SAID REVIEWS.
+Previous investigation of line-of-sight perturbations have focused on 
+magnification and shear.\citet{GunnarssonEtal2006} used a galaxy halo model combined with simple scaling relations to reconstruct
+the line of sight mass distribution and found that the dispersion in
+apparent source brightness due to lensing magnification could be reduced
+by a factor of two.
+Conversely \citet{KarpenkaEtal2012} used the brightness dispersion in type Ia supernovae to infer the parameters of both their galaxy halo model and mass-to-light scaling relation.
+Both \citeauthor{KarpenkaEtal2012} and \citet{JonssonEtal2010} were able to
+detect lensing effects in the supernova data this way.
+%
+\citet{WongEtal2011} estimated the PDF for the external shear,
+$\Pr(\gammax|\data)$ from their survey data,
+\citep{WilliamsEtal2006;MomchevaEtal2006} of galaxies close to the line
+of sight. Comparing the predicted shear
+distributions with the external shear demanded by the strong lens model 
+they found significant
+discrepancies, but were unable to distinguish between the environment
+modelling and the strong lens modelling as the cause of these
+discrepancies. \citeauthor{WongEtal2011} also found that both line of
+sight structures and the group of galaxies in each lens plane contribute
+significant proportions of the shear.
+
+Large numerical simulations have been used to
 predict, from first principles, the distribution of likely external
@@
 discovering or using particular samples of strong lenses were not taken
-into account. Addressing the possibility of using weak lensing shear to
-reconstruct the magnification~$\mu$ that affects cosmography with
-standard candles (and standard sirens), \citet{HilbertEtal2011} used the
-\MS ray-tracing results to explore optimal mapping techniques and
-quantify their performance. They found that deep weak lensing shear
-surveys (with background galaxy number densities of 100 arcmin$^{-2}$)
-would enable $\Pr(\mu|\data)$ to be estimated such that the distance
-uncertainty per object would be reduced by  20\% on average, and by 40\%
-in regions of low convergence, leading to the suggestion that weak
-lensing maps be used to identify the (low convergence)  lines of sight
-that give higher precision distance estimates.
+into account.
 
@@
 $\Pr(\kappa)$, which was then marginalised over when inferring the time
-delay distance in this system. 
+delay distance in this system. A similar proceedure was used in \citet{SuyuEtal2012b}.
 % B1608$+$656 is indeed a high $\kappa$
 % line of sight, but it does not reside in a massive cluster environment.
-In a companion paper to this one, Greene et al (submitted) investigate
+In a companion paper to this one, Greene et al. (submitted) investigate
 improvements to this method by weighting the galaxy counts by galaxy
@@
 \MS mock catalogs and their associated $\kappa$ values to construct
-$\Pr(\kappa|\data)$.
+$\Pr(\kappa|\data)$. For the most overdense lines of sight the
+Green et al. results  show a $\sim$20\% improvement over
+number counts alone, but little improvement for less dense lines.
 
@@
 \citeauthor{WongEtal2011} and others, with the
-idea of calibrating to simulations from \citeauthor{SuyuEtal2010}, in
-order to put the halo model for  estimating the weak lensing convergence
-due to mass along the line of sight to a distant source into a sound
-framework for evaluating this important source of systematic
-uncertainty, as we look forward to ever increasing sample sizes and
-statistical precision. Taking the $\kappa$ values from
+idea of calibrating to simulations from \citeauthor{SuyuEtal2010}.
+Taking the $\kappa$ values from
 \citeauthor{HilbertEtal2009}'s ray-tracing calculations as the ``truth''

### 2012-11-12 MScompare.py

@@ -1,684 +1,0 @@
-#!/usr/bin/env python
-# ======================================================================
-
-import Pangloss
-
-import sys,getopt,atpy,pyfits
-import pylab,matplotlib.pyplot as plt
-import numpy
-import numpy.random as rnd
-import distances
-from scipy import optimize
-from scipy import stats
-import cPickle, copy
-
-arcmin2rad = (1.0/60.0)*numpy.pi/180.0
-rad2arcmin = 1.0/arcmin2rad
-
-N_45mean = 41.8
-N_60mean = 74.475
-N_90mean = 166.864
-N_30mean = 18.831
-N_15mean = 4.812
-
-# ======================================================================
-
-def MScompare(argv):
-   """
-   NAME
-     MScompare.py
-
-   PURPOSE
-     Compare reconstructed convergence with "true" convergence for a set of 
-     lightcones. Truth comes from Stefan Hilbert's ray tracing work in 
-     the Millenium Simulation, in the form of a pixellated convergence
-     map. Reconstructions are made from simulated catalogs in the same
-     field.
-   COMMENTS
-
-   FLAGS
-     -u            Print this message [0]
-
-   INPUTS
-     catalog       Catalog containing halos, stellar mass distributions etc
-     kappafile     FITS file containing true kappa values.
-
-   OPTIONAL INPUTS
-     -n Ncones     No. of cones to compare
-     -r Rcone      Cone radius used in reconstruction
-     -zd zd        Deflector redshift (to match kappafile)
-     -zs zs        Source redshift (to match kappafile)
-     -t truncationscale number of virial radii to truncate NFW halos at.
-
-   OUTPUTS
-     stdout        Useful information
-     pngfiles      Output plots in png format
-
-   EXAMPLES
-
-     MScompare.py -n 1000 catalog.txt kappa.fits
-
-   BUGS
-
-   AUTHORS
-     This file is part of the Pangloss project.
-     Copyright 2012 Tom Collett (IoA) and Phil Marshall (Oxford).
-     
-   HISTORY
[…]

### 2012-11-12 Truthcompare.py

@@ -1,408 +1,0 @@
-#!/usr/bin/env python
-# ======================================================================
-
-import Pangloss
-
-import sys,getopt,atpy,pyfits
-import pylab,matplotlib.pyplot as plt
-import numpy
-import numpy.random as rnd
-import distances
-from scipy import optimize
-from scipy import stats
-import cPickle, copy
-import time
-
-arcmin2rad = (1.0/60.0)*numpy.pi/180.0
-rad2arcmin = 1.0/arcmin2rad
-
-N_45mean = 41.8
-N_60mean = 74.475
-N_90mean = 166.864
-N_30mean = 18.831
-N_15mean = 4.812
-
-# ======================================================================
-
-def MScompare(argv):
-   try:
-      opts, args = getopt.getopt(argv,"hvn:r:",["help","verbose","zd","zs"])
-   except getopt.GetoptError, err:
-      print str(err) # will print something like "option -a not recognized"
-      print MScompare.__doc__  # will print the big comment above.
-      return
-
-   vb = False
-   Rcone = 5 # arcmin
-   truncationscale=numpy.linspace(0.5,6,20) # *R_200 halo truncation
-   truncationscale=numpy.append(truncationscale,[7,8,9,10,12,14,16,18,20])
-   adoptedtruncationscale=10
-   Ntruncs=len(truncationscale)
-   Ncones=100000
-   magcuts=numpy.linspace(14,26,50)
-
-
-   scaling = "add" 
-   #scaling = "tom"
-   # Defaults are for B1608 (CHECK):
-   zl = 0.62
-   zs = 1.39
-  
-   for o,a in opts:
-      if o in ("-v", "--verbose"):
-         vb = True
-      elif o in ("-n"):
-         Ncones = int(a)
-      elif o in ("-r"):
-         Rcone = a
-      elif o in ("-t"):
-         truncationscale = a 
-
-      elif o in ("--zl"):
-         zl = a
-      elif o in ("--zs"):
-         zs = a
-      elif o in ("-h", "--help"):
-         print MScompare.__doc__
-         return
-      else:
-         assert False, "unhandled option"
-
-   # Check for datafiles in array args:
-   if len(args) == 4:
-      catalog = args[0]
-      kappafile = args[1]
[…]

### 2012-11-12 hilbert2fits.py

@@ -1,85 +1,0 @@
-#!/usr/bin/env python
-# ======================================================================
-
-import Pangloss
-
-import sys,getopt,atpy,pyfits
-import numpy
-
-# ======================================================================
-
-def hilbert2fits(argv):
-   """
-   NAME
-     hilbert2fits.py
-
-   PURPOSE
-     Convert input maps in Hilbert's format to FITS. 
-
-   COMMENTS
-
-   FLAGS
-     -h            Print this message [0]
-     -v            Verbose operation
-
-   INPUTS
-     infiles       Files containing true kappa (or gamma) values.
-
-   OPTIONAL INPUTS
-
-   OUTPUTS
-     stdout        Useful information
-     outfiles      Output files in FITS format
-
-   EXAMPLES
-
-     hilbert2fits.py  x.*
-     
-     Outputs are x.kappa.fits, x.gammma_1.fits, x.gamma_2.fits
-
-   BUGS
-
-   AUTHORS
-     This file is part of the Pangloss project.
-     Copyright 2012 Tom Collett (IoA) and Phil Marshall (Oxford).
-     
-   HISTORY
-     2012-06-15 started Marshall (Oxford)
-   """
-
-   # --------------------------------------------------------------------
-
-   try:
-      opts, args = getopt.getopt(argv,"hv",["help","verbose"])
-   except getopt.GetoptError, err:
-      print str(err) # will print something like "option -a not recognized"
-      print hilbert2fits.__doc__  # will print the big comment above.
-      return
-
-   vb = False
-  
-   for o,a in opts:
-      if o in ("-v", "--verbose"):
-         vb = True
-      elif o in ("-h", "--help"):
-         print hilbert2fits.__doc__
-         return
-      else:
-         assert False, "unhandled option"
-
-   # Files to be converted:
-   infiles = args
-   if vb: print "Converting",len(infiles),"files to FITS format"
- 
-   # --------------------------------------------------------------------
-
-   for infile in infiles:
-     # Read in map and convert (done automatically):    
-     map = Pangloss.kappamap(infile,FITS=False,vb=True)
-
-# ======================================================================
-
-if __name__ == '__main__':
-  hilbert2fits(sys.argv[1:])
-
-# ======================================================================

### 2012-11-12 doc/paper-lcr.tex
Edited introduction

@@
 time delay lens cosmography the so-called ``external convergence''
-$\kappa$ due to mass structures along the (unusually over-dense) line
+$\kappax$ due to mass structures along the (unusually over-dense) line
 of sight to the quadruply-imaged radio source B1608$+$656 was the
-dominant source of uncertainty in their 5\% measurement of the time delay distance. The external shear can potentially be recovered in the
+dominant source of uncertainty in their 5\% measurement of the time delay distance. 
+Whilst it is rare for three galaxies to line up well enough for both of
+the background sources to be strongly lensed \citep{GavazziEtal2008,CollettEtal2012a}, 
+the large size of dark matter halos makes partial alignments -- such that they
+act as perturbing weak lenses --  a near certainty. The large scale of the
+perturbers means the external lensing perturbations can be approximated
+by a quadrupole lens characterised only by external convergence and shear.
+The external shear can potentially be recovered in the
 mass-modelling of the lens, but the convergence is undetectable from the
@@
 \citet{WongEtal2011} estimated the PDF for the external shear,
-$\Pr(\gamma|\data)$ from their survey data, running similar Monte Carlo
+$\Pr(\gammax|\data)$ from their survey data, running similar Monte Carlo
 reconstructions of the mass in nine lens fields based on
@@
 chance alignments at any redshift.
-% While it is rare for three galaxies
-% to line up well enough for both of the background sources to be strongly
-% lensed \citep{GavazziEtal2008,CollettEtal2012a}, 
-The large size of dark
-matter halos makes partial alignments -- such that they
-act as perturbing weak lenses --  a near certainty
+
 \citep{Vale+White2003,HilbertEtal2007}. These additional structures

### 2012-11-12 doc/paper-lcr.tex
replace accidentally deleted files

@@
 \label{sec:theory}
-
+\comments{
 Convergence, or Ricci focusing, occurs when a gravitational lens focuses
@@
 appear brighter, and larger than they would if the lens were removed.
-The convergence from an isolated mass sheet at a position
-$\bmath{\theta}$ on the sky is the ratio of the projected surface
-mass density ($\Sigma(D_{\mathrm{od}}\bmath{\theta})$) \devided by the
+The convergence from an isolated mass sheet is the ratio of the projected surface
+mass density ($\Sigma$) \devided by the
 critical surface mass density at the redshift of the mass sheet
@@
 \be
-\kappa(\bmath{\theta})= \frac {\Sigma(D_{\mathrm{od}}\bmath{\theta})}
+\kappax= \frac {\Sigma}
                               {\Sigma_{\rm cr}(\zd,\zs)}
@@
 
-\comments{
 Strong lensing occurs when a massive object and background source are almost perfectly
@@
 
-Strong lenses, type Ia supernovae and other cosmologically interesting objects
-are never viewed unlensed: 
-there is some mass along the line of sight to them coming from intervening
-structures. These structures may be physically associated with the target
-e.g. other members of a group or cluster, or they may be the result of
-chance alignments at any redshift.
-
-\citep{Vale+White2003,HilbertEtal2007}. These additional structures
-induce an external shear which can be recovered in the mass-modelling of
-a strong lens, but they also introduce a convergence that is undetectable even
-in these systems:
+External convergence is undetectable even
+in strong lens systems:
 the lensed image positions, shapes and relative fluxes are affected, but not

### 2012-11-12 MScompare.py
replace accidentally deleted files

@@ -1,0 +1,684 @@
+#!/usr/bin/env python
+# ======================================================================
+
+import Pangloss
+
+import sys,getopt,atpy,pyfits
+import pylab,matplotlib.pyplot as plt
+import numpy
+import numpy.random as rnd
+import distances
+from scipy import optimize
+from scipy import stats
+import cPickle, copy
+
+arcmin2rad = (1.0/60.0)*numpy.pi/180.0
+rad2arcmin = 1.0/arcmin2rad
+
+N_45mean = 41.8
+N_60mean = 74.475
+N_90mean = 166.864
+N_30mean = 18.831
+N_15mean = 4.812
+
+# ======================================================================
+
+def MScompare(argv):
+   """
+   NAME
+     MScompare.py
+
+   PURPOSE
+     Compare reconstructed convergence with "true" convergence for a set of 
+     lightcones. Truth comes from Stefan Hilbert's ray tracing work in 
+     the Millenium Simulation, in the form of a pixellated convergence
+     map. Reconstructions are made from simulated catalogs in the same
+     field.
+   COMMENTS
+
+   FLAGS
+     -u            Print this message [0]
+
+   INPUTS
+     catalog       Catalog containing halos, stellar mass distributions etc
+     kappafile     FITS file containing true kappa values.
+
+   OPTIONAL INPUTS
+     -n Ncones     No. of cones to compare
+     -r Rcone      Cone radius used in reconstruction
+     -zd zd        Deflector redshift (to match kappafile)
+     -zs zs        Source redshift (to match kappafile)
+     -t truncationscale number of virial radii to truncate NFW halos at.
+
+   OUTPUTS
+     stdout        Useful information
+     pngfiles      Output plots in png format
+
+   EXAMPLES
+
+     MScompare.py -n 1000 catalog.txt kappa.fits
+
+   BUGS
+
+   AUTHORS
+     This file is part of the Pangloss project.
+     Copyright 2012 Tom Collett (IoA) and Phil Marshall (Oxford).
+     
+   HISTORY
[…]

### 2012-11-12 PDFcreate.py

@@ -1,0 +1,307 @@
+#!/usr/bin/env python
+# ======================================================================
+
+import Pangloss
+
+import sys,getopt,atpy,pyfits
+import pylab,matplotlib.pyplot as plt
+import numpy
+import numpy.random as rnd
+import distances
+from scipy import optimize
+from scipy import stats
+import cPickle, copy
+import time
+
+arcmin2rad = (1.0/60.0)*numpy.pi/180.0
+rad2arcmin = 1.0/arcmin2rad
+
+N_45mean = 41.8
+N_60mean = 74.475
+N_90mean = 166.864
+N_30mean = 18.831
+N_15mean = 4.812
+
+# ======================================================================
+
+def MScompare(argv):
+   """
+   NAME
+     MScompare.py
+
+   PURPOSE
+     Reconstruct a pdf for the convergence along a LoS and compare with
+     "true" convergence for a set of lightcones. Truth comes from 
+     Stefan Hilbert's ray tracing work in the Millenium Simulation, in
+     the form of a pixellated convergence map. Reconstructions are made
+     from simulated catalogs in the same field.
+   COMMENTS
+
+   FLAGS
+     -u            Print this message [0]
+
+   INPUTS
+     catalog       Catalog containing halos, stellar mass distributions etc
+     kappafile     FITS file containing true kappa values.
+
+   OPTIONAL INPUTS
+     -n Ncones     No. of cones to compare
+     -r Rcone      Cone radius used in reconstruction
+     -zd zd        Deflector redshift (to match kappafile)
+     -zs zs        Source redshift (to match kappafile)
+     -t truncationscale number of virial radii to truncate NFW halos at.
+
+   OUTPUTS
+     stdout        Useful information
+     pngfiles      Output plots in png format
+
+   EXAMPLES
+
+     MScompare.py -n 1000 catalog.txt kappa.fits
+
+   BUGS
+
+   AUTHORS
+     This file is part of the Pangloss project.
+     Copyright 2012 Tom Collett (IoA) and Phil Marshall (Oxford).
+     
+   HISTORY
+     2012-04-06 started Marshall (Oxford)
+   """
+
+   # --------------------------------------------------------------------
+
+   try:
[…]

### 2012-11-12 Truthcompare.py

@@ -1,0 +1,408 @@
+#!/usr/bin/env python
+# ======================================================================
+
+import Pangloss
+
+import sys,getopt,atpy,pyfits
+import pylab,matplotlib.pyplot as plt
+import numpy
+import numpy.random as rnd
+import distances
+from scipy import optimize
+from scipy import stats
+import cPickle, copy
+import time
+
+arcmin2rad = (1.0/60.0)*numpy.pi/180.0
+rad2arcmin = 1.0/arcmin2rad
+
+N_45mean = 41.8
+N_60mean = 74.475
+N_90mean = 166.864
+N_30mean = 18.831
+N_15mean = 4.812
+
+# ======================================================================
+
+def MScompare(argv):
+   try:
+      opts, args = getopt.getopt(argv,"hvn:r:",["help","verbose","zd","zs"])
+   except getopt.GetoptError, err:
+      print str(err) # will print something like "option -a not recognized"
+      print MScompare.__doc__  # will print the big comment above.
+      return
+
+   vb = False
+   Rcone = 5 # arcmin
+   truncationscale=numpy.linspace(0.5,6,20) # *R_200 halo truncation
+   truncationscale=numpy.append(truncationscale,[7,8,9,10,12,14,16,18,20])
+   adoptedtruncationscale=10
+   Ntruncs=len(truncationscale)
+   Ncones=100000
+   magcuts=numpy.linspace(14,26,50)
+
+
+   scaling = "add" 
+   #scaling = "tom"
+   # Defaults are for B1608 (CHECK):
+   zl = 0.62
+   zs = 1.39
+  
+   for o,a in opts:
+      if o in ("-v", "--verbose"):
+         vb = True
+      elif o in ("-n"):
+         Ncones = int(a)
+      elif o in ("-r"):
+         Rcone = a
+      elif o in ("-t"):
+         truncationscale = a 
+
+      elif o in ("--zl"):
+         zl = a
+      elif o in ("--zs"):
+         zs = a
+      elif o in ("-h", "--help"):
+         print MScompare.__doc__
+         return
+      else:
+         assert False, "unhandled option"
+
+   # Check for datafiles in array args:
+   if len(args) == 4:
+      catalog = args[0]
+      kappafile = args[1]
[…]

### 2012-11-12 hilbert2fits.py

@@ -1,0 +1,85 @@
+#!/usr/bin/env python
+# ======================================================================
+
+import Pangloss
+
+import sys,getopt,atpy,pyfits
+import numpy
+
+# ======================================================================
+
+def hilbert2fits(argv):
+   """
+   NAME
+     hilbert2fits.py
+
+   PURPOSE
+     Convert input maps in Hilbert's format to FITS. 
+
+   COMMENTS
+
+   FLAGS
+     -h            Print this message [0]
+     -v            Verbose operation
+
+   INPUTS
+     infiles       Files containing true kappa (or gamma) values.
+
+   OPTIONAL INPUTS
+
+   OUTPUTS
+     stdout        Useful information
+     outfiles      Output files in FITS format
+
+   EXAMPLES
+
+     hilbert2fits.py  x.*
+     
+     Outputs are x.kappa.fits, x.gammma_1.fits, x.gamma_2.fits
+
+   BUGS
+
+   AUTHORS
+     This file is part of the Pangloss project.
+     Copyright 2012 Tom Collett (IoA) and Phil Marshall (Oxford).
+     
+   HISTORY
+     2012-06-15 started Marshall (Oxford)
+   """
+
+   # --------------------------------------------------------------------
+
+   try:
+      opts, args = getopt.getopt(argv,"hv",["help","verbose"])
+   except getopt.GetoptError, err:
+      print str(err) # will print something like "option -a not recognized"
+      print hilbert2fits.__doc__  # will print the big comment above.
+      return
+
+   vb = False
+  
+   for o,a in opts:
+      if o in ("-v", "--verbose"):
+         vb = True
+      elif o in ("-h", "--help"):
+         print hilbert2fits.__doc__
+         return
+      else:
+         assert False, "unhandled option"
+
+   # Files to be converted:
+   infiles = args
+   if vb: print "Converting",len(infiles),"files to FITS format"
+ 
+   # --------------------------------------------------------------------
+
+   for infile in infiles:
+     # Read in map and convert (done automatically):    
+     map = Pangloss.kappamap(infile,FITS=False,vb=True)
+
+# ======================================================================
+
+if __name__ == '__main__':
+  hilbert2fits(sys.argv[1:])
+
+# ======================================================================

### 2012-11-12 setup.py

@@ -1,0 +1,24 @@
+from distutils.core import setup, Extension
+from numpy.distutils.misc_util import get_numpy_include_dirs
+
+numpy_inc = get_numpy_include_dirs()
+
+setup(
+    name="Pangloss",
+    version="n/a",
+    author="Tom Collett (IoA) & Phil Marshall (Oxford)",
+    author_email="",
+    packages=["Pangloss"],
+    ext_modules = [],
+    url="",
+    license="GPLv2",
+    description="line of sight mass reconstruction",
+    long_description="TBD",
+    classifiers=[
+        "Development Status :: 2 - Pre-Alpha",
+        "Intended Audience :: Science/Research",
+        "License :: OSI Approved :: GNU General Public License (GPL)",
+        "Operating System :: OS Independent",
+        "Programming Language :: Python",
+    ],
+)

### 2012-11-14 doc/paper-lcr.tex
more draft editing

@@
 
-External convergence is undetectable even
-in strong lens systems:
-the lensed image positions, shapes and relative fluxes are affected, but not
-in an unambiguous way
-\citep{FalcoEtal1985}.
-
-In time delay lens systems, under the addition of an external convergence (and
-appropriate re-scaling of the lens potential) the relative Fermat potential
-between the images is {\it not} invariant. This means that the time delay
-between the images changes, despite the invariance of the image positions and
-fluxes. As such it is necessary to include $\kappa$ in the lens modelling, if
+\new{
+In strong lens systems where the source is time variable, the images do not 
+vary simultaneously; the optical path length for each image is different due
+to relativistic and geometric effects. The difference in optical path length
+causes a time-delay between the light curves of each image. \citeauthor{FalcoEtal1985}
+showed that the presence of additional matter (in the form of a mass-sheet)
+along the line of sight has no observable effect except to rescale the time-delays.
+As such, it is necessary to include $\kappax$ in the lens modelling, if
 cosmological parameters are to be estimated accurately and precisely from
-observed time delays \citep{SuyuEtal2010}. Mass distributions that are
+observed time delays \citep{SuyuEtal2010}. 
+}
+
+If there is external convergence present that is not included in the
+lens modeling, then the time delay distance -- inferred assuming $\kappax
+= 0$ -- will be $(1-\kappax)$ more than the true value of $\Dt$:
+\be 
+\label{eq:MassSheet:Dtbias}
+\Dt^{\rm{true}}=\frac{\Dt^{{\kappax = 0}}}{1-\kappax}.
+\ee
+
+We can hence estimate the true distance {\it only} if we have with additional
+knowledge of $\kappax$. Since $\kappax$ is typically small the absolute
+uncertainty on the estimate of $\kappax$ corresponds to the fractional
+uncertainty with which time-delay distances can be \infered.
+
+Mass distributions that are
 physically associated with the lens galaxy will affect the stellar dynamics of
@@
 of sight.
-
-If there is external convergence present that is not included in the
-lens modeling, then the time delay distance -- inferred assuming $\kappa
-= 0$ -- will be $(1-\kappa)$ less than the true value of $\Dt$:
-\be 
-\label{eq:MassSheet:Dtbias}
-\Dt^{\rm{true}}=(1-\kappa) \Dt^{{\kappax = 0}}.
-\ee
-We can hence estimate the true distance if we have  with additional
-knowledge of $\kappa$. Since $\kappa$ is typically small the absolute
-uncertainty on the estimate of $\kappa$ \correspends to the fractional
-uncertainty with which time-delay distances can be \infered.
-
-For type Ia supernovae, it is the magnification due to line of sight mass
-structure that is a potential source of cosmographic error.
-The relationship between convergence $\kappa$ and magnification $\mu$ is
-\bea 
-\mu &=&       \frac{1}{(1-\kappa)^2 - |\gamma|^2}, \notag \\
-    &\approx& (1+2\kappa)
-\label{eq:MassSheet:mag}
-\eea
-where we have used the facts that the magnitude of the gravitational
-shear at any point is typically comparable to the magnitude of the 
-convergence, and that both are typically small. 
-Under these assumptions, the fractional uncertainty in the
-inferred luminosity of a magnified source will be approximately  twice
-the absolute uncertainty in the convergence~$\kappa$. These
-relationships will allow us to put our results on convergence estimation
-in context.
 
@@
 \be
-\kappa(\bmath{\theta}) = \sum_i \frac{\Sigma_i(\bmath{\theta})}
+\kappax(\bmath{\theta}) = \sum_i \frac{\Sigma_i(\bmath{\theta})}
                                      {\Sigma_{\rm cr}(z_i,\zs)}.
@@
 This approximation was found to be accurate to a few percent or better
-in $\kappa$, even on 30 arcsecond scales.
+in $\kappax$, even on 30 arcsecond scales.
 
@@
 estimating the mass of each halo in the catalog, so that we can compute
-its contribution to the total $\kappa$ along the line of sight \citep[as
+its contribution to the total $\kappax$ along the line of sight \citep[as
 in \eg][]{GunnarssonEtal2006,WongEtal2011,KarpenkaEtal2012}. 
@@
 attempt a reconstruction of the convergence induced by every halo near a
-line of sight. This is the subject of Section \ref{sec:model:halos}. We
-also need to account for the mass in the Universe that is not associated
-with the galaxies we can see -- this is the subject of Section
-\ref{sec:model:voids}.
+line of sight. \new{We also need to account for the convergence due to dark structures and
+the divergence due to voids; we do not model voids or dark structures, but their
+effects are included statistically by calibration the the convergence in halos,
+$\kappah$, against the ray-traced convergence, $\kappax$, for \MS lines of sight.}
 
@@
 \ee
+\notes{Using the Born approximation, we approximate light rays as straight.}
 
@@
 \Eref{eq:kappai} to compute its contribution to the convergence,
-$\kappa_i$; this can be done for all the halos along the line of sight
+$\kappa_i$; this can be done for all the halos along a specific line of sight
 and summed to give a sample value of $\kappah$;  repeatedly applying
@@
 the effect of voids, our reconstruction cannot -- the halo catalogue does not
-include voids. In principle the absence of a halo could be taken to infer a
-void, but the under-density of such a void is hard to infer. Neglecting voids
+include voids. \new{In principle the absence of galaxies implies something about
+the presence a void, but we do not attempt to use this information}. Neglecting voids
 would lead to a heavily biased estimate of $\kappa$. Moreover, the halos in 
@@
 poor observational data. At fixed $\kappah$ we find in \Fref{fig:jointkh-k}
-that the scatter in $\kapparay$ grows with $\kappah$; our reconstruction is
+that the scatter in $\kappax$ grows with $\kappah$; our reconstruction is
 better at reproducing underdense lines of sight than overdense lines of sight.
@@
 
-% Since voids are not included in the halo model approximation, $\kappah$
-% is a biased estimator of $\kappa$, but this can be calibrated for using
-% the \proceedure of \Sref{sec:model:voids}. Taking the reconstructed
-% $\kappah$ for $10^{5}$ lines of sight we form the joint
-% distribution, $\pr(\kappa,\kappah)$ and marginalize over $\pr(\kappah)$ to
-% give $\pr(\kappa)$. 
-%
-% PJM: WTF? We just went through all of this in the previous section!
-% We need to check that we are doing what we say we are.
-%
-% TEC: yes this doesn't need to be here again
-%
-
 In this section, let us define the ``bias'' of the reconstruction of a given
@@
 
-In an ensemble of $10^{4}$ reconstructed lines of sight, we find the the mean
-bias to be $-9.5\times 10^{-6}$, and the mean width to be 0.0132. This is
+In an ensemble of $10^{5}$ reconstructed lines of sight, we find the the mean
+bias to be $-9.5\times 10^{-6}$, and the mean width to be 0.01. This is
 approximately 1.8 times smaller than the width of the global $\pr(\kappa)$. 
@@
 $\kappa$ distribution; Figure \ref{fig:globaldist} shows that sampling from
-$\pr(\kappa|\data)$ in 100,000 reconstructed lines of sight produces a
+$\pr(\kappa|\data)$ in $10^{5}$ reconstructed lines of sight produces a
 distribution of $\kappa$ values over the sky identical to the global
@@
 $\kappah-\kappa$ (where $\kappah$ is shifted so that its mean is zero) as a
-function of reconstruction magnitude limit.
-
-% Since these objects
-% must be extremely close to the line of sight to make a non-zero $\kappah$
-% contribution, it is likely that neglecting stellar mass and using a spherical
-% NFW prescription are too naive to adequately reconstruct $\kappax$.
-%
-% PJM: the sentence above does not make sense!
-%
-We do
+function of reconstruction magnitude limit. We do
 not expect a deeper survey to decrease the size of the uncertainty in mapping
@@
 redshifts stellar mass uncertainties are typically three times as large. We
-use $\sigma_{M_*}=0.15$ for halos with a spectroscopic redshift and
-$\sigma_{M_*}=0.45$ otherwise. For photometric redshift errors we draw a
+use $\sigma_{M_*}=0.15$ dex for halos with a spectroscopic redshift and
+$\sigma_{M_*}=0.45$ dex otherwise. For photometric redshift errors we draw a
 redshift from $\pr(z_{\rm true}|z_{\rm obs})$ which we take to be a Gaussian
@@
 uncertainties. The median reconstruction width in this idealised situations is
-0.0123; some 22\% of lines of sight would have a reconstruction width less
+0.01; some 22\% of lines of sight would have a reconstruction width less
 than 0.01.
@@
 masses.  With only photometric redshifts the uncertainty on
-$\kappah$ is much larger than in the spectrocopic case and this
+$\kappah$ is larger than in the spectrocopic case and this
 \propogates into a broader $\pr(\kappa|\data)$, although the photometric
-reconstruction still typically produces a 40\% improvement compared to the
+reconstruction still typically produces a 50\% improvement compared to the
 precision of the global $\pr(\kappa)$ (\Fref{fig:widthsvsH}).
@@
 relatively fast with large telescopes: however, we find that if spectroscopic
-redhsifts were known for all $i<22$ galaxies in our field the reconstruction
+redshifts were known for all $i<22$ galaxies in our field the reconstruction
 improves slightly upon the purely photometric reconstruction, although the
@@
 While it is good to reconstruct $\kappa$ precisely, it is more important that
-$\kappa$ is reconstructed accurately. 
+$\kappa$ is reconstructed accurately. The reconstruction must not be biased. 
 We test the accuracy of our reconstructed $\pr(\kappa|\data)$ in the following
-way: for each line of sight we shift the reconstructed $\pr(\kappa|\data)$ by
-the line of sight's true value of $\kappa$ to give
-$\pr(\kappa-\kappatrue|\data)$. Since the $\pr(\kappa-\kappatrue|\data)$ for
-each line of sight is then an \independant estimator of zero, the PDFs can be
-combined according to
+way: for each line of sight we have an estimator for the true convergence along
+that line of sight, by subtracting the line of sight's ray-traced convergence
+$\kappatrue$ from $\pr(\kappa|\data)$ we have an estimator of zero, $\pr(\kappa-\kappatrue|\data)$.
+ Since the $\pr(\kappa-\kappatrue|\data)$ for
+each line of sight is an \independant estimator of zero, the PDFs from $N$ lines of sight
+can be combined according to
 \be
@@
 is smaller than the half-width of $\mathcal{P}_N$, our $\kappa$ estimators can
-be considered accurate. 
-The point at which the modulus of the bias and the width of $\mathcal{P}_N$
-are approximately equal gives an estimate of the number of objects which can
-be combined before the measurement is limited by systematic error.
+be considered accurate. Since the width of $\mathcal{P}_N$ decreases as more
+lenses are combined a small bias will eventually be found for all estimators
+In the context of measuring time delay distance at the one percent level the
+expectation value of $|\mathcal{P}_N|$ needs to be less than 0.01.
 
@@
 We first consider a purely random selection of lines of sight. With the purely
-photometric reconstruction, there is a small bias towards underestimating
-$\kappa$: combining 6 targets the half-width and bias of $\mathcal{P}_{6}$
-both equal 0.007. With targeted spectroscopic follow up this improves
-slightly, for the combination of 8 sightlines the half-width and expectation
-value  $\mathcal{P}_{8}$ equal 0.005.  If these lines of sight hosted time
-delay lenses, the latter number would correspond to a systematic error of
+photometric reconstruction, there is no evidence of bias, even after combining 20
+lines of sight. If these lines of sight hosted time
+delay lenses, the bias number would correspond to a systematic error of
 0.5\% in time delay distance. Since the statistical distance uncertainties due
 to lens modelling and time delay estimation are likely to be at the 3-4\%
-level \citep{SuyuEtal2010},  only a sample containing 50 or more lenses would
+level \citep{SuyuEtal2010},  only a sample containing 200 or more lenses would
 be limited by the residual bias  following external convergence
@@
 
-We find that selecting the most tightly constrained lines of sight {\it
-decreases} the bias -- our reconstruction is most \succesful for the lowest
-$\kappa$ lines of sight. With photometry alone, the bias in this sample is
-0.002. With targeted spectroscopic follow-up of the selected lines of sight
-there is negligible improvement, since the best constrained lines of sight are
+We find that selecting the most tightly constrained lines of sight has no impact on the
+bias -- our reconstruction is most \succesful for the lowest
+$\kappa$ lines of sight. With targeted spectroscopic follow-up of the selected lines of sight
+there is negligible improvement compared to photometry alone, since the best constrained lines of sight are
 the most empty, and it is the high-$\kappa$ lines of sight that benefit the
@@
 select the best lines of sight for cosmology -- and doing so greatly increases
-both the precision and accuracy of the cosmological constraints per system.
-In the context of time delay distance accuracy given in the previous section,
-the sample size would have to be 30 or so before this residual systematic
-error was equal to the statistical uncertainty.
+ the precision of the cosmological constraints per system, with no degredation of the accuracy.
+Since lenses are typically found in locally overdense environments, it is unlikely that 
+an almost empty line of sight would contain a lens; it is somewhat optimistic to 
+suggest that nearly empty lines of sight could be used for time-delay cosmology.
 
@@
 
-By selecting only lines of sight with an external shear of $\gamma>0.03$ we
-can test the impact of shear selection. We find that in this sample, $\kappa$
-is systematically underestimated at the $\sim$0.01 level (corresponding to a
-1\% systematic error in distance, significant in a sample of 12 lenses). 
-Part of this effect is mitigated if only
-the lines of sight with both $\gamma>0.03$ and sharp $\pr(\kappa|\data)$ are
-used, but biases at the $\sim$0.005 level remain. Since our model does not
-include shear constraints it is not surprising that selecting based on shear
+By selecting only lines of sight with an external shear of $\gammax>0.03$ we
+can test the impact of shear selection. We find that in this sample, $\kappax$
+is systematically underestimated at the $\sim$0.003 level (corresponding to a
+0.3\% systematic error in distance; in the absence of other sources of uncertainty, this
+systematic error would be significant in a sample of 40 lenses). 
+This effect is mitigated if only
+the lines of sight with both $\gammax>0.03$ and well constrained $\pr(\kappax|\data)$ are
+used, but biases at the $\sim$0.001 level remain. Since our model does not
+include shear constraints it is not surprising that a selection function based on shear
 can induce a bias. A more sophisticated model that includes the shear
 recovered from the lens modelling may be less susceptible to this bias. The
-cartoon selection model used here ($\gamma>0.03$) is likely to be a much
+toy selection model used here ($\gammax>0.03$) is likely to be a much
 stronger selection than reality, but nevertheless it is worth noting that the
@@
 of sight, with, depending on sample selection,  the width of
-$\pr(\kappa|\data)$ being up to a factor of two smaller than the global
-$\pr(\kappa)$, and  we have quantified the residual bias in the $\kappa$
+$\pr(\kappax|\data)$ being up to a factor of two smaller than the global
+$\pr(\kappax)$, and  we have quantified the residual bias in the $\kappax$
 estimates under our calibration assumptions. We now revisit these assumptions.
@@
 include all of the relevant physics; hence, the width of our resulting
-$\pr(\kappa|\data)$ is still typically $\sim$0.01 for any given lightcone,
+$\pr(\kappax|\data)$ is still typically $\sim$0.01 for any given lightcone,
 even with a perfect knowledge of every halo's virial mass and redshift. To
@@
 included in the halo model in some way. Most importantly for the highest
-$\kappa$ lines of sight will be a better group and cluster model:
+$\kappax$ lines of sight will be a better group and cluster model:
 \citet{MomchevaEtal2006} and  \citet{WongEtal2011} recommend using models
@@
 Interestingly, we have found that it is the most empty lines of sight that 
-can be reconstructed with the highest precision. $\kappa$ estimates for empty
+can be reconstructed with the highest precision. $\kappax$ estimates for empty
 lines of sight receive few contributions from halos, and a large contribution
@@
 resulting precision is still typically 50\%  higher than using the global
-$\kappa$ distribution.
-
-Since the uncertainty on $\pr(\kappa|\data)$ is $\sim$0.01 even
-with perfect knowledge of halo mass and redshift, it seems that voids
-(plus deviations from sphericity and dark matter clumping within the
-main halo) dominate the total $\kappa$ uncertainty even with very
+$\kappax$ distribution.
+
+Since the uncertainty on $\pr(\kappax|\data)$ is $\sim$0.01 even
+with perfect knowledge of halo mass and redshift, it seems that modelling uncertainties
+from voids, deviations from sphericity and dark matter clumping within the
+main halo dominate the total $\kappax$ uncertainty even with very
 uncertain stellar masses. Inferring halo ellipticity and dark matter
@@
 than 24th magnitude does not signifcantly help the reconstruction.
-Because our reconstruction is mostly limited by the model, spectroscopic
-coverage can only provide a modest improvement to the reconstruction and
-at significant observational cost.
-
-For a small fraction of lines of sight, $\pr(\kappa|\data)$ remains very
+
+For a small fraction of lines of sight, $\pr(\kappax|\data)$ remains very
 broad even after applying our reconstruction; these lines of sight are
@@
 relatively cheap. We have shown that with a single epoch observation of
-the region around a strong lens it is possible to infer $\pr(\kappa|\data)$.
-If a line of sight has a broad $\pr(\kappa|\data)$ it can be rejected {\it
+the region around a strong lens it is possible to infer $\pr(\kappax|\data)$.
+If a line of sight has a broad $\pr(\kappax|\data)$ it can be rejected {\it
 before} the investment of follow-up. We find that
 selecting only the lines of sight with the most tightly constrained
-$\pr(\kappa)$ does not induce a bias in $\kappa$, and hence distance.
+$\pr(\kappax)$ does not induce a bias in $\kappax$, and hence distance.
+For the most overdense lines of sight,
+the precision of $\pr(\kappax|\data)$ is improved noticeably by the addition
+of spectroscopic information; currently insufficient time-delay systems are
+know to choose a subset based on their reconstructed $\pr(\kappax|\data)$.
+Spectroscopic coverage will definately be useful for extracting cosmology from
+overdense lines of sight.
 
@@
 environment, but found a tension between the strong lens model and the
-reconstruction of the environment. Since \citet{WongEtal2011} only
-reconstructed the local lens group, rather than the full line of sight
-contribution, it is unclear whether the external shear from lens models can be
-reconciled with a line of sight reconstruction. {\it If} external shear can be
+reconstruction of the environment. Given the \citet{WongEtal2011} results
+it is unclear whether the external shear from lens models can be
+reconciled with a line of sight reconstruction. Alternatively, it may be possible 
+to infer external shear using weak lensing information from near the line of sight. 
+If the true external shear can be
 measured, it provides an additional constraint on which of the \MS lines of
@@
 compared to the PDF from number count overdensity alone,
-$\pr(\kappax|N_{45})$. While not included in this paper, we found that given
+$\pr(\kappax|N_{45})$.
+
+Extending our model to include shear we find that given
 perfect knowledge of the halo mass and redshift the raytraced external shear
@@
 \label{eq:shearineq}
-|{\boldmath{\gamma}-\boldmath{\gamma_{\mathrm{h}}}}| < \mathrm{0.025}
+|{\boldmath{\gammax}-\boldmath{\gamma_{\mathrm{h}}}}| < \mathrm{0.025}
 \ee 
 Future work should investigate whether $\gamma_{\mathrm{h}}$ can be used
-to improve the accuracy and precision of $\kappa$ estimation, given a
+to improve the accuracy and precision of $\kappax$ estimation, given a
 reconstruction of the line of sight.
@@
 high stellar mass. As has already been noted, 
-future work should increasing the precision of the halo
+future work should focus on increasing the precision of the halo
 mass estimates.
@@
 stellar mass--halo mass relation would both enable similar exploration of
-these systematic errors.
+these systematic errors. It is possible that baryonic physics may alter
+the radial profile of dark matter halos, even on large scales. \citet{Semboloni+2012}
+found that baryonic physics had a 30-40\% impact on three-point shear statistics, it is
+unclear how baryons affect one-point convergence statistics.
 
@@
 points: the prior PDF for $\kappah$, and the conditional distribution
-$\pr(\kappa|\kappah)$ used to convert halo model convergence to total
+$\pr(\kappax|\kappah)$ used to convert halo model convergence to total
 convergence. The first tie could potentially be avoided if the halo mass
@@
 discussed above. The second tie is more difficult, since breaking it means
-modelling the unseen mass structures and voids from first principles. It
+modelling the unseen mass structures and voids. It
 should be possible to infer hierarchically  the parameters of a flexible model
@@
 relations) -- how this affects the cosmographic precision is to be
-investigated.  In any case, 
-including more information in this analysis will be important.
-When working with wide field imaging surveys,  weak lensing shears will be
+investigated. When working with wide field imaging surveys,  weak lensing shears will be
 available around every line of sight:  fitting these with the halo models
-described here in order to constrain the hyper-parameters of the model is an
-interesting possibility.
+described here in order to constrain the hyper-parameters of the model presents a 
+possible test of our halo model prescription against real observations.
 
@@
 each object in a photometric catalogue. Having found that the reconstruction
-process is effective given perfect knowledge of halo mass and redshift, we
+process is accurate and precise given perfect knowledge of halo mass and redshift, we
 investigated the effects of reasonable uncertainties in the stellar mass and

### 2012-11-14 doc/paper-lcr.tex
more draft editing

@@
 and stellar mass of galaxies observed in optical imaging surveys of the field
-in question. We use mock catalogs from the Millennium Simulation, and compare
+in question. We use mock catalogues from the Millennium Simulation, and compare
 our reconstructed $\pr(\kappa|\data)$ to ray-traced $\kappa$ truth values: 
@@
   galaxies: halos         --
-  gaaxies: mass function  --
+  galaxies: mass function  --
   cosmology: observations
@@
 
-In order to propogate the effect of line-of-sight perturbations into 
+In order to propagate the effect of line-of-sight perturbations into 
 uncertainties on time-delay distances we require the probability density function (PDF) for the external convergence
@@
 magnification, using a galaxy halo model. Applying empirical galaxy
-scaling relations both to simulate mock catalogs and then to reconstruct
+scaling relations both to simulate mock catalogues and then to reconstruct
 the line of sight mass distribution. While they did not explore highly
-overdense lines of sight, or the impact of groups and clusters, they
+over-dense lines of sight, or the impact of groups and clusters, they
 found that under their simplifying assumptions, the dispersion in
@@
 \citet{HilbertEtal2009} performed similar ray-tracing experiments
-through the Millenium Simulation \citep{SpringelEtal2005}, generating a
+through the Millennium Simulation \citep{SpringelEtal2005}, generating a
 predicted $\kappa$ at every position in a simulated sky.
@@
 \citet{SuyuEtal2010} selected \MS lines of sight by their apparent
-galaxy overdensity, in a 45 arcsec radius aperture down to $i < 24.5$,
-to match the observed overdensity towards the time delay lens
+galaxy over-density, in a 45 arcsec radius aperture down to $i < 24.5$,
+to match the observed over-density towards the time delay lens
 B1608$+$656 \citep{FassnachtEtal2011}.  The resulting distribution of
@@
 $\Pr(\kappa)$, which was then marginalised over when inferring the time
-delay distance in this system. A similar proceedure was used in \citet{SuyuEtal2012b}.
+delay distance in this system. A similar procedure was used in \citet{SuyuEtal2012b}.
 % B1608$+$656 is indeed a high $\kappa$
@@
 mass, and perpendicular distance to the line of sight, again using the
-\MS mock catalogs and their associated $\kappa$ values to construct
-$\Pr(\kappa|\data)$. For the most overdense lines of sight the
+\MS mock catalogues and their associated $\kappa$ values to construct
+$\Pr(\kappa|\data)$. For the most over-dense lines of sight the
 Green et al. results  show a $\sim$20\% improvement over
@@
 \citeauthor{HilbertEtal2009}'s ray-tracing calculations as the ``truth''
-that we have to recover, we use the \MS mock galaxy catalogs first to
+that we have to recover, we use the \MS mock galaxy catalogues first to
 {\it calibrate} the reconstruction, and account for unseen mass and
@@
 \item Faint galaxies, filaments and dark structures will not appear in
-any photometric object catalog, but they will contribute convergence at
+any photometric object catalogue, but they will contribute convergence at
 some level. How much of the total convergence comes from visible
@@
 \item We have some choices to make when planning follow-up observations
-of interesting sightlines. How should we select objects to achieve the
+of interesting sight-lines. How should we select objects to achieve the
 highest accuracy convergence reconstruction? Can such a selection be
@@
 This paper is organized as follows. We review the relevant gravitational
-lensing theory in~\Sref{sec:theory}, and the Millenium Simulation
-ray-traced convergences and mock catalogs in \Sref{sec:MS}, before
+lensing theory in~\Sref{sec:theory}, and the Millennium Simulation
+ray-traced convergences and mock catalogues in \Sref{sec:MS}, before
 introducing our simple reconstruction  model in \Sref{sec:model}. We
@@
 stellar mass--halo mass relation would both enable similar exploration of
-these systematic errors. It is possible that baryonic physics may alter
+these systematic errors. \citet{SuyuEtal2010} used the relative over-density to mitigate this
+effect, but it does not totally remove the dependence on simulation.
+It is also possible that baryonic physics may alter   
 the radial profile of dark matter halos, even on large scales. \citet{Semboloni+2012}
 found that baryonic physics had a 30-40\% impact on three-point shear statistics, it is
-unclear how baryons affect one-point convergence statistics.
+unclear how baryons affect one-point convergence statistics compared to the pure dark matter
+simulations used in this work.
 
@@
 
-\item  For the most overdense lines of sight, the reconstruction produces a
-very broad PDF; conversely, we find that the lines of sight with the sharpest
+\item  For the most over-dense lines of sight, the reconstruction produces a
+broad PDF; conversely, we find that the lines of sight with the sharpest
 inferred $\pr(\kappa|\data)$ are typically under-dense. Since the
@@
 invested, it will be possible to select targets by the precision of their
-$\kappa$ estimates.
+$\kappa$ estimates. This will be useful
+in an era when there are more known lenses than can be followed-up.
 
@@
 follow-up. Spectroscopic coverage helps to tighten  $\pr(\kappa|\data)$ for
-high $\kappa$ lines of sight, but is of limited use for low $\kappa$ lines of
+high $\kappa$ lines of sight, but is of less use for low $\kappa$ lines of
 sight.
@@
 \item Selecting from the highest precision 33\% of the reconstructed lines of sight
-results in a sample with low bias, 0.2\% in terms of the time delay distance,
+results in a sample with low bias, 0.1\% in terms of the time delay distance,
 and a statistical uncertainty due to line of sight mass structure that is half
 that of the parent sample. Neglecting other sources of error, the residual systematic error would be equal to the
-overall statistical uncertainty in a sample of around 30 lenses.
+overall statistical uncertainty in a sample of around 200 lenses.
 
@@
 0.03$ (as might be done inadvertently by focusing on four-image or wide
-separation lenses) results in a sample with bias of 1\% in time delay
-distance. Such a systematic error would become significant in a sample of $\sim$8 lenses.
+separation lenses) results in a sample with bias of 0.3\% in time delay
+distance. Such a systematic error would become significant in a sample of $\sim$30 lenses.
 

### 2012-11-16 doc/acknowledgments.tex
replace accidentally deleted files

@@
 %
-SHS \ldots
-%
-TT acknowledges support from the NSF through CAREER award NSF-0642621,
-and from the Packard Foundation through a Packard Research Fellowship.
+SHS, ZG  and TT gratefully acknowledge support from the Packard Foundation in the form of a Packard Research Fellowship to TT and from the National Science Foundation grant AST-0642621.
 % 

### 2012-11-16 doc/paper-lcr.tex
replace accidentally deleted files

@@
 {Reconstructing the Lensing Mass in the Universe \\
-from Photometric Catalog Data}
+from Photometric Catalogue Data}
 
@@
   Zachary~Greene$^{4}$,
-  Tommaso~Treu$^{4}$\thanks{\packard},
-  Vasiliy~Belokurov$^{1}$,}
+  Tommaso~Treu$^{4}$\thanks{\packard},}
 \newauthor{%
   Christopher~D.~Fassnacht$^{5}$,
-  L\`eon~V.~E.~Koopmans$^{6}$,
+  L\'eon~V.~E.~Koopmans$^{6}$,
   Roger~D.~Blandford$^{3}$} 
@@
 weak lensing perturbations by galaxies and groups along the line of sight.
-Such massive structures contribute an ``external convergence'' $\kappa$ that
-in some cases dominates the uncertainty in the inferred distances.  We
+Such massive structures contribute an ``external convergence'' $\kappax$ that
+in time delay gravitational lenses can dominate the uncertainty in the inferred distances.  We
 characterise this uncertainty by marginalising over a probability density
-function for $\kappa$: here, we investigate the use of a simple halo model to
-estimate $\pr(\kappa|\data)$ given noisy estimates of the photometric redshift
+function for $\kappax$: here, we investigate the use of a simple halo model to
+estimate $\pr(\kappax|\data)$ given noisy estimates of the photometric redshift
 and stellar mass of galaxies observed in optical imaging surveys of the field
 in question. We use mock catalogues from the Millennium Simulation, and compare
-our reconstructed $\pr(\kappa|\data)$ to ray-traced $\kappa$ truth values: 
+our reconstructed $\pr(\kappax|\data)$ to ray-traced $\kappax$ truth values: 
 taking into account realistic uncertainties on redshift and stellar masses, we
-typically find that the reconstruction yields an improvement in precision of
-40\% over the global $\pr(\kappa)$. For any given line of sight the
+typically find that the reconstruction yields a factor of 2 improvement in precision of
+over the global $\pr(\kappax)$. For any given line of sight the
 convergence estimate can be made before the investment of expensive follow-up
-observations: we find that selecting systems by the precision with which
-$\kappa$ can be estimated leads to a low convergence  sample that would give
-time delay distance estimates a factor of 2 more precise than a random
-selection,  with biases as low as 0.3\%. Preferentially selecting lines of
+observations. We find that the lowest $\kappax$ lines of sight have the best constrained 
+$\pr(\kappax)$ after applying our reconstruction. We find that selecting systems by the precision with which
+$\kappax$ can be estimated leads to a sample of unbiased
+time delay distance estimates with 1\% uncertainties due to external convergence effects.
+Photometric data alone is sufficient to pre-select the best lenses and can be done
+before investment in lightcurve monitoring. Preferentially selecting lines of
 sight with high external shear (as might happen in an assembled sample of
-quadruply-imaged time delay lenses) has the opposite effect, with distances
-biased by around 1\%. We suggest areas for the improvement of this general
+quadruply-imaged time delay lenses) produces time-delay distance estimates with
+typical uncertainties of 1.5\% and biases of 0.3\%. We suggest areas for the improvement of this general
 analysis framework that should allow yet more accurate cosmological inferences
@@
 through the Millennium Simulation \citep{SpringelEtal2005}, generating a
-predicted $\kappa$ at every position in a simulated sky.
+predicted $\kappax$ at every position in a simulated sky.
 \citet{HilbertEtal2009} found that \MS lines of sight with strong lenses
-were not biased towards high $\kappa$, although selection functions for
+were not biased towards high $\kappax$, although selection functions for
 discovering or using particular samples of strong lenses were not taken
@@
 B1608$+$656 \citep{FassnachtEtal2011}.  The resulting distribution of
-$\kappa$ values from the ray-tracing was taken to be an estimate of 
-$\Pr(\kappa)$, which was then marginalised over when inferring the time
+$\kappax$ values from the ray-tracing was taken to be an estimate of 
+$\Pr(\kappax)$, which was then marginalised over when inferring the time
 delay distance in this system. A similar procedure was used in \citet{SuyuEtal2012b}.
-% B1608$+$656 is indeed a high $\kappa$
+% B1608$+$656 is indeed a high $\kappax$
 % line of sight, but it does not reside in a massive cluster environment.
@@
 mass, and perpendicular distance to the line of sight, again using the
-\MS mock catalogues and their associated $\kappa$ values to construct
-$\Pr(\kappa|\data)$. For the most over-dense lines of sight the
+\MS mock catalogues and their associated $\kappax$ values to construct
+$\Pr(\kappax|\data)$. For the most over-dense lines of sight the
 Green et al. results  show a $\sim$20\% improvement over
@@
 idea of calibrating to simulations from \citeauthor{SuyuEtal2010}.
-Taking the $\kappa$ values from
+Taking the $\kappax$ values from
 \citeauthor{HilbertEtal2009}'s ray-tracing calculations as the ``truth''
@@
 generate Monte Carlo sample line of sight mass distributions, and so
-construct the PDF $\Pr(\kappa|\data)$ for that field. We then emulate
+construct the PDF $\Pr(\kappax|\data)$ for that field. We then emulate
 the combination of many such PDFs to quantify the residual biases that
@@
 Throughout this paper magnitudes are given in the AB system and
-we adopt the Millenium Simulation's ``concordance'' parameters for our reference cosmology, \ie
+we adopt the Millennium Simulation's ``concordance'' parameters for our reference cosmology, \ie
 $h=0.73$, $\Omega_m=0.25$ and $\Omega_\Lambda=0.75$, where the symbols indicate
@@
 \caption[magcut]{Four different views of a slightly over-dense \MS line
-of sight, with a $\kappa$ of 0.03. 
+of sight, with a $\kappax$ of 0.03. 
 {\it Top row, left:} The positions of galaxies projected on the sky. The area
@@
 of each halo, respectively. There are essentially no empty lightcones. 
-{\it Top row, right:} The individual $\kappa$ contributions of
+{\it Top row, right:} The individual $\kappax$ contributions of
 each halo, assuming a \citet{BMO} profile and the \citet{Neto2007}
@@
 and the $D$'s are the angular diameter distances between the objects
-refered to in the subscripts: o is the observer, d is the deflector and
+referred to in the subscripts: o is the observer, d is the deflector and
 s is the source. If the surface mass density of the sheet exceeds
@@
 If there is external convergence present that is not included in the
-lens modeling, then the time delay distance -- inferred assuming $\kappax
+lens modelling, then the time delay distance -- inferred assuming $\kappax
 = 0$ -- will be $(1-\kappax)$ more than the true value of $\Dt$:
@@
 
-We can hence estimate the true distance {\it only} if we have with additional
+We can hence estimate the true distance {\it only} if we have additional
 knowledge of $\kappax$. Since $\kappax$ is typically small the absolute
@@
 lines of sight for this,  but must use simulated lines of sight instead.
-In this section we briefly review the Millenium Simulation, the ray
+In this section we briefly review the Millennium Simulation, the ray
 tracing calculations that have been carried out in it, and the mock
-galaxy catalogs that have been produced.
+galaxy catalogues that have been produced.
 
@@
 Dark Matter structures in a cubic region approximately 680~Mpc in
-comoving size, followed from redshift 127 to the present day. With an
+co-moving size, followed from redshift 127 to the present day. With an
 approximate halo mass resolution of $2\times10^{10}{\rm M}_{\odot}$
@@
 of the map, and store the result as the ``true'' convergence for that
-line of sight, $\kappa_{\rm true}$.
-
-\todo{Stefan}{Check this is all accurate and complete!}
+line of sight, $\kappax^{\rm true}$.
 
@@
 
-\subsection{Mock Photometric Galaxy Catalogs}
+\subsection{Mock Photometric Galaxy Catalogues}
 \label{sec:MS:mocks}
 
-We construct mock photometric galaxy catalogs by selecting all \MS
+We construct mock photometric galaxy catalogues by selecting all \MS
 galaxies within a circular aperture of a given angular radius centred on
 the line of sight position, with apparent $i$-band magnitude brighter
-than a given limit. The parent catalog, from \citet{HilbertEtal2011},
+than a given limit. The parent catalogue, from \citet{HilbertEtal2011},
 contains galaxy positions and magnitudes, all of which include lensing
@@
 
-\todo{Stefan, Tom}{Check this is all accurate and complete!}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We require a method for estimating the
-convergence at any point on the sky, given a catalog of observed
+convergence at any point on the sky, given a catalogue of observed
 galaxy properties such as positions, brightnesses, colours, and
@@
 the lens, down to some magnitude limit. Since we cannot observe the
-surface mass density of each halo directy, we need some way of
-estimating the mass of each halo in the catalog, so that we can compute
+surface mass density of each halo directly, we need some way of
+estimating the mass of each halo in the catalogue, so that we can compute
 its contribution to the total $\kappax$ along the line of sight \citep[as
@@
 
-Transforming an observed photometometric galaxy catalogue into a 
+Transforming an observed photometric galaxy catalogue into a 
 catalogue of halo masses, positions, and redshifts, will enable us to
@@
 from the mass enclosed within $r_{200}$, which we denote as $M_{200}$.
-We find our results do not change if the \citet{MaccioEtal2008} Mass--concencetration relation is used instead.
+We find our results do not change if the \citet{MaccioEtal2008} Mass--concentration relation is used instead.
 The best fit relation of \citet{Neto2007} is given by
@@
 \Aref{appendix:MSMH}. Given an uncertain stellar mass and redshift for
-each galaxy in the  catalog, we draw a sample halo mass from the PDF
+each galaxy in the  catalogue, we draw a sample halo mass from the PDF
 that describes this uncertainty  (\Eref{eq:mhalo-mstar})  and use
@@
 
-While halos contribute a positive convergence to $\kappa$, voids contribute
+While halos contribute a positive convergence to $\kappax$, voids contribute
 a negative convergence. When a ray bundle passes through a  region of space
@@
 the presence a void, but we do not attempt to use this information}. Neglecting voids
-would lead to a heavily biased estimate of $\kappa$. Moreover, the halos in 
+would lead to a heavily biased estimate of $\kappax$. Moreover, the halos in 
 the model only add mass to the background density, and that background density
@@
 The solution we present here is to calibrate the relationship between halo
-convergence $\kappah$ and underlying convergence $\kappa$ (as calculated
+convergence $\kappah$ and underlying convergence $\kappax$ (as calculated
 during full ray tracing) using the simulations themselves.
@@
 $\pr(\kappah|\mathcal{D})$, but what we are interested in is the total convergence
-along the line of sight $\pr(\kappa|\mathcal{D})$. We can obtain this by
+along the line of sight $\pr(\kappax|\mathcal{D})$. We can obtain this by
 considering the expression:
 \begin{equation}
-\Pr(\kappa|\mathcal{D}) = \int \dee\kappah 
-   \Pr(\kappa|\kappah) \Pr(\kappah|\mathcal{D})
+\Pr(\kappax|\mathcal{D}) = \int \dee\kappah 
+   \Pr(\kappax|\kappah) \Pr(\kappah|\mathcal{D})
 \label{eq:kappaconv}   
@@
 The first term in the integrand relates the convergence due to model halos,
-$\kappah$, to the true convergence, $\kappa$. This conditional distribution
-can be constructed from the Millennium Simulation catalogs, by computing
+$\kappah$, to the true convergence, $\kappax$. This conditional distribution
+can be constructed from the Millennium Simulation catalogues, by computing
 $\kappah$ for each selected line of sight using the true values of the halo
-parameters,  and accumulating $\kappah$ and $\kappa$ along a large number of
+parameters,  and accumulating $\kappah$ and $\kappax$ along a large number of
 such lines of
-sight to  characterize $\Pr(\kappa|\kappah)$.
+sight to  characterize $\Pr(\kappax|\kappah)$.
 For any given line of sight we can then estimate
 $\pr(\kappah|\data)$ as described above, and then
-multiply it by $\Pr(\kappa|\kappah)$ and integrate out the intermediate
+multiply it by $\Pr(\kappax|\kappah)$ and integrate out the intermediate
 nuisance parameter $\kappah$. 
@@
 $\pr(\kappah|\{\Mstar,z\})$ can become skewed relative to
-$\pr(\kappah|\{\Mhalo,z\})$; this is because of the assymetry in the
+$\pr(\kappah|\{\Mhalo,z\})$; this is because of the asymmetry in the
 conversion from stellar mass through halo mass into $\kappah$. A long tail of
 high halo masses gives rise to a tendency to overestimate $\kappah$.
-If this shift is ignored, the resulting $\Pr(\kappa|\data)$ will be 
-biased towards high values of $\kappa$.
+If this shift is ignored, the resulting $\Pr(\kappax|\data)$ will be 
+biased towards high values of $\kappax$.
 
@@
 this PDF be denoted $\kappah^{\rm med}$. We again take a large number of
-calibration sightlines from the \MS catalogs, but this time generate a mock
-stellar mass catalog for each one. We then reconstruct each lightcone in the
+calibration sightlines from the \MS catalogues, but this time generate a mock
+stellar mass catalogue for each one. We then reconstruct each lightcone in the
 same way as we would an observed field,
 estimate $\pr(\kappah|\{\Mstar,z\})$, and extract its median. Accumulating
-these samples and their corresponding true values of $\kappa$, we can form the 
-conditional distribution $\pr(\kappa|\kappah^{\rm med})$. 
-Then, when inferring $\kappa$ from an observed photometric catalog, we would
+these samples and their corresponding true values of $\kappax$, we can form the 
+conditional distribution $\pr(\kappax|\kappah^{\rm med})$. 
+Then, when inferring $\kappax$ from an observed photometric catalogue, we would
 estimate $\pr(\kappah|\{\Mstar,z\}_{\rm obs})$ 
@@
 version of 
-\Eref{eq:kappaconv} to infer $\kappa$: 
+\Eref{eq:kappaconv} to infer $\kappax$: 
 \bea
-\Pr(\kappa|\mathcal{D}) &=& \int \dee\kappah^{\rm med} 
-   \Pr(\kappa|\kappah^{\rm med}) \Pr(\kappah^{\rm med}|\mathcal{D}) \notag \\
-                        &=& \Pr(\kappa|\kappa_{\rm h,obs}^{\rm med}).
+\Pr(\kappax|\mathcal{D}) &=& \int \dee\kappah^{\rm med} 
+   \Pr(\kappax|\kappah^{\rm med}) \Pr(\kappah^{\rm med}|\mathcal{D}) \notag \\
+                        &=& \Pr(\kappax|\kappa_{\rm h,obs}^{\rm med}).
 \label{eq:calkappaconv}   
@@
 risky: the simulated lightcones that have median $\kappah$ values to match are
-not guaranteed to provide an accurate estimate of $\kappa$ via this PDF
+not guaranteed to provide an accurate estimate of $\kappax$ via this PDF
 look-up. We proceed with caution, quantifying the biases and PDF widths in the
@@
 We now put the reconstruction \proceedure outlined above into practice, first
-inferring $\kappa$ from $\kappah$ in the case of hypothetical galaxy catalogs
+inferring $\kappax$ from $\kappah$ in the case of hypothetical galaxy catalogues
 with noiseless redshifts and halo masses. The reason for doing this is to
@@
 
-\subsection{How is $\kappah$ related to $\kappa$?}
-
-\Fref{fig:jointkh-k} shows the joint distribution of $\kappah$ and $\kappa$
+\subsection{How is $\kappah$ related to $\kappax$?}
+
+\Fref{fig:jointkh-k} shows the joint distribution of $\kappah$ and $\kappax$
 values for 100,000 randomly selected \MS lines of sight, assuming noise-free
 halo masses and redshifts. In this case, the PDF $\pr(\kappah|\data)$ is a
-delta function: to read off $\pr(\kappa|\data)$ we must take a thin horizontal
+delta function: to read off $\pr(\kappax|\data)$ we must take a thin horizontal
 slice across this joint distribution. Note that the joint PDF plotted in this
@@
 that the scatter in $\kappax$ grows with $\kappah$; our reconstruction is
-better at reproducing underdense lines of sight than overdense lines of sight.
+better at reproducing under-dense lines of sight than over-dense lines of sight.
 The effect of ignoring voids and the smooth mass component is evident in this
-plot: $\kappah$ is significantly higher than $\kappa$, at any given $\kappa$
+plot: $\kappah$ is significantly higher than $\kappax$, at any given $\kappax$
 value. Multiplying by $\pr(\kappah|\data)$ and integrating over $\kappah$
-gives a PDF for $\kappa$ centred at the correct place, by construction.
+gives a PDF for $\kappax$ centred at the correct place, by construction.
 
@@
 \caption[Biased?]{The joint distribution of 
-$\kappah$ and $\kappa$, from 100,000 reconstructed lines of
-sight. $\kappah$ traces $\kappa$, but with a positive offset which arises from
+$\kappah$ and $\kappax$, from 100,000 reconstructed lines of
+sight. $\kappah$ traces $\kappax$, but with a positive offset which arises from
 $\kappah$ not accounting for any voids, dark structures or smooth mass
-component. At fixed $\kappah$ the scatter in $\kappa$ grows with $\kappah$.}
+component. At fixed $\kappah$ the scatter in $\kappax$ grows with $\kappah$.}
 \label{fig:jointkh-k}
@@
 
-\subsection{How accurate is the $\kappah - \kappa$ calibration?}
+\subsection{How accurate is the $\kappah - \kappax$ calibration?}
 
@@
 \includegraphics[width=\columnwidth]{figs/globaldist.eps}
-\caption[magcut]{Recovering the global $\pr(\kappa)$, shown in red, 
+\caption[magcut]{Recovering the global $\pr(\kappax)$, shown in red, 
 from $10^{5}$ ray-traced lines of
@@
 sample reconstructed 
-$\kappa$ values, each one drawn from an inferred PDF 
-$P(\kappa|\{\Mhalo,z\}$)
+$\kappax$ values, each one drawn from an inferred PDF 
+$P(\kappax|\{\Mhalo,z\}$)
 in one of $10^{5}$ reconstructed lines of sight. 
@@
 In this section, let us define the ``bias'' of the reconstruction of a given
-line of sight as the difference between the expectation value of $\kappa$ over
-the inferred PDF $\pr(\kappa|\data)$ and the known true value $\kappatrue$.
+line of sight as the difference between the expectation value of $\kappax$ over
+the inferred PDF $\pr(\kappax|\data)$ and the known true value $\kappax^{\mathrm{true}}$.
 Let us also define the ``width,'' $\sigma_{\kappa}$, to be half the width of
 the interval containing the central $68\%$ of the posterior probability
-$\pr(\kappa|\data)$.
+$\pr(\kappax|\data)$.
 
@@
 bias to be $-9.5\times 10^{-6}$, and the mean width to be 0.01. This is
-approximately 1.8 times smaller than the width of the global $\pr(\kappa)$. 
-We find that our inferred $\kappa$ PDFs are consistent with the global
-$\kappa$ distribution; Figure \ref{fig:globaldist} shows that sampling from
-$\pr(\kappa|\data)$ in $10^{5}$ reconstructed lines of sight produces a
-distribution of $\kappa$ values over the sky identical to the global
-$\pr(\kappa)$. Given perfect knowledge of halo mass and redshift, the
-calibration \proceedure provides an unbiased estimate of $\kappa$ that is
-$\sim$2 times as precise as using the global $\pr(\kappa)$.
+approximately 1.8 times smaller than the width of the global $\pr(\kappax)$. 
+We find that our inferred $\kappax$ PDFs are consistent with the global
+$\kappax$ distribution; Figure \ref{fig:globaldist} shows that sampling from
+$\pr(\kappax|\data)$ in $10^{5}$ reconstructed lines of sight produces a
+distribution of $\kappax$ values over the sky identical to the global
+$\pr(\kappax)$. Given perfect knowledge of halo mass and redshift, the
+calibration \proceedure provides an unbiased estimate of $\kappax$ that is
+$\sim$2 times as precise as using the global $\pr(\kappax)$.
 
@@
 improve the reconstruction.  \Fref{fig:magcut} shows the scatter on
-$\kappah-\kappa$ (where $\kappah$ is shifted so that its mean is zero) as a
+$\kappah-\kappax$ (where $\kappah$ is shifted so that its mean is zero) as a
 function of reconstruction magnitude limit. We do
 not expect a deeper survey to decrease the size of the uncertainty in mapping
-$\kappah$ onto $\kappa$. Halos at all redshifts out to the source redshift
+$\kappah$ onto $\kappax$. Halos at all redshifts out to the source redshift
 (1.4, here) contribute to the convergence, but the largest contribution comes from
@@
 \caption[magcut]{The 16, 50 and 84th percentiles of $\kappah$ minus
-$\kappa$ as a function of the limiting radius of the halo
+$\kappax$ as a function of the limiting radius of the halo
 reconstruction. $\kappah$ has been shifted such that
@@
 \caption[magcut]{The 16, 50 and 84th percentiles of $\kappah$ minus
-$\kappa$ as a function of the limiting $i$ band depth of the halo
+$\kappax$ as a function of the limiting $i$ band depth of the halo
 reconstruction. $\kappah$ has been shifted such that
@@
 
-\section{Testing the Halo Model Reconstruction on Mock Galaxy Catalogs}
+\section{Testing the Halo Model Reconstruction on Mock Galaxy Catalogues}
 \label{sec:obsMstar+z}
@@
 
-\subsection{Making Mock Observational Catalogs}
-
-While the \MS catalogs do already contain stellar masses for each galaxy, we
+\subsection{Making Mock Observational Catalogues}
+
+While the \MS catalogues do already contain stellar masses for each galaxy, we
 find that these are not well behaved at the low mass end due to unreasonably high dark matter stripping from satellite halos. We also wanted to be able to perform the functional test of
@@
 mass--halo mass relation. For these reasons, we assign a new stellar mass to
-each halo in the \MS catalogs, according to the stellar mass--halo mass
+each halo in the \MS catalogues, according to the stellar mass--halo mass
 relation of \citet{BehrooziEtal2010}. From this true  stellar mass we
@@
 
-\subsection{Reconstructing $\kappa$ given a spectroscopic redshift for every object}
+\subsection{Reconstructing $\kappax$ given a spectroscopic redshift for every object}
 
@@
 estimate $\pr(\kappah|\data)$ for each reconstructed line of sight. We then
-transform this into our target PDF $\pr(\kappa|\data)$.
+transform this into our target PDF $\pr(\kappax|\data)$.
 
@@
 \includegraphics[width=\columnwidth]{figs/Widthvshilberrt.eps}
-\caption{Width of the \infered PDF $\pr(\kappa|\data)$ versus the true
-$\kappa$ along a line of sight. Blue assumes a spectroscopic redshift for
+\caption{Width of the \infered PDF $\pr(\kappax|\data)$ versus the true
+$\kappax$ along a line of sight. Blue assumes a spectroscopic redshift for
 every halo, whilst green assumes only photometric redshifts. The width of the
-\infered $\pr(\kappah|\data)$ increases with $\kappa$.}
+\infered $\pr(\kappah|\data)$ increases with $\kappax$.}
 
@@
 
-The best possible reconstructions of $\kappa$ will come from having a
+The best possible reconstructions of $\kappax$ will come from having a
 spectroscopic redshift for every single object in each field
@@
 case. Reconstructing the lines of sight with perfect knowledge of the redshift
-but an uncertain stellar mass, we find that the width of $\pr(\kappa|\data)$
-grows with the expectation value of $\kappa$ (\Fref{fig:widthsvsH}). The low
-$\kappa$ lines of sight are relatively empty, and so there are few
-opportunities for uncertainties in the halo masses to \propogate into $\kappa$
+but an uncertain stellar mass, we find that the width of $\pr(\kappax|\data)$
+grows with the expectation value of $\kappax$ (\Fref{fig:widthsvsH}). The low
+$\kappax$ lines of sight are relatively empty, and so there are few
+opportunities for uncertainties in the halo masses to \propogate into $\kappax$
 uncertainties. The median reconstruction width in this idealised situations is
@@
 
-\subsection{Reconstructing $\kappa$ from photometry alone}
+\subsection{Reconstructing $\kappax$ from photometry alone}
 
@@
 on redshift at fixed mass: the redshift error has only a small effect on the
-inferred $\pr(\kappa|\data)$ when compared to the effect of uncertain stellar
+inferred $\pr(\kappax|\data)$ when compared to the effect of uncertain stellar
 masses.  With only photometric redshifts the uncertainty on
-$\kappah$ is larger than in the spectrocopic case and this
-\propogates into a broader $\pr(\kappa|\data)$, although the photometric
+$\kappah$ is larger than in the spectroscopic case and this
+\propogates into a broader $\pr(\kappax|\data)$, although the photometric
 reconstruction still typically produces a 50\% improvement compared to the
-precision of the global $\pr(\kappa)$ (\Fref{fig:widthsvsH}).
-
-\subsection{Reconstructing $\kappa$ with partial spectroscopic coverage}
+precision of the global $\pr(\kappax)$ (\Fref{fig:widthsvsH}).
+
+\subsection{Reconstructing $\kappax$ with partial spectroscopic coverage}
 
 While a fully photometric reconstruction provides useful constraints on
-$\pr(\kappa|\data)$, targeted spectroscopy can provide addtional constraints
+$\pr(\kappax|\data)$, targeted spectroscopy can provide additional constraints
 on the masses and redshifts of halos whose $\kappah$ contribution have the
@@
 galaxies and all $i<24$ galaxies within 1 arcminute of the line of sight, the
-$\pr(\kappa|\data)$ would be almost as good as having complete spectroscopic
-coverage (\Fref{fig:reconwidths}). High $\kappa$ lines of sight benefit the
+$\pr(\kappax|\data)$ would be almost as good as having complete spectroscopic
+coverage (\Fref{fig:reconwidths}). High $\kappax$ lines of sight benefit the
 most from additional spectral coverage, since these LoS have the most
-uncertain $\kappah$. Consistent with our previous findings the lowest $\kappa$
-lines of sight have the most constrained $\kappa$ PDFs.
+uncertain $\kappah$. Consistent with our previous findings the lowest $\kappax$
+lines of sight have the most constrained $\kappax$ PDFs.
 
@@
 lenses. By subtracting the true (ray-traced) convergence from the
-\infered $\pr(\kappa)$ for each line of sight we are left with a PDF that
+\infered $\pr(\kappax)$ for each line of sight we are left with a PDF that
 should be estimating zero; these can be multiplied together for multiple
@@
 test for possible bias in it. These plots show the
-expectation value of $\prod_{i=1}^N \pr_i(\kappa-\kappa_{\rm true})$ --
+expectation value of $\prod_{i=1}^N \pr_i(\kappax-\kappax^{\rm true})$ --
 deviations from zero constitute biases. The solid, dashed and dotted
@@
 20, 5 and 2 sightlines respectively. Green lines show the results
-from multiplying $\pr(\kappa|\data)$ \infered from photometry alone, whilst red
-lines are from multiplying $\pr(\kappa)$ \infered from photometry and a
+from multiplying $\pr(\kappax|\data)$ \infered from photometry alone, whilst red
+lines are from multiplying $\pr(\kappax)$ \infered from photometry and a
 spectroscopic redshift for all halos with $i<23$ and all halos within 1
@@
 of sight. The central plot shows sight lines randomly selected from the
-33\% of lines whose P($\kappa$) is most tightly constrained. The right
+33\% of lines whose P($\kappax$) is most tightly constrained. The right
 hand plot shows only lines of sight with external shear of 0.03 or
@@
 
-While it is good to reconstruct $\kappa$ precisely, it is more important that
-$\kappa$ is reconstructed accurately. The reconstruction must not be biased. 
-We test the accuracy of our reconstructed $\pr(\kappa|\data)$ in the following
+While it is good to reconstruct $\kappax$ precisely, it is more important that
+$\kappax$ is reconstructed accurately. The reconstruction must not be biased. 
+We test the accuracy of our reconstructed $\pr(\kappax|\data)$ in the following
 way: for each line of sight we have an estimator for the true convergence along
 that line of sight, by subtracting the line of sight's ray-traced convergence
-$\kappatrue$ from $\pr(\kappa|\data)$ we have an estimator of zero, $\pr(\kappa-\kappatrue|\data)$.
- Since the $\pr(\kappa-\kappatrue|\data)$ for
+$\kappax^{\rm true}$ from $\pr(\kappax|\data)$ we have an estimator of zero, $\pr(\kappax-\kappax^{\rm true}|\data)$.
+ Since the $\pr(\kappax-\kappax^{\rm true}|\data)$ for
 each line of sight is an \independant estimator of zero, the PDFs from $N$ lines of sight
@@
 \label{eq:bias}
-\mathcal{P}_N = \prod_{i=1}^N \pr_i(\kappa-\kappa_{\rm true})
+\mathcal{P}_N = \prod_{i=1}^N \pr_i(\kappax-\kappax^{\rm true})
 \ee
@@
 expectation value of $\mathcal{P}_N$ from zero. If the bias of $\mathcal{P}_N$
-is smaller than the half-width of $\mathcal{P}_N$, our $\kappa$ estimators can
+is smaller than the half-width of $\mathcal{P}_N$, our $\kappax$ estimators can
 be considered accurate. Since the width of $\mathcal{P}_N$ decreases as more
@@
 
-\subsubsection{Selecting only the lines of sight with tight $\pr(\kappa|\data)$}
+\subsubsection{Selecting only the lines of sight with tight $\pr(\kappax|\data)$}
 \label{sec:bias:tightPDF}
@@
 bias -- our reconstruction is most \succesful for the lowest
-$\kappa$ lines of sight. With targeted spectroscopic follow-up of the selected lines of sight
+$\kappax$ lines of sight. With targeted spectroscopic follow-up of the selected lines of sight
 there is negligible improvement compared to photometry alone, since the best constrained lines of sight are
-the most empty, and it is the high-$\kappa$ lines of sight that benefit the
+the most empty, and it is the high-$\kappax$ lines of sight that benefit the
 most from spectroscopy. Photometry of the field is sufficient to adequately
 select the best lines of sight for cosmology -- and doing so greatly increases
- the precision of the cosmological constraints per system, with no degredation of the accuracy.
-Since lenses are typically found in locally overdense environments, it is unlikely that 
+ the precision of the cosmological constraints per system, with no degradation of the accuracy.
+Since lenses are typically found in locally over-dense environments, it is unlikely that 
 an almost empty line of sight would contain a lens; it is somewhat optimistic to 
@@
 separation (to decrease the covariance between the ground-based image
-lightcurves), or the fact that they are quadruply-imaging rather than
+light-curves), or the fact that they are quadruply-imaging rather than
 doubly-imaging, since this yields 3 time delays instead of 1, a higher
@@
 reconstruction; but as \Fref{fig:magcut} shows, observing deeper
-than 24th magnitude does not signifcantly help the reconstruction.
+than 24th magnitude does not significantly help the reconstruction.
 
@@
 broad even after applying our reconstruction; these lines of sight are
-typically the most overdense lines of sight in the universe. For
+typically the most over-dense lines of sight in the universe. For
 time-delay cosmography the most observationally expensive tasks are the
-lightcurve monitoring and high resolution follow-up imaging and spectroscopy,
+light-curve monitoring and high resolution follow-up imaging and spectroscopy,
 while making photometric observations of a
@@
 $\pr(\kappax)$ does not induce a bias in $\kappax$, and hence distance.
-For the most overdense lines of sight,
+For the most over-dense lines of sight,
 the precision of $\pr(\kappax|\data)$ is improved noticeably by the addition
@@
 know to choose a subset based on their reconstructed $\pr(\kappax|\data)$.
-Spectroscopic coverage will definately be useful for extracting cosmology from
-overdense lines of sight.
+Spectroscopic coverage will definitely be useful for extracting cosmology from
+over-dense lines of sight.
 
@@
 sight are similar to the reconstructed line of sight. \citet{SuyuEtal2012}
-found that for RXJ1131 combining shear constriants with galaxy number count
-overdensity, gave a significantly different $\pr(\kappa|\gamma,N_{45})$
-compared to the PDF from number count overdensity alone,
+found that for RXJ1131 combining shear constraints with galaxy number count
+over-density, gave a significantly different $\pr(\kappax|\gamma,N_{45})$
+compared to the PDF from number count over-density alone,
 $\pr(\kappax|N_{45})$.
@@
 Extending our model to include shear we find that given
-perfect knowledge of the halo mass and redshift the raytraced external shear
+perfect knowledge of the halo mass and redshift the ray-traced external shear
 $\gamma$ and the reconstructed external shear $\gamma_{\mathrm{h}}$  are
@@
 \includegraphics[width=\columnwidth]{figs/biasplots3.eps}
-\caption{Convergence estimation accuracy using the full  $\pr(\kappa|\kappah)$
+\caption{Convergence estimation accuracy using the full  $\pr(\kappax|\kappah)$
 distribution, rather than its median.  As in \Fref{fig:biasplots}, solid,
@@
 The reduction of $\pr(\kappah|\data)$ to just its median value, before using
-it to look up the appropriate $\pr(\kappa)$ from the simulated sightline
+it to look up the appropriate $\pr(\kappax)$ from the simulated sightline
 ensemble, is reminiscent of the procedure followed by \citet{SuyuEtal2010},
@@
 thing to do: at present, however, it suffers from significant bias in the
-photometric data case. \Fref{fig:no-median-tricks} shows how $\kappa$ is
+photometric data case. \Fref{fig:no-median-tricks} shows how $\kappax$ is
 overestimated, as a result of the high scatter in halo mass for objects with 
@@
 study using
-a different simulation to make the test catalogs would allow us to quantify
+a different simulation to make the test catalogues would allow us to quantify
 the sensitivity of our results to the simulation used. Similarly the use of a
@@
 source. We have used the ray-traced lensing convergence along lines of sight
-through the Millenium Simulation to test this approach, and to calibrate
+through the Millennium Simulation to test this approach, and to calibrate
 estimates of the total convergence made by summing the convergences due to
@@
 redshift of each halo, and propagated these uncertainties into a
-$\pr(\kappa|\data)$ for each line of sight. We also defined three different
+$\pr(\kappax|\data)$ for each line of sight. We also defined three different
 possible line of sight selections, and investigated the bias induced by these
@@
 \item Despite our model's simplicity, its reconstructed $\kappah$ values are
-good tracers of $\kappa$. $\kappah$ is biased due to our ignorance of voids, but we found that this can be calibrated out. We found that with perfect knowledge of
-the halo mass and redshift (from the Millennium Simulation catalogs), for a
+good tracers of $\kappax$. $\kappah$ is biased due to our ignorance of voids, but we found that this can be calibrated out. We found that with perfect knowledge of
+the halo mass and redshift (from the Millennium Simulation catalogues), for a
 typical line of sight the calibrated reconstruction gives an unbiased estimate
-of $\kappa$ that is a factor of 2 more precise than the global $\pr(\kappa)$.
+of $\kappax$ that is a factor of 2 more precise than the global $\pr(\kappax)$.
 
@@
 $\pr(\kappah|\data)$ is still a useful indicator for inferring
-$\pr(\kappa|\data)$ from the ensemble of simulated lines of sight, but the
+$\pr(\kappax|\data)$ from the ensemble of simulated lines of sight, but the
 resulting PDFs tend to be much broader than for perfect halo mass and redshift
@@
 \item It is very rare for halos further than 2 arcminutes from the line of
-sight to make a significant contribution to $\pr(\kappa|\data)$. Including
+sight to make a significant contribution to $\pr(\kappax|\data)$. Including
 halos whose host galaxy is less luminous than $i=24$ does not significantly
@@
 uncertainties of our simple reconstruction recipe, and yield a 
-$\pr(\kappa|\data)$ that has, on average, a width of 0.016. This is 1.5 times
-less broad than the global $\pr(\kappa)$.
+$\pr(\kappax|\data)$ that has, on average, a width of 0.016. This is 1.5 times
+less broad than the global $\pr(\kappax)$.
 
@@
 broad PDF; conversely, we find that the lines of sight with the sharpest
-inferred $\pr(\kappa|\data)$ are typically under-dense. Since the
+inferred $\pr(\kappax|\data)$ are typically under-dense. Since the
 reconstructions described here can be performed before follow-up time is
 invested, it will be possible to select targets by the precision of their
-$\kappa$ estimates. This will be useful
+$\kappax$ estimates. This will be useful
 in an era when there are more known lenses than can be followed-up.
@@
 \item Photometric data is sufficient  to select the best lines of sight for
-follow-up. Spectroscopic coverage helps to tighten  $\pr(\kappa|\data)$ for
-high $\kappa$ lines of sight, but is of less use for low $\kappa$ lines of
+follow-up. Spectroscopic coverage helps to tighten  $\pr(\kappax|\data)$ for
+high $\kappax$ lines of sight, but is of less use for low $\kappax$ lines of
 sight.
@@
 % \item With only a photometric reconstruction of all time delay lens fields,
-% and following up only the systems with the most precise $\kappa$ estimates,
+% and following up only the systems with the most precise $\kappax$ estimates,
 % the width of the dominant statistical uncertainty in time-delay cosmography
@@
 % lens modelling induces uncertainties at the $\sim$3 percent
-% level, which far exceeds the typical $\kappa$ uncertainties after applying our
+% level, which far exceeds the typical $\kappax$ uncertainties after applying our
 % reconstruction \proceedure. By using reconstruction methods such as that
@@
 
-\section*{Acknowledgments}
+\section*{Acknowledgements}
 
@@
 function for the observed stellar mass. Note that the ``true'' $\Mstar$ of the
-galaxy is marginalised out: we are only interested in infering the halo
+galaxy is marginalised out: we are only interested in inferring the halo
 mass. The last two terms in
@@
 given redshift. We can
-tabulate the product of these two from our Millenium Simulation catalog,
+tabulate the product of these two from our Millennium Simulation catalogue,
 constructing a two-dimensional histogram of halo masses and their associated
@@
 function of the unknown $\Mstar$, and multiply it by our tabulated joint PDF.
-This heavily downweights halos with $\Mstar$ values outside the observed
+This heavily down weights halos with $\Mstar$ values outside the observed
 range. We then do the marginalisation integral by Monte Carlo, drawing
 (two-dimensional) sample parameter vectors
-from the downweighted histogram, discarding the $\Mstar$ values, and
+from the down weighted histogram, discarding the $\Mstar$ values, and
 constructing a one-dimensional histogram that is an estimate of

### 2012-11-16 doc/references.tex
more draft editing
replace accidentally deleted files

@@
 
-\bibitem[LSST Science Collaboration et al.(2009)]{LSST} LSST 
-Science Collaboration, Abell, P.~A., Allison, J., et al.\ 2009, 
+\bibitem[LSST Science Collaboration (2009)]{LSST} LSST 
+Science Collaboration: Abell, P.~A., Allison, J., et al.\ 2009, 
 arXiv:0912.0201
@@
 269
+
+\bibitem[Semboloni et al.(2012)]{Semboloni+2012} Semboloni, E., 
+Hoekstra, H., \& Schaye, J.\ 2012, arXiv:1210.7303
 

### 2012-11-20 doc/paper-lcr.tex
paper update

@@
 by a quadrupole lens characterised only by external convergence and shear.
-The external shear can potentially be recovered in the
+The external shear, $\gammax$ can potentially be recovered in the
 mass-modelling of the lens, but the convergence is undetectable from the
 image positions, shapes and relative fluxes; this is the famous {\emph{ 
-mass sheet-degeneracy}} \citep[see e.g.][for details]{FalcoEtal1985}.
-
+mass-sheet degeneracy}} \citep[see e.g.][for details]{FalcoEtal1985}.
+
+Large samples
+of time-delay lenses are expected to be discovered in the next decade in
+ground-based optical imaging surveys \citep{Oguri+Marshall2010}: both
+the detectability of these lenses, and the selection of sub-samples of
+them for further observation, could induce a selection function in external
+convergence. External convergence must be included in analysis of time-delay
+lenses else the inferred time-delay distance and cosmology be systematically biased.
+
+Since the mass-sheet degeneracy prevents any estimate of $\kappax$ from the 
+strong lens modelling additional information is required. Weak lensing measurements
+can been used for rich lines of sight \citep{NakajimaEtal2009, FadelyEtal2009}, but 
+for lines of sight with low galaxy density we must attempt to reconstruct the distribution
+of mass along the line of sight. Attempts to reconstruct the mass distribution in strong
+lens fields have focused on understanding the external shear which seems to be large in most strong lenses.
+Surveys by \citet{Fassnacht+Lubin2002,AugerEtal2007,WilliamsEtal2006,MomchevaEtal2006}
+all found groups of galaxies hosting or near to known gravitational lenses.
+\citet{WongEtal2011} estimated $\Pr(\gammax)$ given the data of \citet{WilliamsEtal2006}
+and \citet{MomchevaEtal2006} but found significant discrepancy between the predicted shear
+distribution and the external shear demanded by the strong lens model. 
+\citeauthor{WongEtal2011} also found that both line of
+sight structures and the group of galaxies in each lens plane contribute
+significant proportions of the shear.
+
+For non-lens lines of sight magnification is a more useful quantity than convergence; \citet{GunnarssonEtal2006} used a galaxy halo model combined with simple scaling relations to reconstruct supernovae
+lines of sight and found that the dispersion in
+apparent source brightness due to lensing magnification could be reduced
+by a factor of two.
+Conversely \citet{KarpenkaEtal2012} used the brightness dispersion in type Ia supernovae to infer the parameters of both their galaxy halo model and mass-to-light scaling relation.
+Both \citeauthor{KarpenkaEtal2012} and \citet{JonssonEtal2010} were able to
+detect lensing effects in the supernova data this way.
+
+Large numerical simulations can also be used to estimate global convergence distributions.
+ \citet{Holder+Schechter2003} and
+\citet{DalalEtal2005} carried out ray-tracing calculations in N-body
+simulations to estimate the distribution of external shear values. 
+\citet{HilbertEtal2009} performed similar ray-tracing experiments
+through the Millennium Simulation \citep{SpringelEtal2005}, generating a
+predicted $\kappax$ at every position in a simulated sky.
+\citet{HilbertEtal2009} found that after removing the matter on the strong lensing plane
+\MS lines of sight with strong lenses
+were not biased towards high $\kappax$, although selection functions for
+discovering samples of strong lenses were not taken
+into account.
+
+The \MS results have been used to analyse real observations as well. 
+\citet{SuyuEtal2010} selected \MS lines of sight by their apparent
+galaxy over-density, in a 45 arcsec radius aperture down to $i < 24.5$,
+to match the observed over-density towards the time delay lens
+B1608$+$656 \citep{FassnachtEtal2011}.  The resulting distribution of
+$\kappax$ values from the ray-tracing was taken to be an estimate of 
+$\Pr(\kappax)$, which was then marginalised over when inferring the time
+delay distance in this system. A similar procedure was used in \citet{SuyuEtal2012b}.
+In a companion paper to this one, Greene et al. (submitted) investigate
+improvements to this method by weighting the galaxy counts by galaxy
+mass, and perpendicular distance to the line of sight, again using the
+\MS mock catalogues and their associated $\kappax$ values to construct
+$\Pr(\kappax|\data)$. For the most over-dense lines of sight the
+Green et al. results  show a $\sim$20\% improvement over
+number counts alone, but little improvement for less dense lines.
+
+In this paper, we combine the halo model reconstruction approach of
+\citeauthor{GunnarssonEtal2006}, \citeauthor{JonssonEtal2010}, 
+\citeauthor{WongEtal2011} and others, with the
+idea of calibrating to simulations from \citeauthor{SuyuEtal2010}
+Taking the $\kappax$ values from
+\citeauthor{HilbertEtal2009}'s ray-tracing calculations as the ``truth''
+that we have to recover, we use the \MS mock galaxy catalogues first to
+{\it calibrate} the reconstruction, and account for unseen mass and
+voids, and then to {\it test} the accuracy of the line of sight mass
+reconstruction under this assumption. Probabilistically assigning mass
+and redshift to every observed galaxy in a given observed field, we
+generate Monte Carlo sample line of sight mass distributions, and so
+construct the PDF $\Pr(\kappax|\data)$ for that field. We then emulate
+the combination of many such PDFs to quantify the residual biases that
+would be translated to the global (including cosmological) parameters.
+In doing so, we aim to answer the following questions:
+
+\begin{itemize}
+
+\item Faint galaxies, filaments and dark structures will not appear in
+any photometric object catalogue, but they will contribute convergence at
+some level. How much of the total convergence comes from visible
+galaxies, and how much effect do dark structures and voids have?
+
+\item Can the true convergence be recovered from a calibrated halo model
+reconstruction? What scatter and residual bias are induced by the
+reconstruction process, and how might these be reduced in the future?
+
+\item We have some choices to make when planning follow-up observations
+of interesting sight-lines. How should we select objects to achieve the
+highest accuracy convergence reconstruction? Can such a selection be
+made robustly, using the reconstruction results?
+
+\end{itemize}
+
+This paper is organized as follows. We review the relevant gravitational
+lensing theory in~\Sref{sec:theory}, and the Millennium Simulation
+ray-traced convergences and mock catalogues in \Sref{sec:MS}, before
+introducing our simple reconstruction  model in \Sref{sec:model}. We
+then test this model in two phases: first, in \Sref{sec:knownMh+z}, with
+known redshift and halo mass for every galaxy in a lens field, in order
+to quantify the irreducible uncertainty due to unseen mass, and second,
+in \Sref{sec:obsMstar+z}, with realistic observational uncertainties on
+the observed galaxies' stellar masses and redshifts. In
+\Sref{sec:biases} we investigate the potential systematic error induced
+by selecting a subset of sightlines. We discuss our results in
+\Sref{sec:discuss} before concluding in \Sref{sec:conclude}.
+
+Throughout this paper magnitudes are given in the AB system and
+we adopt the Millennium Simulation's ``concordance'' parameters for our reference cosmology, \ie
+$h=0.73$, $\Omega_m=0.25$ and $\Omega_\Lambda=0.75$, where the symbols indicate
+the Hubble Constant in units of 100 km s$^{-1}$ Mpc$^{-1}$ and the matter and
+dark energy density of the Universe in units of the critical density.
+.%\citep[e.g.\ ][]{KomEtal09}.
+
+\comments{
 When inferring global quantities
@@
 measurement of \citet{FadelyEtal2009}. A precise weak lensing estimate of $\kappax$ can only be made if the number density of of weakly lensed, measurable galaxies is high.
-
-In order to make more precise estimates of the convergence at a given
-sky position, we need more information.   There have been some attempts
-to reconstruct the local and line of sight mass distribution in strong
-lens fields in some detail, based on photometric and spectroscopic
-surveys of the galaxies nearby. These efforts have focused on  detecting
-galaxy groups, ascertaining the visible galaxies' membership of those
-groups, and assigning mass to the group and galaxy halos in order to
-predict the external shear apparently required by the strong lens
-models. Surveys by
-\citet{Fassnacht+Lubin2002,AugerEtal2007,WilliamsEtal2006,MomchevaEtal2006}
-all found groups of galaxies both hosting, and lying  along the line of
-sight to, known gravitational lenses. Initial estimates of the effect of
-these structures suggested the importance of assigning mass to both
-galaxy and group halos, and to allowing for significant uncertainty in
-the centroids of group halos.
-
-In order to propagate the effect of line-of-sight perturbations into 
+}
+
+\comments{In order to propagate the effect of line-of-sight perturbations into 
 uncertainties on time-delay distances we require the probability density function (PDF) for the external convergence
-given our available data $\data$, $\Pr(\xkappa|\data)$
-% PHIL's REVIEWS OF THE LITRATURE
+given our available data $\data$, $\Pr(\xkappa|\data)$}
+% PHIL's REVIEWS OF THE LITERATURE
 \comments{\citet{GunnarssonEtal2006} investigated a related PDF,  for the
@@
 }
-% TOM's DISTILLING OF SAID REVIEWS.
-Previous investigation of line-of-sight perturbations have focused on 
-magnification and shear.\citet{GunnarssonEtal2006} used a galaxy halo model combined with simple scaling relations to reconstruct
-the line of sight mass distribution and found that the dispersion in
-apparent source brightness due to lensing magnification could be reduced
-by a factor of two.
-Conversely \citet{KarpenkaEtal2012} used the brightness dispersion in type Ia supernovae to infer the parameters of both their galaxy halo model and mass-to-light scaling relation.
-Both \citeauthor{KarpenkaEtal2012} and \citet{JonssonEtal2010} were able to
-detect lensing effects in the supernova data this way.
-%
-\citet{WongEtal2011} estimated the PDF for the external shear,
-$\Pr(\gammax|\data)$ from their survey data,
-\citep{WilliamsEtal2006;MomchevaEtal2006} of galaxies close to the line
-of sight. Comparing the predicted shear
-distributions with the external shear demanded by the strong lens model 
-they found significant
-discrepancies, but were unable to distinguish between the environment
-modelling and the strong lens modelling as the cause of these
-discrepancies. \citeauthor{WongEtal2011} also found that both line of
-sight structures and the group of galaxies in each lens plane contribute
-significant proportions of the shear.
-
-Large numerical simulations have been used to
-predict, from first principles, the distribution of likely external
-shears and convergences along various lines of sight, including those
-containing strong lens systems.  \citet{Holder+Schechter2003} and
-\citet{DalalEtal2005} carried out ray-tracing calculations in N-body
-simulations to estimate the distribution of external shear values. 
-\citet{HilbertEtal2009} performed similar ray-tracing experiments
-through the Millennium Simulation \citep{SpringelEtal2005}, generating a
-predicted $\kappax$ at every position in a simulated sky.
-\citet{HilbertEtal2009} found that \MS lines of sight with strong lenses
-were not biased towards high $\kappax$, although selection functions for
-discovering or using particular samples of strong lenses were not taken
-into account.
-
-The \MS results have been used to analyse real observations as well. 
-\citet{SuyuEtal2010} selected \MS lines of sight by their apparent
-galaxy over-density, in a 45 arcsec radius aperture down to $i < 24.5$,
-to match the observed over-density towards the time delay lens
-B1608$+$656 \citep{FassnachtEtal2011}.  The resulting distribution of
-$\kappax$ values from the ray-tracing was taken to be an estimate of 
-$\Pr(\kappax)$, which was then marginalised over when inferring the time
-delay distance in this system. A similar procedure was used in \citet{SuyuEtal2012b}.
-% B1608$+$656 is indeed a high $\kappax$
-% line of sight, but it does not reside in a massive cluster environment.
-In a companion paper to this one, Greene et al. (submitted) investigate
-improvements to this method by weighting the galaxy counts by galaxy
-mass, and perpendicular distance to the line of sight, again using the
-\MS mock catalogues and their associated $\kappax$ values to construct
-$\Pr(\kappax|\data)$. For the most over-dense lines of sight the
-Green et al. results  show a $\sim$20\% improvement over
-number counts alone, but little improvement for less dense lines.
-
-In this paper, we combine the halo model reconstruction approach of
-\citeauthor{GunnarssonEtal2006}, \citeauthor{JonssonEtal2010}, 
-\citeauthor{WongEtal2011} and others, with the
-idea of calibrating to simulations from \citeauthor{SuyuEtal2010}.
-Taking the $\kappax$ values from
-\citeauthor{HilbertEtal2009}'s ray-tracing calculations as the ``truth''
-that we have to recover, we use the \MS mock galaxy catalogues first to
-{\it calibrate} the reconstruction, and account for unseen mass and
-voids, and then to {\it test} the accuracy of the line of sight mass
-reconstruction under this assumption. Probabilistically assigning mass
-and redshift to every observed galaxy in a given observed field, we
-generate Monte Carlo sample line of sight mass distributions, and so
-construct the PDF $\Pr(\kappax|\data)$ for that field. We then emulate
-the combination of many such PDFs to quantify the residual biases that
-would be translated to the global (including cosmological) parameters.
-In doing so, we aim to answer the following questions:
-
-\begin{itemize}
-
-\item Faint galaxies, filaments and dark structures will not appear in
-any photometric object catalogue, but they will contribute convergence at
-some level. How much of the total convergence comes from visible
-galaxies, and how much effect do dark structures and voids have?
-
-\item Can the true convergence be recovered from a calibrated halo model
-reconstruction? What scatter and residual bias are induced by the
-reconstruction process, and how might these be reduced in the future?
-
-\item We have some choices to make when planning follow-up observations
-of interesting sight-lines. How should we select objects to achieve the
-highest accuracy convergence reconstruction? Can such a selection be
-made robustly, using the reconstruction results?
-
-\end{itemize}
-
-This paper is organized as follows. We review the relevant gravitational
-lensing theory in~\Sref{sec:theory}, and the Millennium Simulation
-ray-traced convergences and mock catalogues in \Sref{sec:MS}, before
-introducing our simple reconstruction  model in \Sref{sec:model}. We
-then test this model in two phases: first, in \Sref{sec:knownMh+z}, with
-known redshift and halo mass for every galaxy in a lens field, in order
-to quantify the irreducible uncertainty due to unseen mass, and second,
-in \Sref{sec:obsMstar+z}, with realistic observational uncertainties on
-the observed galaxies' stellar masses and redshifts. In
-\Sref{sec:biases} we investigate the potential systematic error induced
-by selecting a subset of sightlines. We discuss our results in
-\Sref{sec:discuss} before concluding in \Sref{sec:conclude}.
-
-Throughout this paper magnitudes are given in the AB system and
-we adopt the Millennium Simulation's ``concordance'' parameters for our reference cosmology, \ie
-$h=0.73$, $\Omega_m=0.25$ and $\Omega_\Lambda=0.75$, where the symbols indicate
-the Hubble Constant in units of 100 km s$^{-1}$ Mpc$^{-1}$ and the matter and
-dark energy density of the Universe in units of the critical density.
-.%\citep[e.g.\ ][]{KomEtal09}.
 
@@
 \ee
-This approximation was found to be accurate to a few percent or better
+\citet{HilbertEtal2009} found this approximation was found to be accurate to a few percent or better
 in $\kappax$, even on 30 arcsecond scales.
@@
 Cosmological dark matter simulations have shown that dark matter
-halos are well-approximated by NFW profiles \citep{NFW}, with a density
+halos are well-approximated by NFW profiles
+
+\citep{NFW}, with a density
 profile given by
@@
 the density slope transitions from $r^{-1}$ to $r^{-3}$. This radius is related
-to the virial radius of the halo by $r_{s}~=~r_{200}/c$, where $r_{200}$ is the radius at 
-which 
-\be
-\rho(r_{200}) = 200\rho_{{\mathrm{crit}}}(z), \text{ where } \rho_{\mathrm{crit}}(z) \equiv \frac{3H^{2}(z)}{8\pi G}
-\ee
-and $c$ is the concentration parameter, which can be estimated from the halo's mass,
+to the virial radius of the halo by $r_{s}~=~r_{200}/c$, where $c$ is the concentration parameter, which can be estimated from the halo's mass,
 using a mass--concentration relation. Typically more massive halos are less concentrated,
 but there is some scatter; we use the relation of \citet{Neto2007} to estimate $c$
-from the mass enclosed within $r_{200}$, which we denote as $M_{200}$.
-We find our results do not change if the \citet{MaccioEtal2008} Mass--concentration relation is used instead.
-The best fit relation of \citet{Neto2007} is given by
-\be
-c_{200} = 4.67 (M_{200}/10^{14} h^{-1} \Msun)^{-0.11}.
-\ee
-
-$\rho_0$ is calculated from the critical density and concentration parameter:
-\be
-\rho_0 = \rho_{\mathrm{crit}}(z)\frac{200}{3}\frac{c^{3}}{\ln(1+c)-c/(1+c)}.
-\ee
+from the mass enclosed within $r_{200}$, which we denote as $M_{200}$. We find our results do not change if the \citet{MaccioEtal2008} Mass--concentration relation is used instead.
 
@@
 which is the same as the NFW profile in the limit that the truncation
-radius, $r_t$ goes to infinity. We use a truncation radius of five times
+radius, $r_t$ goes to infinity; the shear and convergence from such a
+profile are derived in \citet{BMO}.
+ We use a truncation radius of five times
 the virial radius, but our results are robust for any choice of $r_t>2
-\times r_{200}$. The formula for the projected surface mass density 
-$\Sigma(D_{od}\theta)$ for this
-mass profile is given in \citet{BMO}.
+\times r_{200}$.
 
@@
 \ee
-\notes{Using the Born approximation, we approximate light rays as straight.}
 
@@
 
-While halos contribute a positive convergence to $\kappax$, voids contribute
-a negative convergence. When a ray bundle passes through a  region of space
-that is less dense than $\rho_{\rm mean}(z)$ the rays are de-focused\footnote{In
-principle, the convergence caused by halos is also caused by the overdensity,
-but we neglect this effect since halos are typically much more dense than the
-intergalactic medium}. Whilst the  full ray-traced solution takes into account
-the effect of voids, our reconstruction cannot -- the halo catalogue does not
-include voids. \new{In principle the absence of galaxies implies something about
-the presence a void, but we do not attempt to use this information}. Neglecting voids
-would lead to a heavily biased estimate of $\kappax$. Moreover, the halos in 
-the model only add mass to the background density, and that background density
-already accounts for all the mass in the Universe! In order to make voids
-negative relative to the mean density, we must subtract a significant smooth
-mass component. The problem is that we do not have a good model for the
-density structure of that smooth component.
+Our halo model accounts for the convergence contribution of density perturbations that can
+be associated with light. Filaments and dark substructures contribute additional convergence
+whilst voids contribute a divergence; these structures must be included to produce an unbiased estimate of $\kappax$
+in principle the absence of galaxies implies something about
+the presence a void, but we do not currently attempt to use this information. Neglecting voids
+would lead to a heavily biased estimate of $\kappax$, since the halo model's $\kappah$
+can only be positive. It is difficult to correct for unseen structure problem
+since we do not have a good model for its density structure.
 
@@
 during full ray tracing) using the simulations themselves.
-The halo modelling \proceedure outlined in \Sref{sec:model:halos} allows 
+The halo modelling procedure outlined in \Sref{sec:model:halos} allows 
 us to estimate 
@@
 \Pr(\kappax|\mathcal{D}) = \int \dee\kappah 
-   \Pr(\kappax|\kappah) \Pr(\kappah|\mathcal{D})
+   \Pr(\kappax|\kappah,\mathcal{D}) \Pr(\kappah|\mathcal{D})
 \label{eq:kappaconv}   
@@
 can be constructed from the Millennium Simulation catalogues, by computing
-$\kappah$ for each selected line of sight using the true values of the halo
-parameters,  and accumulating $\kappah$ and $\kappax$ along a large number of
+$\kappah$ for each selected line and accumulating $\kappah$ and $\kappax$ along a large number of
 such lines of
@@
 multiply it by $\Pr(\kappax|\kappah)$ and integrate out the intermediate
-nuisance parameter $\kappah$. 
-% We can do the marginalisation over $\kappah$
-% by drawing samples from the two-dimensional grid and keeping only the
-% $\kappa$ values, to form our final result, $\Pr(\kappa|\mathcal{D})$.
-
-However, given an uncertain stellar mass to halo mass conversion, the PDF
-$\pr(\kappah|\{\Mstar,z\})$ can become skewed relative to
-$\pr(\kappah|\{\Mhalo,z\})$; this is because of the asymmetry in the
+parameter $\kappah$.
+
+However, given an uncertain stellar mass to halo mass conversion,
+$\pr(\kappah|\mathcal{D}_1)$ can be shifted relative to
+$\pr(\kappah|\mathcal{D}_2)$ given perfect knowledge of the halo mass; this is because of the asymmetry in the
 conversion from stellar mass through halo mass into $\kappah$. A long tail of
@@
 If this shift is ignored, the resulting $\Pr(\kappax|\data)$ will be 
-biased towards high values of $\kappax$.
-
-We find that we can correct this bias to some extent by artificially 
-suppressing the tails of $\pr(\kappah|\{\Mstar,z\})$. Let the median of
-this PDF be denoted $\kappah^{\rm med}$. We again take a large number of
-calibration sightlines from the \MS catalogues, but this time generate a mock
+biased towards high values of $\kappax$ if $\Pr(\kappax|\kappah)$ is constructed from lines
+of sight with perfect knowledge of the halo mass. Ideally one wants to find the $\kappax$ distribution
+of all calibration lines of sight with a $\pr(\kappah|\data)$ that is identical to $\pr(\kappah|\data)$ for the real line of sight
+{\it given the same data quality}; this is impossible given a finite number of calibration lines of sight.
+We compromise on the similarity of our real line of sight to the calibration lines of sight by 
+selecting considering only the median of the $\pr(\kappah|\data)$ distributions.
+
+We  take a large number of
+calibration sightlines from the \MS catalogues and generate a mock
 stellar mass catalogue for each one. We then reconstruct each lightcone in the
 same way as we would an observed field,
-estimate $\pr(\kappah|\{\Mstar,z\})$, and extract its median. Accumulating
+estimate $\pr(\kappah|\data)$, and extract its median. Accumulating
 these samples and their corresponding true values of $\kappax$, we can form the 
 conditional distribution $\pr(\kappax|\kappah^{\rm med})$. 
-Then, when inferring $\kappax$ from an observed photometric catalogue, we would
-estimate $\pr(\kappah|\{\Mstar,z\}_{\rm obs})$ 
+Then, when inferring $\kappax$ from an observed photometric catalogue, we 
+estimate $\pr(\kappah|\data)$ 
 using the halo model, compute the median value 
-$\kappa_{\rm h,obs}^{\rm med}$, and then use the following alternative
+$\kappa_{\rm h,obs}^{\rm med}$, and then use an alternative
 version of 
@@
 \bea
-\Pr(\kappax|\mathcal{D}) &=& \int \dee\kappah^{\rm med} 
-   \Pr(\kappax|\kappah^{\rm med}) \Pr(\kappah^{\rm med}|\mathcal{D}) \notag \\
-                        &=& \Pr(\kappax|\kappa_{\rm h,obs}^{\rm med}).
+\Pr(\kappax|\kappah^{\rm med},\mathcal{D}) &=& \int \dee\kappah^{\rm med} 
+   \Pr(\kappax|\kappah^{\rm med},\mathcal{D}) \Pr(\kappah^{\rm med}|\mathcal{D}) \notag \\
 \label{eq:calkappaconv}   
 \eea
-Here, we have replaced $\Pr(\kappah^{\rm med}|\mathcal{D})$ with a delta
-function centred at the observed median value $\kappa_{\rm h,obs}$. 
-The procedure of reducing the full PDF for $\kappah$ to just its median is
-risky: the simulated lightcones that have median $\kappah$ values to match are
-not guaranteed to provide an accurate estimate of $\kappax$ via this PDF
-look-up. We proceed with caution, quantifying the biases and PDF widths in the
-sections below.
+Because we only have a finite number of calibration lines of sight, we use all calibration
+lines of sight with $kappah_{\rm calibration}^{\rm med} = kappah^{\rm med}\pm0.003$ to form
+$\Pr(\kappax|\kappah^{\rm med},\mathcal{D})$, with each calibration line weighted
+equally.
+
+The procedure of reducing the full PDF for $\kappah$ to its median increases the 
+importance of the simulation choice: the simulation needs to be a similar as possible
+to the real universe or there is a possibility of systematic errors. The reader
+should keep in mind that we have only performed this analysis using the \MS.
 

### 2012-11-22 doc/paper-lcr.tex
more draft editing

@@
 function for $\kappax$: here, we investigate the use of a simple halo model to
-estimate $\pr(\kappax|\data)$ given noisy estimates of the photometric redshift
+estimate $\pr(\kappax)$ given noisy estimates of the photometric redshift
 and stellar mass of galaxies observed in optical imaging surveys of the field
@@
 quadruply-imaged time delay lenses) produces time-delay distance estimates with
-typical uncertainties of 1.5\% and biases of 0.3\%. We suggest areas for the improvement of this general
+typical uncertainties of 1.8\% and biases of 0.8\%. We suggest areas for the improvement of this general
 analysis framework that should allow yet more accurate cosmological inferences
@@
 $\Pr(\kappax)$, which was then marginalised over when inferring the time
-delay distance in this system. A similar procedure was used in \citet{SuyuEtal2012b}.
+delay distance in this system. A similar procedure was used in \citet{SuyuetAl2012b}.
 In a companion paper to this one, Greene et al. (submitted) investigate
@@
 \Sref{sec:biases} we investigate the potential systematic error induced
-by selecting a subset of sightlines. We discuss our results in
+by selecting a subset of lines of sight. We discuss our results in
 \Sref{sec:discuss} before concluding in \Sref{sec:conclude}.
@@
 mass-sheet degeneracy by providing an additional estimate of the lens galaxy's
-mass \citep[e.g.,][]{SuyuEtal2010}. In this work our aim is to quantify the
+mass \citep[e.g.,][]{Koopmans2004;SuyuEtal2010}. In this work our aim is to quantify the
 lensing effect of massive objects, regardless of their position along the line
@@
 To define a test line of sight, we draw a random sky position from
-within the convergence maps, bilinearly interpolate between the pixels
+within the convergence maps, bi-linearly interpolate between the pixels
 of the map, and store the result as the ``true'' convergence for that
@@
 \ee
-where the critical surface density was defined in \Eref{eq:sigcrit}.
+where $\Sigma_{\mathrm{cr}}(z_i,\zs)$ is the critical surface density \comments{was defined in \Eref{eq:sigcrit}}.
 Following the first order approximation of \citet{HilbertEtal2009}
@@
 To estimate a halo's contribution to $\kappah$ we must first know the
-halo's mass. For the sightlines of the \MS, halo masses are
+halo's mass. For the lines of sight of the \MS, halo masses are
 known, but for  real lines of sight the halo masses have to be \infered
@@
 redshifts, $\pr(\kappah|\data)$ will have very long tails corresponding to
-very overdense sightlines that we do not believe exist. The resolution of this
+very over-dense lines of sight that we do not believe exist. The resolution of this
 is to divide out the effective prior PDF that was applied during the halo mass
@@
 We  take a large number of
-calibration sightlines from the \MS catalogues and generate a mock
+calibration lines of sight from the \MS catalogues and generate a mock
 stellar mass catalogue for each one. We then reconstruct each lightcone in the
@@
 importance of the simulation choice: the simulation needs to be a similar as possible
-to the real universe or there is a possibility of systematic errors. The reader
-should keep in mind that we have only performed this analysis using the \MS.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+to the real universe or there is a possibility of systematic errors. 
 \section{Results: Perfect Halo Data}
@@
 panel, the solid line is the median cumulative contribution over a large
-sample of sightlines, while dashed and dot-dashed show the ranges enclosing 68
-and 95 percent of the sightlines repectively.}
+sample of lines of sight, while dashed and dot-dashed show the ranges enclosing 68
+and 95 percent of the lines of sight respectively.}
 \label{fig:where}
@@
 synergistic survey, or from targeted follow-up. In this section we quantify
-the errors induced by inferring the halo mass and redshift from these
+the uncertainties induced by inferring the halo mass and redshift from these
 observables.
@@
 given measurements of stellar mass. We will investigate two main sources of
-error: inferring halo mass given observed stellar mass, and placing halos at
-the wrong redshift due to photometric redshift error. Much work has already
+uncertainty: inferring halo mass given observed stellar mass, and placing halos at
+the wrong redshift due to photometric redshift uncertainty. Much work has already
 focused on using photometric colours to infer stellar mass
@@
 use $\sigma_{M_*}=0.15$ dex for halos with a spectroscopic redshift and
-$\sigma_{M_*}=0.45$ dex otherwise. For photometric redshift errors we draw a
+$\sigma_{M_*}=0.45$ dex otherwise. For photometric redshift uncertainties we draw a
 redshift from $\pr(z_{\rm true}|z_{\rm obs})$ which we take to be a Gaussian
@@
 convergence from the outskirts of an individual halo is only weakly \dependant
-on redshift at fixed mass: the redshift error has only a small effect on the
+on redshift at fixed mass: the redshift uncertainty has only a small effect on the
 inferred $\pr(\kappax|\data)$ when compared to the effect of uncertain stellar
@@
 \section{Systematic Errors due to Sample Selection}
-\label{sec:bias}
+\label{sec:biases}
 
@@
 
-\subsubsection{Selecting random lines of sight}
+\subsection{Selecting random lines of sight}
 \label{sec:bias:random}
@@
 
-\subsubsection{Selecting only the lines of sight with tight $\pr(\kappax|\data)$}
+\subsection{Selecting only the lines of sight with tight $\pr(\kappax|\data)$}
 \label{sec:bias:tightPDF}
@@
 
-\subsubsection{Selecting only high shear lines of sight}
+\subsection{Selecting only high shear lines of sight}
 \label{sec:bias:tightPDF}
@@
 
-By selecting only lines of sight with an external shear of $\gammax>0.03$ we
+By selecting only lines of sight with an external shear of $\gammax>0.05$ we
 can test the impact of shear selection. We find that in this sample, $\kappax$
-is systematically underestimated at the $\sim$0.003 level (corresponding to a
-0.3\% systematic error in distance; in the absence of other sources of uncertainty, this
-systematic error would be significant in a sample of 40 lenses). 
-This effect is mitigated if only
-the lines of sight with both $\gammax>0.03$ and well constrained $\pr(\kappax|\data)$ are
-used, but biases at the $\sim$0.001 level remain. Since our model does not
+is systematically underestimated at the $\sim$0.008 level (corresponding to a
+0.8\% systematic error in distance); in the absence of other sources of uncertainty, this
+systematic error would be significant in a sample of 5 lenses. Approximating strong-lens
+modelling uncertainties as an unbiased gaussian with width 4\% on time-delay distance a 0.8\% bias would be
+significant for $\sim$20 lenses. 
+The systematic error is mitigated if only
+the lines of sight with both $\gammax>0.05$ and well constrained $\pr(\kappax|\data)$ are
+used, but biases at the $\sim$0.005 level remain. The
+toy selection model used here ($\gammax>0.05$) is likely to be a much
+stronger selection than reality, but nevertheless it is worth noting that the
+reconstruction \proceedure will be biased if lens selection functions are
+extreme and unaccounted for. Since our model does not
 include shear constraints it is not surprising that a selection function based on shear
 can induce a bias. A more sophisticated model that includes the shear
-recovered from the lens modelling may be less susceptible to this bias. The
-toy selection model used here ($\gammax>0.03$) is likely to be a much
-stronger selection than reality, but nevertheless it is worth noting that the
-reconstruction \proceedure will be biased if lens selection functions are
-extreme and unaccounted for.
+recovered from the lens modelling may be less susceptible to this bias.
+
+The halo model can also be used to estimate the external shear
+along a line of sight. Shear is an observable that can be extracted from
+strong lens modelling, however there is a degeneracy between internal and
+external shear. When the Einstein Ring data are very good it is possible to
+disentangle external and internal shear \citep[\eg][]{SuyuEtal2010}, but there are
+still significant uncertainties: \citet{WongEtal2011} attempted to match the
+shear from strong lens models with a reconstruction of the local lens group
+environment, but found a tension between the strong lens model and the
+reconstruction of the environment. Given the \citet{WongEtal2011} results
+it is unclear whether the external shear from lens models can be
+reconciled with a line of sight reconstruction. Alternatively, it may be possible 
+to infer external shear using weak lensing information from near the line of sight. 
+If the true external shear can be
+measured, it provides an additional constraint on which of the \MS lines of
+sight are similar to the reconstructed line of sight. \citet{SuyuEtal2012}
+found that for RXJ1131 combining shear constraints with galaxy number count
+over-density, gave a significantly different $\pr(\kappax|\gamma,N_{45})$
+compared to the PDF from number count over-density alone,
+$\pr(\kappax|N_{45})$.
+
+Extending our model to include shear we find that given
+perfect knowledge of the halo mass and redshift the ray-traced external shear
+$\gamma$ and the reconstructed external shear $\gamma_{\mathrm{h}}$  are
+similar, with 68 percent of lines obeying
+\be
+\label{eq:shearineq}
+|{\boldmath{\gammax}-\boldmath{\gamma_{\mathrm{h}}}}| < \mathrm{0.025}
+\ee 
+Future work should investigate whether $\gamma_{\mathrm{h}}$ can be used
+to improve the accuracy and precision of $\kappax$ estimation, given a
+reconstruction of the line of sight.
 
@@
 
+\comments{
 We have shown that reconstructing the matter due to halos along any line of
@@
 estimates under our calibration assumptions. We now revisit these assumptions.
+}
 
@@
 in the context of their simple halo model, a truncated isothermal profile for
-the galaxy mass distributions. Weak galaxy-galaxy and cluster-galaxy  lensing
-studies \citep[\eg][]{GavazziEtal2006,JohnstonEtal2007} also suggest an
+the galaxy mass distributions. Galaxy-galaxy and cluster-galaxy  lensing
+studies \citep[\eg][]{GavazziEtal2007,JohnstonEtal2007} also suggest an
 approximately isothermal profile for the mass-shear correlation function;
@@
 Likewise,  halo ellipticity may have some small effect on the predicted
-convergence.
+convergence. It is possible that baryonic physics may alter   
+the radial profile of dark matter halos, even on large scales. \citet{Semboloni+2012}
+found that baryonic physics had a 30-40\% impact on three-point shear statistics, it is
+unclear how baryons affect one-point convergence statistics compared to the pure dark matter
+simulations used in this work.
 
@@
 
-Interestingly, we have found that it is the most empty lines of sight that 
+\comments{Interestingly, we have found that it is the most empty lines of sight that 
 can be reconstructed with the highest precision. $\kappax$ estimates for empty
@@
 than 24th magnitude does not significantly help the reconstruction.
-
-For a small fraction of lines of sight, $\pr(\kappax|\data)$ remains very
+}
+
+\comments{For a small fraction of lines of sight, $\pr(\kappax|\data)$ remains very
 broad even after applying our reconstruction; these lines of sight are
@@
 over-dense lines of sight.
-
-The method we have outlined can also be used to estimate the external shear
-along a line of sight. Shear is an observable that can be extracted from
-strong lens modelling, however there is a degeneracy between internal and
-external shear. When the Einstein Ring data are very good it is possible to
-disentangle external and internal shear \citep[\eg][]{xxx}, but there are
-still significant uncertainties: \citet{WongEtal2011} attempted to match the
-shear from strong lens models with a reconstruction of the local lens group
-environment, but found a tension between the strong lens model and the
-reconstruction of the environment. Given the \citet{WongEtal2011} results
-it is unclear whether the external shear from lens models can be
-reconciled with a line of sight reconstruction. Alternatively, it may be possible 
-to infer external shear using weak lensing information from near the line of sight. 
-If the true external shear can be
-measured, it provides an additional constraint on which of the \MS lines of
-sight are similar to the reconstructed line of sight. \citet{SuyuEtal2012}
-found that for RXJ1131 combining shear constraints with galaxy number count
-over-density, gave a significantly different $\pr(\kappax|\gamma,N_{45})$
-compared to the PDF from number count over-density alone,
-$\pr(\kappax|N_{45})$.
-
-Extending our model to include shear we find that given
-perfect knowledge of the halo mass and redshift the ray-traced external shear
-$\gamma$ and the reconstructed external shear $\gamma_{\mathrm{h}}$  are
-similar, with 68 percent of lines obeying
-\be
-\label{eq:shearineq}
-|{\boldmath{\gammax}-\boldmath{\gamma_{\mathrm{h}}}}| < \mathrm{0.025}
-\ee 
-Future work should investigate whether $\gamma_{\mathrm{h}}$ can be used
-to improve the accuracy and precision of $\kappax$ estimation, given a
-reconstruction of the line of sight.
-
+}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\comments{%
 \begin{figure}
@@
 \end{figure}
+}%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 weighted number counts in an aperture, we treat each galaxy individually, and
-predict  $\kappa_{\rm h,obs}^{\rm med}$ for use in their place. One
+predict  $\kappa_{\rm h,obs}^{\rm med}$ for use in their place.
+
+\comments{ One
 significant disadvantage of these types of method is that they impose a
@@
 mass estimates. 
+}
 
@@
 effect, but it does not totally remove the dependence on simulation.
-It is also possible that baryonic physics may alter   
-the radial profile of dark matter halos, even on large scales. \citet{Semboloni+2012}
-found that baryonic physics had a 30-40\% impact on three-point shear statistics, it is
-unclear how baryons affect one-point convergence statistics compared to the pure dark matter
-simulations used in this work.
-
-In particular, the method presented here is tied to the simulations at two
+
+\comments{In particular, the method presented here is tied to the simulations at two
 points: the prior PDF for $\kappah$, and the conditional distribution
@@
 possible test of our halo model prescription against real observations.
-
+}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 of $\kappax$ that is a factor of 2 more precise than the global $\pr(\kappax)$.
-
-\item With uncertain halo masses and redshifts, we find that
+With uncertain halo masses and redshifts, we find that
 $\pr(\kappah|\data)$ is still a useful indicator for inferring
@@
 uncertainties of our simple reconstruction recipe, and yield a 
-$\pr(\kappax|\data)$ that has, on average, a width of 0.016. This is 1.5 times
+$\pr(\kappax|\data)$ that has, on average, a width of 0.016 (inducing a $\sim$1.6\%
+uncertainty on time-delay distances). This is 1.5 times
 less broad than the global $\pr(\kappax)$.
@@
 in an era when there are more known lenses than can be followed-up.
-
-\item Photometric data is sufficient  to select the best lines of sight for
+Photometric data is sufficient to select the best lines of sight for
 follow-up. Spectroscopic coverage helps to tighten  $\pr(\kappax|\data)$ for
@@
 and a statistical uncertainty due to line of sight mass structure that is half
-that of the parent sample. Neglecting other sources of error, the residual systematic error would be equal to the
+that of the parent sample. Neglecting other sources of uncertainty, the residual systematic error would be equal to the
 overall statistical uncertainty in a sample of around 200 lenses.
@@
 \item Conversely, selecting lines of sight with high shear ($|\gamma| >
-0.03$ (as might be done inadvertently by focusing on four-image or wide
-separation lenses) results in a sample with bias of 0.3\% in time delay
-distance. Such a systematic error would become significant in a sample of $\sim$30 lenses.
+0.05$ (as might be done inadvertently by focusing on four-image or wide
+separation lenses) results in a sample with bias of 0.8\% in time delay
+distance. Including realistic estimates of other sources of uncertainty a systematic error
+of 0.8\% would become significant in a sample of $\sim$20 lenses.
 
@@
 % for systems like B1608$+$656 it is the dominant one. For most lines of sight
-% lens modelling induces uncertainties at the $\sim$3 percent
+% lens modelling induces uncertainties at the $\sim$4 percent
 % level, which far exceeds the typical $\kappax$ uncertainties after applying our
@@
 
+TEC thanks Vasily Belokurov for supervision, guidance and suggestions.
 We thank Risa Wechsler and Peter Behroozi 

### 2012-11-22 doc/references.tex
more draft editing

@@
 
-\bibitem[Cropper et al.(2012)]{EUCLID} Cropper, M., Cole, R., 
+\bibitem[Cropper et al.(2012)]{Euclid} Cropper, M., Cole, R., 
 James, A., et al.\ 2012, arXiv:1208.3369
@@
 \& Wong}{2011}]{FassnachtEtal2011} Fassnacht C.~D., Koopmans L.~V.~E., Wong K.~C., 2011, MNRAS, 410, 2167
+
+\bibitem[Gavazzi et al.(2007)]{GavazziEtal2007} Gavazzi, R., Treu, T., 
+Rhodes, J.~D., et al.\ 2007, \apj, 667, 176
 
@@
 % \& Holz}{2004}]{Linder+Holz2004} Linder E.~V., Holz D.~E., 2004, AAS, 36, \#131.02
+
+\bibitem[Koester et al.(2007)]{MaxBCG} Koester, B.~P., McKay, 
+T.~A., Annis, J., et al.\ 2007, \apj, 660, 221
+
+\bibitem[Koopmans(2004)]{Koopmans2004} Koopmans, L.~V.~E.\ 2004, 
+arXiv:astro-ph/0412596
 

### 2012-11-22 doc/paper-lcr.tex
third draft finished

@@
 weak lensing perturbations by galaxies and groups along the line of sight.
-Such massive structures contribute an ``external convergence'' $\kappax$ that
-in time delay gravitational lenses can dominate the uncertainty in the inferred distances.  We
-characterise this uncertainty by marginalising over a probability density
-function for $\kappax$: here, we investigate the use of a simple halo model to
-estimate $\pr(\kappax)$ given noisy estimates of the photometric redshift
-and stellar mass of galaxies observed in optical imaging surveys of the field
-in question. We use mock catalogues from the Millennium Simulation, and compare
+In time delay gravitational lenses,
+``external convergence,'' $\kappax$, can dominate the uncertainty in the inferred distances.
+In this paper we attempt to reconstruct $\kappax$,
+due to line of sight structure using a simple halo model.
+ We use mock catalogues from the Millennium Simulation, and compare
 our reconstructed $\pr(\kappax|\data)$ to ray-traced $\kappax$ truth values: 
@@
 typically find that the reconstruction yields a factor of 2 improvement in precision of
-over the global $\pr(\kappax)$. For any given line of sight the
-convergence estimate can be made before the investment of expensive follow-up
-observations. We find that the lowest $\kappax$ lines of sight have the best constrained 
+over the global $\pr(\kappax)$. We find that the lowest $\kappax$ lines of sight have the best constrained 
 $\pr(\kappax)$ after applying our reconstruction. We find that selecting systems by the precision with which
 $\kappax$ can be estimated leads to a sample of unbiased
-time delay distance estimates with 1\% uncertainties due to external convergence effects.
+time delay distance estimates each with 1\% uncertainties due to external convergence effects.
 Photometric data alone is sufficient to pre-select the best lenses and can be done
@@
 quadruply-imaged time delay lenses) produces time-delay distance estimates with
-typical uncertainties of 1.8\% and biases of 0.8\%. We suggest areas for the improvement of this general
-analysis framework that should allow yet more accurate cosmological inferences
-to be made.
-
+typical external convergence uncertainties of 1.8\% but with systematic errors of 0.8\%.
+We suggest areas for the improvement of this general analysis framework that
+should allow yet more accurate cosmological inferences to be made.
 \end{abstract}
@@
 $\Pr(\kappax)$, which was then marginalised over when inferring the time
-delay distance in this system. A similar procedure was used in \citet{SuyuetAl2012b}.
+delay distance in this system. A similar procedure was used in \citet{SuyuEtal2012}.
 In a companion paper to this one, Greene et al. (submitted) investigate
@@
 
-\new{
 In strong lens systems where the source is time variable, the images do not 
@@
 observed time delays \citep{SuyuEtal2010}.
-}
 
@@
 mass-sheet degeneracy by providing an additional estimate of the lens galaxy's
-mass \citep[e.g.,][]{Koopmans2004;SuyuEtal2010}. In this work our aim is to quantify the
+mass \citep[e.g.,][]{Koopmans2004,SuyuEtal2010}. In this work our aim is to quantify the
 lensing effect of massive objects, regardless of their position along the line
@@
 attempt a reconstruction of the convergence induced by every halo near a
-line of sight. \new{We also need to account for the convergence due to dark structures and
+line of sight. {We also need to account for the convergence due to dark structures and
 the divergence due to voids; we do not model voids or dark structures, but their
@@
 \includegraphics[width=\columnwidth]{figs/cornerplot.eps}
-\caption[Biased?]{The joint distribution of 
-$\kappah$ and $\kappax$, from 100,000 reconstructed lines of
-sight. $\kappah$ traces $\kappax$, but with a positive offset which arises from
-$\kappah$ not accounting for any voids, dark structures or smooth mass
-component. At fixed $\kappah$ the scatter in $\kappax$ grows with $\kappah$.}
+\caption[Biased?]{The conditional distribution of 
+$\kappax$ given $\kappah$, from $10^5$ reconstructed lines of
+sight.
+$\kappah$ was generated from perfect knowledge of halo mass and redshift.
+Solid (dashed) lines show the 68\% (95\%) confidence interval $\kappah$ traces $\kappax$, but with a positive offset which arises from
+$\kappah$ not accounting for any voids or dark structures.
+ At fixed $\kappah$ the scatter in $\kappax$ grows rapidly with $\kappah$.}
 \label{fig:jointkh-k}
@@
 $\kappax$ values, each one drawn from an inferred PDF 
-$P(\kappax|\{\Mhalo,z\}$)
-in one of $10^{5}$ reconstructed lines of sight. 
+$P(\kappax|\kappah)$ in one of $10^{5}$ reconstructed lines of sight. 
 The reconstructions were performed given
 perfect knowledge of halo mass and redshift -- in this case
-the reconstruction recovers the correct convergence.}
+the reconstruction recovers the correct convergence. The reconstruction assumes
+perfect knowledge of the halo mass and redshift.}
 \label{fig:globaldist}
@@
 $10^5$ lines of sight, given different quality of data. Blue:
-spectroscopic redshift for every halo with $i<26$; Purple: 
+spectroscopic redshift for every halo with $i<26$; Red: 
 spectroscopic redshift for every halo with $i<23$, and every halo with $i<24$
-within 1 arcminute; Cyan: spectroscopic redshift for every halo with $i<22$; 
+within 1 arcminute;
 Green: all the objects in the field have only photometric redshifts.}
@@
 \caption{Width of the \infered PDF $\pr(\kappax|\data)$ versus the true
-$\kappax$ along a line of sight. Blue assumes a spectroscopic redshift for
-every halo, whilst green assumes only photometric redshifts. The width of the
+$\kappax$ along a line of sight. Green assumes only photometric redshifts
+whilst red assumes a campaign of targetted spectroscopy. The width of the
 \infered $\pr(\kappah|\data)$ increases with $\kappax$.}
@@
 of sight. The central plot shows sight lines randomly selected from the
-33\% of lines whose P($\kappax$) is most tightly constrained. The right
-hand plot shows only lines of sight with external shear of 0.03 or
+33\% of lines whose P($\kappax$) is most tightly constrained by our model. The right
+hand plot shows only lines of sight with external shear of 0.05 or
 greater.}

### 2012-12-04 doc/paper-lcr.tex
edited Tom's second draft

@@
   Zachary~Greene$^{4}$,
-  Tommaso~Treu$^{4}$\thanks{\packard},}
+  Tommaso~Treu$^{4}$\thanks{\packard},
+  Christopher~D.~Fassnacht$^{5}$,}
 \newauthor{%
-  Christopher~D.~Fassnacht$^{5}$,
   L\'eon~V.~E.~Koopmans$^{6}$,
+  Maru\v{s}a Brada\v{c}$^{5}$,
   Roger~D.~Blandford$^{3}$} 
@@
 such as time delay gravitational lenses or type Ia supernovae are affected by
-weak lensing perturbations by galaxies and groups along the line of sight.
-In time delay gravitational lenses,
-``external convergence,'' $\kappax$, can dominate the uncertainty in the inferred distances.
-In this paper we attempt to reconstruct $\kappax$,
-due to line of sight structure using a simple halo model.
- We use mock catalogues from the Millennium Simulation, and compare
-our reconstructed $\pr(\kappax|\data)$ to ray-traced $\kappax$ truth values: 
-taking into account realistic uncertainties on redshift and stellar masses, we
-typically find that the reconstruction yields a factor of 2 improvement in precision of
-over the global $\pr(\kappax)$. We find that the lowest $\kappax$ lines of sight have the best constrained 
-$\pr(\kappax)$ after applying our reconstruction. We find that selecting systems by the precision with which
-$\kappax$ can be estimated leads to a sample of unbiased
-time delay distance estimates each with 1\% uncertainties due to external convergence effects.
-Photometric data alone is sufficient to pre-select the best lenses and can be done
-before investment in lightcurve monitoring. Preferentially selecting lines of
-sight with high external shear (as might happen in an assembled sample of
-quadruply-imaged time delay lenses) produces time-delay distance estimates with
-typical external convergence uncertainties of 1.8\% but with systematic errors of 0.8\%.
-We suggest areas for the improvement of this general analysis framework that
-should allow yet more accurate cosmological inferences to be made.
+weak lensing perturbations by galaxies and groups along the line of sight. In
+time delay gravitational lenses, ``external convergence,'' $\kappax$, can
+dominate the uncertainty in the inferred distances. In this paper we attempt
+to reconstruct $\kappax$, due to line of sight structure using a simple halo
+model.
+%
+We use mock catalogues from the Millennium Simulation, and calibrate and 
+compare our reconstructed $\pr(\kappax|\data)$ to ray-traced $\kappax$ truth
+values:  taking into account realistic uncertainties on redshift and stellar
+masses, \phil{we find that the reconstruction provides an improvement in
+precision of 50\% over the global $\pr(\kappax)$.} 
+%
+We find that the lowest $\kappax$ lines of sight have the best constrained 
+$\pr(\kappax)$. We find that selecting the third of the systems with the
+highest precision $\kappax$ estimates gives a  sub-sample of unbiased time
+delay distance measurements \phil{with (on average) just} 1\% uncertainty due
+to line of sight external convergence effects. Photometric data alone is
+sufficient to pre-select the best-constrained lines of sight, and can be done
+before investment in lightcurve monitoring. 
+%
+\phil{Conversely, we show that somehow preferentially selecting lines of sight
+with high external shear could, with the reconstruction model presented here,
+induce biases of up to 1\% in time delay distance.}  We suggest areas for the
+improvement of this general analysis framework (including more sophisticated
+treatment of high mass structures) that should allow yet more accurate
+cosmological inferences to be made.
+
 \end{abstract}
@@
 \citet[][]{Oguri+Takahashi2006,Wang+Dai2011},  and for high redshift
-galaxies by \citet{BradacEtal2009}, among others.
-
-Along lines of sight containing strong gravitational lenses, the
-perturbative effects of line of sight mass structure have been found to
-be particularly important, with foreground and background structures
-having a significant effect on the inferred lensing cross-section
-\citep[\eg][]{WongEtal2012} and distance ratios
-\citep[][]{DalalEtal2005}. Indeed, \citet{SuyuEtal2010} found that in
-time delay lens cosmography the so-called ``external convergence''
-$\kappax$ due to mass structures along the (unusually over-dense) line
-of sight to the quadruply-imaged radio source B1608$+$656 was the
-dominant source of uncertainty in their 5\% measurement of the time delay distance. 
-Whilst it is rare for three galaxies to line up well enough for both of
+galaxies by \citet{WyitheEtal2011}, among others.
+
+Along lines of sight containing strong gravitational lenses, the perturbative
+effects of line of sight mass structure have been found to be particularly
+important, with foreground and background structures having a significant
+effect on the inferred lensing cross-section \citep[\eg][]{WongEtal2012} and
+distance ratios \citep[][]{DalalEtal2005}. Indeed, \citet{SuyuEtal2010} found
+that in time delay lens cosmography the so-called ``external convergence''
+$\kappax$ due to mass structures along the (unusually over-dense) line of
+sight to the quadruply-imaged radio source B1608$+$656 had to be included in
+their analysis, and was the dominant source of uncertainty in their 5\%
+measurement of the time  delay distance.  Large samples of time-delay lenses
+are expected to be discovered in the next decade in ground-based optical
+imaging surveys \citep{Oguri+Marshall2010};  the external convergence will
+have to be understood increasingly well in order to prevent its correction
+from dominating the systematic error budget.
+
+While it is rare for three galaxies to line up well enough for both of
 the background sources to be strongly lensed \citep{GavazziEtal2008,CollettEtal2012a}, 
@@
 mass-modelling of the lens, but the convergence is undetectable from the
-image positions, shapes and relative fluxes; this is the famous {\emph{ 
+image positions, shapes and relative fluxes; this is the well-known {\emph{ 
 mass-sheet degeneracy}} \citep[see e.g.][for details]{FalcoEtal1985}.
 
-Large samples
-of time-delay lenses are expected to be discovered in the next decade in
-ground-based optical imaging surveys \citep{Oguri+Marshall2010}: both
-the detectability of these lenses, and the selection of sub-samples of
-them for further observation, could induce a selection function in external
-convergence. External convergence must be included in analysis of time-delay
-lenses else the inferred time-delay distance and cosmology be systematically biased.
-
 Since the mass-sheet degeneracy prevents any estimate of $\kappax$ from the 
-strong lens modelling additional information is required. Weak lensing measurements
+strong lens modelling, additional information is required. Weak lensing measurements
 can been used for rich lines of sight \citep{NakajimaEtal2009, FadelyEtal2009}, but 
@@
 
-For non-lens lines of sight magnification is a more useful quantity than convergence; \citet{GunnarssonEtal2006} used a galaxy halo model combined with simple scaling relations to reconstruct supernovae
-lines of sight and found that the dispersion in
-apparent source brightness due to lensing magnification could be reduced
-by a factor of two.
-Conversely \citet{KarpenkaEtal2012} used the brightness dispersion in type Ia supernovae to infer the parameters of both their galaxy halo model and mass-to-light scaling relation.
-Both \citeauthor{KarpenkaEtal2012} and \citet{JonssonEtal2010} were able to
-detect lensing effects in the supernova data this way.
-
-Large numerical simulations can also be used to estimate global convergence distributions.
- \citet{Holder+Schechter2003} and
-\citet{DalalEtal2005} carried out ray-tracing calculations in N-body
-simulations to estimate the distribution of external shear values. 
-\citet{HilbertEtal2009} performed similar ray-tracing experiments
-through the Millennium Simulation \citep{SpringelEtal2005}, generating a
-predicted $\kappax$ at every position in a simulated sky.
-\citet{HilbertEtal2009} found that after removing the matter on the strong lensing plane
-\MS lines of sight with strong lenses
-were not biased towards high $\kappax$, although selection functions for
-discovering samples of strong lenses were not taken
-into account.
+For lines of sight without strong lenses, magnification is the more relevant
+quantity than convergence; \citet{GunnarssonEtal2006} used a galaxy halo model
+combined with simple scaling relations to reconstruct supernovae lines of
+sight and found that the dispersion in apparent source brightness due to
+lensing magnification could be reduced by a factor of two. Conversely
+\citet{KarpenkaEtal2012} used the brightness dispersion in type Ia supernovae
+to infer the parameters of both their galaxy halo model and mass-to-light
+scaling relation. Both \citeauthor{KarpenkaEtal2012} and
+\citet{JonssonEtal2010} were able to  detect lensing effects in the supernova
+data this way.
+
+Large numerical simulations can also be used to estimate global convergence
+distributions. \citet{Holder+Schechter2003} and \citet{DalalEtal2005} carried
+out ray-tracing calculations in N-body simulations to estimate the
+distribution of external shear values.  \citet{HilbertEtal2009} performed
+similar ray-tracing experiments through the Millennium Simulation
+\citep{SpringelEtal2005}, generating a predicted $\kappax$ at every position
+in a simulated sky. \citet{HilbertEtal2009} found that after removing the
+matter on the strong lensing plane \MS lines of sight with strong lenses were
+not biased towards high $\kappax$, although selection functions for
+discovering samples of strong lenses were not taken into account.
 
@@
 \MS mock catalogues and their associated $\kappax$ values to construct
-$\Pr(\kappax|\data)$. For the most over-dense lines of sight the
-Green et al. results  show a $\sim$20\% improvement over
-number counts alone, but little improvement for less dense lines.
+$\Pr(\kappax|\data)$. For the most over-dense lines of sight their
+results  show a $\sim$20\% improvement over
+number counts alone, but little improvement for less dense ones.
 
@@
 construct the PDF $\Pr(\kappax|\data)$ for that field. We then emulate
-the combination of many such PDFs to quantify the residual biases that
-would be translated to the global (including cosmological) parameters.
+the combination of many such PDFs to quantify the residual bias that
+would be translated to the global (including cosmological) parameters, 
+\phil{if left unaccounted for.}
 In doing so, we aim to answer the following questions:
@@
 any photometric object catalogue, but they will contribute convergence at
-some level. How much of the total convergence comes from visible
+some level. How much of the total line of sight 
+convergence comes from visible
 galaxies, and how much effect do dark structures and voids have?
 
-\item Can the true convergence be recovered from a calibrated halo model
-reconstruction? What scatter and residual bias are induced by the
+\item Can the true line of sight convergence be recovered from a calibrated
+halo model reconstruction? What scatter and residual bias are induced by the
 reconstruction process, and how might these be reduced in the future?
 
-\item We have some choices to make when planning follow-up observations
-of interesting sight-lines. How should we select objects to achieve the
-highest accuracy convergence reconstruction? Can such a selection be
-made robustly, using the reconstruction results?
+\item Both the detectability of lenses, and the selection of sub-samples of
+them for further observation, could potentially induce a selection bias in
+external convergence. How should we select objects to achieve the highest
+accuracy convergence reconstruction? Can such a selection be made robustly,
+using the reconstruction results?
 
@@
 dark energy density of the Universe in units of the critical density.
-.%\citep[e.g.\ ][]{KomEtal09}.
-
-\comments{
-When inferring global quantities
-(such as the cosmological parameters), combining the results from a
-large number of independent objects will tend to reduce the uncertainty
-due to external convergence \citep[\eg][]{Holz+Linder2005}, unless the lines of sight are not representative of the global population.
-If the line of sight selection function is not correctly modelled some residual systematic error will
-remain even as the statistical uncertainty decreases. A selection function may be introduced either at the object
-detection stage, or later on when making decisions about which objects
-to study further. Large samples
-of lenses are expected to be discovered in the next decade in
-ground-based optical imaging surveys \citep{Oguri+Marshall2010}: both
-the detectability of these lenses,  and the selection of sub-samples of
-them for further observation, could be sensitive to the external
-convergence.
-
-Several attempts have been made to do better than simply constructing a
-large sample of objects, and averaging over the resulting convergence
-distribution. The weak lensing effect can be detected observationally 
-by measuring the
-small distortions it induces on the images of many background galaxies
-in the field \citep[see e.g.][for a review]{Schneider2006}. 
-\citet{NakajimaEtal2009} used deep HST imaging to infer $\kappax=0.17\pm0.06$ from weak lensing measurements; this measurement was used in the time delay distance
-measurement of \citet{FadelyEtal2009}. A precise weak lensing estimate of $\kappax$ can only be made if the number density of of weakly lensed, measurable galaxies is high.
-}
+%\citep[e.g.\ ][]{KomEtal09}.
+
+\comments{ When inferring global quantities (such as the cosmological
+parameters), combining the results from a large number of independent objects
+will tend to reduce the uncertainty due to external convergence
+\citep[\eg][]{Holz+Linder2005}, unless the lines of sight are not
+representative of the global population. If the line of sight selection
+function is not correctly modelled some residual systematic error will remain
+even as the statistical uncertainty decreases. A selection function may be
+introduced either at the object detection stage, or later on when making
+decisions about which objects to study further. Large samples of lenses are
+expected to be discovered in the next decade in ground-based optical imaging
+surveys \citep{Oguri+Marshall2010}: both the detectability of these lenses, 
+and the selection of sub-samples of them for further observation, could be
+sensitive to the external convergence.
+
+Several attempts have been made to do better than simply constructing a large
+sample of objects, and averaging over the resulting convergence distribution.
+The weak lensing effect can be detected observationally  by measuring the
+small distortions it induces on the images of many background galaxies in the
+field \citep[see e.g.][for a review]{Schneider2006}.  \citet{NakajimaEtal2009}
+used deep HST imaging to infer $\kappax=0.17\pm0.06$ from weak lensing
+measurements; this measurement was used in the time delay distance measurement
+of \citet{FadelyEtal2009}. A precise weak lensing estimate of $\kappax$ can
+only be made if the number density of of weakly lensed, measurable galaxies is
+high. }
 
@@
 given our available data $\data$, $\Pr(\xkappa|\data)$}
+
 % PHIL's REVIEWS OF THE LITERATURE
@@
 apparent source brightness due to lensing magnification could be reduced
-by a factor of two.
+by a factor of two.}
 %
-\citet{WongEtal2011} estimated the PDF for the external shear,
+\comments{\citet{WongEtal2011} estimated the PDF for the external shear,
 $\Pr(\gammax|\data)$ from their survey data, running similar Monte Carlo
@@
 modelling and the strong lens modelling as the cause of these
-discrepancies.
+discrepancies.}
 %
-\citet{KarpenkaEtal2012} used a halo model to predict deterministically 
+\comments{\citet{KarpenkaEtal2012} used a halo model to predict deterministically 
 the magnification due to
@@
 NFW profiles. Both groups were able to 
-detect lensing effects in the supernova data this way.
-}
+detect lensing effects in the supernova data this way.}
 
@@
 {\it Top row, right:} The individual $\kappax$ contributions of
-each halo, assuming a \citet{BMO} profile and the \citet{Neto2007}
+each halo, assuming a \citet{BMO} truncated NFW 
+profile and the \citet{Neto2007}
 mass-concentration relation. Comparison of
-this panel and the centre panel reveals the relative importance of
+this panel and the centre panel illustrates the relative importance of
 proximity to the line of sight.
@@
 \label{sec:theory}
+
 \comments{
@@
 to relativistic and geometric effects. The difference in optical path length
-causes a time-delay between the light curves of each image. \citeauthor{FalcoEtal1985}
-showed that the presence of additional matter (in the form of a mass-sheet)
-along the line of sight has no observable effect except to rescale the time-delays.
-As such, it is necessary to include $\kappax$ in the lens modelling, if
-cosmological parameters are to be estimated accurately and precisely from
-observed time delays \citep{SuyuEtal2010}.
+causes a time-delay between the light curves of each image.
+\citet{FalcoEtal1985} showed that the presence of additional matter (in the
+form of a mass-sheet) along the line of sight has no observable effect except
+to rescale the time-delays. As such, it is necessary to include $\kappax$ in
+the lens modelling, if cosmological parameters are to be estimated accurately
+and precisely from observed time delays \citep{SuyuEtal2010}.
 
@@
 
-Mass distributions that are
-physically associated with the lens galaxy will affect the stellar dynamics of
-the lens galaxy, so that dynamical observations can break the internal
-mass-sheet degeneracy by providing an additional estimate of the lens galaxy's
-mass \citep[e.g.,][]{Koopmans2004,SuyuEtal2010}. In this work our aim is to quantify the
+Mass distributions that are physically associated with the lens galaxy will
+affect the stellar dynamics of the lens galaxy, so that dynamical observations
+can break the internal mass-sheet degeneracy by providing an additional
+estimate of the lens galaxy's mass
+\citep[e.g.,][]{Koopmans2004,SuyuEtal2010}.  Our aim is to quantify the
 lensing effect of massive objects, regardless of their position along the line
-of sight.
+of sight. \phil{However, in this paper we restrict ourselves to reconstructing
+the line of sight portion of the mass distribution in any given field, which
+allows us to work in the weak lensing regime. Treatment of sightlines
+containing strong lensing events, and the impact of physically-associated mass
+distributions on both the strong lensing and stellar dynamical effects are
+postponed to further work.}
 
@@
 \citet{HilbertEtal2009} calculated the lensing convergence using the
-``lightcone'' dark matter only 
-output of the \MS, providing 1.7 degree square 
-mock sky maps of this
-quantity. In this process, the dark matter density from the simulation
-was projected onto a set of lens planes at discrete redshifts,
-adaptively gridded and smoothed, and then the second derivatives of the 
-lensing potential required for the components of the magnification
-matrix were computed using a multiple lens plane ray tracing algorithm.
-The first order approximation to this algorithm \citep[equation 17
+``lightcone'' dark matter only  output of the \MS, providing 1.7 degree
+square  mock sky maps of this quantity. In this process, the dark matter
+density from the simulation was projected onto a set of lens planes at
+discrete redshifts, adaptively gridded and smoothed, and then the second
+derivatives of the  lensing potential required for the components of the
+magnification matrix were computed using a multiple lens plane ray tracing
+algorithm. The first order approximation to this algorithm \citep[equation 17
 of][]{HilbertEtal2009} gives the total convergence at a given sky
-position~$\bmath{\theta}$ as the simple summation of the surface density
-in each lens plane, weighted by the inverse critical surface density
-$\Sigma_{\rm cr}$ for that plane's redshift:
+position~$\bmath{\theta}$ as the simple summation of the surface density in
+each lens plane, weighted by the inverse critical surface density $\Sigma_{\rm
+cr}$ for that plane's redshift:
 \be
@@
 
+\comment{PJM: This means our sightlines are not typical of strong lenses, because they
+don't include the local overdense region typically found near massive lens
+galaxies. Our lines of sight have typical mass distributions for a lens line
+of sight {\it after excision of the lens plane}. I have tried to explain
+this above.}
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
 
-We construct mock photometric galaxy catalogues by selecting all \MS
-galaxies within a circular aperture of a given angular radius centred on
-the line of sight position, with apparent $i$-band magnitude brighter
+We construct mock photometric galaxy catalogues by selecting all \MS galaxies
+within a circular aperture of a given angular radius centred on each randomly
+selected line of sight position, with apparent $i$-band magnitude brighter
 than a given limit. The parent catalogue, from \citet{HilbertEtal2011},
-contains galaxy positions and magnitudes, all of which include lensing
-effects (deflections and magnifications). We also have access to the
-underlying galaxy halo masses and redshifts, which we will use to
-calibrate the reconstruction, and also to explore any sources of bias
-and scatter. Since the true convergence is that of only the dark matter,
-we focus on reconstructing the dark matter halos alone. Our model for
-doing this is outlined in the next section.
+contains galaxy positions and magnitudes, all of which include lensing effects
+(deflections and magnifications). We also have access to the underlying galaxy
+halo masses and redshifts, which we will use to calibrate the reconstruction,
+and also to explore any sources of bias and scatter. Since the true
+convergence is that of only the dark matter, we focus on reconstructing the
+dark matter halos alone. Our model for doing this is outlined in the next
+section.
 
@@
 
-We require a method for estimating the
-convergence at any point on the sky, given a catalogue of observed
-galaxy properties such as positions, brightnesses, colours, and
-possibly stellar masses and redshifts, for every galaxy in the field of
-the lens, down to some magnitude limit. Since we cannot observe the
-surface mass density of each halo directly, we need some way of
-estimating the mass of each halo in the catalogue, so that we can compute
-its contribution to the total $\kappax$ along the line of sight \citep[as
-in \eg][]{GunnarssonEtal2006,WongEtal2011,KarpenkaEtal2012}. 
-This mass assignment recipe
-will be uncertain, but can be calibrated with cosmological simulations, which
-represent a significant additional source of information to what is present in
-the data.
-
-Transforming an observed photometric galaxy catalogue into a 
-catalogue of halo masses, positions, and redshifts, will enable us to
-attempt a reconstruction of the convergence induced by every halo near a
-line of sight. {We also need to account for the convergence due to dark structures and
-the divergence due to voids; we do not model voids or dark structures, but their
-effects are included statistically by calibration the the convergence in halos,
-$\kappah$, against the ray-traced convergence, $\kappax$, for \MS lines of sight.}
+We require a method for estimating the convergence at any point on the sky,
+given a catalogue of observed galaxy properties such as positions,
+brightnesses, colours, and possibly stellar masses and redshifts, for every
+galaxy in the field of the lens, down to some magnitude limit. Since we cannot
+observe the surface mass density of each halo directly, we need some way of
+estimating the mass of each halo in the catalogue, so that we can compute its
+contribution to the total $\kappax$ along the line of sight \citep[as in
+\eg][]{GunnarssonEtal2006,WongEtal2011,KarpenkaEtal2012}.  This mass
+assignment recipe will be uncertain, and also incomplete, but it can be
+calibrated with cosmological simulations, which represent a significant
+additional source of information to what is present in the data.
+
+Transforming an observed photometric galaxy catalogue into a  catalogue of
+halo masses, positions, and redshifts will enable us to attempt a
+reconstruction of the convergence induced by every halo near a line of sight. 
+We also need to account for the convergence due to dark structures and the
+divergence due to voids; we do not model voids or dark structures, but their
+effects are included statistically by calibrating the convergence in
+halos, $\kappah$, against the ray-traced convergence, $\kappax$, for \MS lines
+of sight.
 
@@
 halos are well-approximated by NFW profiles 
-
-\citep{NFW}, with a density
-profile given by
+\citep{NFW}. We assume each halo to have a spherical mass distribution with 
+density given by
 \be\label{eq:rhonfw}
@@
 \frac{\rho_0}{\left(r/r_{s}\right)
-\left(1+r/r_{s}\right)^{2}},
+\left(1+r/r_{s}\right)^{2}}.
 \ee
-where $r_{s}$ is a characteristic radius of the cluster, representing where
-the density slope transitions from $r^{-1}$ to $r^{-3}$. This radius is related
-to the virial radius of the halo by $r_{s}~=~r_{200}/c$, where $c$ is the concentration parameter, which can be estimated from the halo's mass,
-using a mass--concentration relation. Typically more massive halos are less concentrated,
-but there is some scatter; we use the relation of \citet{Neto2007} to estimate $c$
-from the mass enclosed within $r_{200}$, which we denote as $M_{200}$. We find our results do not change if the \citet{MaccioEtal2008} Mass--concentration relation is used instead.
+Here, $r_{s}$ is a characteristic scale 
+radius of the cluster, representing the point where
+the density slope transitions from $r^{-1}$ to $r^{-3}$. This radius is
+related to the virial radius of the halo by $r_{s}~=~r_{200}/c$, where $c$ is
+the concentration parameter, which can be estimated from the halo's mass,
+using a mass--concentration relation. Typically more massive halos are less
+concentrated, but there is some scatter; we use the relation of
+\citet{Neto2007} to estimate $c$ from the mass enclosed within $r_{200}$,
+which we denote as $M_{200}$. We find our results do not change if the
+\citet{MaccioEtal2008} mass--concentration relation is used instead.
 
@@
 
-Each halo in our catalogue then contributes to
+Many studies have shown that galaxies have total mass density profiles that
+are approximately isothermal in their inner regions
+\citep[\eg][]{AugerEtal2010} due to the more concentrated stellar mass
+component; however, at radii of tens of kpc (tens of arcsec), we expect the
+halo density profile to be dark matter dominated, and fall off faster than
+$r^{-2}$. This has been confirmed by galaxy-galaxy weak lensing measurements 
+\citep[\eg][]{Mandelbaum,Leauthaud}. We note that the two halo term that
+dominates the galaxy-galaxy lensing signal at large radii is explicitly taken
+into account in our model, where every galaxy is assigned a dark matter halo.
+
+Each halo in our catalogue contributes to
 the line of sight convergence by
@@
 distribution from the simulation. In the limiting  case of very poor
-photometric data, $\pr(\kappah|\data)$ then defaults to this distribution.
+photometric data, $\pr(\kappah|\data)$ then defaults to this distribution, as
+required.
 
@@
 
-% TEC: yes it's valid. It only really ties us to the halo mass function of the simulation. It's probably tied at the same level as the "global P(\kappa) as derived from Stefan's ray-tracing"
+% TEC: yes it's valid. It only really ties us to the halo mass function of the
+% simulation. It's probably tied at the same level as the "global P(\kappa) as
+% derived from Stefan's ray-tracing"
 
@@
 
-Our halo model accounts for the convergence contribution of density perturbations that can
-be associated with light. Filaments and dark substructures contribute additional convergence
-whilst voids contribute a divergence; these structures must be included to produce an unbiased estimate of $\kappax$
-in principle the absence of galaxies implies something about
-the presence a void, but we do not currently attempt to use this information. Neglecting voids
-would lead to a heavily biased estimate of $\kappax$, since the halo model's $\kappah$
-can only be positive. It is difficult to correct for unseen structure problem
-since we do not have a good model for its density structure.
-
-The solution we present here is to calibrate the relationship between halo
-convergence $\kappah$ and underlying convergence $\kappax$ (as calculated
-during full ray tracing) using the simulations themselves.
-The halo modelling procedure outlined in \Sref{sec:model:halos} allows 
-us to estimate 
-the convergence due to halos given observations of 
-mass, redshift and position,
-$\pr(\kappah|\mathcal{D})$, but what we are interested in is the total convergence
-along the line of sight $\pr(\kappax|\mathcal{D})$. We can obtain this by
-considering the expression:
+Our halo model accounts for the convergence contribution of density
+perturbations that can be associated with light. Filaments and dark
+substructures contribute additional convergence, while voids contribute a
+divergence; these structures must be included to produce an unbiased estimate
+of $\kappax$. In particular, neglecting voids would lead to a heavily biased
+estimate of $\kappax$, since the halo model's $\kappah$ can only be positive.
+In principle the absence of galaxies implies something about the presence a
+void, but we do not currently attempt to use this information. In general, it
+is difficult to account for the unseen mass, since we do not have a good model
+for its density structure.
+
+The solution we present here is to calibrate the relationship between the halo
+convergence $\kappah$ and the overall convergence $\kappax$ (as would be
+calculated by ray tracing through the full density field)  using the
+simulations themselves. The halo modelling procedure outlined in
+\Sref{sec:model:halos} allows  us to estimate  the convergence due to halos
+given observations of  mass, redshift and position,
+$\pr(\kappah|\data)$, but what we are interested in is the total
+convergence along the line of sight $\pr(\kappax|\data)$. We can obtain
+this by considering the expression: 
 \begin{equation} 
-\Pr(\kappax|\mathcal{D}) = \int \dee\kappah 
-   \Pr(\kappax|\kappah,\mathcal{D}) \Pr(\kappah|\mathcal{D})
+\Pr(\kappax|\data) = 
+   \int \dee\kappah  \Pr(\kappax|\kappah,\data) \Pr(\kappah|\data)
    \label{eq:kappaconv}
@@
 $\kappah$, to the true convergence, $\kappax$. This conditional distribution
-can be constructed from the Millennium Simulation catalogues, by computing
-$\kappah$ for each selected line and accumulating $\kappah$ and $\kappax$ along a large number of
-such lines of
-sight to  characterize $\Pr(\kappax|\kappah)$.
+can be constructed from the \MS catalogues, by computing
+$\kappah$ from the true halo masses and redshifts 
+along each selected line of sight, and then
+accumulating $\kappah$ and $\kappax$
+along a large number of such sightlines. 
 For any given line of sight we can then estimate
-$\pr(\kappah|\data)$ as described above, and then
-multiply it by $\Pr(\kappax|\kappah)$ and integrate out the intermediate
-parameter $\kappah$.
-
-However, given an uncertain stellar mass to halo mass conversion,
-$\pr(\kappah|\mathcal{D}_1)$ can be shifted relative to
-$\pr(\kappah|\mathcal{D}_2)$ given perfect knowledge of the halo mass; this is because of the asymmetry in the
-conversion from stellar mass through halo mass into $\kappah$. A long tail of
-high halo masses gives rise to a tendency to overestimate $\kappah$.
-If this shift is ignored, the resulting $\Pr(\kappax|\data)$ will be 
-biased towards high values of $\kappax$ if $\Pr(\kappax|\kappah)$ is constructed from lines
-of sight with perfect knowledge of the halo mass. Ideally one wants to find the $\kappax$ distribution
-of all calibration lines of sight with a $\pr(\kappah|\data)$ that is identical to $\pr(\kappah|\data)$ for the real line of sight
-{\it given the same data quality}; this is impossible given a finite number of calibration lines of sight.
-We compromise on the similarity of our real line of sight to the calibration lines of sight by 
-selecting considering only the median of the $\pr(\kappah|\data)$ distributions.
+$\pr(\kappah|\data)$ as described above, and then multiply it by
+$\Pr(\kappax|\kappah)$ and integrate out the intermediate parameter
+$\kappah$.
+
+\phil{However, if the conversion between stellar mass and halo mass is very
+uncertain, $\pr(\kappah|\data)$ is shifted relative to what it would
+have been given perfect knowledge of the halo masses.  This is because the
+conversion from stellar mass to halo mass and into $\kappah$ is highly
+asymmetric: a long tail of high halo masses gives rise to a tendency to
+overestimate $\kappah$. If this shift is ignored, the resulting
+$\Pr(\kappax|\data)$ will be systematically biased towards high values of
+$\kappax$. Instead, we need the  distribution of $\kappax$ from all
+calibration lines of sight that have a $\pr(\kappah|\data)$ that is identical
+to the $\pr(\kappah|\data)$ for the real line of sight {\it given the same
+data quality}; however, we found this approach unfeasible  given our finite
+number of calibration lines of sight. A working compromise is to use 
+the median of the $\pr(\kappah|\data)$ distributions in the calibration.}
 
@@
 estimate $\pr(\kappah|\data)$, and extract its median. Accumulating
-these samples and their corresponding true values of $\kappax$, we can form the 
+these median values $\kappah^{\rm med}$ and 
+their corresponding true values of $\kappax$, we can form the 
 conditional distribution $\pr(\kappax|\kappah^{\rm med})$. 
-Then, when inferring $\kappax$ from an observed photometric catalogue, we 
+Then, to infer $\kappax$ from an observed photometric catalogue, we 
 estimate $\pr(\kappah|\data)$ 
 using the halo model, compute the median value 
-$\kappa_{\rm h,obs}^{\rm med}$, and then use an alternative
+$\kappa_{\rm h,obs}^{\rm med}$, and then use a modified
 version of 
@@
 \bea
-\Pr(\kappax|\kappah^{\rm med},\mathcal{D}) &=& \int \dee\kappah^{\rm med} 
-   \Pr(\kappax|\kappah^{\rm med},\mathcal{D}) \Pr(\kappah^{\rm med}|\mathcal{D}) \notag \\
+\Pr(\kappax|\kappah^{\rm med},\data) &=& \int \dee\kappah^{\rm med} 
+   \Pr(\kappax|\kappah^{\rm med},\data) \Pr(\kappah^{\rm med}|\data) \notag \\
 \label{eq:calkappaconv}   
 \eea
-Because we only have a finite number of calibration lines of sight, we use all calibration
-lines of sight with $kappah_{\rm calibration}^{\rm med} = kappah^{\rm med}\pm0.003$ to form
-$\Pr(\kappax|\kappah^{\rm med},\mathcal{D})$, with each calibration line weighted
-equally.
-
-The procedure of reducing the full PDF for $\kappah$ to its median increases the 
-importance of the simulation choice: the simulation needs to be a similar as possible
-to the real universe or there is a possibility of systematic errors. 
+\phil{This integral is trivial, since $\Pr(\kappah^{\rm med}|\data)$ is
+a delta function centred on the median of the inferred PDF for $\kappah$.
+However,}
+because we only have a finite number of calibration lines of sight, we use all
+calibration lines of sight with $\kappa_{\rm h,cal}^{\rm med} =
+\kappah^{\rm med}\pm0.003$ to form $\Pr(\kappax|\kappah^{\rm
+med},\data)$.
+\comments{, with each calibration sightline weighted equally. PJM: why is
+this? Surely one should weight by the value of the Gaussian function implied
+by that ``$\pm 0.003$''?}
+
+This procedure of reducing the full PDF for $\kappah$ to its median increases
+the importance of the realism of the simulation: the simulation needs to be a
+similar as possible to the real universe or there is a possibility of
+systematic errors. \phil{On the other hand, making use of all the information
+in the photometric catalogue yields $\kappax$ estimates of increased
+precision, as we shall see.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Results: Perfect Halo Data}
@@
 We now put the reconstruction \proceedure outlined above into practice, first
-inferring $\kappax$ from $\kappah$ in the case of hypothetical galaxy catalogues
-with noiseless redshifts and halo masses. The reason for doing this is to
-check the validity of the calibration process, and then also to  investigate
-the primary sources of the convergence. It will also provide us with a measure
-of the intrinsic uncertainty introduced by our assumption of all halos being
-spherically-symmetric truncated NFW halos with Neto et al concentration--mass
-relation.
+inferring $\kappax$ from $\kappah$ in the case of hypothetical galaxy
+catalogues with noiseless redshifts and halo masses. The reason for doing this
+is to check the validity of the calibration process, and then also to 
+investigate the primary sources of the convergence. It will also provide us
+with a measure of the intrinsic uncertainty introduced by our assumption of
+all illuminated halos being spherically-symmetric truncated NFW halos with
+Neto et al concentration--mass relation.
 
@@
 
-\Fref{fig:jointkh-k} shows the joint distribution of $\kappah$ and $\kappax$
-values for 100,000 randomly selected \MS lines of sight, assuming noise-free
-halo masses and redshifts. In this case, the PDF $\pr(\kappah|\data)$ is a
-delta function: to read off $\pr(\kappax|\data)$ we must take a thin horizontal
-slice across this joint distribution. Note that the joint PDF plotted in this
-figure is the product of  the conditional distribution that we need for
-calibration, and also the prior PDF for $\kappah$ that we need to ensure that
-the global distribution of $\kappah$ values is defaulted to in the case of
-poor observational data. At fixed $\kappah$ we find in \Fref{fig:jointkh-k}
-that the scatter in $\kappax$ grows with $\kappah$; our reconstruction is
-better at reproducing under-dense lines of sight than over-dense lines of sight.
-The effect of ignoring voids and the smooth mass component is evident in this
-plot: $\kappah$ is significantly higher than $\kappax$, at any given $\kappax$
-value. Multiplying by $\pr(\kappah|\data)$ and integrating over $\kappah$
-gives a PDF for $\kappax$ centred at the correct place, by construction.
-
+\Fref{fig:jointkh-k} shows the conditional distribution of $\kappax$ given 
+$\kappah$, derived from $10^5$ randomly selected \MS lines of sight
+and assuming noise-free halo masses and redshifts. 
+\phil{(In this case, $\kappah^{\rm med} = \kappah$, since 
+$\pr(\kappah|\data)$ is a delta function)}.
+% In this case, the PDF $\pr(\kappah|\data)$ is a delta function: we can read
+% off  $\pr(\kappax|\data)$ just by taking a thin vertical slice through this 
+% distribution. 
+% Note that the joint PDF plotted in this figure is the product
+% of  the conditional distribution that we need for calibration, and also the
+% prior PDF for $\kappah$ that we need to ensure that the global distribution of
+% $\kappah$ values is defaulted to in the case of poor observational data. 
+At fixed $\kappah$ we find in \Fref{fig:jointkh-k} that the scatter in 
+$\kappax$
+grows with $\kappah$; our reconstruction is better at reproducing under-dense
+lines of sight than over-dense lines of sight. The effect of ignoring voids
+and the smooth mass component is evident in this plot: $\kappah$ is
+significantly higher than $\kappax$, at any given $\kappax$ value. 
+\phil{Conditioning on $\kappah$ gives a PDF for
+$\kappax$ centred at the correct place, by construction.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
 \caption[Biased?]{The conditional distribution of 
-$\kappax$ given $\kappah$, from $10^5$ reconstructed lines of
-sight.
-$\kappah$ was generated from perfect knowledge of halo mass and redshift.
-Solid (dashed) lines show the 68\% (95\%) confidence interval $\kappah$ traces $\kappax$, but with a positive offset which arises from
+$\kappax$ given $\kappah$, in the case where  
+we have perfect knowledge of halo mass and redshift.
+$10^5$ reconstructed lines of
+sight were used to make this plot. 
+Solid (dashed) lines enclose 68\% (95\%) of the conditional probability.
+$\kappah$ traces $\kappax$, but with a positive offset which arises from
 $\kappah$ not accounting for any voids or dark structures.
- At fixed $\kappah$ the scatter in $\kappax$ grows rapidly with $\kappah$.}
+At fixed $\kappah$ the scatter in $\kappax$ grows rapidly with $\kappah$.
+\flag{Can you plot a $y=x$ line to show the correction being made, please?}}
 \label{fig:jointkh-k}
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
 \includegraphics[width=\columnwidth]{figs/globaldist.eps}
-\caption[magcut]{Recovering the global $\pr(\kappax)$, shown in red, 
-from $10^{5}$ ray-traced lines of
-sight. The black curve shows a histogram of 
-sample reconstructed 
-$\kappax$ values, each one drawn from an inferred PDF 
-$P(\kappax|\kappah)$ in one of $10^{5}$ reconstructed lines of sight. 
-The reconstructions were performed given
-perfect knowledge of halo mass and redshift -- in this case
-the reconstruction recovers the correct convergence. The reconstruction assumes
-perfect knowledge of the halo mass and redshift.}
+\caption[magcut]{Recovering the global $\pr(\kappax)$ (shown in red). The
+black curve shows a histogram of  inferred  $\kappax$ values from $10^{5}$
+reconstructed lines of sight.  The reconstructions were performed given
+perfect knowledge of halo mass and redshift -- in this case the reconstruction
+recovers the correct convergence.}
 \label{fig:globaldist}
 \end{figure}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure*}
@@
 \end{figure*}
-
-In this section, let us define the ``bias'' of the reconstruction of a given
-line of sight as the difference between the expectation value of $\kappax$ over
-the inferred PDF $\pr(\kappax|\data)$ and the known true value $\kappax^{\mathrm{true}}$.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Let us define the ``bias'' of the reconstruction of a given line of sight as
+the difference between the expectation value of $\kappax$ over its posterior
+PDF $\pr(\kappax|\data)$ and the known true value $\kappax^{\mathrm{true}}$.
 Let us also define the ``width,'' $\sigma_{\kappa}$, to be half the width of
@@
 
-In an ensemble of $10^{5}$ reconstructed lines of sight, we find the the mean
-bias to be $-9.5\times 10^{-6}$, and the mean width to be 0.01. This is
-approximately 1.8 times smaller than the width of the global $\pr(\kappax)$. 
-We find that our inferred $\kappax$ PDFs are consistent with the global
-$\kappax$ distribution; Figure \ref{fig:globaldist} shows that sampling from
-$\pr(\kappax|\data)$ in $10^{5}$ reconstructed lines of sight produces a
-distribution of $\kappax$ values over the sky identical to the global
-$\pr(\kappax)$. Given perfect knowledge of halo mass and redshift, the
-calibration \proceedure provides an unbiased estimate of $\kappax$ that is
-$\sim$2 times as precise as using the global $\pr(\kappax)$.
+In an ensemble of $10^{5}$ reconstructed lines of sight, we find the mean bias
+to be $-1\times 10^{-5}$, and the mean width to be 0.01. This is approximately
+1.8 times smaller than the width of the global $\pr(\kappax)$.  We find that
+our inferred $\kappax$ PDFs are consistent with the global $\kappax$
+distribution; \Fref{fig:globaldist} shows that sampling from the
+$\pr(\kappax|\data)$ inferred from reconstructions of  $10^{5}$ lines of
+sight  produces a distribution of $\kappax$ values over the sky identical to
+the global $\pr(\kappax)$. Given perfect knowledge of halo mass and redshift
+then, the calibration \proceedure provides an unbiased estimate of $\kappax$
+that is $1.8$ times as precise as using the global $\pr(\kappax)$. 
+\phil{This is the maximum precision we can obtain using the current calibrated
+halo model.}
 
@@
 
-Before investigating the uncertainties caused by imperfect knowledge of halo
-mass and redshift, we investigate the uncertainties induced by a limits on the
+Before investigating the impact of imperfect knowledge of halo
+mass and redshift, we investigate the uncertainties induced by limits on the
 magnitude of the observed galaxy sample, and on the field of view. The halos
@@
 of projected distance from the line of sight, magnitude and redshift. We find
-that most of the convergence comes from halos whose galaxies are close to the
-line of sight.  Over half of the  convergence typically comes from halos
-within 30 arcseconds of the line of sight; by 2 arcminutes, this fraction is
-85\%. The contribution from halos beyond 2 arcminutes is relatively constant
-at a contribution of 0.008$\pm$0.003. We find that ignoring halos beyond 2
-arcminutes has no effect on the precision of the reconstruction; this is shown
-in \Fref{fig:radcut}. As a function of magnitude, we find that $\kappah$
-is dominated by objects with magnitudes between $i=18$ and $i=24$. Objects
-brighter than $i=18$ are either too rare, or too close to the observer, to
-make a significant contribution to the convergence. Objects fainter than
-$i=24$ are too small to be important, unless they are extremely close to the
-line of sight, but we find that including halos fainter than $i=24$ does not
-improve the reconstruction.  \Fref{fig:magcut} shows the scatter on
-$\kappah-\kappax$ (where $\kappah$ is shifted so that its mean is zero) as a
-function of reconstruction magnitude limit. We do
-not expect a deeper survey to decrease the size of the uncertainty in mapping
+that most of the convergence comes from halos close to the line of sight. 
+Over half of the  convergence typically comes from halos within 30 arcseconds
+of the line of sight; by 2 arcminutes, this fraction is 85\%. The contribution
+from halos beyond 2 arcminutes is relatively constant at a contribution of
+0.008$\pm$0.003. We find that ignoring halos beyond 2 arcminutes has no effect
+on the precision of the reconstruction; this is shown in \Fref{fig:radcut}. As
+a function of magnitude, we find that $\kappah$ is dominated by objects with
+magnitudes between $i=18$ and $i=24$. Objects brighter than $i=18$ are either
+too rare, or too close to the observer, to make a significant contribution to
+the convergence. Objects fainter than $i=24$ are too small to be important,
+unless they are extremely close to the line of sight, but we find that
+including halos fainter than $i=24$ does not improve the reconstruction. 
+\Fref{fig:magcut} shows the scatter on $\kappah-\kappax$ (where $\kappah$ is
+shifted so that its mean is zero, \phil{to emulate the effect of the eventual
+calibration}) as a function of reconstruction magnitude limit. We do not
+expect a deeper survey to decrease the size of the uncertainty in mapping
 $\kappah$ onto $\kappax$. Halos at all redshifts out to the source redshift
-(1.4, here) contribute to the convergence, but the largest contribution comes from
-halos with $z \sim z_{\rm source}/2$.
-
+(1.4, here) contribute to the convergence, but the largest contribution comes
+from halos with $z \sim z_{\rm source}/2$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
 reconstruction. $\kappah$ has been shifted such that
-$\left\langle\kappah\right\rangle=0$. The majority of the constraining power
-comes from reconstructing halos with magnitudes between $18<i<24$.}
+$\left\langle\kappah\right\rangle=0$ \phil{to emulate the effect of the
+eventual calibration}. 
+The majority of the constraining power
+comes from reconstructing halos within 2~arcmin of the line of sight.}
 \label{fig:radcut}
 \end{figure}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
 reconstruction. $\kappah$ has been shifted such that
-$\left\langle\kappah\right\rangle=0$. The majority of the constraining power
+$\left\langle\kappah\right\rangle=0$ \phil{to emulate the effect of the
+eventual calibration}. The majority of the constraining power
 comes from reconstructing halos with magnitudes between $18<i<24$.}
@@
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-As described in \Sref{sec:model:halos}, in this work we infer halo masses
-given measurements of stellar mass. We will investigate two main sources of
-uncertainty: inferring halo mass given observed stellar mass, and placing halos at
-the wrong redshift due to photometric redshift uncertainty. Much work has already
-focused on using photometric colours to infer stellar mass
-\citep[\eg][]{AugerEtal2009} and redshifts \citep[\eg][]{BPZ}: we will
-estimate the likely uncertainties on stellar mass and redshift based on this
-work.
+\flag{Should we show the relevant calibration plots, analogous to Figure 2?
+Seems a bit odd to give Figure 2 but not illustrate the {\it actual
+calibration procedure we follow on real data}... Maybe we could make one that
+had the conditional distribution for each data quality?}
+
+As described in \Sref{sec:model:halos}, in this work we attempt to  infer halo
+masses from measurements of stellar mass. We will investigate two main sources
+of uncertainty: the stellar masses themselves, and placing halos at
+photometric redshifts. Much work has already focused on using photometric
+colours to infer stellar mass \citep[\eg][]{AugerEtal2009} and redshifts
+\citep[\eg][]{BPZ}: we will estimate the likely uncertainties on stellar mass
+and redshift based on this work.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 
@@
 
-While the \MS catalogues do already contain stellar masses for each galaxy, we
-find that these are not well behaved at the low mass end due to unreasonably high dark matter stripping from satellite halos. We also wanted to be able to perform the functional test of
-trying to recover the convergence having assumed the correct stellar
-mass--halo mass relation. For these reasons, we assign a new stellar mass to
-each halo in the \MS catalogues, according to the stellar mass--halo mass
-relation of \citet{BehrooziEtal2010}. From this true  stellar mass we
-simulate an observed stellar mass by drawing a sample from 
-$\pr(\log{M^{*}_{\rm obs}}|\log{M^{*}_{\rm true}})$ which we take to be a
-Gaussian of width $\sigma_{M_*}$ centred on $\log(M*_{\mathrm {true}})$. Where
-a spectroscopic redshift exists stellar masses can be estimated with typical
-uncertainties of 0.15 dex \citep{AugerEtal2009}; however with photometric
-redshifts stellar mass uncertainties are typically three times as large. We
-use $\sigma_{M_*}=0.15$ dex for halos with a spectroscopic redshift and
-$\sigma_{M_*}=0.45$ dex otherwise. For photometric redshift uncertainties we draw a
-redshift from $\pr(z_{\rm true}|z_{\rm obs})$ which we take to be a Gaussian
-of width $0.1(1+z_{\rm spec})$ centred on $z_{\rm spec}$, where $z_{\rm spec}$
-is the halo's true redshift in the \MS catalogue.
-
-\subsection{Reconstructing $\kappax$ given a spectroscopic redshift for every object}
+\phil{While the \MS catalogues do already contain stellar masses for each
+galaxy, we do not use them for two reasons. The first is that at the low mass
+end, the dark matter-only \MS satellite galaxy halos are highly  stripped
+relative to what we might expect in a universe containing baryons, leading to
+a mismatch between the observed and simulated stellar mass--halo mass
+relations.  The second is that we wanted to be able to perform the functional
+test of trying to recover the convergence having assumed the correct stellar
+mass--halo mass relation.} For these reasons, we assign a new true stellar
+mass to each halo in the \MS catalogues, according to the empirical stellar
+mass--halo mass relation of \citet{BehrooziEtal2010}. From these we simulate
+observed stellar masses by drawing samples from  $\pr(\log{M^{*}_{\rm
+obs}}|\log{M^{*}_{\rm true}})$ which we take to be a Gaussian of width
+$\sigma_{M_*}$ centred on $\log(M*_{\mathrm {true}})$. Where a spectroscopic
+redshift exists, stellar masses can be estimated with typical uncertainties of
+0.15 dex \citep{AugerEtal2009}; however with photometric redshifts stellar
+mass uncertainties are typically three times as large. We use
+$\sigma_{M_*}=0.15$ dex for halos with a spectroscopic redshift and
+$\sigma_{M_*}=0.45$ dex otherwise. For photometric redshift uncertainties we
+draw a redshift from $\pr(z_{\rm true}|z_{\rm obs})$ which we take to be a
+Gaussian of width $0.1(1+z_{\rm spec})$ centred on $z_{\rm spec}$, where
+$z_{\rm spec}$ is the halo's true redshift in the \MS catalogue.
+
+\comment{The following is relevant to all sections on inferring $\kappax$
+given imperfect data, so it belongs here and not in the spectroscopic redshift
+first subsection.}
 
@@
 estimate $\pr(\kappah|\data)$ for each reconstructed line of sight. We then
-transform this into our target PDF $\pr(\kappax|\data)$.
-
+transform this into our target PDF $\pr(\kappax|\data)$ as described above.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Reconstructing $\kappax$ given a spectroscopic redshift for every object}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
 \caption{The widths of the \infered PDFs $\pr(\kappah|\data)$ for
-$10^5$ lines of sight, given different quality of data. Blue:
-spectroscopic redshift for every halo with $i<26$; Red: 
-spectroscopic redshift for every halo with $i<23$, and every halo with $i<24$
-within 1 arcminute;
-Green: all the objects in the field have only photometric redshifts.}
+$10^5$ lines of sight, given different quality of data. 
+Blue: spectroscopic redshift for every halo with $i<26$; 
+Red: spectroscopic redshift for every halo with $i<23$, 
+and every halo with $i<24$ within 1 arcminute, while all other objects just
+have photometric redshifts;
+Green: all the objects in the field have only photometric redshifts. The
+vertical dot-dashed line marks the width of the global $\pr(\kappax)$ for all
+lines of sight.}
 \label{fig:reconwidths}
 \end{figure}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
 \includegraphics[width=\columnwidth]{figs/Widthvshilberrt.eps}
-\caption{Width of the \infered PDF $\pr(\kappax|\data)$ versus the true
-$\kappax$ along a line of sight. Green assumes only photometric redshifts
-whilst red assumes a campaign of targetted spectroscopy. The width of the
-\infered $\pr(\kappah|\data)$ increases with $\kappax$.}
-
+\caption{Width of the \infered PDF $\pr(\kappax|\data)$ as a function of 
+the true convergence, $\kappaxtrue$, for two different data qualities. 
+Green assumes only photometric redshifts for all objects,
+while red assumes a campaign of targeted spectroscopy.}
 \label{fig:widthsvsH}
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%
 
 The best possible reconstructions of $\kappax$ will come from having a
-spectroscopic redshift for every single object in each field
-(\Fref{fig:reconwidths}).  In terms of telescope time, such a reconstruction
-would be prohibitively expensive, but we investigate this scenario as an ideal
-case. Reconstructing the lines of sight with perfect knowledge of the redshift
-but an uncertain stellar mass, we find that the width of $\pr(\kappax|\data)$
-grows with the expectation value of $\kappax$ (\Fref{fig:widthsvsH}). The low
-$\kappax$ lines of sight are relatively empty, and so there are few
-opportunities for uncertainties in the halo masses to \propogate into $\kappax$
-uncertainties. The median reconstruction width in this idealised situations is
-0.01; some 22\% of lines of sight would have a reconstruction width less
-than 0.01.
+spectroscopic redshift for every single object in each field.
+\Fref{fig:reconwidths} shows the distribution of $\kappax$ posterior 
+PDF widths for various data qualities: complete spectroscopic coverage results
+in the smallest widths. In terms of telescope time, such a reconstruction
+would likely be prohibitively expensive, but we investigate this scenario as
+an ideal case.
+
+\comment{PJM: The following does not belong here because \Fref{fig:widthsvsH}
+does not show results for spectroscopic redshifts only!
+
+Reconstructing the lines of sight with perfect knowledge of the
+redshift but an uncertain stellar mass, we find that the width of
+$\pr(\kappax|\data)$ grows with the expectation value of $\kappax$
+(\Fref{fig:widthsvsH}). The low $\kappax$ lines of sight are relatively empty,
+and so there are few opportunities for uncertainties in the halo masses to
+\propogate into $\kappax$ uncertainties. 
+The median reconstruction width in
+this idealised situations is 0.01; some 22\% of lines of sight would have a
+reconstruction width less than 0.01. }
 
@@
 
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
 \subsection{Reconstructing $\kappax$ from photometry alone}
@@
 the \infered stellar mass is less precise. However, obtaining photometry has
-much lower observational cost; over the next few years several large area
-photometric surveys will reach 24th magnitude \citep{Euclid,LSST}, these will
-provide sufficient data to reconstruct lines of sight {\it without} additional
-observations. In principle the photometric redshift is correlated with the
-\infered stellar mass, however we do not model this effect since the
-convergence from the outskirts of an individual halo is only weakly \dependant
-on redshift at fixed mass: the redshift uncertainty has only a small effect on the
-inferred $\pr(\kappax|\data)$ when compared to the effect of uncertain stellar
-masses.  With only photometric redshifts the uncertainty on
-$\kappah$ is larger than in the spectroscopic case and this
-\propogates into a broader $\pr(\kappax|\data)$, although the photometric
-reconstruction still typically produces a 50\% improvement compared to the
-precision of the global $\pr(\kappax)$ (\Fref{fig:widthsvsH}).
+much lower observational cost; all upcoming large area photometric surveys
+will reach 24th magnitude, providing sufficient data to reconstruct lines of
+sight  {\it without} additional observations. In principle the photometric
+redshift is correlated with the \infered stellar mass, however we do not model
+this effect since the convergence from the outskirts of an individual halo is
+only weakly \dependant on redshift at fixed mass due to the breadth of the
+lensing kernel: the redshift uncertainty has only a small effect on the
+inferred $\pr(\kappax|\data)$ in comparison to that of  the uncertain stellar
+masses.  With only photometric redshifts, the uncertainty on $\kappah$ is
+larger than in the spectroscopic case, and this \propogates into a broader
+$\pr(\kappax|\data)$, as can be seen in \Fref{fig:reconwidths}. However, the
+photometric reconstruction still typically produces a 50\% improvement
+compared to the precision of the global $\pr(\kappax)$.
+
+We find that the width of $\pr(\kappax|\data)$ grows with the expectation
+value of $\kappax$; this is shown in \Fref{fig:widthsvsH}. The low $\kappax$
+lines of sight are relatively empty, and so there are few opportunities for
+uncertainties in the halo masses to \propogate into $\kappax$ uncertainties.
+
+\flag{Is there a simple approximation for $\kappax$ and $\sigma_{\kappa}$ as a
+function of $\kappaxtrue$? This would be useful when making forecasts, writing
+proposals etc...}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 
 \subsection{Reconstructing $\kappax$ with partial spectroscopic coverage}
+\label{sec:obsMstar+z:targetedspec}
 
@@
 $\pr(\kappax|\data)$, targeted spectroscopy can provide additional constraints
-on the masses and redshifts of halos whose $\kappah$ contribution have the
+on the masses and redshifts of halos whose $\kappah$ contributions have the
 largest absolute uncertainty. Obtaining spectra of bright ($i<22$) objects is
 relatively fast with large telescopes: however, we find that if spectroscopic
-redshifts were known for all $i<22$ galaxies in our field the reconstruction
-improves slightly upon the purely photometric reconstruction, although the
-improvement can depend strongly on the details of the particular line of
+redshifts were known for all $i<22$ galaxies in our fields the reconstruction
+improves only slightly over the purely photometric reconstruction,  although
+the improvement can depend strongly on the details of the particular line of
 sight. Obtaining spectra for fainter objects would be correspondingly more
 expensive, but if spectroscopic redshifts could be obtained for all $i<23$
-galaxies and all $i<24$ galaxies within 1 arcminute of the line of sight, the
-$\pr(\kappax|\data)$ would be almost as good as having complete spectroscopic
-coverage (\Fref{fig:reconwidths}). High $\kappax$ lines of sight benefit the
-most from additional spectral coverage, since these LoS have the most
-uncertain $\kappah$. Consistent with our previous findings the lowest $\kappax$
-lines of sight have the most constrained $\kappax$ PDFs.
+galaxies (as part of a futuristic baryon acoustic oscillation survey, for
+example) and all $i<24$ galaxies within 1 arcminute of the line of sight, then
+we find that the $\pr(\kappax|\data)$ would be almost as precise as that from
+having complete spectroscopic coverage (\Fref{fig:reconwidths}). High
+$\kappax$ lines of sight benefit the most from additional spectral coverage,
+since these have the most uncertain $\kappah$. \flag{This is not what
+\Fref{fig:widthsvsH} shows at all! Does the $\kappaxtrue$ axis not extend far
+enough?} Consistent with our previous findings, the lowest $\kappax$ lines of
+sight have the most constrained $\kappax$ PDFs.
 
@@
 \includegraphics[width=\textwidth]{figs/biasplots.eps}
-\caption{Convergence accuracy from combining subsets of
-lenses. By subtracting the true (ray-traced) convergence from the
-\infered $\pr(\kappax)$ for each line of sight we are left with a PDF that
-should be estimating zero; these can be multiplied together for multiple
-lines of sight to emulate a joint likelihood analysis, and 
-test for possible bias in it. These plots show the
-expectation value of $\prod_{i=1}^N \pr_i(\kappax-\kappax^{\rm true})$ --
-deviations from zero constitute biases. The solid, dashed and dotted
-lines correspond to combinations of 
-20, 5 and 2 sightlines respectively. Green lines show the results
-from multiplying $\pr(\kappax|\data)$ \infered from photometry alone, whilst red
-lines are from multiplying $\pr(\kappax)$ \infered from photometry and a
-spectroscopic redshift for all halos with $i<23$ and all halos within 1
-arcminute and $i<24$. The leftmost plot shows randomly selected lines
-of sight. The central plot shows sight lines randomly selected from the
-33\% of lines whose P($\kappax$) is most tightly constrained by our model. The right
-hand plot shows only lines of sight with external shear of 0.05 or
-greater.}
+\caption{Accuracy in $\kappax$ from combining samples of lenses.  These plots
+show the expectation value of $\prod_{i=1}^N \pr_i(\kappax-\kappaxtrue|\data)$ --
+deviations from zero represent biases. The solid, dashed and dotted lines
+correspond to combinations of  20, 5 and 2 sightlines respectively. Green
+lines show the results \infered from photometry alone, whilst red lines show
+the results  from the same targeted spectroscopy campaign described in 
+\Sref{sec:obsMstar+z:targetedspec}. The three panels correspond to samples of
+sightlines selected in different ways. Left: randomly selected lines of
+sight.  Centre: sightlines randomly selected from the 33\% of lines whose
+P($\kappax$) is most tightly constrained by our model.  Right: lines of sight
+with external shear of 0.05 or greater.}
 \label{fig:biasplots}
@@
 $\kappax$ is reconstructed accurately. The reconstruction must not be biased. 
-We test the accuracy of our reconstructed $\pr(\kappax|\data)$ in the following
-way: for each line of sight we have an estimator for the true convergence along
-that line of sight, by subtracting the line of sight's ray-traced convergence
-$\kappax^{\rm true}$ from $\pr(\kappax|\data)$ we have an estimator of zero, $\pr(\kappax-\kappax^{\rm true}|\data)$.
- Since the $\pr(\kappax-\kappax^{\rm true}|\data)$ for
-each line of sight is an \independant estimator of zero, the PDFs from $N$ lines of sight
-can be combined according to
+We quantify the accuracy of our reconstructed $\pr(\kappax|\data)$ in the
+following way. By shifting the \infered $\pr(\kappax|\data)$ for each line of
+sight by the true (ray-traced) convergence, we obtain a  PDF that should be
+centred on zero; these offset PDFs can be multiplied together for multiple
+lines of sight to emulate a joint likelihood analysis, and then test for
+possible bias in it:
 \be
 \label{eq:bias}
-\mathcal{P}_N = \prod_{i=1}^N \pr_i(\kappax-\kappax^{\rm true})
+\mathcal{P}_N = \prod_{i=1}^N \pr_i(\kappax-\kappax^{\rm true}|\data)
 \ee
@@
 expectation value of $\mathcal{P}_N$ from zero. If the bias of $\mathcal{P}_N$
-is smaller than the half-width of $\mathcal{P}_N$, our $\kappax$ estimators can
-be considered accurate. Since the width of $\mathcal{P}_N$ decreases as more
-lenses are combined a small bias will eventually be found for all estimators
-In the context of measuring time delay distance at the one percent level the
-expectation value of $|\mathcal{P}_N|$ needs to be less than 0.01.
-
-The source of systematic error that we investigate is that of sample
-selection: we define three different selections of lines of sight, and compute
-the bias present in each one in turn, as a function of data quality. The
-results described below are illustrated in \Fref{fig:biasplots}.
+is smaller than the half-width of $\mathcal{P}_N$, our $\kappax$ inferences
+can be considered accurate. Since the width of $\mathcal{P}_N$ decreases as
+more sightlines are combined, a small bias will always 
+eventually be found. In the context of measuring time delay distance at the 
+one percent level, the expectation value of $|\mathcal{P}_N|$ needs to be 
+significantly less than 0.01.
+\flag{Modify this as advised by Sherry -- introduce model for other
+uncertainties in lenses, and explain number of lenses to see error argument.}
+
+\comment{From Sherry:
+Re: $P_N$:
+Not sure that this is the best way to quantify bias.  First of all, this
+doesn't include the modeling error of $\sim3-4\%$, so the number of lenses listed
+(for when <$P_N$> = half width of $P_N$) is underestimated.  Also, with this
+definition, a large number of lenses could be described as "biased" even if
+the resulting shift is say 0.0001, which won't really trouble us at all.  For
+example, what would the distributions look like in Fig.8 with 100 lenses? 
+Since the peaks of the red curves are within 0.01 of kappa_true, I would
+suspect that with a large number of lenses, the corresponding red curve would
+be within 0.01 of kappa_true.   The present day goal is to get H0 to 1\%, and
+it would be good to state somewhere that with targeted spectroscopy, one could
+recover kext at the 1\% level with a large sample of lenses.}
+
+The source of systematic error that we investigate in this paper  is that of
+sample selection: we define three different example selections of lines of
+sight, and compute the bias  \phil{that would result (if left unaccounted
+for)} in each one in turn, as a function of data quality. The results
+described below are illustrated in \Fref{fig:biasplots}.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 
@@
 We first consider a purely random selection of lines of sight. With the purely
-photometric reconstruction, there is no evidence of bias, even after combining 20
-lines of sight. If these lines of sight hosted time
-delay lenses, the bias number would correspond to a systematic error of
-0.5\% in time delay distance. Since the statistical distance uncertainties due
-to lens modelling and time delay estimation are likely to be at the 3-4\%
-level \citep{SuyuEtal2010},  only a sample containing 200 or more lenses would
-be limited by the residual bias  following external convergence
-reconstruction.
-
-\subsection{Selecting only the lines of sight with tight $\pr(\kappax|\data)$}
+photometric reconstruction, there is no evidence of bias, even after combining
+20 lines of sight. \phil{This result is really a sanity check, since for
+random lines of sight the bias as defined here should be zero by
+construction}. If these lines of sight hosted time delay lenses, the bias
+number would correspond to a systematic error of 0.5\% in time delay distance.
+\flag{What is this number? In the first sentence the bias was given as zero!}
+Since the statistical distance uncertainties due to lens modelling and time
+delay estimation are likely to be at the 3-4\% level \citep{SuyuEtal2010}, 
+only a sample containing 200 or more lenses would be limited by the residual
+bias following external convergence reconstruction.
+\flag{$0.035/\sqrt{200} \neq 0.005$ so what numbers are these? We should
+outline the lens number calculation in the preamble above.}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Selecting only the lines of sight with narrow $\pr(\kappax|\data)$}
 \label{sec:bias:tightPDF}
@@
 detected objects will be observed further. By pre-selecting objects that have 
-the most well constrained convergence, the cosmological value per lens can be
-increased. However, this selection has the potential to induce a bias. It is
-probable that only photometry will be available at the time of sub-sample
+the best-constrained convergence, the cosmological value per lens can be
+increased. However, this selection \phil{(like any other)}
+has the potential to induce a bias. It is
+likely that only photometry will be available at the time of sub-sample
 selection (although spectroscopic follow-up might be conducted at a later
@@
 
-We find that selecting the most tightly constrained lines of sight has no impact on the
-bias -- our reconstruction is most \succesful for the lowest
-$\kappax$ lines of sight. With targeted spectroscopic follow-up of the selected lines of sight
-there is negligible improvement compared to photometry alone, since the best constrained lines of sight are
-the most empty, and it is the high-$\kappax$ lines of sight that benefit the
-most from spectroscopy. Photometry of the field is sufficient to adequately
-select the best lines of sight for cosmology -- and doing so greatly increases
- the precision of the cosmological constraints per system, with no degradation of the accuracy.
-Since lenses are typically found in locally over-dense environments, it is unlikely that 
-an almost empty line of sight would contain a lens; it is somewhat optimistic to 
-suggest that nearly empty lines of sight could be used for time-delay cosmology.
+We find that selecting the most tightly constrained lines of sight in this way
+does not introduce a bias: 
+our reconstruction is most accurate for the lowest
+$\kappax$ lines of sight. With targeted spectroscopic follow-up of the
+selected lines of sight there is only a slight 
+improvement compared to photometry
+alone, since the best constrained lines of sight are also 
+the most empty, and it is
+the high-$\kappax$ lines of sight that benefit the most from spectroscopy.
+\flag{This was not shown conclusiveley earlier. Need to tighten this up.}
+Photometry of the field seems to be sufficient to adequately select these
+empty lines of sight.  However, 
+since lenses are typically found in locally over-dense
+environments, it is unlikely that  an almost empty line of sight would
+actually  contain a lens; \phil{what we can say is that if the local
+environment can be identified spectroscopically, and then the line
+of sight mass distribution reconstructed using our method, selecting lenses
+with low, well-constrained values of $\kappax$ will lead to an increase in
+distance precision at no cost in bias.}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 
@@
 light-curves), or the fact that they are quadruply-imaging rather than
-doubly-imaging, since this yields 3 time delays instead of 1, a higher
-magnification and a more informative Einstein Ring system. All three of these
+doubly-imaging (since this yields 3 time delays instead of 1, a higher
+magnification and a more informative Einstein Ring system). All three of these
 properties favour lenses with high convergence and shear along their lines of
@@
 
-By selecting only lines of sight with an external shear of $\gammax>0.05$ we
-can test the impact of shear selection. We find that in this sample, $\kappax$
-is systematically underestimated at the $\sim$0.008 level (corresponding to a
-0.8\% systematic error in distance); in the absence of other sources of uncertainty, this
-systematic error would be significant in a sample of 5 lenses. Approximating strong-lens
-modelling uncertainties as an unbiased gaussian with width 4\% on time-delay distance a 0.8\% bias would be
+\phil{We can test the impact of such a shear selection by selecting only lines
+of sight with an external shear above some threshold.  We define a somewhat
+extreme selection  of $\gammax>0.05$, and find that in this sample, $\kappax$
+would be systematically underestimated at the $\sim$0.008 level (corresponding to a
+0.8\% systematic error in distance).} 
+In the absence of other sources of uncertainty, this
+systematic error would be significant in a sample of just 5 lenses; 
+approximating strong-lens
+modelling uncertainties as an unbiased Gaussian with width 4\% on time-delay distance a 0.8\% bias would be
 significant for $\sim$20 lenses.
-The systematic error is mitigated if only
+This systematic error is mitigated if only
 the lines of sight with both $\gammax>0.05$ and well constrained $\pr(\kappax|\data)$ are
-used, but biases at the $\sim$0.005 level remain. The
-toy selection model used here ($\gammax>0.05$) is likely to be a much
-stronger selection than reality, but nevertheless it is worth noting that the
-reconstruction \proceedure will be biased if lens selection functions are
-extreme and unaccounted for. Since our model does not
-include shear constraints it is not surprising that a selection function based on shear
-can induce a bias. A more sophisticated model that includes the shear
-recovered from the lens modelling may be less susceptible to this bias.
-
-The halo model can also be used to estimate the external shear
-along a line of sight. Shear is an observable that can be extracted from
-strong lens modelling, however there is a degeneracy between internal and
-external shear. When the Einstein Ring data are very good it is possible to
-disentangle external and internal shear \citep[\eg][]{SuyuEtal2010}, but there are
-still significant uncertainties: \citet{WongEtal2011} attempted to match the
-shear from strong lens models with a reconstruction of the local lens group
-environment, but found a tension between the strong lens model and the
-reconstruction of the environment. Given the \citet{WongEtal2011} results
-it is unclear whether the external shear from lens models can be
-reconciled with a line of sight reconstruction. Alternatively, it may be possible 
-to infer external shear using weak lensing information from near the line of sight. 
-If the true external shear can be
-measured, it provides an additional constraint on which of the \MS lines of
-sight are similar to the reconstructed line of sight. \citet{SuyuEtal2012}
-found that for RXJ1131 combining shear constraints with galaxy number count
-over-density, gave a significantly different $\pr(\kappax|\gamma,N_{45})$
-compared to the PDF from number count over-density alone,
-$\pr(\kappax|N_{45})$.
+used, but in this case a bias at the $\sim$0.005 level remains.
+
+While $\gammax>0.05$) is likely to be a much stronger selection than would
+occur in reality, it is  nevertheless worth noting from this example  that the
+reconstruction \proceedure \phil{can be biased if lens selection functions are
+extreme and unaccounted for.} Since our model does not include shear
+constraints it is not surprising that a selection function based on shear can
+induce a bias. A more sophisticated model that includes the shear recovered
+from the lens modelling may be less susceptible to this bias.
+
+The halo model can also be used to estimate the external shear along a line of
+sight: shear is an observable that can be extracted from strong lens
+modelling. However, there is a degeneracy between internal and external shear.
+When the Einstein Ring imaging data are very good it is possible to
+disentangle external and internal shear \citep[\eg][]{SuyuEtal2010}, but there
+are still significant uncertainties: \citet{WongEtal2011} attempted to match
+the shear from strong lens models with a reconstruction of the local lens
+group environment, but found a tension between the strong lens model and the
+reconstruction of the environment. Given the \citet{WongEtal2011} results, it
+is unclear whether the external shear from lens models can be reconciled with
+a line of sight reconstruction. Alternatively, it may be possible  to infer
+external shear using weak lensing information from near the line of sight.  If
+the true external shear can be measured, it provides an additional constraint
+on which of the \MS lines of sight are similar to the reconstructed line of
+sight. \citet{SuyuEtal2012} found that in the case of 
+RXJ1131, combining shear constraints
+with galaxy number count over-density gave a significantly different
+$\pr(\kappax|\gamma,N_{45})$ compared to the PDF from number count
+over-density alone, $\pr(\kappax|N_{45})$.
 
@@
 $\pr(\kappax|\data)$ is still typically $\sim$0.01 for any given lightcone,
-even with a perfect knowledge of every halo's virial mass and redshift. To
+even assuming perfect knowledge of every halo's virial mass and redshift. To
 make further progress a more advanced treatment of both voids and halos will
-be necessary. \citet{KarpenkaEtal2012} find that their supernova data prefer,
-in the context of their simple halo model, a truncated isothermal profile for
-the galaxy mass distributions. Galaxy-galaxy and cluster-galaxy  lensing
-studies \citep[\eg][]{GavazziEtal2007,JohnstonEtal2007} also suggest an
-approximately isothermal profile for the mass-shear correlation function;
-however, at large radii these profiles are dominated by the effects of
-neighbouring halos, which should be taken into account by our model. Further
-iterations on the analysis presented here should include the stellar mass
-distributions that cause the isothermal density profiles in the centres of
-galaxies, although we do not expect this to have a big impact on the model.
-Likewise,  halo ellipticity may have some small effect on the predicted
-convergence. It is possible that baryonic physics may alter   
-the radial profile of dark matter halos, even on large scales. \citet{Semboloni+2012}
-found that baryonic physics had a 30-40\% impact on three-point shear statistics, it is
-unclear how baryons affect one-point convergence statistics compared to the pure dark matter
-simulations used in this work.
+be needed. \citet{KarpenkaEtal2012} find that their supernova data prefer, in
+the context of their simple halo model, a truncated isothermal profile for the
+galaxy mass distributions. Galaxy-galaxy and cluster-galaxy  lensing studies
+\citep[\eg][]{GavazziEtal2007,JohnstonEtal2007} also suggest an approximately
+isothermal profile for the mass-shear correlation function; however, at large
+radii these profiles are dominated by the effects of neighbouring halos, which
+are already taken into account by our model.  Further iterations on the
+analysis presented here should include the stellar mass distributions that
+cause the isothermal density profiles in the centres of galaxies, although we
+do not expect this to have a big impact on the reconstructions. Likewise, 
+halo ellipticity may have some small effect on the predicted convergence. It
+is possible that baryonic physics may alter    the radial profile of dark
+matter halos, even on large scales. \citet{Semboloni+2012} found that baryonic
+physics had a 30-40\% impact on three-point shear statistics, it is unclear
+how baryons affect one-point convergence statistics compared to the pure dark
+matter simulations used in this work.
 
@@
 ensemble, is reminiscent of the procedure followed by \citet{SuyuEtal2010},
-and Greene et al (in prep.) The reconstruction method can be seen as the
+and Greene et al (submitted). The reconstruction method presented here 
+can be seen as the
 limiting case of the weightings explored by Greene et al: rather than using
@@
 predict  $\kappa_{\rm h,obs}^{\rm med}$ for use in their place.
+\flag{How much more precise are we than Greene et al?}
+
+\flag{Paragraph outlining future work on lens lines of sight (eg including
+local environment). Why wasn't this done here?}
 
@@
 
-In this work, we have used 
-the \MS as a calibration tool. If the real Universe is not
-like the \MS, then this calibration will be incorrect. Repeating this 
-study using
-a different simulation to make the test catalogues would allow us to quantify
-the sensitivity of our results to the simulation used. Similarly the use of a
-different semi-analytic model to paint galaxies onto halos, and an alternative
-stellar mass--halo mass relation would both enable similar exploration of
-these systematic errors. \citet{SuyuEtal2010} used the relative over-density to mitigate this
-effect, but it does not totally remove the dependence on simulation.
+In this work, we have used  the \MS as a calibration tool. If the real
+Universe is not like the \MS, then this calibration will be incorrect.
+Repeating this  study using a different simulation to make the test catalogues
+would allow us to quantify the sensitivity of our results to the simulation
+used. Similarly the use of a different semi-analytic model to paint galaxies
+onto halos, and an alternative stellar mass--halo mass relation would both
+enable similar exploration of these systematic errors. \citet{SuyuEtal2010}
+used the relative over-density to mitigate this effect, but it does not
+completely remove the dependence on simulation.
 
@@
 source. We have used the ray-traced lensing convergence along lines of sight
-through the Millennium Simulation to test this approach, and to calibrate
-estimates of the total convergence made by summing the convergences due to
-each object in a photometric catalogue. Having found that the reconstruction
-process is accurate and precise given perfect knowledge of halo mass and redshift, we
-investigated the effects of reasonable uncertainties in the stellar mass and
-redshift of each halo, and propagated these uncertainties into a
-$\pr(\kappax|\data)$ for each line of sight. We also defined three different
-possible line of sight selections, and investigated the bias induced by these
-selections. We draw the following conclusions:
+through the Millennium Simulation to calibrate estimates of the total
+convergence made by summing the convergences due to each object in a
+photometric catalogue. Having found that the reconstruction process is
+accurate given this calibration and perfect knowledge of halo mass and
+redshift, we investigated the effects of reasonable uncertainties in the
+stellar mass and redshift of each halo, and propagated these uncertainties
+into a $\pr(\kappax|\data)$ for each line of sight. We also defined three
+different possible line of sight selections, and investigated the possible 
+bias induced by these selections. We draw the following conclusions:
 
@@
 \item Despite our model's simplicity, its reconstructed $\kappah$ values are
-good tracers of $\kappax$. $\kappah$ is biased due to our ignorance of voids, but we found that this can be calibrated out. We found that with perfect knowledge of
-the halo mass and redshift (from the Millennium Simulation catalogues), for a
-typical line of sight the calibrated reconstruction gives an unbiased estimate
-of $\kappax$ that is a factor of 2 more precise than the global $\pr(\kappax)$.
-With uncertain halo masses and redshifts, we find that
-$\pr(\kappah|\data)$ is still a useful indicator for inferring
+good tracers of $\kappax$. $\kappah$ is biased due to our ignorance of voids,
+groups and clusters, and the unseen mass in small halos and filaments, but we
+find that this can be calibrated out using the Millenium Simulation
+catalogues. We found that with perfect knowledge of every halo's mass and
+redshift,  calibrated reconstruction of a typical line of sight  gives an
+unbiased estimate of $\kappax$ that is not perfect, but is $1.8$ 
+times more precise than the global
+$\pr(\kappax)$. This factor quantifies the limit to which the halo model can
+represent the external convergence due to line of sight mass structure.
+
+\item With uncertain halo masses and redshifts, we find that
+$\pr(\kappah|\data)$ can still be calibrated in order to infer
 $\pr(\kappax|\data)$ from the ensemble of simulated lines of sight, but the
@@
 \item It is very rare for halos further than 2 arcminutes from the line of
-sight to make a significant contribution to $\pr(\kappax|\data)$. Including
+sight to make a significant contribution to $\pr(\kappax|\data)$; likewise, 
+including
 halos whose host galaxy is less luminous than $i=24$ does not significantly
-improve our reconstruction precision.  A photometric survey to this depth of a
+improve our reconstructions.  A photometric survey to this depth of a
 4$\times$4 arcminute patch around the target would approach the limiting
@@
 invested, it will be possible to select targets by the precision of their
-$\kappax$ estimates. This will be useful
-in an era when there are more known lenses than can be followed-up.
-Photometric data is sufficient to select the best lines of sight for
+$\kappax$ estimates. This will be useful in an era when there are more known
+lenses than can be followed-up.
+
+\item  Photometric data is sufficient to select the best lines of sight for
 follow-up. Spectroscopic coverage helps to tighten  $\pr(\kappax|\data)$ for
-high $\kappax$ lines of sight, but is of less use for low $\kappax$ lines of
-sight.
-
-\item Selecting from the highest precision 33\% of the reconstructed lines of sight
-results in a sample with low bias, 0.1\% in terms of the time delay distance,
-and a statistical uncertainty due to line of sight mass structure that is half
-that of the parent sample. Neglecting other sources of uncertainty, the residual systematic error would be equal to the
-overall statistical uncertainty in a sample of around 200 lenses.
-
-\item Conversely, selecting lines of sight with high shear ($|\gamma| >
-0.05$ (as might be done inadvertently by focusing on four-image or wide
-separation lenses) results in a sample with bias of 0.8\% in time delay
-distance. Including realistic estimates of other sources of uncertainty a systematic error
-of 0.8\% would become significant in a sample of $\sim$20 lenses.
+high $\kappax$ lines of sight.
+% , but is of less use for low $\kappax$ lines of
+% sight.
+
+\item Selecting from the highest precision 33\% of the reconstructed lines of
+sight results in a sample with low bias, 0.1\% in terms of the time delay
+distance, and a statistical uncertainty due to line of sight mass structure
+that is half that of the parent sample. \flag{This is the first time this
+number (0.1\%) has appeared!} Neglecting other sources of uncertainty, the
+residual systematic error would be equal to the overall statistical
+uncertainty in a sample of around 200 lenses. \flag{Needs checking.}
+
+\item Conversely, selecting lines of sight with high shear ($|\gamma| > 0.05$
+(a somewhat extreme selection, but one that  could potentially arise from 
+focusing on four-image or wide separation lenses) results in a sample with
+bias of 0.8\% in time delay distance. Including realistic estimates of other
+sources of uncertainty a systematic error of 0.8\% would become significant in
+a sample of $\sim$20 lenses.
 
@@
 function of the unknown $\Mstar$, and multiply it by our tabulated joint PDF.
-This heavily down weights halos with $\Mstar$ values outside the observed
+This heavily downweights halos with $\Mstar$ values outside the observed
 range. We then do the marginalisation integral by Monte Carlo, drawing

### 2012-12-04 doc/acknowledgments.tex

--- 2012-08-21 doc/acknowledgments.tex
@@
 %
-MWA \ldots
+% MWA \ldots
 %
-SH \ldots
+SH and RDB, and CDF, acknowledge support by the National Science Foundation
+(NSF), grant numbers AST-0807458 and  AST-0909119, respectively.
 %
-SHS \ldots
-%
-TT acknowledges support from the NSF through CAREER award NSF-0642621,
-and from the Packard Foundation through a Packard Research Fellowship.
+SHS, ZG  and TT gratefully acknowledge support from the Packard Foundation in
+the form of a Packard Research Fellowship to TT and from the 
+NSF grant AST-0642621.
 % 
@@
 %
-This research is supported in part by the National Science Foundation under
-Grant No. PHY99-07949.
+% This research is supported in part by the National Science Foundation under
+% Grant No. PHY99-07949.
+%
+The Millennium Simulation databases used in this paper and the web application
+providing online access to them were constructed as part of the activities of
+the German Astrophysical Virtual Observatory.

### 2012-12-04 doc/paper-lcr.tex
draft update
acted on phils comments

@@
 
-\documentclass[useAMS,usenatbib]{mn2e}
+\documentclass[useAMS,usenatbib,a4paper]{mn2e}
 %% letterpaper
@@
 
-\voffset=-0.6in
+%\voffset=-0.6in
 
@@
 similar as possible to the real universe or there is a possibility of
-systematic errors. \phil{On the other hand, making use of all the information
+systematic errors. Conversely, making use of all the information
 in the photometric catalogue yields $\kappax$ estimates of increased
-precision, as we shall see.}
+precision.
 
@@
 and assuming noise-free halo masses and redshifts. 
-\phil{(In this case, $\kappah^{\rm med} = \kappah$, since 
-$\pr(\kappah|\data)$ is a delta function)}.
-% In this case, the PDF $\pr(\kappah|\data)$ is a delta function: we can read
+\phil{(In this case, $\pr(\kappah|\data)$ is almost delta function since the only uncertainty is halo
+concentration, which has minimal effect on $\pr(\kappah|\data)$.  
+)}.
+% In this case, the PDF : we can read
 % off  $\pr(\kappax|\data)$ just by taking a thin vertical slice through this 
@@
 
-\flag{Should we show the relevant calibration plots, analogous to Figure 2?
-Seems a bit odd to give Figure 2 but not illustrate the {\it actual
-calibration procedure we follow on real data}... Maybe we could make one that
-had the conditional distribution for each data quality?}
+%\flag{Should we show the relevant calibration plots, analogous to Figure 2?
+%Seems a bit odd to give Figure 2 but not illustrate the {\it actual
+%calibration procedure we follow on real data}... Maybe we could make one that
+%had the conditional distribution for each data quality?}
+
+%TEC: I think that could lead to figure overload; the concept is given throughout
+% the paper, and it's well illustrated by figure 2.
 
@@
 \comment{PJM: The following does not belong here because \Fref{fig:widthsvsH}
-does not show results for spectroscopic redshifts only!
+does not show results for spectroscopic redshifts only!}
 
@@
 redshift but an uncertain stellar mass, we find that the width of
-$\pr(\kappax|\data)$ grows with the expectation value of $\kappax$
+$\pr(\kappax|\data)$ grows with the expectation of $\kappax$ and the ray-traced $\kappatrue$
 (\Fref{fig:widthsvsH}). The low $\kappax$ lines of sight are relatively empty,
 and so there are few opportunities for uncertainties in the halo masses to
-\propogate into $\kappax$ uncertainties. 
-The median reconstruction width in
-this idealised situations is 0.01; some 22\% of lines of sight would have a
-reconstruction width less than 0.01. }
-
-% PJM: Note that I removed talk of void correction here - surely we should be
-% just applying the method we describe and inferring $\kappa$?
-%
-% TEC: yes.
+\propogate into $\kappax$ uncertainties; low $\kappax$ lines of sight can be reconstructed
+more precisely than high $\kappax$ lines of sight.
 
@@
 
+\tom{With photometric data alone, $\kappah^{\rm med}$ can shift by $\sim$0.01 relative to $\kappah^{\rm med}$
+given spectroscopic coverage. The $\kappax$ contribution of voids cannot change with data quality;
+the shift in $\kappah^{\rm med}$ is due to the asymmetric propogation of stellar mass uncertainties
+into $\kappax$ uncertainties. As stellar mass uncertainty increases $\kappah^{\rm med}$ is pushed higher. 
+To correctly calibrate  $\pr(\kappax|\kappah^{\rm med},\data)$ one {\it must} include the data quality used to generate $\kappah^{\rm med}$.}
+
 We find that the width of $\pr(\kappax|\data)$ grows with the expectation
@@
 
-\flag{Is there a simple approximation for $\kappax$ and $\sigma_{\kappa}$ as a
-function of $\kappaxtrue$? This would be useful when making forecasts, writing
-proposals etc...}
+%\flag{Is there a simple approximation for $\kappax$ and $\sigma_{\kappa}$ as a
+%function of $\kappaxtrue$? This would be useful when making forecasts, writing
+%proposals etc...}
+%
+%TEC: No. It's also not relevant to proposals since kappatrue isnt observable. One can ask is there
+%a formula for sigmakappa given the expectation value of kappax. The answer to that is
+%yes, but it depends on data quality. Concerning forecasting yes we would 
+%want to use a simple approximation, but I don't think it has a place in this paper.
+%When you/I/someone does the forecasting I'd like to be involved; I'll make the
+%approximation then.
 
@@
 we find that the $\pr(\kappax|\data)$ would be almost as precise as that from
-having complete spectroscopic coverage (\Fref{fig:reconwidths}). High
-$\kappax$ lines of sight benefit the most from additional spectral coverage,
-since these have the most uncertain $\kappah$. \flag{This is not what
-\Fref{fig:widthsvsH} shows at all! Does the $\kappaxtrue$ axis not extend far
-enough?} Consistent with our previous findings, the lowest $\kappax$ lines of
+having complete spectroscopic coverage (\Fref{fig:reconwidths}).
+Consistent with our previous findings, the lowest $\kappax$ lines of
 sight have the most constrained $\kappax$ PDFs.
@@
 more sightlines are combined, a small bias will always 
-eventually be found. In the context of measuring time delay distance at the 
+eventually be found. In the context of measuring time-delay distance at the 
 one percent level, the expectation value of $|\mathcal{P}_N|$ needs to be 
-significantly less than 0.01.
-\flag{Modify this as advised by Sherry -- introduce model for other
-uncertainties in lenses, and explain number of lenses to see error argument.}
+significantly less than 0.01. \tom{External convergence is not the only
+source of uncertainty in measuring time-delay distance.
+Since the statistical distance uncertainties due to lens modelling and time
+delay estimation are likely to be at the 3-4\% level \citep{SuyuEtal2010},
+convolving $\mathcal{P}_N$ with a Gaussian of width $0.03/\sqrt{N}$ is a
+reasonable approximation for the 
+likely final uncertainty on time-delay distance.}
 
@@
 photometric reconstruction, there is no evidence of bias, even after combining
-20 lines of sight. \phil{This result is really a sanity check, since for
-random lines of sight the bias as defined here should be zero by
-construction}. If these lines of sight hosted time delay lenses, the bias
-number would correspond to a systematic error of 0.5\% in time delay distance.
-\flag{What is this number? In the first sentence the bias was given as zero!}
-Since the statistical distance uncertainties due to lens modelling and time
-delay estimation are likely to be at the 3-4\% level \citep{SuyuEtal2010}, 
-only a sample containing 200 or more lenses would be limited by the residual
-bias following external convergence reconstruction.
-\flag{$0.035/\sqrt{200} \neq 0.005$ so what numbers are these? We should
-outline the lens number calculation in the preamble above.}
+20 lines of sight. \tom{This result is a sanity check: if we had chosen lines of
+sight with identical $\kappah^{\rm med}$ rather than $\kappah^{\rm med}\pm0.003$ randomly
+selected lines of sight would have zero bias by construction}. If lines of sight hosting time delay lenses
+are truely random,  our method allows $\kappax$ to be reconstructed without inducing a bias\footnote{under the assumption that the universe is like the calibration simulation, and the correct stellar-mass to halo-mass relation has been used}.
 
@@
 our reconstruction is most accurate for the lowest
-$\kappax$ lines of sight. With targeted spectroscopic follow-up of the
-selected lines of sight there is only a slight 
-improvement compared to photometry
-alone, since the best constrained lines of sight are also 
-the most empty, and it is
-the high-$\kappax$ lines of sight that benefit the most from spectroscopy.
-\flag{This was not shown conclusiveley earlier. Need to tighten this up.}
+$\kappax$ lines of sight. Combining 20 such systems the bias is at the 0.001 level.
+
 Photometry of the field seems to be sufficient to adequately select these
@@
 weighted number counts in an aperture, we treat each galaxy individually, and
-predict  $\kappa_{\rm h,obs}^{\rm med}$ for use in their place.
-\flag{How much more precise are we than Greene et al?}
-
-\flag{Paragraph outlining future work on lens lines of sight (eg including
-local environment). Why wasn't this done here?}
+predict $\kappa_{\rm h,obs}^{\rm med}$ for use in their place. \flag{How much more precise are we than Greene et al?}
 
@@
 completely remove the dependence on simulation.
+
+\tom{ Future work should focus on two areas:
+reducing the dependance on simulations; and,
+improving the modeling of dark structures and voids. The analysis should be repeated with different 
+simulations and differrent stellar-mass to halo-mass relations, cross-checking that 
+using the wrong simulation simulation or relation does not induce a systematic error.
+Improving the modelling of of voids could be done using the void models of \citet{voids2}
+or \citet{voids1} combined with a void finder such as in \citet{voids3}.
+Combining the halo model with a void model may allow a direct test of the 
+halo approximation; using real photometric data one could reconstruct lines of sight
+and compare against measured weak lensing shears. This would ensure that the halo model reproduces the
+contents of the real universe, rather than a particular simulation.}
 
@@
 \item Selecting from the highest precision 33\% of the reconstructed lines of
-sight results in a sample with low bias, 0.1\% in terms of the time delay
-distance, and a statistical uncertainty due to line of sight mass structure
-that is half that of the parent sample. \flag{This is the first time this
-number (0.1\%) has appeared!} Neglecting other sources of uncertainty, the
-residual systematic error would be equal to the overall statistical
-uncertainty in a sample of around 200 lenses. \flag{Needs checking.}
+sight results in a sample with low bias, $\sim$0.1\% in terms of the time-delay
+distance. \tom{For these lines of sight the reconstructed $\pr(\kappax)$ induce 
+a statistical uncertainty of $\sim$1\% on individual time-delay distances}
 

### 2012-12-04 doc/paper-lcr.tex
updated figure2
response to Tom's edits

@@
 At fixed $\kappah$ the scatter in $\kappax$ grows rapidly with $\kappah$.
-\flag{Can you plot a $y=x$ line to show the correction being made, please?}}
+\tom{The thin diagonal line follows $\kappax=\kappah$.}}
 \label{fig:jointkh-k}
@@
 
-\tom{With photometric data alone, $\kappah^{\rm med}$ can shift by $\sim$0.01 relative to $\kappah^{\rm med}$
-given spectroscopic coverage. The $\kappax$ contribution of voids cannot change with data quality;
-the shift in $\kappah^{\rm med}$ is due to the asymmetric propogation of stellar mass uncertainties
-into $\kappax$ uncertainties. As stellar mass uncertainty increases $\kappah^{\rm med}$ is pushed higher. 
-To correctly calibrate  $\pr(\kappax|\kappah^{\rm med},\data)$ one {\it must} include the data quality used to generate $\kappah^{\rm med}$.}
+\tom{With photometric data alone, $\kappah^{\rm med}$ can shift by $\sim$0.01
+relative to $\kappah^{\rm med}$ given spectroscopic coverage. Since  the
+$\kappax$ contribution of voids cannot change with data quality, the shift in
+$\kappah^{\rm med}$ must be due to the asymmetric propagation of stellar mass
+uncertainties into $\kappax$ uncertainties. As the stellar mass uncertainty
+increases, $\kappah^{\rm med}$ is pushed higher.  To correctly calibrate 
+$\pr(\kappax|\kappah^{\rm med},\data)$ one {\it must} include the data quality
+used to generate $\kappah^{\rm med}$.}
 
@@
 one percent level, the expectation value of $|\mathcal{P}_N|$ needs to be 
-significantly less than 0.01. \tom{External convergence is not the only
-source of uncertainty in measuring time-delay distance.
-Since the statistical distance uncertainties due to lens modelling and time
-delay estimation are likely to be at the 3-4\% level \citep{SuyuEtal2010},
-convolving $\mathcal{P}_N$ with a Gaussian of width $0.03/\sqrt{N}$ is a
-reasonable approximation for the 
-likely final uncertainty on time-delay distance.}
-
-\comment{From Sherry:
-Re: $P_N$:
-Not sure that this is the best way to quantify bias.  First of all, this
-doesn't include the modeling error of $\sim3-4\%$, so the number of lenses listed
-(for when <$P_N$> = half width of $P_N$) is underestimated.  Also, with this
-definition, a large number of lenses could be described as "biased" even if
-the resulting shift is say 0.0001, which won't really trouble us at all.  For
-example, what would the distributions look like in Fig.8 with 100 lenses? 
-Since the peaks of the red curves are within 0.01 of kappa_true, I would
-suspect that with a large number of lenses, the corresponding red curve would
-be within 0.01 of kappa_true.  The present day goal is to get H0 to 1\%, and
-it would be good to state somewhere that with targeted spectroscopy, one could
-recover kext at the 1\% level with a large sample of lenses.}
+significantly less than 0.01. \tom{External convergence is not the only source
+of uncertainty in measuring time-delay distance. Since the statistical
+distance uncertainties due to lens modelling and time delay estimation are
+likely to be at the 3-4\% level \citep{SuyuEtal2010}, convolving
+$\mathcal{P}_N$ with a Gaussian of width $0.03/\sqrt{N}$ is a reasonable
+approximation for the likely final uncertainty on time-delay distance.}
+
+% \comment{From Sherry:
+% Re: $P_N$:
+% Not sure that this is the best way to quantify bias.  First of all, this
+% doesn't include the modeling error of $\sim3-4\%$, so the number of lenses listed
+% (for when <$P_N$> = half width of $P_N$) is underestimated.  Also, with this
+% definition, a large number of lenses could be described as "biased" even if
+% the resulting shift is say 0.0001, which won't really trouble us at all.  For
+% example, what would the distributions look like in Fig.8 with 100 lenses? 
+% Since the peaks of the red curves are within 0.01 of kappa_true, I would
+% suspect that with a large number of lenses, the corresponding red curve would
+% be within 0.01 of kappa_true.  The present day goal is to get H0 to 1\%, and
+% it would be good to state somewhere that with targeted spectroscopy, one could
+% recover kext at the 1\% level with a large sample of lenses.}
 
@@
 photometric reconstruction, there is no evidence of bias, even after combining
-20 lines of sight. \tom{This result is a sanity check: if we had chosen lines of
-sight with identical $\kappah^{\rm med}$ rather than $\kappah^{\rm med}\pm0.003$ randomly
-selected lines of sight would have zero bias by construction}. If lines of sight hosting time delay lenses
-are truely random,  our method allows $\kappax$ to be reconstructed without inducing a bias\footnote{under the assumption that the universe is like the calibration simulation, and the correct stellar-mass to halo-mass relation has been used}.
+20 lines of sight. \tom{This result is a sanity check: if we had chosen lines
+of sight with identical $\kappah^{\rm med}$ rather than $\kappah^{\rm
+med}\pm0.003$ randomly selected lines of sight would have zero bias by
+construction}. If lines of sight hosting time delay lenses are truely random, 
+our method allows $\kappax$ to be reconstructed without inducing a bias (under
+the basic assumptions that the universe is like the calibration simulation,
+and the correct stellar-mass to halo-mass relation has been used).
 
@@
 We find that selecting the most tightly constrained lines of sight in this way
-does not introduce a bias: 
-our reconstruction is most accurate for the lowest
-$\kappax$ lines of sight. Combining 20 such systems the bias is at the 0.001 level.
+does not introduce a significant bias:  our reconstruction is most accurate
+for the lowest $\kappax$ lines of sight. Combining 20 such systems, the bias
+is at the 0.001 level.
 
@@
 extreme selection  of $\gammax>0.05$, and find that in this sample, $\kappax$
-would be systematically underestimated at the $\sim$0.008 level (corresponding to a
-0.8\% systematic error in distance).} 
-In the absence of other sources of uncertainty, this
-systematic error would be significant in a sample of just 5 lenses; 
-approximating strong-lens
-modelling uncertainties as an unbiased Gaussian with width 4\% on time-delay distance a 0.8\% bias would be
-significant for $\sim$20 lenses.
-This systematic error is mitigated if only
-the lines of sight with both $\gammax>0.05$ and well constrained $\pr(\kappax|\data)$ are
-used, but in this case a bias at the $\sim$0.005 level remains.
+would be systematically underestimated at the $\sim$0.008 level (corresponding
+to a 0.8\% systematic error in distance).}  In the absence of other sources of
+uncertainty, this systematic error would be significant in a sample of just 5
+lenses;  approximating strong-lens modelling uncertainties as an unbiased
+Gaussian with width 4\% on time-delay distance a 0.8\% bias would be
+significant for $\sim$20 lenses. \flag{We said 3\% earlier! Can you check for
+consistency please? And we only need to explain the Gaussian convolution
+once.} This systematic error is mitigated if only the lines of sight with both
+$\gammax>0.05$ and well constrained $\pr(\kappax|\data)$ are used, but in this
+case a bias at the $\sim$0.005 level remains.
 
@@
 
-\comments{
-We have shown that reconstructing the matter due to halos along any line of
-sight can improve the constraints on the external convergence along that line
-of sight, with, depending on sample selection,  the width of
-$\pr(\kappax|\data)$ being up to a factor of two smaller than the global
-$\pr(\kappax)$, and  we have quantified the residual bias in the $\kappax$
-estimates under our calibration assumptions. We now revisit these assumptions.
-}
+% \comments{
+% We have shown that reconstructing the matter due to halos along any line of
+% sight can improve the constraints on the external convergence along that line
+% of sight, with, depending on sample selection,  the width of
+% $\pr(\kappax|\data)$ being up to a factor of two smaller than the global
+% $\pr(\kappax)$, and  we have quantified the residual bias in the $\kappax$
+% estimates under our calibration assumptions. We now revisit these assumptions.
+% }
 
@@
 
-Filaments and voids are more difficult to model, but simple forms could in
-principle be derived from the structures found in the simulations, and
-included in the halo model in some way. Most importantly for the highest
+Clusters, filaments and voids are more difficult to model, but simple forms
+could in principle be derived from the structures found in the simulations,
+and included in the halo model in some way.  Most importantly for the highest
 $\kappax$ lines of sight will be a better group and cluster model:
@@
 group and cluster finder, and then infer halo mass from optical richness
-\citep[\eg][]{MaxBCG} in tandem with BCG stellar mass.
-
-\comments{Interestingly, we have found that it is the most empty lines of sight that 
-can be reconstructed with the highest precision. $\kappax$ estimates for empty
-lines of sight receive few contributions from halos, and a large contribution
-from voids; since they have the tightest PDFs after the reconstruction it
-seems that our model's biggest uncertainties are driven by naively
-reconstructing halos rather than neglecting voids. With a photometric
-reconstruction of the field there is a significant broadening, but the
-resulting precision is still typically 50\%  higher than using the global
-$\kappax$ distribution.
-
-Since the uncertainty on $\pr(\kappax|\data)$ is $\sim$0.01 even
-with perfect knowledge of halo mass and redshift, it seems that modelling uncertainties
-from voids, deviations from sphericity and dark matter clumping within the
-main halo dominate the total $\kappax$ uncertainty even with very
-uncertain stellar masses. Inferring halo ellipticity and dark matter
-clumping will likely always remain a difficulty for line of sight
-reconstruction; but as \Fref{fig:magcut} shows, observing deeper
-than 24th magnitude does not significantly help the reconstruction.
-}
-
-\comments{For a small fraction of lines of sight, $\pr(\kappax|\data)$ remains very
-broad even after applying our reconstruction; these lines of sight are
-typically the most over-dense lines of sight in the universe. For
-time-delay cosmography the most observationally expensive tasks are the
-light-curve monitoring and high resolution follow-up imaging and spectroscopy,
-while making photometric observations of a
-4$\times$4 arcminute patch of sky survey down to 24th magnitude is
-relatively cheap. We have shown that with a single epoch observation of
-the region around a strong lens it is possible to infer $\pr(\kappax|\data)$.
-If a line of sight has a broad $\pr(\kappax|\data)$ it can be rejected {\it
-before} the investment of follow-up. We find that
-selecting only the lines of sight with the most tightly constrained
-$\pr(\kappax)$ does not induce a bias in $\kappax$, and hence distance.
-For the most over-dense lines of sight,
-the precision of $\pr(\kappax|\data)$ is improved noticeably by the addition
-of spectroscopic information; currently insufficient time-delay systems are
-know to choose a subset based on their reconstructed $\pr(\kappax|\data)$.
-Spectroscopic coverage will definitely be useful for extracting cosmology from
-over-dense lines of sight.
-}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\comments{%
-\begin{figure}
-\includegraphics[width=\columnwidth]{figs/biasplots3.eps}
-\caption{Convergence estimation accuracy using the full  $\pr(\kappax|\kappah)$
-distribution, rather than its median.  As in \Fref{fig:biasplots}, solid,
-dashed and dotted lines show combinations of 20, 5 and 2 lines of sight
-respectively, while green lines show the inferences 
-from photometry alone, red lines from photometry and targeted spectroscopy 
-(assuming a spectroscopic redshift for all
-halos with $i<23$ and all halos within 1 arcminute and $i<24$), and blue lines
-from the unrealistic assumption of a spectroscopic redshift for all galaxies
-in the field. }
-\label{fig:no-median-tricks}
-\end{figure}
-}%
+\citep[\eg][]{MaxBCG} in tandem with BCG stellar mass. \tom{Meanwhile,
+improving the modelling of voids could be done using suggestions by
+\citet{voids2} or \citet{voids1} combined with a void finder such as in
+\citet{voids3}. Combining an advanced halo model with a void model will allow
+a direct test of the halo approximation: using real photometric data one could
+reconstruct lines of sight and compare against measured weak lensing shears.
+This would ensure that the reconstruction model reproduces the contents of the
+real universe, rather than a particular simulation.}
+
+% \comments{Interestingly, we have found that it is the most empty lines of sight that 
+% can be reconstructed with the highest precision. $\kappax$ estimates for empty
+% lines of sight receive few contributions from halos, and a large contribution
+% from voids; since they have the tightest PDFs after the reconstruction it
+% seems that our model's biggest uncertainties are driven by naively
+% reconstructing halos rather than neglecting voids. With a photometric
+% reconstruction of the field there is a significant broadening, but the
+% resulting precision is still typically 50\%  higher than using the global
+% $\kappax$ distribution.
+% 
+% Since the uncertainty on $\pr(\kappax|\data)$ is $\sim$0.01 even
+% with perfect knowledge of halo mass and redshift, it seems that modelling uncertainties
+% from voids, deviations from sphericity and dark matter clumping within the
+% main halo dominate the total $\kappax$ uncertainty even with very
+% uncertain stellar masses. Inferring halo ellipticity and dark matter
+% clumping will likely always remain a difficulty for line of sight
+% reconstruction; but as \Fref{fig:magcut} shows, observing deeper
+% than 24th magnitude does not significantly help the reconstruction.
+% }
+
+% \comments{For a small fraction of lines of sight, $\pr(\kappax|\data)$ remains very
+% broad even after applying our reconstruction; these lines of sight are
+% typically the most over-dense lines of sight in the universe. For
+% time-delay cosmography the most observationally expensive tasks are the
+% light-curve monitoring and high resolution follow-up imaging and spectroscopy,
+% while making photometric observations of a
+% 4$\times$4 arcminute patch of sky survey down to 24th magnitude is
+% relatively cheap. We have shown that with a single epoch observation of
+% the region around a strong lens it is possible to infer $\pr(\kappax|\data)$.
+% If a line of sight has a broad $\pr(\kappax|\data)$ it can be rejected {\it
+% before} the investment of follow-up. We find that
+% selecting only the lines of sight with the most tightly constrained
+% $\pr(\kappax)$ does not induce a bias in $\kappax$, and hence distance.
+% For the most over-dense lines of sight,
+% the precision of $\pr(\kappax|\data)$ is improved noticeably by the addition
+% of spectroscopic information; currently insufficient time-delay systems are
+% know to choose a subset based on their reconstructed $\pr(\kappax|\data)$.
+% Spectroscopic coverage will definitely be useful for extracting cosmology from
+% over-dense lines of sight.
+% }
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \comments{%
+% \begin{figure}
+% \includegraphics[width=\columnwidth]{figs/biasplots3.eps}
+% \caption{Convergence estimation accuracy using the full  $\pr(\kappax|\kappah)$
+% distribution, rather than its median.  As in \Fref{fig:biasplots}, solid,
+% dashed and dotted lines show combinations of 20, 5 and 2 lines of sight
+% respectively, while green lines show the inferences 
+% from photometry alone, red lines from photometry and targeted spectroscopy 
+% (assuming a spectroscopic redshift for all
+% halos with $i<23$ and all halos within 1 arcminute and $i<24$), and blue lines
+% from the unrealistic assumption of a spectroscopic redshift for all galaxies
+% in the field. }
+% \label{fig:no-median-tricks}
+% \end{figure}
+% }%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 ensemble, is reminiscent of the procedure followed by \citet{SuyuEtal2010},
-and Greene et al (submitted). The reconstruction method presented here 
-can be seen as the
-limiting case of the weightings explored by Greene et al: rather than using
-weighted number counts in an aperture, we treat each galaxy individually, and
-predict $\kappa_{\rm h,obs}^{\rm med}$ for use in their place. \flag{How much more precise are we than Greene et al?}
-
-\comments{ One
-significant disadvantage of these types of method is that they impose a
-bottleneck in the flow of information. Once you have compressed to one number,
-it is difficult to incorporate more information later; you have to recompute
-all the calibrations. Using the full PDF for $\kappah$ is the more correct
-thing to do: at present, however, it suffers from significant bias in the
-photometric data case. \Fref{fig:no-median-tricks} shows how $\kappax$ is
-overestimated, as a result of the high scatter in halo mass for objects with 
-high stellar mass. As has already been noted, 
-future work should focus on increasing the precision of the halo
-mass estimates. 
-}
+and Greene et al (submitted). The reconstruction method presented here  can be
+seen as the limiting case of the weightings explored by Greene et al: rather
+than using weighted number counts in an aperture, we treat each galaxy
+individually, and predict $\kappa_{\rm h,obs}^{\rm med}$ for use in their
+place. \flag{How much more precise are we than Greene et al?}
+
+% \comments{ One
+% significant disadvantage of these types of method is that they impose a
+% bottleneck in the flow of information. Once you have compressed to one number,
+% it is difficult to incorporate more information later; you have to recompute
+% all the calibrations. Using the full PDF for $\kappah$ is the more correct
+% thing to do: at present, however, it suffers from significant bias in the
+% photometric data case. \Fref{fig:no-median-tricks} shows how $\kappax$ is
+% overestimated, as a result of the high scatter in halo mass for objects with 
+% high stellar mass. As has already been noted, 
+% future work should focus on increasing the precision of the halo
+% mass estimates. 
+% }
 
@@
 used the relative over-density to mitigate this effect, but it does not
-completely remove the dependence on simulation.
-
-\tom{ Future work should focus on two areas:
-reducing the dependance on simulations; and,
-improving the modeling of dark structures and voids. The analysis should be repeated with different 
-simulations and differrent stellar-mass to halo-mass relations, cross-checking that 
-using the wrong simulation simulation or relation does not induce a systematic error.
-Improving the modelling of of voids could be done using the void models of \citet{voids2}
-or \citet{voids1} combined with a void finder such as in \citet{voids3}.
-Combining the halo model with a void model may allow a direct test of the 
-halo approximation; using real photometric data one could reconstruct lines of sight
-and compare against measured weak lensing shears. This would ensure that the halo model reproduces the
-contents of the real universe, rather than a particular simulation.}
-
-\comments{In particular, the method presented here is tied to the simulations at two
-points: the prior PDF for $\kappah$, and the conditional distribution
-$\pr(\kappax|\kappah)$ used to convert halo model convergence to total
-convergence. The first tie could potentially be avoided if the halo mass
-estimation gave rise to a reasonable $\pr(\kappah|\data)$ on its own.
-Possibilities for improving the precision of the halo mass estimation are
-discussed above. The second tie is more difficult, since breaking it means
-modelling the unseen mass structures and voids. It
-should be possible to infer hierarchically  the parameters of a flexible model
-for these things from the data itself, as demonstrated by
-\citet{KarpenkaEtal2012} (albeit under the assumption of scatter-free scaling
-relations) -- how this affects the cosmographic precision is to be
-investigated. When working with wide field imaging surveys,  weak lensing shears will be
-available around every line of sight:  fitting these with the halo models
-described here in order to constrain the hyper-parameters of the model presents a 
-possible test of our halo model prescription against real observations.
-}
+completely remove the dependence on simulation. Future work should include
+investigating the robustness of the reconstruction to these systematic errors.
+
+% \comments{In particular, the method presented here is tied to the simulations at two
+% points: the prior PDF for $\kappah$, and the conditional distribution
+% $\pr(\kappax|\kappah)$ used to convert halo model convergence to total
+% convergence. The first tie could potentially be avoided if the halo mass
+% estimation gave rise to a reasonable $\pr(\kappah|\data)$ on its own.
+% Possibilities for improving the precision of the halo mass estimation are
+% discussed above. The second tie is more difficult, since breaking it means
+% modelling the unseen mass structures and voids. It
+% should be possible to infer hierarchically  the parameters of a flexible model
+% for these things from the data itself, as demonstrated by
+% \citet{KarpenkaEtal2012} (albeit under the assumption of scatter-free scaling
+% relations) -- how this affects the cosmographic precision is to be
+% investigated. When working with wide field imaging surveys,  weak lensing shears will be
+% available around every line of sight:  fitting these with the halo models
+% described here in order to constrain the hyper-parameters of the model presents a 
+% possible test of our halo model prescription against real observations.
+% }
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \item Selecting from the highest precision 33\% of the reconstructed lines of
-sight results in a sample with low bias, $\sim$0.1\% in terms of the time-delay
-distance. \tom{For these lines of sight the reconstructed $\pr(\kappax)$ induce 
-a statistical uncertainty of $\sim$1\% on individual time-delay distances}
+sight results in a sample with low bias, $\sim$0.1\% in terms of the
+time-delay distance. \tom{For these lines of sight the reconstructed
+$\pr(\kappax|\data)$ induces a statistical uncertainty of $\sim$1\% on
+individual time-delay distances.}
 

### 2012-12-04 doc/references.tex
acted on phils comments
response to Tom's edits

@@
 
+\bibitem[Foster 
+\& Nelson(2009)]{voids3} Foster, C., \& Nelson, L.~A.\ 2009, \apj, 699, 1252
+
 \bibitem[Gavazzi et al.(2007)]{GavazziEtal2007} Gavazzi, R., Treu, T., 
@@
 Dahl{\'e}n, T., Goobar, A., J{\"o}nsson, J., M{\"o}rtsell, E.\ 2006, \apj, 640, 417
+
+\bibitem[Higuchi et al.(2012)]{voids1} Higuchi, Y., Oguri, M., 
+\& Hamana, T.\ 2012, arXiv:1211.5966
 
@@
 Sheldon, E.~S., Wechsler, R.~H., et al.\ 2007, arXiv:0709.1159
+
+\bibitem[Krause et al.(2012)]{voids2} Krause, E., Chang, 
+T.-C., Dor{\'e}, O., \& Umetsu, K.\ 2012, arXiv:1210.2446
 
@@
 
+\bibitem[\protect\citeauthoryear{Wyithe et al.}{2011}]{WyitheEtal2011} Wyithe, J.~S.~B., Yan, 
+H., Windhorst, R.~A., \& Mao, S.\ 2011, \nat, 469, 181
+
 % \bibitem[\protect\citeauthoryear{\tom{which paper}}{{9999}}]{xxx} 

### 2012-12-06 doc/paper-lcr.tex
finalized draft

@@
 \newauthor{%
-  Sherry~H.~Suyu$^{4}$,
+  Sherry~H.~Suyu$^{3,4}$,
   Zachary~Greene$^{4}$,
@@
 values:  taking into account realistic uncertainties on redshift and stellar
-masses, \phil{we find that the reconstruction provides an improvement in
-precision of 50\% over the global $\pr(\kappax)$.} 
+masses, \tom{we find that the reconstruction of $\kappax$ provides an improvement in
+precision of $\sim$50\% over previously published schemes.} 
 %
 We find that the lowest $\kappax$ lines of sight have the best constrained 
-$\pr(\kappax)$. We find that selecting the third of the systems with the
+$\pr(\kappax)$. In anticipation of future samples with thousands of lenses,
+we find that selecting the third of the systems with the
 highest precision $\kappax$ estimates gives a  sub-sample of unbiased time
@@
 %
-\phil{Conversely, we show that somehow preferentially selecting lines of sight
+\phil{Conversely, we show that somehow selecting lines of sight
 with high external shear could, with the reconstruction model presented here,
@@
 \ee
-\citet{HilbertEtal2009} found this approximation was found to be accurate to a few percent or better
+\citet{HilbertEtal2009} found that this approximation is accurate to a few percent or better
 in $\kappax$, even on 30 arcsecond scales.
@@
 contribution to the total $\kappax$ along the line of sight \citep[as in
-\eg][]{GunnarssonEtal2006,WongEtal2011,KarpenkaEtal2012}.  This mass
+\eg][]{GunnarssonEtal2006,KarpenkaEtal2012}.  This mass
 assignment recipe will be uncertain, and also incomplete, but it can be
@@
 \citep[\eg][]{AugerEtal2010} due to the more concentrated stellar mass
-component; however, at radii of tens of kpc (tens of arcsec), we expect the
-halo density profile to be dark matter dominated, and fall off faster than
-$r^{-2}$. This has been confirmed by galaxy-galaxy weak lensing measurements 
+component.
+This has been confirmed by galaxy-galaxy weak lensing measurements 
 \citep[\eg][]{Mandelbaum,Leauthaud}. We note that the two halo term that
@@
 into account in our model, where every galaxy is assigned a dark matter halo.
+At large radii an NFW-like profile is probably appropriate, but may not be
+correct when a halo is very close to the line of sight.
 
@@
 estimate of $\kappax$, since the halo model's $\kappah$ can only be positive.
-In principle the absence of galaxies implies something about the presence a
+In principle the absence of galaxies implies something about the presence of a
 void, but we do not currently attempt to use this information. In general, it
@@
 This procedure of reducing the full PDF for $\kappah$ to its median increases
-the importance of the realism of the simulation: the simulation needs to be a
+the importance of the realism of the simulation: the simulation needs to be as
 similar as possible to the real universe or there is a possibility of
@@
 and assuming noise-free halo masses and redshifts. 
-\phil{(In this case, $\pr(\kappah|\data)$ is almost delta function since the only uncertainty is halo
+\phil{(In this case, $\pr(\kappah|\data)$ is almost a delta function since the only uncertainty is halo
 concentration, which has minimal effect on $\pr(\kappah|\data)$.  
@@
 
-We now move on to consider the halo model reconstruction of line of sight mass
+We now move on to consider the halo model reconstruction of line-of-sight mass
 distributions given noisy astronomical observables. A typical imaging survey
@@
 and redshifts, we can infer a sample $\kappah$ using the \proceedure of
-\Sref{sec:model}; repeatedly drawing samples allows us to
+\Sref{sec:model}. Repeatedly drawing samples allows us to
 estimate $\pr(\kappah|\data)$ for each reconstructed line of sight. We then
@@
 likely to be at the 3-4\% level \citep{SuyuEtal2010}, convolving
-$\mathcal{P}_N$ with a Gaussian of width $0.03/\sqrt{N}$ is a reasonable
+$\mathcal{P}_N$ with a Gaussian of width $0.04/\sqrt{N}$ is a reasonable
 approximation for the likely final uncertainty on time-delay distance.}
@@
 uncertainty, this systematic error would be significant in a sample of just 5
-lenses;  approximating strong-lens modelling uncertainties as an unbiased
-Gaussian with width 4\% on time-delay distance a 0.8\% bias would be
-significant for $\sim$20 lenses. \flag{We said 3\% earlier! Can you check for
-consistency please? And we only need to explain the Gaussian convolution
-once.} This systematic error is mitigated if only the lines of sight with both
+lenses; when including other time-delay distance uncertainties a 0.8\% bias would be
+significant for $\sim$20 lenses. This systematic error is mitigated if only the lines of sight with both
 $\gammax>0.05$ and well constrained $\pr(\kappax|\data)$ are used, but in this
@@
 
-While $\gammax>0.05$) is likely to be a much stronger selection than would
+While $\gammax>0.05$ is likely to be a much stronger selection than would
 occur in reality, it is  nevertheless worth noting from this example that the
@@
 induce a bias. A more sophisticated model that includes the shear recovered
-from the lens modelling may be less susceptible to this bias.
+from the lens modelling might be less susceptible to this bias.
 
@@
 disentangle external and internal shear \citep[\eg][]{SuyuEtal2010}, but there
-are still significant uncertainties: \citet{WongEtal2011} attempted to match
+are still significant uncertainties. \citet{WongEtal2011} attempted to match
 the shear from strong lens models with a reconstruction of the local lens
@@
 is unclear whether the external shear from lens models can be reconciled with
-a line of sight reconstruction. Alternatively, it may be possible  to infer
+a line-of-sight reconstruction. Alternatively, it may be possible  to infer
 external shear using weak lensing information from near the line of sight.  If
@@
 where dark mass is assigned to both galaxy-scale halos and halos for the
-groups and clusters they occupy: to make this work, one could incorporate a
+groups and clusters they occupy. To make this work, one could incorporate a
 group and cluster finder, and then infer halo mass from optical richness
@@
 individually, and predict $\kappa_{\rm h,obs}^{\rm med}$ for use in their
-place. \flag{How much more precise are we than Greene et al?}
+place. Given photometry alone, our reconstruction represents a $\sim$50\% improvement of
+the precision compared the number counts used in \citet{SuyuEtal2010}. Greene et al.
+made important progress for the most over-dense lines of sight; our
+reconstructions are $\sim$30\% more precise than those of Greene et al.
 

### 2013-02-27 doc/response.txt
draft update

Author's reply to Reviewer's Comments:

Dear Reviewer,

Thankyou for taking the time to review our paper, below are our replies (and a
summary of the actions taken) to each of your points. To aid you in finding
the changes, all of them are shown in bold face in the new manuscript.

1. The paper does not describe the resolution of the convergence maps
from the simulation.  The only number quoted is 30 arcseconds, which
(hopefully!) is not the resolution of the maps.  For example, the
convergence power spectrum peaks on arcminute scales, even neglecting
baryonic effects which only increase small-scale power. Therefore a 30
arcsecond resolution would be woefully inadequate for the purposes of
this study.  The authors should describe their simulations in more
detail, and discuss what fraction of the convergence power is
unresolved by their simulations.

# We have updated section 3.1 to state the resolution of our simulations,
and explain why it should be sufficient for our purposes.

2. My main concern about this work is that the halo occupation
distribution is assumed to be known.  As mentioned in the final
paragraph of the paper, this is a severe limitation which makes it
difficult to assess the validity of the claimed results. In reality,
uncertainties in the HOD will lead to uncertainties in the
reconstruction, and the authors should provide some estimate of these
errors.  For example, the authors could provide an example in which
the "wrong" HOD is assumed, and then compute the resulting errors in
the convergence reconstruction.  One easy example of this could be to
use the stellar masses from the Millennium catalog, which were
discarded in favor of the model of Behroozi et al.

# We agree that this is an important systematic. We have implemented the
suggested test. Swapping Behroozi stellar masses for the Millenium catalogue's
stellar masses, is an extreme change (the catalogue's stellar masses are
unreasonable) but it results in offsets of ~0.015 in kappa for
individual lines of sight. For the ensemble, there is no change in the mean
reconstructed kappa. We have added a discussion of this in section 8.

3. The halo model used in this paper in not described adequately.  For
example, the paper notes that the SHAM model of Behroozi et al. was
adopted for this work, but the paper is overly vague in describing the
implementation.  For example, there is no discussion of how satellites
are treated.  In the absence of any spatial information, a random
galaxy has a significant probability to be either a central galaxy in
a low mass halo, or a satellite in an even lower-mass subhalo inside a
much larger halo.  Is local spatial information ignored in assigning
probabilities for galaxies to be central or satellite?  If so, the
reconstruction will clearly be suboptimal.  For satellites, how are
the subhalo properties assigned?  Their masses and sizes depend on
their location within the host halo.  What properties are assigned to
the host halos of satellites?  Is it assumed that the host halos
(e.g. clusters or groups) have properties determined from their own
central galaxies (e.g. BCGs)?  This may be overly optimistic, as
significant spatial offsets are frequently found between BCG location
and cluster center.  The SHAM model used here must be described in
greater detail.

# We have clarified the details of our halo model in Section 6.1 (new text is shown in bold font). As we now explain, we do not discriminate between satellites and centrals at all.  As you say, this will be sub-optimal, and is one of the areas we are looking to improve upon in further work. However, we do find that it is rare for satellites to contribute a large amount to the total convergence of a line of sight, and have quantified this in the text. Hence, we do not expect this to be a very large source of uncertainty, compared to the choice of M*-Mhalo relation,  and the calibration simulation.

#We neglected to mention the offsets between halo centre and BCG. We have now
mentioned this but it is unlikely to be significant: most of the impact factors
are much greater than typical spatial offsets.

Finally, I have a very minor comment.  In equation (6), it appears
that the mean density of the universe is not subtracted when
estimating kappa_h.  I did not understand why not.

# kappa_h is used as a tracer of kappa_ext, and the integral in equation (7)
converts kappa_h into kappa_ext. Subtracting the mean density of the universe
decreases all values of kappa_h by something akin to the projected mean
density of the universe devided by an effective critical density. Because
subtracting the mean density is a simple transformation in kappa_h the
resulting kappa_ext values do not change (as long as one remembers to
treat the calibration sightlines in the same way as the 'real' sightline).

#Additionally, we have swapped green for black in figures 8 and 9, to make them
clearer in black and white.

We are grateful for the improvements that your comments have made to the paper.
Regards,
Tom Collett (et al.)

### 2013-02-27 doc/paper-lcr.tex
finalized draft
draft update

@@
 \newauthor{%
-  Sherry~H.~Suyu$^{3,4}$,
+  Sherry~H.~Suyu$^{4,3}$,
   Zachary~Greene$^{4}$,
@@
 time delay gravitational lenses, ``external convergence,'' $\kappax$, can
-dominate the uncertainty in the inferred distances. In this paper we attempt
-to reconstruct $\kappax$, due to line of sight structure using a simple halo
+dominate the uncertainty in the inferred distances and hence cosmological parameters.
+ In this paper we attempt
+to reconstruct $\kappax$, due to line of sight structure, using a simple halo
 model.
@@
 We use mock catalogues from the Millennium Simulation, and calibrate and 
-compare our reconstructed $\pr(\kappax|\data)$ to ray-traced $\kappax$ truth
-values:  taking into account realistic uncertainties on redshift and stellar
-masses, \tom{we find that the reconstruction of $\kappax$ provides an improvement in
-precision of $\sim$50\% over previously published schemes.} 
+compare our reconstructed $\pr(\kappax)$ to ray-traced $\kappax$ ``truth''
+values; taking into account realistic uncertainties on redshift and stellar
+masses. \tom{We find that the reconstruction of $\kappax$ provides an improvement in
+precision of $\sim$50\% over galaxy number counts.} 
 %
-We find that the lowest $\kappax$ lines of sight have the best constrained 
+We find that the lowest-$\kappax$ lines of sight have the best constrained 
 $\pr(\kappax)$. In anticipation of future samples with thousands of lenses,
@@
 delay distance measurements \phil{with (on average) just} 1\% uncertainty due
-to line of sight external convergence effects. Photometric data alone is
+to line of sight external convergence effects. Photometric data alone are
 sufficient to pre-select the best-constrained lines of sight, and can be done
@@
 %
-\phil{Conversely, we show that somehow selecting lines of sight
+\phil{Conversely, we show that selecting lines of sight
 with high external shear could, with the reconstruction model presented here,
@@
 strong lens modelling, additional information is required. Weak lensing measurements
-can been used for rich lines of sight \citep{NakajimaEtal2009, FadelyEtal2009}, but 
+can be used for rich lines of sight \citep{NakajimaEtal2009, FadelyEtal2009}, but 
 for lines of sight with low galaxy density we must attempt to reconstruct the distribution
@@
 lens fields have focused on understanding the external shear which seems to be large in most strong lenses.
-Surveys by \citet{Fassnacht+Lubin2002,AugerEtal2007,WilliamsEtal2006,MomchevaEtal2006}
+Surveys by \citet{Fassnacht+Lubin2002,AugerEtal2007,WilliamsEtal2006,MomchevaEtal2006,FassnachtEtal2006}
 all found groups of galaxies hosting or near to known gravitational lenses.
+Is generally found that lens galaxies, reside in overdense environments,
+indistinguishable from those occupied by similarly massive galaxies \citep{Auger2008,TreuEtal2009}
 \citet{WongEtal2011} estimated $\Pr(\gammax)$ given the data of \citet{WilliamsEtal2006}
@@
 distributions. \citet{Holder+Schechter2003} and \citet{DalalEtal2005} carried
-out ray-tracing calculations in N-body simulations to estimate the
+out ray-tracing calculations in N-body simulations \citep{KauffmannEtal1999,WambsganssEtal2004} to estimate the
 distribution of external shear values.  \citet{HilbertEtal2009} performed
@@
 In a companion paper to this one, Greene et al. (submitted) investigate
-improvements to this method by weighting the galaxy counts by galaxy
-mass, and perpendicular distance to the line of sight, again using the
+improvements to this method by weighting the galaxy counts by observables
+including galaxy luminosity and perpendicular distance to the line of sight, again using the
 \MS mock catalogues and their associated $\kappax$ values to construct
@@
 In this paper, we combine the halo model reconstruction approach of
-\citeauthor{GunnarssonEtal2006}, \citeauthor{JonssonEtal2010}, 
-\citeauthor{WongEtal2011} and others, with the
-idea of calibrating to simulations from \citeauthor{SuyuEtal2010}
+\citet{GunnarssonEtal2006}, \citet{JonssonEtal2010}, 
+\citet{WongEtal2011} and others, with the
+idea of calibrating to simulations from \citet{SuyuEtal2010}
 Taking the $\kappax$ values from
-\citeauthor{HilbertEtal2009}'s ray-tracing calculations as the ``truth''
+\citet{HilbertEtal2009}'s ray-tracing calculations as the ``truth''
 that we have to recover, we use the \MS mock galaxy catalogues first to
-{\it calibrate} the reconstruction, and account for unseen mass and
+{\it calibrate} the reconstruction and account for unseen mass and
 voids, and then to {\it test} the accuracy of the line of sight mass
@@
 generate Monte Carlo sample line of sight mass distributions, and so
-construct the PDF $\Pr(\kappax|\data)$ for that field. We then emulate
+construct the probability distribution function (PDF) $\Pr(\kappax|\data)$ for that field.
+We then emulate
 the combination of many such PDFs to quantify the residual bias that
@@
 form of a mass-sheet) along the line of sight has no observable effect except
-to rescale the time-delays. As such, it is necessary to include $\kappax$ in
-the lens modelling, if cosmological parameters are to be estimated accurately
+to rescale the time-delays and magnifications. As such, it is necessary to include $\kappax$ in
+the lens modelling if cosmological parameters are to be estimated accurately
 and precisely from observed time delays \citep{SuyuEtal2010}.
@@
 lens modelling, then the time delay distance -- inferred assuming $\kappax
-= 0$ -- will be $(1-\kappax)$ more than the true value of $\Dt$:
+= 0$ -- will be $(1-\kappax)$ more than the true value of the time-delay distance $\Dt$:
 \be 
@@
 
-Mass distributions that are physically associated with the lens galaxy will
-affect the stellar dynamics of the lens galaxy, so that dynamical observations
-can break the internal mass-sheet degeneracy by providing an additional
-estimate of the lens galaxy's mass
-\citep[e.g.,][]{Koopmans2004,SuyuEtal2010}.  Our aim is to quantify the
-lensing effect of massive objects, regardless of their position along the line
-of sight. \phil{However, in this paper we restrict ourselves to reconstructing
-the line of sight portion of the mass distribution in any given field, which
-allows us to work in the weak lensing regime. Treatment of sightlines
-containing strong lensing events, and the impact of physically-associated mass
-distributions on both the strong lensing and stellar dynamical effects are
-postponed to further work.}
+Dynamical observations of the lens galaxy
+can help break the mass-sheet degeneracy by providing an additional
+estimate of the lens's mass
+\citep[e.g.,][]{KoopmansEtal2003,Koopmans2004,SuyuEtal2010}. This constraint 
+is useful in excluding the high convergence tails that are often present in 
+PDFs for convergence - we do not include dynamical constraints in our analysis.
+
+In this paper we restrict ourselves to reconstructing
+the line of sight portion of the mass distribution in any given field, {\it our lines of sight do not include a strong lens} which allows us to work in the weak lensing regime.
+
+The impact of weak-lensing perturbations on strong lensing lines-of-sight is
+postponed to further work.
 
@@
 \ee
-\citet{HilbertEtal2009} found that this approximation is accurate to a few percent or better
-in $\kappax$, even on 30 arcsecond scales.
+\citet{HilbertEtal2009} found that this approximation is accurate to a percent level
+in $\kappax$, even on 30 arcsecond scales. This accuracy sufficient for our analysis, but 
+the approximation may need re-visiting in future work.
 
@@
 line of sight, $\kappax^{\rm true}$.
+
+\new{The adaptive smoothing of the matter in the \MS results in a spatial resolution of $\sim 5\,\text{kpc}$ comoving in the densest regions, and $\sim10\,\text{kpc}$ on average.
+This resolution is sufficient to capture most of the variance in the convergence \citep{TakahashiEtal2011}.
+Moreover, we seek to estimate the component of the convergence that is smooth on the angular scales of typical strong galaxy-scale lens systems ($\sim 1\,\text{arcsec}$).
+Any variations of the external convergence on smaller scales can be directly recovered from the resulting image distortions in the lens modelling.}
 
@@
 halo masses and redshifts, which we will use to calibrate the reconstruction,
-and also to explore any sources of bias and scatter. Since the true
+and also to explore any sources of bias and scatter. Since the ``true''
 convergence is that of only the dark matter, we focus on reconstructing the
@@
 Cosmological dark matter simulations have shown that dark matter
-halos are well-approximated by NFW profiles 
+halos are reasonably well-approximated by NFW profiles 
 \citep{NFW}. We assume each halo to have a spherical mass distribution with 
@@
 This has been confirmed by galaxy-galaxy weak lensing measurements 
-\citep[\eg][]{Mandelbaum,Leauthaud}. We note that the two halo term that
+\citep[\eg][]{Mandelbaum,GavazziEtal2007}. We note that the two halo term that
 dominates the galaxy-galaxy lensing signal at large radii is explicitly taken
@@
 To estimate a halo's contribution to $\kappah$ we must first know the
-halo's mass. For the lines of sight of the \MS, halo masses are
+halo's mass \new{and position. The stellar mass
+and host halo are not necessarily concentric, especially for central
+galaxies of giant clusters, but our reconstruction assumes the dark matter halo is centred on
+the visible galaxy.} For the lines of sight of the \MS, halo masses are
 known, but for  real lines of sight the halo masses have to be \infered
-from whatever data is available. 
+from whatever data are available. 
 In this work we investigate the use of the empirical stellar mass --
@@
 along each selected line of sight, and then
-accumulating $\kappah$ and $\kappax$
-along a large number of such sightlines. 
+accumulating $\kappah$, $\kappax$ pairs
+for a large number of such sightlines. 
 For any given line of sight we can then estimate
@@
 investigate the primary sources of the convergence. It will also provide us
-with a measure of the intrinsic uncertainty introduced by our assumption of
-all illuminated halos being spherically-symmetric truncated NFW halos with
-Neto et al concentration--mass relation.
+with a measure of the intrinsic uncertainty introduced by our assumptions of
+all illuminated halos being spherically-symmetric truncated NFW halos following the
+Neto et al concentration--mass relation \new{and of visible galaxies being concentric with their host halos}.
 
@@
 and assuming noise-free halo masses and redshifts. 
-\phil{(In this case, $\pr(\kappah|\data)$ is almost a delta function since the only uncertainty is halo
+\phil{In this case, $\pr(\kappah|\data)$ is almost a delta function since the only uncertainty is halo
 concentration, which has minimal effect on $\pr(\kappah|\data)$.  
-)}.
+}
 % In this case, the PDF : we can read
@@
 sample of lines of sight, while dashed and dot-dashed show the ranges enclosing 68
-and 95 percent of the lines of sight respectively.}
+and 95 percent of the lines of sight respectively. The source is at redshift 1.4.}
 \label{fig:where}
@@
 In an ensemble of $10^{5}$ reconstructed lines of sight, we find the mean bias
-to be $-1\times 10^{-5}$, and the mean width to be 0.01. This is approximately
+to be $-1\times 10^{-5}$, and the mean width to be 0.01. This is
 1.8 times smaller than the width of the global $\pr(\kappax)$.  We find that
@@
 $\pr(\kappax|\data)$ inferred from reconstructions of  $10^{5}$ lines of
-sight  produces a distribution of $\kappax$ values over the sky identical to
+sight  produces a distribution of $\kappax$ values over the sky nearly identical to
 the global $\pr(\kappax)$. Given perfect knowledge of halo mass and redshift
 then, the calibration \proceedure provides an unbiased estimate of $\kappax$
-that is $1.8$ times as precise as using the global $\pr(\kappax)$. 
+that is $1.8$ times more precise than using the global $\pr(\kappax)$. 
 \phil{This is the maximum precision we can obtain using the current calibrated
@@
 the convergence. Objects fainter than $i=24$ are too small to be important,
-unless they are extremely close to the line of sight, but we find that
+unless they are extremely close to the line of sight; we find that
 including halos fainter than $i=24$ does not improve the reconstruction. 
@@
 $\kappah$ onto $\kappax$. Halos at all redshifts out to the source redshift
-(1.4, here) contribute to the convergence, but the largest contribution comes
+(1.4 in this work. The redshift of the source in B1608+656) contribute to the convergence, but the largest contribution comes
 from halos with $z \sim z_{\rm source}/2$.
@@
 mass to each halo in the \MS catalogues, according to the empirical stellar
-mass--halo mass relation of \citet{BehrooziEtal2010}. From these we simulate
+mass--halo mass relation of \citet{BehrooziEtal2010}. \new{When assigning stellar
+masses we have treated satellites in the same way as central halos; in the real
+universe both the density profile and the stellar mass--halo mass relation are
+likely different for satellites and centrals, but our simple model does not include
+these effects}. From these we simulate
 observed stellar masses by drawing samples from  $\pr(\log{M^{*}_{\rm
@@
 Gaussian of width $0.1(1+z_{\rm spec})$ centred on $z_{\rm spec}$, where
-$z_{\rm spec}$ is the halo's true redshift in the \MS catalogue.
+$z_{\rm spec}$ is the halo's true redshift in the \MS catalogue. \new{In our mock catalogues 
+we have used the galaxy position from the \MS; this is not necessarily coincident with the
+centre of the galaxy's host dark matter halo.}
 
@@
 \includegraphics[width=\columnwidth]{figs/Width.eps}
-\caption{The widths of the \infered PDFs $\pr(\kappah|\data)$ for
+\caption{The widths of the \infered PDFs $\pr(\kappax|\data)$ for
 $10^5$ lines of sight, given different quality of data. 
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figs/Widthvshilberrt.eps}
+\includegraphics[width=\columnwidth]{figs/WidthvsHilbert.eps}
 \caption{Width of the \infered PDF $\pr(\kappax|\data)$ as a function of 
 the true convergence, $\kappaxtrue$, for two different data qualities. 
-Green assumes only photometric redshifts for all objects,
-while red assumes a campaign of targeted spectroscopy.}
+Black assumes only photometric redshifts for all objects,
+while red assumes a campaign of targeted spectroscopy. The region between the
+solid (dashed) lines contains 68\% (95\%) of lines-of-sight.}
 \label{fig:widthsvsH}
@@
 we find that the $\pr(\kappax|\data)$ would be almost as precise as that from
-having complete spectroscopic coverage (\Fref{fig:reconwidths}).
+having complete spectroscopic coverage (\Fref{fig:reconwidths}). If any object is
+extremely close to the lines of sight our approximation of weakly lensing
+mass-sheets will break down; also, neglecting baryonic effects will also be a poor
+approximation; a spectrum will be needed
+to adequately model systems with very well alligned pertrubers.
 Consistent with our previous findings, the lowest $\kappax$ lines of
@@
 deviations from zero represent biases. The solid, dashed and dotted lines
-correspond to combinations of  20, 5 and 2 sightlines respectively. Green
+correspond to combinations of  20, 5 and 2 sightlines respectively. Black
 lines show the results \infered from photometry alone, whilst red lines show
@@
 of sight with identical $\kappah^{\rm med}$ rather than $\kappah^{\rm
-med}\pm0.003$ randomly selected lines of sight would have zero bias by
+med}\pm0.003$, randomly selected lines of sight would have zero bias by
 construction}. If lines of sight hosting time delay lenses are truely random, 
@@
 empty lines of sight.  However, 
-since lenses are typically found in locally over-dense
+since lenses are typically massive galaxies and hence found in locally over-dense
 environments, it is unlikely that  an almost empty line of sight would
@@
 sight. \citet{SuyuEtal2012} found that in the case of 
-RXJ1131, combining shear constraints
+RXJ1131-1231, combining shear constraints
 with galaxy number count over-density gave a significantly different
@@
 \label{eq:shearineq}
-|{\boldmath{\gammax}-\boldmath{\gamma_{\mathrm{h}}}}| < \mathrm{0.025}
+|{\pmb{\gamma}_{\mathrm{ext}}-\pmb{\gamma}_{\mathrm{h}}}| < \mathrm{0.025}
 \ee 
@@
 galaxy mass distributions. Galaxy-galaxy and cluster-galaxy  lensing studies
-\citep[\eg][]{GavazziEtal2007,JohnstonEtal2007} also suggest an approximately
+\citep[\eg][]{GavazziEtal2007,JohnstonEtal2007, LagattutaEtal2010} also suggest an approximately
 isothermal profile for the mass-shear correlation function; however, at large
@@
 do not expect this to have a big impact on the reconstructions. Likewise, 
-halo ellipticity may have some small effect on the predicted convergence. It
+halo ellipticity
+may have some small effect on the predicted convergence. It
 is possible that baryonic physics may alter the radial profile of dark
@@
 group and cluster finder, and then infer halo mass from optical richness
-\citep[\eg][]{MaxBCG} in tandem with BCG stellar mass. \tom{Meanwhile,
+\citep[\eg][]{MaxBCG} in tandem with BCG stellar mass. \new{A group finder would also
+allow us to identify central and satellites galaxies; in this work we have neglected
+the differences between central halos and satellites. However, given perfect knowledge of halo masses
+we found that only in 5 percent of sightlines do satellites
+contribute over 20 percent of the sightline's total $\kappax$. Introducing a group finder
+is unlikely to provide major improvement to the reconstruction of satellites.}
+\tom{Meanwhile,
 improving the modelling of voids could be done using suggestions by
@@
 reconstructions are $\sim$30\% more precise than those of Greene et al.
+The use of relative overdensities by Suyu et al. and Greene et al. may decrease 
+their sensitivity to the choice of calibration simulation; this work's use of
+absolute convergence may be less robust to changes in the calibration simulation.
 
@@
 used the relative over-density to mitigate this effect, but it does not
-completely remove the dependence on simulation. Future work should include
+completely remove the dependence on simulation. \new{Throughout this work, we assumed
+that the stellar mass--halo mass relation used for the reconstruction is the stellar mass--halo mass
+relation followed by the real universe. We discarded the stellar masses from the Millenium Catalogue
+due to a large number of excessively stripped satellite galaxies, however if we use these stellar masses
+there is no systematic change in the ensemble, but reconstructed $\kappax$ differs by $\sim 0.015$ for individual lines of sight. The effect is smaller ($\sim 0.008$)
+for the lowest $\kappax$ lines of sight, and larger ($\sim 0.02$) for high shear lines of sight. This 
+change of stellar masses is extreme but demonstrates that using the wrong stellar mass--halo mass relation
+can significantly degrade the quality of inference.} Future work should include
 investigating the robustness of the reconstruction to these systematic errors.
@@
 $\kappax$ estimates. This will be useful in an era when there are more known
-lenses than can be followed-up.
-
-\item  Photometric data is sufficient to select the best lines of sight for
+lenses than can be followed-up. Photometric data are sufficient to select the best lines of sight for
 follow-up. Spectroscopic coverage helps to tighten  $\pr(\kappax|\data)$ for
-high $\kappax$ lines of sight.
+most lines of sight.
 % , but is of less use for low $\kappax$ lines of
@@
 
-\item Conversely, selecting lines of sight with high shear ($|\gamma| > 0.05$
-(a somewhat extreme selection, but one that  could potentially arise from 
+\item Conversely, selecting lines of sight with high shear ($|\gamma| > 0.05$; 
+a somewhat extreme selection, but one that  could potentially arise from 
 focusing on four-image or wide separation lenses) results in a sample with
-bias of 0.8\% in time delay distance. Including realistic estimates of other
+bias of 0.8\% in time delay distance (and hence $H_0$). Including realistic estimates of other
 sources of uncertainty a systematic error of 0.8\% would become significant in
-a sample of $\sim$20 lenses.
+a sample of $\sim$20 lenses. The addition of shear constraints to our model might
+alleviate this potential systematic.
 

### 2013-02-27 doc/references.tex
finalized draft
draft update

@@
   {Squires}, G.~K. 2007, \aj, 134, 668
+
+\bibitem[Auger(2008)]{Auger2008} Auger, M.~W.\ 2008, \mnras, 383, 
+L40
 
@@
 
+\bibitem[Fassnacht et al.(2006)]{FassnachtEtal2006} Fassnacht, C.~D., 
+Gal, R.~R., Lubin, L.~M., et al.\ 2006, \apj, 642, 30
+
 \bibitem[\protect\citeauthoryear{Fassnacht, Koopmans, 
@@
 
+\bibitem[Karpenka et al.(2012)]{KarpenkaEtal2012} Karpenka, N.~V., 
+March, M.~C., Feroz, F., \& Hobson, M.~P.\ 2012, arXiv:1207.3708
+
+\bibitem[Kauffmann et al.(1999)]{KauffmannEtal1999} Kauffmann, G., 
+Colberg, J.~M., Diaferio, A., \& White, S.~D.~M.\ 1999, \mnras, 303, 188
 \bibitem[Krause et al.(2012)]{voids2} Krause, E., Chang, 
 T.-C., Dor{\'e}, O., \& Umetsu, K.\ 2012, arXiv:1210.2446
-
-\bibitem[Karpenka et al.(2012)]{KarpenkaEtal2012} Karpenka, N.~V., 
-March, M.~C., Feroz, F., \& Hobson, M.~P.\ 2012, arXiv:1207.3708
 
@@
 
+\bibitem[Koopmans et al.(2003)]{KoopmansEtal2003} Koopmans, L.~V.~E., 
+Treu, T., Fassnacht, C.~D., Blandford, R.~D., 
+\& Surpi, G.\ 2003, \apj, 599, 70
+
 \bibitem[Koopmans(2004)]{Koopmans2004} Koopmans, L.~V.~E.\ 2004, 
 arXiv:astro-ph/0412596
+
+\bibitem[Lagattuta et al.(2010)]{LagattutaEtal2010} Lagattuta, D.~J., 
+Fassnacht, C.~D., Auger, M.~W., et al.\ 2010, \apj, 716, 1579
 
@@
 Dutton, A.~A., \& van den Bosch, F.~C.\ 2008, \mnras, 391, 1940
+
+\bibitem[Mandelbaum et al.(2009)]{Mandelbaum} Mandelbaum, R., van 
+de Ven, G., \& Keeton, C.~R.\ 2009, \mnras, 398, 635
 
@@
 
+\bibitem[Takahashi et al.(2011)]{TakahashiEtal2011} Takahashi, R., Oguri, 
+M., Sato, M., \& Hamana, T.\ 2011, \apj, 742, 15
+
+\bibitem[Treu et al.(2009)]{TreuEtal2009} Treu, T., Gavazzi, R., 
+Gorecki, A., et al.\ 2009, \apj, 690, 670
+
 \bibitem[\protect\citeauthoryear{Vale 
 \& White}{2003}]{Vale+White2003} Vale C., White M., 2003, ApJ, 592, 699
+
+\bibitem[Wambsganss et al.(2004)]{WambsganssEtal2004} Wambsganss, J., 
+Bode, P., \& Ostriker, J.~P.\ 2004, \apjl, 606, L93
 

### 2013-03-01 doc/response.txt
added section on SM-HM relation

@@
 
-# We agree that this is an important systematic. We have implemented the
+# We agree that this is an important systematic, but we have not implemented the
 suggested test. Swapping Behroozi stellar masses for the Millenium catalogue's
-stellar masses, is an extreme change (the catalogue's stellar masses are
-unreasonable) but it results in offsets of ~0.015 in kappa for
-individual lines of sight. For the ensemble, there is no change in the mean
-reconstructed kappa. We have added a discussion of this in section 8.
+stellar masses is too a extreme a change to be realistic - one wants to test the effect of using a wrong HOD, where both models within the observational limits, in light of this we have applied to the Moster et al.
+(????) stell mass-halo mass relation, to generate 'true' stellar masses and reconstructed these using the Behroozi relation.
+The results of this investigation have been included in a new section 8.
 

### 2013-03-01 doc/paper-lcr.tex
added section on SM-HM relation

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Systematic Errors due to using an incorrect Stellar Mass--Halo Mass Relation}
+\label{sec:biases}
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{figs/SHAMbias.eps}
+\caption{Systematic bias in $\kappax$ due to reconstructing lines of sight with the wrong stellar mass--halo mass relation.
+The real stellar masses were created using the relation of \citet{MosterEtal2010}, but the reconstruction and calibration assumes the relation of \citet{BehrooziEtal2010}.
+These plots
+show the expectation value of $\prod_{i=1}^N \pr_i(\kappax-\kappaxtrue|\data)$ --
+deviations from zero represent biases. The solid, dashed and dotted lines
+correspond to combinations of  20, 5 and 2 sightlines respectively. Black
+lines show the results \infered from photometry alone, whilst red lines show
+the results  from the same targeted spectroscopy campaign described in 
+\Sref{sec:obsMstar+z:targetedspec}. The three panels correspond to samples of
+sightlines selected in different ways. Left: randomly selected lines of
+sight.  Centre: sightlines randomly selected from the 33\% of lines whose
+P($\kappax$) is most tightly constrained by our model.  Right: lines of sight
+with external shear of 0.05 or greater.}
+\label{fig:SHAMbias}
+\end{figure*}
+
+\new{
+Throughout this work we have assumed that the universe's halos are populated with galaxies whose stellar masses are determined purely by the \citet{BehrooziEtal2010} Stellar Mass--Halo Mass relation.
+The real universe is unlikely to follow this relation perfectly; the result is that an ensemble of real lines of sight will differ from the ensemble of calibration lines of sight, potentially introducing a systematic error to the reconstructed convergence.
+
+We test the potential size of this systematic error by using the \citet{BehrooziEtal2010} relation to generate the stellar masses of our calibration lines of sight, but the Stellar Mass--Halo Mass relation of \citet{MosterEtal2010} for the 'real' lines of sight that are reconstructed.
+
+For halos masses of $\sim 10^{12} \Msun$ both stellar mass--halo mass relations estimate a stellar mass of $\sim 10^{10.5} \Msun$, but for halos more massive that this the stellar masses generated from the Moster relation are systematically higher than those generated from the Behroozi relation.
+At halo masses of $\sim 10^{14} \Msun$ the best fit stellar masses differ by $\sim 0.25$ dex.
+
+Applying our Behroozi--based reconstruction to lines of sight with Moster stellar masses results in systematically overestimating $\kappax$.
+In \Fref{fig:SHAMbias} we show the resulting bias on the inferred $\kappax$ after combining several lines of sight.
+With a purely photometric reconstruction there is a typical systematic bias of $\sim 0.025$ on the reconstructed convergence, although it can be shrunk to $\sim 0.01$ if only the low $\kappax$ lines of sight are used, however for the high shear lines of sight the bias is $\sim 0.04$.
+It is not suprising that the low $\kappax$ lines of sight are least affected by changes in the stellar mass--halo mass relation.
+Low $\kappax$ lines of sight are relatively empty hence their $\kappah$ values are small and do not change significantly with stellar mass--halo mass relation.
+The high shear lines of sight have significantly overestimated $\kappax$ since they tend to lie close to massive halos.
+This is the regime where the Moster and Behroozi relations are most different.
+
+Despite the systematic errors the photometric reconstruction is still sufficient to choose the best lines of sight for spectroscopic follow-up.
+With targetted spectroscopy the systematic error decreases to $\sim 0.014$ for the ensemble, $\sim 0.005$ for the low kappa sample and $\sim 0.018$ for the high shear sample.
+}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-03-01 doc/paper-lcr.tex
added section on SM-HM relation

@@
 
-We test the potential size of this systematic error by using the \citet{BehrooziEtal2010} relation to generate the stellar masses of our calibration lines of sight, but the Stellar Mass--Halo Mass relation of \citet{MosterEtal2010} for the 'real' lines of sight that are reconstructed.
+We test the potential size of this systematic error by using the \citet{BehrooziEtal2010} relation to generate the stellar masses of our calibration lines of sight, but the stellar mass--halo mass relation of \citet{MosterEtal2010} for the \"real\" lines of sight that are reconstructed.
 
@@
 This is the regime where the Moster and Behroozi relations are most different.
+Interestingly overestimating the $\kappah$ values of high shear lines of sight pushes them into the region where the $\kappah$ to $\kappax$ calibration is least certain; this has significantly decreased the precision of the reconstructed $\kappax$.
 
@@
 With targetted spectroscopy the systematic error decreases to $\sim 0.014$ for the ensemble, $\sim 0.005$ for the low kappa sample and $\sim 0.018$ for the high shear sample.
+This result provides further motivation for prioritizing the lenses that reside on the underdense lines of sight.
 }

### 2013-03-01 doc/paper-lcr.tex
modified rest

@@
 with high external shear could, with the reconstruction model presented here,
-induce biases of up to 1\% in time delay distance.}  We suggest areas for the
+induce biases of up to 1\% in time delay distance.} \new{We find that a major potential source of systematic error is uncertainty in the high mass end of the stellar mass-halo mass relation; this could introduce ~2\% biases on the time-delay distance if completely ignored.} We suggest areas for the
 improvement of this general analysis framework (including more sophisticated
@@
 \Sref{sec:biases} we investigate the potential systematic error induced
-by selecting a subset of lines of sight. We discuss our results in
+by selecting a subset of lines of sight. In
+\Sref{sec:SHAMfail} we investigate systematic errors caused by assuming an incorrect stellar-mass relation. We discuss our results in
 \Sref{sec:discuss} before concluding in \Sref{sec:conclude}.
@@
 \section{Systematic Errors due to using an incorrect Stellar Mass--Halo Mass Relation}
-\label{sec:biases}
+\label{sec:SHAMfail}
 
@@
 
-We test the potential size of this systematic error by using the \citet{BehrooziEtal2010} relation to generate the stellar masses of our calibration lines of sight, but the stellar mass--halo mass relation of \citet{MosterEtal2010} for the \"real\" lines of sight that are reconstructed.
+We test the potential size of this systematic error by using the \citet{BehrooziEtal2010} relation to generate the stellar masses of our calibration lines of sight, but the stellar mass--halo mass relation of \citet{MosterEtal2010} for the ``real'' lines of sight that are reconstructed.
 
@@
 This result provides further motivation for prioritizing the lenses that reside on the underdense lines of sight.
+
+The systematic errors reported herein may be overly pessimistic; the bias is due to differences in the stellar masses predicted for high mass halos.
+If observations can discriminate between the high mass end of the \citet{BehrooziEtal2010} and \citet{MosterEtal2010} relations then the systematic error on the reconstruction will decrease.
 }
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %\section{Improving precision by including additional information}
@@
 used. Similarly the use of a different semi-analytic model to paint galaxies
-onto halos, and an alternative stellar mass--halo mass relation would both
-enable similar exploration of these systematic errors. \citet{SuyuEtal2010}
-used the relative over-density to mitigate this effect, but it does not
-completely remove the dependence on simulation. \new{Throughout this work, we assumed
-that the stellar mass--halo mass relation used for the reconstruction is the stellar mass--halo mass
-relation followed by the real universe. We discarded the stellar masses from the Millenium Catalogue
-due to a large number of excessively stripped satellite galaxies, however if we use these stellar masses
-there is no systematic change in the ensemble, but reconstructed $\kappax$ differs by $\sim 0.015$ for individual lines of sight. The effect is smaller ($\sim 0.008$)
-for the lowest $\kappax$ lines of sight, and larger ($\sim 0.02$) for high shear lines of sight. This 
-change of stellar masses is extreme but demonstrates that using the wrong stellar mass--halo mass relation
-can significantly degrade the quality of inference.} Future work should include
-investigating the robustness of the reconstruction to these systematic errors.
+onto halos would enable similar exploration of these systematic errors. 
+\citet{SuyuEtal2010}
+used the relative over-density to mitigate the effect of simulatioan and
+simulation, but it does not completely remove the dependence on simulation.
+\new{We have tested the effect of using a different stellar mass--halo mass relation
+and found that this can induce significant systematic biases if the true relation is unknown.} Future work should include
+investigating the robustness of the reconstruction to these systematic errors \new{and develope proscriptions that mitigate against them}
 
@@
 alleviate this potential systematic.
+
+\item \new{Reconstructing a line of sight with an incorrect stellar mass--halo mass relation can introduce systematic errors on the inferrred time-delay distance at the percent level.
+This error can only be reduced by tightening the observational limits on the stellar mass--halo mass relation at the high mass end.}
 

### 2013-03-02 doc/paper-lcr.tex
Edited section 8, added thoughts, made setup clearer?

@@
 
-\section{Systematic Errors due to using an incorrect Stellar Mass--Halo Mass Relation}
+\section{Systematic Errors due to Assuming an Incorrect 
+Stellar Mass--Halo Mass Relation}
 \label{sec:SHAMfail}
@@
 \new{
-Throughout this work we have assumed that the universe's halos are populated with galaxies whose stellar masses are determined purely by the \citet{BehrooziEtal2010} Stellar Mass--Halo Mass relation.
-The real universe is unlikely to follow this relation perfectly; the result is that an ensemble of real lines of sight will differ from the ensemble of calibration lines of sight, potentially introducing a systematic error to the reconstructed convergence.
-
-We test the potential size of this systematic error by using the \citet{BehrooziEtal2010} relation to generate the stellar masses of our calibration lines of sight, but the stellar mass--halo mass relation of \citet{MosterEtal2010} for the ``real'' lines of sight that are reconstructed.
-
-For halos masses of $\sim 10^{12} \Msun$ both stellar mass--halo mass relations estimate a stellar mass of $\sim 10^{10.5} \Msun$, but for halos more massive that this the stellar masses generated from the Moster relation are systematically higher than those generated from the Behroozi relation.
-At halo masses of $\sim 10^{14} \Msun$ the best fit stellar masses differ by $\sim 0.25$ dex.
-
-Applying our Behroozi--based reconstruction to lines of sight with Moster stellar masses results in systematically overestimating $\kappax$.
-In \Fref{fig:SHAMbias} we show the resulting bias on the inferred $\kappax$ after combining several lines of sight.
-With a purely photometric reconstruction there is a typical systematic bias of $\sim 0.025$ on the reconstructed convergence, although it can be shrunk to $\sim 0.01$ if only the low $\kappax$ lines of sight are used, however for the high shear lines of sight the bias is $\sim 0.04$.
-It is not suprising that the low $\kappax$ lines of sight are least affected by changes in the stellar mass--halo mass relation.
-Low $\kappax$ lines of sight are relatively empty hence their $\kappah$ values are small and do not change significantly with stellar mass--halo mass relation.
-The high shear lines of sight have significantly overestimated $\kappax$ since they tend to lie close to massive halos.
-This is the regime where the Moster and Behroozi relations are most different.
-Interestingly overestimating the $\kappah$ values of high shear lines of sight pushes them into the region where the $\kappah$ to $\kappax$ calibration is least certain; this has significantly decreased the precision of the reconstructed $\kappax$.
-
-Despite the systematic errors the photometric reconstruction is still sufficient to choose the best lines of sight for spectroscopic follow-up.
-With targetted spectroscopy the systematic error decreases to $\sim 0.014$ for the ensemble, $\sim 0.005$ for the low kappa sample and $\sim 0.018$ for the high shear sample.
-This result provides further motivation for prioritizing the lenses that reside on the underdense lines of sight.
-
-The systematic errors reported herein may be overly pessimistic; the bias is due to differences in the stellar masses predicted for high mass halos.
-If observations can discriminate between the high mass end of the \citet{BehrooziEtal2010} and \citet{MosterEtal2010} relations then the systematic error on the reconstruction will decrease.
-}
+Throughout this work we have assumed that the universe's halos are populated
+with galaxies whose stellar masses are determined purely by the
+\citet{BehrooziEtal2010} Stellar Mass--Halo Mass relation, which we then use
+in our reconstruction. In practice, the true Stellar Mass--Halo Mass relation
+may well be different to the one we assume in our inference, and if it is, 
+a systematic error could be incurred.
+
+We investigate the potential size of this systematic error by repeating the
+analysis of the previous section, still using the  the
+\citet{BehrooziEtal2010} relation to generate the stellar masses of our
+calibration lines of sight and hence carry out the inference, but now using
+simulated catalog datasets that were generated from the stellar mass--halo
+mass relation of \citet{MosterEtal2010}.
+
+This relation provides a comparable fit to the stellar mass function to the
+Behroozi et al relation, so represents a plausible alternative to our assumed
+form. For halo masses of $\sim 10^{12} \Msun$, both stellar mass--halo mass
+relations predict a stellar mass of $\sim 10^{10.5} \Msun$, but for halos more
+massive than this the stellar masses generated from the Moster relation are
+systematically higher than those generated from the Behroozi relation. At halo
+masses of $\sim 10^{14} \Msun$ the predicted stellar masses differ by some 
+$0.25$ dex.
+
+Applying our Behroozi--based reconstruction to lines of sight with Moster
+stellar masses results in systematic overestimates of $\kappax$. In
+\Fref{fig:SHAMbias} we show this bias emerging after combining several lines
+of sight. With a purely photometric reconstruction there is a typical
+systematic bias of $\sim 0.025$ on the reconstructed convergence. This can be
+shrunk to $\sim 0.01$ if only the low $\kappax$ lines of sight are used;
+however for the high shear lines of sight the bias is $\sim 0.04$. It is not
+too suprising that the low $\kappax$ lines of sight are least affected by
+changes in the stellar mass--halo mass relation. Low $\kappax$ lines of sight
+are relatively empty, their $\kappah$ values are small, and they do not depend
+as strongly on the stellar mass--halo mass relation. In contrast, the high
+shear lines of sight have significantly overestimated $\kappax$ values, since
+they tend to lie close to massive halos -- the regime where the Moster
+and Behroozi relations are most different. Interestingly, overestimating the
+$\kappah$ values of high shear lines of sight pushes them into the region
+where the $\kappah$ to $\kappax$ calibration is least certain; this 
+significantly decreases the precision of the reconstructed $\kappax$.
+
+Despite these systematic errors, we find that the photometric reconstruction
+is still sufficient to choose the best lines of sight for spectroscopic
+follow-up. With targeted spectroscopy the systematic error decreases to $\sim
+0.014$ for the ensemble, $\sim 0.005$ for the low kappa sample and $\sim
+0.018$ for the high shear sample. These results provides further motivation for
+prioritizing the lenses that reside on the underdense lines of sight.
+
+The systematic errors reported here are perhaps overly pessimistic, because
+the bias is due to differences in the stellar masses predicted for high mass
+halos. If new observations can discriminate between the high mass end of the
+\citet{BehrooziEtal2010} and \citet{MosterEtal2010} relations, then the
+systematic error on the reconstruction will decrease. Similarly, incorporating
+additional information about the high mass group and cluster-scale halo
+systems, such as their richness or other occupation statistics, would help
+mitigate the stellar to halo mass conversion error. }
 

### 2013-03-04 doc/response.txt
small changes

@@
 suggested test. Swapping Behroozi stellar masses for the Millenium catalogue's
-stellar masses is too a extreme a change to be realistic - one wants to test the effect of using a wrong HOD, where both models within the observational limits, in light of this we have applied to the Moster et al.
-(????) stell mass-halo mass relation, to generate 'true' stellar masses and reconstructed these using the Behroozi relation.
+stellar masses is too extreme a change to be realistic - one wants to test the effect of using a wrong HOD, but where both models are within the observational limits, in light of this we have applied the Moster et al.
+(2010) stellar mass-halo mass relation, to generate 'true' stellar masses and reconstructed these using the Behroozi relation.
 The results of this investigation have been included in a new section 8.

### 2013-03-04 doc/paper-lcr.tex
small changes

--- 2013-03-01 doc/paper-lcr.tex
@@
 \newauthor{%
-  Sherry~H.~Suyu$^{4,3}$,
+  Sherry~H.~Suyu$^{4,3,5}$,
   Zachary~Greene$^{4}$,
   Tommaso~Treu$^{4}$\thanks{\packard},
-  Christopher~D.~Fassnacht$^{5}$,}
+  Christopher~D.~Fassnacht$^{6}$,}
 \newauthor{%
-  L\'eon~V.~E.~Koopmans$^{6}$,
-  Maru\v{s}a Brada\v{c}$^{5}$,
+  L\'eon~V.~E.~Koopmans$^{7}$,
+  Maru\v{s}a Brada\v{c}$^{6}$,
   Roger~D.~Blandford$^{3}$} 
@@
   $^4$\ucsb\\
-  $^5$\davis\\
-  $^6$\kapteyn
+  $^5$\asiaa\\
+  $^6$\davis\\
+  $^7$\kapteyn
 }
@@
 
-We test the potential size of this systematic error by using the \citet{BehrooziEtal2010} relation to generate the stellar masses of our calibration lines of sight, but the stellar mass--halo mass relation of \citet{MosterEtal2010} for the ``real'' lines of sight that are reconstructed.
-
+It is hard to test the size of this sytematic error, since we do not know how much the real universe differs from the chosen Stellar Mass--Halo Mass relation.
+As wider and deeper surveys are conducted more data will become available with which to construct the Stellar Mass--Halo Mass relation; this should drive the infered Stellar Mass--Halo Mass relation closer to the truth.
+We are only interested in testing the effect of changing the Stellar Mass--Halo Mass relation in a way that is consistant with observational constraints; improving the observational contraints on the Stellar Mass--Halo Mass relation will decrease the the size of the systematic error on reconstructed $\kappax$ induced by assuming a specfic Stellar Mass--Halo Mass relation.
+
+To estimate the potential size of this systematic error we use the Behroozi relation to generate the stellar masses of our calibration lines of sight, but the stellar mass--halo mass relation of Moster for the ``real'' lines of sight that are reconstructed.
 For halos masses of $\sim 10^{12} \Msun$ both stellar mass--halo mass relations estimate a stellar mass of $\sim 10^{10.5} \Msun$, but for halos more massive that this the stellar masses generated from the Moster relation are systematically higher than those generated from the Behroozi relation.
@@
 The systematic errors reported herein may be overly pessimistic; the bias is due to differences in the stellar masses predicted for high mass halos.
-If observations can discriminate between the high mass end of the \citet{BehrooziEtal2010} and \citet{MosterEtal2010} relations then the systematic error on the reconstruction will decrease.
+If observations can discriminate between the high mass end of the Behroozi and Moster relations then the systematic error on the reconstruction will decrease.
 }

### 2013-03-04 doc/paper-lcr.tex
small changes

--- 2013-03-02 doc/paper-lcr.tex
@@
 \new{
+
 Throughout this work we have assumed that the universe's halos are populated
@@
 a systematic error could be incurred.
-
-We investigate the potential size of this systematic error by repeating the
+It is hard to test the size of this sytematic error, since we do not know how much the real universe differs from the chosen Stellar Mass--Halo Mass relation.
+As wider and deeper surveys are conducted more data will become available with which to construct the Stellar Mass--Halo Mass relation; this should drive the infered Stellar Mass--Halo Mass relation closer to the truth.
+We are only interested in testing the effect of changing the Stellar Mass--Halo Mass relation in a way that is consistant with observational constraints; improving the observational contraints on the Stellar Mass--Halo Mass relation will decrease the the potential size of the systematic error on reconstructed $\kappax$ induced by assuming a specfic Stellar Mass--Halo Mass relation.
+
+To estimate the potential size of this systematic error, we repeat the
 analysis of the previous section, still using the  the
@@
 We thank Risa Wechsler and Peter Behroozi 
-for useful discussions and suggestions.
+for useful discussions and suggestions. We are grateful to the referee
+for suggesting improvements to the original manuscript.
 \input{acknowledgments.tex}

### 2013-03-04 doc/paper-lcr.tex
fixed conflict

@@
 with high external shear could, with the reconstruction model presented here,
-induce biases of up to 1\% in time delay distance.} \new{We find that a major potential source of systematic error is uncertainty in the high mass end of the stellar mass-halo mass relation; this could introduce ~2\% biases on the time-delay distance if completely ignored.} We suggest areas for the
+induce biases of up to 1\% in time delay distance.} \new{We find that a major potential source of systematic error is uncertainty in the high mass end of the stellar mass-halo mass relation; this could introduce $\sim$2\% biases on the time-delay distance if completely ignored.} We suggest areas for the
 improvement of this general analysis framework (including more sophisticated
@@
 analysis of the previous section, still using the  the
-\citet{BehrooziEtal2010} relation to generate the stellar masses of our
+Behroozi et al. relation to generate the stellar masses of our
 calibration lines of sight and hence carry out the inference, but now using
 simulated catalog datasets that were generated from the stellar mass--halo
-mass relation of \citet{MosterEtal2010}.
+mass relation of Moster et al.
 
@@
 halos. If new observations can discriminate between the high mass end of the
-\citet{BehrooziEtal2010} and \citet{MosterEtal2010} relations, then the
+Behroozi et al. and Moster et al. relations, then the
 systematic error on the reconstruction will decrease. Similarly, incorporating
@@
 \item \new{Reconstructing a line of sight with an incorrect stellar mass--halo mass relation can introduce systematic errors on the inferrred time-delay distance at the percent level.
-This error can only be reduced by tightening the observational limits on the stellar mass--halo mass relation at the high mass end.}
+This error can be reduced by tightening the observational limits on the stellar mass--halo mass relation at the high mass end.}
 

### 2013-03-20 doc/paper-lcr.tex
new readme

@@
 sufficient to pre-select the best-constrained lines of sight, and can be done
-before investment in lightcurve monitoring. 
+before investment in light-curve monitoring. 
 %
@@
 all found groups of galaxies hosting or near to known gravitational lenses.
-Is generally found that lens galaxies, reside in overdense environments,
+Is generally found that lens galaxies, reside in over-dense environments,
 indistinguishable from those occupied by similarly massive galaxies \citep{Auger2008,TreuEtal2009}
@@
 parameters of scaling relations between light and mass in these galaxies
-from hundreds of supernova lightcone simultaneously. Following
+from hundreds of supernova light-cone simultaneously. Following
 \citet{JonssonEtal2010}, they subtract off the mean convergence to ensure that
@@
 to the $\pr(\kappah|\data)$ for the real line of sight {\it given the same
-data quality}; however, we found this approach unfeasible  given our finite
+data quality}; however, we found this approach infeasible  given our finite
 number of calibration lines of sight. A working compromise is to use 
@@
 approximation; a spectrum will be needed
-to adequately model systems with very well alligned pertrubers.
+to adequately model systems with very well aligned pertrubers.
 Consistent with our previous findings, the lowest $\kappax$ lines of
@@
 med}\pm0.003$, randomly selected lines of sight would have zero bias by
-construction}. If lines of sight hosting time delay lenses are truely random, 
+construction}. If lines of sight hosting time delay lenses are truly random, 
 our method allows $\kappax$ to be reconstructed without inducing a bias (under
@@
 a systematic error could be incurred.
-It is hard to test the size of this sytematic error, since we do not know how much the real universe differs from the chosen Stellar Mass--Halo Mass relation.
-As wider and deeper surveys are conducted more data will become available with which to construct the Stellar Mass--Halo Mass relation; this should drive the infered Stellar Mass--Halo Mass relation closer to the truth.
-We are only interested in testing the effect of changing the Stellar Mass--Halo Mass relation in a way that is consistant with observational constraints; improving the observational contraints on the Stellar Mass--Halo Mass relation will decrease the the potential size of the systematic error on reconstructed $\kappax$ induced by assuming a specfic Stellar Mass--Halo Mass relation.
+It is hard to test the size of this systematic error, since we do not know how much the real universe differs from the chosen Stellar Mass--Halo Mass relation.
+As wider and deeper surveys are conducted more data will become available with which to construct the Stellar Mass--Halo Mass relation; this should drive the inferred Stellar Mass--Halo Mass relation closer to the truth.
+We are only interested in testing the effect of changing the Stellar Mass--Halo Mass relation in a way that is consistent with observational constraints; improving the observational constraints on the Stellar Mass--Halo Mass relation will decrease the the potential size of the systematic error on reconstructed $\kappax$ induced by assuming a specific Stellar Mass--Halo Mass relation.
 
@@
 calibration lines of sight and hence carry out the inference, but now using
-simulated catalog datasets that were generated from the stellar mass--halo
+simulated catalogue datasets that were generated from the stellar mass--halo
 mass relation of Moster et al.
@@
 however for the high shear lines of sight the bias is $\sim 0.04$. It is not
-too suprising that the low $\kappax$ lines of sight are least affected by
+too surprising that the low $\kappax$ lines of sight are least affected by
 changes in the stellar mass--halo mass relation. Low $\kappax$ lines of sight
@@
 0.018$ for the high shear sample. These results provides further motivation for
-prioritizing the lenses that reside on the underdense lines of sight.
+prioritizing the lenses that reside on the under-dense lines of sight.
 
@@
 reconstructions are $\sim$30\% more precise than those of Greene et al.
-The use of relative overdensities by Suyu et al. and Greene et al. may decrease 
+The use of relative over-densities by Suyu et al. and Greene et al. may decrease 
 their sensitivity to the choice of calibration simulation; this work's use of
@@
 \citet{SuyuEtal2010}
-used the relative over-density to mitigate the effect of simulatioan and
+used the relative over-density to mitigate the effect of simulation and
 simulation, but it does not completely remove the dependence on simulation.
@@
 and found that this can induce significant systematic biases if the true relation is unknown.} Future work should include
-investigating the robustness of the reconstruction to these systematic errors \new{and develope proscriptions that mitigate against them}
+investigating the robustness of the reconstruction to these systematic errors \new{and develop prescriptions that mitigate against them}
 
@@
 groups and clusters, and the unseen mass in small halos and filaments, but we
-find that this can be calibrated out using the Millenium Simulation
+find that this can be calibrated out using the Millennium Simulation
 catalogues. We found that with perfect knowledge of every halo's mass and
@@
 
-\item \new{Reconstructing a line of sight with an incorrect stellar mass--halo mass relation can introduce systematic errors on the inferrred time-delay distance at the percent level.
+\item \new{Reconstructing a line of sight with an incorrect stellar mass--halo mass relation can introduce systematic errors on the inferred time-delay distance at the percent level.
 This error can be reduced by tightening the observational limits on the stellar mass--halo mass relation at the high mass end.}

### 2013-03-20 Pangloss4/Pangloss/AnalyseCones.py
pruned pangloss

@@ -1,0 +1,56 @@
+import numpy
+import numpy.random as rnd
+import cPickle
+from scipy import interpolate,optimize
+import time
+import glob
+import copy
+
+def AnalyseWeightingScheme(lc,surveyparams):
+    print "Code up AnalyseWeightingScheme"
+    #note this made need an Nrealisation term depending on if the weight scheme has uncertainties.
+    exit()
+
+
+
+def AnalyzeReconstruction(lc,zl,zs,Grid,behT,behI,Nrealisation,truncationscale,surveyparams):
+    kappa_halo=numpy.empty(Nrealisation)
+    gamma1_halo=numpy.empty(Nrealisation)
+    gamma2_halo=numpy.empty(Nrealisation)
+
+    kappa_Hilbert=lc.kappa_hilbert
+    gamma1_Hilbert=lc.gamma1_hilbert
+    gamma2_Hilbert=lc.gamma2_hilbert
+
+    lc.define_system(zl,zs)
+    #load grid
+    lc.load_grid(Grid)
+
+    #lc.snap_to_grid(Grid)
+    #lc.drawConcentrations(errors=False)
+    #lc.Make_kappas(truncationscale=10)
+    #lc.Scale_kappas()
+    #kappa_T=lc.kappa_add_total
+    #gamma1_T=lc.gamma1_add_total
+    #gamma2_T=lc.gamma2_add_total
+
+
+    #Set up the survey parameters to give appropriate spectroscopic flag.
+    print "set up the survey in Analyse Cones"
+    exit()
+
+    for j in range(Nrealisation):
+        lc.mimik_photoz_error(sigma=)
+        lc.snap_to_grid(Grid)
+        lc.drawMStar(behI)
+        lc.drawMHalo(behT)
+        lc.drawConcentrations(errors=True)
+        lc.Make_kappas(truncationscale=10)
+        lc.Scale_kappas()
+        kappa_halo[j]=lc.kappa_add_total
+        gamma1_halo[j]=lc.gamma1_add_total
+        gamma2_halo[j]=lc.gamma2_add_total
+
+    results=kappa_Hilbert,gamma1_Hilbert,gamma2_Hilbert,kappa_halo,gamma1_halo,gamma2_halo#,kappa_T,gamma1_T,gamma2_T
+
+    return results

### 2013-03-20 Pangloss4/Pangloss/LensingFunc.py

@@ -1,0 +1,93 @@
+'''
+This file is part of the Pangloss project.
+Copyright 2012 Tom Collett (IoA) and Phil Marshall (Oxford).
+
+description:
+------------
+Functions that are useful for lensing (and necessary to the Pangloss Project)
+
+to-do:
+------
+
+
+issues:
+-------
+
+
+'''
+
+import distances
+import pylab
+import matplotlib.pyplot as plt
+import numpy, numpy.random as rnd, atpy
+from time import clock
+
+D = distances.Distance()
+
+# ----------------------------------------------------------------------------
+def SigmaCrit_Da(Da,Da_s,Da_tosource): 
+    # NOTE zl here is the lensing object NOT necessarily the primary lens
+    return (1.663*10**18)*(Da_s/(Da*Da_tosource)) 
+    # numerical factor is c^2/(4 pi G) in Solarmasses per megaparsec
+def SigmaCrit_z(zd,zs): #As above but with redshifts (much slower)
+    return (1.663*10**18)*(D.Da(zs)/(D.Da()*Da_tosource)) 
+
+# ----------------------------------------------------------------------------
+
+# Keeton Beta parameter for a perturber at j:  
+def beta(i,j,k):  
+    if j>k:
+        print "z_pert > z_source? you shouldn't be asking for this"
+    if j>i:
+        R1a = D.Da(i,j)/D.Da(j)
+        R2a = D.Da(i,k)/D.Da(k)
+        return R1a/R2a
+    if i>j:
+        R1b = D.Da(j,i)/D.Da(i)
+        R2b = D.Da(j,k)/D.Da(k)
+        return R1b/R2b
+    if i == j:
+        return 1.0
+    if j==k:
+        return 0.0
+
+# Same but for known angular diameter distances (much faster)
+def beta_Da(D12,Ds,D2,D1s): 
+    return (D12*Ds)/(D2*D1s)
+
+
+# ----------------------------------------------------------------------------
+
+# Kappa Keeton, following Keeton (2003) and Momcheva et al. (2006)
+def KappaKeeton(zl,zd,zs,kappa,shear):
+    output = numpy.zeros(len(zd))
+    for i in range(len(zd)):
+        if zd[i] < zs:
+            B=self.beta(zl,zd[i],zs)
+            K=kappa[i]
+            G=shear[i]
+            D= K**2-G**2
+            output[i] = (1.-B) * (K- B*(D)) /  ( (1-B*K)**2   - (B*G)**2   )
[…]

### 2013-03-20 Pangloss4/Pangloss/LensingProfiles.py

@@ -1,0 +1,174 @@
+import pylab
+import matplotlib.pyplot as plt
+import numpy, numpy.random as rnd, atpy
+import distances
+from mpl_toolkits.axes_grid1 import ImageGrid
+from time import clock
+from numpy import exp,pi
+from scipy.special import gamma,gammainc
+
+D = distances.Distance()
+D.h = 0.7
+
+arcmin2rad = (1.0/60.0)*numpy.pi/180.0
+rad2arcmin = 1.0/arcmin2rad
+# ------------------------------------------------------------------------
+def F(x):
+    z=numpy.ones(len(x))
+    z[x>1]=numpy.arccos(1/x[x>1])/((x[x>1]**2-1)**.5)
+    z[x<1]=numpy.arccosh(1/x[x<1])/((1-x[x<1]**2)**.5)
+    z[x==1]=numpy.log(2)
+    return z
+
+def L(x,t):
+    return numpy.log(x/(((t**2+x**2)**.5)+t))
+
+def F2(x):
+    z=numpy.ones(len(x))
+    z[x>1]=numpy.arctan((x[x>1])**2-1)/((x[x>1]**2-1)**.5)
+    z[x<1]=numpy.arctanh(1-(x[x<1])**2)/((1-x[x<1]**2)**.5)
+    z[x==1]=numpy.log(2)
+    return z
+
+#=========================================================================
+# NFW profile functions.
+#--------------------------------------------------------------
+def delta_c(c):
+    return (200./3)*(c**3)/(numpy.log(1+c)-c/(1+c))
+# ------------------------------------------------------------------------
+    # Function needed to calculate kappa for an NFW halo. 
+def Ffunc(x):
+       z=numpy.zeros(len(x))
+       for i in range(len(x)):
+          if x[i]==-1:
+              z[i]=0.0
+          elif x[i]>1:
+             z[i]= (1-(2./(x[i]**2-1)**.5)*numpy.arctan(((x[i]-1.)/(x[i]+1))**.5))/(x[i]**2-1.)
+          else: 
+             if x[i]==1:
+                z[i] =1./3
+             else:
+                y=(-x[i]**2+1)**.5
+                z[i] = (1.-(2./(1-x[i]**2)**.5)*numpy.arctanh(((1.-x[i])/(x[i]+1))**.5))/(x[i]**2-1)
+
+
+          if z[i] < 0: print 'warning Ffunc'
+       return 2*z
[…]

### 2013-03-20 Pangloss4/Pangloss/MakeCalibrationGuide.py

@@ -1,0 +1,89 @@
+import cPickle
+import pylab as plt
+import scipy.stats as stats
+from scipy import interpolate,optimize
+import numpy
+import numpy.random as rnd
+import glob
+#------------------------------------------------------------------
+def MakeReconstructionCalibration(CalibrationResultsDirectory,surveyname):
+   results="%s/cone*_%s.result"%(CalibrationResultsDirectory,i,surveyname)
+   resultlist=glob.glob(results)
+
+   Zl=len(resultlist)
+   
+   Cal_list=numpy.empty((Zl,5))
+
+   for i in range(len(resultlist)):
+      if i % 1000==0: print "making calibration", i,"of", len(resultlist)
+      F=open(resultlist[i],"rb")
+      res=cPickle.load(F)
+      F.close()
+      
+      kappa_Hilbert,gamma1_Hilbert,gamma2_Hilbert,kappa_halo,gamma1_halo,gamma2_halo=res
+
+      mu_Hilbert=1/((1-kappa_Hilbert)**2 - gamma_Hilbert**2)
+      mu_halo=1/((1-kappa_halo)**2 - gamma_halo**2)
+
+      Cal_list[i,0]=kappa_Hilbert
+      Cal_list[i,1]=mu_Hilbert
+      Cal_list[i,2]=numpy.median(kappa_halo)
+      Cal_list[i,3]=numpy.median(mu_halo)
+      Cal_list[i,4]=1
+
+   F=open("%s/%s.jointdist"%(CalibrationResultsDirectory,surveyname),'wb')
+   cPickle.dump(Cal_list,F,2)
+   F.close()
+   
+def MakeWeightCalibration(CalibrationResultsDirectory,surveyname):
+   results="%s/cone*_%s.result"%(CalibrationResultsDirectory,i,surveyname)
+   resultlist=glob.glob(results)
+
+   Zl=len(resultlist)
+   
+   Cal_list=numpy.empty((Zl,5))
+
+   for i in range(len(resultlist)):
+      if i % 1000==0: print "making calibration", i,"of", len(resultlist)
+      F=open(resultlist[i],"rb")
+      res=cPickle.load(F)
+      F.close()
+      
+   #need to work out what goes in here...
+   """
+      kappa_Hilbert,gamma1_Hilbert,gamma2_Hilbert,=res
+
[…]

### 2013-03-20 Pangloss4/Pangloss/MakeCones.py

@@ -1,0 +1,49 @@
+import lightcone,kappamap
+import cPickle
+import atpy
+import numpy.random as rnd
+import numpy
+#==========================================================================
+arcmin2rad = (1.0/60.0)*numpy.pi/180.0
+rad2arcmin = 1.0/arcmin2rad
+#==========================================================================
+def MakeCones(N,savefolder,radius=5,catalogue=[],kappa=[],gamma1=[],gamma2=[]):
+    if len(catalogue)!=len(kappa): 
+        print "the catalogues and the ray-traced results need to match up!"
+	exit()
+    Ncones=N/len(catalogue)
+    l=0
+    for i in range(len(catalogue)):
+	print "reading in catalogue"
+	master = atpy.Table(catalogue[i], type='ascii')
+
+        xmax = master['pos_0[rad]'].max()
+        xmin = master['pos_0[rad]'].min()
+        ymax = master['pos_1[rad]'].max()
+        ymin = master['pos_1[rad]'].min()
+
+        
+        print "reading in kappamap"
+        kappafile = kappa[i]
+        MSconvergence = kappamap.Kappamap(kappafile)
+        gammafile1 = gamma1[i]
+        MSgamma1 = kappamap.Kappamap(gammafile1)
+        gammafile2 = gamma2[i]
+        MSgamma2 = kappamap.Kappamap(gammafile2)
+
+        x = rnd.uniform(xmin+Rcone*arcmin2rad,xmax-Rcone*arcmin2rad,Ncones)
+        y = rnd.uniform(ymin+Rcone*arcmin2rad,ymax-Rcone*arcmin2rad,Ncones)
+
+        print "Writing out cones"
+        for k in range(Ncones):
+            if k % 200 == 0 and k !=0: print ("saving cone %i of %i" %(k,Ncones))
+            xc = [x[k],y[k]]
+            lc= lightcone.Lightcone(master,xc,Rcone)
+            lc.kappa_hilbert=MSconvergence.at(x[k],y[k],coordinate_system='physical')
+            lc.gamma1_hilbert=MSgamma1.at(x[k],y[k],coordinate_system='physical')
+            lc.gamma2_hilbert=MSgamma2.at(x[k],y[k],coordinate_system='physical')
+            CONE=open("%s/cone%i.cone"%(savefolder,l),"wb")
+            cPickle.dump(lc,CONE,protocol=2)
+            CONE.close()
+            l+=1
+            

### 2013-03-20 Pangloss4/Pangloss/Relations.py

@@ -1,0 +1,217 @@
+import numpy
+#from numpy import exp,pi
+#from scipy.special import gamma
+import numpy.random as rnd
+#import copy
+#import matplotlib,pylab as plt
+#from scipy import interpolate
+
+#--------------------------------------------------------------
+def logerr(l,m,s):
+      c=10**rnd.normal(m,s)
+      return c
+
+def MCrelation(M200,scatter=False,h=0.75):
+      if scatter==True:
+            M200/=h
+            r1=rnd.normal(0,0.015,len(M200))
+            r2=rnd.normal(0,0.005,len(M200))
+            logc_maccio=1.020+r1-(0.109+r2)*(numpy.log10(M200)-12)
+      else:
+           logc_maccio=1.020-(0.109)*(numpy.log10(M200)-12)
+      c_maccio=10**logc_maccio
+      return c_maccio
+
+#Neto stuff
+
+      if MCerror==False:
+         c_200 = 4.67*(M200/(10**14))**-0.11 #Neto et al. equation 5
+      if MCerror==True:
+       c_200=4.67*(M200/(10**14))**-0.11
+       logc_200=numpy.log10(c_200)
+       lM200 = numpy.log10(M200)
+       c_new = c_200*10**(rnd.normal(1,0.2,len(M200)))/10**(1+(0.2**2)/2)
+       #print numpy.max(c_new),numpy.min(c_new)
+
+       return c_new
+
+
+       for i in range(len(M200)):    #best fit scatter parameters of neto et al (double log normal)
+         if lM200[i]<11.875:
+            f=0.205 
+            if rnd.rand()<f:
+               c_200[i]=logerr(logc_200[i],0.683,0.147) * (lM200[i]/11.875)**-0.11
+            else:
+               c_200[i]=logerr(logc_200[i],0.920,0.106) * (lM200[i]/11.875)**-0.11
+         if lM200[i]<12.125:
+            f=0.205
+            if rnd.rand()<f:
+               c_200[i]=logerr(logc_200[i],0.683,0.147)
+            else:
+               c_200[i]=logerr(logc_200[i],0.920,0.106)
+         elif lM200[i]<12.375:
+            f=0.171
+            if rnd.rand()<f:
+               c_200[i]=logerr(logc_200[i],0.658,0.150)
+            else:
+               c_200[i]=logerr(logc_200[i],0.903,0.108)
+         elif lM200[i]<12.625:
+            f=0.199
+            if rnd.rand()<f:
[…]

### 2013-03-20 Pangloss4/Pangloss/__init__.py

@@ -1,0 +1,9 @@
+from lightcone import *
+from kappamap import *
+from grid import *
+from LensingFunc import *
+from LensingProfiles import *
+import Relations as Rel
+from MakeCones import *
+from AnalyseCones import *
+from MakeCalibrationGuide import *

### 2013-03-20 Pangloss4/Pangloss/grid.py

@@ -1,0 +1,114 @@
+import numpy
+import distances
+from scipy import interpolate,optimize
+import cPickle
+
+import Relations as Rel
+#import pylab as plt
+
+arcmin2rad = (1.0/60.0)*numpy.pi/180.0
+rad2arcmin = 1.0/arcmin2rad
+
+vb = False
+
+# ============================================================================
+# Attempt at good Object Orientation. Made code slower :-(.   
+class Lens_Plane():
+    def __init__(self, z,zl,zs,Da_l,Da_s,Da_ls):
+        if z==0: z+=1e-99
+        D=distances.Distance()
+        self.name = "A sheet at redshift %.3f"%z
+        self.z=z
+        self.Da_p=D.Da(0,z)
+        self.rho_crit=D.rho_crit_univ(z)
+        self.Da_l,self.Da_s,self.Da_ls=Da_l,Da_s,Da_ls
+        self.Da_ps = D.Da(z,zs)
+        self.Da_pl = D.Da(z,zl)
+        self.sigma_crit=(1.663*10**18)*(self.Da_s/(self.Da_p*self.Da_ps))
+        if self.z>zl: #1 is lens, 2 is perturber
+            D1s = self.Da_ls
+            D2  = self.Da_p
+        else: #1 is perturber, 2 is lens
+            D1s = self.Da_ps
+            D2  = self.Da_l
+        D12= self.Da_pl
+        self.beta=(D12*self.Da_s)/(D2*D1s)
+
+# ============================================================================
+class Grid():
+    def __init__(self,zl,zs,nplanes=100,cosmo=[0.25,0.75,0.73]): 
+        if zl > zs: zl,zs=zs,zl
+        D=distances.Distance()
+        self.name = '1D Redshift grid of lens planes, each containing precalculated quantities '
+        self.zmax=zs*1.0
+        self.zs=zs*1.0
+        self.zltrue=zl
+        self.nplanes=nplanes
+        self.cosmo=cosmo
+        #These are the plane redshifts:
+        self.redshifts,self.dz=self.redshiftbins=numpy.linspace(0.0,self.zmax,self.nplanes,endpoint=True,retstep=True)
+        self.redshifts+=(self.dz/2.)
+        # SNAP LENS TO GRID:
+        self.zl=self.snap([zl])[0][0]
+        self.Da_l=D.Da(zl)
+        self.Da_s=D.Da(zs)
[…]

### 2013-03-20 Pangloss4/Pangloss/kappamap.py

@@ -1,0 +1,300 @@
+'''
+This file is part of the Pangloss project.
+Copyright 2012 Tom Collett (IoA) and Phil Marshall (Oxford).
+
+to-do
+-----
+- check that kappa map is being read in the right way around...
+'''
+
+import numpy, os, string
+import struct, pyfits
+import pylab as plt
+import random as rnd
+import cPickle
+
+arcmin2rad = (1.0/60.0)*numpy.pi/180.0
+rad2arcmin = 1.0/arcmin2rad
+deg2rad = numpy.pi/180.0
+rad2deg = 1.0/deg2rad
+
+vb = False
+
+# ============================================================================
+    
+# Read in, write out, look up convergence kappa in map from Stefan Hilbert.
+
+class Kappamap:
+
+   def __init__(self,kappafile,FITS=True,vb=False):
+
+      self.name = 'Convergence map kappa from Millenium Simulation, zs = 1.6'
+      self.input = kappafile
+
+      # Read in data from file:
+      
+      if FITS:
+         # Read in FITS image, extract wcs:
+         if vb: print "Reading in map from file "+kappafile
+         self.read_in_fits_data()
+       
+      else:
+
+         # Initialise some necessary WCS parameters:
+         self.field = 4.0 # degrees
+         self.NX = 4096
+         self.PIXSCALE = self.field/(1.0*self.NX) # degrees
+         self.setwcs()
+
+         # Read in binary data, to self.values:
+         if vb: print "Reading in map from file "+kappafile
+         self.read_in_binary_data()
+
+         # If it doesn't already exist, output the map to FITS file:
+         # pieces = string.split(self.input,'.')
+         # self.output = string.join(pieces[0:len(pieces)-1],'.')+'.fits'
+         self.output = self.input+'.fits'
+         if os.path.exists(self.output): 
+           if vb: print "FITS version already exists: ",self.output
+         else:  
+           if vb: print "Writing map to "+self.output
+           self.write_out_to_fits()
+         # This should probably not be in __init__ but hopefully it only gets run once.  
+      
+      return None
+
+# ----------------------------------------------------------------------------
+
+   def __str__(self):
+      return 'Convergence map'
+
[…]

### 2013-03-20 Pangloss4/Pangloss/lightcone.py

@@ -1,0 +1,274 @@
+# ===========================================================================
+
+#import pylab
+#import matplotlib.pyplot as plt
+#from mpl_toolkits.axes_grid1 import ImageGrid
+import cPickle
+import numpy
+import Relations as Rel
+import LensingProfiles as LP
+import LensingFunc as LF
+import numpy.random as rnd
+import pylab as plt
+arcmin2rad = (1.0/60.0)*numpy.pi/180.0
+rad2arcmin = 1.0/arcmin2rad
+
+# ============================================================================
+ 
+class Lightcone(object):
+    def __init__(self,catalog,position,radius,magnitudecut=99,band="r"):
+        self.name = 'Lightcone through the observed Universe'
+        self.catalog = catalog
+        self.xmax = self.catalog['pos_0[rad]'].max()
+        self.xmin = self.catalog['pos_0[rad]'].min()
+        self.ymax = self.catalog['pos_1[rad]'].max()
+        self.ymin = self.catalog['pos_1[rad]'].min() 
+        self.rmax = radius
+        self.xc = [position[0],position[1]]
+
+        dx = self.rmax*arcmin2rad
+        self.galaxies = self.catalog.where((self.catalog['pos_0[rad]'] > (self.xc[0]-dx)) & \
+                                           (self.catalog['pos_0[rad]'] < (self.xc[0]+dx)) & \
+                                           (self.catalog['pos_1[rad]'] > (self.xc[1]-dx)) & \
+                                           (self.catalog['pos_1[rad]'] < (self.xc[1]+dx))   )
+
+ 
+        x = (self.galaxies['pos_0[rad]'] - self.xc[0])*rad2arcmin
+        y = (self.galaxies['pos_1[rad]'] - self.xc[1])*rad2arcmin
+        r = numpy.sqrt(x*x + y*y)
+        phi=numpy.arctan(y/x)
+        self.galaxies.add_column('x',x)
+        self.galaxies.add_column('y',y)
+        self.galaxies.add_column('r',r)
+        self.galaxies.add_column('phi',phi)
+
+
+        self.galaxies = self.galaxies.where(self.galaxies.r < self.rmax)
+        self.galaxies = self.galaxies.where(self.galaxies.Type != 2) 
+
+
+        #log the mass:
+        self.galaxies.add_column('Mh',numpy.log10(self.galaxies['M_Subhalo[M_sol/h]']))
+        self.galaxies.add_column('Mh_obs',self.galaxies.Mh*1)
[…]

### 2013-03-20 Pangloss4/Example.py
pruned pangloss

@@ -1,0 +1,132 @@
+import pangloss
+import glob
+
+#===============================
+#read in any command line inputs
+
+
+
+#===============================
+#open the survey parameterfile and read in:
+
+
+
+
+#===============================
+#make N calibration light-cones:
+# you should only need to do this once, unless you want a new set of lightcones.
+CreateNewCalibrationLightcones=True
+
+N=100 # This number should be at least tens of thousands to do 'science'
+radius=2 #this is the radius out to which halos are included. Larger than 2 doesn't seem to help the reconstruction much
+
+if CreateNewCalibrationLightones:
+    MakeCones(N,calibrationcones,radius=radius,catalogue=cataloguelist,kappa=kappalist,gamma1=gamma1list,gamma2=gamma2list)
+
+
+#===============================
+#Define a few things that are used in the reconstruction:
+
+if DoReconstruction==True:
+        #first we need to define some quantities and load in some often used objects in order to speed up the reconstruction.
+
+        #define the halo truncation scale: this is the scale where the halo profile transitions from r^-3 to r^-5. (needed to keep total halo mass finite)
+        truncationscale=5 #virial radii
+
+        #define how many realisations of each line cone are wanted. larger takes time, but produces smoother results. Nrealisation~500 seems to work well.
+        Nrealisations=100
+
+        #read in the stellar mass to halo mass relation files:
+        BT=open("DATA/SHMR/S2H.behroozi","rb")
+        BI=open("DATA/SHMR/H2S.behroozi","rb")
+        SHMR_S2H=cPickle.load(BT)
+        SHMR_H2S=cPickle.load(BI)
+
+        #generate the redshift grid on which calculations are done:
+        Grid=pangloss.Grid(zl,zs)
+
+#===============================
+#Analyse calibration sightlines according to scheme defined in survey.params
+CreateNewCalibration=True
+if CreateNewCalibration:
+    Conelist=glob.glob(calibrationcones)
+
+    if DoReconstruction==False: #the 'reconstruction' is trivial:
+        for i in range(len(Conelist)):
+            Cone = Conelist[i]
+            #note// this doesn't exist:
+            ConeResult=WeightingScheme(Cone,surveyparams)
+            
+    if DoReconstruction==True:
+        for i in range(len(Conelist)):
+            Cone = Conelist[i]
+
[…]

### 2013-03-20 Pangloss4/Pangloss/distances.py
added distances.py

@@ -1,0 +1,124 @@
+"""
+A module to compute cosmological distances, including:
+    comoving_distance (Dc)
+    angular_diameter_distance (Da)
+    luminosity_distance (Dl)
+    comoving_volume (volume)
+
+"""
+c = 299792458.
+G = 4.3e-6
+from math import pi
+import warnings
+warnings.warn("Default cosmology is Om=0.25,Ol=0.75,h=0.73,w=-1 (MS fiducial) and distance units are Mpc!",ImportWarning) #MS fiducial.
+
+class Distance:
+    def __init__(self,cosmo=[0.25,0.75,0.73]): # altered to the MS fiducials.
+        self.OMEGA_M = cosmo[0]
+        self.OMEGA_L = cosmo[1]
+        self.h = cosmo[2]
+        self.w = -1.
+        self.wpars = None
+        self.w_analytic = False
+        self.Dc = self.comoving_distance
+        self.Dt = self.comoving_transverse_distance
+        self.Dm = self.comoving_transverse_distance
+        self.Da = self.angular_diameter_distance
+        self.Dl = self.luminosity_distance
+        self.dm = self.distance_modulus
+        self.volume = self.comoving_volume
+
+
+    def set(self,cosmo):
+        self.OMEGA_M = cosmo[0]
+        self.OMEGA_L = cosmo[1]
+        self.h = cosmo[2]
+
+    def reset(self):
+        self.OMEGA_M = 0.3
+        self.OMEGA_L = 0.7
+        self.h = 0.7
+        self.w = -1.
+
+    def age(self,z):
+        from scipy import integrate
+        f = lambda zp,m,l,k : (m/zp+k+l*zp**2)**-0.5
+        om = self.OMEGA_M
+        ol = self.OMEGA_L
+        ok = 1.-om-ol
+        return (9.778/self.h)*integrate.romberg(f,1e-300,1/(1.+z),(om,ol,ok))
+
+    def comoving_distance(self,z1,z2=0.):
+        from scipy import integrate
+        if z2<z1:
+            z1,z2 = z2,z1
+        def fa(z):
+            if self.w_analytic==True:
+                return self.w(z,self.wpars)
+            from math import exp
+            wa = lambda z : (1.+self.w(z,self.wpars))/(1.+z)
+            #return exp(3.*integrate.romberg(wa,0,z))
[…]

### 2015-05-20 doc/paper-lcr.tex
Keep Collett et al figs separate from future papers'

@@
 % Packages:
-\input psfig.sty
+%\input psfig.sty
+\usepackage[totalwidth=500pt,totalheight=710pt]{geometry}
 \usepackage{xspace}
@@
 \usepackage{amsmath}
+
+\graphicspath{{./}{figs-lcr/}}
 
@@
 
-\date{to be submitted to MNRAS}
+\date{Accepted for publication in MNRAS}
 \pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2012}
@@
 with high external shear could, with the reconstruction model presented here,
-induce biases of up to 1\% in time delay distance.} \new{We find that a major potential source of systematic error is uncertainty in the high mass end of the stellar mass-halo mass relation; this could introduce $\sim$2\% biases on the time-delay distance if completely ignored.} We suggest areas for the
+induce biases of up to 1\% in time delay distance.} We find that a major potential source of systematic error is uncertainty in the high mass end of the stellar mass-halo mass relation; this could introduce $\sim$2\% biases on the time-delay distance if completely ignored.
+We suggest areas for the
 improvement of this general analysis framework (including more sophisticated
@@
 delay distance in this system. A similar procedure was used in \citet{SuyuEtal2012}.
-In a companion paper to this one, Greene et al. (submitted) investigate
+In a companion paper to this one, \citet{Greene} investigate
 improvements to this method by weighting the galaxy counts by observables
@@
 number counts alone, but little improvement for less dense ones.
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{viewofalightcone.eps}
+\caption[magcut]{Four different views of a slightly over-dense \MS line
+of sight, with a $\kappax$ of 0.03.
+{\it Top row, left:} The positions of galaxies projected on the sky. The area
+of the circles is proportional to observed $i$-band flux; the brightest
+object shown has an $i$ magnitude of 17.7.
+{\it Top row, centre:} The angular sizes of halos projected on the sky.
+Red and blue regions lie within the NFW scale radius and virial radius
+of each halo, respectively. There are essentially no empty lightcones.
+{\it Top row, right:} The individual $\kappax$ contributions of
+each halo, assuming a \citet{BMO} truncated NFW
+profile and the \citet{Neto2007}
+mass-concentration relation. Comparison of
+this panel and the centre panel illustrates the relative importance of
+proximity to the line of sight.
+{\it Bottom:} A view along the redshift axis, showing only halos with
+$|x|<0.3$ arcmin. The area of the points is proportional to each halo's
+mass: the most massive halo shown has $1.6\times10^{12}\Msun$. The
+optical axis is shown by the dashed line, while the dotted lines mark
+the lens and source planes for a B1608-like strong lens.}
+\label{fig:lightcone}
+\end{figure*}
 
@@
 
-\begin{figure*}
-\includegraphics[width=\textwidth]{figs/viewofalightcone.eps}
-\caption[magcut]{Four different views of a slightly over-dense \MS line
-of sight, with a $\kappax$ of 0.03. 
-{\it Top row, left:} The positions of galaxies projected on the sky. The area
-of the circles is proportional to observed $i$-band flux; the brightest
-object shown has an $i$ magnitude of 17.7. 
-{\it Top row, centre:} The angular sizes of halos projected on the sky.
-Red and blue regions lie within the NFW scale radius and virial radius
-of each halo, respectively. There are essentially no empty lightcones. 
-{\it Top row, right:} The individual $\kappax$ contributions of
-each halo, assuming a \citet{BMO} truncated NFW 
-profile and the \citet{Neto2007}
-mass-concentration relation. Comparison of
-this panel and the centre panel illustrates the relative importance of
-proximity to the line of sight.
-{\it Bottom:} A view along the redshift axis, showing only halos with
-$|x|<0.3$ arcmin. The area of the points is proportional to each halo's
-mass: the most massive halo shown has $1.6\times10^{12}\Msun$. The
-optical axis is shown by the dashed line, while the dotted lines mark
-the lens and source planes for a B1608-like strong lens.}
-\label{fig:lightcone}
-\end{figure*}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 med},\data)$.
-\comments{, with each calibration sightline weighted equally. PJM: why is
-this? Surely one should weight by the value of the Gaussian function implied
-by that ``$\pm 0.003$''?}
 
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figs/cornerplot.eps}
+\includegraphics[width=\columnwidth]{cornerplot.eps}
 \caption[Biased?]{The conditional distribution of
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figs/globaldist.eps}
+\includegraphics[width=\columnwidth]{globaldist.eps}
 \caption[magcut]{Recovering the global $\pr(\kappax)$ (shown in red). The
@@
 \begin{figure*}
-\includegraphics[width=\textwidth]{figs/where_is_the_kappa.eps}
+\includegraphics[width=\textwidth]{where_is_the_kappa.eps}
 \caption[magcut]{Which objects dominate the external convergence for a line of
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figs/radius_scatter.eps}
+\includegraphics[width=\columnwidth]{radius_scatter.eps}
 \caption[magcut]{The 16, 50 and 84th percentiles of $\kappah$ minus
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figs/mag_scatter.eps}
+\includegraphics[width=\columnwidth]{mag_scatter.eps}
 \caption[magcut]{The 16, 50 and 84th percentiles of $\kappah$ minus
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figs/Width.eps}
+\includegraphics[width=\columnwidth]{Width.eps}
 \caption{The widths of the \infered PDFs $\pr(\kappax|\data)$ for
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figs/WidthvsHilbert.eps}
+\includegraphics[width=\columnwidth]{WidthvsHilbert.eps}
 \caption{Width of the \infered PDF $\pr(\kappax|\data)$ as a function of
@@
 \begin{figure*}
-\includegraphics[width=\textwidth]{figs/biasplots.eps}
+\includegraphics[width=\textwidth]{biasplots.eps}
 \caption{Accuracy in $\kappax$ from combining samples of lenses.  These plots
@@
 \begin{figure*}
-\includegraphics[width=\textwidth]{figs/SHAMbias.eps}
+\includegraphics[width=\textwidth]{SHAMbias.eps}
 \caption{Systematic bias in $\kappax$ due to reconstructing lines of sight with the wrong stellar mass--halo mass relation.
@@
 ensemble, is reminiscent of the procedure followed by \citet{SuyuEtal2010},
-and Greene et al (submitted). The reconstruction method presented here can be
+and \citet{Greene}. The reconstruction method presented here can be
 seen as the limiting case of the weightings explored by Greene et al: rather
@@
 \section*{Acknowledgements}
-
 TEC thanks Vasily Belokurov for supervision, guidance and suggestions.
@@
 for suggesting improvements to the original manuscript.
-\input{acknowledgments.tex}
+%
+TEC acknowledges support from STFC in the form of a research studentship.
+%
+PJM was given support by the Kavli Foundation and the Royal
+Society, in the form of research fellowships.
+%
+% MWA \ldots
+%
+SH and RDB, and CDF, acknowledge support by the National Science Foundation
+(NSF), grant numbers AST-0807458 and  AST-0909119, respectively.
+%
+SHS, ZG  and TT gratefully acknowledge support from the Packard Foundation in
+the form of a Packard Research Fellowship to TT and from the
+NSF grant AST-0642621.
+%
+LVEK acknowledges the support by an NWO-VIDI programme subsidy
+(programme number 639.042.505).
+%
+% This research is supported in part by the National Science Foundation under
+% Grant No. PHY99-07949.
+%
+The Millennium Simulation databases used in this paper and the web application
+providing online access to them were constructed as part of the activities of
+the German Astrophysical Virtual Observatory.
+
+Our code for reconstructing lines of sight is publicly available at {https://github.com/drphilmarshall/Pangloss.}
 

### 2015-08-14 doc/suli-report-swe.tex
Added the document `suli-report-swe.tek` to `doc` which will become Spencers SULI 2015 report. #56

\documentclass{article}

\usepackage{amsmath,amsthm,enumitem,graphicx,gensymb,color,booktabs,hyperref}
\usepackage[margin=1in]{geometry}

\begin{document}

\section*{SULI Report!}
\subsubsection*{Spencer Everett}

\newtheorem{problem}{Problem}
\newtheorem*{problem*}{Problem}

\setlength\parindent{0pt}

\vspace{0.25 in}

(Clearly some work still needs to be done)

\section*{Abstract}

\section*{Introduction}

\section*{Methods}

\section*{Results}

\section*{Discussion}

\section*{Conclusion}

\section*{Acknowledgements}

\section*{References}

\section*{Appendix}

\end{document}

### 2015-08-17 doc/suli-report-swe.tex
Updated `suli-report-swe.tex` to have a first draft of an abstract, outline for most of the paper, and an appendix with the Jarvis `TreeCorr` derivation. #79, #80

@@
-\documentclass{article}
+% ****** Start of file apssamp.tex ******
+%
+%   This file is part of the APS files in the REVTeX 4.1 distribution.
+%   Version 4.1r of REVTeX, August 2010
+%
+%   Copyright (c) 2009, 2010 The American Physical Society.
+%
+%   See the REVTeX 4 README file for restrictions and more information.
+%
+% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
+% as well as the rest of the prerequisites for REVTeX 4.1
+%
+% See the REVTeX 4 README file
+% It also requires running BibTeX. The commands are as follows:
+%
+%  1)  latex apssamp.tex
+%  2)  bibtex apssamp
+%  3)  latex apssamp.tex
+%  4)  latex apssamp.tex
+%
+\documentclass[%
+ reprint,
+%superscriptaddress,
+%groupedaddress,
+%unsortedaddress,
+%runinaddress,
+%frontmatterverbose, 
+%preprint,
+%showpacs,preprintnumbers,
+%nofootinbib,
+%nobibnotes,
+%bibnotes,
+ amsmath,amssymb,
+ aps,
+%pra,
+%prb,
+%rmp,
+%prstab,
+%prstper,
+%floatfix,
+]{revtex4-1}
 
-\usepackage{amsmath,amsthm,enumitem,graphicx,gensymb,color,booktabs,hyperref}
-\usepackage[margin=1in]{geometry}
+\usepackage{graphicx}% Include figure files
+\usepackage{dcolumn}% Align table columns on decimal point
+\usepackage{bm}% bold math
+%\usepackage{multicol}
+%\usepackage{hyperref}% add hypertext capabilities
+%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
+%\linenumbers\relax % Commence numbering lines
+
+%\usepackage[showframe,%Uncomment any one of the following lines to test 
+%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
+%%text={7in,10in},centering,
+%%margin=1.5in,
+%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
+%%height=10in,a5paper,hmargin={3cm,0.8in},
+%]{geometry}
 
@@
 
-\section*{SULI Report!}
-\subsubsection*{Spencer Everett}
+\preprint{APS/123-QED}
 
-\newtheorem{problem}{Problem}
-\newtheorem*{problem*}{Problem}
+\title{SULI Report!}
+%\thanks{A footnote to the article title}%
 
-\setlength\parindent{0pt}
+\author{Spencer Everett}
+ \affiliation{Department of Physics, DePaul University.}%Lines break automatically or can be forced with \\
+ \email{spencerweverett@gmail.com}
 
-\vspace{0.25 in}
+%\collaboration{MUSO Collaboration}%\noaffiliation
 
-(Clearly some work still needs to be done)
+\date{\today}
 
-\section*{Abstract}
+\begin{abstract}
+As dark matter does not absorb or emit light, its distribution in the universe must be inferred through indirect effects such as the gravitational lensing of distant galaxies.
+While most sources are only weakly lensed, the systematic alignment of background galaxies around a foreground lens can constrain the mass of the lens which is largely in the form of dark matter.
+In this paper, a simple halo model is used to approximate the dark matter mass distribution of the Millennium Simulation on the galaxy and cluster scales.
+Background sources are generated at a redshift of ${z = 1.3857}$ and then weakly lensed by the foreground halos contained in a light cone centered along each line of sight, which is carried out by the \texttt{Pangloss} framework\footnote{https://github.com/drphilmarshall/Pangloss}.
+The model-predicted ellipticities of the background galaxies after lensing are compared to the ``true'' weakly-lensed ellipticities determined by the ray-traced convergence and shear calculated by Hilbert et al.
+(citation).
+Using the shear-shear and galaxy-galaxy correlation functions, I find that the \texttt{Pangloss} framework systematically under-predicts the shear power in both statistics and does not accurately capture the effect of dark matter structure at scales larger than 1 arcminute.
+Physical and computational shortcomings of the Pangloss framework are discussed, as well as potential improvements for upcoming work.
+\end{abstract}
 
-\section*{Introduction}
+%\pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
+                             % Classification Scheme.
+%\keywords{Suggested keywords}%Use showkeys class option if keyword
+                              %display desired
+\maketitle
 
-\section*{Methods}
+%\tableofcontents
 
-\section*{Results}
+\section{Introduction}
 
-\section*{Discussion}
+\begin{itemize}
+\item Broad intro into cosmology and dark matter, set problem in context
+    \begin{itemize}
+    \item (Very) short introduction to history of dark matter, Zwicky, rotation curves, etc.
+    \end{itemize}
+\begin{itemize}
+\item Introduction to gravitational lensing
+    \begin{itemize}
+    \item Convergence and Shear / Strong and Weak lensing
+        \begin{itemize}
+        \item Dramatic effect of strong lensing, how it is used for constraining cos. parameters
+        \item Only a few hundred known, not good for making mass maps
+        \item All galaxies are weakly lensed, good for our purposes
+        \end{itemize}
+    \end{itemize}
+\end{itemize}
+\item What this work does and aims for
+\begin{itemize}
+    \item We aim to implement a simple dark matter halo model to predict weak-lensing effects by foreground mass - and to make the prediction `quickly' and/or with large parallelization
+    \item Quick summary of what we do in paper
+        \begin{itemize}
+        \item Use halo model to make approximation of dark matter mass distribution in Millennium Simulation
+        \item Use shear-shear and galaxy-galaxy correlation functions as summary statistics
+        \item Compare statistics to ray-traced data
+        \item Discuss physial and computational shortcomings with current methodology
+        \end{itemize}
+    \end{itemize}
+\end{itemize}
 
-\section*{Conclusion}
+\section{Theory}
 
-\section*{Acknowledgements}
+\begin{itemize}
+\item Galaxy ellipticities
+    \begin{itemize}
+    \item (Most) galaxies are not circular - have intrinsic ellipticities
+        \begin{itemize}
+        \item If they were all circular, we could measure the change in shape exactly!
+        \end{itemize}
+    \item Galaxies are not always well approximated by ellipses (reference)
+    \item Mathematical formalism
+    \end{itemize}
+\item Shape noise and PSF issues in weak lensing (distorting already weak signal)
+\item Gravitational lensing
+    \begin{itemize}
+    \item Short introduction to problem setup for simple case (point mass maybe?)
+    \item Assumptions made in a typical solution (thin lens approximation?)
+    \item Show solution from Schneider
+    \item Shear and convergence 
+    \item Measuring shear in weak lensing - a statistical feature
+    \end{itemize}
+\item Dark matter halos
+    \begin{itemize}
+    \item NFW profile and equation (reference)
+    \item BMO truncation and equation (reference)
+    \end{itemize}
+\item SMHR? Or too distracting?
+\end{itemize}
 
-\section*{References}
+\section{Methods}
 
-\section*{Appendix}
+\begin{itemize}
+\item Assumptions
+    \begin{itemize}
+    \item A catalog with galaxy ellipticities
+    \item Currently use actual dark matter halo mass for an idea of best case scenario - can run same analysis with masses sampled from SMHR (reference)
+    \item PSF already accounted for in catalog and error low enough for weak lensing analysis
+    \item Use actual redshift for best case scenario (but can easily be replaced by photometric redshift sampling)
+    \end{itemize}
+\item Millennium Simulation
+    \begin{itemize}
+    \item Instead of blindly using \texttt{Pangloss} to make dark matter mass maps using sky survey data, we instead test how accurately and precisely we can predict weakly-lensed shear and convergence
+    \item Mention which M.S. we used
+    \item S. Hilbert`s ray traced M.S. (reference)
+        \begin{itemize}
+        \item Can use the ray-traced convergence and shear to calculate the ``true'' lensed ellipticties and compare to \texttt{Pangloss}
+        \end{itemize}
+    \end{itemize}
+\item Background galaxies
+    \begin{itemize}
+    \item random orientation
+    \item ellipticity range (get numbers!)
+    \item Accounting for shape noise
+    \end{itemize}
+\item Lightcones
+    \begin{itemize}
+    \item Instead of using all foreground mass in a field to calculate the lensing of a single background object, we create a lightcone centered at the source with a chosen radius $R$
+    \item Drilling
+        \begin{itemize}
+        \item redshift grid to speed up calcuations
+        \item Use the physical distance to line of sight in lensing calculations
+            \begin{itemize}
+            \item Redshift-to-distance relation (equation and reference)
+            \end{itemize}
+        \item Ranking galaxy `relevance'
+            \begin{itemize}
+            \item Want to only include the most important galaxies for lensing to speed up computation, as most will have negligable mass or be too far away
+            \item Allows quicker lensing calculations, means we can make $R$ bigger
+            \item Show `relevance` metric ($M/R^3$ but unitless)
+            \item Include plot of predicted relevance vs kappa contribution??
+            \end{itemize}
+        \end{itemize}
+    \item Lensing by Halos
+        \begin{itemize}
+        \item Treat each foreground halo as a separate lensing event
+        \item Total lensing is the sum of each event
+        \item Lookup table??
+        \end{itemize}
+    \item Include cartoon
+    \end{itemize}
+\item Checking the halo model: Use of correlation functions as summary statistics for ellipticity predictions
+    \begin{itemize}
+        \item Introduce the concept of correlation functions in general
+            \begin{itemize}
+            \item Definition
+            \item Autocorrelation vs cross-correlation
+            \item Use of correlation functions in cosmology
+            \item Shear-shear and galaxy-galaxy correlation functions
+                \begin{itemize}
+                \item Reference appendix for Visualizing Correlation Functions
+                \end{itemize}
+            \end{itemize}
+        \item Use of Jarvis`s \texttt{TreeCorr} code to calculate cf`s
+        \begin{itemize}
+            \item Reference appendix for Jarvis proof
+        \end{itemize}
+    \end{itemize}
+\item Show one map with ray-traced features and lensed ellipticities vs another map with \texttt{Pangloss} features and predicted ellipticities?
+\end{itemize}
+
+\section{Results}
+
+\begin{itemize}
+\item Maps??
+\item Correlation Functions
+    \begin{itemize}
+    \item shear-shear
+    \item galaxy-galaxy
+    \item progression of each as $R$ increases??
+    \item cf`s without shape noise and with shape noise
+    \item cf`s with all galaxies vs with only `relevant' galaxies?
+    \end{itemize}
+\item The Need for Speed
+    \begin{itemize}
+    \item Table or graph of speedups and CPU time per lightcone progression (make sure to check \texttt{timeit} first!)
+    \end{itemize}
+\end{itemize}
+
+\section{Discussion}
+
+\begin{itemize}
+\item Issues with the \texttt{Pangloss} framework
+    \begin{itemize}
+    \item Systematic shear power under-prediction in cf`s
+    \item Missing large-scale dark matter structure
+    \end{itemize}
+    \item Possibly missing features in model
+        \begin{itemize}
+        \item voids
+        \item filaments
+        \item stellar mass
+        \end{itemize}
+    \item Speed
+\item Moving Foward
+    \begin{itemize}
+    \item Scaling up
+        \begin{itemize}
+        \item CPU and RAM numbers for lightcone parallelization from discussion with Debbie Bard
+        \end{itemize}
+    \item other stuff - too tired right now
+    \end{itemize}
+\end{itemize}
+
+\section{Conclusion}
+
+pass
+
+\section{Acknowledgements}
+
+\begin{itemize}
+\item DOE
+\item SULI
+\item Stanford University
+\item KIPAC
+\item Risa, Matt, Pat
+\item Phil!!
+\end{itemize}
+
+\section{References}
+
+\begin{itemize}
+\item P.J. Marshall Thesis?
+\item Collett et al.
+\item S. Hilbert (ray-traced)
+\item Millennium Simulation
+\item Schneider
+\item Jarvis \texttt{TreeCorr}
+\item NFW profile
+\item BMO truncation
+\end{itemize}
+
+\onecolumngrid
+\section{Appendix}
+
+\subsection{Visualizing Correlation Functions}
+
+\begin{itemize}
+\item Use as a brief introduction to the shear-shear and galaxy-galaxy correlation function as used in this work
+    \begin{itemize}
+    \item reference other (much more detailed) material for readers to find
+    \end{itemize}
+\item Include correlation value colormaps for $\xi_+$, $\xi_-$, and $\xi_\times$ along with discussion of correlation pattern
+\item Include color-coded correlation visuals along with setup
+    \begin{itemize}
+    \item Galaxies around lens before lensing - correlation values scatter plot with no signal
+    \item Galaxies around lens after lensing - correlation values scatter plot with signal
+    \end{itemize}
+\item B-modes and E-modes plot??
+\end{itemize}
+
+\subsection{Jarvis Proof}
+
+\begin{itemize}
+\item Introduction to difference between the common Schneider definition of lensing correlation functions and that used by Jarvis`s \texttt{TreeCorr} code
+\item Here we derive the connection between the two
+\item Definitions of each, along with references
+\end{itemize}
+
+From Jarvis \href{http://arxiv.org/pdf/astro-ph/0307393v2.pdf}{(Page 3)}:
+\begin{align}
+\xi_+&=\left<\gamma_i\gamma_j^*\right>=\texttt{xip}+i(\texttt{xip\_im})\label{s+}\\
+\xi_-&=\left<\gamma_i\gamma_je^{-4i\alpha}\right>=\texttt{xim}+i(\texttt{xim\_im})\label{s-}
+\end{align}
+
+where $\alpha$ is the angle between the two objects $i,j$ and each $\gamma$ is given by $\gamma_n=|\gamma_n|e^{2i\theta_n}$ in polar form.\\
+
+From Schneider \href{http://arxiv.org/pdf/astro-ph/0509252v1.pdf}{(Page 92)}:
+\begin{align}
+\xi_\pm&=\left<\gamma_{i_t}\gamma_{j_t}\right>\pm\left<\gamma_{i_\times}\gamma_{j_\times}\right>\label{s+-}\\
+\xi_\times&=\left<\gamma_{i_t}\gamma_{j_\times}\right>\label{sx}
+\end{align}
+
+where $\gamma_{n_t}=-\operatorname{Re}\left(\gamma_n e^{-2i\alpha}\right)$ and $\gamma_{n_\times}=-\operatorname{Im}\left(\gamma_n e^{-2i\alpha}\right)$.\\
+
+\section*{Schneider's $\xi_+$ to Jarvis's \texttt{xip}}
+
+Starting with Schneider's definition, observe that
+\begin{align*}
+\xi_+&=\left<\gamma_{i_t}\gamma_{j_t}\right>+\left<\gamma_{i_\times}\gamma_{j_\times}\right>\\
+&=\left<\operatorname{Re}\left(\gamma_ie^{-2i\alpha}\right)\cdot\operatorname{Re}\left(\gamma_je^{-2i\alpha}\right)\right>+\left<\operatorname{Im}\left(\gamma_ie^{-2i\alpha}\right)\cdot\operatorname{Im}\left(\gamma_je^{-2i\alpha}\right)\right>\\
+&=\left<\operatorname{Re}\left(|\gamma_i|e^{2i(\theta_i-\alpha)}\right)\cdot\operatorname{Re}\left(|\gamma_j|e^{2i(\theta_j-\alpha)}\right)\right>+\left<\operatorname{Im}\left(|\gamma_i|e^{2i(\theta_i-\alpha)}\right)\cdot\operatorname{Im}\left(|\gamma_j|e^{2i(\theta_j-\alpha)}\right)\right>\\
+&=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\alpha)\right)\cos\left(2(\theta_j-\alpha)\right)\right>+\left<|\gamma_i|\cdot|\gamma_j|\sin\left(2(\theta_i-\alpha)\right)\sin\left(2(\theta_j-\alpha)\right)\right>.
+\end{align*}
+
+Using the trig identities
+\begin{align}
+\cos(u)\cos(v)&=\frac{1}{2}\left[\cos(u-v)+\cos(u+v)\right],\\
+\sin(u)\sin(v)&=\frac{1}{2}\left[\cos(u-v)-\cos(u+v)\right],
+\end{align}
+
+and the linearity of the expectation operator, it is straightforward to show that
+%\begin{align*}
+%\xi_+&=\left<|\gamma_i|\cdot|\gamma_j|\right>\cdot\left(\left<\frac{1}{2}\left[\cos\left(2(\theta_i-\theta_j)\right)+\cos\left(2(\theta_i+\theta_j-2\alpha)\right)\right]\right>+\left<\frac{1}{2}\left[\cos\left(2(\theta_i-\theta_j)\right)-\cos\left(2(\theta_i+\theta_j-2\alpha)\right)\right]\right>\right)\\
+%&=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\theta_j)\right)\right>.
+%\end{align*}
+$$\xi_+=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\theta_j)\right)\right>.$$
+
+Now using the identity
+\begin{equation}\label{trig2}
+\cos(u\pm v)=\cos\left(u\right)\cos\left(v\right)\mp\sin\left(u\right)\sin\left(v\right),
+\end{equation}
+
+the previous equation can be written as
+
+\begin{align*}
+\xi_+&=\left<|\gamma_i|\cdot|\gamma_j|\cdot\left[\cos\left(2\theta_i\right)\cos\left(2\theta_j\right)+\sin\left(2\theta_i\right)\sin\left(2\theta_j\right)\right]\right>\\
+&=\left<\operatorname{Re}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)+\operatorname{Im}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\right>.
+\end{align*}
+
+Using the complex number identities
+
+\begin{align}
+\operatorname{Re}(z)&=\frac{1}{2}\left[z+z^*\right],\label{complex1}\\
+\operatorname{Im}(z)&=\frac{1}{2i}\left[z-z^*\right]\label{complex2},
+\end{align}
+
+it follows that
+
+\begin{align*}
+\xi_+&=\left<\frac{1}{4}\left[(\gamma_i+\gamma_i^*)(\gamma_j+\gamma_j^*)-(\gamma_i-\gamma_i^*)(\gamma_j-\gamma_j^*)\right]\right>\\
+&=\left<\frac{1}{2}\left[\gamma_i\gamma_j^*+(\gamma_i\gamma_j^*)^*\right]\right>\\
+&=\left<\operatorname{Re}(\gamma_i\gamma_j^*)\right>=\texttt{xip}.
+\end{align*}
+
+\section*{Schneider's $\xi_-$ to Jarvis's \texttt{xim}}
+
+The first few steps are identical to the previous section besides the negative in the definition of $\xi_-$, giving
+\begin{align*}
+\xi_-&=\left<\gamma_{i_t}\gamma_{j_t}\right>-\left<\gamma_{i_\times}\gamma_{j_\times}\right>\\
+&=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\alpha)\right)\cos\left(2(\theta_j-\alpha)\right)\right>-\left<|\gamma_i|\cdot|\gamma_j|\sin\left(2(\theta_i-\alpha)\right)\sin\left(2(\theta_j-\alpha)\right)\right>\\
+&=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i+\theta_j-2\alpha)\right)\right>.
+\end{align*}
+
+Now using Equation \eqref{trig2} twice, first letting $u=2(\theta_i+\theta_j)$ and $v=-4\alpha$, and then letting $u=2\theta_i$ and $v=2\theta_j$, this equation becomes
+
+\begin{align*}
+\xi_-&=\left<|\gamma_i|\cdot|\gamma_j|\Big(\left[\cos(2\theta_i)\cos(2\theta_j)-\sin(2\theta_i)\sin(2\theta_j)\right]\cos(4\alpha)+\left[\sin(2\theta_i)\cos(2\theta_j)+\cos(2\theta_i)\sin(2\theta_j)\right]\sin(4\alpha)\Big)\right>\\
+&=\Big<\big[\operatorname{Re}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)-\operatorname{Im}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\big]\cos(4\alpha)+\big[\operatorname{Im}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)+\operatorname{Re}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\big]\sin(4\alpha)\Big>.
+\end{align*}
+
+Using the identities \eqref{complex1} and \eqref{complex2}, and simplifying the leftover terms, this equation can be shown to equal
+\begin{align*}
+\xi_-=\big<\operatorname{Re}(\gamma_i\gamma_j)\cos(4\alpha)+\operatorname{Im}(\gamma_i\gamma_j)\sin(4\alpha)\big>.
+\end{align*}
+
+Now observe that for two complex numbers $a$ and $b$, it is true that
+
+$$\operatorname{Re}(a\cdot b^*)=\operatorname{Re}(a)\cdot\operatorname{Re}(b)+\operatorname{Im}(a)\cdot\operatorname{Im}(b).$$
+
+Then setting $a=\gamma_i\gamma_j$ and $b=e^{4i\alpha}$, it must be true that
+
+$$\operatorname{Re}\left(\gamma_i\gamma_je^{-4i\alpha}\right)=\operatorname{Re}(\gamma_i\gamma_j)\cos(4\alpha)+\operatorname{Im}(\gamma_i\gamma_j)\sin(4\alpha).$$
+
+Combining this with our previous result, this means that
+
+$$\xi_-=\big<\operatorname{Re}(\gamma_i\gamma_j)\cos(4\alpha)+\operatorname{Im}(\gamma_i\gamma_j)\sin(4\alpha)\big>=\left<\operatorname{Re}\left(\gamma_i\gamma_je^{-4i\alpha}\right)\right>=\texttt{xim}.$$
+
+\section*{Schneider's $\xi_\times$ to Jarvis's $\frac{1}{2}\left(\texttt{xim\_im}-\texttt{xip\_im}\right)$}
+
+Starting from Schneider's definition of $\xi_\times$,
+
+\begin{align*}
+\xi_\times&=\left<\gamma_{i_t}\gamma_{j_\times}\right>\\
+&=\left<\operatorname{Re}\left(|\gamma_i|e^{2i(\theta_i-\alpha)}\right)\cdot\operatorname{Im}\left(|\gamma_j|e^{2i(\theta_j-\alpha)}\right)\right>\\
+&=\big<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\alpha)\right)\sin\left(2(\theta_j-\alpha)\right)\big>.\\
+\end{align*}
+
+Using the trig identity
+
+\begin{equation}\label{trig3}
+\cos(u)\sin(v)=\frac{1}{2}\left[\sin(u+v)-\sin(u-v)\right],
+\end{equation}
+
+the previous equation becomes
+
+\begin{align*}
+\xi_\times&=\left<|\gamma_i|\cdot|\gamma_j|\cdot\frac{1}{2}\big[\sin\left(2(\theta_i+\theta_j-2\alpha)\right)-\sin\left(2(\theta_i-\theta_j)\right)\big]\right>.
+\end{align*}
+
+Next, applying the identities
+
+\begin{equation}\label{trig4}
+\sin(u\pm v)=\sin(u)\cos(v)\pm\cos(u)\sin(v)
+\end{equation}
+
+along with \eqref{trig2} iteratively until each trig function only has a single term, the equation becomes
+
+\begin{align*}
+\xi_\times&=\Big<|\gamma_i|\cdot|\gamma_j|\cdot\frac{1}{2}\Big(\left[\sin(2\theta_i)\cos(2\theta_j)+\cos(2\theta_i)\sin(2\theta_j)\right]\cos(4\alpha)\\
+&\qquad\qquad\qquad\quad-\left[\cos(2\theta_i)\cos(2\theta_j)-\sin(2\theta_i)\sin(2\theta_j)\right]\sin(4\alpha)\\
+&\qquad\qquad\qquad\quad-\sin(2\theta_i)\cos(2\theta_j)+\cos(2\theta_i)\sin(2\theta_j)\Big)\Big>\\
+&=\Big<\frac{1}{2}\Big(\left[\operatorname{Im}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)+\operatorname{Re}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\right]\cos(4\alpha)\\
+&\qquad-\left[\operatorname{Re}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)-\operatorname{Im}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\right]\sin(4\alpha)\\
+&\qquad-\operatorname{Im}(\gamma_i)\operatorname{Re}(\gamma_j)+\operatorname{Re}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\Big)\Big>.\\
+\end{align*}
+
+Using the identities \eqref{complex1} and \eqref{complex2}, this can be simplified to
+
+\begin{align*}
+\xi_\times&=\left<\frac{1}{2}\big[\operatorname{Im}(\gamma_i\gamma_j)\cos(4\alpha)-\operatorname{Re}(\gamma_i\gamma_j)\sin(4\alpha)-\operatorname{Im}(\gamma_i\gamma_j^*)\big]\right>.
+\end{align*}
+
+Consider again two complex numbers $a$ and $b$. Observe that
+
+$$\operatorname{Im}(a\cdot b^*)=\operatorname{Im}(a)\cdot\operatorname{Re}(b)-\operatorname{Re}(a)\cdot\operatorname{Im}(b).$$
+
+Then setting $a=\gamma_i\gamma_j$ and $b=e^{4i\alpha}$, it must be true that
+
+$$\operatorname{Im}\left(\gamma_i\gamma_je^{-4i\alpha}\right)=\operatorname{Im}(\gamma_i\gamma_j)\cos(4\alpha)-\operatorname{Re}(\gamma_i\gamma_j)\sin(4\alpha).$$
+
+Combing these results give
+
+\begin{align*}
+\xi_\times&=\left<\frac{1}{2}\big[\operatorname{Im}(\gamma_i\gamma_j)\cos(4\alpha)-\operatorname{Re}(\gamma_i\gamma_j)\sin(4\alpha)-\operatorname{Im}(\gamma_i\gamma_j^*)\big]\right>\\
+&=\left<\frac{1}{2}\big[\operatorname{Im}\left(\gamma_i\gamma_je^{-4i\alpha}\right)-\operatorname{Im}(\gamma_i\gamma_j^*)\big]\right>\\
+&=\frac{1}{2}\big[\texttt{xim\_im}-\texttt{xip\_im}\big].
+\end{align*}
+
+as desired.
+
+% Bibliography
 
 \end{document}
+%
+% ****** End of file apssamp.tex ******
+
+\end{document}
+
+\begin{itemize}
+
+\end{itemize}

### 2015-08-17 doc/suli-report-swe.tex
Added an introduction to the SULI report. Added points to the outline throughout. #81

@@
 Using the shear-shear and galaxy-galaxy correlation functions, I find that the \texttt{Pangloss} framework systematically under-predicts the shear power in both statistics and does not accurately capture the effect of dark matter structure at scales larger than 1 arcminute.
-Physical and computational shortcomings of the Pangloss framework are discussed, as well as potential improvements for upcoming work.
+Physical and computational shortcomings of the \texttt{Pangloss} framework are discussed, as well as potential improvements for upcoming work.
 \end{abstract}
@@
 
-\begin{itemize}
-\item Broad intro into cosmology and dark matter, set problem in context
-    \begin{itemize}
-    \item (Very) short introduction to history of dark matter, Zwicky, rotation curves, etc.
-    \end{itemize}
-\begin{itemize}
-\item Introduction to gravitational lensing
-    \begin{itemize}
-    \item Convergence and Shear / Strong and Weak lensing
-        \begin{itemize}
-        \item Dramatic effect of strong lensing, how it is used for constraining cos. parameters
-        \item Only a few hundred known, not good for making mass maps
-        \item All galaxies are weakly lensed, good for our purposes
-        \end{itemize}
-    \end{itemize}
-\end{itemize}
-\item What this work does and aims for
-\begin{itemize}
-    \item We aim to implement a simple dark matter halo model to predict weak-lensing effects by foreground mass - and to make the prediction `quickly' and/or with large parallelization
-    \item Quick summary of what we do in paper
-        \begin{itemize}
-        \item Use halo model to make approximation of dark matter mass distribution in Millennium Simulation
-        \item Use shear-shear and galaxy-galaxy correlation functions as summary statistics
-        \item Compare statistics to ray-traced data
-        \item Discuss physial and computational shortcomings with current methodology
-        \end{itemize}
-    \end{itemize}
-\end{itemize}
+In a universe teeming with galaxies and light, it came as a shock to 20th century astronomers that most of the mass in the universe is in fact dark.
+The `normal' matter made of atoms that we interact with in everyday life, called baryonic matter, only accounts for (20\%?) of the mass in the observable universe, and only (4.9\%?) of the mass-energy content of the universe (cite L-CDM).
+While this claim sounds bizarre, there has been an abundance of indirect evidence in recent decades for the existence of dark matter including the flattening of galaxy rotation curves (cite), the existence of baryonic acoustic oscillations (cite), and anisotropies in the cosmic microwave background (cite).
+
+One of the most successful probes of dark matter has been gravitational lensing.
+The path of light from distant `background' galaxies is bent when traveling through regions of space containing large amounts of `foreground' mass.
+The process is described by Einstein's theory of general relativity, but simply put – the more mass, the more light bends.
+Light from different origins in a background galaxy are subject to different bending which results in a distortion of the galaxy image.
+As the foreground mass is known to be largely dark matter, gravitational lensing supplies a direct constraint on the mass of dark matter in that region.
+
+While the effects of gravitational lensing can be dramatic, the shape of most galaxies is only distorted by a few percent (cite) and can only be detected statistically as the intrinsic shape is not known.
+If a model for the distribution of dark matter in a region of foreground mass can accurately predict the statistical signal of this `weak' lensing of background galaxies, then the model can be used on galaxies in existing sky survey data to extrapolate the amount of dark matter in the region and construct large-scale maps of the dark matter in the universe.
+
+In this paper, I aim to do the former by applying a simple dark matter halo model to the Millennium Simulation and predicting the weakly lensed ellipticities of generated background sources.
+A brief introduction into the theory of measuring galaxy ellipticities, the effects of strong and weak gravitational lensing, and dark matter halos is discussed in Section II.
+The implementation of a halo model on the Millennium Simulation is described in Section III, and the results of the model on (x \# of galaxies on a field size of z deg$^2$) as well as a comparison of the predicted lensed ellipticities to the true ellipticities is given in Section IV.
+Section V discusses limitations of the Pangloss framework as well as potential physical and computational improvements that can be made for upcoming work before concluding remarks in Section VI.
 
@@
     \item Mathematical formalism
+    \item Plot of galaxy orientation given e1 and e2 from P.J. Marshall thesis
     \end{itemize}
@@
 \item BMO truncation
+\item Planck
+\item galaxy curves
+\item BAOs
+\item LCDM
+\item GR
+\item wl distortion percent
 \end{itemize}
@@
 \end{itemize}
+
+% Outline:
+
+%% Intro:
+\begin{itemize}
+\item Broad intro into cosmology and dark matter, set problem in context
+    \begin{itemize}
+    \item (Very) short introduction to history of dark matter, Zwicky, rotation curves, etc.
+    \end{itemize}
+\begin{itemize}
+\item Introduction to gravitational lensing
+    \begin{itemize}
+    \item Convergence and Shear / Strong and Weak lensing
+        \begin{itemize}
+        \item Dramatic effect of strong lensing, how it is used for constraining cos. parameters
+        \item Only a few hundred known, not good for making mass maps
+        \item All galaxies are weakly lensed, good for our purposes
+        \end{itemize}
+    \end{itemize}
+\end{itemize}
+\item What this work does and aims for
+\begin{itemize}
+    \item We aim to implement a simple dark matter halo model to predict weak-lensing effects by foreground mass - and to make the prediction `quickly' and/or with large parallelization
+    \item Quick summary of what we do in paper
+        \begin{itemize}
+        \item Use halo model to make approximation of dark matter mass distribution in Millennium Simulation
+        \item Use shear-shear and galaxy-galaxy correlation functions as summary statistics
+        \item Compare statistics to ray-traced data
+        \item Discuss physial and computational shortcomings with current methodology
+        \end{itemize}
+    \end{itemize}
+\end{itemize}

### 2015-08-17 doc/suli-report-swe.tex
Restructured the first two sentences of the introduction to better describe dark matter. #81

@@
 
-In a universe teeming with galaxies and light, it came as a shock to 20th century astronomers that most of the mass in the universe is in fact dark.
-The `normal' matter made of atoms that we interact with in everyday life, called baryonic matter, only accounts for (20\%?) of the mass in the observable universe, and only (4.9\%?) of the mass-energy content of the universe (cite L-CDM).
+In a universe teeming with galaxies and light, it came as a shock when 20\textsuperscript{th} century astronomers unexpectedly discovered that most of the mass in the universe is in fact dark; the `normal' matter made of atoms that we interact with in everyday life, called baryonic matter, only accounts for (20\%?) of the mass in the observable universe, while the rest takes the form of an exotic dark matter that does not absorb or emit light rendering it invisible to our telescopes.
 While this claim sounds bizarre, there has been an abundance of indirect evidence in recent decades for the existence of dark matter including the flattening of galaxy rotation curves (cite), the existence of baryonic acoustic oscillations (cite), and anisotropies in the cosmic microwave background (cite).

### 2015-08-17 doc/suli-report-swe.tex
Broke up the first sentence of the introduction into smaller pieces. Small formatting changes to the second paragraph of the introduction. #81

--- 2015-08-17 doc/suli-report-swe.tex
@@
 
-In a universe teeming with galaxies and light, it came as a shock to 20th century astronomers that most of the mass in the universe is in fact dark.
-The `normal' matter made of atoms that we interact with in everyday life, called baryonic matter, only accounts for (20\%?) of the mass in the observable universe, and only (4.9\%?) of the mass-energy content of the universe (cite L-CDM).
+In a universe teeming with galaxies and light, it came as a shock when 20\textsuperscript{th} century astronomers unexpectedly discovered that most of the mass in the universe is in fact dark; the `normal' matter made of atoms that we interact with in everyday life, called baryonic matter, only accounts for (20\%?) of the mass in the observable universe.
+The remaining mass takes the form of an exotic dark matter that does not absorb or emit light, rendering it invisible to our telescopes.
 While this claim sounds bizarre, there has been an abundance of indirect evidence in recent decades for the existence of dark matter including the flattening of galaxy rotation curves (cite), the existence of baryonic acoustic oscillations (cite), and anisotropies in the cosmic microwave background (cite).
@@
 The path of light from distant `background' galaxies is bent when traveling through regions of space containing large amounts of `foreground' mass.
-The process is described by Einstein's theory of general relativity, but simply put – the more mass, the more light bends.
+The process is described by Einstein's general theory of relativity, but simply put -- the more mass, the more light bends.
 Light from different origins in a background galaxy are subject to different bending which results in a distortion of the galaxy image.

### 2015-08-18 doc/suli-report-swe.tex
Added the first draft of the Methods section in the SULI report. #81

@@
 A brief introduction into the theory of measuring galaxy ellipticities, the effects of strong and weak gravitational lensing, and dark matter halos is discussed in Section II.
-The implementation of a halo model on the Millennium Simulation is described in Section III, and the results of the model on (x \# of galaxies on a field size of z deg$^2$) as well as a comparison of the predicted lensed ellipticities to the true ellipticities is given in Section IV.
-Section V discusses limitations of the Pangloss framework as well as potential physical and computational improvements that can be made for upcoming work before concluding remarks in Section VI.
+The implementation of a halo model on the Millennium Simulation is described in Section III, and the results of the model on (x \# of galaxies on a field size of x \# deg$^2$) as well as a comparison of the predicted lensed ellipticities to the true ellipticities is given in Section IV.
+Section V discusses limitations of the used Pangloss framework as well as potential physical and computational improvements that can be made for upcoming work before concluding remarks in Section VI.
 
-\section{Theory}
+\section{Theoretical Background}
 
@@
 
-\section{Methods}
+\section{The Pangloss Framework}
 
-\begin{itemize}
-\item Assumptions
-    \begin{itemize}
-    \item A catalog with galaxy ellipticities
-    \item Currently use actual dark matter halo mass for an idea of best case scenario - can run same analysis with masses sampled from SMHR (reference)
-    \item PSF already accounted for in catalog and error low enough for weak lensing analysis
-    \item Use actual redshift for best case scenario (but can easily be replaced by photometric redshift sampling)
-    \end{itemize}
-\item Millennium Simulation
-    \begin{itemize}
-    \item Instead of blindly using \texttt{Pangloss} to make dark matter mass maps using sky survey data, we instead test how accurately and precisely we can predict weakly-lensed shear and convergence
-    \item Mention which M.S. we used
-    \item S. Hilbert`s ray traced M.S. (reference)
-        \begin{itemize}
-        \item Can use the ray-traced convergence and shear to calculate the ``true'' lensed ellipticties and compare to \texttt{Pangloss}
-        \end{itemize}
-    \end{itemize}
-\item Background galaxies
-    \begin{itemize}
-    \item random orientation
-    \item ellipticity range (get numbers!)
-    \item Accounting for shape noise
-    \end{itemize}
-\item Lightcones
-    \begin{itemize}
-    \item Instead of using all foreground mass in a field to calculate the lensing of a single background object, we create a lightcone centered at the source with a chosen radius $R$
-    \item Drilling
-        \begin{itemize}
-        \item redshift grid to speed up calcuations
-        \item Use the physical distance to line of sight in lensing calculations
-            \begin{itemize}
-            \item Redshift-to-distance relation (equation and reference)
-            \end{itemize}
-        \item Ranking galaxy `relevance'
-            \begin{itemize}
-            \item Want to only include the most important galaxies for lensing to speed up computation, as most will have negligable mass or be too far away
-            \item Allows quicker lensing calculations, means we can make $R$ bigger
-            \item Show `relevance` metric ($M/R^3$ but unitless)
-            \item Include plot of predicted relevance vs kappa contribution??
-            \end{itemize}
-        \end{itemize}
-    \item Lensing by Halos
-        \begin{itemize}
-        \item Treat each foreground halo as a separate lensing event
-        \item Total lensing is the sum of each event
-        \item Lookup table??
-        \end{itemize}
-    \item Include cartoon
-    \end{itemize}
-\item Checking the halo model: Use of correlation functions as summary statistics for ellipticity predictions
-    \begin{itemize}
-        \item Introduce the concept of correlation functions in general
-            \begin{itemize}
-            \item Definition
-            \item Autocorrelation vs cross-correlation
-            \item Use of correlation functions in cosmology
-            \item Shear-shear and galaxy-galaxy correlation functions
-                \begin{itemize}
-                \item Reference appendix for Visualizing Correlation Functions
-                \end{itemize}
-            \end{itemize}
-        \item Use of Jarvis`s \texttt{TreeCorr} code to calculate cf`s
-        \begin{itemize}
-            \item Reference appendix for Jarvis proof
-        \end{itemize}
-    \end{itemize}
-\item Show one map with ray-traced features and lensed ellipticities vs another map with \texttt{Pangloss} features and predicted ellipticities?
-\end{itemize}
+To constrain the mass of foreground dark matter using weak gravitational lensing, first a model of the relationship between foreground galaxies and the foreground dark matter must be established and robustly tested to see if, statistically, it makes the same lensing predictions of background sources as the true undering dark matter structure.
+To do this, I built upon the publically available \texttt{Pangloss} framework used in Collett et al.
+(cite) to reconstruct all the mass along the line of sight of each background galaxy using dark matter halos.
+The lensing contribution of each halo is calculated, and the total lensing of the background galaxy is the sum of each halo contribution.
+This process is detailed in the following sections.
+
+\subsection*{Assumptions}
+While \texttt{Pangloss} may be used more generally, the present analysis makes some additional strong assumptions to simplify the problem for a first attempt at making weak lensing predictions.
+
+\begin{enumerate}
+\item The dark matter mass distribution can be approximated by spherically symmetric BMO halo profiles attached to each galaxy.
+\item The stellar mass of the foreground galaxy is negligible for lensing calculations.
+\item The mass of the dark matter halo of each foreground galaxy is known.
+\item A spectroscopic redshift of each foreground galaxy is known.
+\end{enumerate}
+
+Testing the first assumption is the main goal of this paper.
+The second assumption is reasonable as it is estimated that dark matter halos are 1-2 orders of magnitude more massive than the host galaxy (cite).
+Clearly the third assumption will never be true for any observational data.
+However, this allows for a best-case scenario estimate of how well the \texttt{Pangloss} framework \textit{could} predict weak lensing effects given all possible information.
+This assumption can be relaxed by sampling a dark matter halo mass from an assumed stellar mass - halo mass relation (cite).
+The fourth assumpition is also unrealistic as most galaxies in sky surveys only have a less-reliable photometric redshift due to time constraints, but this again allows for a best-case estimate.
+This assumption could be relaxed by adding random photometric redshift noise and repeating the upcoming analysis on many realizations of the photometric redshifts.
+
+\subsection*{The Millennium Simulation}
+\texttt{Pangloss} cannot be used to make dark matter mass maps using existing galaxy catalogs until it is tested on a simulated universe with known dark matter structure to determine how accurately and precisely it predicts the lensing of background sources.
+For this purpose, \texttt{Pangloss} was tested on galaxy catalogs from the Millennium Simulation, an N-body simulation consisting of over 10 billion dark matter `particles' each representing a billion solar masses and populated with about 20 million galaxies (cite 2005).
+The simulation uses cosmological parameters from WMAP 1\textsuperscript{st}-year data analysis and contains baryonic and dark matter structure believed to be consistent with our own universe.
+From the work of Hilbert et al.
+(cite), high resolution maps of the shear and convergence from the perspective of a single reference point calculated by ray-tracing are publically available.
+From these maps, the actual lensing of background galaxies when traveling through the foreground mass of the Millennium Simulation towards the reference point can be calculated using Equation (??).
+
+\subsection*{Generating Background Galaxies}
+With a catalog of foreground galaxies chosen, a set of background galaxies with density 10 per square arcminute was generated.
+The intrinsic orientation of each galaxy was sampled from a uniform distribution as, without lensing, there should be no preferred orientation due to the assumption of an isotropic universe.
+The magnitude of the galaxy ellipticities was sampled from a normal distribution with a standard deviation of 0.2, but any ellipticities with magnitude greater than one were re-sampled.
+Random ellipticity noise was sampled from a normal distribution with a standard deviation of 0.1 and added to the intrinsic ellipticities.
+Finally, each ellipticity was multiplied by 0.9 to account for systematic shape noise of 10\%.
+
+\subsection*{Creating Lightcones}
+While ideally all foreground mass in a field would be considered when predicting the weak lensing of a background galaxy, it is computationally prohibitive to do so.
+Instead, all foreground halos contained within a `lightcone' centered along the line of sight to the source and extending out to a chosen lightcone radius $R$ were considered when calculating lensing contributions for the background source.
+A cartoon model of this process is shown in Figure (???).
+Unless otherwise specified, experiments in this paper used a radius of 2 arcminutes.
+
+%************************
+(Pangloss Cartoon Figure)
+%************************
+
+To calculate the convergence and shear contribution of each halo, the physical distance from the halo to the line of sight was needed.
+To increase the speed of distance calculations, the foreground halo redshifts were first snapped to a grid of 100 equally-sized redshift bins and then converted to physical distance using (still trying to decipher the grid.py/distance.py code.
+Ask Phil!).
+
+%************************
+(Redshift-to-distance relation equation?)
+%************************
+
+Using the physical separation distance and halo mass, the shear and convergence of a single foreground halo is calculated using methods described in Wright and Brainerd (cite).
+The total convergence and shear at the center of the lightcone is simply the sum of the convergence and shear contributions of each halo contained in the lightcone.
+The \texttt{Pangloss}-predicted lensed background ellipticity is then calculated using Equation (??).
+
+\subsection*{Checking the Halo Model}
+
+Instead of comparing the ray-traced and \texttt{Pangloss}-predicted lensed ellipticities for individual galaxies, the lensing is characterized globally with correlation functions.
+The ellipticity-ellipticity correlation function measures how correlated the ellipticities of pairs of galaxies are as a function of separation distance, while the galaxy-galaxy correlation function measures the correlation of lensed ellipticities around foreground halos as a function of separation distance.
+For readers that are unfamiliar with correlation functions in the context of cosmology or want a visual aid, see Appendix A.
+Both correlation functions are used in this work to measure how well the \texttt{Pangloss} framework models weak lensing by dark matter structures using the publically available \texttt{TreeCorr}\footnote{https://github.com/rmjarvis/TreeCorr} module written by Mike Jarvis.
+Note that the correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition and the more common Schneider definition (cite), see Appendix B.
 
@@
         \end{itemize}
+    \item infer hyper-parameters from SMHR, physical distance, etc
     \item other stuff - too tired right now
@@
 \item Collett et al.
-\item S. Hilbert (ray-traced)
+\item S. Hilbert (ray-traced) http://arxiv.org/abs/0809.5035
 \item Millennium Simulation
@@
 \item Jarvis \texttt{TreeCorr}
+\item lensing calculation http://arxiv.org/pdf/astro-ph/9908213v1.pdf
 \item NFW profile
@@
 
-%% Intro:
+%% Introduction:
 \begin{itemize}
@@
 \end{itemize}
+
+%% Theoretical Background:
+
+%% The Pangloss Framework:
+\begin{itemize}
+\item Assumptions
+    \begin{itemize}
+    \item A catalog with galaxy
+    \item Currently use actual dark matter halo mass for an idea of best case scenario - can run same analysis with masses sampled from SMHR (reference)
+    \item PSF already accounted for in catalog and error low enough for weak lensing analysis
+    \item Use actual redshift for best case scenario (but can easily be replaced by photometric redshift sampling)
+    \end{itemize}
+\item Millennium Simulation
+    \begin{itemize}
+    \item Instead of blindly using \texttt{Pangloss} to make dark matter mass maps using sky survey data, we instead test how accurately and precisely we can predict weakly-lensed shear and convergence
+    \item Mention which M.S. we used
+    \item S. Hilbert`s ray traced M.S. (reference)
+        \begin{itemize}
+        \item Can use the ray-traced convergence and shear to calculate the ``true'' lensed ellipticties and compare to \texttt{Pangloss}
+        \end{itemize}
+    \end{itemize}
+\item Background galaxies
+    \begin{itemize}
+    \item random orientation
+    \item ellipticity range (get numbers!)
+    \item Accounting for shape noise
+    \end{itemize}
+\item Lightcones
+    \begin{itemize}
+    \item Instead of using all foreground mass in a field to calculate the lensing of a single background object, we create a lightcone centered at the source with a chosen radius $R$
+    \item Drilling
+        \begin{itemize}
+        \item redshift grid to speed up calcuations
+        \item Use the physical distance to line of sight in lensing calculations
+            \begin{itemize}
+            \item Redshift-to-distance relation (equation and reference)
+            \end{itemize}
+        \item Ranking galaxy `relevance'
+            \begin{itemize}
+            \item Want to only include the most important galaxies for lensing to speed up computation, as most will have negligable mass or be too far away
+            \item Allows quicker lensing calculations, means we can make $R$ bigger
+            \item Show `relevance` metric ($M/R^3$ but unitless)
+            \item Include plot of predicted relevance vs kappa contribution??
+            \end{itemize}
+        \end{itemize}
+    \item Lensing by Halos
+        \begin{itemize}
+        \item Treat each foreground halo as a separate lensing event
+        \item Total lensing is the sum of each event
+        \item Lookup table??
+        \end{itemize}
+    \item Include cartoon
+    \end{itemize}
+\item Checking the halo model: Use of correlation functions as summary statistics for ellipticity predictions
+    \begin{itemize}
+        \item Introduce the concept of correlation functions in general
+            \begin{itemize}
+            \item Definition
+            \item Autocorrelation vs cross-correlation
+            \item Use of correlation functions in cosmology
+            \item Shear-shear and galaxy-galaxy correlation functions
+                \begin{itemize}
+                \item Reference appendix for Visualizing Correlation Functions
+                \end{itemize}
+            \end{itemize}
+        \item Use of Jarvis`s \texttt{TreeCorr} code to calculate cf`s
+        \begin{itemize}
+            \item Reference appendix for Jarvis proof
+        \end{itemize}
+    \end{itemize}
+\item Show one map with ray-traced features and lensed ellipticities vs another map with \texttt{Pangloss} features and predicted ellipticities?
+\end{itemize}
+
+Maybe do importance and/or lookup table after paper is submitted? Talk about in discussion?

### 2015-08-18 doc/suli-report-swe.tex
Added the first draft of the theory section to the SULI report. #81

@@
 \usepackage{bm}% bold math
+\usepackage{mathtools}
 %\usepackage{multicol}
@@
 In this paper, I aim to do the former by applying a simple dark matter halo model to the Millennium Simulation and predicting the weakly lensed ellipticities of generated background sources.
-A brief introduction into the theory of measuring galaxy ellipticities, the effects of strong and weak gravitational lensing, and dark matter halos is discussed in Section II.
+A brief introduction into the theory of galaxy ellipticities, the effects of strong and weak gravitational lensing, and dark matter halos is discussed in Section II.
 The implementation of a halo model on the Millennium Simulation is described in Section III, and the results of the model on (x \# of galaxies on a field size of x \# deg$^2$) as well as a comparison of the predicted lensed ellipticities to the true ellipticities is given in Section IV.
@@
 
-\begin{itemize}
-\item Galaxy ellipticities
-    \begin{itemize}
-    \item (Most) galaxies are not circular - have intrinsic ellipticities
-        \begin{itemize}
-        \item If they were all circular, we could measure the change in shape exactly!
-        \end{itemize}
-    \item Galaxies are not always well approximated by ellipses (reference)
-    \item Mathematical formalism
-    \item Plot of galaxy orientation given e1 and e2 from P.J. Marshall thesis
-    \end{itemize}
-\item Shape noise and PSF issues in weak lensing (distorting already weak signal)
-\item Gravitational lensing
-    \begin{itemize}
-    \item Short introduction to problem setup for simple case (point mass maybe?)
-    \item Assumptions made in a typical solution (thin lens approximation?)
-    \item Show solution from Schneider
-    \item Shear and convergence 
-    \item Measuring shear in weak lensing - a statistical feature
-    \end{itemize}
-\item Dark matter halos
-    \begin{itemize}
-    \item NFW profile and equation (reference)
-    \item BMO truncation and equation (reference)
-    \end{itemize}
-\item SMHR? Or too distracting?
-\end{itemize}
+\subsection*{Galaxies as Ellipses}
+Consider a galaxy image that can be well approximated as an ellipse at an angle $\phi$ above an arbitrary reference line. The galaxy's complex ellipticity is defined to be 
+\begin{equation}
+\varepsilon=\varepsilon_1+i\varepsilon_2=|\varepsilon|\,e^{2i\phi}
+\end{equation}
+
+\noindent where the magnitude of the galaxy's ellipticity $|\varepsilon|$ is defined to be
+\begin{equation}
+|\varepsilon|=\frac{1-r}{1+r}
+\end{equation}
+
+\noindent and $r\leq1$ is the ratio of the semi-minor and semi-major axis of the ellipse.
+This compact notation combines the eccentricity and orientation of the ellipse into a single object.
+A plot from (Schneider et al.) showing the shape of elliptical galaxies for various values of $\varepsilon_1$ and $\varepsilon_2$ is shown in Figure (??).
+
+%************************
+(Galaxy Ellipticity Figure)
+%************************
+
+(Mention shape nosie and PSF here?)
+
+\subsection*{Gravitational Lensing}
+
+A full mathematical treatment of the gravitational lensing of galaxies due to the gravitational fields of massive objects requires general relativity (see (Beck cite) for details).
+However, the important results can be summarized as follows.
+Foreground mass distorts the image of a background galaxy in two distinct ways: The image is magnified and sheared tangentially about the foreground mass, making it more elliptical.
+The magnification of the image is determined by the convergence $\kappa$, a scalar which measures the projected mass density along each line of sight.
+The shearing of the source is most often described by the complex shear $\gamma$ defined to be
+\begin{equation}
+\gamma=\gamma_1+i\gamma_2=|\gamma|\,e^{2i\varphi}
+\end{equation}
+
+\noindent where $|\gamma|$ is the magnitude of the shear and $\varphi$ is the orientation of the shear.
+While the intrinsic ellipticity of the source may be in any orientation near the foreground mass, it will be more aligned with the shear field after lensing.
+Figure (??) demonstrates this process visually.
+
+However, usually the quantity of interest in lensing calculations is the \textit{reduced} shear, defined by
+\begin{equation}
+g=\frac{\gamma}{1-\kappa}.
+\end{equation}
+
+\noindent Then using the thin lens approximation for the lensing of a background source of intrinsic ellipticity $\varepsilon_i$ around a point foreground mass with reduced shear $g$, the lensed ellipticity $\varepsilon$ is given by
+\begin{equation}
+ \varepsilon = \begin{dcases} 
+      \frac{\varepsilon_i+g}{1+g^*\varepsilon_i} & : |g|\leq1; \\[0.75em]
+       \frac{1+g\varepsilon_i^*}{\varepsilon^*+g^*} & : |g|>1.
+   \end{dcases}
+\end{equation}
+
+\noindent where an asterisk denotes the complex conjugate (cite Schneider). The behavior of the distortion relies strongly on the magnitude of $g$; the
+effect is called \textit{strong} lensing if $|g|>1$ and \textit{weak} lensing if $|g|<1$.
+The effects of strong lensing can be quite dramatic, distorting sources into large arcs, multiple images, or even a complete Einstein ring shown in Figure (??).
+While strong lenses are rare as the alignment of the source and foreground mass must be nearly perfect, \textit{all} sources are weakly lensed.
+The effect is small, usually an ellipticity distortion of only a few percent (cite?), but can be detected locally by averaging the ellipticities of all sources in a small region.
+As the orientations of the sources should be random, it would be expected that
+$$\left<\varepsilon\right>=0.$$
+
+\noindent However as sources in the same small region are sheared in (approximately) the same way, this implies that
+\begin{equation}
+\left<\varepsilon\right>=g.
+\end{equation}
+
+ \noindent Finally as in the weak lensing regime ${\kappa\ll1}$ and ${|\gamma|\ll1}$, it follows that
+ \begin{equation}
+ \gamma\approx g=\left<\varepsilon\right>
+ \end{equation}
+
+ \noindent which provides a method of detecting the shear observationally.
+
+\subsection*{Dark Matter Halos}
+
+While the exact relation between the distribution of galaxies and dark matter is not known, simulations have shown that galaxies tend to form in overdense regions of dark matter.
+This means that galaxies \textit{should} trace out the larger underlying dark matter structures.
+The simplest way to model this relationship is by enveloping each galaxy in a spherically symmetric dark matter `halo' of mass $M_h$ sampled from the stellar-to-halo mass relation (cite SMHR).
+These halos extend far beyond the edge of the visible galaxy that they enclose.
+While the density profile of the halos may be complex, numerous simulations have shown that it can be well approximated by the Navarro-Frenk-White (NFW) profile of the form
+\begin{equation}
+\rho_{NFW}(r)=\frac{\rho_0}{\frac{r}{R_s}\left(1+\frac{r}{R_s}\right)^2}
+\end{equation}
+
+\noindent where the constant $\rho_0$ and the scale radius $R_s$ are parameters that vary from halo to halo (cite NFW).
+This work uses a truncated NFW profile called the Baltz-Marshall-Oguri (BMO) profile given by
+\begin{equation}
+\rho_{BMO}(r)=\rho_{NFW}\cdot\left(\frac{r_t^2}{r^2+r_t^2}\right)^2
+\end{equation}
+
+\noindent where $r_t$ is a free parameter, as it has been shown to be a better fit to simulated data (cite BMO).
 
@@
 For readers that are unfamiliar with correlation functions in the context of cosmology or want a visual aid, see Appendix A.
-Both correlation functions are used in this work to measure how well the \texttt{Pangloss} framework models weak lensing by dark matter structures using the publically available \texttt{TreeCorr}\footnote{https://github.com/rmjarvis/TreeCorr} module written by Mike Jarvis.
+Both correlation functions are used in this work to measure how well the \texttt{Pangloss} framework models weak lensing by dark matter structures using the publically available \texttt{TreeCorr} module written by Mike Jarvis\footnote{https://github.com/rmjarvis/TreeCorr}.
 Note that the correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition and the more common Schneider definition (cite), see Appendix B.
@@
 \item NFW profile
-\item BMO truncation
+\item BMO truncation, BMO vs NFW http://arxiv.org/pdf/1301.1684v2.pdf
+\item SMHR http://arxiv.org/pdf/1401.7329v1.pdf
 \item Planck
@@
 %% Theoretical Background:
+\begin{itemize}
+\item Galaxy ellipticities
+    \begin{itemize}
+    \item (Most) galaxies are not circular - have intrinsic ellipticities
+        \begin{itemize}
+        \item If they were all circular, we could measure the change in shape exactly!
+        \end{itemize}
+    \item Galaxies are not always well approximated by ellipses (reference)
+    \item Mathematical formalism
+    \item Plot of galaxy orientation given e1 and e2 from P.J. Marshall thesis
+    \end{itemize}
+\item Shape noise and PSF issues in weak lensing (distorting already weak signal)
+\item Gravitational lensing
+    \begin{itemize}
+    \item Short introduction to problem setup for simple case (point mass maybe?)
+    \item Assumptions made in a typical solution (thin lens approximation?)
+    \item Show solution from Schneider
+    \item Shear and convergence 
+    \item Measuring shear in weak lensing - a statistical feature
+    \end{itemize}
+\item Dark matter halos
+    \begin{itemize}
+    \item NFW profile and equation (reference)
+    \item BMO truncation and equation (reference)
+    \end{itemize}
+\item SMHR? Or too distracting?
+\end{itemize}
+
+% Old theory:
+%However, the important results for a point mass using the thin lens approximation can be summarized as follows: The distortion of a background galaxy image can be quantified by the linearized lens mapping Jacobi matrix $\mathcal{A}$ which can be written as
+
+%$$\mathcal{A}=(1-\kappa)\,
+%\begin{pmatrix}
+%1-g_1 & -g2\\
+%-g_2 & 1+g_1
+%\end{pmatrix}$$
+
+%\noindent where $\kappa$ and $g$ are the convergence and reduced shear respectively at the center of the background source. 
+%\begin{displaymath}
+%  \varepsilon = \left\{
+%    \begin{array}{lr}
+%      \frac{\varepsilon_i+g}{1+g^*\varepsilon_i} & : |g|\leq1; \\
+%      \frac{1+g\varepsilon_i^*}{\varepsilon^*+g^*} & : |g|>1.
+%    \end{array}
+%   \right.
+%\end{displaymath}
 

### 2015-08-18 pangloss/lensing.py
Added some comments for the Spencer-added functiosn in `lensing` for clarification.

@@ -207,7 +207,7 @@ def Gfunc(x):
 
 def BMO1FSpencerFunc(x,t):
     '''
-    New BMO1Ffunc method that is more efficient.
+    New BMO1Ffunc method using masks. NOTE: Didn't end up being more efficient.
     '''
 
     x[x==1]=1.+1e-5
@@ -228,7 +228,7 @@ def BMO1FSpencerFunc(x,t):
 
 def BMO1GSpencerFunc(x,t):
     '''
-    New BMO1Gfunc method that is more efficient.
+    New BMO1Gfunc method using masks. NOTE: Didn't end up being more efficient.
     '''
 
     z = np.zeros(len(x))

### 2015-08-18 pangloss/lightcone.py
Cleaned up the `makeKappas()` method in `lightcone`.

@@ -360,7 +360,7 @@ class Lightcone(object):
         self.writeColumn('rs',r_s)
         x = self.galaxies['rphys']/r_s
         self.writeColumn('X',x)
-        #print 'X lims: ',np.min(self.galaxies['X']),np.max(self.galaxies['X'])
+
         return
 
 # ----------------------------------------------------------------------------
@@ -368,17 +368,10 @@ class Lightcone(object):
 
     def makeKappas(self,errors=False,truncationscale=5,profile="BMO1",lensing_table=None):
 
-        #c200 = self.galaxies['c200']
-        #r200 = self.galaxies['r200']
-        #x = self.galaxies['X']
-        #r_s = self.galaxies['rs']
         rho_s = pangloss.delta_c(self.galaxies['c200'])*self.galaxies['rho_crit']
         self.kappa_s = rho_s * self.galaxies['rs'] /self.galaxies['sigma_crit']  #kappa slice for each lightcone
         r_trunc = truncationscale*self.galaxies['r200']
         xtrunc = r_trunc/self.galaxies['rs']
-        #print 'xtrunc lims: ',np.min(xtrunc),np.max(xtrunc)
-        #kappaHalo = self.kappa_s*1.0
-        #gammaHalo = self.kappa_s*1.0
 
         if profile=="BMO1":
             if lensing_table is None:
@@ -395,9 +388,6 @@ class Lightcone(object):
         if profile=="BMO2":
             F=pangloss.BMO2Ffunc(self.galaxies['X'],xtrunc)
             G=pangloss.BMO2Gfunc(self.galaxies['X'],xtrunc)
-
-        #kappaHalo *= F
-        #gammaHalo *= (G-F)
 
         #phi = self.galaxies['phi']
         kappa = 1.0*self.kappa_s*F

### 2015-08-18 doc/suli-report-swe.tex
Added a first draft of the Results section to the SULI report. #81

@@
 (citation).
-Using the shear-shear and galaxy-galaxy correlation functions, I find that the \texttt{Pangloss} framework systematically under-predicts the shear power in both statistics and does not accurately capture the effect of dark matter structure at scales larger than 1 arcminute.
+Using the ellipticity-ellipticity and galaxy-galaxy correlation functions, I find that the \texttt{Pangloss} framework systematically under-predicts the shear power in both statistics and does not accurately capture the effect of dark matter structure at scales larger than 1 arcminute.
 Physical and computational shortcomings of the \texttt{Pangloss} framework are discussed, as well as potential improvements for upcoming work.
@@
 Instead of comparing the ray-traced and \texttt{Pangloss}-predicted lensed ellipticities for individual galaxies, the lensing is characterized globally with correlation functions.
-The ellipticity-ellipticity correlation function measures how correlated the ellipticities of pairs of galaxies are as a function of separation distance, while the galaxy-galaxy correlation function measures the correlation of lensed ellipticities around foreground halos as a function of separation distance.
+The ellipticity-ellipticity correlation function measures how correlated the ellipticities of pairs of galaxies are as a function of separation distance, while the galaxy-galaxy correlation function measures the correlation of lensed ellipticities around foreground halos as a function of separation distance (cite corrFuns).
 For readers that are unfamiliar with correlation functions in the context of cosmology or want a visual aid, see Appendix A.
@@
 
-\begin{itemize}
-\item Maps??
-\item Correlation Functions
-    \begin{itemize}
-    \item shear-shear
-    \item galaxy-galaxy
-    \item progression of each as $R$ increases??
-    \item cf`s without shape noise and with shape noise
-    \item cf`s with all galaxies vs with only `relevant' galaxies?
-    \end{itemize}
-\item The Need for Speed
-    \begin{itemize}
-    \item Table or graph of speedups and CPU time per lightcone progression (make sure to check \texttt{timeit} first!)
-    \end{itemize}
-\end{itemize}
+Using the presented methodology, (x \# of background sources) background galaxies in a (y*y square deg) subset of the (0,0,0,0) Millennium Simulation foreground catalog (cite where to get data) were generated and lensed by both the ray-traced shear and convergence as well as the \texttt{Pangloss} framework.
+Both sets of lensed ellipticities were characterized with correlation functions, as well as the intrinsic ellipticities of the sources before lensing.
+
+\subsection*{Ellipticity-Ellipticity Correlation Function}
+
+The first test of the halo model was with the ellipticity-ellipticity correlation function with a lightcone radius of 2 arcminutes which is given in Figure (??).
+The statistic measured the average correlation between pairs of ellipticities at separation distances between (0.1??) arcminutes and 2 arcminutes.
+The correlation function of the intrinsic ellipticities plotted in blue shows no significant deviation from zero as expected, as before lensing the galaxies had random orientations.
+Both the ray-traced, plotted in green, and \texttt{Pangloss}, plotted in purple, ellipticities show positive correlation on smaller scales up to a separation of 0.8 arcminutes.
+However, the ray-traced correlation is positive on all calculated scales while the halo model does not predict any significant corrlelation at separations above 0.8 arcminutes.
+Additionally, while the shapes of the correlation functions for both sets of lensed ellipticities aggree well until 0.8 arcminutes, there is a clear systematic underprediction of shear power by the halo model on all scales.
+On average, the shear power is underpredicted by (??) percent.
+
+%************************
+(e-e Correlation Function Plot)
+%************************
+
+Using the same catalog of background sources, this statistic was recalculated for the ray-traced and halo model lensed ellipticities for various lightcone radii ranging from $R=1$ arcminute to $R=???$ arcminutes.
+The result is shown in Figure (??).
+
+%************************
+(e-e Correlation Function Plot with multiple R's)
+%************************
+
+(Analysis of plot)
+
+\subsection*{Galaxy-Galaxy Correlation Function}
+
+The catalog of lensed ellipticities was also analyzed using the galaxy-galaxy correlation function with separation distances from (0.1??) arcminutes to 2 arcminutes and a lightcone radius of 2 arcminutes.
+The result is shown in Figure (??).
+As with the ellipticity-ellipticity correlation function, there is no significant correlation for the intrinsic ellipticities at any scale as expected.
+The lensed ellipticities from the ray-tracing and halo model both have positive correlation on all calculated scales and are in excellent agreement on scales from (??) arcminutes to (??) arcminutes.
+However, the halo model is still systematically underpredicting the shear power on scales above (??) arcminutes, although now only by an average of (??) percent.
+A new feature is the large overprediction of shear power on separation scales smaller than (??) arcminutes.
+However, background sources this close to foreground halos are often in the strong lensing regime which is not currently accounted for by the \texttt{Pangloss} framework.
+
+%************************
+(n-g Correlation Function Plot)\\
+%************************
+(Make a plot of n-g correlation function with multiple R's??)
+
+\subsection*{Computational Performance}
+
+A secondary goal of this research was to investigate how quickly the prediction for the shear and convergence for a single background source could be made.
+The average CPU time required for the prediction per lightcone was (??
+$\pm$ ??) for the first run.
+However, many small improvements to the coding infastructure of \texttt{Pangloss} were made to speed up the prediction.
+The average CPU time for a lensing prediction per lightcone after various changes is plotted in Figure (??).
+
+%************************
+(CPU time per lightcone plot)\\
+%************************
+(Include RAM in plot??)
 
@@
 \item GR
+\item corrFuns in cosmology
 \item wl distortion percent
@@
 
-\begin{itemize}
-
-\end{itemize}
-
 % Outline:
@@
 
+%% Results
+\begin{itemize}
+\item Maps??
+\item Correlation Functions
+    \begin{itemize}
+    \item shear-shear
+    \item galaxy-galaxy
+    \item progression of each as $R$ increases??
+    \item cf`s without shape noise and with shape noise
+    \item cf`s with all galaxies vs with only `relevant' galaxies?
+    \end{itemize}
+\item The Need for Speed
+    \begin{itemize}
+    \item Table or graph of speedups and CPU time per lightcone progression (make sure to check \texttt{timeit} first!)
+    \end{itemize}
+\end{itemize}
+
 Maybe do importance and/or lookup table after paper is submitted? Talk about in discussion?

### 2015-08-18 doc/suli-report-swe.tex
Added the first draft of the Discussion section to the SULI report. #81

@@
 Using the presented methodology, (x \# of background sources) background galaxies in a (y*y square deg) subset of the (0,0,0,0) Millennium Simulation foreground catalog (cite where to get data) were generated and lensed by both the ray-traced shear and convergence as well as the \texttt{Pangloss} framework.
+On average, the lightcones contained (950??)$\pm$(25??) foreground halos.
 Both sets of lensed ellipticities were characterized with correlation functions, as well as the intrinsic ellipticities of the sources before lensing.
@@
 
-\begin{itemize}
-\item Issues with the \texttt{Pangloss} framework
-    \begin{itemize}
-    \item Systematic shear power under-prediction in cf`s
-    \item Missing large-scale dark matter structure
-    \end{itemize}
-    \item Possibly missing features in model
-        \begin{itemize}
-        \item voids
-        \item filaments
-        \item stellar mass
-        \end{itemize}
-    \item Speed
-\item Moving Foward
-    \begin{itemize}
-    \item Scaling up
-        \begin{itemize}
-        \item CPU and RAM numbers for lightcone parallelization from discussion with Debbie Bard
-        \end{itemize}
-    \item infer hyper-parameters from SMHR, physical distance, etc
-    \item other stuff - too tired right now
-    \end{itemize}
-\end{itemize}
+\subsection*{Issues with the \texttt{Pangloss} Framework}
+
+Both the ellipticity-ellipticity and galaxy-galaxy correlation functions show clear issues with using the halo model to predict the lensing of background sources with \texttt{Pangloss}, even in the best-case scenario of perfect knowledge of the halo masses and their spectroscopic redshifts.
+The systematic underprediction of shear power present in both correlaton functions is likely do to missing features in the model such as clusters, filaments, and voids.
+While individual galaxies currently recieve halos, a cluster of galaxies will sit in an larger halo whose presence is not being considered as its position, mass, and extent are difficult to determine.
+The absence of this mass undoubtedly effects shear predictions and ellipticity correlations on large scales.
+While some of the filament structure is captured in the framework, as the higher density of galaxies in filaments will lead to a higher density of halos, any additional dark matter structure between halos and clusters is not being accounted for.
+While difficult to do in practice, one can imagine connecting clusters of galaxies with dark matter `cylinders' to account for the extra filament mass.
+Voids are also not currently considered, as the framework assumes the field has constant mass density equal to that of the average mass density of the universe and then adds halo masses on top of this density.
+This would make the average matter density accross the field \textit{larger} than the mean density of the unvierse, and could be counteracted by subtracting mass from regions in between foreground halos.
+Stellar masses could also be incorperated into the \texttt{Pangloss} prediction, but any effect would likely be dominated by the missing features described above.
+
+The progression of model-predicted ellipticity-ellipticity correlation functions at larger radii (somewhat) converging to the ray-traced correlation supports the analysis given above, as the prediction was progressively better with larger number of foreground halos and thus more mass and structure.
+However, the number of foreground objects scales quadratically with the lightcone radius making it prohibitively expensive above $R=16$ arcminutes.
+With a radius this large, most foreground objects will be too far away from the line of sight and have insufficient mass to make a significant contribution to the lensing of the background source.
+This suggests the creation of a metric to predict the `relevance' of each halo to the lensing contribution.
+In this way, the framework could be restructured to only use the most relevant halos in the computationally expensive lensing prediction, while simultaneously allowing for larger lightcones with more relevant halos.
+This could aid in the aforementioned shear power prediction issues.
+
+\subsection*{Scaling Up \texttt{Pangloss}}
+
+While the current \texttt{Pangloss} framework can handle the lensing predictions of (x \# of lightcones) in a (y*y square degree) field comfortably on a single processor, the goal is to scale up the framework to make predictions for background sources of the same number density in a 100 deg$^2$ field; this will require 3.6 million lightcones, each containing up to 1,000 foreground halos.
+Luckily, the prediction is trivially parallelizable as the shear and convergence calculation of each lightcone is independent of all others.
+This makes GPUs an attractive candidate for future work, as it would only take 360 GPUs with 10,000 threads each to carry out the prediction.
+Additionally, the (??) MB of RAM per lightcone is sufficiently small to fit 10,000 lightcones on a GPU.
 
@@
 \section{Acknowledgements}
+
+I would like to thank the Department of Energy's Science Undergraduate Laboratory Internship (SULI) program for funding this research and giving me the opportunity to conduct research at ?.
+asdf.
+Finally, I am incredibly grateful to Phil Marshall for his unending support, patience, and guidance throughout this research.
+
+This work was supported in part by the U.S.
+Department of Energy, Office of Science, Office of Workforce Development for Teachers and Scientists (WDTS) under the Science Undergraduate Laboratory Internships Program (SULI).
 
@@
 \item wl distortion percent
+\item CFHT Lensing Survey
 \end{itemize}
@@
 
+%% Conclusion
+\begin{itemize}
+\item Issues with the \texttt{Pangloss} framework
+    \begin{itemize}
+    \item Systematic shear power under-prediction in cf`s
+    \item Missing large-scale dark matter structure
+    \end{itemize}
+    \item Possibly missing features in model
+        \begin{itemize}
+        \item voids
+        \item filaments
+        \item stellar mass
+        \end{itemize}
+    \item Speed
+\item Moving Foward
+    \begin{itemize}
+    \item Scaling up
+        \begin{itemize}
+        \item CPU and RAM numbers for lightcone parallelization from discussion with Debbie Bard
+        \end{itemize}
+    \item infer hyper-parameters from SMHR, physical distance, etc
+    \item other stuff - too tired right now
+    \end{itemize}
+\end{itemize}
+
 Maybe do importance and/or lookup table after paper is submitted? Talk about in discussion?

### 2015-08-19 doc/suli-report-swe.tex
Made revisions throughout the first draft of the SULI report. Added references and citations in text. #81

@@
 Background sources are generated at a redshift of ${z = 1.3857}$ and then weakly lensed by the foreground halos contained in a light cone centered along each line of sight, which is carried out by the \texttt{Pangloss} framework\footnote{https://github.com/drphilmarshall/Pangloss}.
-The model-predicted ellipticities of the background galaxies after lensing are compared to the ``true'' weakly-lensed ellipticities determined by the ray-traced convergence and shear calculated by Hilbert et al.
-(citation).
-Using the ellipticity-ellipticity and galaxy-galaxy correlation functions, I find that the \texttt{Pangloss} framework systematically under-predicts the shear power in both statistics and does not accurately capture the effect of dark matter structure at scales larger than 1 arcminute.
+The model-predicted ellipticities of the background galaxies after lensing are compared to the ``true'' weakly-lensed ellipticities determined by ray-traced convergence and shear from the simulation.
+Using the ellipticity-ellipticity and galaxy-mass correlation functions, I find that the \texttt{Pangloss} framework systematically under-predicts the shear power in both statistics and does not accurately capture the effect of dark matter structure at scales larger than 1 arcminute.
 Physical and computational shortcomings of the \texttt{Pangloss} framework are discussed, as well as potential improvements for upcoming work.
@@
 The remaining mass takes the form of an exotic dark matter that does not absorb or emit light, rendering it invisible to our telescopes.
-While this claim sounds bizarre, there has been an abundance of indirect evidence in recent decades for the existence of dark matter including the flattening of galaxy rotation curves (cite), the existence of baryonic acoustic oscillations (cite), and anisotropies in the cosmic microwave background (cite).
+While this claim sounds bizarre, there has been an abundance of indirect evidence in recent decades for the existence of dark matter including the flattening of galaxy rotation curves\cite{rotation_curve}, (something else) (cite), and acoustic peaks in the cosmic microwave background\cite{planck_2015}.
 
@@
 
-While the effects of gravitational lensing can be dramatic, the shape of most galaxies is only distorted by a few percent (cite) and can only be detected statistically as the intrinsic shape is not known.
+While the effects of gravitational lensing can be dramatic, the shape of most galaxies is only distorted by a few percent (cite) and must be detected statistically as the intrinsic shape is not known.
 If a model for the distribution of dark matter in a region of foreground mass can accurately predict the statistical signal of this `weak' lensing of background galaxies, then the model can be used on galaxies in existing sky survey data to extrapolate the amount of dark matter in the region and construct large-scale maps of the dark matter in the universe.
 
-In this paper, I aim to do the former by applying a simple dark matter halo model to the Millennium Simulation and predicting the weakly lensed ellipticities of generated background sources.
+In this paper, I attempt to do the former by applying a simple dark matter halo model to reconstruct mass along lines of sight in the Millennium Simulation and predict the weakly lensed ellipticities of generated background sources.
 A brief introduction into the theory of galaxy ellipticities, the effects of strong and weak gravitational lensing, and dark matter halos is discussed in Section II.
-The implementation of a halo model on the Millennium Simulation is described in Section III, and the results of the model on (x \# of galaxies on a field size of x \# deg$^2$) as well as a comparison of the predicted lensed ellipticities to the true ellipticities is given in Section IV.
-Section V discusses limitations of the used Pangloss framework as well as potential physical and computational improvements that can be made for upcoming work before concluding remarks in Section VI.
+The implementation of a halo model on the Millennium Simulation and ellipticity predictions is described in Section III, and the results of the model on (x \# of galaxies on a field size of x \# deg$^2$) as well as a comparison of the predicted lensed ellipticities to the true ellipticities is given in Section IV.
+Section V discusses limitations of the used \texttt{Pangloss} framework as well as potential physical and computational improvements that can be made for upcoming work before concluding remarks in Section VI.
 
@@
 Consider a galaxy image that can be well approximated as an ellipse at an angle $\phi$ above an arbitrary reference line. The galaxy's complex ellipticity is defined to be 
-\begin{equation}
+\begin{equation}\label{complex_ellipticity}
 \varepsilon=\varepsilon_1+i\varepsilon_2=|\varepsilon|\,e^{2i\phi}
@@
 
-(Mention shape nosie and PSF here?)
+There are many complications to using this scheme in practice, most notably the multiplicative bias resulting from the smearing of galaxy images by the observational point spread function (PSF)\cite{multiplicative_bias}.
+While the effects of a PSF can be complex, in general it causes galaxy images to appear less elliptical than they truly are.
+To account for this in generated galaxy images, a multiplicative bias parameter $M$ is often used to lessen the intrinsic ellipticity using
+$$\varepsilon_{obs}=M\cdot\varepsilon_{int}.$$
+
+\noindent where $\varepsilon_{int}$ is the generated intrinsic ellipticity of the image and $\varepsilon_{obs}$ is the ellipticity that would be recorded by a detector.
 
@@
 
-A full mathematical treatment of the gravitational lensing of galaxies due to the gravitational fields of massive objects requires general relativity (see (Beck cite) for details).
+A full mathematical treatment of the gravitational lensing of galaxies due to the gravitational fields of massive objects requires general relativity (see \cite{modern_cosmology} for details).
 However, the important results can be summarized as follows.
@@
 The shearing of the source is most often described by the complex shear $\gamma$ defined to be
-\begin{equation}
+\begin{equation}\label{complex_shear}
 \gamma=\gamma_1+i\gamma_2=|\gamma|\,e^{2i\varphi}
@@
 \noindent where $|\gamma|$ is the magnitude of the shear and $\varphi$ is the orientation of the shear.
-While the intrinsic ellipticity of the source may be in any orientation near the foreground mass, it will be more aligned with the shear field after lensing.
+While the intrinsic ellipticities of source galaxies are randomly oriented near the foreground mass before lensing, they will be systematically more aligned with the shear field after lensing.
 Figure (??) demonstrates this process visually.
@@
 However, usually the quantity of interest in lensing calculations is the \textit{reduced} shear, defined by
-\begin{equation}
+\begin{equation}\label{reduced_shear}
 g=\frac{\gamma}{1-\kappa}.
@@
 \noindent Then using the thin lens approximation for the lensing of a background source of intrinsic ellipticity $\varepsilon_i$ around a point foreground mass with reduced shear $g$, the lensed ellipticity $\varepsilon$ is given by
-\begin{equation}
+\begin{equation}\label{lensing}
  \varepsilon = \begin{dcases} 
-      \frac{\varepsilon_i+g}{1+g^*\varepsilon_i} & : |g|\leq1; \\[0.75em]
-       \frac{1+g\varepsilon_i^*}{\varepsilon^*+g^*} & : |g|>1.
+      \frac{\varepsilon_i+g}{1+g^*\varepsilon_i} & : |g|\leq1 \\[0.75em]
+       \frac{1+g\varepsilon_i^*}{\varepsilon^*+g^*} & : |g|>1
    \end{dcases}
@@
 
-\noindent where an asterisk denotes the complex conjugate (cite Schneider). The behavior of the distortion relies strongly on the magnitude of $g$; the
+\noindent where an asterisk denotes the complex conjugate\cite{schneider}. The behavior of the distortion relies strongly on the magnitude of $g$; the
 effect is called \textit{strong} lensing if $|g|>1$ and \textit{weak} lensing if $|g|<1$.
-The effects of strong lensing can be quite dramatic, distorting sources into large arcs, multiple images, or even a complete Einstein ring shown in Figure (??).
+The effects of strong lensing can be quite dramatic, distorting sources into large arcs, multiple images, or even an Einstein ring as shown in Figure (??).
 While strong lenses are rare as the alignment of the source and foreground mass must be nearly perfect, \textit{all} sources are weakly lensed.
@@
 
-\noindent However as sources in the same small region are sheared in (approximately) the same way, this implies that
+\noindent However, as sources in the same small region are sheared in (approximately) the same way, this implies that
 \begin{equation}
-\left<\varepsilon\right>=g.
+\left<\varepsilon\right>\approx g.
 \end{equation}
@@
  \begin{equation}
- \gamma\approx g=\left<\varepsilon\right>
+ \gamma\approx g\approx\left<\varepsilon\right>
  \end{equation}
@@
 This means that galaxies \textit{should} trace out the larger underlying dark matter structures.
-The simplest way to model this relationship is by enveloping each galaxy in a spherically symmetric dark matter `halo' of mass $M_h$ sampled from the stellar-to-halo mass relation (cite SMHR).
+The simplest way to model this relationship is by enveloping each galaxy in a spherically symmetric dark matter `halo' of mass $M_h$ sampled from the stellar-to-halo mass relation\cite{smhr}.
 These halos extend far beyond the edge of the visible galaxy that they enclose.
-While the density profile of the halos may be complex, numerous simulations have shown that it can be well approximated by the Navarro-Frenk-White (NFW) profile of the form
-\begin{equation}
+While the density profile of the halos may be complex, numerous simulations have shown that it can be well approximated by the Navarro-Frenk-White (NFW) profile which has the form
+\begin{equation}\label{nfw_profile}
 \rho_{NFW}(r)=\frac{\rho_0}{\frac{r}{R_s}\left(1+\frac{r}{R_s}\right)^2}
@@
 
-\noindent where the constant $\rho_0$ and the scale radius $R_s$ are parameters that vary from halo to halo (cite NFW).
+\noindent where the constant $\rho_0$ and the scale radius $R_s$ are parameters that vary from halo to halo\cite{nfw}.
 This work uses a truncated NFW profile called the Baltz-Marshall-Oguri (BMO) profile given by
-\begin{equation}
+\begin{equation}\label{bmo_profile}
 \rho_{BMO}(r)=\rho_{NFW}\cdot\left(\frac{r_t^2}{r^2+r_t^2}\right)^2
@@
 
-\noindent where $r_t$ is a free parameter, as it has been shown to be a better fit to simulated data (cite BMO).
+\noindent where $r_t$ is a free parameter, as it has been shown to be a better fit to simulated data\cite{nfw_bmo}.
 
@@
 To constrain the mass of foreground dark matter using weak gravitational lensing, first a model of the relationship between foreground galaxies and the foreground dark matter must be established and robustly tested to see if, statistically, it makes the same lensing predictions of background sources as the true undering dark matter structure.
-To do this, I built upon the publically available \texttt{Pangloss} framework used in Collett et al.
-(cite) to reconstruct all the mass along the line of sight of each background galaxy using dark matter halos.
+To do this, I built upon the publically available \texttt{Pangloss} framework used in Collett et al.\cite{collett_marshall} to reconstruct all the mass along the line of sight of each background galaxy using dark matter halos.
 The lensing contribution of each halo is calculated, and the total lensing of the background galaxy is the sum of each halo contribution.
@@
 Testing the first assumption is the main goal of this paper.
-The second assumption is reasonable as it is estimated that dark matter halos are 1-2 orders of magnitude more massive than the host galaxy (cite).
+The second assumption is reasonable as it is estimated that dark matter halos are 1-2 orders of magnitude more massive than the host galaxy\cite{smhr}.
 Clearly the third assumption will never be true for any observational data.
 However, this allows for a best-case scenario estimate of how well the \texttt{Pangloss} framework \textit{could} predict weak lensing effects given all possible information.
-This assumption can be relaxed by sampling a dark matter halo mass from an assumed stellar mass - halo mass relation (cite).
+This assumption can be relaxed by sampling a dark matter halo mass from an assumed stellar mass - halo mass relation.
 The fourth assumpition is also unrealistic as most galaxies in sky surveys only have a less-reliable photometric redshift due to time constraints, but this again allows for a best-case estimate.
-This assumption could be relaxed by adding random photometric redshift noise and repeating the upcoming analysis on many realizations of the photometric redshifts.
+This assumption could be relaxed by instead using photometric redshifts, adding random noise, and repeating the upcoming analysis on many realizations of the photometric redshifts.
 
@@
 \texttt{Pangloss} cannot be used to make dark matter mass maps using existing galaxy catalogs until it is tested on a simulated universe with known dark matter structure to determine how accurately and precisely it predicts the lensing of background sources.
-For this purpose, \texttt{Pangloss} was tested on galaxy catalogs from the Millennium Simulation, an N-body simulation consisting of over 10 billion dark matter `particles' each representing a billion solar masses and populated with about 20 million galaxies (cite 2005).
+For this purpose, \texttt{Pangloss} was tested on galaxy catalogs from the Millennium Simulation, an N-body simulation consisting of over 10 billion dark matter `particles' each representing a billion solar masses and populated with about 20 million galaxies\cite{millennium_simulation}.
 The simulation uses cosmological parameters from WMAP 1\textsuperscript{st}-year data analysis and contains baryonic and dark matter structure believed to be consistent with our own universe.
-From the work of Hilbert et al.
-(cite), high resolution maps of the shear and convergence from the perspective of a single reference point calculated by ray-tracing are publically available.
-From these maps, the actual lensing of background galaxies when traveling through the foreground mass of the Millennium Simulation towards the reference point can be calculated using Equation (??).
+From the work of Hilbert et al.\cite{ray_tracing}, high resolution maps of the shear and convergence from the perspective of a single reference point calculated by ray-tracing are publically available.
+From these maps, the actual lensing of background galaxies when traveling through the foreground mass of the Millennium Simulation towards the reference point can be calculated using Equation \eqref{lensing}.
 
 \subsection*{Generating Background Galaxies}
-With a catalog of foreground galaxies chosen, a set of background galaxies with density 10 per square arcminute was generated.
+With a catalog of foreground galaxies chosen, a set of background galaxies with density 10 per arcminute$^2$ was generated.
 The intrinsic orientation of each galaxy was sampled from a uniform distribution as, without lensing, there should be no preferred orientation due to the assumption of an isotropic universe.
@@
 Random ellipticity noise was sampled from a normal distribution with a standard deviation of 0.1 and added to the intrinsic ellipticities.
-Finally, each ellipticity was multiplied by 0.9 to account for systematic shape noise of 10\%.
+Finally, each ellipticity was multiplied by $M=0.9$ to account for a multiplicative bias of 10\%.
 
@@
 While ideally all foreground mass in a field would be considered when predicting the weak lensing of a background galaxy, it is computationally prohibitive to do so.
-Instead, all foreground halos contained within a `lightcone' centered along the line of sight to the source and extending out to a chosen lightcone radius $R$ were considered when calculating lensing contributions for the background source.
+Instead, all foreground halos contained within a `lightcone' centered along the line of sight to the source and extending out to a chosen lightcone radius $R$ were considered when calculating the lensing contributions for the background source.
 A cartoon model of this process is shown in Figure (???).
@@
 To calculate the convergence and shear contribution of each halo, the physical distance from the halo to the line of sight was needed.
-To increase the speed of distance calculations, the foreground halo redshifts were first snapped to a grid of 100 equally-sized redshift bins and then converted to physical distance using (still trying to decipher the grid.py/distance.py code.
-Ask Phil!).
+To increase the speed of distance calculations, the foreground halo redshifts were first snapped to a grid of 100 equally-sized redshift bins and then converted to physical distance.
 
-%************************
-(Redshift-to-distance relation equation?)
-%************************
-
-Using the physical separation distance and halo mass, the shear and convergence of a single foreground halo is calculated using methods described in Wright and Brainerd (cite).
+Using the physical separation distance and halo mass, the shear and convergence contribution of a single foreground halo is calculated using methods described in Wright and Brainerd\cite{lensing_calc}.
 The total convergence and shear at the center of the lightcone is simply the sum of the convergence and shear contributions of each halo contained in the lightcone.
-The \texttt{Pangloss}-predicted lensed background ellipticity is then calculated using Equation (??).
+The \texttt{Pangloss}-predicted lensed background ellipticity is then calculated using Equation \eqref{lensing}.
 
@@
 
-Instead of comparing the ray-traced and \texttt{Pangloss}-predicted lensed ellipticities for individual galaxies, the lensing is characterized globally with correlation functions.
-The ellipticity-ellipticity correlation function measures how correlated the ellipticities of pairs of galaxies are as a function of separation distance, while the galaxy-galaxy correlation function measures the correlation of lensed ellipticities around foreground halos as a function of separation distance (cite corrFuns).
+Instead of comparing the ray-traced and \texttt{Pangloss}-predicted ellipticities for individual galaxies, the lensing is characterized globally with correlation functions.
+The ellipticity-ellipticity correlation function measures how correlated the ellipticities of pairs of galaxies are as a function of separation distance, while the galaxy-mass correlation function measures the correlation of lensed ellipticities around foreground halos as a function of separation distance.
 For readers that are unfamiliar with correlation functions in the context of cosmology or want a visual aid, see Appendix A.
 Both correlation functions are used in this work to measure how well the \texttt{Pangloss} framework models weak lensing by dark matter structures using the publically available \texttt{TreeCorr} module written by Mike Jarvis\footnote{https://github.com/rmjarvis/TreeCorr}.
-Note that the correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition and the more common Schneider definition (cite), see Appendix B.
+Note that the correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition and the more common Schneider definition\cite{schneider}, see Appendix B.
 
@@
 
-Using the presented methodology, (x \# of background sources) background galaxies in a (y*y square deg) subset of the (0,0,0,0) Millennium Simulation foreground catalog (cite where to get data) were generated and lensed by both the ray-traced shear and convergence as well as the \texttt{Pangloss} framework.
+Using the presented methodology, (x \# of background sources) background galaxies in a (y*y square deg) subset of the (0,0,0,0) Millennium Simulation foreground catalog (cite where to get data) were generated and lensed by both the ray-traced shear and convergence maps as well as the \texttt{Pangloss} framework.
 On average, the lightcones contained (950??)$\pm$(25??) foreground halos.
@@
 The correlation function of the intrinsic ellipticities plotted in blue shows no significant deviation from zero as expected, as before lensing the galaxies had random orientations.
-Both the ray-traced, plotted in green, and \texttt{Pangloss}, plotted in purple, ellipticities show positive correlation on smaller scales up to a separation of 0.8 arcminutes.
+Both the ray-traced, plotted in green, and halo model, plotted in purple, ellipticities show positive correlation on small scales up to a separation of 0.8 arcminutes.
 However, the ray-traced correlation is positive on all calculated scales while the halo model does not predict any significant corrlelation at separations above 0.8 arcminutes.
@@
 
-\subsection*{Galaxy-Galaxy Correlation Function}
+\subsection*{Galaxy-mass Correlation Function}
 
-The catalog of lensed ellipticities was also analyzed using the galaxy-galaxy correlation function with separation distances from (0.1??) arcminutes to 2 arcminutes and a lightcone radius of 2 arcminutes.
+The catalog of lensed ellipticities was also analyzed using the galaxy-mass correlation function with separation distances from (0.1??) arcminutes to 2 arcminutes and a lightcone radius of 2 arcminutes.
 The result is shown in Figure (??).
 As with the ellipticity-ellipticity correlation function, there is no significant correlation for the intrinsic ellipticities at any scale as expected.
-The lensed ellipticities from the ray-tracing and halo model both have positive correlation on all calculated scales and are in excellent agreement on scales from (??) arcminutes to (??) arcminutes.
+The lensed ellipticities from the ray-tracing and halo model both have positive correlation on all calculated scales and are in agreement on scales from (??) arcminutes to (??) arcminutes.
 However, the halo model is still systematically underpredicting the shear power on scales above (??) arcminutes, although now only by an average of (??) percent.
@@
 %************************
-(Make a plot of n-g correlation function with multiple R's??)
+(Make a plot of n-g correlation function with multiple R's?? - No, mention that it was made but does not contain any interesting results)
 
@@
 A secondary goal of this research was to investigate how quickly the prediction for the shear and convergence for a single background source could be made.
-The average CPU time required for the prediction per lightcone was (??
-$\pm$ ??) for the first run.
+The average CPU time required for the prediction per lightcone was (80?
+$\pm$ 10?) ms for the first run.
 However, many small improvements to the coding infastructure of \texttt{Pangloss} were made to speed up the prediction.
@@
 
-Both the ellipticity-ellipticity and galaxy-galaxy correlation functions show clear issues with using the halo model to predict the lensing of background sources with \texttt{Pangloss}, even in the best-case scenario of perfect knowledge of the halo masses and their spectroscopic redshifts.
+Both the ellipticity-ellipticity and galaxy-mass correlation functions show clear issues with using the halo model to predict the lensing of background sources with \texttt{Pangloss}, even in the best-case scenario of perfect knowledge of the halo masses and their spectroscopic redshifts.
 The systematic underprediction of shear power present in both correlaton functions is likely do to missing features in the model such as clusters, filaments, and voids.
+
 While individual galaxies currently recieve halos, a cluster of galaxies will sit in an larger halo whose presence is not being considered as its position, mass, and extent are difficult to determine.
@@
 
-The progression of model-predicted ellipticity-ellipticity correlation functions at larger radii (somewhat) converging to the ray-traced correlation supports the analysis given above, as the prediction was progressively better with larger number of foreground halos and thus more mass and structure.
-However, the number of foreground objects scales quadratically with the lightcone radius making it prohibitively expensive above $R=16$ arcminutes.
+The progression of model-predicted ellipticity-ellipticity correlation functions at larger radii converging to the ray-traced correlation supports the analysis given above, as the prediction was progressively better with larger number of foreground halos and thus more mass and structure.
+However, the number of foreground objects scales quadratically with the lightcone radius making it prohibitively expensive above $R=8$ arcminutes.
 With a radius this large, most foreground objects will be too far away from the line of sight and have insufficient mass to make a significant contribution to the lensing of the background source.
@@
 While the current \texttt{Pangloss} framework can handle the lensing predictions of (x \# of lightcones) in a (y*y square degree) field comfortably on a single processor, the goal is to scale up the framework to make predictions for background sources of the same number density in a 100 deg$^2$ field; this will require 3.6 million lightcones, each containing up to 1,000 foreground halos.
-Luckily, the prediction is trivially parallelizable as the shear and convergence calculation of each lightcone is independent of all others.
+Luckily, the prediction is trivially parallelizable as the shear and convergence calculation of each lightcone is independent of all other lightcones.
 This makes GPUs an attractive candidate for future work, as it would only take 360 GPUs with 10,000 threads each to carry out the prediction.
@@
 
-pass
+%A simple halo model was used to reconstruct the mass along a line of sight asfd in the Millennium Simulation to make predictions of how the foreground mass weakly lensed the ellipticities of (x \# of bg) of generated backgrond sources.
+The lensed ellipticities were characterized globally using the ellipticity-ellipticity and galaxy-mass correlation functions and compared to the ray-traced correlations.
 
@@
 
-\begin{itemize}
-\item P.J. Marshall Thesis?
-\item Collett et al.
-\item S. Hilbert (ray-traced) http://arxiv.org/abs/0809.5035
-\item Millennium Simulation
-\item Schneider
-\item Jarvis \texttt{TreeCorr}
-\item lensing calculation http://arxiv.org/pdf/astro-ph/9908213v1.pdf
-\item NFW profile
-\item BMO truncation, BMO vs NFW http://arxiv.org/pdf/1301.1684v2.pdf
-\item SMHR http://arxiv.org/pdf/1401.7329v1.pdf
-\item Planck
-\item galaxy curves
-\item BAOs
-\item LCDM
-\item GR
-\item corrFuns in cosmology
-\item wl distortion percent
-\item CFHT Lensing Survey
-\end{itemize}
+%\bibliographystyle{plain}
+%\bibliography{suli-report-swe}
 
@@
 \begin{itemize}
-\item Use as a brief introduction to the shear-shear and galaxy-galaxy correlation function as used in this work
+\item Use as a brief introduction to the shear-shear and galaxy-mass correlation function as used in this work
     \begin{itemize}
@@
         \item Use halo model to make approximation of dark matter mass distribution in Millennium Simulation
-        \item Use shear-shear and galaxy-galaxy correlation functions as summary statistics
+        \item Use shear-shear and galaxy-mass correlation functions as summary statistics
         \item Compare statistics to ray-traced data
@@
             \item Use of correlation functions in cosmology
-            \item Shear-shear and galaxy-galaxy correlation functions
+            \item Shear-shear and galaxy-mass correlation functions
                 \begin{itemize}
@@
     \item shear-shear
-    \item galaxy-galaxy
+    \item galaxy-mass
     \item progression of each as $R$ increases??
@@
 
+%% References
+\begin{itemize}
+\item P.J. Marshall Thesis?
+\item Collett et al.
+\item S. Hilbert (ray-traced) http://arxiv.org/abs/0809.5035
+\item Millennium Simulation
+\item Schneider
+\item Jarvis \texttt{TreeCorr}
+\item lensing calculation http://arxiv.org/pdf/astro-ph/9908213v1.pdf
+\item NFW profile
+\item BMO truncation, BMO vs NFW http://arxiv.org/pdf/1301.1684v2.pdf
+\item SMHR http://arxiv.org/pdf/1401.7329v1.pdf
+\item Planck
+\item galaxy curves
+\item BAOs
+\item LCDM
+\item GR
+\item corrFuns in cosmology
+\item wl distortion percent
+\item CFHT Lensing Survey
+\end{itemize}
+
 Maybe do importance and/or lookup table after paper is submitted? Talk about in discussion?

### 2015-08-19 pangloss/background.py
Reverted `background.py` to use `lens_by_halos()` without the lensing table for the time being, as the memory leak has yet to be fixed.

@@ -288,7 +288,7 @@ class BackgroundCatalog(pangloss.Catalog):
             self.drill_lightcones()
 
         # Create lensing lookup table
-        lens_table = pangloss.LensingTable()
+        #lens_table = pangloss.lensing.LensingTable()
 
         # Initialize new variables (note: e and g have to be initialized as complex for memory allocation)
         assert self.galaxy_count == len(self.lightcones)
@@ -335,8 +335,8 @@ class BackgroundCatalog(pangloss.Catalog):
             lightcone.drawConcentrations(errors=True)
 
             # Compute each halo's contribution to the convergence and shear:
-            lightcone.makeKappas(truncationscale=10,lensing_table=lens_table)
-            #lightcone.makeKappas(truncationscale=10)
+            #lightcone.makeKappas(truncationscale=10,lensing_table=lens_table)
+            lightcone.makeKappas(truncationscale=10)
 
             # Combine all contributions into a single kappa and gamma for the lightcone
             lightcone.combineKappas(methods=methods)
@@ -363,7 +363,7 @@ class BackgroundCatalog(pangloss.Catalog):
             elapsed = timeit.default_timer() - start_time
             runtimes[lightcone.ID] = elapsed
 
-        del lens_table
+        #del lens_table
 
         if vb is True:
             print 'average CPU time per background galaxy: ',np.mean(runtimes),'+/-',np.std(runtimes)

### 2015-08-19 tests/lens_compare.py
Uncommented the corrleation function calcuations in the `lens_compare` test in `tests`.

@@ -38,10 +38,10 @@ if vb is True: print('Generating background catalog...')
 # Can pick one of the domains below
 #d = [1.85,1.15,-1.85,-1.15]
 #d = [1.75,1.25,-1.75,-1.25]
-#d = [1.65,1.35,-1.65,-1.35]
+d = [1.65,1.35,-1.65,-1.35]
 #d = [1.6,1.4,-1.6,-1.4]
 #d = [1.55,1.45,-1.55,-1.45]
-d = [1.55,1.48,-1.55,-1.48]
+#d = [1.55,1.48,-1.55,-1.48]
 #d = [1.55,1.52,-1.61,-1.59] # only galaxies in subplot
 #d = [1.55,1.54,-1.61,-1.6] # ~3 galaxies
 B = pangloss.BackgroundCatalog(N=10.0,sigma_e=0.01,domain=d,field=[0,0,0,0])
@@ -69,7 +69,7 @@ print 'Lightcones have',mean_galaxies,'+/-',std_galaxies,'galaxies'
 if vb is True: print('Lensing background by halos..')
 cProfile.run('B.lens_by_halos(importance_lim=0.0); print')
 #B.lens_by_halos(importance_lim=0.0)
-'''
+
 # Calculate the correlation function for each lensing type
 if vb is True: print('Calculating correlation...')
 gg_map = B.calculate_corr(corr_type='gg',lensed='map')
@@ -120,5 +120,5 @@ if pickle is True:
     pickle_file2 = open(filename2, 'wb')
     pickle.dump(gg2,pickle_file2)
     pickle_file2.close()
-'''
+
 if vb is True: print('Closing...')

### 2015-08-19 pangloss/plotting.py
Added a `line_style` kwarg to `plot_corr()` in `plotting.py` to allow a manual set of the line style of each correlation plot. Changed the default legend titles from `observed` to `ray-traced` and `predicted` to `halo model`.

@@ -199,7 +199,7 @@ def plot_sticks(ra,dec,mod,phi,axis,color):
 
 # ----------------------------------------------------------------------------
 
-def plot_corr(corr,corr_type='gg',corr_comp='plus',sep_units='arcmin',lensed='map',color=None,fig_size=10,M=None,galaxy_count=None):
+def plot_corr(corr,corr_type='gg',corr_comp='plus',sep_units='arcmin',lensed='map',color=None,line_style=None,fig_size=10,M=None,galaxy_count=None):
     '''
     Plot the correlation component 'corr_comp' of type 'corr_type' in separation units of 'sep_units'.
     By default the method will plot the lensed-by-map correlation, but can also plot without lensing
@@ -261,8 +261,8 @@ def plot_corr(corr,corr_type='gg',corr_comp='plus',sep_units='arcmin',lensed='ma
 
         # Mark first label as intrinsic, observed, or predicted
         if lensed == 'none': label1 = 'Intrinsic '
-        if lensed == 'map': label1 = 'Observed '
-        elif lensed == 'halo': label1 = 'Predicted '
+        if lensed == 'map': label1 = 'Ray-Traced '
+        elif lensed == 'halo': label1 = 'Halo Model '
 
         # Create the correct component label and linestyle to be used in legend
         if corr_comp == 'plus':
@@ -293,6 +293,10 @@ def plot_corr(corr,corr_type='gg',corr_comp='plus',sep_units='arcmin',lensed='ma
             ls = '-.'
             label2 = r'\times^\prime'
 
+        # If a linestyle is passed, overwrite default
+        if not (line_style is None):
+            ls = line_style
+
         # If the multiplicative error M is not None, add it to the legend label
         if M is not None:
             label2 += r',\,M={}'.format(M)
@@ -305,8 +309,8 @@ def plot_corr(corr,corr_type='gg',corr_comp='plus',sep_units='arcmin',lensed='ma
 
         # Mark first label as intrinsic, observed, or predicted
         if lensed == 'none': label1 = 'Intrinsic '
-        if lensed == 'map': label1 = 'Observed '
-        elif lensed == 'halo': label1 = 'Predicted '
+        if lensed == 'map': label1 = 'Ray-Traced '
+        elif lensed == 'halo': label1 = 'Halo Model '
 
         if corr_comp == 'real':
             # Plot real(xi) with a solid line
[…]

### 2015-08-19 doc/suli-report-swe.tex
Added 5 figures and captions to the SULI report. Not all figures are final - a few are mostly for planning the placement of the final figures. #81

@@
 \usepackage{mathtools}
+\usepackage{caption}
+\usepackage{subcaption}
 %\usepackage{multicol}
@@
 %\tableofcontents
+%\onecolumngrid
 
@@
 This compact notation combines the eccentricity and orientation of the ellipse into a single object.
-A plot from (Schneider et al.) showing the shape of elliptical galaxies for various values of $\varepsilon_1$ and $\varepsilon_2$ is shown in Figure (??).
-
-%************************
-(Galaxy Ellipticity Figure)
-%************************
+A plot from (Schneider et al.) showing the shape of elliptical galaxies for various values of $\varepsilon_1$ and $\varepsilon_2$ is shown in Figure \ref{ellipses}.
 
@@
 \subsection*{Gravitational Lensing}
+
+%% Ellipticity Orientation Figure
+\begin{figure*}
+    \centering
+    \begin{subfigure}[H]{0.415\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/ellipse_orientations.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{The shape of a galaxy image for various ellipticity components $\varepsilon_1$ and $\varepsilon_2$ on the $x$ and $y-$axes respectively. Taken from \cite{schneider}.}
+        \label{ellipses}
+    \end{subfigure}
+    ~
+    %% Einstein Ring Figure
+    \begin{subfigure}[H]{0.425\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/einstein_ring.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{An image of the luminous red galaxy LRG 3-757 along with a strongy lensed background galaxy, called the `Cosmic Horseshoe'\cite{einstein_ring}}
+        \label{einstein_ring}
+    \end{subfigure}
+    \caption{}
+\end{figure*}
 
@@
 effect is called \textit{strong} lensing if $|g|>1$ and \textit{weak} lensing if $|g|<1$.
-The effects of strong lensing can be quite dramatic, distorting sources into large arcs, multiple images, or even an Einstein ring as shown in Figure (??).
+The effects of strong lensing can be quite dramatic, distorting sources into large arcs, multiple images, or even an Einstein ring as shown in Figure \ref{einstein_ring}.
 While strong lenses are rare as the alignment of the source and foreground mass must be nearly perfect, \textit{all} sources are weakly lensed.
@@
 \section{The Pangloss Framework}
+
+%% Pangloss Cartoon
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.85\textwidth]{figs-swe/pangloss_cartoon.png}
+    \captionsetup{justification=raggedright,singlelinecheck=false}
+    \caption{A cartoon model of how the \texttt{Pangloss} framework uses a dark matter halo model to reconstruct the foreground mass along the line of sight of a background source galaxy.
+The shear and convergence at the line of sight contributed by each halo is calculated, and the predicted ellipticity is calculated using the sum of these contributions.}
+    \label{pangloss_cartoon}
+\end{figure*}
 
@@
 \subsection*{Creating Lightcones}
+
 While ideally all foreground mass in a field would be considered when predicting the weak lensing of a background galaxy, it is computationally prohibitive to do so.
 Instead, all foreground halos contained within a `lightcone' centered along the line of sight to the source and extending out to a chosen lightcone radius $R$ were considered when calculating the lensing contributions for the background source.
-A cartoon model of this process is shown in Figure (???).
+A cartoon model of this process is shown in Figure \ref{pangloss_cartoon}.
 Unless otherwise specified, experiments in this paper used a radius of 2 arcminutes.
-
-%************************
-(Pangloss Cartoon Figure)
-%************************
 
@@
 
-The first test of the halo model was with the ellipticity-ellipticity correlation function with a lightcone radius of 2 arcminutes which is given in Figure (??).
+The first test of the halo model was with the ellipticity-ellipticity correlation function with a lightcone radius of 2 arcminutes which is given in Figure \ref{gg_corr}.
 The statistic measured the average correlation between pairs of ellipticities at separation distances between (0.1??) arcminutes and 2 arcminutes.
@@
 
-%************************
-(e-e Correlation Function Plot)
-%************************
+%% Ellipticity-Ellipticity Correlation
+\begin{figure}
+    \centering
+    \begin{subfigure}[h]{0.475\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/gg_corr.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{The ellipticity-ellipticity correlation function for (x \# of bg) sources at separation distances from 0.1 arcminutes to 2 arcminutes and a lightcone radius of $R=2$ arcminutes.
+While the correlation of the intrinsic ellitpicities before lensing (blue) shows no correlation, the correlation of the ray-traced ellipticities (green) and halo model predicted ellipticities (purple) both show significant positive correlation on scales up to 0.8 arcminutes.
+The halo model predicts no correlation above this scale, while the ray-tracing shows positive correlation on all scales.}
+        %The correlation of the intrinsic ellitpicities before lensing is plotted in blue, and shows no correlation.
+The correlation of the true ray-traced ellipticities is plotted in green and shows significant positive correlation on all scales.
+The halo predicted correlation, plotted in purple, shows significant positive correlation until a separation distance of 0.8 arcminutes.
+        \label{gg_corr}
+    \end{subfigure}
+    ~~
+    \begin{subfigure}[h]{0.475\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/gg_corr_series.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{The ellipticity-ellipticity correlation functions for a series of halo model frameworks with increasing lightcone radii from $R=1$ arminute to $R=8$ arcminutes, all plotted in purple with various line styles.
+These are compared to the ray-traced correlation using a radius of 2 arcminutes plotted in green.}
+        \label{gg_corr_series}
+    \end{subfigure}
+    \caption{}
+\end{figure}
 
 Using the same catalog of background sources, this statistic was recalculated for the ray-traced and halo model lensed ellipticities for various lightcone radii ranging from $R=1$ arcminute to $R=???$ arcminutes.
-The result is shown in Figure (??).
-
-%************************
-(e-e Correlation Function Plot with multiple R's)
-%************************
+The result is shown in Figure \ref{gg_corr_series}.
 
@@
 
-%************************
-(n-g Correlation Function Plot)\\
-%************************
+%% Galaxy-mass correlation function
+\begin{figure}
+    \centering
+    \includegraphics[width=0.475\textwidth]{figs-swe/ng_corr.png}
+    \captionsetup{justification=raggedright,singlelinecheck=false}
+    \caption{The galaxy-mass correlation function of (x \# of bg) sources at separation distances from 0.1 arcminutes to 2 arcminutes and a lightcone radius of $R=2$ arcminutes.
+There is no significant correlation of the intrinsic ellipticities (blue) as expected, and both the ray-traced corrleation (green) and halo model correlation (purple) are positive on all scales.
+The green and purple curves are in agreement from 0.?
+to 0.?
+arcminutes, but have significant discrepancies on scales above and below this range.}
+    \label{pangloss_cartoon}
+\end{figure}
 (Make a plot of n-g correlation function with multiple R's?? - No, mention that it was made but does not contain any interesting results)
@@
 
-%A simple halo model was used to reconstruct the mass along a line of sight asfd in the Millennium Simulation to make predictions of how the foreground mass weakly lensed the ellipticities of (x \# of bg) of generated backgrond sources.
+A simple halo model was used to reconstruct the mass along line of sights in the Millennium Simulation to make predictions of how the foreground mass weakly lensed the ellipticities of (x \# of bg) of generated background sources.
 The lensed ellipticities were characterized globally using the ellipticity-ellipticity and galaxy-mass correlation functions and compared to the ray-traced correlations.

### 2015-08-19 doc/suli-report-swe.tex
Fixed calls to make the References section, changed it to a single column format. #81

@@
 For readers that are unfamiliar with correlation functions in the context of cosmology or want a visual aid, see Appendix A.
-Both correlation functions are used in this work to measure how well the \texttt{Pangloss} framework models weak lensing by dark matter structures using the publically available \texttt{TreeCorr} module written by Mike Jarvis\footnote{https://github.com/rmjarvis/TreeCorr}.
+Both correlation functions are used in this work to measure how well the \texttt{Pangloss} framework models weak lensing by dark matter structures using the publically available \texttt{TreeCorr} module written by Mike Jarvis (website url?).
 Note that the correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition and the more common Schneider definition\cite{schneider}, see Appendix B.
@@
 
+\onecolumngrid
+
 \section{References}
 
-%\bibliographystyle{plain}
-%\bibliography{suli-report-swe}
+\bibliographystyle{plain}
+\bibliography{suli-report-swe}
 
-\onecolumngrid
 \section{Appendix}
@@
 as desired.
-
-% Bibliography
 

### 2015-08-19 doc/suli-report-swe.tex
Fixed journal name LaTeX commands in SULI report. #81
Added footnotes for the `Pangloss` and `TreeCorr` repository URLs in the SULI report. #81

--- 2015-08-19 doc/suli-report-swe.tex
@@
  amsmath,amssymb,
- aps,
+ aps,nofootinbib
 %pra,
@@
 
+% Used for .bib file
+\newcommand{\mnras}{MNRAS}
+\newcommand{\aap}{A\&A}
+
 \begin{document}
@@
 In this paper, a simple halo model is used to approximate the dark matter mass distribution of the Millennium Simulation on the galaxy and cluster scales.
-Background sources are generated at a redshift of ${z = 1.3857}$ and then weakly lensed by the foreground halos contained in a light cone centered along each line of sight, which is carried out by the \texttt{Pangloss} framework\footnote{https://github.com/drphilmarshall/Pangloss}.
+Background sources are generated at a redshift of ${z = 1.3857}$ and then weakly lensed by the foreground halos contained in a light cone centered along each line of sight, which is carried out by the publically available \texttt{Pangloss} framework.
 The model-predicted ellipticities of the background galaxies after lensing are compared to the ``true'' weakly-lensed ellipticities determined by ray-traced convergence and shear from the simulation.
@@
 To constrain the mass of foreground dark matter using weak gravitational lensing, first a model of the relationship between foreground galaxies and the foreground dark matter must be established and robustly tested to see if, statistically, it makes the same lensing predictions of background sources as the true undering dark matter structure.
-To do this, I built upon the publically available \texttt{Pangloss} framework used in Collett et al.\cite{collett_marshall} to reconstruct all the mass along the line of sight of each background galaxy using dark matter halos.
+To do this, I built upon the publically available \texttt{Pangloss} framework\footnote{https://github.com/drphilmarshall/Pangloss} used in Collett et al.\cite{collett_marshall} to reconstruct all the mass along the line of sight of each background galaxy using dark matter halos.
 The lensing contribution of each halo is calculated, and the total lensing of the background galaxy is the sum of each halo contribution.

### 2015-08-20 doc/suli-report-swe.tex
Made various revisions throughout to the SULI report #81

@@
 \newcommand{\aap}{A\&A}
+\newcommand{\apjl}{ApJ}
 
@@
 In this paper, a simple halo model is used to approximate the dark matter mass distribution of the Millennium Simulation on the galaxy and cluster scales.
-Background sources are generated at a redshift of ${z = 1.3857}$ and then weakly lensed by the foreground halos contained in a light cone centered along each line of sight, which is carried out by the publically available \texttt{Pangloss} framework.
-The model-predicted ellipticities of the background galaxies after lensing are compared to the ``true'' weakly-lensed ellipticities determined by ray-traced convergence and shear from the simulation.
-Using the ellipticity-ellipticity and galaxy-mass correlation functions, I find that the \texttt{Pangloss} framework systematically under-predicts the shear power in both statistics and does not accurately capture the effect of dark matter structure at scales larger than 1 arcminute.
+Background sources are generated at a redshift of ${z = 1.3857}$ and then weakly lensed by the foreground halos contained in a light cone centered along each line of sight, which is carried out by the publicaly available \texttt{Pangloss} framework.
+The modelpredicted ellipticities of the background galaxies after lensing are compared to the ``true'' weakly-lensed ellipticities determined by ray-traced convergence and shear from the simulation.
+Using the ellipticity-ellipticity and galaxy-mass correlation functions, I find that the \texttt{Pangloss} framework systematically underpredicts the shear power in both statistics and does not accurately capture the effect of dark matter structure at scales larger than 1 arcminute.
 Physical and computational shortcomings of the \texttt{Pangloss} framework are discussed, as well as potential improvements for upcoming work.
@@
 
-In a universe teeming with galaxies and light, it came as a shock when 20\textsuperscript{th} century astronomers unexpectedly discovered that most of the mass in the universe is in fact dark; the `normal' matter made of atoms that we interact with in everyday life, called baryonic matter, only accounts for (20\%?) of the mass in the observable universe.
+In a universe teeming with galaxies and light, it came as a shock when 20\textsuperscript{th} century astronomers unexpectedly discovered that most of the mass in the universe is in fact dark; the `normal' matter made of atoms that we interact with in everyday life, called baryonic matter, accounts for less than 20\% of the mass in the observable universe.
 The remaining mass takes the form of an exotic dark matter that does not absorb or emit light, rendering it invisible to our telescopes.
-While this claim sounds bizarre, there has been an abundance of indirect evidence in recent decades for the existence of dark matter including the flattening of galaxy rotation curves\cite{rotation_curve}, (something else) (cite), and acoustic peaks in the cosmic microwave background\cite{planck_2015}.
+While this claim sounds bizarre, there has been an abundance of indirect evidence in recent decades for the existence of dark matter including the flattening of galaxy rotation curves \cite{rotation_curve}, velocity dispersions of galaxies \cite{zwicky} and acoustic peaks in the cosmic microwave background \cite{planck_2015}.
 
@@
 
-While the effects of gravitational lensing can be dramatic, the shape of most galaxies is only distorted by a few percent (cite) and must be detected statistically as the intrinsic shape is not known.
+While the effects of gravitational lensing can be dramatic, the shape of most galaxies is only distorted by a few percent and must be detected statistically as the intrinsic shape is not known.
 If a model for the distribution of dark matter in a region of foreground mass can accurately predict the statistical signal of this `weak' lensing of background galaxies, then the model can be used on galaxies in existing sky survey data to extrapolate the amount of dark matter in the region and construct large-scale maps of the dark matter in the universe.
@@
 A brief introduction into the theory of galaxy ellipticities, the effects of strong and weak gravitational lensing, and dark matter halos is discussed in Section II.
-The implementation of a halo model on the Millennium Simulation and ellipticity predictions is described in Section III, and the results of the model on (x \# of galaxies on a field size of x \# deg$^2$) as well as a comparison of the predicted lensed ellipticities to the true ellipticities is given in Section IV.
-Section V discusses limitations of the used \texttt{Pangloss} framework as well as potential physical and computational improvements that can be made for upcoming work before concluding remarks in Section VI.
+The implementation of a halo model on the Millennium Simulation and ellipticity predictions is described in Section III, and the results of the model on 3,240 galaxies on a field size of 0.09 deg$^2$ as well as a comparison of the predicted lensed ellipticities to the true ellipticities is given in Section IV.
+Section V discusses limitations of the used \texttt{Pangloss} framework along with potential physical and computational improvements that can be made for upcoming work before concluding remarks in Section VI.
 
@@
 This compact notation combines the eccentricity and orientation of the ellipse into a single object.
-A plot from (Schneider et al.) showing the shape of elliptical galaxies for various values of $\varepsilon_1$ and $\varepsilon_2$ is shown in Figure \ref{ellipses}.
+A plot from Schneider et al.
+\cite{schneider} showing the shape of elliptical galaxies for various values of $\varepsilon_1$ and $\varepsilon_2$ is shown in Figure \ref{ellipses}.
 
-There are many complications to using this scheme in practice, most notably the multiplicative bias resulting from the smearing of galaxy images by the observational point spread function (PSF)\cite{multiplicative_bias}.
+There are many complications to using this scheme in practice, most notably the multiplicative bias resulting from the smearing of galaxy images by the observational point spread function (PSF) \cite{multiplicative_bias}.
 While the effects of a PSF can be complex, in general it causes galaxy images to appear less elliptical than they truly are.
@@
         \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{An image of the luminous red galaxy LRG 3-757 along with a strongy lensed background galaxy, called the `Cosmic Horseshoe'\cite{einstein_ring}}
+        \caption{An image of the luminous red galaxy LRG 3-757 along with a strongy lensed background galaxy, called the `Cosmic Horseshoe' \cite{einstein_ring}.}
         \label{einstein_ring}
@@
 \noindent where $|\gamma|$ is the magnitude of the shear and $\varphi$ is the orientation of the shear.
-While the intrinsic ellipticities of source galaxies are randomly oriented near the foreground mass before lensing, they will be systematically more aligned with the shear field after lensing.
-Figure (??) demonstrates this process visually.
+While the intrinsic ellipticities of source galaxies are randomly oriented near the foreground mass before lensing, they will be systematically more aligned with the shear field after lensing.% Figure (??) demonstrates this process visually.
 
@@
 
-\noindent where an asterisk denotes the complex conjugate\cite{schneider}. The behavior of the distortion relies strongly on the magnitude of $g$; the
+\noindent where an asterisk denotes the complex conjugate \cite{schneider}. The behavior of the distortion relies strongly on the magnitude of $g$; the
 effect is called \textit{strong} lensing if $|g|>1$ and \textit{weak} lensing if $|g|<1$.
@@
 While strong lenses are rare as the alignment of the source and foreground mass must be nearly perfect, \textit{all} sources are weakly lensed.
-The effect is small, usually an ellipticity distortion of only a few percent (cite?), but can be detected locally by averaging the ellipticities of all sources in a small region.
+The effect is small, usually an ellipticity distortion of only a few percent, but can be detected locally by averaging the ellipticities of all sources in a small region.
 As the orientations of the sources should be random, it would be expected that
@@
 This means that galaxies \textit{should} trace out the larger underlying dark matter structures.
-The simplest way to model this relationship is by enveloping each galaxy in a spherically symmetric dark matter `halo' of mass $M_h$ sampled from the stellar-to-halo mass relation\cite{smhr}.
+The simplest way to model this relationship is by enveloping each galaxy in a spherically symmetric dark matter `halo' of mass $M_h$ sampled from the stellar-to-halo mass relation \cite{smhr}.
 These halos extend far beyond the edge of the visible galaxy that they enclose.
@@
 
-\noindent where the constant $\rho_0$ and the scale radius $R_s$ are parameters that vary from halo to halo\cite{nfw}.
+\noindent where the constant $\rho_0$ and the scale radius $R_s$ are parameters that vary from halo to halo \cite{nfw}.
 This work uses a truncated NFW profile called the Baltz-Marshall-Oguri (BMO) profile given by
@@
 
-\noindent where $r_t$ is a free parameter, as it has been shown to be a better fit to simulated data\cite{nfw_bmo}.
+\noindent where $r_t$ is a free parameter, as it has been shown to be a better fit to simulated data \cite{nfw_bmo}.
 
@@
     \caption{A cartoon model of how the \texttt{Pangloss} framework uses a dark matter halo model to reconstruct the foreground mass along the line of sight of a background source galaxy.
-The shear and convergence at the line of sight contributed by each halo is calculated, and the predicted ellipticity is calculated using the sum of these contributions.}
+A `lightcone' centered at a background source is constructed with radius $R$ and populated with all foreground galaxies contained in this volume.
+Each foreground object has an attached dark matter halo and physical distance to the line of sight (dashed line).
+The shear and convergence along the line of sight contributed by each halo is calculated, and the predicted ellipticity is calculated using the sum of these contributions.}
     \label{pangloss_cartoon}
@@
 To constrain the mass of foreground dark matter using weak gravitational lensing, first a model of the relationship between foreground galaxies and the foreground dark matter must be established and robustly tested to see if, statistically, it makes the same lensing predictions of background sources as the true undering dark matter structure.
-To do this, I built upon the publically available \texttt{Pangloss} framework\footnote{https://github.com/drphilmarshall/Pangloss} used in Collett et al.\cite{collett_marshall} to reconstruct all the mass along the line of sight of each background galaxy using dark matter halos.
+To do this, I built upon the publicly available \texttt{Pangloss} framework\footnote{https://github.com/drphilmarshall/Pangloss} used in Collett et al.
+\cite{collett_marshall} to reconstruct all the mass along the line of sight of each background galaxy using dark matter halos.
 The lensing contribution of each halo is calculated, and the total lensing of the background galaxy is the sum of each halo contribution.
@@
 Testing the first assumption is the main goal of this paper.
-The second assumption is reasonable as it is estimated that dark matter halos are 1-2 orders of magnitude more massive than the host galaxy\cite{smhr}.
+The second assumption is reasonable as it is estimated that dark matter halos are 1-2 orders of magnitude more massive than the host galaxy \cite{smhr}.
 Clearly the third assumption will never be true for any observational data.
@@
 \texttt{Pangloss} cannot be used to make dark matter mass maps using existing galaxy catalogs until it is tested on a simulated universe with known dark matter structure to determine how accurately and precisely it predicts the lensing of background sources.
-For this purpose, \texttt{Pangloss} was tested on galaxy catalogs from the Millennium Simulation, an N-body simulation consisting of over 10 billion dark matter `particles' each representing a billion solar masses and populated with about 20 million galaxies\cite{millennium_simulation}.
+For this purpose, \texttt{Pangloss} was tested on galaxy catalogs from the Millennium Simulation, an N-body simulation consisting of over 10 billion dark matter `particles' each representing a billion solar masses and populated with about 20 million galaxies \cite{millennium_simulation}.
 The simulation uses cosmological parameters from WMAP 1\textsuperscript{st}-year data analysis and contains baryonic and dark matter structure believed to be consistent with our own universe.
-From the work of Hilbert et al.\cite{ray_tracing}, high resolution maps of the shear and convergence from the perspective of a single reference point calculated by ray-tracing are publically available.
+From the work of Hilbert et al.
+\cite{ray_tracing}, high resolution maps of the shear and convergence from the perspective of a single reference point calculated by ray-tracing are publicly available.
 From these maps, the actual lensing of background galaxies when traveling through the foreground mass of the Millennium Simulation towards the reference point can be calculated using Equation \eqref{lensing}.
@@
 \subsection*{Generating Background Galaxies}
-With a catalog of foreground galaxies chosen, a set of background galaxies with density 10 per arcminute$^2$ was generated.
-The intrinsic orientation of each galaxy was sampled from a uniform distribution as, without lensing, there should be no preferred orientation due to the assumption of an isotropic universe.
+With a catalog of foreground galaxies chosen, a set of 3,240 background galaxies over a field of 0.09 deg$^2$ was generated, with density 10 per arcminute$^2$.
+As the The intrinsic orientation of each galaxy was sampled from a uniform distribution as, without lensing, there should be no preferred orientation due to the assumption of an isotropic universe.
 The magnitude of the galaxy ellipticities was sampled from a normal distribution with a standard deviation of 0.2, but any ellipticities with magnitude greater than one were re-sampled.
@@
 
-Using the physical separation distance and halo mass, the shear and convergence contribution of a single foreground halo is calculated using methods described in Wright and Brainerd\cite{lensing_calc}.
+Using the physical separation distance and halo mass, the shear and convergence contribution of a single foreground halo is calculated using methods described in Wright and Brainerd \cite{lensing_calc}.
 The total convergence and shear at the center of the lightcone is simply the sum of the convergence and shear contributions of each halo contained in the lightcone.
-The \texttt{Pangloss}-predicted lensed background ellipticity is then calculated using Equation \eqref{lensing}.
+The \texttt{Pangloss} predicted lensed background ellipticity is then calculated using Equation \eqref{lensing}.
 
@@
 
-Instead of comparing the ray-traced and \texttt{Pangloss}-predicted ellipticities for individual galaxies, the lensing is characterized globally with correlation functions.
+Instead of comparing the ray-traced and \texttt{Pangloss} predicted ellipticities for individual galaxies, the lensing is characterized globally with correlation functions.
 The ellipticity-ellipticity correlation function measures how correlated the ellipticities of pairs of galaxies are as a function of separation distance, while the galaxy-mass correlation function measures the correlation of lensed ellipticities around foreground halos as a function of separation distance.
-For readers that are unfamiliar with correlation functions in the context of cosmology or want a visual aid, see Appendix A.
-Both correlation functions are used in this work to measure how well the \texttt{Pangloss} framework models weak lensing by dark matter structures using the publically available \texttt{TreeCorr} module written by Mike Jarvis\footnote{https://github.com/rmjarvis/TreeCorr}.
-Note that the correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition and the more common Schneider definition\cite{schneider}, see Appendix B.
+Both correlation functions are used in this work to measure how well the \texttt{Pangloss} framework models weak lensing by dark matter structures using the publicly available \texttt{TreeCorr} module written by Mike Jarvis\footnote{https://github.com/rmjarvis/TreeCorr}.
+Note that the ellipticity-ellipticity correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition and the more common Schneider definition \cite{schneider}, see the appendix.
+%For readers that are unfamiliar with correlation functions in the context of cosmology or want a visual aid, see Appendix A.
 
@@
 
-Using the presented methodology, (x \# of background sources) background galaxies in a (y*y square deg) subset of the (0,0,0,0) Millennium Simulation foreground catalog (cite where to get data) were generated and lensed by both the ray-traced shear and convergence maps as well as the \texttt{Pangloss} framework.
-On average, the lightcones contained (950??)$\pm$(25??) foreground halos.
+Using the presented methodology, 3,240 background galaxies in a 0.09 deg$^2$ subset of the (0,0,0,0) Millennium Simulation foreground catalog were generated and lensed by both the ray-traced shear and convergence maps as well as the \texttt{Pangloss} framework.
+With a lightcone radius of 2 arcminutes, the lightcones contained an average of ${950\pm70}$ foreground halos.
 Both sets of lensed ellipticities were characterized with correlation functions, as well as the intrinsic ellipticities of the sources before lensing.
@@
 The first test of the halo model was with the ellipticity-ellipticity correlation function with a lightcone radius of 2 arcminutes which is given in Figure \ref{gg_corr}.
-The statistic measured the average correlation between pairs of ellipticities at separation distances between (0.1??) arcminutes and 2 arcminutes.
+The statistic measured the average correlation between pairs of ellipticities at separation distances between 0.1 and 2 arcminutes.
 The correlation function of the intrinsic ellipticities plotted in blue shows no significant deviation from zero as expected, as before lensing the galaxies had random orientations.
-Both the ray-traced, plotted in green, and halo model, plotted in purple, ellipticities show positive correlation on small scales up to a separation of 0.8 arcminutes.
-However, the ray-traced correlation is positive on all calculated scales while the halo model does not predict any significant corrlelation at separations above 0.8 arcminutes.
-Additionally, while the shapes of the correlation functions for both sets of lensed ellipticities aggree well until 0.8 arcminutes, there is a clear systematic underprediction of shear power by the halo model on all scales.
-On average, the shear power is underpredicted by (??) percent.
+Both the ray-traced, plotted in green, and halo model, plotted in purple, ellipticities show positive correlation on small scales up to a separation of 1 arcminute.
+However, the ray-traced correlation is positive on all calculated scales while the halo model does not predict any significant corrlelation at separations above 1arcminute.
+Additionally, while the shapes of the correlation functions for both sets of lensed ellipticities aggree well until 1 arcminute, there is a clear systematic underprediction of shear power by the halo model on all scales.
+On average, the shear power is underpredicted by 117.0 percent.
 
@@
         \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{The ellipticity-ellipticity correlation function for (x \# of bg) sources at separation distances from 0.1 arcminutes to 2 arcminutes and a lightcone radius of $R=2$ arcminutes.
-While the correlation of the intrinsic ellitpicities before lensing (blue) shows no correlation, the correlation of the ray-traced ellipticities (green) and halo model predicted ellipticities (purple) both show significant positive correlation on scales up to 0.8 arcminutes.
+        \caption{The ellipticity-ellipticity correlation function for 3,240 sources at separation distances from 0.1 arcminutes to 2 arcminutes and a lightcone radius of $R=2$ arcminutes.
+While the correlation of the intrinsic ellitpicities before lensing (blue) shows no correlation, the correlation of the ray-traced ellipticities (green) and halo model predicted ellipticities (purple) both show significant positive correlation on scales up to 1 arcminute.
 The halo model predicts no correlation above this scale, while the ray-tracing shows positive correlation on all scales.}
@@
 
-Using the same catalog of background sources, this statistic was recalculated for the ray-traced and halo model lensed ellipticities for various lightcone radii ranging from $R=1$ arcminute to $R=???$ arcminutes.
-The result is shown in Figure \ref{gg_corr_series}.
-
-(Analysis of plot)
+Using the same catalog of background sources, this statistic was recalculated for the ray-traced and halo model lensed ellipticities for various lightcone radii ranging from $R=1$ arcminute to $R=8$ arcminutes.
+The result is shown in Figure \ref{gg_corr_series}, where the series of model predicted correlation functions is compared to the ray-traced correlation function for $R=8$ arcminutes.
+As $R$ increases, the mean number of foreground galaxies contained in each lightcone grows quadratically from ${240\pm25}$ galaxies when $R=1$ arcminute to ${15,000\pm300}$ galaxies when $R=8$ arcminutes.
+Increasing the number of foreground objects, and thus increasing the mass and structure considered for shear and convergence predictions, systematically increased the predicted shear power on all scales.
+While the series of predicted correlation functions appears to be converging towards the ray-traced correlation function, (diminishing returns).
 
@@
 
-The catalog of lensed ellipticities was also analyzed using the galaxy-mass correlation function with separation distances from (0.1??) arcminutes to 2 arcminutes and a lightcone radius of 2 arcminutes.
-The result is shown in Figure (??).
+The catalog of lensed ellipticities was also analyzed using the galaxy-mass correlation function with separation distances from 0.1 arcminutes to 2 arcminutes and a lightcone radius of 2 arcminutes.
+The result is shown in Figure \ref{ng_corr}.
 As with the ellipticity-ellipticity correlation function, there is no significant correlation for the intrinsic ellipticities at any scale as expected.
-The lensed ellipticities from the ray-tracing and halo model both have positive correlation on all calculated scales and are in agreement on scales from (??) arcminutes to (??) arcminutes.
-However, the halo model is still systematically underpredicting the shear power on scales above (??) arcminutes, although now only by an average of (??) percent.
-A new feature is the large overprediction of shear power on separation scales smaller than (??) arcminutes.
+The lensed ellipticities from the ray-tracing and halo model both have positive correlation on all calculated scales and are in agreement on scales from 0.2 arcminutes to 0.7 arcminutes.
+However, the halo model is still systematically underpredicting the shear power on scales above 0.7 arcminutes, although now only by an average of 23.2 \%.
+A new feature is the large overprediction of shear power on separation scales smaller than 0.2 arcminutes.
 However, background sources this close to foreground halos are often in the strong lensing regime which is not currently accounted for by the \texttt{Pangloss} framework.
@@
     \captionsetup{justification=raggedright,singlelinecheck=false}
-    \caption{The galaxy-mass correlation function of (x \# of bg) sources at separation distances from 0.1 arcminutes to 2 arcminutes and a lightcone radius of $R=2$ arcminutes.
+    \caption{The galaxy-mass correlation function of 3,240 sources at separation distances from 0.1 arcminutes to 2 arcminutes and a lightcone radius of $R=2$ arcminutes.
 There is no significant correlation of the intrinsic ellipticities (blue) as expected, and both the ray-traced corrleation (green) and halo model correlation (purple) are positive on all scales.
-The green and purple curves are in agreement from 0.?
-to 0.?
-arcminutes, but have significant discrepancies on scales above and below this range.}
-    \label{pangloss_cartoon}
+The green and purple curves are in agreement from 0.2 to 0.7 arcminutes, but have significant discrepancies on scales above and below this range.}
+    \label{ng_corr}
 \end{figure}
-(Make a plot of n-g correlation function with multiple R's?? - No, mention that it was made but does not contain any interesting results)
 
@@
 A secondary goal of this research was to investigate how quickly the prediction for the shear and convergence for a single background source could be made.
-The average CPU time required for the prediction per lightcone was (80?
-$\pm$ 10?) ms for the first run.
+The mean CPU time required for the prediction per lightcone was ${80\pm10}$ ms for the first run.
 However, many small improvements to the coding infastructure of \texttt{Pangloss} were made to speed up the prediction.
-The average CPU time for a lensing prediction per lightcone after various changes is plotted in Figure (??).
+The average CPU time for a lensing prediction per lightcone after various changes is plotted in Figure \ref{cpu_plot}.
 
@@
 
-The progression of model-predicted ellipticity-ellipticity correlation functions at larger radii converging to the ray-traced correlation supports the analysis given above, as the prediction was progressively better with larger number of foreground halos and thus more mass and structure.
+The progression of model predicted ellipticity-ellipticity correlation functions at larger radii converging to the ray-traced correlation supports the analysis given above, as the prediction was progressively better with larger number of foreground halos and thus more mass and structure.
 However, the number of foreground objects scales quadratically with the lightcone radius making it prohibitively expensive above $R=8$ arcminutes.
@@
 
-While the current \texttt{Pangloss} framework can handle the lensing predictions of (x \# of lightcones) in a (y*y square degree) field comfortably on a single processor, the goal is to scale up the framework to make predictions for background sources of the same number density in a 100 deg$^2$ field; this will require 3.6 million lightcones, each containing up to 1,000 foreground halos.
+While the current \texttt{Pangloss} framework can handle the lensing predictions of 3,240 in a 0.09 deg$^2$ field comfortably on a single processor, the goal is to scale up the framework to make predictions for background sources of the same number density in a 100 deg$^2$ field; this will require 3.6 million lightcones, each containing up to 1,000 foreground halos.
 Luckily, the prediction is trivially parallelizable as the shear and convergence calculation of each lightcone is independent of all other lightcones.
@@
 
-A simple halo model was used to reconstruct the mass along line of sights in the Millennium Simulation to make predictions of how the foreground mass weakly lensed the ellipticities of (x \# of bg) of generated background sources.
-The lensed ellipticities were characterized globally using the ellipticity-ellipticity and galaxy-mass correlation functions and compared to the ray-traced correlations.
+In this paper, a simple halo model was used to reconstruct all the mass along lines of sight in the Millennium Simulation to make predictions of how foreground mass weakly lensed the ellipticities of 3,240 generated background sources accross a field of 0.09 deg$^2$.
+The lensed ellipticities were characterized globally using the ellipticity-ellipticity and galaxy-mass correlation functions and then compared with the same statistics from ray-traced data.
+There was a systematic-underprediction of shear power on all scales in the ellipticity-ellipticity correlation function as well as an absence of any predicted correlation on scales larger than 1 arcminute, suggesting missing features in the \texttt{Pangloss} framework.
+The galaxy-mass correlation function predicted by the halo model was in agreement with the ray-traced correlation function on scales from 0.2 to 0.7 arcminutes, but significantly overpredicted the shear power on smaller scales due to strong lensing effects.
+Now that a proof of concept has been demonstrated, there is work being done to scale up the \texttt{Pangloss} framework to make lensing predictions over 100 deg$^2$ using far more computational resources.
+While the results are encouraging for such a simple model, many strong and unrealistic assumptions were made in the methodology that limit its use in observational surveys.
+In the future, a similar analysis should be made after relaxing many of the assumptions to see how different the predictions by the halo model are from this best-case scenario.
 
@@
 
-I would like to thank the Department of Energy's Science Undergraduate Laboratory Internship (SULI) program for funding this research and giving me the opportunity to conduct research at ?.
-asdf.
-Finally, I am incredibly grateful to Phil Marshall for his unending support, patience, and guidance throughout this research.
+I would like to thank the Department of Energy for funding this research and giving me the opportunity to conduct research on (cutting edge physics).
+This work was greatly aided by numerous conversations with Risa Wechsler from Stanford University and Matt Becker from the Kavli Institute for Particle Astrophysics and Cosmology (KIPAC).
+Finally, I am incredly grateful to Phil Marshall for his unending support, patience, and guidance throughout this research.
 
@@
 Department of Energy, Office of Science, Office of Workforce Development for Teachers and Scientists (WDTS) under the Science Undergraduate Laboratory Internships Program (SULI).
-
-\begin{itemize}
-\item DOE
-\item SULI
-\item Stanford University
-\item KIPAC
-\item Risa, Matt, Pat
-\item Phil!!
-\end{itemize}
 
@@
 
-\bibliographystyle{plain}
+\bibliographystyle{unsrt}
 \bibliography{suli-report-swe}
+
+%\end{document}
 
@@
 \subsection{Visualizing Correlation Functions}
+
+At first encounter, the use of correlation functions to analyze data can be difficult to comprehend, let alone visualize.
+While by no means a thorough or mathematical analysis (see (cite) for a general introduction to correlation functions, and (cite) for their many applications in cosmology), I have created some explanatory plots to aid in visualizing how weakly lensed ellipticities can be measured with correlation functions and put the main results of this paper in more context.
+
+The first statistic used in this work is the ellipticity-ellipticity ($\varepsilon-\varepsilon$) correlation function, which has two tangential components $\xi_\pm$ and a cross component $\xi_\times$.
+The components most interesting for gravitational lensing are the positive tangential component $\xi_+$, expected to be positive for lensed galaxies, and the cross component $\xi_\times$, which is expected to be zero.
+To get an intuition for what these quantities measure, first consider the correlation values for individual pairs of galaxies as shown in Figure \ref{corr_colormaps}.
+In each plot, the value of the correlation between two galaxy orientations is plotted as a colormap with a few sampled orientations plotted on top of the graph.
 
@@
 
-\subsection{Jarvis Proof}
+\subsection{Deriving the Standard Correlation Function Definition from \texttt{TreeCorr}'s Definition}
 
@@
 as desired.
-
-\end{document}
-%
-% ****** End of file apssamp.tex ******
 
@@
 
+%% Acknowledgements
+\begin{itemize}
+\item DOE
+\item SULI
+\item Stanford University
+\item KIPAC
+\item Risa, Matt, Pat
+\item Phil!!
+\end{itemize}
+
 %% References

### 2015-08-20 doc/suli-report-swe.tex
Revised the abstract for the SULI report. #81

@@
 While most sources are only weakly lensed, the systematic alignment of background galaxies around a foreground lens can constrain the mass of the lens which is largely in the form of dark matter.
-In this paper, a simple halo model is used to approximate the dark matter mass distribution of the Millennium Simulation on the galaxy and cluster scales.
-Background sources are generated at a redshift of ${z = 1.3857}$ and then weakly lensed by the foreground halos contained in a light cone centered along each line of sight, which is carried out by the publicaly available \texttt{Pangloss} framework.
-The modelpredicted ellipticities of the background galaxies after lensing are compared to the ``true'' weakly-lensed ellipticities determined by ray-traced convergence and shear from the simulation.
-Using the ellipticity-ellipticity and galaxy-mass correlation functions, I find that the \texttt{Pangloss} framework systematically underpredicts the shear power in both statistics and does not accurately capture the effect of dark matter structure at scales larger than 1 arcminute.
-Physical and computational shortcomings of the \texttt{Pangloss} framework are discussed, as well as potential improvements for upcoming work.
+In this paper, I have implemented a framework to reconstruct all of the mass along lines of sight using a  best-case dark matter halo model in which the halo mass is known.
+This framework is then used to make predictions of the weak lensing of 3,240 generated source galaxies through a 0.09 deg$^2$ field of the Millennium Simulation.
+The lensed source ellipticities are characterized by the ellipticity-ellipticity and galaxy-mass correlation functions and compared to the same statistic for the intrinsic and ray-traced ellipticities.
+In the ellipticity-ellipticity correlation function, I find that the framework systematically under predicts the shear power by 117.0\% and fails to capture correlation from dark matter structure at scales larger than 1 arcminute.
+The model predicted galaxy-mass correlation function is in agreement with the ray-traced statistic from scales 0.2 to 0.7 arcminutes, but systematically underpredicts shear power at scales larger than 0.7 arcminutes by 23.2\%.
+Physical and computational shortcomings of the framework are discussed, as well as potential improvements for upcoming work.
 \end{abstract}
@@
         \caption{The ellipticity-ellipticity correlation functions for a series of halo model frameworks with increasing lightcone radii from $R=1$ arminute to $R=8$ arcminutes, all plotted in purple with various line styles.
-These are compared to the ray-traced correlation using a radius of 2 arcminutes plotted in green.}
+These are compared to the same ray-traced correlation from Figure \ref{gg_corr}.}
         \label{gg_corr_series}
@@
 Using the same catalog of background sources, this statistic was recalculated for the ray-traced and halo model lensed ellipticities for various lightcone radii ranging from $R=1$ arcminute to $R=8$ arcminutes.
-The result is shown in Figure \ref{gg_corr_series}, where the series of model predicted correlation functions is compared to the ray-traced correlation function for $R=8$ arcminutes.
+The result is shown in Figure \ref{gg_corr_series}, where the series of model predicted correlation functions is compared to the ray-traced correlation function.
 As $R$ increases, the mean number of foreground galaxies contained in each lightcone grows quadratically from ${240\pm25}$ galaxies when $R=1$ arcminute to ${15,000\pm300}$ galaxies when $R=8$ arcminutes.
 Increasing the number of foreground objects, and thus increasing the mass and structure considered for shear and convergence predictions, systematically increased the predicted shear power on all scales.
-While the series of predicted correlation functions appears to be converging towards the ray-traced correlation function, (diminishing returns).
+While the series of predicted correlation functions appear to be converging towards the ray-traced correlation function, there is clearly diminishing shear power gains as $R$ increases.
 

### 2015-08-20 doc/suli-report-swe.tex
Slight change to abstract wording in the SULI report. #79

@@
 The lensed source ellipticities are characterized by the ellipticity-ellipticity and galaxy-mass correlation functions and compared to the same statistic for the intrinsic and ray-traced ellipticities.
-In the ellipticity-ellipticity correlation function, I find that the framework systematically under predicts the shear power by 117.0\% and fails to capture correlation from dark matter structure at scales larger than 1 arcminute.
-The model predicted galaxy-mass correlation function is in agreement with the ray-traced statistic from scales 0.2 to 0.7 arcminutes, but systematically underpredicts shear power at scales larger than 0.7 arcminutes by 23.2\%.
+In the ellipticity-ellipticity correlation function, I find that the framework systematically under predicts the shear power on average by 117.0\% and fails to capture correlation from dark matter structure at scales larger than 1 arcminute.
+The model predicted galaxy-mass correlation function is in agreement with the ray-traced statistic from scales 0.2 to 0.7 arcminutes, but systematically underpredicts shear power at scales larger than 0.7 arcminutes on average by 23.2\%.
 Physical and computational shortcomings of the framework are discussed, as well as potential improvements for upcoming work.

### 2015-08-20 doc/suli-report-swe.tex
Added a (temporary) CPU per lightcone bar graph in the results section. #81
Rewrote the Computational Performance section of the SULI report to account for the new CPU figure. #81

@@
 However, many small improvements to the coding infastructure of \texttt{Pangloss} were made to speed up the prediction.
-The average CPU time for a lensing prediction per lightcone after various changes is plotted in Figure \ref{cpu_plot}.
+The average CPU time for a lensing prediction per lightcone for four separate runs after various (and cumulative) changes is plotted in Figure \ref{cpu_plot}.
+Run 1 corresponds to the original \texttt{Pangloss} framework code, run 2 only wrote the needed quantities for this analysis to the catalog \texttt{astropy} tables, run 3 changed the redshift grid binning to be done once for all halos in the drilling rather than for every individual halo in lensing, and run 4 optimized various lensing calculations with matrices whenever possible.
+Cumulatively, these changes alone accounted for a 70\% decrease in mean CPU time per lightcone and halved the initial variation.
 
-%************************
-(CPU time per lightcone plot)\\
-%************************
-(Include RAM in plot??)
+%% Mean lightcone CPU time
+\begin{figure}
+    \centering
+    \includegraphics[width=0.475\textwidth]{figs-swe/profile_bar.png}
+    \captionsetup{justification=raggedright,singlelinecheck=false}
+    \caption{The mean CPU runtime per lightcone for various runs with different (and cumulative) code optimizations described in the text.
+The cumulative changes account for a 70\% decrease in the mean CPU time and a halving of the variation.}
+    \label{cpu_plot}
+\end{figure}
 

### 2015-08-20 doc/suli-report-swe.tex
Updated appendix A with the visualizing correlation plots. #81

@@
 \usepackage{mathtools}
-\usepackage{caption}
+\usepackage[format=plain]{caption}
 \usepackage{subcaption}
@@
 \author{Spencer Everett}
- \affiliation{Department of Physics, DePaul University.}%Lines break automatically or can be forced with \\
+ \affiliation{Department of Physics, DePaul University,\\SLAC National Laboratory}
+ %\affiliation{SLAC National Laboratory}
  \email{spencerweverett@gmail.com}
@@
 The path of light from distant `background' galaxies is bent when traveling through regions of space containing large amounts of `foreground' mass.
-The process is described by Einstein's general theory of relativity, but simply put -- the more mass, the more light bends.
 Light from different origins in a background galaxy are subject to different bending which results in a distortion of the galaxy image.
@@
 The total convergence and shear at the center of the lightcone is simply the sum of the convergence and shear contributions of each halo contained in the lightcone.
-The \texttt{Pangloss} predicted lensed background ellipticity is then calculated using Equation \eqref{lensing}.
+The \texttt{Pangloss} predicted lensed source ellipticity is then calculated using Equation \eqref{lensing}.
 
@@
 The ellipticity-ellipticity correlation function measures how correlated the ellipticities of pairs of galaxies are as a function of separation distance, while the galaxy-mass correlation function measures the correlation of lensed ellipticities around foreground halos as a function of separation distance.
+For readers that are unfamiliar with correlation functions in the context of cosmology or want a visual aid, see appendix A.
 Both correlation functions are used in this work to measure how well the \texttt{Pangloss} framework models weak lensing by dark matter structures using the publicly available \texttt{TreeCorr} module written by Mike Jarvis\footnote{https://github.com/rmjarvis/TreeCorr}.
-Note that the ellipticity-ellipticity correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition and the more common Schneider definition \cite{schneider}, see the appendix.
-%For readers that are unfamiliar with correlation functions in the context of cosmology or want a visual aid, see Appendix A.
+Note that the ellipticity-ellipticity correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition and the more common Schneider definition \cite{schneider}, see appendix B.
 
@@
 Additionally, while the shapes of the correlation functions for both sets of lensed ellipticities aggree well until 1 arcminute, there is a clear systematic underprediction of shear power by the halo model on all scales.
-On average, the shear power is underpredicted by 117.0 percent.
+On average, the shear power is underpredicted by 117.0\%.
 
@@
 
-\subsection*{Galaxy-mass Correlation Function}
+\subsection*{Galaxy-Mass Correlation Function}
 
@@
 
-\subsection*{Issues with the \texttt{Pangloss} Framework}
+\subsection*{Issues with the Pangloss Framework}
 
@@
 
-\subsection*{Scaling Up \texttt{Pangloss}}
+\subsection*{Scaling Up Pangloss}
 
@@
 
-The first statistic used in this work is the ellipticity-ellipticity ($\varepsilon-\varepsilon$) correlation function, which has two tangential components $\xi_\pm$ and a cross component $\xi_\times$.
+The main statistic used in this work is the ellipticity-ellipticity ($\varepsilon-\varepsilon$) correlation function, which has two tangential components $\xi_\pm$ and a cross component $\xi_\times$.
 The components most interesting for gravitational lensing are the positive tangential component $\xi_+$, expected to be positive for lensed galaxies, and the cross component $\xi_\times$, which is expected to be zero.
 To get an intuition for what these quantities measure, first consider the correlation values for individual pairs of galaxies as shown in Figure \ref{corr_colormaps}.
-In each plot, the value of the correlation between two galaxy orientations is plotted as a colormap with a few sampled orientations plotted on top of the graph.
+In each plot, the value of the correlation between two galaxies as a function of their orientation is plotted as a colormap with a few sampled galaxy orientations superimposed.
+For $\xi_+$, the correlation is positive for parallel galaxies, negative for perpendicular galaxies, and zero for galaxies offset by 45$^\circ$.
+In contrast, $\xi_\times$ is zero for all parallel and perpendicular orientations while nonzero for most 45$^\circ$ offsets.
 
-\begin{itemize}
-\item Use as a brief introduction to the shear-shear and galaxy-mass correlation function as used in this work
-    \begin{itemize}
-    \item reference other (much more detailed) material for readers to find
-    \end{itemize}
-\item Include correlation value colormaps for $\xi_+$, $\xi_-$, and $\xi_\times$ along with discussion of correlation pattern
-\item Include color-coded correlation visuals along with setup
-    \begin{itemize}
-    \item Galaxies around lens before lensing - correlation values scatter plot with no signal
-    \item Galaxies around lens after lensing - correlation values scatter plot with signal
-    \end{itemize}
-\item B-modes and E-modes plot??
-\end{itemize}
+%% Correlation Colormaps
+\begin{figure*}
+    \centering
+    \begin{subfigure}[H]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/xip_colormap.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{The positive tangential component of the $\varepsilon-\varepsilon$ correlation as a function of galaxy orientation plotted as a colormap.
+The correlation component is positive for parallel galaxies, negative for perpendicular galaxies, and zero for galaxies offset by 45$^\circ$.}
+        \label{xip_colormap}
+    \end{subfigure}
+    ~
+    %% Einstein Ring Figure
+    \begin{subfigure}[H]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/xix_colormap.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{The cross component of the $\varepsilon-\varepsilon$ correlation as a function of galaxy orientation plotted as a colormap.
+While the pattern is more complicated than that of the tangential component, note that the correlation value is zero for all preferred orientations after lensing.}
+        \label{xix_colormap}
+    \end{subfigure}
+    \caption{Correlation pair colormaps for $\xi_+$ and $\xi_\times$.}
+    \label{corr_colormaps}
+\end{figure*}
+
+Now consider
+
+%% Correlation Colormaps
+\begin{figure}[b!]
+    \centering
+    \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/corr_visualization_unlensed.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{A set of background sources around a foreground lens (blue dot).
+The size and orientation of each stick represents the intrinsic source ellipticity and is colored by the distance away from the lens.}
+        \label{color_corr_unlensed}
+    \end{subfigure}
+    ~
+    \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/corr_dist_unlensed.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{The distribution of correlation pairs from the source ellipticities in Figure \ref{color_corr_unlensed}.
+If the pair of galaxies are in the same color bin, then the correlation scatter point is colored in the same scheme.
+Otherwise, the correlation is not plotted.}
+        \label{corr_dist_unlensed}
+    \end{subfigure}
+
+    \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/corr_visualization_lensed.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{The same set of background sources in Figure \ref{color_corr_unlensed} after (magnified for effect) lensing by the foreground mass.
+Regardless of initial orientation, the source galaxies have all at least partially aligned tangentially around the center lensing mass.}
+        \label{color_corr_lensed}
+    \end{subfigure}
+    ~
+    \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/corr_dist_lensed.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{The distribution of correlation pairs from the source ellipticities in Figure \ref{color_corr_lensed}.
+If the pair of galaxies are in the same color bin, then the correlation scatter point is colored in the same scheme.
+Otherwise, the correlation is not plotted.}
+        \label{corr_dist_lensed}
+    \end{subfigure}
+    \caption{Correlation visualizaiton for unlensed galaxies.}
+    \label{corr_colormaps}
+\end{figure}
+
+The $\varepsilon-\varepsilon$ correlation function is simply the average of all the correlations of each possible galaxy pair.
+Before lensing, galaxies should have uniformly distributed orientations as the universe is isotropic.
+Thus when averaged, both $\left<\xi_+\right>$ and $\left<\xi_\times\right>$ should be zero.
+However, as gravitational lensing tends to shear source images tangentially around a foreground mass,
 
@@
 
-Maybe do importance and/or lookup table after paper is submitted? Talk about in discussion?
+%% Appendix A
+\begin{itemize}
+\item Use as a brief introduction to the shear-shear and galaxy-mass correlation function as used in this work
+    \begin{itemize}
+    \item reference other (much more detailed) material for readers to find
+    \end{itemize}
+\item Include correlation value colormaps for $\xi_+$, $\xi_-$, and $\xi_\times$ along with discussion of correlation pattern
+\item Include color-coded correlation visuals along with setup
+    \begin{itemize}
+    \item Galaxies around lens before lensing - correlation values scatter plot with no signal
+    \item Galaxies around lens after lensing - correlation values scatter plot with signal
+    \end{itemize}
+\item B-modes and E-modes plot??
+\end{itemize}

### 2015-08-20 doc/suli-report-swe.tex
Revised the abstract, converted 0.09 deg^2 to 324 arcmin^2 throughout SULI report. #79, #81.

@@
 In this paper, I have implemented a framework to reconstruct all of the mass along lines of sight using a  best-case dark matter halo model in which the halo mass is known.
-This framework is then used to make predictions of the weak lensing of 3,240 generated source galaxies through a 0.09 deg$^2$ field of the Millennium Simulation.
+This framework is then used to make predictions of the weak lensing of 3,240 generated source galaxies through a 324 arcmin$^2$ field of the Millennium Simulation.
 The lensed source ellipticities are characterized by the ellipticity-ellipticity and galaxy-mass correlation functions and compared to the same statistic for the intrinsic and ray-traced ellipticities.
-In the ellipticity-ellipticity correlation function, I find that the framework systematically under predicts the shear power on average by 117.0\% and fails to capture correlation from dark matter structure at scales larger than 1 arcminute.
-The model predicted galaxy-mass correlation function is in agreement with the ray-traced statistic from scales 0.2 to 0.7 arcminutes, but systematically underpredicts shear power at scales larger than 0.7 arcminutes on average by 23.2\%.
+In the ellipticity-ellipticity correlation function, I find that the framework systematically under predicts the shear power on average by a factor of 2.2 and fails to capture correlation from dark matter structure at scales larger than 1 arcminute.
+The model predicted galaxy-mass correlation function is in agreement with the ray-traced statistic from scales 0.2 to 0.7 arcminutes, but systematically underpredicts shear power at scales larger than 0.7 arcminutes on average by a factor of 1.2.
 Physical and computational shortcomings of the framework are discussed, as well as potential improvements for upcoming work.
@@
 A brief introduction into the theory of galaxy ellipticities, the effects of strong and weak gravitational lensing, and dark matter halos is discussed in Section II.
-The implementation of a halo model on the Millennium Simulation and ellipticity predictions is described in Section III, and the results of the model on 3,240 galaxies on a field size of 0.09 deg$^2$ as well as a comparison of the predicted lensed ellipticities to the true ellipticities is given in Section IV.
+The implementation of a halo model on the Millennium Simulation and ellipticity predictions is described in Section III, and the results of the model on 3,240 galaxies on a field size of 324 arcmin$^2$ as well as a comparison of the predicted lensed ellipticities to the true ellipticities is given in Section IV.
 Section V discusses limitations of the used \texttt{Pangloss} framework along with potential physical and computational improvements that can be made for upcoming work before concluding remarks in Section VI.
@@
 \subsection*{Generating Background Galaxies}
-With a catalog of foreground galaxies chosen, a set of 3,240 background galaxies over a field of 0.09 deg$^2$ was generated, with density 10 per arcminute$^2$.
+With a catalog of foreground galaxies chosen, a set of 3,240 background galaxies over a field of 324 arcmin$^2$ was generated, with density 10 per arcminute$^2$.
 As the The intrinsic orientation of each galaxy was sampled from a uniform distribution as, without lensing, there should be no preferred orientation due to the assumption of an isotropic universe.
@@
 
-Using the presented methodology, 3,240 background galaxies in a 0.09 deg$^2$ subset of the (0,0,0,0) Millennium Simulation foreground catalog were generated and lensed by both the ray-traced shear and convergence maps as well as the \texttt{Pangloss} framework.
+Using the presented methodology, 3,240 background galaxies in a 324 arcmin$^2$ subset of the (0,0,0,0) Millennium Simulation foreground catalog were generated and lensed by both the ray-traced shear and convergence maps as well as the \texttt{Pangloss} framework.
 With a lightcone radius of 2 arcminutes, the lightcones contained an average of ${950\pm70}$ foreground halos.
@@
 
-While the current \texttt{Pangloss} framework can handle the lensing predictions of 3,240 in a 0.09 deg$^2$ field comfortably on a single processor, the goal is to scale up the framework to make predictions for background sources of the same number density in a 100 deg$^2$ field; this will require 3.6 million lightcones, each containing up to 1,000 foreground halos.
+While the current \texttt{Pangloss} framework can handle the lensing predictions of 3,240 in a 324 arcmin$^2$ field comfortably on a single processor, the goal is to scale up the framework to make predictions for background sources of the same number density in a 100 deg$^2$ field; this will require 3.6 million lightcones, each containing up to 1,000 foreground halos.
 Luckily, the prediction is trivially parallelizable as the shear and convergence calculation of each lightcone is independent of all other lightcones.
@@
 
-In this paper, a simple halo model was used to reconstruct all the mass along lines of sight in the Millennium Simulation to make predictions of how foreground mass weakly lensed the ellipticities of 3,240 generated background sources accross a field of 0.09 deg$^2$.
+In this paper, a simple halo model was used to reconstruct all the mass along lines of sight in the Millennium Simulation to make predictions of how foreground mass weakly lensed the ellipticities of 3,240 generated background sources accross a field of 324 arcmin$^2$.
 The lensed ellipticities were characterized globally using the ellipticity-ellipticity and galaxy-mass correlation functions and then compared with the same statistics from ray-traced data.

### 2015-08-20 doc/suli-report-swe.tex
Wrote appendix A for the SULI report. #81

@@
 The lensed source ellipticities are characterized by the ellipticity-ellipticity and galaxy-mass correlation functions and compared to the same statistic for the intrinsic and ray-traced ellipticities.
-In the ellipticity-ellipticity correlation function, I find that the framework systematically under predicts the shear power on average by a factor of 2.2 and fails to capture correlation from dark matter structure at scales larger than 1 arcminute.
-The model predicted galaxy-mass correlation function is in agreement with the ray-traced statistic from scales 0.2 to 0.7 arcminutes, but systematically underpredicts shear power at scales larger than 0.7 arcminutes on average by a factor of 1.2.
+In the ellipticity-ellipticity correlation function, I find that the framework systematically under predicts the shear power by an average factor of 2.2 and fails to capture correlation from dark matter structure at scales larger than 1 arcminute.
+The model predicted galaxy-mass correlation function is in agreement with the ray-traced statistic from scales 0.2 to 0.7 arcminutes, but systematically underpredicts shear power at scales larger than 0.7 arcminutes by an average factor of 1.2.
+Optimization of the framework code has reduced the mean CPU time per lensing prediction by 70\% to $24\pm5$ ms.
 Physical and computational shortcomings of the framework are discussed, as well as potential improvements for upcoming work.
@@
 The remaining mass takes the form of an exotic dark matter that does not absorb or emit light, rendering it invisible to our telescopes.
-While this claim sounds bizarre, there has been an abundance of indirect evidence in recent decades for the existence of dark matter including the flattening of galaxy rotation curves \cite{rotation_curve}, velocity dispersions of galaxies \cite{zwicky} and acoustic peaks in the cosmic microwave background \cite{planck_2015}.
+While this claim sounds bizarre, there has been an abundance of indirect evidence in recent decades for the existence of dark matter including the flattening of galaxy rotation curves \cite{rotation_curve}, velocity dispersions of galaxies \cite{zwicky}, and acoustic peaks in the cosmic microwave background \cite{planck_2015}.
 
@@
 The path of light from distant `background' galaxies is bent when traveling through regions of space containing large amounts of `foreground' mass.
-Light from different origins in a background galaxy are subject to different bending which results in a distortion of the galaxy image.
+Light from different origins in a source galaxy is subject to different bending which results in a distortion of the galaxy image.
 As the foreground mass is known to be largely dark matter, gravitational lensing supplies a direct constraint on the mass of dark matter in that region.
@@
 A brief introduction into the theory of galaxy ellipticities, the effects of strong and weak gravitational lensing, and dark matter halos is discussed in Section II.
-The implementation of a halo model on the Millennium Simulation and ellipticity predictions is described in Section III, and the results of the model on 3,240 galaxies on a field size of 324 arcmin$^2$ as well as a comparison of the predicted lensed ellipticities to the true ellipticities is given in Section IV.
+The implementation of a halo model on the Millennium Simulation is described in Section III, and the results of the model on 3,240 galaxies on a field size of 324 arcmin$^2$ as well as a comparison of the predicted lensed ellipticities to ray-traced ellipticities is given in Section IV.
 Section V discusses limitations of the used \texttt{Pangloss} framework along with potential physical and computational improvements that can be made for upcoming work before concluding remarks in Section VI.
@@
 
-However, usually the quantity of interest in lensing calculations is the \textit{reduced} shear, defined by
+However, usually the quantity of interest in lensing calculations is the \textit{reduced} shear, defined as
 \begin{equation}\label{reduced_shear}
@@
 Each foreground object has an attached dark matter halo and physical distance to the line of sight (dashed line).
-The shear and convergence along the line of sight contributed by each halo is calculated, and the predicted ellipticity is calculated using the sum of these contributions.}
+The shear and convergence along the line of sight contributed by each halo is calculated using \cite{lensing_calc}, and the predicted ellipticity is determined using the sum of these contributions.}
     \label{pangloss_cartoon}
@@
 From the work of Hilbert et al.
-\cite{ray_tracing}, high resolution maps of the shear and convergence from the perspective of a single reference point calculated by ray-tracing are publicly available.
-From these maps, the actual lensing of background galaxies when traveling through the foreground mass of the Millennium Simulation towards the reference point can be calculated using Equation \eqref{lensing}.
+\cite{ray_tracing}, high resolution maps of the ray-traced shear and convergence are publicly available.
+From these maps, the actual lensing of background galaxies when traveling through the foreground mass of the Millennium Simulation can be calculated using Equation \eqref{lensing}.
 
@@
 Both the ray-traced, plotted in green, and halo model, plotted in purple, ellipticities show positive correlation on small scales up to a separation of 1 arcminute.
-However, the ray-traced correlation is positive on all calculated scales while the halo model does not predict any significant corrlelation at separations above 1arcminute.
+However, the ray-traced correlation is positive on all calculated scales while the halo model does not predict any significant corrlelation at separations above 1 arcminute.
 Additionally, while the shapes of the correlation functions for both sets of lensed ellipticities aggree well until 1 arcminute, there is a clear systematic underprediction of shear power by the halo model on all scales.
-On average, the shear power is underpredicted by 117.0\%.
-
+On average, the shear power is underpredicted by 117\%.
 %% Ellipticity-Ellipticity Correlation
@@
 While the correlation of the intrinsic ellitpicities before lensing (blue) shows no correlation, the correlation of the ray-traced ellipticities (green) and halo model predicted ellipticities (purple) both show significant positive correlation on scales up to 1 arcminute.
-The halo model predicts no correlation above this scale, while the ray-tracing shows positive correlation on all scales.}
+The halo model predicts a small negative correlation above this scale, while the ray-tracing shows positive correlation on all scales.}
         %The correlation of the intrinsic ellitpicities before lensing is plotted in blue, and shows no correlation.
@@
 
-Using the same catalog of background sources, this statistic was recalculated for the ray-traced and halo model lensed ellipticities for various lightcone radii ranging from $R=1$ arcminute to $R=8$ arcminutes.
+Using the same catalog of background sources, this statistic was recalculated for the halo model ellipticities for various lightcone radii ranging from $R=1$ arcminute to $R=8$ arcminutes.
 The result is shown in Figure \ref{gg_corr_series}, where the series of model predicted correlation functions is compared to the ray-traced correlation function.
@@
 The lensed ellipticities from the ray-tracing and halo model both have positive correlation on all calculated scales and are in agreement on scales from 0.2 arcminutes to 0.7 arcminutes.
-However, the halo model is still systematically underpredicting the shear power on scales above 0.7 arcminutes, although now only by an average of 23.2 \%.
+However, the halo model is still systematically underpredicting the shear power on scales above 0.7 arcminutes, although now only by an average of 23\%.
 A new feature is the large overprediction of shear power on separation scales smaller than 0.2 arcminutes.
@@
 
-The progression of model predicted ellipticity-ellipticity correlation functions at larger radii converging to the ray-traced correlation supports the analysis given above, as the prediction was progressively better with larger number of foreground halos and thus more mass and structure.
+The progression of model predicted ellipticity-ellipticity correlation functions at larger radii converging to the ray-traced correlation in Figure \ref{gg_corr_series} supports the analysis given above, as the prediction was progressively better with larger number of foreground halos and thus more mass and structure.
 However, the number of foreground objects scales quadratically with the lightcone radius making it prohibitively expensive above $R=8$ arcminutes.
@@
 This suggests the creation of a metric to predict the `relevance' of each halo to the lensing contribution.
-In this way, the framework could be restructured to only use the most relevant halos in the computationally expensive lensing prediction, while simultaneously allowing for larger lightcones with more relevant halos.
+In this way, the framework could be restructured to only use the most important halos in the computationally expensive lensing prediction, while simultaneously allowing for larger lightcones with more relevant halos.
 This could aid in the aforementioned shear power prediction issues.
@@
 This makes GPUs an attractive candidate for future work, as it would only take 360 GPUs with 10,000 threads each to carry out the prediction.
-Additionally, the (??) MB of RAM per lightcone is sufficiently small to fit 10,000 lightcones on a GPU.
+Additionally, the 50 MB of RAM per lightcone is sufficiently small to fit 10,000 lightcones on a GPU.
 
@@
 At first encounter, the use of correlation functions to analyze data can be difficult to comprehend, let alone visualize.
-While by no means a thorough or mathematical analysis (see (cite) for a general introduction to correlation functions, and (cite) for their many applications in cosmology), I have created some explanatory plots to aid in visualizing how weakly lensed ellipticities can be measured with correlation functions and put the main results of this paper in more context.
+While by no means a thorough or mathematical analysis (see (cite) for a general introduction to correlation functions, and (cite) for their many applications in cosmology), I have created some explanatory plots to aid in visualizing how weakly lensed ellipticities can be measured with correlation functions and place the main results of this paper in more context.
 
@@
 To get an intuition for what these quantities measure, first consider the correlation values for individual pairs of galaxies as shown in Figure \ref{corr_colormaps}.
-In each plot, the value of the correlation between two galaxies as a function of their orientation is plotted as a colormap with a few sampled galaxy orientations superimposed.
+In each plot, the value of the correlation between two galaxies as a function of their relative orientation is plotted as a colormap with a few sampled galaxy orientations superimposed.
 For $\xi_+$, the correlation is positive for parallel galaxies, negative for perpendicular galaxies, and zero for galaxies offset by 45$^\circ$.
 In contrast, $\xi_\times$ is zero for all parallel and perpendicular orientations while nonzero for most 45$^\circ$ offsets.
+As gravitational lensing shears source images tangentially around a foreground mass, the tangential component is a measure of how similarly two galaxies are lensed, while the cross component is an estimate of the bias (as it should be zero).
 
@@
 
-Now consider
+Now consider a region of space around a foreground lens populated with many background sources \textit{before lensing}, as in Figure \ref{color_corr_unlensed}.
+In this plot, source ellipticities are plotted as sticks and colored by their distance from the lens.
+Calculating the $\xi_+$ component correlation pairs for all galaxies in the same color bin and making a scatter plot as a function of the separation distance between the source pairs, we find the distibution in Figure \ref{corr_dist_unlensed}.
+The $\xi_+$ component of the $\varepsilon-\varepsilon$ correlation function is simply the average of this scatter plot binned in separation distances along the $x$-axis.
+As the scatter is randomly distributed around zero, the $\varepsilon-\varepsilon$ correlation function for unlensed sources should be zero on all scales.
 
-%% Correlation Colormaps
-\begin{figure}[b!]
+%% Color-Coded Correlation Unlensed
+\begin{figure}[H!]
     \centering
@@
     \end{subfigure}
+    \caption{Correlation visualizaiton for unlensed galaxies.}
+    \label{colored_corr}
+\end{figure}
 
+The same plots for the source galaxies \textit{after lensing} are shown in Figure \ref{colored_corr_lensed}.
+The source ellipticities have clearly aligned tangentially around the foreground lens in Figure \ref{color_corr_lensed}, and distinct patterns have appeared in the correlation pair distribution for each color bin in Figure \ref{corr_dist_lensed}.
+First consider a single color bin, such as the yellow.
+Galaxies next to one another are lensed in approximately the same way and thus nearly parallel, leading to a positive correlation at small separation distances in Figure \ref{corr_dist_lensed}.
+Moving a quarter of the way around the yellow circle of galaxies, the lensed ellipticities become perpendicular and have negative correlation.
+This can be seen as the dip in correlation at `middle' separation distances in \ref{corr_dist_lensed}.
+Finally for galaxies on opposite sides of the lens, their relative orientation is again parallel and the correlation has returned to positive values.
+This spike in correlation is clearly visible in the distribution and is shifted to the right for colors further from the lens as the raidus of the color bin increases.
+Averaging all scatter points in discrete separation distance bins, the $\varepsilon-\varepsilon$ correlation function will no longer be zero and a detectable signal will remain.
+
+%% Color-Coded Correlation Lensed
+\begin{figure}[H!]
+    \centering
     \begin{subfigure}{0.45\textwidth}
@@
     \end{subfigure}
-    \caption{Correlation visualizaiton for unlensed galaxies.}
-    \label{corr_colormaps}
+    \caption{Correlation visualizaiton for lensed galaxies.}
+    \label{colored_corr_lensed}
 \end{figure}
 
-The $\varepsilon-\varepsilon$ correlation function is simply the average of all the correlations of each possible galaxy pair.
-Before lensing, galaxies should have uniformly distributed orientations as the universe is isotropic.
-Thus when averaged, both $\left<\xi_+\right>$ and $\left<\xi_\times\right>$ should be zero.
-However, as gravitational lensing tends to shear source images tangentially around a foreground mass,
+\end{document}
 

### 2015-08-20 doc/suli-report-swe.tex
Fixed spelling mistakes throughout SULI report. #81

@@
 \usepackage{mathtools}
+\usepackage{float}
 \usepackage[format=plain]{caption}
@@
         \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{An image of the luminous red galaxy LRG 3-757 along with a strongy lensed background galaxy, called the `Cosmic Horseshoe' \cite{einstein_ring}.}
+        \caption{An image of the luminous red galaxy LRG 3-757 along with a strongly lensed background galaxy, called the `Cosmic Horseshoe' \cite{einstein_ring}.}
         \label{einstein_ring}
@@
 
-While the exact relation between the distribution of galaxies and dark matter is not known, simulations have shown that galaxies tend to form in overdense regions of dark matter.
+While the exact relation between the distribution of galaxies and dark matter is not known, simulations have shown that galaxies tend to form in over-dense regions of dark matter.
 This means that galaxies \textit{should} trace out the larger underlying dark matter structures.
@@
 
-To constrain the mass of foreground dark matter using weak gravitational lensing, first a model of the relationship between foreground galaxies and the foreground dark matter must be established and robustly tested to see if, statistically, it makes the same lensing predictions of background sources as the true undering dark matter structure.
+To constrain the mass of foreground dark matter using weak gravitational lensing, first a model of the relationship between foreground galaxies and the foreground dark matter must be established and robustly tested to see if, statistically, it makes the same lensing predictions of background sources as the true underlying dark matter structure.
 To do this, I built upon the publicly available \texttt{Pangloss} framework\footnote{https://github.com/drphilmarshall/Pangloss} used in Collett et al.
@@
 This assumption can be relaxed by sampling a dark matter halo mass from an assumed stellar mass - halo mass relation.
-The fourth assumpition is also unrealistic as most galaxies in sky surveys only have a less-reliable photometric redshift due to time constraints, but this again allows for a best-case estimate.
+The fourth assumption is also unrealistic as most galaxies in sky surveys only have a less-reliable photometric redshift due to time constraints, but this again allows for a best-case estimate.
 This assumption could be relaxed by instead using photometric redshifts, adding random noise, and repeating the upcoming analysis on many realizations of the photometric redshifts.
@@
 Both the ray-traced, plotted in green, and halo model, plotted in purple, ellipticities show positive correlation on small scales up to a separation of 1 arcminute.
-However, the ray-traced correlation is positive on all calculated scales while the halo model does not predict any significant corrlelation at separations above 1 arcminute.
-Additionally, while the shapes of the correlation functions for both sets of lensed ellipticities aggree well until 1 arcminute, there is a clear systematic underprediction of shear power by the halo model on all scales.
+However, the ray-traced correlation is positive on all calculated scales while the halo model does not predict any significant correlation at separations above 1 arcminute.
+Additionally, while the shapes of the correlation functions for both sets of lensed ellipticities agree well until 1 arcminute, there is a clear systematic underprediction of shear power by the halo model on all scales.
 On average, the shear power is underpredicted by 117\%.
 %% Ellipticity-Ellipticity Correlation
-\begin{figure}
+\begin{figure}[H]
     \centering
-    \begin{subfigure}[h]{0.475\textwidth}
+    \begin{subfigure}{0.475\textwidth}
         \includegraphics[width=\textwidth]{figs-swe/gg_corr.png}
@@
         \caption{The ellipticity-ellipticity correlation function for 3,240 sources at separation distances from 0.1 arcminutes to 2 arcminutes and a lightcone radius of $R=2$ arcminutes.
-While the correlation of the intrinsic ellitpicities before lensing (blue) shows no correlation, the correlation of the ray-traced ellipticities (green) and halo model predicted ellipticities (purple) both show significant positive correlation on scales up to 1 arcminute.
+While the correlation of the intrinsic ellipticities before lensing (blue) shows no correlation, the correlation of the ray-traced ellipticities (green) and halo model predicted ellipticities (purple) both show significant positive correlation on scales up to 1 arcminute.
 The halo model predicts a small negative correlation above this scale, while the ray-tracing shows positive correlation on all scales.}
-        %The correlation of the intrinsic ellitpicities before lensing is plotted in blue, and shows no correlation.
+        %The correlation of the intrinsic ellipticities before lensing is plotted in blue, and shows no correlation.
 The correlation of the true ray-traced ellipticities is plotted in green and shows significant positive correlation on all scales.
@@
     ~~
-    \begin{subfigure}[h]{0.475\textwidth}
+    \begin{subfigure}{0.475\textwidth}
         \includegraphics[width=\textwidth]{figs-swe/gg_corr_series.png}
         \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{The ellipticity-ellipticity correlation functions for a series of halo model frameworks with increasing lightcone radii from $R=1$ arminute to $R=8$ arcminutes, all plotted in purple with various line styles.
+        \caption{The ellipticity-ellipticity correlation functions for a series of halo model frameworks with increasing lightcone radii from $R=1$ arcminute to $R=8$ arcminutes, all plotted in purple with various line styles.
 These are compared to the same ray-traced correlation from Figure \ref{gg_corr}.}
@@
     \caption{The galaxy-mass correlation function of 3,240 sources at separation distances from 0.1 arcminutes to 2 arcminutes and a lightcone radius of $R=2$ arcminutes.
-There is no significant correlation of the intrinsic ellipticities (blue) as expected, and both the ray-traced corrleation (green) and halo model correlation (purple) are positive on all scales.
+There is no significant correlation of the intrinsic ellipticities (blue) as expected, and both the ray-traced correlation (green) and halo model correlation (purple) are positive on all scales.
 The green and purple curves are in agreement from 0.2 to 0.7 arcminutes, but have significant discrepancies on scales above and below this range.}
@@
 The mean CPU time required for the prediction per lightcone was ${80\pm10}$ ms for the first run.
-However, many small improvements to the coding infastructure of \texttt{Pangloss} were made to speed up the prediction.
+However, many small improvements to the coding infrastructure of \texttt{Pangloss} were made to speed up the prediction.
 The average CPU time for a lensing prediction per lightcone for four separate runs after various (and cumulative) changes is plotted in Figure \ref{cpu_plot}.
-Run 1 corresponds to the original \texttt{Pangloss} framework code, run 2 only wrote the needed quantities for this analysis to the catalog \texttt{astropy} tables, run 3 changed the redshift grid binning to be done once for all halos in the drilling rather than for every individual halo in lensing, and run 4 optimized various lensing calculations with matrices whenever possible.
+Run 1 corresponds to the original \texttt{Pangloss} framework code, run 2 only wrote the needed quantities for this analysis to the catalog \texttt{Astropy} tables, run 3 changed the redshift grid binning to be done once for all halos in the drilling rather than for every individual halo in lensing, and run 4 optimized various lensing calculations with matrices whenever possible.
 Cumulatively, these changes alone accounted for a 70\% decrease in mean CPU time per lightcone and halved the initial variation.
@@
 Both the ellipticity-ellipticity and galaxy-mass correlation functions show clear issues with using the halo model to predict the lensing of background sources with \texttt{Pangloss}, even in the best-case scenario of perfect knowledge of the halo masses and their spectroscopic redshifts.
-The systematic underprediction of shear power present in both correlaton functions is likely do to missing features in the model such as clusters, filaments, and voids.
+The systematic underprediction of shear power present in both correlation functions is likely do to missing features in the model such as clusters, filaments, and voids.
 
-While individual galaxies currently recieve halos, a cluster of galaxies will sit in an larger halo whose presence is not being considered as its position, mass, and extent are difficult to determine.
+While individual galaxies currently receive halos, a cluster of galaxies will sit in an larger halo whose presence is not being considered as its position, mass, and extent are difficult to determine.
 The absence of this mass undoubtedly effects shear predictions and ellipticity correlations on large scales.
@@
 Voids are also not currently considered, as the framework assumes the field has constant mass density equal to that of the average mass density of the universe and then adds halo masses on top of this density.
-This would make the average matter density accross the field \textit{larger} than the mean density of the unvierse, and could be counteracted by subtracting mass from regions in between foreground halos.
-Stellar masses could also be incorperated into the \texttt{Pangloss} prediction, but any effect would likely be dominated by the missing features described above.
+This would make the average matter density across the field \textit{larger} than the mean density of the universe, and could be counteracted by subtracting mass from regions in between foreground halos.
+Stellar masses could also be incorporated into the \texttt{Pangloss} prediction, but any effect would likely be dominated by the missing features described above.
 
@@
 
-In this paper, a simple halo model was used to reconstruct all the mass along lines of sight in the Millennium Simulation to make predictions of how foreground mass weakly lensed the ellipticities of 3,240 generated background sources accross a field of 324 arcmin$^2$.
+In this paper, a simple halo model was used to reconstruct all the mass along lines of sight in the Millennium Simulation to make predictions of how foreground mass weakly lensed the ellipticities of 3,240 generated background sources across a field of 324 arcmin$^2$.
 The lensed ellipticities were characterized globally using the ellipticity-ellipticity and galaxy-mass correlation functions and then compared with the same statistics from ray-traced data.
@@
 This work was greatly aided by numerous conversations with Risa Wechsler from Stanford University and Matt Becker from the Kavli Institute for Particle Astrophysics and Cosmology (KIPAC).
-Finally, I am incredly grateful to Phil Marshall for his unending support, patience, and guidance throughout this research.
+Finally, I am incredibly grateful to Phil Marshall for his unending support, patience, and guidance throughout this research.
 
@@
     ~
-    %% Einstein Ring Figure
     \begin{subfigure}[H]{0.45\textwidth}
@@
 In this plot, source ellipticities are plotted as sticks and colored by their distance from the lens.
-Calculating the $\xi_+$ component correlation pairs for all galaxies in the same color bin and making a scatter plot as a function of the separation distance between the source pairs, we find the distibution in Figure \ref{corr_dist_unlensed}.
+Calculating the $\xi_+$ component correlation pairs for all galaxies in the same color bin and making a scatter plot as a function of the separation distance between the source pairs, we find the distribution in Figure \ref{corr_dist_unlensed}.
 The $\xi_+$ component of the $\varepsilon-\varepsilon$ correlation function is simply the average of this scatter plot binned in separation distances along the $x$-axis.
-As the scatter is randomly distributed around zero, the $\varepsilon-\varepsilon$ correlation function for unlensed sources should be zero on all scales.
+As the scatter is randomly distributed around zero, the $\varepsilon-\varepsilon$ correlation function for un-lensed sources should be zero on all scales.
 
-%% Color-Coded Correlation Unlensed
-\begin{figure}[H!]
+%% Color-Coded Correlation Un-lensed
+\begin{figure}[H]
     \centering
@@
     \end{subfigure}
-    \caption{Correlation visualizaiton for unlensed galaxies.}
+    \caption{Correlation visualization for un-lensed galaxies.}
     \label{colored_corr}
@@
 Finally for galaxies on opposite sides of the lens, their relative orientation is again parallel and the correlation has returned to positive values.
-This spike in correlation is clearly visible in the distribution and is shifted to the right for colors further from the lens as the raidus of the color bin increases.
+This spike in correlation is clearly visible in the distribution and is shifted to the right for colors further from the lens as the radius of the color bin increases.
 Averaging all scatter points in discrete separation distance bins, the $\varepsilon-\varepsilon$ correlation function will no longer be zero and a detectable signal will remain.
@@
 %% Color-Coded Correlation Lensed
-\begin{figure}[H!]
+\begin{figure}[H]
     \centering
@@
     \end{subfigure}
-    \caption{Correlation visualizaiton for lensed galaxies.}
+    \caption{Correlation visualization for lensed galaxies.}
     \label{colored_corr_lensed}
@@
 \end{document}
+
+%% Currently, this appendix is not being used
 

### 2015-08-20 doc/suli-report-swe.tex
Cleaned up the SULI report appendix. #81

@@
 \usepackage{mathtools}
-\usepackage{float}
+%\usepackage{float}
 \usepackage[format=plain]{caption}
@@
 
+\raggedbottom
+
 \begin{document}
@@
 
-\title{SULI Report!}
+\title{SULI Report! (Working title)}
 %\thanks{A footnote to the article title}%
@@
 The ellipticity-ellipticity correlation function measures how correlated the ellipticities of pairs of galaxies are as a function of separation distance, while the galaxy-mass correlation function measures the correlation of lensed ellipticities around foreground halos as a function of separation distance.
-For readers that are unfamiliar with correlation functions in the context of cosmology or want a visual aid, see appendix A.
+For readers that are unfamiliar with correlation functions in the context of cosmology or want a visual aid, see the appendix.
 Both correlation functions are used in this work to measure how well the \texttt{Pangloss} framework models weak lensing by dark matter structures using the publicly available \texttt{TreeCorr} module written by Mike Jarvis\footnote{https://github.com/rmjarvis/TreeCorr}.
-Note that the ellipticity-ellipticity correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition and the more common Schneider definition \cite{schneider}, see appendix B.
+Note that the ellipticity-ellipticity correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition and the more common Schneider definition \cite{schneider}, see (???).
 
@@
 
-Using the presented methodology, 3,240 background galaxies in a 324 arcmin$^2$ subset of the (0,0,0,0) Millennium Simulation foreground catalog were generated and lensed by both the ray-traced shear and convergence maps as well as the \texttt{Pangloss} framework.
-With a lightcone radius of 2 arcminutes, the lightcones contained an average of ${950\pm70}$ foreground halos.
-Both sets of lensed ellipticities were characterized with correlation functions, as well as the intrinsic ellipticities of the sources before lensing.
-
-\subsection*{Ellipticity-Ellipticity Correlation Function}
-
-The first test of the halo model was with the ellipticity-ellipticity correlation function with a lightcone radius of 2 arcminutes which is given in Figure \ref{gg_corr}.
-The statistic measured the average correlation between pairs of ellipticities at separation distances between 0.1 and 2 arcminutes.
-The correlation function of the intrinsic ellipticities plotted in blue shows no significant deviation from zero as expected, as before lensing the galaxies had random orientations.
-Both the ray-traced, plotted in green, and halo model, plotted in purple, ellipticities show positive correlation on small scales up to a separation of 1 arcminute.
-However, the ray-traced correlation is positive on all calculated scales while the halo model does not predict any significant correlation at separations above 1 arcminute.
-Additionally, while the shapes of the correlation functions for both sets of lensed ellipticities agree well until 1 arcminute, there is a clear systematic underprediction of shear power by the halo model on all scales.
-On average, the shear power is underpredicted by 117\%.
 %% Ellipticity-Ellipticity Correlation
-\begin{figure}[H]
+\begin{figure}
     \centering
@@
 \end{figure}
+
+Using the presented methodology, 3,240 background galaxies in a 324 arcmin$^2$ subset of the (0,0,0,0) Millennium Simulation foreground catalog were generated and lensed by both the ray-traced shear and convergence maps as well as the \texttt{Pangloss} framework.
+With a lightcone radius of 2 arcminutes, the lightcones contained an average of ${950\pm70}$ foreground halos.
+Both sets of lensed ellipticities were characterized with correlation functions, as well as the intrinsic ellipticities of the sources before lensing.
+
+\subsection*{Ellipticity-Ellipticity Correlation Function}
+
+The first test of the halo model was with the ellipticity-ellipticity correlation function with a lightcone radius of 2 arcminutes which is given in Figure \ref{gg_corr}.
+The statistic measured the average correlation between pairs of ellipticities at separation distances between 0.1 and 2 arcminutes.
+The correlation function of the intrinsic ellipticities plotted in blue shows no significant deviation from zero as expected, as before lensing the galaxies had random orientations.
+Both the ray-traced, plotted in green, and halo model, plotted in purple, ellipticities show positive correlation on small scales up to a separation of 1 arcminute.
+However, the ray-traced correlation is positive on all calculated scales while the halo model does not predict any significant correlation at separations above 1 arcminute.
+Additionally, while the shapes of the correlation functions for both sets of lensed ellipticities agree well until 1 arcminute, there is a clear systematic underprediction of shear power by the halo model on all scales.
+On average, the shear power is underpredicted by 117\%.
 
@@
 
-I would like to thank the Department of Energy for funding this research and giving me the opportunity to conduct research on (cutting edge physics).
+I would like to thank the Department of Energy for funding this research and giving me this wonderful opportunity, as well as SLAC National Laboratory for hosting me.
 This work was greatly aided by numerous conversations with Risa Wechsler from Stanford University and Matt Becker from the Kavli Institute for Particle Astrophysics and Cosmology (KIPAC).
 Finally, I am incredibly grateful to Phil Marshall for his unending support, patience, and guidance throughout this research.
-
 This work was supported in part by the U.S.
@@
 
-\section{References}
-
-\bibliographystyle{unsrt}
-\bibliography{suli-report-swe}
-
-%\end{document}
-
 \section{Appendix}
 
-\subsection{Visualizing Correlation Functions}
+\subsection*{Visualizing Correlation Functions}
+
+%% Correlation Colormaps
+\begin{figure}[!b]
+    \centering
+    \begin{subfigure}{0.425\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/xip_colormap.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{The positive tangential component of the $\varepsilon-\varepsilon$ correlation as a function of galaxy orientation plotted as a colormap.
+The correlation component is positive for parallel galaxies, negative for perpendicular galaxies, and zero for galaxies offset by 45$^\circ$.}
+        \label{xip_colormap}
+    \end{subfigure}
+    ~
+    \begin{subfigure}{0.425\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/xix_colormap.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{The cross component of the $\varepsilon-\varepsilon$ correlation as a function of galaxy orientation plotted as a colormap.
+While the pattern is more complicated than that of the tangential component, note that the correlation value is zero for all preferred orientations after lensing.}
+        \label{xix_colormap}
+    \end{subfigure}
+    \caption{Correlation pair colormaps for $\xi_+$ and $\xi_\times$.}
+    \label{corr_colormaps}
+\end{figure}
 
 At first encounter, the use of correlation functions to analyze data can be difficult to comprehend, let alone visualize.
-While by no means a thorough or mathematical analysis (see (cite) for a general introduction to correlation functions, and (cite) for their many applications in cosmology), I have created some explanatory plots to aid in visualizing how weakly lensed ellipticities can be measured with correlation functions and place the main results of this paper in more context.
+While by no means a thorough or mathematical analysis (see \cite{correlation_functions} for a more formal introduction), I have created some explanatory plots to aid in visualizing how weakly lensed ellipticities can be measured with correlation functions and place the main results of this paper in more context.
 
@@
 
-%% Correlation Colormaps
-\begin{figure*}
-    \centering
-    \begin{subfigure}[H]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{figs-swe/xip_colormap.png}
-        \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{The positive tangential component of the $\varepsilon-\varepsilon$ correlation as a function of galaxy orientation plotted as a colormap.
-The correlation component is positive for parallel galaxies, negative for perpendicular galaxies, and zero for galaxies offset by 45$^\circ$.}
-        \label{xip_colormap}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[H]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{figs-swe/xix_colormap.png}
-        \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{The cross component of the $\varepsilon-\varepsilon$ correlation as a function of galaxy orientation plotted as a colormap.
-While the pattern is more complicated than that of the tangential component, note that the correlation value is zero for all preferred orientations after lensing.}
-        \label{xix_colormap}
-    \end{subfigure}
-    \caption{Correlation pair colormaps for $\xi_+$ and $\xi_\times$.}
-    \label{corr_colormaps}
-\end{figure*}
-
 Now consider a region of space around a foreground lens populated with many background sources \textit{before lensing}, as in Figure \ref{color_corr_unlensed}.
@@
 %% Color-Coded Correlation Un-lensed
-\begin{figure}[H]
+\begin{figure}
     \centering
@@
 %% Color-Coded Correlation Lensed
-\begin{figure}[H]
+\begin{figure}
     \centering
@@
 
+\section{References}
+
+\bibliographystyle{unsrt}
+\bibliography{suli-report-swe}
+
 \end{document}
@@
 
-\subsection{Deriving the Standard Correlation Function Definition from \texttt{TreeCorr}'s Definition}
+% \subsection{Deriving the Standard Correlation Function Definition from \texttt{TreeCorr}'s Definition}
 
-\begin{itemize}
-\item Introduction to difference between the common Schneider definition of lensing correlation functions and that used by Jarvis`s \texttt{TreeCorr} code
-\item Here we derive the connection between the two
-\item Definitions of each, along with references
-\end{itemize}
+% \begin{itemize}
+% \item Introduction to difference between the common Schneider definition of lensing correlation functions and that used by Jarvis`s \texttt{TreeCorr} code
+% \item Here we derive the connection between the two
+% \item Definitions of each, along with references
+% \end{itemize}
 
-From Jarvis \href{http://arxiv.org/pdf/astro-ph/0307393v2.pdf}{(Page 3)}:
-\begin{align}
-\xi_+&=\left<\gamma_i\gamma_j^*\right>=\texttt{xip}+i(\texttt{xip\_im})\label{s+}\\
-\xi_-&=\left<\gamma_i\gamma_je^{-4i\alpha}\right>=\texttt{xim}+i(\texttt{xim\_im})\label{s-}
-\end{align}
+% From Jarvis \href{http://arxiv.org/pdf/astro-ph/0307393v2.pdf}{(Page 3)}:
+% \begin{align}
+% \xi_+&=\left<\gamma_i\gamma_j^*\right>=\texttt{xip}+i(\texttt{xip\_im})\label{s+}\\
+% \xi_-&=\left<\gamma_i\gamma_je^{-4i\alpha}\right>=\texttt{xim}+i(\texttt{xim\_im})\label{s-}
+% \end{align}
 
-where $\alpha$ is the angle between the two objects $i,j$ and each $\gamma$ is given by $\gamma_n=|\gamma_n|e^{2i\theta_n}$ in polar form.\\
+% where $\alpha$ is the angle between the two objects $i,j$ and each $\gamma$ is given by $\gamma_n=|\gamma_n|e^{2i\theta_n}$ in polar form.\\
 
-From Schneider \href{http://arxiv.org/pdf/astro-ph/0509252v1.pdf}{(Page 92)}:
-\begin{align}
-\xi_\pm&=\left<\gamma_{i_t}\gamma_{j_t}\right>\pm\left<\gamma_{i_\times}\gamma_{j_\times}\right>\label{s+-}\\
-\xi_\times&=\left<\gamma_{i_t}\gamma_{j_\times}\right>\label{sx}
-\end{align}
+% From Schneider \href{http://arxiv.org/pdf/astro-ph/0509252v1.pdf}{(Page 92)}:
+% \begin{align}
+% \xi_\pm&=\left<\gamma_{i_t}\gamma_{j_t}\right>\pm\left<\gamma_{i_\times}\gamma_{j_\times}\right>\label{s+-}\\
+% \xi_\times&=\left<\gamma_{i_t}\gamma_{j_\times}\right>\label{sx}
+% \end{align}
 
-where $\gamma_{n_t}=-\operatorname{Re}\left(\gamma_n e^{-2i\alpha}\right)$ and $\gamma_{n_\times}=-\operatorname{Im}\left(\gamma_n e^{-2i\alpha}\right)$.\\
+% where $\gamma_{n_t}=-\operatorname{Re}\left(\gamma_n e^{-2i\alpha}\right)$ and $\gamma_{n_\times}=-\operatorname{Im}\left(\gamma_n e^{-2i\alpha}\right)$.\\
 
-\section*{Schneider's $\xi_+$ to Jarvis's \texttt{xip}}
+% \section*{Schneider's $\xi_+$ to Jarvis's \texttt{xip}}
 
-Starting with Schneider's definition, observe that
-\begin{align*}
-\xi_+&=\left<\gamma_{i_t}\gamma_{j_t}\right>+\left<\gamma_{i_\times}\gamma_{j_\times}\right>\\
-&=\left<\operatorname{Re}\left(\gamma_ie^{-2i\alpha}\right)\cdot\operatorname{Re}\left(\gamma_je^{-2i\alpha}\right)\right>+\left<\operatorname{Im}\left(\gamma_ie^{-2i\alpha}\right)\cdot\operatorname{Im}\left(\gamma_je^{-2i\alpha}\right)\right>\\
-&=\left<\operatorname{Re}\left(|\gamma_i|e^{2i(\theta_i-\alpha)}\right)\cdot\operatorname{Re}\left(|\gamma_j|e^{2i(\theta_j-\alpha)}\right)\right>+\left<\operatorname{Im}\left(|\gamma_i|e^{2i(\theta_i-\alpha)}\right)\cdot\operatorname{Im}\left(|\gamma_j|e^{2i(\theta_j-\alpha)}\right)\right>\\
-&=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\alpha)\right)\cos\left(2(\theta_j-\alpha)\right)\right>+\left<|\gamma_i|\cdot|\gamma_j|\sin\left(2(\theta_i-\alpha)\right)\sin\left(2(\theta_j-\alpha)\right)\right>.
-\end{align*}
+% Starting with Schneider's definition, observe that
+% \begin{align*}
+% \xi_+&=\left<\gamma_{i_t}\gamma_{j_t}\right>+\left<\gamma_{i_\times}\gamma_{j_\times}\right>\\
+% &=\left<\operatorname{Re}\left(\gamma_ie^{-2i\alpha}\right)\cdot\operatorname{Re}\left(\gamma_je^{-2i\alpha}\right)\right>+\left<\operatorname{Im}\left(\gamma_ie^{-2i\alpha}\right)\cdot\operatorname{Im}\left(\gamma_je^{-2i\alpha}\right)\right>\\
+% &=\left<\operatorname{Re}\left(|\gamma_i|e^{2i(\theta_i-\alpha)}\right)\cdot\operatorname{Re}\left(|\gamma_j|e^{2i(\theta_j-\alpha)}\right)\right>+\left<\operatorname{Im}\left(|\gamma_i|e^{2i(\theta_i-\alpha)}\right)\cdot\operatorname{Im}\left(|\gamma_j|e^{2i(\theta_j-\alpha)}\right)\right>\\
+% &=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\alpha)\right)\cos\left(2(\theta_j-\alpha)\right)\right>+\left<|\gamma_i|\cdot|\gamma_j|\sin\left(2(\theta_i-\alpha)\right)\sin\left(2(\theta_j-\alpha)\right)\right>.
+% \end{align*}
 
-Using the trig identities
-\begin{align}
-\cos(u)\cos(v)&=\frac{1}{2}\left[\cos(u-v)+\cos(u+v)\right],\\
-\sin(u)\sin(v)&=\frac{1}{2}\left[\cos(u-v)-\cos(u+v)\right],
-\end{align}
+% Using the trig identities
+% \begin{align}
+% \cos(u)\cos(v)&=\frac{1}{2}\left[\cos(u-v)+\cos(u+v)\right],\\
+% \sin(u)\sin(v)&=\frac{1}{2}\left[\cos(u-v)-\cos(u+v)\right],
+% \end{align}
 
-and the linearity of the expectation operator, it is straightforward to show that
-%\begin{align*}
-%\xi_+&=\left<|\gamma_i|\cdot|\gamma_j|\right>\cdot\left(\left<\frac{1}{2}\left[\cos\left(2(\theta_i-\theta_j)\right)+\cos\left(2(\theta_i+\theta_j-2\alpha)\right)\right]\right>+\left<\frac{1}{2}\left[\cos\left(2(\theta_i-\theta_j)\right)-\cos\left(2(\theta_i+\theta_j-2\alpha)\right)\right]\right>\right)\\
-%&=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\theta_j)\right)\right>.
-%\end{align*}
-$$\xi_+=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\theta_j)\right)\right>.$$
+% and the linearity of the expectation operator, it is straightforward to show that
+% %\begin{align*}
+% %\xi_+&=\left<|\gamma_i|\cdot|\gamma_j|\right>\cdot\left(\left<\frac{1}{2}\left[\cos\left(2(\theta_i-\theta_j)\right)+\cos\left(2(\theta_i+\theta_j-2\alpha)\right)\right]\right>+\left<\frac{1}{2}\left[\cos\left(2(\theta_i-\theta_j)\right)-\cos\left(2(\theta_i+\theta_j-2\alpha)\right)\right]\right>\right)\\
+% %&=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\theta_j)\right)\right>.
+% %\end{align*}
+% $$\xi_+=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\theta_j)\right)\right>.$$
 
-Now using the identity
-\begin{equation}\label{trig2}
-\cos(u\pm v)=\cos\left(u\right)\cos\left(v\right)\mp\sin\left(u\right)\sin\left(v\right),
-\end{equation}
+% Now using the identity
+% \begin{equation}\label{trig2}
+% \cos(u\pm v)=\cos\left(u\right)\cos\left(v\right)\mp\sin\left(u\right)\sin\left(v\right),
+% \end{equation}
 
-the previous equation can be written as
+% the previous equation can be written as
 
-\begin{align*}
-\xi_+&=\left<|\gamma_i|\cdot|\gamma_j|\cdot\left[\cos\left(2\theta_i\right)\cos\left(2\theta_j\right)+\sin\left(2\theta_i\right)\sin\left(2\theta_j\right)\right]\right>\\
-&=\left<\operatorname{Re}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)+\operatorname{Im}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\right>.
-\end{align*}
+% \begin{align*}
+% \xi_+&=\left<|\gamma_i|\cdot|\gamma_j|\cdot\left[\cos\left(2\theta_i\right)\cos\left(2\theta_j\right)+\sin\left(2\theta_i\right)\sin\left(2\theta_j\right)\right]\right>\\
+% &=\left<\operatorname{Re}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)+\operatorname{Im}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\right>.
+% \end{align*}
 
-Using the complex number identities
+% Using the complex number identities
 
-\begin{align}
-\operatorname{Re}(z)&=\frac{1}{2}\left[z+z^*\right],\label{complex1}\\
-\operatorname{Im}(z)&=\frac{1}{2i}\left[z-z^*\right]\label{complex2},
-\end{align}
+% \begin{align}
+% \operatorname{Re}(z)&=\frac{1}{2}\left[z+z^*\right],\label{complex1}\\
+% \operatorname{Im}(z)&=\frac{1}{2i}\left[z-z^*\right]\label{complex2},
+% \end{align}
 
-it follows that
+% it follows that
 
-\begin{align*}
-\xi_+&=\left<\frac{1}{4}\left[(\gamma_i+\gamma_i^*)(\gamma_j+\gamma_j^*)-(\gamma_i-\gamma_i^*)(\gamma_j-\gamma_j^*)\right]\right>\\
-&=\left<\frac{1}{2}\left[\gamma_i\gamma_j^*+(\gamma_i\gamma_j^*)^*\right]\right>\\
-&=\left<\operatorname{Re}(\gamma_i\gamma_j^*)\right>=\texttt{xip}.
-\end{align*}
+% \begin{align*}
+% \xi_+&=\left<\frac{1}{4}\left[(\gamma_i+\gamma_i^*)(\gamma_j+\gamma_j^*)-(\gamma_i-\gamma_i^*)(\gamma_j-\gamma_j^*)\right]\right>\\
+% &=\left<\frac{1}{2}\left[\gamma_i\gamma_j^*+(\gamma_i\gamma_j^*)^*\right]\right>\\
+% &=\left<\operatorname{Re}(\gamma_i\gamma_j^*)\right>=\texttt{xip}.
+% \end{align*}
 
-\section*{Schneider's $\xi_-$ to Jarvis's \texttt{xim}}
+% \section*{Schneider's $\xi_-$ to Jarvis's \texttt{xim}}
 
-The first few steps are identical to the previous section besides the negative in the definition of $\xi_-$, giving
-\begin{align*}
-\xi_-&=\left<\gamma_{i_t}\gamma_{j_t}\right>-\left<\gamma_{i_\times}\gamma_{j_\times}\right>\\
-&=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\alpha)\right)\cos\left(2(\theta_j-\alpha)\right)\right>-\left<|\gamma_i|\cdot|\gamma_j|\sin\left(2(\theta_i-\alpha)\right)\sin\left(2(\theta_j-\alpha)\right)\right>\\
-&=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i+\theta_j-2\alpha)\right)\right>.
-\end{align*}
+% The first few steps are identical to the previous section besides the negative in the definition of $\xi_-$, giving
+% \begin{align*}
+% \xi_-&=\left<\gamma_{i_t}\gamma_{j_t}\right>-\left<\gamma_{i_\times}\gamma_{j_\times}\right>\\
+% &=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\alpha)\right)\cos\left(2(\theta_j-\alpha)\right)\right>-\left<|\gamma_i|\cdot|\gamma_j|\sin\left(2(\theta_i-\alpha)\right)\sin\left(2(\theta_j-\alpha)\right)\right>\\
+% &=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i+\theta_j-2\alpha)\right)\right>.
+% \end{align*}
 
-Now using Equation \eqref{trig2} twice, first letting $u=2(\theta_i+\theta_j)$ and $v=-4\alpha$, and then letting $u=2\theta_i$ and $v=2\theta_j$, this equation becomes
+% Now using Equation \eqref{trig2} twice, first letting $u=2(\theta_i+\theta_j)$ and $v=-4\alpha$, and then letting $u=2\theta_i$ and $v=2\theta_j$, this equation becomes
 
-\begin{align*}
-\xi_-&=\left<|\gamma_i|\cdot|\gamma_j|\Big(\left[\cos(2\theta_i)\cos(2\theta_j)-\sin(2\theta_i)\sin(2\theta_j)\right]\cos(4\alpha)+\left[\sin(2\theta_i)\cos(2\theta_j)+\cos(2\theta_i)\sin(2\theta_j)\right]\sin(4\alpha)\Big)\right>\\
-&=\Big<\big[\operatorname{Re}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)-\operatorname{Im}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\big]\cos(4\alpha)+\big[\operatorname{Im}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)+\operatorname{Re}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\big]\sin(4\alpha)\Big>.
-\end{align*}
+% \begin{align*}
+% \xi_-&=\left<|\gamma_i|\cdot|\gamma_j|\Big(\left[\cos(2\theta_i)\cos(2\theta_j)-\sin(2\theta_i)\sin(2\theta_j)\right]\cos(4\alpha)+\left[\sin(2\theta_i)\cos(2\theta_j)+\cos(2\theta_i)\sin(2\theta_j)\right]\sin(4\alpha)\Big)\right>\\
+% &=\Big<\big[\operatorname{Re}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)-\operatorname{Im}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\big]\cos(4\alpha)+\big[\operatorname{Im}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)+\operatorname{Re}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\big]\sin(4\alpha)\Big>.
+% \end{align*}
 
-Using the identities \eqref{complex1} and \eqref{complex2}, and simplifying the leftover terms, this equation can be shown to equal
-\begin{align*}
-\xi_-=\big<\operatorname{Re}(\gamma_i\gamma_j)\cos(4\alpha)+\operatorname{Im}(\gamma_i\gamma_j)\sin(4\alpha)\big>.
-\end{align*}
+% Using the identities \eqref{complex1} and \eqref{complex2}, and simplifying the leftover terms, this equation can be shown to equal
+% \begin{align*}
+% \xi_-=\big<\operatorname{Re}(\gamma_i\gamma_j)\cos(4\alpha)+\operatorname{Im}(\gamma_i\gamma_j)\sin(4\alpha)\big>.
+% \end{align*}
 
-Now observe that for two complex numbers $a$ and $b$, it is true that
+% Now observe that for two complex numbers $a$ and $b$, it is true that
 
-$$\operatorname{Re}(a\cdot b^*)=\operatorname{Re}(a)\cdot\operatorname{Re}(b)+\operatorname{Im}(a)\cdot\operatorname{Im}(b).$$
+% $$\operatorname{Re}(a\cdot b^*)=\operatorname{Re}(a)\cdot\operatorname{Re}(b)+\operatorname{Im}(a)\cdot\operatorname{Im}(b).$$
 
-Then setting $a=\gamma_i\gamma_j$ and $b=e^{4i\alpha}$, it must be true that
+% Then setting $a=\gamma_i\gamma_j$ and $b=e^{4i\alpha}$, it must be true that
 
-$$\operatorname{Re}\left(\gamma_i\gamma_je^{-4i\alpha}\right)=\operatorname{Re}(\gamma_i\gamma_j)\cos(4\alpha)+\operatorname{Im}(\gamma_i\gamma_j)\sin(4\alpha).$$
+% $$\operatorname{Re}\left(\gamma_i\gamma_je^{-4i\alpha}\right)=\operatorname{Re}(\gamma_i\gamma_j)\cos(4\alpha)+\operatorname{Im}(\gamma_i\gamma_j)\sin(4\alpha).$$
 
-Combining this with our previous result, this means that
+% Combining this with our previous result, this means that
 
-$$\xi_-=\big<\operatorname{Re}(\gamma_i\gamma_j)\cos(4\alpha)+\operatorname{Im}(\gamma_i\gamma_j)\sin(4\alpha)\big>=\left<\operatorname{Re}\left(\gamma_i\gamma_je^{-4i\alpha}\right)\right>=\texttt{xim}.$$
+% $$\xi_-=\big<\operatorname{Re}(\gamma_i\gamma_j)\cos(4\alpha)+\operatorname{Im}(\gamma_i\gamma_j)\sin(4\alpha)\big>=\left<\operatorname{Re}\left(\gamma_i\gamma_je^{-4i\alpha}\right)\right>=\texttt{xim}.$$
 
-\section*{Schneider's $\xi_\times$ to Jarvis's $\frac{1}{2}\left(\texttt{xim\_im}-\texttt{xip\_im}\right)$}
+% \section*{Schneider's $\xi_\times$ to Jarvis's $\frac{1}{2}\left(\texttt{xim\_im}-\texttt{xip\_im}\right)$}
 
-Starting from Schneider's definition of $\xi_\times$,
+% Starting from Schneider's definition of $\xi_\times$,
 
-\begin{align*}
-\xi_\times&=\left<\gamma_{i_t}\gamma_{j_\times}\right>\\
-&=\left<\operatorname{Re}\left(|\gamma_i|e^{2i(\theta_i-\alpha)}\right)\cdot\operatorname{Im}\left(|\gamma_j|e^{2i(\theta_j-\alpha)}\right)\right>\\
-&=\big<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\alpha)\right)\sin\left(2(\theta_j-\alpha)\right)\big>.\\
-\end{align*}
+% \begin{align*}
+% \xi_\times&=\left<\gamma_{i_t}\gamma_{j_\times}\right>\\
+% &=\left<\operatorname{Re}\left(|\gamma_i|e^{2i(\theta_i-\alpha)}\right)\cdot\operatorname{Im}\left(|\gamma_j|e^{2i(\theta_j-\alpha)}\right)\right>\\
+% &=\big<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\alpha)\right)\sin\left(2(\theta_j-\alpha)\right)\big>.\\
+% \end{align*}
 
-Using the trig identity
+% Using the trig identity
 
-\begin{equation}\label{trig3}
-\cos(u)\sin(v)=\frac{1}{2}\left[\sin(u+v)-\sin(u-v)\right],
-\end{equation}
+% \begin{equation}\label{trig3}
+% \cos(u)\sin(v)=\frac{1}{2}\left[\sin(u+v)-\sin(u-v)\right],
+% \end{equation}
 
-the previous equation becomes
+% the previous equation becomes
 
-\begin{align*}
-\xi_\times&=\left<|\gamma_i|\cdot|\gamma_j|\cdot\frac{1}{2}\big[\sin\left(2(\theta_i+\theta_j-2\alpha)\right)-\sin\left(2(\theta_i-\theta_j)\right)\big]\right>.
-\end{align*}
+% \begin{align*}
+% \xi_\times&=\left<|\gamma_i|\cdot|\gamma_j|\cdot\frac{1}{2}\big[\sin\left(2(\theta_i+\theta_j-2\alpha)\right)-\sin\left(2(\theta_i-\theta_j)\right)\big]\right>.
+% \end{align*}
 
-Next, applying the identities
+% Next, applying the identities
 
-\begin{equation}\label{trig4}
-\sin(u\pm v)=\sin(u)\cos(v)\pm\cos(u)\sin(v)
-\end{equation}
+% \begin{equation}\label{trig4}
+% \sin(u\pm v)=\sin(u)\cos(v)\pm\cos(u)\sin(v)
+% \end{equation}
 
-along with \eqref{trig2} iteratively until each trig function only has a single term, the equation becomes
+% along with \eqref{trig2} iteratively until each trig function only has a single term, the equation becomes
 
-\begin{align*}
-\xi_\times&=\Big<|\gamma_i|\cdot|\gamma_j|\cdot\frac{1}{2}\Big(\left[\sin(2\theta_i)\cos(2\theta_j)+\cos(2\theta_i)\sin(2\theta_j)\right]\cos(4\alpha)\\
-&\qquad\qquad\qquad\quad-\left[\cos(2\theta_i)\cos(2\theta_j)-\sin(2\theta_i)\sin(2\theta_j)\right]\sin(4\alpha)\\
-&\qquad\qquad\qquad\quad-\sin(2\theta_i)\cos(2\theta_j)+\cos(2\theta_i)\sin(2\theta_j)\Big)\Big>\\
-&=\Big<\frac{1}{2}\Big(\left[\operatorname{Im}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)+\operatorname{Re}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\right]\cos(4\alpha)\\
-&\qquad-\left[\operatorname{Re}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)-\operatorname{Im}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\right]\sin(4\alpha)\\
-&\qquad-\operatorname{Im}(\gamma_i)\operatorname{Re}(\gamma_j)+\operatorname{Re}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\Big)\Big>.\\
-\end{align*}
+% \begin{align*}
+% \xi_\times&=\Big<|\gamma_i|\cdot|\gamma_j|\cdot\frac{1}{2}\Big(\left[\sin(2\theta_i)\cos(2\theta_j)+\cos(2\theta_i)\sin(2\theta_j)\right]\cos(4\alpha)\\
+% &\qquad\qquad\qquad\quad-\left[\cos(2\theta_i)\cos(2\theta_j)-\sin(2\theta_i)\sin(2\theta_j)\right]\sin(4\alpha)\\
+% &\qquad\qquad\qquad\quad-\sin(2\theta_i)\cos(2\theta_j)+\cos(2\theta_i)\sin(2\theta_j)\Big)\Big>\\
+% &=\Big<\frac{1}{2}\Big(\left[\operatorname{Im}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)+\operatorname{Re}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\right]\cos(4\alpha)\\
+% &\qquad-\left[\operatorname{Re}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)-\operatorname{Im}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\right]\sin(4\alpha)\\
+% &\qquad-\operatorname{Im}(\gamma_i)\operatorname{Re}(\gamma_j)+\operatorname{Re}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\Big)\Big>.\\
+% \end{align*}
 
-Using the identities \eqref{complex1} and \eqref{complex2}, this can be simplified to
+% Using the identities \eqref{complex1} and \eqref{complex2}, this can be simplified to
 
-\begin{align*}
-\xi_\times&=\left<\frac{1}{2}\big[\operatorname{Im}(\gamma_i\gamma_j)\cos(4\alpha)-\operatorname{Re}(\gamma_i\gamma_j)\sin(4\alpha)-\operatorname{Im}(\gamma_i\gamma_j^*)\big]\right>.
-\end{align*}
+% \begin{align*}
+% \xi_\times&=\left<\frac{1}{2}\big[\operatorname{Im}(\gamma_i\gamma_j)\cos(4\alpha)-\operatorname{Re}(\gamma_i\gamma_j)\sin(4\alpha)-\operatorname{Im}(\gamma_i\gamma_j^*)\big]\right>.
+% \end{align*}
 
-Consider again two complex numbers $a$ and $b$. Observe that
+% Consider again two complex numbers $a$ and $b$. Observe that
 
-$$\operatorname{Im}(a\cdot b^*)=\operatorname{Im}(a)\cdot\operatorname{Re}(b)-\operatorname{Re}(a)\cdot\operatorname{Im}(b).$$
+% $$\operatorname{Im}(a\cdot b^*)=\operatorname{Im}(a)\cdot\operatorname{Re}(b)-\operatorname{Re}(a)\cdot\operatorname{Im}(b).$$
 
-Then setting $a=\gamma_i\gamma_j$ and $b=e^{4i\alpha}$, it must be true that
+% Then setting $a=\gamma_i\gamma_j$ and $b=e^{4i\alpha}$, it must be true that
 
-$$\operatorname{Im}\left(\gamma_i\gamma_je^{-4i\alpha}\right)=\operatorname{Im}(\gamma_i\gamma_j)\cos(4\alpha)-\operatorname{Re}(\gamma_i\gamma_j)\sin(4\alpha).$$
+% $$\operatorname{Im}\left(\gamma_i\gamma_je^{-4i\alpha}\right)=\operatorname{Im}(\gamma_i\gamma_j)\cos(4\alpha)-\operatorname{Re}(\gamma_i\gamma_j)\sin(4\alpha).$$
 
-Combing these results give
+% Combing these results give
 
-\begin{align*}
-\xi_\times&=\left<\frac{1}{2}\big[\operatorname{Im}(\gamma_i\gamma_j)\cos(4\alpha)-\operatorname{Re}(\gamma_i\gamma_j)\sin(4\alpha)-\operatorname{Im}(\gamma_i\gamma_j^*)\big]\right>\\
-&=\left<\frac{1}{2}\big[\operatorname{Im}\left(\gamma_i\gamma_je^{-4i\alpha}\right)-\operatorname{Im}(\gamma_i\gamma_j^*)\big]\right>\\
-&=\frac{1}{2}\big[\texttt{xim\_im}-\texttt{xip\_im}\big].
-\end{align*}
+% \begin{align*}
+% \xi_\times&=\left<\frac{1}{2}\big[\operatorname{Im}(\gamma_i\gamma_j)\cos(4\alpha)-\operatorname{Re}(\gamma_i\gamma_j)\sin(4\alpha)-\operatorname{Im}(\gamma_i\gamma_j^*)\big]\right>\\
+% &=\left<\frac{1}{2}\big[\operatorname{Im}\left(\gamma_i\gamma_je^{-4i\alpha}\right)-\operatorname{Im}(\gamma_i\gamma_j^*)\big]\right>\\
+% &=\frac{1}{2}\big[\texttt{xim\_im}-\texttt{xip\_im}\big].
+% \end{align*}
 
-as desired.
+% as desired.
 
-\end{document}
+% \end{document}
 
-% Outline:
+% % Outline:
 
-%% Introduction:
-\begin{itemize}
-\item Broad intro into cosmology and dark matter, set problem in context
-    \begin{itemize}
-    \item (Very) short introduction to history of dark matter, Zwicky, rotation curves, etc.
-    \end{itemize}
-\begin{itemize}
-\item Introduction to gravitational lensing
-    \begin{itemize}
-    \item Convergence and Shear / Strong and Weak lensing
-        \begin{itemize}
-        \item Dramatic effect of strong lensing, how it is used for constraining cos. parameters
-        \item Only a few hundred known, not good for making mass maps
-        \item All galaxies are weakly lensed, good for our purposes
-        \end{itemize}
-    \end{itemize}
-\end{itemize}
-\item What this work does and aims for
-\begin{itemize}
-    \item We aim to implement a simple dark matter halo model to predict weak-lensing effects by foreground mass - and to make the prediction `quickly' and/or with large parallelization
-    \item Quick summary of what we do in paper
-        \begin{itemize}
-        \item Use halo model to make approximation of dark matter mass distribution in Millennium Simulation
-        \item Use shear-shear and galaxy-mass correlation functions as summary statistics
-        \item Compare statistics to ray-traced data
-        \item Discuss physial and computational shortcomings with current methodology
-        \end{itemize}
-    \end{itemize}
-\end{itemize}
+% %% Introduction:
+% \begin{itemize}
+% \item Broad intro into cosmology and dark matter, set problem in context
+%     \begin{itemize}
+%     \item (Very) short introduction to history of dark matter, Zwicky, rotation curves, etc.
+%     \end{itemize}
+% \begin{itemize}
+% \item Introduction to gravitational lensing
+%     \begin{itemize}
+%     \item Convergence and Shear / Strong and Weak lensing
+%         \begin{itemize}
+%         \item Dramatic effect of strong lensing, how it is used for constraining cos. parameters
+%         \item Only a few hundred known, not good for making mass maps
+%         \item All galaxies are weakly lensed, good for our purposes
+%         \end{itemize}
+%     \end{itemize}
+% \end{itemize}
+% \item What this work does and aims for
+% \begin{itemize}
+%     \item We aim to implement a simple dark matter halo model to predict weak-lensing effects by foreground mass - and to make the prediction `quickly' and/or with large parallelization
+%     \item Quick summary of what we do in paper
+%         \begin{itemize}
+%         \item Use halo model to make approximation of dark matter mass distribution in Millennium Simulation
+%         \item Use shear-shear and galaxy-mass correlation functions as summary statistics
+%         \item Compare statistics to ray-traced data
+%         \item Discuss physial and computational shortcomings with current methodology
+%         \end{itemize}
+%     \end{itemize}
+% \end{itemize}
 
-%% Theoretical Background:
-\begin{itemize}
-\item Galaxy ellipticities
-    \begin{itemize}
-    \item (Most) galaxies are not circular - have intrinsic ellipticities
-        \begin{itemize}
-        \item If they were all circular, we could measure the change in shape exactly!
-        \end{itemize}
-    \item Galaxies are not always well approximated by ellipses (reference)
-    \item Mathematical formalism
-    \item Plot of galaxy orientation given e1 and e2 from P.J. Marshall thesis
-    \end{itemize}
-\item Shape noise and PSF issues in weak lensing (distorting already weak signal)
-\item Gravitational lensing
-    \begin{itemize}
-    \item Short introduction to problem setup for simple case (point mass maybe?)
-    \item Assumptions made in a typical solution (thin lens approximation?)
-    \item Show solution from Schneider
-    \item Shear and convergence 
-    \item Measuring shear in weak lensing - a statistical feature
-    \end{itemize}
-\item Dark matter halos
-    \begin{itemize}
-    \item NFW profile and equation (reference)
-    \item BMO truncation and equation (reference)
-    \end{itemize}
-\item SMHR? Or too distracting?
-\end{itemize}
+% %% Theoretical Background:
+% \begin{itemize}
+% \item Galaxy ellipticities
+%     \begin{itemize}
+%     \item (Most) galaxies are not circular - have intrinsic ellipticities
+%         \begin{itemize}
+%         \item If they were all circular, we could measure the change in shape exactly!
+%         \end{itemize}
+%     \item Galaxies are not always well approximated by ellipses (reference)
+%     \item Mathematical formalism
+%     \item Plot of galaxy orientation given e1 and e2 from P.J. Marshall thesis
+%     \end{itemize}
+% \item Shape noise and PSF issues in weak lensing (distorting already weak signal)
+% \item Gravitational lensing
+%     \begin{itemize}
+%     \item Short introduction to problem setup for simple case (point mass maybe?)
+%     \item Assumptions made in a typical solution (thin lens approximation?)
+%     \item Show solution from Schneider
+%     \item Shear and convergence 
+%     \item Measuring shear in weak lensing - a statistical feature
+%     \end{itemize}
+% \item Dark matter halos
+%     \begin{itemize}
+%     \item NFW profile and equation (reference)
+%     \item BMO truncation and equation (reference)
+%     \end{itemize}
+% \item SMHR? Or too distracting?
+% \end{itemize}
 
-% Old theory:
-%However, the important results for a point mass using the thin lens approximation can be summarized as follows: The distortion of a background galaxy image can be quantified by the linearized lens mapping Jacobi matrix $\mathcal{A}$ which can be written as
+% % Old theory:
+% %However, the important results for a point mass using the thin lens approximation can be summarized as follows: The distortion of a background galaxy image can be quantified by the linearized lens mapping Jacobi matrix $\mathcal{A}$ which can be written as
 
-%$$\mathcal{A}=(1-\kappa)\,
-%\begin{pmatrix}
-%1-g_1 & -g2\\
-%-g_2 & 1+g_1
-%\end{pmatrix}$$
+% %$$\mathcal{A}=(1-\kappa)\,
+% %\begin{pmatrix}
+% %1-g_1 & -g2\\
+% %-g_2 & 1+g_1
+% %\end{pmatrix}$$
 
-%\noindent where $\kappa$ and $g$ are the convergence and reduced shear respectively at the center of the background source. 
-%\begin{displaymath}
-%  \varepsilon = \left\{
-%    \begin{array}{lr}
-%      \frac{\varepsilon_i+g}{1+g^*\varepsilon_i} & : |g|\leq1; \\
-%      \frac{1+g\varepsilon_i^*}{\varepsilon^*+g^*} & : |g|>1.
-%    \end{array}
-%   \right.
-%\end{displaymath}
+% %\noindent where $\kappa$ and $g$ are the convergence and reduced shear respectively at the center of the background source. 
+% %\begin{displaymath}
+% %  \varepsilon = \left\{
+% %    \begin{array}{lr}
+% %      \frac{\varepsilon_i+g}{1+g^*\varepsilon_i} & : |g|\leq1; \\
+% %      \frac{1+g\varepsilon_i^*}{\varepsilon^*+g^*} & : |g|>1.
+% %    \end{array}
+% %   \right.
+% %\end{displaymath}
 
-%% The Pangloss Framework:
-\begin{itemize}
-\item Assumptions
-    \begin{itemize}
-    \item A catalog with galaxy
-    \item Currently use actual dark matter halo mass for an idea of best case scenario - can run same analysis with masses sampled from SMHR (reference)
-    \item PSF already accounted for in catalog and error low enough for weak lensing analysis
-    \item Use actual redshift for best case scenario (but can easily be replaced by photometric redshift sampling)
-    \end{itemize}
-\item Millennium Simulation
-    \begin{itemize}
-    \item Instead of blindly using \texttt{Pangloss} to make dark matter mass maps using sky survey data, we instead test how accurately and precisely we can predict weakly-lensed shear and convergence
-    \item Mention which M.S. we used
-    \item S. Hilbert`s ray traced M.S. (reference)
-        \begin{itemize}
-        \item Can use the ray-traced convergence and shear to calculate the ``true'' lensed ellipticties and compare to \texttt{Pangloss}
-        \end{itemize}
-    \end{itemize}
-\item Background galaxies
-    \begin{itemize}
-    \item random orientation
-    \item ellipticity range (get numbers!)
-    \item Accounting for shape noise
-    \end{itemize}
-\item Lightcones
-    \begin{itemize}
-    \item Instead of using all foreground mass in a field to calculate the lensing of a single background object, we create a lightcone centered at the source with a chosen radius $R$
-    \item Drilling
-        \begin{itemize}
-        \item redshift grid to speed up calcuations
-        \item Use the physical distance to line of sight in lensing calculations
-            \begin{itemize}
-            \item Redshift-to-distance relation (equation and reference)
-            \end{itemize}
-        \item Ranking galaxy `relevance'
-            \begin{itemize}
-            \item Want to only include the most important galaxies for lensing to speed up computation, as most will have negligable mass or be too far away
-            \item Allows quicker lensing calculations, means we can make $R$ bigger
-            \item Show `relevance` metric ($M/R^3$ but unitless)
-            \item Include plot of predicted relevance vs kappa contribution??
-            \end{itemize}
-        \end{itemize}
-    \item Lensing by Halos
-        \begin{itemize}
-        \item Treat each foreground halo as a separate lensing event
-        \item Total lensing is the sum of each event
-        \item Lookup table??
-        \end{itemize}
-    \item Include cartoon
-    \end{itemize}
-\item Checking the halo model: Use of correlation functions as summary statistics for ellipticity predictions
-    \begin{itemize}
-        \item Introduce the concept of correlation functions in general
-            \begin{itemize}
-            \item Definition
-            \item Autocorrelation vs cross-correlation
-            \item Use of correlation functions in cosmology
-            \item Shear-shear and galaxy-mass correlation functions
-                \begin{itemize}
-                \item Reference appendix for Visualizing Correlation Functions
-                \end{itemize}
-            \end{itemize}
-        \item Use of Jarvis`s \texttt{TreeCorr} code to calculate cf`s
-        \begin{itemize}
-            \item Reference appendix for Jarvis proof
-        \end{itemize}
-    \end{itemize}
-\item Show one map with ray-traced features and lensed ellipticities vs another map with \texttt{Pangloss} features and predicted ellipticities?
-\end{itemize}
+% %% The Pangloss Framework:
+% \begin{itemize}
+% \item Assumptions
+%     \begin{itemize}
+%     \item A catalog with galaxy
+%     \item Currently use actual dark matter halo mass for an idea of best case scenario - can run same analysis with masses sampled from SMHR (reference)
+%     \item PSF already accounted for in catalog and error low enough for weak lensing analysis
+%     \item Use actual redshift for best case scenario (but can easily be replaced by photometric redshift sampling)
+%     \end{itemize}
+% \item Millennium Simulation
+%     \begin{itemize}
+%     \item Instead of blindly using \texttt{Pangloss} to make dark matter mass maps using sky survey data, we instead test how accurately and precisely we can predict weakly-lensed shear and convergence
+%     \item Mention which M.S. we used
+%     \item S. Hilbert`s ray traced M.S. (reference)
+%         \begin{itemize}
+%         \item Can use the ray-traced convergence and shear to calculate the ``true'' lensed ellipticties and compare to \texttt{Pangloss}
+%         \end{itemize}
+%     \end{itemize}
+% \item Background galaxies
+%     \begin{itemize}
+%     \item random orientation
+%     \item ellipticity range (get numbers!)
+%     \item Accounting for shape noise
+%     \end{itemize}
+% \item Lightcones
+%     \begin{itemize}
+%     \item Instead of using all foreground mass in a field to calculate the lensing of a single background object, we create a lightcone centered at the source with a chosen radius $R$
+%     \item Drilling
+%         \begin{itemize}
+%         \item redshift grid to speed up calcuations
+%         \item Use the physical distance to line of sight in lensing calculations
+%             \begin{itemize}
+%             \item Redshift-to-distance relation (equation and reference)
+%             \end{itemize}
+%         \item Ranking galaxy `relevance'
+%             \begin{itemize}
+%             \item Want to only include the most important galaxies for lensing to speed up computation, as most will have negligable mass or be too far away
+%             \item Allows quicker lensing calculations, means we can make $R$ bigger
+%             \item Show `relevance` metric ($M/R^3$ but unitless)
+%             \item Include plot of predicted relevance vs kappa contribution??
+%             \end{itemize}
+%         \end{itemize}
+%     \item Lensing by Halos
+%         \begin{itemize}
+%         \item Treat each foreground halo as a separate lensing event
+%         \item Total lensing is the sum of each event
+%         \item Lookup table??
+%         \end{itemize}
+%     \item Include cartoon
+%     \end{itemize}
+% \item Checking the halo model: Use of correlation functions as summary statistics for ellipticity predictions
+%     \begin{itemize}
+%         \item Introduce the concept of correlation functions in general
+%             \begin{itemize}
+%             \item Definition
+%             \item Autocorrelation vs cross-correlation
+%             \item Use of correlation functions in cosmology
+%             \item Shear-shear and galaxy-mass correlation functions
+%                 \begin{itemize}
+%                 \item Reference appendix for Visualizing Correlation Functions
+%                 \end{itemize}
+%             \end{itemize}
+%         \item Use of Jarvis`s \texttt{TreeCorr} code to calculate cf`s
+%         \begin{itemize}
+%             \item Reference appendix for Jarvis proof
+%         \end{itemize}
+%     \end{itemize}
+% \item Show one map with ray-traced features and lensed ellipticities vs another map with \texttt{Pangloss} features and predicted ellipticities?
+% \end{itemize}
 
-%% Results
-\begin{itemize}
-\item Maps??
-\item Correlation Functions
-    \begin{itemize}
-    \item shear-shear
-    \item galaxy-mass
-    \item progression of each as $R$ increases??
-    \item cf`s without shape noise and with shape noise
-    \item cf`s with all galaxies vs with only `relevant' galaxies?
-    \end{itemize}
-\item The Need for Speed
-    \begin{itemize}
-    \item Table or graph of speedups and CPU time per lightcone progression (make sure to check \texttt{timeit} first!)
-    \end{itemize}
-\end{itemize}
+% %% Results
+% \begin{itemize}
+% \item Maps??
+% \item Correlation Functions
+%     \begin{itemize}
+%     \item shear-shear
+%     \item galaxy-mass
+%     \item progression of each as $R$ increases??
+%     \item cf`s without shape noise and with shape noise
+%     \item cf`s with all galaxies vs with only `relevant' galaxies?
+%     \end{itemize}
+% \item The Need for Speed
+%     \begin{itemize}
+%     \item Table or graph of speedups and CPU time per lightcone progression (make sure to check \texttt{timeit} first!)
+%     \end{itemize}
+% \end{itemize}
 
-%% Conclusion
-\begin{itemize}
-\item Issues with the \texttt{Pangloss} framework
-    \begin{itemize}
-    \item Systematic shear power under-prediction in cf`s
-    \item Missing large-scale dark matter structure
-    \end{itemize}
-    \item Possibly missing features in model
-        \begin{itemize}
-        \item voids
-        \item filaments
-        \item stellar mass
-        \end{itemize}
-    \item Speed
-\item Moving Foward
-    \begin{itemize}
-    \item Scaling up
-        \begin{itemize}
-        \item CPU and RAM numbers for lightcone parallelization from discussion with Debbie Bard
-        \end{itemize}
-    \item infer hyper-parameters from SMHR, physical distance, etc
-    \item other stuff - too tired right now
-    \end{itemize}
-\end{itemize}
+% %% Conclusion
+% \begin{itemize}
+% \item Issues with the \texttt{Pangloss} framework
+%     \begin{itemize}
+%     \item Systematic shear power under-prediction in cf`s
+%     \item Missing large-scale dark matter structure
+%     \end{itemize}
+%     \item Possibly missing features in model
+%         \begin{itemize}
+%         \item voids
+%         \item filaments
+%         \item stellar mass
+%         \end{itemize}
+%     \item Speed
+% \item Moving Foward
+%     \begin{itemize}
+%     \item Scaling up
+%         \begin{itemize}
+%         \item CPU and RAM numbers for lightcone parallelization from discussion with Debbie Bard
+%         \end{itemize}
+%     \item infer hyper-parameters from SMHR, physical distance, etc
+%     \item other stuff - too tired right now
+%     \end{itemize}
+% \end{itemize}
 
-%% Acknowledgements
-\begin{itemize}
-\item DOE
-\item SULI
-\item Stanford University
-\item KIPAC
-\item Risa, Matt, Pat
-\item Phil!!
-\end{itemize}
+% %% Acknowledgements
+% \begin{itemize}
+% \item DOE
+% \item SULI
+% \item Stanford University
+% \item KIPAC
+% \item Risa, Matt, Pat
+% \item Phil!!
+% \end{itemize}
 
-%% References
-\begin{itemize}
-\item P.J. Marshall Thesis?
-\item Collett et al.
-\item S. Hilbert (ray-traced) http://arxiv.org/abs/0809.5035
-\item Millennium Simulation
-\item Schneider
-\item Jarvis \texttt{TreeCorr}
-\item lensing calculation http://arxiv.org/pdf/astro-ph/9908213v1.pdf
-\item NFW profile
-\item BMO truncation, BMO vs NFW http://arxiv.org/pdf/1301.1684v2.pdf
-\item SMHR http://arxiv.org/pdf/1401.7329v1.pdf
-\item Planck
-\item galaxy curves
-\item BAOs
-\item LCDM
-\item GR
-\item corrFuns in cosmology
-\item wl distortion percent
-\item CFHT Lensing Survey
-\end{itemize}
+% %% References
+% \begin{itemize}
+% \item P.J. Marshall Thesis?
+% \item Collett et al.
+% \item S. Hilbert (ray-traced) http://arxiv.org/abs/0809.5035
+% \item Millennium Simulation
+% \item Schneider
+% \item Jarvis \texttt{TreeCorr}
+% \item lensing calculation http://arxiv.org/pdf/astro-ph/9908213v1.pdf
+% \item NFW profile
+% \item BMO truncation, BMO vs NFW http://arxiv.org/pdf/1301.1684v2.pdf
+% \item SMHR http://arxiv.org/pdf/1401.7329v1.pdf
+% \item Planck
+% \item galaxy curves
+% \item BAOs
+% \item LCDM
+% \item GR
+% \item corrFuns in cosmology
+% \item wl distortion percent
+% \item CFHT Lensing Survey
+% \end{itemize}
 
-%% Appendix A
-\begin{itemize}
-\item Use as a brief introduction to the shear-shear and galaxy-mass correlation function as used in this work
-    \begin{itemize}
-    \item reference other (much more detailed) material for readers to find
-    \end{itemize}
-\item Include correlation value colormaps for $\xi_+$, $\xi_-$, and $\xi_\times$ along with discussion of correlation pattern
-\item Include color-coded correlation visuals along with setup
-    \begin{itemize}
-    \item Galaxies around lens before lensing - correlation values scatter plot with no signal
-    \item Galaxies around lens after lensing - correlation values scatter plot with signal
-    \end{itemize}
-\item B-modes and E-modes plot??
-\end{itemize}
+% %% Appendix A
+% \begin{itemize}
+% \item Use as a brief introduction to the shear-shear and galaxy-mass correlation function as used in this work
+%     \begin{itemize}
+%     \item reference other (much more detailed) material for readers to find
+%     \end{itemize}
+% \item Include correlation value colormaps for $\xi_+$, $\xi_-$, and $\xi_\times$ along with discussion of correlation pattern
+% \item Include color-coded correlation visuals along with setup
+%     \begin{itemize}
+%     \item Galaxies around lens before lensing - correlation values scatter plot with no signal
+%     \item Galaxies around lens after lensing - correlation values scatter plot with signal
+%     \end{itemize}
+% \item B-modes and E-modes plot??
+% \end{itemize}

### 2015-08-20 doc/suli-report-swe.tex
Added a (maybe?) temorary title to the SULI report, and made formating changes to condense the report to 10 pages. #81

@@
 
-\title{SULI Report! (Working title)}
+\title{Predicting Weak Lensing Statistics from Halo Mass Reconstructions}
 %\thanks{A footnote to the article title}%
@@
 Both correlation functions are used in this work to measure how well the \texttt{Pangloss} framework models weak lensing by dark matter structures using the publicly available \texttt{TreeCorr} module written by Mike Jarvis\footnote{https://github.com/rmjarvis/TreeCorr}.
-Note that the ellipticity-ellipticity correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition and the more common Schneider definition \cite{schneider}, see (???).
+Note that the ellipticity-ellipticity correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition and the more common Schneider definition \cite{schneider}, visit the \texttt{Pangloss} repository.
 
@@
     \centering
-    \begin{subfigure}{0.45\textwidth}
+    \begin{subfigure}{0.44\textwidth}
         \includegraphics[width=\textwidth]{figs-swe/corr_visualization_lensed.png}
@@
     ~
-    \begin{subfigure}{0.45\textwidth}
+    \begin{subfigure}{0.44\textwidth}
         \includegraphics[width=\textwidth]{figs-swe/corr_dist_lensed.png}
@@
 \section{References}
-
+\vspace{-.35in}
 \bibliographystyle{unsrt}

### 2015-08-20 doc/suli-report-swe.tex
Changed the structure of the footnotes in the SULI report. #81

@@
 \newcommand{\apjl}{ApJ}
+
+% Used for footnotes
+\makeatletter
+\newcommand\footnoteref[1]{\protected@xdef\@thefnmark{\ref{#1}}\@footnotemark}
+\makeatother
 
@@
 To constrain the mass of foreground dark matter using weak gravitational lensing, first a model of the relationship between foreground galaxies and the foreground dark matter must be established and robustly tested to see if, statistically, it makes the same lensing predictions of background sources as the true underlying dark matter structure.
-To do this, I built upon the publicly available \texttt{Pangloss} framework\footnote{https://github.com/drphilmarshall/Pangloss} used in Collett et al.
+To do this, I built upon the publicly available \texttt{Pangloss} framework\footnote{\label{note1}https://github.com/drphilmarshall/Pangloss} used in Collett et al.
 \cite{collett_marshall} to reconstruct all the mass along the line of sight of each background galaxy using dark matter halos.
@@
 Both correlation functions are used in this work to measure how well the \texttt{Pangloss} framework models weak lensing by dark matter structures using the publicly available \texttt{TreeCorr} module written by Mike Jarvis\footnote{https://github.com/rmjarvis/TreeCorr}.
-Note that the ellipticity-ellipticity correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition and the more common Schneider definition \cite{schneider}, visit the \texttt{Pangloss} repository.
+Note that the ellipticity-ellipticity correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition and the more common Schneider definition \cite{schneider}, visit the \texttt{Pangloss} repository\footnotemark[\ref{note1}].
 

### 2015-08-20 doc/suli-report-swe.tex
Made final revisions to the Introduction and Theory sections of the SULI report. #81

@@
 
-In a universe teeming with galaxies and light, it came as a shock when 20\textsuperscript{th} century astronomers unexpectedly discovered that most of the mass in the universe is in fact dark; the `normal' matter made of atoms that we interact with in everyday life, called baryonic matter, accounts for less than 20\% of the mass in the observable universe.
+In a universe teeming with galaxies and light, it came as a shock when 20\textsuperscript{th} century astronomers discovered that most of the mass in the universe is in fact dark; the `normal' matter made of atoms that we interact with in everyday life, called baryonic matter, accounts for less than 20\% of the mass in the observable universe.
 The remaining mass takes the form of an exotic dark matter that does not absorb or emit light, rendering it invisible to our telescopes.
@@
 While the effects of gravitational lensing can be dramatic, the shape of most galaxies is only distorted by a few percent and must be detected statistically as the intrinsic shape is not known.
-If a model for the distribution of dark matter in a region of foreground mass can accurately predict the statistical signal of this `weak' lensing of background galaxies, then the model can be used on galaxies in existing sky survey data to extrapolate the amount of dark matter in the region and construct large-scale maps of the dark matter in the universe.
+If a model for the distribution of dark matter in a region of foreground mass can accurately predict the statistical signal of this `weak' lensing of background sources, then the model can be used on galaxies in existing sky survey data to extrapolate the amount of dark matter in the region and construct large-scale maps of the dark matter in the universe.
 
@@
 A brief introduction into the theory of galaxy ellipticities, the effects of strong and weak gravitational lensing, and dark matter halos is discussed in Section II.
-The implementation of a halo model on the Millennium Simulation is described in Section III, and the results of the model on 3,240 galaxies on a field size of 324 arcmin$^2$ as well as a comparison of the predicted lensed ellipticities to ray-traced ellipticities is given in Section IV.
-Section V discusses limitations of the used \texttt{Pangloss} framework along with potential physical and computational improvements that can be made for upcoming work before concluding remarks in Section VI.
+The implementation of a halo model on the Millennium Simulation is described in Section III, and the results of the model on 3,240 galaxies on a field size of 324 arcmin$^2$, along with a comparison of the predicted lensed ellipticities to ray-traced ellipticities, is given in Section IV.
+Section V discusses limitations of the used framework as well as potential physical and computational improvements that can be made for upcoming work before concluding remarks in Section VI.
 
@@
 
-\noindent where the magnitude of the galaxy's ellipticity $|\varepsilon|$ is defined to be
+\noindent where the magnitude of the galaxy's ellipticity $|\varepsilon|$ is defined as
 \begin{equation}
@@
 
-\noindent and $r\leq1$ is the ratio of the semi-minor and semi-major axis of the ellipse.
+\noindent and $r\leq1$ is the ratio of the semi-minor and semi-major axes of the ellipse.
 This compact notation combines the eccentricity and orientation of the ellipse into a single object.
@@
 To account for this in generated galaxy images, a multiplicative bias parameter $M$ is often used to lessen the intrinsic ellipticity using
-$$\varepsilon_{obs}=M\cdot\varepsilon_{int}.$$
+$$\varepsilon_{obs}=M\cdot\varepsilon_{int}$$
 
@@
         \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{The shape of a galaxy image for various ellipticity components $\varepsilon_1$ and $\varepsilon_2$ on the $x$ and $y-$axes respectively. Taken from \cite{schneider}.}
+        \caption{The shape of a galaxy image for various ellipticity components $\varepsilon_1$ and $\varepsilon_2$ on the $x$ and $y$-axes respectively. Taken from \cite{schneider}.}
         \label{ellipses}
@@
 
-\noindent Then using the thin lens approximation for the lensing of a background source of intrinsic ellipticity $\varepsilon_i$ around a point foreground mass with reduced shear $g$, the lensed ellipticity $\varepsilon$ is given by
+\noindent Then using the thin lens approximation for the lensing of a background source of intrinsic ellipticity $\varepsilon_i$ by foreground mass at a point with reduced shear $g$, the lensed ellipticity $\varepsilon$ is given by
 \begin{equation}\label{lensing}
@@
 \noindent where an asterisk denotes the complex conjugate \cite{schneider}. The behavior of the distortion relies strongly on the magnitude of $g$; the
-effect is called \textit{strong} lensing if $|g|>1$ and \textit{weak} lensing if $|g|<1$.
+effect is called \textit{strong} lensing if $|g|>1$ and \textit{weak} lensing if $|g|\leq1$.
 The effects of strong lensing can be quite dramatic, distorting sources into large arcs, multiple images, or even an Einstein ring as shown in Figure \ref{einstein_ring}.

### 2015-08-21 doc/suli-report-swe.tex
Made final revisions for the Methods, Results, Discussion, and Conclusion sections of the SULI report. #81

@@
 Each foreground object has an attached dark matter halo and physical distance to the line of sight (dashed line).
-The shear and convergence along the line of sight contributed by each halo is calculated using \cite{lensing_calc}, and the predicted ellipticity is determined using the sum of these contributions.}
+The shear and convergence along the line of sight contributed by each halo is calculated using \cite{lensing_calc}, and the predicted ellipticity is determined using the sum of these contributions and Equation \eqref{lensing}.}
     \label{pangloss_cartoon}
@@
 Testing the first assumption is the main goal of this paper.
-The second assumption is reasonable as it is estimated that dark matter halos are 1-2 orders of magnitude more massive than the host galaxy \cite{smhr}.
+The second assumption is reasonable as it is estimated that dark matter halos are on average 1-2 orders of magnitude more massive than the host galaxy \cite{smhr}.
 Clearly the third assumption will never be true for any observational data.
@@
 \subsection*{Generating Background Galaxies}
-With a catalog of foreground galaxies chosen, a set of 3,240 background galaxies over a field of 324 arcmin$^2$ was generated, with density 10 per arcminute$^2$.
-As the The intrinsic orientation of each galaxy was sampled from a uniform distribution as, without lensing, there should be no preferred orientation due to the assumption of an isotropic universe.
+With a catalog of foreground galaxies chosen, a set of 3,240 background galaxies over a field of 324 arcmin$^2$ was generated, with density 10 per arcmin$^2$.
+The intrinsic orientation of each galaxy was sampled from a uniform distribution as, without lensing, there should be no preferred orientation due to the assumption of an isotropic universe.
 The magnitude of the galaxy ellipticities was sampled from a normal distribution with a standard deviation of 0.2, but any ellipticities with magnitude greater than one were re-sampled.
@@
         \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{The ellipticity-ellipticity correlation function for 3,240 sources at separation distances from 0.1 arcminutes to 2 arcminutes and a lightcone radius of $R=2$ arcminutes.
+        \caption{The ellipticity-ellipticity correlation function for 3,240 sources at separation distances from 0.1 to 2 arcminutes and a lightcone radius of $R=2$ arcminutes.
 While the correlation of the intrinsic ellipticities before lensing (blue) shows no correlation, the correlation of the ray-traced ellipticities (green) and halo model predicted ellipticities (purple) both show significant positive correlation on scales up to 1 arcminute.
@@
         \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{The ellipticity-ellipticity correlation functions for a series of halo model frameworks with increasing lightcone radii from $R=1$ arcminute to $R=8$ arcminutes, all plotted in purple with various line styles.
+        \caption{The ellipticity-ellipticity correlation functions for a series of halo model frameworks with increasing lightcone radii from $R=1$ to $R=8$ arcminutes, all plotted in purple with various line styles.
 These are compared to the same ray-traced correlation from Figure \ref{gg_corr}.}
@@
 
-Using the same catalog of background sources, this statistic was recalculated for the halo model ellipticities for various lightcone radii ranging from $R=1$ arcminute to $R=8$ arcminutes.
+Using the same catalog of background sources, this statistic was recalculated for the halo model ellipticities for various lightcone radii ranging from $R=1$ to $R=8$ arcminutes.
 The result is shown in Figure \ref{gg_corr_series}, where the series of model predicted correlation functions is compared to the ray-traced correlation function.
@@
 
-The catalog of lensed ellipticities was also analyzed using the galaxy-mass correlation function with separation distances from 0.1 arcminutes to 2 arcminutes and a lightcone radius of 2 arcminutes.
+The catalog of lensed ellipticities was also analyzed using the galaxy-mass correlation function with separation distances from 0.1 to 2 arcminutes and a lightcone radius of 2 arcminutes.
 The result is shown in Figure \ref{ng_corr}.
 As with the ellipticity-ellipticity correlation function, there is no significant correlation for the intrinsic ellipticities at any scale as expected.
-The lensed ellipticities from the ray-tracing and halo model both have positive correlation on all calculated scales and are in agreement on scales from 0.2 arcminutes to 0.7 arcminutes.
+The lensed ellipticities from the ray-tracing and halo model both show positive correlation on all calculated scales and are in agreement on separations from 0.2 to 0.7 arcminutes.
 However, the halo model is still systematically underpredicting the shear power on scales above 0.7 arcminutes, although now only by an average of 23\%.
@@
     \captionsetup{justification=raggedright,singlelinecheck=false}
-    \caption{The galaxy-mass correlation function of 3,240 sources at separation distances from 0.1 arcminutes to 2 arcminutes and a lightcone radius of $R=2$ arcminutes.
+    \caption{The galaxy-mass correlation function of 3,240 sources at separation distances from 0.1 to 2 arcminutes and a lightcone radius of $R=2$ arcminutes.
 There is no significant correlation of the intrinsic ellipticities (blue) as expected, and both the ray-traced correlation (green) and halo model correlation (purple) are positive on all scales.
@@
 However, many small improvements to the coding infrastructure of \texttt{Pangloss} were made to speed up the prediction.
-The average CPU time for a lensing prediction per lightcone for four separate runs after various (and cumulative) changes is plotted in Figure \ref{cpu_plot}.
+The average CPU time for a lensing prediction per lightcone for four separate runs after various (and cumulative) changes is plotted in Figure \ref{cpu_plot}, with a final run time of $24\pm5$ ms.
 Run 1 corresponds to the original \texttt{Pangloss} framework code, run 2 only wrote the needed quantities for this analysis to the catalog \texttt{Astropy} tables, run 3 changed the redshift grid binning to be done once for all halos in the drilling rather than for every individual halo in lensing, and run 4 optimized various lensing calculations with matrices whenever possible.
@@
     \caption{The mean CPU runtime per lightcone for various runs with different (and cumulative) code optimizations described in the text.
-The cumulative changes account for a 70\% decrease in the mean CPU time and a halving of the variation.}
+The cumulative changes account for a 70\% decrease in the mean CPU time and a halving of the variation.
+Currently, the prediction can be made for a single lightcone in\\$24\pm5$ ms.}
     \label{cpu_plot}
@@
 
-While the current \texttt{Pangloss} framework can handle the lensing predictions of 3,240 in a 324 arcmin$^2$ field comfortably on a single processor, the goal is to scale up the framework to make predictions for background sources of the same number density in a 100 deg$^2$ field; this will require 3.6 million lightcones, each containing up to 1,000 foreground halos.
+While the current \texttt{Pangloss} framework can handle the lensing predictions of 3,240 sources in a 324 arcmin$^2$ field comfortably on a single processor, the goal is to scale up the framework to make predictions for background sources of the same number density in a 100 deg$^2$ field; this will require 3.6 million lightcones, each containing up to 1,000 foreground halos.
 Luckily, the prediction is trivially parallelizable as the shear and convergence calculation of each lightcone is independent of all other lightcones.
@@
 While the results are encouraging for such a simple model, many strong and unrealistic assumptions were made in the methodology that limit its use in observational surveys.
-In the future, a similar analysis should be made after relaxing many of the assumptions to see how different the predictions by the halo model are from this best-case scenario.
+In the future, a similar analysis should be made after relaxing some of the assumptions to see how different the predictions by the halo model are from this best-case scenario.
 

### 2016-03-21 doc/thesis_swe.tex
Added `thesis_swe` as Spencers work in progress thesis document. Builds from `suli-report-swe.tex`.

--- 2015-08-21 doc/suli-report-swe.tex
@@
 
-\title{Predicting Weak Lensing Statistics from Halo Mass Reconstructions}
+\title{SPENCER THESIS - WORK IN PROGRESS}
 %\thanks{A footnote to the article title}%
@@
         \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{The positive tangential component of the $\varepsilon-\varepsilon$ correlation as a function of galaxy orientation plotted as a colormap.
+        \caption{The positive tangential component of the $\varepsilon$-$\varepsilon$ correlation as a function of galaxy orientation plotted as a colormap.
 The correlation component is positive for parallel galaxies, negative for perpendicular galaxies, and zero for galaxies offset by 45$^\circ$.}
@@
         \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{The cross component of the $\varepsilon-\varepsilon$ correlation as a function of galaxy orientation plotted as a colormap.
-While the pattern is more complicated than that of the tangential component, note that the correlation value is zero for all preferred orientations after lensing.}
+        \caption{The cross component of the $\varepsilon$-$\varepsilon$ correlation as a function of galaxy orientation plotted as a colormap.
+While the pattern is more complicated than that of the tangential component, note that the correlation is zero for all preferred orientations after lensing.}
         \label{xix_colormap}
@@
 In each plot, the value of the correlation between two galaxies as a function of their relative orientation is plotted as a colormap with a few sampled galaxy orientations superimposed.
-For $\xi_+$, the correlation is positive for parallel galaxies, negative for perpendicular galaxies, and zero for galaxies offset by 45$^\circ$.
+For $\xi_+$ the correlation is positive for parallel galaxies, negative for perpendicular galaxies, and zero for galaxies offset by 45$^\circ$.
 In contrast, $\xi_\times$ is zero for all parallel and perpendicular orientations while nonzero for most 45$^\circ$ offsets.
@@
         \caption{The distribution of correlation pairs from the source ellipticities in Figure \ref{color_corr_unlensed}.
-If the pair of galaxies are in the same color bin, then the correlation scatter point is colored in the same scheme.
-Otherwise, the correlation is not plotted.}
+If the pair of galaxies are in the same color bin, then the correlation scatter point is colored in the same scheme.}
         \label{corr_dist_unlensed}
@@
 The source ellipticities have clearly aligned tangentially around the foreground lens in Figure \ref{color_corr_lensed}, and distinct patterns have appeared in the correlation pair distribution for each color bin in Figure \ref{corr_dist_lensed}.
-First consider a single color bin, such as the yellow.
+First consider a single color bin, such as the blue.
 Galaxies next to one another are lensed in approximately the same way and thus nearly parallel, leading to a positive correlation at small separation distances in Figure \ref{corr_dist_lensed}.
-Moving a quarter of the way around the yellow circle of galaxies, the lensed ellipticities become perpendicular and have negative correlation.
+Moving a quarter of the way around the blue circle of galaxies, the lensed ellipticities become perpendicular and have negative correlation.
 This can be seen as the dip in correlation at `middle' separation distances in \ref{corr_dist_lensed}.
@@
         \caption{The distribution of correlation pairs from the source ellipticities in Figure \ref{color_corr_lensed}.
-If the pair of galaxies are in the same color bin, then the correlation scatter point is colored in the same scheme.
-Otherwise, the correlation is not plotted.}
+If the pair of galaxies are in the same color bin, then the correlation scatter point is colored in the same scheme.}
         \label{corr_dist_lensed}
     \end{subfigure}
+    \vspace{-.05in}
     \caption{Correlation visualization for lensed galaxies.}
@@
 \section{References}
-\vspace{-.35in}
+\vspace{-.2825in}
 \bibliographystyle{unsrt}

### 2016-04-05 pangloss/background.py
Started implementing void correction #65

@@ -272,7 +272,7 @@ class BackgroundCatalog(pangloss.Catalog):
 
         return
 
-    def lens_by_halos(self,save=False,methods=['add'],use_method='add',relevance_lim=0.0,lookup_table=False):
+    def lens_by_halos(self,save=False,methods=['add'],use_method='add',relevance_lim=0.0,lookup_table=False,void_corr=False):
         '''
         Lens background galaxies by the combined shear and convergence in their respective lightcones using
         the method given by `use_method`. By default all foreground objects in a lightcone are used in the
@@ -338,13 +338,24 @@ class BackgroundCatalog(pangloss.Catalog):
             # Compute each halo's contribution to the convergence and shear:
             if lookup_table is True:
                 # Use lookup table to speed up kappa calculations
-                lightcone.makeKappas(truncationscale=10,lensing_table=lens_table)
+                lightcone.makeKappas(truncationscale=10,lensing_table=lens_table,void_corr=void_corr)
             else:
                 # Calculate kappa values explicitly
-                lightcone.makeKappas(truncationscale=10)
+                lightcone.makeKappas(truncationscale=10,void_corr=void_corr)
+
+            # Loop over redshift slices and subtract mean foreground kappa (void correction)
+            '''
+            #Old and Slow!!
+            if void_corr is True:
+                redshifts = lightcone.redshifts
+                for i in range(len(redshifts)):
+
+                    # Find foreground galaxies in this slice and sum up the masses
+                    lightcone.galaxies[lightcone.galaxies['z_sz']==redshifts[i]]['kappa'] -= self.foreground_kappas[i]
+            '''
 
             # Combine all contributions into a single kappa and gamma for the lightcone
-            lightcone.combineKappas(methods=methods)
+            lightcone.combineKappas(methods=methods,void_corr=void_corr)
 
             # Populate the kappa and gamma values using the 'use_method'
             if use_method == 'add' :
@@ -526,6 +537,9 @@ class BackgroundCatalog(pangloss.Catalog):
 
         # Only take the columns from foreground that are needed for a lightcone
         lc_catalog = Table(names=['RA','Dec','z_obs','Mhalo_obs','Type'],data=[foreground.galaxies['RA'],foreground.galaxies['Dec'],foreground.galaxies['z_obs'],foreground.galaxies['Mhalo_obs'],foreground.galaxies['Type']])
+
+        # Save mean kappas in foreground redshift slices for void correction
[…]

### 2016-04-05 pangloss/config.py

@@ -10,28 +10,28 @@ class Configuration(object):
         Configuration
 
     PURPOSE
-        Structure of metadata supplied by the Pangloss user to define 
+        Structure of metadata supplied by the Pangloss user to define
         the experiment they want to do.
 
     COMMENTS
 
     INITIALISATION
         configfile    Plain text file containing desired values of pars
-    
+
     METHODS
         read(self): from configfile, get par names and values
-        
+
         convert(self): strings to numbers, and expand paths
-        
+
         prepare(self): set up workspace
-        
-        getLightconePickleName(self,flavor,pointing=None): 
+
+        getLightconePickleName(self,flavor,pointing=None):
 
     BUGS
 
     AUTHORS
       This file is part of the Pangloss project, distributed under the
-      GPL v2, by Tom Collett (IoA) and  Phil Marshall (Oxford). 
+      GPL v2, by Tom Collett (IoA) and  Phil Marshall (Oxford).
       Please cite: Collett et al 2013, http://arxiv.org/abs/1303.6564
 
     HISTORY
@@ -99,6 +99,8 @@ class Configuration(object):
 
         # Calibration catalogs and kappa maps must come in pairs...
         if self.parameters['CalibrationKappamaps'] != None:
+            print self.parameters['CalibrationCatalogs']
+            print self.parameters['CalibrationKappamaps']
             assert len(self.parameters['CalibrationCatalogs']) == \
                   len(self.parameters['CalibrationKappamaps'])
 
@@ -110,7 +112,7 @@ class Configuration(object):
             if self.parameters[key]!=['']:
                 for i in range(len(self.parameters[key])):
                     self.parameters[key][i]=float(self.parameters[key][i])
-            
+
         return
 
     # ------------------------------------------------------------------
@@ -135,11 +137,11 @@ class Configuration(object):
             # In this case, need the name of the obscat:
             x = self.parameters['ObservedCatalog'][0]
             return x.split('.')[0]+"_lightcone.pickle"
-        
+
         elif flavor == 'simulated':
             # In this case, need the CALIB_DIR and pointing number:
             assert pointing != None
-            CALIB_DIR = self.parameters['CalibrationFolder'][0]          
+            CALIB_DIR = self.parameters['CalibrationFolder'][0]
             x = "%s/pointing_%i" % (CALIB_DIR, pointing)
             return x+"_lightcone.pickle"
 
@@ -149,7 +151,7 @@ class Configuration(object):
[…]

### 2016-04-05 pangloss/foreground.py

@@ -71,6 +71,9 @@ class ForegroundCatalog(pangloss.Catalog):
         self.field_i = eval(input_parse[5]) # The i location of the field grid in the (x,y) map
         self.field_j = eval(input_parse[6]) # The j location of the field grid in the (x,y) map
 
+        # Calculate mean kappas on the redshift grid
+        self.find_mean_kappas()
+
         # Initialize common catalog attributes:
         pangloss.Catalog.__init__(self)
 

### 2016-04-05 pangloss/lightcone.py

@@ -306,15 +306,26 @@ class Lightcone(object):
 # ----------------------------------------------------------------------------
 # Snap the parameters z onto the grid, to speed up calculations:
 
-    def snapToGrid(self, Grid):
+    def snapToGrid(self, Grid,foreground_kappas=None):
         z = self.galaxies['z']
         sz,p = Grid.snap(z)
+        self.writeColumn('z_sz',sz)
         self.writeColumn('Da_p',Grid.Da_p[p])
         self.writeColumn('rho_crit',Grid.rho_crit[p])
         self.writeColumn('sigma_crit',Grid.sigma_crit[p])
         self.writeColumn('beta',Grid.beta[p])
         rphys = self.galaxies['r']*pangloss.arcmin2rad*self.galaxies['Da_p']
         self.writeColumn('rphys',rphys)
+
+        # Write foreground mean kappas for void correction (0 if foreground kappas not inputed)
+        if foreground_kappas is None:
+            f_kappa = np.zeros(np.size(z))
+        else:
+            self.foreground_kappas = foreground_kappas
+            f_kappa = foreground_kappas[p]
+            #print('p = {}'.format(p))
+            #print('f_kappa = {}'.format(f_kappa))
+        self.writeColumn('f_kappa',f_kappa)
 # ----------------------------------------------------------------------------
 # Given Mhalo and z, draw an Mstar, and an identical Mstar_obs:
 
@@ -368,7 +379,7 @@ class Lightcone(object):
 # ----------------------------------------------------------------------------
 # Compute halos' contributions to the convergence:
 
-    def makeKappas(self,errors=False,truncationscale=5,profile="BMO1",lensing_table=None):
+    def makeKappas(self,errors=False,truncationscale=5,profile="BMO1",lensing_table=None,void_corr=False):
 
         rho_s = pangloss.delta_c(self.galaxies['c200'])*self.galaxies['rho_crit']
         self.kappa_s = rho_s * self.galaxies['rs'] /self.galaxies['sigma_crit']  #kappa slice for each lightcone
@@ -401,6 +412,14 @@ class Lightcone(object):
 
         #phi = self.galaxies['phi']
         kappa = 1.0*self.kappa_s*F
+
+        '''Don't think this works - kills off all kappa
+        # Subtract mean foreground kappas per redshift slice for void correction
+        print('mean kappa = {}'.format(np.mean(kappa)))
+        if void_corr is True: kappa -= self.galaxies['f_kappa']
[…]

### 2016-04-05 tests/lens_compare.py

@@ -15,6 +15,9 @@ vb = True
 # Turn on for pickling correlation data
 pickle = False
 
+# Turn on for plotting correlation function plots
+corr_plots = True
+
 # Turn on for plotting maps
 maps = True
 
@@ -32,6 +35,7 @@ S = pangloss.Shearmap([PANGLOSS_DIR+'/data/GGL_los_8_0_0_N_4096_ang_4_rays_to_pl
 if vb is True: print('Loading foreground catalog...')
 config = pangloss.Configuration(PANGLOSS_DIR+'/example/example.config')
 F = pangloss.ForegroundCatalog(PANGLOSS_DIR+'/data/GGL_los_8_0_0_0_0_N_4096_ang_4_Guo_galaxies_on_plane_27_to_63.images.txt',config)
+#F.plot_mean_kappas()
 
 # Generate Background Catalog in the middle of the (0,0,0,0) field
 if vb is True: print('Generating background catalog...')
@@ -39,8 +43,8 @@ if vb is True: print('Generating background catalog...')
 #d = [1.85,1.15,-1.85,-1.15]
 #d = [1.75,1.25,-1.75,-1.25]
 d = [1.65,1.35,-1.65,-1.35]
-#d = [1.6,1.4,-1.6,-1.4]
 #d = [1.55,1.45,-1.55,-1.45]
+#d = [1.6,1.4,-1.6,-1.4]
 #d = [1.55,1.48,-1.55,-1.48]
 #d = [1.55,1.52,-1.61,-1.59] # only galaxies in subplot
 #d = [1.55,1.54,-1.61,-1.6] # ~3 galaxies
@@ -53,49 +57,69 @@ print 'Background catalog has',B.galaxy_count,'galaxies'
 
 # Drill the lightcones
 if vb is True: print('Drilling lightcones...')
-B.drill_lightcones(radius=2.0,foreground=F,save=False)
+B.drill_lightcones(radius=8.0,foreground=F,save=False)
 
 # Calculate mean/std galaxies per lightcone
-galaxy_counts = [B.lightcones[i].galaxy_count for i in range(len(B.lightcones))]
+galaxy_counts = [lightcone.galaxy_count for lightcone in B.lightcones]
 mean_galaxies = np.mean(galaxy_counts)
 std_galaxies = np.std(galaxy_counts)
-#important_counts = [B.lightcones[i] for i in range(len(B.lightcones))]
-#mean_important = np.mean(galaxy_counts)
[…]

### 2016-04-05 doc/thesis_swe.tex
Making thesis

@@
 
-To constrain the mass of foreground dark matter using weak gravitational lensing, first a model of the relationship between foreground galaxies and the foreground dark matter must be established and robustly tested to see if, statistically, it makes the same lensing predictions of background sources as the true underlying dark matter structure.
-To do this, I built upon the publicly available \texttt{Pangloss} framework\footnote{\label{note1}https://github.com/drphilmarshall/Pangloss} used in Collett et al.
-\cite{collett_marshall} to reconstruct all the mass along the line of sight of each background galaxy using dark matter halos.
-The lensing contribution of each halo is calculated, and the total lensing of the background galaxy is the sum of each halo contribution.
-This process is detailed in the following sections.
+To constrain the mass of foreground dark matter using weak gravitational
+lensing, first a model of the relationship between foreground galaxies
+and the foreground dark matter must be established and robustly tested
+to see if, statistically, it makes the same lensing predictions of
+background sources as the true underlying dark matter structure. To do
+this, I built upon the publicly available \texttt{Pangloss}
+framework\footnote{\label{note1}https://github.com/drphilmarshall/Pangloss}
+used in Collett et al. \cite{collett_marshall} to reconstruct all the
+mass along the line of sight of each background galaxy using dark matter
+halos. The lensing contribution of each halo is calculated, and the
+total lensing of the background galaxy is the sum of each halo
+contribution. This process is detailed in the following sections.
 
@@
 
-Instead of comparing the ray-traced and \texttt{Pangloss} predicted ellipticities for individual galaxies, the lensing is characterized globally with correlation functions.
-The ellipticity-ellipticity correlation function measures how correlated the ellipticities of pairs of galaxies are as a function of separation distance, while the galaxy-mass correlation function measures the correlation of lensed ellipticities around foreground halos as a function of separation distance.
-For readers that are unfamiliar with correlation functions in the context of cosmology or want a visual aid, see the appendix.
-Both correlation functions are used in this work to measure how well the \texttt{Pangloss} framework models weak lensing by dark matter structures using the publicly available \texttt{TreeCorr} module written by Mike Jarvis\footnote{https://github.com/rmjarvis/TreeCorr}.
-Note that the ellipticity-ellipticity correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition and the more common Schneider definition \cite{schneider}, visit the \texttt{Pangloss} repository\footnotemark[\ref{note1}].
+Instead of comparing the ray-traced and \texttt{Pangloss} predicted
+ellipticities for individual galaxies, the lensing is characterized
+globally with correlation functions. The ellipticity-ellipticity
+correlation function measures how correlated the ellipticities of pairs
+of galaxies are as a function of separation distance, while the
+galaxy-mass correlation function measures the correlation of lensed
+ellipticities around foreground halos as a function of separation
+distance. For readers that are unfamiliar with correlation functions in
+the context of cosmology or want a visual aid, see the appendix. Both
+correlation functions are used in this work to measure how well the
+\texttt{Pangloss} framework models weak lensing by dark matter
+structures using the publicly available \texttt{TreeCorr} module written
+by Mike Jarvis\footnote{https://github.com/rmjarvis/TreeCorr}. Note that
+the ellipticity-ellipticity correlation function definition used in
+\texttt{TreeCorr} is slightly different than that used in most of the
+literature; for a derivation of the connection between Jarvis's
+definition and the more common Schneider definition \cite{schneider},
+visit the \texttt{Pangloss} repository\footnotemark[\ref{note1}].
 

### 2016-04-13 pangloss/background.py
`background.py` now implements the void correction by passing `foreground_kappas` to `combineKappas()` rather than `makeKappas()`. #65

@@ -355,7 +355,12 @@ class BackgroundCatalog(pangloss.Catalog):
             '''
 
             # Combine all contributions into a single kappa and gamma for the lightcone
-            lightcone.combineKappas(methods=methods,void_corr=void_corr)
+            if void_corr is True:
+                # Implement void correction using calcualted mean foreground kappas
+                lightcone.combineKappas(methods=methods,foreground_kappas=self.foreground_kappas)
+            else:
+                # No void correction - simply add all kappas
+                lightcone.combineKappas(methods=methods)
 
             # Populate the kappa and gamma values using the 'use_method'
             if use_method == 'add' :

### 2016-04-13 pangloss/lightcone.py
Removed incorrect void correction in `makeKappas()` and unecessary argument `void_corr` in `combineKappas()`. #65

@@ -379,7 +379,7 @@ class Lightcone(object):
 # ----------------------------------------------------------------------------
 # Compute halos' contributions to the convergence:
 
-    def makeKappas(self,errors=False,truncationscale=5,profile="BMO1",lensing_table=None,void_corr=False):
+    def makeKappas(self,errors=False,truncationscale=5,profile="BMO1",lensing_table=None):
 
         rho_s = pangloss.delta_c(self.galaxies['c200'])*self.galaxies['rho_crit']
         self.kappa_s = rho_s * self.galaxies['rs'] /self.galaxies['sigma_crit']  #kappa slice for each lightcone
@@ -413,13 +413,6 @@ class Lightcone(object):
         #phi = self.galaxies['phi']
         kappa = 1.0*self.kappa_s*F
 
-        '''Don't think this works - kills off all kappa
-        # Subtract mean foreground kappas per redshift slice for void correction
-        print('mean kappa = {}'.format(np.mean(kappa)))
-        if void_corr is True: kappa -= self.galaxies['f_kappa']
-        print('mean corrected kappa = {}'.format(np.mean(kappa)))
-        '''
-
         gamma = 1.0*self.kappa_s*(G-F)
         gamma1 = gamma*np.cos(2*self.galaxies['phi'])
         gamma2 = gamma*np.sin(2*self.galaxies['phi'])
@@ -437,7 +430,7 @@ class Lightcone(object):
 
 # ----------------------------------------------------------------------------
 
-    def combineKappas(self,methods=['add','keeton','tom'],foreground_kappas=None,void_corr=None):
+    def combineKappas(self,methods=['add','keeton','tom'],foreground_kappas=None):
 
         # If a single string is passed for methods, place it in a list
         if type(methods) != list:

### 2016-04-13 pangloss/plotting.py
The `plot_corr()` method can now plot correlations from only relevant halos separately to compare to the correlation calculated using all halos. Added the optional argument `radius` so that the plots now state the radius of lightcones if given. #66

@@ -174,7 +174,7 @@ def plot_sticks(ra,dec,mod,phi,axis,color):
 
 # ----------------------------------------------------------------------------
 
-def plot_corr(corr,corr_type='gg',corr_comp='plus',sep_units='arcmin',lensed='map',color=None,line_style=None,fig_size=10,M=None,galaxy_count=None):
+def plot_corr(corr,corr_type='gg',corr_comp='plus',sep_units='arcmin',lensed='map',color=None,line_style=None,fig_size=10,M=None,galaxy_count=None,radius=None):
     '''
     Plot the correlation component 'corr_comp' of type 'corr_type' in separation units of 'sep_units'.
     By default the method will plot the lensed-by-map correlation, but can also plot without lensing
@@ -234,10 +234,11 @@ def plot_corr(corr,corr_type='gg',corr_comp='plus',sep_units='arcmin',lensed='ma
     if corr_type == 'gg':
         # For shear-shear (or ellipticity-ellipticity) correlation
 
-        # Mark first label as intrinsic, observed, or predicted
+        # Mark first label as intrinsic, ray-traced, or halo model
         if lensed == 'none': label1 = 'Intrinsic '
-        if lensed == 'map': label1 = 'Ray-Traced '
+        elif lensed == 'map': label1 = 'Ray-Traced '
         elif lensed == 'halo': label1 = 'Halo Model '
+        elif lensed == 'halo_rel': label1 = 'Most Relevant Halos '
 
         # Create the correct component label and linestyle to be used in legend
         if corr_comp == 'plus':
@@ -284,8 +285,9 @@ def plot_corr(corr,corr_type='gg',corr_comp='plus',sep_units='arcmin',lensed='ma
 
         # Mark first label as intrinsic, observed, or predicted
         if lensed == 'none': label1 = 'Intrinsic '
-        if lensed == 'map': label1 = 'Ray-Traced '
+        elif lensed == 'map': label1 = 'Ray-Traced '
         elif lensed == 'halo': label1 = 'Halo Model '
+        elif lensed == 'halo_rel': label1 = 'Most Relevant Halos '
 
         if corr_comp == 'real':
             # Plot real(xi) with a solid line
@@ -323,9 +325,9 @@ def plot_corr(corr,corr_type='gg',corr_comp='plus',sep_units='arcmin',lensed='ma
     handles = [h[0] for h in handles]
     plt.legend(handles,labels,fontsize=18)
 
-    if galaxy_count is not None:
[…]

### 2016-04-13 pangloss/background.py
Removed uncecessary argument `void_corr` from the `makeKappas()` call in `background.py`. #65

@@ -338,10 +338,10 @@ class BackgroundCatalog(pangloss.Catalog):
             # Compute each halo's contribution to the convergence and shear:
             if lookup_table is True:
                 # Use lookup table to speed up kappa calculations
-                lightcone.makeKappas(truncationscale=10,lensing_table=lens_table,void_corr=void_corr)
+                lightcone.makeKappas(truncationscale=10,lensing_table=lens_table)
             else:
                 # Calculate kappa values explicitly
-                lightcone.makeKappas(truncationscale=10,void_corr=void_corr)
+                lightcone.makeKappas(truncationscale=10)
 
             # Loop over redshift slices and subtract mean foreground kappa (void correction)
             '''

### 2016-04-13 pangloss/plotting.py
`plot_corr() now prints the number of lightcones even if the lc radius isnt passed; prints both otherwise.

@@ -327,7 +327,10 @@ def plot_corr(corr,corr_type='gg',corr_comp='plus',sep_units='arcmin',lensed='ma
 
     if galaxy_count and radius is not None:
         # place a text box in upper left in axes coords
-        plt.gca().text(0.1,0.95,'{} lightcones with radius {}'.format(galaxy_count,radius),transform=plt.gca().transAxes,fontsize=18,verticalalignment='top')
+        plt.gca().text(0.1,0.95,'{} lightcones with radius {} arcmin'.format(galaxy_count,radius),transform=plt.gca().transAxes,fontsize=18,verticalalignment='top')
+    elif galaxy_count is not None:
+        # place a text box in upper left in axes coords
+        plt.gca().text(0.1,0.95,'{} lightcones'.format(galaxy_count),transform=plt.gca().transAxes,fontsize=18,verticalalignment='top')
 
     return
 

### 2016-04-23 doc/void_correction.tex
Added temporary notes for the foreground and smooth-component corrections. #65

% Notes on the theory and implementation of a void correction

\documentclass[12pt]{article}
\usepackage{amsmath,amsthm,enumitem,amssymb,graphicx,color,bm}
\usepackage[margin=1in]{geometry}

\makeatletter
\def\imod#1{\allowbreak\mkern10mu({\operator@font mod}\,\,#1)}
\makeatother

\begin{document}

\setlength\parindent{0pt}

\vspace{-6in}

\title{Void Correction Notes}
\author{Spencer Everett}
\date{\today}

\maketitle

\section*{Motivation}

The shear and convergence predictions made by the \texttt{Pangloss} framework are dependent upon the cosmology assumed; inherent in all distance calculations are the value and evolution of the universe's mass density, characterized by $\Omega_m(z)$. Yet the current framework overestimates the mass in all regions as it adds the halo masses on top of a uniformly distributed mass density that is already equal to the predicted mass density at the halos' respective redshifts. Even more problematic, much of the mass in the Millennium Simulation isn't contained in halos - and the weak lensing contributions of these mass structures are not currently accounted for.\\

To have a more accurate approximation for the mass density in a given region (and thus more accurate $\gamma$ and $\kappa$ predictions), we must account for mass in \texttt{Pangloss} in three different components:

\begin{enumerate}[label=(\arabic*)]
\item The mass contributed by galaxies (stellar mass), halos, and subhalos,
\item A ``foreground correction'' in the form of a uniformly distributed sheet of negative mass density at each redshift such that the mean density (and thus mean $\kappa$) of the redshift slice is zero, and
\item A ``smooth component correction'' in the form of a uniformly distributed sheet of mass density at each redshift that accounts for all excess mass in the region not contained in galaxies or their halos (i.e. cluster and supercluster halos, filaments, etc.)
\end{enumerate}

The first component is accounted for when calculating $\kappa$ predictions in \texttt{makeKappas()} that is called by \texttt{lens\_by\_halos()}, although we currently ignore the stellar and subhalo masses as they are less significant. We can calculate the other two components in the following ways:

\begin{enumerate}[label=(\arabic*)]
\setcounter{enumi}{1}
\item To start, we can make the foreground correction on each foreground catalog separately by snapping the entire catalog to the same redshift grid that the lightcone halos eventually will use. The surface mass density as a function of redshift then can be calculated by summing the mass in (1) and dividing by the proper surface area at each redshift. This surface mass density is used to calculate the $\kappa$ contribution corresponding to the entire foreground at that redshift.
\item If we derive equations for the universe's mass density and halo mass density in our lightcones as a function of redshisft, then the smooth-component correction at each redshift should simply be the difference between these two densities. Calculating the halo mass density will require an expression for the proper volume element and integrating over each redshift slice.
\end{enumerate}

We now derive each correction below.

\section*{The Foreground Correction}

(Details to be added later!)

\section*{The Smooth-Component Correction}

The foreground catalogs of the Millennium Simulation contain only the stellar masses of foreground galaxies and the masses of their respective dark matter halos and subhalos; all additional mass in the form of filaments, galaxy cluster and supercluster halos, or otherwise must be inferred. However, the mean mass density of large enough ($\sim$100 Mpc) regions should approximate the mean mass density of the universe, so for a first guess we can approximate the additional mass as a series of uniform sheets of matter along each redshift slice that make the total mass density of the foreground catalog equal to the mean density of the universe. This assumption can be expressed as

\begin{equation}\label{smooth_correction1}
\rho_{\text{matter}}(z)=\rho_{\text{halos}}(z)+\rho_{\text{smooth}}(z)
\end{equation}

where $z$ is the redshift and $\rho_{\text{matter}}(z)$, $\rho_{\text{halos}}(z)$, and $\rho_{\text{smooth}}(z)$ are the mean matter densities of the universe, halos, and smooth-component correction respectively. For simplicity, we rename theses quantities ${\rho_m(z)}$, ${\rho_h(z)}$, and ${\rho_s(z)}$ so that Equation \eqref{smooth_correction1} now reads as

\begin{equation}\label{smooth_correction2}
\rho_m(z)=\rho_h(z)+\rho_s(z).
\end{equation}

To solve for the desired smooth component correction, we first need to calcualte ${\rho_m(z)}$ and ${\rho_h(z)}$ and then subtract:

\begin{equation}\label{smooth_correction2}
\rho_s(z)=\rho_m(z)-\rho_h(z).
\end{equation}

Note that, unlike the foreground correction, each mass sheet at a given $z$ can have positive \textit{or} negative mass density as the foreground at that redshift could happen to be in a local overdensity or underdensity.

\subsection*{Calculating $\bm{\rho_m(z)}$:}

Using the fluid equation and equation of state, we can show that the energy density of non-relativistic matter $\varepsilon_m(z)$ evolves as

\begin{equation}\label{energy_evol}
\varepsilon_m(z)=\frac{\varepsilon_{m,0}}{a(z)^3}=\varepsilon_{m,0}(1+z)^3
\end{equation}

where $a(z)=(1+z)^{-1}$ is the cosmic scale factor ($a(0)=1$ by convention) and a subscript of 0 means the value at the present time, or equivalently a redshift of 0. \textcolor{red}{(Maybe show the full derivation in the thesis?)} This makes sense as the (mostly constant) mass is being diluted by an expanding volume. As the mass is non-relativistic, its energy density can be approximated by

\begin{equation*}\label{energy_mass}
\varepsilon_m(z)\approx\rho_m(z)c^2
\end{equation*}

and thus

\begin{equation}\label{mass_evol}
\rho_m(z)\approx\rho_{m,0}(1+z)^3.
\end{equation}

The current matter density $\rho_{m,0}$ is usually reported in literature in terms of the present matter density parameter $\Omega_{m,0}$ defined as

\begin{equation}\label{}
\Omega_{m,0}=\frac{\rho_{m,0}}{\rho_{c,0}}=\frac{8\pi G}{3H_0^2}\,\rho_{m,0}
\end{equation}

where $\rho_{c,0}=\frac{3H_0^2}{8\pi G}$ is the present critical density. Solving for $\rho_{m,0}$ gives

\begin{equation*}\label{}
\rho_{m,0}=\frac{3H_0^2}{8\pi G}\,\Omega_{m,0}
\end{equation*}

and so we may write the non-relativistic mass density of the universe as a function of redshift as

\begin{equation}\label{rho}
\rho_m(z)\approx\left(\frac{3H_0^2}{8\pi G}\,\Omega_{m,0}\right)(1+z)^3.
\end{equation}

Current \texttt{Pangloss} code assumes a cosmology of $\Omega_{m,0}=0.25$, $\Omega_{\Lambda,0}=0.75$ (to ensure a flat universe), and $H_0=73$ km$\cdot$s$^{-1}\cdot$Mpc$^{-1}$ (\textcolor{red}{Were these values chosen to match the original Millennium Simulation parameters? A later run that Stefan used for his ray tracing? Known values when Collett et al. was published?}) which leads to an evolving mass density of

\begin{equation}\label{rho}
\rho_m(z)\approx\left(3.70\times10^{10}\frac{M_{\odot}}{\text{Mpc}^3}\right)(1+z)^3.
\end{equation}

\subsection*{Calculating $\bm{\rho_h(z)}$:}

Now we must calculate $\rho_h(z)$ given the foreground catalogs of the Millennium Simulation. While each galaxy/halo are on a continuum of redshifts, we snap each halo to one of $N$ redshift planes from $z=0$ to the source redshift of $z_s=1.3857$, each separated by a constant $\Delta z=1.3857/N$ for faster computation (typically, $N=100$ and $\Delta z\approx0.014$). We can approximate $\rho_h$ at each of the $N$ redshift values by summing the halo masses and dividing by the integral the proper volume element $dV_p$ over the redshift range $z\pm \Delta z/2$ and solid angle $d\Omega$ covered by the foreground catalog. Figure \ref{rho_slice} visualizes this process.\\

\begin{figure}[!ht]
  \centering
  \includegraphics[width=0.6\textwidth]{figs-swe/comoving_integral.png}
  \caption{Approximating $\rho_h(z)$ by summing the halo mass in each redshift slice and dividing by the proper volume. Each slice covers a redshift range of $\Delta z$ (except for $z=0$ and $z=1.3857$, which have a range of $\Delta z/2$) and solid angle $d\Omega$.}
  \label{rho_slice}
\end{figure}

From Figure \ref{rho_slice}, it is clear that we want a proper volume element that is expressed in terms of the solid angle $d\Omega$ (or really, $d\theta d\phi$) and the redshift $dz$. To do this, we can start with the standard spherical volume element $dV=r^2\sin(\theta)drd\theta d\phi$. However, we must be careful that (1) we are using proper distances, (2) account for the possibility of a curved universe, and (3) use the correct distance measure for $r$ (in this case, the angular diameter distance). From this we can gather that the proper volume element must have the form of

\begin{equation}\label{proper_element}
dV_p=dr_pdA=d_A(z)^2dr_pd\omega=d_A(z)^2\sin(\theta)dr_pd\theta d\phi
\end{equation}
% and $r_a$ is the angular diameter distance 
where $d_A(z)$ is the angular diameter distance and the subscript $p$ denotes proper distance. When the angular diameter distance $d_A(z)$ is multiplied by an angle (i.e. $d_A(z)d\theta$ and $d_A(z)d\phi$), it gives an approximation of the proper distance between two objects at the same redshift. $d_A(z)$ can be expressed in terms of the transverse comoving distance $d_M(z)$,

\begin{equation}\label{angular2transverse}
d_A(z)=a(z)d_M(z)=\frac{d_M(z)}{1+z}
\end{equation}

which is the comoving analog of $d_A(z)$. The transverse comoving distance depends on the assumed cosmology of the universe and takes the form of

\begin{equation}\label{comoving_transverse}
d_M(z)=\left\{
     \begin{array}{lr}
       d_H/\sqrt{\Omega_k}\sinh\left[\sqrt{\Omega_k}d_C(z)/d_H\right] & : \Omega_k>0\\
       d_C(z) & : \Omega_k=0\\
       d_H/\sqrt{|\Omega_k|}\sin\left[\sqrt{|\Omega_k|}d_C(z)/d_H\right] & : \Omega_k<0
     \end{array}
   \right.
\end{equation}

where $d_H=c/H_0$ is the Hubble distance, $\Omega_k$ is the curvature parameter ($\Omega_k=0$ for a flat universe), and $d_C(z)$ is the line-of-sight (LOS) comoving distance given by

\begin{equation}\label{comoving_distance}
d_C(z)=d_H\int_0^z\frac{dz^\prime}{E(z^\prime)}
\end{equation}

where $E(z)$ is the dimensionless Hubble parameter

\begin{equation}\label{dim_hubble_parameter}
E(z)=\sqrt{\Omega_m(1+z)^3+\Omega_k(1+z)^2+\Omega_\Lambda}.
\end{equation}

Substituting Equation \eqref{angular2transverse} into \eqref{proper_element} leads to

\begin{equation}\label{temp_solution}
dV_p=d_a(z)^2\sin(\theta)dr_pd\theta d\phi=\left(\frac{d_m(z)}{(1+z)}\right)^2\sin(\theta)dr_pd\theta d\phi=\frac{d_m(z)^2\sin(\theta)}{(1+z)^2}dr_pd\theta d\phi
\end{equation}

and so all that remains is to express $dr_p$ in terms of $dz$. As the LOS proper distance between two objects $r_p(z)$ is related to the LOS comoving distance $d_C(z)$ by

\begin{equation}\label{physical2comoving}
r_p(z)=a(z)d_C(z)=\frac{d_C(z)}{1+z}=\frac{d_H}{1+z}\int_0^z\frac{dz^\prime}{E(z^\prime)},
\end{equation}

it follows that that an infinitesimal proper displacement $dr_p$ is given by

\begin{equation}\label{physical2comoving_inf}
dr_p=\frac{d_H}{E(z)(1+z)}dz.
\end{equation}

Combining this result with Equation \eqref{temp_solution} leads to the desired proper volume element given by

\begin{align}
dV_p&=\frac{d_m(z)^2\sin(\theta)}{(1+z)^2}dr_pd\theta d\phi\nonumber\\
&=\frac{d_m(z)^2\sin(\theta)}{(1+z)^2}\left(\frac{d_H}{E(z)(1+z)}dz\right)d\theta d\phi\nonumber\\
&=\frac{d_Hd_M(z)^2\sin(\theta)}{E(z)(1+z)^3}dzd\theta d\phi.
\end{align}

We can calculate the proper volume of a given grid slice at redshift $z$ in a foreground catalog centered at ($\theta,\phi$) by integrating the above volume element over the $\Delta z$, $\Delta\theta$, and $\Delta\phi$ range of the redshift slice:

\begin{equation}
V(z)=\int_{V_z}dV_p=d_H\int_{z-\frac{\Delta z}{2}}^{z+\frac{\Delta z}{2}}\int_{\theta-\frac{\Delta\theta}{2}}^{\theta+\frac{\Delta\theta}{2}}\int_{\phi-\frac{\Delta\phi}{2}}^{\phi+\frac{\Delta\phi}{2}} \frac{d_M(z^\prime)^2\sin(\theta^\prime)}{E(z^\prime)(1+z^\prime)^3}dz^\prime d\theta^\prime d\phi^\prime.
\end{equation}

Integrating over $d\theta^\prime$ and $d\phi^\prime$ and using the trig identity ${\cos(u)-\cos(v)=2\sin\left(\frac{u+v}{2}\right)\sin\left(\frac{u-v}{2}\right)}$ gives

\begin{equation}\label{volume_final}
V(z)=2d_H\Delta\phi\sin(\theta)\sin(\Delta\theta/2)\int_{z-\frac{\Delta z}{2}}^{z+\frac{\Delta z}{2}} \frac{d_M(z^\prime)^2\sin(\theta^\prime)}{E(z^\prime)(1+z^\prime)^3}dz^\prime d\theta^\prime d\phi^\prime
\end{equation}

which is our final expression for the proper volume.\\

With the proper volume calculated, the halo mass density $\rho_h(z)$ is simply the sum of the individual halo masses $M_{i,z}$ in the $z$-plane divided by Equation \eqref{volume_final}:

\begin{equation}\label{rho_h}
\rho_h(z)=\frac{\sum_i M_{i,z}}{V(z)}=\frac{\sum_i M_{i,z}}{2d_H\Delta\phi\sin(\theta)\sin(\Delta\theta/2)\int_{z-\frac{\Delta z}{2}}^{z+\frac{\Delta z}{2}} \frac{d_M(z^\prime)^2\sin(\theta^\prime)}{E(z^\prime)(1+z^\prime)^3}dz^\prime d\theta^\prime d\phi^\prime}.
\end{equation}

\subsection*{Calculating $\bm{\rho_s(z)}$:}

Now that $\rho_m(z)$ and $\rho_h(z)$ have been calculated, the smooth-component correction $\rho_s(z)$ is simply the difference between the two:

\begin{align}\label{smooth_component} 
\rho_s(z)&=\rho_m(z)-\rho_h(z)\nonumber\\
&=\left(\frac{3H_0^2}{8\pi G}\,\Omega_{m,0}\right)(1+z)^3 - \frac{\sum_i M_{i,z}}{2d_H\Delta\phi\sin(\theta)\sin(\Delta\theta/2)\int_{z-\frac{\Delta z}{2}}^{z+\frac{\Delta z}{2}} \frac{d_M(z^\prime)^2\sin(\theta^\prime)}{E(z^\prime)(1+z^\prime)^3}dz^\prime d\theta^\prime d\phi^\prime}
\end{align}

where $\rho_s(z)$ is a discrete function only evaluated at the $N$ values of $z$. Finally, note that this equation needs a small correction in the integral bounds for the boundary cases of $z=0$ and $z=1.3857$. Simply change the bounds to ($0,\Delta z$) and ($z-\Delta z,z$) respectively.

\end{document}

% Assumptions: only slow moving (not just non-relativistic!) mass, all extra matter in a sheet, same sigma_crit for the whole plane,

### 2016-04-27 doc/void_correction.tex
Fixed small typo in trig identity.

@@
 
-Integrating over $d\theta^\prime$ and $d\phi^\prime$ and using the trig identity ${\cos(u)-\cos(v)=2\sin\left(\frac{u+v}{2}\right)\sin\left(\frac{u-v}{2}\right)}$ gives
+Integrating over $d\theta^\prime$ and $d\phi^\prime$ and using the trig identity ${\cos(u)-\cos(v)=-2\sin\left(\frac{u+v}{2}\right)\sin\left(\frac{u-v}{2}\right)}$ gives
 

### 2016-05-10 pangloss/background.py
Made changes to `background.py`, `kappamap.py`, `shearmap.py`, and `wlmap.py` to prepare for merge with the `bin_to_maps` branch. #68

@@ -1,7 +1,7 @@
 import numpy as np
 import scipy as sp
 import matplotlib.pyplot as plt
-import os, random, math, cmath, sys, timeit, cProfile
+import os, random, math, cmath, sys, timeit, cProfile, pylab
 import cPickle as pickle
 from astropy.table import Table, Column
 from matplotlib.patches import Ellipse
@@ -55,6 +55,9 @@ class BackgroundCatalog(pangloss.Catalog):
     HISTORY
       2015-06-29  Started Everett (SLAC)
     """
+
+    # ============================================================================
+
     def __init__(self,domain=None,field=None,N=10,mag_lim=[24.0,0.0],mass_lim=[10.0**6,10.0**12],z_lim=[1.3857,1.3857],sigma_e=0.2):
         self.type = 'background'
 
@@ -613,15 +616,87 @@ class BackgroundCatalog(pangloss.Catalog):
 
         return
 
-    def bin_to_map(self,data=['kappa','gamma1','gamma2'],binsize=1.0,bin_units='arcmin'):
+    def bin_to_maps(self,lensed='none',binsize=1.0,center=None):
         '''
-        Bin the background galaxies into WLMaps with data set in the list 'data'. Binsize is in units of arcmin.
+        Bin the background galaxies into WLMaps. We always make both
+        a kappa map and a shear map - the 'lensed' kwarg tells us
+        which type of lensing, by 'halo's or 'map's, has been applied.
+        Binsize is in units of arcmin, and an optional map centroid is
+        passed in as the 'center' list [ra,dec] where these world
+        coordinates are in degrees.
         '''
-        # If a single string is passed for data, turn into list
-        if type(data) == str:
-            data = [data]
 
-        # Finish!!
+        maps=['kappa','gamma1','gamma2']
+
+        count = 0
+        for map in maps:
+
+            if count == 0:
+                # Set up x and y bins - only need to do this the first
+                # time through!
+
+                ra,dec = self.galaxies['RA'],self.galaxies['Dec']
+                decmin,decmax = np.min(dec),np.max(dec)
+                NY = int( np.rad2deg(decmax-decmin)*60.0/binsize )
+                ramin,ramax = np.min(ra),np.max(ra)
+                NX = int( np.rad2deg(ramax-ramin)*60.0/(binsize*np.cos(np.deg2rad(np.mean(dec)))) )
+
+                rabins = np.linspace(ramin,ramax,NX+1)
[…]

### 2016-05-10 tests/lens_compare.py
Updated to allow merge with `bin_to_maps` branch. #68

@@ -56,9 +56,9 @@ if vb is True: print('Generating background catalog...')
 #d = [1.85,1.15,-1.85,-1.15]
 #d = [1.75,1.25,-1.75,-1.25]
 #d = [1.65,1.35,-1.65,-1.35]
-d = [1.6,1.4,-1.6,-1.4] # 1440 galaxies
+#d = [1.6,1.4,-1.6,-1.4] # 1440 galaxies
 #d = [1.55,1.45,-1.55,-1.45]
-#d = [1.55,1.48,-1.55,-1.48] # 176 galaxies
+d = [1.55,1.48,-1.55,-1.48] # 176 galaxies
 #d = [1.55,1.52,-1.61,-1.59] # only galaxies in subplot
 #d = [1.55,1.54,-1.61,-1.6] # ~3 galaxies
 B = pangloss.BackgroundCatalog(N=10.0,sigma_e=0.01,domain=d,field=[0,0,0,0])

### 2016-05-10 pangloss/background.py
Added files for merge with `wl` branch

@@ -1,0 +1,1044 @@
+import numpy as np
+import scipy as sp
+import matplotlib.pyplot as plt
+import os, random, math, cmath, sys, timeit, cProfile, pylab
+import cPickle as pickle
+from astropy.table import Table, Column
+from matplotlib.patches import Ellipse
+from mpl_toolkits.axes_grid1.anchored_artists import AnchoredSizeBar
+
+# Fast correlation functions:
+try:
+    import treecorr
+except ImportError:
+    import pangloss.nocorr as treecorr
+
+# Import Pangloss:
+PANGLOSS_DIR = os.path.expandvars("$PANGLOSS_DIR")
+sys.path.append(PANGLOSS_DIR)
+import pangloss
+
+# Verbose
+vb = True
+
+# Record CPU time per lightcone?
+time = True
+
+# ============================================================================
+
+class BackgroundCatalog(pangloss.Catalog):
+    """
+    NAME
+        BackgroundCatalog
+
+    PURPOSE
+        Generate a catalog of source galaxies, and be able to plot or write out
+        catalog data.
+
+    COMMENTS
+        Inherits from the super class Catalog in catalog.py
+
+    INITIALISATION
+        ???
+
+    METHODS
+        generate()
+        write(output)
+
+    BUGS
+
+    AUTHORS
+      This file is part of the Pangloss project, distributed under the
+      GPL v2, by Tom Collett (IoA) and  Phil Marshall (Oxford).
+      Please cite: Collett et al 2013, http://arxiv.org/abs/1303.6564
+
+    HISTORY
+      2015-06-29  Started Everett (SLAC)
+    """
+
+    # ============================================================================
+
+    def __init__(self,domain=None,field=None,N=10,mag_lim=[24.0,0.0],mass_lim=[10.0**6,10.0**12],z_lim=[1.3857,1.3857],sigma_e=0.2):
+        self.type = 'background'
+
+        # Only a subplot OR a field is allowed, not both!
+        assert not (domain is not None and field is None)
+
+        # The catalog can be created over a field corresponding to a foreground catalog (1 deg^2) or over an inputted subplot
+        if domain is not None and field is not None:
+            self.map_x = field[0]
+            self.map_y = field[1]
+            self.field_i = field[2]
+            self.field_j = field[3]
+            # NB: the domain and field may still be incompatible! Should really check for this.
+
[…]

### 2016-05-10 pangloss/plotting.py

@@ -1,0 +1,1017 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import os, sys
+from astropy.table import Table, Column
+from matplotlib.patches import Ellipse
+from matplotlib.collections import LineCollection
+from mpl_toolkits.axes_grid1.anchored_artists import AnchoredSizeBar
+
+# Import Pangloss:
+PANGLOSS_DIR = os.path.expandvars("$PANGLOSS_DIR")
+sys.path.append(PANGLOSS_DIR)
+import pangloss
+
+viewport = [0.1,0.1,0.8,0.8]
+
+# ============================================================================
+
+"""
+NAME
+    plotting
+
+PURPOSE
+    A collection of functions related to coordinate conversions and plotting,
+    useful for maps, catalogs, and lightcones.
+
+COMMENTS
+
+FUNCTIONS
+    make_axes(fig,subplot,imsubplot):    Creates axes for plotting maps and catalogs.
+
+    set_figure_size(fig,fig_size,Lx,Ly):    Changes figure size.
+
+    plot_ellipse(ra,dec,size,mod,phi,axis,color,alpha):    Plot an ellipse at (ra,dec) with
+                                                           given modulus and angle phi.
+
+    plot_sticks(ra,dec,mod,phi,axis,color):    Plot ellipticity stick at (ra,dec) with given
+                                               modulus, angle, and color.
+
+    plot_corr(corr,corr_type,corr_comp,sep_units,lensed,color,
+                            line_style,fig_size,M,galaxy_count):    Plot the correlation function component of
+                                                                    the given correlation type.
+
+    The following are used to create a demonstrative plot of how correlation functions describe
+    the lensing of galaxies:
+    calc_corr_demo(units):
+    plot_corr_demo(corr,corr_type,units):
+    plot_lensed_colors(B,subplot,center,fig_size):
+    calc_corr_components(points):
+    plot_corr_component(r,corr,corr_type,c):
+    plot_corr_color_demo(N):
+
+BUGS
+    None
+
+AUTHORS
+  This file is part of the Pangloss project, distributed under the
+  GPL v2, by Tom Collett (IoA) and  Phil Marshall (Oxford).
+  Please cite: Collett et al 2013, http://arxiv.org/abs/1303.6564
+
+HISTORY
[…]

### 2016-05-10 pangloss/wlmap.py

@@ -1,0 +1,431 @@
+
+import numpy as np, os, string
+import struct
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+
+arcmin2rad = (1.0/60.0)*np.pi/180.0
+rad2arcmin = 1.0/arcmin2rad
+deg2rad = np.pi/180.0
+rad2deg = 1.0/deg2rad
+
+vb = False
+
+class WLMap:
+    """
+    NAME
+        WLMap
+
+    PURPOSE
+        Superclass for kappamap and gammamap. Used to read in, store,
+        transform and interrogate either a convergence or shear map.
+
+    COMMENTS
+        A "physical" coordinate system is used, where x = -RA (rad)
+        and y = Dec (rad). This is the system favoured by Hilbert et al.
+
+    INITIALISATION
+        mapfile      List of file names containing a convergence or shear map.
+        FITS           Data file format (def=True)
+
+    METHODS
+        read_in_fits_data(self):
+
+        read_in_binary_data(self): to cope with hilbert's homegrown format
+
+        setwcs(self): simulated maps often don't have WCS
+
+        get_fits_wcs(self,hdr,i):
+
+        write_out_to_fits(self,i):
+
+        image2physical(self,i,j,mapfile=0): coord transformation, returns x,y
+
+        physical2image(self,x,y,mapfile=0): coord transformation, returns i,j
+
+        image2world(self,i,j,mapfile=0): coord transformation, returns a,d
+
+        world2image(self,a,d,mapfile=0): coord transformation, returns a,d
+
+        at(self,x,y,mapfile=0,coordinate_system='physical'): return pixel values
+
+        lookup(self,i,j,mapfile): return pixel values given image coords
+
+    BUGS
+
+    AUTHORS
+      This file is part of the Pangloss project, distributed under the
+      GPL v2, by Tom Collett (IoA) and  Phil Marshall (Oxford).
+      Please cite: Collett et al 2013, http://arxiv.org/abs/1303.6564
+
+    HISTORY
+      2015-06-24  Started Everett (SLAC)
+    """
+
+    def __init__(self,mapfiles=None,data=None,FITS=True):
+
+        assert not (mapfiles is not None and data is not None), \
+        "Error: Can only input mapfiles or data; not both!"
+
+        # Make a WLMap by reading in data from a file.
+        # Mapfile should be inputted as list, but is automatically
+        # converted to a list if it is a single file string
+        if mapfiles is not None:
[…]

### 2016-05-10 tests/lens_compare.py
Added one more file for merge

@@ -1,0 +1,209 @@
+# Script to run the `LensByHalo` and `CalculateCorr` demos outside of the notebook
+
+import numpy as np
+import scipy as sp
+import os,sys
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import cmath, cProfile
+import copy
+import cPickle as pickle
+from mpl_toolkits.axes_grid1.anchored_artists import AnchoredSizeBar
+
+# Turn on for verbose
+vb = True
+
+# Turn on for pickling correlation data
+pickle = False
+
+# Turn on for relevance plots
+rel_plots = False
+
+# Turn on for smooth-component correction plots
+smooth_plots = True
+
+# Turn on for plotting correlation function plots
+corr_plots = True
+
+# Turn on for plotting correlation function comparrison plots for relevant halos
+rel_compare = False
+
+# Turn on for plotting correlation function comparrison plots for smooth-component correctoin
+smooth_compare = False
+
+# Turn on for plotting maps
+maps = False
+
+# Pangloss:
+PANGLOSS_DIR = os.path.expandvars("$PANGLOSS_DIR")
+sys.path.append(PANGLOSS_DIR)
+import pangloss
+
+# Import Shear and Convergence maps
+if vb is True: print('Loading Kappa and Shear maps...')
+K = pangloss.Kappamap(PANGLOSS_DIR+'/data/GGL_los_8_0_0_N_4096_ang_4_rays_to_plane_37_f.kappa',FITS=False)
+S = pangloss.Shearmap([PANGLOSS_DIR+'/data/GGL_los_8_0_0_N_4096_ang_4_rays_to_plane_37_f.gamma_1',PANGLOSS_DIR+'/data/GGL_los_8_0_0_N_4096_ang_4_rays_to_plane_37_f.gamma_2'],FITS=False)
+
+# Import Foreground Catalog
+if vb is True: print('Loading foreground catalog...')
+config = pangloss.Configuration(PANGLOSS_DIR+'/example/example.config')
+F = pangloss.ForegroundCatalog(PANGLOSS_DIR+'/data/GGL_los_8_0_0_0_0_N_4096_ang_4_Guo_galaxies_on_plane_27_to_63.images.txt',config)
+#if smooth_plots is True: F.plot_mean_kappas()
+
+# Generate Background Catalog in the middle of the (0,0,0,0) field
+if vb is True: print('Generating background catalog...')
[…]

### 2016-05-10 doc/void_correction.tex
Removed extraneous infinitesimals from the last three integrals.

--- 2016-04-23 doc/void_correction.tex
@@
 
-Current \texttt{Pangloss} code assumes a cosmology of $\Omega_{m,0}=0.25$, $\Omega_{\Lambda,0}=0.75$ (to ensure a flat universe), and $H_0=73$ km$\cdot$s$^{-1}\cdot$Mpc$^{-1}$ (\textcolor{red}{Were these values chosen to match the original Millennium Simulation parameters?
-A later run that Stefan used for his ray tracing?
-Known values when Collett et al.
-was published?}) which leads to an evolving mass density of
+Current \texttt{Pangloss} code assumes a cosmology of $\Omega_{m,0}=0.25$, $\Omega_{\Lambda,0}=0.75$ (to ensure a flat universe), and $H_0=73$ km$\cdot$s$^{-1}\cdot$Mpc$^{-1}$ which leads to an evolving mass density of
 
@@
 While each galaxy/halo are on a continuum of redshifts, we snap each halo to one of $N$ redshift planes from $z=0$ to the source redshift of $z_s=1.3857$, each separated by a constant $\Delta z=1.3857/N$ for faster computation (typically, $N=100$ and $\Delta z\approx0.014$).
-We can approximate $\rho_h$ at each of the $N$ redshift values by summing the halo masses and dividing by the integral the proper volume element $dV_p$ over the redshift range $z\pm \Delta z/2$ and solid angle $d\Omega$ covered by the foreground catalog.
+We can approximate $\rho_h$ at each of the $N$ redshift values by summing the halo masses and dividing by the integral the proper volume element $dV_p$ over the redshift range $z\pm \Delta z/2$ and solid angle $d\Omega$ covered by the lightcone.
 Figure \ref{rho_slice} visualizes this process.\\
@@
 
-From Figure \ref{rho_slice}, it is clear that we want a proper volume element that is expressed in terms of the solid angle $d\Omega$ (or really, $d\theta d\phi$) and the redshift $dz$.
-To do this, we can start with the standard spherical volume element $dV=r^2\sin(\theta)drd\theta d\phi$.
+From Figure \ref{rho_slice}, it is clear that we want a proper volume element that is expressed in terms of the solid angle $d\Omega$ and the redshift $dz$.
+To do this, we can start with the standard spherical volume element $dV=r^2drd\Omega$.
 However, we must be careful that (1) we are using proper distances, (2) account for the possibility of a curved universe, and (3) use the correct distance measure for $r$ (in this case, the angular diameter distance).
@@
 \begin{equation}\label{proper_element}
-dV_p=dr_pdA=d_A(z)^2dr_pd\omega=d_A(z)^2\sin(\theta)dr_pd\theta d\phi
+dV_p=d_A(z)^2dr_pd\Omega
 \end{equation}
@@
 \begin{equation}\label{temp_solution}
-dV_p=d_a(z)^2\sin(\theta)dr_pd\theta d\phi=\left(\frac{d_m(z)}{(1+z)}\right)^2\sin(\theta)dr_pd\theta d\phi=\frac{d_m(z)^2\sin(\theta)}{(1+z)^2}dr_pd\theta d\phi
+dV_p=d_a(z)^2dr_pd\Omega=\left(\frac{d_m(z)}{(1+z)}\right)^2dr_pd\Omega=\frac{d_m(z)^2}{(1+z)^2}dr_pd\Omega
 \end{equation}
@@
 \begin{align}
-dV_p&=\frac{d_m(z)^2\sin(\theta)}{(1+z)^2}dr_pd\theta d\phi\nonumber\\
-&=\frac{d_m(z)^2\sin(\theta)}{(1+z)^2}\left(\frac{d_H}{E(z)(1+z)}dz\right)d\theta d\phi\nonumber\\
-&=\frac{d_Hd_M(z)^2\sin(\theta)}{E(z)(1+z)^3}dzd\theta d\phi.
+dV_p&=\frac{d_m(z)^2}{(1+z)^2}dr_pd\Omega\nonumber\\
+&=\frac{d_m(z)^2}{(1+z)^2}\left(\frac{d_H}{E(z)(1+z)}dz\right)d\Omega\nonumber\\
+&=\frac{d_Hd_M(z)^2}{E(z)(1+z)^3}dzd\Omega.
 \end{align}
 
-We can calculate the proper volume of a given grid slice at redshift $z$ in a foreground catalog centered at ($\theta,\phi$) by integrating the above volume element over the $\Delta z$, $\Delta\theta$, and $\Delta\phi$ range of the redshift slice:
+We can calculate the proper volume of the lightcone a given grid slice at redshift $z$ in a foreground catalog centered at ($\theta,\phi$) by integrating the above volume element over the solid angle $d\Omega$ and $\Delta z$ range of the redshift slice:
 
 \begin{equation}
-V(z)=\int_{V_z}dV_p=d_H\int_{z-\frac{\Delta z}{2}}^{z+\frac{\Delta z}{2}}\int_{\theta-\frac{\Delta\theta}{2}}^{\theta+\frac{\Delta\theta}{2}}\int_{\phi-\frac{\Delta\phi}{2}}^{\phi+\frac{\Delta\phi}{2}} \frac{d_M(z^\prime)^2\sin(\theta^\prime)}{E(z^\prime)(1+z^\prime)^3}dz^\prime d\theta^\prime d\phi^\prime.
+V(z)=\int_{V_z}dV_p=d_H\int_\Omega\int_{z-\frac{\Delta z}{2}}^{z+\frac{\Delta z}{2}} \frac{d_M(z^\prime)^2}{E(z^\prime)(1+z^\prime)^3}dz^\prime d\Omega.
 \end{equation}
 
-Integrating over $d\theta^\prime$ and $d\phi^\prime$ and using the trig identity ${\cos(u)-\cos(v)=2\sin\left(\frac{u+v}{2}\right)\sin\left(\frac{u-v}{2}\right)}$ gives
+Integrating over $d\Omega$ results in the solid angle of a cone given by $\Omega=2\pi(1-\cos\theta)$, so the previous equation becomes
 
 \begin{equation}\label{volume_final}
-V(z)=2d_H\Delta\phi\sin(\theta)\sin(\Delta\theta/2)\int_{z-\frac{\Delta z}{2}}^{z+\frac{\Delta z}{2}} \frac{d_M(z^\prime)^2\sin(\theta^\prime)}{E(z^\prime)(1+z^\prime)^3}dz^\prime d\theta^\prime d\phi^\prime
+V(z)=2\pi(1-\cos\theta)d_H\int_{z-\frac{\Delta z}{2}}^{z+\frac{\Delta z}{2}} \frac{d_M(z^\prime)^2}{E(z^\prime)(1+z^\prime)^3}dz^\prime
 \end{equation}
 
-which is our final expression for the proper volume.\\
+which is our final equation for the proper volume.\\
 
@@
 \begin{equation}\label{rho_h}
-\rho_h(z)=\frac{\sum_i M_{i,z}}{V(z)}=\frac{\sum_i M_{i,z}}{2d_H\Delta\phi\sin(\theta)\sin(\Delta\theta/2)\int_{z-\frac{\Delta z}{2}}^{z+\frac{\Delta z}{2}} \frac{d_M(z^\prime)^2\sin(\theta^\prime)}{E(z^\prime)(1+z^\prime)^3}dz^\prime d\theta^\prime d\phi^\prime}.
+\rho_h(z)=\frac{\sum_i M_{i,z}}{V(z)}=\frac{\sum_i M_{i,z}}{2\pi(1-\cos\theta)d_H\int_{z-\frac{\Delta z}{2}}^{z+\frac{\Delta z}{2}} \frac{d_M(z^\prime)^2}{E(z^\prime)(1+z^\prime)^3}dz^\prime}.
 \end{equation}
@@
 \rho_s(z)&=\rho_m(z)-\rho_h(z)\nonumber\\
-&=\left(\frac{3H_0^2}{8\pi G}\,\Omega_{m,0}\right)(1+z)^3 - \frac{\sum_i M_{i,z}}{2d_H\Delta\phi\sin(\theta)\sin(\Delta\theta/2)\int_{z-\frac{\Delta z}{2}}^{z+\frac{\Delta z}{2}} \frac{d_M(z^\prime)^2\sin(\theta^\prime)}{E(z^\prime)(1+z^\prime)^3}dz^\prime d\theta^\prime d\phi^\prime}
+&=\left(\frac{3H_0^2}{8\pi G}\,\Omega_{m,0}\right)(1+z)^3 - \frac{\sum_i M_{i,z}}{2\pi(1-\cos\theta)d_H\int_{z-\frac{\Delta z}{2}}^{z+\frac{\Delta z}{2}} \frac{d_M(z^\prime)^2}{E(z^\prime)(1+z^\prime)^3}dz^\prime}
 \end{align}

### 2016-05-10 tests/lens_compare.py
Removed unecessary end of `lens_compare.py`.

@@ -32,9 +32,6 @@ rel_compare = False
 smooth_compare = False
 
 # Turn on for plotting maps
-maps = False
-
-# Turn on for plotting maps
 maps = True
 
 # Pangloss:
@@ -183,50 +180,6 @@ if corr_plots is True:
             std_rel = None
         pangloss.plotting.compare_smooth_component(gg_map,gg_halo,gg_halo_s,corr_type='gg',galaxy_count=B.galaxy_count,radius=lc_radius,rel_halos=[mean_rel,std_rel])
         pangloss.plotting.compare_smooth_component(ng_map,ng_halo,ng_halo_s,corr_type='ng',galaxy_count=B.galaxy_count,radius=lc_radius,rel_halos=[mean_rel,std_rel])
-
-B.drill_lightcones(radius=2.0,foreground=F,save=False)
-
-# Calculate mean/std galaxies per lightcone
-galaxy_counts = [B.lightcones[i].galaxy_count for i in range(len(B.lightcones))]
-mean_galaxies = np.mean(galaxy_counts)
-std_galaxies = np.std(galaxy_counts)
-#important_counts = [B.lightcones[i] for i in range(len(B.lightcones))]
-#mean_important = np.mean(galaxy_counts)
-#std_important = np.std(galaxy_counts)
-print 'Lightcones have',mean_galaxies,'+/-',std_galaxies,'galaxies'
-#print 'Lightcones have',mean_important,'+/-',std_important,'important galaxies'
-
-# Lens the background catalog by foreground halos
-if vb is True: print('Lensing background by halos..')
-cProfile.run('B.lens_by_halos(importance_lim=0.0); print')
-#B.lens_by_halos(importance_lim=0.0)
-
-# Calculate the correlation function for each lensing type
-if vb is True: print('Calculating correlation...')
-gg_map = B.calculate_corr(corr_type='gg',lensed='map')
-gg_halo = B.calculate_corr(corr_type='gg',lensed='halo')
-ng_map = B.calculate_corr(corr_type='ng',lensed='map')
-ng_halo = B.calculate_corr(corr_type='ng',lensed='halo')
-
-# Plot the correlation functions
-pangloss.plotting.plot_corr(gg_map,corr_type='gg',corr_comp='plus',lensed='map',color='green',galaxy_count=B.galaxy_count)
[…]

### 2016-05-10 pangloss/background.py
Changed `histogram2d` dependency to `numpy`. #68

@@ -1,7 +1,7 @@
 import numpy as np
 import scipy as sp
 import matplotlib.pyplot as plt
-import os, random, math, cmath, sys, timeit, cProfile, pylab
+import os, random, math, cmath, sys, timeit, cProfile
 import cPickle as pickle
 from astropy.table import Table, Column
 from matplotlib.patches import Ellipse
@@ -709,8 +709,8 @@ class BackgroundCatalog(pangloss.Catalog):
             # gives the sum of the map contributions, the second the
             # number of map contributions. We want the simple average,
             # so we divide one by the other.
-            H,x,y = pylab.histogram2d(ra,dec,weights=values,bins=[rabins,decbins])
-            N,x,y = pylab.histogram2d(ra,dec,bins=[rabins,decbins])
+            H,x,y = np.histogram2d(ra,dec,weights=values,bins=[rabins,decbins])
+            N,x,y = np.histogram2d(ra,dec,bins=[rabins,decbins])
 
             if map == 'kappa':
                 kappadata[0] = H/N

### 2016-05-10 pangloss/wlmap.py
Fixed constructor assertions for the case of inputted `data` to the correct relationships. #68

@@ -80,7 +80,10 @@ class WLMap:
             assert len(data) == 3
             d,x,y = data[0],data[1],data[2]
             assert len(d.shape) == 3
-            assert d[0].shape == d[1].shape == d[2].shape == x.shape == y.shape
+            assert d[0].shape == d[1].shape
+            assert d[0].shape[0] == d[1].shape[0] == x.shape[0]-1
+            assert d[0].shape[1] == d[1].shape[1] == y.shape[0]-1
+            assert x.shape == y.shape
             self.input = ['']
             self.origin = 'scratch'
 

### 2016-05-10 pangloss/lightcone.py
Fixed a few angle unit errors in the constructor. #68

@@ -96,7 +96,7 @@ class Lightcone(object):
         self.rmax = radius
         self.xc = [position[0],position[1]]
 
-        dx = np.deg2rad(self.rmax/60.0)
+        dx = self.rmax*pangloss.arcmin2rad
         # Ra is flipped as it is left-handed
         self.galaxies = self.catalog[np.where((self.catalog['RA'] > (self.xc[0]-dx)) & \
                                               (self.catalog['RA'] < (self.xc[0]+dx)) & \
@@ -105,7 +105,7 @@ class Lightcone(object):
 
         # Trim it to a circle:
         x = -np.cos(self.galaxies['Dec'])*(self.galaxies['RA'] - self.xc[0])*pangloss.rad2arcmin
-        y = np.deg2rad((self.galaxies['Dec'] - self.xc[1])/60.0)
+        y = (self.galaxies['Dec'] - self.xc[1])*pangloss.rad2arcmin
         r = np.sqrt(x*x + y*y)
         phi = np.arctan2(y,x)
         self.writeColumn('x',x)
@@ -320,7 +320,7 @@ class Lightcone(object):
         self.writeColumn('rho_crit',Grid.rho_crit[p])
         self.writeColumn('sigma_crit',Grid.sigma_crit[p])
         self.writeColumn('beta',Grid.beta[p])
-        rphys = np.deg2rad(self.galaxies['r']/60.0)*self.galaxies['Da_p']
+        rphys = self.galaxies['r']*pangloss.arcmin2rad*self.galaxies['Da_p']
         self.writeColumn('rphys',rphys)
 
         # Write foreground mean kappas for foreground correction (0 if foreground kappas not inputed)

### 2016-05-17 doc/thesis_swe.tex
Added a few brainstorming notes for new void correction and relevant halos sections.
Added some headings and notes for planned additional sections.

@@
 \usepackage{mathtools}
+\usepackage{color}
 %\usepackage{float}
@@
 The \texttt{Pangloss} predicted lensed source ellipticity is then calculated using Equation \eqref{lensing}.
+
+\subsection*{Relevant Halos}
+\begin{enumerate}
+\item Metric from McCully et al. (cite)
+\item Implementation
+\item Plot the percent difference between all halos and relevant halos as a function of $\#$ of relevant halos (can adopt relevant-test.py to do this)
+\end{enumerate}
+
+\subsection*{Smooth-Component Correction}
+\begin{enumerate}
+\item Introduce issue
+\item Either derive result or state result with derivation in appendix
+\item Plots of volume/surface density of halos vs mean universe density
+\item Plot distribution of correction kappas
+\item Plot distribution of reduced-shear with and without correction
+\end{enumerate}
+
+\subsection*{Speedups}
+\begin{enumerate}
+\item Lookup tables (lensing table)
+\item relevant halos
+\item pre-calculate grid volumes for s-c correction
+\item more plots to quantify speedup times!
+\end{enumerate}
 
@@
 
+\subsection*{Feasibility of Inference}
+
+\subsubsection*{Likelihood Estimation}
+\begin{enumerate}
+\item Equation from Phil's dissertation
+\item Calculate time with and without drilling
+\item Time per lensing event, time per lightcone
+\end{enumerate}
+
+\subsubsection*{Approximate Bayesian Computation}
+\begin{enumerate}
+\item Difficult to calculate likelihood, can instead make mock data by samping parameters from prior distribution
+\item Come up with `distance' function (compare e-e corr functions) and threshold value
+\item Use accepted simulations to approximate posterior
+\item Time per ABC
+\item Compare time to single lensing event
+\end{enumerate}
+
 \section{Results}
@@
 \end{figure}
+
+\subsection*{Smooth-Component Correction Derivation}
+
+\subsection*{TreeCorr to Schneider Proof}
 

### 2016-05-23 doc/thesis_swe.tex
Restructured thesis and added new content throughout. Temporarily removed most figures to focus on the text. Changed heading formatting to left-justified arabic numerals.

--- 2016-04-05 doc/thesis_swe.tex
@@
 \usepackage{subcaption}
+\usepackage[titletoc]{appendix}
 %\usepackage{multicol}
@@
 
+%----------------------------------------------------------------------
+% %% Use to make section/subsection titles left-justified
+\usepackage{etoolbox}
+\patchcmd{\section}
+  {\centering}
+  {\raggedright}
+  {}
+  {}
+\patchcmd{\subsection}
+  {\centering}
+  {\raggedright}
+  {}
+  {}
+%----------------------------------------------------------------------           
+% %% Use to make new section/subsection formatting
+\usepackage{titlesec}
+\usepackage{tocloft}
+\renewcommand{\thesection}{\arabic{section}}
+\titleformat{\section}{\normalfont\bfseries\uppercase}{\thesection}{0.5em}{}
+\renewcommand{\thesubsection}{\thesection.\arabic{subsection}}
+\titleformat{\subsection}{\normalfont\bfseries}{\thesubsection}{0.5em}{}
+\renewcommand{\thesubsubsection}{\thesubsection.\arabic{subsubsection}}
+\titleformat{\subsubsection}{\normalfont\bfseries}{\thesubsubsection}{0.5em}{}
+%----------------------------------------------------------------------
+
 % Used for .bib file
@@
 
-\preprint{APS/123-QED}
-
 \title{SPENCER THESIS - WORK IN PROGRESS}
@@
 \author{Spencer Everett}
- \affiliation{Department of Physics, DePaul University,\\SLAC National Laboratory}
+ \affiliation{Department of Physics, DePaul University}
  %\affiliation{SLAC National Laboratory}
@@
 
+%%==========================================================================================================================================
 \begin{abstract}
-As dark matter does not absorb or emit light, its distribution in the universe must be inferred through indirect effects such as the gravitational lensing of distant galaxies.
+\noindent (TEMPORARY) Recent evidence suggests that dark matter dominates over the normal matter we experience in everyday life, yet we are unable to directly map it as it does not absorb or emit light.
+Being able to predict high-resolution dark matter mass maps would be interesting in of itself, but from this we can also study structure formation and constrain the parameters of the universe.
+In this work, I develop the Pangloss model which approximates complex mass distributions with a simple dark matter halo model and then analyze how accurate its predictions can be using weak gravitational lensing data in the Millennium Simulation.
+I then do some exploratory work in estimating how feasible a large inference would be using both likelihood estimation and approximate Bayesian computation (ABC).
+I found that ...
+
+% OLD: As dark matter does not absorb or emit light, its distribution in the universe must be inferred through indirect effects such as the gravitational lensing of distant galaxies.
 While most sources are only weakly lensed, the systematic alignment of background galaxies around a foreground lens can constrain the mass of the lens which is largely in the form of dark matter.
@@
 
+%%==========================================================================================================================================
 \section{Introduction}
 
-In a universe teeming with galaxies and light, it came as a shock when 20\textsuperscript{th} century astronomers discovered that most of the mass in the universe is in fact dark; the `normal' matter made of atoms that we interact with in everyday life, called baryonic matter, accounts for less than 20\% of the mass in the observable universe.
+Intro\\
+
+Place in context of recent work\\
+
+The goals of this thesis are two answer the two following questions: How accurately can we reconstruct line-of-sight dark matter mass structures using a halo model?
+From our model outputs, how feasible is an inference of the stellar mass – halo mass relation parameters?\\
+
+Outline thesis
+
+% OLD: In a universe teeming with galaxies and light, it came as a shock when 20\textsuperscript{th} century astronomers discovered that most of the mass in the universe is in fact dark; the `normal' matter made of atoms that we interact with in everyday life, called baryonic matter, accounts for less than 20\% of the mass in the observable universe.
 The remaining mass takes the form of an exotic dark matter that does not absorb or emit light, rendering it invisible to our telescopes.
@@
 
-One of the most successful probes of dark matter has been gravitational lensing.
+% One of the most successful probes of dark matter has been gravitational lensing.
 The path of light from distant `background' galaxies is bent when traveling through regions of space containing large amounts of `foreground' mass.
@@
 
-While the effects of gravitational lensing can be dramatic, the shape of most galaxies is only distorted by a few percent and must be detected statistically as the intrinsic shape is not known.
+% While the effects of gravitational lensing can be dramatic, the shape of most galaxies is only distorted by a few percent and must be detected statistically as the intrinsic shape is not known.
 If a model for the distribution of dark matter in a region of foreground mass can accurately predict the statistical signal of this `weak' lensing of background sources, then the model can be used on galaxies in existing sky survey data to extrapolate the amount of dark matter in the region and construct large-scale maps of the dark matter in the universe.
 
-In this paper, I attempt to do the former by applying a simple dark matter halo model to reconstruct mass along lines of sight in the Millennium Simulation and predict the weakly lensed ellipticities of generated background sources.
+% In this paper, I attempt to do the former by applying a simple dark matter halo model to reconstruct mass along lines of sight in the Millennium Simulation and predict the weakly lensed ellipticities of generated background sources.
 A brief introduction into the theory of galaxy ellipticities, the effects of strong and weak gravitational lensing, and dark matter halos is discussed in Section II.
@@
 
-\section{Theoretical Background}
-
-\subsection*{Galaxies as Ellipses}
-Consider a galaxy image that can be well approximated as an ellipse at an angle $\phi$ above an arbitrary reference line. The galaxy's complex ellipticity is defined to be
-\begin{equation}\label{complex_ellipticity}
-\varepsilon=\varepsilon_1+i\varepsilon_2=|\varepsilon|\,e^{2i\phi}
-\end{equation}
-
-\noindent where the magnitude of the galaxy's ellipticity $|\varepsilon|$ is defined as
+%%==========================================================================================================================================
+\section{Cosmological Background}
+
+Before describing the developed model for line-of-sight dark matter mass map reconstructions from weak lensing measurements, I briefely review a few topics in astronomy and cosmology that are relevant for this thesis such as the dark matter halo model, gravitational lensing, and correlation functions.
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Dark Matter Halos}
+
+Cosmological simulations like the Millennium Simulation (MS) demonstrate that the underlying dark matter distribution of our universe is likely breathtakingly complex; rather than a largely disordered collection of galaxies and interstellar gas, matter appears to condense into clusters and superclusters of galaxies threaded together by large filaments (pocketed) with under-dense regions called voids, as shown in Figure ??(1.a) (CITE MS).
+While the exact relation between the distribution of galaxies and dark matter is not known, simulations predict that early galaxies formed in the large gravitational potentials of over-dense regions of dark matter (CITE!).
+This suggests that, while we cannot map dark matter directly, galaxies should trace out at least some of the underlying dark matter structures \textcolor{red}{(Citation!)}.
+A comparrison of the predicted galaxy and dark matter distribution from a small region of the MS is shown in Figure (???).
+
+%However, these simulations also indicate that galaxies tend to form in the large gravitational potentials of dark matter over-dense regions of dark matter.
+While the exact relation between the distribution of galaxies and dark matter is not known, this m
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+%% FIGURE: Millennium Simulation Distribution plots (cosmic web, galaxy clusters with/without dark matter)
+% \begin{figure*}
+%     \centering
+%     \begin{subfigure}[H]{0.4\textwidth}
+%         \includegraphics[width=\textwidth]{figs-swe/thesis/ms_galaxies.jpg}
+%         \captionsetup{justification=raggedright,singlelinecheck=false}
+%         \caption{CAPTION}
+%         \label{ms_galaxies}
+%     \end{subfigure}
+%     ~
+%     %% Einstein Ring Figure
+%     \begin{subfigure}[H]{0.4\textwidth}
+%         \includegraphics[width=\textwidth]{figs-swe/thesis/ms_halos.jpg}
+%         \captionsetup{justification=raggedright,singlelinecheck=false}
+%         \caption{CAPTION}
+%         \label{ms_halos}
+%     \end{subfigure}
+%     \caption{}
+% \end{figure*}
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+
+The simplest way to model the relationship between galaxies and the dark matter distribution is by enveloping each galaxy in a spherically symmetric dark matter `halo' of a certain mass $M_h$.
+These halos extend far beyond the edge of the visible galaxy that they enclose, with the Milky Way's own halo estimated to have a radius of \textcolor{red}{(Check and cite!)}.
+While the density profile of the halos may be complex, numerous simulations have shown that it can be well approximated locally by the Navarro-Frenk-White (NFW) profile which has the form
+\begin{equation}\label{nfw_profile}
+\rho_{NFW}(r)=\frac{\rho_0}{\frac{r}{R_s}\left(1+\frac{r}{R_s}\right)^2}
+\end{equation}
+
+\noindent \textcolor{red}{where the constant $\rho_0$ and the scale radius $R_s$ are parameters that vary from halo to halo} \cite{nfw}.
+However, the NFW profile is not entierly physical as the total mass diverges as the desntiy is integrated out to an infinite radius, so this work uses a truncated NFW profile called the Baltz-Marshall-Oguri (BMO) profile given by
+\begin{equation}\label{bmo_profile}
+\rho_{BMO}(r)=\rho_{NFW}\cdot\left(\frac{r_t^2}{r^2+r_t^2}\right)^2
+\end{equation}
+
+\noindent where $r_t$ is the truncation radius as it has been shown to be a better fit to simulated data \cite{nfw_bmo}.
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Filaments, Voids, and the Smooth-Component Correction}
+
+The halo model only accounts for dark matter structures associated with galaxies.
+However, this neglects other structures such as the filaments and voids that can be seen in Figure (??).
+Modelling these features accurately would be difficult; we could try, for example, to model filaments by attaching cylinders of dark matter between massive clusters of galaxies.
+While an intriguing idea, rigorously testing for the appropriate filament density distributions, selection criteria, and frequency to statistically match simulations could constitute its own thesis.
+
+% However, the mean mass density of large enough ($\sim$100 Mpc) regions should approximate the mean mass density of the universe, so for a first guess we can approximate the additional mass as a series of uniform sheets of matter a each redshift that make the total mass density of the foreground catalog equal to the mean density of the universe.
+This assumption can be expressed as
+
+Instead, as the mean mass density of large enough ($\sim$100 Mpc) regions should approximate the mean mass density of the universe, we can make a `first-order' approximation by assuming that all additional mass (or absence of mass) is contained in a uniform `smooth-component' density that ensures the total mass density of any region equals the mean density of the universe at that redshift.
+This assumption can be expressed as
+\begin{equation}\label{smooth_correction1}
+\rho_{\text{matter}}(z)=\rho_{\text{halos}}(z)+\rho_{\text{smooth}}(z)
+\end{equation}
+
+\noindent where $z$ is the redshift and $\rho_{\text{matter}}(z)$, $\rho_{\text{halos}}(z)$, and $\rho_{\text{smooth}}(z)$ are the mean matter densities of the universe, halos, and smooth-component correction respectively.
+For simplicity, we rename theses quantities ${\rho_m(z)}$, ${\rho_h(z)}$, and ${\rho_s(z)}$ so that Equation \eqref{smooth_correction1} now reads as
+\begin{equation}\label{smooth_correction2}
+\rho_m(z)=\rho_h(z)+\rho_s(z).
+\end{equation}
+
+To solve for the desired smooth-component correction, we first need to calcualte ${\rho_m(z)}$ and ${\rho_h(z)}$ and then subtract:
+\begin{equation}\label{smooth_correction2}
+\rho_s(z)=\rho_m(z)-\rho_h(z).
+\end{equation}
+
+\noindent Note that, unlike the halo density, each smooth-component mass sheet at a given $z$ can have positive \textit{or} negative mass density as the halos at that redshift could happen to be in a local overdensity or underdensity.
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsubsection{Calculating $\mathbf{\rho_m(z)}$:}
+
+Using the fluid equation and equation of state \textcolor{red}{(CITE)}, we can show that the energy density of non-relativistic matter $\varepsilon_m(z)$ evolves as
+\begin{equation}\label{energy_evol}
+\varepsilon_m(z)=\frac{\varepsilon_{m,0}}{a(z)^3}=\varepsilon_{m,0}(1+z)^3
+\end{equation}
+
+\noindent where $a(z)=(1+z)^{-1}$ is the cosmic scale factor (${a(0)=1}$ by convention) and a subscript of 0 means the value at the present time, or equivalently a redshift of 0.
+This is physically intuitive as the (mostly constant) mass is being diluted by an expanding volume.
+As the mass is non-relativistic, its energy density can be approximated by
+\begin{equation*}\label{energy_mass}
+\varepsilon_m(z)\approx\rho_m(z)c^2
+\end{equation*}
+
+\noindent and thus
+\begin{equation}\label{mass_evol}
+\rho_m(z)\approx\rho_{m,0}(1+z)^3.
+\end{equation}
+
+The current matter density $\rho_{m,0}$ is usually reported in literature in terms of the present matter density parameter $\Omega_{m,0}$ defined as
+\begin{equation}\label{}
+\Omega_{m,0}=\frac{\rho_{m,0}}{\rho_{c,0}}=\frac{8\pi G}{3H_0^2}\,\rho_{m,0}
+\end{equation}
+
+\noindent where $\rho_{c,0}=\frac{3H_0^2}{8\pi G}$ is the present critical density. Solving for $\rho_{m,0}$ gives
+\begin{equation*}\label{}
+\rho_{m,0}=\frac{3H_0^2}{8\pi G}\,\Omega_{m,0}
+\end{equation*}
+
+\noindent and so we may write the non-relativistic mass density of the universe as a function of redshift as
+\begin{equation}\label{rho}
+\rho_m(z)\approx\left(\frac{3H_0^2}{8\pi G}\,\Omega_{m,0}\right)(1+z)^3.
+\end{equation}
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection*{Calculating $\mathbf{\rho_h(z)}$:}
+
+The halo mass density $\rho_h(z)$ at a given redshift is simply the sum of the individual halo masses $M_{h,i}$ over a physical volume $dV_p$.
+However, we want a proper volume element that is expressed in terms of the solid angle $d\Omega$ and the redshift $dz$.
+To do this, we can start with the standard spherical volume element $dV=r^2drd\Omega$.
+However, we must be careful that (1) we are using proper distances, (2) account for the possibility of a curved universe, and (3) use the correct distance measure for $r$ (in this case, the angular diameter distance).
+From this we can infer that the proper volume element must have the form of
+\begin{equation}\label{proper_element}
+dV_p=d_A(z)^2dr_pd\Omega
+\end{equation}
+
+\noindent where $d_A(z)$ is the angular diameter distance and the subscript $p$ denotes proper distance.
+When the angular diameter distance $d_A(z)$ is multiplied by an angle (i.e.
+$d_A(z)d\theta$ and $d_A(z)d\phi$), it gives an approximation of the proper distance between two objects at the same redshift.
+$d_A(z)$ can be expressed in terms of the transverse comoving distance $d_M(z)$,
+\begin{equation}\label{angular2transverse}
+d_A(z)=a(z)d_M(z)=\frac{d_M(z)}{1+z}
+\end{equation}
+
+\noindent which is the comoving analog of $d_A(z)$. The transverse comoving distance depends on the assumed cosmology of the universe and takes the form of
+\begin{equation}\label{comoving_transverse}
+d_M(z)=\left\{
+     \begin{array}{lr}
+       d_H/\sqrt{\Omega_k}\sinh\left[\sqrt{\Omega_k}d_C(z)/d_H\right] & : \Omega_k>0\\
+       d_C(z) & : \Omega_k=0\\
+       d_H/\sqrt{|\Omega_k|}\sin\left[\sqrt{|\Omega_k|}d_C(z)/d_H\right] & : \Omega_k<0
+     \end{array}
+   \right.
+\end{equation}
+
+\noindent where $d_H=c/H_0$ is the Hubble distance, $\Omega_k$ is the curvature parameter ($\Omega_k=0$ for a flat universe), and $d_C(z)$ is the line-of-sight (LOS) comoving distance given by
+\begin{equation}\label{comoving_distance}
+d_C(z)=d_H\int_0^z\frac{dz^\prime}{E(z^\prime)}
+\end{equation}
+
+\noindent where $E(z)$ is the dimensionless Hubble parameter
+\begin{equation}\label{dim_hubble_parameter}
+E(z)=\sqrt{\Omega_m(1+z)^3+\Omega_k(1+z)^2+\Omega_\Lambda}.
+\end{equation}
+
+\noindent Substituting Equation \eqref{angular2transverse} into \eqref{proper_element} leads to
+\begin{align}\label{temp_solution}
+dV_p&=d_a(z)^2dr_pd\Omega\nonumber\\
+&=\frac{d_m(z)^2}{(1+z)^2}dr_pd\Omega
+\end{align}
+
+\noindent and so all that remains is to express $dr_p$ in terms of $dz$.
+
+As the LOS proper distance between two objects $r_p(z)$ is related to the LOS comoving distance $d_C(z)$ by
+\begin{equation}\label{physical2comoving}
+r_p(z)=a(z)d_C(z)=\frac{d_H}{1+z}\int_0^z\frac{dz^\prime}{E(z^\prime)},
+\end{equation}
+
+\noindent it follows that that an infinitesimal proper displacement $dr_p$ is given by
+\begin{equation}\label{physical2comoving_inf}
+dr_p=\frac{d_H}{E(z)(1+z)}dz.
+\end{equation}
+
+\noindent Combining this result with Equation \eqref{temp_solution} leads to the desired proper volume element given by
 \begin{equation}
-|\varepsilon|=\frac{1-r}{1+r}
-\end{equation}
-
-\noindent and $r\leq1$ is the ratio of the semi-minor and semi-major axes of the ellipse.
-This compact notation combines the eccentricity and orientation of the ellipse into a single object.
-A plot from Schneider et al.
-\cite{schneider} showing the shape of elliptical galaxies for various values of $\varepsilon_1$ and $\varepsilon_2$ is shown in Figure \ref{ellipses}.
-
-There are many complications to using this scheme in practice, most notably the multiplicative bias resulting from the smearing of galaxy images by the observational point spread function (PSF) \cite{multiplicative_bias}.
-While the effects of a PSF can be complex, in general it causes galaxy images to appear less elliptical than they truly are.
-To account for this in generated galaxy images, a multiplicative bias parameter $M$ is often used to lessen the intrinsic ellipticity using
-$$\varepsilon_{obs}=M\cdot\varepsilon_{int}$$
-
-\noindent where $\varepsilon_{int}$ is the generated intrinsic ellipticity of the image and $\varepsilon_{obs}$ is the ellipticity that would be recorded by a detector.
-
-\subsection*{Gravitational Lensing}
-
+dV_p=\frac{d_Hd_M(z)^2}{E(z)(1+z)^3}dzd\Omega.
+\end{equation}
+
+The proper volume is found by integrating the above volume element over the solid angle $d\Omega$ and the desired $dz$ range, so the halo density $\rho_h(z)$ is then given by
+
+\begin{align}\label{rho_h}
+\rho_h(z)&=\frac{\sum_i M_{h,i}}{V(z)}\nonumber\\
+&=\sum_i M_{h,i}\cdot\left(d_H\int\frac{d_M(z^\prime)^2}{E(z^\prime)(1+z^\prime)^3}dz^\prime d\Omega\right)^{-1}.
+\end{align}
+
+\noindent and the smooth-component correction is simply the difference between Equations \eqref{rho} and \eqref{rho_h}.
+
+% With this, the proper volume of olume of the lightcone a given grid slice at redshift $z$ in a foreground catalog centered at ($\theta,\phi$) by integrating the above volume element over the solid angle $d\Omega$ and $\Delta z$ range of the redshift slice:
+% \begin{align}
+% V(z)&=\int_{V_z}dV_p\\ \nonumber
+% &=d_H\int_\Omega\int_{z-\frac{\Delta z}{2}}^{z+\frac{\Delta z}{2}} \frac{d_M(z^\prime)^2}{E(z^\prime)(1+z^\prime)^3}dz^\prime d\Omega.
+% \end{align}
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Gravitational Lensing}
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
 %% Ellipticity Orientation Figure
-\begin{figure*}
-    \centering
-    \begin{subfigure}[H]{0.415\textwidth}
-        \includegraphics[width=\textwidth]{figs-swe/ellipse_orientations.png}
-        \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{The shape of a galaxy image for various ellipticity components $\varepsilon_1$ and $\varepsilon_2$ on the $x$ and $y$-axes respectively. Taken from \cite{schneider}.}
-        \label{ellipses}
-    \end{subfigure}
-    ~
-    %% Einstein Ring Figure
-    \begin{subfigure}[H]{0.425\textwidth}
-        \includegraphics[width=\textwidth]{figs-swe/einstein_ring.png}
-        \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{An image of the luminous red galaxy LRG 3-757 along with a strongly lensed background galaxy, called the `Cosmic Horseshoe' \cite{einstein_ring}.}
-        \label{einstein_ring}
-    \end{subfigure}
-    \caption{}
-\end{figure*}
+% \begin{figure*}
+%     \centering
+%     \begin{subfigure}[H]{0.415\textwidth}
+%         \includegraphics[width=\textwidth]{figs-swe/ellipse_orientations.png}
+%         \captionsetup{justification=raggedright,singlelinecheck=false}
+%         \caption{The shape of a galaxy image for various ellipticity components $\varepsilon_1$ and $\varepsilon_2$ on the $x$ and $y$-axes respectively. Taken from \cite{schneider}.}
+%         \label{ellipses}
+%     \end{subfigure}
+%     ~
+%     %% Einstein Ring Figure
+%     \begin{subfigure}[H]{0.425\textwidth}
+%         \includegraphics[width=\textwidth]{figs-swe/einstein_ring.png}
+%         \captionsetup{justification=raggedright,singlelinecheck=false}
+%         \caption{An image of the luminous red galaxy LRG 3-757 along with a strongly lensed background galaxy, called the `Cosmic Horseshoe' \cite{einstein_ring}.}
+%         \label{einstein_ring}
+%     \end{subfigure}
+%     \caption{}
+% \end{figure*}
+%%------------------------------------------------------------------------------------------------------------------------------------------
+
+While dark matter does not absorb or emit light, it does interact with light indirectly through gravitational lensing.
+The presence of matter curves spacetime locally which causes light to follow curved paths called geodesics \textcolor{red}{(clean up!)}.
+The deviation in path is usually negligable, but can be significant in regions containing clusters of galaxies and their massive dark matter halos.
+By observing how the magnitudes and shapes of distant galaxies are distorted when travelling through regions of matter, we can infer the masses of the dark matter halos and reconstruct the hidden dark matter mass distribution.
+A simplified cartoon of this process is shown in Figure ??, as well as a diagram defining the necessary angles and distances in Figure ??.
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+%% Gravitational Lensing Diagram
+% \begin{figure*}
+%     \centering
+%     \begin{subfigure}[H]{0.4\textwidth}
+%         \includegraphics[width=\textwidth]{figs-swe/thesis/lens_cartoon.png}
+%         \captionsetup{justification=raggedright,singlelinecheck=false}
+%         \caption{CAPTION}
+%         \label{lens_cartoon}
+%     \end{subfigure}
+%     ~
+%     %% Einstein Ring Figure
+%     \begin{subfigure}[H]{0.4\textwidth}
+%         \includegraphics[width=\textwidth]{figs-swe/thesis/lens_diagram.png}
+%         \captionsetup{justification=raggedright,singlelinecheck=false}
+%         \caption{CAPTION}
+%         \label{lens_diagram}
+%     \end{subfigure}
+%     \caption{}
+% \end{figure*}
+%%------------------------------------------------------------------------------------------------------------------------------------------
 
@@
 Foreground mass distorts the image of a background galaxy in two distinct ways: The image is magnified and sheared tangentially about the foreground mass, making it more elliptical.
-The magnification of the image is determined by the convergence $\kappa$, a scalar which measures the projected mass density along each line of sight.
+The magnification of the image is determined by the convergence $\kappa$ defined by
+\begin{equation}\label{convergence}
+\kappa(\vec{\theta})=\frac{\sum(\vec{r},z_l)}{\sum_{cr}(z_l,z_s)}
+\end{equation}
+
+\noindent where $\sum(\vec{r},z_l)$ is the projected surface mass density of the lensing mass and $\sum_{cr}(z_l,z_s)$ is the critical surface density for a given source redshift $z_s$ and lens redshift $z_l$ (\textcolor{red}{Citation}).
 The shearing of the source is most often described by the complex shear $\gamma$ defined to be
@@
 
-However, usually the quantity of interest in lensing calculations is the \textit{reduced} shear, defined as
+However, usually the quantity of interest in lensing calculations is the reduced shear, defined as
 \begin{equation}\label{reduced_shear}
@@
 \noindent where an asterisk denotes the complex conjugate \cite{schneider}. The behavior of the distortion relies strongly on the magnitude of $g$; the
-effect is called \textit{strong} lensing if $|g|>1$ and \textit{weak} lensing if $|g|\leq1$.
+effect is called \textit{strong} lensing if $|g|\gtrapprox1$ and \textit{weak} lensing if $|g|\ll1$.
 The effects of strong lensing can be quite dramatic, distorting sources into large arcs, multiple images, or even an Einstein ring as shown in Figure \ref{einstein_ring}.
-While strong lenses are rare as the alignment of the source and foreground mass must be nearly perfect, \textit{all} sources are weakly lensed.
+
+While strong lenses are rare, as the alignment of the source and foreground mass must be nearly perfect, \textit{all} sources are weakly lensed when traveling through foreground halos.
 The effect is small, usually an ellipticity distortion of only a few percent, but can be detected locally by averaging the ellipticities of all sources in a small region.
@@
 
-\subsection*{Dark Matter Halos}
-
-While the exact relation between the distribution of galaxies and dark matter is not known, simulations have shown that galaxies tend to form in over-dense regions of dark matter.
-This means that galaxies \textit{should} trace out the larger underlying dark matter structures.
-The simplest way to model this relationship is by enveloping each galaxy in a spherically symmetric dark matter `halo' of mass $M_h$ sampled from the stellar-to-halo mass relation \cite{smhr}.
-These halos extend far beyond the edge of the visible galaxy that they enclose.
-While the density profile of the halos may be complex, numerous simulations have shown that it can be well approximated by the Navarro-Frenk-White (NFW) profile which has the form
-\begin{equation}\label{nfw_profile}
-\rho_{NFW}(r)=\frac{\rho_0}{\frac{r}{R_s}\left(1+\frac{r}{R_s}\right)^2}
-\end{equation}
-
-\noindent where the constant $\rho_0$ and the scale radius $R_s$ are parameters that vary from halo to halo \cite{nfw}.
-This work uses a truncated NFW profile called the Baltz-Marshall-Oguri (BMO) profile given by
-\begin{equation}\label{bmo_profile}
-\rho_{BMO}(r)=\rho_{NFW}\cdot\left(\frac{r_t^2}{r^2+r_t^2}\right)^2
-\end{equation}
-
-\noindent where $r_t$ is a free parameter, as it has been shown to be a better fit to simulated data \cite{nfw_bmo}.
-
-\section{The Pangloss Framework}
-
+ The analytical form of the convergence and shear contribution from a BMO-profile is quite messy, but is derived and explained in detail in (Cite Phil's paper!!).
+Calculating the lensing contribution of the smooth-component correction is much simpler; the projected surface mass density at at given redshift is found by integrating $\rho_s(z)$ over a sufficiently small $dz$ interval, and then the mass sheet's convergence is found using Equation \eqref{kappa}.
+There is no shear contribution as a uniform sheet of mass causes only magnification due to the mass sheet degeneracy (CITE!).
+However, Equation \eqref{lensing} shows that the lensed ellipticities depend on the \textit{reduced} shear, which does depend on the additional convergence terms resulting from the smooth-component correction.
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Galaxies as Ellipses}
+
+(introduce issue)
+
+Consider a galaxy image that can be well approximated as an ellipse at an angle $\phi$ above an arbitrary reference line. The galaxy's complex ellipticity is defined to be
+\begin{equation}\label{complex_ellipticity}
+\varepsilon=\varepsilon_1+i\varepsilon_2=|\varepsilon|\,e^{2i\phi}
+\end{equation}
+
+\noindent where the magnitude of the galaxy's ellipticity $|\varepsilon|$ is defined as
+\begin{equation}
+|\varepsilon|=\frac{1-r}{1+r}
+\end{equation}
+
+\noindent and $r\leq1$ is the ratio of the semi-minor and semi-major axes of the ellipse.
+This compact notation combines the eccentricity and orientation of the ellipse into a single object.
+A plot from Schneider et al.
+\cite{schneider} showing the shape of elliptical galaxies for various values of $\varepsilon_1$ and $\varepsilon_2$ is shown in Figure \ref{ellipses}.
+
+There are many complications to using this scheme in practice, most notably the multiplicative bias resulting from the smearing of galaxy images by the observational point spread function (PSF) \cite{multiplicative_bias}.
+While the effects of a PSF can be complex, in general it causes galaxy images to appear less elliptical than they truly are.
+To account for this in generated galaxy images, a multiplicative bias parameter $M$ is often used to lessen the intrinsic ellipticity using
+$$\varepsilon_{obs}=M\cdot\varepsilon_{int}$$
+
+\noindent where $\varepsilon_{int}$ is the generated intrinsic ellipticity of the image and $\varepsilon_{obs}$ is the ellipticity that would be recorded by a detector.
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Correlation Functions}
+
+A common tool used by cosmologists to measure...
+
+%%==========================================================================================================================================
+\section{Pangloss: Line of Sight Mass Reconstructions}
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
 %% Pangloss Cartoon
-\begin{figure*}
-    \centering
-    \includegraphics[width=0.85\textwidth]{figs-swe/pangloss_cartoon.png}
-    \captionsetup{justification=raggedright,singlelinecheck=false}
-    \caption{A cartoon model of how the \texttt{Pangloss} framework uses a dark matter halo model to reconstruct the foreground mass along the line of sight of a background source galaxy.
+% \begin{figure*}
+%     \centering
+%     \includegraphics[width=0.85\textwidth]{figs-swe/pangloss_cartoon.png}
+%     \captionsetup{justification=raggedright,singlelinecheck=false}
+%     \caption{A cartoon model of how the \texttt{Pangloss} framework uses a dark matter halo model to reconstruct the foreground mass along the line of sight of a background source galaxy.
 A `lightcone' centered at a background source is constructed with radius $R$ and populated with all foreground galaxies contained in this volume.
@@
 The shear and convergence along the line of sight contributed by each halo is calculated using \cite{lensing_calc}, and the predicted ellipticity is determined using the sum of these contributions and Equation \eqref{lensing}.}
-    \label{pangloss_cartoon}
-\end{figure*}
-
-To constrain the mass of foreground dark matter using weak gravitational
-lensing, first a model of the relationship between foreground galaxies
-and the foreground dark matter must be established and robustly tested
-to see if, statistically, it makes the same lensing predictions of
-background sources as the true underlying dark matter structure. To do
-this, I built upon the publicly available \texttt{Pangloss}
-framework\footnote{\label{note1}https://github.com/drphilmarshall/Pangloss}
-used in Collett et al. \cite{collett_marshall} to reconstruct all the
-mass along the line of sight of each background galaxy using dark matter
-halos. The lensing contribution of each halo is calculated, and the
-total lensing of the background galaxy is the sum of each halo
-contribution. This process is detailed in the following sections.
-
-\subsection*{Assumptions}
+%     \label{pangloss_cartoon}
+% \end{figure*}
+%%------------------------------------------------------------------------------------------------------------------------------------------
+
+To infer foreground dark matter mass structures using weak gravitational lensing, first a model of the relationship between foreground galaxies and the foreground dark matter must be established and robustly tested to see if, statistically, it makes the same lensing predictions of background sources as the true underlying dark matter structure.
+To do this, I built upon the publicly available \texttt{Pangloss}\footnote{\label{note1}https://github.com/drphilmarshall/Pangloss} framework used in Collett et al.
+\cite{collett_marshall} to reconstruct all the
+mass along the line of sight of each background galaxy using a halo model with smooth-component correction.
+The lensing contribution of each halo is calculated, and the total lensing of the background galaxy is the sum of each halo contribution.
+The implementation of this process is detailed in the following sections.
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Model Assumptions}
 While \texttt{Pangloss} may be used more generally, the present analysis makes some additional strong assumptions to simplify the problem for a first attempt at making weak lensing predictions.
@@
 \begin{enumerate}
-\item The dark matter mass distribution can be approximated by spherically symmetric BMO halo profiles attached to each galaxy.
+\item The dark matter mass distribution can be approximated by spherically symmetric BMO halo profiles attached to each galaxy, along with a smooth-component correction.
 \item The stellar mass of the foreground galaxy is negligible for lensing calculations.
@@
 
-\subsection*{The Millennium Simulation}
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{The Millennium Simulation}
 \texttt{Pangloss} cannot be used to make dark matter mass maps using existing galaxy catalogs until it is tested on a simulated universe with known dark matter structure to determine how accurately and precisely it predicts the lensing of background sources.
 For this purpose, \texttt{Pangloss} was tested on galaxy catalogs from the Millennium Simulation, an N-body simulation consisting of over 10 billion dark matter `particles' each representing a billion solar masses and populated with about 20 million galaxies \cite{millennium_simulation}.
-The simulation uses cosmological parameters from WMAP 1\textsuperscript{st}-year data analysis and contains baryonic and dark matter structure believed to be consistent with our own universe.
+The simulation contains baryonic and dark matter structure believed to be similar to our own universe, and uses cosmological parameters from WMAP 1\textsuperscript{st}-year data analysis which assumed a matter density of $\Omega_m=0.25$, a dark energy density of $\Omega_\Lambda=0.75$, and a Hubble constant of $H_0=73$ km$\,$s$^{-1}\,$Mpc$^{-1}$ (\textcolor{red}{CITE!!}).
 From the work of Hilbert et al.
-\cite{ray_tracing}, high resolution maps of the ray-traced shear and convergence are publicly available.
-From these maps, the actual lensing of background galaxies when traveling through the foreground mass of the Millennium Simulation can be calculated using Equation \eqref{lensing}.
-
-\subsection*{Generating Background Galaxies}
-With a catalog of foreground galaxies chosen, a set of 3,240 background galaxies over a field of 324 arcmin$^2$ was generated, with density 10 per arcmin$^2$.
+\cite{ray_tracing}, high resolution maps of the ray-traced shear and convergence of galaxy sources at $z=1.3857$ are publicly available.
+From these maps, an estimate of the `true' lensing of background galaxy ellipticities when traveling through the foreground mass of the Millennium Simulation can be calculated using Equation \eqref{lensing}.
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Generating Background Galaxies}
+With a catalog of foreground galaxies chosen, a set of \textcolor{red}{???} background galaxies over a field of \textcolor{red}{???} arcmin$^2$ was generated, with density 10 per arcmin$^2$.
 The intrinsic orientation of each galaxy was sampled from a uniform distribution as, without lensing, there should be no preferred orientation due to the assumption of an isotropic universe.
@@
 
-\subsection*{Creating Lightcones}
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Creating Lightcones}
 
@@
 A cartoon model of this process is shown in Figure \ref{pangloss_cartoon}.
-Unless otherwise specified, experiments in this paper used a radius of 2 arcminutes.
+Unless otherwise specified, experiments in this paper used a radius of 6 arcminutes and halo truncation scale of five times the virial radius.
 
 To calculate the convergence and shear contribution of each halo, the physical distance from the halo to the line of sight was needed.
-To increase the speed of distance calculations, the foreground halo redshifts were first snapped to a grid of 100 equally-sized redshift bins and then converted to physical distance.
+To increase the speed of distance calculations, the foreground halo redshifts were first binned to a grid of 100 equally-sized redshift bins from $z=0$ to the sourced redshift of $z=1.3857$ and then converted to physical distances using the cosmology defined by the Millennium Simulation.
+
+\subsection{Assigning Relevance to Halos}
+
+Not all foreground halos are equally relevant to the lensing calculation.
+To add a significant contribution to the combined shear and convergence, a halo must be massive, close to the line of sight, or preferably both.
+McCully et al.
+\textcolor{red}{(CITE)} derived that the correct metric for determining the relevance of a given foreground halo to the overall lensing calculation to be given by
+\begin{equation}\label{relevant}
+Rel(M_h,R)\propto\frac{M_h}{R^3}
+\end{equation}
+
+where $M_h$ is the halo mass and $R$ is the distance from the halo to the line of sight.
+The relevance distribution for one background catalog realization with \textcolor{red}{???} foreground halos in a lightcone of radius \textcolor{red}{??} arcminutes is shown in Figure ??.
+As expected, there are very few massive halos along the line of sight and therefore only a small percentage of foreground halos should have a high relative contribution to the predicted lensing quantities.
+This encouraged the intended analysis on lightcones with all halos and those with only a small subset of the most relevant halos to compare the results and see if the computational time saved by using only the most relevant halos was worth the loss in prediction accuracy.
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+%% Relevance Distribution of all Halos
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=0.25\textwidth]{figs-swe/thesis/relevance_distribution.png}
+%     \captionsetup{justification=raggedright,singlelinecheck=false}
+%     \caption{CAPTION}
+%     \label{rel_dist}
+% \end{figure}
+%%------------------------------------------------------------------------------------------------------------------------------------------
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Calculating the Smooth-Component Correction}
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+%% Smooth-Component Correction Diagram
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=0.25\textwidth]{figs-swe/thesis/smooth_correction.png}
+%     \captionsetup{justification=raggedright,singlelinecheck=false}
+%     \caption{CAPTION}
+%     \label{scc}
+% \end{figure}
+%%------------------------------------------------------------------------------------------------------------------------------------------
+
+(Introduce idea in Cosmological background, but cover image and specific details to implementation here.)\\
+
+(Volume and Surface density plots for s.c.c. redshift slices)
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+%% Surface and Volume densities for smooth-component correction redshift slices
+% \begin{figure*}
+%     \centering
+%     \begin{subfigure}[H]{0.415\textwidth}
+%         \includegraphics[width=\textwidth]{figs-swe/thesis/scc_vol_den.png}
+%         \captionsetup{justification=raggedright,singlelinecheck=false}
+%         \caption{CAPTION}
+%         \label{volume_densities}
+%     \end{subfigure}
+%     ~
+%     %% Einstein Ring Figure
+%     \begin{subfigure}[H]{0.425\textwidth}
+%         \includegraphics[width=\textwidth]{figs-swe/thesis/scc_surf_deng.png}
+%         \captionsetup{justification=raggedright,singlelinecheck=false}
+%         \caption{CAPTION}
+%         \label{surface_densities}
+%     \end{subfigure}
+%     \caption{}
+% \end{figure*}
+%%------------------------------------------------------------------------------------------------------------------------------------------
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Line of Sight Lensing Predictions}
+
+(Predict LOS kappa and shear measurements )
 
@@
 
-\subsection*{Checking the Halo Model}
-
-Instead of comparing the ray-traced and \texttt{Pangloss} predicted
-ellipticities for individual galaxies, the lensing is characterized
-globally with correlation functions. The ellipticity-ellipticity
-correlation function measures how correlated the ellipticities of pairs
-of galaxies are as a function of separation distance, while the
-galaxy-mass correlation function measures the correlation of lensed
-ellipticities around foreground halos as a function of separation
-distance. For readers that are unfamiliar with correlation functions in
-the context of cosmology or want a visual aid, see the appendix. Both
-correlation functions are used in this work to measure how well the
-\texttt{Pangloss} framework models weak lensing by dark matter
-structures using the publicly available \texttt{TreeCorr} module written
-by Mike Jarvis\footnote{https://github.com/rmjarvis/TreeCorr}. Note that
-the ellipticity-ellipticity correlation function definition used in
-\texttt{TreeCorr} is slightly different than that used in most of the
-literature; for a derivation of the connection between Jarvis's
-definition and the more common Schneider definition \cite{schneider},
-visit the \texttt{Pangloss} repository\footnotemark[\ref{note1}].
-
-\section{Results}
-
+%%==========================================================================================================================================
+\section{Checking the Pangloss Model}
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+%% Pangloss Lightcone Data
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=0.25\textwidth]{figs-swe/thesis/lightcone_data.png}
+%     \captionsetup{justification=raggedright,singlelinecheck=false}
+%     \caption{CAPTION}
+%     \label{rel_dist}
+% \end{figure}
+%%------------------------------------------------------------------------------------------------------------------------------------------
+
+Using the presented methodology, ???
+background galaxies in a ???
+arcmin$^2$ subset of the (0,0,0,0) Millennium Simulation foreground catalog were generated and lensed by both the ray-traced shear and convergence maps as well as the \texttt{Pangloss} framework.
+With a lightcone radius of ??
+arcminutes, the lightcones contained an average of ${??\pm??}$ foreground halos.
+Both sets of lensed ellipticities were characterized with correlation functions, as well as the intrinsic ellipticities of the sources before lensing.
+
+Figure (??) displays different views an example lightcone where the foreground halos are plotted as circles whose size are proportional to their galaxy brightness (top left), angular size (top center), convergence contributions (top right), and halo mass (bottom).
+Figure (??) shows a few examples of mass structures in the foreground catalog along with the ray-traced convergence and shear maps from (Hilbert cite).
+
+Figure (??) shows a
+
+Instead of comparing the ray-traced and \texttt{Pangloss} predicted ellipticities for individual galaxies, the lensing is characterized globally with correlation functions.
+As described in section (??), the ellipticity-ellipticity correlation function measures how correlated the ellipticities of pairs of galaxies are as a function of separation distance, while the galaxy-mass correlation function measures the correlation of lensed ellipticities around foreground halos as a function of separation distance.
+Both correlation functions are used in this work to estimate how well the \texttt{Pangloss} framework models weak lensing by dark matter structures and are computed using the publicly available \texttt{TreeCorr} module written by Mike Jarvis\footnote{https://github.com/rmjarvis/TreeCorr}.
+Note that the ellipticity-ellipticity correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition and the more common Schneider definition \cite{schneider}, see Appendix (??).
+
+% For readers that are unfamiliar with correlation functions in the context of cosmology or want a visual aid, see the appendix.
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Ellipticity-Ellipticity Correlation Function}
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
 %% Ellipticity-Ellipticity Correlation
-\begin{figure}
-    \centering
-    \begin{subfigure}{0.475\textwidth}
-        \includegraphics[width=\textwidth]{figs-swe/gg_corr.png}
-        \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{The ellipticity-ellipticity correlation function for 3,240 sources at separation distances from 0.1 to 2 arcminutes and a lightcone radius of $R=2$ arcminutes.
+% \begin{figure}
+%     \centering
+%     \begin{subfigure}{0.475\textwidth}
+%         \includegraphics[width=\textwidth]{figs-swe/gg_corr.png}
+%         \captionsetup{justification=raggedright,singlelinecheck=false}
+%         \caption{The ellipticity-ellipticity correlation function for 3,240 sources at separation distances from 0.1 to 2 arcminutes and a lightcone radius of $R=2$ arcminutes.
 While the correlation of the intrinsic ellipticities before lensing (blue) shows no correlation, the correlation of the ray-traced ellipticities (green) and halo model predicted ellipticities (purple) both show significant positive correlation on scales up to 1 arcminute.
 The halo model predicts a small negative correlation above this scale, while the ray-tracing shows positive correlation on all scales.}
-        %The correlation of the intrinsic ellipticities before lensing is plotted in blue, and shows no correlation.
+%         %The correlation of the intrinsic ellipticities before lensing is plotted in blue, and shows no correlation.
 The correlation of the true ray-traced ellipticities is plotted in green and shows significant positive correlation on all scales.
 The halo predicted correlation, plotted in purple, shows significant positive correlation until a separation distance of 0.8 arcminutes.
-        \label{gg_corr}
-    \end{subfigure}
-    ~~
-    \begin{subfigure}{0.475\textwidth}
-        \includegraphics[width=\textwidth]{figs-swe/gg_corr_series.png}
-        \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{The ellipticity-ellipticity correlation functions for a series of halo model frameworks with increasing lightcone radii from $R=1$ to $R=8$ arcminutes, all plotted in purple with various line styles.
+%         \label{gg_corr}
+%     \end{subfigure}
+%     ~~
+%     \begin{subfigure}{0.475\textwidth}
+%         \includegraphics[width=\textwidth]{figs-swe/gg_corr_series.png}
+%         \captionsetup{justification=raggedright,singlelinecheck=false}
+%         \caption{The ellipticity-ellipticity correlation functions for a series of halo model frameworks with increasing lightcone radii from $R=1$ to $R=8$ arcminutes, all plotted in purple with various line styles.
 These are compared to the same ray-traced correlation from Figure \ref{gg_corr}.}
-        \label{gg_corr_series}
-    \end{subfigure}
-    \caption{}
-\end{figure}
-
-Using the presented methodology, 3,240 background galaxies in a 324 arcmin$^2$ subset of the (0,0,0,0) Millennium Simulation foreground catalog were generated and lensed by both the ray-traced shear and convergence maps as well as the \texttt{Pangloss} framework.
-With a lightcone radius of 2 arcminutes, the lightcones contained an average of ${950\pm70}$ foreground halos.
-Both sets of lensed ellipticities were characterized with correlation functions, as well as the intrinsic ellipticities of the sources before lensing.
-
-\subsection*{Ellipticity-Ellipticity Correlation Function}
-
-The first test of the halo model was with the ellipticity-ellipticity correlation function with a lightcone radius of 2 arcminutes which is given in Figure \ref{gg_corr}.
-The statistic measured the average correlation between pairs of ellipticities at separation distances between 0.1 and 2 arcminutes.
+%         \label{gg_corr_series}
+%     \end{subfigure}
+%     \caption{}
+% \end{figure}
+%%------------------------------------------------------------------------------------------------------------------------------------------
+
+The first test of the halo model was with the ellipticity-ellipticity correlation function with a lightcone radius of ??
+arcminutes which is given in Figure \ref{gg_corr}.
+The statistic measured the average correlation between pairs of ellipticities at separation distances between ??
+and ??
+arcminutes.
 The correlation function of the intrinsic ellipticities plotted in blue shows no significant deviation from zero as expected, as before lensing the galaxies had random orientations.
-Both the ray-traced, plotted in green, and halo model, plotted in purple, ellipticities show positive correlation on small scales up to a separation of 1 arcminute.
-However, the ray-traced correlation is positive on all calculated scales while the halo model does not predict any significant correlation at separations above 1 arcminute.
+Both the ray-traced, plotted in green, and halo model, plotted in purple, ellipticities show positive correlation on small scales up to a separation of ??
+arcminutes.
+However, ...
+(New analysis depending on figure)
+
+% OLD: the ray-traced correlation is positive on all calculated scales while the halo model does not predict any significant correlation at separations above 1 arcminute.
 Additionally, while the shapes of the correlation functions for both sets of lensed ellipticities agree well until 1 arcminute, there is a clear systematic underprediction of shear power by the halo model on all scales.
@@
 The result is shown in Figure \ref{gg_corr_series}, where the series of model predicted correlation functions is compared to the ray-traced correlation function.
-As $R$ increases, the mean number of foreground galaxies contained in each lightcone grows quadratically from ${240\pm25}$ galaxies when $R=1$ arcminute to ${15,000\pm300}$ galaxies when $R=8$ arcminutes.
+As $R$ increases, the mean number of foreground galaxies contained in each lightcone grows quadratically from ${??\pm??}$ galaxies when $R=1$ arcminute to ${??\pm??}$ galaxies when $R=8$ arcminutes.
 Increasing the number of foreground objects, and thus increasing the mass and structure considered for shear and convergence predictions, systematically increased the predicted shear power on all scales.
-While the series of predicted correlation functions appear to be converging towards the ray-traced correlation function, there is clearly diminishing shear power gains as $R$ increases.
-
-\subsection*{Galaxy-Mass Correlation Function}
-
-The catalog of lensed ellipticities was also analyzed using the galaxy-mass correlation function with separation distances from 0.1 to 2 arcminutes and a lightcone radius of 2 arcminutes.
+
+%While the series of predicted correlation functions appear to be converging towards the ray-traced correlation function, there is clearly diminishing shear power gains as $R$ increases.
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Galaxy-Mass Correlation Function}
+
+The catalog of lensed ellipticities was also analyzed using the galaxy-mass correlation function with separation distances from ??
+to ??
+arcminutes and a lightcone radius of ??
+arcminutes.
 The result is shown in Figure \ref{ng_corr}.
 As with the ellipticity-ellipticity correlation function, there is no significant correlation for the intrinsic ellipticities at any scale as expected.
-The lensed ellipticities from the ray-tracing and halo model both show positive correlation on all calculated scales and are in agreement on separations from 0.2 to 0.7 arcminutes.
-However, the halo model is still systematically underpredicting the shear power on scales above 0.7 arcminutes, although now only by an average of 23\%.
+The lensed ellipticities from the ray-tracing and halo model both show positive correlation on all calculated scales and are in agreement on separations from ??
+to ??
+arcminutes.
+However, ....
+(New analysis)
+
+%the halo model is still systematically underpredicting the shear power on scales above 0.7 arcminutes, although now only by an average of 23\%.
 A new feature is the large overprediction of shear power on separation scales smaller than 0.2 arcminutes.
@@
 
+The galaxy-mass correlation function was similarly re-calculated at increasing lightcone radii from $R=1$ to $R=8$ arcminutes with the result in Figure ??. (Analyze new figure...)
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
 %% Galaxy-mass correlation function
-\begin{figure}
-    \centering
-    \includegraphics[width=0.475\textwidth]{figs-swe/ng_corr.png}
-    \captionsetup{justification=raggedright,singlelinecheck=false}
-    \caption{The galaxy-mass correlation function of 3,240 sources at separation distances from 0.1 to 2 arcminutes and a lightcone radius of $R=2$ arcminutes.
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=0.475\textwidth]{figs-swe/ng_corr.png}
+%     \captionsetup{justification=raggedright,singlelinecheck=false}
+%     \caption{The galaxy-mass correlation function of 3,240 sources at separation distances from 0.1 to 2 arcminutes and a lightcone radius of $R=2$ arcminutes.
 There is no significant correlation of the intrinsic ellipticities (blue) as expected, and both the ray-traced correlation (green) and halo model correlation (purple) are positive on all scales.
 The green and purple curves are in agreement from 0.2 to 0.7 arcminutes, but have significant discrepancies on scales above and below this range.}
-    \label{ng_corr}
-\end{figure}
-
-\subsection*{Computational Performance}
+%     \label{ng_corr}
+% \end{figure}
+%
+% ...Same progression corr function as gg??
+%
+%%------------------------------------------------------------------------------------------------------------------------------------------
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Correlation Fraction of Relevant Halos}
+
+Of intrinsic interest is the relative number of relevant halos needed in each lightcone to accurately predict the halo correlation functions in Figures ??
+and ??, as a low percentage would allow much faster lensing predictions.
+Figure ??
+displays an example ellipticity-ellipticity correlation function comparrison of the halo model using all halos (purple) and halo model using halos above the relevance limit of (??
+$M_{\odot}/$Mpc$^3$), as well as the percent error of each predicted value between the two (models?).
+This relevance limit resulted in $??\pm??$ relevant halos per lightcone, and resulted in a normalized root-mean-square error (NRMSE) of ??.
+Figures ??
+plots the ellipticity-ellipticity and galaxy-mass correlation function NRMSE and mean correlation fraction as a function of mean relevant halos.
+These results suggest that either correlation function prediction can be approximated with an NRMSE below ??
+using the ??
+most relevant halos.
+(More analysis after plots have been made)
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+%% Ellipticity-Ellipticity Correlation Comparrison
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=0.475\textwidth]{figs-swe/thesis/gg_corr_rel.png}
+%     \captionsetup{justification=raggedright,singlelinecheck=false}
+%     \caption{CAPTION}
+%     \label{gg_corr_rel}
+% \end{figure}
+%
+%%------------------------------------------------------------------------------------------------------------------------------------------
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+%% NRMSE and Correlation Fraction as function of Mean Relevant Halos
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=0.475\textwidth]{figs-swe/thesis/corr_fraction.png}
+%     \captionsetup{justification=raggedright,singlelinecheck=false}
+%     \caption{CAPTION}
+%     \label{corr_fraction}
+% \end{figure}
+%
+%%------------------------------------------------------------------------------------------------------------------------------------------
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{??}
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Computational Performance}
 
@@
 However, many small improvements to the coding infrastructure of \texttt{Pangloss} were made to speed up the prediction.
-The average CPU time for a lensing prediction per lightcone for four separate runs after various (and cumulative) changes is plotted in Figure \ref{cpu_plot}, with a final run time of $24\pm5$ ms.
-Run 1 corresponds to the original \texttt{Pangloss} framework code, run 2 only wrote the needed quantities for this analysis to the catalog \texttt{Astropy} tables, run 3 changed the redshift grid binning to be done once for all halos in the drilling rather than for every individual halo in lensing, and run 4 optimized various lensing calculations with matrices whenever possible.
-Cumulatively, these changes alone accounted for a 70\% decrease in mean CPU time per lightcone and halved the initial variation.
-
+The average CPU time for a lensing prediction per lightcone for four separate runs after various (and cumulative) changes is plotted in Figure \ref{cpu_plot}, with a final run time of $??\pm?$ ms.
+Run 1 corresponds to the original \texttt{Pangloss} framework code, run 2 only wrote the needed quantities for this analysis to the catalog \texttt{Astropy} tables, run 3 changed the redshift grid binning to be done once for all halos in the drilling rather than for every individual halo in lensing, run 4 optimized various lensing calculations with matrices whenever possible, run 5 replaced the computationally expensive lensing calculation functions with a lookup table, and run 6 is using only the most ??
+relevant halos.
+Cumulatively, these changes alone accounted for a ??\% decrease in mean CPU time per lightcone and ??
+the initial variation.
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
 %% Mean lightcone CPU time
-\begin{figure}
-    \centering
-    \includegraphics[width=0.475\textwidth]{figs-swe/profile_bar.png}
-    \captionsetup{justification=raggedright,singlelinecheck=false}
-    \caption{The mean CPU runtime per lightcone for various runs with different (and cumulative) code optimizations described in the text.
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=0.475\textwidth]{figs-swe/profile_bar.png}
+%     \captionsetup{justification=raggedright,singlelinecheck=false}
+%     \caption{The mean CPU runtime per lightcone for various runs with different (and cumulative) code optimizations described in the text.
 The cumulative changes account for a 70\% decrease in the mean CPU time and a halving of the variation.
 Currently, the prediction can be made for a single lightcone in\\$24\pm5$ ms.}
-    \label{cpu_plot}
-\end{figure}
-
+%     \label{cpu_plot}
+% \end{figure}
+%%------------------------------------------------------------------------------------------------------------------------------------------
+
+%%==========================================================================================================================================
+\section{Feasibility of Parameter Inference using Pangloss}
+
+Introduction, explain difference between the two different methods.
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Likelihood Estimation}
+
+\begin{enumerate}
+\item Equation from Phil's dissertation
+\item Calculate time with and without drilling
+\item Time per lensing event, time per lightcone
+\end{enumerate}
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Approximate Bayesian Computation}
+
+\begin{enumerate}
+\item Difficult to calculate likelihood, can instead make mock data by samping parameters from prior distribution
+\item Come up with `distance' function (compare e-e corr functions) and threshold value
+\item Use accepted simulations to approximate posterior
+\item Time per ABC
+\item Compare time to single lensing event
+\end{enumerate}
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Results}
+
+% \subsection{Relevant Halos}
+% \begin{enumerate}
+% \item Metric from McCully et al. (cite)
+% \item Implementation
+% \item Plot the percent difference between all halos and relevant halos as a function of $\#$ of relevant halos (can adopt relevant-test.py to do this)
+% \end{enumerate}
+
+% \subsection{Smooth-Component Correction}
+% \begin{enumerate}
+% \item Introduce issue
+% \item Either derive result or state result with derivation in appendix
+% \item Plots of volume/surface density of halos vs mean universe density
+% \item Plot distribution of correction kappas
+% \item Plot distribution of reduced-shear with and without correction
+% \end{enumerate}
+
+% \subsection{Speedups}
+% \begin{enumerate}
+% \item Lookup tables (lensing table)
+% \item relevant halos
+% \item pre-calculate grid volumes for s-c correction
+% \item more plots to quantify speedup times!
+% \end{enumerate}
+
+% \subsection{Feasibility of Inference}
+
+% \subsubsection*{Likelihood Estimation}
+% \begin{enumerate}
+% \item Equation from Phil's dissertation
+% \item Calculate time with and without drilling
+% \item Time per lensing event, time per lightcone
+% \end{enumerate}
+
+% \subsubsection*{Approximate Bayesian Computation}
+% \begin{enumerate}
+% \item Difficult to calculate likelihood, can instead make mock data by samping parameters from prior distribution
+% \item Come up with `distance' function (compare e-e corr functions) and threshold value
+% \item Use accepted simulations to approximate posterior
+% \item Time per ABC
+% \item Compare time to single lensing event
+% \end{enumerate}
+
+%%==========================================================================================================================================
 \section{Discussion}
 
-\subsection*{Issues with the Pangloss Framework}
-
-Both the ellipticity-ellipticity and galaxy-mass correlation functions show clear issues with using the halo model to predict the lensing of background sources with \texttt{Pangloss}, even in the best-case scenario of perfect knowledge of the halo masses and their spectroscopic redshifts.
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Issues with the Pangloss Framework}
+
+% OLD: Both the ellipticity-ellipticity and galaxy-mass correlation functions show clear issues with using the halo model to predict the lensing of background sources with \texttt{Pangloss}, even in the best-case scenario of perfect knowledge of the halo masses and their spectroscopic redshifts.
 The systematic underprediction of shear power present in both correlation functions is likely do to missing features in the model such as clusters, filaments, and voids.
 
-While individual galaxies currently receive halos, a cluster of galaxies will sit in an larger halo whose presence is not being considered as its position, mass, and extent are difficult to determine.
+% While individual galaxies currently receive halos, a cluster of galaxies will sit in an larger halo whose presence is not being considered as its position, mass, and extent are difficult to determine.
 The absence of this mass undoubtedly effects shear predictions and ellipticity correlations on large scales.
@@
 
-The progression of model predicted ellipticity-ellipticity correlation functions at larger radii converging to the ray-traced correlation in Figure \ref{gg_corr_series} supports the analysis given above, as the prediction was progressively better with larger number of foreground halos and thus more mass and structure.
+% The progression of model predicted ellipticity-ellipticity correlation functions at larger radii converging to the ray-traced correlation in Figure \ref{gg_corr_series} supports the analysis given above, as the prediction was progressively better with larger number of foreground halos and thus more mass and structure.
 However, the number of foreground objects scales quadratically with the lightcone radius making it prohibitively expensive above $R=8$ arcminutes.
@@
 
-\subsection*{Scaling Up Pangloss}
-
-While the current \texttt{Pangloss} framework can handle the lensing predictions of 3,240 sources in a 324 arcmin$^2$ field comfortably on a single processor, the goal is to scale up the framework to make predictions for background sources of the same number density in a 100 deg$^2$ field; this will require 3.6 million lightcones, each containing up to 1,000 foreground halos.
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Scaling Up Pangloss}
+
+% OLD: While the current \texttt{Pangloss} framework can handle the lensing predictions of 3,240 sources in a 324 arcmin$^2$ field comfortably on a single processor, the goal is to scale up the framework to make predictions for background sources of the same number density in a 100 deg$^2$ field; this will require 3.6 million lightcones, each containing up to 1,000 foreground halos.
 Luckily, the prediction is trivially parallelizable as the shear and convergence calculation of each lightcone is independent of all other lightcones.
@@
 
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Systematic Errors}
+
+%%==========================================================================================================================================
 \section{Conclusion}
 
-In this paper, a simple halo model was used to reconstruct all the mass along lines of sight in the Millennium Simulation to make predictions of how foreground mass weakly lensed the ellipticities of 3,240 generated background sources across a field of 324 arcmin$^2$.
+% OLD: In this paper, a simple halo model was used to reconstruct all the mass along lines of sight in the Millennium Simulation to make predictions of how foreground mass weakly lensed the ellipticities of 3,240 generated background sources across a field of 324 arcmin$^2$.
 The lensed ellipticities were characterized globally using the ellipticity-ellipticity and galaxy-mass correlation functions and then compared with the same statistics from ray-traced data.
@@
 
+%%==========================================================================================================================================
 \section{Acknowledgements}
 
-I would like to thank the Department of Energy for funding this research and giving me this wonderful opportunity, as well as SLAC National Laboratory for hosting me.
+% OLD: I would like to thank the Department of Energy for funding this research and giving me this wonderful opportunity, as well as SLAC National Laboratory for hosting me.
 This work was greatly aided by numerous conversations with Risa Wechsler from Stanford University and Matt Becker from the Kavli Institute for Particle Astrophysics and Cosmology (KIPAC).
 Finally, I am incredibly grateful to Phil Marshall for his unending support, patience, and guidance throughout this research.
-This work was supported in part by the U.S.
+% This work was supported in part by the U.S.
 Department of Energy, Office of Science, Office of Workforce Development for Teachers and Scientists (WDTS) under the Science Undergraduate Laboratory Internships Program (SULI).
 
+%%==========================================================================================================================================
+
 \onecolumngrid
 
+\section{References}
+\vspace{-.2825in}
+\bibliographystyle{unsrt}
+\bibliography{suli-report-swe}
+
+%%==========================================================================================================================================
+
+\newpage
+
 \section{Appendix}
 
-\subsection*{Visualizing Correlation Functions}
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Visualizing Correlation Functions}
 
@@
 \end{figure}
+
+(Might need to rework some phrasing)\\
 
@@
 
-\section{References}
-\vspace{-.2825in}
-\bibliographystyle{unsrt}
-\bibliography{suli-report-swe}
+%%------------------------------------------------------------------------------------------------------------------------------------------
+
+\newpage
+
+\subsection{Deriving the Standard Correlation Function Definition from \texttt{TreeCorr}'s Definition}
+
+(Introduce issue a bit)\\
+
+From Jarvis \href{http://arxiv.org/pdf/astro-ph/0307393v2.pdf}{(Page 3)}:
+\begin{align}
+\xi_+&=\left<\gamma_i\gamma_j^*\right>=\texttt{xip}+i(\texttt{xip\_im})\label{s+}\\
+\xi_-&=\left<\gamma_i\gamma_je^{-4i\alpha}\right>=\texttt{xim}+i(\texttt{xim\_im})\label{s-}
+\end{align}
+
+where $\alpha$ is the angle between the two objects $i,j$ and each $\gamma$ is given by $\gamma_n=|\gamma_n|e^{2i\theta_n}$ in polar form.\\
+
+From Schneider \href{http://arxiv.org/pdf/astro-ph/0509252v1.pdf}{(Page 92)}:
+\begin{align}
+\xi_\pm&=\left<\gamma_{i_t}\gamma_{j_t}\right>\pm\left<\gamma_{i_\times}\gamma_{j_\times}\right>\label{s+-}\\
+\xi_\times&=\left<\gamma_{i_t}\gamma_{j_\times}\right>\label{sx}
+\end{align}
+
+where $\gamma_{n_t}=-\operatorname{Re}\left(\gamma_n e^{-2i\alpha}\right)$ and $\gamma_{n_\times}=-\operatorname{Im}\left(\gamma_n e^{-2i\alpha}\right)$.\\
+
+\section*{Schneider's $\xi_+$ to Jarvis's \texttt{xip}}
+
+Starting with Schneider's definition, observe that
+\begin{align*}
+\xi_+&=\left<\gamma_{i_t}\gamma_{j_t}\right>+\left<\gamma_{i_\times}\gamma_{j_\times}\right>\\
+&=\left<\operatorname{Re}\left(\gamma_ie^{-2i\alpha}\right)\cdot\operatorname{Re}\left(\gamma_je^{-2i\alpha}\right)\right>+\left<\operatorname{Im}\left(\gamma_ie^{-2i\alpha}\right)\cdot\operatorname{Im}\left(\gamma_je^{-2i\alpha}\right)\right>\\
+&=\left<\operatorname{Re}\left(|\gamma_i|e^{2i(\theta_i-\alpha)}\right)\cdot\operatorname{Re}\left(|\gamma_j|e^{2i(\theta_j-\alpha)}\right)\right>+\left<\operatorname{Im}\left(|\gamma_i|e^{2i(\theta_i-\alpha)}\right)\cdot\operatorname{Im}\left(|\gamma_j|e^{2i(\theta_j-\alpha)}\right)\right>\\
+&=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\alpha)\right)\cos\left(2(\theta_j-\alpha)\right)\right>+\left<|\gamma_i|\cdot|\gamma_j|\sin\left(2(\theta_i-\alpha)\right)\sin\left(2(\theta_j-\alpha)\right)\right>.
+\end{align*}
+
+Using the trig identities
+\begin{align}
+\cos(u)\cos(v)&=\frac{1}{2}\left[\cos(u-v)+\cos(u+v)\right],\\
+\sin(u)\sin(v)&=\frac{1}{2}\left[\cos(u-v)-\cos(u+v)\right],
+\end{align}
+
+and the linearity of the expectation operator, it is straightforward to show that
+%\begin{align*}
+%\xi_+&=\left<|\gamma_i|\cdot|\gamma_j|\right>\cdot\left(\left<\frac{1}{2}\left[\cos\left(2(\theta_i-\theta_j)\right)+\cos\left(2(\theta_i+\theta_j-2\alpha)\right)\right]\right>+\left<\frac{1}{2}\left[\cos\left(2(\theta_i-\theta_j)\right)-\cos\left(2(\theta_i+\theta_j-2\alpha)\right)\right]\right>\right)\\
+%&=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\theta_j)\right)\right>.
+%\end{align*}
+$$\xi_+=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\theta_j)\right)\right>.$$
+
+Now using the identity
+\begin{equation}\label{trig2}
+\cos(u\pm v)=\cos\left(u\right)\cos\left(v\right)\mp\sin\left(u\right)\sin\left(v\right),
+\end{equation}
+
+the previous equation can be written as
+
+\begin{align*}
+\xi_+&=\left<|\gamma_i|\cdot|\gamma_j|\cdot\left[\cos\left(2\theta_i\right)\cos\left(2\theta_j\right)+\sin\left(2\theta_i\right)\sin\left(2\theta_j\right)\right]\right>\\
+&=\left<\operatorname{Re}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)+\operatorname{Im}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\right>.
+\end{align*}
+
+Using the complex number identities
+
+\begin{align}
+\operatorname{Re}(z)&=\frac{1}{2}\left[z+z^*\right],\label{complex1}\\
+\operatorname{Im}(z)&=\frac{1}{2i}\left[z-z^*\right]\label{complex2},
+\end{align}
+
+it follows that
+
+\begin{align*}
+\xi_+&=\left<\frac{1}{4}\left[(\gamma_i+\gamma_i^*)(\gamma_j+\gamma_j^*)-(\gamma_i-\gamma_i^*)(\gamma_j-\gamma_j^*)\right]\right>\\
+&=\left<\frac{1}{2}\left[\gamma_i\gamma_j^*+(\gamma_i\gamma_j^*)^*\right]\right>\\
+&=\left<\operatorname{Re}(\gamma_i\gamma_j^*)\right>=\texttt{xip}.
+\end{align*}
+
+\section*{Schneider's $\xi_-$ to Jarvis's \texttt{xim}}
+
+The first few steps are identical to the previous section besides the negative in the definition of $\xi_-$, giving
+\begin{align*}
+\xi_-&=\left<\gamma_{i_t}\gamma_{j_t}\right>-\left<\gamma_{i_\times}\gamma_{j_\times}\right>\\
+&=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\alpha)\right)\cos\left(2(\theta_j-\alpha)\right)\right>-\left<|\gamma_i|\cdot|\gamma_j|\sin\left(2(\theta_i-\alpha)\right)\sin\left(2(\theta_j-\alpha)\right)\right>\\
+&=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i+\theta_j-2\alpha)\right)\right>.
+\end{align*}
+
+Now using Equation \eqref{trig2} twice, first letting $u=2(\theta_i+\theta_j)$ and $v=-4\alpha$, and then letting $u=2\theta_i$ and $v=2\theta_j$, this equation becomes
+
+\begin{align*}
+\xi_-&=\left<|\gamma_i|\cdot|\gamma_j|\Big(\left[\cos(2\theta_i)\cos(2\theta_j)-\sin(2\theta_i)\sin(2\theta_j)\right]\cos(4\alpha)+\left[\sin(2\theta_i)\cos(2\theta_j)+\cos(2\theta_i)\sin(2\theta_j)\right]\sin(4\alpha)\Big)\right>\\
+&=\Big<\big[\operatorname{Re}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)-\operatorname{Im}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\big]\cos(4\alpha)+\big[\operatorname{Im}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)+\operatorname{Re}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\big]\sin(4\alpha)\Big>.
+\end{align*}
+
+Using the identities \eqref{complex1} and \eqref{complex2}, and simplifying the leftover terms, this equation can be shown to equal
+\begin{align*}
+\xi_-=\big<\operatorname{Re}(\gamma_i\gamma_j)\cos(4\alpha)+\operatorname{Im}(\gamma_i\gamma_j)\sin(4\alpha)\big>.
+\end{align*}
+
+Now observe that for two complex numbers $a$ and $b$, it is true that
+
+$$\operatorname{Re}(a\cdot b^*)=\operatorname{Re}(a)\cdot\operatorname{Re}(b)+\operatorname{Im}(a)\cdot\operatorname{Im}(b).$$
+
+Then setting $a=\gamma_i\gamma_j$ and $b=e^{4i\alpha}$, it must be true that
+
+$$\operatorname{Re}\left(\gamma_i\gamma_je^{-4i\alpha}\right)=\operatorname{Re}(\gamma_i\gamma_j)\cos(4\alpha)+\operatorname{Im}(\gamma_i\gamma_j)\sin(4\alpha).$$
+
+Combining this with our previous result, this means that
+
+$$\xi_-=\big<\operatorname{Re}(\gamma_i\gamma_j)\cos(4\alpha)+\operatorname{Im}(\gamma_i\gamma_j)\sin(4\alpha)\big>=\left<\operatorname{Re}\left(\gamma_i\gamma_je^{-4i\alpha}\right)\right>=\texttt{xim}.$$
+
+\section*{Schneider's $\xi_\times$ to Jarvis's $\frac{1}{2}\left(\texttt{xim\_im}-\texttt{xip\_im}\right)$}
+
+Starting from Schneider's definition of $\xi_\times$,
+
+\begin{align*}
+\xi_\times&=\left<\gamma_{i_t}\gamma_{j_\times}\right>\\
+&=\left<\operatorname{Re}\left(|\gamma_i|e^{2i(\theta_i-\alpha)}\right)\cdot\operatorname{Im}\left(|\gamma_j|e^{2i(\theta_j-\alpha)}\right)\right>\\
+&=\big<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\alpha)\right)\sin\left(2(\theta_j-\alpha)\right)\big>.\\
+\end{align*}
+
+Using the trig identity
+
+\begin{equation}\label{trig3}
+\cos(u)\sin(v)=\frac{1}{2}\left[\sin(u+v)-\sin(u-v)\right],
+\end{equation}
+
+the previous equation becomes
+
+\begin{align*}
+\xi_\times&=\left<|\gamma_i|\cdot|\gamma_j|\cdot\frac{1}{2}\big[\sin\left(2(\theta_i+\theta_j-2\alpha)\right)-\sin\left(2(\theta_i-\theta_j)\right)\big]\right>.
+\end{align*}
+
+Next, applying the identities
+
+\begin{equation}\label{trig4}
+\sin(u\pm v)=\sin(u)\cos(v)\pm\cos(u)\sin(v)
+\end{equation}
+
+along with \eqref{trig2} iteratively until each trig function only has a single term, the equation becomes
+
+\begin{align*}
+\xi_\times&=\Big<|\gamma_i|\cdot|\gamma_j|\cdot\frac{1}{2}\Big(\left[\sin(2\theta_i)\cos(2\theta_j)+\cos(2\theta_i)\sin(2\theta_j)\right]\cos(4\alpha)\\
+&\qquad\qquad\qquad\quad-\left[\cos(2\theta_i)\cos(2\theta_j)-\sin(2\theta_i)\sin(2\theta_j)\right]\sin(4\alpha)\\
+&\qquad\qquad\qquad\quad-\sin(2\theta_i)\cos(2\theta_j)+\cos(2\theta_i)\sin(2\theta_j)\Big)\Big>\\
+&=\Big<\frac{1}{2}\Big(\left[\operatorname{Im}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)+\operatorname{Re}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\right]\cos(4\alpha)\\
+&\qquad-\left[\operatorname{Re}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)-\operatorname{Im}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\right]\sin(4\alpha)\\
+&\qquad-\operatorname{Im}(\gamma_i)\operatorname{Re}(\gamma_j)+\operatorname{Re}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\Big)\Big>.\\
+\end{align*}
+
+Using the identities \eqref{complex1} and \eqref{complex2}, this can be simplified to
+
+\begin{align*}
+\xi_\times&=\left<\frac{1}{2}\big[\operatorname{Im}(\gamma_i\gamma_j)\cos(4\alpha)-\operatorname{Re}(\gamma_i\gamma_j)\sin(4\alpha)-\operatorname{Im}(\gamma_i\gamma_j^*)\big]\right>.
+\end{align*}
+
+Consider again two complex numbers $a$ and $b$. Observe that
+
+$$\operatorname{Im}(a\cdot b^*)=\operatorname{Im}(a)\cdot\operatorname{Re}(b)-\operatorname{Re}(a)\cdot\operatorname{Im}(b).$$
+
+Then setting $a=\gamma_i\gamma_j$ and $b=e^{4i\alpha}$, it must be true that
+
+$$\operatorname{Im}\left(\gamma_i\gamma_je^{-4i\alpha}\right)=\operatorname{Im}(\gamma_i\gamma_j)\cos(4\alpha)-\operatorname{Re}(\gamma_i\gamma_j)\sin(4\alpha).$$
+
+Combing these results give
+
+\begin{align*}
+\xi_\times&=\left<\frac{1}{2}\big[\operatorname{Im}(\gamma_i\gamma_j)\cos(4\alpha)-\operatorname{Re}(\gamma_i\gamma_j)\sin(4\alpha)-\operatorname{Im}(\gamma_i\gamma_j^*)\big]\right>\\
+&=\left<\frac{1}{2}\big[\operatorname{Im}\left(\gamma_i\gamma_je^{-4i\alpha}\right)-\operatorname{Im}(\gamma_i\gamma_j^*)\big]\right>\\
+&=\frac{1}{2}\big[\texttt{xim\_im}-\texttt{xip\_im}\big].
+\end{align*}
+
+as desired.
 

### 2016-05-24 doc/thesis_swe.tex
Thesis updates.

@@
 
+If all galaxies were spherical, then the measurement of their ellipticities would give an exact description of the lensing done by foreground mass structures.
+Unfortunately, the intrinsic ellipticities of background galaxies contribute significant noise as we do not know how any individual galaxy ellipticity has been altered by lensing.
+However as two sources lensed by the same foreground mass will have their ellipticities distorted (in a similar way), their lensed ellipticities should be correlated regardless of intrinsic orientation.
+The average correlation of a sufficient number of galaxy pairs should overcome the noise and lead to a detectable signal.
+Importantly, this implies that \textit{the correlation of galaxy ellipticities is a probe of the underlying dark matter mass distribution} (Citation!).
+
+The mathematical tool that measures this average correlation as a function of separation distance between two galaxies is called the ellipticity-ellipticity ($\varepsilon$-$\varepsilon$) correlation function.
+A quick overview of this function is given below, but readers that are unfamiliar with correlation functions in the context of cosmology or want a visual aid should see Appendix (??).
+
+Given two galaxies with ellipticities $\varepsilon_i$ and $\varepsilon_j$ whose orientation is offset by polar angle $\alpha$, the tangential and cross-component components of the ellipticities, $\varepsilon_t$ and $\varepsilon_\times$ respectively, for each are defined as
+\begin{align}
+\varepsilon_{n_t}&=-\operatorname{Re}\left(\varepsilon e^{-2i\alpha}\right),\\
+\varepsilon_{n_\times}&=-\operatorname{Im}\left(\varepsilon e^{-2i\alpha}\right).
+\end{align}
+
+\noindent Instead of using the autocorrelation and cross-correlation between these quantities, it turns out to be more convenient to define the combinations
+
+\begin{align}\label{gg_corr_def}
+\xi_\pm&=\left<\varepsilon_{i_t}\varepsilon_{j_t}\right>\pm\left<\varepsilon_{i_\times}\varepsilon_{j_\times}\right>\\
+\xi_\times&=\left<\varepsilon_{i_t}\varepsilon_{j_\times}\right>
+\end{align}
+
+\noindent where $\theta$ is the position vector of the first galaxy and $\Delta\vec{\theta}$ is the angular separation vector between the pair of galaxies \cite{schneider}.
+Gravitational lensing shears ellipticities tangentially, so $\xi_\times(\Delta\theta)$ should vanish with enough galaxies.
+(\textcolor{red}{Why is $\xi_-$ expected to be zero?}), which leaves $\xi_+(\Delta\theta)$ as the desired probe of lensing mass.
+
+As galaxies will only be lensed by the same foreground mass at relatively small separation distances, the $\varepsilon$-$\varepsilon$ correlation function decreases sharply as the separation increases.
+If the distribution of intrinsic galaxy ellipticities is indeed random, then their $\varepsilon$-$\varepsilon$ correlation function should be essentially zero across all separation scales.
+
+A similar asdf often used in asdf is the galaxy-mass correlation function, which measures asdf and isdefined as
+\begin{equation}\label{ng_corr_def}
+\xi=
+\end{equation}
+
+\noindent where...
+
 %%==========================================================================================================================================
@@
 %%------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{??}
+\subsection{Dark Matter Convergence Mass Maps}
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+%% 3 panel plot of binned Hilbert map, Pangloss map, and difference
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=0.475\textwidth]{figs-swe/thesis/kappamaps.png}
+%     \captionsetup{justification=raggedright,singlelinecheck=false}
+%     \caption{CAPTION}
+%     \label{corr_fraction}
+% \end{figure}
+%
+%%------------------------------------------------------------------------------------------------------------------------------------------
+
+(Explain figures, difference in maps, binning process, etc.)
 

### 2016-05-25 doc/thesis_swe.tex
Updated the correlation function and smooth-component correction sections.

@@
 %%==========================================================================================================================================
-\section{Cosmological Background}
+\section{Cosmological Background} \label{background}
 
@@
 %%------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Dark Matter Halos}
+\subsection{Dark Matter Halos} \label{halos}
 
@@
 %%------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Filaments, Voids, and the Smooth-Component Correction}
+\subsection{Filaments, Voids, and the Smooth-Component Correction} \label{scc}
 
@@
 \noindent Combining this result with Equation \eqref{temp_solution} leads to the desired proper volume element given by
-\begin{equation}
+\begin{equation}\label{pvolume_element}
 dV_p=\frac{d_Hd_M(z)^2}{E(z)(1+z)^3}dzd\Omega.
@@
 %%------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Gravitational Lensing}
+\subsection{Gravitational Lensing} \label{grav_lensing}
 
@@
 %%------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Galaxies as Ellipses}
+\subsection{Galaxies as Ellipses} \label{galaxies_as_ellipses}
 
@@
 %%------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Correlation Functions}
-
-A common tool used by cosmologists to measure...
+\subsection{Correlation Functions} \label{corr_functions}
 
@@
 
-The mathematical tool that measures this average correlation as a function of separation distance between two galaxies is called the ellipticity-ellipticity ($\varepsilon$-$\varepsilon$) correlation function.
+The mathematical tool that measures the average correlation as a function of separation distance between two galaxies is called the ellipticity-ellipticity ($\varepsilon$-$\varepsilon$) correlation function.
 A quick overview of this function is given below, but readers that are unfamiliar with correlation functions in the context of cosmology or want a visual aid should see Appendix (??).
@@
 \begin{align}
-\varepsilon_{n_t}&=-\operatorname{Re}\left(\varepsilon e^{-2i\alpha}\right),\\
-\varepsilon_{n_\times}&=-\operatorname{Im}\left(\varepsilon e^{-2i\alpha}\right).
+\varepsilon_{k_t}&=-\operatorname{Re}\left(\varepsilon_k e^{-2i\alpha}\right),\\
+\varepsilon_{k_\times}&=-\operatorname{Im}\left(\varepsilon_k e^{-2i\alpha}\right).
 \end{align}
 
-\noindent Instead of using the autocorrelation and cross-correlation between these quantities, it turns out to be more convenient to define the combinations
+\noindent Instead of using the autocorrelation and cross-correlation of these quantities, it turns out to be more convenient to define the combinations
 
 \begin{align}\label{gg_corr_def}
-\xi_\pm&=\left<\varepsilon_{i_t}\varepsilon_{j_t}\right>\pm\left<\varepsilon_{i_\times}\varepsilon_{j_\times}\right>\\
-\xi_\times&=\left<\varepsilon_{i_t}\varepsilon_{j_\times}\right>
+\xi_\pm(\Delta\theta)&=\left<\varepsilon_{i_t}(\vec{\theta})\varepsilon_{j_t}(\vec{\theta}+\vec{\Delta\theta})\right>\pm\left<\varepsilon_{i_\times}(\vec{\theta})\varepsilon_{j_\times}(\vec{\theta}+\vec{\Delta\theta})\right>\\
+\xi_\times(\vec{\Delta\theta})&=\left<\varepsilon_{i_t}(\vec{\theta})\varepsilon_{j_\times}(\vec{\theta}+\vec{\Delta\theta})\right>
 \end{align}
 
-\noindent where $\theta$ is the position vector of the first galaxy and $\Delta\vec{\theta}$ is the angular separation vector between the pair of galaxies \cite{schneider}.
+\noindent where $\vec{\theta}$ is the position vector of the first galaxy and $\Delta\vec{\theta}$ is the angular separation vector between the pair of galaxies \cite{schneider}.
 Gravitational lensing shears ellipticities tangentially, so $\xi_\times(\Delta\theta)$ should vanish with enough galaxies.
@@
 %%==========================================================================================================================================
-\section{Pangloss: Line of Sight Mass Reconstructions}
+\section{Pangloss: Line of Sight Mass Reconstructions} \label{pangloss}
 
@@
 %%------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Model Assumptions}
+\subsection{Model Assumptions} \label{assumptions}
 While \texttt{Pangloss} may be used more generally, the present analysis makes some additional strong assumptions to simplify the problem for a first attempt at making weak lensing predictions.
@@
 %%------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{The Millennium Simulation}
+\subsection{The Millennium Simulation} \label{ms}
 \texttt{Pangloss} cannot be used to make dark matter mass maps using existing galaxy catalogs until it is tested on a simulated universe with known dark matter structure to determine how accurately and precisely it predicts the lensing of background sources.
@@
 To calculate the convergence and shear contribution of each halo, the physical distance from the halo to the line of sight was needed.
-To increase the speed of distance calculations, the foreground halo redshifts were first binned to a grid of 100 equally-sized redshift bins from $z=0$ to the sourced redshift of $z=1.3857$ and then converted to physical distances using the cosmology defined by the Millennium Simulation.
+To increase the speed of distance calculations, the foreground halo redshifts were first binned to a grid of 100 equally-sized redshift bins $\Delta z\approx0.013857$ from $z=0$ to the sourced redshift of $z=1.3857$, and then converted to physical distances using the cosmology defined by the Millennium Simulation.
 
@@
 %%------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Calculating the Smooth-Component Correction}
+\subsection{Calculating the Smooth-Component Correction} \label{calc_scc}
 
@@
 
-(Introduce idea in Cosmological background, but cover image and specific details to implementation here.)\\
-
-(Volume and Surface density plots for s.c.c. redshift slices)
+As discussed in Section \ref{scc}, the halo model does not account for additional mass structures such as filaments.
+To apply the smooth-component correction to \texttt{Pangloss}, the mean mass density $\rho(z)$ and halo density $\rho_h(z)$ had to be calculated at each of the 100 redshift bins.
+For $\rho_h(z)$, this was done by summing all halo masses $M_{h,i}$ in a given redshift bin and integrating Equation \eqref{pvolume_element} from ${z-\Delta z/2}$ to ${z+\Delta z/2}$, except for the boundary bins.
+Once $\rho_h(z)$ had been calculated for each redshift slice, the projected surface mass density was found by integrating over the redshift interval,
+\begin{equation}\label{surface_density} 
+\sum(z)=\int_{z-\frac{\Delta z}{2}}^{z+\frac{\Delta z}{2}} \rho_s(z)\,dz=\int_{z-\frac{\Delta z}{2}}^{z+\frac{\Delta z}{2}} \rho(z)-\rho_h(z)\,dz,
+\end{equation}
+
+\noindent and the convergence contribution of the mass sheet was calculated using Equation \eqref{convergence} with ${z_l=z}$ and ${z_s=1.3857}$.
+The corrected total convergence for a given background source is simply the sum of the halo contributions and the asfd.
+There is no additional shear produced by a uniform sheet of mass (citation!), but the corrected reduced shear is now calculated using the corrected total $\kappa$ in Equation \eqref{reduced_shear}.
+A diagram of this process is shown in Figure \ref{fig:scc}.
+
+The volume and projected surface mass densities of each redshift slice are shown in Figures \ref{fig:volume_densities} and \ref{fig:surface_densities} respectively. (Describe plots)
 
@@
 %         \caption{CAPTION}
-%         \label{volume_densities}
+%         \label{fig:volume_densities}
 %     \end{subfigure}
@@
 %         \caption{CAPTION}
-%         \label{surface_densities}
+%         \label{fig:surface_densities}
 %     \end{subfigure}

### 2016-05-26 doc/thesis_swe.tex
Thesis update.

@@
 
-Intro\\
-
-Place in context of recent work\\
-
-The goals of this thesis are two answer the two following questions: How accurately can we reconstruct line-of-sight dark matter mass structures using a halo model?
-From our model outputs, how feasible is an inference of the stellar mass – halo mass relation parameters?\\
-
-Outline thesis
-
-% OLD: In a universe teeming with galaxies and light, it came as a shock when 20\textsuperscript{th} century astronomers discovered that most of the mass in the universe is in fact dark; the `normal' matter made of atoms that we interact with in everyday life, called baryonic matter, accounts for less than 20\% of the mass in the observable universe.
+In a universe teeming with galaxies and light, it came as a shock when 20\textsuperscript{th} century astronomers discovered that most of the mass in the universe is in fact dark; the `normal' matter made of atoms that we interact with in everyday life, called baryonic matter, accounts for less than 20\% of the mass in the observable universe.
 The remaining mass takes the form of an exotic dark matter that does not absorb or emit light, rendering it invisible to our telescopes.
@@
 
-% One of the most successful probes of dark matter has been gravitational lensing.
+One of the most successful probes of dark matter has been gravitational lensing.
 The path of light from distant `background' galaxies is bent when traveling through regions of space containing large amounts of `foreground' mass.
@@
 
-% While the effects of gravitational lensing can be dramatic, the shape of most galaxies is only distorted by a few percent and must be detected statistically as the intrinsic shape is not known.
-If a model for the distribution of dark matter in a region of foreground mass can accurately predict the statistical signal of this `weak' lensing of background sources, then the model can be used on galaxies in existing sky survey data to extrapolate the amount of dark matter in the region and construct large-scale maps of the dark matter in the universe.
-
-% In this paper, I attempt to do the former by applying a simple dark matter halo model to reconstruct mass along lines of sight in the Millennium Simulation and predict the weakly lensed ellipticities of generated background sources.
-A brief introduction into the theory of galaxy ellipticities, the effects of strong and weak gravitational lensing, and dark matter halos is discussed in Section II.
-The implementation of a halo model on the Millennium Simulation is described in Section III, and the results of the model on 3,240 galaxies on a field size of 324 arcmin$^2$, along with a comparison of the predicted lensed ellipticities to ray-traced ellipticities, is given in Section IV.
-Section V discusses limitations of the used framework as well as potential physical and computational improvements that can be made for upcoming work before concluding remarks in Section VI.
+While the effects of gravitational lensing can be dramatic, the shape of most galaxies is only distorted by a few percent and must be detected statistically as the intrinsic shape is not known.
+If a model for the distribution of dark matter in a region of foreground mass can accurately predict the statistical signal of this `weak' lensing of background sources, then the model can be used on galaxies in existing sky survey data to extrapolate the amount of dark matter in the region and construct large-scale maps of the dark matter in the universe.\\
+
+(Connect to previous work done by Collett et al., Hilbert et al., McCully et al., Pache et al., etc.)\\
+
+%By applying a simple dark matter halo model to reconstruct lensing mass along lines of sight in the Millennium Simulation to predict the weakly lensed ellipticities of generated background sources, in this thesis I attempt to answer the following questions:
+
+In this thesis, I apply a simple dark matter halo model to reconstruct lensing mass along lines of sight in the Millennium Simulation to predict the weakly lensed ellipticities of generated background sources.
+By doing so, I attempt to answer the following questions: Under the best possible circumstances of having noiseless redshifts and halo masses, how accurately can I reconstruct line-of-sight dark matter mass structures using a simple halo model?
+What fraction of dark matter mass is in halos?
+How feasible is an inference of the Millennium Simulation's cosmological hyper-parameters, such as the stellar mass-halo mass relation, using all available halo data?
+How long does such an inference take?
+
+A brief introduction to the halo model, the effects of strong and weak gravitational lensing, representing galaxy ellipticities, and cosmological correlation functions is discussed in Section II.
+The implementation of the \texttt{Pangloss} framework to make line of sight lensing predictions in the Millennium Simulation is described in Section III, and the results of the framework on ??
+galaxies on a field size of ??
+arcmin$^2$, along with a comparison of the predicted lensed ellipticities to ray-traced ellipticities, is given in Section IV.
+Section V explores the feasibility of using \texttt{Pangloss} to make parameter inferences using all available halo data either by likelihood estimation or approximate Bayesian computation.
+Section VI discusses limitations of the used framework as well as potential physical and computational improvements that can be made for upcoming work before concluding remarks in Section VII.
 
@@
 \subsection{Dark Matter Halos} \label{halos}
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+%% FIGURE: Millennium Simulation Distribution plots (cosmic web, galaxy clusters with/without dark matter)
+\begin{figure*}
+    \centering
+    \begin{subfigure}[H]{0.375\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/thesis/ms_galaxies.jpg}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{CAPTION}
+        \label{ms_galaxies}
+    \end{subfigure}
+    ~
+    %% Einstein Ring Figure
+    \begin{subfigure}[H]{0.375\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/thesis/ms_halos.jpg}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{CAPTION}
+        \label{ms_halos}
+    \end{subfigure}
+    \caption{}
+\end{figure*}
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
 
@@
 While the exact relation between the distribution of galaxies and dark matter is not known, this m
-
-%%------------------------------------------------------------------------------------------------------------------------------------------
-%% FIGURE: Millennium Simulation Distribution plots (cosmic web, galaxy clusters with/without dark matter)
-% \begin{figure*}
-%     \centering
-%     \begin{subfigure}[H]{0.4\textwidth}
-%         \includegraphics[width=\textwidth]{figs-swe/thesis/ms_galaxies.jpg}
-%         \captionsetup{justification=raggedright,singlelinecheck=false}
-%         \caption{CAPTION}
-%         \label{ms_galaxies}
-%     \end{subfigure}
-%     ~
-%     %% Einstein Ring Figure
-%     \begin{subfigure}[H]{0.4\textwidth}
-%         \includegraphics[width=\textwidth]{figs-swe/thesis/ms_halos.jpg}
-%         \captionsetup{justification=raggedright,singlelinecheck=false}
-%         \caption{CAPTION}
-%         \label{ms_halos}
-%     \end{subfigure}
-%     \caption{}
-% \end{figure*}
-
-%%------------------------------------------------------------------------------------------------------------------------------------------
 
@@
 %% Ellipticity Orientation Figure
-% \begin{figure*}
-%     \centering
-%     \begin{subfigure}[H]{0.415\textwidth}
-%         \includegraphics[width=\textwidth]{figs-swe/ellipse_orientations.png}
-%         \captionsetup{justification=raggedright,singlelinecheck=false}
-%         \caption{The shape of a galaxy image for various ellipticity components $\varepsilon_1$ and $\varepsilon_2$ on the $x$ and $y$-axes respectively. Taken from \cite{schneider}.}
-%         \label{ellipses}
-%     \end{subfigure}
-%     ~
-%     %% Einstein Ring Figure
-%     \begin{subfigure}[H]{0.425\textwidth}
-%         \includegraphics[width=\textwidth]{figs-swe/einstein_ring.png}
-%         \captionsetup{justification=raggedright,singlelinecheck=false}
-%         \caption{An image of the luminous red galaxy LRG 3-757 along with a strongly lensed background galaxy, called the `Cosmic Horseshoe' \cite{einstein_ring}.}
-%         \label{einstein_ring}
-%     \end{subfigure}
-%     \caption{}
-% \end{figure*}
+\begin{figure*}
+    \centering
+    \begin{subfigure}[H]{0.415\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/thesis/ellipse_orientations.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{The shape of a galaxy image for various ellipticity components $\varepsilon_1$ and $\varepsilon_2$ on the $x$ and $y$-axes respectively. Taken from \cite{schneider}.}
+        \label{ellipses}
+    \end{subfigure}
+    ~
+    %% Einstein Ring Figure
+    \begin{subfigure}[H]{0.425\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/thesis/einstein_ring.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{An image of the luminous red galaxy LRG 3-757 along with a strongly lensed background galaxy, called the `Cosmic Horseshoe' \cite{einstein_ring}.}
+        \label{einstein_ring}
+    \end{subfigure}
+    \caption{}
+\end{figure*}
 %%------------------------------------------------------------------------------------------------------------------------------------------
@@
 %% Pangloss Cartoon
-% \begin{figure*}
-%     \centering
-%     \includegraphics[width=0.85\textwidth]{figs-swe/pangloss_cartoon.png}
-%     \captionsetup{justification=raggedright,singlelinecheck=false}
-%     \caption{A cartoon model of how the \texttt{Pangloss} framework uses a dark matter halo model to reconstruct the foreground mass along the line of sight of a background source galaxy.
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.85\textwidth]{figs-swe/thesis/pangloss_cartoon.png}
+    \captionsetup{justification=raggedright,singlelinecheck=false}
+    \caption{A cartoon model of how the \texttt{Pangloss} framework uses a dark matter halo model to reconstruct the foreground mass along the line of sight of a background source galaxy.
 A `lightcone' centered at a background source is constructed with radius $R$ and populated with all foreground galaxies contained in this volume.
@@
 The shear and convergence along the line of sight contributed by each halo is calculated using \cite{lensing_calc}, and the predicted ellipticity is determined using the sum of these contributions and Equation \eqref{lensing}.}
-%     \label{pangloss_cartoon}
-% \end{figure*}
+    \label{pangloss_cartoon}
+\end{figure*}
 %%------------------------------------------------------------------------------------------------------------------------------------------
@@
 
-where $M_h$ is the halo mass and $R$ is the distance from the halo to the line of sight.
+\noindent where $M_h$ is the halo mass and $R$ is the distance from the halo to the line of sight.
+Numerical values are assigned by comparing a halo's individual $M_h$ and $R$ to a threshold $M_T$ and $R_T$:
+\begin{equation}\label{relevant_thresh}
+Rel(M_h,R)=\frac{(M_h/M_T)}{(R/R_T)^3}.
+\end{equation}
+
+In this work, the threshold values used are $M_T=10^{12}M_\odot$ and $R_T=10$ kpc.
 The relevance distribution for one background catalog realization with \textcolor{red}{???} foreground halos in a lightcone of radius \textcolor{red}{??} arcminutes is shown in Figure ??.
@@
 %% Relevance Distribution of all Halos
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=0.25\textwidth]{figs-swe/thesis/relevance_distribution.png}
-%     \captionsetup{justification=raggedright,singlelinecheck=false}
-%     \caption{CAPTION}
-%     \label{rel_dist}
-% \end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.475\textwidth]{figs-swe/thesis/relevance_distribution.png}
+    \captionsetup{justification=raggedright,singlelinecheck=false}
+    \caption{CAPTION}
+    \label{fig:rel_dist}
+\end{figure}
 %%------------------------------------------------------------------------------------------------------------------------------------------
@@
 %% Smooth-Component Correction Diagram
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=0.25\textwidth]{figs-swe/thesis/smooth_correction.png}
-%     \captionsetup{justification=raggedright,singlelinecheck=false}
-%     \caption{CAPTION}
-%     \label{scc}
-% \end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{figs-swe/thesis/smooth_correction.png}
+    \captionsetup{justification=raggedright,singlelinecheck=false}
+    \caption{CAPTION}
+    \label{fig:scc}
+\end{figure}
 %%------------------------------------------------------------------------------------------------------------------------------------------
@@
 Once $\rho_h(z)$ had been calculated for each redshift slice, the projected surface mass density was found by integrating over the redshift interval,
-\begin{equation}\label{surface_density} 
-\sum(z)=\int_{z-\frac{\Delta z}{2}}^{z+\frac{\Delta z}{2}} \rho_s(z)\,dz=\int_{z-\frac{\Delta z}{2}}^{z+\frac{\Delta z}{2}} \rho(z)-\rho_h(z)\,dz,
-\end{equation}
+\begin{align}\label{surface_density} 
+\sum(z)&=\int_{z-\frac{\Delta z}{2}}^{z+\frac{\Delta z}{2}} \rho_s(z)\,dz\nonumber\\
+&=\int_{z-\frac{\Delta z}{2}}^{z+\frac{\Delta z}{2}} \rho(z)-\rho_h(z)\,dz,
+\end{align}
 
 \noindent and the convergence contribution of the mass sheet was calculated using Equation \eqref{convergence} with ${z_l=z}$ and ${z_s=1.3857}$.
-The corrected total convergence for a given background source is simply the sum of the halo contributions and the asfd.
+The corrected total convergence for a given background source is simply the sum of the halo contributions and the smooth-component contributions.
 There is no additional shear produced by a uniform sheet of mass (citation!), but the corrected reduced shear is now calculated using the corrected total $\kappa$ in Equation \eqref{reduced_shear}.
@@
 
-The volume and projected surface mass densities of each redshift slice are shown in Figures \ref{fig:volume_densities} and \ref{fig:surface_densities} respectively. (Describe plots)
+The volume and projected surface mass densities of each redshift slice are shown in Figures \ref{fig:volume_densities} and \ref{fig:surface_densities} respectively.
+(Describe plots) (reduced shears before and after correction)
 
@@
 %% Surface and Volume densities for smooth-component correction redshift slices
-% \begin{figure*}
-%     \centering
-%     \begin{subfigure}[H]{0.415\textwidth}
-%         \includegraphics[width=\textwidth]{figs-swe/thesis/scc_vol_den.png}
-%         \captionsetup{justification=raggedright,singlelinecheck=false}
-%         \caption{CAPTION}
-%         \label{fig:volume_densities}
-%     \end{subfigure}
-%     ~
-%     %% Einstein Ring Figure
-%     \begin{subfigure}[H]{0.425\textwidth}
-%         \includegraphics[width=\textwidth]{figs-swe/thesis/scc_surf_deng.png}
-%         \captionsetup{justification=raggedright,singlelinecheck=false}
-%         \caption{CAPTION}
-%         \label{fig:surface_densities}
-%     \end{subfigure}
-%     \caption{}
-% \end{figure*}
+\begin{figure*}
+    \centering
+    % Volume
+    \begin{subfigure}[H]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/thesis/vol_densities.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{CAPTION}
+        \label{fig:volume_densities}
+    \end{subfigure}
+    ~
+    % Surface
+    \begin{subfigure}[H]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/thesis/surf_densities.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{CAPTION}
+        \label{fig:surface_densities}
+    \end{subfigure}
+    \caption{}
+\end{figure*}
+%%------------------------------------------------------------------------------------------------------------------------------------------
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+%% Kappa Contributions of S.C.C.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.425\textwidth]{figs-swe/thesis/kappa_distribution.png}
+    \captionsetup{justification=raggedright,singlelinecheck=false}
+    \caption{CAPTION}
+    \label{fig:kappa_dist}
+\end{figure}
 %%------------------------------------------------------------------------------------------------------------------------------------------
@@
 
-(Predict LOS kappa and shear measurements )
-
-Using the physical separation distance and halo mass, the shear and convergence contribution of a single foreground halo is calculated using methods described in Wright and Brainerd \cite{lensing_calc}.
-The total convergence and shear at the center of the lightcone is simply the sum of the convergence and shear contributions of each halo contained in the lightcone.
+Using the physical separation distance and halo mass, the shear and convergence contribution of a single foreground halo is calculated using methods described in Section \ref{grav_lensing} (see Wright and Brainerd \cite{lensing_calc} for far more detail).
+The total convergence and shear along the LOS of the lightcone is simply the sum of the convergence and shear contributions of each halo contained in the lightcone, as well as the additional convergence terms from the smooth-component correction.
 The \texttt{Pangloss} predicted lensed source ellipticity is then calculated using Equation \eqref{lensing}.
@@
 %%------------------------------------------------------------------------------------------------------------------------------------------
-%% Pangloss Lightcone Data
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=0.25\textwidth]{figs-swe/thesis/lightcone_data.png}
-%     \captionsetup{justification=raggedright,singlelinecheck=false}
-%     \caption{CAPTION}
-%     \label{rel_dist}
-% \end{figure}
+%% Pangloss Lightcone Data Plots
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.75\textwidth]{figs-swe/thesis/lightcone_plots.png}
+    \captionsetup{justification=raggedright,singlelinecheck=false}
+    \caption{CAPTION}
+    \label{fig:lightcone}
+\end{figure*}
 %%------------------------------------------------------------------------------------------------------------------------------------------
@@
 
-Figure (??) displays different views an example lightcone where the foreground halos are plotted as circles whose size are proportional to their galaxy brightness (top left), angular size (top center), convergence contributions (top right), and halo mass (bottom).
-Figure (??) shows a few examples of mass structures in the foreground catalog along with the ray-traced convergence and shear maps from (Hilbert cite).
-
-Figure (??) shows a
+Figure \ref{fig:lightcone} displays different views an example lightcone where the foreground halos are plotted as circles whose size are proportional to their galaxy brightness (top left), angular size (top center), convergence contributions (top right), and halo mass (bottom).
+Figure \ref{fig:subplots} shows a few examples of mass structures in the foreground catalog along with the ray-traced convergence (plotted in inverse greyscale) and shear maps (plotted as red ellipticity sticks) from \cite{ray_tracing}.
 
 Instead of comparing the ray-traced and \texttt{Pangloss} predicted ellipticities for individual galaxies, the lensing is characterized globally with correlation functions.
-As described in section (??), the ellipticity-ellipticity correlation function measures how correlated the ellipticities of pairs of galaxies are as a function of separation distance, while the galaxy-mass correlation function measures the correlation of lensed ellipticities around foreground halos as a function of separation distance.
+As described in section \ref{corr_functions}, the ellipticity-ellipticity correlation function measures how correlated the ellipticities of pairs of galaxies are as a function of separation distance, while the galaxy-mass correlation function measures the correlation of lensed ellipticities around foreground halos as a function of separation distance.
 Both correlation functions are used in this work to estimate how well the \texttt{Pangloss} framework models weak lensing by dark matter structures and are computed using the publicly available \texttt{TreeCorr} module written by Mike Jarvis\footnote{https://github.com/rmjarvis/TreeCorr}.
@@
 
-% For readers that are unfamiliar with correlation functions in the context of cosmology or want a visual aid, see the appendix.
+%%------------------------------------------------------------------------------------------------------------------------------------------
+%% Two or Three subplots of foreground/background/shear/kappa maps
+% \begin{figure*}
+%     \centering
+%     % Volume
+%     \begin{subfigure}[H]{0.415\textwidth}
+%         \includegraphics[width=\textwidth]{figs-swe/thesis/vol_densities.png}
+%         \captionsetup{justification=raggedright,singlelinecheck=false}
+%         \caption{CAPTION}
+%         \label{fig:volume_densities}
+%     \end{subfigure}
+%     ~
+%     % Surface
+%     \begin{subfigure}[H]{0.425\textwidth}
+%         \includegraphics[width=\textwidth]{figs-swe/thesis/surf_densities.png}
+%         \captionsetup{justification=raggedright,singlelinecheck=false}
+%         \caption{CAPTION}
+%         \label{fig:surface_densities}
+%     \end{subfigure}
+%     \caption{}
+%     \label{fig:subplots}
+% \end{figure*}
+%%------------------------------------------------------------------------------------------------------------------------------------------
 
@@
 %%------------------------------------------------------------------------------------------------------------------------------------------
-%% Ellipticity-Ellipticity Correlation
-% \begin{figure}
-%     \centering
-%     \begin{subfigure}{0.475\textwidth}
-%         \includegraphics[width=\textwidth]{figs-swe/gg_corr.png}
-%         \captionsetup{justification=raggedright,singlelinecheck=false}
-%         \caption{The ellipticity-ellipticity correlation function for 3,240 sources at separation distances from 0.1 to 2 arcminutes and a lightcone radius of $R=2$ arcminutes.
+% Ellipticity-Ellipticity Correlation
+\begin{figure}
+    \centering
+    \begin{subfigure}{0.475\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/gg_corr.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{CAPTION}
+        %The ellipticity-ellipticity correlation function for ??
+sources at separation distances from 0.1 to 2 arcminutes and a lightcone radius of $R=2$ arcminutes.
 While the correlation of the intrinsic ellipticities before lensing (blue) shows no correlation, the correlation of the ray-traced ellipticities (green) and halo model predicted ellipticities (purple) both show significant positive correlation on scales up to 1 arcminute.
 The halo model predicts a small negative correlation above this scale, while the ray-tracing shows positive correlation on all scales.}
-%         %The correlation of the intrinsic ellipticities before lensing is plotted in blue, and shows no correlation.
+        %The correlation of the intrinsic ellipticities before lensing is plotted in blue, and shows no correlation.
 The correlation of the true ray-traced ellipticities is plotted in green and shows significant positive correlation on all scales.
 The halo predicted correlation, plotted in purple, shows significant positive correlation until a separation distance of 0.8 arcminutes.
-%         \label{gg_corr}
-%     \end{subfigure}
-%     ~~
-%     \begin{subfigure}{0.475\textwidth}
-%         \includegraphics[width=\textwidth]{figs-swe/gg_corr_series.png}
-%         \captionsetup{justification=raggedright,singlelinecheck=false}
-%         \caption{The ellipticity-ellipticity correlation functions for a series of halo model frameworks with increasing lightcone radii from $R=1$ to $R=8$ arcminutes, all plotted in purple with various line styles.
+        \label{gg_corr}
+    \end{subfigure}
+    ~~
+    \begin{subfigure}{0.475\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/gg_corr_series.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{CAPTION}
+        %The ellipticity-ellipticity correlation functions for a series of halo model frameworks with increasing lightcone radii from $R=1$ to $R=8$ arcminutes, all plotted in purple with various line styles.
 These are compared to the same ray-traced correlation from Figure \ref{gg_corr}.}
-%         \label{gg_corr_series}
-%     \end{subfigure}
-%     \caption{}
-% \end{figure}
-%%------------------------------------------------------------------------------------------------------------------------------------------
+        \label{gg_corr_series}
+    \end{subfigure}
+    \caption{}
+\end{figure}
+%------------------------------------------------------------------------------------------------------------------------------------------
 
@@
 %% Galaxy-mass correlation function
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=0.475\textwidth]{figs-swe/ng_corr.png}
-%     \captionsetup{justification=raggedright,singlelinecheck=false}
-%     \caption{The galaxy-mass correlation function of 3,240 sources at separation distances from 0.1 to 2 arcminutes and a lightcone radius of $R=2$ arcminutes.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.475\textwidth]{figs-swe/ng_corr.png}
+    \captionsetup{justification=raggedright,singlelinecheck=false}
+    \caption{CAPTION}
+    %The galaxy-mass correlation function of 3,240 sources at separation distances from 0.1 to 2 arcminutes and a lightcone radius of $R=2$ arcminutes.
 There is no significant correlation of the intrinsic ellipticities (blue) as expected, and both the ray-traced correlation (green) and halo model correlation (purple) are positive on all scales.
 The green and purple curves are in agreement from 0.2 to 0.7 arcminutes, but have significant discrepancies on scales above and below this range.}
-%     \label{ng_corr}
-% \end{figure}
+    \label{ng_corr}
+\end{figure}
 %
@@
 %% 3 panel plot of binned Hilbert map, Pangloss map, and difference
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=0.475\textwidth]{figs-swe/thesis/kappamaps.png}
-%     \captionsetup{justification=raggedright,singlelinecheck=false}
-%     \caption{CAPTION}
-%     \label{corr_fraction}
-% \end{figure}
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{figs-swe/thesis/kappamaps.png}
+    \captionsetup{justification=raggedright,singlelinecheck=false}
+    \caption{CAPTION}
+    \label{fig:kappamaps}
+\end{figure*}
 %
@@
 %%------------------------------------------------------------------------------------------------------------------------------------------
-%% Mean lightcone CPU time
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=0.475\textwidth]{figs-swe/profile_bar.png}
-%     \captionsetup{justification=raggedright,singlelinecheck=false}
-%     \caption{The mean CPU runtime per lightcone for various runs with different (and cumulative) code optimizations described in the text.
-The cumulative changes account for a 70\% decrease in the mean CPU time and a halving of the variation.
-Currently, the prediction can be made for a single lightcone in\\$24\pm5$ ms.}
-%     \label{cpu_plot}
-% \end{figure}
+% Mean lightcone CPU time
+\begin{figure}
+    \centering
+    \includegraphics[width=0.475\textwidth]{figs-swe/thesis/profile_bar.png}
+    \captionsetup{justification=raggedright,singlelinecheck=false}
+    \caption{OLD: The mean CPU runtime per lightcone for various runs with different (and cumulative) code optimizations described in the text.
+The cumulative changes account for a ??\% decrease in the mean CPU time and a ??
+of the variation.
+Currently, the prediction can be made for a single lightcone in\\$??\pm??$ ms.}
+    \label{fig:cpu_plot}
+\end{figure}
 %%------------------------------------------------------------------------------------------------------------------------------------------
@@
 
-% OLD: While the current \texttt{Pangloss} framework can handle the lensing predictions of 3,240 sources in a 324 arcmin$^2$ field comfortably on a single processor, the goal is to scale up the framework to make predictions for background sources of the same number density in a 100 deg$^2$ field; this will require 3.6 million lightcones, each containing up to 1,000 foreground halos.
+While the current \texttt{Pangloss} framework can handle the lensing predictions of ??
+sources in a ??
+arcmin$^2$ field comfortably on a single processor, the goal is to scale up the framework to make predictions for background sources of the same number density in a 100 deg$^2$ field; this will require 3.6 million lightcones, each containing at least ???
+relevant foreground halos.
 Luckily, the prediction is trivially parallelizable as the shear and convergence calculation of each lightcone is independent of all other lightcones.
 This makes GPUs an attractive candidate for future work, as it would only take 360 GPUs with 10,000 threads each to carry out the prediction.
-Additionally, the 50 MB of RAM per lightcone is sufficiently small to fit 10,000 lightcones on a GPU.
+Additionally, the ??
+MB of RAM per lightcone is sufficiently small to fit 10,000 lightcones on a GPU.\\
+
+(More??)
 
@@
 % OLD: I would like to thank the Department of Energy for funding this research and giving me this wonderful opportunity, as well as SLAC National Laboratory for hosting me.
-This work was greatly aided by numerous conversations with Risa Wechsler from Stanford University and Matt Becker from the Kavli Institute for Particle Astrophysics and Cosmology (KIPAC).
+
+%This work was greatly aided by numerous conversations with Risa Wechsler from Stanford University and Matt Becker from the Kavli Institute for Particle Astrophysics and Cosmology (KIPAC), as well as Jesus Pando from DePaul University.
 Finally, I am incredibly grateful to Phil Marshall for his unending support, patience, and guidance throughout this research.
@@
 
-(Introduce issue a bit)\\
-
-From Jarvis \href{http://arxiv.org/pdf/astro-ph/0307393v2.pdf}{(Page 3)}:
+The definition for the shear-shear (or equivalently, in the case of weak lensing, ellipticity-ellipticity) correlation function components in Mike Jarvis's \texttt{TreeCorr} package is different from the common definition given in Equation \eqref{gg_corr_def} from Schneider \cite{schneider}.
+For the aid of those who wish to use this very useful package but still use the conventional correlation function defintion, I have outlined the connection between the two definitions and the outputs of \texttt{TreeCorr} below:
+
+\setlength\parindent{0pt}
+
+\vspace{0.25 in}
+
+From Jarvis \cite{jarvis} (Page 3):
 \begin{align}
@@
 
-From Schneider \href{http://arxiv.org/pdf/astro-ph/0509252v1.pdf}{(Page 92)}:
+From Schneider \cite{schneider} (Page 92):
 \begin{align}
@@
 \end{document}
-
-%% Currently, this appendix is not being used
-
-% \subsection{Deriving the Standard Correlation Function Definition from \texttt{TreeCorr}'s Definition}
-
-% \begin{itemize}
-% \item Introduction to difference between the common Schneider definition of lensing correlation functions and that used by Jarvis`s \texttt{TreeCorr} code
-% \item Here we derive the connection between the two
-% \item Definitions of each, along with references
-% \end{itemize}
-
-% From Jarvis \href{http://arxiv.org/pdf/astro-ph/0307393v2.pdf}{(Page 3)}:
-% \begin{align}
-% \xi_+&=\left<\gamma_i\gamma_j^*\right>=\texttt{xip}+i(\texttt{xip\_im})\label{s+}\\
-% \xi_-&=\left<\gamma_i\gamma_je^{-4i\alpha}\right>=\texttt{xim}+i(\texttt{xim\_im})\label{s-}
-% \end{align}
-
-% where $\alpha$ is the angle between the two objects $i,j$ and each $\gamma$ is given by $\gamma_n=|\gamma_n|e^{2i\theta_n}$ in polar form.\\
-
-% From Schneider \href{http://arxiv.org/pdf/astro-ph/0509252v1.pdf}{(Page 92)}:
-% \begin{align}
-% \xi_\pm&=\left<\gamma_{i_t}\gamma_{j_t}\right>\pm\left<\gamma_{i_\times}\gamma_{j_\times}\right>\label{s+-}\\
-% \xi_\times&=\left<\gamma_{i_t}\gamma_{j_\times}\right>\label{sx}
-% \end{align}
-
-% where $\gamma_{n_t}=-\operatorname{Re}\left(\gamma_n e^{-2i\alpha}\right)$ and $\gamma_{n_\times}=-\operatorname{Im}\left(\gamma_n e^{-2i\alpha}\right)$.\\
-
-% \section*{Schneider's $\xi_+$ to Jarvis's \texttt{xip}}
-
-% Starting with Schneider's definition, observe that
-% \begin{align*}
-% \xi_+&=\left<\gamma_{i_t}\gamma_{j_t}\right>+\left<\gamma_{i_\times}\gamma_{j_\times}\right>\\
-% &=\left<\operatorname{Re}\left(\gamma_ie^{-2i\alpha}\right)\cdot\operatorname{Re}\left(\gamma_je^{-2i\alpha}\right)\right>+\left<\operatorname{Im}\left(\gamma_ie^{-2i\alpha}\right)\cdot\operatorname{Im}\left(\gamma_je^{-2i\alpha}\right)\right>\\
-% &=\left<\operatorname{Re}\left(|\gamma_i|e^{2i(\theta_i-\alpha)}\right)\cdot\operatorname{Re}\left(|\gamma_j|e^{2i(\theta_j-\alpha)}\right)\right>+\left<\operatorname{Im}\left(|\gamma_i|e^{2i(\theta_i-\alpha)}\right)\cdot\operatorname{Im}\left(|\gamma_j|e^{2i(\theta_j-\alpha)}\right)\right>\\
-% &=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\alpha)\right)\cos\left(2(\theta_j-\alpha)\right)\right>+\left<|\gamma_i|\cdot|\gamma_j|\sin\left(2(\theta_i-\alpha)\right)\sin\left(2(\theta_j-\alpha)\right)\right>.
-% \end{align*}
-
-% Using the trig identities
-% \begin{align}
-% \cos(u)\cos(v)&=\frac{1}{2}\left[\cos(u-v)+\cos(u+v)\right],\\
-% \sin(u)\sin(v)&=\frac{1}{2}\left[\cos(u-v)-\cos(u+v)\right],
-% \end{align}
-
-% and the linearity of the expectation operator, it is straightforward to show that
-% %\begin{align*}
-% %\xi_+&=\left<|\gamma_i|\cdot|\gamma_j|\right>\cdot\left(\left<\frac{1}{2}\left[\cos\left(2(\theta_i-\theta_j)\right)+\cos\left(2(\theta_i+\theta_j-2\alpha)\right)\right]\right>+\left<\frac{1}{2}\left[\cos\left(2(\theta_i-\theta_j)\right)-\cos\left(2(\theta_i+\theta_j-2\alpha)\right)\right]\right>\right)\\
-% %&=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\theta_j)\right)\right>.
-% %\end{align*}
-% $$\xi_+=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\theta_j)\right)\right>.$$
-
-% Now using the identity
-% \begin{equation}\label{trig2}
-% \cos(u\pm v)=\cos\left(u\right)\cos\left(v\right)\mp\sin\left(u\right)\sin\left(v\right),
-% \end{equation}
-
-% the previous equation can be written as
-
-% \begin{align*}
-% \xi_+&=\left<|\gamma_i|\cdot|\gamma_j|\cdot\left[\cos\left(2\theta_i\right)\cos\left(2\theta_j\right)+\sin\left(2\theta_i\right)\sin\left(2\theta_j\right)\right]\right>\\
-% &=\left<\operatorname{Re}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)+\operatorname{Im}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\right>.
-% \end{align*}
-
-% Using the complex number identities
-
-% \begin{align}
-% \operatorname{Re}(z)&=\frac{1}{2}\left[z+z^*\right],\label{complex1}\\
-% \operatorname{Im}(z)&=\frac{1}{2i}\left[z-z^*\right]\label{complex2},
-% \end{align}
-
-% it follows that
-
-% \begin{align*}
-% \xi_+&=\left<\frac{1}{4}\left[(\gamma_i+\gamma_i^*)(\gamma_j+\gamma_j^*)-(\gamma_i-\gamma_i^*)(\gamma_j-\gamma_j^*)\right]\right>\\
-% &=\left<\frac{1}{2}\left[\gamma_i\gamma_j^*+(\gamma_i\gamma_j^*)^*\right]\right>\\
-% &=\left<\operatorname{Re}(\gamma_i\gamma_j^*)\right>=\texttt{xip}.
-% \end{align*}
-
-% \section*{Schneider's $\xi_-$ to Jarvis's \texttt{xim}}
-
-% The first few steps are identical to the previous section besides the negative in the definition of $\xi_-$, giving
-% \begin{align*}
-% \xi_-&=\left<\gamma_{i_t}\gamma_{j_t}\right>-\left<\gamma_{i_\times}\gamma_{j_\times}\right>\\
-% &=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\alpha)\right)\cos\left(2(\theta_j-\alpha)\right)\right>-\left<|\gamma_i|\cdot|\gamma_j|\sin\left(2(\theta_i-\alpha)\right)\sin\left(2(\theta_j-\alpha)\right)\right>\\
-% &=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i+\theta_j-2\alpha)\right)\right>.
-% \end{align*}
-
-% Now using Equation \eqref{trig2} twice, first letting $u=2(\theta_i+\theta_j)$ and $v=-4\alpha$, and then letting $u=2\theta_i$ and $v=2\theta_j$, this equation becomes
-
-% \begin{align*}
-% \xi_-&=\left<|\gamma_i|\cdot|\gamma_j|\Big(\left[\cos(2\theta_i)\cos(2\theta_j)-\sin(2\theta_i)\sin(2\theta_j)\right]\cos(4\alpha)+\left[\sin(2\theta_i)\cos(2\theta_j)+\cos(2\theta_i)\sin(2\theta_j)\right]\sin(4\alpha)\Big)\right>\\
-% &=\Big<\big[\operatorname{Re}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)-\operatorname{Im}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\big]\cos(4\alpha)+\big[\operatorname{Im}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)+\operatorname{Re}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\big]\sin(4\alpha)\Big>.
-% \end{align*}
-
-% Using the identities \eqref{complex1} and \eqref{complex2}, and simplifying the leftover terms, this equation can be shown to equal
-% \begin{align*}
-% \xi_-=\big<\operatorname{Re}(\gamma_i\gamma_j)\cos(4\alpha)+\operatorname{Im}(\gamma_i\gamma_j)\sin(4\alpha)\big>.
-% \end{align*}
-
-% Now observe that for two complex numbers $a$ and $b$, it is true that
-
-% $$\operatorname{Re}(a\cdot b^*)=\operatorname{Re}(a)\cdot\operatorname{Re}(b)+\operatorname{Im}(a)\cdot\operatorname{Im}(b).$$
-
-% Then setting $a=\gamma_i\gamma_j$ and $b=e^{4i\alpha}$, it must be true that
-
-% $$\operatorname{Re}\left(\gamma_i\gamma_je^{-4i\alpha}\right)=\operatorname{Re}(\gamma_i\gamma_j)\cos(4\alpha)+\operatorname{Im}(\gamma_i\gamma_j)\sin(4\alpha).$$
-
-% Combining this with our previous result, this means that
-
-% $$\xi_-=\big<\operatorname{Re}(\gamma_i\gamma_j)\cos(4\alpha)+\operatorname{Im}(\gamma_i\gamma_j)\sin(4\alpha)\big>=\left<\operatorname{Re}\left(\gamma_i\gamma_je^{-4i\alpha}\right)\right>=\texttt{xim}.$$
-
-% \section*{Schneider's $\xi_\times$ to Jarvis's $\frac{1}{2}\left(\texttt{xim\_im}-\texttt{xip\_im}\right)$}
-
-% Starting from Schneider's definition of $\xi_\times$,
-
-% \begin{align*}
-% \xi_\times&=\left<\gamma_{i_t}\gamma_{j_\times}\right>\\
-% &=\left<\operatorname{Re}\left(|\gamma_i|e^{2i(\theta_i-\alpha)}\right)\cdot\operatorname{Im}\left(|\gamma_j|e^{2i(\theta_j-\alpha)}\right)\right>\\
-% &=\big<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\alpha)\right)\sin\left(2(\theta_j-\alpha)\right)\big>.\\
-% \end{align*}
-
-% Using the trig identity
-
-% \begin{equation}\label{trig3}
-% \cos(u)\sin(v)=\frac{1}{2}\left[\sin(u+v)-\sin(u-v)\right],
-% \end{equation}
-
-% the previous equation becomes
-
-% \begin{align*}
-% \xi_\times&=\left<|\gamma_i|\cdot|\gamma_j|\cdot\frac{1}{2}\big[\sin\left(2(\theta_i+\theta_j-2\alpha)\right)-\sin\left(2(\theta_i-\theta_j)\right)\big]\right>.
-% \end{align*}
-
-% Next, applying the identities
-
-% \begin{equation}\label{trig4}
-% \sin(u\pm v)=\sin(u)\cos(v)\pm\cos(u)\sin(v)
-% \end{equation}
-
-% along with \eqref{trig2} iteratively until each trig function only has a single term, the equation becomes
-
-% \begin{align*}
-% \xi_\times&=\Big<|\gamma_i|\cdot|\gamma_j|\cdot\frac{1}{2}\Big(\left[\sin(2\theta_i)\cos(2\theta_j)+\cos(2\theta_i)\sin(2\theta_j)\right]\cos(4\alpha)\\
-% &\qquad\qquad\qquad\quad-\left[\cos(2\theta_i)\cos(2\theta_j)-\sin(2\theta_i)\sin(2\theta_j)\right]\sin(4\alpha)\\
-% &\qquad\qquad\qquad\quad-\sin(2\theta_i)\cos(2\theta_j)+\cos(2\theta_i)\sin(2\theta_j)\Big)\Big>\\
-% &=\Big<\frac{1}{2}\Big(\left[\operatorname{Im}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)+\operatorname{Re}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\right]\cos(4\alpha)\\
-% &\qquad-\left[\operatorname{Re}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)-\operatorname{Im}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\right]\sin(4\alpha)\\
-% &\qquad-\operatorname{Im}(\gamma_i)\operatorname{Re}(\gamma_j)+\operatorname{Re}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\Big)\Big>.\\
-% \end{align*}
-
-% Using the identities \eqref{complex1} and \eqref{complex2}, this can be simplified to
-
-% \begin{align*}
-% \xi_\times&=\left<\frac{1}{2}\big[\operatorname{Im}(\gamma_i\gamma_j)\cos(4\alpha)-\operatorname{Re}(\gamma_i\gamma_j)\sin(4\alpha)-\operatorname{Im}(\gamma_i\gamma_j^*)\big]\right>.
-% \end{align*}
-
-% Consider again two complex numbers $a$ and $b$. Observe that
-
-% $$\operatorname{Im}(a\cdot b^*)=\operatorname{Im}(a)\cdot\operatorname{Re}(b)-\operatorname{Re}(a)\cdot\operatorname{Im}(b).$$
-
-% Then setting $a=\gamma_i\gamma_j$ and $b=e^{4i\alpha}$, it must be true that
-
-% $$\operatorname{Im}\left(\gamma_i\gamma_je^{-4i\alpha}\right)=\operatorname{Im}(\gamma_i\gamma_j)\cos(4\alpha)-\operatorname{Re}(\gamma_i\gamma_j)\sin(4\alpha).$$
-
-% Combing these results give
-
-% \begin{align*}
-% \xi_\times&=\left<\frac{1}{2}\big[\operatorname{Im}(\gamma_i\gamma_j)\cos(4\alpha)-\operatorname{Re}(\gamma_i\gamma_j)\sin(4\alpha)-\operatorname{Im}(\gamma_i\gamma_j^*)\big]\right>\\
-% &=\left<\frac{1}{2}\big[\operatorname{Im}\left(\gamma_i\gamma_je^{-4i\alpha}\right)-\operatorname{Im}(\gamma_i\gamma_j^*)\big]\right>\\
-% &=\frac{1}{2}\big[\texttt{xim\_im}-\texttt{xip\_im}\big].
-% \end{align*}
-
-% as desired.
-
-% \end{document}
-
-% % Outline:
-
-% %% Introduction:
-% \begin{itemize}
-% \item Broad intro into cosmology and dark matter, set problem in context
-%     \begin{itemize}
-%     \item (Very) short introduction to history of dark matter, Zwicky, rotation curves, etc.
-%     \end{itemize}
-% \begin{itemize}
-% \item Introduction to gravitational lensing
-%     \begin{itemize}
-%     \item Convergence and Shear / Strong and Weak lensing
-%         \begin{itemize}
-%         \item Dramatic effect of strong lensing, how it is used for constraining cos. parameters
-%         \item Only a few hundred known, not good for making mass maps
-%         \item All galaxies are weakly lensed, good for our purposes
-%         \end{itemize}
-%     \end{itemize}
-% \end{itemize}
-% \item What this work does and aims for
-% \begin{itemize}
-%     \item We aim to implement a simple dark matter halo model to predict weak-lensing effects by foreground mass - and to make the prediction `quickly' and/or with large parallelization
-%     \item Quick summary of what we do in paper
-%         \begin{itemize}
-%         \item Use halo model to make approximation of dark matter mass distribution in Millennium Simulation
-%         \item Use shear-shear and galaxy-mass correlation functions as summary statistics
-%         \item Compare statistics to ray-traced data
-%         \item Discuss physial and computational shortcomings with current methodology
-%         \end{itemize}
-%     \end{itemize}
-% \end{itemize}
-
-% %% Theoretical Background:
-% \begin{itemize}
-% \item Galaxy ellipticities
-%     \begin{itemize}
-%     \item (Most) galaxies are not circular - have intrinsic ellipticities
-%         \begin{itemize}
-%         \item If they were all circular, we could measure the change in shape exactly!
-%         \end{itemize}
-%     \item Galaxies are not always well approximated by ellipses (reference)
-%     \item Mathematical formalism
-%     \item Plot of galaxy orientation given e1 and e2 from P.J. Marshall thesis
-%     \end{itemize}
-% \item Shape noise and PSF issues in weak lensing (distorting already weak signal)
-% \item Gravitational lensing
-%     \begin{itemize}
-%     \item Short introduction to problem setup for simple case (point mass maybe?)
-%     \item Assumptions made in a typical solution (thin lens approximation?)
-%     \item Show solution from Schneider
-%     \item Shear and convergence
-%     \item Measuring shear in weak lensing - a statistical feature
-%     \end{itemize}
-% \item Dark matter halos
-%     \begin{itemize}
-%     \item NFW profile and equation (reference)
-%     \item BMO truncation and equation (reference)
-%     \end{itemize}
-% \item SMHR? Or too distracting?
-% \end{itemize}
-
-% % Old theory:
-% %However, the important results for a point mass using the thin lens approximation can be summarized as follows: The distortion of a background galaxy image can be quantified by the linearized lens mapping Jacobi matrix $\mathcal{A}$ which can be written as
-
-% %$$\mathcal{A}=(1-\kappa)\,
-% %\begin{pmatrix}
-% %1-g_1 & -g2\\
-% %-g_2 & 1+g_1
-% %\end{pmatrix}$$
-
-% %\noindent where $\kappa$ and $g$ are the convergence and reduced shear respectively at the center of the background source.
-% %\begin{displaymath}
-% %  \varepsilon = \left\{
-% %    \begin{array}{lr}
-% %      \frac{\varepsilon_i+g}{1+g^*\varepsilon_i} & : |g|\leq1; \\
-% %      \frac{1+g\varepsilon_i^*}{\varepsilon^*+g^*} & : |g|>1.
-% %    \end{array}
-% %   \right.
-% %\end{displaymath}
-
-% %% The Pangloss Framework:
-% \begin{itemize}
-% \item Assumptions
-%     \begin{itemize}
-%     \item A catalog with galaxy
-%     \item Currently use actual dark matter halo mass for an idea of best case scenario - can run same analysis with masses sampled from SMHR (reference)
-%     \item PSF already accounted for in catalog and error low enough for weak lensing analysis
-%     \item Use actual redshift for best case scenario (but can easily be replaced by photometric redshift sampling)
-%     \end{itemize}
-% \item Millennium Simulation
-%     \begin{itemize}
-%     \item Instead of blindly using \texttt{Pangloss} to make dark matter mass maps using sky survey data, we instead test how accurately and precisely we can predict weakly-lensed shear and convergence
-%     \item Mention which M.S. we used
-%     \item S. Hilbert`s ray traced M.S. (reference)
-%         \begin{itemize}
-%         \item Can use the ray-traced convergence and shear to calculate the ``true'' lensed ellipticties and compare to \texttt{Pangloss}
-%         \end{itemize}
-%     \end{itemize}
-% \item Background galaxies
-%     \begin{itemize}
-%     \item random orientation
-%     \item ellipticity range (get numbers!)
-%     \item Accounting for shape noise
-%     \end{itemize}
-% \item Lightcones
-%     \begin{itemize}
-%     \item Instead of using all foreground mass in a field to calculate the lensing of a single background object, we create a lightcone centered at the source with a chosen radius $R$
-%     \item Drilling
-%         \begin{itemize}
-%         \item redshift grid to speed up calcuations
-%         \item Use the physical distance to line of sight in lensing calculations
-%             \begin{itemize}
-%             \item Redshift-to-distance relation (equation and reference)
-%             \end{itemize}
-%         \item Ranking galaxy `relevance'
-%             \begin{itemize}
-%             \item Want to only include the most important galaxies for lensing to speed up computation, as most will have negligable mass or be too far away
-%             \item Allows quicker lensing calculations, means we can make $R$ bigger
-%             \item Show `relevance` metric ($M/R^3$ but unitless)
-%             \item Include plot of predicted relevance vs kappa contribution??
-%             \end{itemize}
-%         \end{itemize}
-%     \item Lensing by Halos
-%         \begin{itemize}
-%         \item Treat each foreground halo as a separate lensing event
-%         \item Total lensing is the sum of each event
-%         \item Lookup table??
-%         \end{itemize}
-%     \item Include cartoon
-%     \end{itemize}
-% \item Checking the halo model: Use of correlation functions as summary statistics for ellipticity predictions
-%     \begin{itemize}
-%         \item Introduce the concept of correlation functions in general
-%             \begin{itemize}
-%             \item Definition
-%             \item Autocorrelation vs cross-correlation
-%             \item Use of correlation functions in cosmology
-%             \item Shear-shear and galaxy-mass correlation functions
-%                 \begin{itemize}
-%                 \item Reference appendix for Visualizing Correlation Functions
-%                 \end{itemize}
-%             \end{itemize}
-%         \item Use of Jarvis`s \texttt{TreeCorr} code to calculate cf`s
-%         \begin{itemize}
-%             \item Reference appendix for Jarvis proof
-%         \end{itemize}
-%     \end{itemize}
-% \item Show one map with ray-traced features and lensed ellipticities vs another map with \texttt{Pangloss} features and predicted ellipticities?
-% \end{itemize}
-
-% %% Results
-% \begin{itemize}
-% \item Maps??
-% \item Correlation Functions
-%     \begin{itemize}
-%     \item shear-shear
-%     \item galaxy-mass
-%     \item progression of each as $R$ increases??
-%     \item cf`s without shape noise and with shape noise
-%     \item cf`s with all galaxies vs with only `relevant' galaxies?
-%     \end{itemize}
-% \item The Need for Speed
-%     \begin{itemize}
-%     \item Table or graph of speedups and CPU time per lightcone progression (make sure to check \texttt{timeit} first!)
-%     \end{itemize}
-% \end{itemize}
-
-% %% Conclusion
-% \begin{itemize}
-% \item Issues with the \texttt{Pangloss} framework
-%     \begin{itemize}
-%     \item Systematic shear power under-prediction in cf`s
-%     \item Missing large-scale dark matter structure
-%     \end{itemize}
-%     \item Possibly missing features in model
-%         \begin{itemize}
-%         \item voids
-%         \item filaments
-%         \item stellar mass
-%         \end{itemize}
-%     \item Speed
-% \item Moving Foward
-%     \begin{itemize}
-%     \item Scaling up
-%         \begin{itemize}
-%         \item CPU and RAM numbers for lightcone parallelization from discussion with Debbie Bard
-%         \end{itemize}
-%     \item infer hyper-parameters from SMHR, physical distance, etc
-%     \item other stuff - too tired right now
-%     \end{itemize}
-% \end{itemize}
-
-% %% Acknowledgements
-% \begin{itemize}
-% \item DOE
-% \item SULI
-% \item Stanford University
-% \item KIPAC
-% \item Risa, Matt, Pat
-% \item Phil!!
-% \end{itemize}
-
-% %% References
-% \begin{itemize}
-% \item P.J. Marshall Thesis?
-% \item Collett et al.
-% \item S. Hilbert (ray-traced) http://arxiv.org/abs/0809.5035
-% \item Millennium Simulation
-% \item Schneider
-% \item Jarvis \texttt{TreeCorr}
-% \item lensing calculation http://arxiv.org/pdf/astro-ph/9908213v1.pdf
-% \item NFW profile
-% \item BMO truncation, BMO vs NFW http://arxiv.org/pdf/1301.1684v2.pdf
-% \item SMHR http://arxiv.org/pdf/1401.7329v1.pdf
-% \item Planck
-% \item galaxy curves
-% \item BAOs
-% \item LCDM
-% \item GR
-% \item corrFuns in cosmology
-% \item wl distortion percent
-% \item CFHT Lensing Survey
-% \end{itemize}
-
-% %% Appendix A
-% \begin{itemize}
-% \item Use as a brief introduction to the shear-shear and galaxy-mass correlation function as used in this work
-%     \begin{itemize}
-%     \item reference other (much more detailed) material for readers to find
-%     \end{itemize}
-% \item Include correlation value colormaps for $\xi_+$, $\xi_-$, and $\xi_\times$ along with discussion of correlation pattern
-% \item Include color-coded correlation visuals along with setup
-%     \begin{itemize}
-%     \item Galaxies around lens before lensing - correlation values scatter plot with no signal
-%     \item Galaxies around lens after lensing - correlation values scatter plot with signal
-%     \end{itemize}
-% \item B-modes and E-modes plot??
-% \end{itemize}

### 2016-05-26 doc/thesis_swe.tex
Thesis update.

@@
 \noindent where $\vec{\theta}$ is the position vector of the first galaxy and $\Delta\vec{\theta}$ is the angular separation vector between the pair of galaxies \cite{schneider}.
-Gravitational lensing shears ellipticities tangentially, so $\xi_\times(\Delta\theta)$ should vanish with enough galaxies.
+Gravitational lensing shears ellipticities tangentially, so $\xi_\times(\Delta\theta)$ should vanish with enough galaxies and therefore is a useful estimate of the bias.
 (\textcolor{red}{Why is $\xi_-$ expected to be zero?}), which leaves $\xi_+(\Delta\theta)$ as the desired probe of lensing mass.
@@
 
-A similar asdf often used in asdf is the galaxy-mass correlation function, which measures asdf and isdefined as
+A similar statistical measure often used in ... is the galaxy-mass correlation function, which measures ... and is defined as
 \begin{equation}\label{ng_corr_def}
@@
 %%==========================================================================================================================================
-\section{Feasibility of Parameter Inference using Pangloss}
+\section{Feasibility of Parameter Inference using Pangloss} \label{feasibility}
 
@@
 
-%%------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Likelihood Estimation}
-
-\begin{enumerate}
-\item Equation from Phil's dissertation
-\item Calculate time with and without drilling
-\item Time per lensing event, time per lightcone
-\end{enumerate}
-
-%%------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Approximate Bayesian Computation}
+One of the long-term goals of \texttt{Pangloss} is to be able to use all available sky survey data (sky positions, stellar masses, magnitude, photometric redshift, ellipticities, etc.) to make a hierarchial inference of the Universe's cosmological and galaxy population model hyper-parameters such as the density paramters $\Omega_m$ and $\Omega_\Lambda$, the Hubble constant $H_0$, and stellar mass - halo mass relation.
+This is a large undertaking and will require considerable testing and calibration on large N-body simulations such as the Millennium Simulation.
+As a first step towards this goal, I attempted to gague the feasibility of implementing two methods of parameter inference, maximum likelihood estimation and approximate Bayesian computation (ABC), using the current framework.
+The results of this feasibility test, particularly the CPU time per likelihood estimation, will help guide fugure work on \texttt{Pangloss}.
+For a detailed description of a probablistic modeling approach to gravitational lensing inference for large sky surveys, see \cite{grav_lens_inference}.
+Exploratory notes of implementing such an inference in the framework is available on \texttt{Pangloss}'s public github repository\footnote{https://github.com/drphilmarshall/Pangloss/issues/23}.
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Likelihood Estimation} \label{mle}
+
+Perhaps the most common method of parameter estimation of statistical models is called maximum-likelihood estimation (MLE).
+The likelihood is a function of the parameters of a statistical model that measures the probability of a data set or outcomes given the model parameters \cite{??}.
+It is the mathematical answer to the question, ``\textit{Given a particular set of parameters, what is the probability that this data set could have occured?}" The form of the likelihood depends on the properties and circumstances of the data, but generally has the form of the product of the probability density function $f$ of each individual observation $x_i$ given model parameters $\vec{\theta}$ \cite{likelihood}:
+\begin{equation}
+\mathcal{L}(\vec{\theta},x_1,x_2,\ldots,x_n)=\prod_{i=1}^nf(x_i|\vec{\theta}).
+\end{equation}
+
+A much more detailed introduction to likelihood and MLE is given in \cite{likelihood}. For this work, the likelihood is given by \cite{marshall_thesis}:
+\begin{equation}\label{likelihood}
+\mathcal{L}(\Sigma|\varepsilon_i,j,g_i,j)=\frac{1}{Z_L}\exp\left(\frac{-\chi^2}{2}\right),
+\end{equation}
+
+\noindent where $\varepsilon_i,j$ is the $j$-component of the $i$-th predicted lensed galaxy ellipticity, $g_i,j$ is the $j$-th component of the `true' reduced shear corresponding to $\varepsilon_i$, $\chi^2$ is the typical test statistic
+\begin{equation}\label{chi2}
+\chi^2=\sum_{i=1}^N\sum_{j=1}^2\frac{(\varepsilon_{i,j}-g_{i,j})^2}{\sigma^2},
+\end{equation}
+
+\noindent the normalization factor $Z_L$ is
+\begin{equation}
+Z_L=(2\pi\sigma^2)^{(2N)/2},
+\end{equation}
+
+\noindent where $N$ is the number of background galaxies (the $2N$ exponent is a result of the two ellipticity components for each of the $N$ galaxies), and the uncertainty in galaxy ellipticity estimation $\sigma$ is the sum in quadrature of the dispersions of intrinsic and `observed' (i.e.
+\texttt{Pangloss}-predicted) ellipticities:
+\begin{equation}\label{sigma}
+\sigma=\sqrt{\sigma_{\text{int}}^2+\sigma_{\text{obs}}^2}.
+\end{equation}
+
+While this works in principle, computationally it is much easier to work with the natural logarithm of the likelihood function called the log-likelihood.
+As the logarithm is a monotonically increasing function, the likelihood and log-likelihood achieve their maximum at the same points and so can be used interchangably in maximum likelihood estimation.
+From Equations \eqref{likelihood}-\eqref{sigma} is follows that the log-likelihood is given by
+\begin{align}\label{log-likelihood}
+\ln\mathcal{L}&=-\ln Z_L-\frac{1}{2}\chi^2\\
+&=-\frac{N}{2}\ln(2\pi\sigma)-\frac{1}{2}\sum_{i=1}^N\sum_{j=1}^2\frac{(\varepsilon_{i,j}-g_{i,j})^2}{\sigma^2}.
+\end{align}
+
+To use \texttt{Pangloss} to infer hyperparameters using MLE, a set of trial parameters would be sampled from appropriate prior distributions and used to calculate the lensed ellipticities of a mock background catalog using the methodology shown in Section \ref{pangloss}.
+The log-likelihood of this set of parameters would be calculated using Equation \eqref{log-likelihood}, and the process would be repeated for many parameter combinations until a sufficient approximation of the likelihood is made.
+The most likely hyperparameters would then simply be the set of parameters that led to the maximum likelihood.
+
+However, exploring the parameter space efficiently is a significant problem in MLE, especially in a dataset such as this which there are potentially millions or even billions of parameters (i.e.
+halo masses).
+For this thesis, I only compute the log-likelihood for a small handful of parameter sets to gague how feasible such an inference would be in future work with far more computational power.
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Approximate Bayesian Computation} \label{abc}
 
@@
 \end{enumerate}
+
+As discussed in the previous section, the likelihood is computationally expensive to calculate and difficult to ...
+
+ABC is a class of computational methods that estimate the posterior distribution of ... without calculating the likelihood function.
+
+A general overview of the ABC process is shown in Figure \ref{fig:abc} which is taken from \cite{abc}, which offers an excellent introduction to the topic.
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+% Mean lightcone CPU time
+\begin{figure}
+    \centering
+    \includegraphics[width=0.475\textwidth]{figs-swe/thesis/abc.png}
+    \captionsetup{justification=raggedright,singlelinecheck=false}
+    \caption{CAPTION}
+    \label{fig:abc}
+\end{figure}
+%%------------------------------------------------------------------------------------------------------------------------------------------
 

### 2016-05-26 pangloss/background.py
Added the `calculate_log_likelihood()` method to `background.py`. #93

@@ -213,6 +213,9 @@ class BackgroundCatalog(pangloss.Catalog):
         e1_int = np.random.normal(0.0,sigma_e,self.galaxy_count)
         e2_int = np.random.normal(0.0,sigma_e,self.galaxy_count)
 
+        # Save intrinsic ellipticity std
+        self.std_int = sigma_e
+
         # Change any |e|> 1 ellipticity components
         while (e1_int>1.0).any() or (e2_int>1.0).any():
 
@@ -909,6 +912,37 @@ class BackgroundCatalog(pangloss.Catalog):
         std_err = 1.0/np.sqrt(np.sum(w)) * 100.0
 
         return chi2, n_sigma, mean_err, std_err
+
+# ----------------------------------------------------------------------------
+
+    def calculate_log_likelihood(self):
+        '''
+        Calculate the log likelihood of the predicted ellipticities given model parameters.
+        Taken from Phil's thesis (page 61): http://www.slac.stanford.edu/~pjm/Site/CV_files/Marshall_PhDthesis.pdf
+        '''
+
+        # Calculate sigma
+        std_int = self.std_int
+        std_e1 = np.std(self.galaxies['e1_halo'])
+        std_e2 = np.std(self.galaxies['e2_halo'])
+        std_obs = np.mean([std_e1,std_e2])
+        sigma = np.sqrt(std_int**2+std_obs**2)
+
+        # Calculate the (log of) normalization constant
+        N = 2.*self.galaxy_count
+        logZ = (N/2.)*np.log(2.*np.pi*sigma**2)
+
+        # Calculate chi2
+        g = self.galaxies['g']
+        g1, g2 = g.real, g.imag
+        e1, e2 = self.galaxies['e1_halo'], self.galaxies['e2_halo']
+
+        chi2 = ( np.sum( (e1 - g1)**2 / sigma**2 ) + np.sum( (e2 - g2)**2 / sigma**2 ) )
+
+        # Calculate log-likelihood
+        log_likelihood = -logZ + (-0.5) * chi2
+
+        return log_likelihood
 
 # ----------------------------------------------------------------------------
 

### 2016-05-26 tests/mle_vs_abc.py
Added a new test to compare the time taken for a single likelihood calculation vs a single ABC selection. #93

@@ -1,0 +1,121 @@
+# Script to test feasibility of maximum likelihood estimation (MLE) vs approximate
+# Bayesian computation (ABC) for pangloss inference
+
+import numpy as np
+import scipy as sp
+import os,sys,timeit
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import cmath, cProfile
+import copy
+import cPickle as pickle
+from mpl_toolkits.axes_grid1.anchored_artists import AnchoredSizeBar
+
+# Turn on for verbose
+vb = True
+
+# Turn on for recording times
+time = True
+
+# Turn on for plotting correlation function plots
+corr_plots = True
+
+# time should only be used if `rel_compare` and `smooth_compare` are False!
+if time is True: assert rel_compare is False and smooth_compare is False
+
+# Pangloss:
+PANGLOSS_DIR = os.path.expandvars("$PANGLOSS_DIR")
+sys.path.append(PANGLOSS_DIR)
+import pangloss
+
+# Import Shear and Convergence maps
+if vb is True: print('Loading Kappa and Shear maps...')
+K = pangloss.Kappamap(PANGLOSS_DIR+'/data/GGL_los_8_0_0_N_4096_ang_4_rays_to_plane_37_f.kappa',FITS=False)
+S = pangloss.Shearmap([PANGLOSS_DIR+'/data/GGL_los_8_0_0_N_4096_ang_4_rays_to_plane_37_f.gamma_1',PANGLOSS_DIR+'/data/GGL_los_8_0_0_N_4096_ang_4_rays_to_plane_37_f.gamma_2'],FITS=False)
+
+# Import Foreground Catalog
+if vb is True: print('Loading foreground catalog...')
+config = pangloss.Configuration(PANGLOSS_DIR+'/example/example.config')
+F = pangloss.ForegroundCatalog(PANGLOSS_DIR+'/data/GGL_los_8_0_0_0_0_N_4096_ang_4_Guo_galaxies_on_plane_27_to_63.images.txt',config)
+#if smooth_plots is True: F.plot_mean_kappas()
+
+# Generate Background Catalog in the middle of the (0,0,0,0) field
+if vb is True: print('Generating background catalog...')
+
+# Can pick one of the domains below
+#d = [1.85,1.15,-1.85,-1.15]
+#d = [1.75,1.25,-1.75,-1.25]
[…]

### 2016-05-28 tests/correlation_progression.py
Created a new test file `correlation_progression.py` that calculates a series of `gg` and `ng` correlation functions from different lightcone radii, stores the data, creates both plots with all data, and saves the images to `/data/tests/`

@@ -1,0 +1,201 @@
+# Script used to create correlation function progression plots
+
+import numpy as np
+import scipy as sp
+import os,sys,timeit
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import cmath, cProfile
+import copy
+import cPickle as pickle
+from mpl_toolkits.axes_grid1.anchored_artists import AnchoredSizeBar
+
+# Fast correlation functions:
+try:
+    import treecorr
+except ImportError:
+    import pangloss.nocorr as treecorr
+
+# Turn on for verbose
+vb = True
+
+# Turn on for plotting correlation function plots
+corr_plots = True
+
+# Pangloss:
+PANGLOSS_DIR = os.path.expandvars("$PANGLOSS_DIR")
+sys.path.append(PANGLOSS_DIR)
+import pangloss
+
+# Import Shear and Convergence maps
+if vb is True: print('Loading Kappa and Shear maps...')
+K = pangloss.Kappamap(PANGLOSS_DIR+'/data/GGL_los_8_0_0_N_4096_ang_4_rays_to_plane_37_f.kappa',FITS=False)
+S = pangloss.Shearmap([PANGLOSS_DIR+'/data/GGL_los_8_0_0_N_4096_ang_4_rays_to_plane_37_f.gamma_1',PANGLOSS_DIR+'/data/GGL_los_8_0_0_N_4096_ang_4_rays_to_plane_37_f.gamma_2'],FITS=False)
+
+# Import Foreground Catalog
+if vb is True: print('Loading foreground catalog...')
+config = pangloss.Configuration(PANGLOSS_DIR+'/example/example.config')
+F = pangloss.ForegroundCatalog(PANGLOSS_DIR+'/data/GGL_los_8_0_0_0_0_N_4096_ang_4_Guo_galaxies_on_plane_27_to_63.images.txt',config)
+#if smooth_plots is True: F.plot_mean_kappas()
+
+# Generate Background Catalog in the middle of the (0,0,0,0) field
+if vb is True: print('Generating background catalog...')
+
+# Can pick one of the domains below
+#d = [1.85,1.15,-1.85,-1.15]
+#d = [1.75,1.25,-1.75,-1.25]
+#d = [1.65,1.35,-1.65,-1.35]
+d = [1.6,1.4,-1.6,-1.4] # 1440 galaxies
+#d = [1.55,1.45,-1.55,-1.45]
[…]

### 2016-05-28 tests/lens_compare.py
Test files update.

@@ -2,7 +2,7 @@
 
 import numpy as np
 import scipy as sp
-import os,sys
+import os,sys,timeit
 import astropy.io.fits as pyfits
 import matplotlib.pyplot as plt
 import cmath, cProfile
@@ -13,6 +13,9 @@ from mpl_toolkits.axes_grid1.anchored_artists import AnchoredSizeBar
 # Turn on for verbose
 vb = True
 
+# Turn on for likelihood estimation time
+time = True
+
 # Turn on for pickling correlation data
 pickle = False
 
@@ -20,7 +23,7 @@ pickle = False
 rel_plots = False
 
 # Turn on for smooth-component correction plots
-smooth_plots = True
+smooth_plots = False
 
 # Turn on for plotting correlation function plots
 corr_plots = True
@@ -32,7 +35,10 @@ rel_compare = False
 smooth_compare = False
 
 # Turn on for plotting maps
-maps = True
+maps = False
+
+# time should only be used if `rel_compare` and `smooth_compare` are False!
+if time is True: assert rel_compare is False and smooth_compare is False
 
 # Pangloss:
 PANGLOSS_DIR = os.path.expandvars("$PANGLOSS_DIR")
@@ -52,6 +58,7 @@ F = pangloss.ForegroundCatalog(PANGLOSS_DIR+'/data/GGL_los_8_0_0_0_0_N_4096_ang_
 
 # Generate Background Catalog in the middle of the (0,0,0,0) field
 if vb is True: print('Generating background catalog...')
+
 # Can pick one of the domains below
 #d = [1.85,1.15,-1.85,-1.15]
 #d = [1.75,1.25,-1.75,-1.25]
@@ -62,6 +69,9 @@ d = [1.6,1.4,-1.6,-1.4] # 1440 galaxies
 #d = [1.55,1.52,-1.61,-1.59] # only galaxies in subplot
 #d = [1.55,1.54,-1.61,-1.6] # ~3 galaxies
 B = pangloss.BackgroundCatalog(N=10.0,sigma_e=0.01,domain=d,field=[0,0,0,0])
+
+# Start likelihood clock
+if time is True: start_time = timeit.default_timer()
 
 # Lens the background catalog by map
 if vb is True: print('Lensing background by map...')
@@ -88,15 +98,21 @@ print 'Lightcones have {0:.2f} +/- {1:.2f} galaxies'.format(mean_galaxies,std_ga
 if vb is True: print('Lensing background by halos..')
 relevance_lim = 0.0
[…]

### 2016-05-28 tests/mle_vs_abc.py

@@ -20,9 +20,6 @@ time = True
 # Turn on for plotting correlation function plots
 corr_plots = True
 
-# time should only be used if `rel_compare` and `smooth_compare` are False!
-if time is True: assert rel_compare is False and smooth_compare is False
-
 # Pangloss:
 PANGLOSS_DIR = os.path.expandvars("$PANGLOSS_DIR")
 sys.path.append(PANGLOSS_DIR)
@@ -52,70 +49,76 @@ d = [1.6,1.4,-1.6,-1.4] # 1440 galaxies
 #d = [1.55,1.52,-1.61,-1.59] # only galaxies in subplot
 #d = [1.55,1.54,-1.61,-1.6] # ~3 galaxies
 
-# Start all clocks
-if time is True: start_time = timeit.default_timer()
+# time data is stored in these arrays...
+T = 10 # number of time data points
+likelihood_time = []
+likelihood_total_time = []
+abc_time = []
+abc_total_time = []
 
-B = pangloss.BackgroundCatalog(N=10.0,sigma_e=0.01,domain=d,field=[0,0,0,0])
+for i in range(T):
+    print 'Run {}'.format(i)
+    # Start all clocks
+    if time is True: start_time = timeit.default_timer()
 
-# Lens the background catalog by map
-if vb is True: print('Lensing background by map...')
-B.lens_by_map(K,S)
-print 'Background catalog has',B.galaxy_count,'galaxies'
+    B = pangloss.BackgroundCatalog(N=10.0,sigma_e=0.01,domain=d,field=[0,0,0,0])
 
-# Drill the lightcones
-if vb is True: print('Drilling lightcones...')
-lc_radius = 6.0
-B.drill_lightcones(radius=lc_radius,foreground=F,save=False)
+    # Lens the background catalog by map
+    if vb is True: print('Lensing background by map...')
+    B.lens_by_map(K,S)
+    print 'Background catalog has',B.galaxy_count,'galaxies'
 
-# Calculate mean/std galaxies per lightcone
-galaxy_counts = [lightcone.galaxy_count for lightcone in B.lightcones]
-mean_galaxies = np.mean(galaxy_counts)
-std_galaxies = np.std(galaxy_counts)
-print 'Lightcones have {0:.2f} +/- {1:.2f} galaxies'.format(mean_galaxies,std_galaxies)
+    # Drill the lightcones
+    if vb is True: print('Drilling lightcones...')
+    lc_radius = 4.0
[…]

### 2016-05-28 doc/thesis_swe.tex
Thesis update.

@@
     \caption{}
+    \label{ms_compare}
 \end{figure*}
@@
 While the exact relation between the distribution of galaxies and dark matter is not known, simulations predict that early galaxies formed in the large gravitational potentials of over-dense regions of dark matter (CITE!).
-This suggests that, while we cannot map dark matter directly, galaxies should trace out at least some of the underlying dark matter structures \textcolor{red}{(Citation!)}.
-A comparrison of the predicted galaxy and dark matter distribution from a small region of the MS is shown in Figure (???).
+This suggests that, while we cannot map dark matter directly, galaxies should trace out at least some of the underlying dark matter structures (Citation!).
+A comparrison of the predicted galaxy and dark matter distribution from a small region of the MS is shown in Figure \ref{ms_compare}.
 
@@
 The simplest way to model the relationship between galaxies and the dark matter distribution is by enveloping each galaxy in a spherically symmetric dark matter `halo' of a certain mass $M_h$.
-These halos extend far beyond the edge of the visible galaxy that they enclose, with the Milky Way's own halo estimated to have a radius of \textcolor{red}{(Check and cite!)}.
+These halos extend far beyond the edge of the visible galaxy that they enclose, with the Milky Way's own halo estimated to have a radius of (Check and cite!).
 While the density profile of the halos may be complex, numerous simulations have shown that it can be well approximated locally by the Navarro-Frenk-White (NFW) profile which has the form
@@
 
-\noindent \textcolor{red}{where the constant $\rho_0$ and the scale radius $R_s$ are parameters that vary from halo to halo} \cite{nfw}.
+\noindent where the constant $\rho_0$ and the scale radius $R_s$ are parameters that vary from halo to halo \cite{nfw}.
 However, the NFW profile is not entierly physical as the total mass diverges as the desntiy is integrated out to an infinite radius, so this work uses a truncated NFW profile called the Baltz-Marshall-Oguri (BMO) profile given by
@@
 The halo model only accounts for dark matter structures associated with galaxies.
-However, this neglects other structures such as the filaments and voids that can be seen in Figure (??).
+However, this neglects other mass structures such as the filaments and voids that can be seen in Figure (??).
 Modelling these features accurately would be difficult; we could try, for example, to model filaments by attaching cylinders of dark matter between massive clusters of galaxies.
@@
 
-Instead, as the mean mass density of large enough ($\sim$100 Mpc) regions should approximate the mean mass density of the universe, we can make a `first-order' approximation by assuming that all additional mass (or absence of mass) is contained in a uniform `smooth-component' density that ensures the total mass density of any region equals the mean density of the universe at that redshift.
+Instead, as the mean mass density of large enough ($\sim$100 Mpc) regions should approximate the mean mass density of the universe, we can make a `first-order' approximation by assuming that all additional mass (or absence of mass) is contained in a uniform `smooth-component' density that ensures the total mass density of any sufficiently large region equals the mean density of the universe at that redshift.
 This assumption can be expressed as
@@
 
-Using the fluid equation and equation of state \textcolor{red}{(CITE)}, we can show that the energy density of non-relativistic matter $\varepsilon_m(z)$ evolves as
+Using the fluid equation and equation of state (Cite), we can show that the energy density of non-relativistic matter $\varepsilon_m(z)$ evolves as
 \begin{equation}\label{energy_evol}
@@
 To do this, we can start with the standard spherical volume element $dV=r^2drd\Omega$.
-However, we must be careful that (1) we are using proper distances, (2) account for the possibility of a curved universe, and (3) use the correct distance measure for $r$ (in this case, the angular diameter distance).
-From this we can infer that the proper volume element must have the form of
+However, one must be careful to (1) use proper distances, (2) account for the possibility of a curved universe, and (3) use the correct distance measure for $r$ (in this case, the angular diameter distance).
+From this one can infer that the proper volume element must have the form of
 \begin{equation}\label{proper_element}
@@
 While dark matter does not absorb or emit light, it does interact with light indirectly through gravitational lensing.
-The presence of matter curves spacetime locally which causes light to follow curved paths called geodesics \textcolor{red}{(clean up!)}.
+The presence of matter curves spacetime locally which causes light to follow curved paths called geodesics.
 The deviation in path is usually negligable, but can be significant in regions containing clusters of galaxies and their massive dark matter halos.
@@
 
-\noindent where $\sum(\vec{r},z_l)$ is the projected surface mass density of the lensing mass and $\sum_{cr}(z_l,z_s)$ is the critical surface density for a given source redshift $z_s$ and lens redshift $z_l$ (\textcolor{red}{Citation}).
+\noindent where $\sum(\vec{r},z_l)$ is the projected surface mass density of the lensing mass and $\sum_{cr}(z_l,z_s)$ is the critical surface density for a given source redshift $z_s$ and lens redshift $z_l$ (Citation).
 The shearing of the source is most often described by the complex shear $\gamma$ defined to be
@@
 
-(introduce issue)
+To calculate the lensed ellipticities in the previous section, galaxies must first be translated from pixel intensities into elliptical representations of the galaxies.
+This is not always possible for galaxies are diverse in type and shape and not all are well approximated by ellipses.
+However for this thesis, all galaxy ellipticities are simulated so this issue is avoided.
+For a more thorough analysis of measuring image ellipticities, see Schneider (2003) \cite{schneider}.
 
@@
 This compact notation combines the eccentricity and orientation of the ellipse into a single object.
-A plot from Schneider et al.
-\cite{schneider} showing the shape of elliptical galaxies for various values of $\varepsilon_1$ and $\varepsilon_2$ is shown in Figure \ref{ellipses}.
+A plot from Schneider (2003) \cite{schneider} showing the shape of elliptical galaxies for various values of $\varepsilon_1$ and $\varepsilon_2$ is shown in Figure \ref{ellipses}.
 
@@
 To account for this in generated galaxy images, a multiplicative bias parameter $M$ is often used to lessen the intrinsic ellipticity using
-$$\varepsilon_{obs}=M\cdot\varepsilon_{int}$$
-
-\noindent where $\varepsilon_{int}$ is the generated intrinsic ellipticity of the image and $\varepsilon_{obs}$ is the ellipticity that would be recorded by a detector.
+\begin{equation}\label{mult_bias}
+\varepsilon_{\text{obs}}=M\cdot\varepsilon_{\text{int}}
+\end{equation}
+
+\noindent where $\varepsilon_{\text{int}}$ is the generated intrinsic ellipticity of the image and $\varepsilon_{\text{obs}}$ is the ellipticity that would be recorded by a detector.
 
@@
     \caption{A cartoon model of how the \texttt{Pangloss} framework uses a dark matter halo model to reconstruct the foreground mass along the line of sight of a background source galaxy.
-A `lightcone' centered at a background source is constructed with radius $R$ and populated with all foreground galaxies contained in this volume.
+A `lightcone' centered at a background source is constructed with radius $R_L$ and populated with all foreground galaxies contained in this volume.
 Each foreground object has an attached dark matter halo and physical distance to the line of sight (dashed line).
@@
 \cite{collett_marshall} to reconstruct all the
-mass along the line of sight of each background galaxy using a halo model with smooth-component correction.
+mass along the lines of sight of generated background galaxies in the MS using a halo model with smooth-component correction.
 The lensing contribution of each halo is calculated, and the total lensing of the background galaxy is the sum of each halo contribution.
@@
 \subsection{Model Assumptions} \label{assumptions}
-While \texttt{Pangloss} may be used more generally, the present analysis makes some additional strong assumptions to simplify the problem for a first attempt at making weak lensing predictions.
+While \texttt{Pangloss} may be used more generally, the present analysis makes some additional strong assumptions to simplify the problem for a first attempt at making weak lensing predictions:
 
@@
 Clearly the third assumption will never be true for any observational data.
-However, this allows for a best-case scenario estimate of how well the \texttt{Pangloss} framework \textit{could} predict weak lensing effects given all possible information.
+However, this allows for a best-case estimate of how well the \texttt{Pangloss} framework \textit{could} predict weak lensing effects given all possible information.
 This assumption can be relaxed by sampling a dark matter halo mass from an assumed stellar mass - halo mass relation.
@@
 For this purpose, \texttt{Pangloss} was tested on galaxy catalogs from the Millennium Simulation, an N-body simulation consisting of over 10 billion dark matter `particles' each representing a billion solar masses and populated with about 20 million galaxies \cite{millennium_simulation}.
-The simulation contains baryonic and dark matter structure believed to be similar to our own universe, and uses cosmological parameters from WMAP 1\textsuperscript{st}-year data analysis which assumed a matter density of $\Omega_m=0.25$, a dark energy density of $\Omega_\Lambda=0.75$, and a Hubble constant of $H_0=73$ km$\,$s$^{-1}\,$Mpc$^{-1}$ (\textcolor{red}{CITE!!}).
+The simulation contains baryonic and dark matter structure believed to be similar to our own universe, and uses cosmological parameters from WMAP 1\textsuperscript{st}-year data analysis which assumed a matter density of $\Omega_m=0.25$, a dark energy density of $\Omega_\Lambda=0.75$, and a Hubble constant of $H_0=73$ km$\,$s$^{-1}\,$Mpc$^{-1}$ (Cite).
 From the work of Hilbert et al.
@@
 \subsection{Generating Background Galaxies}
-With a catalog of foreground galaxies chosen, a set of \textcolor{red}{???} background galaxies over a field of \textcolor{red}{???} arcmin$^2$ was generated, with density 10 per arcmin$^2$.
+With the (0,0,0,0) catalog of MS foreground galaxies chosen, a set of ??
+background galaxies over a field of ??
+arcmin$^2$ was generated, with density 10 per arcmin$^2$.
 The intrinsic orientation of each galaxy was sampled from a uniform distribution as, without lensing, there should be no preferred orientation due to the assumption of an isotropic universe.
@@
 While ideally all foreground mass in a field would be considered when predicting the weak lensing of a background galaxy, it is computationally prohibitive to do so.
-Instead, all foreground halos contained within a `lightcone' centered along the line of sight to the source and extending out to a chosen lightcone radius $R$ were considered when calculating the lensing contributions for the background source.
+Instead, all foreground halos contained within a `lightcone' centered along the line of sight to the source and extending out to a chosen lightcone radius $R_L$ were considered when calculating the lensing contributions for the background source.
 A cartoon model of this process is shown in Figure \ref{pangloss_cartoon}.
@@
 To calculate the convergence and shear contribution of each halo, the physical distance from the halo to the line of sight was needed.
-To increase the speed of distance calculations, the foreground halo redshifts were first binned to a grid of 100 equally-sized redshift bins $\Delta z\approx0.013857$ from $z=0$ to the sourced redshift of $z=1.3857$, and then converted to physical distances using the cosmology defined by the Millennium Simulation.
+To increase the speed of distance calculations, the foreground halo redshifts were first binned to a grid of 100 equally-sized redshift bins $\Delta z=0.013857$ from $z=0$ to the sourced redshift of $z=1.3857$, and then converted to physical distances using the cosmology defined by the Millennium Simulation.
 
@@
 McCully et al.
-\textcolor{red}{(CITE)} derived that the correct metric for determining the relevance of a given foreground halo to the overall lensing calculation to be given by
+(Cite) derived that the correct metric for determining the relevance of a given foreground halo to the overall lensing calculation to be given by
 \begin{equation}\label{relevant}
@@
 In this work, the threshold values used are $M_T=10^{12}M_\odot$ and $R_T=10$ kpc.
-The relevance distribution for one background catalog realization with \textcolor{red}{???} foreground halos in a lightcone of radius \textcolor{red}{??} arcminutes is shown in Figure ??.
+The relevance distribution for one background catalog realization with ??
+foreground halos in a lightcone of radius ??
+arcminutes is shown in Figure ??.
 As expected, there are very few massive halos along the line of sight and therefore only a small percentage of foreground halos should have a high relative contribution to the predicted lensing quantities.
@@
     \centering
-    \includegraphics[width=0.475\textwidth]{figs-swe/thesis/relevance_distribution.png}
+    \includegraphics[width=0.5\textwidth]{figs-swe/thesis/relevance_distribution.png}
     \captionsetup{justification=raggedright,singlelinecheck=false}
@@
 To apply the smooth-component correction to \texttt{Pangloss}, the mean mass density $\rho(z)$ and halo density $\rho_h(z)$ had to be calculated at each of the 100 redshift bins.
-For $\rho_h(z)$, this was done by summing all halo masses $M_{h,i}$ in a given redshift bin and integrating Equation \eqref{pvolume_element} from ${z-\Delta z/2}$ to ${z+\Delta z/2}$, except for the boundary bins.
+For $\rho_h(z)$, this was done by summing all halo masses $M_{h,i}$ in a given redshift bin and integrating Equation \eqref{pvolume_element} from ${z-\Delta z/2}$ to ${z+\Delta z/2}$, except for the boundary bins, and multiplying by the solid angle of a cone ${\Omega=2\pi(1-\cos R_L)}$.
 Once $\rho_h(z)$ had been calculated for each redshift slice, the projected surface mass density was found by integrating over the redshift interval,
@@
 The volume and projected surface mass densities of each redshift slice are shown in Figures \ref{fig:volume_densities} and \ref{fig:surface_densities} respectively.
-(Describe plots) (reduced shears before and after correction)
-
+In each plot, the halo density at each redshift slice is plotted in green, the smooth-component density in blue, and universe mean density in black, and a histogram of the galaxies per bin is shown in the background.
+In most redshift bins, the halo density is one to two orders of magnitude lower than than the universe mean density leading to a smooth-component density very close to that of the mean density.
+This seems to be in opposition to Pache et al.
+(year) \cite{pache} who found that halos constituted ??\% of simulation mass in ??.
+However, all mass densities are far below the critial density, plotted in red, and so well within the weak-lensing regime.
+The convergence distribution of each halo and 100 smooth-components is plotted in Figure \ref{fig:kappa_dist}.
 %%------------------------------------------------------------------------------------------------------------------------------------------
@@
     \centering
-    \includegraphics[width=0.425\textwidth]{figs-swe/thesis/kappa_distribution.png}
+    \includegraphics[width=0.475\textwidth]{figs-swe/thesis/kappa_distribution.png}
     \captionsetup{justification=raggedright,singlelinecheck=false}
@@
 %%==========================================================================================================================================
-\section{Checking the Pangloss Model}
+\section{Checking the Pangloss Model} \label{check}
 
@@
     \begin{subfigure}{0.475\textwidth}
-        \includegraphics[width=\textwidth]{figs-swe/gg_corr.png}
+        \includegraphics[width=\textwidth]{figs-swe/thesis/gg_corr.png}
         \captionsetup{justification=raggedright,singlelinecheck=false}
@@
     \begin{subfigure}{0.475\textwidth}
-        \includegraphics[width=\textwidth]{figs-swe/gg_corr_series.png}
+        \includegraphics[width=\textwidth]{figs-swe/thesis/gg_progression.png}
         \captionsetup{justification=raggedright,singlelinecheck=false}
@@
 
-The first test of the halo model was with the ellipticity-ellipticity correlation function with a lightcone radius of ??
+The first test of the halo model was with the $\varepsilon$-$\varepsilon$ correlation function with a lightcone radius of ??
 arcminutes which is given in Figure \ref{gg_corr}.
@@
 arcminutes.
-The correlation function of the intrinsic ellipticities plotted in blue shows no significant deviation from zero as expected, as before lensing the galaxies had random orientations.
-Both the ray-traced, plotted in green, and halo model, plotted in purple, ellipticities show positive correlation on small scales up to a separation of ??
-arcminutes.
-However, ...
-(New analysis depending on figure)
-
-% OLD: the ray-traced correlation is positive on all calculated scales while the halo model does not predict any significant correlation at separations above 1 arcminute.
-Additionally, while the shapes of the correlation functions for both sets of lensed ellipticities agree well until 1 arcminute, there is a clear systematic underprediction of shear power by the halo model on all scales.
-On average, the shear power is underpredicted by 117\%.
-
-Using the same catalog of background sources, this statistic was recalculated for the halo model ellipticities for various lightcone radii ranging from $R=1$ to $R=8$ arcminutes.
+The cross-component of the correlation function shows no significant deviation from zero as expected, as gravitational lensing only shears galaxies tangentially.
+For the $\xi_+$ component, the ray-traced (plotted in green) and halo model (plotted in purple) are in relative agreement from seperation scales of ??
+to ??
+minutes, but there is a clear systematic underprediction of shear power by the halo model on scales larger than ??.
+This may be indicative that the halo model does not adequately address large-scale mass structures, or that there is significant dark matter mass not correlated with galaxies.
+The normalized root-mean-square error (NRMSE) of the halo correlation is ??.
+
+Using the same catalog of background sources, this statistic was recalculated for the halo model ellipticities for various lightcone radii ranging from $R_L=1$ to $R_L=8$ arcminutes.
 The result is shown in Figure \ref{gg_corr_series}, where the series of model predicted correlation functions is compared to the ray-traced correlation function.
-As $R$ increases, the mean number of foreground galaxies contained in each lightcone grows quadratically from ${??\pm??}$ galaxies when $R=1$ arcminute to ${??\pm??}$ galaxies when $R=8$ arcminutes.
+As $R_L$ increases, the mean number of foreground galaxies contained in each lightcone grows quadratically from ${??\pm??}$ galaxies when $R_L=1$ arcminute to ${??\pm??}$ galaxies when $R_L=8$ arcminutes.
 Increasing the number of foreground objects, and thus increasing the mass and structure considered for shear and convergence predictions, systematically increased the predicted shear power on all scales.
 
-%While the series of predicted correlation functions appear to be converging towards the ray-traced correlation function, there is clearly diminishing shear power gains as $R$ increases.
+%While the series of predicted correlation functions appear to be converging towards the ray-traced correlation function, there is clearly diminishing shear power gains as $R_L$ increases.
 
@@
 The result is shown in Figure \ref{ng_corr}.
-As with the ellipticity-ellipticity correlation function, there is no significant correlation for the intrinsic ellipticities at any scale as expected.
 The lensed ellipticities from the ray-tracing and halo model both show positive correlation on all calculated scales and are in agreement on separations from ??
@@
 arcminutes.
-However, ....
-(New analysis)
-
-%the halo model is still systematically underpredicting the shear power on scales above 0.7 arcminutes, although now only by an average of 23\%.
-A new feature is the large overprediction of shear power on separation scales smaller than 0.2 arcminutes.
-However, background sources this close to foreground halos are often in the strong lensing regime which is not currently accounted for by the \texttt{Pangloss} framework.
-
-The galaxy-mass correlation function was similarly re-calculated at increasing lightcone radii from $R=1$ to $R=8$ arcminutes with the result in Figure ??. (Analyze new figure...)
+However, the halo model is still systematically underpredicting the shear power on scales above ??
+arcminutes, although now only by an average of ??\%.
+A new feature is the large overprediction of shear power on separation scales smaller than ??
+arcminutes.
+This is likely because background sources this close to foreground halos are often in the strong lensing regime which is not currently accounted for by the \texttt{Pangloss} framework.
+The NRMSE of the halo correlation is ??.
+
+The galaxy-mass correlation function was similarly re-calculated at increasing lightcone radii from $R=1$ to $R=8$ arcminutes with the result in Figure ??.
+As with the $\varepsilon$-$\varepsilon$ correlation, ...
 
@@
     \centering
-    \includegraphics[width=0.475\textwidth]{figs-swe/ng_corr.png}
+    \begin{subfigure}{0.475\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/thesis/ng_corr.png}
         \captionsetup{justification=raggedright,singlelinecheck=false}
@@
 The green and purple curves are in agreement from 0.2 to 0.7 arcminutes, but have significant discrepancies on scales above and below this range.}
-    \label{ng_corr}
+        \label{gg_corr}
+    \end{subfigure}
+    ~~
+    \begin{subfigure}{0.475\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/thesis/ng_progression.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{CAPTION}
+        \label{gg_corr_series}
+    \end{subfigure}
+    \caption{}
 \end{figure}
 %
-% ...Same progression corr function as gg??
-%
-%%------------------------------------------------------------------------------------------------------------------------------------------
-
-%%------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Correlation Fraction of Relevant Halos}
+%%------------------------------------------------------------------------------------------------------------------------------------------
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Correlation Fraction of Relevant Halos} \label{halo_fraction}
 
@@
 displays an example ellipticity-ellipticity correlation function comparrison of the halo model using all halos (purple) and halo model using halos above the relevance limit of (??
-$M_{\odot}/$Mpc$^3$), as well as the percent error of each predicted value between the two (models?).
+$M_{\odot}/$Mpc$^3$), as well as the percent error of each predicted value between the two implementations.
 This relevance limit resulted in $??\pm??$ relevant halos per lightcone, and resulted in a normalized root-mean-square error (NRMSE) of ??.
@@
 %%------------------------------------------------------------------------------------------------------------------------------------------
-%% Ellipticity-Ellipticity Correlation Comparrison
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=0.475\textwidth]{figs-swe/thesis/gg_corr_rel.png}
-%     \captionsetup{justification=raggedright,singlelinecheck=false}
-%     \caption{CAPTION}
-%     \label{gg_corr_rel}
-% \end{figure}
-%
-%%------------------------------------------------------------------------------------------------------------------------------------------
-
-%%------------------------------------------------------------------------------------------------------------------------------------------
-%% NRMSE and Correlation Fraction as function of Mean Relevant Halos
+% Correlation Function Comparrison
+\begin{figure}
+    \centering
+    \begin{subfigure}{0.475\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/thesis/rel_gg_compare.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{CAPTION}
+        %The ellipticity-ellipticity correlation function for ??
+sources at separation distances from 0.1 to 2 arcminutes and a lightcone radius of $R=2$ arcminutes.
+While the correlation of the intrinsic ellipticities before lensing (blue) shows no correlation, the correlation of the ray-traced ellipticities (green) and halo model predicted ellipticities (purple) both show significant positive correlation on scales up to 1 arcminute.
+The halo model predicts a small negative correlation above this scale, while the ray-tracing shows positive correlation on all scales.}
+        %The correlation of the intrinsic ellipticities before lensing is plotted in blue, and shows no correlation.
+The correlation of the true ray-traced ellipticities is plotted in green and shows significant positive correlation on all scales.
+The halo predicted correlation, plotted in purple, shows significant positive correlation until a separation distance of 0.8 arcminutes.
+        \label{fig:rel_gg_compare}
+    \end{subfigure}
+    ~~
+    \begin{subfigure}{0.475\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/thesis/rel_ng_compare.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{CAPTION}
+        %The ellipticity-ellipticity correlation functions for a series of halo model frameworks with increasing lightcone radii from $R=1$ to $R=8$ arcminutes, all plotted in purple with various line styles.
+These are compared to the same ray-traced correlation from Figure \ref{gg_corr}.}
+        \label{fig:rel_ng_compare}
+    \end{subfigure}
+    \caption{}
+\end{figure}
+
+%------------------------------------------------------------------------------------------------------------------------------------------
+
+%------------------------------------------------------------------------------------------------------------------------------------------
+% NRMSE and Correlation Fraction as function of Mean Relevant Halos
 % \begin{figure}
@@
 % \end{figure}
-%
+
 %%------------------------------------------------------------------------------------------------------------------------------------------
@@
 
-(Explain figures, difference in maps, binning process, etc.)
+While correlation functions can describe how well the lensing predictions are being made globally, it is still instructive to analyze the difference between the ray-traced and halo model projected mass maps.
+This was done by selecting a region of foreground mass, calculating the ray-traced and \texttt{Pangloss}-predicted convergence of a uniform grid of background sources in the field, and binning the convergence maps to a desired resolution.
+Convergence is proportional to projected surface mass density, so comparring the two convergence maps is equivalent to comparing their respecitve projected mass distributions.
+
+The result of a particular ??
+arcmin$^2$ field is shown in Figure \ref{fig:kappamaps}, where the ray-traced convergence is shown on the left, the halo model convergence is in the center, and the ray-traced convergence subtracted from the halo model convergence is shown on the right.
+While particular foreground masses are almost always predicted, the currently implemented halo model over-predicts the convergence throughout most of the field.
+The halo model does not appear to accurately account for the voids between foreground masses and over-predicts the mass of most ...
+This could partially be a result of incorrect halo profiles, but it is apparent that the smooth-component correction is not adequate to ...
 
@@
 A secondary goal of this research was to investigate how quickly the prediction for the shear and convergence for a single background source could be made.
-The mean CPU time required for the prediction per lightcone was ${80\pm10}$ ms for the first run.
+The mean CPU time required for the prediction per lightcone was ${??\pm??}$ ms for the first run.
 However, many small improvements to the coding infrastructure of \texttt{Pangloss} were made to speed up the prediction.
@@
 
-Introduction, explain difference between the two different methods.
-
-One of the long-term goals of \texttt{Pangloss} is to be able to use all available sky survey data (sky positions, stellar masses, magnitude, photometric redshift, ellipticities, etc.) to make a hierarchial inference of the Universe's cosmological and galaxy population model hyper-parameters such as the density paramters $\Omega_m$ and $\Omega_\Lambda$, the Hubble constant $H_0$, and stellar mass - halo mass relation.
+One of the long-term goals of \texttt{Pangloss} is to be able to use all available sky survey data (sky positions, stellar masses, magnitude, photometric redshift, ellipticities, etc.) to make a hierarchial inference of the Universe's cosmological and galaxy population model hyper-parameters such as the density paramters $\Omega_m$ and $\Omega_\Lambda$, the Hubble constant $H_0$, and stellar mass-halo mass relation \cite{smhr}.
 This is a large undertaking and will require considerable testing and calibration on large N-body simulations such as the Millennium Simulation.
-As a first step towards this goal, I attempted to gague the feasibility of implementing two methods of parameter inference, maximum likelihood estimation and approximate Bayesian computation (ABC), using the current framework.
+As a first step towards this goal, I attempted to gague the feasibility of implementing two methods of parameter inference, maximum likelihood estimation and approximate Bayesian computation, using the current framework.
 The results of this feasibility test, particularly the CPU time per likelihood estimation, will help guide fugure work on \texttt{Pangloss}.
 For a detailed description of a probablistic modeling approach to gravitational lensing inference for large sky surveys, see \cite{grav_lens_inference}.
-Exploratory notes of implementing such an inference in the framework is available on \texttt{Pangloss}'s public github repository\footnote{https://github.com/drphilmarshall/Pangloss/issues/23}.
+Exploratory notes of implementing such an inference in the framework is available on \texttt{Pangloss}'s public github repository\footnote{https://github.com/drphilmarshall/Pangloss/issues/23}.\\
+
+(Introduce Bayes' Theorem, likelihood, prior, posterior, etc.??)
 
@@
 The likelihood is a function of the parameters of a statistical model that measures the probability of a data set or outcomes given the model parameters \cite{??}.
-It is the mathematical answer to the question, ``\textit{Given a particular set of parameters, what is the probability that this data set could have occured?}" The form of the likelihood depends on the properties and circumstances of the data, but generally has the form of the product of the probability density function $f$ of each individual observation $x_i$ given model parameters $\vec{\theta}$ \cite{likelihood}:
+It is the mathematical answer to the question, ``\textit{Given a particular set of parameters, what is the probability that this data set could have occured?}" The form of the likelihood depends on the properties and circumstances of the data but generally has the form of the product of the probability density function $f$ of each individual observation $x_i$ given model parameters $\vec{\theta}$ \cite{likelihood}:
 \begin{equation}
@@
 \begin{equation}\label{likelihood}
-\mathcal{L}(\Sigma|\varepsilon_i,j,g_i,j)=\frac{1}{Z_L}\exp\left(\frac{-\chi^2}{2}\right),
+\mathcal{L}(\Sigma|\varepsilon_{i,j},g_{i,j})=\frac{1}{Z_L}\exp\left(\frac{-\chi^2}{2}\right),
 \end{equation}
@@
 \begin{align}\label{log-likelihood}
-\ln\mathcal{L}&=-\ln Z_L-\frac{1}{2}\chi^2\\
+\ln\mathcal{L}&=-\ln Z_L-\frac{1}{2}\chi^2\nonumber \\
 &=-\frac{N}{2}\ln(2\pi\sigma)-\frac{1}{2}\sum_{i=1}^N\sum_{j=1}^2\frac{(\varepsilon_{i,j}-g_{i,j})^2}{\sigma^2}.
@@
 
-\begin{enumerate}
-\item Difficult to calculate likelihood, can instead make mock data by samping parameters from prior distribution
-\item Come up with `distance' function (compare e-e corr functions) and threshold value
-\item Use accepted simulations to approximate posterior
-\item Time per ABC
-\item Compare time to single lensing event
-\end{enumerate}
-
-As discussed in the previous section, the likelihood is computationally expensive to calculate and difficult to ...
-
-ABC is a class of computational methods that estimate the posterior distribution of ... without calculating the likelihood function.
-
-A general overview of the ABC process is shown in Figure \ref{fig:abc} which is taken from \cite{abc}, which offers an excellent introduction to the topic.
-
-%%------------------------------------------------------------------------------------------------------------------------------------------
-% Mean lightcone CPU time
+MLE is not the only common method of parameter inference.
+As discussed in the previous section, the likelihood is computationally expensive to calculate and so MLE may not lend itself well to inference when large number of background galaxies are used.
+Approximate Bayesian computation (ABC) is a class of computational methods that estimate the posterior distribution without calculating the likelihood function.
+This can be vital for complex models in which the likelihood function does not have an analytic form or is computationally costly to evaluate.
+While fortunately Equation \eqref{log-likelihood} is a relatively simple likelihood function, the calculation may become too costly for very large mock catalogs of millions or billions of source galaxies.
+However, ABC does come at a cost; as the name implies, there are various assumptions and approximations made in the process that can potentially lead to an innaccurate posterior prediction.
+A general overview of the ABC process is shown in Figure \ref{fig:abc} taken from (first author name et al.) \cite{abc}, which offers an excellent introduction to the topic.
+I summarize a common ABC implementation and its application to \texttt{Pangloss} below.
+
+% In order to gague future inference feasibility, I analyzed whether ABC could make posterior
+
+All ABC methods approximate the likelihood function by simulating data using parameters sampled from the prior distribution.
+If the simulated data are very `similar' to the observed data, then the parameter set is accepted; if not, the parameter set is rejected.
+The posterior is then approximated by a histogram of the accepted parameters after a large number of simulations have been run.
+These methods are approximations as simulated data that is `similar enough' to observed data is accepted rather than requiring exact matches.
+Practically, determining what metric of `similar' to use and what threshold value $\delta$ should be chosen for data rejection becomes a compromise of computation speed and posterior accuracy.
+
+ABC using a simple distance metric like Euclidean distance or $\chi^2$ is highly inefficient for data with large dimensionality as the probability of the `distance' being small quickly vanishes.
+Instead, the similarity of observed and simulated data is often characterized by summary statistics such as mean and variance for simple data or correlation functions for more ...
+data.
+Thus an ABC rejection algorithm reduces to predicting the summary statistic for the simulated data, comparing to the corresponding summary statistic of the observed data, and basing rejection on a chosen threshold of difference in summary statistics.
+
+A possible implemenetation of the above for \texttt{Pangloss} would be as follows: Choose the the ray-traced lensed ellipticities as the `observed' data and compute its $\varepsilon$-$\varepsilon$ correlation function to be used as the desired summary statistic.
+Let the distance metric to be the NRMSE between the predicted and ray-traced $\varepsilon$-$\varepsilon$ correlation function.
+Compute the best-case $\varepsilon$-$\varepsilon$ correlation function using all halo data as shown in Section \ref{pangloss} and make the threshold value $\delta$ be some multiple of the best-case NRMSE (e.g.
+${\delta=2\cdot\text{RMSE}_{\text{best-case}}}$.
+Create mock data by repeating the methodology in \ref{pangloss} except use the stellar mass-halo mass relation, dependent on paramters we sample from a prior, to predict halo masses based upon each galaxy's stellar mass.
+Compute the simulated $\varepsilon$-$\varepsilon$ correlation function and determine whether to accept or reject the data by determining if the NRMSE is below the threshold $\delta$.
+The posterior will be estimated after a large number of iterations through the rejection algorithm.
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+% ABC Diagram
 \begin{figure}
     \centering
-    \includegraphics[width=0.475\textwidth]{figs-swe/thesis/abc.png}
+    \includegraphics[width=0.5\textwidth]{figs-swe/thesis/abc.png}
     \captionsetup{justification=raggedright,singlelinecheck=false}
@@
 
-% \subsection{Relevant Halos}
-% \begin{enumerate}
-% \item Metric from McCully et al. (cite)
-% \item Implementation
-% \item Plot the percent difference between all halos and relevant halos as a function of $\#$ of relevant halos (can adopt relevant-test.py to do this)
-% \end{enumerate}
-
-% \subsection{Smooth-Component Correction}
-% \begin{enumerate}
-% \item Introduce issue
-% \item Either derive result or state result with derivation in appendix
-% \item Plots of volume/surface density of halos vs mean universe density
-% \item Plot distribution of correction kappas
-% \item Plot distribution of reduced-shear with and without correction
-% \end{enumerate}
-
-% \subsection{Speedups}
-% \begin{enumerate}
-% \item Lookup tables (lensing table)
-% \item relevant halos
-% \item pre-calculate grid volumes for s-c correction
-% \item more plots to quantify speedup times!
-% \end{enumerate}
-
-% \subsection{Feasibility of Inference}
-
-% \subsubsection*{Likelihood Estimation}
-% \begin{enumerate}
-% \item Equation from Phil's dissertation
-% \item Calculate time with and without drilling
-% \item Time per lensing event, time per lightcone
-% \end{enumerate}
-
-% \subsubsection*{Approximate Bayesian Computation}
-% \begin{enumerate}
-% \item Difficult to calculate likelihood, can instead make mock data by samping parameters from prior distribution
-% \item Come up with `distance' function (compare e-e corr functions) and threshold value
-% \item Use accepted simulations to approximate posterior
-% \item Time per ABC
-% \item Compare time to single lensing event
-% \end{enumerate}
+I implemented the methodology in section \ref{Pangloss} to make weakly lensed ellipticity predictions in 10 mock catalogs of $N$ background sources ranging from $N=??$ to $N=??$.
+The mean CPU times for a single likelihood calulation and ABC rejection decision as a function of $N$ is shown in Figure \ref{mle_vs_abc}.
+(Clearly abc is slower, and inherently approximate, and requires arbitrary threshold cutoff, so clearly we will be using MLE moving forward.) Additionally, the time spent for either inference method is quite small; the CPU time per likelihood estimation or ABC rejection decision are \textit{far} less than the CPU time required to create lightcones and make the LOS lensing prediction.
+This is an encouraging result and suggests that further work on the framework should be on additional optimization of the lensing prediction code rather than posterior estimation.
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+% ABC Diagram
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=0.475\textwidth]{figs-swe/thesis/mle_vs_abc.png}
+%     \captionsetup{justification=raggedright,singlelinecheck=false}
+%     \caption{CAPTION}
+%     \label{fig:mle_vs_abc}
+% \end{figure}
+%%------------------------------------------------------------------------------------------------------------------------------------------
 
@@
 %%------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Issues with the Pangloss Framework}
+\subsection{Issues with the Halo Model}
+
+\begin{enumerate}
+\item Under-predicting shear on large scales
+\item Not accounting for strong lensing
+\item Smooth-component correction not enough
+\end{enumerate}
 
@@
 This could aid in the aforementioned shear power prediction issues.
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Most Halos are not Relevant}
+
+From Section \ref{halo_fraction}, we clearly do not need to use all halos in the field to predict the best-case scenario correlation functions within a mean ??\% error or NRMSE below ??. (more).
 
@@
 %%------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Systematic Errors}
+\subsection{Future Inference Work}
+
+The results of Section \ref{feasibility} demonstrated that the likelihood calculation does not present a computational issue in comparrison to the lensing calculation, so MLE is a feasible approach for a hierarchial inference of the stellar mass-halo mass relation.
+A single ABC rejection algorithm in fact performed \textit{worse} than a single likelihood calculation, so clearly ABC is not suitable for this work.
+However as discussed above, there is still much more work to the \texttt{Pangloss} framework that needs to be done, both in modeling features and computational infastructure, before an inference using a large number of background sources comparable to modern sky surves can be achieved.
 
@@
 
+\vspace{0.25 in}
+
 \section{References}
@@
 
-The main statistic used in this work is the ellipticity-ellipticity ($\varepsilon-\varepsilon$) correlation function, which has two tangential components $\xi_\pm$ and a cross component $\xi_\times$.
+The main statistic used in this work is the ellipticity-ellipticity ($\varepsilon$-$\varepsilon$) correlation function, which has two tangential components $\xi_\pm$ and a cross component $\xi_\times$.
 The components most interesting for gravitational lensing are the positive tangential component $\xi_+$, expected to be positive for lensed galaxies, and the cross component $\xi_\times$, which is expected to be zero.
@@
 Calculating the $\xi_+$ component correlation pairs for all galaxies in the same color bin and making a scatter plot as a function of the separation distance between the source pairs, we find the distribution in Figure \ref{corr_dist_unlensed}.
-The $\xi_+$ component of the $\varepsilon-\varepsilon$ correlation function is simply the average of this scatter plot binned in separation distances along the $x$-axis.
-As the scatter is randomly distributed around zero, the $\varepsilon-\varepsilon$ correlation function for un-lensed sources should be zero on all scales.
+The $\xi_+$ component of the $\varepsilon$-$\varepsilon$ correlation function is simply the average of this scatter plot binned in separation distances along the $x$-axis.
+As the scatter is randomly distributed around zero, the $\varepsilon$-$\varepsilon$ correlation function for un-lensed sources should be zero on all scales.
 
@@
 This spike in correlation is clearly visible in the distribution and is shifted to the right for colors further from the lens as the radius of the color bin increases.
-Averaging all scatter points in discrete separation distance bins, the $\varepsilon-\varepsilon$ correlation function will no longer be zero and a detectable signal will remain.
+Averaging all scatter points in discrete separation distance bins, the $\varepsilon$-$\varepsilon$ correlation function will no longer be zero and a detectable signal will remain.
 

### 2016-05-28 tests/binmap_test.py
Thesis, demo, and test update.

@@ -91,5 +91,9 @@ Kdiff = pangloss.Kappamap(data=[kappadata,domain,map_xy])
 Kdiff.plot(subplot=d,coords='world')
 plt.savefig(PANGLOSS_DIR+'/data/binned_maps/'+'kappa_difference', bbox_inches='tight')
 
+### Testing
+print 'mean Khalo = {}'.format(np.mean(Khalo.values[0]))
+Khalo.values[0] = Khalo.values[0] - np.mean(Khalo.values[0])
+
 # Make 3 subplots of all maps
 pangloss.plotting.compare_binned_maps(Kmap,Khalo,fig_size=10,savefile='kappamap_plots')

### 2016-05-29 doc/thesis_swe.tex
Thesis, demo, and test update.
Thesis update.

@@
 
-In a universe teeming with galaxies and light, it came as a shock when 20\textsuperscript{th} century astronomers discovered that most of the mass in the universe is in fact dark; the `normal' matter made of atoms that we interact with in everyday life, called baryonic matter, accounts for less than 20\% of the mass in the observable universe.
-The remaining mass takes the form of an exotic dark matter that does not absorb or emit light, rendering it invisible to our telescopes.
-While this claim sounds bizarre, there has been an abundance of indirect evidence in recent decades for the existence of dark matter including the flattening of galaxy rotation curves \cite{rotation_curve}, velocity dispersions of galaxies \cite{zwicky}, and acoustic peaks in the cosmic microwave background \cite{planck_2015}.
+In a universe teeming with galaxies and light, it came as a shock when 20\textsuperscript{th} century astronomers discovered that most of the mass in the universe is in fact dark; the `normal' matter made of atoms that we interact with in everyday life, called baryonic matter, accounts for less than 20\% of the mass in the observable universe \cite{planck}.
+The remaining mass takes the form of an exotic dark matter that does not absorb or emit light rendering it invisible to our telescopes.
+While this claim sounds bizarre, there has been an abundance of indirect evidence in recent decades for the existence of dark matter including the flattening of galaxy rotation curves \cite{rotation_curve}, velocity dispersions of galaxies \cite{zwicky}, acoustic peaks in the cosmic microwave background \cite{planck_2015}, and galaxy cluster collisions \cite{bullet_cluster}.
 
@@
 Light from different origins in a source galaxy is subject to different bending which results in a distortion of the galaxy image.
-As the foreground mass is known to be largely dark matter, gravitational lensing supplies a direct constraint on the mass of dark matter in that region.
-
-While the effects of gravitational lensing can be dramatic, the shape of most galaxies is only distorted by a few percent and must be detected statistically as the intrinsic shape is not known.
-If a model for the distribution of dark matter in a region of foreground mass can accurately predict the statistical signal of this `weak' lensing of background sources, then the model can be used on galaxies in existing sky survey data to extrapolate the amount of dark matter in the region and construct large-scale maps of the dark matter in the universe.\\
-
-(Connect to previous work done by Collett et al., Hilbert et al., McCully et al., Pache et al., etc.)\\
-
-%By applying a simple dark matter halo model to reconstruct lensing mass along lines of sight in the Millennium Simulation to predict the weakly lensed ellipticities of generated background sources, in this thesis I attempt to answer the following questions:
-
-In this thesis, I apply a simple dark matter halo model to reconstruct lensing mass along lines of sight in the Millennium Simulation to predict the weakly lensed ellipticities of generated background sources.
-By doing so, I attempt to answer the following questions: Under the best possible circumstances of having noiseless redshifts and halo masses, how accurately can I reconstruct line-of-sight dark matter mass structures using a simple halo model?
+As the foreground mass is known to be largely dark matter, gravitational lensing supplies a direct constraint on the mass of dark matter in that region \cite{mass_constraint}.
+
+While the effects of gravitational lensing can be dramatic, it is extremely rare for background galaxies to be perfectly aligned with large foreground mass to produce strongly lensed images.
+However, as Tyson et al.
+postulated in \cite{tyson_postulate} and confirmed in \cite{tyson_confirm}, background sources are also `weakly' lensed by lesser foreground mass nearby the line of sight by what is now called galaxy-galaxy lensing.
+As the shape of most galaxies is only distorted by a few percent and the instrinsic shape is not known, it must be must be detected statistically using a large number of sources.
+
+% While the effects of gravitational lensing can be dramatic, the shape of most galaxies is only distorted by a few percent and must be detected statistically as the intrinsic shape is not known.
+
+Predicting accurate dark matter mass maps from weak lensing requires understanding the correlation between galaxies and dark matter structure.
+Numerous N-body simulations have predicted dark matter structure to have evolved from overdense regions in the early universe into `halos' of virialized matter that eventually collapsed from self-gravity (cite), where galaxies could then form in the large gravitational potentials of the halos.
+However, there is still extensive reserach being done on the correct density profile of the halos (isothermal spheres \cite{isothermal_spheres}, NFW \cite{nfw}, BMO \cite{bmo}, Einasto \cite{einasto}), identifying the stellar mass-halo mass relation \cite{smhr}, abundance matching \cite{reddick}, halo substructure \cite{substructure}, and the lensing effects of line of sight halo structure \cite{collet} and dark matter structures not associated with galaxies \cite{mccully}.
+If a model for the distribution of dark matter in a region of foreground mass can accurately predict the statistical signal of the weak lensing of background sources, then the model can be used on galaxies in existing sky survey data to extrapolate the amount of dark matter in the region and construct large-scale maps of the dark matter in the universe.
+
+Guided by these results, in this thesis I build upon the work of Collet et al.
+in \cite{collet} to apply a simple dark matter halo model to reconstruct lensing mass along lines of sight in the Millennium Simulation using the \texttt{Pangloss} framework in order to predict the weakly lensed ellipticities of generated background sources.
+I then compare my predicted lensed ellipticities to the `true' lensing calculated by Hilbert et al.
+in \cite{ray_tracing} by ray-tracing light through the Millennium Simulation.
+By doing so, I attempt to answer the following questions: Under the best possible circumstances of having noiseless redshifts and halo masses, how accurately can I reconstruct line-of-sight dark matter mass structures using a halo model?
 What fraction of dark matter mass is in halos?
@@
 
-A brief introduction to the halo model, the effects of strong and weak gravitational lensing, representing galaxy ellipticities, and cosmological correlation functions is discussed in Section II.
-The implementation of the \texttt{Pangloss} framework to make line of sight lensing predictions in the Millennium Simulation is described in Section III, and the results of the framework on ??
+A brief introduction to the halo model, the effects of strong and weak gravitational lensing, representing galaxy ellipticities, and cosmological correlation functions is discussed in Section \ref{background}.
+The implementation of the \texttt{Pangloss} framework to make line of sight lensing predictions in the Millennium Simulation is described in Section \ref{pangloss}, and the results of the framework on ??
 galaxies on a field size of ??
-arcmin$^2$, along with a comparison of the predicted lensed ellipticities to ray-traced ellipticities, is given in Section IV.
-Section V explores the feasibility of using \texttt{Pangloss} to make parameter inferences using all available halo data either by likelihood estimation or approximate Bayesian computation.
-Section VI discusses limitations of the used framework as well as potential physical and computational improvements that can be made for upcoming work before concluding remarks in Section VII.
+arcmin$^2$, along with a comparison of the predicted lensed ellipticities to ray-traced ellipticities, is given in Section \ref{check}.
+Section \ref{feasibility} explores the feasibility of using \texttt{Pangloss} to make parameter inferences using all available halo data either by likelihood estimation or approximate Bayesian computation.
+Section \ref{discussion} discusses limitations of the used framework as well as potential physical and computational improvements that can be made for upcoming work before concluding remarks in Section \ref{conclusion}.
 
@@
 \section{Cosmological Background} \label{background}
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+%% Millennium Siulation structure
+\begin{figure}
+    \centering
+    \includegraphics[width=0.475\textwidth]{figs-swe/thesis/ms_structure.jpg}
+    \captionsetup{justification=raggedright,singlelinecheck=false}
+    \caption{CAPTION}
+    \label{fig:ms_structure}
+\end{figure}
+%%------------------------------------------------------------------------------------------------------------------------------------------
 
@@
 
-Cosmological simulations like the Millennium Simulation (MS) demonstrate that the underlying dark matter distribution of our universe is likely breathtakingly complex; rather than a largely disordered collection of galaxies and interstellar gas, matter appears to condense into clusters and superclusters of galaxies threaded together by large filaments (pocketed) with under-dense regions called voids, as shown in Figure ??(1.a) (CITE MS).
-While the exact relation between the distribution of galaxies and dark matter is not known, simulations predict that early galaxies formed in the large gravitational potentials of over-dense regions of dark matter (CITE!).
-This suggests that, while we cannot map dark matter directly, galaxies should trace out at least some of the underlying dark matter structures (Citation!).
+Cosmological simulations like the Millennium Simulation (MS) demonstrate that the underlying dark matter distribution of our universe is likely breathtakingly complex; rather than a largely disordered collection of galaxies and interstellar gas, matter appears to condense into clusters and superclusters of galaxies threaded together by large filaments (pocketed) with under-dense regions called voids, as shown in Figure \ref{fig:ms_structure} (Cite MS).
+While the exact relation between the distribution of galaxies and dark matter is not known, simulations predict that early galaxies formed in the large gravitational potentials of over-dense regions of dark matter (Citation).
+This suggests that, while we cannot map dark matter directly, galaxies should trace out at least some of the underlying dark matter structures (Citation).
 A comparrison of the predicted galaxy and dark matter distribution from a small region of the MS is shown in Figure \ref{ms_compare}.
@@
 The simplest way to model the relationship between galaxies and the dark matter distribution is by enveloping each galaxy in a spherically symmetric dark matter `halo' of a certain mass $M_h$.
-These halos extend far beyond the edge of the visible galaxy that they enclose, with the Milky Way's own halo estimated to have a radius of (Check and cite!).
+These halos extend far beyond the edge of the visible galaxy that they enclose, with the Milky Way's own halo estimated to have a radius of (Check and cite).
 While the density profile of the halos may be complex, numerous simulations have shown that it can be well approximated locally by the Navarro-Frenk-White (NFW) profile which has the form
@@
 The halo model only accounts for dark matter structures associated with galaxies.
-However, this neglects other mass structures such as the filaments and voids that can be seen in Figure (??).
+However, this neglects other mass structures such as the filaments and voids that can be seen in Figure \ref{fig:ms_structure}.
 Modelling these features accurately would be difficult; we could try, for example, to model filaments by attaching cylinders of dark matter between massive clusters of galaxies.
 While an intriguing idea, rigorously testing for the appropriate filament density distributions, selection criteria, and frequency to statistically match simulations could constitute its own thesis.
-
-% However, the mean mass density of large enough ($\sim$100 Mpc) regions should approximate the mean mass density of the universe, so for a first guess we can approximate the additional mass as a series of uniform sheets of matter a each redshift that make the total mass density of the foreground catalog equal to the mean density of the universe.
-This assumption can be expressed as
 
@@
 
-In this work, the threshold values used are $M_T=10^{12}M_\odot$ and $R_T=10$ kpc.
+In this work, the threshold values used are ${M_T=10^{12}M_\odot}$ and ${R_T=10}$ kpc.
 The relevance distribution for one background catalog realization with ??
 foreground halos in a lightcone of radius ??
-arcminutes is shown in Figure ??.
-As expected, there are very few massive halos along the line of sight and therefore only a small percentage of foreground halos should have a high relative contribution to the predicted lensing quantities.
+arcminutes is shown in Figure \ref{fig:rel_dist} As expected, there are very few massive halos along the line of sight and therefore only a small percentage of foreground halos should have a high relative contribution to the predicted lensing quantities.
 This encouraged the intended analysis on lightcones with all halos and those with only a small subset of the most relevant halos to compare the results and see if the computational time saved by using only the most relevant halos was worth the loss in prediction accuracy.
@@
 
-The galaxy-mass correlation function was similarly re-calculated at increasing lightcone radii from $R=1$ to $R=8$ arcminutes with the result in Figure ??.
-As with the $\varepsilon$-$\varepsilon$ correlation, ...
+The galaxy-mass correlation function was similarly re-calculated at increasing lightcone radii from $R=1$ to $R=8$ arcminutes with the result in Figure \ref{ng_corr_series} As with the $\varepsilon$-$\varepsilon$ correlation, ...
 
@@
 The green and purple curves are in agreement from 0.2 to 0.7 arcminutes, but have significant discrepancies on scales above and below this range.}
-        \label{gg_corr}
+        \label{ng_corr}
     \end{subfigure}
@@
         \caption{CAPTION}
-        \label{gg_corr_series}
+        \label{ng_corr_series}
     \end{subfigure}
@@
 However, many small improvements to the coding infrastructure of \texttt{Pangloss} were made to speed up the prediction.
-The average CPU time for a lensing prediction per lightcone for four separate runs after various (and cumulative) changes is plotted in Figure \ref{cpu_plot}, with a final run time of $??\pm?$ ms.
+The average CPU time for a lensing prediction per lightcone for ??
+separate runs after various (and cumulative) changes is plotted in Figure \ref{cpu_plot}, with a final run time of $??\pm?$ ms.
 Run 1 corresponds to the original \texttt{Pangloss} framework code, run 2 only wrote the needed quantities for this analysis to the catalog \texttt{Astropy} tables, run 3 changed the redshift grid binning to be done once for all halos in the drilling rather than for every individual halo in lensing, run 4 optimized various lensing calculations with matrices whenever possible, run 5 replaced the computationally expensive lensing calculation functions with a lookup table, and run 6 is using only the most ??
@@
 the initial variation.
+
+(Analyze profile for future optimization recommendations!!)
 
@@
     \captionsetup{justification=raggedright,singlelinecheck=false}
-    \caption{CAPTION}
+    \caption{CAPTION; Will replace with a self-made plot made specifically for \texttt{Pangloss} before thesis submission.}
     \label{fig:abc}
@@
 %%==========================================================================================================================================
-\section{Discussion}
+\section{Discussion} \label{discussion}
 
@@
 %%==========================================================================================================================================
-\section{Conclusion}
-
-% OLD: In this paper, a simple halo model was used to reconstruct all the mass along lines of sight in the Millennium Simulation to make predictions of how foreground mass weakly lensed the ellipticities of 3,240 generated background sources across a field of 324 arcmin$^2$.
+\section{Conclusion} \label{conclusion}
+
+In this thesis...
+\begin{enumerate}
+\item implement simple halo model to predict weak lensing of background sources along LOS by halos
+\item characterized success of model by correlation functions
+\item good and bad results in correlation function
+\item correlation fraction of relevant halos
+\item missing features in the model
+\item scaling up pangloss
+\end{enumerate}
+
+OLD: In this thesis, a simple halo model was used to reconstruct lensing mass along lines of sight in the Millennium Simulation to make predictions of how foreground mass weakly lensed the ellipticities of ??
+generated background sources across a field of ??
+arcmin$^2$.
 The lensed ellipticities were characterized globally using the ellipticity-ellipticity and galaxy-mass correlation functions and then compared with the same statistics from ray-traced data.
@@
 
-% OLD: I would like to thank the Department of Energy for funding this research and giving me this wonderful opportunity, as well as SLAC National Laboratory for hosting me.
-
-%This work was greatly aided by numerous conversations with Risa Wechsler from Stanford University and Matt Becker from the Kavli Institute for Particle Astrophysics and Cosmology (KIPAC), as well as Jesus Pando from DePaul University.
-Finally, I am incredibly grateful to Phil Marshall for his unending support, patience, and guidance throughout this research.
-% This work was supported in part by the U.S.
+I would like to thank the Department of Energy for funding this research and giving me the wonderful opportunity to meet so many talented peers from accross the country.
+This work was greatly aided by numerous conversations with Risa Wechsler from Stanford University and Matt Becker from the Kavli Institute for Particle Astrophysics and Cosmology (KIPAC), as well as Jesus Pando and Anuj Sarma from DePaul University.
+Additionally, I am sincerely appreciative of the many scientists, faculty, and graduate students at SLAC National Laboratory and Stanford University who continually welcomed a unknown undergraduate student who wanted to learn a little bit more about the universe.
+Finally, I am incredibly grateful to Phil Marshall of SLAC National Laboratory for his ceaseless support, guidance, enthusiasm, and friendship throughout this research and thesis.
+I look forward to continued collaboration in the future!
+
+This work was supported in part by the U.S.
 Department of Energy, Office of Science, Office of Workforce Development for Teachers and Scientists (WDTS) under the Science Undergraduate Laboratory Internships Program (SULI).
@@
 
-\section{References}
+\section{\centerline{References}}
 \vspace{-.2825in}
 \bibliographystyle{unsrt}
-\bibliography{suli-report-swe}
+\bibliography{thesis_swe}
 

### 2016-05-30 doc/thesis_swe.tex
Thesis update.

@@
 
-% While the effects of gravitational lensing can be dramatic, the shape of most galaxies is only distorted by a few percent and must be detected statistically as the intrinsic shape is not known.
-
 Predicting accurate dark matter mass maps from weak lensing requires understanding the correlation between galaxies and dark matter structure.
 Numerous N-body simulations have predicted dark matter structure to have evolved from overdense regions in the early universe into `halos' of virialized matter that eventually collapsed from self-gravity (cite), where galaxies could then form in the large gravitational potentials of the halos.
-However, there is still extensive reserach being done on the correct density profile of the halos (isothermal spheres \cite{isothermal_spheres}, NFW \cite{nfw}, BMO \cite{bmo}, Einasto \cite{einasto}), identifying the stellar mass-halo mass relation \cite{smhr}, abundance matching \cite{reddick}, halo substructure \cite{substructure}, and the lensing effects of line of sight halo structure \cite{collet} and dark matter structures not associated with galaxies \cite{mccully}.
+However, there is still extensive reserach being done on the correct density profile of the halos (isothermal spheres \cite{isothermal_spheres}, NFW \cite{nfw}, BMO \cite{bmo}, Einasto \cite{einasto}), identifying the stellar mass - halo mass relation \cite{smhr}, abundance matching \cite{reddick}, halo substructure \cite{substructure}, and the lensing by line-of-sight halos \cite{collet} and by dark matter structures not associated with galaxies \cite{mccully}.
 If a model for the distribution of dark matter in a region of foreground mass can accurately predict the statistical signal of the weak lensing of background sources, then the model can be used on galaxies in existing sky survey data to extrapolate the amount of dark matter in the region and construct large-scale maps of the dark matter in the universe.
@@
 Guided by these results, in this thesis I build upon the work of Collet et al.
-in \cite{collet} to apply a simple dark matter halo model to reconstruct lensing mass along lines of sight in the Millennium Simulation using the \texttt{Pangloss} framework in order to predict the weakly lensed ellipticities of generated background sources.
+in \cite{collet} to apply a simple dark matter halo model to reconstruct lensing mass along lines of sight in the Millennium Simulation in order to predict the weakly lensed ellipticities of generated background sources.
 I then compare my predicted lensed ellipticities to the `true' lensing calculated by Hilbert et al.
@@
 What fraction of dark matter mass is in halos?
-How feasible is an inference of the Millennium Simulation's cosmological hyper-parameters, such as the stellar mass-halo mass relation, using all available halo data?
+How feasible is an inference of the Millennium Simulation's cosmological hyper-parameters, such as the stellar mass - halo mass relation, using all available halo data?
 How long does such an inference take?
+
+%Guided by these results, in this thesis I build upon the work of Collet et al.
+in \cite{collet} to apply a simple dark matter halo model to reconstruct lensing mass along lines of sight in the Millennium Simulation using the \texttt{Pangloss} framework in order to predict the weakly lensed ellipticities of generated background sources.
 
@@
 arcmin$^2$, along with a comparison of the predicted lensed ellipticities to ray-traced ellipticities, is given in Section \ref{check}.
-Section \ref{feasibility} explores the feasibility of using \texttt{Pangloss} to make parameter inferences using all available halo data either by likelihood estimation or approximate Bayesian computation.
+Section \ref{feasibility} explores the feasibility of using the presented \texttt{Pangloss} framework to make parameter inferences using all available halo data either by likelihood estimation or approximate Bayesian computation.
 Section \ref{discussion} discusses limitations of the used framework as well as potential physical and computational improvements that can be made for upcoming work before concluding remarks in Section \ref{conclusion}.
@@
 
-Cosmological simulations like the Millennium Simulation (MS) demonstrate that the underlying dark matter distribution of our universe is likely breathtakingly complex; rather than a largely disordered collection of galaxies and interstellar gas, matter appears to condense into clusters and superclusters of galaxies threaded together by large filaments (pocketed) with under-dense regions called voids, as shown in Figure \ref{fig:ms_structure} (Cite MS).
+Cosmological simulations like the Millennium Simulation (MS) demonstrate that the underlying matter distribution of our universe is likely breathtakingly complex; rather than a largely disordered collection of galaxies and interstellar gas, matter appears to condense into clusters and superclusters of galaxies threaded together by large filaments pocketed with under-dense regions called voids, as shown in Figure \ref{fig:ms_structure} (Cite MS).
 While the exact relation between the distribution of galaxies and dark matter is not known, simulations predict that early galaxies formed in the large gravitational potentials of over-dense regions of dark matter (Citation).
@@
 
-The simplest way to model the relationship between galaxies and the dark matter distribution is by enveloping each galaxy in a spherically symmetric dark matter `halo' of a certain mass $M_h$.
+The simplest way to model the relationship between galaxies and dark matter is by enveloping each galaxy in a spherically symmetric dark matter `halo' of a certain mass $M_h$.
 These halos extend far beyond the edge of the visible galaxy that they enclose, with the Milky Way's own halo estimated to have a radius of (Check and cite).
@@
 \noindent where the constant $\rho_0$ and the scale radius $R_s$ are parameters that vary from halo to halo \cite{nfw}.
-However, the NFW profile is not entierly physical as the total mass diverges as the desntiy is integrated out to an infinite radius, so this work uses a truncated NFW profile called the Baltz-Marshall-Oguri (BMO) profile given by
+However, the NFW profile is not entierly physical as the total mass diverges as the desntiy is integrated out to an infinite radius.
+Instead this work uses a truncated NFW profile called the Baltz-Marshall-Oguri (BMO) profile given by
 \begin{equation}\label{bmo_profile}
@@
 
-\noindent where $d_H=c/H_0$ is the Hubble distance, $\Omega_k$ is the curvature parameter ($\Omega_k=0$ for a flat universe), and $d_C(z)$ is the line-of-sight (LOS) comoving distance given by
+\noindent where $d_H=c/H_0$ is the Hubble distance, $\Omega_k$ is the curvature parameter ($\Omega_k=0$ for a flat universe), and $d_C(z)$ is the line-of-sight comoving distance given by
 \begin{equation}\label{comoving_distance}
@@
 
-As the LOS proper distance between two objects $r_p(z)$ is related to the LOS comoving distance $d_C(z)$ by
+As the proper distance between two objects $r_p(z)$ is related to the comoving distance $d_C(z)$ by
 \begin{equation}\label{physical2comoving}
@@
 
-\noindent Combining this result with Equation \eqref{temp_solution} leads to the desired proper volume element given by
+\noindent Combining this result with Equation \eqref{temp_solution} leads to the desired proper volume element
 \begin{equation}\label{pvolume_element}
@@
 However, the important results can be summarized as follows.
-Foreground mass distorts the image of a background galaxy in two distinct ways: The image is magnified and sheared tangentially about the foreground mass, making it more elliptical.
-The magnification of the image is determined by the convergence $\kappa$ defined by
+Foreground mass distorts the image of a background galaxy in two distinct ways: The image is magnified and sheared tangentially about the foreground mass making it more elliptical.
+The magnification of the image is determined by the convergence $\kappa$ defined as
 \begin{equation}\label{convergence}
@@
 
-However, usually the quantity of interest in lensing calculations is the reduced shear, defined as
+The quantity usually of interest in lensing calculations is the reduced shear, defined as
 \begin{equation}\label{reduced_shear}
@@
 
- The analytical form of the convergence and shear contribution from a BMO-profile is quite messy, but is derived and explained in detail in (Cite Phil's paper!!).
+ The analytical form of the convergence and shear contribution from a BMO-profile is quite messy, but is derived and explained in detail in \ref{bmo}.
 Calculating the lensing contribution of the smooth-component correction is much simpler; the projected surface mass density at at given redshift is found by integrating $\rho_s(z)$ over a sufficiently small $dz$ interval, and then the mass sheet's convergence is found using Equation \eqref{kappa}.
@@
 To calculate the lensed ellipticities in the previous section, galaxies must first be translated from pixel intensities into elliptical representations of the galaxies.
-This is not always possible for galaxies are diverse in type and shape and not all are well approximated by ellipses.
+This is not always possible as galaxies are diverse in type and shape and not all are well approximated by ellipses.
 However for this thesis, all galaxy ellipticities are simulated so this issue is avoided.
-For a more thorough analysis of measuring image ellipticities, see Schneider (2003) \cite{schneider}.
+For a more thorough analysis of measuring image ellipticities, see \cite{schneider}.
 
@@
 This compact notation combines the eccentricity and orientation of the ellipse into a single object.
-A plot from Schneider (2003) \cite{schneider} showing the shape of elliptical galaxies for various values of $\varepsilon_1$ and $\varepsilon_2$ is shown in Figure \ref{ellipses}.
+A plot from \cite{schneider} showing the shape of elliptical galaxies for various values of $\varepsilon_1$ and $\varepsilon_2$ is shown in Figure \ref{ellipses}.
 
@@
 
-If all galaxies were spherical, then the measurement of their ellipticities would give an exact description of the lensing done by foreground mass structures.
+If all galaxies were spherical then the measurement of their ellipticities would give an exact description of the lensing done by foreground mass structures.
 Unfortunately, the intrinsic ellipticities of background galaxies contribute significant noise as we do not know how any individual galaxy ellipticity has been altered by lensing.
-However as two sources lensed by the same foreground mass will have their ellipticities distorted (in a similar way), their lensed ellipticities should be correlated regardless of intrinsic orientation.
+However as two sources lensed by the same foreground mass will have their ellipticities distorted in a similar way, their lensed ellipticities should be correlated regardless of intrinsic orientation.
 The average correlation of a sufficient number of galaxy pairs should overcome the noise and lead to a detectable signal.
-Importantly, this implies that \textit{the correlation of galaxy ellipticities is a probe of the underlying dark matter mass distribution} (Citation!).
+Importantly, this implies that \textit{the correlation of galaxy ellipticities is a probe of the underlying dark matter mass distribution} (Citation).
 
@@
 As galaxies will only be lensed by the same foreground mass at relatively small separation distances, the $\varepsilon$-$\varepsilon$ correlation function decreases sharply as the separation increases.
-If the distribution of intrinsic galaxy ellipticities is indeed random, then their $\varepsilon$-$\varepsilon$ correlation function should be essentially zero across all separation scales.
-
-A similar statistical measure often used in ... is the galaxy-mass correlation function, which measures ... and is defined as
-\begin{equation}\label{ng_corr_def}
-\xi=
-\end{equation}
-
-\noindent where...
+If the distribution of intrinsic galaxy ellipticities is indeed random, then their $\varepsilon$-$\varepsilon$ correlation function should vanish across all separation scales.
+
+A similar statistical measure often used in weak lensing measurements is the galaxy-mass correlation function which, in this setting, measures the cross-correlation of galaxy ellipticities and halo locations.
+Simply put, the function measures the correlation of lensed ellipticities around foreground halos as a function of separation distance and only has one component relevant for this work (see \cite{ng_corr} for details).
+
+%  and is defined as
+% \begin{equation}\label{ng_corr_def}
+% \xi=
+% \end{equation}
+
+% \noindent where...\textcolor{red}{Can't seem to find definition??}
 
@@
 
-To infer foreground dark matter mass structures using weak gravitational lensing, first a model of the relationship between foreground galaxies and the foreground dark matter must be established and robustly tested to see if, statistically, it makes the same lensing predictions of background sources as the true underlying dark matter structure.
+To infer foreground dark matter mass structures using weak gravitational lensing, first a model of the relationship between foreground galaxies and dark matter must be established and robustly tested to see if, statistically, it makes the same lensing predictions of background sources as the true underlying dark matter structure.
 To do this, I built upon the publicly available \texttt{Pangloss}\footnote{\label{note1}https://github.com/drphilmarshall/Pangloss} framework used in Collett et al.
-\cite{collett_marshall} to reconstruct all the
+(\cite{collett_marshall}) to reconstruct all the
 mass along the lines of sight of generated background galaxies in the MS using a halo model with smooth-component correction.
@@
 
-Testing the first assumption is the main goal of this paper.
-The second assumption is reasonable as it is estimated that dark matter halos are on average 1-2 orders of magnitude more massive than the host galaxy \cite{smhr}.
+Testing the first assumption is the main goal of this thesis.
+The second assumption is reasonable as it is estimated that dark matter halos are on average one to two orders of magnitude more massive than their host galaxies \cite{smhr}.
 Clearly the third assumption will never be true for any observational data.
@@
 background galaxies over a field of ??
-arcmin$^2$ was generated, with density 10 per arcmin$^2$.
+arcmin$^2$ was generated, with density 10 galaxies per arcmin$^2$.
 The intrinsic orientation of each galaxy was sampled from a uniform distribution as, without lensing, there should be no preferred orientation due to the assumption of an isotropic universe.
@@
 
-One of the long-term goals of \texttt{Pangloss} is to be able to use all available sky survey data (sky positions, stellar masses, magnitude, photometric redshift, ellipticities, etc.) to make a hierarchial inference of the Universe's cosmological and galaxy population model hyper-parameters such as the density paramters $\Omega_m$ and $\Omega_\Lambda$, the Hubble constant $H_0$, and stellar mass-halo mass relation \cite{smhr}.
+One of the long-term goals of \texttt{Pangloss} is to be able to use all available sky survey data (sky positions, stellar masses, magnitude, photometric redshift, ellipticities, etc.) to make a hierarchial inference of the Universe's cosmological and galaxy population model hyper-parameters such as the density paramters $\Omega_m$ and $\Omega_\Lambda$, the Hubble constant $H_0$, and stellar mass - halo mass relation \cite{smhr}.
 This is a large undertaking and will require considerable testing and calibration on large N-body simulations such as the Millennium Simulation.
@@
 However, ABC does come at a cost; as the name implies, there are various assumptions and approximations made in the process that can potentially lead to an innaccurate posterior prediction.
-A general overview of the ABC process is shown in Figure \ref{fig:abc} taken from (first author name et al.) \cite{abc}, which offers an excellent introduction to the topic.
+A general overview of the ABC process is shown in Figure \ref{fig:abc} taken from \cite{abc}, which offers an excellent introduction to the topic.
 I summarize a common ABC implementation and its application to \texttt{Pangloss} below.
@@
 ABC using a simple distance metric like Euclidean distance or $\chi^2$ is highly inefficient for data with large dimensionality as the probability of the `distance' being small quickly vanishes.
-Instead, the similarity of observed and simulated data is often characterized by summary statistics such as mean and variance for simple data or correlation functions for more ...
-data.
+Instead, the similarity of observed and simulated data is often characterized by summary statistics such as mean and variance for simple data or correlation functions for more (advanced) data.
 Thus an ABC rejection algorithm reduces to predicting the summary statistic for the simulated data, comparing to the corresponding summary statistic of the observed data, and basing rejection on a chosen threshold of difference in summary statistics.
@@
 Compute the best-case $\varepsilon$-$\varepsilon$ correlation function using all halo data as shown in Section \ref{pangloss} and make the threshold value $\delta$ be some multiple of the best-case NRMSE (e.g.
-${\delta=2\cdot\text{RMSE}_{\text{best-case}}}$.
-Create mock data by repeating the methodology in \ref{pangloss} except use the stellar mass-halo mass relation, dependent on paramters we sample from a prior, to predict halo masses based upon each galaxy's stellar mass.
+${\delta=2\cdot\text{RMSE}_{\text{best-case}}}$).
+Create mock data by repeating the methodology in \ref{pangloss} except use the stellar mass - halo mass relation, dependent on paramters we sample from a prior, to predict halo masses based upon each galaxy's stellar mass.
 Compute the simulated $\varepsilon$-$\varepsilon$ correlation function and determine whether to accept or reject the data by determining if the NRMSE is below the threshold $\delta$.
@@
 
-The results of Section \ref{feasibility} demonstrated that the likelihood calculation does not present a computational issue in comparrison to the lensing calculation, so MLE is a feasible approach for a hierarchial inference of the stellar mass-halo mass relation.
+The results of Section \ref{feasibility} demonstrated that the likelihood calculation does not present a computational issue in comparrison to the lensing calculation, so MLE is a feasible approach for a hierarchial inference of the stellar mass - halo mass relation.
 A single ABC rejection algorithm in fact performed \textit{worse} than a single likelihood calculation, so clearly ABC is not suitable for this work.
@@
 
-OLD: In this thesis, a simple halo model was used to reconstruct lensing mass along lines of sight in the Millennium Simulation to make predictions of how foreground mass weakly lensed the ellipticities of ??
+%OLD: In this thesis, a simple halo model was used to reconstruct lensing mass along lines of sight in the Millennium Simulation to make predictions of how foreground mass weakly lensed the ellipticities of ??
 generated background sources across a field of ??

### 2016-06-03 doc/thesis_swe.tex
Thesis update. #98

@@
 in \cite{ray_tracing} by ray-tracing light through the Millennium Simulation.
-By doing so, I attempt to answer the following questions: Under the best possible circumstances of having noiseless redshifts and halo masses, how accurately can I reconstruct line-of-sight dark matter mass structures using a halo model?
-What fraction of dark matter mass is in halos?
-How feasible is an inference of the Millennium Simulation's cosmological hyper-parameters, such as the stellar mass - halo mass relation, using all available halo data?
-How long does such an inference take?
-
+By doing so, I attempt to answer the following questions:
+
+\begin{enumerate}
+\item Under the best possible circumstances of having noiseless redshifts and halo masses, how accurately can I reconstruct line-of-sight dark matter mass structures using a halo model?
+%\item What fraction of dark matter mass is in halos?
+\item How many halos are needed to make these predictions?
+\item How feasible is an inference of the Millennium Simulation's cosmological hyper-parameters, such as the stellar mass - halo mass relation, using all available halo data? 
+\item How long does such an inference take?
+\end{enumerate}
 %Guided by these results, in this thesis I build upon the work of Collet et al.
@@
 A brief introduction to the halo model, the effects of strong and weak gravitational lensing, representing galaxy ellipticities, and cosmological correlation functions is discussed in Section \ref{background}.
-The implementation of the \texttt{Pangloss} framework to make line of sight lensing predictions in the Millennium Simulation is described in Section \ref{pangloss}, and the results of the framework on ??
-galaxies on a field size of ??
-arcmin$^2$, along with a comparison of the predicted lensed ellipticities to ray-traced ellipticities, is given in Section \ref{check}.
+The implementation of the \texttt{Pangloss} framework to make line of sight lensing predictions in the Millennium Simulation is described in Section \ref{pangloss}, and the results of the framework on 1440 galaxies on a field size of 144 arcmin$^2$, along with a comparison of the predicted lensed ellipticities to ray-traced ellipticities, is given in Section \ref{check}.
 Section \ref{feasibility} explores the feasibility of using the presented \texttt{Pangloss} framework to make parameter inferences using all available halo data either by likelihood estimation or approximate Bayesian computation.
@@
 \begin{align}\label{gg_corr_def}
-\xi_\pm(\Delta\theta)&=\left<\varepsilon_{i_t}(\vec{\theta})\varepsilon_{j_t}(\vec{\theta}+\vec{\Delta\theta})\right>\pm\left<\varepsilon_{i_\times}(\vec{\theta})\varepsilon_{j_\times}(\vec{\theta}+\vec{\Delta\theta})\right>\\
-\xi_\times(\vec{\Delta\theta})&=\left<\varepsilon_{i_t}(\vec{\theta})\varepsilon_{j_\times}(\vec{\theta}+\vec{\Delta\theta})\right>
+\xi_\pm(\Delta\theta)&=\left<\varepsilon_{i_t}(\vec{\theta})\,\varepsilon_{j_t}(\vec{\theta}+\vec{\Delta\theta})\right>\nonumber \\
+&\pm\left<\varepsilon_{i_\times}(\vec{\theta})\,\varepsilon_{j_\times}(\vec{\theta}+\vec{\Delta\theta})\right>\\
+\xi_\times(\vec{\Delta\theta})&=\left<\varepsilon_{i_t}(\vec{\theta})\,\varepsilon_{j_\times}(\vec{\theta}+\vec{\Delta\theta})\right>
 \end{align}
@@
 Gravitational lensing shears ellipticities tangentially, so $\xi_\times(\Delta\theta)$ should vanish with enough galaxies and therefore is a useful estimate of the bias.
-(\textcolor{red}{Why is $\xi_-$ expected to be zero?}), which leaves $\xi_+(\Delta\theta)$ as the desired probe of lensing mass.
-
+The amplitude of $\xi_-$ is significantly lower than $\xi_+$ as it depends on the initial orientation of \textit{both} ellipticities and not just their offset, which leaves $\xi_+(\Delta\theta)$ as the desired probe of lensing mass.
 As galaxies will only be lensed by the same foreground mass at relatively small separation distances, the $\varepsilon$-$\varepsilon$ correlation function decreases sharply as the separation increases.
@@
 Simply put, the function measures the correlation of lensed ellipticities around foreground halos as a function of separation distance and only has one component relevant for this work (see \cite{ng_corr} for details).
-
-%  and is defined as
-% \begin{equation}\label{ng_corr_def}
-% \xi=
-% \end{equation}
-
-% \noindent where...\textcolor{red}{Can't seem to find definition??}
 
@@
 \subsection{Generating Background Galaxies}
-With the (0,0,0,0) catalog of MS foreground galaxies chosen, a set of ??
-background galaxies over a field of ??
-arcmin$^2$ was generated, with density 10 galaxies per arcmin$^2$.
+With the (0,0,0,0) catalog of MS foreground galaxies chosen, a set of 1440 background galaxies over a field of 144 arcmin$^2$ was generated, with density 10 galaxies per arcmin$^2$.
 The intrinsic orientation of each galaxy was sampled from a uniform distribution as, without lensing, there should be no preferred orientation due to the assumption of an isotropic universe.
@@
 In this work, the threshold values used are ${M_T=10^{12}M_\odot}$ and ${R_T=10}$ kpc.
-The relevance distribution for one background catalog realization with ??
-foreground halos in a lightcone of radius ??
-arcminutes is shown in Figure \ref{fig:rel_dist} As expected, there are very few massive halos along the line of sight and therefore only a small percentage of foreground halos should have a high relative contribution to the predicted lensing quantities.
+The relevance distribution for one background catalog realization with 1440 foreground halos in a lightcone of radius 6 arcminutes is shown in Figure \ref{fig:rel_dist} As expected, there are very few massive halos along the line of sight and therefore only a small percentage of foreground halos should have a high relative contribution to the predicted lensing quantities.
 This encouraged the intended analysis on lightcones with all halos and those with only a small subset of the most relevant halos to compare the results and see if the computational time saved by using only the most relevant halos was worth the loss in prediction accuracy.
@@
 
+\textcolor{red}{Talk about lensing table!!! ??}
+
 %%==========================================================================================================================================
@@
 
-Using the presented methodology, ???
-background galaxies in a ???
-arcmin$^2$ subset of the (0,0,0,0) Millennium Simulation foreground catalog were generated and lensed by both the ray-traced shear and convergence maps as well as the \texttt{Pangloss} framework.
-With a lightcone radius of ??
-arcminutes, the lightcones contained an average of ${??\pm??}$ foreground halos.
+Using the presented methodology, 1440 background galaxies in a 144 arcmin$^2$ subset of the (0,0,0,0) Millennium Simulation foreground catalog were generated and lensed by both the ray-traced shear and convergence maps as well as the \texttt{Pangloss} framework.
+With a lightcone radius of 6 arcminutes, the lightcones contained an average of ${4836\pm104}$ foreground halos.
 Both sets of lensed ellipticities were characterized with correlation functions, as well as the intrinsic ellipticities of the sources before lensing.
@@
 
-The first test of the halo model was with the $\varepsilon$-$\varepsilon$ correlation function with a lightcone radius of ??
-arcminutes which is given in Figure \ref{gg_corr}.
-The statistic measured the average correlation between pairs of ellipticities at separation distances between ??
-and ??
-arcminutes.
+The first test of the halo model was with the $\varepsilon$-$\varepsilon$ correlation function with a lightcone radius of 6 arcminutes which is given in Figure \ref{gg_corr}.
+The statistic measured the average correlation between pairs of ellipticities at separation distances between 0.1 and 2 arcminutes.
 The cross-component of the correlation function shows no significant deviation from zero as expected, as gravitational lensing only shears galaxies tangentially.
-For the $\xi_+$ component, the ray-traced (plotted in green) and halo model (plotted in purple) are in relative agreement from seperation scales of ??
-to ??
-minutes, but there is a clear systematic underprediction of shear power by the halo model on scales larger than ??.
-This may be indicative that the halo model does not adequately address large-scale mass structures, or that there is significant dark matter mass not correlated with galaxies.
-The normalized root-mean-square error (NRMSE) of the halo correlation is ??.
+For the $\xi_+$ component, the ray-traced (plotted in green) and halo model (plotted in purple) are in relative agreement from seperation scales of 0.1 to 0.2 arcminutes, but there is a clear systematic underprediction of correlation by the halo model on scales larger than 0.2 arcminutes.
+This may be indicative that not enough halo mass is being used in the lensing prediction, the halo model does not adequately address large-scale mass structures, or that there is significant dark matter mass not correlated with galaxies.
+These issues are discussed further in Section \ref{issues}.
 
@@
 The result is shown in Figure \ref{gg_corr_series}, where the series of model predicted correlation functions is compared to the ray-traced correlation function.
-As $R_L$ increases, the mean number of foreground galaxies contained in each lightcone grows quadratically from ${??\pm??}$ galaxies when $R_L=1$ arcminute to ${??\pm??}$ galaxies when $R_L=8$ arcminutes.
-Increasing the number of foreground objects, and thus increasing the mass and structure considered for shear and convergence predictions, systematically increased the predicted shear power on all scales.
-
-%While the series of predicted correlation functions appear to be converging towards the ray-traced correlation function, there is clearly diminishing shear power gains as $R_L$ increases.
+As $R_L$ increases, the mean number of foreground galaxies contained in each lightcone grows quadratically from ${134\pm17}$ galaxies when $R_L=1$ arcminute to ${8570\pm87}$ galaxies when $R_L=8$ arcminutes.
+Increasing the number of foreground objects, and thus increasing the mass and structure considered for shear and convergence predictions, systematically increased the predicted correlation on all scales.
+This result encourages the use of lightcones with radii of at least 8 arcminutes, and further emphasizes the need for computational efficiency to allow the timely use of large lightcones.
 
@@
 
-The catalog of lensed ellipticities was also analyzed using the galaxy-mass correlation function with separation distances from ??
-to ??
-arcminutes and a lightcone radius of ??
-arcminutes.
+The catalog of lensed ellipticities was also analyzed using the galaxy-mass correlation function with separation distances from 0.1 to 2 arcminutes and a lightcone radius of 6 arcminutes.
 The result is shown in Figure \ref{ng_corr}.
-The lensed ellipticities from the ray-tracing and halo model both show positive correlation on all calculated scales and are in agreement on separations from ??
-to ??
-arcminutes.
-However, the halo model is still systematically underpredicting the shear power on scales above ??
-arcminutes, although now only by an average of ??\%.
-A new feature is the large overprediction of shear power on separation scales smaller than ??
-arcminutes.
-This is likely because background sources this close to foreground halos are often in the strong lensing regime which is not currently accounted for by the \texttt{Pangloss} framework.
-The NRMSE of the halo correlation is ??.
-
-The galaxy-mass correlation function was similarly re-calculated at increasing lightcone radii from $R=1$ to $R=8$ arcminutes with the result in Figure \ref{ng_corr_series} As with the $\varepsilon$-$\varepsilon$ correlation, ...
+The lensed ellipticities from the ray-tracing and halo model both show positive correlation on all calculated scales and largely agree on scales larger than 0.3 arcminutes except for a slight overprediction by the halo model near 0.45 arcminutes.
+However, a new feature is the large overprediction of correlation on separation scales smaller than 0.2 arcminutes.
+This is likely because background sources this close to massive foreground halos are often in the strong lensing regime which is not currently accounted for by the \texttt{Pangloss} framework.
+
+The galaxy-mass correlation function was similarly re-calculated at increasing lightcone radii from $R=1$ to $R=8$ arcminutes with the result in Figure \ref{ng_corr_series} As with the $\varepsilon$-$\varepsilon$ correlation, structure larger than $\sim$1 arcminute is captured much better by increasingly large lightcone radii as expected.
+However, there is little to no improvement of the galaxy-mass correlation on scales smaller than 0.3 arcminutes which futher points to the need to model strong lensing.
 
@@
 
-Of intrinsic interest is the relative number of relevant halos needed in each lightcone to accurately predict the halo correlation functions in Figures ??
-and ??, as a low percentage would allow much faster lensing predictions.
-Figure ??
-displays an example ellipticity-ellipticity correlation function comparrison of the halo model using all halos (purple) and halo model using halos above the relevance limit of (??
-$M_{\odot}/$Mpc$^3$), as well as the percent error of each predicted value between the two implementations.
+Of intrinsic interest is the relative number of relevant halos needed in each lightcone to accurately predict the halo correlation functions in Figures \ref{fig:gg_corr} and \ref{fig:ng_corr}, as a low percentage would allow much faster lensing predictions.
+Figure \ref{fig:rel_corr} displays an example $\varepsilon$-$\varepsilon$ and galaxy-mass correlation function comparrison of the halo model using all halos (purple) and halo model using halos above the relevance limit of ${10^{-5} M_{\odot}/\text{Mpc}^3}$, as well as the percent error of each predicted value between the two implementations.
 This relevance limit resulted in $??\pm??$ relevant halos per lightcone, and resulted in a normalized root-mean-square error (NRMSE) of ??.
-Figures ??
-plots the ellipticity-ellipticity and galaxy-mass correlation function NRMSE and mean correlation fraction as a function of mean relevant halos.
-These results suggest that either correlation function prediction can be approximated with an NRMSE below ??
-using the ??
+Figure \ref{fig:halo_fraction} plots the $\varepsilon$-$\varepsilon$ and galaxy-mass correlation function NRMSE as a function of relevance limits and mean relevant halos.
+These results suggest that either correlation function prediction can be approximated with an NRMSE below 10\% using around the ??
+most relevant halos, or an NRMSE of below 5\% using around the ??
 most relevant halos.
-(More analysis after plots have been made)
+Calibration curves such as this can allow the best-case correlation function to be predicted within a desired accuracy at only a fraction of the full lensing calculation which will be especially helpful in future analyses with much larger fields of view.
 
@@
     \caption{}
+    \label{fig:rel_corr}
 \end{figure}
@@
 % NRMSE and Correlation Fraction as function of Mean Relevant Halos
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=0.475\textwidth]{figs-swe/thesis/corr_fraction.png}
-%     \captionsetup{justification=raggedright,singlelinecheck=false}
-%     \caption{CAPTION}
-%     \label{corr_fraction}
-% \end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.475\textwidth]{figs-swe/thesis/halo_fraction.png}
+    \captionsetup{justification=raggedright,singlelinecheck=false}
+    \caption{CAPTION!}
+    \label{fig:halo_fraction}
+\end{figure}
 
@@
 
-(Analyze profile for future optimization recommendations!!)
+The distribution of total CPU time in significant parts of the lensing calculation for run 6 are as follows: 24.0\% of total time calculating individual halo convergence contributions where 14.4\% is spent in lensing lookup tables, 65.1\% of CPU time spent combining all convergence contributions where 62.1\% is spent on the smooth-component correction, and the majority of the remaining time spent on writing \texttt{Astropy}\footnote{http://www.astropy.org/} and \texttt{NumPy}\footnote{http://www.numpy.org/} columns.
+
+While progress has been made, the code needs to be further optimized to allow lensing predictions of fields of many square degrees to be done in a few seconds.
+Section \ref{scaling_up} discusses the details of future computational scale-up plans.
 
@@
 Exploratory notes of implementing such an inference in the framework is available on \texttt{Pangloss}'s public github repository\footnote{https://github.com/drphilmarshall/Pangloss/issues/23}.\\
-
-(Introduce Bayes' Theorem, likelihood, prior, posterior, etc.??)
 
@@
 Compute the best-case $\varepsilon$-$\varepsilon$ correlation function using all halo data as shown in Section \ref{pangloss} and make the threshold value $\delta$ be some multiple of the best-case NRMSE (e.g.
-${\delta=2\cdot\text{RMSE}_{\text{best-case}}}$).
+${\delta=2\cdot\text{NRMSE}_{\text{best-case}}}$).
 Create mock data by repeating the methodology in \ref{pangloss} except use the stellar mass - halo mass relation, dependent on paramters we sample from a prior, to predict halo masses based upon each galaxy's stellar mass.
@@
 
-I implemented the methodology in section \ref{Pangloss} to make weakly lensed ellipticity predictions in 10 mock catalogs of $N$ background sources ranging from $N=??$ to $N=??$.
+I implemented the methodology in section \ref{Pangloss} to make weakly lensed ellipticity predictions in 20 mock catalogs of $N$ background sources ranging from $N=10^2$ to $N=10^6$.
 The mean CPU times for a single likelihood calulation and ABC rejection decision as a function of $N$ is shown in Figure \ref{mle_vs_abc}.
-(Clearly abc is slower, and inherently approximate, and requires arbitrary threshold cutoff, so clearly we will be using MLE moving forward.) Additionally, the time spent for either inference method is quite small; the CPU time per likelihood estimation or ABC rejection decision are \textit{far} less than the CPU time required to create lightcones and make the LOS lensing prediction.
+The two methods take approximately the same amount of time up to $N=10^3$ sources, but the correlation function quickly becomes far too computationally inefficient at $N$ values above $10^4$.
+As ABC is fundamentally an approximation of the posterior \textit{and} a single decision is orders of magnitude slower than a likelihood calculation, any future inference work should use MLE instead of ABC.
+Additionally, the time spent for either inference method is quite small in comparrison to the CPU time required to create lightcones and make the line-of-sight lensing predictions.
 This is an encouraging result and suggests that further work on the framework should be on additional optimization of the lensing prediction code rather than posterior estimation.
@@
 % ABC Diagram
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=0.475\textwidth]{figs-swe/thesis/mle_vs_abc.png}
-%     \captionsetup{justification=raggedright,singlelinecheck=false}
-%     \caption{CAPTION}
-%     \label{fig:mle_vs_abc}
-% \end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.475\textwidth]{figs-swe/thesis/mle_vs_abc.png}
+    \captionsetup{justification=raggedright,singlelinecheck=false}
+    \caption{CAPTION}
+    \label{fig:mle_vs_abc}
+\end{figure}
 %%------------------------------------------------------------------------------------------------------------------------------------------
@@
 %%------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Issues with the Halo Model}
-
-\begin{enumerate}
-\item Under-predicting shear on large scales
-\item Not accounting for strong lensing
-\item Smooth-component correction not enough
-\end{enumerate}
-
-% OLD: Both the ellipticity-ellipticity and galaxy-mass correlation functions show clear issues with using the halo model to predict the lensing of background sources with \texttt{Pangloss}, even in the best-case scenario of perfect knowledge of the halo masses and their spectroscopic redshifts.
-The systematic underprediction of shear power present in both correlation functions is likely do to missing features in the model such as clusters, filaments, and voids.
+\subsection{Issues with the Halo Model} \label{issues}
+
+Both the $\varepsilon$-$\varepsilon$ and galaxy-mass correlation functions show clear issues with using the halo model to predict the lensing of background sources with \texttt{Pangloss}, even in the best-case scenario of perfect knowledge of the halo masses and their spectroscopic redshifts.
+The systematic underprediction of correlation on scales larger than ??
+in the $\varepsilon$-$\varepsilon$ function indicates that larger structures like filaments and voids are not being fully captured by the halo model.
+This is not entierly surprising, as the only structure beyond halos accounted for in the presented model was the smooth-component correction which only adds sheets of uniform mass; clearly a better model of filaments and voids is needed to make accurate correlation predictions on scales larger than $\sim$1 arcminute.
+The progression of model predicted ellipticity-ellipticity correlation functions at larger radii converging to the ray-traced correlation in Figure \ref{gg_corr_series} supports the analysis given above, as the prediction was progressively better with larger number of foreground halos and thus more mass and structure.
+
+A possible solution, briefly discussed in Section \ref{scc}, would be to model filaments as `cylinders' of dark matter attached to the most massive halos with densities, length distributions, and frequencies matching simulated data.
+This implementation might lead to better correlation predictions on large scales, but the details of the implementation, as well as analyzing how filaments affect line-of-sight lensing measurements, still needs to be explored.
+Stellar masses could also be incorporated into the \texttt{Pangloss} prediction, but any effect would likely be dominated by the missing features described above.
+Resolving the overprediction of correlation on scales below ??
+in the galaxy-mass function is likely more straightforward as sources this close to the center of foreground mass are often in the strong lensing regime.
+\texttt{Pangloss} currently removes any sources with total reduced shear $g$ greater than 0.5, but this potentially leaves sources that are not entierly described by weak lensing.
+Correctly modeling line-of-sight strong lensing will require analyzing the convergence and shear contributions of BMO halos in the strong lening regime and at the interface between strong and weak lensing.
+
+(Mention something about kappamaps)
 
@@
 
-% The progression of model predicted ellipticity-ellipticity correlation functions at larger radii converging to the ray-traced correlation in Figure \ref{gg_corr_series} supports the analysis given above, as the prediction was progressively better with larger number of foreground halos and thus more mass and structure.
-However, the number of foreground objects scales quadratically with the lightcone radius making it prohibitively expensive above $R=8$ arcminutes.
-With a radius this large, most foreground objects will be too far away from the line of sight and have insufficient mass to make a significant contribution to the lensing of the background source.
+%The progression of model predicted ellipticity-ellipticity correlation functions at larger radii converging to the ray-traced correlation in Figure \ref{gg_corr_series} supports the analysis given above, as the prediction was progressively better with larger number of foreground halos and thus more mass and structure.
+However, the number of foreground objects scales quadratically with the lightcone radius making it prohibitively expensive above $R_L=8$ arcminutes without using only a small fraction of the most relevant halos.
+%With a radius this large, most foreground objects will be too far away from the line of sight and have insufficient mass to make a significant contribution to the lensing of the background source.
 This suggests the creation of a metric to predict the `relevance' of each halo to the lensing contribution.
 In this way, the framework could be restructured to only use the most important halos in the computationally expensive lensing prediction, while simultaneously allowing for larger lightcones with more relevant halos.
-This could aid in the aforementioned shear power prediction issues.
+This could aid in the aforementioned correlation prediction issues.
 
@@
 %%------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Scaling Up Pangloss}
-
-While the current \texttt{Pangloss} framework can handle the lensing predictions of ??
-sources in a ??
-arcmin$^2$ field comfortably on a single processor, the goal is to scale up the framework to make predictions for background sources of the same number density in a 100 deg$^2$ field; this will require 3.6 million lightcones, each containing at least ???
+\subsection{Scaling Up Pangloss} \label{scaling_up}
+
+While the current \texttt{Pangloss} framework can handle the lensing predictions of 1440 sources in a 144 arcmin$^2$ field comfortably on a single processor, the goal is to scale up the framework to make predictions for background sources of the same number density in a 100 deg$^2$ field; this will require 3.6 million lightcones, each containing at least ???
 relevant foreground halos.
@@
 
-(More??)
+(Future code optimizations to get source prediction under ?? seconds)
 
@@
 The results of Section \ref{feasibility} demonstrated that the likelihood calculation does not present a computational issue in comparrison to the lensing calculation, so MLE is a feasible approach for a hierarchial inference of the stellar mass - halo mass relation.
-A single ABC rejection algorithm in fact performed \textit{worse} than a single likelihood calculation, so clearly ABC is not suitable for this work.
+A single ABC rejection algorithm in fact performed \textit{worse} than a single likelihood calculation for ${10^2\leq N\leq10^6}$ sources, so ABC does not appear to be suitable for this work.
 However as discussed above, there is still much more work to the \texttt{Pangloss} framework that needs to be done, both in modeling features and computational infastructure, before an inference using a large number of background sources comparable to modern sky surves can be achieved.
@@
 \end{enumerate}
-
+Answer the following:
+\begin{enumerate}
+\item Under the best possible circumstances of having noiseless redshifts and halo masses, how accurately can I reconstruct line-of-sight dark matter mass structures using a halo model?
+\item What fraction of dark matter mass is in halos?
+\item How feasible is an inference of the Millennium Simulation's cosmological hyper-parameters, such as the stellar mass - halo mass relation, using all available halo data? 
+\item How long does such an inference take?
+\end{enumerate}
 %OLD: In this thesis, a simple halo model was used to reconstruct lensing mass along lines of sight in the Millennium Simulation to make predictions of how foreground mass weakly lensed the ellipticities of ??
@@
 
-(Might need to rework some phrasing)\\
-
 At first encounter, the use of correlation functions to analyze data can be difficult to comprehend, let alone visualize.

### 2016-06-03 tests/lens_compare.py
Thesis demos and tests updated. #98

@@ -14,7 +14,7 @@ from mpl_toolkits.axes_grid1.anchored_artists import AnchoredSizeBar
 vb = True
 
 # Turn on for likelihood estimation time
-time = True
+time = False
 
 # Turn on for pickling correlation data
 pickle = False
@@ -81,7 +81,8 @@ print 'Background catalog has',B.galaxy_count,'galaxies'
 # Drill the lightcones
 if vb is True: print('Drilling lightcones...')
 lc_radius = 6.0
-B.drill_lightcones(radius=lc_radius,foreground=F,save=False)
+smooth_corr = True
+B.drill_lightcones(radius=lc_radius,foreground=F,save=False,smooth_corr=smooth_corr)
 
 # Save copy of background lightcones for relevant halos:
 if rel_compare is True: B_rel = copy.deepcopy(B)
@@ -98,15 +99,15 @@ print 'Lightcones have {0:.2f} +/- {1:.2f} galaxies'.format(mean_galaxies,std_ga
 if vb is True: print('Lensing background by halos..')
 relevance_lim = 0.0
 #relevance_lim = 0.00001
-smooth_corr = False
-#cProfile.run('B.lens_by_halos(relevance_lim=relevance_lim,lookup_table=True); print')
-B.lens_by_halos(relevance_lim=relevance_lim,lookup_table=True,smooth_corr=smooth_corr)
+cProfile.run('B.lens_by_halos(relevance_lim=relevance_lim,lookup_table=True,smooth_corr=smooth_corr); print')
+#B.lens_by_halos(relevance_lim=relevance_lim,lookup_table=True,smooth_corr=smooth_corr)
 print 'Lightcones have {0:.2f} +/- {1:.2f} relevant galaxies'.format(B.mean_relevant_halos,B.std_relevant_halos)
 
 # Calculate likelihood
 likelihood = B.calculate_log_likelihood()
-elapsed_time = timeit.default_timer() - start_time
-print 'lens_by_halos likelihood = {}; Total time taken was {} s'.format(likelihood,elapsed_time)
+if time is True:
+    elapsed_time = timeit.default_timer() - start_time
+    print 'lens_by_halos likelihood = {}; Total time taken was {} s'.format(likelihood,elapsed_time)
 
 if rel_compare is True:
     # Lens the background catalog using only relevant foreground halos

### 2016-06-03 tests/mle_vs_abc.py

@@ -50,27 +50,33 @@ d = [1.6,1.4,-1.6,-1.4] # 1440 galaxies
 #d = [1.55,1.54,-1.61,-1.6] # ~3 galaxies
 
 # time data is stored in these arrays...
-T = 10 # number of time data points
+T = 1 # number of time data points
 likelihood_time = []
 likelihood_total_time = []
 abc_time = []
 abc_total_time = []
+
+#
+area = 0.2*0.2*(3600) #arcmin^2
+n = 1000000 # number of sources
+N = n / area # number of soruces per arcmin^2
 
 for i in range(T):
     print 'Run {}'.format(i)
     # Start all clocks
     if time is True: start_time = timeit.default_timer()
 
-    B = pangloss.BackgroundCatalog(N=10.0,sigma_e=0.01,domain=d,field=[0,0,0,0])
+    B = pangloss.BackgroundCatalog(N=N,sigma_e=0.01,domain=d,field=[0,0,0,0])
 
     # Lens the background catalog by map
     if vb is True: print('Lensing background by map...')
     B.lens_by_map(K,S)
     print 'Background catalog has',B.galaxy_count,'galaxies'
 
+    ''' OLD: can use lens-by-map!
     # Drill the lightcones
     if vb is True: print('Drilling lightcones...')
-    lc_radius = 4.0
+    lc_radius = 0.5
     B.drill_lightcones(radius=lc_radius,foreground=F,save=False)
 
     # Calculate mean/std galaxies per lightcone
@@ -81,24 +87,26 @@ for i in range(T):
 
     # Lens the background catalog by foreground halos
     if vb is True: print('Lensing background by halos..')
-    relevance_lim = 0.0
+    #relevance_lim = 0.0
     #relevance_lim = 0.0001
-    #relevance_lim = 0.00001
+    relevance_lim = 0.000005
     smooth_corr = False
     #cProfile.run('B.lens_by_halos(relevance_lim=relevance_lim,lookup_table=True); print')
     B.lens_by_halos(relevance_lim=relevance_lim,lookup_table=True,smooth_corr=smooth_corr)
     print 'Lightcones have {0:.2f} +/- {1:.2f} relevant galaxies'.format(B.mean_relevant_halos,B.std_relevant_halos)
+    '''
 
     # Calculate likelihood
     start_likelihood = timeit.default_timer()
-    likelihood = B.calculate_log_likelihood()
+    likelihood = B.calculate_log_likelihood(lensed='map')
[…]

### 2016-06-04 doc/thesis_swe.tex
Thesis, figure demo, and test update. #98

@@
 \end{enumerate}
-%Guided by these results, in this thesis I build upon the work of Collet et al.
-in \cite{collet} to apply a simple dark matter halo model to reconstruct lensing mass along lines of sight in the Millennium Simulation using the \texttt{Pangloss} framework in order to predict the weakly lensed ellipticities of generated background sources.
 
@@
 
-Cosmological simulations like the Millennium Simulation (MS) demonstrate that the underlying matter distribution of our universe is likely breathtakingly complex; rather than a largely disordered collection of galaxies and interstellar gas, matter appears to condense into clusters and superclusters of galaxies threaded together by large filaments pocketed with under-dense regions called voids, as shown in Figure \ref{fig:ms_structure} (Cite MS).
-While the exact relation between the distribution of galaxies and dark matter is not known, simulations predict that early galaxies formed in the large gravitational potentials of over-dense regions of dark matter (Citation).
-This suggests that, while we cannot map dark matter directly, galaxies should trace out at least some of the underlying dark matter structures (Citation).
+Cosmological simulations like the Millennium Simulation (MS) demonstrate that the underlying matter distribution of our universe is likely breathtakingly complex; rather than a largely disordered collection of galaxies and interstellar gas, matter appears to condense into clusters and superclusters of galaxies threaded together by large filaments pocketed with under-dense regions called voids, as shown in Figure \ref{fig:ms_structure} \cite{??}.
+While the exact relation between the distribution of galaxies and dark matter is not known, simulations predict that early galaxies formed in the large gravitational potentials of over-dense regions of dark matter \cite{??}.
+This suggests that, while we cannot map dark matter directly, galaxies should trace out at least some of the underlying dark matter structures \cite{??}.
 A comparrison of the predicted galaxy and dark matter distribution from a small region of the MS is shown in Figure \ref{ms_compare}.
@@
 The simplest way to model the relationship between galaxies and dark matter is by enveloping each galaxy in a spherically symmetric dark matter `halo' of a certain mass $M_h$.
-These halos extend far beyond the edge of the visible galaxy that they enclose, with the Milky Way's own halo estimated to have a radius of (Check and cite).
+These halos extend far beyond the edge of the visible galaxy that they enclose, with the Milky Way's own halo estimated to have a radius of ??
+\cite{??}.
 While the density profile of the halos may be complex, numerous simulations have shown that it can be well approximated locally by the Navarro-Frenk-White (NFW) profile which has the form
@@
 \rho_h(z)&=\frac{\sum_i M_{h,i}}{V(z)}\nonumber\\
-&=\sum_i M_{h,i}\cdot\left(d_H\int\frac{d_M(z^\prime)^2}{E(z^\prime)(1+z^\prime)^3}dz^\prime d\Omega\right)^{-1}.
+&=\sum_i M_{h,i}\cdot\left(d_H\int\frac{d_M(z^\prime)^2}{E(z^\prime)(1+z^\prime)^3}dz^\prime d\Omega\right)^{-1}
 \end{align}
@@
 By observing how the magnitudes and shapes of distant galaxies are distorted when travelling through regions of matter, we can infer the masses of the dark matter halos and reconstruct the hidden dark matter mass distribution.
-A simplified cartoon of this process is shown in Figure ??, as well as a diagram defining the necessary angles and distances in Figure ??.
+A simplified cartoon of this process is shown in Figure ??.
 
@@
 
-\noindent where $\sum(\vec{r},z_l)$ is the projected surface mass density of the lensing mass and $\sum_{cr}(z_l,z_s)$ is the critical surface density for a given source redshift $z_s$ and lens redshift $z_l$ (Citation).
+\noindent where $\sum(\vec{r},z_l)$ is the projected surface mass density of the lensing mass and $\sum_{cr}(z_l,z_s)$ is the critical surface density for a given source redshift $z_s$ and lens redshift $z_l$ \cite{??}.
 The shearing of the source is most often described by the complex shear $\gamma$ defined to be
@@
 Calculating the lensing contribution of the smooth-component correction is much simpler; the projected surface mass density at at given redshift is found by integrating $\rho_s(z)$ over a sufficiently small $dz$ interval, and then the mass sheet's convergence is found using Equation \eqref{kappa}.
-There is no shear contribution as a uniform sheet of mass causes only magnification due to the mass sheet degeneracy (CITE!).
+There is no shear contribution as a uniform sheet of mass causes only magnification due to the mass sheet degeneracy \cite{??}.
 However, Equation \eqref{lensing} shows that the lensed ellipticities depend on the \textit{reduced} shear, which does depend on the additional convergence terms resulting from the smooth-component correction.
@@
 The average correlation of a sufficient number of galaxy pairs should overcome the noise and lead to a detectable signal.
-Importantly, this implies that \textit{the correlation of galaxy ellipticities is a probe of the underlying dark matter mass distribution} (Citation).
+Importantly, this implies that \textit{the correlation of galaxy ellipticities is a probe of the underlying dark matter mass distribution} \cite{??}.
 
 The mathematical tool that measures the average correlation as a function of separation distance between two galaxies is called the ellipticity-ellipticity ($\varepsilon$-$\varepsilon$) correlation function.
-A quick overview of this function is given below, but readers that are unfamiliar with correlation functions in the context of cosmology or want a visual aid should see Appendix (??).
+A quick overview of this function is given below, but readers that are unfamiliar with correlation functions in the context of cosmology or want a visual aid should see Appendix \ref{visualize_corr}.
 
@@
 McCully et al.
-(Cite) derived that the correct metric for determining the relevance of a given foreground halo to the overall lensing calculation to be given by
+in \ref{mccully} derived that the correct metric for determining the relevance of a given foreground halo to the overall lensing calculation to be given by
 \begin{equation}\label{relevant}
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{figs-swe/thesis/smooth_correction.png}
+    \includegraphics[width=0.475\textwidth]{figs-swe/thesis/smooth_correction.png}
     \captionsetup{justification=raggedright,singlelinecheck=false}
@@
 
-\textcolor{red}{Talk about lensing table!!! ??}
-
 %%==========================================================================================================================================
@@
 Both correlation functions are used in this work to estimate how well the \texttt{Pangloss} framework models weak lensing by dark matter structures and are computed using the publicly available \texttt{TreeCorr} module written by Mike Jarvis\footnote{https://github.com/rmjarvis/TreeCorr}.
-Note that the ellipticity-ellipticity correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition and the more common Schneider definition \cite{schneider}, see Appendix (??).
+Note that the ellipticity-ellipticity correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition and the more common Schneider definition \cite{schneider}, see Appendix \ref{corr_defs}.
 
@@
 The halo predicted correlation, plotted in purple, shows significant positive correlation until a separation distance of 0.8 arcminutes.
-        \label{gg_corr}
+        \label{fig:gg_corr}
     \end{subfigure}
@@
 These are compared to the same ray-traced correlation from Figure \ref{gg_corr}.}
-        \label{gg_corr_series}
+        \label{fig:gg_corr_series}
     \end{subfigure}
@@
 
-The first test of the halo model was with the $\varepsilon$-$\varepsilon$ correlation function with a lightcone radius of 6 arcminutes which is given in Figure \ref{gg_corr}.
+The first test of the halo model was with the $\varepsilon$-$\varepsilon$ correlation function with a lightcone radius of 6 arcminutes which is given in Figure \ref{fig:gg_corr}.
 The statistic measured the average correlation between pairs of ellipticities at separation distances between 0.1 and 2 arcminutes.
@@
 Using the same catalog of background sources, this statistic was recalculated for the halo model ellipticities for various lightcone radii ranging from $R_L=1$ to $R_L=8$ arcminutes.
-The result is shown in Figure \ref{gg_corr_series}, where the series of model predicted correlation functions is compared to the ray-traced correlation function.
+The result is shown in Figure \ref{fig:gg_corr_series}, where the series of model predicted correlation functions is compared to the ray-traced correlation function.
 As $R_L$ increases, the mean number of foreground galaxies contained in each lightcone grows quadratically from ${134\pm17}$ galaxies when $R_L=1$ arcminute to ${8570\pm87}$ galaxies when $R_L=8$ arcminutes.
@@
 The catalog of lensed ellipticities was also analyzed using the galaxy-mass correlation function with separation distances from 0.1 to 2 arcminutes and a lightcone radius of 6 arcminutes.
-The result is shown in Figure \ref{ng_corr}.
+The result is shown in Figure \ref{fig:ng_corr}.
 The lensed ellipticities from the ray-tracing and halo model both show positive correlation on all calculated scales and largely agree on scales larger than 0.3 arcminutes except for a slight overprediction by the halo model near 0.45 arcminutes.
@@
 
-The galaxy-mass correlation function was similarly re-calculated at increasing lightcone radii from $R=1$ to $R=8$ arcminutes with the result in Figure \ref{ng_corr_series} As with the $\varepsilon$-$\varepsilon$ correlation, structure larger than $\sim$1 arcminute is captured much better by increasingly large lightcone radii as expected.
+The galaxy-mass correlation function was similarly re-calculated at increasing lightcone radii from $R=1$ to $R=8$ arcminutes with the result in Figure \ref{fig:ng_corr_series} As with the $\varepsilon$-$\varepsilon$ correlation, structure larger than $\sim$1 arcminute is captured much better by increasingly large lightcone radii as expected.
 However, there is little to no improvement of the galaxy-mass correlation on scales smaller than 0.3 arcminutes which futher points to the need to model strong lensing.
@@
 The green and purple curves are in agreement from 0.2 to 0.7 arcminutes, but have significant discrepancies on scales above and below this range.}
-        \label{ng_corr}
+        \label{fig:ng_corr}
     \end{subfigure}
@@
         \caption{CAPTION}
-        \label{ng_corr_series}
+        \label{fig:ng_corr_series}
     \end{subfigure}
@@
 Of intrinsic interest is the relative number of relevant halos needed in each lightcone to accurately predict the halo correlation functions in Figures \ref{fig:gg_corr} and \ref{fig:ng_corr}, as a low percentage would allow much faster lensing predictions.
-Figure \ref{fig:rel_corr} displays an example $\varepsilon$-$\varepsilon$ and galaxy-mass correlation function comparrison of the halo model using all halos (purple) and halo model using halos above the relevance limit of ${10^{-5} M_{\odot}/\text{Mpc}^3}$, as well as the percent error of each predicted value between the two implementations.
+Figures \ref{fig:rel_gg_compare} and \ref{fig:rel_ng_compare} display an example $\varepsilon$-$\varepsilon$ and galaxy-mass correlation function comparrison of the halo model using all halos (purple) and halo model using halos above the relevance limit of ${10^{-5} M_{\odot}/\text{Mpc}^3}$, as well as the percent error of each predicted value between the two implementations.
 This relevance limit resulted in $??\pm??$ relevant halos per lightcone, and resulted in a normalized root-mean-square error (NRMSE) of ??.
@@
 % NRMSE and Correlation Fraction as function of Mean Relevant Halos
-\begin{figure}
-    \centering
-    \includegraphics[width=0.475\textwidth]{figs-swe/thesis/halo_fraction.png}
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.925\textwidth]{figs-swe/thesis/halo_fraction_long.png}
+    % \includegraphics[width=0.475\textwidth]{figs-swe/thesis/halo_fraction.png}
     \captionsetup{justification=raggedright,singlelinecheck=false}
@@
     \label{fig:halo_fraction}
-\end{figure}
-
-%%------------------------------------------------------------------------------------------------------------------------------------------
-
-%%------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Dark Matter Convergence Mass Maps}
+\end{figure*}
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Convergence Mass Maps} \label{mass_maps}
+
+While correlation functions can describe how well the lensing predictions are being made globally, it is still instructive to analyze the difference between the ray-traced and halo model projected mass maps.
+This was done by selecting a region of foreground mass, calculating the ray-traced and \texttt{Pangloss}-predicted convergence of a uniform grid of background sources in the field, and binning the convergence maps to a desired resolution.
+Convergence is proportional to projected surface mass density, so comparring the two convergence maps is equivalent to comparing their respecitve projected mass distributions.
+
+The result of a particular 9 arcmin$^2$ field is shown in Figure \ref{fig:kappamaps}, where the ray-traced convergence is shown on the left, the halo model convergence is in the center, and the ray-traced convergence subtracted from the halo model convergence is shown on the right.
+While particular foreground masses are almost always predicted, the currently implemented halo model over-predicts the convergence throughout most of the field; b.
+The halo model does not appear to accurately account for the voids between foreground masses and over-predicts the mass of most ...
+This could partially be a result of incorrect halo profiles, but it is apparent that the smooth-component correction is not adequate to ...
 
@@
 
-While correlation functions can describe how well the lensing predictions are being made globally, it is still instructive to analyze the difference between the ray-traced and halo model projected mass maps.
-This was done by selecting a region of foreground mass, calculating the ray-traced and \texttt{Pangloss}-predicted convergence of a uniform grid of background sources in the field, and binning the convergence maps to a desired resolution.
-Convergence is proportional to projected surface mass density, so comparring the two convergence maps is equivalent to comparing their respecitve projected mass distributions.
-
-The result of a particular ??
-arcmin$^2$ field is shown in Figure \ref{fig:kappamaps}, where the ray-traced convergence is shown on the left, the halo model convergence is in the center, and the ray-traced convergence subtracted from the halo model convergence is shown on the right.
-While particular foreground masses are almost always predicted, the currently implemented halo model over-predicts the convergence throughout most of the field.
-The halo model does not appear to accurately account for the voids between foreground masses and over-predicts the mass of most ...
-This could partially be a result of incorrect halo profiles, but it is apparent that the smooth-component correction is not adequate to ...
-
-%%------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Computational Performance}
-
-A secondary goal of this research was to investigate how quickly the prediction for the shear and convergence for a single background source could be made.
-The mean CPU time required for the prediction per lightcone was ${??\pm??}$ ms for the first run.
-However, many small improvements to the coding infrastructure of \texttt{Pangloss} were made to speed up the prediction.
-The average CPU time for a lensing prediction per lightcone for ??
-separate runs after various (and cumulative) changes is plotted in Figure \ref{cpu_plot}, with a final run time of $??\pm?$ ms.
-Run 1 corresponds to the original \texttt{Pangloss} framework code, run 2 only wrote the needed quantities for this analysis to the catalog \texttt{Astropy} tables, run 3 changed the redshift grid binning to be done once for all halos in the drilling rather than for every individual halo in lensing, run 4 optimized various lensing calculations with matrices whenever possible, run 5 replaced the computationally expensive lensing calculation functions with a lookup table, and run 6 is using only the most ??
-relevant halos.
-Cumulatively, these changes alone accounted for a ??\% decrease in mean CPU time per lightcone and ??
-the initial variation.
-
-The distribution of total CPU time in significant parts of the lensing calculation for run 6 are as follows: 24.0\% of total time calculating individual halo convergence contributions where 14.4\% is spent in lensing lookup tables, 65.1\% of CPU time spent combining all convergence contributions where 62.1\% is spent on the smooth-component correction, and the majority of the remaining time spent on writing \texttt{Astropy}\footnote{http://www.astropy.org/} and \texttt{NumPy}\footnote{http://www.numpy.org/} columns.
-
-While progress has been made, the code needs to be further optimized to allow lensing predictions of fields of many square degrees to be done in a few seconds.
-Section \ref{scaling_up} discusses the details of future computational scale-up plans.
+%%------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Computational Performance} \label{comp_perform}
 
@@
     \caption{OLD: The mean CPU runtime per lightcone for various runs with different (and cumulative) code optimizations described in the text.
-The cumulative changes account for a ??\% decrease in the mean CPU time and a ??
-of the variation.
-Currently, the prediction can be made for a single lightcone in\\$??\pm??$ ms.}
+The cumulative changes account for a 59\% decrease in the mean CPU time and a halving of the variation.
+Currently, the prediction can be made for a single lightcone in $57\pm8$ ms.}
     \label{fig:cpu_plot}
 \end{figure}
+%%------------------------------------------------------------------------------------------------------------------------------------------
+
+A secondary goal of this research was to investigate how quickly the shear and convergence prediction for a single background source could be made.
+The mean CPU time required for the lensing prediction of a single lightcone with radius $R_L=6$ arcminutes was ${140\pm20}$ ms for the first run.
+However, many small improvements to the coding infrastructure of \texttt{Pangloss} were made to speed up the prediction.
+The mean CPU time for a single lightcone lensing prediction for 6 separate runs after various (and cumulative) changes is plotted in Figure \ref{fig:cpu_plot}, with a final run time of $57\pm8$ ms.
+Run 1 corresponds to the original \texttt{Pangloss} framework code, run 2 wrote only the needed quantities for this analysis to the catalog \texttt{Astropy}\footnote{http://www.astropy.org/} tables, run 3 changed the redshift grid binning to be done once for all halos in the drilling rather than for every individual halo in lensing, run 4 optimized various lensing calculations with matrices whenever possible, run 5 replaced the computationally expensive lensing calculation functions with a lookup table, and run 6 used only the ${65\pm9}$ most relevant halos from a relevance limit of ${10^{-5}M_\odot/\text{Mpc}^3}$.
+Cumulatively, these changes accounted for a 59\% decrease in mean CPU time per lightcone and halved the initial variation.
+While significant progress has been made, the code needs to be further optimized to allow lensing predictions of fields of many square degrees to be done in a few seconds.
+Section \ref{scaling_up} discusses the details of future computational scale-up plans.
+
+Figure \ref{fig:cpu_scaling} displays how the mean CPU runtime per lightcone scales as a function of lightcone radius $R_L$ with all halos (left) and relevance limit at a constant radius of $R_L=4$ and $R_L=8$ arcminutes (right).
+Unsurprisingly, the runtime depends strongly on the number of galaxies per lightcone.
+Both figures show that the lensing calculation requires an overhead of about ${55\pm10}$ ms, but then the calculation speed depends quadratically on the number of halos and logarithmically on the relevance limit.
+The runtime saved by using only the most relevant halos helps can only counteract the increase in runtime due to larger lightcones for so long before the desired correlation function NRMSE becomes too large, so accurate analysis with radii above $R_L=8$ arcminutes may only be feasible with parallelization.
+
+The distribution of total CPU time in significant parts of the lensing calculation for run 6 are as follows: 24.0\% of total time calculating individual halo convergence contributions where 14.4\% is spent in lensing lookup tables, 65.1\% of CPU time was spent combining all convergence contributions where 62.1\% is spent on the smooth-component correction, and the majority of the remaining time spent on writing the output \texttt{Astropy} columns.
+However, time spent accross all components of the lensing calculation was dominated by \texttt{Astropy} column use with nearly 55\% of total time spent initializing, copying, or summing columns.
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+%% Mean CPU time scaling
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.8\textwidth]{figs-swe/thesis/cpu_scaling.png}
+    \captionsetup{justification=raggedright,singlelinecheck=false}
+    \caption{CAPTION}
+    \label{fig:cpu_scaling}
+\end{figure*}
+%
 %%------------------------------------------------------------------------------------------------------------------------------------------
@@
 ABC using a simple distance metric like Euclidean distance or $\chi^2$ is highly inefficient for data with large dimensionality as the probability of the `distance' being small quickly vanishes.
-Instead, the similarity of observed and simulated data is often characterized by summary statistics such as mean and variance for simple data or correlation functions for more (advanced) data.
+Instead, the similarity of observed and simulated data is often characterized by summary statistics such as mean and variance for simple data or correlation functions for more advanced data.
 Thus an ABC rejection algorithm reduces to predicting the summary statistic for the simulated data, comparing to the corresponding summary statistic of the observed data, and basing rejection on a chosen threshold of difference in summary statistics.
@@
 %%------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Results}
-
-I implemented the methodology in section \ref{Pangloss} to make weakly lensed ellipticity predictions in 20 mock catalogs of $N$ background sources ranging from $N=10^2$ to $N=10^6$.
-The mean CPU times for a single likelihood calulation and ABC rejection decision as a function of $N$ is shown in Figure \ref{mle_vs_abc}.
+\subsection{Results} \label{inference_results}
+
+I implemented the methodology in section \ref{pangloss} to make weakly lensed ellipticity predictions for 20 mock catalogs of $N$ background sources ranging from $N=10^2$ to $N=10^6$.
+The mean CPU times for a single likelihood calulation and ABC rejection decision as a function of $N$ is shown in Figure \ref{fig:mle_vs_abc}.
 The two methods take approximately the same amount of time up to $N=10^3$ sources, but the correlation function quickly becomes far too computationally inefficient at $N$ values above $10^4$.
-As ABC is fundamentally an approximation of the posterior \textit{and} a single decision is orders of magnitude slower than a likelihood calculation, any future inference work should use MLE instead of ABC.
-Additionally, the time spent for either inference method is quite small in comparrison to the CPU time required to create lightcones and make the line-of-sight lensing predictions.
-This is an encouraging result and suggests that further work on the framework should be on additional optimization of the lensing prediction code rather than posterior estimation.
+While further analysis is needed to determine whether more or less ABC samples are required than posterior samples from MLE, this result, as well as the limitation that ABC is fundamentally an approximation of the posterior,
+suggests that any future inference work will likely use MLE instead of ABC.
+However, the time spent for either inference method is quite small in comparrison to the CPU time required to create lightcones and make the line-of-sight lensing predictions.
+This is an encouraging result which de-emphasizes the choice of sampling method and suggests that further work on the framework should be on additional optimization of the lensing prediction code rather than posterior estimation.
+% Additionally as ABC is fundamentally an approximation of the posterior \textit{and} a single decision is orders of magnitude slower than a likelihood calculation for a large $N$
 
@@
 Both the $\varepsilon$-$\varepsilon$ and galaxy-mass correlation functions show clear issues with using the halo model to predict the lensing of background sources with \texttt{Pangloss}, even in the best-case scenario of perfect knowledge of the halo masses and their spectroscopic redshifts.
-The systematic underprediction of correlation on scales larger than ??
-in the $\varepsilon$-$\varepsilon$ function indicates that larger structures like filaments and voids are not being fully captured by the halo model.
-This is not entierly surprising, as the only structure beyond halos accounted for in the presented model was the smooth-component correction which only adds sheets of uniform mass; clearly a better model of filaments and voids is needed to make accurate correlation predictions on scales larger than $\sim$1 arcminute.
-The progression of model predicted ellipticity-ellipticity correlation functions at larger radii converging to the ray-traced correlation in Figure \ref{gg_corr_series} supports the analysis given above, as the prediction was progressively better with larger number of foreground halos and thus more mass and structure.
+The systematic underprediction of correlation on scales larger than 0.2 arcminutes in the $\varepsilon$-$\varepsilon$ function indicates that larger structures like filaments and voids are not being fully captured by the halo model.
+This is not entierly surprising as the only structure beyond halos accounted for in the presented model was the smooth-component correction which only adds sheets of uniform mass; clearly a better model of filaments and voids is needed to make accurate correlation predictions on scales larger than $\sim$1 arcminute.
+The progression of model predicted ellipticity-ellipticity correlation functions at larger radii converging to the ray-traced correlation in Figure \ref{fig:gg_corr_series} supports the analysis given above as the prediction was progressively better with larger number of foreground halos and thus more mass and structure.
 
@@
 This implementation might lead to better correlation predictions on large scales, but the details of the implementation, as well as analyzing how filaments affect line-of-sight lensing measurements, still needs to be explored.
-Stellar masses could also be incorporated into the \texttt{Pangloss} prediction, but any effect would likely be dominated by the missing features described above.
-Resolving the overprediction of correlation on scales below ??
-in the galaxy-mass function is likely more straightforward as sources this close to the center of foreground mass are often in the strong lensing regime.
+Stellar masses could also be incorporated into the \texttt{Pangloss} prediction but any effect would likely be dominated by the missing features described above.
+Resolving the overprediction of correlation on scales below 0.2 arcminutes in the galaxy-mass function is likely more straightforward as sources this close to the center of foreground mass are often in the strong lensing regime.
 \texttt{Pangloss} currently removes any sources with total reduced shear $g$ greater than 0.5, but this potentially leaves sources that are not entierly described by weak lensing.
-Correctly modeling line-of-sight strong lensing will require analyzing the convergence and shear contributions of BMO halos in the strong lening regime and at the interface between strong and weak lensing.
+Correctly modeling line-of-sight strong lensing will require analyzing the convergence and shear contributions of BMO halos in the strong lening regime and at the interface between strong and weak lensing.\\
 
@@
 
-% While individual galaxies currently receive halos, a cluster of galaxies will sit in an larger halo whose presence is not being considered as its position, mass, and extent are difficult to determine.
-The absence of this mass undoubtedly effects shear predictions and ellipticity correlations on large scales.
-While some of the filament structure is captured in the framework, as the higher density of galaxies in filaments will lead to a higher density of halos, any additional dark matter structure between halos and clusters is not being accounted for.
-While difficult to do in practice, one can imagine connecting clusters of galaxies with dark matter `cylinders' to account for the extra filament mass.
-Voids are also not currently considered, as the framework assumes the field has constant mass density equal to that of the average mass density of the universe and then adds halo masses on top of this density.
-This would make the average matter density across the field \textit{larger} than the mean density of the universe, and could be counteracted by subtracting mass from regions in between foreground halos.
-Stellar masses could also be incorporated into the \texttt{Pangloss} prediction, but any effect would likely be dominated by the missing features described above.
-
-%The progression of model predicted ellipticity-ellipticity correlation functions at larger radii converging to the ray-traced correlation in Figure \ref{gg_corr_series} supports the analysis given above, as the prediction was progressively better with larger number of foreground halos and thus more mass and structure.
-However, the number of foreground objects scales quadratically with the lightcone radius making it prohibitively expensive above $R_L=8$ arcminutes without using only a small fraction of the most relevant halos.
-%With a radius this large, most foreground objects will be too far away from the line of sight and have insufficient mass to make a significant contribution to the lensing of the background source.
-This suggests the creation of a metric to predict the `relevance' of each halo to the lensing contribution.
-In this way, the framework could be restructured to only use the most important halos in the computationally expensive lensing prediction, while simultaneously allowing for larger lightcones with more relevant halos.
-This could aid in the aforementioned correlation prediction issues.
-
 %%------------------------------------------------------------------------------------------------------------------------------------------
@@
 
-From Section \ref{halo_fraction}, we clearly do not need to use all halos in the field to predict the best-case scenario correlation functions within a mean ??\% error or NRMSE below ??. (more).
+From Section \ref{halo_fraction} and Figure \ref{fig:halo_fraction}, we clearly do not need to use all halos in the field to predict the best-case scenario correlation functions within a NRMSE below 10\% or even 5\%.
+This will be of essential importance when making lensing predictions in fields of many square degrees that otherwise would be computationally infeasible.
+Figure \ref{fig:cpu_scaling} suggests that setting the relevance limit to ${10^{-6}M_\odot\,\text{Mpc}^3}$, or $~300$ relevant halos per lightcone, will decrease the mean CPU time per lightcone prediction to roughly the minimum overhead runtime of about 60 ms.
+According to Figure \ref{fig:halo_fraction}, this relevance limit will on average keep the $\varepsilon$-$\varepsilon$ and galaxy-mass correlation function NRMSE's at or below 5\%.
+These two figures can be used in this way to decide what relevance limit is appropriate for the desired tradeoff between mean runtime speed and correlation function accuracy.
 
@@
 This makes GPUs an attractive candidate for future work, as it would only take 360 GPUs with 10,000 threads each to carry out the prediction.
-Additionally, the ??
-MB of RAM per lightcone is sufficiently small to fit 10,000 lightcones on a GPU.\\
-
-(Future code optimizations to get source prediction under ?? seconds)
+Additionally, the $\sim$5 MB of RAM per lightcone is sufficiently small to fit 10,000 lightcones on a GPU.
+
+However, the \texttt{Pangloss} code needs to be optimized before the parallelization will be efficient or even feasible.
+The breakdown of CPU time spent on various components of the lensing calculation in Section \ref{comp_perform} indicates that (1) the smooth-component correction needs to be implemented \textit{far} quicker as it is responsible for on average 62.1\% of the total runtime and (2) the current use of \texttt{Astropy} tables for data storage is not practical for fields much larger than 1,000 arcmin$^2$ or with lightcone radii larger than 8 arcminutes.
+Possible solutions to (1) are to experiment with faster numerical integrators or, more importantly, ???.
+The second issue suggests that \texttt{Pangloss} should store catalog data in databases rather than \texttt{Astropy} tables as databases are designed for rapid retrieval, modification, and deletion of data \cite{??}.
+While this will require significant reworking of the framework to implement, the CPU distribution indicates that such a change is necessary for even a moderate scale up.
 
@@
 
-The results of Section \ref{feasibility} demonstrated that the likelihood calculation does not present a computational issue in comparrison to the lensing calculation, so MLE is a feasible approach for a hierarchial inference of the stellar mass - halo mass relation.
-A single ABC rejection algorithm in fact performed \textit{worse} than a single likelihood calculation for ${10^2\leq N\leq10^6}$ sources, so ABC does not appear to be suitable for this work.
-However as discussed above, there is still much more work to the \texttt{Pangloss} framework that needs to be done, both in modeling features and computational infastructure, before an inference using a large number of background sources comparable to modern sky surves can be achieved.
+The results of Section \ref{feasibility} demonstrated that neither the likelihood nor correlation function computation present a significant computational issue in comparrison to the lensing calculation, so either are feasible approaches for a hierarchial inference of the stellar mass - halo mass relation.
+As a single ABC rejection algorithm performed many orders of magnitude \textit{worse} than a single likelihood calculation for ${10^2\leq N\leq10^6}$ sources and ABC fundementally an approximation, it appears that the method is not suitable for this work unless ABC ends up requiring far less samples than the number of needed posterior samples in MLE.
+However as discussed above and in Section \ref{inference_results}, there is still much more work to the \texttt{Pangloss} framework that needs to be done, both in modeling features and computational infastructure, before an inference using a large number of background sources comparable to modern sky surveys can be achieved.
 
@@
 
-In this thesis...
-\begin{enumerate}
-\item implement simple halo model to predict weak lensing of background sources along LOS by halos
-\item characterized success of model by correlation functions
-\item good and bad results in correlation function
-\item correlation fraction of relevant halos
-\item missing features in the model
-\item scaling up pangloss
-\end{enumerate}
-Answer the following:
-\begin{enumerate}
-\item Under the best possible circumstances of having noiseless redshifts and halo masses, how accurately can I reconstruct line-of-sight dark matter mass structures using a halo model?
-\item What fraction of dark matter mass is in halos?
-\item How feasible is an inference of the Millennium Simulation's cosmological hyper-parameters, such as the stellar mass - halo mass relation, using all available halo data? 
-\item How long does such an inference take?
-\end{enumerate}
-%OLD: In this thesis, a simple halo model was used to reconstruct lensing mass along lines of sight in the Millennium Simulation to make predictions of how foreground mass weakly lensed the ellipticities of ??
-generated background sources across a field of ??
-arcmin$^2$.
-The lensed ellipticities were characterized globally using the ellipticity-ellipticity and galaxy-mass correlation functions and then compared with the same statistics from ray-traced data.
-There was a systematic-underprediction of shear power on all scales in the ellipticity-ellipticity correlation function as well as an absence of any predicted correlation on scales larger than 1 arcminute, suggesting missing features in the \texttt{Pangloss} framework.
-The galaxy-mass correlation function predicted by the halo model was in agreement with the ray-traced correlation function on scales from 0.2 to 0.7 arcminutes, but significantly overpredicted the shear power on smaller scales due to strong lensing effects.
-Now that a proof of concept has been demonstrated, there is work being done to scale up the \texttt{Pangloss} framework to make lensing predictions over 100 deg$^2$ using far more computational resources.
+% In this thesis...
+% \begin{enumerate}
+% \item implement simple halo model to predict weak lensing of background sources along LOS by halos
+% \item characterized success of model by correlation functions
+% \item good and bad results in correlation function
+% \item correlation fraction of relevant halos
+% \item missing features in the model
+% \item scaling up pangloss
+% \end{enumerate}
+
+In this thesis, a simple halo model was used to reconstruct lensing mass along lines of sight in the Millennium Simulation to make predictions of how foreground mass weakly lensed the ellipticities of 1440 generated background sources across a field of 144 arcmin$^2$.
+The lensed ellipticities were characterized globally using the $\varepsilon$-$\varepsilon$ and galaxy-mass correlation functions and then compared with the same statistics from the ray-traced data calculated in \cite{ray_tracing}.
+There was a systematic-underprediction of correlation on scales larger than 0.2 arcminutes in the $\varepsilon$-$\varepsilon$ correlation function suggesting missing features in the halo model.
+The galaxy-mass correlation function predicted by the halo model was in relative agreement with the ray-traced correlation function on scales from 0.2 to 2 arcminutes, but significantly overpredicted the correlation on scales below 0.2 arcminutes due to unaccounted for strong lensing effects.
+Figures \ref{fig:gg_corr_series} and \ref{fig:ng_corr_series} show that the predicted summary statistics converge towards the `true' statistics at large lightcone radii, although at quickly prohibitive computational cost.
+The model was also used to predict convergence mass maps in small 9 arcmin$^2$ regions that visually demonstrated the prediction of excess mass both in regions of foreground mass and the voids between them.
+This result suggested that a more complex model of filaments and voids is needed to accurately predict lensing mass and the correlation from large-scale mass structures.
+
+One of the main results of this thesis is Figure \ref{fig:halo_fraction} which describes the fraction of relevant halos needed to reproduce the best-case correlation functions to a desired accuracy using the relevance metric given in Equation \eqref{relevant} derived by McCully et al.
+in \cite{mccully}.
+It suggests that, on average, the best-case correlation functions can be approximated to a NRMSE of less than 10\% or 5\% using a relevance limit of ${10^{-6}M_\odot\,\text{Mpc}^3}$, or $\sim300$ halos, and ${10^{-5}M_\odot\,\text{Mpc}^3}$, or $\sim70$ halos, respectively.
+
+Finally, this thesis explored the feasibility of implementing a future inference of model hyperparameters like the stellar mass - halo mass relation by characterizing the mean CPU time per likelihood evaluation and ABC decision for catalogs of background sources ranging from $10^2\leq N\leq10^6$ as shown in Figure \ref{fig:mle_vs_abc}.
+While the likelihood calculation outperformed the summary statistic calculation for all values of $N$, the main result is that neither computation took a significant amount of time relative to the lensing calculation for a given $N$.
+This indicates that inference feasibility rests upon optimizing the lensing prediction code to sufficient speed as discussed in Sections \ref{comp_perform} and \ref{scaling_up}.
+% Answer the following:
+% \begin{enumerate}
+% \item Under the best possible circumstances of having noiseless redshifts and halo masses, how accurately can I reconstruct line-of-sight dark matter mass structures using a halo model?
+% \item How many halos are needed to make these predictions?
+% \item How feasible is an inference of the Millennium Simulation's cosmological hyper-parameters, such as the stellar mass - halo mass relation, using all available halo data? 
+% \item How long does such an inference take?
+% \end{enumerate}
+
+Now that a proof of concept has been demonstrated, work can be done to scale up the \texttt{Pangloss} framework to make lensing predictions over 100 deg$^2$ after implementing the suggested computational and model improvements.
 While the results are encouraging for such a simple model, many strong and unrealistic assumptions were made in the methodology that limit its use in observational surveys.
-In the future, a similar analysis should be made after relaxing some of the assumptions to see how different the predictions by the halo model are from this best-case scenario.
+In the future, a similar analysis should be made using simulated photometric redshifts and inferred halo masses to see how different the predictions by the halo model are from this best-case scenario.
+
+\vspace{0.04 in}
 
@@
 
-\section{\centerline{References}}
+\section*{\centerline{References}}
 \vspace{-.2825in}
@@
 %%------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Visualizing Correlation Functions}
+\subsection{Visualizing Correlation Functions} \label{visualize_corr}
 
@@
 
-\subsection{Deriving the Standard Correlation Function Definition from \texttt{TreeCorr}'s Definition}
+\subsection{Deriving the Standard Correlation Function Definition from \texttt{TreeCorr}'s Definition} \label{corr_defs}
 

### 2016-06-04 tests/binmap_test.py

@@ -60,8 +60,9 @@ Kmap, Smap = B.bin_to_maps(lensed='map',binsize=binsize,savefile='kappa_map')
 
 # Drill the lightcones
 if vb is True: print('Drilling lightcones...')
-lc_radius = 2.0
-B.drill_lightcones(radius=lc_radius,foreground=F,save=False)
+lc_radius = 6.0
+smooth_corr = True
+B.drill_lightcones(radius=lc_radius,foreground=F,save=False,smooth_corr=smooth_corr)
 
 # Calculate mean/std galaxies per lightcone
 galaxy_counts = [lightcone.galaxy_count for lightcone in B.lightcones]
@@ -72,8 +73,8 @@ print 'Lightcones have {0:.2f} +/- {1:.2f} galaxies'.format(mean_galaxies,std_ga
 # Lens the background catalog by foreground halos
 if vb is True: print('Lensing background by halos..')
 #relevance_lim = 0.0
-relevance_lim = 0.00001
-B.lens_by_halos(relevance_lim=relevance_lim,lookup_table=True,smooth_corr=False)
+relevance_lim = 10**-5
+B.lens_by_halos(relevance_lim=relevance_lim,lookup_table=True,smooth_corr=smooth_corr)
 print 'Lightcones have {0:.2f} +/- {1:.2f} relevant galaxies'.format(B.mean_relevant_halos,B.std_relevant_halos)
 
 # Bin kappa and shear maps
@@ -96,4 +97,4 @@ print 'mean Khalo = {}'.format(np.mean(Khalo.values[0]))
 Khalo.values[0] = Khalo.values[0] - np.mean(Khalo.values[0])
 
 # Make 3 subplots of all maps
-pangloss.plotting.compare_binned_maps(Kmap,Khalo,fig_size=10,savefile='kappamap_plots')
+pangloss.plotting.compare_binned_maps(Kmap,Khalo,fig_size=20,savefile='kappamap_plots')

### 2016-06-04 tests/lens_compare.py

@@ -79,8 +79,8 @@ B.lens_by_map(K,S)
 print 'Background catalog has',B.galaxy_count,'galaxies'
 
 # Drill the lightcones
-if vb is True: print('Drilling lightcones...')
-lc_radius = 6.0
+if vb is True: print('Drilling ligh7cones...')
+lc_radius = 7.0
 smooth_corr = True
 B.drill_lightcones(radius=lc_radius,foreground=F,save=False,smooth_corr=smooth_corr)
 
@@ -99,8 +99,9 @@ print 'Lightcones have {0:.2f} +/- {1:.2f} galaxies'.format(mean_galaxies,std_ga
 if vb is True: print('Lensing background by halos..')
 relevance_lim = 0.0
 #relevance_lim = 0.00001
-cProfile.run('B.lens_by_halos(relevance_lim=relevance_lim,lookup_table=True,smooth_corr=smooth_corr); print')
-#B.lens_by_halos(relevance_lim=relevance_lim,lookup_table=True,smooth_corr=smooth_corr)
+#relevance_lim = 10**-7
+#cProfile.run('B.lens_by_halos(relevance_lim=relevance_lim,lookup_table=True,smooth_corr=smooth_corr); print')
+B.lens_by_halos(relevance_lim=relevance_lim,lookup_table=True,smooth_corr=smooth_corr)
 print 'Lightcones have {0:.2f} +/- {1:.2f} relevant galaxies'.format(B.mean_relevant_halos,B.std_relevant_halos)
 
 # Calculate likelihood
@@ -171,10 +172,18 @@ if corr_plots is True:
     plt.gcf().set_size_inches(10,10)
     plt.show()
 
+    # Calculate RMSE
+    gg_nrmse = np.sqrt( np.sum( (gg_halo.xip - gg_map.xip)**2 ) / np.size(gg_map.xip) ) / np.sqrt( np.sum( gg_halo.xip**2 ) / np.size(gg_map.xip) )
+    print 'The shear-shear correlation function NRMSE = {}'.format(gg_nrmse)
+
     pangloss.plotting.plot_corr(ng_map,corr_type='ng',corr_comp='real',lensed='map',color='green',galaxy_count=B.galaxy_count)
     pangloss.plotting.plot_corr(ng_halo,corr_type='ng',corr_comp='real',lensed='halo',color='purple')
     plt.gcf().set_size_inches(10,10)
     plt.show()
+
[…]

### 2016-06-04 tests/mle_vs_abc.py

@@ -50,7 +50,7 @@ d = [1.6,1.4,-1.6,-1.4] # 1440 galaxies
 #d = [1.55,1.54,-1.61,-1.6] # ~3 galaxies
 
 # time data is stored in these arrays...
-T = 1 # number of time data points
+T = 20 # number of time data points
 likelihood_time = []
 likelihood_total_time = []
 abc_time = []
@@ -58,7 +58,7 @@ abc_total_time = []
 
 #
 area = 0.2*0.2*(3600) #arcmin^2
-n = 1000000 # number of sources
+n = 3*10**2 # number of sources
 N = n / area # number of soruces per arcmin^2
 
 for i in range(T):
@@ -100,6 +100,7 @@ for i in range(T):
     start_likelihood = timeit.default_timer()
     likelihood = B.calculate_log_likelihood(lensed='map')
     cProfile.run('B.calculate_log_likelihood(lensed="map"); print')
+    B.calculate_log_likelihood(lensed='map')
     likelihood_time.append(timeit.default_timer() - start_likelihood)
     likelihood_total_time.append(timeit.default_timer() - start_time)
     print 'lens_by_halos likelihood = {}; likelihood time was {} s, Total time taken was {} s'.format(likelihood,likelihood_time[i],likelihood_total_time[i])

### 2016-06-05 doc/thesis_swe.tex
Thesis update. #98

@@
 \newcommand{\apjl}{ApJ}
-
-% Used for footnotes
+\newcommand{\jcap}{JCAP}
+\newcommand{\aj}{AJ}
+\newcommand{\apjs}{ApJS}
+
 \makeatletter
-\newcommand\footnoteref[1]{\protected@xdef\@thefnmark{\ref{#1}}\@footnotemark}
+\newcommand\footnoteref[1]{\protected@xdef\@thefnmark{\ref{#1}}\@footnotemark} % Used for footnotes
+\def\p@subsection{} % Fixes section references
 \makeatother
 
-\raggedbottom
+% \raggedbottom
 
@@
 
-\title{SPENCER THESIS - WORK IN PROGRESS}
+\title{Line of Sight Lensing Mass Reconstructions in the Millennium Simulation}
 %\thanks{A footnote to the article title}%
@@
 \begin{abstract}
-\noindent (TEMPORARY) Recent evidence suggests that dark matter dominates over the normal matter we experience in everyday life, yet we are unable to directly map it as it does not absorb or emit light.
+\noindent 
+% (TEMPORARY) Recent evidence suggests that dark matter dominates over the normal matter we experience in everyday life, yet we are unable to directly map it as it does not absorb or emit light.
 Being able to predict high-resolution dark matter mass maps would be interesting in of itself, but from this we can also study structure formation and constrain the parameters of the universe.
@@
 I found that ...
-
-% OLD: As dark matter does not absorb or emit light, its distribution in the universe must be inferred through indirect effects such as the gravitational lensing of distant galaxies.
-While most sources are only weakly lensed, the systematic alignment of background galaxies around a foreground lens can constrain the mass of the lens which is largely in the form of dark matter.
-In this paper, I have implemented a framework to reconstruct all of the mass along lines of sight using a  best-case dark matter halo model in which the halo mass is known.
-This framework is then used to make predictions of the weak lensing of 3,240 generated source galaxies through a 324 arcmin$^2$ field of the Millennium Simulation.
-The lensed source ellipticities are characterized by the ellipticity-ellipticity and galaxy-mass correlation functions and compared to the same statistic for the intrinsic and ray-traced ellipticities.
-In the ellipticity-ellipticity correlation function, I find that the framework systematically under predicts the shear power by an average factor of 2.2 and fails to capture correlation from dark matter structure at scales larger than 1 arcminute.
-The model predicted galaxy-mass correlation function is in agreement with the ray-traced statistic from scales 0.2 to 0.7 arcminutes, but systematically underpredicts shear power at scales larger than 0.7 arcminutes by an average factor of 1.2.
-Optimization of the framework code has reduced the mean CPU time per lensing prediction by 70\% to $24\pm5$ ms.
-Physical and computational shortcomings of the framework are discussed, as well as potential improvements for upcoming work.
+As dark matter does not absorb or emit light, its distribution in the universe must be inferred through indirect effects such as the gravitational lensing of distant galaxies.
+While most sources are only weakly lensed, the systematic alignment of background galaxies around a foreground lens can constrain the mass of the lens which is largely dark matter.
+In this thesis, I have implemented a framework to reconstruct lensing mass along lines of sight in a 144 arcmin$^2$ field of the Millennium Simulation by predicting the weak lensing of 1440 generated source galaxies using a best-case dark matter halo model in which the halo mass is known.
+The lensed source ellipticities are characterized by the ellipticity-ellipticity and galaxy-mass correlation functions and compared to the same statistic using the `true' ray-traced ellipticities.
+In the ellipticity-ellipticity correlation function, I find that the halo model systematically underpredicts the correlation on scales above 0.2 arcminutes by a mean NRMSE of 0.22, although this can be decreased by including more halo contributions.
+The model predicted galaxy-mass correlation function is in agreement with the ray-traced statistic on scales from 0.2 to 2 arcminutes but overpredicts the correlation on scales below 0.2 arcminutes due to strong lensing effects with a mean NRMSE of 0.36.
+Both best-case statistics were found to be well approximated by using only the most `relevant' halos, which on average only needed the 300 and 70 most relevant halos to predict the correlation functions with a NRMSE below 5\% and 10\% respectively.
+The feasibility of using the halo model to infer hyperparameters of the Millennium Simulation with either maximum likelihood estimation or approximate Bayesian computation is explored, with preliminary results favoring likelihood estimation.
+Optimization of the framework code has reduced the mean CPU time per lensing prediction by 59\% to $57\pm8$ ms, although this is approximately two orders of magnitude slower than required for a planned scale-up to a 100 arcmin$^2$ field.
+Physical and computational limitations of the framework are discussed, as well as potential improvements for future work.
 \end{abstract}
 
-%\pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
-                             % Classification Scheme.
-%\keywords{Suggested keywords}%Use showkeys class option if keyword
-                              %display desired
 \maketitle
@@
 
-In a universe teeming with galaxies and light, it came as a shock when 20\textsuperscript{th} century astronomers discovered that most of the mass in the universe is in fact dark; the `normal' matter made of atoms that we interact with in everyday life, called baryonic matter, accounts for less than 20\% of the mass in the observable universe \cite{planck}.
+In a universe teeming with galaxies and light, it came as a shock when 20\textsuperscript{th} century astronomers discovered that most of the mass in the universe is in fact dark; the `normal' matter made of atoms that we interact with in everyday life, called baryonic matter, accounts for less than 20\% of the mass in the observable universe \cite{planck_2015}.
 The remaining mass takes the form of an exotic dark matter that does not absorb or emit light rendering it invisible to our telescopes.
-While this claim sounds bizarre, there has been an abundance of indirect evidence in recent decades for the existence of dark matter including the flattening of galaxy rotation curves \cite{rotation_curve}, velocity dispersions of galaxies \cite{zwicky}, acoustic peaks in the cosmic microwave background \cite{planck_2015}, and galaxy cluster collisions \cite{bullet_cluster}.
+While this claim sounds bizarre, there has been an abundance of indirect evidence in recent decades for the existence of dark matter including the flattening of galaxy rotation curves \cite{rotation_curve}, velocity dispersions of galaxies \cite{zwicky}, the power spectrum of the cosmic microwave background radiation \cite{planck_2015}, acoustic peaks in the correlation function of luminous red galaxies \cite{bao_detection}, and galaxy cluster collisions \cite{bullet_cluster}.
 
@@
 Light from different origins in a source galaxy is subject to different bending which results in a distortion of the galaxy image.
-As the foreground mass is known to be largely dark matter, gravitational lensing supplies a direct constraint on the mass of dark matter in that region \cite{mass_constraint}.
+As the foreground mass is known to be largely dark matter, gravitational lensing supplies a direct constraint on the mass of dark matter in that region \cite{dark_matter_probe}.
 
@@
 Predicting accurate dark matter mass maps from weak lensing requires understanding the correlation between galaxies and dark matter structure.
-Numerous N-body simulations have predicted dark matter structure to have evolved from overdense regions in the early universe into `halos' of virialized matter that eventually collapsed from self-gravity (cite), where galaxies could then form in the large gravitational potentials of the halos.
-However, there is still extensive reserach being done on the correct density profile of the halos (isothermal spheres \cite{isothermal_spheres}, NFW \cite{nfw}, BMO \cite{bmo}, Einasto \cite{einasto}), identifying the stellar mass - halo mass relation \cite{smhr}, abundance matching \cite{reddick}, halo substructure \cite{substructure}, and the lensing by line-of-sight halos \cite{collet} and by dark matter structures not associated with galaxies \cite{mccully}.
+Numerous N-body simulations have predicted dark matter structure to have evolved from overdense regions in the early universe into `halos' of virialized matter that eventually collapsed from self-gravity \cite{halo_formation}, where galaxies could then form in the large gravitational potentials of the halos.
+However, there is still extensive reserach being done on the correct density profile of the halos (isothermal spheres \cite{isothermal_spheres}, NFW \cite{nfw}, BMO \cite{nfw_bmo}, Einasto \cite{einasto}), identifying the stellar mass - halo mass relation \cite{smhr}, abundance matching \cite{abundance_matching}, halo substructure \cite{halo_substructure}, and the lensing by line-of-sight halos \cite{collett} and by dark matter structures not associated with galaxies \cite{mccully}.
 If a model for the distribution of dark matter in a region of foreground mass can accurately predict the statistical signal of the weak lensing of background sources, then the model can be used on galaxies in existing sky survey data to extrapolate the amount of dark matter in the region and construct large-scale maps of the dark matter in the universe.
 
-Guided by these results, in this thesis I build upon the work of Collet et al.
-in \cite{collet} to apply a simple dark matter halo model to reconstruct lensing mass along lines of sight in the Millennium Simulation in order to predict the weakly lensed ellipticities of generated background sources.
+Guided by these results, in this thesis I build upon the work of Collett et al.
+in \cite{collett} to apply a simple dark matter halo model to reconstruct lensing mass along lines of sight in the Millennium Simulation in order to predict the weakly lensed ellipticities of generated background sources.
 I then compare my predicted lensed ellipticities to the `true' lensing calculated by Hilbert et al.
@@
 
-\begin{enumerate}
+\begin{itemize}
 \item Under the best possible circumstances of having noiseless redshifts and halo masses, how accurately can I reconstruct line-of-sight dark matter mass structures using a halo model?
-%\item What fraction of dark matter mass is in halos?
 \item How many halos are needed to make these predictions?
@@
 \item How long does such an inference take?
-\end{enumerate}
+\end{itemize}
 
@@
     \captionsetup{justification=raggedright,singlelinecheck=false}
-    \caption{CAPTION}
+    \caption{\cite{ms_figures}}
     \label{fig:ms_structure}
@@
     \end{subfigure}
-    \caption{}
+    \caption{\cite{ms_figures}}
     \label{ms_compare}
@@
 
-Cosmological simulations like the Millennium Simulation (MS) demonstrate that the underlying matter distribution of our universe is likely breathtakingly complex; rather than a largely disordered collection of galaxies and interstellar gas, matter appears to condense into clusters and superclusters of galaxies threaded together by large filaments pocketed with under-dense regions called voids, as shown in Figure \ref{fig:ms_structure} \cite{??}.
-While the exact relation between the distribution of galaxies and dark matter is not known, simulations predict that early galaxies formed in the large gravitational potentials of over-dense regions of dark matter \cite{??}.
-This suggests that, while we cannot map dark matter directly, galaxies should trace out at least some of the underlying dark matter structures \cite{??}.
+Cosmological simulations like the Millennium Simulation (MS) demonstrate that the underlying matter distribution of our universe is likely breathtakingly complex; rather than a largely disordered collection of galaxies and interstellar gas, matter appears to condense into clusters and superclusters of galaxies threaded together by large filaments pocketed with under-dense regions called voids, as shown in Figure \ref{fig:ms_structure} \cite{ms_figures}.
+While the exact relation between the distribution of galaxies and dark matter is not known, simulations predict that early galaxies formed in the large gravitational potentials of over-dense regions of dark matter \cite{halo_formation}.
+This suggests that, while we cannot map dark matter directly, galaxies should trace out at least some of the underlying dark matter structures \cite{abundance_matching}.
 A comparrison of the predicted galaxy and dark matter distribution from a small region of the MS is shown in Figure \ref{ms_compare}.
 
-%However, these simulations also indicate that galaxies tend to form in the large gravitational potentials of dark matter over-dense regions of dark matter.
-While the exact relation between the distribution of galaxies and dark matter is not known, this m
-
 The simplest way to model the relationship between galaxies and dark matter is by enveloping each galaxy in a spherically symmetric dark matter `halo' of a certain mass $M_h$.
-These halos extend far beyond the edge of the visible galaxy that they enclose, with the Milky Way's own halo estimated to have a radius of ??
-\cite{??}.
+These halos extend far beyond the edge of the visible galaxy that they enclose, with the Milky Way's own halo estimated to have a radius of between 300,000 and 400,000 light-yeras \cite{milky_way_halo}.
 While the density profile of the halos may be complex, numerous simulations have shown that it can be well approximated locally by the Navarro-Frenk-White (NFW) profile which has the form
@@
 %%------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Filaments, Voids, and the Smooth-Component Correction} \label{scc}
+\subsection{Filaments, Voids, and the Smooth-Component Correction}\label{scc}
 
@@
 
-% With this, the proper volume of olume of the lightcone a given grid slice at redshift $z$ in a foreground catalog centered at ($\theta,\phi$) by integrating the above volume element over the solid angle $d\Omega$ and $\Delta z$ range of the redshift slice:
-% \begin{align}
-% V(z)&=\int_{V_z}dV_p\\ \nonumber
-% &=d_H\int_\Omega\int_{z-\frac{\Delta z}{2}}^{z+\frac{\Delta z}{2}} \frac{d_M(z^\prime)^2}{E(z^\prime)(1+z^\prime)^3}dz^\prime d\Omega.
-% \end{align}
-
 %%------------------------------------------------------------------------------------------------------------------------------------------
@@
 By observing how the magnitudes and shapes of distant galaxies are distorted when travelling through regions of matter, we can infer the masses of the dark matter halos and reconstruct the hidden dark matter mass distribution.
-A simplified cartoon of this process is shown in Figure ??.
+%A simplified cartoon of this process is shown in Figure \ref{fig:lens_diagram}.
 
@@
 %% Gravitational Lensing Diagram
-% \begin{figure*}
+% \begin{figure}
 %     \centering
-%     \begin{subfigure}[H]{0.4\textwidth}
-%         \includegraphics[width=\textwidth]{figs-swe/thesis/lens_cartoon.png}
+%     \includegraphics[width=0.475\textwidth]{figs-swe/thesis/lensing_diagram.jpg}
 %     \captionsetup{justification=raggedright,singlelinecheck=false}
-%         \caption{CAPTION}
-%         \label{lens_cartoon}
-%     \end{subfigure}
-%     ~
-%     %% Einstein Ring Figure
-%     \begin{subfigure}[H]{0.4\textwidth}
-%         \includegraphics[width=\textwidth]{figs-swe/thesis/lens_diagram.png}
-%         \captionsetup{justification=raggedright,singlelinecheck=false}
-%         \caption{CAPTION}
-%         \label{lens_diagram}
-%     \end{subfigure}
-%     \caption{}
-% \end{figure*}
+%     \caption{CAPTION, Illustration by Ian Worpole (www.ianworpole.com)}
+%     \label{fig:lens_diagram}
+% \end{figure}
 %%------------------------------------------------------------------------------------------------------------------------------------------
@@
 
-\noindent where $\sum(\vec{r},z_l)$ is the projected surface mass density of the lensing mass and $\sum_{cr}(z_l,z_s)$ is the critical surface density for a given source redshift $z_s$ and lens redshift $z_l$ \cite{??}.
+\noindent where $\sum(\vec{r},z_l)$ is the projected surface mass density of the lensing mass and $\sum_{cr}(z_l,z_s)$ is the critical surface density for a given source redshift $z_s$ and lens redshift $z_l$ \cite{schneider}.
 The shearing of the source is most often described by the complex shear $\gamma$ defined to be
@@
 \noindent where $|\gamma|$ is the magnitude of the shear and $\varphi$ is the orientation of the shear.
-While the intrinsic ellipticities of source galaxies are randomly oriented near the foreground mass before lensing, they will be systematically more aligned with the shear field after lensing.% Figure (??) demonstrates this process visually.
+While the intrinsic ellipticities of source galaxies are randomly oriented near the foreground mass before lensing, they will be systematically more aligned with the shear field after lensing.
 
@@
  The analytical form of the convergence and shear contribution from a BMO-profile is quite messy, but is derived and explained in detail in \ref{bmo}.
-Calculating the lensing contribution of the smooth-component correction is much simpler; the projected surface mass density at at given redshift is found by integrating $\rho_s(z)$ over a sufficiently small $dz$ interval, and then the mass sheet's convergence is found using Equation \eqref{kappa}.
-There is no shear contribution as a uniform sheet of mass causes only magnification due to the mass sheet degeneracy \cite{??}.
+Calculating the lensing contribution of the smooth-component correction is much simpler; the projected surface mass density at at given redshift is found by integrating $\rho_s(z)$ over a sufficiently small $dz$ interval, and then the mass sheet's convergence is found using Equation \eqref{convergence}.
+There is no shear contribution as a uniform sheet of mass causes only magnification due to the mass sheet degeneracy \cite{mass_degeneracy}.
 However, Equation \eqref{lensing} shows that the lensed ellipticities depend on the \textit{reduced} shear, which does depend on the additional convergence terms resulting from the smooth-component correction.
@@
 The average correlation of a sufficient number of galaxy pairs should overcome the noise and lead to a detectable signal.
-Importantly, this implies that \textit{the correlation of galaxy ellipticities is a probe of the underlying dark matter mass distribution} \cite{??}.
+Importantly, this implies that \textit{the correlation of galaxy ellipticities is a probe of the underlying dark matter mass distribution} \cite{dark_matter_probe}.
 
@@
 A similar statistical measure often used in weak lensing measurements is the galaxy-mass correlation function which, in this setting, measures the cross-correlation of galaxy ellipticities and halo locations.
-Simply put, the function measures the correlation of lensed ellipticities around foreground halos as a function of separation distance and only has one component relevant for this work (see \cite{ng_corr} for details).
+Simply put, the function measures the correlation of lensed ellipticities around foreground halos as a function of separation distance and only has one component relevant for this work (see \cite{gm_corr} for details).
 
@@
 To do this, I built upon the publicly available \texttt{Pangloss}\footnote{\label{note1}https://github.com/drphilmarshall/Pangloss} framework used in Collett et al.
-(\cite{collett_marshall}) to reconstruct all the
+(\cite{collett}) to reconstruct all the
 mass along the lines of sight of generated background galaxies in the MS using a halo model with smooth-component correction.
@@
 For this purpose, \texttt{Pangloss} was tested on galaxy catalogs from the Millennium Simulation, an N-body simulation consisting of over 10 billion dark matter `particles' each representing a billion solar masses and populated with about 20 million galaxies \cite{millennium_simulation}.
-The simulation contains baryonic and dark matter structure believed to be similar to our own universe, and uses cosmological parameters from WMAP 1\textsuperscript{st}-year data analysis which assumed a matter density of $\Omega_m=0.25$, a dark energy density of $\Omega_\Lambda=0.75$, and a Hubble constant of $H_0=73$ km$\,$s$^{-1}\,$Mpc$^{-1}$ (Cite).
+The simulation contains baryonic and dark matter structure believed to be similar to our own universe, and uses cosmological parameters from WMAP 1\textsuperscript{st}-year data analysis which assumed a matter density of $\Omega_m=0.25$, a dark energy density of $\Omega_\Lambda=0.75$, and a Hubble constant of $H_0=73$ km$\,$s$^{-1}\,$Mpc$^{-1}$ \cite{wmap1}.
 From the work of Hilbert et al.
@@
 In most redshift bins, the halo density is one to two orders of magnitude lower than than the universe mean density leading to a smooth-component density very close to that of the mean density.
-This seems to be in opposition to Pache et al.
-(year) \cite{pache} who found that halos constituted ??\% of simulation mass in ??.
 However, all mass densities are far below the critial density, plotted in red, and so well within the weak-lensing regime.
 The convergence distribution of each halo and 100 smooth-components is plotted in Figure \ref{fig:kappa_dist}.
+% This seems to be in opposition to Pace et al. in \cite{pace}, which found that halos constituted ??\% of simulation mass in ??.
 %%------------------------------------------------------------------------------------------------------------------------------------------
@@
 Both correlation functions are used in this work to estimate how well the \texttt{Pangloss} framework models weak lensing by dark matter structures and are computed using the publicly available \texttt{TreeCorr} module written by Mike Jarvis\footnote{https://github.com/rmjarvis/TreeCorr}.
-Note that the ellipticity-ellipticity correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition and the more common Schneider definition \cite{schneider}, see Appendix \ref{corr_defs}.
+Note that the ellipticity-ellipticity correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition \cite{jarvis} and the more common Schneider definition \cite{schneider}, see Appendix \ref{corr_defs}.
 
@@
 The cross-component of the correlation function shows no significant deviation from zero as expected, as gravitational lensing only shears galaxies tangentially.
-For the $\xi_+$ component, the ray-traced (plotted in green) and halo model (plotted in purple) are in relative agreement from seperation scales of 0.1 to 0.2 arcminutes, but there is a clear systematic underprediction of correlation by the halo model on scales larger than 0.2 arcminutes.
+For the $\xi_+$ component, the ray-traced (plotted in green) and halo model (plotted in purple) are in relative agreement from seperation scales of 0.1 to 0.2 arcminutes, but there is a systematic underprediction of correlation by the halo model on scales larger than 0.2 arcminutes by an average of 31\%.
+This result is consistent with Pace et al.
+in \cite{pace} which found that a purely halo model underpredicted the lensing correlation on average by 40\%.
 This may be indicative that not enough halo mass is being used in the lensing prediction, the halo model does not adequately address large-scale mass structures, or that there is significant dark matter mass not correlated with galaxies.
@@
 Figure \ref{fig:halo_fraction} plots the $\varepsilon$-$\varepsilon$ and galaxy-mass correlation function NRMSE as a function of relevance limits and mean relevant halos.
-These results suggest that either correlation function prediction can be approximated with an NRMSE below 10\% using around the ??
-most relevant halos, or an NRMSE of below 5\% using around the ??
-most relevant halos.
+These results suggest that either correlation function prediction can be approximated on average with an NRMSE below 10\% using around the 70 most relevant halos, or an NRMSE of below 5\% using around the 300 most relevant halos.
 Calibration curves such as this can allow the best-case correlation function to be predicted within a desired accuracy at only a fraction of the full lensing calculation which will be especially helpful in future analyses with much larger fields of view.
@@
 The result of a particular 9 arcmin$^2$ field is shown in Figure \ref{fig:kappamaps}, where the ray-traced convergence is shown on the left, the halo model convergence is in the center, and the ray-traced convergence subtracted from the halo model convergence is shown on the right.
-While particular foreground masses are almost always predicted, the currently implemented halo model over-predicts the convergence throughout most of the field; b.
+While particular foreground objects are almost always predicted, the currently implemented halo model over-predicts the convergence throughout most of the field; (more).
 The halo model does not appear to accurately account for the voids between foreground masses and over-predicts the mass of most ...
 This could partially be a result of incorrect halo profiles, but it is apparent that the smooth-component correction is not adequate to ...
+(rework)
 
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{figs-swe/thesis/cpu_scaling.png}
+    \includegraphics[width=0.875\textwidth]{figs-swe/thesis/cpu_scaling.png}
     \captionsetup{justification=raggedright,singlelinecheck=false}
@@
 The results of this feasibility test, particularly the CPU time per likelihood estimation, will help guide fugure work on \texttt{Pangloss}.
-For a detailed description of a probablistic modeling approach to gravitational lensing inference for large sky surveys, see \cite{grav_lens_inference}.
+For a detailed description of a probablistic modeling approach to gravitational lensing inference for large sky surveys, see \cite{hierarchial_inference}.
 Exploratory notes of implementing such an inference in the framework is available on \texttt{Pangloss}'s public github repository\footnote{https://github.com/drphilmarshall/Pangloss/issues/23}.\\
@@
 Perhaps the most common method of parameter estimation of statistical models is called maximum-likelihood estimation (MLE).
-The likelihood is a function of the parameters of a statistical model that measures the probability of a data set or outcomes given the model parameters \cite{??}.
-It is the mathematical answer to the question, ``\textit{Given a particular set of parameters, what is the probability that this data set could have occured?}" The form of the likelihood depends on the properties and circumstances of the data but generally has the form of the product of the probability density function $f$ of each individual observation $x_i$ given model parameters $\vec{\theta}$ \cite{likelihood}:
+The likelihood is a function of the parameters of a statistical model that measures the probability of a data set or outcomes given the model parameters \cite{bayes_in_sky}.
+It is the mathematical answer to the question, ``\textit{Given a particular set of parameters, what is the probability that this data set could have occured?}" The form of the likelihood depends on the properties and circumstances of the data but generally has the form of the product of the probability density function $f$ of each individual observation $x_i$ given model parameters $\vec{\theta}$:
 \begin{equation}
@@
 
-A much more detailed introduction to likelihood and MLE is given in \cite{likelihood}. For this work, the likelihood is given by \cite{marshall_thesis}:
+A much more detailed introduction to likelihood and MLE is given in \cite{bayes_in_sky}. For this work, the likelihood is given by \cite{marshall_thesis}:
 \begin{equation}\label{likelihood}
@@
 This is not entierly surprising as the only structure beyond halos accounted for in the presented model was the smooth-component correction which only adds sheets of uniform mass; clearly a better model of filaments and voids is needed to make accurate correlation predictions on scales larger than $\sim$1 arcminute.
-The progression of model predicted ellipticity-ellipticity correlation functions at larger radii converging to the ray-traced correlation in Figure \ref{fig:gg_corr_series} supports the analysis given above as the prediction was progressively better with larger number of foreground halos and thus more mass and structure.
+The progression of model predicted ellipticity-ellipticity correlation functions at larger radii converging to the ray-traced correlation in Figure \ref{fig:gg_corr_series} supports this analysis as the prediction was progressively better with larger number of foreground halos and thus more mass and structure.
 
@@
 
-While the current \texttt{Pangloss} framework can handle the lensing predictions of 1440 sources in a 144 arcmin$^2$ field comfortably on a single processor, the goal is to scale up the framework to make predictions for background sources of the same number density in a 100 deg$^2$ field; this will require 3.6 million lightcones, each containing at least ???
-relevant foreground halos.
+While the current \texttt{Pangloss} framework can handle the lensing predictions of 1440 sources in a 144 arcmin$^2$ field comfortably on a single processor, the goal is to scale up the framework to make predictions for background sources of the same number density in a 100 deg$^2$ field; this will require 3.6 million lightcones, each containing at least 300 relevant foreground halos for an estimated NRMSE of less than 5\%.
 Luckily, the prediction is trivially parallelizable as the shear and convergence calculation of each lightcone is independent of all other lightcones.
@@
 Possible solutions to (1) are to experiment with faster numerical integrators or, more importantly, ???.
-The second issue suggests that \texttt{Pangloss} should store catalog data in databases rather than \texttt{Astropy} tables as databases are designed for rapid retrieval, modification, and deletion of data \cite{??}.
+The second issue suggests that \texttt{Pangloss} should store catalog data in databases rather than \texttt{Astropy} tables as databases are designed for rapid retrieval, modification, and deletion of data \cite{databases}.
 While this will require significant reworking of the framework to implement, the CPU distribution indicates that such a change is necessary for even a moderate scale up.
@@
 
-% In this thesis...
-% \begin{enumerate}
-% \item implement simple halo model to predict weak lensing of background sources along LOS by halos
-% \item characterized success of model by correlation functions
-% \item good and bad results in correlation function
-% \item correlation fraction of relevant halos
-% \item missing features in the model
-% \item scaling up pangloss
-% \end{enumerate}
-
 In this thesis, a simple halo model was used to reconstruct lensing mass along lines of sight in the Millennium Simulation to make predictions of how foreground mass weakly lensed the ellipticities of 1440 generated background sources across a field of 144 arcmin$^2$.
 The lensed ellipticities were characterized globally using the $\varepsilon$-$\varepsilon$ and galaxy-mass correlation functions and then compared with the same statistics from the ray-traced data calculated in \cite{ray_tracing}.
-There was a systematic-underprediction of correlation on scales larger than 0.2 arcminutes in the $\varepsilon$-$\varepsilon$ correlation function suggesting missing features in the halo model.
+I then explored what fraction of foreground halos were truly relevant to the lensing prediction, the computational performance of the used framework, and how feasible an inference of hyperparameters like the stellar mass - halo mass relation will be in future work using either MLE or ABC.
+My conclusions to the questions posed in the introduction are as follows:
+
+\begin{itemize}
+\item There was a systematic-underprediction of correlation on scales larger than 0.2 arcminutes in the $\varepsilon$-$\varepsilon$ correlation function suggesting missing features of large-scale structure in the halo model.
 The galaxy-mass correlation function predicted by the halo model was in relative agreement with the ray-traced correlation function on scales from 0.2 to 2 arcminutes, but significantly overpredicted the correlation on scales below 0.2 arcminutes due to unaccounted for strong lensing effects.
@@
 
-One of the main results of this thesis is Figure \ref{fig:halo_fraction} which describes the fraction of relevant halos needed to reproduce the best-case correlation functions to a desired accuracy using the relevance metric given in Equation \eqref{relevant} derived by McCully et al.
+\item Figure \ref{fig:halo_fraction} describes the fraction of relevant halos needed to reproduce the best-case correlation functions to a desired accuracy using the relevance metric given in Equation \eqref{relevant} derived by McCully et al.
 in \cite{mccully}.
-It suggests that, on average, the best-case correlation functions can be approximated to a NRMSE of less than 10\% or 5\% using a relevance limit of ${10^{-6}M_\odot\,\text{Mpc}^3}$, or $\sim300$ halos, and ${10^{-5}M_\odot\,\text{Mpc}^3}$, or $\sim70$ halos, respectively.
-
-Finally, this thesis explored the feasibility of implementing a future inference of model hyperparameters like the stellar mass - halo mass relation by characterizing the mean CPU time per likelihood evaluation and ABC decision for catalogs of background sources ranging from $10^2\leq N\leq10^6$ as shown in Figure \ref{fig:mle_vs_abc}.
+It suggests that, on average, the best-case correlation functions can be approximated to a NRMSE of less than 5\% or 10\% using a relevance limit of ${10^{-6}M_\odot\,\text{Mpc}^3}$, or $\sim300$ halos, and ${10^{-5}M_\odot\,\text{Mpc}^3}$, or $\sim70$ halos, respectively.
+This is an encouraging result as Figure \ref{fig:cpu_scaling} shows that the lensing prediction scales quadratically with the $R_l$ and thus halo number.
+Instead of using the many thousands of halos contained in each lightcone for radii above 4 arcminutes, only a few hundred are needed to reproduce the best-case summary statistics within a NRMSE of below 5\%.
+This will be essential in future scale-ups where the lightcone radius and field of view will both be much larger.
+
+\item The mean CPU time per likelihood evaluation and ABC decision for catalogs of background sources ranging from $10^2\leq N\leq10^6$ is shown in Figure \ref{fig:mle_vs_abc}.
 While the likelihood calculation outperformed the summary statistic calculation for all values of $N$, the main result is that neither computation took a significant amount of time relative to the lensing calculation for a given $N$.
-This indicates that inference feasibility rests upon optimizing the lensing prediction code to sufficient speed as discussed in Sections \ref{comp_perform} and \ref{scaling_up}.
-% Answer the following:
-% \begin{enumerate}
-% \item Under the best possible circumstances of having noiseless redshifts and halo masses, how accurately can I reconstruct line-of-sight dark matter mass structures using a halo model?
-% \item How many halos are needed to make these predictions?
-% \item How feasible is an inference of the Millennium Simulation's cosmological hyper-parameters, such as the stellar mass - halo mass relation, using all available halo data? 
-% \item How long does such an inference take?
-% \end{enumerate}
-
-Now that a proof of concept has been demonstrated, work can be done to scale up the \texttt{Pangloss} framework to make lensing predictions over 100 deg$^2$ after implementing the suggested computational and model improvements.
-While the results are encouraging for such a simple model, many strong and unrealistic assumptions were made in the methodology that limit its use in observational surveys.
+This indicates that inference feasibility rests upon optimizing the lensing prediction code to sufficient speed as discussed in Sections \ref{comp_perform} and \ref{scaling_up} rather than the chosen sampling method.
+\end{itemize}
+
+Now that a proof of concept has been demonstrated, work can be done to scale up the \texttt{Pangloss} framework to make lensing predictions of sources accross 100 deg$^2$ after implementing the suggested computational and model improvements.
+While the results are encouraging for a toy model, many strong and unrealistic assumptions were made in the methodology that limit its use in observational surveys.
 In the future, a similar analysis should be made using simulated photometric redshifts and inferred halo masses to see how different the predictions by the halo model are from this best-case scenario.
@@
     \centering
-    \begin{subfigure}{0.45\textwidth}
+    \begin{subfigure}{0.425\textwidth}
         \includegraphics[width=\textwidth]{figs-swe/corr_visualization_unlensed.png}
@@
     ~
-    \begin{subfigure}{0.45\textwidth}
+    \begin{subfigure}{0.425\textwidth}
         \includegraphics[width=\textwidth]{figs-swe/corr_dist_unlensed.png}
@@
     \end{subfigure}
-    \caption{Correlation visualization for un-lensed galaxies.}
+
+    \begin{subfigure}{0.425\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/corr_visualization_lensed.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{The same set of background sources in Figure \ref{color_corr_unlensed} after (magnified for effect) lensing by the foreground mass.
+Regardless of initial orientation, the source galaxies have all at least partially aligned tangentially around the center lensing mass.}
+        \label{color_corr_lensed}
+    \end{subfigure}
+    ~
+    \begin{subfigure}{0.425\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/corr_dist_lensed.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{The distribution of correlation pairs from the source ellipticities in Figure \ref{color_corr_lensed}.
+If the pair of galaxies are in the same color bin, then the correlation scatter point is colored in the same scheme.}
+        \label{corr_dist_lensed}
+    \end{subfigure}
+    \vspace{-.05in}
+    \caption{Correlation visualization for...}
+    % \label{colored_corr_lensed}
+    % \caption{Correlation visualization for un-lensed galaxies.}
     \label{colored_corr}
@@
 %% Color-Coded Correlation Lensed
-\begin{figure}
-    \centering
-    \begin{subfigure}{0.44\textwidth}
-        \includegraphics[width=\textwidth]{figs-swe/corr_visualization_lensed.png}
-        \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{The same set of background sources in Figure \ref{color_corr_unlensed} after (magnified for effect) lensing by the foreground mass.
+% \begin{figure}
+%     \centering
+%     \begin{subfigure}{0.425\textwidth}
+%         \includegraphics[width=\textwidth]{figs-swe/corr_visualization_lensed.png}
+%         \captionsetup{justification=raggedright,singlelinecheck=false}
+%         \caption{The same set of background sources in Figure \ref{color_corr_unlensed} after (magnified for effect) lensing by the foreground mass.
 Regardless of initial orientation, the source galaxies have all at least partially aligned tangentially around the center lensing mass.}
-        \label{color_corr_lensed}
-    \end{subfigure}
-    ~
-    \begin{subfigure}{0.44\textwidth}
-        \includegraphics[width=\textwidth]{figs-swe/corr_dist_lensed.png}
-        \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{The distribution of correlation pairs from the source ellipticities in Figure \ref{color_corr_lensed}.
+%         \label{color_corr_lensed}
+%     \end{subfigure}
+%     ~
+%     \begin{subfigure}{0.425\textwidth}
+%         \includegraphics[width=\textwidth]{figs-swe/corr_dist_lensed.png}
+%         \captionsetup{justification=raggedright,singlelinecheck=false}
+%         \caption{The distribution of correlation pairs from the source ellipticities in Figure \ref{color_corr_lensed}.
 If the pair of galaxies are in the same color bin, then the correlation scatter point is colored in the same scheme.}
-        \label{corr_dist_lensed}
-    \end{subfigure}
-    \vspace{-.05in}
-    \caption{Correlation visualization for lensed galaxies.}
-    \label{colored_corr_lensed}
-\end{figure}
+%         \label{corr_dist_lensed}
+%     \end{subfigure}
+%     \vspace{-.05in}
+%     \caption{Correlation visualization for lensed galaxies.}
+%     \label{colored_corr_lensed}
+% \end{figure}
 

### 2016-06-05 doc/thesis_swe.tex
Thesis update. All captions and citations added. #98

@@
 \def\p@subsection{} % Fixes section references
+\renewcommand\@make@capt@title[2]{%
+     \@ifx@empty\float@link{\@firstofone}{\expandafter\href\expandafter{\float@link}}%
+      {\textbf{#1}}\@caption@fignum@sep#2\quad}% % Fixes caption justification
 \makeatother
@@
     \captionsetup{justification=raggedright,singlelinecheck=false}
-    \caption{\cite{ms_figures}}
+    \caption{A visualization of the large-scale dark matter distribution in the Millennium Simulation.
+The largest bright spots correspond to superclusters of galaxies which are connected by thread-like structures of matter called filaments.
+Taken from \cite{ms_figures}.}
     \label{fig:ms_structure}
@@
         \includegraphics[width=\textwidth]{figs-swe/thesis/ms_galaxies.jpg}
-        \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{CAPTION}
+        %\captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{Galaxy distribution.}
         \label{ms_galaxies}
@@
         \includegraphics[width=\textwidth]{figs-swe/thesis/ms_halos.jpg}
-        \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{CAPTION}
+        %\captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{Halo distribution.}
         \label{ms_halos}
     \end{subfigure}
-    \caption{\cite{ms_figures}}
+    \captionsetup{justification=raggedright,singlelinecheck=false}
+    \caption{A comparison of the galaxy and dark matter distribution for a single cluster in the Millennium Simulation.
+The galaxies tend to be located in the centers of clumps of dark matter called `halos', which suggests that galaxies at least partially trace out the underlying dark matter distribution.
+Taken from \cite{ms_figures}.}
     \label{ms_compare}
@@
 
-Cosmological simulations like the Millennium Simulation (MS) demonstrate that the underlying matter distribution of our universe is likely breathtakingly complex; rather than a largely disordered collection of galaxies and interstellar gas, matter appears to condense into clusters and superclusters of galaxies threaded together by large filaments pocketed with under-dense regions called voids, as shown in Figure \ref{fig:ms_structure} \cite{ms_figures}.
+Cosmological simulations like the Millennium Simulation demonstrate that the underlying matter distribution of our universe is likely breathtakingly complex; rather than a largely disordered collection of galaxies and interstellar gas, matter appears to condense into clusters and superclusters of galaxies threaded together by large filaments pocketed with under-dense regions called voids, as shown in Figure \ref{fig:ms_structure} \cite{ms_figures}.
 While the exact relation between the distribution of galaxies and dark matter is not known, simulations predict that early galaxies formed in the large gravitational potentials of over-dense regions of dark matter \cite{halo_formation}.
 This suggests that, while we cannot map dark matter directly, galaxies should trace out at least some of the underlying dark matter structures \cite{abundance_matching}.
-A comparrison of the predicted galaxy and dark matter distribution from a small region of the MS is shown in Figure \ref{ms_compare}.
+A comparison of the predicted galaxy and dark matter distribution from a small region of the simulation is shown in Figure \ref{ms_compare}.
 
@@
 
- The analytical form of the convergence and shear contribution from a BMO-profile is quite messy, but is derived and explained in detail in \ref{bmo}.
+ The analytical form of the convergence and shear contribution from a BMO-profile is quite messy, but is derived and explained in detail in \ref{nfw_bmo}.
 Calculating the lensing contribution of the smooth-component correction is much simpler; the projected surface mass density at at given redshift is found by integrating $\rho_s(z)$ over a sufficiently small $dz$ interval, and then the mass sheet's convergence is found using Equation \eqref{convergence}.
@@
 (\cite{collett}) to reconstruct all the
-mass along the lines of sight of generated background galaxies in the MS using a halo model with smooth-component correction.
+mass along the lines of sight of generated background galaxies in the Millennium Simulation using a halo model with smooth-component correction.
 The lensing contribution of each halo is calculated, and the total lensing of the background galaxy is the sum of each halo contribution.
@@
 \subsection{Generating Background Galaxies}
-With the (0,0,0,0) catalog of MS foreground galaxies chosen, a set of 1440 background galaxies over a field of 144 arcmin$^2$ was generated, with density 10 galaxies per arcmin$^2$.
+With the (0,0,0,0) catalog of Millennium Simulation foreground galaxies chosen, a set of 1440 background galaxies over a field of 144 arcmin$^2$ was generated, with density 10 galaxies per arcmin$^2$.
 The intrinsic orientation of each galaxy was sampled from a uniform distribution as, without lensing, there should be no preferred orientation due to the assumption of an isotropic universe.
@@
 McCully et al.
-in \ref{mccully} derived that the correct metric for determining the relevance of a given foreground halo to the overall lensing calculation to be given by
+in \cite{mccully} derived that the correct metric for determining the relevance of a given foreground halo to the overall lensing calculation to be given by
 \begin{equation}\label{relevant}
@@
     \captionsetup{justification=raggedright,singlelinecheck=false}
-    \caption{CAPTION}
+    \caption{The mean number of relevant galaxies in a single realization of 1440 source galaxies determined by Equation \eqref{relevant_thresh} with a threshold mass and distance of ${M_T=10^{12}M_\odot}$ and ${R_T=10}$ kpc respectively.
+The errorbars correspond to the standard deviation of relevant halos accross all lightcones.
+As expected, most halos are either too far away from the line-of-sight or not massive enough to make a significant contribution, or both.
+The number of halos falls logarithmically with the relevance limit and reaches a mean of one halo at a relevance of ${10^{-2}M_\odot\,\text{Mpc}^3}$.}
     \label{fig:rel_dist}
@@
     \captionsetup{justification=raggedright,singlelinecheck=false}
-    \caption{CAPTION}
+    \caption{A diagram of the smooth-component correction implementation in \texttt{Pangloss}.
+The halo density at each redshift slice $z$ was calculated by summing the masses of all foreground halos within $\Delta z$ and dividing by the proper volume of the cone slice using Equation \eqref{pvolume_element} and solid angle $d\Omega$.}
     \label{fig:scc}
@@
     % Volume
-    \begin{subfigure}[H]{0.49\textwidth}
+    \begin{subfigure}[H]{0.48\textwidth}
         \includegraphics[width=\textwidth]{figs-swe/thesis/vol_densities.png}
-        \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{CAPTION}
+        % \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{Smooth-component volume densities.}
         \label{fig:volume_densities}
@@
     % Surface
-    \begin{subfigure}[H]{0.49\textwidth}
+    \begin{subfigure}[H]{0.48\textwidth}
         \includegraphics[width=\textwidth]{figs-swe/thesis/surf_densities.png}
-        \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{CAPTION}
+        % \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{Smooth-component projected surface densities.}
         \label{fig:surface_densities}
     \end{subfigure}
-    \caption{}
+    \captionsetup{justification=raggedright,singlelinecheck=false}
+    \caption{The surface and volume densities for each of the 100 smooth-component correction and halo densities in a lightcone with radius $R_L=6$ arcminutes.
+The green line is the halo density of each slice and the blue line is the calculated smooth-component density such that the two densities sum to the universe mean density plotted in black.
+The number of halos in each redshift bin is plotted as a histogram in the background.
+The red line in plot (b) is the ciritical surface density.}
+    \label{densities}
 \end{figure*}
@@
     \captionsetup{justification=raggedright,singlelinecheck=false}
-    \caption{CAPTION}
+    \caption{The convergence distribution of the 4838 individual halos, plotted in green, and the 100 smooth-component slices, plotted in blue, contained in the same lightcone as Figure \ref{densities}.
+The mass sheets have a higher convergence contribution than all but the most relevant halos in the lightcone.
+The curve of smooth component $\kappa$'s indicates how foreground mass at the center of the light's path has the highest lensing efficiency.}
     \label{fig:kappa_dist}
@@
 
-Using the physical separation distance and halo mass, the shear and convergence contribution of a single foreground halo is calculated using methods described in Section \ref{grav_lensing} (see Wright and Brainerd \cite{lensing_calc} for far more detail).
+Using the physical separation distance and halo mass, the shear and convergence contribution of a single foreground halo is calculated using methods described in Section \ref{grav_lensing} (see \cite{lensing_calc} and \cite{nfw_bmo} for more details).
 The total convergence and shear along the LOS of the lightcone is simply the sum of the convergence and shear contributions of each halo contained in the lightcone, as well as the additional convergence terms from the smooth-component correction.
@@
     \captionsetup{justification=raggedright,singlelinecheck=false}
-    \caption{CAPTION}
+    \caption{Four different views of a lightcone centered on the line-of-sight of a particular background source.
+The top left figure plots the positions of the halos with the size proportional to their galaxy brightness in the $i$-band, the center figure plots the angular size of foreground halos with red and blue regions representing the NFW scale radius and virial radius of each halo respectively, the top right figure plots the $\kappa$ contributions of each halo, and the bottom plots the positions of each halo along the redshift axis with size proportional to halo mass.}
     \label{fig:lightcone}
@@
 
-Figure \ref{fig:lightcone} displays different views an example lightcone where the foreground halos are plotted as circles whose size are proportional to their galaxy brightness (top left), angular size (top center), convergence contributions (top right), and halo mass (bottom).
+Figure \ref{fig:lightcone} displays different views an example lightcone where the foreground halos are plotted as circles whose size are proportional to their galaxy brightness (top left), angular size (top center), \texttt{Pangloss} predicted convergence contributions (top right), and halo mass (bottom).
+Comparing the center and top right figures demonstrates the importance of proximity to the line-of-sight for significant $\kappa$ contributions.
 Figure \ref{fig:subplots} shows a few examples of mass structures in the foreground catalog along with the ray-traced convergence (plotted in inverse greyscale) and shear maps (plotted as red ellipticity sticks) from \cite{ray_tracing}.
@@
         \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{CAPTION}
-        %The ellipticity-ellipticity correlation function for ??
-sources at separation distances from 0.1 to 2 arcminutes and a lightcone radius of $R=2$ arcminutes.
-While the correlation of the intrinsic ellipticities before lensing (blue) shows no correlation, the correlation of the ray-traced ellipticities (green) and halo model predicted ellipticities (purple) both show significant positive correlation on scales up to 1 arcminute.
-The halo model predicts a small negative correlation above this scale, while the ray-tracing shows positive correlation on all scales.}
-        %The correlation of the intrinsic ellipticities before lensing is plotted in blue, and shows no correlation.
-The correlation of the true ray-traced ellipticities is plotted in green and shows significant positive correlation on all scales.
-The halo predicted correlation, plotted in purple, shows significant positive correlation until a separation distance of 0.8 arcminutes.
+        \caption{The $\varepsilon$-$\varepsilon$ correlation function for 1440 sources at separation distances from 0.1 to 2 arcminutes using lightcones with radii of $R_L=6$ arcminutes, where green is the `true' ray-traced correlation and purple is the halo model predicted correlation.
+While the cross-component $\xi_\times(\Delta\theta)$ for both is consistent with zero accross all scales as expected, the halo model systematically underpredicts the correlation on scales larger than 0.2 arcminutes.}
         \label{fig:gg_corr}
@@
         \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{CAPTION}
-        %The ellipticity-ellipticity correlation functions for a series of halo model frameworks with increasing lightcone radii from $R=1$ to $R=8$ arcminutes, all plotted in purple with various line styles.
-These are compared to the same ray-traced correlation from Figure \ref{gg_corr}.}
+        \caption{The $\varepsilon$-$\varepsilon$ correlation functions of 1440 sources for a series of halo model frameworks with increasing lightcone radii from $R_L=1$ to $R_L=8$ arcminutes, all plotted in purple with various line styles.
+These are compared to the same ray-traced correlation from Figure \ref{fig:gg_corr}.
+The predicted correlation seems to converge to the ray-traced value with larger $R_L$ as more halo contributions are accounted for.}
         \label{fig:gg_corr_series}
@@
 
-The first test of the halo model was with the $\varepsilon$-$\varepsilon$ correlation function with a lightcone radius of 6 arcminutes which is given in Figure \ref{fig:gg_corr}.
+The first test of the halo model was with the $\varepsilon$-$\varepsilon$ correlation function with a lightcone radius of 6 arcminutes and all halos which is given in Figure \ref{fig:gg_corr}.
 The statistic measured the average correlation between pairs of ellipticities at separation distances between 0.1 and 2 arcminutes.
@@
 
-The catalog of lensed ellipticities was also analyzed using the galaxy-mass correlation function with separation distances from 0.1 to 2 arcminutes and a lightcone radius of 6 arcminutes.
+The catalog of lensed ellipticities was also analyzed using the galaxy-mass correlation function with separation distances from 0.1 to 2 arcminutes and a lightcone radius of 6 arcminutes and all halo.
 The result is shown in Figure \ref{fig:ng_corr}.
@@
         \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{CAPTION}
-        %The galaxy-mass correlation function of 3,240 sources at separation distances from 0.1 to 2 arcminutes and a lightcone radius of $R=2$ arcminutes.
-There is no significant correlation of the intrinsic ellipticities (blue) as expected, and both the ray-traced correlation (green) and halo model correlation (purple) are positive on all scales.
-The green and purple curves are in agreement from 0.2 to 0.7 arcminutes, but have significant discrepancies on scales above and below this range.}
+        \caption{The galaxy-mass correlation function of 1440 sources at separation distances from 0.1 to 2 arcminutes and a lightcone radius of $R_L=6$ arcminutes.
+The halo model predicts the statistic well on scales above 0.3 arcminutes, but systematically overpredicts correlation on scales below 0.2 arcminutes.
+This is likely due to strong lensing effects which are not currently accounted for in \texttt{Pangloss}.}
         \label{fig:ng_corr}
@@
         \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{CAPTION}
+        \caption{The galaxy-mass correlation functions of 1440 sources for a series of halo model frameworks with increasing lightcone radii from $R_L=1$ to $R_L=8$ arcminutes, all plotted in purple with various line styles.
+These are compared to the same ray-traced correlation from Figure \ref{fig:ng_corr}.
+The predicted correlation seems to converge to the ray-traced value with larger $R_L$ as more halo contributions are accounted for.}
         \label{fig:ng_corr_series}
@@
 
-Of intrinsic interest is the relative number of relevant halos needed in each lightcone to accurately predict the halo correlation functions in Figures \ref{fig:gg_corr} and \ref{fig:ng_corr}, as a low percentage would allow much faster lensing predictions.
-Figures \ref{fig:rel_gg_compare} and \ref{fig:rel_ng_compare} display an example $\varepsilon$-$\varepsilon$ and galaxy-mass correlation function comparrison of the halo model using all halos (purple) and halo model using halos above the relevance limit of ${10^{-5} M_{\odot}/\text{Mpc}^3}$, as well as the percent error of each predicted value between the two implementations.
-This relevance limit resulted in $??\pm??$ relevant halos per lightcone, and resulted in a normalized root-mean-square error (NRMSE) of ??.
-Figure \ref{fig:halo_fraction} plots the $\varepsilon$-$\varepsilon$ and galaxy-mass correlation function NRMSE as a function of relevance limits and mean relevant halos.
+Of intrinsic interest is the relative number of relevant halos needed in each lightcone to accurately predict the halo correlation functions in Figures \ref{fig:gg_corr} and \ref{fig:ng_corr} as a low percentage would allow much faster lensing predictions.
+Figures \ref{fig:rel_gg_compare} and \ref{fig:rel_ng_compare} display an example $\varepsilon$-$\varepsilon$ and galaxy-mass correlation function comparison of the halo model using all halos (plotted in purple) and halo model using halos above the relevance limit of ${10^{-5} M_{\odot}/\text{Mpc}^3}$ (plotted in blue) with $R_L=6$ arcminutes, as well as the percent error of each predicted value between the two implementations.
+This relevance limit corresponded to $66\pm10$ relevant halos per lightcone and resulted in a normalized root-mean-square error (NRMSE) of 0.164 and 0.082 for the two statistics.
+Figure \ref{fig:halo_fraction} plots the $\varepsilon$-$\varepsilon$ and galaxy-mass correlation function NRMSE as a function of relevance limits and mean relevant halos, still using a lightcone radius of 6 arcminutes.
 These results suggest that either correlation function prediction can be approximated on average with an NRMSE below 10\% using around the 70 most relevant halos, or an NRMSE of below 5\% using around the 300 most relevant halos.
@@
 %%------------------------------------------------------------------------------------------------------------------------------------------
-% Correlation Function Comparrison
+% Correlation Function comparison
 \begin{figure}
@@
         \includegraphics[width=\textwidth]{figs-swe/thesis/rel_gg_compare.png}
-        \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{CAPTION}
-        %The ellipticity-ellipticity correlation function for ??
-sources at separation distances from 0.1 to 2 arcminutes and a lightcone radius of $R=2$ arcminutes.
-While the correlation of the intrinsic ellipticities before lensing (blue) shows no correlation, the correlation of the ray-traced ellipticities (green) and halo model predicted ellipticities (purple) both show significant positive correlation on scales up to 1 arcminute.
-The halo model predicts a small negative correlation above this scale, while the ray-tracing shows positive correlation on all scales.}
-        %The correlation of the intrinsic ellipticities before lensing is plotted in blue, and shows no correlation.
-The correlation of the true ray-traced ellipticities is plotted in green and shows significant positive correlation on all scales.
-The halo predicted correlation, plotted in purple, shows significant positive correlation until a separation distance of 0.8 arcminutes.
+        % \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{$\varepsilon$-$\varepsilon$ correlation function comparison.}
         \label{fig:rel_gg_compare}
@@
         \includegraphics[width=\textwidth]{figs-swe/thesis/rel_ng_compare.png}
-        \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{CAPTION}
-        %The ellipticity-ellipticity correlation functions for a series of halo model frameworks with increasing lightcone radii from $R=1$ to $R=8$ arcminutes, all plotted in purple with various line styles.
-These are compared to the same ray-traced correlation from Figure \ref{gg_corr}.}
+        % \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{Galaxy-mass correlation function comparison.}
         \label{fig:rel_ng_compare}
     \end{subfigure}
-    \caption{}
+    \captionsetup{justification=raggedright,singlelinecheck=false}
+    \caption{Comparing the two correlation functions using all halos (purple) and only the $66\pm10$ most relevant halos resulting from a relevance limit of ${10^{-5} M_{\odot}/\text{Mpc}^3}$ (blue).
+The percent error of each point as well as the mean error and NRMSE is plotted below each figure.}
     \label{fig:rel_corr}
@@
     \centering
-    \includegraphics[width=0.925\textwidth]{figs-swe/thesis/halo_fraction_long.png}
+    \includegraphics[width=0.95\textwidth]{figs-swe/thesis/halo_fraction_long.png}
     % \includegraphics[width=0.475\textwidth]{figs-swe/thesis/halo_fraction.png}
     \captionsetup{justification=raggedright,singlelinecheck=false}
-    \caption{CAPTION!}
+    \caption{The NRMSE of the $\varepsilon$-$\varepsilon$ and galaxy-mass correlation function, plotted in blue and green respectively, as a function of relevance limit / number of relevant halos used for 1440 sources with $R_L=6$ arcminutes.
+The lines corresponding to an NRMSE of 5\% and 10\% are plotted for convenience.
+This suggests that, on average, either best-case summary statistic can be approximated using only the 70 most relevant halos for a NRMSE below 10\% and the 300 most relevant halos for a NRMSE below 5\%.
+This figure can be used to determine what relevance limit should be used to recover the statistics to a desired accuracy.}
     \label{fig:halo_fraction}
@@
 This was done by selecting a region of foreground mass, calculating the ray-traced and \texttt{Pangloss}-predicted convergence of a uniform grid of background sources in the field, and binning the convergence maps to a desired resolution.
-Convergence is proportional to projected surface mass density, so comparring the two convergence maps is equivalent to comparing their respecitve projected mass distributions.
+Convergence is proportional to projected surface mass density, so comparing the two convergence maps is equivalent to comparing their respecitve projected mass distributions.
 
 The result of a particular 9 arcmin$^2$ field is shown in Figure \ref{fig:kappamaps}, where the ray-traced convergence is shown on the left, the halo model convergence is in the center, and the ray-traced convergence subtracted from the halo model convergence is shown on the right.
-While particular foreground objects are almost always predicted, the currently implemented halo model over-predicts the convergence throughout most of the field; (more).
-The halo model does not appear to accurately account for the voids between foreground masses and over-predicts the mass of most ...
-This could partially be a result of incorrect halo profiles, but it is apparent that the smooth-component correction is not adequate to ...
-(rework)
+While particular foreground objects are almost always predicted, the currently implemented halo model over-predicts the convergence throughout most of the field; the halo model does not appear to accurately account for the voids between foreground masses and over-predicts the mass of most foreground objects.
+This could be a result of incorrect halo profiles, a too-simplistic implementation of the smooth-component correction, missing features in the halo model, a significant amount of dark matter mass not being correlated with galaxies, or some combination of all four possibilities..
 
@@
     \captionsetup{justification=raggedright,singlelinecheck=false}
-    \caption{CAPTION}
+    \caption{The projected convergence map of a 9 arcmin$^2$ field of the Millennium Simulation using (left) the ray-traced convergence, (center) the \texttt{Pangloss} predicted halo model convergence, and (right) the ray-traced convergence subtracted from the halo model convergence.
+All maps are plotted with the same intensity scaling.
+The halo model predicts individual foreground objects, but systematically overpredicts the convergence throughout the map.
+This could be a result of incorrect halo profiles, a too-simplistic modeling of large-scale mass structures, and/or a significant amount of dark matter that is not correlated with galaxies.}
     \label{fig:kappamaps}
@@
     \captionsetup{justification=raggedright,singlelinecheck=false}
-    \caption{OLD: The mean CPU runtime per lightcone for various runs with different (and cumulative) code optimizations described in the text.
-The cumulative changes account for a 59\% decrease in the mean CPU time and a halving of the variation.
-Currently, the prediction can be made for a single lightcone in $57\pm8$ ms.}
+    \caption{The mean CPU runtime per lightcone for various runs with different (and cumulative) code optimizations described in Section \ref{comp_perform}.
+The cumulative changes account for a 59\% decrease in the mean CPU time and a halving of the initial variation.
+On average, the lensing prediction for a single lightcone can now be made in $57\pm8$.}
     \label{fig:cpu_plot}
@@
     \captionsetup{justification=raggedright,singlelinecheck=false}
-    \caption{CAPTION}
+    \caption{The mean CPU runtime required for a single lensing prediction as a function of lightcone radius $R_L$ (left) and relevance limit at constant radius (right).
+The mean runtime scales quadratically with lightcone radius, and therefore halo count, with a overhead of about ${55\pm10}$ ms.
+Increasing the relevance limit to ${10^{-6}M_\odot\,\text{Mpc}^3}$, or about 300 relevant halos, decreases the mean runtime to near the minimum overhead.}
     \label{fig:cpu_scaling}
@@
 However, ABC does come at a cost; as the name implies, there are various assumptions and approximations made in the process that can potentially lead to an innaccurate posterior prediction.
-A general overview of the ABC process is shown in Figure \ref{fig:abc} taken from \cite{abc}, which offers an excellent introduction to the topic.
+See \cite{abc} for an excellent introduction to the topic.
 I summarize a common ABC implementation and its application to \texttt{Pangloss} below.
-
-% In order to gague future inference feasibility, I analyzed whether ABC could make posterior
+%A general overview of the ABC process is shown in Figure \ref{fig:abc} taken from \cite{abc}, which offers an excellent introduction to the topic.
 
@@
 % ABC Diagram
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\textwidth]{figs-swe/thesis/abc.png}
-    \captionsetup{justification=raggedright,singlelinecheck=false}
-    \caption{CAPTION; Will replace with a self-made plot made specifically for \texttt{Pangloss} before thesis submission.}
-    \label{fig:abc}
-\end{figure}
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=0.5\textwidth]{figs-swe/thesis/abc.png}
+%     \captionsetup{justification=raggedright,singlelinecheck=false}
+%     \caption{CAPTION; Will replace with a self-made plot made specifically for \texttt{Pangloss} before thesis submission.}
+%     \label{fig:abc}
+% \end{figure}
 %%------------------------------------------------------------------------------------------------------------------------------------------
@@
 suggests that any future inference work will likely use MLE instead of ABC.
-However, the time spent for either inference method is quite small in comparrison to the CPU time required to create lightcones and make the line-of-sight lensing predictions.
+However, the time spent for either inference method is quite small in comparison to the CPU time required to create lightcones and make the line-of-sight lensing predictions.
 This is an encouraging result which de-emphasizes the choice of sampling method and suggests that further work on the framework should be on additional optimization of the lensing prediction code rather than posterior estimation.
@@
     \centering
-    \includegraphics[width=0.475\textwidth]{figs-swe/thesis/mle_vs_abc.png}
-    \captionsetup{justification=raggedright,singlelinecheck=false}
-    \caption{CAPTION}
+    \includegraphics[width=0.49\textwidth]{figs-swe/thesis/mle_vs_abc.png}
+    \captionsetup{justification=raggedright,singlelinecheck=false}
+    \caption{The mean CPU runtime of a single likelihood evaluation and ABC decision, based upon the $\varepsilon$-$\varepsilon$ correlation function calculation, as a function of the number of background sources $N$.
+The mean runtime was determined using 20 mock catalogs for each $N$.
+Both sampling methods require an overhead of about 3 ms and increase runtime with $N$, but a single ABC decision takes three orders of magnitude more runtime for $N\geq10^5$ galaxies.}
     \label{fig:mle_vs_abc}
@@
 
-The results of Section \ref{feasibility} demonstrated that neither the likelihood nor correlation function computation present a significant computational issue in comparrison to the lensing calculation, so either are feasible approaches for a hierarchial inference of the stellar mass - halo mass relation.
+The results of Section \ref{feasibility} demonstrated that neither the likelihood nor correlation function computation present a significant computational issue in comparison to the lensing calculation, so either are feasible approaches for a hierarchial inference of the stellar mass - halo mass relation.
 As a single ABC rejection algorithm performed many orders of magnitude \textit{worse} than a single likelihood calculation for ${10^2\leq N\leq10^6}$ sources and ABC fundementally an approximation, it appears that the method is not suitable for this work unless ABC ends up requiring far less samples than the number of needed posterior samples in MLE.
@@
 
-The same plots for the source galaxies \textit{after lensing} are shown in Figure \ref{colored_corr_lensed}.
+The same plots for the source galaxies \textit{after lensing} are shown in Figure \ref{color_corr_lensed}.
 The source ellipticities have clearly aligned tangentially around the foreground lens in Figure \ref{color_corr_lensed}, and distinct patterns have appeared in the correlation pair distribution for each color bin in Figure \ref{corr_dist_lensed}.

### 2016-06-05 doc/thesis_swe.tex
Thesis update. #98

@@
 \begin{abstract}
-\noindent 
-% (TEMPORARY) Recent evidence suggests that dark matter dominates over the normal matter we experience in everyday life, yet we are unable to directly map it as it does not absorb or emit light.
-Being able to predict high-resolution dark matter mass maps would be interesting in of itself, but from this we can also study structure formation and constrain the parameters of the universe.
-In this work, I develop the Pangloss model which approximates complex mass distributions with a simple dark matter halo model and then analyze how accurate its predictions can be using weak gravitational lensing data in the Millennium Simulation.
-I then do some exploratory work in estimating how feasible a large inference would be using both likelihood estimation and approximate Bayesian computation (ABC).
-I found that ...
-As dark matter does not absorb or emit light, its distribution in the universe must be inferred through indirect effects such as the gravitational lensing of distant galaxies.
+\noindent As dark matter does not absorb or emit light, its distribution in the universe must be inferred through indirect effects such as the gravitational lensing of distant galaxies.
 While most sources are only weakly lensed, the systematic alignment of background galaxies around a foreground lens can constrain the mass of the lens which is largely dark matter.
@@
 Optimization of the framework code has reduced the mean CPU time per lensing prediction by 59\% to $57\pm8$ ms, although this is approximately two orders of magnitude slower than required for a planned scale-up to a 100 arcmin$^2$ field.
-Physical and computational limitations of the framework are discussed, as well as potential improvements for future work.
+Physical and computational limitations of the framework are discussed as well as potential improvements for future work.
 \end{abstract}
@@
 
- The analytical form of the convergence and shear contribution from a BMO-profile is quite messy, but is derived and explained in detail in \ref{nfw_bmo}.
+ The analytical form of the convergence and shear contribution from a BMO-profile is quite messy, but is derived and explained in detail in \cite{nfw_bmo}.
 Calculating the lensing contribution of the smooth-component correction is much simpler; the projected surface mass density at at given redshift is found by integrating $\rho_s(z)$ over a sufficiently small $dz$ interval, and then the mass sheet's convergence is found using Equation \eqref{convergence}.
@@
     \centering
-    \includegraphics[width=0.75\textwidth]{figs-swe/thesis/lightcone_plots.png}
+    \includegraphics[width=0.8\textwidth]{figs-swe/thesis/lightcone_plots.png}
     \captionsetup{justification=raggedright,singlelinecheck=false}
@@
 Comparing the center and top right figures demonstrates the importance of proximity to the line-of-sight for significant $\kappa$ contributions.
-Figure \ref{fig:subplots} shows a few examples of mass structures in the foreground catalog along with the ray-traced convergence (plotted in inverse greyscale) and shear maps (plotted as red ellipticity sticks) from \cite{ray_tracing}.
+Figure \ref{fig:field2} shows a foreground cluster in a 1.44 arcmin$^2$ section of the Millennium Simulation along with the ray-traced convergence (plotted in inverse greyscale) and shear maps (plotted as red ellipticity sticks) from \cite{ray_tracing}.
+Figure \ref{fig:field3} displays the generated background ellipticities in blue, the `true' lensed ellipticities in green, and the halo model lensed ellipticities in purple.
+While there is a visible difference between the lensed ellipticities, both align tangentially around the foreground mass as expected.
 
 Instead of comparing the ray-traced and \texttt{Pangloss} predicted ellipticities for individual galaxies, the lensing is characterized globally with correlation functions.
-As described in section \ref{corr_functions}, the ellipticity-ellipticity correlation function measures how correlated the ellipticities of pairs of galaxies are as a function of separation distance, while the galaxy-mass correlation function measures the correlation of lensed ellipticities around foreground halos as a function of separation distance.
+As described in section \ref{corr_functions}, the $\varepsilon$-$\varepsilon$ correlation function measures how correlated the ellipticities of pairs of galaxies are as a function of separation distance, while the galaxy-mass correlation function measures the correlation of lensed ellipticities around foreground halos as a function of separation distance.
 Both correlation functions are used in this work to estimate how well the \texttt{Pangloss} framework models weak lensing by dark matter structures and are computed using the publicly available \texttt{TreeCorr} module written by Mike Jarvis\footnote{https://github.com/rmjarvis/TreeCorr}.
-Note that the ellipticity-ellipticity correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition \cite{jarvis} and the more common Schneider definition \cite{schneider}, see Appendix \ref{corr_defs}.
-
-%%------------------------------------------------------------------------------------------------------------------------------------------
-%% Two or Three subplots of foreground/background/shear/kappa maps
-% \begin{figure*}
-%     \centering
-%     % Volume
-%     \begin{subfigure}[H]{0.415\textwidth}
-%         \includegraphics[width=\textwidth]{figs-swe/thesis/vol_densities.png}
-%         \captionsetup{justification=raggedright,singlelinecheck=false}
-%         \caption{CAPTION}
-%         \label{fig:volume_densities}
-%     \end{subfigure}
-%     ~
-%     % Surface
-%     \begin{subfigure}[H]{0.425\textwidth}
-%         \includegraphics[width=\textwidth]{figs-swe/thesis/surf_densities.png}
-%         \captionsetup{justification=raggedright,singlelinecheck=false}
-%         \caption{CAPTION}
-%         \label{fig:surface_densities}
-%     \end{subfigure}
-%     \caption{}
-%     \label{fig:subplots}
-% \end{figure*}
+Note that the $\varepsilon$-$\varepsilon$ correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition \cite{jarvis} and the more common Schneider definition \cite{schneider}, see Appendix \ref{corr_defs}.
+
+%%------------------------------------------------------------------------------------------------------------------------------------------
+%% Lensing of a few background sources
+\begin{figure*}
+    \centering
+    % Convergence / shear map, background source ellipticities
+    \begin{subfigure}[H]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/thesis/field2.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{The ray-traced convergence and shear in a 1.44 arcmin$^2$ field of the Millennium Simulation, as calculated from \cite{ray_tracing}.
+The convergence, plotted in inverse greyscale, is proportional to the projected mass density and representes foreground mass.
+The shear field is plotted as sparsely-sampled sticks that have size proportional to their magnitude.
+A few of the generated background sources are plotted as blue ellipticitiy sticks with length proportional to their eccentricities.}
+        \label{fig:field2}
+    \end{subfigure}
+     ~
+    % Lensed ellipticities
+    \begin{subfigure}[H]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/thesis/field3.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{The same 1.44 arcmin$^2$ field as \ref{fig:field2}, but now with the `true' lensed ellipticities in green, the halo model predicted lensed ellipticities in purple, and a few of the most massive foreground halos plotted as orange circles.
+Lensed ellipticity predictions tend to be more accurate further from the lensing mass, with significant differences near the centers of massive objects.
+All are sheared tangentially around the massive structures as expected.}
+        \label{fig:field3}
+    \end{subfigure}
+    \caption{}
+    \label{field}
+\end{figure*}
 %%------------------------------------------------------------------------------------------------------------------------------------------
@@
 The cross-component of the correlation function shows no significant deviation from zero as expected, as gravitational lensing only shears galaxies tangentially.
-For the $\xi_+$ component, the ray-traced (plotted in green) and halo model (plotted in purple) are in relative agreement from seperation scales of 0.1 to 0.2 arcminutes, but there is a systematic underprediction of correlation by the halo model on scales larger than 0.2 arcminutes by an average of 31\%.
+For the $\xi_+$ component, the ray-traced (plotted in green) and halo model (plotted in purple) are in relative agreement from seperation scales of 0.1 to 0.2 arcminutes, but there is a systematic underprediction of correlation by the halo model on scales larger than 0.2 arcminutes by an average of 31\% percent error.
 This result is consistent with Pace et al.
@@
 While particular foreground objects are almost always predicted, the currently implemented halo model over-predicts the convergence throughout most of the field; the halo model does not appear to accurately account for the voids between foreground masses and over-predicts the mass of most foreground objects.
-This could be a result of incorrect halo profiles, a too-simplistic implementation of the smooth-component correction, missing features in the halo model, a significant amount of dark matter mass not being correlated with galaxies, or some combination of all four possibilities..
+This could be a result of incorrect halo profiles, a too-simplistic implementation of the smooth-component correction, missing features in the halo model, a significant amount of dark matter mass not being correlated with galaxies, or some combination of all four possibilities.
 
@@
 
-I implemented the methodology in section \ref{pangloss} to make weakly lensed ellipticity predictions for 20 mock catalogs of $N$ background sources ranging from $N=10^2$ to $N=10^6$.
+I implemented the methodology in section \ref{pangloss} to make weakly lensed ellipticity predictions for 20 mock catalogs of $N$ background sources with lightcone radii of $R_L=4$ arcminutes for $N$ ranging from $N=10^2$ to $N=10^6$.
 The mean CPU times for a single likelihood calulation and ABC rejection decision as a function of $N$ is shown in Figure \ref{fig:mle_vs_abc}.
 The two methods take approximately the same amount of time up to $N=10^3$ sources, but the correlation function quickly becomes far too computationally inefficient at $N$ values above $10^4$.
-While further analysis is needed to determine whether more or less ABC samples are required than posterior samples from MLE, this result, as well as the limitation that ABC is fundamentally an approximation of the posterior,
-suggests that any future inference work will likely use MLE instead of ABC.
+While further analysis is needed to determine whether more or less ABC samples are required than posterior samples from MLE, this result, as well as the limitation that ABC is fundamentally an approximation of the posterior, suggests that any future inference work will likely use MLE instead of ABC.
 However, the time spent for either inference method is quite small in comparison to the CPU time required to create lightcones and make the line-of-sight lensing predictions.
@@
 \texttt{Pangloss} currently removes any sources with total reduced shear $g$ greater than 0.5, but this potentially leaves sources that are not entierly described by weak lensing.
-Correctly modeling line-of-sight strong lensing will require analyzing the convergence and shear contributions of BMO halos in the strong lening regime and at the interface between strong and weak lensing.\\
-
-(Mention something about kappamaps)
+Correctly modeling line-of-sight strong lensing will require analyzing the convergence and shear contributions of BMO halos in the strong lening regime and at the interface between strong and weak lensing.
 
@@
 The breakdown of CPU time spent on various components of the lensing calculation in Section \ref{comp_perform} indicates that (1) the smooth-component correction needs to be implemented \textit{far} quicker as it is responsible for on average 62.1\% of the total runtime and (2) the current use of \texttt{Astropy} tables for data storage is not practical for fields much larger than 1,000 arcmin$^2$ or with lightcone radii larger than 8 arcminutes.
-Possible solutions to (1) are to experiment with faster numerical integrators or, more importantly, ???.
-The second issue suggests that \texttt{Pangloss} should store catalog data in databases rather than \texttt{Astropy} tables as databases are designed for rapid retrieval, modification, and deletion of data \cite{databases}.
+Possible solutions to (1) are to experiment with faster numerical integrators or use a lookup table for appropriate parts of the calculation, while the second issue suggests that \texttt{Pangloss} should store catalog data in databases rather than \texttt{Astropy} tables as databases are designed for rapid retrieval, modification, and deletion of data \cite{databases}.
 While this will require significant reworking of the framework to implement, the CPU distribution indicates that such a change is necessary for even a moderate scale up.
@@
         \caption{The distribution of correlation pairs from the source ellipticities in Figure \ref{color_corr_unlensed}.
-If the pair of galaxies are in the same color bin, then the correlation scatter point is colored in the same scheme.}
+Pairs of galaxies in the same color bin are plotted in the correlation scatter using the same color scheme.}
         \label{corr_dist_unlensed}
@@
         \caption{The distribution of correlation pairs from the source ellipticities in Figure \ref{color_corr_lensed}.
-If the pair of galaxies are in the same color bin, then the correlation scatter point is colored in the same scheme.}
+Unlike Figure \ref{corr_dist_unlensed}, there is now a non-zero signal in the correlation distribution.}
         \label{corr_dist_lensed}
@@
     \vspace{-.05in}
-    \caption{Correlation visualization for...}
+    \caption{$\varepsilon$-$\varepsilon$ correlation function visualization.}
     % \label{colored_corr_lensed}

### 2016-06-06 doc/thesis_swe.tex
Thesis revisions! #98

@@
 The lensed source ellipticities are characterized by the ellipticity-ellipticity and galaxy-mass correlation functions and compared to the same statistic using the `true' ray-traced ellipticities.
-In the ellipticity-ellipticity correlation function, I find that the halo model systematically underpredicts the correlation on scales above 0.2 arcminutes by a mean NRMSE of 0.22, although this can be decreased by including more halo contributions.
-The model predicted galaxy-mass correlation function is in agreement with the ray-traced statistic on scales from 0.2 to 2 arcminutes but overpredicts the correlation on scales below 0.2 arcminutes due to strong lensing effects with a mean NRMSE of 0.36.
+In the ellipticity-ellipticity correlation function, I find that the halo model systematically underpredicts the correlation on scales above 0.2 arcminutes by a mean NRMSE of 0.22 using an average of 4836 halos per lensing prediction, although this can be decreased by including more halo contributions.
+The model predicted galaxy-mass correlation function is in agreement with the ray-traced statistic on scales from 0.2 to 2 arcminutes but overpredicts the correlation on scales below 0.2 arcminutes by a mean NRMSE of 0.36 due to strong lensing effects.
 Both best-case statistics were found to be well approximated by using only the most `relevant' halos, which on average only needed the 300 and 70 most relevant halos to predict the correlation functions with a NRMSE below 5\% and 10\% respectively.
 The feasibility of using the halo model to infer hyperparameters of the Millennium Simulation with either maximum likelihood estimation or approximate Bayesian computation is explored, with preliminary results favoring likelihood estimation.
-Optimization of the framework code has reduced the mean CPU time per lensing prediction by 59\% to $57\pm8$ ms, although this is approximately two orders of magnitude slower than required for a planned scale-up to a 100 arcmin$^2$ field.
+Optimization of the framework code has reduced the mean CPU time per lensing prediction by 59\% to $57\pm8$ ms, although this is approximately two orders of magnitude slower than required for a planned scale-up to a 100 deg$^2$ field.
 Physical and computational limitations of the framework are discussed as well as potential improvements for future work.
@@
 However, as Tyson et al.
-postulated in \cite{tyson_postulate} and confirmed in \cite{tyson_confirm}, background sources are also `weakly' lensed by lesser foreground mass nearby the line of sight by what is now called galaxy-galaxy lensing.
-As the shape of most galaxies is only distorted by a few percent and the instrinsic shape is not known, it must be must be detected statistically using a large number of sources.
+postulated in \cite{tyson_postulate} and confirmed in \cite{tyson_confirm}, background sources are also `weakly' lensed by lesser foreground mass nearby the line of sight (LOS) by what is now called galaxy-galaxy lensing.
+As the shape of most galaxies is only distorted by a few percent, and the instrinsic shape is not known, weak lensing must be detected statistically using a large number of sources.
 
@@
 Numerous N-body simulations have predicted dark matter structure to have evolved from overdense regions in the early universe into `halos' of virialized matter that eventually collapsed from self-gravity \cite{halo_formation}, where galaxies could then form in the large gravitational potentials of the halos.
-However, there is still extensive reserach being done on the correct density profile of the halos (isothermal spheres \cite{isothermal_spheres}, NFW \cite{nfw}, BMO \cite{nfw_bmo}, Einasto \cite{einasto}), identifying the stellar mass - halo mass relation \cite{smhr}, abundance matching \cite{abundance_matching}, halo substructure \cite{halo_substructure}, and the lensing by line-of-sight halos \cite{collett} and by dark matter structures not associated with galaxies \cite{mccully}.
+However, there is still extensive reserach being done on the correct density profile of the halos (isothermal spheres \cite{isothermal_spheres}, NFW \cite{nfw}, BMO \cite{nfw_bmo}, Einasto \cite{einasto}), identifying the stellar mass - halo mass relation \cite{smhr}, abundance matching \cite{abundance_matching}, halo substructure \cite{halo_substructure}, and the lensing by LOS halos \cite{collett} and by dark matter structures not associated with galaxies \cite{mccully}.
 If a model for the distribution of dark matter in a region of foreground mass can accurately predict the statistical signal of the weak lensing of background sources, then the model can be used on galaxies in existing sky survey data to extrapolate the amount of dark matter in the region and construct large-scale maps of the dark matter in the universe.
@@
 \begin{itemize}
-\item Under the best possible circumstances of having noiseless redshifts and halo masses, how accurately can I reconstruct line-of-sight dark matter mass structures using a halo model?
+\item Under the best possible circumstances of having noiseless redshifts and halo masses, how accurately can I reconstruct LOS dark matter mass structures using a halo model?
 \item How many halos are needed to make these predictions?
@@
 A brief introduction to the halo model, the effects of strong and weak gravitational lensing, representing galaxy ellipticities, and cosmological correlation functions is discussed in Section \ref{background}.
-The implementation of the \texttt{Pangloss} framework to make line of sight lensing predictions in the Millennium Simulation is described in Section \ref{pangloss}, and the results of the framework on 1440 galaxies on a field size of 144 arcmin$^2$, along with a comparison of the predicted lensed ellipticities to ray-traced ellipticities, is given in Section \ref{check}.
+The implementation of the \texttt{Pangloss} framework to make LOS lensing predictions in the Millennium Simulation is described in Section \ref{pangloss}, and the results of the framework on 1440 galaxies on a field size of 144 arcmin$^2$, along with a comparison of the predicted lensed ellipticities to ray-traced ellipticities, is given in Section \ref{check}.
 Section \ref{feasibility} explores the feasibility of using the presented \texttt{Pangloss} framework to make parameter inferences using all available halo data either by likelihood estimation or approximate Bayesian computation.
@@
 
-Before describing the developed model for line-of-sight dark matter mass map reconstructions from weak lensing measurements, I briefely review a few topics in astronomy and cosmology that are relevant for this thesis such as the dark matter halo model, gravitational lensing, and correlation functions.
+Before describing the developed model for LOS dark matter mass map reconstructions from weak lensing measurements, I briefely review a few topics in astronomy and cosmology that are relevant for this thesis such as the dark matter halo model, gravitational lensing, and correlation functions.
 
@@
 \noindent where the constant $\rho_0$ and the scale radius $R_s$ are parameters that vary from halo to halo \cite{nfw}.
-However, the NFW profile is not entierly physical as the total mass diverges as the desntiy is integrated out to an infinite radius.
-Instead this work uses a truncated NFW profile called the Baltz-Marshall-Oguri (BMO) profile given by
+However, the NFW profile is not entierly physical as the total mass diverges as the density is integrated out to an infinite radius.
+Instead, this work uses a truncated NFW profile called the Baltz-Marshall-Oguri (BMO) profile given by
 \begin{equation}\label{bmo_profile}
@@
 %%------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Filaments, Voids, and the Smooth-Component Correction}\label{scc}
+\subsection{Filaments, Voids, and the Smooth Component Correction}\label{scc}
 
@@
 
-Using the fluid equation and equation of state (Cite), we can show that the energy density of non-relativistic matter $\varepsilon_m(z)$ evolves as
+Using the fluid equation and equation of state \cite{modern_cosmology}, we can show that the energy density of non-relativistic matter $\varepsilon_m(z)$ evolves as
 \begin{equation}\label{energy_evol}
-\varepsilon_m(z)=\frac{\varepsilon_{m,0}}{a(z)^3}=\varepsilon_{m,0}(1+z)^3
+\varepsilon_m(z)=\frac{\varepsilon_{m,0}}{a(z)^3}=\varepsilon_{m,0}(1+z)^3,
 \end{equation}
@@
 \begin{equation}\label{}
-\Omega_{m,0}=\frac{\rho_{m,0}}{\rho_{c,0}}=\frac{8\pi G}{3H_0^2}\,\rho_{m,0}
+\Omega_{m,0}=\frac{\rho_{m,0}}{\rho_{c,0}}=\frac{8\pi G}{3H_0^2}\,\rho_{m,0},
 \end{equation}
@@
 However, one must be careful to (1) use proper distances, (2) account for the possibility of a curved universe, and (3) use the correct distance measure for $r$ (in this case, the angular diameter distance).
-From this one can infer that the proper volume element must have the form of
+From this we that the proper volume element must have the form of
 \begin{equation}\label{proper_element}
@@
 
-\noindent where $d_H=c/H_0$ is the Hubble distance, $\Omega_k$ is the curvature parameter ($\Omega_k=0$ for a flat universe), and $d_C(z)$ is the line-of-sight comoving distance given by
+\noindent where $d_H=c/H_0$ is the Hubble distance, $\Omega_k$ is the curvature parameter ($\Omega_k=0$ for a flat universe), and $d_C(z)$ is the LOS comoving distance given by
 \begin{equation}\label{comoving_distance}
@@
 %%------------------------------------------------------------------------------------------------------------------------------------------
-%% Ellipticity Orientation Figure
 \begin{figure*}
     \centering
-    \begin{subfigure}[H]{0.415\textwidth}
-        \includegraphics[width=\textwidth]{figs-swe/thesis/ellipse_orientations.png}
-        \captionsetup{justification=raggedright,singlelinecheck=false}
-        \caption{The shape of a galaxy image for various ellipticity components $\varepsilon_1$ and $\varepsilon_2$ on the $x$ and $y$-axes respectively. Taken from \cite{schneider}.}
-        \label{ellipses}
-    \end{subfigure}
-    ~
     %% Einstein Ring Figure
@@
         \label{einstein_ring}
+    \end{subfigure}
+    ~
+    %% Ellipticity Orientation Figure
+    \begin{subfigure}[H]{0.415\textwidth}
+        \includegraphics[width=\textwidth]{figs-swe/thesis/ellipse_orientations.png}
+        \captionsetup{justification=raggedright,singlelinecheck=false}
+        \caption{The shape of a galaxy image for various ellipticity components $\varepsilon_1$ and $\varepsilon_2$ on the $x$ and $y$-axes respectively. Taken from \cite{schneider}.}
+        \label{ellipses}
     \end{subfigure}
@@
 A full mathematical treatment of the gravitational lensing of galaxies due to the gravitational fields of massive objects requires general relativity (see \cite{modern_cosmology} for details).
-However, the important results can be summarized as follows.
-Foreground mass distorts the image of a background galaxy in two distinct ways: The image is magnified and sheared tangentially about the foreground mass making it more elliptical.
+However, the important results can be summarized as follows: Foreground mass distorts the image of a background galaxy in two distinct ways; the image is magnified and sheared tangentially about the foreground mass making it more elliptical.
 The magnification of the image is determined by the convergence $\kappa$ defined as
@@
 
-While strong lenses are rare, as the alignment of the source and foreground mass must be nearly perfect, \textit{all} sources are weakly lensed when traveling through foreground halos.
+While strong lenses are rare as the alignment of the source and foreground mass must be nearly perfect, \textit{all} sources are weakly lensed when traveling through foreground halos.
 The effect is small, usually an ellipticity distortion of only a few percent, but can be detected locally by averaging the ellipticities of all sources in a small region.
@@
 
- \noindent Finally as in the weak lensing regime ${\kappa\ll1}$ and ${|\gamma|\ll1}$, it follows that
+ \noindent Finally, as in the weak lensing regime ${\kappa\ll1}$ and ${|\gamma|\ll1}$, it follows that
  \begin{equation}
@@
 
- The analytical form of the convergence and shear contribution from a BMO-profile is quite messy, but is derived and explained in detail in \cite{nfw_bmo}.
+ The analytical form of the convergence and shear contribution from a BMO-profile halo is quite messy, but is derived and explained in detail in \cite{nfw_bmo}.
 Calculating the lensing contribution of the smooth-component correction is much simpler; the projected surface mass density at at given redshift is found by integrating $\rho_s(z)$ over a sufficiently small $dz$ interval, and then the mass sheet's convergence is found using Equation \eqref{convergence}.
@@
 If all galaxies were spherical then the measurement of their ellipticities would give an exact description of the lensing done by foreground mass structures.
-Unfortunately, the intrinsic ellipticities of background galaxies contribute significant noise as we do not know how any individual galaxy ellipticity has been altered by lensing.
+Unfortunately, the intrinsic ellipticities of background galaxies contribute significant noise as we do not know how any individual galaxy ellipticity has been altered by weak lensing.
 However as two sources lensed by the same foreground mass will have their ellipticities distorted in a similar way, their lensed ellipticities should be correlated regardless of intrinsic orientation.
@@
 \xi_\pm(\Delta\theta)&=\left<\varepsilon_{i_t}(\vec{\theta})\,\varepsilon_{j_t}(\vec{\theta}+\vec{\Delta\theta})\right>\nonumber \\
-&\pm\left<\varepsilon_{i_\times}(\vec{\theta})\,\varepsilon_{j_\times}(\vec{\theta}+\vec{\Delta\theta})\right>\\
+&\pm\left<\varepsilon_{i_\times}(\vec{\theta})\,\varepsilon_{j_\times}(\vec{\theta}+\vec{\Delta\theta})\right>,\\
 \xi_\times(\vec{\Delta\theta})&=\left<\varepsilon_{i_t}(\vec{\theta})\,\varepsilon_{j_\times}(\vec{\theta}+\vec{\Delta\theta})\right>
@@
 As galaxies will only be lensed by the same foreground mass at relatively small separation distances, the $\varepsilon$-$\varepsilon$ correlation function decreases sharply as the separation increases.
-If the distribution of intrinsic galaxy ellipticities is indeed random, then their $\varepsilon$-$\varepsilon$ correlation function should vanish across all separation scales.
+%If the distribution of intrinsic galaxy ellipticities is indeed random, then their $\varepsilon$-$\varepsilon$ correlation function should vanish across all separation scales.
 
@@
     \captionsetup{justification=raggedright,singlelinecheck=false}
-    \caption{A cartoon model of how the \texttt{Pangloss} framework uses a dark matter halo model to reconstruct the foreground mass along the line of sight of a background source galaxy.
+    \caption{A cartoon model of how the \texttt{Pangloss} framework uses a dark matter halo model to reconstruct the foreground mass along the LOS of a background source galaxy.
 A `lightcone' centered at a background source is constructed with radius $R_L$ and populated with all foreground galaxies contained in this volume.
-Each foreground object has an attached dark matter halo and physical distance to the line of sight (dashed line).
-The shear and convergence along the line of sight contributed by each halo is calculated using \cite{lensing_calc}, and the predicted ellipticity is determined using the sum of these contributions and Equation \eqref{lensing}.}
+Each foreground object has an attached dark matter halo and physical distance to the LOS (dashed line).
+The shear and convergence along the LOS contributed by each halo is calculated using \cite{lensing_calc}, and the predicted ellipticity is determined using the sum of these contributions and Equation \eqref{lensing}.}
     \label{pangloss_cartoon}
@@
 To infer foreground dark matter mass structures using weak gravitational lensing, first a model of the relationship between foreground galaxies and dark matter must be established and robustly tested to see if, statistically, it makes the same lensing predictions of background sources as the true underlying dark matter structure.
-To do this, I built upon the publicly available \texttt{Pangloss}\footnote{\label{note1}https://github.com/drphilmarshall/Pangloss} framework used in Collett et al.
-(\cite{collett}) to reconstruct all the
+To do this, I built upon the publicly available \texttt{Pangloss}\footnote{\label{note1}https://github.com/drphilmarshall/Pangloss} framework used by Collett et al.
+in \cite{collett} to reconstruct all the
 mass along the lines of sight of generated background galaxies in the Millennium Simulation using a halo model with smooth-component correction.
@@
 From the work of Hilbert et al.
-\cite{ray_tracing}, high resolution maps of the ray-traced shear and convergence of galaxy sources at $z=1.3857$ are publicly available.
+in \cite{ray_tracing}, high resolution maps of the ray-traced shear and convergence of galaxy sources at $z=1.3857$ are publicly available.
 From these maps, an estimate of the `true' lensing of background galaxy ellipticities when traveling through the foreground mass of the Millennium Simulation can be calculated using Equation \eqref{lensing}.
@@
 While ideally all foreground mass in a field would be considered when predicting the weak lensing of a background galaxy, it is computationally prohibitive to do so.
-Instead, all foreground halos contained within a `lightcone' centered along the line of sight to the source and extending out to a chosen lightcone radius $R_L$ were considered when calculating the lensing contributions for the background source.
+Instead, all foreground halos contained within a `lightcone' centered along the LOS to the source and extending out to a chosen lightcone radius $R_L$ were considered when calculating the lensing contributions for the background source.
 A cartoon model of this process is shown in Figure \ref{pangloss_cartoon}.
@@
 
-To calculate the convergence and shear contribution of each halo, the physical distance from the halo to the line of sight was needed.
+To calculate the convergence and shear contribution of each halo, the physical distance from the halo to the LOS was needed.
 To increase the speed of distance calculations, the foreground halo redshifts were first binned to a grid of 100 equally-sized redshift bins $\Delta z=0.013857$ from $z=0$ to the sourced redshift of $z=1.3857$, and then converted to physical distances using the cosmology defined by the Millennium Simulation.
@@
 Not all foreground halos are equally relevant to the lensing calculation.
-To add a significant contribution to the combined shear and convergence, a halo must be massive, close to the line of sight, or preferably both.
+To add a significant contribution to the combined shear and convergence, a halo must be massive, close to the LOS, or preferably both.
 McCully et al.
-in \cite{mccully} derived that the correct metric for determining the relevance of a given foreground halo to the overall lensing calculation to be given by
+in \cite{mccully} derived that the correct metric for determining the relevance of a given foreground halo to the overall lensing calculation is given by
 \begin{equation}\label{relevant}
@@
 
-\noindent where $M_h$ is the halo mass and $R$ is the distance from the halo to the line of sight.
-Numerical values are assigned by comparing a halo's individual $M_h$ and $R$ to a threshold $M_T$ and $R_T$:
+\noindent where $M_h$ is the halo mass and $R$ is the distance from the halo to the LOS. Numerical values are assigned by comparing a halo's individual $M_h$ and $R$ to a threshold $M_T$ and $R_T$:
 \begin{equation}\label{relevant_thresh}
@@
 In this work, the threshold values used are ${M_T=10^{12}M_\odot}$ and ${R_T=10}$ kpc.
-The relevance distribution for one background catalog realization with 1440 foreground halos in a lightcone of radius 6 arcminutes is shown in Figure \ref{fig:rel_dist} As expected, there are very few massive halos along the line of sight and therefore only a small percentage of foreground halos should have a high relative contribution to the predicted lensing quantities.
-This encouraged the intended analysis on lightcones with all halos and those with only a small subset of the most relevant halos to compare the results and see if the computational time saved by using only the most relevant halos was worth the loss in prediction accuracy.
+The relevance distribution for one background catalog realization of 1440 sources with ${4836\pm104}$ foreground halos per lightcone with radii of 6 arcminutes is shown in Figure \ref{fig:rel_dist}.
+As expected, there are very few massive halos along the LOS and therefore only a small percentage of foreground halos should have a high relative contribution to the predicted lensing quantities.
+This encouraged the intended analysis to be done on lightcones with all halos and those with only a small subset of the most relevant halos to compare the results and see if the computational time saved by using only the most relevant halos was worth the loss in prediction accuracy.
 
@@
     \captionsetup{justification=raggedright,singlelinecheck=false}
-    \caption{The mean number of relevant galaxies in a single realization of 1440 source galaxies determined by Equation \eqref{relevant_thresh} with a threshold mass and distance of ${M_T=10^{12}M_\odot}$ and ${R_T=10}$ kpc respectively.
+    \caption{The mean number of relevant halos in a single realization of 1440 source galaxies, each with ${4836\pm104}$ halos per lightcone, determined by Equation \eqref{relevant_thresh} with a threshold mass and distance of ${M_T=10^{12}M_\odot}$ and ${R_T=10}$ kpc respectively.
 The errorbars correspond to the standard deviation of relevant halos accross all lightcones.
-As expected, most halos are either too far away from the line-of-sight or not massive enough to make a significant contribution, or both.
-The number of halos falls logarithmically with the relevance limit and reaches a mean of one halo at a relevance of ${10^{-2}M_\odot\,\text{Mpc}^3}$.}
+As expected, most halos are either too far away from the LOS or not massive enough to make a significant contribution, or both.
+The number of halos falls logarithmically with the relevance limit and reaches a mean of one halo at a relevance of ${10^{-2}M_\odot/\text{Mpc}^3}$.}
     \label{fig:rel_dist}
@@
 The corrected total convergence for a given background source is simply the sum of the halo contributions and the smooth-component contributions.
-There is no additional shear produced by a uniform sheet of mass (citation!), but the corrected reduced shear is now calculated using the corrected total $\kappa$ in Equation \eqref{reduced_shear}.
+There is no additional shear produced by a uniform sheet of mass \cite{mass_degeneracy}, but the corrected reduced shear is now calculated using the corrected total $\kappa$ in Equation \eqref{reduced_shear}.
 A diagram of this process is shown in Figure \ref{fig:scc}.
 
-The volume and projected surface mass densities of each redshift slice are shown in Figures \ref{fig:volume_densities} and \ref{fig:surface_densities} respectively.
-In each plot, the halo density at each redshift slice is plotted in green, the smooth-component density in blue, and universe mean density in black, and a histogram of the galaxies per bin is shown in the background.
+The volume and projected surface mass densities of each redshift slice for the same source realization as Figure \ref{fig:rel_dist} are shown in Figures \ref{fig:volume_densities} and \ref{fig:surface_densities} respectively.
+In each plot, the halo density at each redshift slice is plotted in green, the smooth-component density in blue, and universe mean density in black, as well as a histogram of the galaxies per bin in the background.
 In most redshift bins, the halo density is one to two orders of magnitude lower than than the universe mean density leading to a smooth-component density very close to that of the mean density.
 However, all mass densities are far below the critial density, plotted in red, and so well within the weak-lensing regime.
-The convergence distribution of each halo and 100 smooth-components is plotted in Figure \ref{fig:kappa_dist}.
+The convergence distribution of each halo and the 100 smooth-components is plotted in Figure \ref{fig:kappa_dist}.
 % This seems to be in opposition to Pace et al. in \cite{pace}, which found that halos constituted ??\% of simulation mass in ??.
@@
     \captionsetup{justification=raggedright,singlelinecheck=false}
-    \caption{The convergence distribution of the 4838 individual halos, plotted in green, and the 100 smooth-component slices, plotted in blue, contained in the same lightcone as Figure \ref{densities}.
+    \caption{The convergence distribution of the 4836 individual halos, plotted in green, and the 100 smooth-component slices, plotted in blue, contained in the same lightcone as Figure \ref{densities}.
 The mass sheets have a higher convergence contribution than all but the most relevant halos in the lightcone.
@@
 
-Using the physical separation distance and halo mass, the shear and convergence contribution of a single foreground halo is calculated using methods described in Section \ref{grav_lensing} (see \cite{lensing_calc} and \cite{nfw_bmo} for more details).
+Using the halo mass and physical separation distance to the LOS, the shear and convergence contribution of a single foreground halo with BMO profile is calculated using methods described in Section \ref{grav_lensing} (see \cite{nfw_bmo} and \cite{lensing_calc} for more details).
 The total convergence and shear along the LOS of the lightcone is simply the sum of the convergence and shear contributions of each halo contained in the lightcone, as well as the additional convergence terms from the smooth-component correction.
@@
     \captionsetup{justification=raggedright,singlelinecheck=false}
-    \caption{Four different views of a lightcone centered on the line-of-sight of a particular background source.
-The top left figure plots the positions of the halos with the size proportional to their galaxy brightness in the $i$-band, the center figure plots the angular size of foreground halos with red and blue regions representing the NFW scale radius and virial radius of each halo respectively, the top right figure plots the $\kappa$ contributions of each halo, and the bottom plots the positions of each halo along the redshift axis with size proportional to halo mass.}
+    \caption{Four different views of a lightcone centered on the LOS of a particular background source.
+The top left figure plots the positions of the halos with the size proportional to their galaxy brightness in the $i$-band, the center figure plots the angular size of foreground halos with red and blue regions representing the NFW scale radius and virial radius of each halo respectively, the top right figure plots the $\kappa$ contributions of each halo, and the bottom plots the positions of each halo along the redshift axis with size proportional to $\kappa$ contribution.}
     \label{fig:lightcone}
@@
 
-Using the presented methodology, 1440 background galaxies in a 144 arcmin$^2$ subset of the (0,0,0,0) Millennium Simulation foreground catalog were generated and lensed by both the ray-traced shear and convergence maps as well as the \texttt{Pangloss} framework.
+Using the methodology presented in Section \ref{pangloss}, 1440 background galaxies in a 144 arcmin$^2$ subset of the (0,0,0,0) Millennium Simulation foreground catalog were generated and lensed by both the ray-traced shear and convergence maps as well as the \texttt{Pangloss} framework.
 With a lightcone radius of 6 arcminutes, the lightcones contained an average of ${4836\pm104}$ foreground halos.
@@
 Figure \ref{fig:lightcone} displays different views an example lightcone where the foreground halos are plotted as circles whose size are proportional to their galaxy brightness (top left), angular size (top center), \texttt{Pangloss} predicted convergence contributions (top right), and halo mass (bottom).
-Comparing the center and top right figures demonstrates the importance of proximity to the line-of-sight for significant $\kappa$ contributions.
-Figure \ref{fig:field2} shows a foreground cluster in a 1.44 arcmin$^2$ section of the Millennium Simulation along with the ray-traced convergence (plotted in inverse greyscale) and shear maps (plotted as red ellipticity sticks) from \cite{ray_tracing}.
+Comparing the center and top right figures demonstrates the importance of proximity to the LOS for significant $\kappa$ contributions.
+Figure \ref{fig:field2} shows a foreground cluster in a 1.44 arcmin$^2$ section of the Millennium Simulation along with the ray-traced convergence (plotted in inverse greyscale) and shear maps (plotted as red shear sticks) from \cite{ray_tracing}.
 Figure \ref{fig:field3} displays the generated background ellipticities in blue, the `true' lensed ellipticities in green, and the halo model lensed ellipticities in purple.
@@
 The convergence, plotted in inverse greyscale, is proportional to the projected mass density and representes foreground mass.
-The shear field is plotted as sparsely-sampled sticks that have size proportional to their magnitude.
+The shear field is plotted as sparsely-sampled red sticks that have size proportional to their magnitude.
 A few of the generated background sources are plotted as blue ellipticitiy sticks with length proportional to their eccentricities.}
@@
 
-The first test of the halo model was with the $\varepsilon$-$\varepsilon$ correlation function with a lightcone radius of 6 arcminutes and all halos which is given in Figure \ref{fig:gg_corr}.
+The first test of the halo model was with the $\varepsilon$-$\varepsilon$ correlation function with a lightcone radius of 6 arcminutes and all $4836\pm104$ halos per lightcone which is given in Figure \ref{fig:gg_corr}.
 The statistic measured the average correlation between pairs of ellipticities at separation distances between 0.1 and 2 arcminutes.
-The cross-component of the correlation function shows no significant deviation from zero as expected, as gravitational lensing only shears galaxies tangentially.
-For the $\xi_+$ component, the ray-traced (plotted in green) and halo model (plotted in purple) are in relative agreement from seperation scales of 0.1 to 0.2 arcminutes, but there is a systematic underprediction of correlation by the halo model on scales larger than 0.2 arcminutes by an average of 31\% percent error.
+The cross-component of the correlation function $\xi_\times$ shows no significant deviation from zero as expected, as gravitational lensing only shears galaxies tangentially.
+For the $\xi_+$ component, the ray-traced (plotted in green) and halo model (plotted in purple) are in relative agreement from seperation scales of 0.1 to 0.2 arcminutes, but there is a systematic underprediction of correlation by the halo model on scales larger than 0.2 arcminutes by an average 31\% percent error.
 This result is consistent with Pace et al.
@@
 
-Using the same catalog of background sources, this statistic was recalculated for the halo model ellipticities for various lightcone radii ranging from $R_L=1$ to $R_L=8$ arcminutes.
+Using the same catalog of background sources, this statistic was recalculated for the halo model using various lightcone radii ranging from $R_L=1$ to $R_L=8$ arcminutes.
 The result is shown in Figure \ref{fig:gg_corr_series}, where the series of model predicted correlation functions is compared to the ray-traced correlation function.
@@
 
-The catalog of lensed ellipticities was also analyzed using the galaxy-mass correlation function with separation distances from 0.1 to 2 arcminutes and a lightcone radius of 6 arcminutes and all halo.
+The catalog of lensed ellipticities was also analyzed using the galaxy-mass correlation function with separation distances from 0.1 to 2 arcminutes using the same lightcones and halo number.
 The result is shown in Figure \ref{fig:ng_corr}.
@@
 
-The galaxy-mass correlation function was similarly re-calculated at increasing lightcone radii from $R=1$ to $R=8$ arcminutes with the result in Figure \ref{fig:ng_corr_series} As with the $\varepsilon$-$\varepsilon$ correlation, structure larger than $\sim$1 arcminute is captured much better by increasingly large lightcone radii as expected.
+The galaxy-mass correlation function was similarly re-calculated at increasing lightcone radii from $R=1$ to $R=8$ arcminutes with the result in Figure \ref{fig:ng_corr_series}.
+As with the $\varepsilon$-$\varepsilon$ correlation, structure larger than $\sim$1 arcminute is captured much better by increasingly large lightcone radii as expected.
 However, there is little to no improvement of the galaxy-mass correlation on scales smaller than 0.3 arcminutes which futher points to the need to model strong lensing.
@@
 
-Of intrinsic interest is the relative number of relevant halos needed in each lightcone to accurately predict the halo correlation functions in Figures \ref{fig:gg_corr} and \ref{fig:ng_corr} as a low percentage would allow much faster lensing predictions.
-Figures \ref{fig:rel_gg_compare} and \ref{fig:rel_ng_compare} display an example $\varepsilon$-$\varepsilon$ and galaxy-mass correlation function comparison of the halo model using all halos (plotted in purple) and halo model using halos above the relevance limit of ${10^{-5} M_{\odot}/\text{Mpc}^3}$ (plotted in blue) with $R_L=6$ arcminutes, as well as the percent error of each predicted value between the two implementations.
+Of intrinsic interest is the relative number of relevant halos needed in each lightcone to accurately predict the halo correlation functions in Figures \ref{fig:gg_corr} and \ref{fig:ng_corr}, as a low percentage would allow much faster lensing predictions.
+Figures \ref{fig:rel_gg_compare} and \ref{fig:rel_ng_compare} display an example $\varepsilon$-$\varepsilon$ and galaxy-mass correlation function comparison of the halo model using all halos (plotted in purple) and using only halos above the relevance limit of ${10^{-5} M_{\odot}/\text{Mpc}^3}$ (plotted in blue) with $R_L=6$ arcminutes, as well as the percent error of each predicted value between the two implementations.
 This relevance limit corresponded to $66\pm10$ relevant halos per lightcone and resulted in a normalized root-mean-square error (NRMSE) of 0.164 and 0.082 for the two statistics.
@@
 The cumulative changes account for a 59\% decrease in the mean CPU time and a halving of the initial variation.
-On average, the lensing prediction for a single lightcone can now be made in $57\pm8$.}
+On average, the lensing prediction for a single lightcone can now be made in $57\pm8$ ms.}
     \label{fig:cpu_plot}
@@
 A secondary goal of this research was to investigate how quickly the shear and convergence prediction for a single background source could be made.
-The mean CPU time required for the lensing prediction of a single lightcone with radius $R_L=6$ arcminutes was ${140\pm20}$ ms for the first run.
+The mean CPU time required for the lensing prediction of a single lightcone with radius $R_L=6$ arcminutes using all halos was ${140\pm20}$ ms for the first run.
 However, many small improvements to the coding infrastructure of \texttt{Pangloss} were made to speed up the prediction.
@@
 Both figures show that the lensing calculation requires an overhead of about ${55\pm10}$ ms, but then the calculation speed depends quadratically on the number of halos and logarithmically on the relevance limit.
-The runtime saved by using only the most relevant halos helps can only counteract the increase in runtime due to larger lightcones for so long before the desired correlation function NRMSE becomes too large, so accurate analysis with radii above $R_L=8$ arcminutes may only be feasible with parallelization.
-
-The distribution of total CPU time in significant parts of the lensing calculation for run 6 are as follows: 24.0\% of total time calculating individual halo convergence contributions where 14.4\% is spent in lensing lookup tables, 65.1\% of CPU time was spent combining all convergence contributions where 62.1\% is spent on the smooth-component correction, and the majority of the remaining time spent on writing the output \texttt{Astropy} columns.
-However, time spent accross all components of the lensing calculation was dominated by \texttt{Astropy} column use with nearly 55\% of total time spent initializing, copying, or summing columns.
+The runtime saved by using only the most relevant halos can only counteract the increase in runtime due to larger lightcones for so long before the desired correlation function NRMSE becomes too large, so accurate analysis with radii above $R_L=8$ arcminutes may only be feasible with parallelization.
+
+The distribution of total CPU time in significant parts of the lensing calculation for run 6 are as follows: 24.0\% of total time calculating individual halo convergence contributions where 14.4\% is spent in lensing table lookup functions, 65.1\% of CPU time was spent combining all convergence contributions where 62.1\% is spent on the smooth-component correction, and the majority of the remaining time spent on writing the output \texttt{Astropy} columns.
+However, time spent accross all components of the lensing calculation was dominated by \texttt{Astropy} column use with nearly 55\% of total time spent initializing, copying, or summing column elements.
 
@@
 The mean runtime scales quadratically with lightcone radius, and therefore halo count, with a overhead of about ${55\pm10}$ ms.
-Increasing the relevance limit to ${10^{-6}M_\odot\,\text{Mpc}^3}$, or about 300 relevant halos, decreases the mean runtime to near the minimum overhead.}
+Increasing the relevance limit to ${10^{-6}M_\odot/\text{Mpc}^3}$, or about 300 relevant halos, decreases the mean runtime to near the minimum overhead.}
     \label{fig:cpu_scaling}
@@
 As a first step towards this goal, I attempted to gague the feasibility of implementing two methods of parameter inference, maximum likelihood estimation and approximate Bayesian computation, using the current framework.
-The results of this feasibility test, particularly the CPU time per likelihood estimation, will help guide fugure work on \texttt{Pangloss}.
+The results of this feasibility test, particularly the CPU time per likelihood estimation, will help guide future work on \texttt{Pangloss}.
 For a detailed description of a probablistic modeling approach to gravitational lensing inference for large sky surveys, see \cite{hierarchial_inference}.
@@
 The likelihood is a function of the parameters of a statistical model that measures the probability of a data set or outcomes given the model parameters \cite{bayes_in_sky}.
-It is the mathematical answer to the question, ``\textit{Given a particular set of parameters, what is the probability that this data set could have occured?}" The form of the likelihood depends on the properties and circumstances of the data but generally has the form of the product of the probability density function $f$ of each individual observation $x_i$ given model parameters $\vec{\theta}$:
+It is the mathematical answer to the question, ``\textit{Given a particular set of parameters, what is the probability that this data set could have occured?}" The form of the likelihood depends on the properties and circumstances of the data, but generally has the form of the product of the probability density function $f$ of each individual observation $x_i$ given model parameters $\vec{\theta}$:
 \begin{equation}
@@
 
-\noindent where $\varepsilon_i,j$ is the $j$-component of the $i$-th predicted lensed galaxy ellipticity, $g_i,j$ is the $j$-th component of the `true' reduced shear corresponding to $\varepsilon_i$, $\chi^2$ is the typical test statistic
+\noindent where $\varepsilon_{i,j}$ is the $j$-component of the $i$-th predicted lensed galaxy ellipticity, $g_{i,j}$ is the $j$-th component of the `true' reduced shear corresponding to $\varepsilon_i$, $\chi^2$ is the typical test statistic
 \begin{equation}\label{chi2}
@@
 While this works in principle, computationally it is much easier to work with the natural logarithm of the likelihood function called the log-likelihood.
-As the logarithm is a monotonically increasing function, the likelihood and log-likelihood achieve their maximum at the same points and so can be used interchangably in maximum likelihood estimation.
-From Equations \eqref{likelihood}-\eqref{sigma} is follows that the log-likelihood is given by
+As the logarithm is a monotonically increasing function, the likelihood and log-likelihood achieve their maximum at the same points and so can be used interchangeably in maximum likelihood estimation.
+From Equations \eqref{likelihood}-\eqref{sigma} it follows that the log-likelihood is given by
 \begin{align}\label{log-likelihood}
@@
 While fortunately Equation \eqref{log-likelihood} is a relatively simple likelihood function, the calculation may become too costly for very large mock catalogs of millions or billions of source galaxies.
-However, ABC does come at a cost; as the name implies, there are various assumptions and approximations made in the process that can potentially lead to an innaccurate posterior prediction.
+However, ABC does come at a cost; as the name implies, there are various assumptions and approximations made in the process that can potentially lead to an inaccurate posterior prediction.
 See \cite{abc} for an excellent introduction to the topic.
@@
 
-A possible implemenetation of the above for \texttt{Pangloss} would be as follows: Choose the the ray-traced lensed ellipticities as the `observed' data and compute its $\varepsilon$-$\varepsilon$ correlation function to be used as the desired summary statistic.
+A possible implementation of the above for \texttt{Pangloss} would be as follows: Choose the the ray-traced lensed ellipticities as the `observed' data and compute its $\varepsilon$-$\varepsilon$ correlation function to be used as the desired summary statistic.
 Let the distance metric to be the NRMSE between the predicted and ray-traced $\varepsilon$-$\varepsilon$ correlation function.
@@
 
-I implemented the methodology in section \ref{pangloss} to make weakly lensed ellipticity predictions for 20 mock catalogs of $N$ background sources with lightcone radii of $R_L=4$ arcminutes for $N$ ranging from $N=10^2$ to $N=10^6$.
-The mean CPU times for a single likelihood calulation and ABC rejection decision as a function of $N$ is shown in Figure \ref{fig:mle_vs_abc}.
+I implemented the methodology in section \ref{pangloss} to make weakly lensed ellipticity predictions for 20 mock catalogs of $N$ background sources with lightcone radii of $R_L=4$ arcminutes for $N$ ranging from $N=10^2$ to $N=5\cdot10^6$.
+The mean CPU runtimes for a single likelihood calulation and ABC rejection decision as a function of $N$ is shown in Figure \ref{fig:mle_vs_abc}.
 The two methods take approximately the same amount of time up to $N=10^3$ sources, but the correlation function quickly becomes far too computationally inefficient at $N$ values above $10^4$.
 While further analysis is needed to determine whether more or less ABC samples are required than posterior samples from MLE, this result, as well as the limitation that ABC is fundamentally an approximation of the posterior, suggests that any future inference work will likely use MLE instead of ABC.
-However, the time spent for either inference method is quite small in comparison to the CPU time required to create lightcones and make the line-of-sight lensing predictions.
+However, the time spent for either inference method is quite small in comparison to the CPU time required to create lightcones and make the LOS lensing predictions.
 This is an encouraging result which de-emphasizes the choice of sampling method and suggests that further work on the framework should be on additional optimization of the lensing prediction code rather than posterior estimation.
@@
 A possible solution, briefly discussed in Section \ref{scc}, would be to model filaments as `cylinders' of dark matter attached to the most massive halos with densities, length distributions, and frequencies matching simulated data.
-This implementation might lead to better correlation predictions on large scales, but the details of the implementation, as well as analyzing how filaments affect line-of-sight lensing measurements, still needs to be explored.
+This implementation might lead to better correlation predictions on large scales, but the details of the implementation, as well as analyzing how filaments affect LOS lensing measurements, still needs to be explored.
 Stellar masses could also be incorporated into the \texttt{Pangloss} prediction but any effect would likely be dominated by the missing features described above.
-Resolving the overprediction of correlation on scales below 0.2 arcminutes in the galaxy-mass function is likely more straightforward as sources this close to the center of foreground mass are often in the strong lensing regime.
+Resolving the overprediction of correlation on scales below 0.2 arcminutes in the galaxy-mass function is likely more straightforward, as sources this close to the center of foreground masses are often in the strong lensing regime.
 \texttt{Pangloss} currently removes any sources with total reduced shear $g$ greater than 0.5, but this potentially leaves sources that are not entierly described by weak lensing.
-Correctly modeling line-of-sight strong lensing will require analyzing the convergence and shear contributions of BMO halos in the strong lening regime and at the interface between strong and weak lensing.
+Correctly modeling LOS strong lensing will require analyzing the convergence and shear contributions of BMO halos in the strong lening regime and at the interface between strong and weak lensing.
 
@@
 This will be of essential importance when making lensing predictions in fields of many square degrees that otherwise would be computationally infeasible.
-Figure \ref{fig:cpu_scaling} suggests that setting the relevance limit to ${10^{-6}M_\odot\,\text{Mpc}^3}$, or $~300$ relevant halos per lightcone, will decrease the mean CPU time per lightcone prediction to roughly the minimum overhead runtime of about 60 ms.
+Figure \ref{fig:cpu_scaling} suggests that setting the relevance limit to ${10^{-6}M_\odot/\text{Mpc}^3}$, or $~300$ relevant halos per lightcone, will decrease the mean CPU time per lightcone prediction to roughly the minimum overhead runtime of about 60 ms.
 According to Figure \ref{fig:halo_fraction}, this relevance limit will on average keep the $\varepsilon$-$\varepsilon$ and galaxy-mass correlation function NRMSE's at or below 5\%.
@@
 
-While the current \texttt{Pangloss} framework can handle the lensing predictions of 1440 sources in a 144 arcmin$^2$ field comfortably on a single processor, the goal is to scale up the framework to make predictions for background sources of the same number density in a 100 deg$^2$ field; this will require 3.6 million lightcones, each containing at least 300 relevant foreground halos for an estimated NRMSE of less than 5\%.
+While the current \texttt{Pangloss} framework can handle the lensing predictions of 1440 sources in a 144 arcmin$^2$ field comfortably on a single processor, the goal is to scale up the framework to make predictions for background sources of the same number density in a 100 deg$^2$ field; this will require 3.6 million lightcones, each containing at least 300 relevant foreground halos for an estimated $\varepsilon$-$\varepsilon$ NRMSE of less than 5\%.
 Luckily, the prediction is trivially parallelizable as the shear and convergence calculation of each lightcone is independent of all other lightcones.
@@
 However, the \texttt{Pangloss} code needs to be optimized before the parallelization will be efficient or even feasible.
-The breakdown of CPU time spent on various components of the lensing calculation in Section \ref{comp_perform} indicates that (1) the smooth-component correction needs to be implemented \textit{far} quicker as it is responsible for on average 62.1\% of the total runtime and (2) the current use of \texttt{Astropy} tables for data storage is not practical for fields much larger than 1,000 arcmin$^2$ or with lightcone radii larger than 8 arcminutes.
+The breakdown of CPU time spent on various components of the lensing calculation in Section \ref{comp_perform} indicates that (1) the smooth-component correction needs to be implemented \textit{far} more quickly as it is responsible for on average 62.1\% of the total runtime and (2) the current use of \texttt{Astropy} tables for data storage is not practical for fields much larger than 1,000 arcmin$^2$ or with lightcone radii larger than 8 arcminutes.
 Possible solutions to (1) are to experiment with faster numerical integrators or use a lookup table for appropriate parts of the calculation, while the second issue suggests that \texttt{Pangloss} should store catalog data in databases rather than \texttt{Astropy} tables as databases are designed for rapid retrieval, modification, and deletion of data \cite{databases}.
@@
 The results of Section \ref{feasibility} demonstrated that neither the likelihood nor correlation function computation present a significant computational issue in comparison to the lensing calculation, so either are feasible approaches for a hierarchial inference of the stellar mass - halo mass relation.
-As a single ABC rejection algorithm performed many orders of magnitude \textit{worse} than a single likelihood calculation for ${10^2\leq N\leq10^6}$ sources and ABC fundementally an approximation, it appears that the method is not suitable for this work unless ABC ends up requiring far less samples than the number of needed posterior samples in MLE.
+As a single ABC rejection algorithm performed many orders of magnitude \textit{worse} than a single likelihood calculation for ${10^2\leq N\leq5\cdot10^6}$ sources, and ABC fundementally an approximation, it appears that the method is not suitable for this work unless ABC ends up requiring far less samples than the number of needed posterior samples in MLE.
 However as discussed above and in Section \ref{inference_results}, there is still much more work to the \texttt{Pangloss} framework that needs to be done, both in modeling features and computational infastructure, before an inference using a large number of background sources comparable to modern sky surveys can be achieved.
@@
 
-\item Figure \ref{fig:halo_fraction} describes the fraction of relevant halos needed to reproduce the best-case correlation functions to a desired accuracy using the relevance metric given in Equation \eqref{relevant} derived by McCully et al.
+\item Figure \ref{fig:halo_fraction} describes the fraction of relevant halos needed to reproduce the best-case correlation functions to a desired accuracy using the relevance metric in Equation \eqref{relevant} derived by McCully et al.
 in \cite{mccully}.
-It suggests that, on average, the best-case correlation functions can be approximated to a NRMSE of less than 5\% or 10\% using a relevance limit of ${10^{-6}M_\odot\,\text{Mpc}^3}$, or $\sim300$ halos, and ${10^{-5}M_\odot\,\text{Mpc}^3}$, or $\sim70$ halos, respectively.
-This is an encouraging result as Figure \ref{fig:cpu_scaling} shows that the lensing prediction scales quadratically with the $R_l$ and thus halo number.
+It suggests that, on average, the best-case correlation functions can be approximated to a NRMSE of less than 5\% or 10\% using a relevance limit of ${10^{-6}M_\odot/\text{Mpc}^3}$, or $\sim300$ halos, and ${10^{-5}M_\odot/\text{Mpc}^3}$, or $\sim70$ halos, respectively.
+This is an encouraging result as Figure \ref{fig:cpu_scaling} shows that the lensing prediction scales quadratically with $R_L$ and thus halo number.
 Instead of using the many thousands of halos contained in each lightcone for radii above 4 arcminutes, only a few hundred are needed to reproduce the best-case summary statistics within a NRMSE of below 5\%.
@@
 
-\item The mean CPU time per likelihood evaluation and ABC decision for catalogs of background sources ranging from $10^2\leq N\leq10^6$ is shown in Figure \ref{fig:mle_vs_abc}.
+\item The mean CPU time per likelihood evaluation and ABC decision for catalogs of background sources ranging from $10^2\leq N\leq5\cdot10^6$ is shown in Figure \ref{fig:mle_vs_abc}.
 While the likelihood calculation outperformed the summary statistic calculation for all values of $N$, the main result is that neither computation took a significant amount of time relative to the lensing calculation for a given $N$.
@@
 I would like to thank the Department of Energy for funding this research and giving me the wonderful opportunity to meet so many talented peers from accross the country.
-This work was greatly aided by numerous conversations with Risa Wechsler from Stanford University and Matt Becker from the Kavli Institute for Particle Astrophysics and Cosmology (KIPAC), as well as Jesus Pando and Anuj Sarma from DePaul University.
+This work was greatly aided by numerous conversations with Risa Wechsler from Stanford University and Matthew Becker from the Kavli Institute for Particle Astrophysics and Cosmology (KIPAC), as well as Jesus Pando and Anuj Sarma from DePaul University.
 Additionally, I am sincerely appreciative of the many scientists, faculty, and graduate students at SLAC National Laboratory and Stanford University who continually welcomed a unknown undergraduate student who wanted to learn a little bit more about the universe.
@@
 In each plot, the value of the correlation between two galaxies as a function of their relative orientation is plotted as a colormap with a few sampled galaxy orientations superimposed.
-For $\xi_+$ the correlation is positive for parallel galaxies, negative for perpendicular galaxies, and zero for galaxies offset by 45$^\circ$.
+For $\xi_+$, the correlation is positive for parallel galaxies, negative for perpendicular galaxies, and zero for galaxies offset by 45$^\circ$.
 In contrast, $\xi_\times$ is zero for all parallel and perpendicular orientations while nonzero for most 45$^\circ$ offsets.
@@
 
-The first few steps are identical to the previous section besides the negative in the definition of $\xi_-$, giving
+The first few steps are identical to the previous section except for the minus sign in the definition of $\xi_-$, giving
 \begin{align*}

### 2016-06-06 tests/binmap_test.py

@@ -72,8 +72,8 @@ print 'Lightcones have {0:.2f} +/- {1:.2f} galaxies'.format(mean_galaxies,std_ga
 
 # Lens the background catalog by foreground halos
 if vb is True: print('Lensing background by halos..')
-#relevance_lim = 0.0
-relevance_lim = 10**-5
+relevance_lim = 0.0
+#relevance_lim = 10**-5
 B.lens_by_halos(relevance_lim=relevance_lim,lookup_table=True,smooth_corr=smooth_corr)
 print 'Lightcones have {0:.2f} +/- {1:.2f} relevant galaxies'.format(B.mean_relevant_halos,B.std_relevant_halos)
 

### 2016-06-06 tests/lens_compare.py

@@ -80,7 +80,7 @@ print 'Background catalog has',B.galaxy_count,'galaxies'
 
 # Drill the lightcones
 if vb is True: print('Drilling ligh7cones...')
-lc_radius = 7.0
+lc_radius = 2.0
 smooth_corr = True
 B.drill_lightcones(radius=lc_radius,foreground=F,save=False,smooth_corr=smooth_corr)
 
@@ -97,9 +97,9 @@ print 'Lightcones have {0:.2f} +/- {1:.2f} galaxies'.format(mean_galaxies,std_ga
 
 # Lens the background catalog by foreground halos
 if vb is True: print('Lensing background by halos..')
-relevance_lim = 0.0
+#relevance_lim = 0.0
 #relevance_lim = 0.00001
-#relevance_lim = 10**-7
+relevance_lim = 10**-5
 #cProfile.run('B.lens_by_halos(relevance_lim=relevance_lim,lookup_table=True,smooth_corr=smooth_corr); print')
 B.lens_by_halos(relevance_lim=relevance_lim,lookup_table=True,smooth_corr=smooth_corr)
 print 'Lightcones have {0:.2f} +/- {1:.2f} relevant galaxies'.format(B.mean_relevant_halos,B.std_relevant_halos)

### 2016-06-06 tests/mle_vs_abc.py

@@ -99,7 +99,7 @@ for i in range(T):
     # Calculate likelihood
     start_likelihood = timeit.default_timer()
     likelihood = B.calculate_log_likelihood(lensed='map')
-    cProfile.run('B.calculate_log_likelihood(lensed="map"); print')
+    #cProfile.run('B.calculate_log_likelihood(lensed="map"); print')
     B.calculate_log_likelihood(lensed='map')
     likelihood_time.append(timeit.default_timer() - start_likelihood)
     likelihood_total_time.append(timeit.default_timer() - start_time)

### 2016-09-07 doc/thesis_swe.tex

@@
 postulated in \cite{tyson_postulate} and confirmed in \cite{tyson_confirm}, background sources are also `weakly' lensed by lesser foreground mass nearby the line of sight (LOS) by what is now called galaxy-galaxy lensing.
-As the shape of most galaxies is only distorted by a few percent, and the instrinsic shape is not known, weak lensing must be detected statistically using a large number of sources.
+As the shape of most galaxies is only distorted by a few percent, and the intrinsic shape is not known, weak lensing must be detected statistically using a large number of sources.
 
@@
 Numerous N-body simulations have predicted dark matter structure to have evolved from overdense regions in the early universe into `halos' of virialized matter that eventually collapsed from self-gravity \cite{halo_formation}, where galaxies could then form in the large gravitational potentials of the halos.
-However, there is still extensive reserach being done on the correct density profile of the halos (isothermal spheres \cite{isothermal_spheres}, NFW \cite{nfw}, BMO \cite{nfw_bmo}, Einasto \cite{einasto}), identifying the stellar mass - halo mass relation \cite{smhr}, abundance matching \cite{abundance_matching}, halo substructure \cite{halo_substructure}, and the lensing by LOS halos \cite{collett} and by dark matter structures not associated with galaxies \cite{mccully}.
+However, there is still extensive research being done on the correct density profile of the halos (isothermal spheres \cite{isothermal_spheres}, NFW \cite{nfw}, BMO \cite{nfw_bmo}, Einasto \cite{einasto}), identifying the stellar mass - halo mass relation \cite{smhr}, abundance matching \cite{abundance_matching}, halo substructure \cite{halo_substructure}, and the lensing by LOS halos \cite{collett} and by dark matter structures not associated with galaxies \cite{mccully}.
 If a model for the distribution of dark matter in a region of foreground mass can accurately predict the statistical signal of the weak lensing of background sources, then the model can be used on galaxies in existing sky survey data to extrapolate the amount of dark matter in the region and construct large-scale maps of the dark matter in the universe.
@@
 \item How many halos are needed to make these predictions?
-\item How feasible is an inference of the Millennium Simulation's cosmological hyper-parameters, such as the stellar mass - halo mass relation, using all available halo data? 
+\item How feasible is an inference of the Millennium Simulation's cosmological hyperparameters, such as the stellar mass - halo mass relation, using all available halo data? 
 \item How long does such an inference take?
@@
 
-Before describing the developed model for LOS dark matter mass map reconstructions from weak lensing measurements, I briefely review a few topics in astronomy and cosmology that are relevant for this thesis such as the dark matter halo model, gravitational lensing, and correlation functions.
+Before describing the developed model for LOS dark matter mass map reconstructions from weak lensing measurements, I briefly review a few topics in astronomy and cosmology that are relevant for this thesis such as the dark matter halo model, gravitational lensing, and correlation functions.
 
@@
     \caption{A comparison of the galaxy and dark matter distribution for a single cluster in the Millennium Simulation.
-The galaxies tend to be located in the centers of clumps of dark matter called `halos', which suggests that galaxies at least partially trace out the underlying dark matter distribution.
+Galaxies tend to be located in the centers of clumps of dark matter called `halos', which suggests that galaxies at least partially trace out the underlying dark matter distribution.
 Taken from \cite{ms_figures}.}
@@
 The simplest way to model the relationship between galaxies and dark matter is by enveloping each galaxy in a spherically symmetric dark matter `halo' of a certain mass $M_h$.
-These halos extend far beyond the edge of the visible galaxy that they enclose, with the Milky Way's own halo estimated to have a radius of between 300,000 and 400,000 light-yeras \cite{milky_way_halo}.
+These halos extend far beyond the edge of the visible galaxy that they enclose, with the Milky Way's own halo estimated to have a radius of between 300,000 and 400,000 light-years \cite{milky_way_halo}.
 While the density profile of the halos may be complex, numerous simulations have shown that it can be well approximated locally by the Navarro-Frenk-White (NFW) profile which has the form
@@
 \noindent where the constant $\rho_0$ and the scale radius $R_s$ are parameters that vary from halo to halo \cite{nfw}.
-However, the NFW profile is not entierly physical as the total mass diverges as the density is integrated out to an infinite radius.
+However, the NFW profile is not entirely physical as the total mass diverges as the density is integrated out to an infinite radius.
 Instead, this work uses a truncated NFW profile called the Baltz-Marshall-Oguri (BMO) profile given by
@@
 However, this neglects other mass structures such as the filaments and voids that can be seen in Figure \ref{fig:ms_structure}.
-Modelling these features accurately would be difficult; we could try, for example, to model filaments by attaching cylinders of dark matter between massive clusters of galaxies.
+Modeling these features accurately would be difficult; we could try, for example, to model filaments by attaching cylinders of dark matter between massive clusters of galaxies.
 While an intriguing idea, rigorously testing for the appropriate filament density distributions, selection criteria, and frequency to statistically match simulations could constitute its own thesis.
@@
 
-To solve for the desired smooth-component correction, we first need to calcualte ${\rho_m(z)}$ and ${\rho_h(z)}$ and then subtract:
+To solve for the desired smooth-component correction, we first need to calculate ${\rho_m(z)}$ and ${\rho_h(z)}$ and then subtract:
 \begin{equation}\label{smooth_correction2}
@@
 The presence of matter curves spacetime locally which causes light to follow curved paths called geodesics.
-The deviation in path is usually negligable, but can be significant in regions containing clusters of galaxies and their massive dark matter halos.
-By observing how the magnitudes and shapes of distant galaxies are distorted when travelling through regions of matter, we can infer the masses of the dark matter halos and reconstruct the hidden dark matter mass distribution.
+The deviation in path is usually negligible, but can be significant in regions containing clusters of galaxies and their massive dark matter halos.
+By observing how the magnitudes and shapes of distant galaxies are distorted when traveling through regions of matter, we can infer the masses of the dark matter halos and reconstruct the hidden dark matter mass distribution.
 %A simplified cartoon of this process is shown in Figure \ref{fig:lens_diagram}.
@@
     \caption{The mean number of relevant halos in a single realization of 1440 source galaxies, each with ${4836\pm104}$ halos per lightcone, determined by Equation \eqref{relevant_thresh} with a threshold mass and distance of ${M_T=10^{12}M_\odot}$ and ${R_T=10}$ kpc respectively.
-The errorbars correspond to the standard deviation of relevant halos accross all lightcones.
+The error bars correspond to the standard deviation of relevant halos across all lightcones.
 As expected, most halos are either too far away from the LOS or not massive enough to make a significant contribution, or both.
@@
 In most redshift bins, the halo density is one to two orders of magnitude lower than than the universe mean density leading to a smooth-component density very close to that of the mean density.
-However, all mass densities are far below the critial density, plotted in red, and so well within the weak-lensing regime.
+However, all mass densities are far below the critical density, plotted in red, and so well within the weak-lensing regime.
 The convergence distribution of each halo and the 100 smooth-components is plotted in Figure \ref{fig:kappa_dist}.
@@
 The number of halos in each redshift bin is plotted as a histogram in the background.
-The red line in plot (b) is the ciritical surface density.}
+The red line in plot (b) is the critical surface density.}
     \label{densities}
@@
     \captionsetup{justification=raggedright,singlelinecheck=false}
-    \caption{Four different views of a lightcone centered on the LOS of a particular background source.
+    \caption{Four different views of a lightcone with radius $R_L=6$ arcminutes centered on the LOS of a particular background source containing 4829 halos.
 The top left figure plots the positions of the halos with the size proportional to their galaxy brightness in the $i$-band, the center figure plots the angular size of foreground halos with red and blue regions representing the NFW scale radius and virial radius of each halo respectively, the top right figure plots the $\kappa$ contributions of each halo, and the bottom plots the positions of each halo along the redshift axis with size proportional to $\kappa$ contribution.}
@@
 Comparing the center and top right figures demonstrates the importance of proximity to the LOS for significant $\kappa$ contributions.
-Figure \ref{fig:field2} shows a foreground cluster in a 1.44 arcmin$^2$ section of the Millennium Simulation along with the ray-traced convergence (plotted in inverse greyscale) and shear maps (plotted as red shear sticks) from \cite{ray_tracing}.
+Figure \ref{fig:field2} shows a foreground cluster in a 1.44 arcmin$^2$ section of the Millennium Simulation along with the ray-traced convergence (plotted in inverse grayscale) and shear maps (plotted as red shear sticks) from \cite{ray_tracing}.
 Figure \ref{fig:field3} displays the generated background ellipticities in blue, the `true' lensed ellipticities in green, and the halo model lensed ellipticities in purple.
@@
         \caption{The ray-traced convergence and shear in a 1.44 arcmin$^2$ field of the Millennium Simulation, as calculated from \cite{ray_tracing}.
-The convergence, plotted in inverse greyscale, is proportional to the projected mass density and representes foreground mass.
+The convergence, plotted in inverse grayscale, is proportional to the projected mass density and represents foreground mass.
 The shear field is plotted as sparsely-sampled red sticks that have size proportional to their magnitude.
-A few of the generated background sources are plotted as blue ellipticitiy sticks with length proportional to their eccentricities.}
+A few of the generated background sources are plotted as blue ellipticity sticks with length proportional to their eccentricities.}
         \label{fig:field2}
@@
         \caption{The $\varepsilon$-$\varepsilon$ correlation function for 1440 sources at separation distances from 0.1 to 2 arcminutes using lightcones with radii of $R_L=6$ arcminutes, where green is the `true' ray-traced correlation and purple is the halo model predicted correlation.
-While the cross-component $\xi_\times(\Delta\theta)$ for both is consistent with zero accross all scales as expected, the halo model systematically underpredicts the correlation on scales larger than 0.2 arcminutes.}
+While the cross-component $\xi_\times(\Delta\theta)$ for both is consistent with zero across all scales as expected, the halo model systematically underpredicts the correlation on scales larger than 0.2 arcminutes.}
         \label{fig:gg_corr}
@@
 The cross-component of the correlation function $\xi_\times$ shows no significant deviation from zero as expected, as gravitational lensing only shears galaxies tangentially.
-For the $\xi_+$ component, the ray-traced (plotted in green) and halo model (plotted in purple) are in relative agreement from seperation scales of 0.1 to 0.2 arcminutes, but there is a systematic underprediction of correlation by the halo model on scales larger than 0.2 arcminutes by an average 31\% percent error.
+For the $\xi_+$ component, the ray-traced (plotted in green) and halo model (plotted in purple) are in relative agreement from separation scales of 0.1 to 0.2 arcminutes, but there is a systematic underprediction of correlation by the halo model on scales larger than 0.2 arcminutes by an average 31\% error.
 This result is consistent with Pace et al.
@@
 As with the $\varepsilon$-$\varepsilon$ correlation, structure larger than $\sim$1 arcminute is captured much better by increasingly large lightcone radii as expected.
-However, there is little to no improvement of the galaxy-mass correlation on scales smaller than 0.3 arcminutes which futher points to the need to model strong lensing.
+However, there is little to no improvement of the galaxy-mass correlation on scales smaller than 0.3 arcminutes which further points to the need to model strong lensing.
 
@@
 This was done by selecting a region of foreground mass, calculating the ray-traced and \texttt{Pangloss}-predicted convergence of a uniform grid of background sources in the field, and binning the convergence maps to a desired resolution.
-Convergence is proportional to projected surface mass density, so comparing the two convergence maps is equivalent to comparing their respecitve projected mass distributions.
+Convergence is proportional to projected surface mass density, so comparing the two convergence maps is equivalent to comparing their respective projected mass distributions.
 
@@
     \captionsetup{justification=raggedright,singlelinecheck=false}
-    \caption{The mean CPU runtime per lightcone for various runs with different (and cumulative) code optimizations described in Section \ref{comp_perform}.
+    \caption{The mean CPU runtime per lightcone with radius $R_L=6$ arcminutes for various runs with different (and cumulative) code optimizations described in Section \ref{comp_perform}.
 The cumulative changes account for a 59\% decrease in the mean CPU time and a halving of the initial variation.
@@
 The distribution of total CPU time in significant parts of the lensing calculation for run 6 are as follows: 24.0\% of total time calculating individual halo convergence contributions where 14.4\% is spent in lensing table lookup functions, 65.1\% of CPU time was spent combining all convergence contributions where 62.1\% is spent on the smooth-component correction, and the majority of the remaining time spent on writing the output \texttt{Astropy} columns.
-However, time spent accross all components of the lensing calculation was dominated by \texttt{Astropy} column use with nearly 55\% of total time spent initializing, copying, or summing column elements.
+However, time spent across all components of the lensing calculation was dominated by \texttt{Astropy} column use with nearly 55\% of total time spent initializing, copying, or summing column elements.
 
@@
 
-One of the long-term goals of \texttt{Pangloss} is to be able to use all available sky survey data (sky positions, stellar masses, magnitude, photometric redshift, ellipticities, etc.) to make a hierarchial inference of the Universe's cosmological and galaxy population model hyper-parameters such as the density paramters $\Omega_m$ and $\Omega_\Lambda$, the Hubble constant $H_0$, and stellar mass - halo mass relation \cite{smhr}.
+One of the long-term goals of \texttt{Pangloss} is to be able to use all available sky survey data (sky positions, stellar masses, magnitude, photometric redshift, ellipticities, etc.) to make a hierarchical inference of the Universe's cosmological and galaxy population model hyperparameters such as the density parameters $\Omega_m$ and $\Omega_\Lambda$, the Hubble constant $H_0$, and stellar mass - halo mass relation \cite{smhr}.
 This is a large undertaking and will require considerable testing and calibration on large N-body simulations such as the Millennium Simulation.
-As a first step towards this goal, I attempted to gague the feasibility of implementing two methods of parameter inference, maximum likelihood estimation and approximate Bayesian computation, using the current framework.
+As a first step towards this goal, I attempted to gauge the feasibility of implementing two methods of parameter inference, maximum likelihood estimation and approximate Bayesian computation, using the current framework.
 The results of this feasibility test, particularly the CPU time per likelihood estimation, will help guide future work on \texttt{Pangloss}.
-For a detailed description of a probablistic modeling approach to gravitational lensing inference for large sky surveys, see \cite{hierarchial_inference}.
-Exploratory notes of implementing such an inference in the framework is available on \texttt{Pangloss}'s public github repository\footnote{https://github.com/drphilmarshall/Pangloss/issues/23}.\\
+For a detailed description of a probablistic modeling approach to gravitational lensing inference for large sky surveys, see \cite{hierarchical_inference}.
+Exploratory notes of implementing such an inference in the framework is available on \texttt{Pangloss}'s public GitHub repository\footnote{https://github.com/drphilmarshall/Pangloss/issues/23}.\\
 
@@
 The likelihood is a function of the parameters of a statistical model that measures the probability of a data set or outcomes given the model parameters \cite{bayes_in_sky}.
-It is the mathematical answer to the question, ``\textit{Given a particular set of parameters, what is the probability that this data set could have occured?}" The form of the likelihood depends on the properties and circumstances of the data, but generally has the form of the product of the probability density function $f$ of each individual observation $x_i$ given model parameters $\vec{\theta}$:
+It is the mathematical answer to the question, ``\textit{Given a particular set of parameters, what is the probability that this data set could have occurred?}" The form of the likelihood depends on the properties and circumstances of the data, but generally has the form of the product of the probability density function $f$ of each individual observation $x_i$ given model parameters $\vec{\theta}$:
 \begin{equation}
@@
 \ln\mathcal{L}&=-\ln Z_L-\frac{1}{2}\chi^2\nonumber \\
-&=-\frac{N}{2}\ln(2\pi\sigma)-\frac{1}{2}\sum_{i=1}^N\sum_{j=1}^2\frac{(\varepsilon_{i,j}-g_{i,j})^2}{\sigma^2}.
+&=-N\ln(2\pi\sigma)-\frac{1}{2}\sum_{i=1}^N\sum_{j=1}^2\frac{(\varepsilon_{i,j}-g_{i,j})^2}{\sigma^2}.
 \end{align}
@@
 halo masses).
-For this thesis, I only compute the log-likelihood for a small handful of parameter sets to gague how feasible such an inference would be in future work with far more computational power.
+For this thesis, I only compute the log-likelihood for a small handful of parameter sets to gauge how feasible such an inference would be in future work with far more computational power.
 
@@
 ${\delta=2\cdot\text{NRMSE}_{\text{best-case}}}$).
-Create mock data by repeating the methodology in \ref{pangloss} except use the stellar mass - halo mass relation, dependent on paramters we sample from a prior, to predict halo masses based upon each galaxy's stellar mass.
+Create mock data by repeating the methodology in \ref{pangloss} except use the stellar mass - halo mass relation, dependent on parameters we sample from a prior, to predict halo masses based upon each galaxy's stellar mass.
 Compute the simulated $\varepsilon$-$\varepsilon$ correlation function and determine whether to accept or reject the data by determining if the NRMSE is below the threshold $\delta$.
@@
 I implemented the methodology in section \ref{pangloss} to make weakly lensed ellipticity predictions for 20 mock catalogs of $N$ background sources with lightcone radii of $R_L=4$ arcminutes for $N$ ranging from $N=10^2$ to $N=5\cdot10^6$.
-The mean CPU runtimes for a single likelihood calulation and ABC rejection decision as a function of $N$ is shown in Figure \ref{fig:mle_vs_abc}.
+The mean CPU runtimes for a single likelihood calculation and ABC rejection decision as a function of $N$ is shown in Figure \ref{fig:mle_vs_abc}.
 The two methods take approximately the same amount of time up to $N=10^3$ sources, but the correlation function quickly becomes far too computationally inefficient at $N$ values above $10^4$.
@@
 The systematic underprediction of correlation on scales larger than 0.2 arcminutes in the $\varepsilon$-$\varepsilon$ function indicates that larger structures like filaments and voids are not being fully captured by the halo model.
-This is not entierly surprising as the only structure beyond halos accounted for in the presented model was the smooth-component correction which only adds sheets of uniform mass; clearly a better model of filaments and voids is needed to make accurate correlation predictions on scales larger than $\sim$1 arcminute.
+This is not entirely surprising as the only structure beyond halos accounted for in the presented model was the smooth-component correction which only adds sheets of uniform mass; clearly a better model of filaments and voids is needed to make accurate correlation predictions on scales larger than $\sim$1 arcminute.
 The progression of model predicted ellipticity-ellipticity correlation functions at larger radii converging to the ray-traced correlation in Figure \ref{fig:gg_corr_series} supports this analysis as the prediction was progressively better with larger number of foreground halos and thus more mass and structure.
@@
 Resolving the overprediction of correlation on scales below 0.2 arcminutes in the galaxy-mass function is likely more straightforward, as sources this close to the center of foreground masses are often in the strong lensing regime.
-\texttt{Pangloss} currently removes any sources with total reduced shear $g$ greater than 0.5, but this potentially leaves sources that are not entierly described by weak lensing.
-Correctly modeling LOS strong lensing will require analyzing the convergence and shear contributions of BMO halos in the strong lening regime and at the interface between strong and weak lensing.
+\texttt{Pangloss} currently removes any sources with total reduced shear $g$ greater than 0.5, but this potentially leaves sources that are not entirely described by weak lensing.
+Correctly modeling LOS strong lensing will require analyzing the convergence and shear contributions of BMO halos in the strong lensing regime and at the interface between strong and weak lensing.
 
@@
 Figure \ref{fig:cpu_scaling} suggests that setting the relevance limit to ${10^{-6}M_\odot/\text{Mpc}^3}$, or $~300$ relevant halos per lightcone, will decrease the mean CPU time per lightcone prediction to roughly the minimum overhead runtime of about 60 ms.
-According to Figure \ref{fig:halo_fraction}, this relevance limit will on average keep the $\varepsilon$-$\varepsilon$ and galaxy-mass correlation function NRMSE's at or below 5\%.
+According to Figure \ref{fig:halo_fraction}, this relevance limit will on average keep the $\varepsilon$-$\varepsilon$ and galaxy-mass correlation function's NRMSE at or below 5\%.
 These two figures can be used in this way to decide what relevance limit is appropriate for the desired tradeoff between mean runtime speed and correlation function accuracy.
@@
 
-The results of Section \ref{feasibility} demonstrated that neither the likelihood nor correlation function computation present a significant computational issue in comparison to the lensing calculation, so either are feasible approaches for a hierarchial inference of the stellar mass - halo mass relation.
-As a single ABC rejection algorithm performed many orders of magnitude \textit{worse} than a single likelihood calculation for ${10^2\leq N\leq5\cdot10^6}$ sources, and ABC fundementally an approximation, it appears that the method is not suitable for this work unless ABC ends up requiring far less samples than the number of needed posterior samples in MLE.
-However as discussed above and in Section \ref{inference_results}, there is still much more work to the \texttt{Pangloss} framework that needs to be done, both in modeling features and computational infastructure, before an inference using a large number of background sources comparable to modern sky surveys can be achieved.
+The results of Section \ref{feasibility} demonstrated that neither the likelihood nor correlation function computation present a significant computational issue in comparison to the lensing calculation, so either are feasible approaches for a hierarchical inference of the stellar mass - halo mass relation.
+As a single ABC rejection algorithm performed many orders of magnitude \textit{worse} than a single likelihood calculation for ${10^2\leq N\leq5\cdot10^6}$ sources, and ABC fundamentally an approximation, it appears that the method is not suitable for this work unless ABC ends up requiring far less samples than the number of needed posterior samples in MLE.
+However as discussed above and in Section \ref{inference_results}, there is still much more work to the \texttt{Pangloss} framework that needs to be done, both in modeling features and computational infrastructure, before an inference using a large number of background sources comparable to modern sky surveys can be achieved.
 
@@
 
-Now that a proof of concept has been demonstrated, work can be done to scale up the \texttt{Pangloss} framework to make lensing predictions of sources accross 100 deg$^2$ after implementing the suggested computational and model improvements.
+Now that a proof of concept has been demonstrated, work can be done to scale up the \texttt{Pangloss} framework to make lensing predictions of sources across 100 deg$^2$ after implementing the suggested computational and model improvements.
 While the results are encouraging for a toy model, many strong and unrealistic assumptions were made in the methodology that limit its use in observational surveys.
@@
 
-I would like to thank the Department of Energy for funding this research and giving me the wonderful opportunity to meet so many talented peers from accross the country.
+I would like to thank the Department of Energy for funding this research and giving me the wonderful opportunity to meet so many talented peers from across the country.
 This work was greatly aided by numerous conversations with Risa Wechsler from Stanford University and Matthew Becker from the Kavli Institute for Particle Astrophysics and Cosmology (KIPAC), as well as Jesus Pando and Anuj Sarma from DePaul University.
@@
 The $\xi_+$ component of the $\varepsilon$-$\varepsilon$ correlation function is simply the average of this scatter plot binned in separation distances along the $x$-axis.
-As the scatter is randomly distributed around zero, the $\varepsilon$-$\varepsilon$ correlation function for un-lensed sources should be zero on all scales.
-
-%% Color-Coded Correlation Un-lensed
+As the scatter is randomly distributed around zero, the $\varepsilon$-$\varepsilon$ correlation function for unlensed sources should be zero on all scales.
+
+%% Color-Coded Correlation Unlensed
 \begin{figure}
@@
     % \label{colored_corr_lensed}
-    % \caption{Correlation visualization for un-lensed galaxies.}
+    % \caption{Correlation visualization for unlensed galaxies.}
     \label{colored_corr}
@@
 The definition for the shear-shear (or equivalently, in the case of weak lensing, ellipticity-ellipticity) correlation function components in Mike Jarvis's \texttt{TreeCorr} package is different from the common definition given in Equation \eqref{gg_corr_def} from Schneider \cite{schneider}.
-For the aid of those who wish to use this very useful package but still use the conventional correlation function defintion, I have outlined the connection between the two definitions and the outputs of \texttt{TreeCorr} below:
+For the aid of those who wish to use this very useful package but still use the conventional correlation function definition, I have outlined the connection between the two definitions and the outputs of \texttt{TreeCorr} below:
 
@@
 
-\begin{align*}
-\xi_+&=\left<\frac{1}{4}\left[(\gamma_i+\gamma_i^*)(\gamma_j+\gamma_j^*)-(\gamma_i-\gamma_i^*)(\gamma_j-\gamma_j^*)\right]\right>\\
-&=\left<\frac{1}{2}\left[\gamma_i\gamma_j^*+(\gamma_i\gamma_j^*)^*\right]\right>\\
+\begin{align}
+\xi_+&=\left<\frac{1}{4}\left[(\gamma_i+\gamma_i^*)(\gamma_j+\gamma_j^*)-(\gamma_i-\gamma_i^*)(\gamma_j-\gamma_j^*)\right]\right>\nonumber \\
+&=\left<\frac{1}{2}\left[\gamma_i\gamma_j^*+(\gamma_i\gamma_j^*)^*\right]\right>\nonumber \\
 &=\left<\operatorname{Re}(\gamma_i\gamma_j^*)\right>=\texttt{xip}.
-\end{align*}
+\end{align}
 
@@
 
-$$\operatorname{Re}(a\cdot b^*)=\operatorname{Re}(a)\cdot\operatorname{Re}(b)+\operatorname{Im}(a)\cdot\operatorname{Im}(b).$$
+\begin{equation}
+\operatorname{Re}(a\cdot b^*)=\operatorname{Re}(a)\cdot\operatorname{Re}(b)+\operatorname{Im}(a)\cdot\operatorname{Im}(b).
+\end{equation}
 
@@
 
-$$\xi_-=\big<\operatorname{Re}(\gamma_i\gamma_j)\cos(4\alpha)+\operatorname{Im}(\gamma_i\gamma_j)\sin(4\alpha)\big>=\left<\operatorname{Re}\left(\gamma_i\gamma_je^{-4i\alpha}\right)\right>=\texttt{xim}.$$
+\begin{equation}
+\xi_-=\big<\operatorname{Re}(\gamma_i\gamma_j)\cos(4\alpha)+\operatorname{Im}(\gamma_i\gamma_j)\sin(4\alpha)\big>=\left<\operatorname{Re}\left(\gamma_i\gamma_je^{-4i\alpha}\right)\right>=\texttt{xim}.
+\end{equation}
 
@@
 
-$$\operatorname{Im}(a\cdot b^*)=\operatorname{Im}(a)\cdot\operatorname{Re}(b)-\operatorname{Re}(a)\cdot\operatorname{Im}(b).$$
+\begin{equation}
+\operatorname{Im}(a\cdot b^*)=\operatorname{Im}(a)\cdot\operatorname{Re}(b)-\operatorname{Re}(a)\cdot\operatorname{Im}(b).
+\end{equation}
 
@@
 
-\begin{align*}
-\xi_\times&=\left<\frac{1}{2}\big[\operatorname{Im}(\gamma_i\gamma_j)\cos(4\alpha)-\operatorname{Re}(\gamma_i\gamma_j)\sin(4\alpha)-\operatorname{Im}(\gamma_i\gamma_j^*)\big]\right>\\
-&=\left<\frac{1}{2}\big[\operatorname{Im}\left(\gamma_i\gamma_je^{-4i\alpha}\right)-\operatorname{Im}(\gamma_i\gamma_j^*)\big]\right>\\
+\begin{align}
+\xi_\times&=\left<\frac{1}{2}\big[\operatorname{Im}(\gamma_i\gamma_j)\cos(4\alpha)-\operatorname{Re}(\gamma_i\gamma_j)\sin(4\alpha)-\operatorname{Im}(\gamma_i\gamma_j^*)\big]\right>\nonumber \\
+&=\left<\frac{1}{2}\big[\operatorname{Im}\left(\gamma_i\gamma_je^{-4i\alpha}\right)-\operatorname{Im}(\gamma_i\gamma_j^*)\big]\right>\nonumber \\
 &=\frac{1}{2}\big[\texttt{xim\_im}-\texttt{xip\_im}\big].
-\end{align*}
+\end{align}
 
